### 2020-04-09 rR.tex
initial push

% Created by tikzDevice version 0.12.3 on 2020-04-09 01:19:07
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,433.62);
\begin{scope}
\path[clip] (  0.00,216.81) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,216.81) rectangle (289.08,433.62);
\end{scope}
\begin{scope}
\path[clip] ( 27.31,247.50) rectangle (283.58,410.96);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.31,247.50) rectangle (283.58,410.96);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 35.86,249.99) --
	( 38.99,250.83) --
	( 42.13,251.68) --
	( 45.26,252.56) --
	( 48.40,253.45) --
	( 51.53,254.37) --
	( 54.67,255.30) --
	( 57.81,256.26) --
	( 60.94,257.23) --
	( 64.08,258.23) --
	( 67.21,259.24) --
	( 70.35,260.28) --
	( 73.48,261.33) --
	( 76.62,262.40) --
	( 79.76,263.50) --
	( 82.89,264.61) --
	( 86.03,265.75) --
	( 89.16,266.90) --
	( 92.30,268.08) --
	( 95.43,269.28) --
	( 98.57,270.49) --
	(101.71,271.73) --
	(104.84,272.98) --
	(107.98,274.24) --
	(111.11,275.53) --
	(114.25,276.84) --
	(117.39,278.17) --
	(120.52,279.52) --
	(123.66,280.90) --
	(126.79,282.30) --
	(129.93,283.73) --
	(133.06,285.18) --
	(136.20,286.64) --
	(139.34,288.13) --
	(142.47,289.63) --
	(145.61,291.16) --
	(148.74,292.71) --
	(151.88,294.29) --
	(155.01,295.91) --
	(158.15,297.56) --
	(161.29,299.22) --
	(164.42,300.90) --
	(167.56,302.61) --
	(170.69,304.34) --
	(173.83,306.09) --
	(176.96,307.87) --
	(180.10,309.69) --
	(183.24,311.54) --
	(186.37,313.42) --
	(189.51,315.35) --
	(192.64,317.30) --
	(195.78,319.28) --
	(198.91,321.29) --
	(202.05,323.33) --
	(205.19,325.39) --
	(208.32,327.49) --
	(211.46,329.62) --
	(214.59,331.79) --
	(217.73,334.00) --
	(220.86,336.24) --
	(224.00,338.53) --
	(227.14,340.85) --
	(230.27,343.21) --
	(233.41,345.59) --
	(236.54,348.02) --
	(239.68,350.47) --
	(242.82,352.96) --
	(245.95,355.49) --
	(249.09,358.05) --
	(252.22,360.64) --
	(255.36,363.27) --
	(258.49,365.94) --
	(261.63,368.64) --
	(264.77,371.37) --
	(267.90,374.15) --
	(271.04,376.95) --
	(274.17,379.79) --
	(277.31,382.67) --
	(280.44,385.58) --
	(283.58,388.52);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 35.86,249.94) --
	( 38.99,250.75) --
	( 42.13,251.59) --
	( 45.26,252.45) --
	( 48.40,253.32) --
	( 51.53,254.22) --
	( 54.67,255.14) --
	( 57.81,256.08) --
	( 60.94,257.04) --
	( 64.08,258.02) --
	( 67.21,259.02) --
	( 70.35,260.04) --
	( 73.48,261.08) --
	( 76.62,262.14) --
	( 79.76,263.22) --
	( 82.89,264.33) --
	( 86.03,265.45) --
	( 89.16,266.60) --
	( 92.30,267.77) --
	( 95.43,268.96) --
	( 98.57,270.16) --
	(101.71,271.39) --
	(104.84,272.63) --
	(107.98,273.89) --
	(111.11,275.17) --
	(114.25,276.47) --
	(117.39,277.79) --
	(120.52,279.14) --
	(123.66,280.51) --
	(126.79,281.91) --
	(129.93,283.34) --
	(133.06,284.79) --
	(136.20,286.25) --
	(139.34,287.72) --
	(142.47,289.22) --
	(145.61,290.74) --
	(148.74,292.29) --
	(151.88,293.88) --
	(155.01,295.51) --
	(158.15,297.16) --
	(161.29,298.84) --
	(164.42,300.53) --
	(167.56,302.25) --
	(170.69,303.99) --
	(173.83,305.76) --
	(176.96,307.57) --
	(180.10,309.41) --
	(183.24,311.28) --
	(186.37,313.20) --
	(189.51,315.16) --
	(192.64,317.16) --
	(195.78,319.19) --
	(198.91,321.24) --
	(202.05,323.33) --
	(205.19,325.45) --
	(208.32,327.61) --
	(211.46,329.80) --
	(214.59,332.03) --
	(217.73,334.31) --
	(220.86,336.63) --
	(224.00,339.00) --
	(227.14,341.41) --
	(230.27,343.86) --
	(233.41,346.34) --
	(236.54,348.86) --
	(239.68,351.42) --
	(242.82,354.02) --
	(245.95,356.66) --
	(249.09,359.33) --
	(252.22,362.05) --
	(255.36,364.80) --
	(258.49,367.59) --
	(261.63,370.43) --
	(264.77,373.30) --
	(267.90,376.22) --
	(271.04,379.17) --
	(274.17,382.16) --
	(277.31,385.19) --
	(280.44,388.26) --
	(283.58,391.37);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.86,249.92) --
	( 38.99,250.73) --
	( 42.13,251.56) --
	( 45.26,252.41) --
	( 48.40,253.28) --
	( 51.53,254.17) --
	( 54.67,255.09) --
	( 57.81,256.02) --
	( 60.94,256.97) --
	( 64.08,257.95) --
	( 67.21,258.94) --
	( 70.35,259.96) --
	( 73.48,260.99) --
	( 76.62,262.05) --
	( 79.76,263.13) --
	( 82.89,264.23) --
	( 86.03,265.35) --
	( 89.16,266.49) --
	( 92.30,267.65) --
	( 95.43,268.84) --
	( 98.57,270.04) --
	(101.71,271.26) --
	(104.84,272.50) --
	(107.98,273.76) --
	(111.11,275.03) --
	(114.25,276.33) --
	(117.39,277.65) --
	(120.52,279.00) --
	(123.66,280.37) --
	(126.79,281.76) --
	(129.93,283.19) --
	(133.06,284.64) --
	(136.20,286.09) --
	(139.34,287.56) --
	(142.47,289.06) --
	(145.61,290.58) --
	(148.74,292.13) --
	(151.88,293.72) --
	(155.01,295.35) --
	(158.15,297.01) --
	(161.29,298.68) --
	(164.42,300.38) --
	(167.56,302.10) --
	(170.69,303.84) --
	(173.83,305.62) --
	(176.96,307.42) --
	(180.10,309.27) --
	(183.24,311.15) --
	(186.37,313.08) --
	(189.51,315.05) --
	(192.64,317.07) --
	(195.78,319.11) --
	(198.91,321.18) --
	(202.05,323.28) --
	(205.19,325.42) --
	(208.32,327.59) --
	(211.46,329.81) --
	(214.59,332.07) --
	(217.73,334.37) --
	(220.86,336.72) --
	(224.00,339.12) --
	(227.14,341.56) --
	(230.27,344.04) --
	(233.41,346.57) --
	(236.54,349.13) --
	(239.68,351.73) --
	(242.82,354.37) --
	(245.95,357.05) --
	(249.09,359.77) --
	(252.22,362.53) --
	(255.36,365.34) --
	(258.49,368.19) --
	(261.63,371.07) --
	(264.77,374.01) --
	(267.90,376.98) --
	(271.04,379.99) --
	(274.17,383.04) --
	(277.31,386.14) --
	(280.44,389.27) --
	(283.58,392.45);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 35.86,249.92) --
	( 38.99,250.74) --
	( 42.13,251.58) --
	( 45.26,252.44) --
	( 48.40,253.32) --
	( 51.53,254.22) --
	( 54.67,255.14) --
	( 57.81,256.08) --
	( 60.94,257.05) --
	( 64.08,258.03) --
	( 67.21,259.03) --
	( 70.35,260.05) --
	( 73.48,261.10) --
	( 76.62,262.16) --
	( 79.76,263.24) --
	( 82.89,264.35) --
	( 86.03,265.47) --
	( 89.16,266.62) --
	( 92.30,267.79) --
	( 95.43,268.98) --
	( 98.57,270.19) --
	(101.71,271.41) --
	(104.84,272.65) --
	(107.98,273.91) --
	(111.11,275.19) --
	(114.25,276.49) --
	(117.39,277.81) --
	(120.52,279.16) --
	(123.66,280.53) --
	(126.79,281.93) --
	(129.93,283.35) --
	(133.06,284.80) --
	(136.20,286.25) --
	(139.34,287.72) --
	(142.47,289.22) --
	(145.61,290.73) --
	(148.74,292.28) --
	(151.88,293.87) --
	(155.01,295.49) --
	(158.15,297.14) --
	(161.29,298.82) --
	(164.42,300.51) --
	(167.56,302.22) --
	(170.69,303.95) --
	(173.83,305.72) --
	(176.96,307.52) --
	(180.10,309.35) --
	(183.24,311.23) --
	(186.37,313.14) --
	(189.51,315.11) --
	(192.64,317.11) --
	(195.78,319.14) --
	(198.91,321.20) --
	(202.05,323.29) --
	(205.19,325.41) --
	(208.32,327.58) --
	(211.46,329.78) --
	(214.59,332.02) --
	(217.73,334.31) --
	(220.86,336.64) --
	(224.00,339.03) --
	(227.14,341.45) --
	(230.27,343.92) --
	(233.41,346.42) --
	(236.54,348.96) --
	(239.68,351.54) --
	(242.82,354.16) --
	(245.95,356.82) --
	(249.09,359.52) --
	(252.22,362.27) --
	(255.36,365.05) --
	(258.49,367.87) --
	(261.63,370.74) --
	(264.77,373.64) --
	(267.90,376.59) --
	(271.04,379.58) --
	(274.17,382.60) --
	(277.31,385.67) --
	(280.44,388.78) --
	(283.58,391.93);
\definecolor{fillColor}{RGB}{230,159,0}

\path[fill=fillColor] ( 35.86,253.66) --
	( 39.22,247.84) --
	( 32.49,247.84) --
	cycle;

\path[fill=fillColor] ( 44.40,256.05) --
	( 47.76,250.22) --
	( 41.03,250.22) --
	cycle;

\path[fill=fillColor] ( 52.94,258.56) --
	( 56.30,252.73) --
	( 49.58,252.73) --
	cycle;

\path[fill=fillColor] ( 61.48,261.19) --
	( 64.85,255.36) --
	( 58.12,255.36) --
	cycle;

\path[fill=fillColor] ( 70.02,263.94) --
	( 73.39,258.11) --
	( 66.66,258.11) --
	cycle;

\path[fill=fillColor] ( 78.57,266.81) --
	( 81.93,260.99) --
	( 75.20,260.99) --
	cycle;

\path[fill=fillColor] ( 87.11,269.83) --
	( 90.47,264.01) --
	( 83.75,264.01) --
	cycle;

\path[fill=fillColor] ( 95.65,273.00) --
	( 99.01,267.18) --
	( 92.29,267.18) --
	cycle;

\path[fill=fillColor] (104.19,276.33) --
	(107.56,270.51) --
	(100.83,270.51) --
	cycle;

\path[fill=fillColor] (112.74,279.79) --
	(116.10,273.97) --
	(109.37,273.97) --
	cycle;

\path[fill=fillColor] (121.28,283.41) --
	(124.64,277.58) --
	(117.91,277.58) --
	cycle;

\path[fill=fillColor] (129.82,287.19) --
	(133.18,281.36) --
	(126.46,281.36) --
	cycle;

\path[fill=fillColor] (138.36,291.15) --
	(141.73,285.33) --
	(135.00,285.33) --
	cycle;

\path[fill=fillColor] (146.90,295.31) --
	(150.27,289.49) --
	(143.54,289.49) --
	cycle;

\path[fill=fillColor] (155.45,299.62) --
	(158.81,293.80) --
	(152.08,293.80) --
	cycle;

\path[fill=fillColor] (163.99,304.14) --
	(167.35,298.31) --
	(160.63,298.31) --
	cycle;

\path[fill=fillColor] (172.53,308.85) --
	(175.89,303.03) --
	(169.17,303.03) --
	cycle;

\path[fill=fillColor] (181.07,313.93) --
	(184.44,308.10) --
	(177.71,308.10) --
	cycle;

\path[fill=fillColor] (189.62,319.15) --
	(192.98,313.32) --
	(186.25,313.32) --
	cycle;

\path[fill=fillColor] (198.16,324.63) --
	(201.52,318.80) --
	(194.79,318.80) --
	cycle;

\path[fill=fillColor] (206.70,330.30) --
	(210.06,324.48) --
	(203.34,324.48) --
	cycle;

\path[fill=fillColor] (215.24,336.32) --
	(218.61,330.49) --
	(211.88,330.49) --
	cycle;

\path[fill=fillColor] (223.78,342.61) --
	(227.15,336.78) --
	(220.42,336.78) --
	cycle;

\path[fill=fillColor] (232.33,349.11) --
	(235.69,343.29) --
	(228.96,343.29) --
	cycle;

\path[fill=fillColor] (240.87,356.01) --
	(244.23,350.19) --
	(237.51,350.19) --
	cycle;

\path[fill=fillColor] (249.41,363.19) --
	(252.77,357.37) --
	(246.05,357.37) --
	cycle;

\path[fill=fillColor] (257.95,370.87) --
	(261.32,365.04) --
	(254.59,365.04) --
	cycle;

\path[fill=fillColor] (266.50,378.77) --
	(269.86,372.95) --
	(263.13,372.95) --
	cycle;

\path[fill=fillColor] (275.04,386.88) --
	(278.40,381.05) --
	(271.67,381.05) --
	cycle;

\path[fill=fillColor] (283.58,395.60) --
	(286.94,389.77) --
	(280.22,389.77) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] ( 33.36,247.26) --
	( 38.35,247.26) --
	( 38.35,252.26) --
	( 33.36,252.26) --
	cycle;

\path[fill=fillColor] ( 41.90,249.63) --
	( 46.90,249.63) --
	( 46.90,254.63) --
	( 41.90,254.63) --
	cycle;

\path[fill=fillColor] ( 50.44,252.12) --
	( 55.44,252.12) --
	( 55.44,257.12) --
	( 50.44,257.12) --
	cycle;

\path[fill=fillColor] ( 58.98,254.74) --
	( 63.98,254.74) --
	( 63.98,259.73) --
	( 58.98,259.73) --
	cycle;

\path[fill=fillColor] ( 67.53,257.47) --
	( 72.52,257.47) --
	( 72.52,262.47) --
	( 67.53,262.47) --
	cycle;

\path[fill=fillColor] ( 76.07,260.33) --
	( 81.06,260.33) --
	( 81.06,265.33) --
	( 76.07,265.33) --
	cycle;

\path[fill=fillColor] ( 84.61,263.34) --
	( 89.61,263.34) --
	( 89.61,268.34) --
	( 84.61,268.34) --
	cycle;

\path[fill=fillColor] ( 93.15,266.51) --
	( 98.15,266.51) --
	( 98.15,271.50) --
	( 93.15,271.50) --
	cycle;

\path[fill=fillColor] (101.70,269.84) --
	(106.69,269.84) --
	(106.69,274.83) --
	(101.70,274.83) --
	cycle;

\path[fill=fillColor] (110.24,273.29) --
	(115.23,273.29) --
	(115.23,278.28) --
	(110.24,278.28) --
	cycle;

\path[fill=fillColor] (118.78,276.89) --
	(123.78,276.89) --
	(123.78,281.88) --
	(118.78,281.88) --
	cycle;

\path[fill=fillColor] (127.32,280.66) --
	(132.32,280.66) --
	(132.32,285.65) --
	(127.32,285.65) --
	cycle;

\path[fill=fillColor] (135.86,284.62) --
	(140.86,284.62) --
	(140.86,289.62) --
	(135.86,289.62) --
	cycle;

\path[fill=fillColor] (144.41,288.79) --
	(149.40,288.79) --
	(149.40,293.79) --
	(144.41,293.79) --
	cycle;

\path[fill=fillColor] (152.95,293.08) --
	(157.94,293.08) --
	(157.94,298.08) --
	(152.95,298.08) --
	cycle;

\path[fill=fillColor] (161.49,297.59) --
	(166.49,297.59) --
	(166.49,302.58) --
	(161.49,302.58) --
	cycle;

\path[fill=fillColor] (170.03,302.29) --
	(175.03,302.29) --
	(175.03,307.29) --
	(170.03,307.29) --
	cycle;

\path[fill=fillColor] (178.58,307.43) --
	(183.57,307.43) --
	(183.57,312.42) --
	(178.58,312.42) --
	cycle;

\path[fill=fillColor] (187.12,312.67) --
	(192.11,312.67) --
	(192.11,317.67) --
	(187.12,317.67) --
	cycle;

\path[fill=fillColor] (195.66,318.20) --
	(200.66,318.20) --
	(200.66,323.19) --
	(195.66,323.19) --
	cycle;

\path[fill=fillColor] (204.20,323.88) --
	(209.20,323.88) --
	(209.20,328.88) --
	(204.20,328.88) --
	cycle;

\path[fill=fillColor] (212.74,329.97) --
	(217.74,329.97) --
	(217.74,334.96) --
	(212.74,334.96) --
	cycle;

\path[fill=fillColor] (221.29,336.33) --
	(226.28,336.33) --
	(226.28,341.33) --
	(221.29,341.33) --
	cycle;

\path[fill=fillColor] (229.83,342.88) --
	(234.82,342.88) --
	(234.82,347.87) --
	(229.83,347.87) --
	cycle;

\path[fill=fillColor] (238.37,349.88) --
	(243.37,349.88) --
	(243.37,354.88) --
	(238.37,354.88) --
	cycle;

\path[fill=fillColor] (246.91,357.20) --
	(251.91,357.20) --
	(251.91,362.20) --
	(246.91,362.20) --
	cycle;

\path[fill=fillColor] (255.46,365.13) --
	(260.45,365.13) --
	(260.45,370.13) --
	(255.46,370.13) --
	cycle;

\path[fill=fillColor] (264.00,373.18) --
	(268.99,373.18) --
	(268.99,378.18) --
	(264.00,378.18) --
	cycle;

\path[fill=fillColor] (272.54,381.37) --
	(277.54,381.37) --
	(277.54,386.36) --
	(272.54,386.36) --
	cycle;

\path[fill=fillColor] (281.08,390.32) --
	(286.08,390.32) --
	(286.08,395.31) --
	(281.08,395.31) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32,249.78) -- ( 39.39,249.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86,246.24) -- ( 35.86,253.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87,252.16) -- ( 47.93,252.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.63) -- ( 44.40,255.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41,254.67) -- ( 56.47,254.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94,251.14) -- ( 52.94,258.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95,257.30) -- ( 65.01,257.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48,253.77) -- ( 61.48,260.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.05) -- ( 73.56,260.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02,256.52) -- ( 70.02,263.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,262.93) -- ( 82.10,262.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57,259.40) -- ( 78.57,266.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,265.95) -- ( 90.64,265.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,262.42) -- ( 87.11,269.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.13) -- ( 99.18,269.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,265.60) -- ( 95.65,272.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,272.49) -- (107.73,272.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,268.95) -- (104.19,276.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,275.94) -- (116.27,275.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,272.41) -- (112.74,279.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,279.55) -- (124.81,279.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.01) -- (121.28,283.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.32) -- (133.35,283.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,279.79) -- (129.82,286.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.28) -- (141.89,287.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,283.75) -- (138.36,290.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.46) -- (150.44,291.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,287.92) -- (146.90,294.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,295.73) -- (158.98,295.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,292.19) -- (155.45,299.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.20) -- (167.52,300.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,296.66) -- (163.99,303.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.86) -- (176.06,304.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.33) -- (172.53,308.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,310.02) -- (184.61,310.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.49) -- (181.07,313.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,315.24) -- (193.15,315.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.71) -- (189.62,318.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,320.74) -- (201.69,320.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,317.21) -- (198.16,324.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,326.37) -- (210.23,326.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,322.83) -- (206.70,329.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,332.43) -- (218.77,332.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,328.90) -- (215.24,335.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,338.75) -- (227.32,338.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,335.22) -- (223.78,342.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,345.19) -- (235.86,345.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,341.65) -- (232.33,348.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,352.15) -- (244.40,352.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,348.62) -- (240.87,355.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,359.43) -- (252.94,359.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,355.90) -- (249.41,362.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,367.42) -- (261.49,367.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,363.89) -- (257.95,370.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,375.38) -- (270.03,375.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,371.85) -- (266.50,378.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,383.38) -- (278.57,383.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,379.85) -- (275.04,386.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,392.25) -- (287.11,392.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,388.71) -- (283.58,395.78);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 35.86,249.83) circle (  2.50);

\path[fill=fillColor] ( 44.40,252.27) circle (  2.50);

\path[fill=fillColor] ( 52.94,254.83) circle (  2.50);

\path[fill=fillColor] ( 61.48,257.48) circle (  2.50);

\path[fill=fillColor] ( 70.02,260.30) circle (  2.50);

\path[fill=fillColor] ( 78.57,263.20) circle (  2.50);

\path[fill=fillColor] ( 87.11,266.25) circle (  2.50);

\path[fill=fillColor] ( 95.65,269.47) circle (  2.50);

\path[fill=fillColor] (104.19,272.76) circle (  2.50);

\path[fill=fillColor] (112.74,276.27) circle (  2.50);

\path[fill=fillColor] (121.28,279.87) circle (  2.50);

\path[fill=fillColor] (129.82,283.65) circle (  2.50);

\path[fill=fillColor] (138.36,287.63) circle (  2.50);

\path[fill=fillColor] (146.90,291.84) circle (  2.50);

\path[fill=fillColor] (155.45,296.08) circle (  2.50);

\path[fill=fillColor] (163.99,300.69) circle (  2.50);

\path[fill=fillColor] (172.53,305.43) circle (  2.50);

\path[fill=fillColor] (181.07,310.31) circle (  2.50);

\path[fill=fillColor] (189.62,315.45) circle (  2.50);

\path[fill=fillColor] (198.16,320.77) circle (  2.50);

\path[fill=fillColor] (206.70,326.39) circle (  2.50);

\path[fill=fillColor] (215.24,332.07) circle (  2.50);

\path[fill=fillColor] (223.78,338.31) circle (  2.50);

\path[fill=fillColor] (232.33,344.46) circle (  2.50);

\path[fill=fillColor] (240.87,351.03) circle (  2.50);

\path[fill=fillColor] (249.41,358.29) circle (  2.50);

\path[fill=fillColor] (257.95,365.51) circle (  2.50);

\path[fill=fillColor] (266.50,372.75) circle (  2.50);

\path[fill=fillColor] (275.04,380.66) circle (  2.50);

\path[fill=fillColor] (283.58,388.74) circle (  2.50);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.31,247.50) rectangle (283.58,410.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,244.47) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,291.17) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,337.88) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,384.58) {4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,247.50) --
	( 27.31,247.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,294.20) --
	( 27.31,294.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,340.91) --
	( 27.31,340.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,387.61) --
	( 27.31,387.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31,244.75) --
	( 27.31,247.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (112.74,244.75) --
	(112.74,247.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.16,244.75) --
	(198.16,247.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.31,236.49) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (112.74,236.49) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.16,236.49) {0.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (155.45,224.45) {Exponential growth rate $r$ (1/day)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,329.23) {Reproduction number $\mathcal R$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 39.98,332.94) rectangle (168.41,407.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 45.48,381.80) rectangle ( 59.93,396.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.93,389.03) -- ( 58.49,389.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 52.71,389.03) circle (  2.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 45.48,367.35) rectangle ( 59.93,381.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 46.93,374.57) -- ( 58.49,374.57);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{230,159,0}

\path[fill=fillColor] ( 52.71,378.46) --
	( 56.07,372.63) --
	( 49.34,372.63) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 45.48,352.89) rectangle ( 59.93,367.35);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 46.93,360.12) -- ( 58.49,360.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] ( 50.21,357.62) --
	( 55.20,357.62) --
	( 55.20,362.62) --
	( 50.21,362.62) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 45.48,338.44) rectangle ( 59.93,352.89);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 46.93,345.67) -- ( 58.49,345.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.17,345.67) -- ( 56.24,345.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.71,342.13) -- ( 52.71,349.20);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 65.43,386.00) {Generation interval};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 65.43,371.54) {Serial interval ($\rho=0.5$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 65.43,357.09) {Serial interval ($\rho=0$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 65.43,342.63) {Serial interval ($\rho=-0.5$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.31,419.03) {A};
\end{scope}
\begin{scope}
\path[clip] (289.08,216.81) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.08,216.81) rectangle (578.16,433.62);
\end{scope}
\begin{scope}
\path[clip] (316.39,247.50) rectangle (572.66,410.96);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (316.39,247.50) rectangle (572.66,410.96);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (324.94,249.99) --
	(328.07,250.83) --
	(331.21,251.68) --
	(334.34,252.56) --
	(337.48,253.45) --
	(340.61,254.37) --
	(343.75,255.30) --
	(346.89,256.26) --
	(350.02,257.23) --
	(353.16,258.23) --
	(356.29,259.24) --
	(359.43,260.28) --
	(362.56,261.33) --
	(365.70,262.40) --
	(368.84,263.50) --
	(371.97,264.61) --
	(375.11,265.75) --
	(378.24,266.90) --
	(381.38,268.08) --
	(384.51,269.28) --
	(387.65,270.50) --
	(390.79,271.73) --
	(393.92,272.98) --
	(397.06,274.24) --
	(400.19,275.53) --
	(403.33,276.84) --
	(406.47,278.17) --
	(409.60,279.52) --
	(412.74,280.89) --
	(415.87,282.30) --
	(419.01,283.73) --
	(422.14,285.17) --
	(425.28,286.64) --
	(428.42,288.12) --
	(431.55,289.62) --
	(434.69,291.14) --
	(437.82,292.70) --
	(440.96,294.28) --
	(444.09,295.90) --
	(447.23,297.55) --
	(450.37,299.21) --
	(453.50,300.90) --
	(456.64,302.61) --
	(459.77,304.34) --
	(462.91,306.10) --
	(466.04,307.89) --
	(469.18,309.70) --
	(472.32,311.56) --
	(475.45,313.44) --
	(478.59,315.37) --
	(481.72,317.32) --
	(484.86,319.30) --
	(487.99,321.31) --
	(491.13,323.34) --
	(494.27,325.40) --
	(497.40,327.50) --
	(500.54,329.63) --
	(503.67,331.79) --
	(506.81,334.00) --
	(509.94,336.24) --
	(513.08,338.52) --
	(516.22,340.85) --
	(519.35,343.20) --
	(522.49,345.59) --
	(525.62,348.02) --
	(528.76,350.47) --
	(531.90,352.96) --
	(535.03,355.49) --
	(538.17,358.05) --
	(541.30,360.65) --
	(544.44,363.28) --
	(547.57,365.95) --
	(550.71,368.65) --
	(553.85,371.39) --
	(556.98,374.16) --
	(560.12,376.97) --
	(563.25,379.82) --
	(566.39,382.70) --
	(569.52,385.61) --
	(572.66,388.56);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (324.94,249.67) --
	(328.07,250.54) --
	(331.21,251.42) --
	(334.34,252.31) --
	(337.48,253.20) --
	(340.61,254.10) --
	(343.75,255.00) --
	(346.89,255.91) --
	(350.02,256.83) --
	(353.16,257.75) --
	(356.29,258.68) --
	(359.43,259.62) --
	(362.56,260.56) --
	(365.70,261.51) --
	(368.84,262.46) --
	(371.97,263.42) --
	(375.11,264.39) --
	(378.24,265.36) --
	(381.38,266.34) --
	(384.51,267.32) --
	(387.65,268.31) --
	(390.79,269.31) --
	(393.92,270.31) --
	(397.06,271.33) --
	(400.19,272.35) --
	(403.33,273.37) --
	(406.47,274.41) --
	(409.60,275.44) --
	(412.74,276.48) --
	(415.87,277.52) --
	(419.01,278.57) --
	(422.14,279.62) --
	(425.28,280.68) --
	(428.42,281.75) --
	(431.55,282.83) --
	(434.69,283.91) --
	(437.82,284.99) --
	(440.96,286.07) --
	(444.09,287.14) --
	(447.23,288.21) --
	(450.37,289.29) --
	(453.50,290.38) --
	(456.64,291.48) --
	(459.77,292.58) --
	(462.91,293.68) --
	(466.04,294.78) --
	(469.18,295.87) --
	(472.32,296.96) --
	(475.45,298.03) --
	(478.59,299.08) --
	(481.72,300.14) --
	(484.86,301.19) --
	(487.99,302.25) --
	(491.13,303.30) --
	(494.27,304.35) --
	(497.40,305.39) --
	(500.54,306.43) --
	(503.67,307.45) --
	(506.81,308.45) --
	(509.94,309.44) --
	(513.08,310.40) --
	(516.22,311.35) --
	(519.35,312.29) --
	(522.49,313.23) --
	(525.62,314.15) --
	(528.76,315.06) --
	(531.90,315.97) --
	(535.03,316.86) --
	(538.17,317.74) --
	(541.30,318.61) --
	(544.44,319.47) --
	(547.57,320.31) --
	(550.71,321.14) --
	(553.85,321.96) --
	(556.98,322.77) --
	(560.12,323.57) --
	(563.25,324.36) --
	(566.39,325.13) --
	(569.52,325.89) --
	(572.66,326.65);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (324.94,249.52) --
	(328.07,250.42) --
	(331.21,251.31) --
	(334.34,252.21) --
	(337.48,253.10) --
	(340.61,254.00) --
	(343.75,254.89) --
	(346.89,255.79) --
	(350.02,256.69) --
	(353.16,257.58) --
	(356.29,258.48) --
	(359.43,259.38) --
	(362.56,260.28) --
	(365.70,261.18) --
	(368.84,262.07) --
	(371.97,262.97) --
	(375.11,263.87) --
	(378.24,264.76) --
	(381.38,265.66) --
	(384.51,266.55) --
	(387.65,267.45) --
	(390.79,268.35) --
	(393.92,269.25) --
	(397.06,270.16) --
	(400.19,271.07) --
	(403.33,271.98) --
	(406.47,272.89) --
	(409.60,273.80) --
	(412.74,274.69) --
	(415.87,275.58) --
	(419.01,276.46) --
	(422.14,277.34) --
	(425.28,278.24) --
	(428.42,279.14) --
	(431.55,280.04) --
	(434.69,280.93) --
	(437.82,281.81) --
	(440.96,282.67) --
	(444.09,283.51) --
	(447.23,284.33) --
	(450.37,285.16) --
	(453.50,285.99) --
	(456.64,286.82) --
	(459.77,287.65) --
	(462.91,288.46) --
	(466.04,289.26) --
	(469.18,290.04) --
	(472.32,290.78) --
	(475.45,291.50) --
	(478.59,292.17) --
	(481.72,292.82) --
	(484.86,293.46) --
	(487.99,294.10) --
	(491.13,294.71) --
	(494.27,295.31) --
	(497.40,295.88) --
	(500.54,296.42) --
	(503.67,296.93) --
	(506.81,297.40) --
	(509.94,297.83) --
	(513.08,298.21) --
	(516.22,298.55) --
	(519.35,298.86) --
	(522.49,299.15) --
	(525.62,299.41) --
	(528.76,299.64) --
	(531.90,299.83) --
	(535.03,300.00) --
	(538.17,300.14) --
	(541.30,300.24) --
	(544.44,300.31) --
	(547.57,300.35) --
	(550.71,300.35) --
	(553.85,300.33) --
	(556.98,300.26) --
	(560.12,300.17) --
	(563.25,300.05) --
	(566.39,299.89) --
	(569.52,299.70) --
	(572.66,299.48);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (324.94,249.43) --
	(328.07,250.36) --
	(331.21,251.28) --
	(334.34,252.19) --
	(337.48,253.10) --
	(340.61,254.00) --
	(343.75,254.90) --
	(346.89,255.79) --
	(350.02,256.67) --
	(353.16,257.56) --
	(356.29,258.43) --
	(359.43,259.30) --
	(362.56,260.17) --
	(365.70,261.03) --
	(368.84,261.89) --
	(371.97,262.74) --
	(375.11,263.58) --
	(378.24,264.41) --
	(381.38,265.24) --
	(384.51,266.06) --
	(387.65,266.87) --
	(390.79,267.69) --
	(393.92,268.52) --
	(397.06,269.34) --
	(400.19,270.15) --
	(403.33,270.96) --
	(406.47,271.76) --
	(409.60,272.55) --
	(412.74,273.32) --
	(415.87,274.07) --
	(419.01,274.81) --
	(422.14,275.55) --
	(425.28,276.29) --
	(428.42,277.04) --
	(431.55,277.78) --
	(434.69,278.50) --
	(437.82,279.20) --
	(440.96,279.87) --
	(444.09,280.50) --
	(447.23,281.10) --
	(450.37,281.71) --
	(453.50,282.32) --
	(456.64,282.91) --
	(459.77,283.49) --
	(462.91,284.05) --
	(466.04,284.59) --
	(469.18,285.08) --
	(472.32,285.54) --
	(475.45,285.96) --
	(478.59,286.31) --
	(481.72,286.64) --
	(484.86,286.94) --
	(487.99,287.23) --
	(491.13,287.48) --
	(494.27,287.71) --
	(497.40,287.90) --
	(500.54,288.05) --
	(503.67,288.16) --
	(506.81,288.22) --
	(509.94,288.22) --
	(513.08,288.16) --
	(516.22,288.06) --
	(519.35,287.92) --
	(522.49,287.74) --
	(525.62,287.52) --
	(528.76,287.27) --
	(531.90,286.97) --
	(535.03,286.63) --
	(538.17,286.24) --
	(541.30,285.82) --
	(544.44,285.35) --
	(547.57,284.84) --
	(550.71,284.28) --
	(553.85,283.68) --
	(556.98,283.04) --
	(560.12,282.35) --
	(563.25,281.63) --
	(566.39,280.86) --
	(569.52,280.05) --
	(572.66,279.19);
\definecolor{fillColor}{RGB}{230,159,0}

\path[fill=fillColor] (324.94,253.65) --
	(328.30,247.82) --
	(321.57,247.82) --
	cycle;

\path[fill=fillColor] (333.48,255.98) --
	(336.84,250.15) --
	(330.11,250.15) --
	cycle;

\path[fill=fillColor] (342.02,258.37) --
	(345.38,252.54) --
	(338.66,252.54) --
	cycle;

\path[fill=fillColor] (350.56,260.82) --
	(353.93,255.00) --
	(347.20,255.00) --
	cycle;

\path[fill=fillColor] (359.10,263.33) --
	(362.47,257.51) --
	(355.74,257.51) --
	cycle;

\path[fill=fillColor] (367.65,265.91) --
	(371.01,260.08) --
	(364.28,260.08) --
	cycle;

\path[fill=fillColor] (376.19,268.53) --
	(379.55,262.71) --
	(372.83,262.71) --
	cycle;

\path[fill=fillColor] (384.73,271.21) --
	(388.09,265.39) --
	(381.37,265.39) --
	cycle;

\path[fill=fillColor] (393.27,273.94) --
	(396.64,268.12) --
	(389.91,268.12) --
	cycle;

\path[fill=fillColor] (401.82,276.72) --
	(405.18,270.90) --
	(398.45,270.90) --
	cycle;

\path[fill=fillColor] (410.36,279.54) --
	(413.72,273.72) --
	(406.99,273.72) --
	cycle;

\path[fill=fillColor] (418.90,282.40) --
	(422.26,276.58) --
	(415.54,276.58) --
	cycle;

\path[fill=fillColor] (427.44,285.29) --
	(430.81,279.47) --
	(424.08,279.47) --
	cycle;

\path[fill=fillColor] (435.98,288.22) --
	(439.35,282.39) --
	(432.62,282.39) --
	cycle;

\path[fill=fillColor] (444.53,291.16) --
	(447.89,285.33) --
	(441.16,285.33) --
	cycle;

\path[fill=fillColor] (453.07,294.11) --
	(456.43,288.29) --
	(449.71,288.29) --
	cycle;

\path[fill=fillColor] (461.61,297.08) --
	(464.97,291.25) --
	(458.25,291.25) --
	cycle;

\path[fill=fillColor] (470.15,300.04) --
	(473.52,294.21) --
	(466.79,294.21) --
	cycle;

\path[fill=fillColor] (478.70,302.98) --
	(482.06,297.15) --
	(475.33,297.15) --
	cycle;

\path[fill=fillColor] (487.24,305.90) --
	(490.60,300.08) --
	(483.87,300.08) --
	cycle;

\path[fill=fillColor] (495.78,308.78) --
	(499.14,302.96) --
	(492.42,302.96) --
	cycle;

\path[fill=fillColor] (504.32,311.61) --
	(507.69,305.79) --
	(500.96,305.79) --
	cycle;

\path[fill=fillColor] (512.86,314.38) --
	(516.23,308.55) --
	(509.50,308.55) --
	cycle;

\path[fill=fillColor] (521.41,317.05) --
	(524.77,311.23) --
	(518.04,311.23) --
	cycle;

\path[fill=fillColor] (529.95,319.62) --
	(533.31,313.79) --
	(526.59,313.79) --
	cycle;

\path[fill=fillColor] (538.49,322.06) --
	(541.85,316.24) --
	(535.13,316.24) --
	cycle;

\path[fill=fillColor] (547.03,324.35) --
	(550.40,318.52) --
	(543.67,318.52) --
	cycle;

\path[fill=fillColor] (555.58,326.46) --
	(558.94,320.63) --
	(552.21,320.63) --
	cycle;

\path[fill=fillColor] (564.12,328.36) --
	(567.48,322.54) --
	(560.75,322.54) --
	cycle;

\path[fill=fillColor] (572.66,330.02) --
	(576.02,324.20) --
	(569.30,324.20) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] (322.44,247.24) --
	(327.43,247.24) --
	(327.43,252.23) --
	(322.44,252.23) --
	cycle;

\path[fill=fillColor] (330.98,249.53) --
	(335.98,249.53) --
	(335.98,254.52) --
	(330.98,254.52) --
	cycle;

\path[fill=fillColor] (339.52,251.86) --
	(344.52,251.86) --
	(344.52,256.85) --
	(339.52,256.85) --
	cycle;

\path[fill=fillColor] (348.06,254.23) --
	(353.06,254.23) --
	(353.06,259.22) --
	(348.06,259.22) --
	cycle;

\path[fill=fillColor] (356.61,256.63) --
	(361.60,256.63) --
	(361.60,261.63) --
	(356.61,261.63) --
	cycle;

\path[fill=fillColor] (365.15,259.06) --
	(370.14,259.06) --
	(370.14,264.06) --
	(365.15,264.06) --
	cycle;

\path[fill=fillColor] (373.69,261.52) --
	(378.69,261.52) --
	(378.69,266.52) --
	(373.69,266.52) --
	cycle;

\path[fill=fillColor] (382.23,264.00) --
	(387.23,264.00) --
	(387.23,268.99) --
	(382.23,268.99) --
	cycle;

\path[fill=fillColor] (390.78,266.48) --
	(395.77,266.48) --
	(395.77,271.48) --
	(390.78,271.48) --
	cycle;

\path[fill=fillColor] (399.32,268.97) --
	(404.31,268.97) --
	(404.31,273.96) --
	(399.32,273.96) --
	cycle;

\path[fill=fillColor] (407.86,271.45) --
	(412.86,271.45) --
	(412.86,276.44) --
	(407.86,276.44) --
	cycle;

\path[fill=fillColor] (416.40,273.91) --
	(421.40,273.91) --
	(421.40,278.91) --
	(416.40,278.91) --
	cycle;

\path[fill=fillColor] (424.94,276.35) --
	(429.94,276.35) --
	(429.94,281.35) --
	(424.94,281.35) --
	cycle;

\path[fill=fillColor] (433.49,278.75) --
	(438.48,278.75) --
	(438.48,283.74) --
	(433.49,283.74) --
	cycle;

\path[fill=fillColor] (442.03,281.10) --
	(447.02,281.10) --
	(447.02,286.09) --
	(442.03,286.09) --
	cycle;

\path[fill=fillColor] (450.57,283.38) --
	(455.57,283.38) --
	(455.57,288.37) --
	(450.57,288.37) --
	cycle;

\path[fill=fillColor] (459.11,285.58) --
	(464.11,285.58) --
	(464.11,290.57) --
	(459.11,290.57) --
	cycle;

\path[fill=fillColor] (467.66,287.68) --
	(472.65,287.68) --
	(472.65,292.67) --
	(467.66,292.67) --
	cycle;

\path[fill=fillColor] (476.20,289.66) --
	(481.19,289.66) --
	(481.19,294.66) --
	(476.20,294.66) --
	cycle;

\path[fill=fillColor] (484.74,291.50) --
	(489.74,291.50) --
	(489.74,296.50) --
	(484.74,296.50) --
	cycle;

\path[fill=fillColor] (493.28,293.19) --
	(498.28,293.19) --
	(498.28,298.18) --
	(493.28,298.18) --
	cycle;

\path[fill=fillColor] (501.82,294.68) --
	(506.82,294.68) --
	(506.82,299.67) --
	(501.82,299.67) --
	cycle;

\path[fill=fillColor] (510.37,295.96) --
	(515.36,295.96) --
	(515.36,300.95) --
	(510.37,300.95) --
	cycle;

\path[fill=fillColor] (518.91,296.99) --
	(523.90,296.99) --
	(523.90,301.99) --
	(518.91,301.99) --
	cycle;

\path[fill=fillColor] (527.45,297.75) --
	(532.45,297.75) --
	(532.45,302.75) --
	(527.45,302.75) --
	cycle;

\path[fill=fillColor] (535.99,298.20) --
	(540.99,298.20) --
	(540.99,303.20) --
	(535.99,303.20) --
	cycle;

\path[fill=fillColor] (544.54,298.31) --
	(549.53,298.31) --
	(549.53,303.30) --
	(544.54,303.30) --
	cycle;

\path[fill=fillColor] (553.08,298.03) --
	(558.07,298.03) --
	(558.07,303.03) --
	(553.08,303.03) --
	cycle;

\path[fill=fillColor] (561.62,297.34) --
	(566.62,297.34) --
	(566.62,302.34) --
	(561.62,302.34) --
	cycle;

\path[fill=fillColor] (570.16,296.21) --
	(575.16,296.21) --
	(575.16,301.20) --
	(570.16,301.20) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.40,249.75) -- (328.47,249.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.94,246.21) -- (324.94,253.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.95,252.03) -- (337.01,252.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.48,248.49) -- (333.48,255.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.49,254.33) -- (345.55,254.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.02,250.80) -- (342.02,257.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.03,256.65) -- (354.09,256.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.12) -- (350.56,260.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,258.98) -- (362.64,258.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,255.45) -- (359.10,262.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,261.32) -- (371.18,261.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,257.78) -- (367.65,264.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,263.64) -- (379.72,263.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,260.11) -- (376.19,267.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,265.95) -- (388.26,265.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,262.42) -- (384.73,269.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,268.23) -- (396.81,268.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,264.69) -- (393.27,271.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,270.46) -- (405.35,270.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,266.93) -- (401.82,274.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,272.65) -- (413.89,272.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,269.12) -- (410.36,276.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,274.77) -- (422.43,274.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,271.23) -- (418.90,278.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,276.80) -- (430.97,276.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,273.27) -- (427.44,280.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,278.74) -- (439.52,278.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,275.21) -- (435.98,282.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,280.56) -- (448.06,280.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,277.03) -- (444.53,284.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,282.25) -- (456.60,282.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,278.72) -- (453.07,285.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,283.78) -- (465.14,283.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,280.25) -- (461.61,287.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,285.14) -- (473.69,285.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,281.61) -- (470.15,288.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,286.31) -- (482.23,286.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,282.77) -- (478.70,289.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,287.25) -- (490.77,287.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,283.71) -- (487.24,290.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,287.94) -- (499.31,287.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,284.40) -- (495.78,291.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,288.35) -- (507.85,288.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,284.82) -- (504.32,291.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,288.47) -- (516.40,288.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,284.93) -- (512.86,292.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,288.25) -- (524.94,288.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,284.72) -- (521.41,291.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,287.67) -- (533.48,287.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,284.14) -- (529.95,291.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,286.70) -- (542.02,286.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,283.17) -- (538.49,290.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,285.32) -- (550.57,285.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,281.79) -- (547.03,288.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,283.50) -- (559.11,283.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,279.97) -- (555.58,287.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,281.24) -- (567.65,281.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,277.71) -- (564.12,284.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,278.52) -- (576.19,278.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,274.99) -- (572.66,282.05);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (324.94,249.83) circle (  2.50);

\path[fill=fillColor] (333.48,252.27) circle (  2.50);

\path[fill=fillColor] (342.02,254.82) circle (  2.50);

\path[fill=fillColor] (350.56,257.50) circle (  2.50);

\path[fill=fillColor] (359.10,260.28) circle (  2.50);

\path[fill=fillColor] (367.65,263.20) circle (  2.50);

\path[fill=fillColor] (376.19,266.26) circle (  2.50);

\path[fill=fillColor] (384.73,269.45) circle (  2.50);

\path[fill=fillColor] (393.27,272.76) circle (  2.50);

\path[fill=fillColor] (401.82,276.31) circle (  2.50);

\path[fill=fillColor] (410.36,279.87) circle (  2.50);

\path[fill=fillColor] (418.90,283.69) circle (  2.50);

\path[fill=fillColor] (427.44,287.63) circle (  2.50);

\path[fill=fillColor] (435.98,291.76) circle (  2.50);

\path[fill=fillColor] (444.53,296.10) circle (  2.50);

\path[fill=fillColor] (453.07,300.70) circle (  2.50);

\path[fill=fillColor] (461.61,305.28) circle (  2.50);

\path[fill=fillColor] (470.15,310.36) circle (  2.50);

\path[fill=fillColor] (478.70,315.52) circle (  2.50);

\path[fill=fillColor] (487.24,320.84) circle (  2.50);

\path[fill=fillColor] (495.78,326.35) circle (  2.50);

\path[fill=fillColor] (504.32,332.10) circle (  2.50);

\path[fill=fillColor] (512.86,338.43) circle (  2.50);

\path[fill=fillColor] (521.41,344.40) circle (  2.50);

\path[fill=fillColor] (529.95,351.37) circle (  2.50);

\path[fill=fillColor] (538.49,357.84) circle (  2.50);

\path[fill=fillColor] (547.03,365.25) circle (  2.50);

\path[fill=fillColor] (555.58,372.83) circle (  2.50);

\path[fill=fillColor] (564.12,380.80) circle (  2.50);

\path[fill=fillColor] (572.66,388.87) circle (  2.50);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.39,247.50) rectangle (572.66,410.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,244.47) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,291.17) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,337.88) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,384.58) {4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,247.50) --
	(316.39,247.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,294.20) --
	(316.39,294.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,340.91) --
	(316.39,340.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,387.61) --
	(316.39,387.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (316.39,244.75) --
	(316.39,247.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (401.82,244.75) --
	(401.82,247.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (487.24,244.75) --
	(487.24,247.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (316.39,236.49) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (401.82,236.49) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (487.24,236.49) {0.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (444.53,224.45) {Exponential growth rate $r$ (1/day)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,329.23) {Reproduction number $\mathcal R$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (316.39,419.03) {B};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 34.16, 30.69) rectangle (283.58,194.15);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.16, 30.69) rectangle (283.58,194.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 42.47, 40.78) --
	( 45.52, 40.81) --
	( 48.57, 40.84) --
	( 51.63, 40.86) --
	( 54.68, 40.89) --
	( 57.73, 40.91) --
	( 60.78, 40.93) --
	( 63.83, 40.95) --
	( 66.89, 40.97) --
	( 69.94, 40.99) --
	( 72.99, 41.00) --
	( 76.04, 41.01) --
	( 79.09, 41.02) --
	( 82.15, 41.03) --
	( 85.20, 41.04) --
	( 88.25, 41.04) --
	( 91.30, 41.05) --
	( 94.35, 41.05) --
	( 97.41, 41.06) --
	(100.46, 41.06) --
	(103.51, 41.07) --
	(106.56, 41.06) --
	(109.61, 41.06) --
	(112.67, 41.05) --
	(115.72, 41.05) --
	(118.77, 41.04) --
	(121.82, 41.03) --
	(124.87, 41.02) --
	(127.93, 41.02) --
	(130.98, 41.01) --
	(134.03, 41.02) --
	(137.08, 41.02) --
	(140.13, 41.03) --
	(143.19, 41.05) --
	(146.24, 41.06) --
	(149.29, 41.08) --
	(152.34, 41.09) --
	(155.40, 41.10) --
	(158.45, 41.11) --
	(161.50, 41.12) --
	(164.55, 41.12) --
	(167.60, 41.13) --
	(170.66, 41.14) --
	(173.71, 41.14) --
	(176.76, 41.15) --
	(179.81, 41.16) --
	(182.86, 41.16) --
	(185.92, 41.17) --
	(188.97, 41.17) --
	(192.02, 41.17) --
	(195.07, 41.17) --
	(198.12, 41.16) --
	(201.18, 41.15) --
	(204.23, 41.15) --
	(207.28, 41.14) --
	(210.33, 41.13) --
	(213.38, 41.12) --
	(216.44, 41.11) --
	(219.49, 41.10) --
	(222.54, 41.10) --
	(225.59, 41.10) --
	(228.64, 41.10) --
	(231.70, 41.10) --
	(234.75, 41.10) --
	(237.80, 41.10) --
	(240.85, 41.10) --
	(243.90, 41.10) --
	(246.96, 41.11) --
	(250.01, 41.11) --
	(253.06, 41.11) --
	(256.11, 41.12) --
	(259.16, 41.12) --
	(262.22, 41.13) --
	(265.27, 41.14) --
	(268.32, 41.15) --
	(271.37, 41.16) --
	(274.42, 41.17) --
	(277.48, 41.18) --
	(280.53, 41.20) --
	(283.58, 41.21);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 42.47, 33.33) --
	( 45.52, 34.95) --
	( 48.57, 36.56) --
	( 51.63, 38.16) --
	( 54.68, 39.73) --
	( 57.73, 41.29) --
	( 60.78, 42.83) --
	( 63.83, 44.35) --
	( 66.89, 45.86) --
	( 69.94, 47.35) --
	( 72.99, 48.82) --
	( 76.04, 50.27) --
	( 79.09, 51.71) --
	( 82.15, 53.13) --
	( 85.20, 54.53) --
	( 88.25, 55.91) --
	( 91.30, 57.28) --
	( 94.35, 58.63) --
	( 97.41, 59.97) --
	(100.46, 61.29) --
	(103.51, 62.59) --
	(106.56, 63.87) --
	(109.61, 65.13) --
	(112.67, 66.36) --
	(115.72, 67.58) --
	(118.77, 68.78) --
	(121.82, 69.97) --
	(124.87, 71.15) --
	(127.93, 72.31) --
	(130.98, 73.46) --
	(134.03, 74.61) --
	(137.08, 75.73) --
	(140.13, 76.83) --
	(143.19, 77.91) --
	(146.24, 78.98) --
	(149.29, 80.03) --
	(152.34, 81.07) --
	(155.40, 82.12) --
	(158.45, 83.16) --
	(161.50, 84.21) --
	(164.55, 85.23) --
	(167.60, 86.25) --
	(170.66, 87.26) --
	(173.71, 88.26) --
	(176.76, 89.24) --
	(179.81, 90.22) --
	(182.86, 91.20) --
	(185.92, 92.16) --
	(188.97, 93.13) --
	(192.02, 94.09) --
	(195.07, 95.04) --
	(198.12, 95.99) --
	(201.18, 96.93) --
	(204.23, 97.87) --
	(207.28, 98.79) --
	(210.33, 99.71) --
	(213.38,100.62) --
	(216.44,101.53) --
	(219.49,102.42) --
	(222.54,103.32) --
	(225.59,104.20) --
	(228.64,105.08) --
	(231.70,105.95) --
	(234.75,106.81) --
	(237.80,107.67) --
	(240.85,108.51) --
	(243.90,109.36) --
	(246.96,110.19) --
	(250.01,111.02) --
	(253.06,111.84) --
	(256.11,112.65) --
	(259.16,113.46) --
	(262.22,114.26) --
	(265.27,115.05) --
	(268.32,115.83) --
	(271.37,116.61) --
	(274.42,117.38) --
	(277.48,118.15) --
	(280.53,118.91) --
	(283.58,119.66);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 42.47, 30.69) --
	( 45.52, 32.91) --
	( 48.57, 35.11) --
	( 51.63, 37.29) --
	( 54.68, 39.45) --
	( 57.73, 41.58) --
	( 60.78, 43.69) --
	( 63.83, 45.78) --
	( 66.89, 47.85) --
	( 69.94, 49.90) --
	( 72.99, 51.92) --
	( 76.04, 53.92) --
	( 79.09, 55.90) --
	( 82.15, 57.85) --
	( 85.20, 59.79) --
	( 88.25, 61.70) --
	( 91.30, 63.59) --
	( 94.35, 65.46) --
	( 97.41, 67.31) --
	(100.46, 69.14) --
	(103.51, 70.95) --
	(106.56, 72.73) --
	(109.61, 74.47) --
	(112.67, 76.20) --
	(115.72, 77.90) --
	(118.77, 79.57) --
	(121.82, 81.23) --
	(124.87, 82.88) --
	(127.93, 84.50) --
	(130.98, 86.12) --
	(134.03, 87.72) --
	(137.08, 89.31) --
	(140.13, 90.86) --
	(143.19, 92.38) --
	(146.24, 93.88) --
	(149.29, 95.37) --
	(152.34, 96.85) --
	(155.40, 98.32) --
	(158.45, 99.80) --
	(161.50,101.28) --
	(164.55,102.73) --
	(167.60,104.18) --
	(170.66,105.61) --
	(173.71,107.03) --
	(176.76,108.44) --
	(179.81,109.83) --
	(182.86,111.22) --
	(185.92,112.60) --
	(188.97,113.98) --
	(192.02,115.35) --
	(195.07,116.72) --
	(198.12,118.07) --
	(201.18,119.42) --
	(204.23,120.76) --
	(207.28,122.08) --
	(210.33,123.40) --
	(213.38,124.71) --
	(216.44,126.01) --
	(219.49,127.30) --
	(222.54,128.58) --
	(225.59,129.86) --
	(228.64,131.12) --
	(231.70,132.38) --
	(234.75,133.62) --
	(237.80,134.86) --
	(240.85,136.09) --
	(243.90,137.31) --
	(246.96,138.51) --
	(250.01,139.71) --
	(253.06,140.91) --
	(256.11,142.09) --
	(259.16,143.26) --
	(262.22,144.42) --
	(265.27,145.58) --
	(268.32,146.73) --
	(271.37,147.86) --
	(274.42,148.99) --
	(277.48,150.11) --
	(280.53,151.22) --
	(283.58,152.32);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 42.47, 35.97) --
	( 45.52, 38.77) --
	( 48.57, 41.54) --
	( 51.63, 44.28) --
	( 54.68, 47.00) --
	( 57.73, 49.69) --
	( 60.78, 52.36) --
	( 63.83, 55.00) --
	( 66.89, 57.61) --
	( 69.94, 60.20) --
	( 72.99, 62.76) --
	( 76.04, 65.30) --
	( 79.09, 67.81) --
	( 82.15, 70.29) --
	( 85.20, 72.75) --
	( 88.25, 75.18) --
	( 91.30, 77.59) --
	( 94.35, 79.97) --
	( 97.41, 82.33) --
	(100.46, 84.67) --
	(103.51, 86.98) --
	(106.56, 89.25) --
	(109.61, 91.49) --
	(112.67, 93.71) --
	(115.72, 95.89) --
	(118.77, 98.05) --
	(121.82,100.18) --
	(124.87,102.30) --
	(127.93,104.40) --
	(130.98,106.49) --
	(134.03,108.56) --
	(137.08,110.61) --
	(140.13,112.62) --
	(143.19,114.60) --
	(146.24,116.55) --
	(149.29,118.49) --
	(152.34,120.42) --
	(155.40,122.34) --
	(158.45,124.27) --
	(161.50,126.20) --
	(164.55,128.11) --
	(167.60,130.00) --
	(170.66,131.87) --
	(173.71,133.74) --
	(176.76,135.59) --
	(179.81,137.42) --
	(182.86,139.25) --
	(185.92,141.07) --
	(188.97,142.89) --
	(192.02,144.69) --
	(195.07,146.49) --
	(198.12,148.28) --
	(201.18,150.06) --
	(204.23,151.83) --
	(207.28,153.58) --
	(210.33,155.33) --
	(213.38,157.06) --
	(216.44,158.79) --
	(219.49,160.50) --
	(222.54,162.20) --
	(225.59,163.90) --
	(228.64,165.58) --
	(231.70,167.25) --
	(234.75,168.91) --
	(237.80,170.56) --
	(240.85,172.20) --
	(243.90,173.83) --
	(246.96,175.45) --
	(250.01,177.06) --
	(253.06,178.66) --
	(256.11,180.24) --
	(259.16,181.82) --
	(262.22,183.39) --
	(265.27,184.94) --
	(268.32,186.49) --
	(271.37,188.02) --
	(274.42,189.55) --
	(277.48,191.06) --
	(280.53,192.56) --
	(283.58,194.05);
\definecolor{fillColor}{RGB}{230,159,0}

\path[fill=fillColor] ( 42.47, 37.24) --
	( 45.83, 31.41) --
	( 39.11, 31.41) --
	cycle;

\path[fill=fillColor] ( 50.78, 41.30) --
	( 54.15, 35.47) --
	( 47.42, 35.47) --
	cycle;

\path[fill=fillColor] ( 59.10, 45.93) --
	( 62.46, 40.10) --
	( 55.73, 40.10) --
	cycle;

\path[fill=fillColor] ( 67.41, 50.15) --
	( 70.78, 44.32) --
	( 64.05, 44.32) --
	cycle;

\path[fill=fillColor] ( 75.73, 54.15) --
	( 79.09, 48.32) --
	( 72.36, 48.32) --
	cycle;

\path[fill=fillColor] ( 84.04, 57.90) --
	( 87.40, 52.07) --
	( 80.68, 52.07) --
	cycle;

\path[fill=fillColor] ( 92.36, 61.62) --
	( 95.72, 55.79) --
	( 88.99, 55.79) --
	cycle;

\path[fill=fillColor] (100.67, 65.39) --
	(104.03, 59.57) --
	( 97.31, 59.57) --
	cycle;

\path[fill=fillColor] (108.98, 69.12) --
	(112.35, 63.29) --
	(105.62, 63.29) --
	cycle;

\path[fill=fillColor] (117.30, 72.29) --
	(120.66, 66.47) --
	(113.93, 66.47) --
	cycle;

\path[fill=fillColor] (125.61, 75.42) --
	(128.98, 69.59) --
	(122.25, 69.59) --
	cycle;

\path[fill=fillColor] (133.93, 78.32) --
	(137.29, 72.50) --
	(130.56, 72.50) --
	cycle;

\path[fill=fillColor] (142.24, 81.35) --
	(145.60, 75.53) --
	(138.88, 75.53) --
	cycle;

\path[fill=fillColor] (150.55, 84.41) --
	(153.92, 78.59) --
	(147.19, 78.59) --
	cycle;

\path[fill=fillColor] (158.87, 87.15) --
	(162.23, 81.33) --
	(155.50, 81.33) --
	cycle;

\path[fill=fillColor] (167.18, 89.83) --
	(170.55, 84.00) --
	(163.82, 84.00) --
	cycle;

\path[fill=fillColor] (175.50, 92.46) --
	(178.86, 86.63) --
	(172.13, 86.63) --
	cycle;

\path[fill=fillColor] (183.81, 95.48) --
	(187.17, 89.65) --
	(180.45, 89.65) --
	cycle;

\path[fill=fillColor] (192.12, 98.05) --
	(195.49, 92.23) --
	(188.76, 92.23) --
	cycle;

\path[fill=fillColor] (200.44,100.78) --
	(203.80, 94.95) --
	(197.07, 94.95) --
	cycle;

\path[fill=fillColor] (208.75,103.02) --
	(212.12, 97.20) --
	(205.39, 97.20) --
	cycle;

\path[fill=fillColor] (217.07,105.54) --
	(220.43, 99.72) --
	(213.70, 99.72) --
	cycle;

\path[fill=fillColor] (225.38,108.04) --
	(228.74,102.22) --
	(222.02,102.22) --
	cycle;

\path[fill=fillColor] (233.70,110.36) --
	(237.06,104.53) --
	(230.33,104.53) --
	cycle;

\path[fill=fillColor] (242.01,112.69) --
	(245.37,106.87) --
	(238.65,106.87) --
	cycle;

\path[fill=fillColor] (250.32,115.02) --
	(253.69,109.20) --
	(246.96,109.20) --
	cycle;

\path[fill=fillColor] (258.64,117.14) --
	(262.00,111.31) --
	(255.27,111.31) --
	cycle;

\path[fill=fillColor] (266.95,119.41) --
	(270.32,113.59) --
	(263.59,113.59) --
	cycle;

\path[fill=fillColor] (275.27,121.42) --
	(278.63,115.60) --
	(271.90,115.60) --
	cycle;

\path[fill=fillColor] (283.58,123.59) --
	(286.94,117.77) --
	(280.22,117.77) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] ( 39.97, 28.24) --
	( 44.97, 28.24) --
	( 44.97, 33.24) --
	( 39.97, 33.24) --
	cycle;

\path[fill=fillColor] ( 48.29, 33.79) --
	( 53.28, 33.79) --
	( 53.28, 38.78) --
	( 48.29, 38.78) --
	cycle;

\path[fill=fillColor] ( 56.60, 40.12) --
	( 61.60, 40.12) --
	( 61.60, 45.11) --
	( 56.60, 45.11) --
	cycle;

\path[fill=fillColor] ( 64.91, 45.85) --
	( 69.91, 45.85) --
	( 69.91, 50.84) --
	( 64.91, 50.84) --
	cycle;

\path[fill=fillColor] ( 73.23, 51.39) --
	( 78.22, 51.39) --
	( 78.22, 56.38) --
	( 73.23, 56.38) --
	cycle;

\path[fill=fillColor] ( 81.54, 56.59) --
	( 86.54, 56.59) --
	( 86.54, 61.58) --
	( 81.54, 61.58) --
	cycle;

\path[fill=fillColor] ( 89.86, 61.73) --
	( 94.85, 61.73) --
	( 94.85, 66.73) --
	( 89.86, 66.73) --
	cycle;

\path[fill=fillColor] ( 98.17, 66.95) --
	(103.17, 66.95) --
	(103.17, 71.95) --
	( 98.17, 71.95) --
	cycle;

\path[fill=fillColor] (106.49, 72.16) --
	(111.48, 72.16) --
	(111.48, 77.15) --
	(106.49, 77.15) --
	cycle;

\path[fill=fillColor] (114.80, 76.50) --
	(119.80, 76.50) --
	(119.80, 81.49) --
	(114.80, 81.49) --
	cycle;

\path[fill=fillColor] (123.11, 80.91) --
	(128.11, 80.91) --
	(128.11, 85.91) --
	(123.11, 85.91) --
	cycle;

\path[fill=fillColor] (131.43, 84.98) --
	(136.42, 84.98) --
	(136.42, 89.98) --
	(131.43, 89.98) --
	cycle;

\path[fill=fillColor] (139.74, 89.24) --
	(144.74, 89.24) --
	(144.74, 94.24) --
	(139.74, 94.24) --
	cycle;

\path[fill=fillColor] (148.06, 93.58) --
	(153.05, 93.58) --
	(153.05, 98.58) --
	(148.06, 98.58) --
	cycle;

\path[fill=fillColor] (156.37, 97.49) --
	(161.37, 97.49) --
	(161.37,102.49) --
	(156.37,102.49) --
	cycle;

\path[fill=fillColor] (164.68,101.24) --
	(169.68,101.24) --
	(169.68,106.23) --
	(164.68,106.23) --
	cycle;

\path[fill=fillColor] (173.00,104.98) --
	(177.99,104.98) --
	(177.99,109.98) --
	(173.00,109.98) --
	cycle;

\path[fill=fillColor] (181.31,109.30) --
	(186.31,109.30) --
	(186.31,114.30) --
	(181.31,114.30) --
	cycle;

\path[fill=fillColor] (189.63,112.96) --
	(194.62,112.96) --
	(194.62,117.96) --
	(189.63,117.96) --
	cycle;

\path[fill=fillColor] (197.94,116.88) --
	(202.94,116.88) --
	(202.94,121.88) --
	(197.94,121.88) --
	cycle;

\path[fill=fillColor] (206.26,120.08) --
	(211.25,120.08) --
	(211.25,125.07) --
	(206.26,125.07) --
	cycle;

\path[fill=fillColor] (214.57,123.71) --
	(219.56,123.71) --
	(219.56,128.71) --
	(214.57,128.71) --
	cycle;

\path[fill=fillColor] (222.88,127.30) --
	(227.88,127.30) --
	(227.88,132.30) --
	(222.88,132.30) --
	cycle;

\path[fill=fillColor] (231.20,130.64) --
	(236.19,130.64) --
	(236.19,135.63) --
	(231.20,135.63) --
	cycle;

\path[fill=fillColor] (239.51,133.97) --
	(244.51,133.97) --
	(244.51,138.97) --
	(239.51,138.97) --
	cycle;

\path[fill=fillColor] (247.83,137.46) --
	(252.82,137.46) --
	(252.82,142.45) --
	(247.83,142.45) --
	cycle;

\path[fill=fillColor] (256.14,140.45) --
	(261.14,140.45) --
	(261.14,145.45) --
	(256.14,145.45) --
	cycle;

\path[fill=fillColor] (264.45,143.78) --
	(269.45,143.78) --
	(269.45,148.78) --
	(264.45,148.78) --
	cycle;

\path[fill=fillColor] (272.77,146.72) --
	(277.76,146.72) --
	(277.76,151.71) --
	(272.77,151.71) --
	cycle;

\path[fill=fillColor] (281.08,149.90) --
	(286.08,149.90) --
	(286.08,154.89) --
	(281.08,154.89) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.94, 36.06) -- ( 46.00, 36.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.47, 32.52) -- ( 42.47, 39.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 47.25, 43.04) -- ( 54.32, 43.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.78, 39.50) -- ( 50.78, 46.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 55.57, 51.01) -- ( 62.63, 51.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.10, 47.48) -- ( 59.10, 54.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.88, 58.15) -- ( 70.94, 58.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 67.41, 54.62) -- ( 67.41, 61.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.19, 65.24) -- ( 79.26, 65.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.73, 61.70) -- ( 75.73, 68.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.51, 71.87) -- ( 87.57, 71.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.04, 68.33) -- ( 84.04, 75.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.82, 78.42) -- ( 95.89, 78.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.36, 74.89) -- ( 92.36, 81.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.14, 85.07) -- (104.20, 85.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.67, 81.54) -- (100.67, 88.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.45, 91.77) -- (112.52, 91.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.98, 88.23) -- (108.98, 95.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.77, 97.23) -- (120.83, 97.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.30, 93.70) -- (117.30,100.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.08,102.98) -- (129.14,102.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.61, 99.45) -- (125.61,106.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.39,108.23) -- (137.46,108.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.93,104.70) -- (133.93,111.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.71,113.74) -- (145.77,113.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.24,110.21) -- (142.24,117.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.02,119.44) -- (154.09,119.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.55,115.91) -- (150.55,122.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.34,124.58) -- (162.40,124.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.87,121.05) -- (158.87,128.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.65,129.41) -- (170.71,129.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.18,125.87) -- (167.18,132.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.96,134.32) -- (179.03,134.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.50,130.79) -- (175.50,137.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.28,140.02) -- (187.34,140.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.81,136.49) -- (183.81,143.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.59,144.84) -- (195.66,144.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.12,141.31) -- (192.12,148.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.91,150.03) -- (203.97,150.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.44,146.50) -- (200.44,153.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.22,154.23) -- (212.28,154.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.75,150.70) -- (208.75,157.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.53,159.05) -- (220.60,159.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.07,155.52) -- (217.07,162.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.85,163.83) -- (228.91,163.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.38,160.30) -- (225.38,167.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.16,168.26) -- (237.23,168.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.70,164.72) -- (233.70,171.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.48,172.64) -- (245.54,172.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.01,169.11) -- (242.01,176.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.79,177.48) -- (253.86,177.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.32,173.94) -- (250.32,181.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.11,181.38) -- (262.17,181.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (258.64,177.84) -- (258.64,184.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.42,185.89) -- (270.48,185.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.95,182.35) -- (266.95,189.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.73,189.84) -- (278.80,189.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.27,186.31) -- (275.27,193.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,194.15) -- (287.11,194.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,190.62) -- (283.58,197.68);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 42.47, 40.20) circle (  2.50);

\path[fill=fillColor] ( 50.78, 41.22) circle (  2.50);

\path[fill=fillColor] ( 59.10, 41.25) circle (  2.50);

\path[fill=fillColor] ( 67.41, 40.48) circle (  2.50);

\path[fill=fillColor] ( 75.73, 41.69) circle (  2.50);

\path[fill=fillColor] ( 84.04, 41.00) circle (  2.50);

\path[fill=fillColor] ( 92.36, 41.07) circle (  2.50);

\path[fill=fillColor] (100.67, 41.57) circle (  2.50);

\path[fill=fillColor] (108.98, 40.91) circle (  2.50);

\path[fill=fillColor] (117.30, 41.28) circle (  2.50);

\path[fill=fillColor] (125.61, 40.87) circle (  2.50);

\path[fill=fillColor] (133.93, 40.53) circle (  2.50);

\path[fill=fillColor] (142.24, 40.65) circle (  2.50);

\path[fill=fillColor] (150.55, 41.43) circle (  2.50);

\path[fill=fillColor] (158.87, 40.83) circle (  2.50);

\path[fill=fillColor] (167.18, 41.46) circle (  2.50);

\path[fill=fillColor] (175.50, 41.54) circle (  2.50);

\path[fill=fillColor] (183.81, 41.28) circle (  2.50);

\path[fill=fillColor] (192.12, 41.18) circle (  2.50);

\path[fill=fillColor] (200.44, 41.05) circle (  2.50);

\path[fill=fillColor] (208.75, 41.17) circle (  2.50);

\path[fill=fillColor] (217.07, 40.69) circle (  2.50);

\path[fill=fillColor] (225.38, 41.23) circle (  2.50);

\path[fill=fillColor] (233.70, 40.72) circle (  2.50);

\path[fill=fillColor] (242.01, 40.73) circle (  2.50);

\path[fill=fillColor] (250.32, 41.40) circle (  2.50);

\path[fill=fillColor] (258.64, 41.47) circle (  2.50);

\path[fill=fillColor] (266.95, 41.12) circle (  2.50);

\path[fill=fillColor] (275.27, 41.34) circle (  2.50);

\path[fill=fillColor] (283.58, 41.00) circle (  2.50);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.16, 30.69) rectangle (283.58,194.15);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 28.82) {4.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 72.16) {5.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,115.50) {5.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,158.84) {6.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 31.85) --
	( 34.16, 31.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 75.19) --
	( 34.16, 75.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,118.53) --
	( 34.16,118.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,161.87) --
	( 34.16,161.87);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 27.94) --
	( 34.16, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.30, 27.94) --
	(117.30, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.44, 27.94) --
	(200.44, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 34.16, 19.68) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (117.30, 19.68) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (200.44, 19.68) {0.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (158.87,  7.64) {Exponential growth rate $r$ (1/day)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,112.42) {Mean generation/serial interval};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.16,202.22) {C};
\end{scope}
\begin{scope}
\path[clip] (289.08,  0.00) rectangle (578.16,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.08,  0.00) rectangle (578.16,216.81);
\end{scope}
\begin{scope}
\path[clip] (323.24, 30.69) rectangle (572.66,194.15);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (323.24, 30.69) rectangle (572.66,194.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (331.55, 49.95) --
	(334.60, 49.96) --
	(337.65, 49.96) --
	(340.71, 49.96) --
	(343.76, 49.97) --
	(346.81, 49.97) --
	(349.86, 49.98) --
	(352.91, 49.98) --
	(355.97, 49.98) --
	(359.02, 49.98) --
	(362.07, 49.99) --
	(365.12, 49.99) --
	(368.17, 49.99) --
	(371.23, 49.99) --
	(374.28, 49.99) --
	(377.33, 49.99) --
	(380.38, 50.00) --
	(383.43, 50.00) --
	(386.49, 50.00) --
	(389.54, 50.00) --
	(392.59, 50.00) --
	(395.64, 50.00) --
	(398.69, 50.00) --
	(401.75, 50.00) --
	(404.80, 50.00) --
	(407.85, 50.00) --
	(410.90, 50.00) --
	(413.95, 49.99) --
	(417.01, 49.99) --
	(420.06, 49.99) --
	(423.11, 49.99) --
	(426.16, 49.99) --
	(429.21, 49.98) --
	(432.27, 49.98) --
	(435.32, 49.97) --
	(438.37, 49.96) --
	(441.42, 49.96) --
	(444.48, 49.95) --
	(447.53, 49.95) --
	(450.58, 49.95) --
	(453.63, 49.95) --
	(456.68, 49.95) --
	(459.74, 49.95) --
	(462.79, 49.95) --
	(465.84, 49.95) --
	(468.89, 49.95) --
	(471.94, 49.95) --
	(475.00, 49.96) --
	(478.05, 49.96) --
	(481.10, 49.96) --
	(484.15, 49.96) --
	(487.20, 49.96) --
	(490.26, 49.97) --
	(493.31, 49.97) --
	(496.36, 49.97) --
	(499.41, 49.97) --
	(502.46, 49.98) --
	(505.52, 49.98) --
	(508.57, 49.98) --
	(511.62, 49.99) --
	(514.67, 49.99) --
	(517.72, 49.99) --
	(520.78, 49.99) --
	(523.83, 49.99) --
	(526.88, 50.00) --
	(529.93, 50.00) --
	(532.98, 50.00) --
	(536.04, 50.00) --
	(539.09, 50.01) --
	(542.14, 50.01) --
	(545.19, 50.01) --
	(548.24, 50.01) --
	(551.30, 50.01) --
	(554.35, 50.02) --
	(557.40, 50.02) --
	(560.45, 50.02) --
	(563.50, 50.02) --
	(566.56, 50.02) --
	(569.61, 50.02) --
	(572.66, 50.02);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (331.55,128.70) --
	(334.60,127.69) --
	(337.65,126.70) --
	(340.71,125.73) --
	(343.76,124.77) --
	(346.81,123.83) --
	(349.86,122.90) --
	(352.91,122.00) --
	(355.97,121.11) --
	(359.02,120.24) --
	(362.07,119.39) --
	(365.12,118.55) --
	(368.17,117.74) --
	(371.23,116.94) --
	(374.28,116.16) --
	(377.33,115.39) --
	(380.38,114.64) --
	(383.43,113.91) --
	(386.49,113.20) --
	(389.54,112.50) --
	(392.59,111.82) --
	(395.64,111.16) --
	(398.69,110.53) --
	(401.75,109.91) --
	(404.80,109.32) --
	(407.85,108.74) --
	(410.90,108.18) --
	(413.95,107.63) --
	(417.01,107.09) --
	(420.06,106.55) --
	(423.11,106.03) --
	(426.16,105.52) --
	(429.21,105.04) --
	(432.27,104.58) --
	(435.32,104.14) --
	(438.37,103.71) --
	(441.42,103.28) --
	(444.48,102.85) --
	(447.53,102.42) --
	(450.58,101.98) --
	(453.63,101.56) --
	(456.68,101.15) --
	(459.74,100.75) --
	(462.79,100.36) --
	(465.84, 99.98) --
	(468.89, 99.60) --
	(471.94, 99.23) --
	(475.00, 98.86) --
	(478.05, 98.49) --
	(481.10, 98.12) --
	(484.15, 97.75) --
	(487.20, 97.39) --
	(490.26, 97.04) --
	(493.31, 96.69) --
	(496.36, 96.35) --
	(499.41, 96.01) --
	(502.46, 95.67) --
	(505.52, 95.35) --
	(508.57, 95.02) --
	(511.62, 94.70) --
	(514.67, 94.39) --
	(517.72, 94.08) --
	(520.78, 93.77) --
	(523.83, 93.47) --
	(526.88, 93.17) --
	(529.93, 92.88) --
	(532.98, 92.60) --
	(536.04, 92.32) --
	(539.09, 92.04) --
	(542.14, 91.77) --
	(545.19, 91.50) --
	(548.24, 91.24) --
	(551.30, 90.99) --
	(554.35, 90.74) --
	(557.40, 90.49) --
	(560.45, 90.25) --
	(563.50, 90.01) --
	(566.56, 89.78) --
	(569.61, 89.55) --
	(572.66, 89.33);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (331.55,158.08) --
	(334.60,156.41) --
	(337.65,154.76) --
	(340.71,153.14) --
	(343.76,151.56) --
	(346.81,150.00) --
	(349.86,148.47) --
	(352.91,146.97) --
	(355.97,145.51) --
	(359.02,144.07) --
	(362.07,142.67) --
	(365.12,141.30) --
	(368.17,139.95) --
	(371.23,138.64) --
	(374.28,137.36) --
	(377.33,136.10) --
	(380.38,134.88) --
	(383.43,133.68) --
	(386.49,132.51) --
	(389.54,131.36) --
	(392.59,130.25) --
	(395.64,129.18) --
	(398.69,128.15) --
	(401.75,127.16) --
	(404.80,126.20) --
	(407.85,125.26) --
	(410.90,124.35) --
	(413.95,123.47) --
	(417.01,122.60) --
	(420.06,121.74) --
	(423.11,120.90) --
	(426.16,120.08) --
	(429.21,119.31) --
	(432.27,118.58) --
	(435.32,117.87) --
	(438.37,117.18) --
	(441.42,116.50) --
	(444.48,115.82) --
	(447.53,115.13) --
	(450.58,114.43) --
	(453.63,113.77) --
	(456.68,113.12) --
	(459.74,112.48) --
	(462.79,111.86) --
	(465.84,111.26) --
	(468.89,110.66) --
	(471.94,110.08) --
	(475.00,109.50) --
	(478.05,108.92) --
	(481.10,108.34) --
	(484.15,107.77) --
	(487.20,107.20) --
	(490.26,106.65) --
	(493.31,106.10) --
	(496.36,105.57) --
	(499.41,105.04) --
	(502.46,104.53) --
	(505.52,104.01) --
	(508.57,103.51) --
	(511.62,103.02) --
	(514.67,102.53) --
	(517.72,102.05) --
	(520.78,101.57) --
	(523.83,101.11) --
	(526.88,100.65) --
	(529.93,100.21) --
	(532.98, 99.77) --
	(536.04, 99.33) --
	(539.09, 98.91) --
	(542.14, 98.50) --
	(545.19, 98.09) --
	(548.24, 97.69) --
	(551.30, 97.30) --
	(554.35, 96.92) --
	(557.40, 96.54) --
	(560.45, 96.17) --
	(563.50, 95.82) --
	(566.56, 95.46) --
	(569.61, 95.12) --
	(572.66, 94.79);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (331.55,189.58) --
	(334.60,187.22) --
	(337.65,184.90) --
	(340.71,182.62) --
	(343.76,180.39) --
	(346.81,178.20) --
	(349.86,176.05) --
	(352.91,173.94) --
	(355.97,171.88) --
	(359.02,169.87) --
	(362.07,167.90) --
	(365.12,165.97) --
	(368.17,164.09) --
	(371.23,162.25) --
	(374.28,160.45) --
	(377.33,158.70) --
	(380.38,156.98) --
	(383.43,155.31) --
	(386.49,153.67) --
	(389.54,152.07) --
	(392.59,150.52) --
	(395.64,149.04) --
	(398.69,147.61) --
	(401.75,146.23) --
	(404.80,144.89) --
	(407.85,143.60) --
	(410.90,142.34) --
	(413.95,141.12) --
	(417.01,139.92) --
	(420.06,138.73) --
	(423.11,137.56) --
	(426.16,136.44) --
	(429.21,135.38) --
	(432.27,134.37) --
	(435.32,133.39) --
	(438.37,132.44) --
	(441.42,131.51) --
	(444.48,130.57) --
	(447.53,129.63) --
	(450.58,128.68) --
	(453.63,127.76) --
	(456.68,126.87) --
	(459.74,126.01) --
	(462.79,125.17) --
	(465.84,124.34) --
	(468.89,123.53) --
	(471.94,122.73) --
	(475.00,121.94) --
	(478.05,121.15) --
	(481.10,120.36) --
	(484.15,119.59) --
	(487.20,118.82) --
	(490.26,118.07) --
	(493.31,117.34) --
	(496.36,116.61) --
	(499.41,115.90) --
	(502.46,115.20) --
	(505.52,114.52) --
	(508.57,113.84) --
	(511.62,113.17) --
	(514.67,112.51) --
	(517.72,111.86) --
	(520.78,111.23) --
	(523.83,110.60) --
	(526.88,109.99) --
	(529.93,109.39) --
	(532.98,108.80) --
	(536.04,108.22) --
	(539.09,107.66) --
	(542.14,107.10) --
	(545.19,106.56) --
	(548.24,106.03) --
	(551.30,105.51) --
	(554.35,105.00) --
	(557.40,104.50) --
	(560.45,104.02) --
	(563.50,103.54) --
	(566.56,103.08) --
	(569.61,102.63) --
	(572.66,102.19);
\definecolor{fillColor}{RGB}{230,159,0}

\path[fill=fillColor] (331.55,132.76) --
	(334.91,126.93) --
	(328.19,126.93) --
	cycle;

\path[fill=fillColor] (339.86,130.03) --
	(343.23,124.20) --
	(336.50,124.20) --
	cycle;

\path[fill=fillColor] (348.18,127.27) --
	(351.54,121.44) --
	(344.81,121.44) --
	cycle;

\path[fill=fillColor] (356.49,124.54) --
	(359.86,118.71) --
	(353.13,118.71) --
	cycle;

\path[fill=fillColor] (364.81,122.40) --
	(368.17,116.58) --
	(361.44,116.58) --
	cycle;

\path[fill=fillColor] (373.12,120.30) --
	(376.48,114.48) --
	(369.76,114.48) --
	cycle;

\path[fill=fillColor] (381.44,118.23) --
	(384.80,112.40) --
	(378.07,112.40) --
	cycle;

\path[fill=fillColor] (389.75,116.23) --
	(393.11,110.40) --
	(386.39,110.40) --
	cycle;

\path[fill=fillColor] (398.06,114.29) --
	(401.43,108.46) --
	(394.70,108.46) --
	cycle;

\path[fill=fillColor] (406.38,112.64) --
	(409.74,106.81) --
	(403.01,106.81) --
	cycle;

\path[fill=fillColor] (414.69,111.28) --
	(418.06,105.45) --
	(411.33,105.45) --
	cycle;

\path[fill=fillColor] (423.01,109.94) --
	(426.37,104.12) --
	(419.64,104.12) --
	cycle;

\path[fill=fillColor] (431.32,108.67) --
	(434.68,102.84) --
	(427.96,102.84) --
	cycle;

\path[fill=fillColor] (439.63,107.39) --
	(443.00,101.56) --
	(436.27,101.56) --
	cycle;

\path[fill=fillColor] (447.95,106.36) --
	(451.31,100.53) --
	(444.58,100.53) --
	cycle;

\path[fill=fillColor] (456.26,105.24) --
	(459.63, 99.41) --
	(452.90, 99.41) --
	cycle;

\path[fill=fillColor] (464.58,104.30) --
	(467.94, 98.47) --
	(461.21, 98.47) --
	cycle;

\path[fill=fillColor] (472.89,102.96) --
	(476.25, 97.14) --
	(469.53, 97.14) --
	cycle;

\path[fill=fillColor] (481.20,101.91) --
	(484.57, 96.08) --
	(477.84, 96.08) --
	cycle;

\path[fill=fillColor] (489.52,100.96) --
	(492.88, 95.13) --
	(486.15, 95.13) --
	cycle;

\path[fill=fillColor] (497.83,100.04) --
	(501.20, 94.21) --
	(494.47, 94.21) --
	cycle;

\path[fill=fillColor] (506.15, 99.12) --
	(509.51, 93.30) --
	(502.78, 93.30) --
	cycle;

\path[fill=fillColor] (514.46, 98.26) --
	(517.82, 92.43) --
	(511.10, 92.43) --
	cycle;

\path[fill=fillColor] (522.78, 97.51) --
	(526.14, 91.68) --
	(519.41, 91.68) --
	cycle;

\path[fill=fillColor] (531.09, 96.69) --
	(534.45, 90.87) --
	(527.73, 90.87) --
	cycle;

\path[fill=fillColor] (539.40, 96.04) --
	(542.77, 90.21) --
	(536.04, 90.21) --
	cycle;

\path[fill=fillColor] (547.72, 95.19) --
	(551.08, 89.36) --
	(544.35, 89.36) --
	cycle;

\path[fill=fillColor] (556.03, 94.44) --
	(559.40, 88.61) --
	(552.67, 88.61) --
	cycle;

\path[fill=fillColor] (564.35, 93.85) --
	(567.71, 88.03) --
	(560.98, 88.03) --
	cycle;

\path[fill=fillColor] (572.66, 93.15) --
	(576.02, 87.33) --
	(569.30, 87.33) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] (329.05,155.91) --
	(334.05,155.91) --
	(334.05,160.91) --
	(329.05,160.91) --
	cycle;

\path[fill=fillColor] (337.37,151.39) --
	(342.36,151.39) --
	(342.36,156.38) --
	(337.37,156.38) --
	cycle;

\path[fill=fillColor] (345.68,146.74) --
	(350.68,146.74) --
	(350.68,151.74) --
	(345.68,151.74) --
	cycle;

\path[fill=fillColor] (353.99,142.21) --
	(358.99,142.21) --
	(358.99,147.21) --
	(353.99,147.21) --
	cycle;

\path[fill=fillColor] (362.31,138.68) --
	(367.30,138.68) --
	(367.30,143.67) --
	(362.31,143.67) --
	cycle;

\path[fill=fillColor] (370.62,135.24) --
	(375.62,135.24) --
	(375.62,140.23) --
	(370.62,140.23) --
	cycle;

\path[fill=fillColor] (378.94,131.84) --
	(383.93,131.84) --
	(383.93,136.84) --
	(378.94,136.84) --
	cycle;

\path[fill=fillColor] (387.25,128.58) --
	(392.25,128.58) --
	(392.25,133.58) --
	(387.25,133.58) --
	cycle;

\path[fill=fillColor] (395.57,125.47) --
	(400.56,125.47) --
	(400.56,130.46) --
	(395.57,130.46) --
	cycle;

\path[fill=fillColor] (403.88,122.80) --
	(408.88,122.80) --
	(408.88,127.79) --
	(403.88,127.79) --
	cycle;

\path[fill=fillColor] (412.19,120.61) --
	(417.19,120.61) --
	(417.19,125.61) --
	(412.19,125.61) --
	cycle;

\path[fill=fillColor] (420.51,118.48) --
	(425.50,118.48) --
	(425.50,123.48) --
	(420.51,123.48) --
	cycle;

\path[fill=fillColor] (428.82,116.42) --
	(433.82,116.42) --
	(433.82,121.41) --
	(428.82,121.41) --
	cycle;

\path[fill=fillColor] (437.14,114.36) --
	(442.13,114.36) --
	(442.13,119.36) --
	(437.14,119.36) --
	cycle;

\path[fill=fillColor] (445.45,112.70) --
	(450.45,112.70) --
	(450.45,117.70) --
	(445.45,117.70) --
	cycle;

\path[fill=fillColor] (453.76,110.90) --
	(458.76,110.90) --
	(458.76,115.90) --
	(453.76,115.90) --
	cycle;

\path[fill=fillColor] (462.08,109.42) --
	(467.07,109.42) --
	(467.07,114.41) --
	(462.08,114.41) --
	cycle;

\path[fill=fillColor] (470.39,107.36) --
	(475.39,107.36) --
	(475.39,112.35) --
	(470.39,112.35) --
	cycle;

\path[fill=fillColor] (478.71,105.71) --
	(483.70,105.71) --
	(483.70,110.71) --
	(478.71,110.71) --
	cycle;

\path[fill=fillColor] (487.02,104.22) --
	(492.02,104.22) --
	(492.02,109.21) --
	(487.02,109.21) --
	cycle;

\path[fill=fillColor] (495.34,102.80) --
	(500.33,102.80) --
	(500.33,107.79) --
	(495.34,107.79) --
	cycle;

\path[fill=fillColor] (503.65,101.36) --
	(508.64,101.36) --
	(508.64,106.36) --
	(503.65,106.36) --
	cycle;

\path[fill=fillColor] (511.96,100.01) --
	(516.96,100.01) --
	(516.96,105.01) --
	(511.96,105.01) --
	cycle;

\path[fill=fillColor] (520.28, 98.85) --
	(525.27, 98.85) --
	(525.27,103.85) --
	(520.28,103.85) --
	cycle;

\path[fill=fillColor] (528.59, 97.60) --
	(533.59, 97.60) --
	(533.59,102.59) --
	(528.59,102.59) --
	cycle;

\path[fill=fillColor] (536.91, 96.60) --
	(541.90, 96.60) --
	(541.90,101.59) --
	(536.91,101.59) --
	cycle;

\path[fill=fillColor] (545.22, 95.31) --
	(550.22, 95.31) --
	(550.22,100.31) --
	(545.22,100.31) --
	cycle;

\path[fill=fillColor] (553.53, 94.15) --
	(558.53, 94.15) --
	(558.53, 99.14) --
	(553.53, 99.14) --
	cycle;

\path[fill=fillColor] (561.85, 93.24) --
	(566.84, 93.24) --
	(566.84, 98.24) --
	(561.85, 98.24) --
	cycle;

\path[fill=fillColor] (570.16, 92.17) --
	(575.16, 92.17) --
	(575.16, 97.17) --
	(570.16, 97.17) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.02,190.09) -- (335.08,190.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.55,186.56) -- (331.55,193.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.33,183.71) -- (343.40,183.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.86,180.17) -- (339.86,187.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.65,177.10) -- (351.71,177.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.18,173.57) -- (348.18,180.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.96,170.72) -- (360.02,170.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.49,167.18) -- (356.49,174.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,165.75) -- (368.34,165.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,162.22) -- (364.81,169.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,160.93) -- (376.65,160.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,157.40) -- (373.12,164.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,156.17) -- (384.97,156.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,152.64) -- (381.44,159.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,151.65) -- (393.28,151.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,148.12) -- (389.75,155.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,147.35) -- (401.60,147.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,143.82) -- (398.06,150.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,143.66) -- (409.91,143.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,140.13) -- (406.38,147.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,140.64) -- (418.22,140.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,137.11) -- (414.69,144.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,137.72) -- (426.54,137.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,134.19) -- (423.01,141.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,134.84) -- (434.85,134.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,131.31) -- (431.32,138.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,132.03) -- (443.17,132.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,128.50) -- (439.63,135.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,129.73) -- (451.48,129.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,126.20) -- (447.95,133.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,127.22) -- (459.79,127.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,123.69) -- (456.26,130.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,125.20) -- (468.11,125.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,121.67) -- (464.58,128.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,122.43) -- (476.42,122.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,118.90) -- (472.89,125.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,120.20) -- (484.74,120.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,116.67) -- (481.20,123.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,118.17) -- (493.05,118.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,114.64) -- (489.52,121.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,116.28) -- (501.36,116.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,112.74) -- (497.83,119.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,114.31) -- (509.68,114.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,110.78) -- (506.15,117.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,112.49) -- (517.99,112.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,108.96) -- (514.46,116.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,110.92) -- (526.31,110.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,107.38) -- (522.78,114.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,109.24) -- (534.62,109.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,105.71) -- (531.09,112.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,107.92) -- (542.94,107.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,104.39) -- (539.40,111.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,106.23) -- (551.25,106.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72,102.70) -- (547.72,109.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,104.64) -- (559.56,104.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03,101.11) -- (556.03,108.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,103.43) -- (567.88,103.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35, 99.90) -- (564.35,106.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,102.01) -- (576.19,102.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66, 98.48) -- (572.66,105.55);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (331.55, 49.94) circle (  2.50);

\path[fill=fillColor] (339.86, 50.02) circle (  2.50);

\path[fill=fillColor] (348.18, 50.01) circle (  2.50);

\path[fill=fillColor] (356.49, 49.81) circle (  2.50);

\path[fill=fillColor] (364.81, 49.97) circle (  2.50);

\path[fill=fillColor] (373.12, 50.10) circle (  2.50);

\path[fill=fillColor] (381.44, 49.98) circle (  2.50);

\path[fill=fillColor] (389.75, 50.04) circle (  2.50);

\path[fill=fillColor] (398.06, 50.05) circle (  2.50);

\path[fill=fillColor] (406.38, 49.95) circle (  2.50);

\path[fill=fillColor] (414.69, 50.17) circle (  2.50);

\path[fill=fillColor] (423.01, 49.86) circle (  2.50);

\path[fill=fillColor] (431.32, 49.74) circle (  2.50);

\path[fill=fillColor] (439.63, 49.98) circle (  2.50);

\path[fill=fillColor] (447.95, 50.13) circle (  2.50);

\path[fill=fillColor] (456.26, 50.04) circle (  2.50);

\path[fill=fillColor] (464.58, 49.94) circle (  2.50);

\path[fill=fillColor] (472.89, 49.95) circle (  2.50);

\path[fill=fillColor] (481.20, 49.84) circle (  2.50);

\path[fill=fillColor] (489.52, 49.92) circle (  2.50);

\path[fill=fillColor] (497.83, 49.86) circle (  2.50);

\path[fill=fillColor] (506.15, 50.08) circle (  2.50);

\path[fill=fillColor] (514.46, 49.96) circle (  2.50);

\path[fill=fillColor] (522.78, 50.12) circle (  2.50);

\path[fill=fillColor] (531.09, 50.25) circle (  2.50);

\path[fill=fillColor] (539.40, 49.77) circle (  2.50);

\path[fill=fillColor] (547.72, 49.90) circle (  2.50);

\path[fill=fillColor] (556.03, 50.13) circle (  2.50);

\path[fill=fillColor] (564.35, 50.12) circle (  2.50);

\path[fill=fillColor] (572.66, 49.92) circle (  2.50);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.24, 30.69) rectangle (572.66,194.15);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29, 27.66) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29, 78.74) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,129.82) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,180.91) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49, 30.69) --
	(323.24, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49, 81.77) --
	(323.24, 81.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,132.85) --
	(323.24,132.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,183.94) --
	(323.24,183.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.24, 27.94) --
	(323.24, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (406.38, 27.94) --
	(406.38, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (489.52, 27.94) --
	(489.52, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (323.24, 19.68) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (406.38, 19.68) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (489.52, 19.68) {0.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (447.95,  7.64) {Exponential growth rate $r$ (1/day)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,112.42) {Squared coefficient of variation};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (323.24,202.22) {D};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-04-09 serial.tex
initial push

\documentclass[12pt]{article}
\usepackage[top=1in,left=1in, right = 1in, footskip=1in]{geometry}

\usepackage{graphicx}
%\usepackage{adjustbox}

%% \newcommand{\comment}{\showcomment}
\newcommand{\comment}{\nocomment}

\newcommand{\showcomment}[3]{\textcolor{#1}{\textbf{[#2: }\textsl{#3}\textbf{]}}}
\newcommand{\nocomment}[3]{}

\newcommand{\jd}[1]{\comment{cyan}{JD}{#1}}
\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}

\newcommand{\eref}[1]{Eq.~\ref{eq:#1}}
\newcommand{\fref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Fref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\sref}[1]{Sec.~\ref{#1}}
\newcommand{\frange}[2]{Fig.~\ref{fig:#1}--\ref{fig:#2}}
\newcommand{\tref}[1]{Table~\ref{tab:#1}}
\newcommand{\tlab}[1]{\label{tab:#1}}
\newcommand{\seminar}{SE\mbox{$^m$}I\mbox{$^n$}R}

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}

% \usepackage{lineno}
% \linenumbers

\usepackage[pdfencoding=auto, psdextra]{hyperref}

\usepackage{natbib}
\bibliographystyle{chicago}
\date{\today}

\usepackage{xspace}
\newcommand*{\ie}{i.e.\@\xspace}

\usepackage{color}

\newcommand{\Rx}[1]{\ensuremath{{\mathcal R}_{#1}}} 
\newcommand{\Ro}{\Rx{0}}
\newcommand{\RR}{\ensuremath{{\mathcal R}}}
\newcommand{\Rhat}{\ensuremath{{\hat\RR}}}
\newcommand{\tsub}[2]{#1_{{\textrm{\tiny #2}}}}

\begin{document}

\begin{flushleft}{
	\Large
	\textbf\newline{
		Understanding serial interval distributions: applications to the COVID-19 pandemic
	}
}
Sang Woo Park
\end{flushleft}

\section*{Abstract}

\pagebreak

%The key distributions for understanding the spread of COVID-19 include:
%\begin{enumerate}
%  \item Incubation period distribution: time between infection and symptom onset \citep{backer2020incubation, %li2020early, linton2020incubation, tian2020characteristics}
%  \item Serial interval distribution: time between symptom onset of an infector and an infectee \citep{du2020s%erial, nishiura2020serial, zhao2020estimating}
%  \item Generation interval distribution: time between infection of an infector and an infectee \citep{ganyani%2020estimating}
%\end{enumerate}

\section{Introduction}

Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its basic reproduction number $\mathcal R_0$.
The basic reproduction number, which is defined as the average number of secondary cases caused by a primary case, allows us to predict the extent to which a disease will spread and the amount of intervention to prevent an outbreak.
Since the basic reproduction number cannot be measured directly, it is often inferred from the observed exponential growth rate using generation or serial intervals.

Generation intervals are defined as the time between when an individual is infected and when an individual infects another person.
Similarly, serial intervals are defined as the time between when an infector and an infectee become symptomatic.
While

We show that the serial-interval distribution can provide a correct link between the speed

\section{Backward and forward delay distributions}

\bibliography{serial}

\end{document}

### 2020-04-09 figure_sir.R

@@ -1,0 +1,285 @@
+library(tidyr)
+library(dplyr)
+library(ggplot2); theme_set(theme_bw())
+library(gridExtra)
+source("renewal_det.R")
+
+load("sir_sim.rda")
+
+rr <- renewal_det(tmax=110)
+
+plot(sir_sim$data, type="l", log="y")
+
+lines(rr$tvec, cumsum(rr$Ivec), col=2)
+
+## model parameters
+meanlog <- 1.621
+sdlog <- 0.418
+scale <- 5.5
+shape <- 4.1
+r <- 1/5.5
+
+set.seed(101)
+inc <- rlnorm(50000, meanlog, sdlog)
+minc <- mean(inc)
+winc <- weighted.mean(inc, exp(-r*inc))
+
+gen <- rweibull(50000, shape, scale)
+mgen <- mean(gen)
+wgen <- weighted.mean(gen, exp(-r*gen))
+
+serforward <- gen+rlnorm(50000, meanlog, sdlog)
+ser <- -inc+serforward
+mser <- mean(ser)
+ser2 <- -sample(inc, prob=exp(-r*inc), replace=TRUE)+serforward
+ww <- exp(-r*ser2)
+ww[ser2 < 0] <- 1
+wser <- weighted.mean(ser2, ww)
+
+g1 <- ggplot(sir_sim$data) +
+  stat_function(fun=function(x)15*exp(1/5.5*x), lty=2) +
+  geom_line(aes(time, infected)) +
+  scale_x_continuous("Time", expand=c(0, 0), limits=c(0, 80)) +
+  scale_y_log10("Cumulative incidence", expand=c(0, 0), limits=c(10, 49999)) +
+  ggtitle("A") +
+  theme(
+    panel.grid = element_blank(),
+    panel.border = element_blank(),
+    axis.line = element_line()
+  )
+
+tcut <- 10:32*2
+icut <- -80:80/2
+
+incdata0 <- data.frame(
+  cohort=sir_sim$t_infected,
+  tdiff=sir_sim$t_symptomatic-sir_sim$t_infected
+) %>%
+  filter(!is.na(cohort), !is.na(tdiff), cohort > 20, cohort <= 64) %>%
+  mutate(
+    cc=cut(cohort, tcut),
+    tt=cut(tdiff, icut)
+  ) %>%
+  group_by(cc, tt) %>%
+  summarize(
+    size=length(tt)
+  ) %>%
+  mutate(
+    prop=size/sum(size)
+  ) %>%
[…]

### 2020-04-09 forward.R

@@ -1,0 +1,207 @@
+library(tidyr)
+library(dplyr)
+library(ggplot2); theme_set(theme_bw())
+library(gridExtra)
+source("renewal_det.R")
+
+load("sir_sim.rda")
+
+rr <- renewal_det()
+
+summfun <- function(dd) {
+  dd %>%
+    filter(!is.na(cohort), !is.na(tdiff), cohort > 0, cohort <= 100) %>%
+    mutate(
+      cc=cut(cohort, tcut)
+    ) %>%
+    group_by(cc) %>%
+    summarize(
+      mean=mean(tdiff)
+    ) %>%
+    ungroup %>%
+    mutate(
+      cc=as.character(cc),
+      cc=(as.numeric(gsub("\\(", "", gsub(",.*", "", cc)))+as.numeric(gsub("]", "", gsub(".*,", "", cc))))/2
+    )
+}
+
+## model parameters
+meanlog <- 1.621
+sdlog <- 0.418
+scale <- 5.5
+shape <- 4.1
+r <- rr$r
+
+detdata <- data.frame(
+  tvec=rr$tvec,
+  ci=rr$cI
+)
+
+g1 <- ggplot(sir_sim$data) +
+  geom_line(data=detdata, aes(tvec, ci)) +
+  geom_line(aes(time, infected), col=2) +
+  scale_x_continuous("Time", expand=c(0, 0), limits=c(0, 82)) +
+  scale_y_log10("Cumulative incidence", expand=c(0, 0), limits=c(10, 49999)) +
+  ggtitle("A") +
+  theme(
+    panel.grid = element_blank(),
+    panel.border = element_blank(),
+    axis.line = element_line()
+  )
+
+tcut <- 0:20*4
+
+incdata0 <- data.frame(
+  cohort=sir_sim$t_infected,
+  tdiff=sir_sim$t_symptomatic-sir_sim$t_infected
+) %>%
+  summfun()
+
+incdet <- data.frame(
+  tvec=rr$tvec,
+  mf=rr$mfinc
+)
+
+g2 <- ggplot(incdata0) +
+  geom_line(data=incdet, aes(tvec, mf)) +
+  geom_point(aes(cc, mean), shape=1, col="red") +
+  scale_x_continuous("Cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
+  scale_y_continuous("Forward incubation period (days)", expand=c(0, 0), limits=c(0, 7)) +
+  scale_fill_gradientn(colors=c("white", "black")) +
[…]

### 2020-04-09 rR.R

@@ -1,0 +1,259 @@
+library(dplyr)
+library(ggplot2); theme_set(theme_bw())
+library(tikzDevice)
+library(gridExtra)
+source("cpalette.R")
+
+## incubation!
+meanlog1 <- 1.621
+sdlog1 <- 0.418
+## generation
+shape <- 4.1
+scale <- 5.5
+
+## rough moment matching...for now... doesn't matter -- it works.
+mean(rweibull(50000, shape = shape, scale=scale))
+var(rweibull(50000, shape = shape, scale=scale))
+
+mean(rlnorm(50000, meanlog = 1.55, sdlog=0.27))
+var(rlnorm(50000, meanlog = 1.55, sdlog=0.27))
+
+serialR <- function(r=0.1,
+                    rho=0.5,
+                    meanlog1=1.621,
+                    sdlog1=0.418,
+                    meanlog2=1.55,
+                    sdlog2=0.27,
+                    nsim=100000,
+                    seed=101) {
+  set.seed(seed)
+  backinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
+  
+  backinc <- sample(backinc, replace=TRUE, prob=exp(-r*backinc))
+  
+  logbackinc <- log(backinc)
+  
+  muloggen <- meanlog2 + sdlog2 * rho * (logbackinc - meanlog1)/sdlog1
+  sigmaloggen <- sdlog2^2 * (1 - rho^2)
+  
+  forwardgen <- exp(rnorm(nsim, muloggen, sigmaloggen))
+  forwardinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
+  
+  ser <- -backinc + forwardgen + forwardinc
+  
+  list(
+    mean=mean(ser),
+    kappa=var(ser)/mean(ser)^2,
+    R=1/mean(exp(-r*ser))
+  )
+}
+
+serialR2 <- function(r=0.1,
+                    rho=0.5,
+                    meanlog1=1.621,
+                    sdlog1=0.418,
+                    meanlog2=1.55,
+                    sdlog2=0.27,
+                    nsim=100000,
+                    seed=101) {
+  set.seed(seed)
+  backinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
+  
+  logbackinc <- log(backinc)
+  
[…]

### 2020-04-09 renewal_det.R

@@ -1,0 +1,51 @@
+renewal_det <- function(R0=2.5,
+                        N=40000,
+                        S0=40000-10,
+                        dt=0.1,
+                        incfun=function(x) dlnorm(x, meanlog=1.621, sdlog=0.418),
+                        genfun=function(x) dweibull(x, shape=4.1, scale=5.5),
+                        I0=10,
+                        tmax=150,
+                        genmax=150) {
+  inc <- incfun(0:genmax*dt)
+  inc <- inc/sum(inc)
+  gen <- genfun(0:genmax*dt)
+  gen <- gen/sum(gen)
+  tvec <- seq(0, tmax, by=dt)
+  Ivec <- rep(0, dt*tmax)
+  
+  r <- optim(0.19, function(x) (1/sum(exp(-x*(0:genmax*dt)) * gen)-R0)^2,
+        lower=0.1,
+        upper=0.3,
+        method="Brent")[[1]]
+  
+  ## r=0.1904075 for R0=2.5
+  Ivec[1:genmax] <- exp(r*1:genmax*dt)
+  Ivec[1:genmax] <- I0*Ivec[1:genmax]/sum(Ivec[1:genmax])
+  Svec <- rep(0, dt*tmax)
+  Svec[1:genmax] <- N - cumsum(Ivec)
+  
+  for (i in (genmax+1):length(tvec)) {
+    Ivec[i] <- Svec[i-1] * R0 * sum(Ivec[max(1, i-genmax):(i-1)] * gen[min(i, genmax+1):2])/N
+    Svec[i] <- Svec[i-1] - Ivec[i]
+  }
+  
+  forwardgen <- sapply(1:(length(Svec)-genmax), function(x) gen[1:(1+genmax)]*Svec[x:(x+genmax)]/sum(gen[1:(1+genmax)]*Svec[x:(x+genmax)]))
+  backwardgen <- sapply((genmax+1):(length(Svec)), function(x) gen[1:(1+genmax)]*Ivec[x:(x-genmax)]/sum(gen[1:(1+genmax)]*Ivec[x:(x-genmax)]))
+  forwardinc <- sapply(1:(length(Svec)-genmax), function(x) inc)
+  backwardinc <- sapply((genmax+1):(length(Svec)), function(x) inc[1:(1+genmax)]*Ivec[x:(x-genmax)]/sum(inc[1:(1+genmax)]*Ivec[x:(x-genmax)]))
+  
[…]

### 2020-04-09 sir.R

@@ -1,0 +1,109 @@
+##' @param x a vector of nodes
+##' @param size number of nodes to pick at random
+sample2 <- function(x, size) {
+  if(length(x)==1) {
+    rep(x, size)
+  } else{
+    sample(x, size, replace=TRUE)
+  }
+}
+
+sir.full <- function(size,
+                     R0=2.5,
+                     meanlog=1.621,
+                     sdlog=0.418,
+                     scale=5.5,
+                     shape=4.1,
+                     I0,
+                     seed = NULL,
+                     imax,
+                     keep.intrinsic=FALSE){
+  
+  if (!is.null(seed)) set.seed(seed)
+  
+  V <- 1:size
+  
+  if (missing(I0)) {
+    if (missing(I0)) stop("specify the initial conditions")
+    
+  }
+  initial_infected <- 1:I0
+  
+  if (missing(imax)) imax <- size
+  
+  queue_v <- queue_t <- queue_infector <- rep(NA, I0)
+  
+  queue_v[1:I0] <- initial_infected 
+  queue_t[1:I0] <- 0
+  
+  t_infected <- t_symptomatic <- rep(NA, size)
+  t_infected[initial_infected] <- 0
+  
+  t_gillespie <- NULL
+  c_infected <- 0
+  
+  if (keep.intrinsic) {
+    intrinsic_generation <- vector('list', length(V))
+  } else {
+    intrinsic_generation <- NULL
+  }
+  
+  done <- rep(FALSE, size)
+  infected_by <- rep(NA, size)
+  
+  stop <- FALSE
+  
+  while (!stop) {
+    j.index <- which.min(queue_t)
+    j <- queue_v[j.index]
+    
+    infected_by[j] <- queue_infector[j.index]
+    t_infected[j] <- queue_t[j.index]
+    
+    t <- queue_t[j.index]; t_gillespie <- c(t_gillespie, t)
+    
+    incubation <- rlnorm(1, meanlog, sdlog)
+    t_symptomatic[j] <- t+incubation
+    
+    c_infected <- c_infected +1
+    
+    ncontact <- rpois(1, R0)
+    
+    n <- V[V != j]
+    
+    if (ncontact > 0) {
+      queue_v <- c(queue_v, sample2(n, ncontact))
+      queue_infector <- c(queue_infector, rep(j, ncontact))
+    }
+    
+    generation <- rweibull(ncontact, shape, scale)
+    
[…]

### 2020-04-09 sir_sim.R

@@ -1,0 +1,5 @@
+source("sir.R")
+
+sir_sim <- sir.full(size=40000, I0=10, seed=101, keep.intrinsic = TRUE)
+
+save("sir_sim", file="sir_sim.rda")

### 2020-04-09 rR.tex
started writing

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-09 01:19:07
+% Created by tikzDevice version 0.12.3 on 2020-04-09 18:48:49
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 35.86,249.99) --
-	( 38.99,250.83) --
-	( 42.13,251.68) --
-	( 45.26,252.56) --
-	( 48.40,253.45) --
-	( 51.53,254.37) --
-	( 54.67,255.30) --
-	( 57.81,256.26) --
-	( 60.94,257.23) --
-	( 64.08,258.23) --
-	( 67.21,259.24) --
-	( 70.35,260.28) --
-	( 73.48,261.33) --
-	( 76.62,262.40) --
-	( 79.76,263.50) --
-	( 82.89,264.61) --
-	( 86.03,265.75) --
-	( 89.16,266.90) --
-	( 92.30,268.08) --
-	( 95.43,269.28) --
-	( 98.57,270.49) --
-	(101.71,271.73) --
-	(104.84,272.98) --
-	(107.98,274.24) --
-	(111.11,275.53) --
-	(114.25,276.84) --
-	(117.39,278.17) --
-	(120.52,279.52) --
-	(123.66,280.90) --
-	(126.79,282.30) --
-	(129.93,283.73) --
-	(133.06,285.18) --
-	(136.20,286.64) --
-	(139.34,288.13) --
-	(142.47,289.63) --
-	(145.61,291.16) --
-	(148.74,292.71) --
-	(151.88,294.29) --
-	(155.01,295.91) --
-	(158.15,297.56) --
-	(161.29,299.22) --
-	(164.42,300.90) --
-	(167.56,302.61) --
-	(170.69,304.34) --
-	(173.83,306.09) --
-	(176.96,307.87) --
-	(180.10,309.69) --
-	(183.24,311.54) --
-	(186.37,313.42) --
-	(189.51,315.35) --
-	(192.64,317.30) --
-	(195.78,319.28) --
-	(198.91,321.29) --
-	(202.05,323.33) --
-	(205.19,325.39) --
-	(208.32,327.49) --
-	(211.46,329.62) --
-	(214.59,331.79) --
-	(217.73,334.00) --
-	(220.86,336.24) --
-	(224.00,338.53) --
-	(227.14,340.85) --
-	(230.27,343.21) --
-	(233.41,345.59) --
-	(236.54,348.02) --
-	(239.68,350.47) --
-	(242.82,352.96) --
-	(245.95,355.49) --
-	(249.09,358.05) --
-	(252.22,360.64) --
-	(255.36,363.27) --
-	(258.49,365.94) --
-	(261.63,368.64) --
-	(264.77,371.37) --
-	(267.90,374.15) --
-	(271.04,376.95) --
-	(274.17,379.79) --
-	(277.31,382.67) --
-	(280.44,385.58) --
-	(283.58,388.52);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.68) --
+	( 30.56,248.50) --
+	( 33.80,249.34) --
+	( 37.04,250.20) --
+	( 40.29,251.09) --
+	( 43.53,251.99) --
+	( 46.78,252.92) --
+	( 50.02,253.86) --
+	( 53.26,254.83) --
+	( 56.51,255.81) --
+	( 59.75,256.82) --
+	( 63.00,257.85) --
+	( 66.24,258.90) --
+	( 69.48,259.97) --
+	( 72.73,261.06) --
+	( 75.97,262.17) --
+	( 79.22,263.30) --
+	( 82.46,264.46) --
+	( 85.70,265.64) --
+	( 88.95,266.84) --
+	( 92.19,268.05) --
+	( 95.43,269.29) --
+	( 98.68,270.54) --
+	(101.92,271.81) --
+	(105.17,273.11) --
+	(108.41,274.42) --
+	(111.65,275.76) --
+	(114.90,277.13) --
+	(118.14,278.52) --
+	(121.39,279.93) --
+	(124.63,281.37) --
+	(127.87,282.82) --
+	(131.12,284.29) --
+	(134.36,285.79) --
+	(137.61,287.30) --
+	(140.85,288.84) --
+	(144.09,290.41) --
+	(147.34,292.01) --
+	(150.58,293.64) --
+	(153.82,295.30) --
+	(157.07,296.99) --
+	(160.31,298.71) --
+	(163.56,300.44) --
+	(166.80,302.19) --
+	(170.04,303.97) --
+	(173.29,305.78) --
+	(176.53,307.62) --
+	(179.78,309.49) --
+	(183.02,311.40) --
+	(186.26,313.35) --
+	(189.51,315.33) --
+	(192.75,317.36) --
+	(196.00,319.41) --
+	(199.24,321.50) --
+	(202.48,323.61) --
+	(205.73,325.76) --
+	(208.97,327.95) --
+	(212.21,330.17) --
+	(215.46,332.42) --
+	(218.70,334.72) --
+	(221.95,337.06) --
+	(225.19,339.44) --
+	(228.43,341.86) --
+	(231.68,344.31) --
+	(234.92,346.79) --
+	(238.17,349.31) --
+	(241.41,351.87) --
+	(244.65,354.47) --
+	(247.90,357.09) --
+	(251.14,359.76) --
+	(254.39,362.46) --
+	(257.63,365.21) --
+	(260.87,367.98) --
+	(264.12,370.80) --
+	(267.36,373.65) --
+	(270.60,376.54) --
+	(273.85,379.47) --
+	(277.09,382.43) --
+	(280.34,385.43) --
+	(283.58,388.46);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 35.86,249.94) --
-	( 38.99,250.75) --
-	( 42.13,251.59) --
-	( 45.26,252.45) --
-	( 48.40,253.32) --
-	( 51.53,254.22) --
-	( 54.67,255.14) --
-	( 57.81,256.08) --
-	( 60.94,257.04) --
-	( 64.08,258.02) --
-	( 67.21,259.02) --
-	( 70.35,260.04) --
-	( 73.48,261.08) --
-	( 76.62,262.14) --
-	( 79.76,263.22) --
-	( 82.89,264.33) --
-	( 86.03,265.45) --
-	( 89.16,266.60) --
-	( 92.30,267.77) --
-	( 95.43,268.96) --
-	( 98.57,270.16) --
-	(101.71,271.39) --
-	(104.84,272.63) --
-	(107.98,273.89) --
-	(111.11,275.17) --
-	(114.25,276.47) --
-	(117.39,277.79) --
-	(120.52,279.14) --
-	(123.66,280.51) --
-	(126.79,281.91) --
-	(129.93,283.34) --
-	(133.06,284.79) --
-	(136.20,286.25) --
-	(139.34,287.72) --
-	(142.47,289.22) --
-	(145.61,290.74) --
-	(148.74,292.29) --
-	(151.88,293.88) --
-	(155.01,295.51) --
-	(158.15,297.16) --
-	(161.29,298.84) --
-	(164.42,300.53) --
-	(167.56,302.25) --
-	(170.69,303.99) --
-	(173.83,305.76) --
-	(176.96,307.57) --
-	(180.10,309.41) --
-	(183.24,311.28) --
-	(186.37,313.20) --
-	(189.51,315.16) --
-	(192.64,317.16) --
-	(195.78,319.19) --
-	(198.91,321.24) --
-	(202.05,323.33) --
-	(205.19,325.45) --
-	(208.32,327.61) --
-	(211.46,329.80) --
-	(214.59,332.03) --
-	(217.73,334.31) --
-	(220.86,336.63) --
-	(224.00,339.00) --
-	(227.14,341.41) --
-	(230.27,343.86) --
-	(233.41,346.34) --
-	(236.54,348.86) --
-	(239.68,351.42) --
-	(242.82,354.02) --
-	(245.95,356.66) --
-	(249.09,359.33) --
-	(252.22,362.05) --
-	(255.36,364.80) --
-	(258.49,367.59) --
-	(261.63,370.43) --
-	(264.77,373.30) --
-	(267.90,376.22) --
-	(271.04,379.17) --
-	(274.17,382.16) --
-	(277.31,385.19) --
-	(280.44,388.26) --
-	(283.58,391.37);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.65) --
+	( 30.56,248.48) --
+	( 33.80,249.33) --
+	( 37.04,250.20) --
+	( 40.29,251.09) --
+	( 43.53,252.00) --
+	( 46.78,252.94) --
+	( 50.02,253.89) --
+	( 53.26,254.86) --
+	( 56.51,255.85) --
+	( 59.75,256.87) --
+	( 63.00,257.90) --
+	( 66.24,258.95) --
+	( 69.48,260.03) --
+	( 72.73,261.12) --
+	( 75.97,262.24) --
+	( 79.22,263.38) --
+	( 82.46,264.54) --
+	( 85.70,265.72) --
+	( 88.95,266.92) --
+	( 92.19,268.14) --
+	( 95.43,269.38) --
+	( 98.68,270.63) --
+	(101.92,271.91) --
+	(105.17,273.21) --
+	(108.41,274.52) --
+	(111.65,275.86) --
+	(114.90,277.23) --
+	(118.14,278.62) --
+	(121.39,280.03) --
+	(124.63,281.47) --
+	(127.87,282.92) --
+	(131.12,284.38) --
+	(134.36,285.87) --
+	(137.61,287.38) --
+	(140.85,288.91) --
+	(144.09,290.47) --
+	(147.34,292.06) --
+	(150.58,293.68) --
+	(153.82,295.34) --
+	(157.07,297.03) --
+	(160.31,298.74) --
+	(163.56,300.47) --
+	(166.80,302.22) --
+	(170.04,304.00) --
+	(173.29,305.80) --
+	(176.53,307.64) --
+	(179.78,309.51) --
+	(183.02,311.41) --
+	(186.26,313.36) --
+	(189.51,315.34) --
+	(192.75,317.37) --
+	(196.00,319.42) --
+	(199.24,321.50) --
+	(202.48,323.61) --
+	(205.73,325.76) --
+	(208.97,327.94) --
+	(212.21,330.16) --
+	(215.46,332.42) --
+	(218.70,334.72) --
+	(221.95,337.06) --
+	(225.19,339.44) --
+	(228.43,341.86) --
+	(231.68,344.32) --
+	(234.92,346.81) --
+	(238.17,349.33) --
+	(241.41,351.90) --
+	(244.65,354.49) --
+	(247.90,357.13) --
+	(251.14,359.80) --
+	(254.39,362.51) --
+	(257.63,365.26) --
+	(260.87,368.04) --
+	(264.12,370.87) --
+	(267.36,373.73) --
+	(270.60,376.62) --
+	(273.85,379.56) --
+	(277.09,382.53) --
+	(280.34,385.54) --
+	(283.58,388.58);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.86,249.92) --
-	( 38.99,250.73) --
-	( 42.13,251.56) --
-	( 45.26,252.41) --
-	( 48.40,253.28) --
-	( 51.53,254.17) --
-	( 54.67,255.09) --
-	( 57.81,256.02) --
-	( 60.94,256.97) --
-	( 64.08,257.95) --
-	( 67.21,258.94) --
-	( 70.35,259.96) --
-	( 73.48,260.99) --
-	( 76.62,262.05) --
-	( 79.76,263.13) --
-	( 82.89,264.23) --
-	( 86.03,265.35) --
-	( 89.16,266.49) --
-	( 92.30,267.65) --
-	( 95.43,268.84) --
-	( 98.57,270.04) --
-	(101.71,271.26) --
-	(104.84,272.50) --
-	(107.98,273.76) --
-	(111.11,275.03) --
-	(114.25,276.33) --
-	(117.39,277.65) --
-	(120.52,279.00) --
-	(123.66,280.37) --
-	(126.79,281.76) --
-	(129.93,283.19) --
-	(133.06,284.64) --
-	(136.20,286.09) --
-	(139.34,287.56) --
-	(142.47,289.06) --
-	(145.61,290.58) --
-	(148.74,292.13) --
-	(151.88,293.72) --
-	(155.01,295.35) --
-	(158.15,297.01) --
-	(161.29,298.68) --
-	(164.42,300.38) --
-	(167.56,302.10) --
-	(170.69,303.84) --
-	(173.83,305.62) --
-	(176.96,307.42) --
-	(180.10,309.27) --
-	(183.24,311.15) --
-	(186.37,313.08) --
-	(189.51,315.05) --
-	(192.64,317.07) --
-	(195.78,319.11) --
-	(198.91,321.18) --
-	(202.05,323.28) --
-	(205.19,325.42) --
-	(208.32,327.59) --
-	(211.46,329.81) --
-	(214.59,332.07) --
-	(217.73,334.37) --
-	(220.86,336.72) --
-	(224.00,339.12) --
-	(227.14,341.56) --
-	(230.27,344.04) --
-	(233.41,346.57) --
-	(236.54,349.13) --
-	(239.68,351.73) --
-	(242.82,354.37) --
-	(245.95,357.05) --
-	(249.09,359.77) --
-	(252.22,362.53) --
-	(255.36,365.34) --
-	(258.49,368.19) --
-	(261.63,371.07) --
-	(264.77,374.01) --
-	(267.90,376.98) --
-	(271.04,379.99) --
-	(274.17,383.04) --
-	(277.31,386.14) --
-	(280.44,389.27) --
-	(283.58,392.45);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.64) --
+	( 30.56,248.47) --
+	( 33.80,249.33) --
+	( 37.04,250.20) --
+	( 40.29,251.09) --
+	( 43.53,252.00) --
+	( 46.78,252.94) --
+	( 50.02,253.89) --
+	( 53.26,254.86) --
+	( 56.51,255.86) --
+	( 59.75,256.87) --
+	( 63.00,257.91) --
+	( 66.24,258.96) --
+	( 69.48,260.04) --
+	( 72.73,261.13) --
+	( 75.97,262.25) --
+	( 79.22,263.39) --
+	( 82.46,264.55) --
+	( 85.70,265.73) --
+	( 88.95,266.93) --
+	( 92.19,268.15) --
+	( 95.43,269.39) --
+	( 98.68,270.65) --
+	(101.92,271.92) --
+	(105.17,273.22) --
+	(108.41,274.54) --
+	(111.65,275.88) --
+	(114.90,277.24) --
+	(118.14,278.63) --
+	(121.39,280.04) --
+	(124.63,281.48) --
+	(127.87,282.92) --
+	(131.12,284.39) --
+	(134.36,285.87) --
+	(137.61,287.38) --
+	(140.85,288.91) --
+	(144.09,290.47) --
+	(147.34,292.05) --
+	(150.58,293.67) --
+	(153.82,295.33) --
+	(157.07,297.02) --
+	(160.31,298.73) --
+	(163.56,300.45) --
+	(166.80,302.20) --
+	(170.04,303.97) --
+	(173.29,305.78) --
+	(176.53,307.61) --
+	(179.78,309.47) --
+	(183.02,311.38) --
+	(186.26,313.32) --
+	(189.51,315.31) --
+	(192.75,317.33) --
+	(196.00,319.38) --
+	(199.24,321.47) --
+	(202.48,323.58) --
+	(205.73,325.73) --
+	(208.97,327.92) --
+	(212.21,330.14) --
+	(215.46,332.40) --
+	(218.70,334.70) --
+	(221.95,337.05) --
+	(225.19,339.44) --
+	(228.43,341.86) --
+	(231.68,344.33) --
+	(234.92,346.82) --
+	(238.17,349.36) --
+	(241.41,351.93) --
+	(244.65,354.54) --
+	(247.90,357.18) --
+	(251.14,359.87) --
+	(254.39,362.59) --
+	(257.63,365.35) --
+	(260.87,368.14) --
+	(264.12,370.98) --
+	(267.36,373.85) --
+	(270.60,376.76) --
+	(273.85,379.71) --
+	(277.09,382.70) --
+	(280.34,385.72) --
+	(283.58,388.79);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 35.86,249.92) --
-	( 38.99,250.74) --
-	( 42.13,251.58) --
-	( 45.26,252.44) --
-	( 48.40,253.32) --
-	( 51.53,254.22) --
-	( 54.67,255.14) --
-	( 57.81,256.08) --
-	( 60.94,257.05) --
-	( 64.08,258.03) --
-	( 67.21,259.03) --
-	( 70.35,260.05) --
-	( 73.48,261.10) --
-	( 76.62,262.16) --
-	( 79.76,263.24) --
-	( 82.89,264.35) --
-	( 86.03,265.47) --
-	( 89.16,266.62) --
-	( 92.30,267.79) --
-	( 95.43,268.98) --
-	( 98.57,270.19) --
-	(101.71,271.41) --
-	(104.84,272.65) --
-	(107.98,273.91) --
-	(111.11,275.19) --
-	(114.25,276.49) --
-	(117.39,277.81) --
-	(120.52,279.16) --
-	(123.66,280.53) --
-	(126.79,281.93) --
-	(129.93,283.35) --
-	(133.06,284.80) --
-	(136.20,286.25) --
-	(139.34,287.72) --
-	(142.47,289.22) --
-	(145.61,290.73) --
-	(148.74,292.28) --
-	(151.88,293.87) --
-	(155.01,295.49) --
-	(158.15,297.14) --
-	(161.29,298.82) --
-	(164.42,300.51) --
-	(167.56,302.22) --
-	(170.69,303.95) --
-	(173.83,305.72) --
-	(176.96,307.52) --
-	(180.10,309.35) --
-	(183.24,311.23) --
-	(186.37,313.14) --
-	(189.51,315.11) --
-	(192.64,317.11) --
-	(195.78,319.14) --
-	(198.91,321.20) --
-	(202.05,323.29) --
-	(205.19,325.41) --
-	(208.32,327.58) --
-	(211.46,329.78) --
-	(214.59,332.02) --
-	(217.73,334.31) --
-	(220.86,336.64) --
-	(224.00,339.03) --
-	(227.14,341.45) --
-	(230.27,343.92) --
-	(233.41,346.42) --
-	(236.54,348.96) --
-	(239.68,351.54) --
-	(242.82,354.16) --
-	(245.95,356.82) --
-	(249.09,359.52) --
-	(252.22,362.27) --
-	(255.36,365.05) --
-	(258.49,367.87) --
-	(261.63,370.74) --
-	(264.77,373.64) --
-	(267.90,376.59) --
-	(271.04,379.58) --
-	(274.17,382.60) --
-	(277.31,385.67) --
-	(280.44,388.78) --
-	(283.58,391.93);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.64) --
+	( 30.56,248.47) --
+	( 33.80,249.32) --
+	( 37.04,250.19) --
+	( 40.29,251.09) --
+	( 43.53,252.00) --
+	( 46.78,252.94) --
+	( 50.02,253.89) --
+	( 53.26,254.86) --
+	( 56.51,255.86) --
+	( 59.75,256.87) --
+	( 63.00,257.91) --
+	( 66.24,258.97) --
+	( 69.48,260.04) --
+	( 72.73,261.14) --
+	( 75.97,262.26) --
+	( 79.22,263.40) --
+	( 82.46,264.56) --
+	( 85.70,265.74) --
+	( 88.95,266.94) --
+	( 92.19,268.16) --
+	( 95.43,269.40) --
+	( 98.68,270.66) --
+	(101.92,271.93) --
+	(105.17,273.23) --
+	(108.41,274.55) --
+	(111.65,275.89) --
+	(114.90,277.25) --
+	(118.14,278.64) --
+	(121.39,280.05) --
+	(124.63,281.48) --
+	(127.87,282.93) --
+	(131.12,284.39) --
+	(134.36,285.88) --
+	(137.61,287.38) --
+	(140.85,288.91) --
+	(144.09,290.46) --
+	(147.34,292.05) --
+	(150.58,293.67) --
+	(153.82,295.32) --
+	(157.07,297.01) --
+	(160.31,298.72) --
+	(163.56,300.44) --
+	(166.80,302.19) --
+	(170.04,303.96) --
+	(173.29,305.76) --
+	(176.53,307.59) --
+	(179.78,309.45) --
+	(183.02,311.35) --
+	(186.26,313.30) --
+	(189.51,315.28) --
+	(192.75,317.31) --
+	(196.00,319.36) --
+	(199.24,321.45) --
+	(202.48,323.57) --
+	(205.73,325.72) --
+	(208.97,327.91) --
+	(212.21,330.14) --
+	(215.46,332.41) --
+	(218.70,334.71) --
+	(221.95,337.07) --
+	(225.19,339.46) --
+	(228.43,341.90) --
+	(231.68,344.37) --
+	(234.92,346.88) --
+	(238.17,349.42) --
+	(241.41,352.01) --
+	(244.65,354.63) --
+	(247.90,357.28) --
+	(251.14,359.98) --
+	(254.39,362.71) --
+	(257.63,365.49) --
+	(260.87,368.30) --
+	(264.12,371.15) --
+	(267.36,374.05) --
+	(270.60,376.98) --
+	(273.85,379.94) --
+	(277.09,382.95) --
+	(280.34,385.99) --
+	(283.58,389.07);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] ( 35.86,253.66) --
-	( 39.22,247.84) --
-	( 32.49,247.84) --
-	cycle;
-
-\path[fill=fillColor] ( 44.40,256.05) --
-	( 47.76,250.22) --
-	( 41.03,250.22) --
-	cycle;
-
-\path[fill=fillColor] ( 52.94,258.56) --
-	( 56.30,252.73) --
-	( 49.58,252.73) --
-	cycle;
-
-\path[fill=fillColor] ( 61.48,261.19) --
-	( 64.85,255.36) --
-	( 58.12,255.36) --
-	cycle;
-
-\path[fill=fillColor] ( 70.02,263.94) --
-	( 73.39,258.11) --
-	( 66.66,258.11) --
-	cycle;
-
-\path[fill=fillColor] ( 78.57,266.81) --
-	( 81.93,260.99) --
-	( 75.20,260.99) --
-	cycle;
-
-\path[fill=fillColor] ( 87.11,269.83) --
-	( 90.47,264.01) --
-	( 83.75,264.01) --
-	cycle;
-
-\path[fill=fillColor] ( 95.65,273.00) --
-	( 99.01,267.18) --
-	( 92.29,267.18) --
-	cycle;
-
-\path[fill=fillColor] (104.19,276.33) --
-	(107.56,270.51) --
-	(100.83,270.51) --
-	cycle;
-
-\path[fill=fillColor] (112.74,279.79) --
-	(116.10,273.97) --
-	(109.37,273.97) --
-	cycle;
-
-\path[fill=fillColor] (121.28,283.41) --
-	(124.64,277.58) --
-	(117.91,277.58) --
-	cycle;
-
-\path[fill=fillColor] (129.82,287.19) --
-	(133.18,281.36) --
-	(126.46,281.36) --
-	cycle;
-
-\path[fill=fillColor] (138.36,291.15) --
-	(141.73,285.33) --
-	(135.00,285.33) --
-	cycle;
-
-\path[fill=fillColor] (146.90,295.31) --
-	(150.27,289.49) --
-	(143.54,289.49) --
-	cycle;
-
-\path[fill=fillColor] (155.45,299.62) --
-	(158.81,293.80) --
-	(152.08,293.80) --
-	cycle;
-
-\path[fill=fillColor] (163.99,304.14) --
-	(167.35,298.31) --
-	(160.63,298.31) --
-	cycle;
-
-\path[fill=fillColor] (172.53,308.85) --
-	(175.89,303.03) --
-	(169.17,303.03) --
-	cycle;
-
-\path[fill=fillColor] (181.07,313.93) --
-	(184.44,308.10) --
-	(177.71,308.10) --
-	cycle;
-
-\path[fill=fillColor] (189.62,319.15) --
-	(192.98,313.32) --
-	(186.25,313.32) --
-	cycle;
-
-\path[fill=fillColor] (198.16,324.63) --
-	(201.52,318.80) --
-	(194.79,318.80) --
-	cycle;
-
-\path[fill=fillColor] (206.70,330.30) --
-	(210.06,324.48) --
-	(203.34,324.48) --
-	cycle;
-
-\path[fill=fillColor] (215.24,336.32) --
-	(218.61,330.49) --
-	(211.88,330.49) --
-	cycle;
-
-\path[fill=fillColor] (223.78,342.61) --
-	(227.15,336.78) --
-	(220.42,336.78) --
-	cycle;
-
-\path[fill=fillColor] (232.33,349.11) --
-	(235.69,343.29) --
-	(228.96,343.29) --
-	cycle;
-
-\path[fill=fillColor] (240.87,356.01) --
-	(244.23,350.19) --
-	(237.51,350.19) --
-	cycle;
-
-\path[fill=fillColor] (249.41,363.19) --
-	(252.77,357.37) --
-	(246.05,357.37) --
-	cycle;
-
-\path[fill=fillColor] (257.95,370.87) --
-	(261.32,365.04) --
-	(254.59,365.04) --
-	cycle;
-
-\path[fill=fillColor] (266.50,378.77) --
-	(269.86,372.95) --
-	(263.13,372.95) --
-	cycle;
-
-\path[fill=fillColor] (275.04,386.88) --
-	(278.40,381.05) --
-	(271.67,381.05) --
-	cycle;
-
-\path[fill=fillColor] (283.58,395.60) --
-	(286.94,389.77) --
-	(280.22,389.77) --
+\path[fill=fillColor] ( 27.31,251.38) --
+	( 30.68,245.55) --
+	( 23.95,245.55) --
+	cycle;
+
+\path[fill=fillColor] ( 35.86,253.72) --
+	( 39.22,247.89) --
+	( 32.49,247.89) --
+	cycle;
+
+\path[fill=fillColor] ( 44.40,256.16) --
+	( 47.76,250.34) --
+	( 41.03,250.34) --
+	cycle;
+
+\path[fill=fillColor] ( 52.94,258.73) --
+	( 56.30,252.90) --
+	( 49.58,252.90) --
+	cycle;
+
+\path[fill=fillColor] ( 61.48,261.41) --
+	( 64.85,255.58) --
+	( 58.12,255.58) --
+	cycle;
+
+\path[fill=fillColor] ( 70.02,264.21) --
+	( 73.39,258.38) --
+	( 66.66,258.38) --
+	cycle;
+
+\path[fill=fillColor] ( 78.57,267.14) --
+	( 81.93,261.31) --
+	( 75.20,261.31) --
+	cycle;
+
+\path[fill=fillColor] ( 87.11,270.19) --
+	( 90.47,264.37) --
+	( 83.75,264.37) --
+	cycle;
+
+\path[fill=fillColor] ( 95.65,273.40) --
+	( 99.01,267.58) --
+	( 92.29,267.58) --
+	cycle;
+
+\path[fill=fillColor] (104.19,276.77) --
+	(107.56,270.94) --
+	(100.83,270.94) --
+	cycle;
+
+\path[fill=fillColor] (112.74,280.26) --
+	(116.10,274.43) --
+	(109.37,274.43) --
+	cycle;
+
+\path[fill=fillColor] (121.28,283.89) --
+	(124.64,278.06) --
+	(117.91,278.06) --
+	cycle;
+
+\path[fill=fillColor] (129.82,287.67) --
+	(133.18,281.85) --
+	(126.46,281.85) --
+	cycle;
+
+\path[fill=fillColor] (138.36,291.63) --
+	(141.73,285.80) --
+	(135.00,285.80) --
+	cycle;
+
+\path[fill=fillColor] (146.90,295.78) --
+	(150.27,289.96) --
+	(143.54,289.96) --
+	cycle;
+
+\path[fill=fillColor] (155.45,300.06) --
+	(158.81,294.24) --
+	(152.08,294.24) --
+	cycle;
+
+\path[fill=fillColor] (163.99,304.54) --
+	(167.35,298.72) --
+	(160.63,298.72) --
+	cycle;
+
+\path[fill=fillColor] (172.53,309.20) --
+	(175.89,303.38) --
+	(169.17,303.38) --
+	cycle;
+
+\path[fill=fillColor] (181.07,314.20) --
+	(184.44,308.38) --
+	(177.71,308.38) --
+	cycle;
+
+\path[fill=fillColor] (189.62,319.33) --
+	(192.98,313.51) --
+	(186.25,313.51) --
+	cycle;
+
+\path[fill=fillColor] (198.16,324.68) --
+	(201.52,318.86) --
+	(194.79,318.86) --
+	cycle;
+
+\path[fill=fillColor] (206.70,330.22) --
+	(210.06,324.39) --
+	(203.34,324.39) --
+	cycle;
+
+\path[fill=fillColor] (215.24,336.05) --
+	(218.61,330.22) --
+	(211.88,330.22) --
+	cycle;
+
+\path[fill=fillColor] (223.78,342.17) --
+	(227.15,336.34) --
+	(220.42,336.34) --
+	cycle;
+
+\path[fill=fillColor] (232.33,348.47) --
+	(235.69,342.65) --
+	(228.96,342.65) --
+	cycle;
+
+\path[fill=fillColor] (240.87,355.10) --
+	(244.23,349.27) --
+	(237.51,349.27) --
+	cycle;
+
+\path[fill=fillColor] (249.41,361.97) --
+	(252.77,356.14) --
+	(246.05,356.14) --
+	cycle;
+
+\path[fill=fillColor] (257.95,369.32) --
+	(261.32,363.50) --
+	(254.59,363.50) --
+	cycle;
+
+\path[fill=fillColor] (266.50,376.85) --
+	(269.86,371.02) --
+	(263.13,371.02) --
+	cycle;
+
+\path[fill=fillColor] (275.04,384.53) --
+	(278.40,378.70) --
+	(271.67,378.70) --
+	cycle;
+
+\path[fill=fillColor] (283.58,392.80) --
+	(286.94,386.97) --
+	(280.22,386.97) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 33.36,247.26) --
-	( 38.35,247.26) --
-	( 38.35,252.26) --
-	( 33.36,252.26) --
-	cycle;
-
-\path[fill=fillColor] ( 41.90,249.63) --
-	( 46.90,249.63) --
-	( 46.90,254.63) --
-	( 41.90,254.63) --
-	cycle;
-
-\path[fill=fillColor] ( 50.44,252.12) --
-	( 55.44,252.12) --
-	( 55.44,257.12) --
-	( 50.44,257.12) --
-	cycle;
-
-\path[fill=fillColor] ( 58.98,254.74) --
-	( 63.98,254.74) --
-	( 63.98,259.73) --
-	( 58.98,259.73) --
-	cycle;
-
-\path[fill=fillColor] ( 67.53,257.47) --
-	( 72.52,257.47) --
-	( 72.52,262.47) --
-	( 67.53,262.47) --
-	cycle;
-
-\path[fill=fillColor] ( 76.07,260.33) --
-	( 81.06,260.33) --
-	( 81.06,265.33) --
-	( 76.07,265.33) --
-	cycle;
-
-\path[fill=fillColor] ( 84.61,263.34) --
-	( 89.61,263.34) --
-	( 89.61,268.34) --
-	( 84.61,268.34) --
-	cycle;
-
-\path[fill=fillColor] ( 93.15,266.51) --
-	( 98.15,266.51) --
-	( 98.15,271.50) --
-	( 93.15,271.50) --
-	cycle;
-
-\path[fill=fillColor] (101.70,269.84) --
-	(106.69,269.84) --
-	(106.69,274.83) --
-	(101.70,274.83) --
-	cycle;
-
-\path[fill=fillColor] (110.24,273.29) --
-	(115.23,273.29) --
-	(115.23,278.28) --
-	(110.24,278.28) --
-	cycle;
-
-\path[fill=fillColor] (118.78,276.89) --
-	(123.78,276.89) --
-	(123.78,281.88) --
-	(118.78,281.88) --
-	cycle;
-
-\path[fill=fillColor] (127.32,280.66) --
-	(132.32,280.66) --
-	(132.32,285.65) --
-	(127.32,285.65) --
-	cycle;
-
-\path[fill=fillColor] (135.86,284.62) --
-	(140.86,284.62) --
-	(140.86,289.62) --
-	(135.86,289.62) --
-	cycle;
-
-\path[fill=fillColor] (144.41,288.79) --
-	(149.40,288.79) --
-	(149.40,293.79) --
-	(144.41,293.79) --
-	cycle;
-
-\path[fill=fillColor] (152.95,293.08) --
-	(157.94,293.08) --
-	(157.94,298.08) --
-	(152.95,298.08) --
-	cycle;
-
-\path[fill=fillColor] (161.49,297.59) --
-	(166.49,297.59) --
-	(166.49,302.58) --
-	(161.49,302.58) --
-	cycle;
-
-\path[fill=fillColor] (170.03,302.29) --
-	(175.03,302.29) --
-	(175.03,307.29) --
-	(170.03,307.29) --
-	cycle;
-
-\path[fill=fillColor] (178.58,307.43) --
-	(183.57,307.43) --
-	(183.57,312.42) --
-	(178.58,312.42) --
-	cycle;
-
-\path[fill=fillColor] (187.12,312.67) --
-	(192.11,312.67) --
-	(192.11,317.67) --
-	(187.12,317.67) --
-	cycle;
-
-\path[fill=fillColor] (195.66,318.20) --
-	(200.66,318.20) --
-	(200.66,323.19) --
-	(195.66,323.19) --
-	cycle;
-
-\path[fill=fillColor] (204.20,323.88) --
-	(209.20,323.88) --
-	(209.20,328.88) --
-	(204.20,328.88) --
-	cycle;
-
-\path[fill=fillColor] (212.74,329.97) --
-	(217.74,329.97) --
-	(217.74,334.96) --
-	(212.74,334.96) --
-	cycle;
-
-\path[fill=fillColor] (221.29,336.33) --
-	(226.28,336.33) --
-	(226.28,341.33) --
-	(221.29,341.33) --
-	cycle;
-
-\path[fill=fillColor] (229.83,342.88) --
-	(234.82,342.88) --
-	(234.82,347.87) --
-	(229.83,347.87) --
-	cycle;
-
-\path[fill=fillColor] (238.37,349.88) --
-	(243.37,349.88) --
-	(243.37,354.88) --
-	(238.37,354.88) --
-	cycle;
-
-\path[fill=fillColor] (246.91,357.20) --
-	(251.91,357.20) --
-	(251.91,362.20) --
-	(246.91,362.20) --
-	cycle;
-
-\path[fill=fillColor] (255.46,365.13) --
-	(260.45,365.13) --
-	(260.45,370.13) --
-	(255.46,370.13) --
-	cycle;
-
-\path[fill=fillColor] (264.00,373.18) --
-	(268.99,373.18) --
-	(268.99,378.18) --
-	(264.00,378.18) --
-	cycle;
-
-\path[fill=fillColor] (272.54,381.37) --
-	(277.54,381.37) --
-	(277.54,386.36) --
-	(272.54,386.36) --
-	cycle;
-
-\path[fill=fillColor] (281.08,390.32) --
-	(286.08,390.32) --
-	(286.08,395.31) --
-	(281.08,395.31) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32,249.78) -- ( 39.39,249.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86,246.24) -- ( 35.86,253.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87,252.16) -- ( 47.93,252.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.63) -- ( 44.40,255.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41,254.67) -- ( 56.47,254.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94,251.14) -- ( 52.94,258.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95,257.30) -- ( 65.01,257.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48,253.77) -- ( 61.48,260.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.05) -- ( 73.56,260.05);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02,256.52) -- ( 70.02,263.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,262.93) -- ( 82.10,262.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57,259.40) -- ( 78.57,266.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,265.95) -- ( 90.64,265.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,262.42) -- ( 87.11,269.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.13) -- ( 99.18,269.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,265.60) -- ( 95.65,272.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,272.49) -- (107.73,272.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,268.95) -- (104.19,276.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,275.94) -- (116.27,275.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,272.41) -- (112.74,279.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,279.55) -- (124.81,279.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.01) -- (121.28,283.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.32) -- (133.35,283.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,279.79) -- (129.82,286.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.28) -- (141.89,287.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,283.75) -- (138.36,290.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.46) -- (150.44,291.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,287.92) -- (146.90,294.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,295.73) -- (158.98,295.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,292.19) -- (155.45,299.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.20) -- (167.52,300.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,296.66) -- (163.99,303.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.86) -- (176.06,304.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.33) -- (172.53,308.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,310.02) -- (184.61,310.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.49) -- (181.07,313.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,315.24) -- (193.15,315.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.71) -- (189.62,318.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,320.74) -- (201.69,320.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,317.21) -- (198.16,324.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,326.37) -- (210.23,326.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,322.83) -- (206.70,329.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,332.43) -- (218.77,332.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,328.90) -- (215.24,335.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,338.75) -- (227.32,338.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,335.22) -- (223.78,342.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,345.19) -- (235.86,345.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,341.65) -- (232.33,348.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,352.15) -- (244.40,352.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,348.62) -- (240.87,355.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,359.43) -- (252.94,359.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,355.90) -- (249.41,362.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,367.42) -- (261.49,367.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,363.89) -- (257.95,370.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,375.38) -- (270.03,375.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,371.85) -- (266.50,378.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,383.38) -- (278.57,383.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,379.85) -- (275.04,386.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,392.25) -- (287.11,392.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,388.71) -- (283.58,395.78);
+\path[fill=fillColor] ( 24.82,245.00) --
+	( 29.81,245.00) --
+	( 29.81,249.99) --
+	( 24.82,249.99) --
+	cycle;
+
+\path[fill=fillColor] ( 33.36,247.34) --
+	( 38.35,247.34) --
+	( 38.35,252.33) --
+	( 33.36,252.33) --
+	cycle;
+
+\path[fill=fillColor] ( 41.90,249.78) --
+	( 46.90,249.78) --
+	( 46.90,254.78) --
+	( 41.90,254.78) --
+	cycle;
+
+\path[fill=fillColor] ( 50.44,252.35) --
+	( 55.44,252.35) --
+	( 55.44,257.34) --
+	( 50.44,257.34) --
+	cycle;
+
+\path[fill=fillColor] ( 58.98,255.03) --
+	( 63.98,255.03) --
+	( 63.98,260.02) --
+	( 58.98,260.02) --
+	cycle;
+
+\path[fill=fillColor] ( 67.53,257.83) --
+	( 72.52,257.83) --
+	( 72.52,262.83) --
+	( 67.53,262.83) --
+	cycle;
+
+\path[fill=fillColor] ( 76.07,260.76) --
+	( 81.06,260.76) --
+	( 81.06,265.75) --
+	( 76.07,265.75) --
+	cycle;
+
+\path[fill=fillColor] ( 84.61,263.82) --
+	( 89.61,263.82) --
+	( 89.61,268.81) --
+	( 84.61,268.81) --
+	cycle;
+
+\path[fill=fillColor] ( 93.15,267.03) --
+	( 98.15,267.03) --
+	( 98.15,272.03) --
+	( 93.15,272.03) --
+	cycle;
+
+\path[fill=fillColor] (101.70,270.41) --
+	(106.69,270.41) --
+	(106.69,275.40) --
+	(101.70,275.40) --
+	cycle;
+
+\path[fill=fillColor] (110.24,273.89) --
+	(115.23,273.89) --
+	(115.23,278.89) --
+	(110.24,278.89) --
+	cycle;
+
+\path[fill=fillColor] (118.78,277.52) --
+	(123.78,277.52) --
+	(123.78,282.51) --
+	(118.78,282.51) --
+	cycle;
+
+\path[fill=fillColor] (127.32,281.30) --
+	(132.32,281.30) --
+	(132.32,286.30) --
+	(127.32,286.30) --
+	cycle;
+
+\path[fill=fillColor] (135.86,285.26) --
+	(140.86,285.26) --
+	(140.86,290.25) --
+	(135.86,290.25) --
+	cycle;
+
+\path[fill=fillColor] (144.41,289.41) --
+	(149.40,289.41) --
+	(149.40,294.41) --
+	(144.41,294.41) --
+	cycle;
+
+\path[fill=fillColor] (152.95,293.67) --
+	(157.94,293.67) --
+	(157.94,298.67) --
+	(152.95,298.67) --
+	cycle;
+
+\path[fill=fillColor] (161.49,298.13) --
+	(166.49,298.13) --
+	(166.49,303.13) --
+	(161.49,303.13) --
+	cycle;
+
+\path[fill=fillColor] (170.03,302.76) --
+	(175.03,302.76) --
+	(175.03,307.76) --
+	(170.03,307.76) --
+	cycle;
+
+\path[fill=fillColor] (178.58,307.80) --
+	(183.57,307.80) --
+	(183.57,312.80) --
+	(178.58,312.80) --
+	cycle;
+
+\path[fill=fillColor] (187.12,312.93) --
+	(192.11,312.93) --
+	(192.11,317.93) --
+	(187.12,317.93) --
+	cycle;
+
+\path[fill=fillColor] (195.66,318.29) --
+	(200.66,318.29) --
+	(200.66,323.28) --
+	(195.66,323.28) --
+	cycle;
+
+\path[fill=fillColor] (204.20,323.80) --
+	(209.20,323.80) --
+	(209.20,328.79) --
+	(204.20,328.79) --
+	cycle;
+
+\path[fill=fillColor] (212.74,329.65) --
+	(217.74,329.65) --
+	(217.74,334.64) --
+	(212.74,334.64) --
+	cycle;
+
+\path[fill=fillColor] (221.29,335.78) --
+	(226.28,335.78) --
+	(226.28,340.78) --
+	(221.29,340.78) --
+	cycle;
+
+\path[fill=fillColor] (229.83,342.05) --
+	(234.82,342.05) --
+	(234.82,347.05) --
+	(229.83,347.05) --
+	cycle;
+
+\path[fill=fillColor] (238.37,348.70) --
+	(243.37,348.70) --
+	(243.37,353.69) --
+	(238.37,353.69) --
+	cycle;
+
+\path[fill=fillColor] (246.91,355.61) --
+	(251.91,355.61) --
+	(251.91,360.60) --
+	(246.91,360.60) --
+	cycle;
+
+\path[fill=fillColor] (255.46,363.10) --
+	(260.45,363.10) --
+	(260.45,368.10) --
+	(255.46,368.10) --
+	cycle;
+
+\path[fill=fillColor] (264.00,370.65) --
+	(268.99,370.65) --
+	(268.99,375.65) --
+	(264.00,375.65) --
+	cycle;
+
+\path[fill=fillColor] (272.54,378.27) --
+	(277.54,378.27) --
+	(277.54,383.27) --
+	(272.54,383.27) --
+	cycle;
+
+\path[fill=fillColor] (281.08,386.62) --
+	(286.08,386.62) --
+	(286.08,391.61) --
+	(281.08,391.61) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78,247.50) -- ( 30.85,247.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31,243.96) -- ( 27.31,251.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32,249.83) -- ( 39.39,249.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86,246.30) -- ( 35.86,253.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87,252.27) -- ( 47.93,252.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.74) -- ( 44.40,255.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41,254.84) -- ( 56.47,254.84);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94,251.31) -- ( 52.94,258.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95,257.52) -- ( 65.01,257.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48,253.99) -- ( 61.48,261.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.33) -- ( 73.56,260.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02,256.79) -- ( 70.02,263.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,263.25) -- ( 82.10,263.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57,259.72) -- ( 78.57,266.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.32) -- ( 90.64,266.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,262.78) -- ( 87.11,269.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.54) -- ( 99.18,269.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,266.00) -- ( 95.65,273.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,272.92) -- (107.73,272.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,269.39) -- (104.19,276.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.41) -- (116.27,276.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,272.87) -- (112.74,279.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,280.03) -- (124.81,280.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.49) -- (121.28,283.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.81) -- (133.35,283.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.27) -- (129.82,287.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.76) -- (141.89,287.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,284.23) -- (138.36,291.30);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.93) -- (150.44,291.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.39) -- (146.90,295.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,296.17) -- (158.98,296.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,292.64) -- (155.45,299.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.60) -- (167.52,300.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,297.07) -- (163.99,304.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,305.21) -- (176.06,305.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.68) -- (172.53,308.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,310.29) -- (184.61,310.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.76) -- (181.07,313.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,315.42) -- (193.15,315.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.89) -- (189.62,318.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,320.79) -- (201.69,320.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,317.26) -- (198.16,324.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,326.28) -- (210.23,326.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,322.74) -- (206.70,329.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,332.15) -- (218.77,332.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,328.62) -- (215.24,335.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,338.30) -- (227.32,338.30);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,334.76) -- (223.78,341.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,344.53) -- (235.86,344.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,341.00) -- (232.33,348.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,351.21) -- (244.40,351.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,347.68) -- (240.87,354.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,358.17) -- (252.94,358.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,354.64) -- (249.41,361.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,365.83) -- (261.49,365.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,362.30) -- (257.95,369.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,373.41) -- (270.03,373.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,369.87) -- (266.50,376.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,380.97) -- (278.57,380.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,377.44) -- (275.04,384.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,389.39) -- (287.11,389.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,385.85) -- (283.58,392.92);
 \definecolor{fillColor}{RGB}{0,0,0}
 
+\path[fill=fillColor] ( 27.31,247.50) circle (  2.50);
+
 \path[fill=fillColor] ( 35.86,249.83) circle (  2.50);
@@
 
-\path[fill=fillColor] ( 52.94,254.83) circle (  2.50);
-
-\path[fill=fillColor] ( 61.48,257.48) circle (  2.50);
-
-\path[fill=fillColor] ( 70.02,260.30) circle (  2.50);
+\path[fill=fillColor] ( 52.94,254.82) circle (  2.50);
+
+\path[fill=fillColor] ( 61.48,257.51) circle (  2.50);
+
+\path[fill=fillColor] ( 70.02,260.28) circle (  2.50);
 
@@
 
-\path[fill=fillColor] ( 87.11,266.25) circle (  2.50);
-
-\path[fill=fillColor] ( 95.65,269.47) circle (  2.50);
-
-\path[fill=fillColor] (104.19,272.76) circle (  2.50);
-
-\path[fill=fillColor] (112.74,276.27) circle (  2.50);
-
-\path[fill=fillColor] (121.28,279.87) circle (  2.50);
-
-\path[fill=fillColor] (129.82,283.65) circle (  2.50);
-
-\path[fill=fillColor] (138.36,287.63) circle (  2.50);
-
-\path[fill=fillColor] (146.90,291.84) circle (  2.50);
-
-\path[fill=fillColor] (155.45,296.08) circle (  2.50);
-
-\path[fill=fillColor] (163.99,300.69) circle (  2.50);
-
-\path[fill=fillColor] (172.53,305.43) circle (  2.50);
+\path[fill=fillColor] ( 87.11,266.27) circle (  2.50);
+
+\path[fill=fillColor] ( 95.65,269.43) circle (  2.50);
+
+\path[fill=fillColor] (104.19,272.79) circle (  2.50);
+
+\path[fill=fillColor] (112.74,276.24) circle (  2.50);
+
+\path[fill=fillColor] (121.28,279.86) circle (  2.50);
+
+\path[fill=fillColor] (129.82,283.67) circle (  2.50);
+
+\path[fill=fillColor] (138.36,287.69) circle (  2.50);
+
+\path[fill=fillColor] (146.90,291.76) circle (  2.50);
+
+\path[fill=fillColor] (155.45,296.17) circle (  2.50);
+
+\path[fill=fillColor] (163.99,300.71) circle (  2.50);
+
+\path[fill=fillColor] (172.53,305.39) circle (  2.50);
 
@@
 
-\path[fill=fillColor] (189.62,315.45) circle (  2.50);
-
-\path[fill=fillColor] (198.16,320.77) circle (  2.50);
-
-\path[fill=fillColor] (206.70,326.39) circle (  2.50);
-
-\path[fill=fillColor] (215.24,332.07) circle (  2.50);
-
-\path[fill=fillColor] (223.78,338.31) circle (  2.50);
-
-\path[fill=fillColor] (232.33,344.46) circle (  2.50);
-
-\path[fill=fillColor] (240.87,351.03) circle (  2.50);
-
-\path[fill=fillColor] (249.41,358.29) circle (  2.50);
-
-\path[fill=fillColor] (257.95,365.51) circle (  2.50);
-
-\path[fill=fillColor] (266.50,372.75) circle (  2.50);
-
-\path[fill=fillColor] (275.04,380.66) circle (  2.50);
-
-\path[fill=fillColor] (283.58,388.74) circle (  2.50);
+\path[fill=fillColor] (189.62,315.41) circle (  2.50);
+
+\path[fill=fillColor] (198.16,320.80) circle (  2.50);
+
+\path[fill=fillColor] (206.70,326.25) circle (  2.50);
+
+\path[fill=fillColor] (215.24,332.23) circle (  2.50);
+
+\path[fill=fillColor] (223.78,338.13) circle (  2.50);
+
+\path[fill=fillColor] (232.33,344.44) circle (  2.50);
+
+\path[fill=fillColor] (240.87,351.38) circle (  2.50);
+
+\path[fill=fillColor] (249.41,358.30) circle (  2.50);
+
+\path[fill=fillColor] (257.95,365.26) circle (  2.50);
+
+\path[fill=fillColor] (266.50,372.85) circle (  2.50);
+
+\path[fill=fillColor] (275.04,380.60) circle (  2.50);
+
+\path[fill=fillColor] (283.58,388.73) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (324.94,249.99) --
-	(328.07,250.83) --
-	(331.21,251.68) --
-	(334.34,252.56) --
-	(337.48,253.45) --
-	(340.61,254.37) --
-	(343.75,255.30) --
-	(346.89,256.26) --
-	(350.02,257.23) --
-	(353.16,258.23) --
-	(356.29,259.24) --
-	(359.43,260.28) --
-	(362.56,261.33) --
-	(365.70,262.40) --
-	(368.84,263.50) --
-	(371.97,264.61) --
-	(375.11,265.75) --
-	(378.24,266.90) --
-	(381.38,268.08) --
-	(384.51,269.28) --
-	(387.65,270.50) --
-	(390.79,271.73) --
-	(393.92,272.98) --
-	(397.06,274.24) --
-	(400.19,275.53) --
-	(403.33,276.84) --
-	(406.47,278.17) --
-	(409.60,279.52) --
-	(412.74,280.89) --
-	(415.87,282.30) --
-	(419.01,283.73) --
-	(422.14,285.17) --
-	(425.28,286.64) --
-	(428.42,288.12) --
-	(431.55,289.62) --
-	(434.69,291.14) --
-	(437.82,292.70) --
-	(440.96,294.28) --
-	(444.09,295.90) --
-	(447.23,297.55) --
-	(450.37,299.21) --
-	(453.50,300.90) --
-	(456.64,302.61) --
-	(459.77,304.34) --
-	(462.91,306.10) --
-	(466.04,307.89) --
-	(469.18,309.70) --
-	(472.32,311.56) --
-	(475.45,313.44) --
-	(478.59,315.37) --
-	(481.72,317.32) --
-	(484.86,319.30) --
-	(487.99,321.31) --
-	(491.13,323.34) --
-	(494.27,325.40) --
-	(497.40,327.50) --
-	(500.54,329.63) --
-	(503.67,331.79) --
-	(506.81,334.00) --
-	(509.94,336.24) --
-	(513.08,338.52) --
-	(516.22,340.85) --
-	(519.35,343.20) --
-	(522.49,345.59) --
-	(525.62,348.02) --
-	(528.76,350.47) --
-	(531.90,352.96) --
-	(535.03,355.49) --
-	(538.17,358.05) --
-	(541.30,360.65) --
-	(544.44,363.28) --
-	(547.57,365.95) --
-	(550.71,368.65) --
-	(553.85,371.39) --
-	(556.98,374.16) --
-	(560.12,376.97) --
-	(563.25,379.82) --
-	(566.39,382.70) --
-	(569.52,385.61) --
-	(572.66,388.56);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (316.39,247.68) --
+	(319.64,248.50) --
+	(322.88,249.34) --
+	(326.12,250.20) --
+	(329.37,251.09) --
+	(332.61,251.99) --
+	(335.86,252.92) --
+	(339.10,253.86) --
+	(342.34,254.83) --
+	(345.59,255.81) --
+	(348.83,256.82) --
+	(352.08,257.85) --
+	(355.32,258.90) --
+	(358.56,259.97) --
+	(361.81,261.06) --
+	(365.05,262.17) --
+	(368.30,263.30) --
+	(371.54,264.46) --
+	(374.78,265.64) --
+	(378.03,266.84) --
+	(381.27,268.05) --
+	(384.51,269.29) --
+	(387.76,270.54) --
+	(391.00,271.81) --
+	(394.25,273.10) --
+	(397.49,274.42) --
+	(400.73,275.76) --
+	(403.98,277.12) --
+	(407.22,278.51) --
+	(410.47,279.93) --
+	(413.71,281.36) --
+	(416.95,282.81) --
+	(420.20,284.29) --
+	(423.44,285.78) --
+	(426.69,287.29) --
+	(429.93,288.83) --
+	(433.17,290.40) --
+	(436.42,292.00) --
+	(439.66,293.63) --
+	(442.90,295.29) --
+	(446.15,296.98) --
+	(449.39,298.70) --
+	(452.64,300.44) --
+	(455.88,302.19) --
+	(459.12,303.98) --
+	(462.37,305.79) --
+	(465.61,307.63) --
+	(468.86,309.51) --
+	(472.10,311.42) --
+	(475.34,313.37) --
+	(478.59,315.36) --
+	(481.83,317.38) --
+	(485.08,319.43) --
+	(488.32,321.51) --
+	(491.56,323.63) --
+	(494.81,325.77) --
+	(498.05,327.95) --
+	(501.29,330.17) --
+	(504.54,332.42) --
+	(507.78,334.72) --
+	(511.03,337.06) --
+	(514.27,339.44) --
+	(517.51,341.85) --
+	(520.76,344.31) --
+	(524.00,346.79) --
+	(527.25,349.31) --
+	(530.49,351.87) --
+	(533.73,354.47) --
+	(536.98,357.10) --
+	(540.22,359.77) --
+	(543.47,362.47) --
+	(546.71,365.21) --
+	(549.95,367.99) --
+	(553.20,370.81) --
+	(556.44,373.67) --
+	(559.68,376.56) --
+	(562.93,379.49) --
+	(566.17,382.45) --
+	(569.42,385.45) --
+	(572.66,388.49);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (324.94,249.67) --
-	(328.07,250.54) --
-	(331.21,251.42) --
-	(334.34,252.31) --
-	(337.48,253.20) --
-	(340.61,254.10) --
-	(343.75,255.00) --
-	(346.89,255.91) --
-	(350.02,256.83) --
-	(353.16,257.75) --
-	(356.29,258.68) --
-	(359.43,259.62) --
-	(362.56,260.56) --
-	(365.70,261.51) --
-	(368.84,262.46) --
-	(371.97,263.42) --
-	(375.11,264.39) --
-	(378.24,265.36) --
-	(381.38,266.34) --
-	(384.51,267.32) --
-	(387.65,268.31) --
-	(390.79,269.31) --
-	(393.92,270.31) --
-	(397.06,271.33) --
-	(400.19,272.35) --
-	(403.33,273.37) --
-	(406.47,274.41) --
-	(409.60,275.44) --
-	(412.74,276.48) --
-	(415.87,277.52) --
-	(419.01,278.57) --
-	(422.14,279.62) --
-	(425.28,280.68) --
-	(428.42,281.75) --
-	(431.55,282.83) --
-	(434.69,283.91) --
-	(437.82,284.99) --
-	(440.96,286.07) --
-	(444.09,287.14) --
-	(447.23,288.21) --
-	(450.37,289.29) --
-	(453.50,290.38) --
-	(456.64,291.48) --
-	(459.77,292.58) --
-	(462.91,293.68) --
-	(466.04,294.78) --
-	(469.18,295.87) --
-	(472.32,296.96) --
-	(475.45,298.03) --
-	(478.59,299.08) --
-	(481.72,300.14) --
-	(484.86,301.19) --
-	(487.99,302.25) --
-	(491.13,303.30) --
-	(494.27,304.35) --
-	(497.40,305.39) --
-	(500.54,306.43) --
-	(503.67,307.45) --
-	(506.81,308.45) --
-	(509.94,309.44) --
-	(513.08,310.40) --
-	(516.22,311.35) --
-	(519.35,312.29) --
-	(522.49,313.23) --
-	(525.62,314.15) --
-	(528.76,315.06) --
-	(531.90,315.97) --
-	(535.03,316.86) --
-	(538.17,317.74) --
-	(541.30,318.61) --
-	(544.44,319.47) --
-	(547.57,320.31) --
-	(550.71,321.14) --
-	(553.85,321.96) --
-	(556.98,322.77) --
-	(560.12,323.57) --
-	(563.25,324.36) --
-	(566.39,325.13) --
-	(569.52,325.89) --
-	(572.66,326.65);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (319.64,248.28) --
+	(322.88,249.19) --
+	(326.12,250.12) --
+	(329.37,251.04) --
+	(332.61,251.98) --
+	(335.86,252.92) --
+	(339.10,253.86) --
+	(342.34,254.82) --
+	(345.59,255.77) --
+	(348.83,256.74) --
+	(352.08,257.71) --
+	(355.32,258.69) --
+	(358.56,259.67) --
+	(361.81,260.66) --
+	(365.05,261.65) --
+	(368.30,262.65) --
+	(371.54,263.65) --
+	(374.78,264.66) --
+	(378.03,265.68) --
+	(381.27,266.70) --
+	(384.51,267.73) --
+	(387.76,268.77) --
+	(391.00,269.81) --
+	(394.25,270.86) --
+	(397.49,271.92) --
+	(400.73,272.98) --
+	(403.98,274.04) --
+	(407.22,275.11) --
+	(410.47,276.18) --
+	(413.71,277.25) --
+	(416.95,278.34) --
+	(420.20,279.43) --
+	(423.44,280.54) --
+	(426.69,281.64) --
+	(429.93,282.75) --
+	(433.17,283.86) --
+	(436.42,284.97) --
+	(439.66,286.07) --
+	(442.90,287.16) --
+	(446.15,288.24) --
+	(449.39,289.34) --
+	(452.64,290.44) --
+	(455.88,291.56) --
+	(459.12,292.67) --
+	(462.37,293.78) --
+	(465.61,294.89) --
+	(468.86,295.99) --
+	(472.10,297.07) --
+	(475.34,298.14) --
+	(478.59,299.19) --
+	(481.83,300.23) --
+	(485.08,301.27) --
+	(488.32,302.30) --
+	(491.56,303.33) --
+	(494.81,304.35) --
+	(498.05,305.36) --
+	(501.29,306.36) --
+	(504.54,307.33) --
+	(507.78,308.29) --
+	(511.03,309.23) --
+	(514.27,310.14) --
+	(517.51,311.04) --
+	(520.76,311.93) --
+	(524.00,312.80) --
+	(527.25,313.67) --
+	(530.49,314.51) --
+	(533.73,315.35) --
+	(536.98,316.17) --
+	(540.22,316.98) --
+	(543.47,317.77) --
+	(546.71,318.55) --
+	(549.95,319.31) --
+	(553.20,320.05) --
+	(556.44,320.78) --
+	(559.68,321.50) --
+	(562.93,322.20) --
+	(566.17,322.89) --
+	(569.42,323.56) --
+	(572.66,324.22);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (324.94,249.52) --
-	(328.07,250.42) --
-	(331.21,251.31) --
-	(334.34,252.21) --
-	(337.48,253.10) --
-	(340.61,254.00) --
-	(343.75,254.89) --
-	(346.89,255.79) --
-	(350.02,256.69) --
-	(353.16,257.58) --
-	(356.29,258.48) --
-	(359.43,259.38) --
-	(362.56,260.28) --
-	(365.70,261.18) --
-	(368.84,262.07) --
-	(371.97,262.97) --
-	(375.11,263.87) --
-	(378.24,264.76) --
-	(381.38,265.66) --
-	(384.51,266.55) --
-	(387.65,267.45) --
-	(390.79,268.35) --
-	(393.92,269.25) --
-	(397.06,270.16) --
-	(400.19,271.07) --
-	(403.33,271.98) --
-	(406.47,272.89) --
-	(409.60,273.80) --
-	(412.74,274.69) --
-	(415.87,275.58) --
-	(419.01,276.46) --
-	(422.14,277.34) --
-	(425.28,278.24) --
-	(428.42,279.14) --
-	(431.55,280.04) --
-	(434.69,280.93) --
-	(437.82,281.81) --
-	(440.96,282.67) --
-	(444.09,283.51) --
-	(447.23,284.33) --
-	(450.37,285.16) --
-	(453.50,285.99) --
-	(456.64,286.82) --
-	(459.77,287.65) --
-	(462.91,288.46) --
-	(466.04,289.26) --
-	(469.18,290.04) --
-	(472.32,290.78) --
-	(475.45,291.50) --
-	(478.59,292.17) --
-	(481.72,292.82) --
-	(484.86,293.46) --
-	(487.99,294.10) --
-	(491.13,294.71) --
-	(494.27,295.31) --
-	(497.40,295.88) --
-	(500.54,296.42) --
-	(503.67,296.93) --
-	(506.81,297.40) --
-	(509.94,297.83) --
-	(513.08,298.21) --
-	(516.22,298.55) --
-	(519.35,298.86) --
-	(522.49,299.15) --
-	(525.62,299.41) --
-	(528.76,299.64) --
-	(531.90,299.83) --
-	(535.03,300.00) --
-	(538.17,300.14) --
-	(541.30,300.24) --
-	(544.44,300.31) --
-	(547.57,300.35) --
-	(550.71,300.35) --
-	(553.85,300.33) --
-	(556.98,300.26) --
-	(560.12,300.17) --
-	(563.25,300.05) --
-	(566.39,299.89) --
-	(569.52,299.70) --
-	(572.66,299.48);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (319.64,248.18) --
+	(322.88,249.13) --
+	(326.12,250.07) --
+	(329.37,251.02) --
+	(332.61,251.97) --
+	(335.86,252.91) --
+	(339.10,253.86) --
+	(342.34,254.80) --
+	(345.59,255.75) --
+	(348.83,256.69) --
+	(352.08,257.64) --
+	(355.32,258.59) --
+	(358.56,259.53) --
+	(361.81,260.48) --
+	(365.05,261.42) --
+	(368.30,262.36) --
+	(371.54,263.30) --
+	(374.78,264.24) --
+	(378.03,265.18) --
+	(381.27,266.12) --
+	(384.51,267.07) --
+	(387.76,268.02) --
+	(391.00,268.97) --
+	(394.25,269.92) --
+	(397.49,270.86) --
+	(400.73,271.81) --
+	(403.98,272.75) --
+	(407.22,273.68) --
+	(410.47,274.60) --
+	(413.71,275.53) --
+	(416.95,276.46) --
+	(420.20,277.40) --
+	(423.44,278.34) --
+	(426.69,279.28) --
+	(429.93,280.21) --
+	(433.17,281.13) --
+	(436.42,282.03) --
+	(439.66,282.92) --
+	(442.90,283.77) --
+	(446.15,284.61) --
+	(449.39,285.45) --
+	(452.64,286.29) --
+	(455.88,287.13) --
+	(459.12,287.97) --
+	(462.37,288.79) --
+	(465.61,289.59) --
+	(468.86,290.36) --
+	(472.10,291.11) --
+	(475.34,291.82) --
+	(478.59,292.49) --
+	(481.83,293.12) --
+	(485.08,293.74) --
+	(488.32,294.35) --
+	(491.56,294.93) --
+	(494.81,295.49) --
+	(498.05,296.02) --
+	(501.29,296.52) --
+	(504.54,296.98) --
+	(507.78,297.40) --
+	(511.03,297.78) --
+	(514.27,298.10) --
+	(517.51,298.40) --
+	(520.76,298.67) --
+	(524.00,298.90) --
+	(527.25,299.11) --
+	(530.49,299.28) --
+	(533.73,299.42) --
+	(536.98,299.53) --
+	(540.22,299.60) --
+	(543.47,299.64) --
+	(546.71,299.65) --
+	(549.95,299.62) --
+	(553.20,299.56) --
+	(556.44,299.46) --
+	(559.68,299.32) --
+	(562.93,299.16) --
+	(566.17,298.96) --
+	(569.42,298.72) --
+	(572.66,298.46);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (324.94,249.43) --
-	(328.07,250.36) --
-	(331.21,251.28) --
-	(334.34,252.19) --
-	(337.48,253.10) --
-	(340.61,254.00) --
-	(343.75,254.90) --
-	(346.89,255.79) --
-	(350.02,256.67) --
-	(353.16,257.56) --
-	(356.29,258.43) --
-	(359.43,259.30) --
-	(362.56,260.17) --
-	(365.70,261.03) --
-	(368.84,261.89) --
-	(371.97,262.74) --
-	(375.11,263.58) --
-	(378.24,264.41) --
-	(381.38,265.24) --
-	(384.51,266.06) --
-	(387.65,266.87) --
-	(390.79,267.69) --
-	(393.92,268.52) --
-	(397.06,269.34) --
-	(400.19,270.15) --
-	(403.33,270.96) --
-	(406.47,271.76) --
-	(409.60,272.55) --
-	(412.74,273.32) --
-	(415.87,274.07) --
-	(419.01,274.81) --
-	(422.14,275.55) --
-	(425.28,276.29) --
-	(428.42,277.04) --
-	(431.55,277.78) --
-	(434.69,278.50) --
-	(437.82,279.20) --
-	(440.96,279.87) --
-	(444.09,280.50) --
-	(447.23,281.10) --
-	(450.37,281.71) --
-	(453.50,282.32) --
-	(456.64,282.91) --
-	(459.77,283.49) --
-	(462.91,284.05) --
-	(466.04,284.59) --
-	(469.18,285.08) --
-	(472.32,285.54) --
-	(475.45,285.96) --
-	(478.59,286.31) --
-	(481.72,286.64) --
-	(484.86,286.94) --
-	(487.99,287.23) --
-	(491.13,287.48) --
-	(494.27,287.71) --
-	(497.40,287.90) --
-	(500.54,288.05) --
-	(503.67,288.16) --
-	(506.81,288.22) --
-	(509.94,288.22) --
-	(513.08,288.16) --
-	(516.22,288.06) --
-	(519.35,287.92) --
-	(522.49,287.74) --
-	(525.62,287.52) --
-	(528.76,287.27) --
-	(531.90,286.97) --
-	(535.03,286.63) --
-	(538.17,286.24) --
-	(541.30,285.82) --
-	(544.44,285.35) --
-	(547.57,284.84) --
-	(550.71,284.28) --
-	(553.85,283.68) --
-	(556.98,283.04) --
-	(560.12,282.35) --
-	(563.25,281.63) --
-	(566.39,280.86) --
-	(569.52,280.05) --
-	(572.66,279.19);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (319.64,248.11) --
+	(322.88,249.08) --
+	(326.12,250.04) --
+	(329.37,251.00) --
+	(332.61,251.95) --
+	(335.86,252.90) --
+	(339.10,253.84) --
+	(342.34,254.78) --
+	(345.59,255.71) --
+	(348.83,256.63) --
+	(352.08,257.56) --
+	(355.32,258.47) --
+	(358.56,259.38) --
+	(361.81,260.28) --
+	(365.05,261.18) --
+	(368.30,262.07) --
+	(371.54,262.95) --
+	(374.78,263.83) --
+	(378.03,264.69) --
+	(381.27,265.56) --
+	(384.51,266.43) --
+	(387.76,267.30) --
+	(391.00,268.16) --
+	(394.25,269.02) --
+	(397.49,269.87) --
+	(400.73,270.71) --
+	(403.98,271.54) --
+	(407.22,272.35) --
+	(410.47,273.15) --
+	(413.71,273.94) --
+	(416.95,274.74) --
+	(420.20,275.54) --
+	(423.44,276.33) --
+	(426.69,277.12) --
+	(429.93,277.89) --
+	(433.17,278.64) --
+	(436.42,279.36) --
+	(439.66,280.06) --
+	(442.90,280.71) --
+	(446.15,281.34) --
+	(449.39,281.96) --
+	(452.64,282.57) --
+	(455.88,283.18) --
+	(459.12,283.78) --
+	(462.37,284.35) --
+	(465.61,284.89) --
+	(468.86,285.40) --
+	(472.10,285.86) --
+	(475.34,286.28) --
+	(478.59,286.64) --
+	(481.83,286.95) --
+	(485.08,287.25) --
+	(488.32,287.51) --
+	(491.56,287.75) --
+	(494.81,287.95) --
+	(498.05,288.11) --
+	(501.29,288.23) --
+	(504.54,288.30) --
+	(507.78,288.32) --
+	(511.03,288.28) --
+	(514.27,288.19) --
+	(517.51,288.05) --
+	(520.76,287.88) --
+	(524.00,287.67) --
+	(527.25,287.41) --
+	(530.49,287.11) --
+	(533.73,286.77) --
+	(536.98,286.39) --
+	(540.22,285.96) --
+	(543.47,285.49) --
+	(546.71,284.98) --
+	(549.95,284.41) --
+	(553.20,283.81) --
+	(556.44,283.16) --
+	(559.68,282.46) --
+	(562.93,281.72) --
+	(566.17,280.94) --
+	(569.42,280.11) --
+	(572.66,279.25);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] (324.94,253.65) --
-	(328.30,247.82) --
-	(321.57,247.82) --
-	cycle;
-
-\path[fill=fillColor] (333.48,255.98) --
-	(336.84,250.15) --
-	(330.11,250.15) --
-	cycle;
-
-\path[fill=fillColor] (342.02,258.37) --
-	(345.38,252.54) --
-	(338.66,252.54) --
-	cycle;
-
-\path[fill=fillColor] (350.56,260.82) --
-	(353.93,255.00) --
-	(347.20,255.00) --
-	cycle;
-
-\path[fill=fillColor] (359.10,263.33) --
-	(362.47,257.51) --
-	(355.74,257.51) --
-	cycle;
-
-\path[fill=fillColor] (367.65,265.91) --
-	(371.01,260.08) --
-	(364.28,260.08) --
-	cycle;
-
-\path[fill=fillColor] (376.19,268.53) --
-	(379.55,262.71) --
-	(372.83,262.71) --
-	cycle;
-
-\path[fill=fillColor] (384.73,271.21) --
-	(388.09,265.39) --
-	(381.37,265.39) --
-	cycle;
-
-\path[fill=fillColor] (393.27,273.94) --
-	(396.64,268.12) --
-	(389.91,268.12) --
-	cycle;
-
-\path[fill=fillColor] (401.82,276.72) --
-	(405.18,270.90) --
-	(398.45,270.90) --
-	cycle;
-
-\path[fill=fillColor] (410.36,279.54) --
-	(413.72,273.72) --
-	(406.99,273.72) --
-	cycle;
-
-\path[fill=fillColor] (418.90,282.40) --
-	(422.26,276.58) --
-	(415.54,276.58) --
-	cycle;
-
-\path[fill=fillColor] (427.44,285.29) --
-	(430.81,279.47) --
-	(424.08,279.47) --
-	cycle;
-
-\path[fill=fillColor] (435.98,288.22) --
-	(439.35,282.39) --
-	(432.62,282.39) --
-	cycle;
-
-\path[fill=fillColor] (444.53,291.16) --
-	(447.89,285.33) --
-	(441.16,285.33) --
-	cycle;
-
-\path[fill=fillColor] (453.07,294.11) --
-	(456.43,288.29) --
-	(449.71,288.29) --
-	cycle;
-
-\path[fill=fillColor] (461.61,297.08) --
-	(464.97,291.25) --
-	(458.25,291.25) --
-	cycle;
-
-\path[fill=fillColor] (470.15,300.04) --
-	(473.52,294.21) --
-	(466.79,294.21) --
-	cycle;
-
-\path[fill=fillColor] (478.70,302.98) --
-	(482.06,297.15) --
-	(475.33,297.15) --
-	cycle;
-
-\path[fill=fillColor] (487.24,305.90) --
-	(490.60,300.08) --
-	(483.87,300.08) --
-	cycle;
-
-\path[fill=fillColor] (495.78,308.78) --
-	(499.14,302.96) --
-	(492.42,302.96) --
-	cycle;
-
-\path[fill=fillColor] (504.32,311.61) --
-	(507.69,305.79) --
-	(500.96,305.79) --
-	cycle;
-
-\path[fill=fillColor] (512.86,314.38) --
-	(516.23,308.55) --
-	(509.50,308.55) --
-	cycle;
-
-\path[fill=fillColor] (521.41,317.05) --
-	(524.77,311.23) --
-	(518.04,311.23) --
-	cycle;
-
-\path[fill=fillColor] (529.95,319.62) --
-	(533.31,313.79) --
-	(526.59,313.79) --
-	cycle;
-
-\path[fill=fillColor] (538.49,322.06) --
-	(541.85,316.24) --
-	(535.13,316.24) --
-	cycle;
-
-\path[fill=fillColor] (547.03,324.35) --
-	(550.40,318.52) --
-	(543.67,318.52) --
-	cycle;
-
-\path[fill=fillColor] (555.58,326.46) --
-	(558.94,320.63) --
-	(552.21,320.63) --
-	cycle;
-
-\path[fill=fillColor] (564.12,328.36) --
-	(567.48,322.54) --
-	(560.75,322.54) --
-	cycle;
-
-\path[fill=fillColor] (572.66,330.02) --
-	(576.02,324.20) --
-	(569.30,324.20) --
+\path[fill=fillColor] (316.39,251.38) --
+	(319.76,245.55) --
+	(313.03,245.55) --
+	cycle;
+
+\path[fill=fillColor] (324.94,253.70) --
+	(328.30,247.88) --
+	(321.57,247.88) --
+	cycle;
+
+\path[fill=fillColor] (333.48,256.09) --
+	(336.84,250.27) --
+	(330.11,250.27) --
+	cycle;
+
+\path[fill=fillColor] (342.02,258.54) --
+	(345.38,252.71) --
+	(338.66,252.71) --
+	cycle;
+
+\path[fill=fillColor] (350.56,261.05) --
+	(353.93,255.22) --
+	(347.20,255.22) --
+	cycle;
+
+\path[fill=fillColor] (359.10,263.61) --
+	(362.47,257.79) --
+	(355.74,257.79) --
+	cycle;
+
+\path[fill=fillColor] (367.65,266.23) --
+	(371.01,260.40) --
+	(364.28,260.40) --
+	cycle;
+
+\path[fill=fillColor] (376.19,268.90) --
+	(379.55,263.07) --
+	(372.83,263.07) --
+	cycle;
+
+\path[fill=fillColor] (384.73,271.62) --
+	(388.09,265.79) --
+	(381.37,265.79) --
+	cycle;
+
+\path[fill=fillColor] (393.27,274.38) --
+	(396.64,268.55) --
+	(389.91,268.55) --
+	cycle;
+
+\path[fill=fillColor] (401.82,277.18) --
+	(405.18,271.35) --
+	(398.45,271.35) --
+	cycle;
+
+\path[fill=fillColor] (410.36,280.01) --
+	(413.72,274.19) --
+	(406.99,274.19) --
+	cycle;
+
+\path[fill=fillColor] (418.90,282.88) --
+	(422.26,277.05) --
+	(415.54,277.05) --
+	cycle;
+
+\path[fill=fillColor] (427.44,285.76) --
+	(430.81,279.94) --
+	(424.08,279.94) --
+	cycle;
+
+\path[fill=fillColor] (435.98,288.66) --
+	(439.35,282.84) --
+	(432.62,282.84) --
+	cycle;
+
+\path[fill=fillColor] (444.53,291.57) --
+	(447.89,285.74) --
+	(441.16,285.74) --
+	cycle;
+
+\path[fill=fillColor] (453.07,294.48) --
+	(456.43,288.65) --
+	(449.71,288.65) --
+	cycle;
+
+\path[fill=fillColor] (461.61,297.37) --
+	(464.97,291.55) --
+	(458.25,291.55) --
+	cycle;
+
+\path[fill=fillColor] (470.15,300.25) --
+	(473.52,294.42) --
+	(466.79,294.42) --
+	cycle;
+
+\path[fill=fillColor] (478.70,303.09) --
+	(482.06,297.26) --
+	(475.33,297.26) --
+	cycle;
+
+\path[fill=fillColor] (487.24,305.88) --
+	(490.60,300.06) --
+	(483.87,300.06) --
+	cycle;
+
+\path[fill=fillColor] (495.78,308.62) --
+	(499.14,302.79) --
+	(492.42,302.79) --
+	cycle;
+
+\path[fill=fillColor] (504.32,311.28) --
+	(507.69,305.46) --
+	(500.96,305.46) --
+	cycle;
+
+\path[fill=fillColor] (512.86,313.85) --
+	(516.23,308.03) --
+	(509.50,308.03) --
+	cycle;
+
+\path[fill=fillColor] (521.41,316.31) --
+	(524.77,310.49) --
+	(518.04,310.49) --
+	cycle;
+
+\path[fill=fillColor] (529.95,318.64) --
+	(533.31,312.82) --
+	(526.59,312.82) --
+	cycle;
+
+\path[fill=fillColor] (538.49,320.82) --
+	(541.85,314.99) --
+	(535.13,314.99) --
+	cycle;
+
+\path[fill=fillColor] (547.03,322.82) --
+	(550.40,317.00) --
+	(543.67,317.00) --
+	cycle;
+
+\path[fill=fillColor] (555.58,324.63) --
+	(558.94,318.80) --
+	(552.21,318.80) --
+	cycle;
+
+\path[fill=fillColor] (564.12,326.21) --
+	(567.48,320.38) --
+	(560.75,320.38) --
+	cycle;
+
+\path[fill=fillColor] (572.66,327.53) --
+	(576.02,321.70) --
+	(569.30,321.70) --
 	cycle;
@@
 
-\path[fill=fillColor] (322.44,247.24) --
-	(327.43,247.24) --
-	(327.43,252.23) --
-	(322.44,252.23) --
-	cycle;
-
-\path[fill=fillColor] (330.98,249.53) --
-	(335.98,249.53) --
-	(335.98,254.52) --
-	(330.98,254.52) --
-	cycle;
-
-\path[fill=fillColor] (339.52,251.86) --
-	(344.52,251.86) --
-	(344.52,256.85) --
-	(339.52,256.85) --
-	cycle;
-
-\path[fill=fillColor] (348.06,254.23) --
-	(353.06,254.23) --
-	(353.06,259.22) --
-	(348.06,259.22) --
-	cycle;
-
-\path[fill=fillColor] (356.61,256.63) --
-	(361.60,256.63) --
-	(361.60,261.63) --
-	(356.61,261.63) --
-	cycle;
-
-\path[fill=fillColor] (365.15,259.06) --
-	(370.14,259.06) --
-	(370.14,264.06) --
-	(365.15,264.06) --
-	cycle;
-
-\path[fill=fillColor] (373.69,261.52) --
-	(378.69,261.52) --
-	(378.69,266.52) --
-	(373.69,266.52) --
-	cycle;
-
-\path[fill=fillColor] (382.23,264.00) --
-	(387.23,264.00) --
-	(387.23,268.99) --
-	(382.23,268.99) --
-	cycle;
-
-\path[fill=fillColor] (390.78,266.48) --
-	(395.77,266.48) --
-	(395.77,271.48) --
-	(390.78,271.48) --
-	cycle;
-
-\path[fill=fillColor] (399.32,268.97) --
-	(404.31,268.97) --
-	(404.31,273.96) --
-	(399.32,273.96) --
-	cycle;
-
-\path[fill=fillColor] (407.86,271.45) --
-	(412.86,271.45) --
-	(412.86,276.44) --
-	(407.86,276.44) --
-	cycle;
-
-\path[fill=fillColor] (416.40,273.91) --
-	(421.40,273.91) --
-	(421.40,278.91) --
-	(416.40,278.91) --
-	cycle;
-
-\path[fill=fillColor] (424.94,276.35) --
-	(429.94,276.35) --
-	(429.94,281.35) --
-	(424.94,281.35) --
-	cycle;
-
-\path[fill=fillColor] (433.49,278.75) --
-	(438.48,278.75) --
-	(438.48,283.74) --
-	(433.49,283.74) --
-	cycle;
-
-\path[fill=fillColor] (442.03,281.10) --
-	(447.02,281.10) --
-	(447.02,286.09) --
-	(442.03,286.09) --
-	cycle;
-
-\path[fill=fillColor] (450.57,283.38) --
-	(455.57,283.38) --
-	(455.57,288.37) --
-	(450.57,288.37) --
-	cycle;
-
-\path[fill=fillColor] (459.11,285.58) --
-	(464.11,285.58) --
-	(464.11,290.57) --
-	(459.11,290.57) --
-	cycle;
-
-\path[fill=fillColor] (467.66,287.68) --
-	(472.65,287.68) --
-	(472.65,292.67) --
-	(467.66,292.67) --
-	cycle;
-
-\path[fill=fillColor] (476.20,289.66) --
-	(481.19,289.66) --
-	(481.19,294.66) --
-	(476.20,294.66) --
-	cycle;
-
-\path[fill=fillColor] (484.74,291.50) --
-	(489.74,291.50) --
-	(489.74,296.50) --
-	(484.74,296.50) --
-	cycle;
-
-\path[fill=fillColor] (493.28,293.19) --
-	(498.28,293.19) --
-	(498.28,298.18) --
-	(493.28,298.18) --
-	cycle;
-
-\path[fill=fillColor] (501.82,294.68) --
-	(506.82,294.68) --
-	(506.82,299.67) --
-	(501.82,299.67) --
-	cycle;
-
-\path[fill=fillColor] (510.37,295.96) --
-	(515.36,295.96) --
-	(515.36,300.95) --
-	(510.37,300.95) --
-	cycle;
-
-\path[fill=fillColor] (518.91,296.99) --
-	(523.90,296.99) --
-	(523.90,301.99) --
-	(518.91,301.99) --
-	cycle;
-
-\path[fill=fillColor] (527.45,297.75) --
-	(532.45,297.75) --
-	(532.45,302.75) --
-	(527.45,302.75) --
-	cycle;
-
-\path[fill=fillColor] (535.99,298.20) --
-	(540.99,298.20) --
-	(540.99,303.20) --
-	(535.99,303.20) --
-	cycle;
-
-\path[fill=fillColor] (544.54,298.31) --
-	(549.53,298.31) --
-	(549.53,303.30) --
-	(544.54,303.30) --
-	cycle;
-
-\path[fill=fillColor] (553.08,298.03) --
-	(558.07,298.03) --
-	(558.07,303.03) --
-	(553.08,303.03) --
-	cycle;
-
-\path[fill=fillColor] (561.62,297.34) --
-	(566.62,297.34) --
-	(566.62,302.34) --
-	(561.62,302.34) --
-	cycle;
-
-\path[fill=fillColor] (570.16,296.21) --
-	(575.16,296.21) --
-	(575.16,301.20) --
-	(570.16,301.20) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.40,249.75) -- (328.47,249.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.94,246.21) -- (324.94,253.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.95,252.03) -- (337.01,252.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.48,248.49) -- (333.48,255.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.49,254.33) -- (345.55,254.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.02,250.80) -- (342.02,257.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.03,256.65) -- (354.09,256.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.12) -- (350.56,260.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,258.98) -- (362.64,258.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,255.45) -- (359.10,262.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,261.32) -- (371.18,261.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,257.78) -- (367.65,264.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,263.64) -- (379.72,263.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,260.11) -- (376.19,267.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,265.95) -- (388.26,265.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,262.42) -- (384.73,269.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,268.23) -- (396.81,268.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,264.69) -- (393.27,271.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,270.46) -- (405.35,270.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,266.93) -- (401.82,274.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,272.65) -- (413.89,272.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,269.12) -- (410.36,276.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,274.77) -- (422.43,274.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,271.23) -- (418.90,278.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,276.80) -- (430.97,276.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,273.27) -- (427.44,280.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,278.74) -- (439.52,278.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,275.21) -- (435.98,282.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,280.56) -- (448.06,280.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,277.03) -- (444.53,284.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,282.25) -- (456.60,282.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,278.72) -- (453.07,285.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,283.78) -- (465.14,283.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,280.25) -- (461.61,287.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,285.14) -- (473.69,285.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,281.61) -- (470.15,288.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,286.31) -- (482.23,286.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,282.77) -- (478.70,289.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,287.25) -- (490.77,287.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,283.71) -- (487.24,290.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,287.94) -- (499.31,287.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,284.40) -- (495.78,291.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,288.35) -- (507.85,288.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,284.82) -- (504.32,291.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,288.47) -- (516.40,288.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,284.93) -- (512.86,292.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,288.25) -- (524.94,288.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,284.72) -- (521.41,291.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,287.67) -- (533.48,287.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,284.14) -- (529.95,291.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,286.70) -- (542.02,286.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,283.17) -- (538.49,290.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,285.32) -- (550.57,285.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,281.79) -- (547.03,288.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,283.50) -- (559.11,283.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,279.97) -- (555.58,287.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,281.24) -- (567.65,281.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,277.71) -- (564.12,284.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,278.52) -- (576.19,278.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,274.99) -- (572.66,282.05);
+\path[fill=fillColor] (313.90,245.00) --
+	(318.89,245.00) --
+	(318.89,249.99) --
+	(313.90,249.99) --
+	cycle;
+
+\path[fill=fillColor] (322.44,247.31) --
+	(327.43,247.31) --
+	(327.43,252.31) --
+	(322.44,252.31) --
+	cycle;
+
+\path[fill=fillColor] (330.98,249.68) --
+	(335.98,249.68) --
+	(335.98,254.67) --
+	(330.98,254.67) --
+	cycle;
+
+\path[fill=fillColor] (339.52,252.08) --
+	(344.52,252.08) --
+	(344.52,257.07) --
+	(339.52,257.07) --
+	cycle;
+
+\path[fill=fillColor] (348.06,254.52) --
+	(353.06,254.52) --
+	(353.06,259.51) --
+	(348.06,259.51) --
+	cycle;
+
+\path[fill=fillColor] (356.61,256.99) --
+	(361.60,256.99) --
+	(361.60,261.98) --
+	(356.61,261.98) --
+	cycle;
+
+\path[fill=fillColor] (365.15,259.48) --
+	(370.14,259.48) --
+	(370.14,264.47) --
+	(365.15,264.47) --
+	cycle;
+
+\path[fill=fillColor] (373.69,261.99) --
+	(378.69,261.99) --
+	(378.69,266.99) --
+	(373.69,266.99) --
+	cycle;
+
+\path[fill=fillColor] (382.23,264.51) --
+	(387.23,264.51) --
+	(387.23,269.51) --
+	(382.23,269.51) --
+	cycle;
+
+\path[fill=fillColor] (390.78,267.04) --
+	(395.77,267.04) --
+	(395.77,272.03) --
+	(390.78,272.03) --
+	cycle;
+
+\path[fill=fillColor] (399.32,269.56) --
+	(404.31,269.56) --
+	(404.31,274.55) --
+	(399.32,274.55) --
+	cycle;
+
+\path[fill=fillColor] (407.86,272.06) --
+	(412.86,272.06) --
+	(412.86,277.05) --
+	(407.86,277.05) --
+	cycle;
+
+\path[fill=fillColor] (416.40,274.53) --
+	(421.40,274.53) --
+	(421.40,279.53) --
+	(416.40,279.53) --
+	cycle;
+
+\path[fill=fillColor] (424.94,276.97) --
+	(429.94,276.97) --
+	(429.94,281.96) --
+	(424.94,281.96) --
+	cycle;
+
+\path[fill=fillColor] (433.49,279.35) --
+	(438.48,279.35) --
+	(438.48,284.35) --
+	(433.49,284.35) --
+	cycle;
+
+\path[fill=fillColor] (442.03,281.67) --
+	(447.02,281.67) --
+	(447.02,286.67) --
+	(442.03,286.67) --
+	cycle;
+
+\path[fill=fillColor] (450.57,283.91) --
+	(455.57,283.91) --
+	(455.57,288.91) --
+	(450.57,288.91) --
+	cycle;
+
+\path[fill=fillColor] (459.11,286.06) --
+	(464.11,286.06) --
+	(464.11,291.05) --
+	(459.11,291.05) --
+	cycle;
+
+\path[fill=fillColor] (467.66,288.09) --
+	(472.65,288.09) --
+	(472.65,293.08) --
+	(467.66,293.08) --
+	cycle;
+
+\path[fill=fillColor] (476.20,289.98) --
+	(481.19,289.98) --
+	(481.19,294.98) --
+	(476.20,294.98) --
+	cycle;
+
+\path[fill=fillColor] (484.74,291.73) --
+	(489.74,291.73) --
+	(489.74,296.72) --
+	(484.74,296.72) --
+	cycle;
+
+\path[fill=fillColor] (493.28,293.30) --
+	(498.28,293.30) --
+	(498.28,298.29) --
+	(493.28,298.29) --
+	cycle;
+
+\path[fill=fillColor] (501.82,294.66) --
+	(506.82,294.66) --
+	(506.82,299.66) --
+	(501.82,299.66) --
+	cycle;
+
+\path[fill=fillColor] (510.37,295.81) --
+	(515.36,295.81) --
+	(515.36,300.80) --
+	(510.37,300.80) --
+	cycle;
+
+\path[fill=fillColor] (518.91,296.70) --
+	(523.90,296.70) --
+	(523.90,301.70) --
+	(518.91,301.70) --
+	cycle;
+
+\path[fill=fillColor] (527.45,297.31) --
+	(532.45,297.31) --
+	(532.45,302.31) --
+	(527.45,302.31) --
+	cycle;
+
+\path[fill=fillColor] (535.99,297.62) --
+	(540.99,297.62) --
+	(540.99,302.61) --
+	(535.99,302.61) --
+	cycle;
+
+\path[fill=fillColor] (544.54,297.58) --
+	(549.53,297.58) --
+	(549.53,302.58) --
+	(544.54,302.58) --
+	cycle;
+
+\path[fill=fillColor] (553.08,297.18) --
+	(558.07,297.18) --
+	(558.07,302.18) --
+	(553.08,302.18) --
+	cycle;
+
+\path[fill=fillColor] (561.62,296.38) --
+	(566.62,296.38) --
+	(566.62,301.38) --
+	(561.62,301.38) --
+	cycle;
+
+\path[fill=fillColor] (570.16,295.16) --
+	(575.16,295.16) --
+	(575.16,300.16) --
+	(570.16,300.16) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.86,247.50) -- (319.93,247.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.39,243.96) -- (316.39,251.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.40,249.80) -- (328.47,249.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.94,246.27) -- (324.94,253.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.95,252.14) -- (337.01,252.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.48,248.61) -- (333.48,255.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.49,254.50) -- (345.55,254.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.02,250.97) -- (342.02,258.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.03,256.87) -- (354.09,256.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.34) -- (350.56,260.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,259.25) -- (362.64,259.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,255.72) -- (359.10,262.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,261.63) -- (371.18,261.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,258.10) -- (367.65,265.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,263.99) -- (379.72,263.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,260.46) -- (376.19,267.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,266.33) -- (388.26,266.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,262.80) -- (384.73,269.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,268.64) -- (396.81,268.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,265.11) -- (393.27,272.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,270.90) -- (405.35,270.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,267.37) -- (401.82,274.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,273.10) -- (413.89,273.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,269.57) -- (410.36,276.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,275.23) -- (422.43,275.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,271.70) -- (418.90,278.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,277.27) -- (430.97,277.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,273.73) -- (427.44,280.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,279.20) -- (439.52,279.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,275.67) -- (435.98,282.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,281.01) -- (448.06,281.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,277.48) -- (444.53,284.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,282.68) -- (456.60,282.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,279.14) -- (453.07,286.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,284.18) -- (465.14,284.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,280.65) -- (461.61,287.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,285.51) -- (473.69,285.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,281.98) -- (470.15,289.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,286.63) -- (482.23,286.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,283.10) -- (478.70,290.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,287.53) -- (490.77,287.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,283.99) -- (487.24,291.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,288.17) -- (499.31,288.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,284.64) -- (495.78,291.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,288.54) -- (507.85,288.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,285.00) -- (504.32,292.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,288.60) -- (516.40,288.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,285.07) -- (512.86,292.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,288.33) -- (524.94,288.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,284.80) -- (521.41,291.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,287.71) -- (533.48,287.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,284.18) -- (529.95,291.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,286.71) -- (542.02,286.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,283.17) -- (538.49,290.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,285.30) -- (550.57,285.30);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,281.77) -- (547.03,288.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,283.48) -- (559.11,283.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,279.95) -- (555.58,287.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,281.22) -- (567.65,281.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,277.69) -- (564.12,284.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,278.53) -- (576.19,278.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,275.00) -- (572.66,282.06);
 \definecolor{fillColor}{RGB}{0,0,0}
 
+\path[fill=fillColor] (316.39,247.50) circle (  2.50);
+
 \path[fill=fillColor] (324.94,249.83) circle (  2.50);
@@
 
-\path[fill=fillColor] (342.02,254.82) circle (  2.50);
-
-\path[fill=fillColor] (350.56,257.50) circle (  2.50);
-
-\path[fill=fillColor] (359.10,260.28) circle (  2.50);
-
-\path[fill=fillColor] (367.65,263.20) circle (  2.50);
+\path[fill=fillColor] (342.02,254.83) circle (  2.50);
+
+\path[fill=fillColor] (350.56,257.49) circle (  2.50);
+
+\path[fill=fillColor] (359.10,260.29) circle (  2.50);
+
+\path[fill=fillColor] (367.65,263.21) circle (  2.50);
 
@@
 
-\path[fill=fillColor] (384.73,269.45) circle (  2.50);
-
-\path[fill=fillColor] (393.27,272.76) circle (  2.50);
-
-\path[fill=fillColor] (401.82,276.31) circle (  2.50);
-
-\path[fill=fillColor] (410.36,279.87) circle (  2.50);
-
-\path[fill=fillColor] (418.90,283.69) circle (  2.50);
+\path[fill=fillColor] (384.73,269.43) circle (  2.50);
+
+\path[fill=fillColor] (393.27,272.82) circle (  2.50);
+
+\path[fill=fillColor] (401.82,276.23) circle (  2.50);
+
+\path[fill=fillColor] (410.36,279.89) circle (  2.50);
+
+\path[fill=fillColor] (418.90,283.67) circle (  2.50);
 
@@
 
-\path[fill=fillColor] (435.98,291.76) circle (  2.50);
-
-\path[fill=fillColor] (444.53,296.10) circle (  2.50);
-
-\path[fill=fillColor] (453.07,300.70) circle (  2.50);
-
-\path[fill=fillColor] (461.61,305.28) circle (  2.50);
-
-\path[fill=fillColor] (470.15,310.36) circle (  2.50);
-
-\path[fill=fillColor] (478.70,315.52) circle (  2.50);
-
-\path[fill=fillColor] (487.24,320.84) circle (  2.50);
-
-\path[fill=fillColor] (495.78,326.35) circle (  2.50);
-
-\path[fill=fillColor] (504.32,332.10) circle (  2.50);
-
-\path[fill=fillColor] (512.86,338.43) circle (  2.50);
-
-\path[fill=fillColor] (521.41,344.40) circle (  2.50);
-
-\path[fill=fillColor] (529.95,351.37) circle (  2.50);
-
-\path[fill=fillColor] (538.49,357.84) circle (  2.50);
-
-\path[fill=fillColor] (547.03,365.25) circle (  2.50);
-
-\path[fill=fillColor] (555.58,372.83) circle (  2.50);
-
-\path[fill=fillColor] (564.12,380.80) circle (  2.50);
-
-\path[fill=fillColor] (572.66,388.87) circle (  2.50);
+\path[fill=fillColor] (435.98,291.78) circle (  2.50);
+
+\path[fill=fillColor] (444.53,296.18) circle (  2.50);
+
+\path[fill=fillColor] (453.07,300.57) circle (  2.50);
+
+\path[fill=fillColor] (461.61,305.43) circle (  2.50);
+
+\path[fill=fillColor] (470.15,310.38) circle (  2.50);
+
+\path[fill=fillColor] (478.70,315.48) circle (  2.50);
+
+\path[fill=fillColor] (487.24,320.76) circle (  2.50);
+
+\path[fill=fillColor] (495.78,326.28) circle (  2.50);
+
+\path[fill=fillColor] (504.32,332.33) circle (  2.50);
+
+\path[fill=fillColor] (512.86,338.07) circle (  2.50);
+
+\path[fill=fillColor] (521.41,344.75) circle (  2.50);
+
+\path[fill=fillColor] (529.95,350.97) circle (  2.50);
+
+\path[fill=fillColor] (538.49,358.06) circle (  2.50);
+
+\path[fill=fillColor] (547.03,365.33) circle (  2.50);
+
+\path[fill=fillColor] (555.58,372.97) circle (  2.50);
+
+\path[fill=fillColor] (564.12,380.73) circle (  2.50);
+
+\path[fill=fillColor] (572.66,388.73) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 \begin{scope}
-\path[clip] ( 34.16, 30.69) rectangle (283.58,194.15);
+\path[clip] ( 27.31, 30.69) rectangle (283.58,194.15);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 34.16, 30.69) rectangle (283.58,194.15);
+\path[fill=fillColor] ( 27.31, 30.69) rectangle (283.58,194.15);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 42.47, 40.78) --
-	( 45.52, 40.81) --
-	( 48.57, 40.84) --
-	( 51.63, 40.86) --
-	( 54.68, 40.89) --
-	( 57.73, 40.91) --
-	( 60.78, 40.93) --
-	( 63.83, 40.95) --
-	( 66.89, 40.97) --
-	( 69.94, 40.99) --
-	( 72.99, 41.00) --
-	( 76.04, 41.01) --
-	( 79.09, 41.02) --
-	( 82.15, 41.03) --
-	( 85.20, 41.04) --
-	( 88.25, 41.04) --
-	( 91.30, 41.05) --
-	( 94.35, 41.05) --
-	( 97.41, 41.06) --
-	(100.46, 41.06) --
-	(103.51, 41.07) --
-	(106.56, 41.06) --
-	(109.61, 41.06) --
-	(112.67, 41.05) --
-	(115.72, 41.05) --
-	(118.77, 41.04) --
-	(121.82, 41.03) --
-	(124.87, 41.02) --
-	(127.93, 41.02) --
-	(130.98, 41.01) --
-	(134.03, 41.02) --
-	(137.08, 41.02) --
-	(140.13, 41.03) --
-	(143.19, 41.05) --
-	(146.24, 41.06) --
-	(149.29, 41.08) --
-	(152.34, 41.09) --
-	(155.40, 41.10) --
-	(158.45, 41.11) --
-	(161.50, 41.12) --
-	(164.55, 41.12) --
-	(167.60, 41.13) --
-	(170.66, 41.14) --
-	(173.71, 41.14) --
-	(176.76, 41.15) --
-	(179.81, 41.16) --
-	(182.86, 41.16) --
-	(185.92, 41.17) --
-	(188.97, 41.17) --
-	(192.02, 41.17) --
-	(195.07, 41.17) --
-	(198.12, 41.16) --
-	(201.18, 41.15) --
-	(204.23, 41.15) --
-	(207.28, 41.14) --
-	(210.33, 41.13) --
-	(213.38, 41.12) --
-	(216.44, 41.11) --
-	(219.49, 41.10) --
-	(222.54, 41.10) --
-	(225.59, 41.10) --
-	(228.64, 41.10) --
-	(231.70, 41.10) --
-	(234.75, 41.10) --
-	(237.80, 41.10) --
-	(240.85, 41.10) --
-	(243.90, 41.10) --
-	(246.96, 41.11) --
-	(250.01, 41.11) --
-	(253.06, 41.11) --
-	(256.11, 41.12) --
-	(259.16, 41.12) --
-	(262.22, 41.13) --
-	(265.27, 41.14) --
-	(268.32, 41.15) --
-	(271.37, 41.16) --
-	(274.42, 41.17) --
-	(277.48, 41.18) --
-	(280.53, 41.20) --
-	(283.58, 41.21);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 47.92) --
+	( 30.56, 47.94) --
+	( 33.80, 47.96) --
+	( 37.04, 47.98) --
+	( 40.29, 48.00) --
+	( 43.53, 48.02) --
+	( 46.78, 48.03) --
+	( 50.02, 48.05) --
+	( 53.26, 48.06) --
+	( 56.51, 48.07) --
+	( 59.75, 48.09) --
+	( 63.00, 48.09) --
+	( 66.24, 48.10) --
+	( 69.48, 48.11) --
+	( 72.73, 48.12) --
+	( 75.97, 48.12) --
+	( 79.22, 48.13) --
+	( 82.46, 48.13) --
+	( 85.70, 48.14) --
+	( 88.95, 48.14) --
+	( 92.19, 48.14) --
+	( 95.43, 48.14) --
+	( 98.68, 48.14) --
+	(101.92, 48.13) --
+	(105.17, 48.12) --
+	(108.41, 48.12) --
+	(111.65, 48.11) --
+	(114.90, 48.10) --
+	(118.14, 48.10) --
+	(121.39, 48.10) --
+	(124.63, 48.11) --
+	(127.87, 48.12) --
+	(131.12, 48.13) --
+	(134.36, 48.14) --
+	(137.61, 48.16) --
+	(140.85, 48.17) --
+	(144.09, 48.19) --
+	(147.34, 48.20) --
+	(150.58, 48.21) --
+	(153.82, 48.22) --
+	(157.07, 48.22) --
+	(160.31, 48.22) --
+	(163.56, 48.22) --
+	(166.80, 48.22) --
+	(170.04, 48.22) --
+	(173.29, 48.22) --
+	(176.53, 48.22) --
+	(179.78, 48.21) --
+	(183.02, 48.21) --
+	(186.26, 48.21) --
+	(189.51, 48.20) --
+	(192.75, 48.20) --
+	(196.00, 48.20) --
+	(199.24, 48.20) --
+	(202.48, 48.19) --
+	(205.73, 48.19) --
+	(208.97, 48.19) --
+	(212.21, 48.18) --
+	(215.46, 48.18) --
+	(218.70, 48.18) --
+	(221.95, 48.18) --
+	(225.19, 48.18) --
+	(228.43, 48.18) --
+	(231.68, 48.17) --
+	(234.92, 48.17) --
+	(238.17, 48.17) --
+	(241.41, 48.17) --
+	(244.65, 48.17) --
+	(247.90, 48.17) --
+	(251.14, 48.16) --
+	(254.39, 48.16) --
+	(257.63, 48.16) --
+	(260.87, 48.16) --
+	(264.12, 48.16) --
+	(267.36, 48.16) --
+	(270.60, 48.16) --
+	(273.85, 48.17) --
+	(277.09, 48.17) --
+	(280.34, 48.17) --
+	(283.58, 48.17);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 42.47, 33.33) --
-	( 45.52, 34.95) --
-	( 48.57, 36.56) --
-	( 51.63, 38.16) --
-	( 54.68, 39.73) --
-	( 57.73, 41.29) --
-	( 60.78, 42.83) --
-	( 63.83, 44.35) --
-	( 66.89, 45.86) --
-	( 69.94, 47.35) --
-	( 72.99, 48.82) --
-	( 76.04, 50.27) --
-	( 79.09, 51.71) --
-	( 82.15, 53.13) --
-	( 85.20, 54.53) --
-	( 88.25, 55.91) --
-	( 91.30, 57.28) --
-	( 94.35, 58.63) --
-	( 97.41, 59.97) --
-	(100.46, 61.29) --
-	(103.51, 62.59) --
-	(106.56, 63.87) --
-	(109.61, 65.13) --
-	(112.67, 66.36) --
-	(115.72, 67.58) --
-	(118.77, 68.78) --
-	(121.82, 69.97) --
-	(124.87, 71.15) --
-	(127.93, 72.31) --
-	(130.98, 73.46) --
-	(134.03, 74.61) --
-	(137.08, 75.73) --
-	(140.13, 76.83) --
-	(143.19, 77.91) --
-	(146.24, 78.98) --
-	(149.29, 80.03) --
-	(152.34, 81.07) --
-	(155.40, 82.12) --
-	(158.45, 83.16) --
-	(161.50, 84.21) --
-	(164.55, 85.23) --
-	(167.60, 86.25) --
-	(170.66, 87.26) --
-	(173.71, 88.26) --
-	(176.76, 89.24) --
-	(179.81, 90.22) --
-	(182.86, 91.20) --
-	(185.92, 92.16) --
-	(188.97, 93.13) --
-	(192.02, 94.09) --
-	(195.07, 95.04) --
-	(198.12, 95.99) --
-	(201.18, 96.93) --
-	(204.23, 97.87) --
-	(207.28, 98.79) --
-	(210.33, 99.71) --
-	(213.38,100.62) --
-	(216.44,101.53) --
-	(219.49,102.42) --
-	(222.54,103.32) --
-	(225.59,104.20) --
-	(228.64,105.08) --
-	(231.70,105.95) --
-	(234.75,106.81) --
-	(237.80,107.67) --
-	(240.85,108.51) --
-	(243.90,109.36) --
-	(246.96,110.19) --
-	(250.01,111.02) --
-	(253.06,111.84) --
-	(256.11,112.65) --
-	(259.16,113.46) --
-	(262.22,114.26) --
-	(265.27,115.05) --
-	(268.32,115.83) --
-	(271.37,116.61) --
-	(274.42,117.38) --
-	(277.48,118.15) --
-	(280.53,118.91) --
-	(283.58,119.66);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31, 49.28) --
+	( 30.56, 50.77) --
+	( 33.80, 52.24) --
+	( 37.04, 53.70) --
+	( 40.29, 55.14) --
+	( 43.53, 56.57) --
+	( 46.78, 57.98) --
+	( 50.02, 59.38) --
+	( 53.26, 60.76) --
+	( 56.51, 62.12) --
+	( 59.75, 63.47) --
+	( 63.00, 64.80) --
+	( 66.24, 66.12) --
+	( 69.48, 67.42) --
+	( 72.73, 68.70) --
+	( 75.97, 69.97) --
+	( 79.22, 71.22) --
+	( 82.46, 72.46) --
+	( 85.70, 73.69) --
+	( 88.95, 74.89) --
+	( 92.19, 76.08) --
+	( 95.43, 77.25) --
+	( 98.68, 78.41) --
+	(101.92, 79.55) --
+	(105.17, 80.67) --
+	(108.41, 81.77) --
+	(111.65, 82.86) --
+	(114.90, 83.94) --
+	(118.14, 85.01) --
+	(121.39, 86.06) --
+	(124.63, 87.10) --
+	(127.87, 88.12) --
+	(131.12, 89.11) --
+	(134.36, 90.09) --
+	(137.61, 91.06) --
+	(140.85, 92.01) --
+	(144.09, 92.95) --
+	(147.34, 93.89) --
+	(150.58, 94.82) --
+	(153.82, 95.75) --
+	(157.07, 96.69) --
+	(160.31, 97.61) --
+	(163.56, 98.51) --
+	(166.80, 99.41) --
+	(170.04,100.30) --
+	(173.29,101.18) --
+	(176.53,102.05) --
+	(179.78,102.92) --
+	(183.02,103.78) --
+	(186.26,104.64) --
+	(189.51,105.49) --
+	(192.75,106.34) --
+	(196.00,107.19) --
+	(199.24,108.02) --
+	(202.48,108.85) --
+	(205.73,109.67) --
+	(208.97,110.49) --
+	(212.21,111.30) --
+	(215.46,112.10) --
+	(218.70,112.90) --
+	(221.95,113.69) --
+	(225.19,114.48) --
+	(228.43,115.26) --
+	(231.68,116.03) --
+	(234.92,116.79) --
+	(238.17,117.55) --
+	(241.41,118.30) --
+	(244.65,119.05) --
+	(247.90,119.79) --
+	(251.14,120.52) --
+	(254.39,121.25) --
+	(257.63,121.97) --
+	(260.87,122.69) --
+	(264.12,123.39) --
+	(267.36,124.10) --
+	(270.60,124.79) --
+	(273.85,125.48) --
+	(277.09,126.16) --
+	(280.34,126.84) --
+	(283.58,127.51);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 42.47, 30.69) --
-	( 45.52, 32.91) --
-	( 48.57, 35.11) --
-	( 51.63, 37.29) --
-	( 54.68, 39.45) --
-	( 57.73, 41.58) --
-	( 60.78, 43.69) --
-	( 63.83, 45.78) --
-	( 66.89, 47.85) --
-	( 69.94, 49.90) --
-	( 72.99, 51.92) --
-	( 76.04, 53.92) --
-	( 79.09, 55.90) --
-	( 82.15, 57.85) --
-	( 85.20, 59.79) --
-	( 88.25, 61.70) --
-	( 91.30, 63.59) --
-	( 94.35, 65.46) --
-	( 97.41, 67.31) --
-	(100.46, 69.14) --
-	(103.51, 70.95) --
-	(106.56, 72.73) --
-	(109.61, 74.47) --
-	(112.67, 76.20) --
-	(115.72, 77.90) --
-	(118.77, 79.57) --
-	(121.82, 81.23) --
-	(124.87, 82.88) --
-	(127.93, 84.50) --
-	(130.98, 86.12) --
-	(134.03, 87.72) --
-	(137.08, 89.31) --
-	(140.13, 90.86) --
-	(143.19, 92.38) --
-	(146.24, 93.88) --
-	(149.29, 95.37) --
-	(152.34, 96.85) --
-	(155.40, 98.32) --
-	(158.45, 99.80) --
-	(161.50,101.28) --
-	(164.55,102.73) --
-	(167.60,104.18) --
-	(170.66,105.61) --
-	(173.71,107.03) --
-	(176.76,108.44) --
-	(179.81,109.83) --
-	(182.86,111.22) --
-	(185.92,112.60) --
-	(188.97,113.98) --
-	(192.02,115.35) --
-	(195.07,116.72) --
-	(198.12,118.07) --
-	(201.18,119.42) --
-	(204.23,120.76) --
-	(207.28,122.08) --
-	(210.33,123.40) --
-	(213.38,124.71) --
-	(216.44,126.01) --
-	(219.49,127.30) --
-	(222.54,128.58) --
-	(225.59,129.86) --
-	(228.64,131.12) --
-	(231.70,132.38) --
-	(234.75,133.62) --
-	(237.80,134.86) --
-	(240.85,136.09) --
-	(243.90,137.31) --
-	(246.96,138.51) --
-	(250.01,139.71) --
-	(253.06,140.91) --
-	(256.11,142.09) --
-	(259.16,143.26) --
-	(262.22,144.42) --
-	(265.27,145.58) --
-	(268.32,146.73) --
-	(271.37,147.86) --
-	(274.42,148.99) --
-	(277.48,150.11) --
-	(280.53,151.22) --
-	(283.58,152.32);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31, 49.13) --
+	( 30.56, 51.18) --
+	( 33.80, 53.21) --
+	( 37.04, 55.22) --
+	( 40.29, 57.21) --
+	( 43.53, 59.18) --
+	( 46.78, 61.13) --
+	( 50.02, 63.06) --
+	( 53.26, 64.97) --
+	( 56.51, 66.86) --
+	( 59.75, 68.72) --
+	( 63.00, 70.57) --
+	( 66.24, 72.40) --
+	( 69.48, 74.20) --
+	( 72.73, 75.99) --
+	( 75.97, 77.75) --
+	( 79.22, 79.50) --
+	( 82.46, 81.23) --
+	( 85.70, 82.94) --
+	( 88.95, 84.63) --
+	( 92.19, 86.29) --
+	( 95.43, 87.93) --
+	( 98.68, 89.55) --
+	(101.92, 91.15) --
+	(105.17, 92.73) --
+	(108.41, 94.28) --
+	(111.65, 95.82) --
+	(114.90, 97.35) --
+	(118.14, 98.86) --
+	(121.39,100.35) --
+	(124.63,101.82) --
+	(127.87,103.26) --
+	(131.12,104.67) --
+	(134.36,106.06) --
+	(137.61,107.43) --
+	(140.85,108.79) --
+	(144.09,110.14) --
+	(147.34,111.48) --
+	(150.58,112.81) --
+	(153.82,114.15) --
+	(157.07,115.48) --
+	(160.31,116.80) --
+	(163.56,118.11) --
+	(166.80,119.40) --
+	(170.04,120.68) --
+	(173.29,121.95) --
+	(176.53,123.21) --
+	(179.78,124.46) --
+	(183.02,125.71) --
+	(186.26,126.95) --
+	(189.51,128.18) --
+	(192.75,129.41) --
+	(196.00,130.63) --
+	(199.24,131.84) --
+	(202.48,133.05) --
+	(205.73,134.24) --
+	(208.97,135.43) --
+	(212.21,136.61) --
+	(215.46,137.78) --
+	(218.70,138.94) --
+	(221.95,140.09) --
+	(225.19,141.23) --
+	(228.43,142.37) --
+	(231.68,143.50) --
+	(234.92,144.62) --
+	(238.17,145.73) --
+	(241.41,146.83) --
+	(244.65,147.92) --
+	(247.90,149.01) --
+	(251.14,150.08) --
+	(254.39,151.15) --
+	(257.63,152.21) --
+	(260.87,153.26) --
+	(264.12,154.30) --
+	(267.36,155.33) --
+	(270.60,156.36) --
+	(273.85,157.38) --
+	(277.09,158.39) --
+	(280.34,159.39) --
+	(283.58,160.38);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 42.47, 35.97) --
-	( 45.52, 38.77) --
-	( 48.57, 41.54) --
-	( 51.63, 44.28) --
-	( 54.68, 47.00) --
-	( 57.73, 49.69) --
-	( 60.78, 52.36) --
-	( 63.83, 55.00) --
-	( 66.89, 57.61) --
-	( 69.94, 60.20) --
-	( 72.99, 62.76) --
-	( 76.04, 65.30) --
-	( 79.09, 67.81) --
-	( 82.15, 70.29) --
-	( 85.20, 72.75) --
-	( 88.25, 75.18) --
-	( 91.30, 77.59) --
-	( 94.35, 79.97) --
-	( 97.41, 82.33) --
-	(100.46, 84.67) --
-	(103.51, 86.98) --
-	(106.56, 89.25) --
-	(109.61, 91.49) --
-	(112.67, 93.71) --
-	(115.72, 95.89) --
-	(118.77, 98.05) --
-	(121.82,100.18) --
-	(124.87,102.30) --
-	(127.93,104.40) --
-	(130.98,106.49) --
-	(134.03,108.56) --
-	(137.08,110.61) --
-	(140.13,112.62) --
-	(143.19,114.60) --
-	(146.24,116.55) --
-	(149.29,118.49) --
-	(152.34,120.42) --
-	(155.40,122.34) --
-	(158.45,124.27) --
-	(161.50,126.20) --
-	(164.55,128.11) --
-	(167.60,130.00) --
-	(170.66,131.87) --
-	(173.71,133.74) --
-	(176.76,135.59) --
-	(179.81,137.42) --
-	(182.86,139.25) --
-	(185.92,141.07) --
-	(188.97,142.89) --
-	(192.02,144.69) --
-	(195.07,146.49) --
-	(198.12,148.28) --
-	(201.18,150.06) --
-	(204.23,151.83) --
-	(207.28,153.58) --
-	(210.33,155.33) --
-	(213.38,157.06) --
-	(216.44,158.79) --
-	(219.49,160.50) --
-	(222.54,162.20) --
-	(225.59,163.90) --
-	(228.64,165.58) --
-	(231.70,167.25) --
-	(234.75,168.91) --
-	(237.80,170.56) --
-	(240.85,172.20) --
-	(243.90,173.83) --
-	(246.96,175.45) --
-	(250.01,177.06) --
-	(253.06,178.66) --
-	(256.11,180.24) --
-	(259.16,181.82) --
-	(262.22,183.39) --
-	(265.27,184.94) --
-	(268.32,186.49) --
-	(271.37,188.02) --
-	(274.42,189.55) --
-	(277.48,191.06) --
-	(280.53,192.56) --
-	(283.58,194.05);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 48.86) --
+	( 30.56, 51.44) --
+	( 33.80, 54.00) --
+	( 37.04, 56.54) --
+	( 40.29, 59.06) --
+	( 43.53, 61.55) --
+	( 46.78, 64.02) --
+	( 50.02, 66.46) --
+	( 53.26, 68.88) --
+	( 56.51, 71.28) --
+	( 59.75, 73.65) --
+	( 63.00, 76.00) --
+	( 66.24, 78.32) --
+	( 69.48, 80.62) --
+	( 72.73, 82.90) --
+	( 75.97, 85.15) --
+	( 79.22, 87.38) --
+	( 82.46, 89.59) --
+	( 85.70, 91.78) --
+	( 88.95, 93.94) --
+	( 92.19, 96.08) --
+	( 95.43, 98.19) --
+	( 98.68,100.27) --
+	(101.92,102.33) --
+	(105.17,104.37) --
+	(108.41,106.38) --
+	(111.65,108.37) --
+	(114.90,110.34) --
+	(118.14,112.29) --
+	(121.39,114.23) --
+	(124.63,116.14) --
+	(127.87,118.01) --
+	(131.12,119.85) --
+	(134.36,121.67) --
+	(137.61,123.46) --
+	(140.85,125.24) --
+	(144.09,127.00) --
+	(147.34,128.75) --
+	(150.58,130.50) --
+	(153.82,132.25) --
+	(157.07,134.01) --
+	(160.31,135.74) --
+	(163.56,137.46) --
+	(166.80,139.17) --
+	(170.04,140.86) --
+	(173.29,142.54) --
+	(176.53,144.21) --
+	(179.78,145.87) --
+	(183.02,147.53) --
+	(186.26,149.17) --
+	(189.51,150.81) --
+	(192.75,152.44) --
+	(196.00,154.07) --
+	(199.24,155.68) --
+	(202.48,157.28) --
+	(205.73,158.87) --
+	(208.97,160.45) --
+	(212.21,162.03) --
+	(215.46,163.59) --
+	(218.70,165.14) --
+	(221.95,166.68) --
+	(225.19,168.21) --
+	(228.43,169.74) --
+	(231.68,171.25) --
+	(234.92,172.75) --
+	(238.17,174.24) --
+	(241.41,175.72) --
+	(244.65,177.20) --
+	(247.90,178.66) --
+	(251.14,180.11) --
+	(254.39,181.55) --
+	(257.63,182.98) --
+	(260.87,184.41) --
+	(264.12,185.82) --
+	(267.36,187.22) --
+	(270.60,188.61) --
+	(273.85,189.99) --
+	(277.09,191.36) --
+	(280.34,192.73) --
+	(283.58,194.08);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] ( 42.47, 37.24) --
-	( 45.83, 31.41) --
-	( 39.11, 31.41) --
-	cycle;
-
-\path[fill=fillColor] ( 50.78, 41.30) --
-	( 54.15, 35.47) --
-	( 47.42, 35.47) --
-	cycle;
-
-\path[fill=fillColor] ( 59.10, 45.93) --
-	( 62.46, 40.10) --
-	( 55.73, 40.10) --
-	cycle;
-
-\path[fill=fillColor] ( 67.41, 50.15) --
-	( 70.78, 44.32) --
-	( 64.05, 44.32) --
-	cycle;
-
-\path[fill=fillColor] ( 75.73, 54.15) --
-	( 79.09, 48.32) --
-	( 72.36, 48.32) --
-	cycle;
-
-\path[fill=fillColor] ( 84.04, 57.90) --
-	( 87.40, 52.07) --
-	( 80.68, 52.07) --
-	cycle;
-
-\path[fill=fillColor] ( 92.36, 61.62) --
-	( 95.72, 55.79) --
-	( 88.99, 55.79) --
-	cycle;
-
-\path[fill=fillColor] (100.67, 65.39) --
-	(104.03, 59.57) --
-	( 97.31, 59.57) --
-	cycle;
-
-\path[fill=fillColor] (108.98, 69.12) --
-	(112.35, 63.29) --
-	(105.62, 63.29) --
-	cycle;
-
-\path[fill=fillColor] (117.30, 72.29) --
-	(120.66, 66.47) --
-	(113.93, 66.47) --
-	cycle;
-
-\path[fill=fillColor] (125.61, 75.42) --
-	(128.98, 69.59) --
-	(122.25, 69.59) --
-	cycle;
-
-\path[fill=fillColor] (133.93, 78.32) --
-	(137.29, 72.50) --
-	(130.56, 72.50) --
-	cycle;
-
-\path[fill=fillColor] (142.24, 81.35) --
-	(145.60, 75.53) --
-	(138.88, 75.53) --
-	cycle;
-
-\path[fill=fillColor] (150.55, 84.41) --
-	(153.92, 78.59) --
-	(147.19, 78.59) --
-	cycle;
-
-\path[fill=fillColor] (158.87, 87.15) --
-	(162.23, 81.33) --
-	(155.50, 81.33) --
-	cycle;
-
-\path[fill=fillColor] (167.18, 89.83) --
-	(170.55, 84.00) --
-	(163.82, 84.00) --
-	cycle;
-
-\path[fill=fillColor] (175.50, 92.46) --
-	(178.86, 86.63) --
-	(172.13, 86.63) --
-	cycle;
-
-\path[fill=fillColor] (183.81, 95.48) --
-	(187.17, 89.65) --
-	(180.45, 89.65) --
-	cycle;
-
-\path[fill=fillColor] (192.12, 98.05) --
-	(195.49, 92.23) --
-	(188.76, 92.23) --
-	cycle;
-
-\path[fill=fillColor] (200.44,100.78) --
-	(203.80, 94.95) --
-	(197.07, 94.95) --
-	cycle;
-
-\path[fill=fillColor] (208.75,103.02) --
-	(212.12, 97.20) --
-	(205.39, 97.20) --
-	cycle;
-
-\path[fill=fillColor] (217.07,105.54) --
-	(220.43, 99.72) --
-	(213.70, 99.72) --
-	cycle;
-
-\path[fill=fillColor] (225.38,108.04) --
-	(228.74,102.22) --
-	(222.02,102.22) --
-	cycle;
-
-\path[fill=fillColor] (233.70,110.36) --
-	(237.06,104.53) --
-	(230.33,104.53) --
-	cycle;
-
-\path[fill=fillColor] (242.01,112.69) --
-	(245.37,106.87) --
-	(238.65,106.87) --
-	cycle;
-
-\path[fill=fillColor] (250.32,115.02) --
-	(253.69,109.20) --
-	(246.96,109.20) --
-	cycle;
-
-\path[fill=fillColor] (258.64,117.14) --
-	(262.00,111.31) --
-	(255.27,111.31) --
-	cycle;
-
-\path[fill=fillColor] (266.95,119.41) --
-	(270.32,113.59) --
-	(263.59,113.59) --
-	cycle;
-
-\path[fill=fillColor] (275.27,121.42) --
-	(278.63,115.60) --
-	(271.90,115.60) --
-	cycle;
-
-\path[fill=fillColor] (283.58,123.59) --
-	(286.94,117.77) --
-	(280.22,117.77) --
+\path[fill=fillColor] ( 27.31, 53.19) --
+	( 30.68, 47.36) --
+	( 23.95, 47.36) --
+	cycle;
+
+\path[fill=fillColor] ( 35.86, 57.06) --
+	( 39.22, 51.23) --
+	( 32.49, 51.23) --
+	cycle;
+
+\path[fill=fillColor] ( 44.40, 60.55) --
+	( 47.76, 54.73) --
+	( 41.03, 54.73) --
+	cycle;
+
+\path[fill=fillColor] ( 52.94, 64.55) --
+	( 56.30, 58.73) --
+	( 49.58, 58.73) --
+	cycle;
+
+\path[fill=fillColor] ( 61.48, 68.20) --
+	( 64.85, 62.37) --
+	( 58.12, 62.37) --
+	cycle;
+
+\path[fill=fillColor] ( 70.02, 71.66) --
+	( 73.39, 65.83) --
+	( 66.66, 65.83) --
+	cycle;
+
+\path[fill=fillColor] ( 78.57, 74.89) --
+	( 81.93, 69.06) --
+	( 75.20, 69.06) --
+	cycle;
+
+\path[fill=fillColor] ( 87.11, 78.06) --
+	( 90.47, 72.23) --
+	( 83.75, 72.23) --
+	cycle;
+
+\path[fill=fillColor] ( 95.65, 81.32) --
+	( 99.01, 75.49) --
+	( 92.29, 75.49) --
+	cycle;
+
+\path[fill=fillColor] (104.19, 84.53) --
+	(107.56, 78.70) --
+	(100.83, 78.70) --
+	cycle;
+
+\path[fill=fillColor] (112.74, 87.29) --
+	(116.10, 81.47) --
+	(109.37, 81.47) --
+	cycle;
+
+\path[fill=fillColor] (121.28, 89.96) --
+	(124.64, 84.14) --
+	(117.91, 84.14) --
+	cycle;
+
+\path[fill=fillColor] (129.82, 92.46) --
+	(133.18, 86.64) --
+	(126.46, 86.64) --
+	cycle;
+
+\path[fill=fillColor] (138.36, 95.06) --
+	(141.73, 89.23) --
+	(135.00, 89.23) --
+	cycle;
+
+\path[fill=fillColor] (146.90, 97.72) --
+	(150.27, 91.89) --
+	(143.54, 91.89) --
+	cycle;
+
+\path[fill=fillColor] (155.45,100.07) --
+	(158.81, 94.25) --
+	(152.08, 94.25) --
+	cycle;
+
+\path[fill=fillColor] (163.99,102.38) --
+	(167.35, 96.55) --
+	(160.63, 96.55) --
+	cycle;
+
+\path[fill=fillColor] (172.53,104.65) --
+	(175.89, 98.82) --
+	(169.17, 98.82) --
+	cycle;
+
+\path[fill=fillColor] (181.07,107.23) --
+	(184.44,101.41) --
+	(177.71,101.41) --
+	cycle;
+
+\path[fill=fillColor] (189.62,109.45) --
+	(192.98,103.63) --
+	(186.25,103.63) --
+	cycle;
+
+\path[fill=fillColor] (198.16,111.78) --
+	(201.52,105.95) --
+	(194.79,105.95) --
+	cycle;
+
+\path[fill=fillColor] (206.70,113.72) --
+	(210.06,107.89) --
+	(203.34,107.89) --
+	cycle;
+
+\path[fill=fillColor] (215.24,115.86) --
+	(218.61,110.04) --
+	(211.88,110.04) --
+	cycle;
+
+\path[fill=fillColor] (223.78,118.03) --
+	(227.15,112.20) --
+	(220.42,112.20) --
+	cycle;
+
+\path[fill=fillColor] (232.33,120.05) --
+	(235.69,114.22) --
+	(228.96,114.22) --
+	cycle;
+
+\path[fill=fillColor] (240.87,122.05) --
+	(244.23,116.22) --
+	(237.51,116.22) --
+	cycle;
+
+\path[fill=fillColor] (249.41,124.03) --
+	(252.77,118.21) --
+	(246.05,118.21) --
+	cycle;
+
+\path[fill=fillColor] (257.95,125.86) --
+	(261.32,120.04) --
+	(254.59,120.04) --
+	cycle;
+
+\path[fill=fillColor] (266.50,127.84) --
+	(269.86,122.01) --
+	(263.13,122.01) --
+	cycle;
+
+\path[fill=fillColor] (275.04,129.56) --
+	(278.40,123.73) --
+	(271.67,123.73) --
+	cycle;
+
+\path[fill=fillColor] (283.58,131.45) --
+	(286.94,125.62) --
+	(280.22,125.62) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 39.97, 28.24) --
-	( 44.97, 28.24) --
-	( 44.97, 33.24) --
-	( 39.97, 33.24) --
-	cycle;
-
-\path[fill=fillColor] ( 48.29, 33.79) --
-	( 53.28, 33.79) --
-	( 53.28, 38.78) --
-	( 48.29, 38.78) --
-	cycle;
-
-\path[fill=fillColor] ( 56.60, 40.12) --
-	( 61.60, 40.12) --
-	( 61.60, 45.11) --
-	( 56.60, 45.11) --
-	cycle;
-
-\path[fill=fillColor] ( 64.91, 45.85) --
-	( 69.91, 45.85) --
-	( 69.91, 50.84) --
-	( 64.91, 50.84) --
-	cycle;
-
-\path[fill=fillColor] ( 73.23, 51.39) --
-	( 78.22, 51.39) --
-	( 78.22, 56.38) --
-	( 73.23, 56.38) --
-	cycle;
-
-\path[fill=fillColor] ( 81.54, 56.59) --
-	( 86.54, 56.59) --
-	( 86.54, 61.58) --
-	( 81.54, 61.58) --
-	cycle;
-
-\path[fill=fillColor] ( 89.86, 61.73) --
-	( 94.85, 61.73) --
-	( 94.85, 66.73) --
-	( 89.86, 66.73) --
-	cycle;
-
-\path[fill=fillColor] ( 98.17, 66.95) --
-	(103.17, 66.95) --
-	(103.17, 71.95) --
-	( 98.17, 71.95) --
-	cycle;
-
-\path[fill=fillColor] (106.49, 72.16) --
-	(111.48, 72.16) --
-	(111.48, 77.15) --
-	(106.49, 77.15) --
-	cycle;
-
-\path[fill=fillColor] (114.80, 76.50) --
-	(119.80, 76.50) --
-	(119.80, 81.49) --
-	(114.80, 81.49) --
-	cycle;
-
-\path[fill=fillColor] (123.11, 80.91) --
-	(128.11, 80.91) --
-	(128.11, 85.91) --
-	(123.11, 85.91) --
-	cycle;
-
-\path[fill=fillColor] (131.43, 84.98) --
-	(136.42, 84.98) --
-	(136.42, 89.98) --
-	(131.43, 89.98) --
-	cycle;
-
-\path[fill=fillColor] (139.74, 89.24) --
-	(144.74, 89.24) --
-	(144.74, 94.24) --
-	(139.74, 94.24) --
-	cycle;
-
-\path[fill=fillColor] (148.06, 93.58) --
-	(153.05, 93.58) --
-	(153.05, 98.58) --
-	(148.06, 98.58) --
-	cycle;
-
-\path[fill=fillColor] (156.37, 97.49) --
-	(161.37, 97.49) --
-	(161.37,102.49) --
-	(156.37,102.49) --
-	cycle;
-
-\path[fill=fillColor] (164.68,101.24) --
-	(169.68,101.24) --
-	(169.68,106.23) --
-	(164.68,106.23) --
-	cycle;
-
-\path[fill=fillColor] (173.00,104.98) --
-	(177.99,104.98) --
-	(177.99,109.98) --
-	(173.00,109.98) --
-	cycle;
-
-\path[fill=fillColor] (181.31,109.30) --
-	(186.31,109.30) --
-	(186.31,114.30) --
-	(181.31,114.30) --
-	cycle;
-
-\path[fill=fillColor] (189.63,112.96) --
-	(194.62,112.96) --
-	(194.62,117.96) --
-	(189.63,117.96) --
-	cycle;
-
-\path[fill=fillColor] (197.94,116.88) --
-	(202.94,116.88) --
-	(202.94,121.88) --
-	(197.94,121.88) --
-	cycle;
-
-\path[fill=fillColor] (206.26,120.08) --
-	(211.25,120.08) --
-	(211.25,125.07) --
-	(206.26,125.07) --
-	cycle;
-
-\path[fill=fillColor] (214.57,123.71) --
-	(219.56,123.71) --
-	(219.56,128.71) --
-	(214.57,128.71) --
-	cycle;
-
-\path[fill=fillColor] (222.88,127.30) --
-	(227.88,127.30) --
-	(227.88,132.30) --
-	(222.88,132.30) --
-	cycle;
-
-\path[fill=fillColor] (231.20,130.64) --
-	(236.19,130.64) --
-	(236.19,135.63) --
-	(231.20,135.63) --
-	cycle;
-
-\path[fill=fillColor] (239.51,133.97) --
-	(244.51,133.97) --
-	(244.51,138.97) --
-	(239.51,138.97) --
-	cycle;
-
-\path[fill=fillColor] (247.83,137.46) --
-	(252.82,137.46) --
-	(252.82,142.45) --
-	(247.83,142.45) --
-	cycle;
-
-\path[fill=fillColor] (256.14,140.45) --
-	(261.14,140.45) --
-	(261.14,145.45) --
-	(256.14,145.45) --
-	cycle;
-
-\path[fill=fillColor] (264.45,143.78) --
-	(269.45,143.78) --
-	(269.45,148.78) --
-	(264.45,148.78) --
-	cycle;
-
-\path[fill=fillColor] (272.77,146.72) --
-	(277.76,146.72) --
-	(277.76,151.71) --
-	(272.77,151.71) --
-	cycle;
-
-\path[fill=fillColor] (281.08,149.90) --
-	(286.08,149.90) --
-	(286.08,154.89) --
-	(281.08,154.89) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.94, 36.06) -- ( 46.00, 36.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.47, 32.52) -- ( 42.47, 39.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 47.25, 43.04) -- ( 54.32, 43.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.78, 39.50) -- ( 50.78, 46.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 55.57, 51.01) -- ( 62.63, 51.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.10, 47.48) -- ( 59.10, 54.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.88, 58.15) -- ( 70.94, 58.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 67.41, 54.62) -- ( 67.41, 61.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.19, 65.24) -- ( 79.26, 65.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.73, 61.70) -- ( 75.73, 68.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.51, 71.87) -- ( 87.57, 71.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.04, 68.33) -- ( 84.04, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.82, 78.42) -- ( 95.89, 78.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.36, 74.89) -- ( 92.36, 81.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.14, 85.07) -- (104.20, 85.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.67, 81.54) -- (100.67, 88.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.45, 91.77) -- (112.52, 91.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.98, 88.23) -- (108.98, 95.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.77, 97.23) -- (120.83, 97.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.30, 93.70) -- (117.30,100.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.08,102.98) -- (129.14,102.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.61, 99.45) -- (125.61,106.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.39,108.23) -- (137.46,108.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.93,104.70) -- (133.93,111.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.71,113.74) -- (145.77,113.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.24,110.21) -- (142.24,117.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.02,119.44) -- (154.09,119.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.55,115.91) -- (150.55,122.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.34,124.58) -- (162.40,124.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.87,121.05) -- (158.87,128.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.65,129.41) -- (170.71,129.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.18,125.87) -- (167.18,132.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.96,134.32) -- (179.03,134.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.50,130.79) -- (175.50,137.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.28,140.02) -- (187.34,140.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.81,136.49) -- (183.81,143.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.59,144.84) -- (195.66,144.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.12,141.31) -- (192.12,148.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.91,150.03) -- (203.97,150.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.44,146.50) -- (200.44,153.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.22,154.23) -- (212.28,154.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.75,150.70) -- (208.75,157.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.53,159.05) -- (220.60,159.05);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.07,155.52) -- (217.07,162.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.85,163.83) -- (228.91,163.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.38,160.30) -- (225.38,167.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.16,168.26) -- (237.23,168.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.70,164.72) -- (233.70,171.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.48,172.64) -- (245.54,172.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.01,169.11) -- (242.01,176.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.79,177.48) -- (253.86,177.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.32,173.94) -- (250.32,181.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.11,181.38) -- (262.17,181.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (258.64,177.84) -- (258.64,184.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.42,185.89) -- (270.48,185.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.95,182.35) -- (266.95,189.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.73,189.84) -- (278.80,189.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.27,186.31) -- (275.27,193.38);
+\path[fill=fillColor] ( 24.82, 46.71) --
+	( 29.81, 46.71) --
+	( 29.81, 51.71) --
+	( 24.82, 51.71) --
+	cycle;
+
+\path[fill=fillColor] ( 33.36, 51.99) --
+	( 38.35, 51.99) --
+	( 38.35, 56.98) --
+	( 33.36, 56.98) --
+	cycle;
+
+\path[fill=fillColor] ( 41.90, 56.82) --
+	( 46.90, 56.82) --
+	( 46.90, 61.82) --
+	( 41.90, 61.82) --
+	cycle;
+
+\path[fill=fillColor] ( 50.44, 62.34) --
+	( 55.44, 62.34) --
+	( 55.44, 67.33) --
+	( 50.44, 67.33) --
+	cycle;
+
+\path[fill=fillColor] ( 58.98, 67.33) --
+	( 63.98, 67.33) --
+	( 63.98, 72.32) --
+	( 58.98, 72.32) --
+	cycle;
+
+\path[fill=fillColor] ( 67.53, 72.15) --
+	( 72.52, 72.15) --
+	( 72.52, 77.15) --
+	( 67.53, 77.15) --
+	cycle;
+
+\path[fill=fillColor] ( 76.07, 76.68) --
+	( 81.06, 76.68) --
+	( 81.06, 81.67) --
+	( 76.07, 81.67) --
+	cycle;
+
+\path[fill=fillColor] ( 84.61, 81.16) --
+	( 89.61, 81.16) --
+	( 89.61, 86.16) --
+	( 84.61, 86.16) --
+	cycle;
+
+\path[fill=fillColor] ( 93.15, 85.71) --
+	( 98.15, 85.71) --
+	( 98.15, 90.70) --
+	( 93.15, 90.70) --
+	cycle;
+
+\path[fill=fillColor] (101.70, 90.24) --
+	(106.69, 90.24) --
+	(106.69, 95.23) --
+	(101.70, 95.23) --
+	cycle;
+
+\path[fill=fillColor] (110.24, 94.02) --
+	(115.23, 94.02) --
+	(115.23, 99.01) --
+	(110.24, 99.01) --
+	cycle;
+
+\path[fill=fillColor] (118.78, 97.87) --
+	(123.78, 97.87) --
+	(123.78,102.86) --
+	(118.78,102.86) --
+	cycle;
+
+\path[fill=fillColor] (127.32,101.41) --
+	(132.32,101.41) --
+	(132.32,106.41) --
+	(127.32,106.41) --
+	cycle;
+
+\path[fill=fillColor] (135.86,105.12) --
+	(140.86,105.12) --
+	(140.86,110.12) --
+	(135.86,110.12) --
+	cycle;
+
+\path[fill=fillColor] (144.41,108.90) --
+	(149.40,108.90) --
+	(149.40,113.89) --
+	(144.41,113.89) --
+	cycle;
+
+\path[fill=fillColor] (152.95,112.30) --
+	(157.94,112.30) --
+	(157.94,117.30) --
+	(152.95,117.30) --
+	cycle;
+
+\path[fill=fillColor] (161.49,115.57) --
+	(166.49,115.57) --
+	(166.49,120.56) --
+	(161.49,120.56) --
+	cycle;
+
+\path[fill=fillColor] (170.03,118.83) --
+	(175.03,118.83) --
+	(175.03,123.82) --
+	(170.03,123.82) --
+	cycle;
+
+\path[fill=fillColor] (178.58,122.59) --
+	(183.57,122.59) --
+	(183.57,127.59) --
+	(178.58,127.59) --
+	cycle;
+
+\path[fill=fillColor] (187.12,125.78) --
+	(192.11,125.78) --
+	(192.11,130.78) --
+	(187.12,130.78) --
+	cycle;
+
+\path[fill=fillColor] (195.66,129.19) --
+	(200.66,129.19) --
+	(200.66,134.19) --
+	(195.66,134.19) --
+	cycle;
+
+\path[fill=fillColor] (204.20,131.97) --
+	(209.20,131.97) --
+	(209.20,136.97) --
+	(204.20,136.97) --
+	cycle;
+
+\path[fill=fillColor] (212.74,135.14) --
+	(217.74,135.14) --
+	(217.74,140.13) --
+	(212.74,140.13) --
+	cycle;
+
+\path[fill=fillColor] (221.29,138.27) --
+	(226.28,138.27) --
+	(226.28,143.26) --
+	(221.29,143.26) --
+	cycle;
+
+\path[fill=fillColor] (229.83,141.17) --
+	(234.82,141.17) --
+	(234.82,146.17) --
+	(229.83,146.17) --
+	cycle;
+
+\path[fill=fillColor] (238.37,144.08) --
+	(243.37,144.08) --
+	(243.37,149.07) --
+	(238.37,149.07) --
+	cycle;
+
+\path[fill=fillColor] (246.91,147.11) --
+	(251.91,147.11) --
+	(251.91,152.11) --
+	(246.91,152.11) --
+	cycle;
+
+\path[fill=fillColor] (255.46,149.72) --
+	(260.45,149.72) --
+	(260.45,154.72) --
+	(255.46,154.72) --
+	cycle;
+
+\path[fill=fillColor] (264.00,152.62) --
+	(268.99,152.62) --
+	(268.99,157.62) --
+	(264.00,157.62) --
+	cycle;
+
+\path[fill=fillColor] (272.54,155.18) --
+	(277.54,155.18) --
+	(277.54,160.17) --
+	(272.54,160.17) --
+	cycle;
+
+\path[fill=fillColor] (281.08,157.94) --
+	(286.08,157.94) --
+	(286.08,162.94) --
+	(281.08,162.94) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78, 49.02) -- ( 30.85, 49.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31, 45.48) -- ( 27.31, 52.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32, 55.61) -- ( 39.39, 55.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86, 52.08) -- ( 35.86, 59.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87, 61.73) -- ( 47.93, 61.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40, 58.20) -- ( 44.40, 65.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41, 68.71) -- ( 56.47, 68.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94, 65.18) -- ( 52.94, 72.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95, 74.96) -- ( 65.01, 74.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48, 71.43) -- ( 61.48, 78.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49, 81.15) -- ( 73.56, 81.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02, 77.61) -- ( 70.02, 84.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03, 86.95) -- ( 82.10, 86.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57, 83.42) -- ( 78.57, 90.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58, 92.74) -- ( 90.64, 92.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11, 89.21) -- ( 87.11, 96.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12, 98.56) -- ( 99.18, 98.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 95.03) -- ( 95.65,102.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,104.43) -- (107.73,104.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,100.89) -- (104.19,107.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,109.18) -- (116.27,109.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,105.64) -- (112.74,112.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,114.24) -- (124.81,114.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,110.71) -- (121.28,117.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,118.85) -- (133.35,118.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,115.32) -- (129.82,122.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,123.69) -- (141.89,123.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,120.16) -- (138.36,127.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,128.65) -- (150.44,128.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,125.12) -- (146.90,132.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,133.17) -- (158.98,133.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,129.63) -- (155.45,136.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,137.39) -- (167.52,137.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,133.86) -- (163.99,140.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,141.70) -- (176.06,141.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,138.17) -- (172.53,145.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,146.71) -- (184.61,146.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,143.18) -- (181.07,150.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,150.92) -- (193.15,150.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,147.39) -- (189.62,154.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,155.51) -- (201.69,155.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,151.98) -- (198.16,159.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,159.19) -- (210.23,159.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,155.65) -- (206.70,162.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,163.43) -- (218.77,163.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,159.90) -- (215.24,166.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,167.61) -- (227.32,167.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,164.08) -- (223.78,171.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,171.46) -- (235.86,171.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,167.93) -- (232.33,174.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,175.31) -- (244.40,175.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,171.78) -- (240.87,178.84);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,179.58) -- (252.94,179.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,176.04) -- (249.41,183.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,182.99) -- (261.49,182.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,179.46) -- (257.95,186.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,186.92) -- (270.03,186.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,183.38) -- (266.50,190.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,190.40) -- (278.57,190.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,186.87) -- (275.04,193.93);
 
@@
 
-\path[fill=fillColor] ( 42.47, 40.20) circle (  2.50);
-
-\path[fill=fillColor] ( 50.78, 41.22) circle (  2.50);
-
-\path[fill=fillColor] ( 59.10, 41.25) circle (  2.50);
-
-\path[fill=fillColor] ( 67.41, 40.48) circle (  2.50);
-
-\path[fill=fillColor] ( 75.73, 41.69) circle (  2.50);
-
-\path[fill=fillColor] ( 84.04, 41.00) circle (  2.50);
-
-\path[fill=fillColor] ( 92.36, 41.07) circle (  2.50);
-
-\path[fill=fillColor] (100.67, 41.57) circle (  2.50);
-
-\path[fill=fillColor] (108.98, 40.91) circle (  2.50);
-
-\path[fill=fillColor] (117.30, 41.28) circle (  2.50);
-
-\path[fill=fillColor] (125.61, 40.87) circle (  2.50);
-
-\path[fill=fillColor] (133.93, 40.53) circle (  2.50);
-
-\path[fill=fillColor] (142.24, 40.65) circle (  2.50);
-
-\path[fill=fillColor] (150.55, 41.43) circle (  2.50);
-
-\path[fill=fillColor] (158.87, 40.83) circle (  2.50);
-
-\path[fill=fillColor] (167.18, 41.46) circle (  2.50);
-
-\path[fill=fillColor] (175.50, 41.54) circle (  2.50);
-
-\path[fill=fillColor] (183.81, 41.28) circle (  2.50);
-
-\path[fill=fillColor] (192.12, 41.18) circle (  2.50);
-
-\path[fill=fillColor] (200.44, 41.05) circle (  2.50);
-
-\path[fill=fillColor] (208.75, 41.17) circle (  2.50);
-
-\path[fill=fillColor] (217.07, 40.69) circle (  2.50);
-
-\path[fill=fillColor] (225.38, 41.23) circle (  2.50);
-
-\path[fill=fillColor] (233.70, 40.72) circle (  2.50);
-
-\path[fill=fillColor] (242.01, 40.73) circle (  2.50);
-
-\path[fill=fillColor] (250.32, 41.40) circle (  2.50);
-
-\path[fill=fillColor] (258.64, 41.47) circle (  2.50);
-
-\path[fill=fillColor] (266.95, 41.12) circle (  2.50);
-
-\path[fill=fillColor] (275.27, 41.34) circle (  2.50);
-
-\path[fill=fillColor] (283.58, 41.00) circle (  2.50);
+\path[fill=fillColor] ( 27.31, 47.39) circle (  2.50);
+
+\path[fill=fillColor] ( 35.86, 48.28) circle (  2.50);
+
+\path[fill=fillColor] ( 44.40, 48.31) circle (  2.50);
+
+\path[fill=fillColor] ( 52.94, 47.63) circle (  2.50);
+
+\path[fill=fillColor] ( 61.48, 48.69) circle (  2.50);
+
+\path[fill=fillColor] ( 70.02, 48.09) circle (  2.50);
+
+\path[fill=fillColor] ( 78.57, 48.15) circle (  2.50);
+
+\path[fill=fillColor] ( 87.11, 48.59) circle (  2.50);
+
+\path[fill=fillColor] ( 95.65, 48.01) circle (  2.50);
+
+\path[fill=fillColor] (104.19, 48.33) circle (  2.50);
+
+\path[fill=fillColor] (112.74, 47.97) circle (  2.50);
+
+\path[fill=fillColor] (121.28, 47.68) circle (  2.50);
+
+\path[fill=fillColor] (129.82, 47.78) circle (  2.50);
+
+\path[fill=fillColor] (138.36, 48.47) circle (  2.50);
+
+\path[fill=fillColor] (146.90, 47.94) circle (  2.50);
+
+\path[fill=fillColor] (155.45, 48.48) circle (  2.50);
+
+\path[fill=fillColor] (163.99, 48.56) circle (  2.50);
+
+\path[fill=fillColor] (172.53, 48.33) circle (  2.50);
+
+\path[fill=fillColor] (181.07, 48.25) circle (  2.50);
+
+\path[fill=fillColor] (189.62, 48.13) circle (  2.50);
+
+\path[fill=fillColor] (198.16, 48.23) circle (  2.50);
+
+\path[fill=fillColor] (206.70, 47.82) circle (  2.50);
+
+\path[fill=fillColor] (215.24, 48.29) circle (  2.50);
+
+\path[fill=fillColor] (223.78, 47.84) circle (  2.50);
+
+\path[fill=fillColor] (232.33, 47.85) circle (  2.50);
+
+\path[fill=fillColor] (240.87, 48.44) circle (  2.50);
+
+\path[fill=fillColor] (249.41, 48.50) circle (  2.50);
+
+\path[fill=fillColor] (257.95, 48.19) circle (  2.50);
+
+\path[fill=fillColor] (266.50, 48.39) circle (  2.50);
+
+\path[fill=fillColor] (275.04, 48.09) circle (  2.50);
+
+\path[fill=fillColor] (283.58, 47.98) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.16, 30.69) rectangle (283.58,194.15);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.31, 30.69) rectangle (283.58,194.15);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 28.82) {4.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 72.16) {5.2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,115.50) {5.6};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,158.84) {6.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 55.97) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,150.33) {6};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 31.85) --
-	( 34.16, 31.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 75.19) --
-	( 34.16, 75.19);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,118.53) --
-	( 34.16,118.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,161.87) --
-	( 34.16,161.87);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 59.00) --
+	( 27.31, 59.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,153.36) --
+	( 27.31,153.36);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 27.94) --
-	( 34.16, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (117.30, 27.94) --
-	(117.30, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.44, 27.94) --
-	(200.44, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31, 27.94) --
+	( 27.31, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (112.74, 27.94) --
+	(112.74, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.16, 27.94) --
+	(198.16, 30.69);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 34.16, 19.68) {0.0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (117.30, 19.68) {0.1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (200.44, 19.68) {0.2};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.31, 19.68) {0.0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (112.74, 19.68) {0.1};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.16, 19.68) {0.2};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (158.87,  7.64) {Exponential growth rate $r$ (1/day)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (155.45,  7.64) {Exponential growth rate $r$ (1/day)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.16,202.22) {C};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.31,202.22) {C};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (331.55, 49.95) --
-	(334.60, 49.96) --
-	(337.65, 49.96) --
-	(340.71, 49.96) --
-	(343.76, 49.97) --
-	(346.81, 49.97) --
-	(349.86, 49.98) --
-	(352.91, 49.98) --
-	(355.97, 49.98) --
-	(359.02, 49.98) --
-	(362.07, 49.99) --
-	(365.12, 49.99) --
-	(368.17, 49.99) --
-	(371.23, 49.99) --
-	(374.28, 49.99) --
-	(377.33, 49.99) --
-	(380.38, 50.00) --
-	(383.43, 50.00) --
-	(386.49, 50.00) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] (323.24, 49.95) --
+	(326.39, 49.96) --
+	(329.55, 49.96) --
+	(332.71, 49.96) --
+	(335.87, 49.97) --
+	(339.02, 49.97) --
+	(342.18, 49.98) --
+	(345.34, 49.98) --
+	(348.49, 49.98) --
+	(351.65, 49.98) --
+	(354.81, 49.99) --
+	(357.97, 49.99) --
+	(361.12, 49.99) --
+	(364.28, 49.99) --
+	(367.44, 49.99) --
+	(370.60, 50.00) --
+	(373.75, 50.00) --
+	(376.91, 50.00) --
+	(380.07, 50.00) --
+	(383.22, 50.00) --
+	(386.38, 50.00) --
 	(389.54, 50.00) --
-	(392.59, 50.00) --
-	(395.64, 50.00) --
-	(398.69, 50.00) --
-	(401.75, 50.00) --
-	(404.80, 50.00) --
-	(407.85, 50.00) --
-	(410.90, 50.00) --
-	(413.95, 49.99) --
-	(417.01, 49.99) --
-	(420.06, 49.99) --
-	(423.11, 49.99) --
-	(426.16, 49.99) --
-	(429.21, 49.98) --
-	(432.27, 49.98) --
-	(435.32, 49.97) --
-	(438.37, 49.96) --
-	(441.42, 49.96) --
-	(444.48, 49.95) --
-	(447.53, 49.95) --
-	(450.58, 49.95) --
-	(453.63, 49.95) --
-	(456.68, 49.95) --
-	(459.74, 49.95) --
-	(462.79, 49.95) --
-	(465.84, 49.95) --
-	(468.89, 49.95) --
-	(471.94, 49.95) --
-	(475.00, 49.96) --
-	(478.05, 49.96) --
-	(481.10, 49.96) --
-	(484.15, 49.96) --
-	(487.20, 49.96) --
-	(490.26, 49.97) --
-	(493.31, 49.97) --
-	(496.36, 49.97) --
-	(499.41, 49.97) --
-	(502.46, 49.98) --
-	(505.52, 49.98) --
-	(508.57, 49.98) --
-	(511.62, 49.99) --
-	(514.67, 49.99) --
-	(517.72, 49.99) --
-	(520.78, 49.99) --
-	(523.83, 49.99) --
-	(526.88, 50.00) --
-	(529.93, 50.00) --
-	(532.98, 50.00) --
-	(536.04, 50.00) --
-	(539.09, 50.01) --
-	(542.14, 50.01) --
-	(545.19, 50.01) --
-	(548.24, 50.01) --
-	(551.30, 50.01) --
-	(554.35, 50.02) --
-	(557.40, 50.02) --
-	(560.45, 50.02) --
-	(563.50, 50.02) --
-	(566.56, 50.02) --
-	(569.61, 50.02) --
-	(572.66, 50.02);
+	(392.70, 50.00) --
+	(395.85, 50.00) --
+	(399.01, 50.00) --
+	(402.17, 50.00) --
+	(405.32, 50.00) --
+	(408.48, 49.99) --
+	(411.64, 49.99) --
+	(414.80, 49.99) --
+	(417.95, 49.99) --
+	(421.11, 49.98) --
+	(424.27, 49.98) --
+	(427.43, 49.97) --
+	(430.58, 49.97) --
+	(433.74, 49.96) --
+	(436.90, 49.95) --
+	(440.05, 49.95) --
+	(443.21, 49.94) --
+	(446.37, 49.94) --
+	(449.53, 49.94) --
+	(452.68, 49.94) --
+	(455.84, 49.94) --
+	(459.00, 49.95) --
+	(462.16, 49.95) --
+	(465.31, 49.95) --
+	(468.47, 49.95) --
+	(471.63, 49.96) --
+	(474.78, 49.96) --
+	(477.94, 49.96) --
+	(481.10, 49.97) --
+	(484.26, 49.97) --
+	(487.41, 49.97) --
+	(490.57, 49.98) --
+	(493.73, 49.98) --
+	(496.89, 49.98) --
+	(500.04, 49.99) --
+	(503.20, 49.99) --
+	(506.36, 49.99) --
+	(509.51, 50.00) --
+	(512.67, 50.00) --
+	(515.83, 50.00) --
+	(518.99, 50.00) --
+	(522.14, 50.00) --
+	(525.30, 50.00) --
+	(528.46, 50.00) --
+	(531.62, 50.00) --
+	(534.77, 49.99) --
+	(537.93, 49.99) --
+	(541.09, 49.99) --
+	(544.24, 49.99) --
+	(547.40, 49.99) --
+	(550.56, 49.98) --
+	(553.72, 49.98) --
+	(556.87, 49.97) --
+	(560.03, 49.97) --
+	(563.19, 49.96) --
+	(566.35, 49.96) --
+	(569.50, 49.95) --
+	(572.66, 49.94);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (331.55,128.70) --
-	(334.60,127.69) --
-	(337.65,126.70) --
-	(340.71,125.73) --
-	(343.76,124.77) --
-	(346.81,123.83) --
-	(349.86,122.90) --
-	(352.91,122.00) --
-	(355.97,121.11) --
-	(359.02,120.24) --
-	(362.07,119.39) --
-	(365.12,118.55) --
-	(368.17,117.74) --
-	(371.23,116.94) --
-	(374.28,116.16) --
-	(377.33,115.39) --
-	(380.38,114.64) --
-	(383.43,113.91) --
-	(386.49,113.20) --
-	(389.54,112.50) --
-	(392.59,111.82) --
-	(395.64,111.16) --
-	(398.69,110.53) --
-	(401.75,109.91) --
-	(404.80,109.32) --
-	(407.85,108.74) --
-	(410.90,108.18) --
-	(413.95,107.63) --
-	(417.01,107.09) --
-	(420.06,106.55) --
-	(423.11,106.03) --
-	(426.16,105.52) --
-	(429.21,105.04) --
-	(432.27,104.58) --
-	(435.32,104.14) --
-	(438.37,103.71) --
-	(441.42,103.28) --
-	(444.48,102.85) --
-	(447.53,102.42) --
-	(450.58,101.98) --
-	(453.63,101.56) --
-	(456.68,101.15) --
-	(459.74,100.75) --
-	(462.79,100.36) --
-	(465.84, 99.98) --
-	(468.89, 99.60) --
-	(471.94, 99.23) --
-	(475.00, 98.86) --
-	(478.05, 98.49) --
-	(481.10, 98.12) --
-	(484.15, 97.75) --
-	(487.20, 97.39) --
-	(490.26, 97.04) --
-	(493.31, 96.69) --
-	(496.36, 96.35) --
-	(499.41, 96.01) --
-	(502.46, 95.67) --
-	(505.52, 95.35) --
-	(508.57, 95.02) --
-	(511.62, 94.70) --
-	(514.67, 94.39) --
-	(517.72, 94.08) --
-	(520.78, 93.77) --
-	(523.83, 93.47) --
-	(526.88, 93.17) --
-	(529.93, 92.88) --
-	(532.98, 92.60) --
-	(536.04, 92.32) --
-	(539.09, 92.04) --
-	(542.14, 91.77) --
-	(545.19, 91.50) --
-	(548.24, 91.24) --
-	(551.30, 90.99) --
-	(554.35, 90.74) --
-	(557.40, 90.49) --
-	(560.45, 90.25) --
-	(563.50, 90.01) --
-	(566.56, 89.78) --
-	(569.61, 89.55) --
-	(572.66, 89.33);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24,140.06) --
+	(326.39,138.91) --
+	(329.55,137.78) --
+	(332.71,136.67) --
+	(335.87,135.58) --
+	(339.02,134.51) --
+	(342.18,133.46) --
+	(345.34,132.43) --
+	(348.49,131.43) --
+	(351.65,130.44) --
+	(354.81,129.47) --
+	(357.97,128.52) --
+	(361.12,127.60) --
+	(364.28,126.69) --
+	(367.44,125.80) --
+	(370.60,124.93) --
+	(373.75,124.08) --
+	(376.91,123.25) --
+	(380.07,122.43) --
+	(383.22,121.64) --
+	(386.38,120.87) --
+	(389.54,120.12) --
+	(392.70,119.40) --
+	(395.85,118.70) --
+	(399.01,118.02) --
+	(402.17,117.36) --
+	(405.32,116.71) --
+	(408.48,116.08) --
+	(411.64,115.46) --
+	(414.80,114.85) --
+	(417.95,114.27) --
+	(421.11,113.70) --
+	(424.27,113.17) --
+	(427.43,112.65) --
+	(430.58,112.15) --
+	(433.74,111.66) --
+	(436.90,111.18) --
+	(440.05,110.70) --
+	(443.21,110.23) --
+	(446.37,109.76) --
+	(449.53,109.28) --
+	(452.68,108.82) --
+	(455.84,108.37) --
+	(459.00,107.93) --
+	(462.16,107.50) --
+	(465.31,107.08) --
+	(468.47,106.66) --
+	(471.63,106.25) --
+	(474.78,105.85) --
+	(477.94,105.44) --
+	(481.10,105.04) --
+	(484.26,104.64) --
+	(487.41,104.25) --
+	(490.57,103.86) --
+	(493.73,103.48) --
+	(496.89,103.10) --
+	(500.04,102.73) --
+	(503.20,102.36) --
+	(506.36,102.00) --
+	(509.51,101.65) --
+	(512.67,101.30) --
+	(515.83,100.95) --
+	(518.99,100.61) --
+	(522.14,100.27) --
+	(525.30, 99.94) --
+	(528.46, 99.61) --
+	(531.62, 99.29) --
+	(534.77, 98.98) --
+	(537.93, 98.67) --
+	(541.09, 98.37) --
+	(544.24, 98.07) --
+	(547.40, 97.77) --
+	(550.56, 97.48) --
+	(553.72, 97.20) --
+	(556.87, 96.92) --
+	(560.03, 96.65) --
+	(563.19, 96.38) --
+	(566.35, 96.12) --
+	(569.50, 95.86) --
+	(572.66, 95.61);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (331.55,158.08) --
-	(334.60,156.41) --
-	(337.65,154.76) --
-	(340.71,153.14) --
-	(343.76,151.56) --
-	(346.81,150.00) --
-	(349.86,148.47) --
-	(352.91,146.97) --
-	(355.97,145.51) --
-	(359.02,144.07) --
-	(362.07,142.67) --
-	(365.12,141.30) --
-	(368.17,139.95) --
-	(371.23,138.64) --
-	(374.28,137.36) --
-	(377.33,136.10) --
-	(380.38,134.88) --
-	(383.43,133.68) --
-	(386.49,132.51) --
-	(389.54,131.36) --
-	(392.59,130.25) --
-	(395.64,129.18) --
-	(398.69,128.15) --
-	(401.75,127.16) --
-	(404.80,126.20) --
-	(407.85,125.26) --
-	(410.90,124.35) --
-	(413.95,123.47) --
-	(417.01,122.60) --
-	(420.06,121.74) --
-	(423.11,120.90) --
-	(426.16,120.08) --
-	(429.21,119.31) --
-	(432.27,118.58) --
-	(435.32,117.87) --
-	(438.37,117.18) --
-	(441.42,116.50) --
-	(444.48,115.82) --
-	(447.53,115.13) --
-	(450.58,114.43) --
-	(453.63,113.77) --
-	(456.68,113.12) --
-	(459.74,112.48) --
-	(462.79,111.86) --
-	(465.84,111.26) --
-	(468.89,110.66) --
-	(471.94,110.08) --
-	(475.00,109.50) --
-	(478.05,108.92) --
-	(481.10,108.34) --
-	(484.15,107.77) --
-	(487.20,107.20) --
-	(490.26,106.65) --
-	(493.31,106.10) --
-	(496.36,105.57) --
-	(499.41,105.04) --
-	(502.46,104.53) --
-	(505.52,104.01) --
-	(508.57,103.51) --
-	(511.62,103.02) --
-	(514.67,102.53) --
-	(517.72,102.05) --
-	(520.78,101.57) --
-	(523.83,101.11) --
-	(526.88,100.65) --
-	(529.93,100.21) --
-	(532.98, 99.77) --
-	(536.04, 99.33) --
-	(539.09, 98.91) --
-	(542.14, 98.50) --
-	(545.19, 98.09) --
-	(548.24, 97.69) --
-	(551.30, 97.30) --
-	(554.35, 96.92) --
-	(557.40, 96.54) --
-	(560.45, 96.17) --
-	(563.50, 95.82) --
-	(566.56, 95.46) --
-	(569.61, 95.12) --
-	(572.66, 94.79);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,172.74) --
+	(326.39,170.89) --
+	(329.55,169.07) --
+	(332.71,167.28) --
+	(335.87,165.53) --
+	(339.02,163.81) --
+	(342.18,162.12) --
+	(345.34,160.46) --
+	(348.49,158.84) --
+	(351.65,157.25) --
+	(354.81,155.70) --
+	(357.97,154.18) --
+	(361.12,152.70) --
+	(364.28,151.25) --
+	(367.44,149.83) --
+	(370.60,148.44) --
+	(373.75,147.08) --
+	(376.91,145.75) --
+	(380.07,144.46) --
+	(383.22,143.19) --
+	(386.38,141.97) --
+	(389.54,140.79) --
+	(392.70,139.65) --
+	(395.85,138.55) --
+	(399.01,137.48) --
+	(402.17,136.44) --
+	(405.32,135.42) --
+	(408.48,134.43) --
+	(411.64,133.46) --
+	(414.80,132.50) --
+	(417.95,131.58) --
+	(421.11,130.71) --
+	(424.27,129.87) --
+	(427.43,129.06) --
+	(430.58,128.28) --
+	(433.74,127.53) --
+	(436.90,126.78) --
+	(440.05,126.05) --
+	(443.21,125.32) --
+	(446.37,124.59) --
+	(449.53,123.86) --
+	(452.68,123.14) --
+	(455.84,122.45) --
+	(459.00,121.78) --
+	(462.16,121.12) --
+	(465.31,120.48) --
+	(468.47,119.84) --
+	(471.63,119.22) --
+	(474.78,118.60) --
+	(477.94,117.99) --
+	(481.10,117.38) --
+	(484.26,116.77) --
+	(487.41,116.17) --
+	(490.57,115.58) --
+	(493.73,115.01) --
+	(496.89,114.44) --
+	(500.04,113.88) --
+	(503.20,113.33) --
+	(506.36,112.79) --
+	(509.51,112.25) --
+	(512.67,111.72) --
+	(515.83,111.20) --
+	(518.99,110.69) --
+	(522.14,110.19) --
+	(525.30,109.69) --
+	(528.46,109.21) --
+	(531.62,108.73) --
+	(534.77,108.26) --
+	(537.93,107.80) --
+	(541.09,107.35) --
+	(544.24,106.91) --
+	(547.40,106.48) --
+	(550.56,106.05) --
+	(553.72,105.63) --
+	(556.87,105.22) --
+	(560.03,104.82) --
+	(563.19,104.43) --
+	(566.35,104.05) --
+	(569.50,103.67) --
+	(572.66,103.31);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (331.55,189.58) --
-	(334.60,187.22) --
-	(337.65,184.90) --
-	(340.71,182.62) --
-	(343.76,180.39) --
-	(346.81,178.20) --
-	(349.86,176.05) --
-	(352.91,173.94) --
-	(355.97,171.88) --
-	(359.02,169.87) --
-	(362.07,167.90) --
-	(365.12,165.97) --
-	(368.17,164.09) --
-	(371.23,162.25) --
-	(374.28,160.45) --
-	(377.33,158.70) --
-	(380.38,156.98) --
-	(383.43,155.31) --
-	(386.49,153.67) --
-	(389.54,152.07) --
-	(392.59,150.52) --
-	(395.64,149.04) --
-	(398.69,147.61) --
-	(401.75,146.23) --
-	(404.80,144.89) --
-	(407.85,143.60) --
-	(410.90,142.34) --
-	(413.95,141.12) --
-	(417.01,139.92) --
-	(420.06,138.73) --
-	(423.11,137.56) --
-	(426.16,136.44) --
-	(429.21,135.38) --
-	(432.27,134.37) --
-	(435.32,133.39) --
-	(438.37,132.44) --
-	(441.42,131.51) --
-	(444.48,130.57) --
-	(447.53,129.63) --
-	(450.58,128.68) --
-	(453.63,127.76) --
-	(456.68,126.87) --
-	(459.74,126.01) --
-	(462.79,125.17) --
-	(465.84,124.34) --
-	(468.89,123.53) --
-	(471.94,122.73) --
-	(475.00,121.94) --
-	(478.05,121.15) --
-	(481.10,120.36) --
-	(484.15,119.59) --
-	(487.20,118.82) --
-	(490.26,118.07) --
-	(493.31,117.34) --
-	(496.36,116.61) --
-	(499.41,115.90) --
-	(502.46,115.20) --
-	(505.52,114.52) --
-	(508.57,113.84) --
-	(511.62,113.17) --
-	(514.67,112.51) --
-	(517.72,111.86) --
-	(520.78,111.23) --
-	(523.83,110.60) --
-	(526.88,109.99) --
-	(529.93,109.39) --
-	(532.98,108.80) --
-	(536.04,108.22) --
-	(539.09,107.66) --
-	(542.14,107.10) --
-	(545.19,106.56) --
-	(548.24,106.03) --
-	(551.30,105.51) --
-	(554.35,105.00) --
-	(557.40,104.50) --
-	(560.45,104.02) --
-	(563.50,103.54) --
-	(566.56,103.08) --
-	(569.61,102.63) --
-	(572.66,102.19);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (339.86,189.79) --
+	(342.81,187.67) --
+	(345.76,185.60) --
+	(348.70,183.56) --
+	(351.65,181.56) --
+	(354.60,179.59) --
+	(357.55,177.67) --
+	(360.49,175.78) --
+	(363.44,173.93) --
+	(366.39,172.12) --
+	(369.33,170.35) --
+	(372.28,168.62) --
+	(375.23,166.93) --
+	(378.17,165.28) --
+	(381.12,163.66) --
+	(384.07,162.09) --
+	(387.01,160.54) --
+	(389.96,159.03) --
+	(392.91,157.56) --
+	(395.85,156.12) --
+	(398.80,154.71) --
+	(401.75,153.36) --
+	(404.69,152.05) --
+	(407.64,150.80) --
+	(410.59,149.59) --
+	(413.53,148.42) --
+	(416.48,147.28) --
+	(419.43,146.18) --
+	(422.37,145.09) --
+	(425.32,144.03) --
+	(428.27,142.98) --
+	(431.21,141.94) --
+	(434.16,140.93) --
+	(437.11,139.96) --
+	(440.05,139.04) --
+	(443.00,138.14) --
+	(445.95,137.27) --
+	(448.90,136.41) --
+	(451.84,135.56) --
+	(454.79,134.70) --
+	(457.74,133.83) --
+	(460.68,132.98) --
+	(463.63,132.14) --
+	(466.58,131.32) --
+	(469.52,130.52) --
+	(472.47,129.73) --
+	(475.42,128.95) --
+	(478.36,128.19) --
+	(481.31,127.43) --
+	(484.26,126.69) --
+	(487.20,125.95) --
+	(490.15,125.22) --
+	(493.10,124.50) --
+	(496.04,123.80) --
+	(498.99,123.11) --
+	(501.94,122.43) --
+	(504.88,121.76) --
+	(507.83,121.11) --
+	(510.78,120.46) --
+	(513.72,119.81) --
+	(516.67,119.18) --
+	(519.62,118.55) --
+	(522.56,117.94) --
+	(525.51,117.34) --
+	(528.46,116.75) --
+	(531.41,116.16) --
+	(534.35,115.59) --
+	(537.30,115.03) --
+	(540.25,114.48) --
+	(543.19,113.94) --
+	(546.14,113.41) --
+	(549.09,112.89) --
+	(552.03,112.37) --
+	(554.98,111.87) --
+	(557.93,111.38) --
+	(560.87,110.90) --
+	(563.82,110.43) --
+	(566.77,109.97) --
+	(569.71,109.51) --
+	(572.66,109.07);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] (331.55,132.76) --
-	(334.91,126.93) --
-	(328.19,126.93) --
-	cycle;
-
-\path[fill=fillColor] (339.86,130.03) --
-	(343.23,124.20) --
-	(336.50,124.20) --
-	cycle;
-
-\path[fill=fillColor] (348.18,127.27) --
-	(351.54,121.44) --
-	(344.81,121.44) --
-	cycle;
-
-\path[fill=fillColor] (356.49,124.54) --
-	(359.86,118.71) --
-	(353.13,118.71) --
-	cycle;
-
-\path[fill=fillColor] (364.81,122.40) --
-	(368.17,116.58) --
-	(361.44,116.58) --
-	cycle;
-
-\path[fill=fillColor] (373.12,120.30) --
-	(376.48,114.48) --
-	(369.76,114.48) --
-	cycle;
-
-\path[fill=fillColor] (381.44,118.23) --
-	(384.80,112.40) --
-	(378.07,112.40) --
-	cycle;
-
-\path[fill=fillColor] (389.75,116.23) --
-	(393.11,110.40) --
-	(386.39,110.40) --
-	cycle;
-
-\path[fill=fillColor] (398.06,114.29) --
-	(401.43,108.46) --
-	(394.70,108.46) --
-	cycle;
-
-\path[fill=fillColor] (406.38,112.64) --
-	(409.74,106.81) --
-	(403.01,106.81) --
-	cycle;
-
-\path[fill=fillColor] (414.69,111.28) --
-	(418.06,105.45) --
-	(411.33,105.45) --
-	cycle;
-
-\path[fill=fillColor] (423.01,109.94) --
-	(426.37,104.12) --
-	(419.64,104.12) --
-	cycle;
-
-\path[fill=fillColor] (431.32,108.67) --
-	(434.68,102.84) --
-	(427.96,102.84) --
-	cycle;
-
-\path[fill=fillColor] (439.63,107.39) --
-	(443.00,101.56) --
-	(436.27,101.56) --
-	cycle;
-
-\path[fill=fillColor] (447.95,106.36) --
-	(451.31,100.53) --
-	(444.58,100.53) --
-	cycle;
-
-\path[fill=fillColor] (456.26,105.24) --
-	(459.63, 99.41) --
-	(452.90, 99.41) --
-	cycle;
-
-\path[fill=fillColor] (464.58,104.30) --
-	(467.94, 98.47) --
-	(461.21, 98.47) --
-	cycle;
-
-\path[fill=fillColor] (472.89,102.96) --
-	(476.25, 97.14) --
-	(469.53, 97.14) --
-	cycle;
-
-\path[fill=fillColor] (481.20,101.91) --
-	(484.57, 96.08) --
-	(477.84, 96.08) --
-	cycle;
-
-\path[fill=fillColor] (489.52,100.96) --
-	(492.88, 95.13) --
-	(486.15, 95.13) --
-	cycle;
-
-\path[fill=fillColor] (497.83,100.04) --
-	(501.20, 94.21) --
-	(494.47, 94.21) --
-	cycle;
-
-\path[fill=fillColor] (506.15, 99.12) --
-	(509.51, 93.30) --
-	(502.78, 93.30) --
-	cycle;
-
-\path[fill=fillColor] (514.46, 98.26) --
-	(517.82, 92.43) --
-	(511.10, 92.43) --
-	cycle;
-
-\path[fill=fillColor] (522.78, 97.51) --
-	(526.14, 91.68) --
-	(519.41, 91.68) --
-	cycle;
-
-\path[fill=fillColor] (531.09, 96.69) --
-	(534.45, 90.87) --
-	(527.73, 90.87) --
-	cycle;
-
-\path[fill=fillColor] (539.40, 96.04) --
-	(542.77, 90.21) --
-	(536.04, 90.21) --
-	cycle;
-
-\path[fill=fillColor] (547.72, 95.19) --
-	(551.08, 89.36) --
-	(544.35, 89.36) --
-	cycle;
-
-\path[fill=fillColor] (556.03, 94.44) --
-	(559.40, 88.61) --
-	(552.67, 88.61) --
-	cycle;
-
-\path[fill=fillColor] (564.35, 93.85) --
-	(567.71, 88.03) --
-	(560.98, 88.03) --
-	cycle;
-
-\path[fill=fillColor] (572.66, 93.15) --
-	(576.02, 87.33) --
-	(569.30, 87.33) --
+\path[fill=fillColor] (323.24,144.25) --
+	(326.60,138.42) --
+	(319.87,138.42) --
+	cycle;
+
+\path[fill=fillColor] (331.55,140.97) --
+	(334.91,135.14) --
+	(328.19,135.14) --
+	cycle;
+
+\path[fill=fillColor] (339.86,138.16) --
+	(343.23,132.34) --
+	(336.50,132.34) --
+	cycle;
+
+\path[fill=fillColor] (348.18,135.26) --
+	(351.54,129.43) --
+	(344.81,129.43) --
+	cycle;
+
+\path[fill=fillColor] (356.49,132.48) --
+	(359.86,126.65) --
+	(353.13,126.65) --
+	cycle;
+
+\path[fill=fillColor] (364.81,130.21) --
+	(368.17,124.38) --
+	(361.44,124.38) --
+	cycle;
+
+\path[fill=fillColor] (373.12,128.06) --
+	(376.48,122.24) --
+	(369.76,122.24) --
+	cycle;
+
+\path[fill=fillColor] (381.44,125.99) --
+	(384.80,120.16) --
+	(378.07,120.16) --
+	cycle;
+
+\path[fill=fillColor] (389.75,123.88) --
+	(393.11,118.06) --
+	(386.39,118.06) --
+	cycle;
+
+\path[fill=fillColor] (398.06,121.85) --
+	(401.43,116.03) --
+	(394.70,116.03) --
+	cycle;
+
+\path[fill=fillColor] (406.38,120.12) --
+	(409.74,114.29) --
+	(403.01,114.29) --
+	cycle;
+
+\path[fill=fillColor] (414.69,118.70) --
+	(418.06,112.87) --
+	(411.33,112.87) --
+	cycle;
+
+\path[fill=fillColor] (423.01,117.31) --
+	(426.37,111.48) --
+	(419.64,111.48) --
+	cycle;
+
+\path[fill=fillColor] (431.32,116.01) --
+	(434.68,110.19) --
+	(427.96,110.19) --
+	cycle;
+
+\path[fill=fillColor] (439.63,114.62) --
+	(443.00,108.79) --
+	(436.27,108.79) --
+	cycle;
+
+\path[fill=fillColor] (447.95,113.52) --
+	(451.31,107.69) --
+	(444.58,107.69) --
+	cycle;
+
+\path[fill=fillColor] (456.26,112.31) --
+	(459.63,106.48) --
+	(452.90,106.48) --
+	cycle;
+
+\path[fill=fillColor] (464.58,111.32) --
+	(467.94,105.49) --
+	(461.21,105.49) --
+	cycle;
+
+\path[fill=fillColor] (472.89,109.94) --
+	(476.25,104.11) --
+	(469.53,104.11) --
+	cycle;
+
+\path[fill=fillColor] (481.20,108.82) --
+	(484.57,102.99) --
+	(477.84,102.99) --
+	cycle;
+
+\path[fill=fillColor] (489.52,107.83) --
+	(492.88,102.00) --
+	(486.15,102.00) --
+	cycle;
+
+\path[fill=fillColor] (497.83,106.85) --
+	(501.20,101.02) --
+	(494.47,101.02) --
+	cycle;
+
+\path[fill=fillColor] (506.15,105.93) --
+	(509.51,100.10) --
+	(502.78,100.10) --
+	cycle;
+
+\path[fill=fillColor] (514.46,104.96) --
+	(517.82, 99.14) --
+	(511.10, 99.14) --
+	cycle;
+
+\path[fill=fillColor] (522.78,104.12) --
+	(526.14, 98.29) --
+	(519.41, 98.29) --
+	cycle;
+
+\path[fill=fillColor] (531.09,103.27) --
+	(534.45, 97.45) --
+	(527.73, 97.45) --
+	cycle;
+
+\path[fill=fillColor] (539.40,102.56) --
+	(542.77, 96.73) --
+	(536.04, 96.73) --
+	cycle;
+
+\path[fill=fillColor] (547.72,101.64) --
+	(551.08, 95.82) --
+	(544.35, 95.82) --
+	cycle;
+
+\path[fill=fillColor] (556.03,100.83) --
+	(559.40, 95.01) --
+	(552.67, 95.01) --
+	cycle;
+
+\path[fill=fillColor] (564.35,100.20) --
+	(567.71, 94.37) --
+	(560.98, 94.37) --
+	cycle;
+
+\path[fill=fillColor] (572.66, 99.42) --
+	(576.02, 93.59) --
+	(569.30, 93.59) --
 	cycle;
@@
 
-\path[fill=fillColor] (329.05,155.91) --
-	(334.05,155.91) --
-	(334.05,160.91) --
-	(329.05,160.91) --
-	cycle;
-
-\path[fill=fillColor] (337.37,151.39) --
-	(342.36,151.39) --
-	(342.36,156.38) --
-	(337.37,156.38) --
-	cycle;
-
-\path[fill=fillColor] (345.68,146.74) --
-	(350.68,146.74) --
-	(350.68,151.74) --
-	(345.68,151.74) --
-	cycle;
-
-\path[fill=fillColor] (353.99,142.21) --
-	(358.99,142.21) --
-	(358.99,147.21) --
-	(353.99,147.21) --
-	cycle;
-
-\path[fill=fillColor] (362.31,138.68) --
-	(367.30,138.68) --
-	(367.30,143.67) --
-	(362.31,143.67) --
-	cycle;
-
-\path[fill=fillColor] (370.62,135.24) --
-	(375.62,135.24) --
-	(375.62,140.23) --
-	(370.62,140.23) --
-	cycle;
-
-\path[fill=fillColor] (378.94,131.84) --
-	(383.93,131.84) --
-	(383.93,136.84) --
-	(378.94,136.84) --
-	cycle;
-
-\path[fill=fillColor] (387.25,128.58) --
-	(392.25,128.58) --
-	(392.25,133.58) --
-	(387.25,133.58) --
-	cycle;
-
-\path[fill=fillColor] (395.57,125.47) --
-	(400.56,125.47) --
-	(400.56,130.46) --
-	(395.57,130.46) --
-	cycle;
-
-\path[fill=fillColor] (403.88,122.80) --
-	(408.88,122.80) --
-	(408.88,127.79) --
-	(403.88,127.79) --
-	cycle;
-
-\path[fill=fillColor] (412.19,120.61) --
-	(417.19,120.61) --
-	(417.19,125.61) --
-	(412.19,125.61) --
-	cycle;
-
-\path[fill=fillColor] (420.51,118.48) --
-	(425.50,118.48) --
-	(425.50,123.48) --
-	(420.51,123.48) --
-	cycle;
-
-\path[fill=fillColor] (428.82,116.42) --
-	(433.82,116.42) --
-	(433.82,121.41) --
-	(428.82,121.41) --
-	cycle;
-
-\path[fill=fillColor] (437.14,114.36) --
-	(442.13,114.36) --
-	(442.13,119.36) --
-	(437.14,119.36) --
-	cycle;
-
-\path[fill=fillColor] (445.45,112.70) --
-	(450.45,112.70) --
-	(450.45,117.70) --
-	(445.45,117.70) --
-	cycle;
-
-\path[fill=fillColor] (453.76,110.90) --
-	(458.76,110.90) --
-	(458.76,115.90) --
-	(453.76,115.90) --
-	cycle;
-
-\path[fill=fillColor] (462.08,109.42) --
-	(467.07,109.42) --
-	(467.07,114.41) --
-	(462.08,114.41) --
-	cycle;
-
-\path[fill=fillColor] (470.39,107.36) --
-	(475.39,107.36) --
-	(475.39,112.35) --
-	(470.39,112.35) --
-	cycle;
-
-\path[fill=fillColor] (478.71,105.71) --
-	(483.70,105.71) --
-	(483.70,110.71) --
-	(478.71,110.71) --
-	cycle;
-
-\path[fill=fillColor] (487.02,104.22) --
-	(492.02,104.22) --
-	(492.02,109.21) --
-	(487.02,109.21) --
-	cycle;
-
-\path[fill=fillColor] (495.34,102.80) --
-	(500.33,102.80) --
-	(500.33,107.79) --
-	(495.34,107.79) --
-	cycle;
-
-\path[fill=fillColor] (503.65,101.36) --
-	(508.64,101.36) --
-	(508.64,106.36) --
-	(503.65,106.36) --
-	cycle;
-
-\path[fill=fillColor] (511.96,100.01) --
-	(516.96,100.01) --
-	(516.96,105.01) --
-	(511.96,105.01) --
-	cycle;
-
-\path[fill=fillColor] (520.28, 98.85) --
-	(525.27, 98.85) --
-	(525.27,103.85) --
-	(520.28,103.85) --
-	cycle;
-
-\path[fill=fillColor] (528.59, 97.60) --
-	(533.59, 97.60) --
-	(533.59,102.59) --
-	(528.59,102.59) --
-	cycle;
-
-\path[fill=fillColor] (536.91, 96.60) --
-	(541.90, 96.60) --
-	(541.90,101.59) --
-	(536.91,101.59) --
-	cycle;
-
-\path[fill=fillColor] (545.22, 95.31) --
-	(550.22, 95.31) --
-	(550.22,100.31) --
-	(545.22,100.31) --
-	cycle;
-
-\path[fill=fillColor] (553.53, 94.15) --
-	(558.53, 94.15) --
-	(558.53, 99.14) --
-	(553.53, 99.14) --
-	cycle;
-
-\path[fill=fillColor] (561.85, 93.24) --
-	(566.84, 93.24) --
-	(566.84, 98.24) --
-	(561.85, 98.24) --
-	cycle;
-
-\path[fill=fillColor] (570.16, 92.17) --
-	(575.16, 92.17) --
-	(575.16, 97.17) --
-	(570.16, 97.17) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.02,190.09) -- (335.08,190.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.55,186.56) -- (331.55,193.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.33,183.71) -- (343.40,183.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.86,180.17) -- (339.86,187.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.65,177.10) -- (351.71,177.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.18,173.57) -- (348.18,180.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.96,170.72) -- (360.02,170.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.49,167.18) -- (356.49,174.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,165.75) -- (368.34,165.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,162.22) -- (364.81,169.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,160.93) -- (376.65,160.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,157.40) -- (373.12,164.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,156.17) -- (384.97,156.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,152.64) -- (381.44,159.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,151.65) -- (393.28,151.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,148.12) -- (389.75,155.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,147.35) -- (401.60,147.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,143.82) -- (398.06,150.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,143.66) -- (409.91,143.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,140.13) -- (406.38,147.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,140.64) -- (418.22,140.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,137.11) -- (414.69,144.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,137.72) -- (426.54,137.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,134.19) -- (423.01,141.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,134.84) -- (434.85,134.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,131.31) -- (431.32,138.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,132.03) -- (443.17,132.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,128.50) -- (439.63,135.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,129.73) -- (451.48,129.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,126.20) -- (447.95,133.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,127.22) -- (459.79,127.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,123.69) -- (456.26,130.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,125.20) -- (468.11,125.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,121.67) -- (464.58,128.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,122.43) -- (476.42,122.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,118.90) -- (472.89,125.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,120.20) -- (484.74,120.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,116.67) -- (481.20,123.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,118.17) -- (493.05,118.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,114.64) -- (489.52,121.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,116.28) -- (501.36,116.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,112.74) -- (497.83,119.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,114.31) -- (509.68,114.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,110.78) -- (506.15,117.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,112.49) -- (517.99,112.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,108.96) -- (514.46,116.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,110.92) -- (526.31,110.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,107.38) -- (522.78,114.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,109.24) -- (534.62,109.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,105.71) -- (531.09,112.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,107.92) -- (542.94,107.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,104.39) -- (539.40,111.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,106.23) -- (551.25,106.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72,102.70) -- (547.72,109.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,104.64) -- (559.56,104.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03,101.11) -- (556.03,108.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,103.43) -- (567.88,103.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35, 99.90) -- (564.35,106.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,102.01) -- (576.19,102.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66, 98.48) -- (572.66,105.55);
+\path[fill=fillColor] (320.74,170.78) --
+	(325.73,170.78) --
+	(325.73,175.77) --
+	(320.74,175.77) --
+	cycle;
+
+\path[fill=fillColor] (329.05,165.46) --
+	(334.05,165.46) --
+	(334.05,170.45) --
+	(329.05,170.45) --
+	cycle;
+
+\path[fill=fillColor] (337.37,160.96) --
+	(342.36,160.96) --
+	(342.36,165.95) --
+	(337.37,165.95) --
+	cycle;
+
+\path[fill=fillColor] (345.68,156.26) --
+	(350.68,156.26) --
+	(350.68,161.25) --
+	(345.68,161.25) --
+	cycle;
+
+\path[fill=fillColor] (353.99,151.74) --
+	(358.99,151.74) --
+	(358.99,156.74) --
+	(353.99,156.74) --
+	cycle;
+
+\path[fill=fillColor] (362.31,148.12) --
+	(367.30,148.12) --
+	(367.30,153.11) --
+	(362.31,153.11) --
+	cycle;
+
+\path[fill=fillColor] (370.62,144.68) --
+	(375.62,144.68) --
+	(375.62,149.67) --
+	(370.62,149.67) --
+	cycle;
+
+\path[fill=fillColor] (378.94,141.38) --
+	(383.93,141.38) --
+	(383.93,146.38) --
+	(378.94,146.38) --
+	cycle;
+
+\path[fill=fillColor] (387.25,138.08) --
+	(392.25,138.08) --
+	(392.25,143.07) --
+	(387.25,143.07) --
+	cycle;
+
+\path[fill=fillColor] (395.57,134.92) --
+	(400.56,134.92) --
+	(400.56,139.92) --
+	(395.57,139.92) --
+	cycle;
+
+\path[fill=fillColor] (403.88,132.16) --
+	(408.88,132.16) --
+	(408.88,137.16) --
+	(403.88,137.16) --
+	cycle;
+
+\path[fill=fillColor] (412.19,129.98) --
+	(417.19,129.98) --
+	(417.19,134.97) --
+	(412.19,134.97) --
+	cycle;
+
+\path[fill=fillColor] (420.51,127.83) --
+	(425.50,127.83) --
+	(425.50,132.82) --
+	(420.51,132.82) --
+	cycle;
+
+\path[fill=fillColor] (428.82,125.76) --
+	(433.82,125.76) --
+	(433.82,130.76) --
+	(428.82,130.76) --
+	cycle;
+
+\path[fill=fillColor] (437.14,123.59) --
+	(442.13,123.59) --
+	(442.13,128.58) --
+	(437.14,128.58) --
+	cycle;
+
+\path[fill=fillColor] (445.45,121.88) --
+	(450.45,121.88) --
+	(450.45,126.88) --
+	(445.45,126.88) --
+	cycle;
+
+\path[fill=fillColor] (453.76,120.04) --
+	(458.76,120.04) --
+	(458.76,125.03) --
+	(453.76,125.03) --
+	cycle;
+
+\path[fill=fillColor] (462.08,118.49) --
+	(467.07,118.49) --
+	(467.07,123.48) --
+	(462.08,123.48) --
+	cycle;
+
+\path[fill=fillColor] (470.39,116.43) --
+	(475.39,116.43) --
+	(475.39,121.43) --
+	(470.39,121.43) --
+	cycle;
+
+\path[fill=fillColor] (478.71,114.73) --
+	(483.70,114.73) --
+	(483.70,119.72) --
+	(478.71,119.72) --
+	cycle;
+
+\path[fill=fillColor] (487.02,113.23) --
+	(492.02,113.23) --
+	(492.02,118.23) --
+	(487.02,118.23) --
+	cycle;
+
+\path[fill=fillColor] (495.34,111.77) --
+	(500.33,111.77) --
+	(500.33,116.77) --
+	(495.34,116.77) --
+	cycle;
+
+\path[fill=fillColor] (503.65,110.35) --
+	(508.64,110.35) --
+	(508.64,115.34) --
+	(503.65,115.34) --
+	cycle;
+
+\path[fill=fillColor] (511.96,108.90) --
+	(516.96,108.90) --
+	(516.96,113.90) --
+	(511.96,113.90) --
+	cycle;
+
+\path[fill=fillColor] (520.28,107.65) --
+	(525.27,107.65) --
+	(525.27,112.64) --
+	(520.28,112.64) --
+	cycle;
+
+\path[fill=fillColor] (528.59,106.36) --
+	(533.59,106.36) --
+	(533.59,111.36) --
+	(528.59,111.36) --
+	cycle;
+
+\path[fill=fillColor] (536.91,105.34) --
+	(541.90,105.34) --
+	(541.90,110.33) --
+	(536.91,110.33) --
+	cycle;
+
+\path[fill=fillColor] (545.22,104.01) --
+	(550.22,104.01) --
+	(550.22,109.01) --
+	(545.22,109.01) --
+	cycle;
+
+\path[fill=fillColor] (553.53,102.76) --
+	(558.53,102.76) --
+	(558.53,107.75) --
+	(553.53,107.75) --
+	cycle;
+
+\path[fill=fillColor] (561.85,101.83) --
+	(566.84,101.83) --
+	(566.84,106.83) --
+	(561.85,106.83) --
+	cycle;
+
+\path[fill=fillColor] (570.16,100.67) --
+	(575.16,100.67) --
+	(575.16,105.66) --
+	(570.16,105.66) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.33,190.59) -- (343.40,190.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.86,187.06) -- (339.86,194.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.65,184.03) -- (351.71,184.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.18,180.49) -- (348.18,187.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.96,177.69) -- (360.02,177.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.49,174.16) -- (356.49,181.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,172.70) -- (368.34,172.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,169.17) -- (364.81,176.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,167.92) -- (376.65,167.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,164.38) -- (373.12,171.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,163.35) -- (384.97,163.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,159.82) -- (381.44,166.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,158.83) -- (393.28,158.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,155.30) -- (389.75,162.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,154.55) -- (401.60,154.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,151.01) -- (398.06,158.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,150.76) -- (409.91,150.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,147.23) -- (406.38,154.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,147.81) -- (418.22,147.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,144.28) -- (414.69,151.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,144.92) -- (426.54,144.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,141.39) -- (423.01,148.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,142.06) -- (434.85,142.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,138.53) -- (431.32,145.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,139.16) -- (443.17,139.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,135.62) -- (439.63,142.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,136.86) -- (451.48,136.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,133.33) -- (447.95,140.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,134.36) -- (459.79,134.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,130.83) -- (456.26,137.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,132.27) -- (468.11,132.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,128.74) -- (464.58,135.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,129.57) -- (476.42,129.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,126.04) -- (472.89,133.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,127.31) -- (484.74,127.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,123.78) -- (481.20,130.84);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,125.32) -- (493.05,125.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,121.79) -- (489.52,128.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,123.43) -- (501.36,123.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,119.89) -- (497.83,126.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,121.47) -- (509.68,121.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,117.93) -- (506.15,125.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,119.60) -- (517.99,119.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,116.06) -- (514.46,123.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,117.95) -- (526.31,117.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,114.42) -- (522.78,121.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,116.25) -- (534.62,116.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,112.72) -- (531.09,119.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,114.97) -- (542.94,114.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,111.44) -- (539.40,118.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,113.27) -- (551.25,113.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72,109.73) -- (547.72,116.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,111.59) -- (559.56,111.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03,108.05) -- (556.03,115.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,110.40) -- (567.88,110.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35,106.87) -- (564.35,113.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,108.89) -- (576.19,108.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,105.36) -- (572.66,112.42);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[fill=fillColor] (331.55, 49.94) circle (  2.50);
-
-\path[fill=fillColor] (339.86, 50.02) circle (  2.50);
-
-\path[fill=fillColor] (348.18, 50.01) circle (  2.50);
-
-\path[fill=fillColor] (356.49, 49.81) circle (  2.50);
-
-\path[fill=fillColor] (364.81, 49.97) circle (  2.50);
-
-\path[fill=fillColor] (373.12, 50.10) circle (  2.50);
-
-\path[fill=fillColor] (381.44, 49.98) circle (  2.50);
-
-\path[fill=fillColor] (389.75, 50.04) circle (  2.50);
-
-\path[fill=fillColor] (398.06, 50.05) circle (  2.50);
-
-\path[fill=fillColor] (406.38, 49.95) circle (  2.50);
-
-\path[fill=fillColor] (414.69, 50.17) circle (  2.50);
-
-\path[fill=fillColor] (423.01, 49.86) circle (  2.50);
-
-\path[fill=fillColor] (431.32, 49.74) circle (  2.50);
-
-\path[fill=fillColor] (439.63, 49.98) circle (  2.50);
-
-\path[fill=fillColor] (447.95, 50.13) circle (  2.50);
-
-\path[fill=fillColor] (456.26, 50.04) circle (  2.50);
-
-\path[fill=fillColor] (464.58, 49.94) circle (  2.50);
-
-\path[fill=fillColor] (472.89, 49.95) circle (  2.50);
-
-\path[fill=fillColor] (481.20, 49.84) circle (  2.50);
-
-\path[fill=fillColor] (489.52, 49.92) circle (  2.50);
-
-\path[fill=fillColor] (497.83, 49.86) circle (  2.50);
-
-\path[fill=fillColor] (506.15, 50.08) circle (  2.50);
-
-\path[fill=fillColor] (514.46, 49.96) circle (  2.50);
-
-\path[fill=fillColor] (522.78, 50.12) circle (  2.50);
-
-\path[fill=fillColor] (531.09, 50.25) circle (  2.50);
-
-\path[fill=fillColor] (539.40, 49.77) circle (  2.50);
-
-\path[fill=fillColor] (547.72, 49.90) circle (  2.50);
-
-\path[fill=fillColor] (556.03, 50.13) circle (  2.50);
-
-\path[fill=fillColor] (564.35, 50.12) circle (  2.50);
-
-\path[fill=fillColor] (572.66, 49.92) circle (  2.50);
+\path[fill=fillColor] (323.24, 49.94) circle (  2.50);
+
+\path[fill=fillColor] (331.55, 50.02) circle (  2.50);
+
+\path[fill=fillColor] (339.86, 50.01) circle (  2.50);
+
+\path[fill=fillColor] (348.18, 49.81) circle (  2.50);
+
+\path[fill=fillColor] (356.49, 49.97) circle (  2.50);
+
+\path[fill=fillColor] (364.81, 50.10) circle (  2.50);
+
+\path[fill=fillColor] (373.12, 49.98) circle (  2.50);
+
+\path[fill=fillColor] (381.44, 50.04) circle (  2.50);
+
+\path[fill=fillColor] (389.75, 50.05) circle (  2.50);
+
+\path[fill=fillColor] (398.06, 49.95) circle (  2.50);
+
+\path[fill=fillColor] (406.38, 50.17) circle (  2.50);
+
+\path[fill=fillColor] (414.69, 49.86) circle (  2.50);
+
+\path[fill=fillColor] (423.01, 49.74) circle (  2.50);
+
+\path[fill=fillColor] (431.32, 49.98) circle (  2.50);
+
+\path[fill=fillColor] (439.63, 50.13) circle (  2.50);
+
+\path[fill=fillColor] (447.95, 50.04) circle (  2.50);
+
+\path[fill=fillColor] (456.26, 49.94) circle (  2.50);
+
+\path[fill=fillColor] (464.58, 49.95) circle (  2.50);
+
+\path[fill=fillColor] (472.89, 49.84) circle (  2.50);
+
+\path[fill=fillColor] (481.20, 49.92) circle (  2.50);
+
+\path[fill=fillColor] (489.52, 49.86) circle (  2.50);
+
+\path[fill=fillColor] (497.83, 50.08) circle (  2.50);
+
+\path[fill=fillColor] (506.15, 49.96) circle (  2.50);
+
+\path[fill=fillColor] (514.46, 50.12) circle (  2.50);
+
+\path[fill=fillColor] (522.78, 50.25) circle (  2.50);
+
+\path[fill=fillColor] (531.09, 49.77) circle (  2.50);
+
+\path[fill=fillColor] (539.40, 49.90) circle (  2.50);
+
+\path[fill=fillColor] (547.72, 50.13) circle (  2.50);
+
+\path[fill=fillColor] (556.03, 50.12) circle (  2.50);
+
+\path[fill=fillColor] (564.35, 49.92) circle (  2.50);
+
+\path[fill=fillColor] (572.66, 49.83) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}

### 2020-04-09 serial.tex
started writing

@@
 
-Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its basic reproduction number $\mathcal R_0$.
-The basic reproduction number, which is defined as the average number of secondary cases caused by a primary case, allows us to predict the extent to which a disease will spread and the amount of intervention to prevent an outbreak.
+Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its reproduction number $\mathcal R$.
+The reproduction number, which is defined as the average number of secondary cases caused by a primary case, allows us to predict the extent to which a disease will spread and the amount of intervention to prevent an outbreak.
 Since the basic reproduction number cannot be measured directly, it is often inferred from the observed exponential growth rate using generation or serial intervals.
@@
 Similarly, serial intervals are defined as the time between when an infector and an infectee become symptomatic.
-While
+
+There is an apparent paradox between generation and serial intervals.
+When the epidemic is growing exponentially, the disease dynamics can be described by the ``renewal'' of incidence based on previous incidence of infection and the associated generation-interval distribution.
+This renewal formulation allows us to link the exponential growth rate of an epidemic with its reproduction number.
+Likewise, if infection leads to symptoms, we should be able to describe the renewal of symptomatic cases based on previous incidence of symptomatic cases and the associated serial-interval distribution.
+The current literature does not support this idea.
+
+Here, we resolve the apparent paradox.
 

### 2020-04-09 figure_sir.R

@@ -1,285 +1,0 @@
-library(tidyr)
-library(dplyr)
-library(ggplot2); theme_set(theme_bw())
-library(gridExtra)
-source("renewal_det.R")
-
-load("sir_sim.rda")
-
-rr <- renewal_det(tmax=110)
-
-plot(sir_sim$data, type="l", log="y")
-
-lines(rr$tvec, cumsum(rr$Ivec), col=2)
-
-## model parameters
-meanlog <- 1.621
-sdlog <- 0.418
-scale <- 5.5
-shape <- 4.1
-r <- 1/5.5
-
-set.seed(101)
-inc <- rlnorm(50000, meanlog, sdlog)
-minc <- mean(inc)
-winc <- weighted.mean(inc, exp(-r*inc))
-
-gen <- rweibull(50000, shape, scale)
-mgen <- mean(gen)
-wgen <- weighted.mean(gen, exp(-r*gen))
-
-serforward <- gen+rlnorm(50000, meanlog, sdlog)
-ser <- -inc+serforward
-mser <- mean(ser)
-ser2 <- -sample(inc, prob=exp(-r*inc), replace=TRUE)+serforward
-ww <- exp(-r*ser2)
-ww[ser2 < 0] <- 1
-wser <- weighted.mean(ser2, ww)
-
-g1 <- ggplot(sir_sim$data) +
-  stat_function(fun=function(x)15*exp(1/5.5*x), lty=2) +
-  geom_line(aes(time, infected)) +
-  scale_x_continuous("Time", expand=c(0, 0), limits=c(0, 80)) +
-  scale_y_log10("Cumulative incidence", expand=c(0, 0), limits=c(10, 49999)) +
-  ggtitle("A") +
-  theme(
-    panel.grid = element_blank(),
-    panel.border = element_blank(),
-    axis.line = element_line()
-  )
-
-tcut <- 10:32*2
-icut <- -80:80/2
-
-incdata0 <- data.frame(
-  cohort=sir_sim$t_infected,
-  tdiff=sir_sim$t_symptomatic-sir_sim$t_infected
-) %>%
-  filter(!is.na(cohort), !is.na(tdiff), cohort > 20, cohort <= 64) %>%
-  mutate(
-    cc=cut(cohort, tcut),
-    tt=cut(tdiff, icut)
-  ) %>%
-  group_by(cc, tt) %>%
-  summarize(
-    size=length(tt)
-  ) %>%
-  mutate(
-    prop=size/sum(size)
-  ) %>%
[…]

### 2020-04-09 forward.R

@@ -2,6 +2,7 @@ library(tidyr)
 library(dplyr)
 library(ggplot2); theme_set(theme_bw())
 library(gridExtra)
+library(tikzDevice)
 source("renewal_det.R")
 
 load("sir_sim.rda")
@@ -38,18 +39,19 @@ detdata <- data.frame(
 )
 
 g1 <- ggplot(sir_sim$data) +
-  geom_line(data=detdata, aes(tvec, ci)) +
-  geom_line(aes(time, infected), col=2) +
-  scale_x_continuous("Time", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_log10("Cumulative incidence", expand=c(0, 0), limits=c(10, 49999)) +
+  geom_line(data=detdata, aes(tvec, ci, col="Deterministic"), lwd=1) +
+  geom_line(aes(time, infected, col="Stochastic"), lwd=1) +
+  scale_x_continuous("Time (days)", expand=c(0, 0), limits=c(0, 82)) +
+  scale_y_continuous("Cumulative incidence", expand=c(0, 0), limits=c(10, 49999)) +
+  scale_color_manual(values=c(1, "#D55E00")) +
   ggtitle("A") +
   theme(
     panel.grid = element_blank(),
-    panel.border = element_blank(),
-    axis.line = element_line()
+    legend.title = element_blank(),
+    legend.position = c(0.1, 0.7)
   )
 
-tcut <- 0:20*4
+tcut <- 0:40*2
 
 incdata0 <- data.frame(
   cohort=sir_sim$t_infected,
@@ -63,16 +65,15 @@ incdet <- data.frame(
 )
 
 g2 <- ggplot(incdata0) +
-  geom_line(data=incdet, aes(tvec, mf)) +
-  geom_point(aes(cc, mean), shape=1, col="red") +
-  scale_x_continuous("Cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
+  geom_line(data=incdet, aes(tvec, mf), lwd=1) +
+  geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
+  geom_hline(yintercept=incdet$mf[1], lty=2) +
+  scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
   scale_y_continuous("Forward incubation period (days)", expand=c(0, 0), limits=c(0, 7)) +
   scale_fill_gradientn(colors=c("white", "black")) +
   ggtitle("B") +
[…]

### 2020-04-09 rR.R

@@ -34,7 +34,7 @@ serialR <- function(r=0.1,
   logbackinc <- log(backinc)
   
   muloggen <- meanlog2 + sdlog2 * rho * (logbackinc - meanlog1)/sdlog1
-  sigmaloggen <- sdlog2^2 * (1 - rho^2)
+  sigmaloggen <- sqrt(sdlog2^2 * (1 - rho^2))
   
   forwardgen <- exp(rnorm(nsim, muloggen, sigmaloggen))
   forwardinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
@@ -62,7 +62,7 @@ serialR2 <- function(r=0.1,
   logbackinc <- log(backinc)
   
   muloggen <- meanlog2 + sdlog2 * rho * (logbackinc - meanlog1)/sdlog1
-  sigmaloggen <- sdlog2^2 * (1 - rho^2)
+  sigmaloggen <- sqrt(sdlog2^2 * (1 - rho^2))
   
   forwardgen <- exp(rnorm(nsim, muloggen, sigmaloggen))
   forwardinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
@@ -91,23 +91,23 @@ generationR <- function(r=0.1,
 
 rRdata <- list(
   data.frame(
-    r=seq(0.01, 0.3, by=0.01),
-    R=sapply(seq(0.01, 0.3, by=0.01), function(x) serialR(x, rho=0.5)$R),
+    r=seq(0, 0.3, by=0.01),
+    R=sapply(seq(0, 0.3, by=0.01), function(x) serialR(x, rho=0.5)$R),
     type="Serial interval ($\\rho=0.5$)"
   ),
   data.frame(
-    r=seq(0.01, 0.3, by=0.01),
-    R=sapply(seq(0.01, 0.3, by=0.01), function(x) serialR(x, rho=0)$R),
+    r=seq(0, 0.3, by=0.01),
+    R=sapply(seq(0, 0.3, by=0.01), function(x) serialR(x, rho=0)$R),
     type="Serial interval ($\\rho=0$)"
   ),
   data.frame(
-    r=seq(0.01, 0.3, by=0.01),
-    R=sapply(seq(0.01, 0.3, by=0.01), function(x) serialR(x, rho=-0.5)$R),
+    r=seq(0, 0.3, by=0.01),
+    R=sapply(seq(0, 0.3, by=0.01), function(x) serialR(x, rho=-0.5)$R),
[…]

### 2020-04-09 renewal_det.R

@@ -1,12 +1,12 @@
 renewal_det <- function(R0=2.5,
                         N=40000,
                         S0=40000-10,
-                        dt=0.1,
+                        dt=0.025,
                         incfun=function(x) dlnorm(x, meanlog=1.621, sdlog=0.418),
                         genfun=function(x) dweibull(x, shape=4.1, scale=5.5),
                         I0=10,
-                        tmax=150,
-                        genmax=150) {
+                        tmax=200,
+                        genmax=2000) {
   inc <- incfun(0:genmax*dt)
   inc <- inc/sum(inc)
   gen <- genfun(0:genmax*dt)
@@ -35,15 +35,44 @@ renewal_det <- function(R0=2.5,
   forwardinc <- sapply(1:(length(Svec)-genmax), function(x) inc)
   backwardinc <- sapply((genmax+1):(length(Svec)), function(x) inc[1:(1+genmax)]*Ivec[x:(x-genmax)]/sum(inc[1:(1+genmax)]*Ivec[x:(x-genmax)]))
   
+  mfgen <- apply(forwardgen, 2, function(x) sum(x*0:genmax*dt)/sum(x))
+  mbgen <- apply(backwardgen, 2, function(x) sum(x*0:genmax*dt)/sum(x))
+  mfinc <- apply(forwardinc, 2, function(x) sum(x*0:genmax*dt)/sum(x))
+  mbinc <- apply(backwardinc, 2, function(x) sum(x*0:genmax*dt)/sum(x))
+  
+  ## Jensen's inequality!!!!!
+  # sum(backwardinc[,x-genmax]*rev(mfgen[(x-genmax):x]))-mbinc[1]
+  
+  #tmpmat <- matrix(0:(genmax)*dt, nrow=genmax+1, ncol=genmax+1) - t(matrix(0:genmax*dt, nrow=genmax+1, ncol=genmax+1))
+  
+  # mfser0 <- sapply((genmax+1):(length(Svec)-genmax), function(x) {
+  #  sum(t(backwardinc[,x-genmax] * t(forwardgen[,x:(x-genmax)])) * tmpmat)
+  #}) +
+  #  tail(mfinc, -genmax)
+
+  # sapply((genmax+1):(length(Svec)-genmax), function(x) sum(backwardinc[,x-genmax]*rev(mfgen[(x-genmax):x])))
+    
[…]

### 2020-04-09 sir_sim.R

@@ -1,5 +1,5 @@
 source("sir.R")
 
-sir_sim <- sir.full(size=40000, I0=10, seed=101, keep.intrinsic = TRUE)
+sir_sim <- sir.full(size=40000, I0=10, seed=123, keep.intrinsic = TRUE)
 
 save("sir_sim", file="sir_sim.rda")

### 2020-04-09 serial.tex
backward and forward

@@
 
+\section{Methods}
+
 \section{Backward and forward delay distributions}
+
+In order to model serial intervals, we first explain the differences between backward and forward delays.
+To do so, we divide epidemiological events as \emph{primary} and \emph{secondary} events.
+When we measure a within-individual delay, we define primary and secondary events based on their timing;
+the primary event always occurs before the secondary event.
+When we measure between-individual delays, we define primary and secondary events based on whether they occurred within an infector or an infectee, respectively;
+the primary event does not necessarily occur before the secondary event.
+
+We model time delays between a primary and a secondary event from a cohort perspective.
+A primary cohort consists of \emph{all} individuals whose primary event occurred at a given time; 
+a secondary cohort can be defined similarly based on the secondary events.
+For example, when we are measurign serial intervals, a primary cohort $s$ consists of all infectors who became symptomatic at time $s$.
+Then, for each primary cohort $s$, we can define the expected time distribution between primary and secondary events for primary cohort $s$.
+We refer to this distribution as the forward delay distribution and denote it as $f_s(\tau)$.
+We assume that forward delay distributions can vary across primary cohorts.
+
+Likewise, we can define a backward delay distribution $b_s(\tau)$ for a secondary cohort $s$:
+The backward delay distribution for secondary host $s$ describes the time delays between a primary and secondary host given that the secondary event occurred at time $s$.
+It follows that:
+\begin{equation}
+b_s(\tau) \propto i(s-\tau) f_{s-\tau}(\tau)
+\end{equation}
+where $i(s)$ is the size of the primary cohort $s$.
+Therefore, changes in the backward delay distribution depends on the changes in cohort size $i(s)$ (therefore incidence of infection) as well as changes in the forward delay distribution.
+This concept generalizes the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
 

### 2020-04-10 serial.tex
slowly making progress...

@@
 
+\section{Serial interval distributions}
+
+The serial interval is defined as the time between when an infector becomes symptomatic and when and infectee becomes symptomatic.
+We express realized serial intervals as:
+\begin{equation}
+- x_0 + \sigma + x_1
+\end{equation}
+where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\sigma$ represents the realized generation interval.
+Previous studies have assumed that (i) $x_0$ and $x_1$ have the same mean and (ii) therefore the serial and generation intervals have the same mean;
+however, these results implicitly assume that incidence stays constant.
+
+Using the cohort-based framework provides a clear way of understanding the serial-interval distribution.
+Given that an infector became symptomatic at time $\ell$, we have to first go backward in time by asking when the infector was infected and go forward in time by asking when the infectee became symptomatic.
+Then, it is clear that $x_0$ should follow the backward incubation period distribution for secondary cohort $\ell$; 
+$\sigma$ the forward generation-interval distribution for a primary cohort $\ell - x_0$ conditional on the realized incubation period $x_0$;
+and $s_1$ forward incubation period distribution for a primary cohort $\ell - x_0 + \sigma$.
+Assuming that the forward incubation distribution does not vary across cohorts, the forward serial interval distribution of a primary cohort $\ell$ can be written as follows:
+\begin{equation}
+f_\ell(\tau) = \int_{0}^\infty \int_{0}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) d x_0 d\sigma
+\end{equation}
+where $h$ is the joint probability distribution of the incubation period and generation interval of a primary cohort $\ell - x_0$, and $k$ is a marginal probability distribution describing incubation periods.
+
+Likewise, we can define backward serial interval distribution for a secondary cohort $\ell$.
+Given that an infectee became symptomatic at time $\ell$, we have to first go backward in time by asking when the infectee became infected and when the infectee was infected by the infector; 
+then, we have to go forward in time by asking when the infector became symptomatic.
+In this case, $x_1$ and $\sigma$ follow the backward incubation period and generation-interval distributions, respectively, and $x_0$ follows the forward incubation period distribution.
+Therefore, the backward serial interval distribution of a primary cohort $\ell$ can be written as follows
+\begin{equation}
+f_\ell(\tau) = \int_{0}^\infty \int_{0}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) d x_0 d\sigma
+\end{equation}
+
 \bibliography{serial}

### 2020-04-11 serial.tex
working on it

@@
 	\textbf\newline{
-		Understanding serial interval distributions: applications to the COVID-19 pandemic
+		Unraveling the paradox between generation and serial intervals: applications to COVID-19 pandemic
 	}
-}
+}\\
 Sang Woo Park
@@
 Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its reproduction number $\mathcal R$.
-The reproduction number, which is defined as the average number of secondary cases caused by a primary case, allows us to predict the extent to which a disease will spread and the amount of intervention to prevent an outbreak.
-Since the basic reproduction number cannot be measured directly, it is often inferred from the observed exponential growth rate using generation or serial intervals.
+The reproduction number, which is defined as the average number of secondary cases caused by a primary case, allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak.
+Since the reproduction number cannot be measured directly, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions.
 
-Generation intervals are defined as the time between when an individual is infected and when an individual infects another person.
-Similarly, serial intervals are defined as the time between when an infector and an infectee become symptomatic.
+The generation interval is defined as the time between when an individual (infector) is infected and when an individual infects another person (infectee).
+On the other hand, the serial interval is defined as the time between when an infector and an infectee become symptomatic.
+% Despite having similar definitions, generation and serial intervals are different because serial intervals rely on the generation intervals as well as the incubation periods of an infector and an infectee.
+Previous studies have often alluded to differences in their variances, despite having identical expected values, and noted that using serial-interval distribution can give different estimates of $\mathcal R$.
+Even though these distinctions were first made over a decade ago \citep{svensson2007note}, 
+the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds:
+Researchers continue to rely on both generation and serial intervals to estimate $\mathcal R$ for COVID-19 without making a clear distinction, and some even mislabel them.
 
-There is an apparent paradox between generation and serial intervals.
-When the epidemic is growing exponentially, the disease dynamics can be described by the ``renewal'' of incidence based on previous incidence of infection and the associated generation-interval distribution.
-This renewal formulation allows us to link the exponential growth rate of an epidemic with its reproduction number.
-Likewise, if infection leads to symptoms, we should be able to describe the renewal of symptomatic cases based on previous incidence of symptomatic cases and the associated serial-interval distribution.
-The current literature does not support this idea.
+The lack of clear understanding of their differences can be largely attributed to an apparent paradox.
+When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
+This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number $\mathcal R$.
+Likewise, since infection typically leads to symptoms, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
+Therefore, both generation- and serial-interval distributions should give us identical estimates of  $\mathcal R$ based the observed epidemic growth rate.
+Current theory seems to contradict our biological intution.
 
-Here, we resolve the apparent paradox.
-
-We show that the serial-interval distribution can provide a correct link between the speed
+Here, we provide an answer to the decade-old paradox.
+We provide a new framework for understanding serial intervals and show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.
 
@@
 
-\section{Backward and forward delay distributions}
+\subsection{Backward and forward delay distributions}
 
@@
 
-\section{Serial interval distributions}
+\subsection{Serial interval distributions}
 
@@
 \begin{equation}
-f_\ell(\tau) = \int_{0}^\infty \int_{0}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) d x_0 d\sigma
+f_\ell(\tau) \propto \int_{0}^\infty \int_{0}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma
 \end{equation}
-where $h$ is the joint probability distribution of the incubation period and generation interval of a primary cohort $\ell - x_0$, and $k$ is a marginal probability distribution describing incubation periods.
+where $i$ is the incidence of infection, $h$ is the joint probability distribution of the incubation period and generation interval of a primary cohort $\ell - x_0$, and $k$ is a marginal probability distribution of $h$ describing the forward incubation periods.
 
@@
 In this case, $x_1$ and $\sigma$ follow the backward incubation period and generation-interval distributions, respectively, and $x_0$ follows the forward incubation period distribution.
-Therefore, the backward serial interval distribution of a primary cohort $\ell$ can be written as follows
+Therefore, the backward serial interval distribution of a secondary cohort $\ell$ can be written as follows
 \begin{equation}
-f_\ell(\tau) = \int_{0}^\infty \int_{0}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) d x_0 d\sigma
+\begin{aligned}
+b_\ell(\tau) &\propto j(\ell) f_{\ell}(\tau)\\
+&\propto \int_0^\infty i(\ell-x_0) k(x_0) f_{\ell}(\tau) \mathrm{d} x_0
+\end{aligned}
 \end{equation}
+where $j$ is the incidence of symptomatic cases.
+
+\subsection{Serial link between $r$ and $\mathcal R$}
+
+Here, we show that the forward serial-interval distribution during the exponential growth phase provides the correct link between the exponential growth rate $r$ of an epidemic.
+This link is identical to the $r$--$\mathcal R$ link based on the generation-interval distribution.
+During the exponential growth phase, we have 
+\begin{equation}
+f_{\tiny\textrm{exp}}(\tau) \propto \int_{0}^\infty \int_{0}^\infty \exp( -r x_0) h(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma
+\end{equation}
+
+\section{Results}
+
+\section{Appendix}
+
+Recall that the forward serial interval can be written as:
+\begin{equation}
+- x_0 + \sigma + x_1
+\end{equation}
+Note that $x_1$ is independent of $x_0$ and $\sigma$. Then, we get:
+\begin{equation}
+M_{- x_0 + \sigma + x_1}(-r) = M_{- x_0 + \sigma}(-r) M_{x_1}(-r).
+\end{equation}
+We want to show that 
+\begin{equation}
+M_{- x_0 + \sigma}(-r)= \frac{M_\sigma(-r)}{M_{x_1}(-r)}
+\end{equation}
+for $r \geq 0$.
+Note that the time between symptom onset and infection of an infectee follows the following distribution:
+\begin{equation}
+z(\tau) \propto \int_{\max(0, -\tau)}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \tau+x_0) \mathrm{d} x_0.
+\end{equation}
+During the exponential growth phase, we have
+\begin{equation}
+\begin{aligned}
+z_{\tiny\textrm{exp}}(\tau) &= \frac{1}{N} \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\\
+% &= \frac{1}{N} \int_{0}^\infty \left[ \exp(- r x_0) k(x_0) \times \frac{h(x_0, \tau+x_0)}{k(x_0)}\right] \mathrm{d} x_0
+\end{aligned}
+\end{equation}
+where $N$ is the normalization factor:
+\begin{equation}
+\begin{aligned}
+N &= \int_{-\infty}^\infty \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\,\mathrm{d}\tau\\
+&= \int_{0}^\infty \int_{-x_0}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d}\tau\,\mathrm{d} x_0\\
+&= \int_{0}^\infty \exp(- r x_0) k(x_0) dx_0\\
+&= M_{x_1}(-r)
+\end{aligned}
+\end{equation}
+Therefore,
+\begin{equation}
+\begin{aligned}
+&\int_{-\infty}^{\infty} \exp(-r\tau) z_{\tiny\textrm{exp}}(\tau) \mathrm{d}\tau\\
+&=\frac{1}{M_{-x_1}(-r)} \int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\, \mathrm{d}\tau
+\end{aligned}
+\end{equation}
+
+Finally, we are left to prove that 
+\begin{equation}
+\int_0^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau = \int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\, \mathrm{d}\tau
+\end{equation}
+where $g$ is a marginal probability distribution of $h$ describing the forward generation intervals:
+\begin{equation}
+g(\tau) = \int_0^\infty h(x_0, \tau)  \mathrm{d} x_0.
+\end{equation}
+Let $a = x_0 + \tau$. Then, by change of variables, it immediately follows that
+\begin{equation}
+\begin{aligned}
+&\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\, \mathrm{d}\tau\\
+&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r a) h(x_0, a) \mathrm{d} x_0\, \mathrm{d}a\\
+&=\int_{0}^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau
+\end{aligned}
+\end{equation}
+Therefore, the forward serial- and generation-interval distributions give the same link between $r$ and $\mathcal R$.
 

### 2020-04-11 serial.tex
making progress

@@
 
-In order to model serial intervals, we first explain the differences between backward and forward delays.
-To do so, we divide epidemiological events as \emph{primary} and \emph{secondary} events.
-When we measure a within-individual delay, we define primary and secondary events based on their timing;
-the primary event always occurs before the secondary event.
-When we measure between-individual delays, we define primary and secondary events based on whether they occurred within an infector or an infectee, respectively;
-the primary event does not necessarily occur before the secondary event.
+We first begin by describing a general framework for characterizing a distribution of time delays between \emph{any} two epidemiological events;
+these events can be defined either within an infected individual (e.g., infection and symptom onset of an individual) or between infected individuals (e.g., symptom onsets of an infector and an infectee).
+Then, we can further divide these events into \emph{primary} and \emph{secondary} events.
+When we measure an epidemiological time delay within an infected individual (e.g., time between infection and symptom onset), the primary event always occurs before the secondary event.
+When we measure an epidemiological time delay between infected individuals (e.g., serial interval), 
+the primary and secondary events are defined in terms of the direction of transmission:
+The primary event refers to the event that occurs within an infector and does not necessarily occur before the secondary event.
 
@@
 For example, when we are measurign serial intervals, a primary cohort $s$ consists of all infectors who became symptomatic at time $s$.
-Then, for each primary cohort $s$, we can define the expected time distribution between primary and secondary events for primary cohort $s$.
+Then, for each primary cohort $s$, we can define the expected time distribution between primary and secondary events.
 We refer to this distribution as the forward delay distribution and denote it as $f_s(\tau)$.
@@
 \begin{equation}
-b_s(\tau) \propto i(s-\tau) f_{s-\tau}(\tau)
+b_s(\tau) \propto C(s-\tau) f_{s-\tau}(\tau)
 \end{equation}
-where $i(s)$ is the size of the primary cohort $s$.
-Therefore, changes in the backward delay distribution depends on the changes in cohort size $i(s)$ (therefore incidence of infection) as well as changes in the forward delay distribution.
-This concept generalizes the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
+where $C(s)$ is the size of the primary cohort $s$.
+Therefore, changes in the backward delay distribution depends on the changes in cohort size $C(s)$ (therefore incidence of infection) as well as changes in the forward delay distribution.
+These ideas apply to all epidemiological delay distributions and generalize the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
 
-\subsection{Serial interval distributions}
+\subsection{Realized serial interval distributions}
 
 The serial interval is defined as the time between when an infector becomes symptomatic and when and infectee becomes symptomatic.
-We express realized serial intervals as:
+Here, we denote realized serial intervals $\tau$ as:
 \begin{equation}
-- x_0 + \sigma + x_1
+\tau = - x_0 + \sigma + x_1
 \end{equation}
 where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\sigma$ represents the realized generation interval.
-Previous studies have assumed that (i) $x_0$ and $x_1$ have the same mean and (ii) therefore the serial and generation intervals have the same mean;
+Previous studies have assumed that (i) $x_0$ and $x_1$ have the same means and (ii) therefore the serial and generation intervals have the same mean;
 however, these results implicitly assume that incidence stays constant.
@@
 Given that an infector became symptomatic at time $\ell$, we have to first go backward in time by asking when the infector was infected and go forward in time by asking when the infectee became symptomatic.
-Then, it is clear that $x_0$ should follow the backward incubation period distribution for secondary cohort $\ell$; 
-$\sigma$ the forward generation-interval distribution for a primary cohort $\ell - x_0$ conditional on the realized incubation period $x_0$;
-and $s_1$ forward incubation period distribution for a primary cohort $\ell - x_0 + \sigma$.
+Then, it is clear that $x_0$ follows the backward incubation period distribution for secondary cohort $\ell$; 
+$\sigma$ follows the forward generation-interval distribution for a primary cohort $\ell - x_0$ conditional on the incubation period  $x_0$ of the infector;
+and $x_1$ follows forward incubation period distribution for a primary cohort $\ell - x_0 + \sigma$.
 Assuming that the forward incubation distribution does not vary across cohorts, the forward serial interval distribution of a primary cohort $\ell$ can be written as follows:
@@
 where $i$ is the incidence of infection, $h$ is the joint probability distribution of the incubation period and generation interval of a primary cohort $\ell - x_0$, and $k$ is a marginal probability distribution of $h$ describing the forward incubation periods.
+Therefore, the forward serial interval distribution depends on previous changes in incidence and generally have different means from the generation interval distribution.
 
 Likewise, we can define backward serial interval distribution for a secondary cohort $\ell$.
-Given that an infectee became symptomatic at time $\ell$, we have to first go backward in time by asking when the infectee became infected and when the infectee was infected by the infector; 
+Given that an infectee became symptomatic at time $\ell$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
 then, we have to go forward in time by asking when the infector became symptomatic.
@@
 \end{equation}
-where $j$ is the incidence of symptomatic cases.
+where $j$ represents the incidence of symptomatic cases.
 
-\subsection{Serial link between $r$ and $\mathcal R$}
+\subsection{Observed serial interval distributions}
 
-Here, we show that the forward serial-interval distribution during the exponential growth phase provides the correct link between the exponential growth rate $r$ of an epidemic.
-This link is identical to the $r$--$\mathcal R$ link based on the generation-interval distribution.
-During the exponential growth phase, we have 
+\subsection{Relating $\mathcal R$ and $r$ using generation and serial-interval distributions}
+
+Assuming that the forward generation-interval distribution remains constant during the exponential growth phase,
+we can estimate the reproduction number from the exponential growth rate $r$ via the Euler-Lotka equation:
 \begin{equation}
-f_{\tiny\textrm{exp}}(\tau) \propto \int_{0}^\infty \int_{0}^\infty \exp( -r x_0) h(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma
+\frac{1}{\mathcal R} = \int_0^\infty \exp(-r\tau) g(\tau) \mathrm{d} \tau,
 \end{equation}
+where $g(\tau)$ is the forward generation-interval distribution during the exponential growth phase (and also a marginal probability distribution of $h$).
+Like the forward generation-interval distribution, 
+the forward serial-interval distribution describes the renewal process of symptomatic cases.
+Therefore, the forward serial-interval distribution $f_{\tiny\textrm{exp}}(\tau)$ during the exponential growth phase should provide the identical $r$--$\mathcal R$ link as the generation-interval distribution:
+\begin{equation}
+\frac{1}{\mathcal R} = \int_{-\infty}^\infty \exp(-r\tau) f_{\tiny\textrm{exp}}(\tau) \mathrm{d} \tau,
+\end{equation}
+where the forward serial-interval distribution during the exponential growth phase is defined as:
+\begin{equation}
+f_{\tiny\textrm{exp}}(\tau) \propto \int_{0}^\infty \int_{0}^\infty \exp( -r x_0) h(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma.
+\end{equation}
+In Appendix, we provide a mathematical proof that this relationship holds.
+
+We note that the forward serial-interval distribution depends on the exponential growth rate $r$.
+When the epidemic grows fast (high $r$), we expect the backward incubation period to be short, and therefore, the forward serial-interval distribution will generally have a longer mean than the forward generation-interval distribution.
+The Susceptible-Exposed-Infected-Recovered model, which assumes that incubation and exposed periods are equivalent, is a special case where the conditional forward generation-interval distribution cancels out with the backward generation-interval distribution exactly because (i) infected individuals can only transmit after symptom onset and (ii) the incubation period distribution is independent of the time between symptom onset to infection;
+in this case, the forward serial- and generation-interval distributions follow identical distributions.
 

### 2020-04-12 serial.tex
writing is hard

@@
 We refer to this distribution as the forward delay distribution and denote it as $f_s(\tau)$.
-We assume that forward delay distributions can vary across primary cohorts.
+The forward delay distributions can vary across primary cohorts.
 
@@
 \end{equation}
-where $i$ is the incidence of infection, $h$ is the joint probability distribution of the incubation period and generation interval of a primary cohort $\ell - x_0$, and $k$ is a marginal probability distribution of $h$ describing the forward incubation periods.
-Therefore, the forward serial interval distribution depends on previous changes in incidence and generally have different means from the generation interval distribution.
+where $i$ is the incidence of infection, $h$ is the joint probability distribution of the forward incubation period and forward generation interval of a primary cohort $\ell - x_0$, and $k$ is a marginal probability distribution of $h$ describing the forward incubation periods:
+\begin{equation}
+k(x_0) = \int_0^\infty h_\ell(x_0, \sigma) \mathrm{d}\sigma.
+\end{equation}
+Here, we assume that the forward incubation period distribution does not vary across cohorts over the course of an epidemic as it represents an intrinsic property of the natrual history of a disease.
+% Therefore, the forward serial interval distribution depends on previous changes in incidence and generally have different means from the forward generation interval distribution.
 
@@
 
-\subsection{Observed serial interval distributions}
+\subsection{Epidemic model}
 
-\subsection{Relating $\mathcal R$ and $r$ using generation and serial-interval distributions}
+Here, use a renewal equation to model the spread of disease in a population:
+\begin{equation}
+i(t) = \mathcal R_0 S(t) \int_0^\infty i(t-\tau) g(\tau) \mathrm{d}\tau,
+\end{equation}
+where $\mathcal R_0$ is the basic reproduction number (i.e., the average number of secondary cases caused by a primary case  in a fully susceptible population), $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population), $S(t)$ is the proportion of susceptible individuals.
+Then, the forward generation-interval for a primary cohort $\ell$ follows \citep{champredon2015intrinsic}:
+\begin{equation}
+g_\ell (\tau) \propto g(\tau) S(\ell + \tau),
+\end{equation}
+which allows us to separate the joint probability distribution $h_\ell$ of the forward incubation period and the forward generation-interval distribution as a product of joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals and the proportion of susceptible individuals $S$:
+\begin{equation}
+h_\ell (x_0, \tau) \propto h(x_0, \tau) S(\ell + \tau),
+\end{equation}
+which satisfies the following:
+\begin{equation}
+g(\tau) = \int_0^\infty h(x_0, \tau) \mathrm{d}x_0.
+\end{equation}
 
-Assuming that the forward generation-interval distribution remains constant during the exponential growth phase,
-we can estimate the reproduction number from the exponential growth rate $r$ via the Euler-Lotka equation:
+During the initial phase of an epidemic, the proprotion susceptible remains constant ($S(t) = S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
+Then, we can estimate the reproduction number from the exponential growth rate $r$ via the Euler-Lotka equation:
 \begin{equation}
-\frac{1}{\mathcal R} = \int_0^\infty \exp(-r\tau) g(\tau) \mathrm{d} \tau,
+\frac{1}{\mathcal R} = \int_0^\infty \exp(-r\tau) g(\tau) \mathrm{d} \tau.
 \end{equation}
-where $g(\tau)$ is the forward generation-interval distribution during the exponential growth phase (and also a marginal probability distribution of $h$).
-Like the forward generation-interval distribution, 
-the forward serial-interval distribution describes the renewal process of symptomatic cases.
-Therefore, the forward serial-interval distribution $f_{\tiny\textrm{exp}}(\tau)$ during the exponential growth phase should provide the identical $r$--$\mathcal R$ link as the generation-interval distribution:
+Like forward generation-interval distributions, 
+forward serial-interval distributions describe the renewal process of symptomatic cases.
+Therefore, the forward serial-interval distribution $f_{\tiny\textrm{exp}}(\tau)$ during the exponential growth phase provides the identical $r$--$\mathcal R$ link as the intrinsic generation-interval distribution:
 \begin{equation}
@@
 We note that the forward serial-interval distribution depends on the exponential growth rate $r$.
-When the epidemic grows fast (high $r$), we expect the backward incubation period to be short, and therefore, the forward serial-interval distribution will generally have a longer mean than the forward generation-interval distribution.
-The Susceptible-Exposed-Infected-Recovered model, which assumes that incubation and exposed periods are equivalent, is a special case where the conditional forward generation-interval distribution cancels out with the backward generation-interval distribution exactly because (i) infected individuals can only transmit after symptom onset and (ii) the incubation period distribution is independent of the time between symptom onset to infection;
-in this case, the forward serial- and generation-interval distributions follow identical distributions.
+When the epidemic grows fast (high $r$), we expect the backward incubation period to be short, and therefore, the forward serial-interval distribution will generally have a larger mean than the forward generation-interval distribution.
+The Susceptible-Exposed-Infected-Recovered model, which assumes that incubation and exposed periods are equivalent, is a special case where the conditional forward generation-interval distribution cancels out with the backward generation-interval distribution exactly because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector;
+in this case, the forward serial- and generation-intervals have the same distributions during the exponential growth phase.
 
 \section{Results}
+
+\begin{figure}[!ht]
+\includegraphics[width=\textwidth]{forward.pdf}
+\caption{
+\textbf{Epidemiological dynamics and changes in mean forward and backward delay distributions.}
+}
+\label{fig:epi}
+\end{figure}
+
+\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions.
+The mean forward incubation period remains constant throughout an epidemic as expected (\fref{epi}B).
+The mean forward generation interval contracts as epidemic progresses because an infected individual is less likely to infect another person as the proportion of susceptible individuals decreases (\fref{epi}C; \cite{champredon2015intrinsic}).
+In contrast to mean forward incubation period or generation interval, the mean serial interval depends on previous incidence and therefore decreases over time (\fref{epi}D):
+When incidence is increasing, a symptomatic individual is more likely to have been infected more recently (shorter backward incubation period and therefore longer forward serial interval) whereas when incidence is decreasing, a symptomatic individual is more likely to have been infected later (longer backward incubation period and therefore shorter forward serial interval).
+Qualitative patterns in the changes in the mean backward delays is robust across all delay distributions because they are largely driven by changes in incidence (\fref{epi}D).
+
+\begin{figure}[!ht]
+\includegraphics[width=\textwidth]{rR.pdf}
+\caption{
+\textbf{Estimating of the reproduction number from the exponential growth rate.}
+}
+\label{fig:rR}
+\end{figure}
+
+\fref{rR} compares the estimates of the reproduction number $\mathcal R$ using forward serial-interval distributions and naive serial-interval distributions that does not account for the differences between backward and forward incubation periods.
+When we use the forward serial-interval distributions to estimate $\mathcal R$, we obtain identical values regardless of the correlation between incubation periods and generation intervals;
+as expected, these estimates match $\mathcal R$ estimes using the intrinsic generation-interval distributions (\fref{rR}A).
+On the other hand, when naive serial-interval distributions are used, we underestimate $\mathcal R$ (\fref{rR}B); $\mathcal R$ even decreases for high $r$ because negative serial intervals are given too much weight.
 

### 2020-04-12 serial.tex
new fig

@@
 
+\subsection{Linking $r$ and $\mathcal R$}
+
 During the initial phase of an epidemic, the proprotion susceptible remains constant ($S(t) = S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
@@
 \caption{
-\textbf{Estimating of the reproduction number from the exponential growth rate.}
+\textbf{Estimates of the reproduction number from the exponential growth rate.}
 }
@@
 
-\fref{rR} compares the estimates of the reproduction number $\mathcal R$ using forward serial-interval distributions and naive serial-interval distributions that does not account for the differences between backward and forward incubation periods.
+\fref{rR} compares the estimates of the reproduction number $\mathcal R$ from the exponential growth rate $r$ using forward serial-interval distributions and naive serial-interval distributions that do not account for the differences between backward and forward incubation periods.
 When we use the forward serial-interval distributions to estimate $\mathcal R$, we obtain identical values regardless of the correlation between incubation periods and generation intervals;
 as expected, these estimates match $\mathcal R$ estimes using the intrinsic generation-interval distributions (\fref{rR}A).
-On the other hand, when naive serial-interval distributions are used, we underestimate $\mathcal R$ (\fref{rR}B); $\mathcal R$ even decreases for high $r$ because negative serial intervals are given too much weight.
+On the other hand, when naive serial-interval distributions are used, we underestimate $\mathcal R$; $\mathcal R$ even decreases for high $r$ because negative serial intervals are given too much weight (\fref{rR}B).
+While the forward serial intervals can be also negative, the proportion of negative intervals are appropriately balances because faster epidemic growth will lead to shorter backward incubation period (and therefore less negative serial intervals).
 
-\section{Appendix}
+Comapring the shapes of forward serial-interval distributions and the intrinsic generation-interval distribution allow us to better understand how they are able to give identical estimates of $\mathcal R$.
+Generation-interval distributions with higher means and less variability are generally expected to give higher $\mathcal R$ for a given $r$.
+Here, we find that the forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
+The effects of higher means (which increases $\mathcal R$) and higher variability (which decreases $\mathcal R$) cancel out exactly;
+therefore, the estimates of $\mathcal R$ remain unchanged.
+
+\begin{figure}[!ht]
+\includegraphics[width=\textwidth]{observedrR.pdf}
+\caption{
+\textbf{Estimates of the reproduction number from the observed serial intervals.}
+}
+\label{fig:obsrR}
+\end{figure}
+
+When the epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms.
+\fref{obsrR} demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of $\mathcal R$.
+However, even if we can observe \emph{all} serial intervals after the epidemic has ended, we still underestimate $\mathcal R$ by a large amount because it does not account for changes in the forward serial-interval distribution.
+As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean forward serial-interval distribution during the exponential growth phase, which provides the correct linke between $r$ and $\mathcal R$.
+
+Here, we provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ retrospctively.
+Instead of taking the average
+
+\section{Discussion}
+
+\section*{Appendix}
 

### 2020-04-12 observedrR.R

@@ -1,0 +1,89 @@
+library(tidyr)
+library(dplyr)
+library(ggplot2); theme_set(theme_bw())
+library(gridExtra)
+library(tikzDevice)
+source("renewal_det.R")
+source("cpalette.R")
+
+nboot <- 200
+
+load("sir_sim.rda")
+
+rr <- renewal_det()
+r <- rr$r
+
+tcut <- seq(10, 80, by=2)
+
+serdata0 <- data_frame(
+  cohort=sir_sim$t_symptomatic[sir_sim$infected_by],
+  tdiff=sir_sim$t_symptomatic-sir_sim$t_symptomatic[sir_sim$infected_by],
+  tobs=cohort+tdiff
+)
+
+R0_obs <- lapply(tcut, function(x) {
+  set.seed(123)
+  tmp <- serdata0 %>%
+    filter(tobs < x)
+  
+  R0samp <- replicate(nboot, {
+    ss <- tmp$tdiff
+    ss <- sample(ss, replace=TRUE)
+    1/mean(exp(-r*ss), na.rm=TRUE)
+  })
+  
+  data.frame(
+    t=x,
+    R0=1/mean(exp(-r*tmp$tdiff), na.rm=TRUE),
+    lwr=quantile(R0samp, 0.025),
+    upr=quantile(R0samp, 0.975)
+  )
+}) %>%
+  bind_rows %>%
+  mutate(
+    type="Observed"
+  )
+
+R0_cohort <- lapply(tcut, function(x) {
+  set.seed(123)
+  tmp <- serdata0 %>%
+    filter(cohort < x)
+  
+  R0samp <- replicate(nboot, {
+    ss <- tmp$tdiff
+    ss <- sample(ss, replace=TRUE)
+    1/mean(exp(-r*ss), na.rm=TRUE)
+  })
+  
+  data.frame(
+    t=x,
+    R0=1/mean(exp(-r*tmp$tdiff), na.rm=TRUE),
+    lwr=quantile(R0samp, 0.025),
+    upr=quantile(R0samp, 0.975)
+  )
+}) %>%
+  bind_rows  %>%
+  mutate(
+    type="Cohort-averaged"
+  )
+
+R0all <- bind_rows(R0_obs, R0_cohort)
+
+g1 <- ggplot(R0all) +
+  geom_ribbon(aes(t, ymin=lwr, ymax=upr, fill=type, lty=type, col=type), alpha=0.5) +
+  geom_line(aes(t, R0, col=type, lty=type)) +
[…]

### 2020-04-12 serial.tex
tweak

@@
 
-When the epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms.
+When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms.
 \fref{obsrR} demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of $\mathcal R$.
@@
 Here, we provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ retrospctively.
-Instead of taking the average
+Once a set of serial intervals has been observed from the line list, we can group observed serial intervals by their primary cohort times.
+Then, we can compare how estimates of $\mathcal R$ change as we include more cohorts into the analysis (see `cohort-averaged' in \fref{obsrR}).
+During the exponential growth phase, the estimates of $\mathcal R$ remains consistent;
+adding more data allows us to make more precise inference about $\mathcal R$ during this period.
+However, the cohort-averaged estimates of $\mathcal R$ decreases rapidly soon after the exponential growth period.
+Confidence intervals associated with the cohort-averaged estimates of $\mathcal R$ becomes narrower and do not overlap with earlier estimates.
+This approach allows us to visualize how changes in the forward serial intervals translate to biases in estimates of $\mathcal R$.
 

### 2020-04-12 observedrR.R

@@ -74,7 +74,7 @@ g1 <- ggplot(R0all) +
   geom_line(aes(t, R0, col=type, lty=type)) +
   geom_hline(yintercept=rr$R0, lty=2) +
   scale_x_continuous("Time (days)", limits=c(0, 80), expand=c(0, 0)) +
-  scale_y_continuous("Reproduction number $\\mathcal R$", limits=c(1, 3), expand=c(0, 0)) +
+  scale_y_continuous("Reproduction number $\\mathcal R$", expand=c(0, 0)) +
   scale_color_manual(values=tail(cpalette, 2)) +
   scale_fill_manual(values=tail(cpalette, 2)) +
   theme(

### 2020-04-13 serial.tex
we
reorder

@@
 
+First, we compare the estimates of the reproduction number $\mathcal R$ based on the intrinsic generation-interval distribution and the forward serial-interval distribution during the exponential growth phase (\fref{rR}A).
+Both distributions provide identical estimates of $\mathcal R$ regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution.
+On the other hand, using naive serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates $\mathcal R$;
+as $r$ increases, estimates of $\mathcal R$ eventually saturate and decrease because negative serial intervals are given too much weight (\fref{rR}B)
+While the forward serial intervals during the exponential growth phase can be also negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation period (and therefore less negative serial intervals).
+
+\begin{figure}[!ht]
+\includegraphics[width=\textwidth]{rR.pdf}
+\caption{
+\textbf{Estimates of the reproduction number from the exponential growth rate.}
+}
+\label{fig:rR}
+\end{figure}
+
+Comapring the shapes of forward serial-interval distributions and the intrinsic generation-interval distribution allow us to better understand how they are able to give identical estimates of $\mathcal R$.
+Generation-interval distributions with higher means and less variability are generally expected to give higher $\mathcal R$ for a given $r$.
+Here, we find that the forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
+The effects of higher means (which increases $\mathcal R$) and higher variability (which decreases $\mathcal R$) cancel out exactly;
+therefore, the estimates of $\mathcal R$ remain unchanged.
+
 \begin{figure}[!ht]
@@
 \begin{figure}[!ht]
-\includegraphics[width=\textwidth]{rR.pdf}
-\caption{
-\textbf{Estimates of the reproduction number from the exponential growth rate.}
-}
-\label{fig:rR}
-\end{figure}
-
-\fref{rR} compares the estimates of the reproduction number $\mathcal R$ from the exponential growth rate $r$ using forward serial-interval distributions and naive serial-interval distributions that do not account for the differences between backward and forward incubation periods.
-When we use the forward serial-interval distributions to estimate $\mathcal R$, we obtain identical values regardless of the correlation between incubation periods and generation intervals;
-as expected, these estimates match $\mathcal R$ estimes using the intrinsic generation-interval distributions (\fref{rR}A).
-On the other hand, when naive serial-interval distributions are used, we underestimate $\mathcal R$; $\mathcal R$ even decreases for high $r$ because negative serial intervals are given too much weight (\fref{rR}B).
-While the forward serial intervals can be also negative, the proportion of negative intervals are appropriately balances because faster epidemic growth will lead to shorter backward incubation period (and therefore less negative serial intervals).
-
-Comapring the shapes of forward serial-interval distributions and the intrinsic generation-interval distribution allow us to better understand how they are able to give identical estimates of $\mathcal R$.
-Generation-interval distributions with higher means and less variability are generally expected to give higher $\mathcal R$ for a given $r$.
-Here, we find that the forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
-The effects of higher means (which increases $\mathcal R$) and higher variability (which decreases $\mathcal R$) cancel out exactly;
-therefore, the estimates of $\mathcal R$ remain unchanged.
-
-\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{observedrR.pdf}
@@
 
-Here, we provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ retrospctively.
+We provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ retrospctively.
 Once a set of serial intervals has been observed from the line list, we can group observed serial intervals by their primary cohort times.
@@
 This approach allows us to visualize how changes in the forward serial intervals translate to biases in estimates of $\mathcal R$.
+
+Finally, we apply these ideas and reanalyze serial intervals of COVID-19 collected from mainland China, outside Hubei province, between XXX and XXX (REF).
 

### 2020-04-13 serial.tex
more to unpack

@@
 Generation-interval distributions with higher means and less variability are generally expected to give higher $\mathcal R$ for a given $r$.
-Here, we find that the forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
+The forward serial intervals during the exponential growth phase have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
 The effects of higher means (which increases $\mathcal R$) and higher variability (which decreases $\mathcal R$) cancel out exactly;
@@
 The mean forward generation interval contracts as epidemic progresses because an infected individual is less likely to infect another person as the proportion of susceptible individuals decreases (\fref{epi}C; \cite{champredon2015intrinsic}).
-In contrast to mean forward incubation period or generation interval, the mean serial interval depends on previous incidence and therefore decreases over time (\fref{epi}D):
-When incidence is increasing, a symptomatic individual is more likely to have been infected more recently (shorter backward incubation period and therefore longer forward serial interval) whereas when incidence is decreasing, a symptomatic individual is more likely to have been infected later (longer backward incubation period and therefore shorter forward serial interval).
-Qualitative patterns in the changes in the mean backward delays is robust across all delay distributions because they are largely driven by changes in incidence (\fref{epi}D).
+In contrast, the mean serial interval depends on previous incidence and therefore decreases over time (\fref{epi}D):
+When incidence is increasing, symptomatic individuals are more likely to have been infected more recently (shorter backward incubation period and therefore longer forward serial interval) whereas when incidence is decreasing, symptomatic individuals are more likely to have been infected later (longer backward incubation period and therefore shorter forward serial interval).
+Qualitative patterns in the changes in the mean backward delays is robust across all delay distributions because they are predominantly driven by the changes in incidence (\fref{epi}D).
 
@@
 \fref{obsrR} demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of $\mathcal R$.
-However, even if we can observe \emph{all} serial intervals after the epidemic has ended, we still underestimate $\mathcal R$ by a large amount because it does not account for changes in the forward serial-interval distribution.
+Notably, even if we can observe \emph{all} serial intervals after the epidemic has ended, we still underestimate $\mathcal R$ by a large amount because the observed serial-interval distribution does not account for changes in the forward serial-interval distribution.
 As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean forward serial-interval distribution during the exponential growth phase, which provides the correct linke between $r$ and $\mathcal R$.
@@
 We provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ retrospctively.
-Once a set of serial intervals has been observed from the line list, we can group observed serial intervals by their primary cohort times.
+Once a set of serial intervals has been observed, we can group observed serial intervals by their primary cohort times.
 Then, we can compare how estimates of $\mathcal R$ change as we include more cohorts into the analysis (see `cohort-averaged' in \fref{obsrR}).
-During the exponential growth phase, the estimates of $\mathcal R$ remains consistent;
+During the exponential growth phase, the estimates of $\mathcal R$ are consistent with the true value;
 adding more data allows us to make more precise inference about $\mathcal R$ during this period.
@@
 Confidence intervals associated with the cohort-averaged estimates of $\mathcal R$ becomes narrower and do not overlap with earlier estimates.
-This approach allows us to visualize how changes in the forward serial intervals translate to biases in estimates of $\mathcal R$.
+This approach allows us to detect how changes in the forward serial intervals bias the estimates of $\mathcal R$.
 
-Finally, we apply these ideas and reanalyze serial intervals of COVID-19 collected from mainland China, outside Hubei province, between XXX and XXX (REF).
+\begin{figure}
+\includegraphics[width=\textwidth]{serial_analysis.pdf}
+\caption{
+\textbf{Observed serial intervals of COVID-19 and estimates of $\mathcal R$.}
+}
+\label{fig:du}
+\end{figure}
+
+Finally, we revisit serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on transmission events reported between January 21--February 8, 2020;
+they estimated the mean serial of 3.96 days (95\% CI 3.53–4.39 days) and $\mathcal R_0$ of 1.32 (95\% CI 1.16–1.48).
+\fref{du}A shows changes in the forward serial-interval distribution across cohorts.
+While the observed serial intervals may be subject to right-censoring, increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution.
+\fref{du}B shows the cohort-averaged estimates of $\mathcal R_0$, which remain constant until day 7 and suddenly decreases.
+The early cohort-averaged estimates are also consistent with earlier estimates.
+This example clearly demonstrates the danger of naively averaging the observed serial intervals and calculating the reproduction number from them.
 

### 2020-04-13 serial.tex
novel

@@
 
-Here, we provide an answer to the decade-old paradox.
-We provide a new framework for understanding serial intervals and show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.
+Here, we provide an answer to this decade-old paradox.
+We develop a novel framework for understanding serial intervals and show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.
 

### 2020-04-13 serial.tex
intro

@@
 % Despite having similar definitions, generation and serial intervals are different because serial intervals rely on the generation intervals as well as the incubation periods of an infector and an infectee.
-Previous studies have often alluded to differences in their variances, despite having identical expected values, and noted that using serial-interval distribution can give different estimates of $\mathcal R$.
+Previous studies have often alluded to differences in their variances, despite having seemingly identical expected values, and noted that using serial-interval distribution can give different estimates of $\mathcal R$.
 Even though these distinctions were first made over a decade ago \citep{svensson2007note}, 
@@
 Therefore, both generation- and serial-interval distributions should give us identical estimates of  $\mathcal R$ based the observed epidemic growth rate.
-Current theory seems to contradict our biological intution.
+Current theory suggests that using generation- and serial-interval distributions give different estimates of $\mathcal R$ and contradicts our biological intution.
 

### 2020-04-13 serial.tex
intro

@@
 Here, we provide an answer to this decade-old paradox.
-We develop a novel framework for understanding serial intervals and show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.
+We develop a novel framework for understanding serial intervals and show that the serial-interval distribution must be defined with reference to disease incidence;
+previous frameworks implicitly assume that incidence remains constant.
+Using our framework, we are able to show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.
+However, failing to account for changes in the serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
+We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using serial intervals in the analysis of the ongoing pandemic.
 

### 2020-04-13 serial.tex
tweak

@@
 However, failing to account for changes in the serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
-We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using serial intervals in the analysis of the ongoing pandemic.
+We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of the ongoing pandemic.
 

### 2020-04-14 serial.tex
more progress

@@
 
+We use a simulation-based approach to compare the estimates of $\mathcal R$ based on the serial- and generation-interval distributions. 
+To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and correlation $\rho$.
+The multivariate log-normal distribution is parameterized based on pameter estimates for COVID-19.
+We construct the forward serial-interval distribution during the exponential growth period as follows:
+\begin{equation}
+S_i = -B_i + (G_i|B_i) + I_i,
+\end{equation}
+where the backward incubation period $B_i$ of an infector is simulated by drawing random log-normal samples $A_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $A_i$, each weighted by the inverse of the exponential growth function $\exp(-rA_i)$;
+the intrinsic generation interval conditional on the incubation period of the infector $(G_i|B_i)$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(B_i) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
+the forward incubation period $I_i$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
+We then calculate the reproduction number $\mathcal R$ using the empirical estimator:
+\begin{equation}
+\mathcal R = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r S_i)}.
+\end{equation}
+We compare this estimate with a naive estimate of $\mathcal R$ that assumes that the backward and the forward incubation periods are identically distributed:
+\begin{equation}
+\mathcal R = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r T_i)},
+\end{equation}
+where
+\begin{equation}
+T_i = -A_i + (G_i|A_i) + I_i.
+\end{equation}
+
 \section{Results}

### 2020-04-14 serial.tex
a bit more

@@
 
-Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its reproduction number $\mathcal R$.
-The reproduction number, which is defined as the average number of secondary cases caused by a primary case, allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak.
+Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its basic reproduction number $\mathcal R_0$ \citep{majumder2020early}.
+The basic reproduction number, which is defined as the average number of secondary cases caused by a primary case in a fully susceptible population, allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
 Since the reproduction number cannot be measured directly, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions.
 
-The generation interval is defined as the time between when an individual (infector) is infected and when an individual infects another person (infectee).
+The generation interval is defined as the time between when an individual (infector) is infected and when an individual infects another person (infectee);
+the generation-interval distributions plays a key role in shaping the relationship between the exponential growth rate $r$ and the reproduction number $\mathcal R$.
 On the other hand, the serial interval is defined as the time between when an infector and an infectee become symptomatic.
-% Despite having similar definitions, generation and serial intervals are different because serial intervals rely on the generation intervals as well as the incubation periods of an infector and an infectee.
 Previous studies have often alluded to differences in their variances, despite having seemingly identical expected values, and noted that using serial-interval distribution can give different estimates of $\mathcal R$.
@@
 forward serial-interval distributions describe the renewal process of symptomatic cases.
-Therefore, the forward serial-interval distribution $f_{\tiny\textrm{exp}}(\tau)$ during the exponential growth phase provides the identical $r$--$\mathcal R$ link as the intrinsic generation-interval distribution:
+Therefore, the forward serial-interval distribution $f_{\textrm{\tiny exp}}(\tau)$ during the exponential growth phase provides the identical $r$--$\mathcal R$ link as the intrinsic generation-interval distribution:
 \begin{equation}
-\frac{1}{\mathcal R} = \int_{-\infty}^\infty \exp(-r\tau) f_{\tiny\textrm{exp}}(\tau) \mathrm{d} \tau,
+\frac{1}{\mathcal R} = \int_{-\infty}^\infty \exp(-r\tau) f_{\textrm{\tiny exp}}(\tau) \mathrm{d} \tau,
 \end{equation}
@@
 \begin{equation}
-f_{\tiny\textrm{exp}}(\tau) \propto \int_{0}^\infty \int_{0}^\infty \exp( -r x_0) h(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma.
+f_{\textrm{\tiny exp}}(\tau) \propto \int_{0}^\infty \int_{0}^\infty \exp( -r x_0) h(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma.
 \end{equation}
@@
 \begin{equation}
-\mathcal R = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r T_i)},
+{\mathcal R}_{\textrm{\tiny naive}} = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r T_i)},
 \end{equation}
@@
 \begin{aligned}
-z_{\tiny\textrm{exp}}(\tau) &= \frac{1}{N} \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\\
+z_{\textrm{\tiny exp}}(\tau) &= \frac{1}{N} \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\\
 % &= \frac{1}{N} \int_{0}^\infty \left[ \exp(- r x_0) k(x_0) \times \frac{h(x_0, \tau+x_0)}{k(x_0)}\right] \mathrm{d} x_0
@@
 \begin{aligned}
-&\int_{-\infty}^{\infty} \exp(-r\tau) z_{\tiny\textrm{exp}}(\tau) \mathrm{d}\tau\\
+&\int_{-\infty}^{\infty} \exp(-r\tau) z_{\textrm{\tiny exp}}(\tau) \mathrm{d}\tau\\
 &=\frac{1}{M_{-x_1}(-r)} \int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\, \mathrm{d}\tau

### 2020-04-14 serial.tex
tweak

@@
 
-Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its basic reproduction number $\mathcal R_0$ \citep{majumder2020early}.
-The basic reproduction number, which is defined as the average number of secondary cases caused by a primary case in a fully susceptible population, allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
+Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its reproduction number $\mathcal R$ \citep{majumder2020early}.
+The reproduction number is defined as the average number of secondary cases caused by a primary case;
+the corresponding reproduction number in a fully susceptible population --- referred to as the basic reproduction number $\mathcal R_0$ --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
 Since the reproduction number cannot be measured directly, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions.

### 2020-04-14 serial.tex
i like this new figure

@@
 On the other hand, the serial interval is defined as the time between when an infector and an infectee become symptomatic.
-Previous studies have often alluded to differences in their variances, despite having seemingly identical expected values, and noted that using serial-interval distribution can give different estimates of $\mathcal R$.
+While serial intervals are similar to generation intervals, previous studies noted that using serial intervals can give different estimates of $\mathcal R$ and have often alluded to differences in their variances, despite having seemingly identical expected values.
 Even though these distinctions were first made over a decade ago \citep{svensson2007note}, 
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds:
-Researchers continue to rely on both generation and serial intervals to estimate $\mathcal R$ for COVID-19 without making a clear distinction, and some even mislabel them.
+Researchers continue to rely on both generation and serial intervals to estimate $\mathcal R$ for COVID-19 without making a clear distinction.
 
@@
 Likewise, since infection typically leads to symptoms, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
-Therefore, both generation- and serial-interval distributions should give us identical estimates of  $\mathcal R$ based the observed epidemic growth rate.
-Current theory suggests that using generation- and serial-interval distributions give different estimates of $\mathcal R$ and contradicts our biological intution.
+Therefore, both generation- and serial-interval distributions should give us identical estimates of  $\mathcal R$ based the observed epidemic growth rate $r$.
+However, current theory suggests that using generation- and serial-interval distributions give different estimates of $\mathcal R$ and contradicts our biological intution.
 
-Here, we provide an answer to this decade-old paradox.
-We develop a novel framework for understanding serial intervals and show that the serial-interval distribution must be defined with reference to disease incidence;
+Here, we provide an answer to the decade-old paradox between generation and serial intervals.
+We present a novel framework for understanding serial intervals and show that the serial-interval distribution must be defined with reference to disease incidence;
 previous frameworks implicitly assume that incidence remains constant.
-Using our framework, we are able to show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.
-However, failing to account for changes in the serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
+Using our framework, we are able to show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ based on the exponential growth phase of an epidemic.
+However, failing to account for changes in the observed serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
 We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of the ongoing pandemic.
@@
 these events can be defined either within an infected individual (e.g., infection and symptom onset of an individual) or between infected individuals (e.g., symptom onsets of an infector and an infectee).
-Then, we can further divide these events into \emph{primary} and \emph{secondary} events.
-When we measure an epidemiological time delay within an infected individual (e.g., time between infection and symptom onset), the primary event always occurs before the secondary event.
+We can further divide these events into \emph{primary} and \emph{secondary} events.
+When we measure an epidemiological time delay within an infected individual (e.g., incubation period), the primary event always occurs before the secondary event.
 When we measure an epidemiological time delay between infected individuals (e.g., serial interval), 
@@
 
-Likewise, we can define a backward delay distribution $b_s(\tau)$ for a secondary cohort $s$:
+Likewise, we can define the backward delay distribution $b_s(\tau)$ for a secondary cohort $s$:
 The backward delay distribution for secondary host $s$ describes the time delays between a primary and secondary host given that the secondary event occurred at time $s$.
@@
 The serial interval is defined as the time between when an infector becomes symptomatic and when and infectee becomes symptomatic.
-Here, we denote realized serial intervals $\tau$ as:
+Serial intervals $\tau$ are typically written as:
 \begin{equation}
@@
 where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\sigma$ represents the realized generation interval.
-Previous studies have assumed that (i) $x_0$ and $x_1$ have the same means and (ii) therefore the serial and generation intervals have the same mean;
+Previous studies have often assumed that $x_0$ and $x_1$ have the same means and concluded that the serial and generation intervals have the same mean;
 however, these results implicitly assume that incidence stays constant.
 
+\begin{figure}[!ht]
+\includegraphics[width=\textwidth]{serial_guide.pdf}
+\caption{
+\textbf{Forward and backward serial intervals.}
+}
+\label{fig:diagram}
+\end{figure}
+
 Using the cohort-based framework provides a clear way of understanding the serial-interval distribution.
-Given that an infector became symptomatic at time $\ell$, we have to first go backward in time by asking when the infector was infected and go forward in time by asking when the infectee became symptomatic.
-Then, it is clear that $x_0$ follows the backward incubation period distribution for secondary cohort $\ell$; 
-$\sigma$ follows the forward generation-interval distribution for a primary cohort $\ell - x_0$ conditional on the incubation period $x_0$ of the infector;
-and $x_1$ follows forward incubation period distribution for a primary cohort $\ell - x_0 + \sigma$.
+Given that an infector became symptomatic at time $\ell$, we have to first go backward in time by asking when the infector was infected and go forward in time by asking when the infector infected infectee and when the infectee became symptomatic;
+this defines the forward serial interval (\fref{diagram}A).
+Then, it is clear that $x_0$ represents the backward incubation period for secondary cohort $\ell$; 
+$\sigma$ represents the forward generation interval for a primary cohort $\ell - x_0$ conditional on the incubation period $x_0$ of the infector;
+and $x_1$ represents the forward incubation period for a primary cohort $\ell - x_0 + \sigma$.
 Assuming that the forward incubation distribution does not vary across cohorts, the forward serial interval distribution of a primary cohort $\ell$ can be written as follows:
@@
 Here, we assume that the forward incubation period distribution does not vary across cohorts over the course of an epidemic as it represents an intrinsic property of the natrual history of a disease.
-% Therefore, the forward serial interval distribution depends on previous changes in incidence and generally have different means from the forward generation interval distribution.
 
-Likewise, we can define backward serial interval distribution for a secondary cohort $\ell$.
+Likewise, we can define the backward serial interval distribution for a secondary cohort $\ell$ (\fref{diagram}B).
 Given that an infectee became symptomatic at time $\ell$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
 then, we have to go forward in time by asking when the infector became symptomatic.
-In this case, $x_1$ and $\sigma$ follow the backward incubation period and generation-interval distributions, respectively, and $x_0$ follows the forward incubation period distribution.
+In this case, $x_1$ and $\sigma$ represent the backward incubation period and generation-interval distributions, respectively, and $x_0$ represents the forward incubation period distribution.
 Therefore, the backward serial interval distribution of a secondary cohort $\ell$ can be written as follows

### 2020-04-14 serial_analysis.tex
i like this new figure

% Created by tikzDevice version 0.12.3 on 2020-04-12 17:51:37
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 34.64, 30.69) rectangle (283.58,266.42);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.64, 30.69) rectangle (283.58,266.42);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.97,138.18) -- ( 41.97,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.97,138.18) -- ( 41.97,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 39.22,138.18) --
	( 39.22,138.18) --
	( 44.71,138.18) --
	( 44.71,138.18) --
	( 39.22,138.18) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 39.22,138.18) -- ( 44.71,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.61,226.33) -- ( 56.61,234.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.61,209.04) -- ( 56.61,186.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 53.86,226.33) --
	( 53.86,209.04) --
	( 59.36,209.04) --
	( 59.36,226.33) --
	( 53.86,226.33) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 53.86,217.69) -- ( 59.36,217.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93,196.95) -- ( 63.93,228.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93,158.92) -- ( 63.93,152.01);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 61.19,196.95) --
	( 61.19,158.92) --
	( 66.68,158.92) --
	( 66.68,196.95) --
	( 61.19,196.95) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 61.19,165.84) -- ( 66.68,165.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 71.25,200.40) -- ( 71.25,207.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 71.25,186.58) -- ( 71.25,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.51,200.40) --
	( 68.51,186.58) --
	( 74.00,186.58) --
	( 74.00,200.40) --
	( 68.51,200.40) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.51,193.49) -- ( 74.00,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.57,221.14) -- ( 78.57,234.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.57,172.75) -- ( 78.57,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 75.83,221.14) --
	( 75.83,172.75) --
	( 81.32,172.75) --
	( 81.32,221.14) --
	( 75.83,221.14) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 75.83,207.32) -- ( 81.32,207.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.90,221.14) -- ( 85.90,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.90,221.14) -- ( 85.90,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 83.15,221.14) --
	( 83.15,221.14) --
	( 88.64,221.14) --
	( 88.64,221.14) --
	( 83.15,221.14) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 83.15,221.14) -- ( 88.64,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.22,238.42) -- ( 93.22,255.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.22,203.86) -- ( 93.22,186.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 90.47,238.42) --
	( 90.47,203.86) --
	( 95.96,203.86) --
	( 95.96,238.42) --
	( 90.47,238.42) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 90.47,221.14) -- ( 95.96,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,200.40) -- (100.54,207.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,186.58) -- (100.54,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 97.79,200.40) --
	( 97.79,186.58) --
	(103.29,186.58) --
	(103.29,200.40) --
	( 97.79,200.40) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 97.79,193.49) -- (103.29,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.86,214.23) -- (107.86,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.86,214.23) -- (107.86,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (105.12,214.23) --
	(105.12,214.23) --
	(110.61,214.23) --
	(110.61,214.23) --
	(105.12,214.23) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (105.12,214.23) -- (110.61,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (115.18,198.67) -- (115.18,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (115.18,164.11) -- (115.18,158.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.44,198.67) --
	(112.44,164.11) --
	(117.93,164.11) --
	(117.93,198.67) --
	(112.44,198.67) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (112.44,179.66) -- (117.93,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.50,186.58) -- (122.50,234.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.50,138.18) -- (122.50,103.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (119.76,186.58) --
	(119.76,138.18) --
	(125.25,138.18) --
	(125.25,186.58) --
	(119.76,186.58) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (119.76,158.92) -- (125.25,158.92);
\definecolor{fillColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.83,221.14) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.83,171.02) -- (129.83,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.83,139.91) -- (129.83,124.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (127.08,171.02) --
	(127.08,139.91) --
	(132.57,139.91) --
	(132.57,171.02) --
	(127.08,171.02) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (127.08,155.47) -- (132.57,155.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15,183.12) -- (137.15,200.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15,148.55) -- (137.15,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (134.40,183.12) --
	(134.40,148.55) --
	(139.89,148.55) --
	(139.89,183.12) --
	(134.40,183.12) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (134.40,165.84) -- (139.89,165.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.47,172.75) -- (144.47,214.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.47,131.27) -- (144.47,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (141.72,172.75) --
	(141.72,131.27) --
	(147.21,131.27) --
	(147.21,172.75) --
	(141.72,172.75) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (141.72,152.01) -- (147.21,152.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.79,179.66) -- (151.79,221.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.79,138.18) -- (151.79,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (149.05,179.66) --
	(149.05,138.18) --
	(154.54,138.18) --
	(154.54,179.66) --
	(149.05,179.66) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (149.05,158.92) -- (154.54,158.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,184.85) -- (159.11,228.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,126.09) -- (159.11, 55.23);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (156.37,184.85) --
	(156.37,126.09) --
	(161.86,126.09) --
	(161.86,184.85) --
	(156.37,184.85) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (156.37,155.47) -- (161.86,155.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.43,174.48) -- (166.43,200.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (166.43,129.54) -- (166.43,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (163.69,174.48) --
	(163.69,129.54) --
	(169.18,129.54) --
	(169.18,174.48) --
	(163.69,174.48) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (163.69,152.01) -- (169.18,152.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.76,171.02) -- (173.76,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.76,133.00) -- (173.76,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (171.01,171.02) --
	(171.01,133.00) --
	(176.50,133.00) --
	(176.50,171.02) --
	(171.01,171.02) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (171.01,152.01) -- (176.50,152.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (181.08,152.01) -- (181.08,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (181.08,110.53) -- (181.08, 82.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (178.33,152.01) --
	(178.33,110.53) --
	(183.82,110.53) --
	(183.82,152.01) --
	(178.33,152.01) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (178.33,131.27) -- (183.82,131.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.40,165.84) -- (188.40,193.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.40,110.53) -- (188.40, 75.97);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (185.65,165.84) --
	(185.65,110.53) --
	(191.14,110.53) --
	(191.14,165.84) --
	(185.65,165.84) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (185.65,138.18) -- (191.14,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (195.72,160.65) -- (195.72,200.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (195.72,108.80) -- (195.72, 82.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (192.97,160.65) --
	(192.97,108.80) --
	(198.47,108.80) --
	(198.47,160.65) --
	(192.97,160.65) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (192.97,134.73) -- (198.47,134.73);
\definecolor{fillColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.04, 48.31) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (203.04,155.47) -- (203.04,179.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (203.04,120.90) -- (203.04,103.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (200.30,155.47) --
	(200.30,120.90) --
	(205.79,120.90) --
	(205.79,155.47) --
	(200.30,155.47) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (200.30,138.18) -- (205.79,138.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36,143.37) -- (210.36,172.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36,107.08) -- (210.36, 62.14);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (207.62,143.37) --
	(207.62,107.08) --
	(213.11,107.08) --
	(213.11,143.37) --
	(207.62,143.37) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (207.62,127.81) -- (213.11,127.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.69,131.27) -- (217.69,145.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.69, 96.71) -- (217.69, 75.97);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (214.94,131.27) --
	(214.94, 96.71) --
	(220.43, 96.71) --
	(220.43,131.27) --
	(214.94,131.27) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (214.94,117.45) -- (220.43,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.01,134.73) -- (225.01,145.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.01,113.99) -- (225.01, 82.88);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (222.26,134.73) --
	(222.26,113.99) --
	(227.75,113.99) --
	(227.75,134.73) --
	(222.26,134.73) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (222.26,124.36) -- (227.75,124.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.33,134.73) -- (232.33,145.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.33,113.99) -- (232.33, 96.71);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (229.58,134.73) --
	(229.58,113.99) --
	(235.07,113.99) --
	(235.07,134.73) --
	(229.58,134.73) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (229.58,124.36) -- (235.07,124.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.65,126.09) -- (239.65,131.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.65,115.72) -- (239.65,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (236.90,126.09) --
	(236.90,115.72) --
	(242.40,115.72) --
	(242.40,126.09) --
	(236.90,126.09) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (236.90,120.90) -- (242.40,120.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (246.97,110.53) -- (246.97,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (246.97,110.53) -- (246.97,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (244.23,110.53) --
	(244.23,110.53) --
	(249.72,110.53) --
	(249.72,110.53) --
	(244.23,110.53) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (244.23,110.53) -- (249.72,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (261.62, 89.79) -- (261.62, 89.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (261.62, 89.79) -- (261.62, 89.79);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (258.87, 89.79) --
	(258.87, 89.79) --
	(264.36, 89.79) --
	(264.36, 89.79) --
	(258.87, 89.79) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (258.87, 89.79) -- (264.36, 89.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (276.26, 93.25) -- (276.26,110.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (276.26, 58.68) -- (276.26, 41.40);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (273.51, 93.25) --
	(273.51, 58.68) --
	(279.00, 58.68) --
	(279.00, 93.25) --
	(273.51, 93.25) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (273.51, 75.97) -- (279.00, 75.97);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.64, 30.69) rectangle (283.58,266.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69, 45.28) {-10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,114.41) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,183.55) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,252.68) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89, 48.31) --
	( 34.64, 48.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,117.45) --
	( 34.64,117.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,186.58) --
	( 34.64,186.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,255.71) --
	( 34.64,255.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93, 27.94) --
	( 63.93, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15, 27.94) --
	(137.15, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36, 27.94) --
	(210.36, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.58, 27.94) --
	(283.58, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 63.93, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (137.15, 19.68) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (210.36, 19.68) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (283.58, 19.68) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (159.11,  7.64) {Cohort time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,148.55) {Forward serial intervals (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.64,274.49) {A};
\end{scope}
\begin{scope}
\path[clip] (289.08,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.08,  0.00) rectangle (578.16,289.08);
\end{scope}
\begin{scope}
\path[clip] (316.39, 30.69) rectangle (572.66,266.42);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (316.39, 30.69) rectangle (572.66,266.42);
\definecolor{drawColor}{RGB}{240,228,66}
\definecolor{fillColor}{RGB}{240,228,66}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (346.54,255.71) --
	(354.08,234.51) --
	(361.62,227.85) --
	(369.15,224.34) --
	(376.69,232.95) --
	(384.23,225.18) --
	(391.77,220.08) --
	(399.30,212.60) --
	(406.84,137.83) --
	(414.38,119.60) --
	(421.91,116.21) --
	(429.45,104.34) --
	(436.99,101.52) --
	(444.53, 91.89) --
	(452.06, 87.88) --
	(459.60, 85.77) --
	(467.14, 79.62) --
	(474.68, 76.53) --
	(482.21, 72.74) --
	(489.75, 71.32) --
	(497.29, 69.30) --
	(504.82, 68.00) --
	(512.36, 66.17) --
	(519.90, 65.86) --
	(527.44, 65.06) --
	(534.97, 64.84) --
	(542.51, 64.84) --
	(550.05, 64.82) --
	(557.59, 64.82) --
	(565.12, 64.08) --
	(565.12, 56.77) --
	(557.59, 57.72) --
	(550.05, 57.72) --
	(542.51, 58.18) --
	(534.97, 58.18) --
	(527.44, 58.40) --
	(519.90, 58.16) --
	(512.36, 58.79) --
	(504.82, 60.03) --
	(497.29, 60.94) --
	(489.75, 62.46) --
	(482.21, 65.05) --
	(474.68, 66.78) --
	(467.14, 70.56) --
	(459.60, 73.93) --
	(452.06, 74.95) --
	(444.53, 77.75) --
	(436.99, 84.76) --
	(429.45, 84.17) --
	(421.91, 90.54) --
	(414.38, 89.60) --
	(406.84, 93.27) --
	(399.30,129.71) --
	(391.77,137.14) --
	(384.23,136.34) --
	(376.69,134.94) --
	(369.15,135.04) --
	(361.62,120.43) --
	(354.08,124.23) --
	(346.54,119.49) --
	cycle;
\definecolor{drawColor}{RGB}{0,114,178}
\definecolor{fillColor}{RGB}{0,114,178}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (346.54,167.99) --
	(354.08,158.37) --
	(361.62,155.61) --
	(369.15,153.41) --
	(376.69,158.49) --
	(384.23,154.03) --
	(391.77,151.93) --
	(399.30,148.30) --
	(406.84,107.71) --
	(414.38, 96.60) --
	(421.91, 94.03) --
	(429.45, 86.26) --
	(436.99, 84.52) --
	(444.53, 77.77) --
	(452.06, 75.45) --
	(459.60, 73.98) --
	(467.14, 69.74) --
	(474.68, 67.73) --
	(482.21, 65.35) --
	(489.75, 64.41) --
	(497.29, 62.76) --
	(504.82, 61.94) --
	(512.36, 60.56) --
	(519.90, 60.51) --
	(527.44, 60.01) --
	(534.97, 59.88) --
	(542.51, 59.88) --
	(550.05, 59.77) --
	(557.59, 59.77) --
	(565.12, 59.40) --
	(565.12, 54.49) --
	(557.59, 54.89) --
	(550.05, 54.89) --
	(542.51, 55.23) --
	(534.97, 55.23) --
	(527.44, 55.32) --
	(519.90, 55.43) --
	(512.36, 55.76) --
	(504.82, 56.48) --
	(497.29, 57.32) --
	(489.75, 58.34) --
	(482.21, 59.85) --
	(474.68, 61.35) --
	(467.14, 63.63) --
	(459.60, 66.52) --
	(452.06, 66.97) --
	(444.53, 68.74) --
	(436.99, 73.15) --
	(429.45, 73.04) --
	(421.91, 77.40) --
	(414.38, 77.19) --
	(406.84, 79.82) --
	(399.30,101.35) --
	(391.77,108.09) --
	(384.23,107.05) --
	(376.69,105.61) --
	(369.15,105.29) --
	(361.62, 96.62) --
	(354.08, 98.80) --
	(346.54, 95.78) --
	cycle;
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (316.39, 41.40) -- (572.66, 41.40);
\definecolor{drawColor}{RGB}{240,228,66}

\path[draw=drawColor,line width= 0.6pt,line join=round] (346.54,170.94) --
	(354.08,170.79) --
	(361.62,163.30) --
	(369.15,167.34) --
	(376.69,172.68) --
	(384.23,172.43) --
	(391.77,174.86) --
	(399.30,167.73) --
	(406.84,112.65) --
	(414.38,105.04) --
	(421.91,102.84) --
	(429.45, 93.38) --
	(436.99, 91.84) --
	(444.53, 83.99) --
	(452.06, 80.95) --
	(459.60, 80.00) --
	(467.14, 75.18) --
	(474.68, 71.77) --
	(482.21, 68.56) --
	(489.75, 66.30) --
	(497.29, 65.11) --
	(504.82, 63.71) --
	(512.36, 62.37) --
	(519.90, 61.91) --
	(527.44, 61.69) --
	(534.97, 61.52) --
	(542.51, 61.52) --
	(550.05, 61.33) --
	(557.59, 61.33) --
	(565.12, 60.65);
\definecolor{drawColor}{RGB}{0,114,178}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (346.54,126.39) --
	(354.08,125.79) --
	(361.62,122.09) --
	(369.15,124.37) --
	(376.69,127.48) --
	(384.23,126.99) --
	(391.77,128.28) --
	(399.30,123.96) --
	(406.84, 92.40) --
	(414.38, 87.06) --
	(421.91, 85.30) --
	(429.45, 79.23) --
	(436.99, 77.99) --
	(444.53, 73.04) --
	(452.06, 70.90) --
	(459.60, 70.16) --
	(467.14, 66.88) --
	(474.68, 64.57) --
	(482.21, 62.37) --
	(489.75, 60.94) --
	(497.29, 60.13) --
	(504.82, 59.14) --
	(512.36, 58.16) --
	(519.90, 57.82) --
	(527.44, 57.64) --
	(534.97, 57.52) --
	(542.51, 57.52) --
	(550.05, 57.39) --
	(557.59, 57.39) --
	(565.12, 56.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.39, 30.69) rectangle (572.66,266.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44, 38.37) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44, 90.38) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,142.40) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,194.41) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,246.42) {5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64, 41.40) --
	(316.39, 41.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64, 93.41) --
	(316.39, 93.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,145.43) --
	(316.39,145.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,197.44) --
	(316.39,197.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,249.45) --
	(316.39,249.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (346.54, 27.94) --
	(346.54, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (421.91, 27.94) --
	(421.91, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.29, 27.94) --
	(497.29, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (572.66, 27.94) --
	(572.66, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (346.54, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (421.91, 19.68) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (497.29, 19.68) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.66, 19.68) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (444.53,  7.64) {Cohort time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,148.55) {Reproduction number $\mathcal R$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (450.83,208.36) rectangle (566.36,253.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (456.33,228.31) rectangle (470.78,242.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{240,228,66}
\definecolor{fillColor}{RGB}{240,228,66}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor,fill opacity=0.50] (457.04,229.02) rectangle (470.07,242.05);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{240,228,66}

\path[draw=drawColor,line width= 0.6pt,line join=round] (457.77,235.54) -- (469.33,235.54);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (456.33,213.86) rectangle (470.78,228.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,114,178}
\definecolor{fillColor}{RGB}{0,114,178}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line cap=rect,fill=fillColor,fill opacity=0.50] (457.04,214.57) rectangle (470.07,227.60);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,114,178}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (457.77,221.09) -- (469.33,221.09);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.28,232.51) {6 day doubling period};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.28,218.05) {8 day doubling period};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (316.39,274.49) {B};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-04-14 serial_guide.tex
i like this new figure

% Created by tikzDevice version 0.12.3 on 2020-04-14 02:04:29
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (722.70,433.62);
\begin{scope}
\path[clip] (  0.00,216.81) rectangle (722.70,433.62);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,216.81) rectangle (722.70,433.62);
\end{scope}
\begin{scope}
\path[clip] (  8.25,225.06) rectangle (717.20,410.96);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (  8.25,225.06) rectangle (717.20,410.96);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,275.76) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16,275.76) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,275.76) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41,275.76) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,332.09) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16,388.43) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,360.26) circle (  3.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,257.88) {$\ell$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,257.88) {$\ell-x_0$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,243.79) {Infector};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,243.79) {Primary cohort};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,243.79) {Infectee};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,257.88) {$\ell-x_0+\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,257.88) {$\ell-x_0+\sigma+x_1$};

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 40.48,275.76) -- (684.98,275.76);

\path[draw=drawColor,line width= 1.1pt,line join=round] (672.46,268.53) --
	(684.98,275.76) --
	(672.46,282.99);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (121.04,275.76) -- (121.04,332.09);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.16,275.76) -- (282.16,388.43);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (443.29,275.76) -- (443.29,360.26);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (604.41,275.76) -- (604.41,388.43);

\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,303.93) -- (121.04,303.93);

\path[draw=drawColor,line width= 1.1pt,line join=round] (127.30,307.54) --
	(121.04,303.93) --
	(127.30,300.31);

\path[draw=drawColor,line width= 1.1pt,line join=round] (121.04,332.09) -- (443.29,332.09);

\path[draw=drawColor,line width= 1.1pt,line join=round] (437.03,328.48) --
	(443.29,332.09) --
	(437.03,335.71);

\path[draw=drawColor,line width= 1.1pt,line join=round] (443.29,360.26) -- (604.41,360.26);

\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,356.65) --
	(604.41,360.26) --
	(598.15,363.88);

\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,388.43) -- (604.41,388.43);

\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,384.82) --
	(604.41,388.43) --
	(598.15,392.04);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,398.71) {Forward serial interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,314.21) {Backward incubation period};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,342.38) {Forward generation interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,370.54) {Forward incubation period};
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16,275.76) circle (  5.71);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41,275.76) circle (  5.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  8.25,419.03) {A};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,216.81);
\end{scope}
\begin{scope}
\path[clip] (  8.25,  8.25) rectangle (717.20,194.15);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (  8.25,  8.25) rectangle (717.20,194.15);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04, 58.95) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16, 58.95) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29, 58.95) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41, 58.95) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,143.45) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41,171.62) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,115.28) circle (  3.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 41.07) {$\ell$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 41.07) {$\ell-x_1$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 41.07) {$\ell-x_1-\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 41.07) {$\ell-x_1-\sigma+x_0$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 26.98) {Infector};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 26.98) {Infectee};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 26.98) {Secondary cohort};

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 40.48, 58.95) -- (684.98, 58.95);

\path[draw=drawColor,line width= 1.1pt,line join=round] (672.46, 51.72) --
	(684.98, 58.95) --
	(672.46, 66.18);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (121.04, 58.95) -- (121.04,143.45);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.16, 58.95) -- (282.16,171.62);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (443.29, 58.95) -- (443.29,115.28);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (604.41, 58.95) -- (604.41,171.62);

\path[draw=drawColor,line width= 1.1pt,line join=round] (604.41, 87.12) -- (443.29, 87.12);

\path[draw=drawColor,line width= 1.1pt,line join=round] (449.55, 90.73) --
	(443.29, 87.12) --
	(449.55, 83.50);

\path[draw=drawColor,line width= 1.1pt,line join=round] (443.29,115.28) -- (121.04,115.28);

\path[draw=drawColor,line width= 1.1pt,line join=round] (127.30,118.90) --
	(121.04,115.28) --
	(127.30,111.67);

\path[draw=drawColor,line width= 1.1pt,line join=round] (121.04,143.45) -- (282.16,143.45);

\path[draw=drawColor,line width= 1.1pt,line join=round] (275.90,139.84) --
	(282.16,143.45) --
	(275.90,147.07);

\path[draw=drawColor,line width= 1.1pt,line join=round] (604.41,171.62) -- (282.16,171.62);

\path[draw=drawColor,line width= 1.1pt,line join=round] (288.42,175.23) --
	(282.16,171.62) --
	(288.42,168.01);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,181.90) {Backward serial interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85, 97.40) {Backward incubation period};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (362.72,125.57) {Backward generation interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,153.73) {Forward incubation period};
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41, 58.95) circle (  5.71);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16, 58.95) circle (  5.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  8.25,202.22) {B};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-04-14 serial_analysis.R

@@ -1,0 +1,112 @@
+library(readxl)
+library(tidyr)
+library(dplyr)
+library(ggplot2); theme_set(theme_bw())
+library(gridExtra)
+library(tikzDevice)
+source("cpalette.R")
+
+nboot <- 200
+
+r1 <- log(2)/8
+r2 <- log(2)/6
+
+rr <- read_xlsx("Table S5.xlsx", skip=1) %>%
+  mutate(
+    cohort=`Index - symptom onset date`,
+    serial=`Seconday - symptom onset date`- `Index - symptom onset date`
+  )
+
+rr_summ <- rr %>%
+  group_by(cohort, serial) %>%
+  summarize(
+    size=length(serial)
+  )
+
+rr_summ2 <- rr %>%
+  group_by(cohort) %>%
+  summarize(
+    mean=mean(serial)
+  )
+
+tcut <- seq(0, 29, by=1)
+
+serdata1 <- lapply(tcut, function(x) {
+  set.seed(123)
+  tmp <- rr %>%
+    filter(cohort <= x)
+  
+  R0samp <- replicate(nboot, {
+    ss <- tmp$serial
+    ss <- sample(ss, replace=TRUE)
+    1/mean(exp(-r1*ss), na.rm=TRUE)
+  })
+  
+  data.frame(
+    t=x,
+    R0=1/mean(exp(-r1*tmp$serial), na.rm=TRUE),
+    lwr=quantile(R0samp, 0.025),
+    upr=quantile(R0samp, 0.975)
+  )
+}) %>%
+  bind_rows  %>%
+  mutate(
+    type="8 day doubling period"
+  )
+
+serdata2 <- lapply(tcut, function(x) {
+  set.seed(123)
+  tmp <- rr %>%
+    filter(cohort <= x)
+  
+  R0samp <- replicate(nboot, {
+    ss <- tmp$serial
+    ss <- sample(ss, replace=TRUE)
+    1/mean(exp(-r2*ss), na.rm=TRUE)
+  })
+  
+  data.frame(
+    t=x,
+    R0=1/mean(exp(-r2*tmp$serial), na.rm=TRUE),
+    lwr=quantile(R0samp, 0.025),
+    upr=quantile(R0samp, 0.975)
+  )
+}) %>%
+  bind_rows  %>%
+  mutate(
+    type="6 day doubling period"
+  )
+
+serall <- bind_rows(serdata1, serdata2)
+
[…]

### 2020-04-14 serial_guide.R

@@ -1,0 +1,95 @@
+library(ggplot2); theme_set(theme_bw())
+library(gridExtra)
+library(tikzDevice)
+
+arrow <- data.frame(
+  x=0,
+  y=0,
+  x1=4,
+  y1=0
+)
+
+g1 <- ggplot(arrow) +
+  geom_point(aes(0.5, 0), size=3) +
+  geom_point(aes(1.5, 0), size=3) +
+  geom_point(aes(2.5, 0), size=3) +
+  geom_point(aes(3.5, 0), size=3) +
+  geom_point(aes(0.5, 0.2), size=3) +
+  geom_point(aes(1.5, 0.4), size=3) +
+  geom_point(aes(2.5, 0.3), size=3) +
+  annotate("text", x=1.5, y=-0.05, label="$\\ell$") +
+  annotate("text", x=0.5, y=-0.05, label="$\\ell-x_0$") +
+  annotate("text", x=0.5, y=-0.1, label="Infector") +
+  annotate("text", x=1.5, y=-0.1, label="Primary cohort") +
+  annotate("text", x=2.5, y=-0.1, label="Infectee") +
+  annotate("text", x=2.5, y=-0.05, label="$\\ell-x_0+\\sigma$") +
+  annotate("text", x=3.5, y=-0.05, label="$\\ell-x_0+\\sigma+x_1$") +
+  geom_segment(aes(x, y, xend=x1, yend=y1), arrow = arrow(length = unit(0.2, "inches")), lwd=1) +
+  geom_segment(aes(0.5, 0, xend=0.5, yend=0.2), lty=2) +
+  geom_segment(aes(1.5, 0, xend=1.5, yend=0.4), lty=2) +
+  geom_segment(aes(2.5, 0, xend=2.5, yend=0.3), lty=2) +
+  geom_segment(aes(3.5, 0, xend=3.5, yend=0.4), lty=2) +
+  geom_segment(aes(1.5, 0.1, xend=0.5, yend=0.1), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
+  geom_segment(aes(0.5, 0.2, xend=2.5, yend=0.2), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
+  geom_segment(aes(2.5, 0.3, xend=3.5, yend=0.3), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
[…]

### 2020-04-14 rR.tex
there's one thing that I'm missing...huh...

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-09 18:48:49
+% Created by tikzDevice version 0.12.3 on 2020-04-14 11:43:25
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.68) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.65) --
 	( 30.56,248.50) --
+	( 33.80,249.37) --
+	( 37.04,250.25) --
+	( 40.29,251.16) --
+	( 43.53,252.09) --
+	( 46.78,253.03) --
+	( 50.02,254.00) --
+	( 53.26,254.98) --
+	( 56.51,255.98) --
+	( 59.75,257.00) --
+	( 63.00,258.04) --
+	( 66.24,259.10) --
+	( 69.48,260.18) --
+	( 72.73,261.28) --
+	( 75.97,262.40) --
+	( 79.22,263.54) --
+	( 82.46,264.70) --
+	( 85.70,265.88) --
+	( 88.95,267.07) --
+	( 92.19,268.29) --
+	( 95.43,269.52) --
+	( 98.68,270.77) --
+	(101.92,272.04) --
+	(105.17,273.33) --
+	(108.41,274.63) --
+	(111.65,275.96) --
+	(114.90,277.31) --
+	(118.14,278.69) --
+	(121.39,280.08) --
+	(124.63,281.50) --
+	(127.87,282.94) --
+	(131.12,284.39) --
+	(134.36,285.86) --
+	(137.61,287.35) --
+	(140.85,288.87) --
+	(144.09,290.41) --
+	(147.34,291.97) --
+	(150.58,293.56) --
+	(153.82,295.18) --
+	(157.07,296.83) --
+	(160.31,298.49) --
+	(163.56,300.18) --
+	(166.80,301.88) --
+	(170.04,303.60) --
+	(173.29,305.35) --
+	(176.53,307.13) --
+	(179.78,308.93) --
+	(183.02,310.77) --
+	(186.26,312.64) --
+	(189.51,314.55) --
+	(192.75,316.48) --
+	(196.00,318.44) --
+	(199.24,320.43) --
+	(202.48,322.45) --
+	(205.73,324.49) --
+	(208.97,326.57) --
+	(212.21,328.67) --
+	(215.46,330.81) --
+	(218.70,332.98) --
+	(221.95,335.19) --
+	(225.19,337.43) --
+	(228.43,339.70) --
+	(231.68,342.00) --
+	(234.92,344.33) --
+	(238.17,346.69) --
+	(241.41,349.09) --
+	(244.65,351.51) --
+	(247.90,353.96) --
+	(251.14,356.45) --
+	(254.39,358.97) --
+	(257.63,361.51) --
+	(260.87,364.10) --
+	(264.12,366.71) --
+	(267.36,369.35) --
+	(270.60,372.03) --
+	(273.85,374.73) --
+	(277.09,377.47) --
+	(280.34,380.24) --
+	(283.58,383.04);
+\definecolor{drawColor}{RGB}{230,159,0}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.62) --
+	( 30.56,248.48) --
+	( 33.80,249.35) --
+	( 37.04,250.25) --
+	( 40.29,251.16) --
+	( 43.53,252.10) --
+	( 46.78,253.05) --
+	( 50.02,254.02) --
+	( 53.26,255.01) --
+	( 56.51,256.02) --
+	( 59.75,257.05) --
+	( 63.00,258.09) --
+	( 66.24,259.16) --
+	( 69.48,260.24) --
+	( 72.73,261.35) --
+	( 75.97,262.47) --
+	( 79.22,263.61) --
+	( 82.46,264.77) --
+	( 85.70,265.96) --
+	( 88.95,267.16) --
+	( 92.19,268.37) --
+	( 95.43,269.61) --
+	( 98.68,270.86) --
+	(101.92,272.13) --
+	(105.17,273.42) --
+	(108.41,274.73) --
+	(111.65,276.06) --
+	(114.90,277.41) --
+	(118.14,278.78) --
+	(121.39,280.18) --
+	(124.63,281.60) --
+	(127.87,283.02) --
+	(131.12,284.47) --
+	(134.36,285.93) --
+	(137.61,287.42) --
+	(140.85,288.93) --
+	(144.09,290.46) --
+	(147.34,292.01) --
+	(150.58,293.60) --
+	(153.82,295.21) --
+	(157.07,296.86) --
+	(160.31,298.52) --
+	(163.56,300.20) --
+	(166.80,301.90) --
+	(170.04,303.62) --
+	(173.29,305.37) --
+	(176.53,307.15) --
+	(179.78,308.95) --
+	(183.02,310.78) --
+	(186.26,312.65) --
+	(189.51,314.56) --
+	(192.75,316.49) --
+	(196.00,318.45) --
+	(199.24,320.44) --
+	(202.48,322.45) --
+	(205.73,324.50) --
+	(208.97,326.57) --
+	(212.21,328.67) --
+	(215.46,330.81) --
+	(218.70,332.98) --
+	(221.95,335.19) --
+	(225.19,337.43) --
+	(228.43,339.70) --
+	(231.68,342.01) --
+	(234.92,344.34) --
+	(238.17,346.70) --
+	(241.41,349.10) --
+	(244.65,351.53) --
+	(247.90,353.98) --
+	(251.14,356.47) --
+	(254.39,358.99) --
+	(257.63,361.55) --
+	(260.87,364.13) --
+	(264.12,366.75) --
+	(267.36,369.40) --
+	(270.60,372.08) --
+	(273.85,374.79) --
+	(277.09,377.53) --
+	(280.34,380.31) --
+	(283.58,383.11);
+\definecolor{drawColor}{RGB}{86,180,233}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.61) --
+	( 30.56,248.47) --
+	( 33.80,249.35) --
+	( 37.04,250.24) --
+	( 40.29,251.16) --
+	( 43.53,252.10) --
+	( 46.78,253.05) --
+	( 50.02,254.02) --
+	( 53.26,255.02) --
+	( 56.51,256.03) --
+	( 59.75,257.05) --
+	( 63.00,258.10) --
+	( 66.24,259.17) --
+	( 69.48,260.25) --
+	( 72.73,261.36) --
+	( 75.97,262.48) --
+	( 79.22,263.63) --
+	( 82.46,264.79) --
+	( 85.70,265.97) --
+	( 88.95,267.17) --
+	( 92.19,268.39) --
+	( 95.43,269.63) --
+	( 98.68,270.88) --
+	(101.92,272.15) --
+	(105.17,273.44) --
+	(108.41,274.75) --
+	(111.65,276.08) --
+	(114.90,277.43) --
+	(118.14,278.80) --
+	(121.39,280.20) --
+	(124.63,281.61) --
+	(127.87,283.04) --
+	(131.12,284.48) --
+	(134.36,285.94) --
+	(137.61,287.42) --
+	(140.85,288.92) --
+	(144.09,290.45) --
+	(147.34,292.01) --
+	(150.58,293.59) --
+	(153.82,295.20) --
+	(157.07,296.84) --
+	(160.31,298.50) --
+	(163.56,300.18) --
+	(166.80,301.87) --
+	(170.04,303.59) --
+	(173.29,305.33) --
+	(176.53,307.10) --
+	(179.78,308.90) --
+	(183.02,310.74) --
+	(186.26,312.60) --
+	(189.51,314.51) --
+	(192.75,316.44) --
+	(196.00,318.40) --
+	(199.24,320.39) --
+	(202.48,322.41) --
+	(205.73,324.45) --
+	(208.97,326.53) --
+	(212.21,328.64) --
+	(215.46,330.78) --
+	(218.70,332.95) --
+	(221.95,335.17) --
+	(225.19,337.42) --
+	(228.43,339.70) --
+	(231.68,342.01) --
+	(234.92,344.35) --
+	(238.17,346.73) --
+	(241.41,349.13) --
+	(244.65,351.57) --
+	(247.90,354.04) --
+	(251.14,356.54) --
+	(254.39,359.07) --
+	(257.63,361.64) --
+	(260.87,364.24) --
+	(264.12,366.87) --
+	(267.36,369.54) --
+	(270.60,372.24) --
+	(273.85,374.97) --
+	(277.09,377.73) --
+	(280.34,380.52) --
+	(283.58,383.35);
+\definecolor{drawColor}{RGB}{0,158,115}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.60) --
+	( 30.56,248.46) --
 	( 33.80,249.34) --
-	( 37.04,250.20) --
-	( 40.29,251.09) --
-	( 43.53,251.99) --
-	( 46.78,252.92) --
-	( 50.02,253.86) --
-	( 53.26,254.83) --
-	( 56.51,255.81) --
-	( 59.75,256.82) --
-	( 63.00,257.85) --
-	( 66.24,258.90) --
-	( 69.48,259.97) --
-	( 72.73,261.06) --
-	( 75.97,262.17) --
-	( 79.22,263.30) --
-	( 82.46,264.46) --
-	( 85.70,265.64) --
-	( 88.95,266.84) --
-	( 92.19,268.05) --
-	( 95.43,269.29) --
-	( 98.68,270.54) --
-	(101.92,271.81) --
-	(105.17,273.11) --
-	(108.41,274.42) --
-	(111.65,275.76) --
-	(114.90,277.13) --
-	(118.14,278.52) --
-	(121.39,279.93) --
-	(124.63,281.37) --
-	(127.87,282.82) --
-	(131.12,284.29) --
-	(134.36,285.79) --
-	(137.61,287.30) --
-	(140.85,288.84) --
-	(144.09,290.41) --
-	(147.34,292.01) --
-	(150.58,293.64) --
-	(153.82,295.30) --
-	(157.07,296.99) --
-	(160.31,298.71) --
-	(163.56,300.44) --
-	(166.80,302.19) --
-	(170.04,303.97) --
-	(173.29,305.78) --
-	(176.53,307.62) --
-	(179.78,309.49) --
-	(183.02,311.40) --
-	(186.26,313.35) --
-	(189.51,315.33) --
-	(192.75,317.36) --
-	(196.00,319.41) --
-	(199.24,321.50) --
-	(202.48,323.61) --
-	(205.73,325.76) --
-	(208.97,327.95) --
-	(212.21,330.17) --
-	(215.46,332.42) --
-	(218.70,334.72) --
-	(221.95,337.06) --
-	(225.19,339.44) --
-	(228.43,341.86) --
-	(231.68,344.31) --
-	(234.92,346.79) --
-	(238.17,349.31) --
-	(241.41,351.87) --
-	(244.65,354.47) --
-	(247.90,357.09) --
-	(251.14,359.76) --
-	(254.39,362.46) --
-	(257.63,365.21) --
-	(260.87,367.98) --
-	(264.12,370.80) --
-	(267.36,373.65) --
-	(270.60,376.54) --
-	(273.85,379.47) --
-	(277.09,382.43) --
-	(280.34,385.43) --
-	(283.58,388.46);
-\definecolor{drawColor}{RGB}{230,159,0}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.65) --
-	( 30.56,248.48) --
-	( 33.80,249.33) --
-	( 37.04,250.20) --
-	( 40.29,251.09) --
-	( 43.53,252.00) --
-	( 46.78,252.94) --
-	( 50.02,253.89) --
-	( 53.26,254.86) --
-	( 56.51,255.85) --
-	( 59.75,256.87) --
-	( 63.00,257.90) --
-	( 66.24,258.95) --
-	( 69.48,260.03) --
-	( 72.73,261.12) --
-	( 75.97,262.24) --
-	( 79.22,263.38) --
-	( 82.46,264.54) --
-	( 85.70,265.72) --
-	( 88.95,266.92) --
-	( 92.19,268.14) --
-	( 95.43,269.38) --
-	( 98.68,270.63) --
-	(101.92,271.91) --
-	(105.17,273.21) --
-	(108.41,274.52) --
-	(111.65,275.86) --
-	(114.90,277.23) --
-	(118.14,278.62) --
-	(121.39,280.03) --
-	(124.63,281.47) --
-	(127.87,282.92) --
-	(131.12,284.38) --
-	(134.36,285.87) --
-	(137.61,287.38) --
-	(140.85,288.91) --
-	(144.09,290.47) --
-	(147.34,292.06) --
-	(150.58,293.68) --
-	(153.82,295.34) --
-	(157.07,297.03) --
-	(160.31,298.74) --
-	(163.56,300.47) --
-	(166.80,302.22) --
-	(170.04,304.00) --
-	(173.29,305.80) --
-	(176.53,307.64) --
-	(179.78,309.51) --
-	(183.02,311.41) --
-	(186.26,313.36) --
-	(189.51,315.34) --
-	(192.75,317.37) --
-	(196.00,319.42) --
-	(199.24,321.50) --
-	(202.48,323.61) --
-	(205.73,325.76) --
-	(208.97,327.94) --
-	(212.21,330.16) --
-	(215.46,332.42) --
-	(218.70,334.72) --
-	(221.95,337.06) --
-	(225.19,339.44) --
-	(228.43,341.86) --
-	(231.68,344.32) --
-	(234.92,346.81) --
-	(238.17,349.33) --
-	(241.41,351.90) --
-	(244.65,354.49) --
-	(247.90,357.13) --
-	(251.14,359.80) --
-	(254.39,362.51) --
-	(257.63,365.26) --
-	(260.87,368.04) --
-	(264.12,370.87) --
-	(267.36,373.73) --
-	(270.60,376.62) --
-	(273.85,379.56) --
-	(277.09,382.53) --
-	(280.34,385.54) --
-	(283.58,388.58);
-\definecolor{drawColor}{RGB}{86,180,233}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.64) --
-	( 30.56,248.47) --
-	( 33.80,249.33) --
-	( 37.04,250.20) --
-	( 40.29,251.09) --
-	( 43.53,252.00) --
-	( 46.78,252.94) --
-	( 50.02,253.89) --
-	( 53.26,254.86) --
-	( 56.51,255.86) --
-	( 59.75,256.87) --
-	( 63.00,257.91) --
-	( 66.24,258.96) --
-	( 69.48,260.04) --
-	( 72.73,261.13) --
-	( 75.97,262.25) --
-	( 79.22,263.39) --
-	( 82.46,264.55) --
-	( 85.70,265.73) --
-	( 88.95,266.93) --
-	( 92.19,268.15) --
-	( 95.43,269.39) --
-	( 98.68,270.65) --
-	(101.92,271.92) --
-	(105.17,273.22) --
-	(108.41,274.54) --
-	(111.65,275.88) --
-	(114.90,277.24) --
-	(118.14,278.63) --
-	(121.39,280.04) --
-	(124.63,281.48) --
-	(127.87,282.92) --
-	(131.12,284.39) --
-	(134.36,285.87) --
-	(137.61,287.38) --
-	(140.85,288.91) --
-	(144.09,290.47) --
-	(147.34,292.05) --
-	(150.58,293.67) --
-	(153.82,295.33) --
-	(157.07,297.02) --
-	(160.31,298.73) --
-	(163.56,300.45) --
-	(166.80,302.20) --
-	(170.04,303.97) --
-	(173.29,305.78) --
-	(176.53,307.61) --
-	(179.78,309.47) --
-	(183.02,311.38) --
-	(186.26,313.32) --
-	(189.51,315.31) --
-	(192.75,317.33) --
-	(196.00,319.38) --
-	(199.24,321.47) --
-	(202.48,323.58) --
-	(205.73,325.73) --
-	(208.97,327.92) --
-	(212.21,330.14) --
-	(215.46,332.40) --
-	(218.70,334.70) --
-	(221.95,337.05) --
-	(225.19,339.44) --
-	(228.43,341.86) --
-	(231.68,344.33) --
-	(234.92,346.82) --
-	(238.17,349.36) --
-	(241.41,351.93) --
-	(244.65,354.54) --
-	(247.90,357.18) --
-	(251.14,359.87) --
-	(254.39,362.59) --
-	(257.63,365.35) --
-	(260.87,368.14) --
-	(264.12,370.98) --
-	(267.36,373.85) --
-	(270.60,376.76) --
-	(273.85,379.71) --
-	(277.09,382.70) --
-	(280.34,385.72) --
-	(283.58,388.79);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.64) --
-	( 30.56,248.47) --
-	( 33.80,249.32) --
-	( 37.04,250.19) --
-	( 40.29,251.09) --
-	( 43.53,252.00) --
-	( 46.78,252.94) --
-	( 50.02,253.89) --
-	( 53.26,254.86) --
-	( 56.51,255.86) --
-	( 59.75,256.87) --
-	( 63.00,257.91) --
-	( 66.24,258.97) --
-	( 69.48,260.04) --
-	( 72.73,261.14) --
-	( 75.97,262.26) --
-	( 79.22,263.40) --
-	( 82.46,264.56) --
-	( 85.70,265.74) --
-	( 88.95,266.94) --
-	( 92.19,268.16) --
-	( 95.43,269.40) --
-	( 98.68,270.66) --
-	(101.92,271.93) --
-	(105.17,273.23) --
-	(108.41,274.55) --
-	(111.65,275.89) --
-	(114.90,277.25) --
-	(118.14,278.64) --
-	(121.39,280.05) --
-	(124.63,281.48) --
-	(127.87,282.93) --
-	(131.12,284.39) --
-	(134.36,285.88) --
-	(137.61,287.38) --
-	(140.85,288.91) --
-	(144.09,290.46) --
-	(147.34,292.05) --
-	(150.58,293.67) --
-	(153.82,295.32) --
-	(157.07,297.01) --
-	(160.31,298.72) --
-	(163.56,300.44) --
-	(166.80,302.19) --
-	(170.04,303.96) --
-	(173.29,305.76) --
-	(176.53,307.59) --
-	(179.78,309.45) --
-	(183.02,311.35) --
-	(186.26,313.30) --
-	(189.51,315.28) --
-	(192.75,317.31) --
-	(196.00,319.36) --
-	(199.24,321.45) --
-	(202.48,323.57) --
-	(205.73,325.72) --
-	(208.97,327.91) --
-	(212.21,330.14) --
-	(215.46,332.41) --
-	(218.70,334.71) --
-	(221.95,337.07) --
-	(225.19,339.46) --
-	(228.43,341.90) --
-	(231.68,344.37) --
-	(234.92,346.88) --
-	(238.17,349.42) --
-	(241.41,352.01) --
-	(244.65,354.63) --
-	(247.90,357.28) --
-	(251.14,359.98) --
-	(254.39,362.71) --
-	(257.63,365.49) --
-	(260.87,368.30) --
-	(264.12,371.15) --
-	(267.36,374.05) --
-	(270.60,376.98) --
-	(273.85,379.94) --
-	(277.09,382.95) --
-	(280.34,385.99) --
-	(283.58,389.07);
+	( 37.04,250.24) --
+	( 40.29,251.16) --
+	( 43.53,252.09) --
+	( 46.78,253.05) --
+	( 50.02,254.02) --
+	( 53.26,255.02) --
+	( 56.51,256.03) --
+	( 59.75,257.06) --
+	( 63.00,258.11) --
+	( 66.24,259.17) --
+	( 69.48,260.26) --
+	( 72.73,261.37) --
+	( 75.97,262.49) --
+	( 79.22,263.64) --
+	( 82.46,264.80) --
+	( 85.70,265.98) --
+	( 88.95,267.18) --
+	( 92.19,268.40) --
+	( 95.43,269.64) --
+	( 98.68,270.89) --
+	(101.92,272.16) --
+	(105.17,273.45) --
+	(108.41,274.76) --
+	(111.65,276.09) --
+	(114.90,277.44) --
+	(118.14,278.81) --
+	(121.39,280.21) --
+	(124.63,281.62) --
+	(127.87,283.04) --
+	(131.12,284.48) --
+	(134.36,285.94) --
+	(137.61,287.42) --
+	(140.85,288.92) --
+	(144.09,290.45) --
+	(147.34,292.00) --
+	(150.58,293.58) --
+	(153.82,295.19) --
+	(157.07,296.83) --
+	(160.31,298.48) --
+	(163.56,300.16) --
+	(166.80,301.85) --
+	(170.04,303.57) --
+	(173.29,305.31) --
+	(176.53,307.07) --
+	(179.78,308.87) --
+	(183.02,310.70) --
+	(186.26,312.57) --
+	(189.51,314.47) --
+	(192.75,316.41) --
+	(196.00,318.37) --
+	(199.24,320.36) --
+	(202.48,322.38) --
+	(205.73,324.43) --
+	(208.97,326.51) --
+	(212.21,328.63) --
+	(215.46,330.77) --
+	(218.70,332.96) --
+	(221.95,335.18) --
+	(225.19,337.44) --
+	(228.43,339.73) --
+	(231.68,342.05) --
+	(234.92,344.41) --
+	(238.17,346.80) --
+	(241.41,349.22) --
+	(244.65,351.67) --
+	(247.90,354.15) --
+	(251.14,356.67) --
+	(254.39,359.22) --
+	(257.63,361.81) --
+	(260.87,364.43) --
+	(264.12,367.08) --
+	(267.36,369.77) --
+	(270.60,372.48) --
+	(273.85,375.24) --
+	(277.09,378.02) --
+	(280.34,380.84) --
+	(283.58,383.69);
 \definecolor{fillColor}{RGB}{230,159,0}
@@
 
-\path[fill=fillColor] ( 35.86,253.72) --
-	( 39.22,247.89) --
-	( 32.49,247.89) --
-	cycle;
-
-\path[fill=fillColor] ( 44.40,256.16) --
-	( 47.76,250.34) --
-	( 41.03,250.34) --
-	cycle;
-
-\path[fill=fillColor] ( 52.94,258.73) --
-	( 56.30,252.90) --
-	( 49.58,252.90) --
-	cycle;
-
-\path[fill=fillColor] ( 61.48,261.41) --
-	( 64.85,255.58) --
-	( 58.12,255.58) --
-	cycle;
-
-\path[fill=fillColor] ( 70.02,264.21) --
-	( 73.39,258.38) --
-	( 66.66,258.38) --
-	cycle;
-
-\path[fill=fillColor] ( 78.57,267.14) --
-	( 81.93,261.31) --
-	( 75.20,261.31) --
-	cycle;
-
-\path[fill=fillColor] ( 87.11,270.19) --
-	( 90.47,264.37) --
-	( 83.75,264.37) --
-	cycle;
-
-\path[fill=fillColor] ( 95.65,273.40) --
-	( 99.01,267.58) --
-	( 92.29,267.58) --
-	cycle;
-
-\path[fill=fillColor] (104.19,276.77) --
-	(107.56,270.94) --
-	(100.83,270.94) --
-	cycle;
-
-\path[fill=fillColor] (112.74,280.26) --
-	(116.10,274.43) --
-	(109.37,274.43) --
-	cycle;
-
-\path[fill=fillColor] (121.28,283.89) --
-	(124.64,278.06) --
-	(117.91,278.06) --
-	cycle;
-
-\path[fill=fillColor] (129.82,287.67) --
-	(133.18,281.85) --
-	(126.46,281.85) --
-	cycle;
-
-\path[fill=fillColor] (138.36,291.63) --
-	(141.73,285.80) --
-	(135.00,285.80) --
-	cycle;
-
-\path[fill=fillColor] (146.90,295.78) --
-	(150.27,289.96) --
-	(143.54,289.96) --
-	cycle;
-
-\path[fill=fillColor] (155.45,300.06) --
-	(158.81,294.24) --
-	(152.08,294.24) --
-	cycle;
-
-\path[fill=fillColor] (163.99,304.54) --
-	(167.35,298.72) --
-	(160.63,298.72) --
-	cycle;
-
-\path[fill=fillColor] (172.53,309.20) --
-	(175.89,303.38) --
-	(169.17,303.38) --
-	cycle;
-
-\path[fill=fillColor] (181.07,314.20) --
-	(184.44,308.38) --
-	(177.71,308.38) --
-	cycle;
-
-\path[fill=fillColor] (189.62,319.33) --
-	(192.98,313.51) --
-	(186.25,313.51) --
-	cycle;
-
-\path[fill=fillColor] (198.16,324.68) --
-	(201.52,318.86) --
-	(194.79,318.86) --
-	cycle;
-
-\path[fill=fillColor] (206.70,330.22) --
-	(210.06,324.39) --
-	(203.34,324.39) --
-	cycle;
-
-\path[fill=fillColor] (215.24,336.05) --
-	(218.61,330.22) --
-	(211.88,330.22) --
-	cycle;
-
-\path[fill=fillColor] (223.78,342.17) --
-	(227.15,336.34) --
-	(220.42,336.34) --
-	cycle;
-
-\path[fill=fillColor] (232.33,348.47) --
-	(235.69,342.65) --
-	(228.96,342.65) --
-	cycle;
-
-\path[fill=fillColor] (240.87,355.10) --
-	(244.23,349.27) --
-	(237.51,349.27) --
-	cycle;
-
-\path[fill=fillColor] (249.41,361.97) --
-	(252.77,356.14) --
-	(246.05,356.14) --
-	cycle;
-
-\path[fill=fillColor] (257.95,369.32) --
-	(261.32,363.50) --
-	(254.59,363.50) --
-	cycle;
-
-\path[fill=fillColor] (266.50,376.85) --
-	(269.86,371.02) --
-	(263.13,371.02) --
-	cycle;
-
-\path[fill=fillColor] (275.04,384.53) --
-	(278.40,378.70) --
-	(271.67,378.70) --
-	cycle;
-
-\path[fill=fillColor] (283.58,392.80) --
-	(286.94,386.97) --
-	(280.22,386.97) --
+\path[fill=fillColor] ( 35.86,253.77) --
+	( 39.22,247.94) --
+	( 32.49,247.94) --
+	cycle;
+
+\path[fill=fillColor] ( 44.40,256.26) --
+	( 47.76,250.43) --
+	( 41.03,250.43) --
+	cycle;
+
+\path[fill=fillColor] ( 52.94,258.86) --
+	( 56.30,253.03) --
+	( 49.58,253.03) --
+	cycle;
+
+\path[fill=fillColor] ( 61.48,261.57) --
+	( 64.85,255.75) --
+	( 58.12,255.75) --
+	cycle;
+
+\path[fill=fillColor] ( 70.02,264.40) --
+	( 73.39,258.58) --
+	( 66.66,258.58) --
+	cycle;
+
+\path[fill=fillColor] ( 78.57,267.35) --
+	( 81.93,261.52) --
+	( 75.20,261.52) --
+	cycle;
+
+\path[fill=fillColor] ( 87.11,270.41) --
+	( 90.47,264.59) --
+	( 83.75,264.59) --
+	cycle;
+
+\path[fill=fillColor] ( 95.65,273.62) --
+	( 99.01,267.79) --
+	( 92.29,267.79) --
+	cycle;
+
+\path[fill=fillColor] (104.19,276.97) --
+	(107.56,271.14) --
+	(100.83,271.14) --
+	cycle;
+
+\path[fill=fillColor] (112.74,280.44) --
+	(116.10,274.61) --
+	(109.37,274.61) --
+	cycle;
+
+\path[fill=fillColor] (121.28,284.03) --
+	(124.64,278.21) --
+	(117.91,278.21) --
+	cycle;
+
+\path[fill=fillColor] (129.82,287.77) --
+	(133.18,281.94) --
+	(126.46,281.94) --
+	cycle;
+
+\path[fill=fillColor] (138.36,291.66) --
+	(141.73,285.83) --
+	(135.00,285.83) --
+	cycle;
+
+\path[fill=fillColor] (146.90,295.73) --
+	(150.27,289.90) --
+	(143.54,289.90) --
+	cycle;
+
+\path[fill=fillColor] (155.45,299.91) --
+	(158.81,294.09) --
+	(152.08,294.09) --
+	cycle;
+
+\path[fill=fillColor] (163.99,304.28) --
+	(167.35,298.45) --
+	(160.63,298.45) --
+	cycle;
+
+\path[fill=fillColor] (172.53,308.80) --
+	(175.89,302.97) --
+	(169.17,302.97) --
+	cycle;
+
+\path[fill=fillColor] (181.07,313.61) --
+	(184.44,307.78) --
+	(177.71,307.78) --
+	cycle;
+
+\path[fill=fillColor] (189.62,318.54) --
+	(192.98,312.71) --
+	(186.25,312.71) --
+	cycle;
+
+\path[fill=fillColor] (198.16,323.65) --
+	(201.52,317.83) --
+	(194.79,317.83) --
+	cycle;
+
+\path[fill=fillColor] (206.70,328.94) --
+	(210.06,323.11) --
+	(203.34,323.11) --
+	cycle;
+
+\path[fill=fillColor] (215.24,334.46) --
+	(218.61,328.63) --
+	(211.88,328.63) --
+	cycle;
+
+\path[fill=fillColor] (223.78,340.25) --
+	(227.15,334.42) --
+	(220.42,334.42) --
+	cycle;
+
+\path[fill=fillColor] (232.33,346.20) --
+	(235.69,340.38) --
+	(228.96,340.38) --
+	cycle;
+
+\path[fill=fillColor] (240.87,352.40) --
+	(244.23,346.58) --
+	(237.51,346.58) --
+	cycle;
+
+\path[fill=fillColor] (249.41,358.80) --
+	(252.77,352.98) --
+	(246.05,352.98) --
+	cycle;
+
+\path[fill=fillColor] (257.95,365.62) --
+	(261.32,359.79) --
+	(254.59,359.79) --
+	cycle;
+
+\path[fill=fillColor] (266.50,372.58) --
+	(269.86,366.75) --
+	(263.13,366.75) --
+	cycle;
+
+\path[fill=fillColor] (275.04,379.67) --
+	(278.40,373.84) --
+	(271.67,373.84) --
+	cycle;
+
+\path[fill=fillColor] (283.58,387.25) --
+	(286.94,381.43) --
+	(280.22,381.43) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 33.36,247.34) --
-	( 38.35,247.34) --
-	( 38.35,252.33) --
-	( 33.36,252.33) --
-	cycle;
-
-\path[fill=fillColor] ( 41.90,249.78) --
-	( 46.90,249.78) --
-	( 46.90,254.78) --
-	( 41.90,254.78) --
-	cycle;
-
-\path[fill=fillColor] ( 50.44,252.35) --
-	( 55.44,252.35) --
-	( 55.44,257.34) --
-	( 50.44,257.34) --
-	cycle;
-
-\path[fill=fillColor] ( 58.98,255.03) --
-	( 63.98,255.03) --
-	( 63.98,260.02) --
-	( 58.98,260.02) --
-	cycle;
-
-\path[fill=fillColor] ( 67.53,257.83) --
-	( 72.52,257.83) --
-	( 72.52,262.83) --
-	( 67.53,262.83) --
-	cycle;
-
-\path[fill=fillColor] ( 76.07,260.76) --
-	( 81.06,260.76) --
-	( 81.06,265.75) --
-	( 76.07,265.75) --
-	cycle;
-
-\path[fill=fillColor] ( 84.61,263.82) --
-	( 89.61,263.82) --
-	( 89.61,268.81) --
-	( 84.61,268.81) --
-	cycle;
-
-\path[fill=fillColor] ( 93.15,267.03) --
-	( 98.15,267.03) --
-	( 98.15,272.03) --
-	( 93.15,272.03) --
-	cycle;
-
-\path[fill=fillColor] (101.70,270.41) --
-	(106.69,270.41) --
-	(106.69,275.40) --
-	(101.70,275.40) --
-	cycle;
-
-\path[fill=fillColor] (110.24,273.89) --
-	(115.23,273.89) --
-	(115.23,278.89) --
-	(110.24,278.89) --
-	cycle;
-
-\path[fill=fillColor] (118.78,277.52) --
-	(123.78,277.52) --
-	(123.78,282.51) --
-	(118.78,282.51) --
-	cycle;
-
-\path[fill=fillColor] (127.32,281.30) --
-	(132.32,281.30) --
-	(132.32,286.30) --
-	(127.32,286.30) --
-	cycle;
-
-\path[fill=fillColor] (135.86,285.26) --
-	(140.86,285.26) --
-	(140.86,290.25) --
-	(135.86,290.25) --
-	cycle;
-
-\path[fill=fillColor] (144.41,289.41) --
-	(149.40,289.41) --
-	(149.40,294.41) --
-	(144.41,294.41) --
-	cycle;
-
-\path[fill=fillColor] (152.95,293.67) --
-	(157.94,293.67) --
-	(157.94,298.67) --
-	(152.95,298.67) --
-	cycle;
-
-\path[fill=fillColor] (161.49,298.13) --
-	(166.49,298.13) --
-	(166.49,303.13) --
-	(161.49,303.13) --
-	cycle;
-
-\path[fill=fillColor] (170.03,302.76) --
-	(175.03,302.76) --
-	(175.03,307.76) --
-	(170.03,307.76) --
-	cycle;
-
-\path[fill=fillColor] (178.58,307.80) --
-	(183.57,307.80) --
-	(183.57,312.80) --
-	(178.58,312.80) --
-	cycle;
-
-\path[fill=fillColor] (187.12,312.93) --
-	(192.11,312.93) --
-	(192.11,317.93) --
-	(187.12,317.93) --
-	cycle;
-
-\path[fill=fillColor] (195.66,318.29) --
-	(200.66,318.29) --
-	(200.66,323.28) --
-	(195.66,323.28) --
-	cycle;
-
-\path[fill=fillColor] (204.20,323.80) --
-	(209.20,323.80) --
-	(209.20,328.79) --
-	(204.20,328.79) --
-	cycle;
-
-\path[fill=fillColor] (212.74,329.65) --
-	(217.74,329.65) --
-	(217.74,334.64) --
-	(212.74,334.64) --
-	cycle;
-
-\path[fill=fillColor] (221.29,335.78) --
-	(226.28,335.78) --
-	(226.28,340.78) --
-	(221.29,340.78) --
-	cycle;
-
-\path[fill=fillColor] (229.83,342.05) --
-	(234.82,342.05) --
-	(234.82,347.05) --
-	(229.83,347.05) --
-	cycle;
-
-\path[fill=fillColor] (238.37,348.70) --
-	(243.37,348.70) --
-	(243.37,353.69) --
-	(238.37,353.69) --
-	cycle;
-
-\path[fill=fillColor] (246.91,355.61) --
-	(251.91,355.61) --
-	(251.91,360.60) --
-	(246.91,360.60) --
-	cycle;
-
-\path[fill=fillColor] (255.46,363.10) --
-	(260.45,363.10) --
-	(260.45,368.10) --
-	(255.46,368.10) --
-	cycle;
-
-\path[fill=fillColor] (264.00,370.65) --
-	(268.99,370.65) --
-	(268.99,375.65) --
-	(264.00,375.65) --
-	cycle;
-
-\path[fill=fillColor] (272.54,378.27) --
-	(277.54,378.27) --
-	(277.54,383.27) --
-	(272.54,383.27) --
-	cycle;
-
-\path[fill=fillColor] (281.08,386.62) --
-	(286.08,386.62) --
-	(286.08,391.61) --
-	(281.08,391.61) --
+\path[fill=fillColor] ( 33.36,247.39) --
+	( 38.35,247.39) --
+	( 38.35,252.38) --
+	( 33.36,252.38) --
+	cycle;
+
+\path[fill=fillColor] ( 41.90,249.87) --
+	( 46.90,249.87) --
+	( 46.90,254.87) --
+	( 41.90,254.87) --
+	cycle;
+
+\path[fill=fillColor] ( 50.44,252.48) --
+	( 55.44,252.48) --
+	( 55.44,257.47) --
+	( 50.44,257.47) --
+	cycle;
+
+\path[fill=fillColor] ( 58.98,255.19) --
+	( 63.98,255.19) --
+	( 63.98,260.19) --
+	( 58.98,260.19) --
+	cycle;
+
+\path[fill=fillColor] ( 67.53,258.02) --
+	( 72.52,258.02) --
+	( 72.52,263.02) --
+	( 67.53,263.02) --
+	cycle;
+
+\path[fill=fillColor] ( 76.07,260.97) --
+	( 81.06,260.97) --
+	( 81.06,265.96) --
+	( 76.07,265.96) --
+	cycle;
+
+\path[fill=fillColor] ( 84.61,264.04) --
+	( 89.61,264.04) --
+	( 89.61,269.03) --
+	( 84.61,269.03) --
+	cycle;
+
+\path[fill=fillColor] ( 93.15,267.25) --
+	( 98.15,267.25) --
+	( 98.15,272.25) --
+	( 93.15,272.25) --
+	cycle;
+
+\path[fill=fillColor] (101.70,270.62) --
+	(106.69,270.62) --
+	(106.69,275.61) --
+	(101.70,275.61) --
+	cycle;
+
+\path[fill=fillColor] (110.24,274.08) --
+	(115.23,274.08) --
+	(115.23,279.08) --
+	(110.24,279.08) --
+	cycle;
+
+\path[fill=fillColor] (118.78,277.67) --
+	(123.78,277.67) --
+	(123.78,282.67) --
+	(118.78,282.67) --
+	cycle;
+
+\path[fill=fillColor] (127.32,281.40) --
+	(132.32,281.40) --
+	(132.32,286.40) --
+	(127.32,286.40) --
+	cycle;
+
+\path[fill=fillColor] (135.86,285.29) --
+	(140.86,285.29) --
+	(140.86,290.28) --
+	(135.86,290.28) --
+	cycle;
+
+\path[fill=fillColor] (144.41,289.36) --
+	(149.40,289.36) --
+	(149.40,294.36) --
+	(144.41,294.36) --
+	cycle;
+
+\path[fill=fillColor] (152.95,293.52) --
+	(157.94,293.52) --
+	(157.94,298.51) --
+	(152.95,298.51) --
+	cycle;
+
+\path[fill=fillColor] (161.49,297.85) --
+	(166.49,297.85) --
+	(166.49,302.85) --
+	(161.49,302.85) --
+	cycle;
+
+\path[fill=fillColor] (170.03,302.34) --
+	(175.03,302.34) --
+	(175.03,307.33) --
+	(170.03,307.33) --
+	cycle;
+
+\path[fill=fillColor] (178.58,307.20) --
+	(183.57,307.20) --
+	(183.57,312.19) --
+	(178.58,312.19) --
+	cycle;
+
+\path[fill=fillColor] (187.12,312.13) --
+	(192.11,312.13) --
+	(192.11,317.12) --
+	(187.12,317.12) --
+	cycle;
+
+\path[fill=fillColor] (195.66,317.25) --
+	(200.66,317.25) --
+	(200.66,322.24) --
+	(195.66,322.24) --
+	cycle;
+
+\path[fill=fillColor] (204.20,322.50) --
+	(209.20,322.50) --
+	(209.20,327.49) --
+	(204.20,327.49) --
+	cycle;
+
+\path[fill=fillColor] (212.74,328.04) --
+	(217.74,328.04) --
+	(217.74,333.04) --
+	(212.74,333.04) --
+	cycle;
+
+\path[fill=fillColor] (221.29,333.85) --
+	(226.28,333.85) --
+	(226.28,338.85) --
+	(221.29,338.85) --
+	cycle;
+
+\path[fill=fillColor] (229.83,339.77) --
+	(234.82,339.77) --
+	(234.82,344.76) --
+	(229.83,344.76) --
+	cycle;
+
+\path[fill=fillColor] (238.37,345.99) --
+	(243.37,345.99) --
+	(243.37,350.98) --
+	(238.37,350.98) --
+	cycle;
+
+\path[fill=fillColor] (246.91,352.43) --
+	(251.91,352.43) --
+	(251.91,357.43) --
+	(246.91,357.43) --
+	cycle;
+
+\path[fill=fillColor] (255.46,359.42) --
+	(260.45,359.42) --
+	(260.45,364.42) --
+	(255.46,364.42) --
+	cycle;
+
+\path[fill=fillColor] (264.00,366.41) --
+	(268.99,366.41) --
+	(268.99,371.40) --
+	(264.00,371.40) --
+	cycle;
+
+\path[fill=fillColor] (272.54,373.42) --
+	(277.54,373.42) --
+	(277.54,378.41) --
+	(272.54,378.41) --
+	cycle;
+
+\path[fill=fillColor] (281.08,381.10) --
+	(286.08,381.10) --
+	(286.08,386.09) --
+	(281.08,386.09) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32,249.83) -- ( 39.39,249.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86,246.30) -- ( 35.86,253.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87,252.27) -- ( 47.93,252.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.74) -- ( 44.40,255.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41,254.84) -- ( 56.47,254.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94,251.31) -- ( 52.94,258.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95,257.52) -- ( 65.01,257.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48,253.99) -- ( 61.48,261.05);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.33) -- ( 73.56,260.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02,256.79) -- ( 70.02,263.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,263.25) -- ( 82.10,263.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57,259.72) -- ( 78.57,266.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.32) -- ( 90.64,266.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,262.78) -- ( 87.11,269.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.54) -- ( 99.18,269.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,266.00) -- ( 95.65,273.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,272.92) -- (107.73,272.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,269.39) -- (104.19,276.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.41) -- (116.27,276.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,272.87) -- (112.74,279.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,280.03) -- (124.81,280.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.49) -- (121.28,283.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.81) -- (133.35,283.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.27) -- (129.82,287.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.76) -- (141.89,287.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,284.23) -- (138.36,291.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.93) -- (150.44,291.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.39) -- (146.90,295.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,296.17) -- (158.98,296.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,292.64) -- (155.45,299.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.60) -- (167.52,300.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,297.07) -- (163.99,304.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,305.21) -- (176.06,305.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.68) -- (172.53,308.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,310.29) -- (184.61,310.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.76) -- (181.07,313.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,315.42) -- (193.15,315.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.89) -- (189.62,318.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,320.79) -- (201.69,320.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,317.26) -- (198.16,324.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,326.28) -- (210.23,326.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,322.74) -- (206.70,329.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,332.15) -- (218.77,332.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,328.62) -- (215.24,335.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,338.30) -- (227.32,338.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,334.76) -- (223.78,341.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,344.53) -- (235.86,344.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,341.00) -- (232.33,348.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,351.21) -- (244.40,351.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,347.68) -- (240.87,354.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,358.17) -- (252.94,358.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,354.64) -- (249.41,361.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,365.83) -- (261.49,365.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,362.30) -- (257.95,369.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,373.41) -- (270.03,373.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,369.87) -- (266.50,376.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,380.97) -- (278.57,380.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,377.44) -- (275.04,384.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,389.39) -- (287.11,389.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,385.85) -- (283.58,392.92);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32,249.88) -- ( 39.39,249.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86,246.35) -- ( 35.86,253.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87,252.37) -- ( 47.93,252.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.83) -- ( 44.40,255.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41,254.97) -- ( 56.47,254.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94,251.44) -- ( 52.94,258.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95,257.69) -- ( 65.01,257.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48,254.15) -- ( 61.48,261.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.52) -- ( 73.56,260.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02,256.98) -- ( 70.02,264.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,263.46) -- ( 82.10,263.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57,259.93) -- ( 78.57,266.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.54) -- ( 90.64,266.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,263.01) -- ( 87.11,270.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.76) -- ( 99.18,269.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,266.23) -- ( 95.65,273.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,273.14) -- (107.73,273.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,269.61) -- (104.19,276.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.60) -- (116.27,276.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,273.07) -- (112.74,280.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,280.18) -- (124.81,280.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.65) -- (121.28,283.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.91) -- (133.35,283.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.38) -- (129.82,287.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.80) -- (141.89,287.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,284.26) -- (138.36,291.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.88) -- (150.44,291.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.34) -- (146.90,295.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,296.01) -- (158.98,296.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,292.47) -- (155.45,299.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.31) -- (167.52,300.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,296.78) -- (163.99,303.84);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.77) -- (176.06,304.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.23) -- (172.53,308.30);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.68) -- (184.61,309.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.15) -- (181.07,313.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,314.61) -- (193.15,314.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.08) -- (189.62,318.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,319.74) -- (201.69,319.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,316.21) -- (198.16,323.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,324.96) -- (210.23,324.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,321.43) -- (206.70,328.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.54) -- (218.77,330.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,327.01) -- (215.24,334.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,336.37) -- (227.32,336.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,332.83) -- (223.78,339.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,342.23) -- (235.86,342.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,338.70) -- (232.33,345.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,348.49) -- (244.40,348.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,344.96) -- (240.87,352.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,355.00) -- (252.94,355.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,351.47) -- (249.41,358.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,362.19) -- (261.49,362.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,358.66) -- (257.95,365.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,369.22) -- (270.03,369.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,365.69) -- (266.50,372.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,376.15) -- (278.57,376.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,372.62) -- (275.04,379.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,383.92) -- (287.11,383.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,380.39) -- (283.58,387.45);
 \definecolor{fillColor}{RGB}{0,0,0}
@@
 
-\path[fill=fillColor] ( 35.86,249.83) circle (  2.50);
-
-\path[fill=fillColor] ( 44.40,252.27) circle (  2.50);
-
-\path[fill=fillColor] ( 52.94,254.82) circle (  2.50);
-
-\path[fill=fillColor] ( 61.48,257.51) circle (  2.50);
-
-\path[fill=fillColor] ( 70.02,260.28) circle (  2.50);
-
-\path[fill=fillColor] ( 78.57,263.20) circle (  2.50);
-
-\path[fill=fillColor] ( 87.11,266.27) circle (  2.50);
-
-\path[fill=fillColor] ( 95.65,269.43) circle (  2.50);
-
-\path[fill=fillColor] (104.19,272.79) circle (  2.50);
-
-\path[fill=fillColor] (112.74,276.24) circle (  2.50);
-
-\path[fill=fillColor] (121.28,279.86) circle (  2.50);
-
-\path[fill=fillColor] (129.82,283.67) circle (  2.50);
-
-\path[fill=fillColor] (138.36,287.69) circle (  2.50);
-
-\path[fill=fillColor] (146.90,291.76) circle (  2.50);
-
-\path[fill=fillColor] (155.45,296.17) circle (  2.50);
-
-\path[fill=fillColor] (163.99,300.71) circle (  2.50);
-
-\path[fill=fillColor] (172.53,305.39) circle (  2.50);
-
-\path[fill=fillColor] (181.07,310.31) circle (  2.50);
-
-\path[fill=fillColor] (189.62,315.41) circle (  2.50);
-
-\path[fill=fillColor] (198.16,320.80) circle (  2.50);
-
-\path[fill=fillColor] (206.70,326.25) circle (  2.50);
-
-\path[fill=fillColor] (215.24,332.23) circle (  2.50);
-
-\path[fill=fillColor] (223.78,338.13) circle (  2.50);
-
-\path[fill=fillColor] (232.33,344.44) circle (  2.50);
-
-\path[fill=fillColor] (240.87,351.38) circle (  2.50);
-
-\path[fill=fillColor] (249.41,358.30) circle (  2.50);
-
-\path[fill=fillColor] (257.95,365.26) circle (  2.50);
-
-\path[fill=fillColor] (266.50,372.85) circle (  2.50);
-
-\path[fill=fillColor] (275.04,380.60) circle (  2.50);
-
-\path[fill=fillColor] (283.58,388.73) circle (  2.50);
+\path[fill=fillColor] ( 35.86,249.88) circle (  2.50);
+
+\path[fill=fillColor] ( 44.40,252.37) circle (  2.50);
+
+\path[fill=fillColor] ( 52.94,254.94) circle (  2.50);
+
+\path[fill=fillColor] ( 61.48,257.68) circle (  2.50);
+
+\path[fill=fillColor] ( 70.02,260.47) circle (  2.50);
+
+\path[fill=fillColor] ( 78.57,263.41) circle (  2.50);
+
+\path[fill=fillColor] ( 87.11,266.50) circle (  2.50);
+
+\path[fill=fillColor] ( 95.65,269.65) circle (  2.50);
+
+\path[fill=fillColor] (104.19,273.00) circle (  2.50);
+
+\path[fill=fillColor] (112.74,276.42) circle (  2.50);
+
+\path[fill=fillColor] (121.28,279.99) circle (  2.50);
+
+\path[fill=fillColor] (129.82,283.76) circle (  2.50);
+
+\path[fill=fillColor] (138.36,287.74) circle (  2.50);
+
+\path[fill=fillColor] (146.90,291.70) circle (  2.50);
+
+\path[fill=fillColor] (155.45,296.03) circle (  2.50);
+
+\path[fill=fillColor] (163.99,300.46) circle (  2.50);
+
+\path[fill=fillColor] (172.53,304.98) circle (  2.50);
+
+\path[fill=fillColor] (181.07,309.73) circle (  2.50);
+
+\path[fill=fillColor] (189.62,314.62) circle (  2.50);
+
+\path[fill=fillColor] (198.16,319.79) circle (  2.50);
+
+\path[fill=fillColor] (206.70,324.93) circle (  2.50);
+
+\path[fill=fillColor] (215.24,330.66) circle (  2.50);
+
+\path[fill=fillColor] (223.78,336.18) circle (  2.50);
+
+\path[fill=fillColor] (232.33,342.09) circle (  2.50);
+
+\path[fill=fillColor] (240.87,348.75) circle (  2.50);
+
+\path[fill=fillColor] (249.41,355.20) circle (  2.50);
+
+\path[fill=fillColor] (257.95,361.58) circle (  2.50);
+
+\path[fill=fillColor] (266.50,368.62) circle (  2.50);
+
+\path[fill=fillColor] (275.04,375.76) circle (  2.50);
+
+\path[fill=fillColor] (283.58,383.22) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (316.39,247.68) --
-	(319.64,248.50) --
-	(322.88,249.34) --
-	(326.12,250.20) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] (316.39,247.65) --
+	(319.64,248.49) --
+	(322.88,249.36) --
+	(326.12,250.25) --
+	(329.37,251.16) --
+	(332.61,252.08) --
+	(335.86,253.03) --
+	(339.10,254.00) --
+	(342.34,254.98) --
+	(345.59,255.98) --
+	(348.83,257.00) --
+	(352.08,258.04) --
+	(355.32,259.10) --
+	(358.56,260.18) --
+	(361.81,261.28) --
+	(365.05,262.40) --
+	(368.30,263.54) --
+	(371.54,264.70) --
+	(374.78,265.88) --
+	(378.03,267.07) --
+	(381.27,268.29) --
+	(384.51,269.52) --
+	(387.76,270.77) --
+	(391.00,272.04) --
+	(394.25,273.32) --
+	(397.49,274.63) --
+	(400.73,275.96) --
+	(403.98,277.31) --
+	(407.22,278.68) --
+	(410.47,280.08) --
+	(413.71,281.49) --
+	(416.95,282.93) --
+	(420.20,284.38) --
+	(423.44,285.85) --
+	(426.69,287.34) --
+	(429.93,288.85) --
+	(433.17,290.39) --
+	(436.42,291.96) --
+	(439.66,293.55) --
+	(442.90,295.17) --
+	(446.15,296.82) --
+	(449.39,298.48) --
+	(452.64,300.17) --
+	(455.88,301.88) --
+	(459.12,303.61) --
+	(462.37,305.37) --
+	(465.61,307.15) --
+	(468.86,308.96) --
+	(472.10,310.80) --
+	(475.34,312.67) --
+	(478.59,314.58) --
+	(481.83,316.51) --
+	(485.08,318.47) --
+	(488.32,320.46) --
+	(491.56,322.47) --
+	(494.81,324.51) --
+	(498.05,326.58) --
+	(501.29,328.68) --
+	(504.54,330.81) --
+	(507.78,332.98) --
+	(511.03,335.19) --
+	(514.27,337.43) --
+	(517.51,339.70) --
+	(520.76,342.00) --
+	(524.00,344.33) --
+	(527.25,346.69) --
+	(530.49,349.09) --
+	(533.73,351.51) --
+	(536.98,353.97) --
+	(540.22,356.45) --
+	(543.47,358.97) --
+	(546.71,361.52) --
+	(549.95,364.10) --
+	(553.20,366.72) --
+	(556.44,369.36) --
+	(559.68,372.04) --
+	(562.93,374.75) --
+	(566.17,377.49) --
+	(569.42,380.26) --
+	(572.66,383.06);
+\definecolor{drawColor}{RGB}{230,159,0}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (319.64,248.30) --
+	(322.88,249.24) --
+	(326.12,250.18) --
+	(329.37,251.12) --
+	(332.61,252.08) --
+	(335.86,253.04) --
+	(339.10,254.00) --
+	(342.34,254.98) --
+	(345.59,255.96) --
+	(348.83,256.94) --
+	(352.08,257.94) --
+	(355.32,258.94) --
+	(358.56,259.94) --
+	(361.81,260.95) --
+	(365.05,261.97) --
+	(368.30,263.00) --
+	(371.54,264.03) --
+	(374.78,265.06) --
+	(378.03,266.11) --
+	(381.27,267.16) --
+	(384.51,268.22) --
+	(387.76,269.28) --
+	(391.00,270.36) --
+	(394.25,271.44) --
+	(397.49,272.53) --
+	(400.73,273.62) --
+	(403.98,274.72) --
+	(407.22,275.82) --
+	(410.47,276.92) --
+	(413.71,278.03) --
+	(416.95,279.15) --
+	(420.20,280.28) --
+	(423.44,281.42) --
+	(426.69,282.56) --
+	(429.93,283.71) --
+	(433.17,284.85) --
+	(436.42,286.00) --
+	(439.66,287.14) --
+	(442.90,288.28) --
+	(446.15,289.41) --
+	(449.39,290.55) --
+	(452.64,291.70) --
+	(455.88,292.86) --
+	(459.12,294.02) --
+	(462.37,295.18) --
+	(465.61,296.34) --
+	(468.86,297.49) --
+	(472.10,298.64) --
+	(475.34,299.77) --
+	(478.59,300.88) --
+	(481.83,301.99) --
+	(485.08,303.10) --
+	(488.32,304.20) --
+	(491.56,305.31) --
+	(494.81,306.40) --
+	(498.05,307.49) --
+	(501.29,308.57) --
+	(504.54,309.63) --
+	(507.78,310.68) --
+	(511.03,311.72) --
+	(514.27,312.73) --
+	(517.51,313.74) --
+	(520.76,314.73) --
+	(524.00,315.72) --
+	(527.25,316.70) --
+	(530.49,317.67) --
+	(533.73,318.63) --
+	(536.98,319.58) --
+	(540.22,320.52) --
+	(543.47,321.45) --
+	(546.71,322.36) --
+	(549.95,323.27) --
+	(553.20,324.16) --
+	(556.44,325.04) --
+	(559.68,325.91) --
+	(562.93,326.77) --
+	(566.17,327.62) --
+	(569.42,328.46) --
+	(572.66,329.29);
+\definecolor{drawColor}{RGB}{86,180,233}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (319.64,248.18) --
+	(322.88,249.16) --
+	(326.12,250.13) --
 	(329.37,251.09) --
-	(332.61,251.99) --
-	(335.86,252.92) --
-	(339.10,253.86) --
-	(342.34,254.83) --
-	(345.59,255.81) --
-	(348.83,256.82) --
-	(352.08,257.85) --
-	(355.32,258.90) --
-	(358.56,259.97) --
-	(361.81,261.06) --
-	(365.05,262.17) --
-	(368.30,263.30) --
-	(371.54,264.46) --
-	(374.78,265.64) --
-	(378.03,266.84) --
-	(381.27,268.05) --
-	(384.51,269.29) --
-	(387.76,270.54) --
-	(391.00,271.81) --
-	(394.25,273.10) --
-	(397.49,274.42) --
-	(400.73,275.76) --
-	(403.98,277.12) --
-	(407.22,278.51) --
-	(410.47,279.93) --
-	(413.71,281.36) --
-	(416.95,282.81) --
-	(420.20,284.29) --
-	(423.44,285.78) --
-	(426.69,287.29) --
-	(429.93,288.83) --
-	(433.17,290.40) --
-	(436.42,292.00) --
-	(439.66,293.63) --
-	(442.90,295.29) --
-	(446.15,296.98) --
-	(449.39,298.70) --
-	(452.64,300.44) --
-	(455.88,302.19) --
-	(459.12,303.98) --
-	(462.37,305.79) --
-	(465.61,307.63) --
-	(468.86,309.51) --
-	(472.10,311.42) --
-	(475.34,313.37) --
-	(478.59,315.36) --
-	(481.83,317.38) --
-	(485.08,319.43) --
-	(488.32,321.51) --
-	(491.56,323.63) --
-	(494.81,325.77) --
-	(498.05,327.95) --
-	(501.29,330.17) --
-	(504.54,332.42) --
-	(507.78,334.72) --
-	(511.03,337.06) --
-	(514.27,339.44) --
-	(517.51,341.85) --
-	(520.76,344.31) --
-	(524.00,346.79) --
-	(527.25,349.31) --
-	(530.49,351.87) --
-	(533.73,354.47) --
-	(536.98,357.10) --
-	(540.22,359.77) --
-	(543.47,362.47) --
-	(546.71,365.21) --
-	(549.95,367.99) --
-	(553.20,370.81) --
-	(556.44,373.67) --
-	(559.68,376.56) --
-	(562.93,379.49) --
-	(566.17,382.45) --
-	(569.42,385.45) --
-	(572.66,388.49);
-\definecolor{drawColor}{RGB}{230,159,0}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (319.64,248.28) --
-	(322.88,249.19) --
-	(326.12,250.12) --
-	(329.37,251.04) --
-	(332.61,251.98) --
-	(335.86,252.92) --
-	(339.10,253.86) --
-	(342.34,254.82) --
-	(345.59,255.77) --
-	(348.83,256.74) --
-	(352.08,257.71) --
-	(355.32,258.69) --
-	(358.56,259.67) --
-	(361.81,260.66) --
-	(365.05,261.65) --
-	(368.30,262.65) --
-	(371.54,263.65) --
-	(374.78,264.66) --
-	(378.03,265.68) --
-	(381.27,266.70) --
-	(384.51,267.73) --
-	(387.76,268.77) --
-	(391.00,269.81) --
-	(394.25,270.86) --
-	(397.49,271.92) --
-	(400.73,272.98) --
-	(403.98,274.04) --
-	(407.22,275.11) --
-	(410.47,276.18) --
-	(413.71,277.25) --
-	(416.95,278.34) --
-	(420.20,279.43) --
-	(423.44,280.54) --
-	(426.69,281.64) --
-	(429.93,282.75) --
-	(433.17,283.86) --
-	(436.42,284.97) --
-	(439.66,286.07) --
-	(442.90,287.16) --
-	(446.15,288.24) --
-	(449.39,289.34) --
-	(452.64,290.44) --
-	(455.88,291.56) --
-	(459.12,292.67) --
-	(462.37,293.78) --
-	(465.61,294.89) --
-	(468.86,295.99) --
-	(472.10,297.07) --
-	(475.34,298.14) --
-	(478.59,299.19) --
-	(481.83,300.23) --
-	(485.08,301.27) --
-	(488.32,302.30) --
-	(491.56,303.33) --
-	(494.81,304.35) --
-	(498.05,305.36) --
-	(501.29,306.36) --
-	(504.54,307.33) --
-	(507.78,308.29) --
-	(511.03,309.23) --
-	(514.27,310.14) --
-	(517.51,311.04) --
-	(520.76,311.93) --
-	(524.00,312.80) --
-	(527.25,313.67) --
-	(530.49,314.51) --
-	(533.73,315.35) --
-	(536.98,316.17) --
-	(540.22,316.98) --
-	(543.47,317.77) --
-	(546.71,318.55) --
-	(549.95,319.31) --
-	(553.20,320.05) --
-	(556.44,320.78) --
-	(559.68,321.50) --
-	(562.93,322.20) --
-	(566.17,322.89) --
-	(569.42,323.56) --
-	(572.66,324.22);
-\definecolor{drawColor}{RGB}{86,180,233}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (319.64,248.18) --
-	(322.88,249.13) --
-	(326.12,250.07) --
-	(329.37,251.02) --
-	(332.61,251.97) --
-	(335.86,252.91) --
-	(339.10,253.86) --
-	(342.34,254.80) --
-	(345.59,255.75) --
-	(348.83,256.69) --
-	(352.08,257.64) --
-	(355.32,258.59) --
-	(358.56,259.53) --
-	(361.81,260.48) --
-	(365.05,261.42) --
-	(368.30,262.36) --
-	(371.54,263.30) --
-	(374.78,264.24) --
-	(378.03,265.18) --
-	(381.27,266.12) --
-	(384.51,267.07) --
-	(387.76,268.02) --
-	(391.00,268.97) --
-	(394.25,269.92) --
-	(397.49,270.86) --
-	(400.73,271.81) --
-	(403.98,272.75) --
-	(407.22,273.68) --
-	(410.47,274.60) --
-	(413.71,275.53) --
-	(416.95,276.46) --
-	(420.20,277.40) --
-	(423.44,278.34) --
-	(426.69,279.28) --
-	(429.93,280.21) --
+	(332.61,252.06) --
+	(335.86,253.02) --
+	(339.10,253.99) --
+	(342.34,254.95) --
+	(345.59,255.91) --
+	(348.83,256.87) --
+	(352.08,257.83) --
+	(355.32,258.78) --
+	(358.56,259.74) --
+	(361.81,260.69) --
+	(365.05,261.64) --
+	(368.30,262.58) --
+	(371.54,263.53) --
+	(374.78,264.47) --
+	(378.03,265.40) --
+	(381.27,266.35) --
+	(384.51,267.29) --
+	(387.76,268.24) --
+	(391.00,269.18) --
+	(394.25,270.13) --
+	(397.49,271.07) --
+	(400.73,272.00) --
+	(403.98,272.93) --
+	(407.22,273.85) --
+	(410.47,274.75) --
+	(413.71,275.66) --
+	(416.95,276.58) --
+	(420.20,277.50) --
+	(423.44,278.42) --
+	(426.69,279.33) --
+	(429.93,280.24) --
 	(433.17,281.13) --
-	(436.42,282.03) --
-	(439.66,282.92) --
-	(442.90,283.77) --
-	(446.15,284.61) --
-	(449.39,285.45) --
-	(452.64,286.29) --
-	(455.88,287.13) --
-	(459.12,287.97) --
-	(462.37,288.79) --
-	(465.61,289.59) --
-	(468.86,290.36) --
-	(472.10,291.11) --
-	(475.34,291.82) --
-	(478.59,292.49) --
-	(481.83,293.12) --
-	(485.08,293.74) --
-	(488.32,294.35) --
-	(491.56,294.93) --
-	(494.81,295.49) --
-	(498.05,296.02) --
-	(501.29,296.52) --
-	(504.54,296.98) --
-	(507.78,297.40) --
-	(511.03,297.78) --
-	(514.27,298.10) --
-	(517.51,298.40) --
-	(520.76,298.67) --
-	(524.00,298.90) --
-	(527.25,299.11) --
-	(530.49,299.28) --
-	(533.73,299.42) --
-	(536.98,299.53) --
-	(540.22,299.60) --
-	(543.47,299.64) --
-	(546.71,299.65) --
-	(549.95,299.62) --
-	(553.20,299.56) --
-	(556.44,299.46) --
-	(559.68,299.32) --
-	(562.93,299.16) --
-	(566.17,298.96) --
-	(569.42,298.72) --
-	(572.66,298.46);
+	(436.42,282.00) --
+	(439.66,282.86) --
+	(442.90,283.68) --
+	(446.15,284.48) --
+	(449.39,285.28) --
+	(452.64,286.08) --
+	(455.88,286.88) --
+	(459.12,287.67) --
+	(462.37,288.45) --
+	(465.61,289.20) --
+	(468.86,289.93) --
+	(472.10,290.62) --
+	(475.34,291.28) --
+	(478.59,291.89) --
+	(481.83,292.48) --
+	(485.08,293.04) --
+	(488.32,293.59) --
+	(491.56,294.11) --
+	(494.81,294.61) --
+	(498.05,295.08) --
+	(501.29,295.51) --
+	(504.54,295.91) --
+	(507.78,296.26) --
+	(511.03,296.58) --
+	(514.27,296.84) --
+	(517.51,297.07) --
+	(520.76,297.27) --
+	(524.00,297.44) --
+	(527.25,297.58) --
+	(530.49,297.68) --
+	(533.73,297.76) --
+	(536.98,297.79) --
+	(540.22,297.80) --
+	(543.47,297.77) --
+	(546.71,297.70) --
+	(549.95,297.60) --
+	(553.20,297.46) --
+	(556.44,297.29) --
+	(559.68,297.08) --
+	(562.93,296.84) --
+	(566.17,296.56) --
+	(569.42,296.25) --
+	(572.66,295.91);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (319.64,248.11) --
-	(322.88,249.08) --
-	(326.12,250.04) --
-	(329.37,251.00) --
-	(332.61,251.95) --
-	(335.86,252.90) --
-	(339.10,253.84) --
-	(342.34,254.78) --
-	(345.59,255.71) --
-	(348.83,256.63) --
-	(352.08,257.56) --
-	(355.32,258.47) --
-	(358.56,259.38) --
-	(361.81,260.28) --
-	(365.05,261.18) --
-	(368.30,262.07) --
-	(371.54,262.95) --
-	(374.78,263.83) --
-	(378.03,264.69) --
-	(381.27,265.56) --
-	(384.51,266.43) --
-	(387.76,267.30) --
-	(391.00,268.16) --
-	(394.25,269.02) --
-	(397.49,269.87) --
-	(400.73,270.71) --
-	(403.98,271.54) --
-	(407.22,272.35) --
-	(410.47,273.15) --
-	(413.71,273.94) --
-	(416.95,274.74) --
-	(420.20,275.54) --
-	(423.44,276.33) --
-	(426.69,277.12) --
-	(429.93,277.89) --
-	(433.17,278.64) --
-	(436.42,279.36) --
-	(439.66,280.06) --
-	(442.90,280.71) --
-	(446.15,281.34) --
-	(449.39,281.96) --
-	(452.64,282.57) --
-	(455.88,283.18) --
-	(459.12,283.78) --
-	(462.37,284.35) --
-	(465.61,284.89) --
-	(468.86,285.40) --
-	(472.10,285.86) --
-	(475.34,286.28) --
-	(478.59,286.64) --
-	(481.83,286.95) --
-	(485.08,287.25) --
-	(488.32,287.51) --
-	(491.56,287.75) --
-	(494.81,287.95) --
-	(498.05,288.11) --
-	(501.29,288.23) --
-	(504.54,288.30) --
-	(507.78,288.32) --
-	(511.03,288.28) --
-	(514.27,288.19) --
-	(517.51,288.05) --
-	(520.76,287.88) --
-	(524.00,287.67) --
-	(527.25,287.41) --
-	(530.49,287.11) --
-	(533.73,286.77) --
-	(536.98,286.39) --
-	(540.22,285.96) --
-	(543.47,285.49) --
-	(546.71,284.98) --
-	(549.95,284.41) --
-	(553.20,283.81) --
-	(556.44,283.16) --
-	(559.68,282.46) --
-	(562.93,281.72) --
-	(566.17,280.94) --
-	(569.42,280.11) --
-	(572.66,279.25);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (319.64,248.10) --
+	(322.88,249.10) --
+	(326.12,250.09) --
+	(329.37,251.07) --
+	(332.61,252.04) --
+	(335.86,253.00) --
+	(339.10,253.95) --
+	(342.34,254.90) --
+	(345.59,255.84) --
+	(348.83,256.77) --
+	(352.08,257.69) --
+	(355.32,258.61) --
+	(358.56,259.51) --
+	(361.81,260.41) --
+	(365.05,261.29) --
+	(368.30,262.17) --
+	(371.54,263.03) --
+	(374.78,263.89) --
+	(378.03,264.73) --
+	(381.27,265.58) --
+	(384.51,266.42) --
+	(387.76,267.26) --
+	(391.00,268.09) --
+	(394.25,268.91) --
+	(397.49,269.72) --
+	(400.73,270.52) --
+	(403.98,271.30) --
+	(407.22,272.06) --
+	(410.47,272.80) --
+	(413.71,273.54) --
+	(416.95,274.28) --
+	(420.20,275.02) --
+	(423.44,275.74) --
+	(426.69,276.46) --
+	(429.93,277.16) --
+	(433.17,277.83) --
+	(436.42,278.48) --
+	(439.66,279.09) --
+	(442.90,279.66) --
+	(446.15,280.19) --
+	(449.39,280.71) --
+	(452.64,281.23) --
+	(455.88,281.73) --
+	(459.12,282.22) --
+	(462.37,282.68) --
+	(465.61,283.10) --
+	(468.86,283.49) --
+	(472.10,283.84) --
+	(475.34,284.13) --
+	(478.59,284.37) --
+	(481.83,284.56) --
+	(485.08,284.73) --
+	(488.32,284.86) --
+	(491.56,284.96) --
+	(494.81,285.02) --
+	(498.05,285.04) --
+	(501.29,285.02) --
+	(504.54,284.95) --
+	(507.78,284.83) --
+	(511.03,284.65) --
+	(514.27,284.42) --
+	(517.51,284.15) --
+	(520.76,283.83) --
+	(524.00,283.47) --
+	(527.25,283.07) --
+	(530.49,282.63) --
+	(533.73,282.14) --
+	(536.98,281.61) --
+	(540.22,281.03) --
+	(543.47,280.41) --
+	(546.71,279.74) --
+	(549.95,279.03) --
+	(553.20,278.27) --
+	(556.44,277.46) --
+	(559.68,276.61) --
+	(562.93,275.72) --
+	(566.17,274.78) --
+	(569.42,273.79) --
+	(572.66,272.77);
 \definecolor{fillColor}{RGB}{230,159,0}
@@
 
-\path[fill=fillColor] (324.94,253.70) --
-	(328.30,247.88) --
-	(321.57,247.88) --
-	cycle;
-
-\path[fill=fillColor] (333.48,256.09) --
-	(336.84,250.27) --
-	(330.11,250.27) --
-	cycle;
-
-\path[fill=fillColor] (342.02,258.54) --
-	(345.38,252.71) --
-	(338.66,252.71) --
-	cycle;
-
-\path[fill=fillColor] (350.56,261.05) --
-	(353.93,255.22) --
-	(347.20,255.22) --
-	cycle;
-
-\path[fill=fillColor] (359.10,263.61) --
-	(362.47,257.79) --
-	(355.74,257.79) --
-	cycle;
-
-\path[fill=fillColor] (367.65,266.23) --
-	(371.01,260.40) --
-	(364.28,260.40) --
-	cycle;
-
-\path[fill=fillColor] (376.19,268.90) --
-	(379.55,263.07) --
-	(372.83,263.07) --
-	cycle;
-
-\path[fill=fillColor] (384.73,271.62) --
-	(388.09,265.79) --
-	(381.37,265.79) --
-	cycle;
-
-\path[fill=fillColor] (393.27,274.38) --
-	(396.64,268.55) --
-	(389.91,268.55) --
-	cycle;
-
-\path[fill=fillColor] (401.82,277.18) --
-	(405.18,271.35) --
-	(398.45,271.35) --
-	cycle;
-
-\path[fill=fillColor] (410.36,280.01) --
-	(413.72,274.19) --
-	(406.99,274.19) --
-	cycle;
-
-\path[fill=fillColor] (418.90,282.88) --
-	(422.26,277.05) --
-	(415.54,277.05) --
-	cycle;
-
-\path[fill=fillColor] (427.44,285.76) --
-	(430.81,279.94) --
-	(424.08,279.94) --
-	cycle;
-
-\path[fill=fillColor] (435.98,288.66) --
-	(439.35,282.84) --
-	(432.62,282.84) --
-	cycle;
-
-\path[fill=fillColor] (444.53,291.57) --
-	(447.89,285.74) --
-	(441.16,285.74) --
-	cycle;
-
-\path[fill=fillColor] (453.07,294.48) --
-	(456.43,288.65) --
-	(449.71,288.65) --
-	cycle;
-
-\path[fill=fillColor] (461.61,297.37) --
-	(464.97,291.55) --
-	(458.25,291.55) --
-	cycle;
-
-\path[fill=fillColor] (470.15,300.25) --
-	(473.52,294.42) --
-	(466.79,294.42) --
-	cycle;
-
-\path[fill=fillColor] (478.70,303.09) --
-	(482.06,297.26) --
-	(475.33,297.26) --
-	cycle;
-
-\path[fill=fillColor] (487.24,305.88) --
-	(490.60,300.06) --
-	(483.87,300.06) --
-	cycle;
-
-\path[fill=fillColor] (495.78,308.62) --
-	(499.14,302.79) --
-	(492.42,302.79) --
-	cycle;
-
-\path[fill=fillColor] (504.32,311.28) --
-	(507.69,305.46) --
-	(500.96,305.46) --
-	cycle;
-
-\path[fill=fillColor] (512.86,313.85) --
-	(516.23,308.03) --
-	(509.50,308.03) --
-	cycle;
-
-\path[fill=fillColor] (521.41,316.31) --
-	(524.77,310.49) --
-	(518.04,310.49) --
-	cycle;
-
-\path[fill=fillColor] (529.95,318.64) --
-	(533.31,312.82) --
-	(526.59,312.82) --
-	cycle;
-
-\path[fill=fillColor] (538.49,320.82) --
-	(541.85,314.99) --
-	(535.13,314.99) --
-	cycle;
-
-\path[fill=fillColor] (547.03,322.82) --
-	(550.40,317.00) --
-	(543.67,317.00) --
-	cycle;
-
-\path[fill=fillColor] (555.58,324.63) --
-	(558.94,318.80) --
-	(552.21,318.80) --
-	cycle;
-
-\path[fill=fillColor] (564.12,326.21) --
-	(567.48,320.38) --
-	(560.75,320.38) --
-	cycle;
-
-\path[fill=fillColor] (572.66,327.53) --
-	(576.02,321.70) --
-	(569.30,321.70) --
+\path[fill=fillColor] (324.94,253.76) --
+	(328.30,247.93) --
+	(321.57,247.93) --
+	cycle;
+
+\path[fill=fillColor] (333.48,256.20) --
+	(336.84,250.37) --
+	(330.11,250.37) --
+	cycle;
+
+\path[fill=fillColor] (342.02,258.70) --
+	(345.38,252.88) --
+	(338.66,252.88) --
+	cycle;
+
+\path[fill=fillColor] (350.56,261.27) --
+	(353.93,255.45) --
+	(347.20,255.45) --
+	cycle;
+
+\path[fill=fillColor] (359.10,263.90) --
+	(362.47,258.07) --
+	(355.74,258.07) --
+	cycle;
+
+\path[fill=fillColor] (367.65,266.58) --
+	(371.01,260.76) --
+	(364.28,260.76) --
+	cycle;
+
+\path[fill=fillColor] (376.19,269.32) --
+	(379.55,263.50) --
+	(372.83,263.50) --
+	cycle;
+
+\path[fill=fillColor] (384.73,272.11) --
+	(388.09,266.29) --
+	(381.37,266.29) --
+	cycle;
+
+\path[fill=fillColor] (393.27,274.95) --
+	(396.64,269.13) --
+	(389.91,269.13) --
+	cycle;
+
+\path[fill=fillColor] (401.82,277.83) --
+	(405.18,272.01) --
+	(398.45,272.01) --
+	cycle;
+
+\path[fill=fillColor] (410.36,280.75) --
+	(413.72,274.93) --
+	(406.99,274.93) --
+	cycle;
+
+\path[fill=fillColor] (418.90,283.71) --
+	(422.26,277.88) --
+	(415.54,277.88) --
+	cycle;
+
+\path[fill=fillColor] (427.44,286.69) --
+	(430.81,280.87) --
+	(424.08,280.87) --
+	cycle;
+
+\path[fill=fillColor] (435.98,289.70) --
+	(439.35,283.87) --
+	(432.62,283.87) --
+	cycle;
+
+\path[fill=fillColor] (444.53,292.72) --
+	(447.89,286.89) --
+	(441.16,286.89) --
+	cycle;
+
+\path[fill=fillColor] (453.07,295.74) --
+	(456.43,289.92) --
+	(449.71,289.92) --
+	cycle;
+
+\path[fill=fillColor] (461.61,298.77) --
+	(464.97,292.94) --
+	(458.25,292.94) --
+	cycle;
+
+\path[fill=fillColor] (470.15,301.79) --
+	(473.52,295.96) --
+	(466.79,295.96) --
+	cycle;
+
+\path[fill=fillColor] (478.70,304.79) --
+	(482.06,298.96) --
+	(475.33,298.96) --
+	cycle;
+
+\path[fill=fillColor] (487.24,307.75) --
+	(490.60,301.93) --
+	(483.87,301.93) --
+	cycle;
+
+\path[fill=fillColor] (495.78,310.68) --
+	(499.14,304.85) --
+	(492.42,304.85) --
+	cycle;
+
+\path[fill=fillColor] (504.32,313.55) --
+	(507.69,307.73) --
+	(500.96,307.73) --
+	cycle;
+
+\path[fill=fillColor] (512.86,316.36) --
+	(516.23,310.53) --
+	(509.50,310.53) --
+	cycle;
+
+\path[fill=fillColor] (521.41,319.08) --
+	(524.77,313.25) --
+	(518.04,313.25) --
+	cycle;
+
+\path[fill=fillColor] (529.95,321.70) --
+	(533.31,315.88) --
+	(526.59,315.88) --
+	cycle;
+
+\path[fill=fillColor] (538.49,324.21) --
+	(541.85,318.39) --
+	(535.13,318.39) --
+	cycle;
+
+\path[fill=fillColor] (547.03,326.59) --
+	(550.40,320.76) --
+	(543.67,320.76) --
+	cycle;
+
+\path[fill=fillColor] (555.58,328.81) --
+	(558.94,322.98) --
+	(552.21,322.98) --
+	cycle;
+
+\path[fill=fillColor] (564.12,330.86) --
+	(567.48,325.03) --
+	(560.75,325.03) --
+	cycle;
+
+\path[fill=fillColor] (572.66,332.71) --
+	(576.02,326.88) --
+	(569.30,326.88) --
 	cycle;
@@
 
-\path[fill=fillColor] (322.44,247.31) --
-	(327.43,247.31) --
-	(327.43,252.31) --
-	(322.44,252.31) --
-	cycle;
-
-\path[fill=fillColor] (330.98,249.68) --
-	(335.98,249.68) --
-	(335.98,254.67) --
-	(330.98,254.67) --
-	cycle;
-
-\path[fill=fillColor] (339.52,252.08) --
-	(344.52,252.08) --
-	(344.52,257.07) --
-	(339.52,257.07) --
-	cycle;
-
-\path[fill=fillColor] (348.06,254.52) --
-	(353.06,254.52) --
-	(353.06,259.51) --
-	(348.06,259.51) --
-	cycle;
-
-\path[fill=fillColor] (356.61,256.99) --
-	(361.60,256.99) --
-	(361.60,261.98) --
-	(356.61,261.98) --
-	cycle;
-
-\path[fill=fillColor] (365.15,259.48) --
-	(370.14,259.48) --
-	(370.14,264.47) --
-	(365.15,264.47) --
-	cycle;
-
-\path[fill=fillColor] (373.69,261.99) --
-	(378.69,261.99) --
-	(378.69,266.99) --
-	(373.69,266.99) --
-	cycle;
-
-\path[fill=fillColor] (382.23,264.51) --
-	(387.23,264.51) --
-	(387.23,269.51) --
-	(382.23,269.51) --
-	cycle;
-
-\path[fill=fillColor] (390.78,267.04) --
-	(395.77,267.04) --
-	(395.77,272.03) --
-	(390.78,272.03) --
-	cycle;
-
-\path[fill=fillColor] (399.32,269.56) --
-	(404.31,269.56) --
-	(404.31,274.55) --
-	(399.32,274.55) --
-	cycle;
-
-\path[fill=fillColor] (407.86,272.06) --
-	(412.86,272.06) --
-	(412.86,277.05) --
-	(407.86,277.05) --
-	cycle;
-
-\path[fill=fillColor] (416.40,274.53) --
-	(421.40,274.53) --
-	(421.40,279.53) --
-	(416.40,279.53) --
-	cycle;
-
-\path[fill=fillColor] (424.94,276.97) --
-	(429.94,276.97) --
-	(429.94,281.96) --
-	(424.94,281.96) --
-	cycle;
-
-\path[fill=fillColor] (433.49,279.35) --
-	(438.48,279.35) --
-	(438.48,284.35) --
-	(433.49,284.35) --
-	cycle;
-
-\path[fill=fillColor] (442.03,281.67) --
-	(447.02,281.67) --
-	(447.02,286.67) --
-	(442.03,286.67) --
-	cycle;
-
-\path[fill=fillColor] (450.57,283.91) --
-	(455.57,283.91) --
-	(455.57,288.91) --
-	(450.57,288.91) --
-	cycle;
-
-\path[fill=fillColor] (459.11,286.06) --
-	(464.11,286.06) --
-	(464.11,291.05) --
-	(459.11,291.05) --
-	cycle;
-
-\path[fill=fillColor] (467.66,288.09) --
-	(472.65,288.09) --
-	(472.65,293.08) --
-	(467.66,293.08) --
-	cycle;
-
-\path[fill=fillColor] (476.20,289.98) --
-	(481.19,289.98) --
-	(481.19,294.98) --
-	(476.20,294.98) --
-	cycle;
-
-\path[fill=fillColor] (484.74,291.73) --
-	(489.74,291.73) --
-	(489.74,296.72) --
-	(484.74,296.72) --
-	cycle;
-
-\path[fill=fillColor] (493.28,293.30) --
-	(498.28,293.30) --
-	(498.28,298.29) --
-	(493.28,298.29) --
-	cycle;
-
-\path[fill=fillColor] (501.82,294.66) --
-	(506.82,294.66) --
-	(506.82,299.66) --
-	(501.82,299.66) --
-	cycle;
-
-\path[fill=fillColor] (510.37,295.81) --
-	(515.36,295.81) --
-	(515.36,300.80) --
-	(510.37,300.80) --
-	cycle;
-
-\path[fill=fillColor] (518.91,296.70) --
-	(523.90,296.70) --
-	(523.90,301.70) --
-	(518.91,301.70) --
-	cycle;
-
-\path[fill=fillColor] (527.45,297.31) --
-	(532.45,297.31) --
-	(532.45,302.31) --
-	(527.45,302.31) --
-	cycle;
-
-\path[fill=fillColor] (535.99,297.62) --
-	(540.99,297.62) --
-	(540.99,302.61) --
-	(535.99,302.61) --
-	cycle;
-
-\path[fill=fillColor] (544.54,297.58) --
-	(549.53,297.58) --
-	(549.53,302.58) --
-	(544.54,302.58) --
-	cycle;
-
-\path[fill=fillColor] (553.08,297.18) --
-	(558.07,297.18) --
-	(558.07,302.18) --
-	(553.08,302.18) --
-	cycle;
-
-\path[fill=fillColor] (561.62,296.38) --
-	(566.62,296.38) --
-	(566.62,301.38) --
-	(561.62,301.38) --
-	cycle;
-
-\path[fill=fillColor] (570.16,295.16) --
-	(575.16,295.16) --
-	(575.16,300.16) --
-	(570.16,300.16) --
+\path[fill=fillColor] (322.44,247.36) --
+	(327.43,247.36) --
+	(327.43,252.36) --
+	(322.44,252.36) --
+	cycle;
+
+\path[fill=fillColor] (330.98,249.77) --
+	(335.98,249.77) --
+	(335.98,254.76) --
+	(330.98,254.76) --
+	cycle;
+
+\path[fill=fillColor] (339.52,252.21) --
+	(344.52,252.21) --
+	(344.52,257.20) --
+	(339.52,257.20) --
+	cycle;
+
+\path[fill=fillColor] (348.06,254.68) --
+	(353.06,254.68) --
+	(353.06,259.68) --
+	(348.06,259.68) --
+	cycle;
+
+\path[fill=fillColor] (356.61,257.18) --
+	(361.60,257.18) --
+	(361.60,262.17) --
+	(356.61,262.17) --
+	cycle;
+
+\path[fill=fillColor] (365.15,259.69) --
+	(370.14,259.69) --
+	(370.14,264.68) --
+	(365.15,264.68) --
+	cycle;
+
+\path[fill=fillColor] (373.69,262.21) --
+	(378.69,262.21) --
+	(378.69,267.20) --
+	(373.69,267.20) --
+	cycle;
+
+\path[fill=fillColor] (382.23,264.73) --
+	(387.23,264.73) --
+	(387.23,269.73) --
+	(382.23,269.73) --
+	cycle;
+
+\path[fill=fillColor] (390.78,267.25) --
+	(395.77,267.25) --
+	(395.77,272.24) --
+	(390.78,272.24) --
+	cycle;
+
+\path[fill=fillColor] (399.32,269.74) --
+	(404.31,269.74) --
+	(404.31,274.74) --
+	(399.32,274.74) --
+	cycle;
+
+\path[fill=fillColor] (407.86,272.21) --
+	(412.86,272.21) --
+	(412.86,277.21) --
+	(407.86,277.21) --
+	cycle;
+
+\path[fill=fillColor] (416.40,274.64) --
+	(421.40,274.64) --
+	(421.40,279.63) --
+	(416.40,279.63) --
+	cycle;
+
+\path[fill=fillColor] (424.94,277.02) --
+	(429.94,277.02) --
+	(429.94,282.01) --
+	(424.94,282.01) --
+	cycle;
+
+\path[fill=fillColor] (433.49,279.33) --
+	(438.48,279.33) --
+	(438.48,284.33) --
+	(433.49,284.33) --
+	cycle;
+
+\path[fill=fillColor] (442.03,281.56) --
+	(447.02,281.56) --
+	(447.02,286.56) --
+	(442.03,286.56) --
+	cycle;
+
+\path[fill=fillColor] (450.57,283.70) --
+	(455.57,283.70) --
+	(455.57,288.70) --
+	(450.57,288.70) --
+	cycle;
+
+\path[fill=fillColor] (459.11,285.74) --
+	(464.11,285.74) --
+	(464.11,290.73) --
+	(459.11,290.73) --
+	cycle;
+
+\path[fill=fillColor] (467.66,287.64) --
+	(472.65,287.64) --
+	(472.65,292.63) --
+	(467.66,292.63) --
+	cycle;
+
+\path[fill=fillColor] (476.20,289.40) --
+	(481.19,289.40) --
+	(481.19,294.39) --
+	(476.20,294.39) --
+	cycle;
+
+\path[fill=fillColor] (484.74,290.99) --
+	(489.74,290.99) --
+	(489.74,295.98) --
+	(484.74,295.98) --
+	cycle;
+
+\path[fill=fillColor] (493.28,292.39) --
+	(498.28,292.39) --
+	(498.28,297.39) --
+	(493.28,297.39) --
+	cycle;
+
+\path[fill=fillColor] (501.82,293.59) --
+	(506.82,293.59) --
+	(506.82,298.58) --
+	(501.82,298.58) --
+	cycle;
+
+\path[fill=fillColor] (510.37,294.55) --
+	(515.36,294.55) --
+	(515.36,299.55) --
+	(510.37,299.55) --
+	cycle;
+
+\path[fill=fillColor] (518.91,295.26) --
+	(523.90,295.26) --
+	(523.90,300.25) --
+	(518.91,300.25) --
+	cycle;
+
+\path[fill=fillColor] (527.45,295.68) --
+	(532.45,295.68) --
+	(532.45,300.68) --
+	(527.45,300.68) --
+	cycle;
+
+\path[fill=fillColor] (535.99,295.80) --
+	(540.99,295.80) --
+	(540.99,300.79) --
+	(535.99,300.79) --
+	cycle;
+
+\path[fill=fillColor] (544.54,295.58) --
+	(549.53,295.58) --
+	(549.53,300.58) --
+	(544.54,300.58) --
+	cycle;
+
+\path[fill=fillColor] (553.08,295.01) --
+	(558.07,295.01) --
+	(558.07,300.00) --
+	(553.08,300.00) --
+	cycle;
+
+\path[fill=fillColor] (561.62,294.05) --
+	(566.62,294.05) --
+	(566.62,299.05) --
+	(561.62,299.05) --
+	cycle;
+
+\path[fill=fillColor] (570.16,292.69) --
+	(575.16,292.69) --
+	(575.16,297.69) --
+	(570.16,297.69) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.40,249.80) -- (328.47,249.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.94,246.27) -- (324.94,253.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.95,252.14) -- (337.01,252.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.48,248.61) -- (333.48,255.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.49,254.50) -- (345.55,254.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.02,250.97) -- (342.02,258.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.03,256.87) -- (354.09,256.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.34) -- (350.56,260.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,259.25) -- (362.64,259.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,255.72) -- (359.10,262.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,261.63) -- (371.18,261.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,258.10) -- (367.65,265.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,263.99) -- (379.72,263.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,260.46) -- (376.19,267.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,266.33) -- (388.26,266.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,262.80) -- (384.73,269.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,268.64) -- (396.81,268.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,265.11) -- (393.27,272.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,270.90) -- (405.35,270.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,267.37) -- (401.82,274.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,273.10) -- (413.89,273.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,269.57) -- (410.36,276.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,275.23) -- (422.43,275.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,271.70) -- (418.90,278.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,277.27) -- (430.97,277.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,273.73) -- (427.44,280.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,279.20) -- (439.52,279.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,275.67) -- (435.98,282.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,281.01) -- (448.06,281.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,277.48) -- (444.53,284.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,282.68) -- (456.60,282.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,279.14) -- (453.07,286.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,284.18) -- (465.14,284.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,280.65) -- (461.61,287.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,285.51) -- (473.69,285.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,281.98) -- (470.15,289.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,286.63) -- (482.23,286.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,283.10) -- (478.70,290.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,287.53) -- (490.77,287.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,283.99) -- (487.24,291.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,288.17) -- (499.31,288.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,284.64) -- (495.78,291.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,288.54) -- (507.85,288.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,285.00) -- (504.32,292.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,288.60) -- (516.40,288.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,285.07) -- (512.86,292.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,288.33) -- (524.94,288.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,284.80) -- (521.41,291.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,287.71) -- (533.48,287.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,284.18) -- (529.95,291.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,286.71) -- (542.02,286.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,283.17) -- (538.49,290.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,285.30) -- (550.57,285.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,281.77) -- (547.03,288.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,283.48) -- (559.11,283.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,279.95) -- (555.58,287.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,281.22) -- (567.65,281.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,277.69) -- (564.12,284.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,278.53) -- (576.19,278.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,275.00) -- (572.66,282.06);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.40,249.85) -- (328.47,249.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.94,246.32) -- (324.94,253.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.95,252.22) -- (337.01,252.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.48,248.69) -- (333.48,255.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.49,254.60) -- (345.55,254.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.02,251.07) -- (342.02,258.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.03,256.98) -- (354.09,256.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.45) -- (350.56,260.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,259.36) -- (362.64,259.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,255.82) -- (359.10,262.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,261.71) -- (371.18,261.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,258.18) -- (367.65,265.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,264.03) -- (379.72,264.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,260.50) -- (376.19,267.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,266.31) -- (388.26,266.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,262.78) -- (384.73,269.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,268.54) -- (396.81,268.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,265.01) -- (393.27,272.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,270.69) -- (405.35,270.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,267.16) -- (401.82,274.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,272.77) -- (413.89,272.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,269.23) -- (410.36,276.30);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,274.74) -- (422.43,274.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,271.21) -- (418.90,278.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,276.60) -- (430.97,276.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,273.07) -- (427.44,280.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,278.33) -- (439.52,278.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,274.80) -- (435.98,281.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,279.91) -- (448.06,279.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,276.38) -- (444.53,283.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,281.32) -- (456.60,281.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,277.79) -- (453.07,284.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,282.55) -- (465.14,282.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,279.02) -- (461.61,286.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,283.58) -- (473.69,283.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,280.04) -- (470.15,287.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,284.37) -- (482.23,284.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,280.84) -- (478.70,287.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,284.92) -- (490.77,284.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,281.39) -- (487.24,288.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,285.20) -- (499.31,285.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,281.66) -- (495.78,288.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,285.18) -- (507.85,285.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,281.65) -- (504.32,288.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,284.85) -- (516.40,284.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,281.32) -- (512.86,288.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,284.18) -- (524.94,284.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,280.65) -- (521.41,287.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,283.15) -- (533.48,283.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,279.62) -- (529.95,286.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,281.75) -- (542.02,281.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,278.22) -- (538.49,285.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,279.96) -- (550.57,279.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,276.43) -- (547.03,283.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,277.78) -- (559.11,277.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,274.24) -- (555.58,281.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,275.19) -- (567.65,275.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,271.66) -- (564.12,278.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,272.21) -- (576.19,272.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,268.68) -- (572.66,275.74);
 \definecolor{fillColor}{RGB}{0,0,0}
@@
 
-\path[fill=fillColor] (324.94,249.83) circle (  2.50);
-
-\path[fill=fillColor] (333.48,252.27) circle (  2.50);
-
-\path[fill=fillColor] (342.02,254.83) circle (  2.50);
-
-\path[fill=fillColor] (350.56,257.49) circle (  2.50);
-
-\path[fill=fillColor] (359.10,260.29) circle (  2.50);
-
-\path[fill=fillColor] (367.65,263.21) circle (  2.50);
-
-\path[fill=fillColor] (376.19,266.26) circle (  2.50);
-
-\path[fill=fillColor] (384.73,269.43) circle (  2.50);
-
-\path[fill=fillColor] (393.27,272.82) circle (  2.50);
-
-\path[fill=fillColor] (401.82,276.23) circle (  2.50);
-
-\path[fill=fillColor] (410.36,279.89) circle (  2.50);
-
-\path[fill=fillColor] (418.90,283.67) circle (  2.50);
-
-\path[fill=fillColor] (427.44,287.63) circle (  2.50);
-
-\path[fill=fillColor] (435.98,291.78) circle (  2.50);
-
-\path[fill=fillColor] (444.53,296.18) circle (  2.50);
-
-\path[fill=fillColor] (453.07,300.57) circle (  2.50);
-
-\path[fill=fillColor] (461.61,305.43) circle (  2.50);
-
-\path[fill=fillColor] (470.15,310.38) circle (  2.50);
-
-\path[fill=fillColor] (478.70,315.48) circle (  2.50);
-
-\path[fill=fillColor] (487.24,320.76) circle (  2.50);
-
-\path[fill=fillColor] (495.78,326.28) circle (  2.50);
-
-\path[fill=fillColor] (504.32,332.33) circle (  2.50);
-
-\path[fill=fillColor] (512.86,338.07) circle (  2.50);
-
-\path[fill=fillColor] (521.41,344.75) circle (  2.50);
-
-\path[fill=fillColor] (529.95,350.97) circle (  2.50);
-
-\path[fill=fillColor] (538.49,358.06) circle (  2.50);
-
-\path[fill=fillColor] (547.03,365.33) circle (  2.50);
-
-\path[fill=fillColor] (555.58,372.97) circle (  2.50);
-
-\path[fill=fillColor] (564.12,380.73) circle (  2.50);
-
-\path[fill=fillColor] (572.66,388.73) circle (  2.50);
+\path[fill=fillColor] (324.94,249.88) circle (  2.50);
+
+\path[fill=fillColor] (333.48,252.36) circle (  2.50);
+
+\path[fill=fillColor] (342.02,254.96) circle (  2.50);
+
+\path[fill=fillColor] (350.56,257.65) circle (  2.50);
+
+\path[fill=fillColor] (359.10,260.48) circle (  2.50);
+
+\path[fill=fillColor] (367.65,263.42) circle (  2.50);
+
+\path[fill=fillColor] (376.19,266.48) circle (  2.50);
+
+\path[fill=fillColor] (384.73,269.65) circle (  2.50);
+
+\path[fill=fillColor] (393.27,273.04) circle (  2.50);
+
+\path[fill=fillColor] (401.82,276.42) circle (  2.50);
+
+\path[fill=fillColor] (410.36,280.04) circle (  2.50);
+
+\path[fill=fillColor] (418.90,283.76) circle (  2.50);
+
+\path[fill=fillColor] (427.44,287.65) circle (  2.50);
+
+\path[fill=fillColor] (435.98,291.72) circle (  2.50);
+
+\path[fill=fillColor] (444.53,296.05) circle (  2.50);
+
+\path[fill=fillColor] (453.07,300.28) circle (  2.50);
+
+\path[fill=fillColor] (461.61,305.03) circle (  2.50);
+
+\path[fill=fillColor] (470.15,309.81) circle (  2.50);
+
+\path[fill=fillColor] (478.70,314.71) circle (  2.50);
+
+\path[fill=fillColor] (487.24,319.74) circle (  2.50);
+
+\path[fill=fillColor] (495.78,324.97) circle (  2.50);
+
+\path[fill=fillColor] (504.32,330.80) circle (  2.50);
+
+\path[fill=fillColor] (512.86,336.10) circle (  2.50);
+
+\path[fill=fillColor] (521.41,342.50) circle (  2.50);
+
+\path[fill=fillColor] (529.95,348.19) circle (  2.50);
+
+\path[fill=fillColor] (538.49,354.89) circle (  2.50);
+
+\path[fill=fillColor] (547.03,361.68) circle (  2.50);
+
+\path[fill=fillColor] (555.58,368.79) circle (  2.50);
+
+\path[fill=fillColor] (564.12,375.90) circle (  2.50);
+
+\path[fill=fillColor] (572.66,383.19) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 47.92) --
-	( 30.56, 47.94) --
-	( 33.80, 47.96) --
-	( 37.04, 47.98) --
-	( 40.29, 48.00) --
-	( 43.53, 48.02) --
-	( 46.78, 48.03) --
-	( 50.02, 48.05) --
-	( 53.26, 48.06) --
-	( 56.51, 48.07) --
-	( 59.75, 48.09) --
-	( 63.00, 48.09) --
-	( 66.24, 48.10) --
-	( 69.48, 48.11) --
-	( 72.73, 48.12) --
-	( 75.97, 48.12) --
-	( 79.22, 48.13) --
-	( 82.46, 48.13) --
-	( 85.70, 48.14) --
-	( 88.95, 48.14) --
-	( 92.19, 48.14) --
-	( 95.43, 48.14) --
-	( 98.68, 48.14) --
-	(101.92, 48.13) --
-	(105.17, 48.12) --
-	(108.41, 48.12) --
-	(111.65, 48.11) --
-	(114.90, 48.10) --
-	(118.14, 48.10) --
-	(121.39, 48.10) --
-	(124.63, 48.11) --
-	(127.87, 48.12) --
-	(131.12, 48.13) --
-	(134.36, 48.14) --
-	(137.61, 48.16) --
-	(140.85, 48.17) --
-	(144.09, 48.19) --
-	(147.34, 48.20) --
-	(150.58, 48.21) --
-	(153.82, 48.22) --
-	(157.07, 48.22) --
-	(160.31, 48.22) --
-	(163.56, 48.22) --
-	(166.80, 48.22) --
-	(170.04, 48.22) --
-	(173.29, 48.22) --
-	(176.53, 48.22) --
-	(179.78, 48.21) --
-	(183.02, 48.21) --
-	(186.26, 48.21) --
-	(189.51, 48.20) --
-	(192.75, 48.20) --
-	(196.00, 48.20) --
-	(199.24, 48.20) --
-	(202.48, 48.19) --
-	(205.73, 48.19) --
-	(208.97, 48.19) --
-	(212.21, 48.18) --
-	(215.46, 48.18) --
-	(218.70, 48.18) --
-	(221.95, 48.18) --
-	(225.19, 48.18) --
-	(228.43, 48.18) --
-	(231.68, 48.17) --
-	(234.92, 48.17) --
-	(238.17, 48.17) --
-	(241.41, 48.17) --
-	(244.65, 48.17) --
-	(247.90, 48.17) --
-	(251.14, 48.16) --
-	(254.39, 48.16) --
-	(257.63, 48.16) --
-	(260.87, 48.16) --
-	(264.12, 48.16) --
-	(267.36, 48.16) --
-	(270.60, 48.16) --
-	(273.85, 48.17) --
-	(277.09, 48.17) --
-	(280.34, 48.17) --
-	(283.58, 48.17);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 54.52) --
+	( 30.56, 54.54) --
+	( 33.80, 54.57) --
+	( 37.04, 54.60) --
+	( 40.29, 54.62) --
+	( 43.53, 54.64) --
+	( 46.78, 54.67) --
+	( 50.02, 54.69) --
+	( 53.26, 54.70) --
+	( 56.51, 54.72) --
+	( 59.75, 54.73) --
+	( 63.00, 54.75) --
+	( 66.24, 54.76) --
+	( 69.48, 54.77) --
+	( 72.73, 54.77) --
+	( 75.97, 54.78) --
+	( 79.22, 54.79) --
+	( 82.46, 54.80) --
+	( 85.70, 54.80) --
+	( 88.95, 54.81) --
+	( 92.19, 54.81) --
+	( 95.43, 54.81) --
+	( 98.68, 54.80) --
+	(101.92, 54.79) --
+	(105.17, 54.78) --
+	(108.41, 54.77) --
+	(111.65, 54.77) --
+	(114.90, 54.76) --
+	(118.14, 54.76) --
+	(121.39, 54.76) --
+	(124.63, 54.76) --
+	(127.87, 54.77) --
+	(131.12, 54.79) --
+	(134.36, 54.80) --
+	(137.61, 54.82) --
+	(140.85, 54.83) --
+	(144.09, 54.85) --
+	(147.34, 54.87) --
+	(150.58, 54.88) --
+	(153.82, 54.89) --
+	(157.07, 54.89) --
+	(160.31, 54.89) --
+	(163.56, 54.89) --
+	(166.80, 54.89) --
+	(170.04, 54.89) --
+	(173.29, 54.89) --
+	(176.53, 54.89) --
+	(179.78, 54.88) --
+	(183.02, 54.88) --
+	(186.26, 54.88) --
+	(189.51, 54.88) --
+	(192.75, 54.87) --
+	(196.00, 54.87) --
+	(199.24, 54.87) --
+	(202.48, 54.87) --
+	(205.73, 54.86) --
+	(208.97, 54.86) --
+	(212.21, 54.86) --
+	(215.46, 54.86) --
+	(218.70, 54.86) --
+	(221.95, 54.85) --
+	(225.19, 54.85) --
+	(228.43, 54.85) --
+	(231.68, 54.85) --
+	(234.92, 54.85) --
+	(238.17, 54.84) --
+	(241.41, 54.84) --
+	(244.65, 54.84) --
+	(247.90, 54.84) --
+	(251.14, 54.83) --
+	(254.39, 54.83) --
+	(257.63, 54.83) --
+	(260.87, 54.83) --
+	(264.12, 54.83) --
+	(267.36, 54.83) --
+	(270.60, 54.83) --
+	(273.85, 54.83) --
+	(277.09, 54.82) --
+	(280.34, 54.82) --
+	(283.58, 54.82);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31, 49.28) --
-	( 30.56, 50.77) --
-	( 33.80, 52.24) --
-	( 37.04, 53.70) --
-	( 40.29, 55.14) --
-	( 43.53, 56.57) --
-	( 46.78, 57.98) --
-	( 50.02, 59.38) --
-	( 53.26, 60.76) --
-	( 56.51, 62.12) --
-	( 59.75, 63.47) --
-	( 63.00, 64.80) --
-	( 66.24, 66.12) --
-	( 69.48, 67.42) --
-	( 72.73, 68.70) --
-	( 75.97, 69.97) --
-	( 79.22, 71.22) --
-	( 82.46, 72.46) --
-	( 85.70, 73.69) --
-	( 88.95, 74.89) --
-	( 92.19, 76.08) --
-	( 95.43, 77.25) --
-	( 98.68, 78.41) --
-	(101.92, 79.55) --
-	(105.17, 80.67) --
-	(108.41, 81.77) --
-	(111.65, 82.86) --
-	(114.90, 83.94) --
-	(118.14, 85.01) --
-	(121.39, 86.06) --
-	(124.63, 87.10) --
-	(127.87, 88.12) --
-	(131.12, 89.11) --
-	(134.36, 90.09) --
-	(137.61, 91.06) --
-	(140.85, 92.01) --
-	(144.09, 92.95) --
-	(147.34, 93.89) --
-	(150.58, 94.82) --
-	(153.82, 95.75) --
-	(157.07, 96.69) --
-	(160.31, 97.61) --
-	(163.56, 98.51) --
-	(166.80, 99.41) --
-	(170.04,100.30) --
-	(173.29,101.18) --
-	(176.53,102.05) --
-	(179.78,102.92) --
-	(183.02,103.78) --
-	(186.26,104.64) --
-	(189.51,105.49) --
-	(192.75,106.34) --
-	(196.00,107.19) --
-	(199.24,108.02) --
-	(202.48,108.85) --
-	(205.73,109.67) --
-	(208.97,110.49) --
-	(212.21,111.30) --
-	(215.46,112.10) --
-	(218.70,112.90) --
-	(221.95,113.69) --
-	(225.19,114.48) --
-	(228.43,115.26) --
-	(231.68,116.03) --
-	(234.92,116.79) --
-	(238.17,117.55) --
-	(241.41,118.30) --
-	(244.65,119.05) --
-	(247.90,119.79) --
-	(251.14,120.52) --
-	(254.39,121.25) --
-	(257.63,121.97) --
-	(260.87,122.69) --
-	(264.12,123.39) --
-	(267.36,124.10) --
-	(270.60,124.79) --
-	(273.85,125.48) --
-	(277.09,126.16) --
-	(280.34,126.84) --
-	(283.58,127.51);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31, 55.83) --
+	( 30.56, 56.93) --
+	( 33.80, 58.02) --
+	( 37.04, 59.09) --
+	( 40.29, 60.16) --
+	( 43.53, 61.21) --
+	( 46.78, 62.25) --
+	( 50.02, 63.27) --
+	( 53.26, 64.29) --
+	( 56.51, 65.29) --
+	( 59.75, 66.28) --
+	( 63.00, 67.26) --
+	( 66.24, 68.22) --
+	( 69.48, 69.18) --
+	( 72.73, 70.12) --
+	( 75.97, 71.05) --
+	( 79.22, 71.97) --
+	( 82.46, 72.88) --
+	( 85.70, 73.77) --
+	( 88.95, 74.66) --
+	( 92.19, 75.53) --
+	( 95.43, 76.38) --
+	( 98.68, 77.22) --
+	(101.92, 78.05) --
+	(105.17, 78.87) --
+	(108.41, 79.68) --
+	(111.65, 80.48) --
+	(114.90, 81.26) --
+	(118.14, 82.04) --
+	(121.39, 82.81) --
+	(124.63, 83.56) --
+	(127.87, 84.30) --
+	(131.12, 85.03) --
+	(134.36, 85.74) --
+	(137.61, 86.44) --
+	(140.85, 87.13) --
+	(144.09, 87.82) --
+	(147.34, 88.50) --
+	(150.58, 89.18) --
+	(153.82, 89.85) --
+	(157.07, 90.53) --
+	(160.31, 91.19) --
+	(163.56, 91.85) --
+	(166.80, 92.50) --
+	(170.04, 93.14) --
+	(173.29, 93.78) --
+	(176.53, 94.41) --
+	(179.78, 95.03) --
+	(183.02, 95.66) --
+	(186.26, 96.27) --
+	(189.51, 96.89) --
+	(192.75, 97.50) --
+	(196.00, 98.11) --
+	(199.24, 98.72) --
+	(202.48, 99.31) --
+	(205.73, 99.91) --
+	(208.97,100.50) --
+	(212.21,101.08) --
+	(215.46,101.66) --
+	(218.70,102.23) --
+	(221.95,102.80) --
+	(225.19,103.37) --
+	(228.43,103.93) --
+	(231.68,104.49) --
+	(234.92,105.04) --
+	(238.17,105.59) --
+	(241.41,106.13) --
+	(244.65,106.66) --
+	(247.90,107.20) --
+	(251.14,107.72) --
+	(254.39,108.25) --
+	(257.63,108.77) --
+	(260.87,109.28) --
+	(264.12,109.79) --
+	(267.36,110.29) --
+	(270.60,110.79) --
+	(273.85,111.29) --
+	(277.09,111.78) --
+	(280.34,112.27) --
+	(283.58,112.75);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31, 49.13) --
-	( 30.56, 51.18) --
-	( 33.80, 53.21) --
-	( 37.04, 55.22) --
-	( 40.29, 57.21) --
-	( 43.53, 59.18) --
-	( 46.78, 61.13) --
-	( 50.02, 63.06) --
-	( 53.26, 64.97) --
-	( 56.51, 66.86) --
-	( 59.75, 68.72) --
-	( 63.00, 70.57) --
-	( 66.24, 72.40) --
-	( 69.48, 74.20) --
-	( 72.73, 75.99) --
-	( 75.97, 77.75) --
-	( 79.22, 79.50) --
-	( 82.46, 81.23) --
-	( 85.70, 82.94) --
-	( 88.95, 84.63) --
-	( 92.19, 86.29) --
-	( 95.43, 87.93) --
-	( 98.68, 89.55) --
-	(101.92, 91.15) --
-	(105.17, 92.73) --
-	(108.41, 94.28) --
-	(111.65, 95.82) --
-	(114.90, 97.35) --
-	(118.14, 98.86) --
-	(121.39,100.35) --
-	(124.63,101.82) --
-	(127.87,103.26) --
-	(131.12,104.67) --
-	(134.36,106.06) --
-	(137.61,107.43) --
-	(140.85,108.79) --
-	(144.09,110.14) --
-	(147.34,111.48) --
-	(150.58,112.81) --
-	(153.82,114.15) --
-	(157.07,115.48) --
-	(160.31,116.80) --
-	(163.56,118.11) --
-	(166.80,119.40) --
-	(170.04,120.68) --
-	(173.29,121.95) --
-	(176.53,123.21) --
-	(179.78,124.46) --
-	(183.02,125.71) --
-	(186.26,126.95) --
-	(189.51,128.18) --
-	(192.75,129.41) --
-	(196.00,130.63) --
-	(199.24,131.84) --
-	(202.48,133.05) --
-	(205.73,134.24) --
-	(208.97,135.43) --
-	(212.21,136.61) --
-	(215.46,137.78) --
-	(218.70,138.94) --
-	(221.95,140.09) --
-	(225.19,141.23) --
-	(228.43,142.37) --
-	(231.68,143.50) --
-	(234.92,144.62) --
-	(238.17,145.73) --
-	(241.41,146.83) --
-	(244.65,147.92) --
-	(247.90,149.01) --
-	(251.14,150.08) --
-	(254.39,151.15) --
-	(257.63,152.21) --
-	(260.87,153.26) --
-	(264.12,154.30) --
-	(267.36,155.33) --
-	(270.60,156.36) --
-	(273.85,157.38) --
-	(277.09,158.39) --
-	(280.34,159.39) --
-	(283.58,160.38);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31, 55.69) --
+	( 30.56, 57.48) --
+	( 33.80, 59.25) --
+	( 37.04, 61.00) --
+	( 40.29, 62.74) --
+	( 43.53, 64.46) --
+	( 46.78, 66.16) --
+	( 50.02, 67.84) --
+	( 53.26, 69.50) --
+	( 56.51, 71.15) --
+	( 59.75, 72.78) --
+	( 63.00, 74.39) --
+	( 66.24, 75.98) --
+	( 69.48, 77.56) --
+	( 72.73, 79.11) --
+	( 75.97, 80.65) --
+	( 79.22, 82.18) --
+	( 82.46, 83.68) --
+	( 85.70, 85.17) --
+	( 88.95, 86.65) --
+	( 92.19, 88.10) --
+	( 95.43, 89.53) --
+	( 98.68, 90.94) --
+	(101.92, 92.34) --
+	(105.17, 93.71) --
+	(108.41, 95.07) --
+	(111.65, 96.42) --
+	(114.90, 97.74) --
+	(118.14, 99.06) --
+	(121.39,100.36) --
+	(124.63,101.64) --
+	(127.87,102.90) --
+	(131.12,104.13) --
+	(134.36,105.34) --
+	(137.61,106.54) --
+	(140.85,107.73) --
+	(144.09,108.90) --
+	(147.34,110.07) --
+	(150.58,111.23) --
+	(153.82,112.39) --
+	(157.07,113.56) --
+	(160.31,114.71) --
+	(163.56,115.85) --
+	(166.80,116.97) --
+	(170.04,118.09) --
+	(173.29,119.20) --
+	(176.53,120.30) --
+	(179.78,121.39) --
+	(183.02,122.48) --
+	(186.26,123.56) --
+	(189.51,124.64) --
+	(192.75,125.71) --
+	(196.00,126.77) --
+	(199.24,127.83) --
+	(202.48,128.88) --
+	(205.73,129.92) --
+	(208.97,130.96) --
+	(212.21,131.98) --
+	(215.46,133.00) --
+	(218.70,134.02) --
+	(221.95,135.02) --
+	(225.19,136.02) --
+	(228.43,137.01) --
+	(231.68,137.99) --
+	(234.92,138.97) --
+	(238.17,139.94) --
+	(241.41,140.90) --
+	(244.65,141.85) --
+	(247.90,142.80) --
+	(251.14,143.74) --
+	(254.39,144.67) --
+	(257.63,145.59) --
+	(260.87,146.51) --
+	(264.12,147.42) --
+	(267.36,148.32) --
+	(270.60,149.21) --
+	(273.85,150.10) --
+	(277.09,150.98) --
+	(280.34,151.85) --
+	(283.58,152.72);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 48.86) --
-	( 30.56, 51.44) --
-	( 33.80, 54.00) --
-	( 37.04, 56.54) --
-	( 40.29, 59.06) --
-	( 43.53, 61.55) --
-	( 46.78, 64.02) --
-	( 50.02, 66.46) --
-	( 53.26, 68.88) --
-	( 56.51, 71.28) --
-	( 59.75, 73.65) --
-	( 63.00, 76.00) --
-	( 66.24, 78.32) --
-	( 69.48, 80.62) --
-	( 72.73, 82.90) --
-	( 75.97, 85.15) --
-	( 79.22, 87.38) --
-	( 82.46, 89.59) --
-	( 85.70, 91.78) --
-	( 88.95, 93.94) --
-	( 92.19, 96.08) --
-	( 95.43, 98.19) --
-	( 98.68,100.27) --
-	(101.92,102.33) --
-	(105.17,104.37) --
-	(108.41,106.38) --
-	(111.65,108.37) --
-	(114.90,110.34) --
-	(118.14,112.29) --
-	(121.39,114.23) --
-	(124.63,116.14) --
-	(127.87,118.01) --
-	(131.12,119.85) --
-	(134.36,121.67) --
-	(137.61,123.46) --
-	(140.85,125.24) --
-	(144.09,127.00) --
-	(147.34,128.75) --
-	(150.58,130.50) --
-	(153.82,132.25) --
-	(157.07,134.01) --
-	(160.31,135.74) --
-	(163.56,137.46) --
-	(166.80,139.17) --
-	(170.04,140.86) --
-	(173.29,142.54) --
-	(176.53,144.21) --
-	(179.78,145.87) --
-	(183.02,147.53) --
-	(186.26,149.17) --
-	(189.51,150.81) --
-	(192.75,152.44) --
-	(196.00,154.07) --
-	(199.24,155.68) --
-	(202.48,157.28) --
-	(205.73,158.87) --
-	(208.97,160.45) --
-	(212.21,162.03) --
-	(215.46,163.59) --
-	(218.70,165.14) --
-	(221.95,166.68) --
-	(225.19,168.21) --
-	(228.43,169.74) --
-	(231.68,171.25) --
-	(234.92,172.75) --
-	(238.17,174.24) --
-	(241.41,175.72) --
-	(244.65,177.20) --
-	(247.90,178.66) --
-	(251.14,180.11) --
-	(254.39,181.55) --
-	(257.63,182.98) --
-	(260.87,184.41) --
-	(264.12,185.82) --
-	(267.36,187.22) --
-	(270.60,188.61) --
-	(273.85,189.99) --
-	(277.09,191.36) --
-	(280.34,192.73) --
-	(283.58,194.08);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 55.36) --
+	( 30.56, 57.79) --
+	( 33.80, 60.21) --
+	( 37.04, 62.60) --
+	( 40.29, 64.97) --
+	( 43.53, 67.32) --
+	( 46.78, 69.65) --
+	( 50.02, 71.96) --
+	( 53.26, 74.25) --
+	( 56.51, 76.51) --
+	( 59.75, 78.75) --
+	( 63.00, 80.97) --
+	( 66.24, 83.17) --
+	( 69.48, 85.34) --
+	( 72.73, 87.50) --
+	( 75.97, 89.63) --
+	( 79.22, 91.75) --
+	( 82.46, 93.84) --
+	( 85.70, 95.91) --
+	( 88.95, 97.97) --
+	( 92.19, 99.99) --
+	( 95.43,102.00) --
+	( 98.68,103.98) --
+	(101.92,105.93) --
+	(105.17,107.87) --
+	(108.41,109.78) --
+	(111.65,111.68) --
+	(114.90,113.56) --
+	(118.14,115.41) --
+	(121.39,117.26) --
+	(124.63,119.08) --
+	(127.87,120.86) --
+	(131.12,122.62) --
+	(134.36,124.35) --
+	(137.61,126.07) --
+	(140.85,127.76) --
+	(144.09,129.45) --
+	(147.34,131.13) --
+	(150.58,132.80) --
+	(153.82,134.48) --
+	(157.07,136.16) --
+	(160.31,137.82) --
+	(163.56,139.47) --
+	(166.80,141.11) --
+	(170.04,142.73) --
+	(173.29,144.35) --
+	(176.53,145.95) --
+	(179.78,147.55) --
+	(183.02,149.14) --
+	(186.26,150.72) --
+	(189.51,152.30) --
+	(192.75,153.87) --
+	(196.00,155.43) --
+	(199.24,156.98) --
+	(202.48,158.52) --
+	(205.73,160.06) --
+	(208.97,161.58) --
+	(212.21,163.09) --
+	(215.46,164.60) --
+	(218.70,166.10) --
+	(221.95,167.58) --
+	(225.19,169.06) --
+	(228.43,170.53) --
+	(231.68,171.99) --
+	(234.92,173.44) --
+	(238.17,174.88) --
+	(241.41,176.31) --
+	(244.65,177.74) --
+	(247.90,179.15) --
+	(251.14,180.55) --
+	(254.39,181.95) --
+	(257.63,183.34) --
+	(260.87,184.71) --
+	(264.12,186.08) --
+	(267.36,187.44) --
+	(270.60,188.79) --
+	(273.85,190.13) --
+	(277.09,191.46) --
+	(280.34,192.78) --
+	(283.58,194.09);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] ( 27.31, 53.19) --
-	( 30.68, 47.36) --
-	( 23.95, 47.36) --
-	cycle;
-
-\path[fill=fillColor] ( 35.86, 57.06) --
-	( 39.22, 51.23) --
-	( 32.49, 51.23) --
-	cycle;
-
-\path[fill=fillColor] ( 44.40, 60.55) --
-	( 47.76, 54.73) --
-	( 41.03, 54.73) --
-	cycle;
-
-\path[fill=fillColor] ( 52.94, 64.55) --
-	( 56.30, 58.73) --
-	( 49.58, 58.73) --
-	cycle;
-
-\path[fill=fillColor] ( 61.48, 68.20) --
-	( 64.85, 62.37) --
-	( 58.12, 62.37) --
-	cycle;
-
-\path[fill=fillColor] ( 70.02, 71.66) --
-	( 73.39, 65.83) --
-	( 66.66, 65.83) --
-	cycle;
-
-\path[fill=fillColor] ( 78.57, 74.89) --
-	( 81.93, 69.06) --
-	( 75.20, 69.06) --
-	cycle;
-
-\path[fill=fillColor] ( 87.11, 78.06) --
-	( 90.47, 72.23) --
-	( 83.75, 72.23) --
-	cycle;
-
-\path[fill=fillColor] ( 95.65, 81.32) --
-	( 99.01, 75.49) --
-	( 92.29, 75.49) --
-	cycle;
-
-\path[fill=fillColor] (104.19, 84.53) --
-	(107.56, 78.70) --
-	(100.83, 78.70) --
-	cycle;
-
-\path[fill=fillColor] (112.74, 87.29) --
-	(116.10, 81.47) --
-	(109.37, 81.47) --
-	cycle;
-
-\path[fill=fillColor] (121.28, 89.96) --
-	(124.64, 84.14) --
-	(117.91, 84.14) --
-	cycle;
-
-\path[fill=fillColor] (129.82, 92.46) --
-	(133.18, 86.64) --
-	(126.46, 86.64) --
-	cycle;
-
-\path[fill=fillColor] (138.36, 95.06) --
-	(141.73, 89.23) --
-	(135.00, 89.23) --
-	cycle;
-
-\path[fill=fillColor] (146.90, 97.72) --
-	(150.27, 91.89) --
-	(143.54, 91.89) --
-	cycle;
-
-\path[fill=fillColor] (155.45,100.07) --
-	(158.81, 94.25) --
-	(152.08, 94.25) --
-	cycle;
-
-\path[fill=fillColor] (163.99,102.38) --
-	(167.35, 96.55) --
-	(160.63, 96.55) --
-	cycle;
-
-\path[fill=fillColor] (172.53,104.65) --
-	(175.89, 98.82) --
-	(169.17, 98.82) --
-	cycle;
-
-\path[fill=fillColor] (181.07,107.23) --
-	(184.44,101.41) --
-	(177.71,101.41) --
-	cycle;
-
-\path[fill=fillColor] (189.62,109.45) --
-	(192.98,103.63) --
-	(186.25,103.63) --
-	cycle;
-
-\path[fill=fillColor] (198.16,111.78) --
-	(201.52,105.95) --
-	(194.79,105.95) --
-	cycle;
-
-\path[fill=fillColor] (206.70,113.72) --
-	(210.06,107.89) --
-	(203.34,107.89) --
-	cycle;
-
-\path[fill=fillColor] (215.24,115.86) --
-	(218.61,110.04) --
-	(211.88,110.04) --
-	cycle;
-
-\path[fill=fillColor] (223.78,118.03) --
-	(227.15,112.20) --
-	(220.42,112.20) --
-	cycle;
-
-\path[fill=fillColor] (232.33,120.05) --
-	(235.69,114.22) --
-	(228.96,114.22) --
-	cycle;
-
-\path[fill=fillColor] (240.87,122.05) --
-	(244.23,116.22) --
-	(237.51,116.22) --
-	cycle;
-
-\path[fill=fillColor] (249.41,124.03) --
-	(252.77,118.21) --
-	(246.05,118.21) --
-	cycle;
-
-\path[fill=fillColor] (257.95,125.86) --
-	(261.32,120.04) --
-	(254.59,120.04) --
-	cycle;
-
-\path[fill=fillColor] (266.50,127.84) --
-	(269.86,122.01) --
-	(263.13,122.01) --
-	cycle;
-
-\path[fill=fillColor] (275.04,129.56) --
-	(278.40,123.73) --
-	(271.67,123.73) --
-	cycle;
-
-\path[fill=fillColor] (283.58,131.45) --
-	(286.94,125.62) --
-	(280.22,125.62) --
+\path[fill=fillColor] ( 27.31, 59.72) --
+	( 30.68, 53.90) --
+	( 23.95, 53.90) --
+	cycle;
+
+\path[fill=fillColor] ( 35.86, 62.59) --
+	( 39.22, 56.77) --
+	( 32.49, 56.77) --
+	cycle;
+
+\path[fill=fillColor] ( 44.40, 65.16) --
+	( 47.76, 59.33) --
+	( 41.03, 59.33) --
+	cycle;
+
+\path[fill=fillColor] ( 52.94, 68.11) --
+	( 56.30, 62.29) --
+	( 49.58, 62.29) --
+	cycle;
+
+\path[fill=fillColor] ( 61.48, 70.80) --
+	( 64.85, 64.98) --
+	( 58.12, 64.98) --
+	cycle;
+
+\path[fill=fillColor] ( 70.02, 73.35) --
+	( 73.39, 67.53) --
+	( 66.66, 67.53) --
+	cycle;
+
+\path[fill=fillColor] ( 78.57, 75.71) --
+	( 81.93, 69.89) --
+	( 75.20, 69.89) --
+	cycle;
+
+\path[fill=fillColor] ( 87.11, 77.99) --
+	( 90.47, 72.17) --
+	( 83.75, 72.17) --
+	cycle;
+
+\path[fill=fillColor] ( 95.65, 80.38) --
+	( 99.01, 74.56) --
+	( 92.29, 74.56) --
+	cycle;
+
+\path[fill=fillColor] (104.19, 82.73) --
+	(107.56, 76.90) --
+	(100.83, 76.90) --
+	cycle;
+
+\path[fill=fillColor] (112.74, 84.79) --
+	(116.10, 78.96) --
+	(109.37, 78.96) --
+	cycle;
+
+\path[fill=fillColor] (121.28, 86.71) --
+	(124.64, 80.88) --
+	(117.91, 80.88) --
+	cycle;
+
+\path[fill=fillColor] (129.82, 88.52) --
+	(133.18, 82.69) --
+	(126.46, 82.69) --
+	cycle;
+
+\path[fill=fillColor] (138.36, 90.39) --
+	(141.73, 84.57) --
+	(135.00, 84.57) --
+	cycle;
+
+\path[fill=fillColor] (146.90, 92.35) --
+	(150.27, 86.52) --
+	(143.54, 86.52) --
+	cycle;
+
+\path[fill=fillColor] (155.45, 94.05) --
+	(158.81, 88.22) --
+	(152.08, 88.22) --
+	cycle;
+
+\path[fill=fillColor] (163.99, 95.73) --
+	(167.35, 89.90) --
+	(160.63, 89.90) --
+	cycle;
+
+\path[fill=fillColor] (172.53, 97.38) --
+	(175.89, 91.55) --
+	(169.17, 91.55) --
+	cycle;
+
+\path[fill=fillColor] (181.07, 99.22) --
+	(184.44, 93.40) --
+	(177.71, 93.40) --
+	cycle;
+
+\path[fill=fillColor] (189.62,100.84) --
+	(192.98, 95.02) --
+	(186.25, 95.02) --
+	cycle;
+
+\path[fill=fillColor] (198.16,102.49) --
+	(201.52, 96.67) --
+	(194.79, 96.67) --
+	cycle;
+
+\path[fill=fillColor] (206.70,103.90) --
+	(210.06, 98.08) --
+	(203.34, 98.08) --
+	cycle;
+
+\path[fill=fillColor] (215.24,105.43) --
+	(218.61, 99.60) --
+	(211.88, 99.60) --
+	cycle;
+
+\path[fill=fillColor] (223.78,107.01) --
+	(227.15,101.18) --
+	(220.42,101.18) --
+	cycle;
+
+\path[fill=fillColor] (232.33,108.48) --
+	(235.69,102.65) --
+	(228.96,102.65) --
+	cycle;
+
+\path[fill=fillColor] (240.87,109.92) --
+	(244.23,104.10) --
+	(237.51,104.10) --
+	cycle;
+
+\path[fill=fillColor] (249.41,111.32) --
+	(252.77,105.49) --
+	(246.05,105.49) --
+	cycle;
+
+\path[fill=fillColor] (257.95,112.65) --
+	(261.32,106.82) --
+	(254.59,106.82) --
+	cycle;
+
+\path[fill=fillColor] (266.50,114.09) --
+	(269.86,108.26) --
+	(263.13,108.26) --
+	cycle;
+
+\path[fill=fillColor] (275.04,115.30) --
+	(278.40,109.48) --
+	(271.67,109.48) --
+	cycle;
+
+\path[fill=fillColor] (283.58,116.69) --
+	(286.94,110.86) --
+	(280.22,110.86) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 24.82, 46.71) --
-	( 29.81, 46.71) --
-	( 29.81, 51.71) --
-	( 24.82, 51.71) --
-	cycle;
-
-\path[fill=fillColor] ( 33.36, 51.99) --
-	( 38.35, 51.99) --
-	( 38.35, 56.98) --
-	( 33.36, 56.98) --
-	cycle;
-
-\path[fill=fillColor] ( 41.90, 56.82) --
-	( 46.90, 56.82) --
-	( 46.90, 61.82) --
-	( 41.90, 61.82) --
-	cycle;
-
-\path[fill=fillColor] ( 50.44, 62.34) --
-	( 55.44, 62.34) --
-	( 55.44, 67.33) --
-	( 50.44, 67.33) --
-	cycle;
-
-\path[fill=fillColor] ( 58.98, 67.33) --
-	( 63.98, 67.33) --
-	( 63.98, 72.32) --
-	( 58.98, 72.32) --
-	cycle;
-
-\path[fill=fillColor] ( 67.53, 72.15) --
-	( 72.52, 72.15) --
-	( 72.52, 77.15) --
-	( 67.53, 77.15) --
-	cycle;
-
-\path[fill=fillColor] ( 76.07, 76.68) --
-	( 81.06, 76.68) --
-	( 81.06, 81.67) --
-	( 76.07, 81.67) --
-	cycle;
-
-\path[fill=fillColor] ( 84.61, 81.16) --
-	( 89.61, 81.16) --
-	( 89.61, 86.16) --
-	( 84.61, 86.16) --
-	cycle;
-
-\path[fill=fillColor] ( 93.15, 85.71) --
-	( 98.15, 85.71) --
-	( 98.15, 90.70) --
-	( 93.15, 90.70) --
-	cycle;
-
-\path[fill=fillColor] (101.70, 90.24) --
-	(106.69, 90.24) --
-	(106.69, 95.23) --
-	(101.70, 95.23) --
-	cycle;
-
-\path[fill=fillColor] (110.24, 94.02) --
-	(115.23, 94.02) --
-	(115.23, 99.01) --
-	(110.24, 99.01) --
-	cycle;
-
-\path[fill=fillColor] (118.78, 97.87) --
-	(123.78, 97.87) --
-	(123.78,102.86) --
-	(118.78,102.86) --
-	cycle;
-
-\path[fill=fillColor] (127.32,101.41) --
-	(132.32,101.41) --
-	(132.32,106.41) --
-	(127.32,106.41) --
-	cycle;
-
-\path[fill=fillColor] (135.86,105.12) --
-	(140.86,105.12) --
-	(140.86,110.12) --
-	(135.86,110.12) --
-	cycle;
-
-\path[fill=fillColor] (144.41,108.90) --
-	(149.40,108.90) --
-	(149.40,113.89) --
-	(144.41,113.89) --
-	cycle;
-
-\path[fill=fillColor] (152.95,112.30) --
-	(157.94,112.30) --
-	(157.94,117.30) --
-	(152.95,117.30) --
-	cycle;
-
-\path[fill=fillColor] (161.49,115.57) --
-	(166.49,115.57) --
-	(166.49,120.56) --
-	(161.49,120.56) --
-	cycle;
-
-\path[fill=fillColor] (170.03,118.83) --
-	(175.03,118.83) --
-	(175.03,123.82) --
-	(170.03,123.82) --
-	cycle;
-
-\path[fill=fillColor] (178.58,122.59) --
-	(183.57,122.59) --
-	(183.57,127.59) --
-	(178.58,127.59) --
-	cycle;
-
-\path[fill=fillColor] (187.12,125.78) --
-	(192.11,125.78) --
-	(192.11,130.78) --
-	(187.12,130.78) --
-	cycle;
-
-\path[fill=fillColor] (195.66,129.19) --
-	(200.66,129.19) --
-	(200.66,134.19) --
-	(195.66,134.19) --
-	cycle;
-
-\path[fill=fillColor] (204.20,131.97) --
-	(209.20,131.97) --
-	(209.20,136.97) --
-	(204.20,136.97) --
-	cycle;
-
-\path[fill=fillColor] (212.74,135.14) --
-	(217.74,135.14) --
-	(217.74,140.13) --
-	(212.74,140.13) --
-	cycle;
-
-\path[fill=fillColor] (221.29,138.27) --
-	(226.28,138.27) --
-	(226.28,143.26) --
-	(221.29,143.26) --
-	cycle;
-
-\path[fill=fillColor] (229.83,141.17) --
-	(234.82,141.17) --
-	(234.82,146.17) --
-	(229.83,146.17) --
-	cycle;
-
-\path[fill=fillColor] (238.37,144.08) --
-	(243.37,144.08) --
-	(243.37,149.07) --
-	(238.37,149.07) --
-	cycle;
-
-\path[fill=fillColor] (246.91,147.11) --
-	(251.91,147.11) --
-	(251.91,152.11) --
-	(246.91,152.11) --
-	cycle;
-
-\path[fill=fillColor] (255.46,149.72) --
-	(260.45,149.72) --
-	(260.45,154.72) --
-	(255.46,154.72) --
-	cycle;
-
-\path[fill=fillColor] (264.00,152.62) --
-	(268.99,152.62) --
-	(268.99,157.62) --
-	(264.00,157.62) --
-	cycle;
-
-\path[fill=fillColor] (272.54,155.18) --
-	(277.54,155.18) --
-	(277.54,160.17) --
-	(272.54,160.17) --
-	cycle;
-
-\path[fill=fillColor] (281.08,157.94) --
-	(286.08,157.94) --
-	(286.08,162.94) --
-	(281.08,162.94) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78, 49.02) -- ( 30.85, 49.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31, 45.48) -- ( 27.31, 52.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32, 55.61) -- ( 39.39, 55.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86, 52.08) -- ( 35.86, 59.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87, 61.73) -- ( 47.93, 61.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40, 58.20) -- ( 44.40, 65.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41, 68.71) -- ( 56.47, 68.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94, 65.18) -- ( 52.94, 72.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95, 74.96) -- ( 65.01, 74.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48, 71.43) -- ( 61.48, 78.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49, 81.15) -- ( 73.56, 81.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02, 77.61) -- ( 70.02, 84.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03, 86.95) -- ( 82.10, 86.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57, 83.42) -- ( 78.57, 90.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58, 92.74) -- ( 90.64, 92.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11, 89.21) -- ( 87.11, 96.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12, 98.56) -- ( 99.18, 98.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 95.03) -- ( 95.65,102.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,104.43) -- (107.73,104.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,100.89) -- (104.19,107.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,109.18) -- (116.27,109.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,105.64) -- (112.74,112.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,114.24) -- (124.81,114.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,110.71) -- (121.28,117.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,118.85) -- (133.35,118.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,115.32) -- (129.82,122.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,123.69) -- (141.89,123.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,120.16) -- (138.36,127.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,128.65) -- (150.44,128.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,125.12) -- (146.90,132.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,133.17) -- (158.98,133.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,129.63) -- (155.45,136.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,137.39) -- (167.52,137.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,133.86) -- (163.99,140.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,141.70) -- (176.06,141.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,138.17) -- (172.53,145.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,146.71) -- (184.61,146.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,143.18) -- (181.07,150.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,150.92) -- (193.15,150.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,147.39) -- (189.62,154.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,155.51) -- (201.69,155.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,151.98) -- (198.16,159.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,159.19) -- (210.23,159.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,155.65) -- (206.70,162.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,163.43) -- (218.77,163.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,159.90) -- (215.24,166.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,167.61) -- (227.32,167.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,164.08) -- (223.78,171.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,171.46) -- (235.86,171.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,167.93) -- (232.33,174.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,175.31) -- (244.40,175.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,171.78) -- (240.87,178.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,179.58) -- (252.94,179.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,176.04) -- (249.41,183.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,182.99) -- (261.49,182.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,179.46) -- (257.95,186.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,186.92) -- (270.03,186.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,183.38) -- (266.50,190.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,190.40) -- (278.57,190.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,186.87) -- (275.04,193.93);
+\path[fill=fillColor] ( 24.82, 53.26) --
+	( 29.81, 53.26) --
+	( 29.81, 58.26) --
+	( 24.82, 58.26) --
+	cycle;
+
+\path[fill=fillColor] ( 33.36, 57.87) --
+	( 38.35, 57.87) --
+	( 38.35, 62.86) --
+	( 33.36, 62.86) --
+	cycle;
+
+\path[fill=fillColor] ( 41.90, 62.08) --
+	( 46.90, 62.08) --
+	( 46.90, 67.07) --
+	( 41.90, 67.07) --
+	cycle;
+
+\path[fill=fillColor] ( 50.44, 66.89) --
+	( 55.44, 66.89) --
+	( 55.44, 71.88) --
+	( 50.44, 71.88) --
+	cycle;
+
+\path[fill=fillColor] ( 58.98, 71.24) --
+	( 63.98, 71.24) --
+	( 63.98, 76.24) --
+	( 58.98, 76.24) --
+	cycle;
+
+\path[fill=fillColor] ( 67.53, 75.45) --
+	( 72.52, 75.45) --
+	( 72.52, 80.44) --
+	( 67.53, 80.44) --
+	cycle;
+
+\path[fill=fillColor] ( 76.07, 79.40) --
+	( 81.06, 79.40) --
+	( 81.06, 84.39) --
+	( 76.07, 84.39) --
+	cycle;
+
+\path[fill=fillColor] ( 84.61, 83.31) --
+	( 89.61, 83.31) --
+	( 89.61, 88.30) --
+	( 84.61, 88.30) --
+	cycle;
+
+\path[fill=fillColor] ( 93.15, 87.27) --
+	( 98.15, 87.27) --
+	( 98.15, 92.27) --
+	( 93.15, 92.27) --
+	cycle;
+
+\path[fill=fillColor] (101.70, 91.22) --
+	(106.69, 91.22) --
+	(106.69, 96.22) --
+	(101.70, 96.22) --
+	cycle;
+
+\path[fill=fillColor] (110.24, 94.52) --
+	(115.23, 94.52) --
+	(115.23, 99.52) --
+	(110.24, 99.52) --
+	cycle;
+
+\path[fill=fillColor] (118.78, 97.88) --
+	(123.78, 97.88) --
+	(123.78,102.87) --
+	(118.78,102.87) --
+	cycle;
+
+\path[fill=fillColor] (127.32,100.97) --
+	(132.32,100.97) --
+	(132.32,105.96) --
+	(127.32,105.96) --
+	cycle;
+
+\path[fill=fillColor] (135.86,104.20) --
+	(140.86,104.20) --
+	(140.86,109.20) --
+	(135.86,109.20) --
+	cycle;
+
+\path[fill=fillColor] (144.41,107.50) --
+	(149.40,107.50) --
+	(149.40,112.49) --
+	(144.41,112.49) --
+	cycle;
+
+\path[fill=fillColor] (152.95,110.47) --
+	(157.94,110.47) --
+	(157.94,115.46) --
+	(152.95,115.46) --
+	cycle;
+
+\path[fill=fillColor] (161.49,113.31) --
+	(166.49,113.31) --
+	(166.49,118.31) --
+	(161.49,118.31) --
+	cycle;
+
+\path[fill=fillColor] (170.03,116.16) --
+	(175.03,116.16) --
+	(175.03,121.15) --
+	(170.03,121.15) --
+	cycle;
+
+\path[fill=fillColor] (178.58,119.44) --
+	(183.57,119.44) --
+	(183.57,124.44) --
+	(178.58,124.44) --
+	cycle;
+
+\path[fill=fillColor] (187.12,122.22) --
+	(192.11,122.22) --
+	(192.11,127.22) --
+	(187.12,127.22) --
+	cycle;
+
+\path[fill=fillColor] (195.66,125.20) --
+	(200.66,125.20) --
+	(200.66,130.19) --
+	(195.66,130.19) --
+	cycle;
+
+\path[fill=fillColor] (204.20,127.62) --
+	(209.20,127.62) --
+	(209.20,132.62) --
+	(204.20,132.62) --
+	cycle;
+
+\path[fill=fillColor] (212.74,130.39) --
+	(217.74,130.39) --
+	(217.74,135.38) --
+	(212.74,135.38) --
+	cycle;
+
+\path[fill=fillColor] (221.29,133.11) --
+	(226.28,133.11) --
+	(226.28,138.11) --
+	(221.29,138.11) --
+	cycle;
+
+\path[fill=fillColor] (229.83,135.65) --
+	(234.82,135.65) --
+	(234.82,140.64) --
+	(229.83,140.64) --
+	cycle;
+
+\path[fill=fillColor] (238.37,138.18) --
+	(243.37,138.18) --
+	(243.37,143.18) --
+	(238.37,143.18) --
+	cycle;
+
+\path[fill=fillColor] (246.91,140.83) --
+	(251.91,140.83) --
+	(251.91,145.82) --
+	(246.91,145.82) --
+	cycle;
+
+\path[fill=fillColor] (255.46,143.10) --
+	(260.45,143.10) --
+	(260.45,148.10) --
+	(255.46,148.10) --
+	cycle;
+
+\path[fill=fillColor] (264.00,145.63) --
+	(268.99,145.63) --
+	(268.99,150.63) --
+	(264.00,150.63) --
+	cycle;
+
+\path[fill=fillColor] (272.54,147.86) --
+	(277.54,147.86) --
+	(277.54,152.86) --
+	(272.54,152.86) --
+	cycle;
+
+\path[fill=fillColor] (281.08,150.27) --
+	(286.08,150.27) --
+	(286.08,155.27) --
+	(281.08,155.27) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78, 55.53) -- ( 30.85, 55.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31, 52.00) -- ( 27.31, 59.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32, 61.72) -- ( 39.39, 61.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86, 58.18) -- ( 35.86, 65.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87, 67.50) -- ( 47.93, 67.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40, 63.97) -- ( 44.40, 71.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41, 74.08) -- ( 56.47, 74.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94, 70.55) -- ( 52.94, 77.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95, 79.95) -- ( 65.01, 79.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48, 76.42) -- ( 61.48, 83.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49, 85.82) -- ( 73.56, 85.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02, 82.28) -- ( 70.02, 89.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03, 91.32) -- ( 82.10, 91.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57, 87.79) -- ( 78.57, 94.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58, 96.85) -- ( 90.64, 96.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11, 93.32) -- ( 87.11,100.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,102.37) -- ( 99.18,102.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 98.84) -- ( 95.65,105.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,107.95) -- (107.73,107.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,104.42) -- (104.19,111.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,112.40) -- (116.27,112.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,108.86) -- (112.74,115.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,117.27) -- (124.81,117.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,113.74) -- (121.28,120.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,121.67) -- (133.35,121.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,118.13) -- (129.82,125.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,126.30) -- (141.89,126.30);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,122.76) -- (138.36,129.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,131.03) -- (150.44,131.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,127.50) -- (146.90,134.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,135.37) -- (158.98,135.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,131.84) -- (155.45,138.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,139.39) -- (167.52,139.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,135.86) -- (163.99,142.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,143.52) -- (176.06,143.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,139.99) -- (172.53,147.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,148.36) -- (184.61,148.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,144.83) -- (181.07,151.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,152.40) -- (193.15,152.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,148.86) -- (189.62,155.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,156.84) -- (201.69,156.84);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,153.31) -- (198.16,160.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,160.37) -- (210.23,160.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,156.84) -- (206.70,163.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,164.46) -- (218.77,164.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,160.93) -- (215.24,168.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,168.49) -- (227.32,168.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,164.96) -- (223.78,172.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,172.17) -- (235.86,172.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,168.64) -- (232.33,175.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,175.87) -- (244.40,175.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,172.34) -- (240.87,179.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,180.09) -- (252.94,180.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,176.56) -- (249.41,183.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,183.35) -- (261.49,183.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,179.81) -- (257.95,186.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,187.13) -- (270.03,187.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,183.60) -- (266.50,190.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,190.53) -- (278.57,190.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,187.00) -- (275.04,194.06);
 
@@
 
-\path[fill=fillColor] ( 27.31, 47.39) circle (  2.50);
-
-\path[fill=fillColor] ( 35.86, 48.28) circle (  2.50);
-
-\path[fill=fillColor] ( 44.40, 48.31) circle (  2.50);
-
-\path[fill=fillColor] ( 52.94, 47.63) circle (  2.50);
-
-\path[fill=fillColor] ( 61.48, 48.69) circle (  2.50);
-
-\path[fill=fillColor] ( 70.02, 48.09) circle (  2.50);
-
-\path[fill=fillColor] ( 78.57, 48.15) circle (  2.50);
-
-\path[fill=fillColor] ( 87.11, 48.59) circle (  2.50);
-
-\path[fill=fillColor] ( 95.65, 48.01) circle (  2.50);
-
-\path[fill=fillColor] (104.19, 48.33) circle (  2.50);
-
-\path[fill=fillColor] (112.74, 47.97) circle (  2.50);
-
-\path[fill=fillColor] (121.28, 47.68) circle (  2.50);
-
-\path[fill=fillColor] (129.82, 47.78) circle (  2.50);
-
-\path[fill=fillColor] (138.36, 48.47) circle (  2.50);
-
-\path[fill=fillColor] (146.90, 47.94) circle (  2.50);
-
-\path[fill=fillColor] (155.45, 48.48) circle (  2.50);
-
-\path[fill=fillColor] (163.99, 48.56) circle (  2.50);
-
-\path[fill=fillColor] (172.53, 48.33) circle (  2.50);
-
-\path[fill=fillColor] (181.07, 48.25) circle (  2.50);
-
-\path[fill=fillColor] (189.62, 48.13) circle (  2.50);
-
-\path[fill=fillColor] (198.16, 48.23) circle (  2.50);
-
-\path[fill=fillColor] (206.70, 47.82) circle (  2.50);
-
-\path[fill=fillColor] (215.24, 48.29) circle (  2.50);
-
-\path[fill=fillColor] (223.78, 47.84) circle (  2.50);
-
-\path[fill=fillColor] (232.33, 47.85) circle (  2.50);
-
-\path[fill=fillColor] (240.87, 48.44) circle (  2.50);
-
-\path[fill=fillColor] (249.41, 48.50) circle (  2.50);
-
-\path[fill=fillColor] (257.95, 48.19) circle (  2.50);
-
-\path[fill=fillColor] (266.50, 48.39) circle (  2.50);
-
-\path[fill=fillColor] (275.04, 48.09) circle (  2.50);
-
-\path[fill=fillColor] (283.58, 47.98) circle (  2.50);
+\path[fill=fillColor] ( 27.31, 53.86) circle (  2.50);
+
+\path[fill=fillColor] ( 35.86, 54.98) circle (  2.50);
+
+\path[fill=fillColor] ( 44.40, 55.01) circle (  2.50);
+
+\path[fill=fillColor] ( 52.94, 54.11) circle (  2.50);
+
+\path[fill=fillColor] ( 61.48, 55.47) circle (  2.50);
+
+\path[fill=fillColor] ( 70.02, 54.78) circle (  2.50);
+
+\path[fill=fillColor] ( 78.57, 54.81) circle (  2.50);
+
+\path[fill=fillColor] ( 87.11, 55.37) circle (  2.50);
+
+\path[fill=fillColor] ( 95.65, 54.67) circle (  2.50);
+
+\path[fill=fillColor] (104.19, 55.03) circle (  2.50);
+
+\path[fill=fillColor] (112.74, 54.66) circle (  2.50);
+
+\path[fill=fillColor] (121.28, 54.19) circle (  2.50);
+
+\path[fill=fillColor] (129.82, 54.27) circle (  2.50);
+
+\path[fill=fillColor] (138.36, 55.20) circle (  2.50);
+
+\path[fill=fillColor] (146.90, 54.61) circle (  2.50);
+
+\path[fill=fillColor] (155.45, 55.25) circle (  2.50);
+
+\path[fill=fillColor] (163.99, 55.30) circle (  2.50);
+
+\path[fill=fillColor] (172.53, 55.03) circle (  2.50);
+
+\path[fill=fillColor] (181.07, 54.88) circle (  2.50);
+
+\path[fill=fillColor] (189.62, 54.77) circle (  2.50);
+
+\path[fill=fillColor] (198.16, 54.88) circle (  2.50);
+
+\path[fill=fillColor] (206.70, 54.44) circle (  2.50);
+
+\path[fill=fillColor] (215.24, 54.97) circle (  2.50);
+
+\path[fill=fillColor] (223.78, 54.48) circle (  2.50);
+
+\path[fill=fillColor] (232.33, 54.54) circle (  2.50);
+
+\path[fill=fillColor] (240.87, 55.09) circle (  2.50);
+
+\path[fill=fillColor] (249.41, 55.20) circle (  2.50);
+
+\path[fill=fillColor] (257.95, 54.91) circle (  2.50);
+
+\path[fill=fillColor] (266.50, 55.15) circle (  2.50);
+
+\path[fill=fillColor] (275.04, 54.72) circle (  2.50);
+
+\path[fill=fillColor] (283.58, 54.55) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 55.97) {5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,150.33) {6};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 52.35) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,134.65) {6};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 59.00) --
-	( 27.31, 59.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,153.36) --
-	( 27.31,153.36);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 55.38) --
+	( 27.31, 55.38);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,137.68) --
+	( 27.31,137.68);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (323.24, 49.95) --
-	(326.39, 49.96) --
-	(329.55, 49.96) --
-	(332.71, 49.96) --
-	(335.87, 49.97) --
-	(339.02, 49.97) --
-	(342.18, 49.98) --
-	(345.34, 49.98) --
-	(348.49, 49.98) --
-	(351.65, 49.98) --
-	(354.81, 49.99) --
-	(357.97, 49.99) --
-	(361.12, 49.99) --
-	(364.28, 49.99) --
-	(367.44, 49.99) --
-	(370.60, 50.00) --
-	(373.75, 50.00) --
-	(376.91, 50.00) --
-	(380.07, 50.00) --
-	(383.22, 50.00) --
-	(386.38, 50.00) --
-	(389.54, 50.00) --
-	(392.70, 50.00) --
-	(395.85, 50.00) --
-	(399.01, 50.00) --
-	(402.17, 50.00) --
-	(405.32, 50.00) --
-	(408.48, 49.99) --
-	(411.64, 49.99) --
-	(414.80, 49.99) --
-	(417.95, 49.99) --
-	(421.11, 49.98) --
-	(424.27, 49.98) --
-	(427.43, 49.97) --
-	(430.58, 49.97) --
-	(433.74, 49.96) --
-	(436.90, 49.95) --
-	(440.05, 49.95) --
-	(443.21, 49.94) --
-	(446.37, 49.94) --
-	(449.53, 49.94) --
-	(452.68, 49.94) --
-	(455.84, 49.94) --
-	(459.00, 49.95) --
-	(462.16, 49.95) --
-	(465.31, 49.95) --
-	(468.47, 49.95) --
-	(471.63, 49.96) --
-	(474.78, 49.96) --
-	(477.94, 49.96) --
-	(481.10, 49.97) --
-	(484.26, 49.97) --
-	(487.41, 49.97) --
-	(490.57, 49.98) --
-	(493.73, 49.98) --
-	(496.89, 49.98) --
-	(500.04, 49.99) --
-	(503.20, 49.99) --
-	(506.36, 49.99) --
-	(509.51, 50.00) --
-	(512.67, 50.00) --
-	(515.83, 50.00) --
-	(518.99, 50.00) --
-	(522.14, 50.00) --
-	(525.30, 50.00) --
-	(528.46, 50.00) --
-	(531.62, 50.00) --
-	(534.77, 49.99) --
-	(537.93, 49.99) --
-	(541.09, 49.99) --
-	(544.24, 49.99) --
-	(547.40, 49.99) --
-	(550.56, 49.98) --
-	(553.72, 49.98) --
-	(556.87, 49.97) --
-	(560.03, 49.97) --
-	(563.19, 49.96) --
-	(566.35, 49.96) --
-	(569.50, 49.95) --
-	(572.66, 49.94);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (323.24, 68.09) --
+	(326.39, 68.10) --
+	(329.55, 68.10) --
+	(332.71, 68.11) --
+	(335.87, 68.12) --
+	(339.02, 68.12) --
+	(342.18, 68.13) --
+	(345.34, 68.14) --
+	(348.49, 68.14) --
+	(351.65, 68.14) --
+	(354.81, 68.15) --
+	(357.97, 68.15) --
+	(361.12, 68.15) --
+	(364.28, 68.16) --
+	(367.44, 68.16) --
+	(370.60, 68.16) --
+	(373.75, 68.16) --
+	(376.91, 68.16) --
+	(380.07, 68.16) --
+	(383.22, 68.16) --
+	(386.38, 68.16) --
+	(389.54, 68.16) --
+	(392.70, 68.16) --
+	(395.85, 68.16) --
+	(399.01, 68.16) --
+	(402.17, 68.16) --
+	(405.32, 68.15) --
+	(408.48, 68.15) --
+	(411.64, 68.15) --
+	(414.80, 68.14) --
+	(417.95, 68.13) --
+	(421.11, 68.12) --
+	(424.27, 68.11) --
+	(427.43, 68.09) --
+	(430.58, 68.08) --
+	(433.74, 68.06) --
+	(436.90, 68.04) --
+	(440.05, 68.03) --
+	(443.21, 68.02) --
+	(446.37, 68.01) --
+	(449.53, 68.01) --
+	(452.68, 68.01) --
+	(455.84, 68.01) --
+	(459.00, 68.02) --
+	(462.16, 68.02) --
+	(465.31, 68.03) --
+	(468.47, 68.04) --
+	(471.63, 68.04) --
+	(474.78, 68.05) --
+	(477.94, 68.06) --
+	(481.10, 68.06) --
+	(484.26, 68.07) --
+	(487.41, 68.08) --
+	(490.57, 68.09) --
+	(493.73, 68.10) --
+	(496.89, 68.11) --
+	(500.04, 68.12) --
+	(503.20, 68.13) --
+	(506.36, 68.13) --
+	(509.51, 68.14) --
+	(512.67, 68.14) --
+	(515.83, 68.15) --
+	(518.99, 68.15) --
+	(522.14, 68.15) --
+	(525.30, 68.15) --
+	(528.46, 68.15) --
+	(531.62, 68.14) --
+	(534.77, 68.14) --
+	(537.93, 68.14) --
+	(541.09, 68.14) --
+	(544.24, 68.13) --
+	(547.40, 68.12) --
+	(550.56, 68.12) --
+	(553.72, 68.11) --
+	(556.87, 68.10) --
+	(560.03, 68.08) --
+	(563.19, 68.07) --
+	(566.35, 68.06) --
+	(569.50, 68.04) --
+	(572.66, 68.03);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24,140.06) --
-	(326.39,138.91) --
-	(329.55,137.78) --
-	(332.71,136.67) --
-	(335.87,135.58) --
-	(339.02,134.51) --
-	(342.18,133.46) --
-	(345.34,132.43) --
-	(348.49,131.43) --
-	(351.65,130.44) --
-	(354.81,129.47) --
-	(357.97,128.52) --
-	(361.12,127.60) --
-	(364.28,126.69) --
-	(367.44,125.80) --
-	(370.60,124.93) --
-	(373.75,124.08) --
-	(376.91,123.25) --
-	(380.07,122.43) --
-	(383.22,121.64) --
-	(386.38,120.87) --
-	(389.54,120.12) --
-	(392.70,119.40) --
-	(395.85,118.70) --
-	(399.01,118.02) --
-	(402.17,117.36) --
-	(405.32,116.71) --
-	(408.48,116.08) --
-	(411.64,115.46) --
-	(414.80,114.85) --
-	(417.95,114.27) --
-	(421.11,113.70) --
-	(424.27,113.17) --
-	(427.43,112.65) --
-	(430.58,112.15) --
-	(433.74,111.66) --
-	(436.90,111.18) --
-	(440.05,110.70) --
-	(443.21,110.23) --
-	(446.37,109.76) --
-	(449.53,109.28) --
-	(452.68,108.82) --
-	(455.84,108.37) --
-	(459.00,107.93) --
-	(462.16,107.50) --
-	(465.31,107.08) --
-	(468.47,106.66) --
-	(471.63,106.25) --
-	(474.78,105.85) --
-	(477.94,105.44) --
-	(481.10,105.04) --
-	(484.26,104.64) --
-	(487.41,104.25) --
-	(490.57,103.86) --
-	(493.73,103.48) --
-	(496.89,103.10) --
-	(500.04,102.73) --
-	(503.20,102.36) --
-	(506.36,102.00) --
-	(509.51,101.65) --
-	(512.67,101.30) --
-	(515.83,100.95) --
-	(518.99,100.61) --
-	(522.14,100.27) --
-	(525.30, 99.94) --
-	(528.46, 99.61) --
-	(531.62, 99.29) --
-	(534.77, 98.98) --
-	(537.93, 98.67) --
-	(541.09, 98.37) --
-	(544.24, 98.07) --
-	(547.40, 97.77) --
-	(550.56, 97.48) --
-	(553.72, 97.20) --
-	(556.87, 96.92) --
-	(560.03, 96.65) --
-	(563.19, 96.38) --
-	(566.35, 96.12) --
-	(569.50, 95.86) --
-	(572.66, 95.61);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24,141.29) --
+	(326.39,140.30) --
+	(329.55,139.33) --
+	(332.71,138.37) --
+	(335.87,137.43) --
+	(339.02,136.50) --
+	(342.18,135.60) --
+	(345.34,134.71) --
+	(348.49,133.83) --
+	(351.65,132.97) --
+	(354.81,132.13) --
+	(357.97,131.31) --
+	(361.12,130.51) --
+	(364.28,129.71) --
+	(367.44,128.94) --
+	(370.60,128.18) --
+	(373.75,127.44) --
+	(376.91,126.71) --
+	(380.07,126.00) --
+	(383.22,125.30) --
+	(386.38,124.63) --
+	(389.54,123.97) --
+	(392.70,123.33) --
+	(395.85,122.72) --
+	(399.01,122.12) --
+	(402.17,121.53) --
+	(405.32,120.96) --
+	(408.48,120.39) --
+	(411.64,119.84) --
+	(414.80,119.30) --
+	(417.95,118.78) --
+	(421.11,118.27) --
+	(424.27,117.79) --
+	(427.43,117.32) --
+	(430.58,116.87) --
+	(433.74,116.43) --
+	(436.90,115.99) --
+	(440.05,115.56) --
+	(443.21,115.13) --
+	(446.37,114.70) --
+	(449.53,114.27) --
+	(452.68,113.85) --
+	(455.84,113.44) --
+	(459.00,113.04) --
+	(462.16,112.65) --
+	(465.31,112.27) --
+	(468.47,111.89) --
+	(471.63,111.52) --
+	(474.78,111.14) --
+	(477.94,110.78) --
+	(481.10,110.41) --
+	(484.26,110.04) --
+	(487.41,109.68) --
+	(490.57,109.32) --
+	(493.73,108.97) --
+	(496.89,108.62) --
+	(500.04,108.28) --
+	(503.20,107.94) --
+	(506.36,107.61) --
+	(509.51,107.28) --
+	(512.67,106.96) --
+	(515.83,106.63) --
+	(518.99,106.32) --
+	(522.14,106.01) --
+	(525.30,105.70) --
+	(528.46,105.39) --
+	(531.62,105.09) --
+	(534.77,104.80) --
+	(537.93,104.51) --
+	(541.09,104.23) --
+	(544.24,103.94) --
+	(547.40,103.67) --
+	(550.56,103.40) --
+	(553.72,103.13) --
+	(556.87,102.86) --
+	(560.03,102.60) --
+	(563.19,102.35) --
+	(566.35,102.10) --
+	(569.50,101.85) --
+	(572.66,101.61);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,172.74) --
-	(326.39,170.89) --
-	(329.55,169.07) --
-	(332.71,167.28) --
-	(335.87,165.53) --
-	(339.02,163.81) --
-	(342.18,162.12) --
-	(345.34,160.46) --
-	(348.49,158.84) --
-	(351.65,157.25) --
-	(354.81,155.70) --
-	(357.97,154.18) --
-	(361.12,152.70) --
-	(364.28,151.25) --
-	(367.44,149.83) --
-	(370.60,148.44) --
-	(373.75,147.08) --
-	(376.91,145.75) --
-	(380.07,144.46) --
-	(383.22,143.19) --
-	(386.38,141.97) --
-	(389.54,140.79) --
-	(392.70,139.65) --
-	(395.85,138.55) --
-	(399.01,137.48) --
-	(402.17,136.44) --
-	(405.32,135.42) --
-	(408.48,134.43) --
-	(411.64,133.46) --
-	(414.80,132.50) --
-	(417.95,131.58) --
-	(421.11,130.71) --
-	(424.27,129.87) --
-	(427.43,129.06) --
-	(430.58,128.28) --
-	(433.74,127.53) --
-	(436.90,126.78) --
-	(440.05,126.05) --
-	(443.21,125.32) --
-	(446.37,124.59) --
-	(449.53,123.86) --
-	(452.68,123.14) --
-	(455.84,122.45) --
-	(459.00,121.78) --
-	(462.16,121.12) --
-	(465.31,120.48) --
-	(468.47,119.84) --
-	(471.63,119.22) --
-	(474.78,118.60) --
-	(477.94,117.99) --
-	(481.10,117.38) --
-	(484.26,116.77) --
-	(487.41,116.17) --
-	(490.57,115.58) --
-	(493.73,115.01) --
-	(496.89,114.44) --
-	(500.04,113.88) --
-	(503.20,113.33) --
-	(506.36,112.79) --
-	(509.51,112.25) --
-	(512.67,111.72) --
-	(515.83,111.20) --
-	(518.99,110.69) --
-	(522.14,110.19) --
-	(525.30,109.69) --
-	(528.46,109.21) --
-	(531.62,108.73) --
-	(534.77,108.26) --
-	(537.93,107.80) --
-	(541.09,107.35) --
-	(544.24,106.91) --
-	(547.40,106.48) --
-	(550.56,106.05) --
-	(553.72,105.63) --
-	(556.87,105.22) --
-	(560.03,104.82) --
-	(563.19,104.43) --
-	(566.35,104.05) --
-	(569.50,103.67) --
-	(572.66,103.31);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,185.67) --
+	(326.39,183.76) --
+	(329.55,181.89) --
+	(332.71,180.05) --
+	(335.87,178.24) --
+	(339.02,176.47) --
+	(342.18,174.73) --
+	(345.34,173.02) --
+	(348.49,171.35) --
+	(351.65,169.71) --
+	(354.81,168.11) --
+	(357.97,166.55) --
+	(361.12,165.01) --
+	(364.28,163.51) --
+	(367.44,162.05) --
+	(370.60,160.61) --
+	(373.75,159.21) --
+	(376.91,157.84) --
+	(380.07,156.49) --
+	(383.22,155.18) --
+	(386.38,153.92) --
+	(389.54,152.70) --
+	(392.70,151.52) --
+	(395.85,150.37) --
+	(399.01,149.26) --
+	(402.17,148.17) --
+	(405.32,147.12) --
+	(408.48,146.09) --
+	(411.64,145.08) --
+	(414.80,144.08) --
+	(417.95,143.12) --
+	(421.11,142.21) --
+	(424.27,141.33) --
+	(427.43,140.48) --
+	(430.58,139.67) --
+	(433.74,138.87) --
+	(436.90,138.09) --
+	(440.05,137.32) --
+	(443.21,136.56) --
+	(446.37,135.79) --
+	(449.53,135.02) --
+	(452.68,134.27) --
+	(455.84,133.54) --
+	(459.00,132.83) --
+	(462.16,132.14) --
+	(465.31,131.46) --
+	(468.47,130.80) --
+	(471.63,130.14) --
+	(474.78,129.49) --
+	(477.94,128.85) --
+	(481.10,128.20) --
+	(484.26,127.56) --
+	(487.41,126.93) --
+	(490.57,126.31) --
+	(493.73,125.70) --
+	(496.89,125.11) --
+	(500.04,124.52) --
+	(503.20,123.94) --
+	(506.36,123.36) --
+	(509.51,122.80) --
+	(512.67,122.24) --
+	(515.83,121.69) --
+	(518.99,121.15) --
+	(522.14,120.61) --
+	(525.30,120.09) --
+	(528.46,119.58) --
+	(531.62,119.07) --
+	(534.77,118.57) --
+	(537.93,118.08) --
+	(541.09,117.60) --
+	(544.24,117.13) --
+	(547.40,116.67) --
+	(550.56,116.22) --
+	(553.72,115.77) --
+	(556.87,115.33) --
+	(560.03,114.91) --
+	(563.19,114.49) --
+	(566.35,114.07) --
+	(569.50,113.67) --
+	(572.66,113.28);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (339.86,189.79) --
-	(342.81,187.67) --
-	(345.76,185.60) --
-	(348.70,183.56) --
-	(351.65,181.56) --
-	(354.60,179.59) --
-	(357.55,177.67) --
-	(360.49,175.78) --
-	(363.44,173.93) --
-	(366.39,172.12) --
-	(369.33,170.35) --
-	(372.28,168.62) --
-	(375.23,166.93) --
-	(378.17,165.28) --
-	(381.12,163.66) --
-	(384.07,162.09) --
-	(387.01,160.54) --
-	(389.96,159.03) --
-	(392.91,157.56) --
-	(395.85,156.12) --
-	(398.80,154.71) --
-	(401.75,153.36) --
-	(404.69,152.05) --
-	(407.64,150.80) --
-	(410.59,149.59) --
-	(413.53,148.42) --
-	(416.48,147.28) --
-	(419.43,146.18) --
-	(422.37,145.09) --
-	(425.32,144.03) --
-	(428.27,142.98) --
-	(431.21,141.94) --
-	(434.16,140.93) --
-	(437.11,139.96) --
-	(440.05,139.04) --
-	(443.00,138.14) --
-	(445.95,137.27) --
-	(448.90,136.41) --
-	(451.84,135.56) --
-	(454.79,134.70) --
-	(457.74,133.83) --
-	(460.68,132.98) --
-	(463.63,132.14) --
-	(466.58,131.32) --
-	(469.52,130.52) --
-	(472.47,129.73) --
-	(475.42,128.95) --
-	(478.36,128.19) --
-	(481.31,127.43) --
-	(484.26,126.69) --
-	(487.20,125.95) --
-	(490.15,125.22) --
-	(493.10,124.50) --
-	(496.04,123.80) --
-	(498.99,123.11) --
-	(501.94,122.43) --
-	(504.88,121.76) --
-	(507.83,121.11) --
-	(510.78,120.46) --
-	(513.72,119.81) --
-	(516.67,119.18) --
-	(519.62,118.55) --
-	(522.56,117.94) --
-	(525.51,117.34) --
-	(528.46,116.75) --
-	(531.41,116.16) --
-	(534.35,115.59) --
-	(537.30,115.03) --
-	(540.25,114.48) --
-	(543.19,113.94) --
-	(546.14,113.41) --
-	(549.09,112.89) --
-	(552.03,112.37) --
-	(554.98,111.87) --
-	(557.93,111.38) --
-	(560.87,110.90) --
-	(563.82,110.43) --
-	(566.77,109.97) --
-	(569.71,109.51) --
-	(572.66,109.07);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (364.81,191.74) --
+	(367.44,190.07) --
+	(370.07,188.42) --
+	(372.70,186.81) --
+	(375.33,185.22) --
+	(377.96,183.67) --
+	(380.59,182.13) --
+	(383.22,180.63) --
+	(385.86,179.15) --
+	(388.49,177.70) --
+	(391.12,176.27) --
+	(393.75,174.87) --
+	(396.38,173.50) --
+	(399.01,172.16) --
+	(401.64,170.85) --
+	(404.27,169.56) --
+	(406.90,168.29) --
+	(409.53,167.05) --
+	(412.17,165.83) --
+	(414.80,164.63) --
+	(417.43,163.47) --
+	(420.06,162.34) --
+	(422.69,161.26) --
+	(425.32,160.20) --
+	(427.95,159.18) --
+	(430.58,158.17) --
+	(433.21,157.19) --
+	(435.85,156.21) --
+	(438.48,155.25) --
+	(441.11,154.29) --
+	(443.74,153.36) --
+	(446.37,152.46) --
+	(449.00,151.59) --
+	(451.63,150.73) --
+	(454.26,149.89) --
+	(456.89,149.05) --
+	(459.52,148.23) --
+	(462.16,147.40) --
+	(464.79,146.58) --
+	(467.42,145.76) --
+	(470.05,144.95) --
+	(472.68,144.16) --
+	(475.31,143.38) --
+	(477.94,142.60) --
+	(480.57,141.84) --
+	(483.20,141.09) --
+	(485.84,140.34) --
+	(488.47,139.61) --
+	(491.10,138.89) --
+	(493.73,138.18) --
+	(496.36,137.48) --
+	(498.99,136.79) --
+	(501.62,136.11) --
+	(504.25,135.44) --
+	(506.88,134.78) --
+	(509.51,134.14) --
+	(512.15,133.50) --
+	(514.78,132.87) --
+	(517.41,132.25) --
+	(520.04,131.64) --
+	(522.67,131.03) --
+	(525.30,130.43) --
+	(527.93,129.84) --
+	(530.56,129.25) --
+	(533.19,128.68) --
+	(535.83,128.11) --
+	(538.46,127.56) --
+	(541.09,127.01) --
+	(543.72,126.47) --
+	(546.35,125.94) --
+	(548.98,125.42) --
+	(551.61,124.90) --
+	(554.24,124.39) --
+	(556.87,123.90) --
+	(559.50,123.41) --
+	(562.14,122.93) --
+	(564.77,122.45) --
+	(567.40,121.99) --
+	(570.03,121.53) --
+	(572.66,121.08);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] (323.24,144.25) --
-	(326.60,138.42) --
-	(319.87,138.42) --
-	cycle;
-
-\path[fill=fillColor] (331.55,140.97) --
-	(334.91,135.14) --
-	(328.19,135.14) --
-	cycle;
-
-\path[fill=fillColor] (339.86,138.16) --
-	(343.23,132.34) --
-	(336.50,132.34) --
-	cycle;
-
-\path[fill=fillColor] (348.18,135.26) --
-	(351.54,129.43) --
-	(344.81,129.43) --
-	cycle;
-
-\path[fill=fillColor] (356.49,132.48) --
-	(359.86,126.65) --
-	(353.13,126.65) --
-	cycle;
-
-\path[fill=fillColor] (364.81,130.21) --
-	(368.17,124.38) --
-	(361.44,124.38) --
-	cycle;
-
-\path[fill=fillColor] (373.12,128.06) --
-	(376.48,122.24) --
-	(369.76,122.24) --
-	cycle;
-
-\path[fill=fillColor] (381.44,125.99) --
-	(384.80,120.16) --
-	(378.07,120.16) --
-	cycle;
-
-\path[fill=fillColor] (389.75,123.88) --
-	(393.11,118.06) --
-	(386.39,118.06) --
-	cycle;
-
-\path[fill=fillColor] (398.06,121.85) --
-	(401.43,116.03) --
-	(394.70,116.03) --
-	cycle;
-
-\path[fill=fillColor] (406.38,120.12) --
-	(409.74,114.29) --
-	(403.01,114.29) --
-	cycle;
-
-\path[fill=fillColor] (414.69,118.70) --
-	(418.06,112.87) --
-	(411.33,112.87) --
-	cycle;
-
-\path[fill=fillColor] (423.01,117.31) --
-	(426.37,111.48) --
-	(419.64,111.48) --
-	cycle;
-
-\path[fill=fillColor] (431.32,116.01) --
-	(434.68,110.19) --
-	(427.96,110.19) --
-	cycle;
-
-\path[fill=fillColor] (439.63,114.62) --
-	(443.00,108.79) --
-	(436.27,108.79) --
-	cycle;
-
-\path[fill=fillColor] (447.95,113.52) --
-	(451.31,107.69) --
-	(444.58,107.69) --
-	cycle;
-
-\path[fill=fillColor] (456.26,112.31) --
-	(459.63,106.48) --
-	(452.90,106.48) --
-	cycle;
-
-\path[fill=fillColor] (464.58,111.32) --
-	(467.94,105.49) --
-	(461.21,105.49) --
-	cycle;
-
-\path[fill=fillColor] (472.89,109.94) --
-	(476.25,104.11) --
-	(469.53,104.11) --
-	cycle;
-
-\path[fill=fillColor] (481.20,108.82) --
-	(484.57,102.99) --
-	(477.84,102.99) --
-	cycle;
-
-\path[fill=fillColor] (489.52,107.83) --
-	(492.88,102.00) --
-	(486.15,102.00) --
-	cycle;
-
-\path[fill=fillColor] (497.83,106.85) --
-	(501.20,101.02) --
-	(494.47,101.02) --
-	cycle;
-
-\path[fill=fillColor] (506.15,105.93) --
-	(509.51,100.10) --
-	(502.78,100.10) --
-	cycle;
-
-\path[fill=fillColor] (514.46,104.96) --
-	(517.82, 99.14) --
-	(511.10, 99.14) --
-	cycle;
-
-\path[fill=fillColor] (522.78,104.12) --
-	(526.14, 98.29) --
-	(519.41, 98.29) --
-	cycle;
-
-\path[fill=fillColor] (531.09,103.27) --
-	(534.45, 97.45) --
-	(527.73, 97.45) --
-	cycle;
-
-\path[fill=fillColor] (539.40,102.56) --
-	(542.77, 96.73) --
-	(536.04, 96.73) --
-	cycle;
-
-\path[fill=fillColor] (547.72,101.64) --
-	(551.08, 95.82) --
-	(544.35, 95.82) --
-	cycle;
-
-\path[fill=fillColor] (556.03,100.83) --
-	(559.40, 95.01) --
-	(552.67, 95.01) --
-	cycle;
-
-\path[fill=fillColor] (564.35,100.20) --
-	(567.71, 94.37) --
-	(560.98, 94.37) --
-	cycle;
-
-\path[fill=fillColor] (572.66, 99.42) --
-	(576.02, 93.59) --
-	(569.30, 93.59) --
+\path[fill=fillColor] (323.24,145.42) --
+	(326.60,139.59) --
+	(319.87,139.59) --
+	cycle;
+
+\path[fill=fillColor] (331.55,142.62) --
+	(334.91,136.79) --
+	(328.19,136.79) --
+	cycle;
+
+\path[fill=fillColor] (339.86,140.20) --
+	(343.23,134.37) --
+	(336.50,134.37) --
+	cycle;
+
+\path[fill=fillColor] (348.18,137.66) --
+	(351.54,131.83) --
+	(344.81,131.83) --
+	cycle;
+
+\path[fill=fillColor] (356.49,135.29) --
+	(359.86,129.47) --
+	(353.13,129.47) --
+	cycle;
+
+\path[fill=fillColor] (364.81,133.27) --
+	(368.17,127.44) --
+	(361.44,127.44) --
+	cycle;
+
+\path[fill=fillColor] (373.12,131.42) --
+	(376.48,125.59) --
+	(369.76,125.59) --
+	cycle;
+
+\path[fill=fillColor] (381.44,129.62) --
+	(384.80,123.79) --
+	(378.07,123.79) --
+	cycle;
+
+\path[fill=fillColor] (389.75,127.76) --
+	(393.11,121.93) --
+	(386.39,121.93) --
+	cycle;
+
+\path[fill=fillColor] (398.06,125.95) --
+	(401.43,120.13) --
+	(394.70,120.13) --
+	cycle;
+
+\path[fill=fillColor] (406.38,124.42) --
+	(409.74,118.60) --
+	(403.01,118.60) --
+	cycle;
+
+\path[fill=fillColor] (414.69,123.14) --
+	(418.06,117.32) --
+	(411.33,117.32) --
+	cycle;
+
+\path[fill=fillColor] (423.01,121.89) --
+	(426.37,116.06) --
+	(419.64,116.06) --
+	cycle;
+
+\path[fill=fillColor] (431.32,120.75) --
+	(434.68,114.92) --
+	(427.96,114.92) --
+	cycle;
+
+\path[fill=fillColor] (439.63,119.48) --
+	(443.00,113.66) --
+	(436.27,113.66) --
+	cycle;
+
+\path[fill=fillColor] (447.95,118.47) --
+	(451.31,112.64) --
+	(444.58,112.64) --
+	cycle;
+
+\path[fill=fillColor] (456.26,117.35) --
+	(459.63,111.52) --
+	(452.90,111.52) --
+	cycle;
+
+\path[fill=fillColor] (464.58,116.47) --
+	(467.94,110.64) --
+	(461.21,110.64) --
+	cycle;
+
+\path[fill=fillColor] (472.89,115.21) --
+	(476.25,109.39) --
+	(469.53,109.39) --
+	cycle;
+
+\path[fill=fillColor] (481.20,114.19) --
+	(484.57,108.37) --
+	(477.84,108.37) --
+	cycle;
+
+\path[fill=fillColor] (489.52,113.29) --
+	(492.88,107.46) --
+	(486.15,107.46) --
+	cycle;
+
+\path[fill=fillColor] (497.83,112.38) --
+	(501.20,106.55) --
+	(494.47,106.55) --
+	cycle;
+
+\path[fill=fillColor] (506.15,111.57) --
+	(509.51,105.74) --
+	(502.78,105.74) --
+	cycle;
+
+\path[fill=fillColor] (514.46,110.65) --
+	(517.82,104.82) --
+	(511.10,104.82) --
+	cycle;
+
+\path[fill=fillColor] (522.78,109.83) --
+	(526.14,104.01) --
+	(519.41,104.01) --
+	cycle;
+
+\path[fill=fillColor] (531.09,109.08) --
+	(534.45,103.25) --
+	(527.73,103.25) --
+	cycle;
+
+\path[fill=fillColor] (539.40,108.38) --
+	(542.77,102.55) --
+	(536.04,102.55) --
+	cycle;
+
+\path[fill=fillColor] (547.72,107.52) --
+	(551.08,101.70) --
+	(544.35,101.70) --
+	cycle;
+
+\path[fill=fillColor] (556.03,106.78) --
+	(559.40,100.96) --
+	(552.67,100.96) --
+	cycle;
+
+\path[fill=fillColor] (564.35,106.17) --
+	(567.71,100.34) --
+	(560.98,100.34) --
+	cycle;
+
+\path[fill=fillColor] (572.66,105.44) --
+	(576.02, 99.61) --
+	(569.30, 99.61) --
 	cycle;
@@
 
-\path[fill=fillColor] (320.74,170.78) --
-	(325.73,170.78) --
-	(325.73,175.77) --
-	(320.74,175.77) --
-	cycle;
-
-\path[fill=fillColor] (329.05,165.46) --
-	(334.05,165.46) --
-	(334.05,170.45) --
-	(329.05,170.45) --
-	cycle;
-
-\path[fill=fillColor] (337.37,160.96) --
-	(342.36,160.96) --
-	(342.36,165.95) --
-	(337.37,165.95) --
-	cycle;
-
-\path[fill=fillColor] (345.68,156.26) --
-	(350.68,156.26) --
-	(350.68,161.25) --
-	(345.68,161.25) --
-	cycle;
-
-\path[fill=fillColor] (353.99,151.74) --
-	(358.99,151.74) --
-	(358.99,156.74) --
-	(353.99,156.74) --
-	cycle;
-
-\path[fill=fillColor] (362.31,148.12) --
-	(367.30,148.12) --
-	(367.30,153.11) --
-	(362.31,153.11) --
-	cycle;
-
-\path[fill=fillColor] (370.62,144.68) --
-	(375.62,144.68) --
-	(375.62,149.67) --
-	(370.62,149.67) --
-	cycle;
-
-\path[fill=fillColor] (378.94,141.38) --
-	(383.93,141.38) --
-	(383.93,146.38) --
-	(378.94,146.38) --
-	cycle;
-
-\path[fill=fillColor] (387.25,138.08) --
-	(392.25,138.08) --
-	(392.25,143.07) --
-	(387.25,143.07) --
-	cycle;
-
-\path[fill=fillColor] (395.57,134.92) --
-	(400.56,134.92) --
-	(400.56,139.92) --
-	(395.57,139.92) --
-	cycle;
-
-\path[fill=fillColor] (403.88,132.16) --
-	(408.88,132.16) --
-	(408.88,137.16) --
-	(403.88,137.16) --
-	cycle;
-
-\path[fill=fillColor] (412.19,129.98) --
-	(417.19,129.98) --
-	(417.19,134.97) --
-	(412.19,134.97) --
-	cycle;
-
-\path[fill=fillColor] (420.51,127.83) --
-	(425.50,127.83) --
-	(425.50,132.82) --
-	(420.51,132.82) --
-	cycle;
-
-\path[fill=fillColor] (428.82,125.76) --
-	(433.82,125.76) --
-	(433.82,130.76) --
-	(428.82,130.76) --
-	cycle;
-
-\path[fill=fillColor] (437.14,123.59) --
-	(442.13,123.59) --
-	(442.13,128.58) --
-	(437.14,128.58) --
-	cycle;
-
-\path[fill=fillColor] (445.45,121.88) --
-	(450.45,121.88) --
-	(450.45,126.88) --
-	(445.45,126.88) --
-	cycle;
-
-\path[fill=fillColor] (453.76,120.04) --
-	(458.76,120.04) --
-	(458.76,125.03) --
-	(453.76,125.03) --
-	cycle;
-
-\path[fill=fillColor] (462.08,118.49) --
-	(467.07,118.49) --
-	(467.07,123.48) --
-	(462.08,123.48) --
-	cycle;
-
-\path[fill=fillColor] (470.39,116.43) --
-	(475.39,116.43) --
-	(475.39,121.43) --
-	(470.39,121.43) --
-	cycle;
-
-\path[fill=fillColor] (478.71,114.73) --
-	(483.70,114.73) --
-	(483.70,119.72) --
-	(478.71,119.72) --
-	cycle;
-
-\path[fill=fillColor] (487.02,113.23) --
-	(492.02,113.23) --
-	(492.02,118.23) --
-	(487.02,118.23) --
-	cycle;
-
-\path[fill=fillColor] (495.34,111.77) --
-	(500.33,111.77) --
-	(500.33,116.77) --
-	(495.34,116.77) --
-	cycle;
-
-\path[fill=fillColor] (503.65,110.35) --
-	(508.64,110.35) --
-	(508.64,115.34) --
-	(503.65,115.34) --
-	cycle;
-
-\path[fill=fillColor] (511.96,108.90) --
-	(516.96,108.90) --
-	(516.96,113.90) --
-	(511.96,113.90) --
-	cycle;
-
-\path[fill=fillColor] (520.28,107.65) --
-	(525.27,107.65) --
-	(525.27,112.64) --
-	(520.28,112.64) --
-	cycle;
-
-\path[fill=fillColor] (528.59,106.36) --
-	(533.59,106.36) --
-	(533.59,111.36) --
-	(528.59,111.36) --
-	cycle;
-
-\path[fill=fillColor] (536.91,105.34) --
-	(541.90,105.34) --
-	(541.90,110.33) --
-	(536.91,110.33) --
-	cycle;
-
-\path[fill=fillColor] (545.22,104.01) --
-	(550.22,104.01) --
-	(550.22,109.01) --
-	(545.22,109.01) --
-	cycle;
-
-\path[fill=fillColor] (553.53,102.76) --
-	(558.53,102.76) --
-	(558.53,107.75) --
-	(553.53,107.75) --
-	cycle;
-
-\path[fill=fillColor] (561.85,101.83) --
-	(566.84,101.83) --
-	(566.84,106.83) --
-	(561.85,106.83) --
-	cycle;
-
-\path[fill=fillColor] (570.16,100.67) --
-	(575.16,100.67) --
-	(575.16,105.66) --
-	(570.16,105.66) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.33,190.59) -- (343.40,190.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.86,187.06) -- (339.86,194.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.65,184.03) -- (351.71,184.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.18,180.49) -- (348.18,187.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.96,177.69) -- (360.02,177.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.49,174.16) -- (356.49,181.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,172.70) -- (368.34,172.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,169.17) -- (364.81,176.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,167.92) -- (376.65,167.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,164.38) -- (373.12,171.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,163.35) -- (384.97,163.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,159.82) -- (381.44,166.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,158.83) -- (393.28,158.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,155.30) -- (389.75,162.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,154.55) -- (401.60,154.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,151.01) -- (398.06,158.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,150.76) -- (409.91,150.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,147.23) -- (406.38,154.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,147.81) -- (418.22,147.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,144.28) -- (414.69,151.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,144.92) -- (426.54,144.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,141.39) -- (423.01,148.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,142.06) -- (434.85,142.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,138.53) -- (431.32,145.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,139.16) -- (443.17,139.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,135.62) -- (439.63,142.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,136.86) -- (451.48,136.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,133.33) -- (447.95,140.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,134.36) -- (459.79,134.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,130.83) -- (456.26,137.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,132.27) -- (468.11,132.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,128.74) -- (464.58,135.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,129.57) -- (476.42,129.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,126.04) -- (472.89,133.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,127.31) -- (484.74,127.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,123.78) -- (481.20,130.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,125.32) -- (493.05,125.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,121.79) -- (489.52,128.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,123.43) -- (501.36,123.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,119.89) -- (497.83,126.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,121.47) -- (509.68,121.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,117.93) -- (506.15,125.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,119.60) -- (517.99,119.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,116.06) -- (514.46,123.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,117.95) -- (526.31,117.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,114.42) -- (522.78,121.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,116.25) -- (534.62,116.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,112.72) -- (531.09,119.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,114.97) -- (542.94,114.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,111.44) -- (539.40,118.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,113.27) -- (551.25,113.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72,109.73) -- (547.72,116.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,111.59) -- (559.56,111.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03,108.05) -- (556.03,115.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,110.40) -- (567.88,110.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35,106.87) -- (564.35,113.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,108.89) -- (576.19,108.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,105.36) -- (572.66,112.42);
+\path[fill=fillColor] (320.74,183.71) --
+	(325.73,183.71) --
+	(325.73,188.71) --
+	(320.74,188.71) --
+	cycle;
+
+\path[fill=fillColor] (329.05,178.25) --
+	(334.05,178.25) --
+	(334.05,183.24) --
+	(329.05,183.24) --
+	cycle;
+
+\path[fill=fillColor] (337.37,173.63) --
+	(342.36,173.63) --
+	(342.36,178.62) --
+	(337.37,178.62) --
+	cycle;
+
+\path[fill=fillColor] (345.68,168.76) --
+	(350.68,168.76) --
+	(350.68,173.76) --
+	(345.68,173.76) --
+	cycle;
+
+\path[fill=fillColor] (353.99,164.12) --
+	(358.99,164.12) --
+	(358.99,169.12) --
+	(353.99,169.12) --
+	cycle;
+
+\path[fill=fillColor] (362.31,160.33) --
+	(367.30,160.33) --
+	(367.30,165.33) --
+	(362.31,165.33) --
+	cycle;
+
+\path[fill=fillColor] (370.62,156.78) --
+	(375.62,156.78) --
+	(375.62,161.77) --
+	(370.62,161.77) --
+	cycle;
+
+\path[fill=fillColor] (378.94,153.43) --
+	(383.93,153.43) --
+	(383.93,158.43) --
+	(378.94,158.43) --
+	cycle;
+
+\path[fill=fillColor] (387.25,149.99) --
+	(392.25,149.99) --
+	(392.25,154.99) --
+	(387.25,154.99) --
+	cycle;
+
+\path[fill=fillColor] (395.57,146.71) --
+	(400.56,146.71) --
+	(400.56,151.71) --
+	(395.57,151.71) --
+	cycle;
+
+\path[fill=fillColor] (403.88,143.82) --
+	(408.88,143.82) --
+	(408.88,148.82) --
+	(403.88,148.82) --
+	cycle;
+
+\path[fill=fillColor] (412.19,141.55) --
+	(417.19,141.55) --
+	(417.19,146.55) --
+	(412.19,146.55) --
+	cycle;
+
+\path[fill=fillColor] (420.51,139.32) --
+	(425.50,139.32) --
+	(425.50,144.31) --
+	(420.51,144.31) --
+	cycle;
+
+\path[fill=fillColor] (428.82,137.17) --
+	(433.82,137.17) --
+	(433.82,142.17) --
+	(428.82,142.17) --
+	cycle;
+
+\path[fill=fillColor] (437.14,134.85) --
+	(442.13,134.85) --
+	(442.13,139.85) --
+	(437.14,139.85) --
+	cycle;
+
+\path[fill=fillColor] (445.45,133.06) --
+	(450.45,133.06) --
+	(450.45,138.05) --
+	(445.45,138.05) --
+	cycle;
+
+\path[fill=fillColor] (453.76,131.12) --
+	(458.76,131.12) --
+	(458.76,136.11) --
+	(453.76,136.11) --
+	cycle;
+
+\path[fill=fillColor] (462.08,129.46) --
+	(467.07,129.46) --
+	(467.07,134.45) --
+	(462.08,134.45) --
+	cycle;
+
+\path[fill=fillColor] (470.39,127.34) --
+	(475.39,127.34) --
+	(475.39,132.34) --
+	(470.39,132.34) --
+	cycle;
+
+\path[fill=fillColor] (478.71,125.54) --
+	(483.70,125.54) --
+	(483.70,130.54) --
+	(478.71,130.54) --
+	cycle;
+
+\path[fill=fillColor] (487.02,123.98) --
+	(492.02,123.98) --
+	(492.02,128.97) --
+	(487.02,128.97) --
+	cycle;
+
+\path[fill=fillColor] (495.34,122.45) --
+	(500.33,122.45) --
+	(500.33,127.44) --
+	(495.34,127.44) --
+	cycle;
+
+\path[fill=fillColor] (503.65,120.96) --
+	(508.64,120.96) --
+	(508.64,125.95) --
+	(503.65,125.95) --
+	cycle;
+
+\path[fill=fillColor] (511.96,119.41) --
+	(516.96,119.41) --
+	(516.96,124.40) --
+	(511.96,124.40) --
+	cycle;
+
+\path[fill=fillColor] (520.28,118.05) --
+	(525.27,118.05) --
+	(525.27,123.05) --
+	(520.28,123.05) --
+	cycle;
+
+\path[fill=fillColor] (528.59,116.70) --
+	(533.59,116.70) --
+	(533.59,121.70) --
+	(528.59,121.70) --
+	cycle;
+
+\path[fill=fillColor] (536.91,115.61) --
+	(541.90,115.61) --
+	(541.90,120.60) --
+	(536.91,120.60) --
+	cycle;
+
+\path[fill=fillColor] (545.22,114.22) --
+	(550.22,114.22) --
+	(550.22,119.22) --
+	(545.22,119.22) --
+	cycle;
+
+\path[fill=fillColor] (553.53,112.86) --
+	(558.53,112.86) --
+	(558.53,117.86) --
+	(553.53,117.86) --
+	cycle;
+
+\path[fill=fillColor] (561.85,111.89) --
+	(566.84,111.89) --
+	(566.84,116.88) --
+	(561.85,116.88) --
+	cycle;
+
+\path[fill=fillColor] (570.16,110.62) --
+	(575.16,110.62) --
+	(575.16,115.62) --
+	(570.16,115.62) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,192.11) -- (368.34,192.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,188.58) -- (364.81,195.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,186.73) -- (376.65,186.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,183.20) -- (373.12,190.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,181.78) -- (384.97,181.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,178.25) -- (381.44,185.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,176.74) -- (393.28,176.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,173.21) -- (389.75,180.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,171.94) -- (401.60,171.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,168.41) -- (398.06,175.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,167.61) -- (409.91,167.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,164.08) -- (406.38,171.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,164.39) -- (418.22,164.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,160.86) -- (414.69,167.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,161.21) -- (426.54,161.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,157.67) -- (423.01,164.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,157.99) -- (434.85,157.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,154.46) -- (431.32,161.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,154.70) -- (443.17,154.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,151.16) -- (439.63,158.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,152.12) -- (451.48,152.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,148.59) -- (447.95,155.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,149.36) -- (459.79,149.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,145.83) -- (456.26,152.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,146.94) -- (468.11,146.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,143.40) -- (464.58,150.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,144.00) -- (476.42,144.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,140.47) -- (472.89,147.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,141.47) -- (484.74,141.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,137.94) -- (481.20,145.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,139.29) -- (493.05,139.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,135.76) -- (489.52,142.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,137.22) -- (501.36,137.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,133.69) -- (497.83,140.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,134.96) -- (509.68,134.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,131.43) -- (506.15,138.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,132.89) -- (517.99,132.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,129.36) -- (514.46,136.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,131.00) -- (526.31,131.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,127.46) -- (522.78,134.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,129.08) -- (534.62,129.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,125.55) -- (531.09,132.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,127.75) -- (542.94,127.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,124.22) -- (539.40,131.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,125.86) -- (551.25,125.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72,122.33) -- (547.72,129.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,123.89) -- (559.56,123.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03,120.36) -- (556.03,127.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,122.63) -- (567.88,122.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35,119.09) -- (564.35,126.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,120.90) -- (576.19,120.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,117.37) -- (572.66,124.44);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[fill=fillColor] (323.24, 49.94) circle (  2.50);
-
-\path[fill=fillColor] (331.55, 50.02) circle (  2.50);
-
-\path[fill=fillColor] (339.86, 50.01) circle (  2.50);
-
-\path[fill=fillColor] (348.18, 49.81) circle (  2.50);
-
-\path[fill=fillColor] (356.49, 49.97) circle (  2.50);
-
-\path[fill=fillColor] (364.81, 50.10) circle (  2.50);
-
-\path[fill=fillColor] (373.12, 49.98) circle (  2.50);
-
-\path[fill=fillColor] (381.44, 50.04) circle (  2.50);
-
-\path[fill=fillColor] (389.75, 50.05) circle (  2.50);
-
-\path[fill=fillColor] (398.06, 49.95) circle (  2.50);
-
-\path[fill=fillColor] (406.38, 50.17) circle (  2.50);
-
-\path[fill=fillColor] (414.69, 49.86) circle (  2.50);
-
-\path[fill=fillColor] (423.01, 49.74) circle (  2.50);
-
-\path[fill=fillColor] (431.32, 49.98) circle (  2.50);
-
-\path[fill=fillColor] (439.63, 50.13) circle (  2.50);
-
-\path[fill=fillColor] (447.95, 50.04) circle (  2.50);
-
-\path[fill=fillColor] (456.26, 49.94) circle (  2.50);
-
-\path[fill=fillColor] (464.58, 49.95) circle (  2.50);
-
-\path[fill=fillColor] (472.89, 49.84) circle (  2.50);
-
-\path[fill=fillColor] (481.20, 49.92) circle (  2.50);
-
-\path[fill=fillColor] (489.52, 49.86) circle (  2.50);
-
-\path[fill=fillColor] (497.83, 50.08) circle (  2.50);
-
-\path[fill=fillColor] (506.15, 49.96) circle (  2.50);
-
-\path[fill=fillColor] (514.46, 50.12) circle (  2.50);
-
-\path[fill=fillColor] (522.78, 50.25) circle (  2.50);
-
-\path[fill=fillColor] (531.09, 49.77) circle (  2.50);
-
-\path[fill=fillColor] (539.40, 49.90) circle (  2.50);
-
-\path[fill=fillColor] (547.72, 50.13) circle (  2.50);
-
-\path[fill=fillColor] (556.03, 50.12) circle (  2.50);
-
-\path[fill=fillColor] (564.35, 49.92) circle (  2.50);
-
-\path[fill=fillColor] (572.66, 49.83) circle (  2.50);
+\path[fill=fillColor] (323.24, 68.06) circle (  2.50);
+
+\path[fill=fillColor] (331.55, 68.24) circle (  2.50);
+
+\path[fill=fillColor] (339.86, 68.21) circle (  2.50);
+
+\path[fill=fillColor] (348.18, 67.81) circle (  2.50);
+
+\path[fill=fillColor] (356.49, 68.07) circle (  2.50);
+
+\path[fill=fillColor] (364.81, 68.35) circle (  2.50);
+
+\path[fill=fillColor] (373.12, 68.10) circle (  2.50);
+
+\path[fill=fillColor] (381.44, 68.30) circle (  2.50);
+
+\path[fill=fillColor] (389.75, 68.27) circle (  2.50);
+
+\path[fill=fillColor] (398.06, 68.02) circle (  2.50);
+
+\path[fill=fillColor] (406.38, 68.54) circle (  2.50);
+
+\path[fill=fillColor] (414.69, 67.86) circle (  2.50);
+
+\path[fill=fillColor] (423.01, 67.64) circle (  2.50);
+
+\path[fill=fillColor] (431.32, 68.15) circle (  2.50);
+
+\path[fill=fillColor] (439.63, 68.39) circle (  2.50);
+
+\path[fill=fillColor] (447.95, 68.19) circle (  2.50);
+
+\path[fill=fillColor] (456.26, 68.00) circle (  2.50);
+
+\path[fill=fillColor] (464.58, 68.03) circle (  2.50);
+
+\path[fill=fillColor] (472.89, 67.80) circle (  2.50);
+
+\path[fill=fillColor] (481.20, 67.94) circle (  2.50);
+
+\path[fill=fillColor] (489.52, 67.80) circle (  2.50);
+
+\path[fill=fillColor] (497.83, 68.37) circle (  2.50);
+
+\path[fill=fillColor] (506.15, 68.09) circle (  2.50);
+
+\path[fill=fillColor] (514.46, 68.40) circle (  2.50);
+
+\path[fill=fillColor] (522.78, 68.75) circle (  2.50);
+
+\path[fill=fillColor] (531.09, 67.59) circle (  2.50);
+
+\path[fill=fillColor] (539.40, 68.00) circle (  2.50);
+
+\path[fill=fillColor] (547.72, 68.44) circle (  2.50);
+
+\path[fill=fillColor] (556.03, 68.43) circle (  2.50);
+
+\path[fill=fillColor] (564.35, 67.96) circle (  2.50);
+
+\path[fill=fillColor] (572.66, 67.78) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}

### 2020-04-14 forward.R

@@ -113,8 +113,11 @@ serdet <- data.frame(
 )
 
 g4 <- ggplot(serdata0) +
-  geom_line(data=serdet, aes(tvec, mf), lwd=1) +
-  geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
+  # geom_point(aes(cohort, tdiff), shape=1, col="#D55E00", size=2) +
+  geom_smooth(aes(cohort, tdiff), shape=1, col="#D55E00", size=2) +
+  geom_line(data=serdet, aes(tvec, mf), lwd=1) 
+  
+  
   geom_hline(yintercept=serdet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
   scale_y_continuous("Forward serial interval (days)", expand=c(0, 0), limits=c(0, 7)) +

### 2020-04-14 rR.R

@@ -8,22 +8,16 @@ source("cpalette.R")
 meanlog1 <- 1.621
 sdlog1 <- 0.418
 ## generation
-shape <- 4.1
-scale <- 5.5
-
-## rough moment matching...for now... doesn't matter -- it works.
-mean(rweibull(50000, shape = shape, scale=scale))
-var(rweibull(50000, shape = shape, scale=scale))
-
-mean(rlnorm(50000, meanlog = 1.55, sdlog=0.27))
-var(rlnorm(50000, meanlog = 1.55, sdlog=0.27))
+## moment matching
+mean(rlnorm(50000, meanlog = 1.54, sdlog=0.37)) ## 5 days
+sd(rlnorm(50000, meanlog = 1.54, sdlog=0.37)) ## 1.9 days
 
 serialR <- function(r=0.1,
                     rho=0.5,
                     meanlog1=1.621,
                     sdlog1=0.418,
-                    meanlog2=1.55,
-                    sdlog2=0.27,
+                    meanlog2=1.54,
+                    sdlog2=0.37,
                     nsim=100000,
                     seed=101) {
   set.seed(seed)
@@ -52,8 +46,8 @@ serialR2 <- function(r=0.1,
                     rho=0.5,
                     meanlog1=1.621,
                     sdlog1=0.418,
-                    meanlog2=1.55,
-                    sdlog2=0.27,
+                    meanlog2=1.54,
+                    sdlog2=0.37,
                     nsim=100000,
                     seed=101) {
   set.seed(seed)
@@ -77,8 +71,8 @@ serialR2 <- function(r=0.1,
 }
 
 generationR <- function(r=0.1,
-                        meanlog2=1.55,
-                        sdlog2=0.27,
+                        meanlog2=1.54,
+                        sdlog2=0.37,
                         nsim=100000) {
   gen <- rlnorm(nsim, meanlog2, sdlog2)
                           

### 2020-04-14 renewal_det.R

@@ -3,7 +3,7 @@ renewal_det <- function(R0=2.5,
                         S0=40000-10,
                         dt=0.025,
                         incfun=function(x) dlnorm(x, meanlog=1.621, sdlog=0.418),
-                        genfun=function(x) dweibull(x, shape=4.1, scale=5.5),
+                        genfun=function(x) dlnorm(x, meanlog=1.54, sdlog=0.37),
                         I0=10,
                         tmax=200,
                         genmax=2000) {

### 2020-04-14 sir.R

@@ -12,8 +12,8 @@ sir.full <- function(size,
                      R0=2.5,
                      meanlog=1.621,
                      sdlog=0.418,
-                     scale=5.5,
-                     shape=4.1,
+                     meanlog2=1.54,
+                     sdlog2=0.37,
                      I0,
                      seed = NULL,
                      imax,
@@ -76,7 +76,7 @@ sir.full <- function(size,
       queue_infector <- c(queue_infector, rep(j, ncontact))
     }
     
-    generation <- rweibull(ncontact, shape, scale)
+    generation <- rlnorm(ncontact, meanlog2, sdlog2)
     
     if (keep.intrinsic) intrinsic_generation[[j]] <- generation
     

### 2020-04-15 rR.tex
almost done with the results section

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-14 11:43:25
+% Created by tikzDevice version 0.12.3 on 2020-04-14 17:43:43
 % !TEX encoding = UTF-8 Unicode
@@
 	( 88.95,267.16) --
-	( 92.19,268.37) --
+	( 92.19,268.38) --
 	( 95.43,269.61) --
@@
 	(137.61,287.42) --
-	(140.85,288.93) --
-	(144.09,290.46) --
+	(140.85,288.92) --
+	(144.09,290.45) --
 	(147.34,292.01) --
-	(150.58,293.60) --
+	(150.58,293.59) --
 	(153.82,295.21) --
-	(157.07,296.86) --
-	(160.31,298.52) --
+	(157.07,296.85) --
+	(160.31,298.51) --
 	(163.56,300.20) --
@@
 	(173.29,305.37) --
-	(176.53,307.15) --
+	(176.53,307.14) --
 	(179.78,308.95) --
@@
 	(186.26,312.65) --
-	(189.51,314.56) --
+	(189.51,314.55) --
 	(192.75,316.49) --
@@
 	(202.48,322.45) --
-	(205.73,324.50) --
+	(205.73,324.49) --
 	(208.97,326.57) --
@@
 	(234.92,344.34) --
-	(238.17,346.70) --
-	(241.41,349.10) --
+	(238.17,346.71) --
+	(241.41,349.11) --
 	(244.65,351.53) --
-	(247.90,353.98) --
-	(251.14,356.47) --
-	(254.39,358.99) --
-	(257.63,361.55) --
-	(260.87,364.13) --
-	(264.12,366.75) --
-	(267.36,369.40) --
-	(270.60,372.08) --
-	(273.85,374.79) --
-	(277.09,377.53) --
-	(280.34,380.31) --
-	(283.58,383.11);
+	(247.90,353.99) --
+	(251.14,356.48) --
+	(254.39,359.01) --
+	(257.63,361.56) --
+	(260.87,364.15) --
+	(264.12,366.77) --
+	(267.36,369.42) --
+	(270.60,372.10) --
+	(273.85,374.82) --
+	(277.09,377.56) --
+	(280.34,380.34) --
+	(283.58,383.15);
 \definecolor{drawColor}{RGB}{86,180,233}
@@
 	( 56.51,256.03) --
-	( 59.75,257.05) --
+	( 59.75,257.06) --
 	( 63.00,258.10) --
 	( 66.24,259.17) --
-	( 69.48,260.25) --
+	( 69.48,260.26) --
 	( 72.73,261.36) --
@@
 	(144.09,290.45) --
-	(147.34,292.01) --
-	(150.58,293.59) --
-	(153.82,295.20) --
+	(147.34,292.00) --
+	(150.58,293.58) --
+	(153.82,295.19) --
 	(157.07,296.84) --
-	(160.31,298.50) --
-	(163.56,300.18) --
+	(160.31,298.49) --
+	(163.56,300.17) --
 	(166.80,301.87) --
@@
 	(179.78,308.90) --
-	(183.02,310.74) --
+	(183.02,310.73) --
 	(186.26,312.60) --
-	(189.51,314.51) --
+	(189.51,314.50) --
 	(192.75,316.44) --
@@
 	(199.24,320.39) --
-	(202.48,322.41) --
+	(202.48,322.40) --
 	(205.73,324.45) --
 	(208.97,326.53) --
-	(212.21,328.64) --
+	(212.21,328.63) --
 	(215.46,330.78) --
@@
 	(231.68,342.01) --
-	(234.92,344.35) --
-	(238.17,346.73) --
-	(241.41,349.13) --
-	(244.65,351.57) --
-	(247.90,354.04) --
-	(251.14,356.54) --
-	(254.39,359.07) --
-	(257.63,361.64) --
-	(260.87,364.24) --
-	(264.12,366.87) --
-	(267.36,369.54) --
-	(270.60,372.24) --
-	(273.85,374.97) --
-	(277.09,377.73) --
-	(280.34,380.52) --
-	(283.58,383.35);
+	(234.92,344.36) --
+	(238.17,346.74) --
+	(241.41,349.14) --
+	(244.65,351.58) --
+	(247.90,354.06) --
+	(251.14,356.56) --
+	(254.39,359.10) --
+	(257.63,361.67) --
+	(260.87,364.27) --
+	(264.12,366.91) --
+	(267.36,369.58) --
+	(270.60,372.28) --
+	(273.85,375.01) --
+	(277.09,377.78) --
+	(280.34,380.58) --
+	(283.58,383.41);
 \definecolor{drawColor}{RGB}{0,158,115}
@@
 	( 63.00,258.11) --
-	( 66.24,259.17) --
+	( 66.24,259.18) --
 	( 69.48,260.26) --
@@
 	( 85.70,265.98) --
-	( 88.95,267.18) --
+	( 88.95,267.19) --
 	( 92.19,268.40) --
@@
 	(140.85,288.92) --
-	(144.09,290.45) --
-	(147.34,292.00) --
-	(150.58,293.58) --
-	(153.82,295.19) --
-	(157.07,296.83) --
+	(144.09,290.44) --
+	(147.34,291.99) --
+	(150.58,293.57) --
+	(153.82,295.18) --
+	(157.07,296.82) --
 	(160.31,298.48) --
-	(163.56,300.16) --
+	(163.56,300.15) --
 	(166.80,301.85) --
-	(170.04,303.57) --
-	(173.29,305.31) --
+	(170.04,303.56) --
+	(173.29,305.30) --
 	(176.53,307.07) --
@@
 	(183.02,310.70) --
-	(186.26,312.57) --
+	(186.26,312.56) --
 	(189.51,314.47) --
@@
 	(221.95,335.18) --
-	(225.19,337.44) --
-	(228.43,339.73) --
-	(231.68,342.05) --
-	(234.92,344.41) --
-	(238.17,346.80) --
-	(241.41,349.22) --
-	(244.65,351.67) --
-	(247.90,354.15) --
-	(251.14,356.67) --
-	(254.39,359.22) --
-	(257.63,361.81) --
-	(260.87,364.43) --
-	(264.12,367.08) --
-	(267.36,369.77) --
-	(270.60,372.48) --
-	(273.85,375.24) --
-	(277.09,378.02) --
-	(280.34,380.84) --
-	(283.58,383.69);
+	(225.19,337.45) --
+	(228.43,339.74) --
+	(231.68,342.07) --
+	(234.92,344.42) --
+	(238.17,346.82) --
+	(241.41,349.24) --
+	(244.65,351.70) --
+	(247.90,354.18) --
+	(251.14,356.71) --
+	(254.39,359.26) --
+	(257.63,361.85) --
+	(260.87,364.48) --
+	(264.12,367.14) --
+	(267.36,369.83) --
+	(270.60,372.55) --
+	(273.85,375.31) --
+	(277.09,378.11) --
+	(280.34,380.93) --
+	(283.58,383.79);
 \definecolor{fillColor}{RGB}{230,159,0}
@@
 \path[fill=fillColor] ( 70.02,264.40) --
-	( 73.39,258.58) --
-	( 66.66,258.58) --
-	cycle;
-
-\path[fill=fillColor] ( 78.57,267.35) --
+	( 73.39,258.57) --
+	( 66.66,258.57) --
+	cycle;
+
+\path[fill=fillColor] ( 78.57,267.34) --
 	( 81.93,261.52) --
@@
 
-\path[fill=fillColor] ( 87.11,270.41) --
+\path[fill=fillColor] ( 87.11,270.42) --
 	( 90.47,264.59) --
@@
 
-\path[fill=fillColor] ( 95.65,273.62) --
-	( 99.01,267.79) --
-	( 92.29,267.79) --
+\path[fill=fillColor] ( 95.65,273.63) --
+	( 99.01,267.80) --
+	( 92.29,267.80) --
 	cycle;
@@
 \path[fill=fillColor] (121.28,284.03) --
-	(124.64,278.21) --
-	(117.91,278.21) --
-	cycle;
-
-\path[fill=fillColor] (129.82,287.77) --
-	(133.18,281.94) --
-	(126.46,281.94) --
-	cycle;
-
-\path[fill=fillColor] (138.36,291.66) --
-	(141.73,285.83) --
-	(135.00,285.83) --
-	cycle;
-
-\path[fill=fillColor] (146.90,295.73) --
-	(150.27,289.90) --
-	(143.54,289.90) --
+	(124.64,278.20) --
+	(117.91,278.20) --
+	cycle;
+
+\path[fill=fillColor] (129.82,287.78) --
+	(133.18,281.95) --
+	(126.46,281.95) --
+	cycle;
+
+\path[fill=fillColor] (138.36,291.67) --
+	(141.73,285.84) --
+	(135.00,285.84) --
+	cycle;
+
+\path[fill=fillColor] (146.90,295.72) --
+	(150.27,289.89) --
+	(143.54,289.89) --
 	cycle;
@@
 
-\path[fill=fillColor] (163.99,304.28) --
-	(167.35,298.45) --
-	(160.63,298.45) --
-	cycle;
-
-\path[fill=fillColor] (172.53,308.80) --
-	(175.89,302.97) --
-	(169.17,302.97) --
-	cycle;
-
-\path[fill=fillColor] (181.07,313.61) --
-	(184.44,307.78) --
-	(177.71,307.78) --
-	cycle;
-
-\path[fill=fillColor] (189.62,318.54) --
-	(192.98,312.71) --
-	(186.25,312.71) --
-	cycle;
-
-\path[fill=fillColor] (198.16,323.65) --
-	(201.52,317.83) --
-	(194.79,317.83) --
-	cycle;
-
-\path[fill=fillColor] (206.70,328.94) --
-	(210.06,323.11) --
-	(203.34,323.11) --
-	cycle;
-
-\path[fill=fillColor] (215.24,334.46) --
-	(218.61,328.63) --
-	(211.88,328.63) --
-	cycle;
-
-\path[fill=fillColor] (223.78,340.25) --
-	(227.15,334.42) --
-	(220.42,334.42) --
+\path[fill=fillColor] (163.99,304.26) --
+	(167.35,298.43) --
+	(160.63,298.43) --
+	cycle;
+
+\path[fill=fillColor] (172.53,308.81) --
+	(175.89,302.98) --
+	(169.17,302.98) --
+	cycle;
+
+\path[fill=fillColor] (181.07,313.60) --
+	(184.44,307.77) --
+	(177.71,307.77) --
+	cycle;
+
+\path[fill=fillColor] (189.62,318.53) --
+	(192.98,312.70) --
+	(186.25,312.70) --
+	cycle;
+
+\path[fill=fillColor] (198.16,323.63) --
+	(201.52,317.81) --
+	(194.79,317.81) --
+	cycle;
+
+\path[fill=fillColor] (206.70,328.95) --
+	(210.06,323.12) --
+	(203.34,323.12) --
+	cycle;
+
+\path[fill=fillColor] (215.24,334.48) --
+	(218.61,328.65) --
+	(211.88,328.65) --
+	cycle;
+
+\path[fill=fillColor] (223.78,340.26) --
+	(227.15,334.44) --
+	(220.42,334.44) --
 	cycle;
@@
 \path[fill=fillColor] (232.33,346.20) --
-	(235.69,340.38) --
-	(228.96,340.38) --
-	cycle;
-
-\path[fill=fillColor] (240.87,352.40) --
-	(244.23,346.58) --
-	(237.51,346.58) --
-	cycle;
-
-\path[fill=fillColor] (249.41,358.80) --
-	(252.77,352.98) --
-	(246.05,352.98) --
-	cycle;
-
-\path[fill=fillColor] (257.95,365.62) --
+	(235.69,340.37) --
+	(228.96,340.37) --
+	cycle;
+
+\path[fill=fillColor] (240.87,352.35) --
+	(244.23,346.52) --
+	(237.51,346.52) --
+	cycle;
+
+\path[fill=fillColor] (249.41,358.83) --
+	(252.77,353.01) --
+	(246.05,353.01) --
+	cycle;
+
+\path[fill=fillColor] (257.95,365.61) --
 	(261.32,359.79) --
@@
 
-\path[fill=fillColor] (266.50,372.58) --
-	(269.86,366.75) --
-	(263.13,366.75) --
-	cycle;
-
-\path[fill=fillColor] (275.04,379.67) --
-	(278.40,373.84) --
-	(271.67,373.84) --
-	cycle;
-
-\path[fill=fillColor] (283.58,387.25) --
-	(286.94,381.43) --
-	(280.22,381.43) --
+\path[fill=fillColor] (266.50,372.59) --
+	(269.86,366.77) --
+	(263.13,366.77) --
+	cycle;
+
+\path[fill=fillColor] (275.04,379.74) --
+	(278.40,373.92) --
+	(271.67,373.92) --
+	cycle;
+
+\path[fill=fillColor] (283.58,387.27) --
+	(286.94,381.45) --
+	(280.22,381.45) --
 	cycle;
@@
 	( 72.52,258.02) --
-	( 72.52,263.02) --
-	( 67.53,263.02) --
+	( 72.52,263.01) --
+	( 67.53,263.01) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 84.61,264.04) --
-	( 89.61,264.04) --
-	( 89.61,269.03) --
-	( 84.61,269.03) --
-	cycle;
-
-\path[fill=fillColor] ( 93.15,267.25) --
-	( 98.15,267.25) --
-	( 98.15,272.25) --
-	( 93.15,272.25) --
-	cycle;
-
-\path[fill=fillColor] (101.70,270.62) --
-	(106.69,270.62) --
+\path[fill=fillColor] ( 84.61,264.05) --
+	( 89.61,264.05) --
+	( 89.61,269.04) --
+	( 84.61,269.04) --
+	cycle;
+
+\path[fill=fillColor] ( 93.15,267.26) --
+	( 98.15,267.26) --
+	( 98.15,272.26) --
+	( 93.15,272.26) --
+	cycle;
+
+\path[fill=fillColor] (101.70,270.61) --
+	(106.69,270.61) --
 	(106.69,275.61) --
@@
 	(115.23,274.08) --
-	(115.23,279.08) --
-	(110.24,279.08) --
+	(115.23,279.07) --
+	(110.24,279.07) --
 	cycle;
@@
 
-\path[fill=fillColor] (127.32,281.40) --
-	(132.32,281.40) --
-	(132.32,286.40) --
-	(127.32,286.40) --
-	cycle;
-
-\path[fill=fillColor] (135.86,285.29) --
-	(140.86,285.29) --
-	(140.86,290.28) --
-	(135.86,290.28) --
-	cycle;
-
-\path[fill=fillColor] (144.41,289.36) --
-	(149.40,289.36) --
-	(149.40,294.36) --
-	(144.41,294.36) --
+\path[fill=fillColor] (127.32,281.41) --
+	(132.32,281.41) --
+	(132.32,286.41) --
+	(127.32,286.41) --
+	cycle;
+
+\path[fill=fillColor] (135.86,285.30) --
+	(140.86,285.30) --
+	(140.86,290.30) --
+	(135.86,290.30) --
+	cycle;
+
+\path[fill=fillColor] (144.41,289.34) --
+	(149.40,289.34) --
+	(149.40,294.33) --
+	(144.41,294.33) --
 	cycle;
@@
 
-\path[fill=fillColor] (161.49,297.85) --
-	(166.49,297.85) --
-	(166.49,302.85) --
-	(161.49,302.85) --
-	cycle;
-
-\path[fill=fillColor] (170.03,302.34) --
-	(175.03,302.34) --
-	(175.03,307.33) --
-	(170.03,307.33) --
-	cycle;
-
-\path[fill=fillColor] (178.58,307.20) --
-	(183.57,307.20) --
-	(183.57,312.19) --
-	(178.58,312.19) --
-	cycle;
-
-\path[fill=fillColor] (187.12,312.13) --
-	(192.11,312.13) --
+\path[fill=fillColor] (161.49,297.83) --
+	(166.49,297.83) --
+	(166.49,302.82) --
+	(161.49,302.82) --
+	cycle;
+
+\path[fill=fillColor] (170.03,302.36) --
+	(175.03,302.36) --
+	(175.03,307.36) --
+	(170.03,307.36) --
+	cycle;
+
+\path[fill=fillColor] (178.58,307.19) --
+	(183.57,307.19) --
+	(183.57,312.18) --
+	(178.58,312.18) --
+	cycle;
+
+\path[fill=fillColor] (187.12,312.12) --
+	(192.11,312.12) --
 	(192.11,317.12) --
@@
 
-\path[fill=fillColor] (195.66,317.25) --
-	(200.66,317.25) --
-	(200.66,322.24) --
-	(195.66,322.24) --
-	cycle;
-
-\path[fill=fillColor] (204.20,322.50) --
-	(209.20,322.50) --
-	(209.20,327.49) --
-	(204.20,327.49) --
-	cycle;
-
-\path[fill=fillColor] (212.74,328.04) --
-	(217.74,328.04) --
-	(217.74,333.04) --
-	(212.74,333.04) --
-	cycle;
-
-\path[fill=fillColor] (221.29,333.85) --
-	(226.28,333.85) --
-	(226.28,338.85) --
-	(221.29,338.85) --
-	cycle;
-
-\path[fill=fillColor] (229.83,339.77) --
-	(234.82,339.77) --
-	(234.82,344.76) --
-	(229.83,344.76) --
-	cycle;
-
-\path[fill=fillColor] (238.37,345.99) --
-	(243.37,345.99) --
-	(243.37,350.98) --
-	(238.37,350.98) --
-	cycle;
-
-\path[fill=fillColor] (246.91,352.43) --
-	(251.91,352.43) --
-	(251.91,357.43) --
-	(246.91,357.43) --
-	cycle;
-
-\path[fill=fillColor] (255.46,359.42) --
-	(260.45,359.42) --
-	(260.45,364.42) --
-	(255.46,364.42) --
-	cycle;
-
-\path[fill=fillColor] (264.00,366.41) --
-	(268.99,366.41) --
-	(268.99,371.40) --
-	(264.00,371.40) --
-	cycle;
-
-\path[fill=fillColor] (272.54,373.42) --
-	(277.54,373.42) --
-	(277.54,378.41) --
-	(272.54,378.41) --
-	cycle;
-
-\path[fill=fillColor] (281.08,381.10) --
-	(286.08,381.10) --
-	(286.08,386.09) --
-	(281.08,386.09) --
+\path[fill=fillColor] (195.66,317.22) --
+	(200.66,317.22) --
+	(200.66,322.21) --
+	(195.66,322.21) --
+	cycle;
+
+\path[fill=fillColor] (204.20,322.52) --
+	(209.20,322.52) --
+	(209.20,327.51) --
+	(204.20,327.51) --
+	cycle;
+
+\path[fill=fillColor] (212.74,328.07) --
+	(217.74,328.07) --
+	(217.74,333.06) --
+	(212.74,333.06) --
+	cycle;
+
+\path[fill=fillColor] (221.29,333.88) --
+	(226.28,333.88) --
+	(226.28,338.88) --
+	(221.29,338.88) --
+	cycle;
+
+\path[fill=fillColor] (229.83,339.76) --
+	(234.82,339.76) --
+	(234.82,344.75) --
+	(229.83,344.75) --
+	cycle;
+
+\path[fill=fillColor] (238.37,345.90) --
+	(243.37,345.90) --
+	(243.37,350.89) --
+	(238.37,350.89) --
+	cycle;
+
+\path[fill=fillColor] (246.91,352.51) --
+	(251.91,352.51) --
+	(251.91,357.51) --
+	(246.91,357.51) --
+	cycle;
+
+\path[fill=fillColor] (255.46,359.41) --
+	(260.45,359.41) --
+	(260.45,364.40) --
+	(255.46,364.40) --
+	cycle;
+
+\path[fill=fillColor] (264.00,366.42) --
+	(268.99,366.42) --
+	(268.99,371.41) --
+	(264.00,371.41) --
+	cycle;
+
+\path[fill=fillColor] (272.54,373.53) --
+	(277.54,373.53) --
+	(277.54,378.53) --
+	(272.54,378.53) --
+	cycle;
+
+\path[fill=fillColor] (281.08,381.15) --
+	(286.08,381.15) --
+	(286.08,386.15) --
+	(281.08,386.15) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.52) -- ( 73.56,260.52);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.51) -- ( 73.56,260.51);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.54) -- ( 90.64,266.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,263.01) -- ( 87.11,270.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.76) -- ( 99.18,269.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,266.23) -- ( 95.65,273.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,273.14) -- (107.73,273.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,269.61) -- (104.19,276.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.60) -- (116.27,276.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,273.07) -- (112.74,280.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,280.18) -- (124.81,280.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.65) -- (121.28,283.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.91) -- (133.35,283.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.38) -- (129.82,287.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.80) -- (141.89,287.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,284.26) -- (138.36,291.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.88) -- (150.44,291.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.34) -- (146.90,295.41);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.55) -- ( 90.64,266.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,263.02) -- ( 87.11,270.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.78) -- ( 99.18,269.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,266.24) -- ( 95.65,273.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,273.13) -- (107.73,273.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,269.60) -- (104.19,276.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.59) -- (116.27,276.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,273.06) -- (112.74,280.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,280.19) -- (124.81,280.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.66) -- (121.28,283.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.92) -- (133.35,283.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.39) -- (129.82,287.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.81) -- (141.89,287.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,284.28) -- (138.36,291.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.84) -- (150.44,291.84);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.31) -- (146.90,295.37);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.31) -- (167.52,300.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,296.78) -- (163.99,303.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.77) -- (176.06,304.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.23) -- (172.53,308.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.68) -- (184.61,309.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.15) -- (181.07,313.21);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.29) -- (167.52,300.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,296.75) -- (163.99,303.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.81) -- (176.06,304.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.27) -- (172.53,308.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.66) -- (184.61,309.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.13) -- (181.07,313.20);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.08) -- (189.62,318.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,319.74) -- (201.69,319.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,316.21) -- (198.16,323.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,324.96) -- (210.23,324.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,321.43) -- (206.70,328.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.54) -- (218.77,330.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,327.01) -- (215.24,334.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,336.37) -- (227.32,336.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,332.83) -- (223.78,339.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,342.23) -- (235.86,342.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,338.70) -- (232.33,345.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,348.49) -- (244.40,348.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,344.96) -- (240.87,352.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,355.00) -- (252.94,355.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,351.47) -- (249.41,358.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,362.19) -- (261.49,362.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,358.66) -- (257.95,365.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,369.22) -- (270.03,369.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,365.69) -- (266.50,372.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,376.15) -- (278.57,376.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,372.62) -- (275.04,379.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,383.92) -- (287.11,383.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,380.39) -- (283.58,387.45);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.07) -- (189.62,318.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,319.70) -- (201.69,319.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,316.17) -- (198.16,323.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,324.99) -- (210.23,324.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,321.46) -- (206.70,328.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.57) -- (218.77,330.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,327.04) -- (215.24,334.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,336.41) -- (227.32,336.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,332.88) -- (223.78,339.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,342.22) -- (235.86,342.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,338.69) -- (232.33,345.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,348.37) -- (244.40,348.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,344.84) -- (240.87,351.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,355.17) -- (252.94,355.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,351.64) -- (249.41,358.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,362.17) -- (261.49,362.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,358.64) -- (257.95,365.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,369.21) -- (270.03,369.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,365.68) -- (266.50,372.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,376.31) -- (278.57,376.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,372.78) -- (275.04,379.84);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,384.02) -- (287.11,384.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,380.49) -- (283.58,387.55);
 \definecolor{fillColor}{RGB}{0,0,0}
@@
 	(348.83,256.94) --
-	(352.08,257.94) --
-	(355.32,258.94) --
+	(352.08,257.93) --
+	(355.32,258.93) --
 	(358.56,259.94) --
@@
 	(365.05,261.97) --
-	(368.30,263.00) --
-	(371.54,264.03) --
-	(374.78,265.06) --
-	(378.03,266.11) --
-	(381.27,267.16) --
-	(384.51,268.22) --
-	(387.76,269.28) --
-	(391.00,270.36) --
-	(394.25,271.44) --
-	(397.49,272.53) --
-	(400.73,273.62) --
-	(403.98,274.72) --
-	(407.22,275.82) --
-	(410.47,276.92) --
-	(413.71,278.03) --
-	(416.95,279.15) --
-	(420.20,280.28) --
-	(423.44,281.42) --
-	(426.69,282.56) --
-	(429.93,283.71) --
-	(433.17,284.85) --
-	(436.42,286.00) --
-	(439.66,287.14) --
-	(442.90,288.28) --
-	(446.15,289.41) --
-	(449.39,290.55) --
-	(452.64,291.70) --
-	(455.88,292.86) --
-	(459.12,294.02) --
-	(462.37,295.18) --
-	(465.61,296.34) --
-	(468.86,297.49) --
-	(472.10,298.64) --
-	(475.34,299.77) --
-	(478.59,300.88) --
-	(481.83,301.99) --
-	(485.08,303.10) --
-	(488.32,304.20) --
-	(491.56,305.31) --
-	(494.81,306.40) --
-	(498.05,307.49) --
-	(501.29,308.57) --
-	(504.54,309.63) --
-	(507.78,310.68) --
-	(511.03,311.72) --
-	(514.27,312.73) --
-	(517.51,313.74) --
-	(520.76,314.73) --
-	(524.00,315.72) --
-	(527.25,316.70) --
-	(530.49,317.67) --
-	(533.73,318.63) --
-	(536.98,319.58) --
-	(540.22,320.52) --
-	(543.47,321.45) --
-	(546.71,322.36) --
-	(549.95,323.27) --
-	(553.20,324.16) --
-	(556.44,325.04) --
-	(559.68,325.91) --
-	(562.93,326.77) --
-	(566.17,327.62) --
-	(569.42,328.46) --
-	(572.66,329.29);
+	(368.30,262.99) --
+	(371.54,264.02) --
+	(374.78,265.05) --
+	(378.03,266.09) --
+	(381.27,267.14) --
+	(384.51,268.20) --
+	(387.76,269.26) --
+	(391.00,270.34) --
+	(394.25,271.42) --
+	(397.49,272.50) --
+	(400.73,273.59) --
+	(403.98,274.68) --
+	(407.22,275.78) --
+	(410.47,276.87) --
+	(413.71,277.98) --
+	(416.95,279.10) --
+	(420.20,280.22) --
+	(423.44,281.36) --
+	(426.69,282.50) --
+	(429.93,283.64) --
+	(433.17,284.78) --
+	(436.42,285.92) --
+	(439.66,287.06) --
+	(442.90,288.19) --
+	(446.15,289.31) --
+	(449.39,290.45) --
+	(452.64,291.59) --
+	(455.88,292.74) --
+	(459.12,293.89) --
+	(462.37,295.05) --
+	(465.61,296.19) --
+	(468.86,297.34) --
+	(472.10,298.47) --
+	(475.34,299.59) --
+	(478.59,300.69) --
+	(481.83,301.79) --
+	(485.08,302.89) --
+	(488.32,303.98) --
+	(491.56,305.07) --
+	(494.81,306.15) --
+	(498.05,307.23) --
+	(501.29,308.29) --
+	(504.54,309.34) --
+	(507.78,310.37) --
+	(511.03,311.39) --
+	(514.27,312.39) --
+	(517.51,313.37) --
+	(520.76,314.35) --
+	(524.00,315.32) --
+	(527.25,316.28) --
+	(530.49,317.22) --
+	(533.73,318.16) --
+	(536.98,319.09) --
+	(540.22,320.00) --
+	(543.47,320.91) --
+	(546.71,321.80) --
+	(549.95,322.67) --
+	(553.20,323.54) --
+	(556.44,324.40) --
+	(559.68,325.24) --
+	(562.93,326.07) --
+	(566.17,326.89) --
+	(569.42,327.70) --
+	(572.66,328.50);
 \definecolor{drawColor}{RGB}{86,180,233}
@@
 \path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (319.64,248.18) --
-	(322.88,249.16) --
-	(326.12,250.13) --
+	(322.88,249.15) --
+	(326.12,250.12) --
 	(329.37,251.09) --
@@
 	(348.83,256.87) --
-	(352.08,257.83) --
+	(352.08,257.82) --
 	(355.32,258.78) --
-	(358.56,259.74) --
-	(361.81,260.69) --
-	(365.05,261.64) --
+	(358.56,259.73) --
+	(361.81,260.68) --
+	(365.05,261.63) --
 	(368.30,262.58) --
-	(371.54,263.53) --
-	(374.78,264.47) --
-	(378.03,265.40) --
-	(381.27,266.35) --
-	(384.51,267.29) --
-	(387.76,268.24) --
-	(391.00,269.18) --
-	(394.25,270.13) --
-	(397.49,271.07) --
-	(400.73,272.00) --
-	(403.98,272.93) --
-	(407.22,273.85) --
-	(410.47,274.75) --
-	(413.71,275.66) --
-	(416.95,276.58) --
-	(420.20,277.50) --
-	(423.44,278.42) --
-	(426.69,279.33) --
-	(429.93,280.24) --
-	(433.17,281.13) --
-	(436.42,282.00) --
-	(439.66,282.86) --
-	(442.90,283.68) --
-	(446.15,284.48) --
-	(449.39,285.28) --
-	(452.64,286.08) --
-	(455.88,286.88) --
-	(459.12,287.67) --
-	(462.37,288.45) --
-	(465.61,289.20) --
-	(468.86,289.93) --
-	(472.10,290.62) --
-	(475.34,291.28) --
-	(478.59,291.89) --
-	(481.83,292.48) --
-	(485.08,293.04) --
-	(488.32,293.59) --
-	(491.56,294.11) --
-	(494.81,294.61) --
-	(498.05,295.08) --
-	(501.29,295.51) --
-	(504.54,295.91) --
-	(507.78,296.26) --
-	(511.03,296.58) --
-	(514.27,296.84) --
-	(517.51,297.07) --
-	(520.76,297.27) --
-	(524.00,297.44) --
-	(527.25,297.58) --
-	(530.49,297.68) --
-	(533.73,297.76) --
-	(536.98,297.79) --
-	(540.22,297.80) --
-	(543.47,297.77) --
-	(546.71,297.70) --
-	(549.95,297.60) --
-	(553.20,297.46) --
-	(556.44,297.29) --
-	(559.68,297.08) --
-	(562.93,296.84) --
-	(566.17,296.56) --
-	(569.42,296.25) --
-	(572.66,295.91);
+	(371.54,263.52) --
+	(374.78,264.45) --
+	(378.03,265.39) --
+	(381.27,266.33) --
+	(384.51,267.27) --
+	(387.76,268.21) --
+	(391.00,269.15) --
+	(394.25,270.09) --
+	(397.49,271.03) --
+	(400.73,271.96) --
+	(403.98,272.88) --
+	(407.22,273.79) --
+	(410.47,274.70) --
+	(413.71,275.60) --
+	(416.95,276.51) --
+	(420.20,277.43) --
+	(423.44,278.34) --
+	(426.69,279.25) --
+	(429.93,280.15) --
+	(433.17,281.03) --
+	(436.42,281.90) --
+	(439.66,282.74) --
+	(442.90,283.56) --
+	(446.15,284.35) --
+	(449.39,285.14) --
+	(452.64,285.93) --
+	(455.88,286.72) --
+	(459.12,287.50) --
+	(462.37,288.26) --
+	(465.61,289.01) --
+	(468.86,289.72) --
+	(472.10,290.40) --
+	(475.34,291.04) --
+	(478.59,291.64) --
+	(481.83,292.21) --
+	(485.08,292.76) --
+	(488.32,293.29) --
+	(491.56,293.79) --
+	(494.81,294.27) --
+	(498.05,294.72) --
+	(501.29,295.13) --
+	(504.54,295.51) --
+	(507.78,295.84) --
+	(511.03,296.12) --
+	(514.27,296.36) --
+	(517.51,296.57) --
+	(520.76,296.74) --
+	(524.00,296.88) --
+	(527.25,296.99) --
+	(530.49,297.06) --
+	(533.73,297.10) --
+	(536.98,297.11) --
+	(540.22,297.08) --
+	(543.47,297.02) --
+	(546.71,296.91) --
+	(549.95,296.77) --
+	(553.20,296.60) --
+	(556.44,296.39) --
+	(559.68,296.14) --
+	(562.93,295.86) --
+	(566.17,295.54) --
+	(569.42,295.19) --
+	(572.66,294.80);
 \definecolor{drawColor}{RGB}{0,158,115}
@@
 	(352.08,257.69) --
-	(355.32,258.61) --
+	(355.32,258.60) --
 	(358.56,259.51) --
-	(361.81,260.41) --
+	(361.81,260.40) --
 	(365.05,261.29) --
-	(368.30,262.17) --
-	(371.54,263.03) --
-	(374.78,263.89) --
-	(378.03,264.73) --
-	(381.27,265.58) --
-	(384.51,266.42) --
-	(387.76,267.26) --
-	(391.00,268.09) --
-	(394.25,268.91) --
-	(397.49,269.72) --
-	(400.73,270.52) --
-	(403.98,271.30) --
-	(407.22,272.06) --
-	(410.47,272.80) --
-	(413.71,273.54) --
-	(416.95,274.28) --
-	(420.20,275.02) --
-	(423.44,275.74) --
-	(426.69,276.46) --
-	(429.93,277.16) --
-	(433.17,277.83) --
-	(436.42,278.48) --
-	(439.66,279.09) --
-	(442.90,279.66) --
-	(446.15,280.19) --
-	(449.39,280.71) --
-	(452.64,281.23) --
-	(455.88,281.73) --
-	(459.12,282.22) --
-	(462.37,282.68) --
-	(465.61,283.10) --
-	(468.86,283.49) --
-	(472.10,283.84) --
-	(475.34,284.13) --
-	(478.59,284.37) --
-	(481.83,284.56) --
-	(485.08,284.73) --
-	(488.32,284.86) --
-	(491.56,284.96) --
-	(494.81,285.02) --
-	(498.05,285.04) --
-	(501.29,285.02) --
-	(504.54,284.95) --
-	(507.78,284.83) --
-	(511.03,284.65) --
-	(514.27,284.42) --
-	(517.51,284.15) --
-	(520.76,283.83) --
-	(524.00,283.47) --
-	(527.25,283.07) --
-	(530.49,282.63) --
-	(533.73,282.14) --
-	(536.98,281.61) --
-	(540.22,281.03) --
-	(543.47,280.41) --
-	(546.71,279.74) --
-	(549.95,279.03) --
-	(553.20,278.27) --
-	(556.44,277.46) --
-	(559.68,276.61) --
-	(562.93,275.72) --
-	(566.17,274.78) --
-	(569.42,273.79) --
-	(572.66,272.77);
+	(368.30,262.16) --
+	(371.54,263.02) --
+	(374.78,263.87) --
+	(378.03,264.71) --
+	(381.27,265.55) --
+	(384.51,266.39) --
+	(387.76,267.23) --
+	(391.00,268.05) --
+	(394.25,268.87) --
+	(397.49,269.68) --
+	(400.73,270.47) --
+	(403.98,271.25) --
+	(407.22,272.00) --
+	(410.47,272.74) --
+	(413.71,273.47) --
+	(416.95,274.20) --
+	(420.20,274.93) --
+	(423.44,275.65) --
+	(426.69,276.36) --
+	(429.93,277.05) --
+	(433.17,277.72) --
+	(436.42,278.35) --
+	(439.66,278.95) --
+	(442.90,279.51) --
+	(446.15,280.03) --
+	(449.39,280.54) --
+	(452.64,281.05) --
+	(455.88,281.54) --
+	(459.12,282.01) --
+	(462.37,282.46) --
+	(465.61,282.87) --
+	(468.86,283.25) --
+	(472.10,283.58) --
+	(475.34,283.86) --
+	(478.59,284.08) --
+	(481.83,284.25) --
+	(485.08,284.40) --
+	(488.32,284.51) --
+	(491.56,284.59) --
+	(494.81,284.63) --
+	(498.05,284.63) --
+	(501.29,284.58) --
+	(504.54,284.48) --
+	(507.78,284.34) --
+	(511.03,284.13) --
+	(514.27,283.88) --
+	(517.51,283.57) --
+	(520.76,283.23) --
+	(524.00,282.84) --
+	(527.25,282.40) --
+	(530.49,281.93) --
+	(533.73,281.41) --
+	(536.98,280.84) --
+	(540.22,280.23) --
+	(543.47,279.57) --
+	(546.71,278.87) --
+	(549.95,278.12) --
+	(553.20,277.32) --
+	(556.44,276.47) --
+	(559.68,275.58) --
+	(562.93,274.65) --
+	(566.17,273.66) --
+	(569.42,272.64) --
+	(572.66,271.57);
 \definecolor{fillColor}{RGB}{230,159,0}
@@
 \path[fill=fillColor] (350.56,261.27) --
-	(353.93,255.45) --
-	(347.20,255.45) --
-	cycle;
-
-\path[fill=fillColor] (359.10,263.90) --
+	(353.93,255.44) --
+	(347.20,255.44) --
+	cycle;
+
+\path[fill=fillColor] (359.10,263.89) --
 	(362.47,258.07) --
@@
 
-\path[fill=fillColor] (367.65,266.58) --
-	(371.01,260.76) --
-	(364.28,260.76) --
-	cycle;
-
-\path[fill=fillColor] (376.19,269.32) --
-	(379.55,263.50) --
-	(372.83,263.50) --
-	cycle;
-
-\path[fill=fillColor] (384.73,272.11) --
-	(388.09,266.29) --
-	(381.37,266.29) --
-	cycle;
-
-\path[fill=fillColor] (393.27,274.95) --
-	(396.64,269.13) --
-	(389.91,269.13) --
-	cycle;
-
-\path[fill=fillColor] (401.82,277.83) --
-	(405.18,272.01) --
-	(398.45,272.01) --
-	cycle;
-
-\path[fill=fillColor] (410.36,280.75) --
-	(413.72,274.93) --
-	(406.99,274.93) --
-	cycle;
-
-\path[fill=fillColor] (418.90,283.71) --
-	(422.26,277.88) --
-	(415.54,277.88) --
-	cycle;
-
-\path[fill=fillColor] (427.44,286.69) --
-	(430.81,280.87) --
-	(424.08,280.87) --
-	cycle;
-
-\path[fill=fillColor] (435.98,289.70) --
-	(439.35,283.87) --
-	(432.62,283.87) --
-	cycle;
-
-\path[fill=fillColor] (444.53,292.72) --
-	(447.89,286.89) --
-	(441.16,286.89) --
-	cycle;
-
-\path[fill=fillColor] (453.07,295.74) --
-	(456.43,289.92) --
-	(449.71,289.92) --
-	cycle;
-
-\path[fill=fillColor] (461.61,298.77) --
-	(464.97,292.94) --
-	(458.25,292.94) --
-	cycle;
-
-\path[fill=fillColor] (470.15,301.79) --
-	(473.52,295.96) --
-	(466.79,295.96) --
-	cycle;
-
-\path[fill=fillColor] (478.70,304.79) --
-	(482.06,298.96) --
-	(475.33,298.96) --
-	cycle;
-
-\path[fill=fillColor] (487.24,307.75) --
-	(490.60,301.93) --
-	(483.87,301.93) --
-	cycle;
-
-\path[fill=fillColor] (495.78,310.68) --
-	(499.14,304.85) --
-	(492.42,304.85) --
-	cycle;
-
-\path[fill=fillColor] (504.32,313.55) --
-	(507.69,307.73) --
-	(500.96,307.73) --
-	cycle;
-
-\path[fill=fillColor] (512.86,316.36) --
-	(516.23,310.53) --
-	(509.50,310.53) --
-	cycle;
-
-\path[fill=fillColor] (521.41,319.08) --
-	(524.77,313.25) --
-	(518.04,313.25) --
-	cycle;
-
-\path[fill=fillColor] (529.95,321.70) --
-	(533.31,315.88) --
-	(526.59,315.88) --
-	cycle;
-
-\path[fill=fillColor] (538.49,324.21) --
-	(541.85,318.39) --
-	(535.13,318.39) --
-	cycle;
-
-\path[fill=fillColor] (547.03,326.59) --
-	(550.40,320.76) --
-	(543.67,320.76) --
-	cycle;
-
-\path[fill=fillColor] (555.58,328.81) --
-	(558.94,322.98) --
-	(552.21,322.98) --
-	cycle;
-
-\path[fill=fillColor] (564.12,330.86) --
-	(567.48,325.03) --
-	(560.75,325.03) --
-	cycle;
-
-\path[fill=fillColor] (572.66,332.71) --
-	(576.02,326.88) --
-	(569.30,326.88) --
+\path[fill=fillColor] (367.65,266.57) --
+	(371.01,260.75) --
+	(364.28,260.75) --
+	cycle;
+
+\path[fill=fillColor] (376.19,269.31) --
+	(379.55,263.48) --
+	(372.83,263.48) --
+	cycle;
+
+\path[fill=fillColor] (384.73,272.09) --
+	(388.09,266.27) --
+	(381.37,266.27) --
+	cycle;
+
+\path[fill=fillColor] (393.27,274.93) --
+	(396.64,269.10) --
+	(389.91,269.10) --
+	cycle;
+
+\path[fill=fillColor] (401.82,277.80) --
+	(405.18,271.97) --
+	(398.45,271.97) --
+	cycle;
+
+\path[fill=fillColor] (410.36,280.71) --
+	(413.72,274.89) --
+	(406.99,274.89) --
+	cycle;
+
+\path[fill=fillColor] (418.90,283.66) --
+	(422.26,277.83) --
+	(415.54,277.83) --
+	cycle;
+
+\path[fill=fillColor] (427.44,286.63) --
+	(430.81,280.80) --
+	(424.08,280.80) --
+	cycle;
+
+\path[fill=fillColor] (435.98,289.62) --
+	(439.35,283.79) --
+	(432.62,283.79) --
+	cycle;
+
+\path[fill=fillColor] (444.53,292.62) --
+	(447.89,286.79) --
+	(441.16,286.79) --
+	cycle;
+
+\path[fill=fillColor] (453.07,295.63) --
+	(456.43,289.80) --
+	(449.71,289.80) --
+	cycle;
+
+\path[fill=fillColor] (461.61,298.63) --
+	(464.97,292.81) --
+	(458.25,292.81) --
+	cycle;
+
+\path[fill=fillColor] (470.15,301.63) --
+	(473.52,295.80) --
+	(466.79,295.80) --
+	cycle;
+
+\path[fill=fillColor] (478.70,304.60) --
+	(482.06,298.77) --
+	(475.33,298.77) --
+	cycle;
+
+\path[fill=fillColor] (487.24,307.54) --
+	(490.60,301.71) --
+	(483.87,301.71) --
+	cycle;
+
+\path[fill=fillColor] (495.78,310.43) --
+	(499.14,304.60) --
+	(492.42,304.60) --
+	cycle;
+
+\path[fill=fillColor] (504.32,313.26) --
+	(507.69,307.44) --
+	(500.96,307.44) --
+	cycle;
+
+\path[fill=fillColor] (512.86,316.03) --
+	(516.23,310.20) --
+	(509.50,310.20) --
+	cycle;
+
+\path[fill=fillColor] (521.41,318.70) --
+	(524.77,312.87) --
+	(518.04,312.87) --
+	cycle;
+
+\path[fill=fillColor] (529.95,321.27) --
+	(533.31,315.44) --
+	(526.59,315.44) --
+	cycle;
+
+\path[fill=fillColor] (538.49,323.72) --
+	(541.85,317.89) --
+	(535.13,317.89) --
+	cycle;
+
+\path[fill=fillColor] (547.03,326.03) --
+	(550.40,320.20) --
+	(543.67,320.20) --
+	cycle;
+
+\path[fill=fillColor] (555.58,328.18) --
+	(558.94,322.35) --
+	(552.21,322.35) --
+	cycle;
+
+\path[fill=fillColor] (564.12,330.14) --
+	(567.48,324.32) --
+	(560.75,324.32) --
+	cycle;
+
+\path[fill=fillColor] (572.66,331.91) --
+	(576.02,326.08) --
+	(569.30,326.08) --
 	cycle;
@@
 	(353.06,254.68) --
-	(353.06,259.68) --
-	(348.06,259.68) --
-	cycle;
-
-\path[fill=fillColor] (356.61,257.18) --
-	(361.60,257.18) --
-	(361.60,262.17) --
-	(356.61,262.17) --
-	cycle;
-
-\path[fill=fillColor] (365.15,259.69) --
-	(370.14,259.69) --
-	(370.14,264.68) --
-	(365.15,264.68) --
-	cycle;
-
-\path[fill=fillColor] (373.69,262.21) --
-	(378.69,262.21) --
-	(378.69,267.20) --
-	(373.69,267.20) --
-	cycle;
-
-\path[fill=fillColor] (382.23,264.73) --
-	(387.23,264.73) --
-	(387.23,269.73) --
-	(382.23,269.73) --
-	cycle;
-
-\path[fill=fillColor] (390.78,267.25) --
-	(395.77,267.25) --
-	(395.77,272.24) --
-	(390.78,272.24) --
-	cycle;
-
-\path[fill=fillColor] (399.32,269.74) --
-	(404.31,269.74) --
-	(404.31,274.74) --
-	(399.32,274.74) --
-	cycle;
-
-\path[fill=fillColor] (407.86,272.21) --
-	(412.86,272.21) --
-	(412.86,277.21) --
-	(407.86,277.21) --
-	cycle;
-
-\path[fill=fillColor] (416.40,274.64) --
-	(421.40,274.64) --
-	(421.40,279.63) --
-	(416.40,279.63) --
-	cycle;
-
-\path[fill=fillColor] (424.94,277.02) --
-	(429.94,277.02) --
-	(429.94,282.01) --
-	(424.94,282.01) --
-	cycle;
-
-\path[fill=fillColor] (433.49,279.33) --
-	(438.48,279.33) --
-	(438.48,284.33) --
-	(433.49,284.33) --
-	cycle;
-
-\path[fill=fillColor] (442.03,281.56) --
-	(447.02,281.56) --
-	(447.02,286.56) --
-	(442.03,286.56) --
-	cycle;
-
-\path[fill=fillColor] (450.57,283.70) --
-	(455.57,283.70) --
-	(455.57,288.70) --
-	(450.57,288.70) --
-	cycle;
-
-\path[fill=fillColor] (459.11,285.74) --
-	(464.11,285.74) --
-	(464.11,290.73) --
-	(459.11,290.73) --
-	cycle;
-
-\path[fill=fillColor] (467.66,287.64) --
-	(472.65,287.64) --
-	(472.65,292.63) --
-	(467.66,292.63) --
-	cycle;
-
-\path[fill=fillColor] (476.20,289.40) --
-	(481.19,289.40) --
-	(481.19,294.39) --
-	(476.20,294.39) --
-	cycle;
-
-\path[fill=fillColor] (484.74,290.99) --
-	(489.74,290.99) --
-	(489.74,295.98) --
-	(484.74,295.98) --
-	cycle;
-
-\path[fill=fillColor] (493.28,292.39) --
-	(498.28,292.39) --
-	(498.28,297.39) --
-	(493.28,297.39) --
-	cycle;
-
-\path[fill=fillColor] (501.82,293.59) --
-	(506.82,293.59) --
-	(506.82,298.58) --
-	(501.82,298.58) --
-	cycle;
-
-\path[fill=fillColor] (510.37,294.55) --
-	(515.36,294.55) --
-	(515.36,299.55) --
-	(510.37,299.55) --
-	cycle;
-
-\path[fill=fillColor] (518.91,295.26) --
-	(523.90,295.26) --
-	(523.90,300.25) --
-	(518.91,300.25) --
-	cycle;
-
-\path[fill=fillColor] (527.45,295.68) --
-	(532.45,295.68) --
-	(532.45,300.68) --
-	(527.45,300.68) --
-	cycle;
-
-\path[fill=fillColor] (535.99,295.80) --
-	(540.99,295.80) --
-	(540.99,300.79) --
-	(535.99,300.79) --
-	cycle;
-
-\path[fill=fillColor] (544.54,295.58) --
-	(549.53,295.58) --
-	(549.53,300.58) --
-	(544.54,300.58) --
-	cycle;
-
-\path[fill=fillColor] (553.08,295.01) --
-	(558.07,295.01) --
-	(558.07,300.00) --
-	(553.08,300.00) --
-	cycle;
-
-\path[fill=fillColor] (561.62,294.05) --
-	(566.62,294.05) --
-	(566.62,299.05) --
-	(561.62,299.05) --
-	cycle;
-
-\path[fill=fillColor] (570.16,292.69) --
-	(575.16,292.69) --
-	(575.16,297.69) --
-	(570.16,297.69) --
+	(353.06,259.67) --
+	(348.06,259.67) --
+	cycle;
+
+\path[fill=fillColor] (356.61,257.17) --
+	(361.60,257.17) --
+	(361.60,262.16) --
+	(356.61,262.16) --
+	cycle;
+
+\path[fill=fillColor] (365.15,259.67) --
+	(370.14,259.67) --
+	(370.14,264.67) --
+	(365.15,264.67) --
+	cycle;
+
+\path[fill=fillColor] (373.69,262.19) --
+	(378.69,262.19) --
+	(378.69,267.19) --
+	(373.69,267.19) --
+	cycle;
+
+\path[fill=fillColor] (382.23,264.71) --
+	(387.23,264.71) --
+	(387.23,269.70) --
+	(382.23,269.70) --
+	cycle;
+
+\path[fill=fillColor] (390.78,267.21) --
+	(395.77,267.21) --
+	(395.77,272.21) --
+	(390.78,272.21) --
+	cycle;
+
+\path[fill=fillColor] (399.32,269.70) --
+	(404.31,269.70) --
+	(404.31,274.69) --
+	(399.32,274.69) --
+	cycle;
+
+\path[fill=fillColor] (407.86,272.15) --
+	(412.86,272.15) --
+	(412.86,277.15) --
+	(407.86,277.15) --
+	cycle;
+
+\path[fill=fillColor] (416.40,274.57) --
+	(421.40,274.57) --
+	(421.40,279.56) --
+	(416.40,279.56) --
+	cycle;
+
+\path[fill=fillColor] (424.94,276.93) --
+	(429.94,276.93) --
+	(429.94,281.93) --
+	(424.94,281.93) --
+	cycle;
+
+\path[fill=fillColor] (433.49,279.22) --
+	(438.48,279.22) --
+	(438.48,284.22) --
+	(433.49,284.22) --
+	cycle;
+
+\path[fill=fillColor] (442.03,281.44) --
+	(447.02,281.44) --
+	(447.02,286.43) --
+	(442.03,286.43) --
+	cycle;
+
+\path[fill=fillColor] (450.57,283.55) --
+	(455.57,283.55) --
+	(455.57,288.55) --
+	(450.57,288.55) --
+	cycle;
+
+\path[fill=fillColor] (459.11,285.55) --
+	(464.11,285.55) --
+	(464.11,290.55) --
+	(459.11,290.55) --
+	cycle;
+
+\path[fill=fillColor] (467.66,287.42) --
+	(472.65,287.42) --
+	(472.65,292.42) --
+	(467.66,292.42) --
+	cycle;
+
+\path[fill=fillColor] (476.20,289.14) --
+	(481.19,289.14) --
+	(481.19,294.14) --
+	(476.20,294.14) --
+	cycle;
+
+\path[fill=fillColor] (484.74,290.69) --
+	(489.74,290.69) --
+	(489.74,295.69) --
+	(484.74,295.69) --
+	cycle;
+
+\path[fill=fillColor] (493.28,292.05) --
+	(498.28,292.05) --
+	(498.28,297.04) --
+	(493.28,297.04) --
+	cycle;
+
+\path[fill=fillColor] (501.82,293.19) --
+	(506.82,293.19) --
+	(506.82,298.19) --
+	(501.82,298.19) --
+	cycle;
+
+\path[fill=fillColor] (510.37,294.09) --
+	(515.36,294.09) --
+	(515.36,299.09) --
+	(510.37,299.09) --
+	cycle;
+
+\path[fill=fillColor] (518.91,294.73) --
+	(523.90,294.73) --
+	(523.90,299.73) --
+	(518.91,299.73) --
+	cycle;
+
+\path[fill=fillColor] (527.45,295.08) --
+	(532.45,295.08) --
+	(532.45,300.07) --
+	(527.45,300.07) --
+	cycle;
+
+\path[fill=fillColor] (535.99,295.11) --
+	(540.99,295.11) --
+	(540.99,300.11) --
+	(535.99,300.11) --
+	cycle;
+
+\path[fill=fillColor] (544.54,294.80) --
+	(549.53,294.80) --
+	(549.53,299.79) --
+	(544.54,299.79) --
+	cycle;
+
+\path[fill=fillColor] (553.08,294.12) --
+	(558.07,294.12) --
+	(558.07,299.12) --
+	(553.08,299.12) --
+	cycle;
+
+\path[fill=fillColor] (561.62,293.05) --
+	(566.62,293.05) --
+	(566.62,298.05) --
+	(561.62,298.05) --
+	cycle;
+
+\path[fill=fillColor] (570.16,291.57) --
+	(575.16,291.57) --
+	(575.16,296.57) --
+	(570.16,296.57) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.45) -- (350.56,260.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,259.36) -- (362.64,259.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,255.82) -- (359.10,262.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,261.71) -- (371.18,261.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,258.18) -- (367.65,265.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,264.03) -- (379.72,264.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,260.50) -- (376.19,267.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,266.31) -- (388.26,266.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,262.78) -- (384.73,269.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,268.54) -- (396.81,268.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,265.01) -- (393.27,272.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,270.69) -- (405.35,270.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,267.16) -- (401.82,274.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,272.77) -- (413.89,272.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,269.23) -- (410.36,276.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,274.74) -- (422.43,274.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,271.21) -- (418.90,278.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,276.60) -- (430.97,276.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,273.07) -- (427.44,280.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,278.33) -- (439.52,278.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,274.80) -- (435.98,281.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,279.91) -- (448.06,279.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,276.38) -- (444.53,283.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,281.32) -- (456.60,281.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,277.79) -- (453.07,284.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,282.55) -- (465.14,282.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,279.02) -- (461.61,286.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,283.58) -- (473.69,283.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,280.04) -- (470.15,287.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,284.37) -- (482.23,284.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,280.84) -- (478.70,287.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,284.92) -- (490.77,284.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,281.39) -- (487.24,288.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,285.20) -- (499.31,285.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,281.66) -- (495.78,288.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,285.18) -- (507.85,285.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,281.65) -- (504.32,288.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,284.85) -- (516.40,284.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,281.32) -- (512.86,288.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,284.18) -- (524.94,284.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,280.65) -- (521.41,287.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,283.15) -- (533.48,283.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,279.62) -- (529.95,286.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,281.75) -- (542.02,281.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,278.22) -- (538.49,285.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,279.96) -- (550.57,279.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,276.43) -- (547.03,283.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,277.78) -- (559.11,277.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,274.24) -- (555.58,281.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,275.19) -- (567.65,275.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,271.66) -- (564.12,278.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,272.21) -- (576.19,272.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,268.68) -- (572.66,275.74);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.45) -- (350.56,260.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,259.35) -- (362.64,259.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,255.81) -- (359.10,262.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,261.70) -- (371.18,261.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,258.16) -- (367.65,265.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,264.01) -- (379.72,264.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,260.48) -- (376.19,267.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,266.28) -- (388.26,266.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,262.75) -- (384.73,269.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,268.50) -- (396.81,268.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,264.97) -- (393.27,272.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,270.64) -- (405.35,270.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,267.11) -- (401.82,274.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,272.70) -- (413.89,272.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,269.17) -- (410.36,276.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,274.66) -- (422.43,274.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,271.13) -- (418.90,278.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,276.50) -- (430.97,276.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,272.97) -- (427.44,280.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,278.21) -- (439.52,278.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,274.67) -- (435.98,281.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,279.76) -- (448.06,279.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,276.23) -- (444.53,283.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,281.15) -- (456.60,281.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,277.61) -- (453.07,284.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,282.34) -- (465.14,282.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,278.81) -- (461.61,285.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,283.32) -- (473.69,283.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,279.79) -- (470.15,286.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,284.08) -- (482.23,284.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,280.55) -- (478.70,287.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,284.58) -- (490.77,284.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,281.04) -- (487.24,288.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,284.80) -- (499.31,284.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,281.27) -- (495.78,288.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,284.72) -- (507.85,284.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,281.19) -- (504.32,288.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,284.32) -- (516.40,284.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,280.79) -- (512.86,287.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,283.58) -- (524.94,283.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,280.04) -- (521.41,287.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,282.47) -- (533.48,282.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,278.94) -- (529.95,286.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,280.98) -- (542.02,280.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,277.44) -- (538.49,284.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,279.09) -- (550.57,279.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,275.56) -- (547.03,282.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,276.80) -- (559.11,276.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,273.26) -- (555.58,280.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,274.10) -- (567.65,274.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,270.57) -- (564.12,277.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,271.01) -- (576.19,271.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,267.47) -- (572.66,274.54);
 \definecolor{fillColor}{RGB}{0,0,0}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,329.23) {Reproduction number $\mathcal R$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,329.23) {Naive reproduction number ${\mathcal R}_{\textrm{\tiny naive}}$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 54.52) --
-	( 30.56, 54.54) --
-	( 33.80, 54.57) --
-	( 37.04, 54.60) --
-	( 40.29, 54.62) --
-	( 43.53, 54.64) --
-	( 46.78, 54.67) --
-	( 50.02, 54.69) --
-	( 53.26, 54.70) --
-	( 56.51, 54.72) --
-	( 59.75, 54.73) --
-	( 63.00, 54.75) --
-	( 66.24, 54.76) --
-	( 69.48, 54.77) --
-	( 72.73, 54.77) --
-	( 75.97, 54.78) --
-	( 79.22, 54.79) --
-	( 82.46, 54.80) --
-	( 85.70, 54.80) --
-	( 88.95, 54.81) --
-	( 92.19, 54.81) --
-	( 95.43, 54.81) --
-	( 98.68, 54.80) --
-	(101.92, 54.79) --
-	(105.17, 54.78) --
-	(108.41, 54.77) --
-	(111.65, 54.77) --
-	(114.90, 54.76) --
-	(118.14, 54.76) --
-	(121.39, 54.76) --
-	(124.63, 54.76) --
-	(127.87, 54.77) --
-	(131.12, 54.79) --
-	(134.36, 54.80) --
-	(137.61, 54.82) --
-	(140.85, 54.83) --
-	(144.09, 54.85) --
-	(147.34, 54.87) --
-	(150.58, 54.88) --
-	(153.82, 54.89) --
-	(157.07, 54.89) --
-	(160.31, 54.89) --
-	(163.56, 54.89) --
-	(166.80, 54.89) --
-	(170.04, 54.89) --
-	(173.29, 54.89) --
-	(176.53, 54.89) --
-	(179.78, 54.88) --
-	(183.02, 54.88) --
-	(186.26, 54.88) --
-	(189.51, 54.88) --
-	(192.75, 54.87) --
-	(196.00, 54.87) --
-	(199.24, 54.87) --
-	(202.48, 54.87) --
-	(205.73, 54.86) --
-	(208.97, 54.86) --
-	(212.21, 54.86) --
-	(215.46, 54.86) --
-	(218.70, 54.86) --
-	(221.95, 54.85) --
-	(225.19, 54.85) --
-	(228.43, 54.85) --
-	(231.68, 54.85) --
-	(234.92, 54.85) --
-	(238.17, 54.84) --
-	(241.41, 54.84) --
-	(244.65, 54.84) --
-	(247.90, 54.84) --
-	(251.14, 54.83) --
-	(254.39, 54.83) --
-	(257.63, 54.83) --
-	(260.87, 54.83) --
-	(264.12, 54.83) --
-	(267.36, 54.83) --
-	(270.60, 54.83) --
-	(273.85, 54.83) --
-	(277.09, 54.82) --
-	(280.34, 54.82) --
-	(283.58, 54.82);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 54.39) --
+	( 30.56, 54.42) --
+	( 33.80, 54.45) --
+	( 37.04, 54.47) --
+	( 40.29, 54.50) --
+	( 43.53, 54.52) --
+	( 46.78, 54.54) --
+	( 50.02, 54.56) --
+	( 53.26, 54.58) --
+	( 56.51, 54.59) --
+	( 59.75, 54.61) --
+	( 63.00, 54.62) --
+	( 66.24, 54.63) --
+	( 69.48, 54.64) --
+	( 72.73, 54.65) --
+	( 75.97, 54.66) --
+	( 79.22, 54.66) --
+	( 82.46, 54.67) --
+	( 85.70, 54.68) --
+	( 88.95, 54.68) --
+	( 92.19, 54.68) --
+	( 95.43, 54.68) --
+	( 98.68, 54.67) --
+	(101.92, 54.67) --
+	(105.17, 54.66) --
+	(108.41, 54.65) --
+	(111.65, 54.64) --
+	(114.90, 54.63) --
+	(118.14, 54.63) --
+	(121.39, 54.63) --
+	(124.63, 54.64) --
+	(127.87, 54.65) --
+	(131.12, 54.66) --
+	(134.36, 54.67) --
+	(137.61, 54.69) --
+	(140.85, 54.71) --
+	(144.09, 54.72) --
+	(147.34, 54.74) --
+	(150.58, 54.75) --
+	(153.82, 54.76) --
+	(157.07, 54.76) --
+	(160.31, 54.76) --
+	(163.56, 54.76) --
+	(166.80, 54.76) --
+	(170.04, 54.76) --
+	(173.29, 54.76) --
+	(176.53, 54.76) --
+	(179.78, 54.76) --
+	(183.02, 54.75) --
+	(186.26, 54.75) --
+	(189.51, 54.75) --
+	(192.75, 54.75) --
+	(196.00, 54.75) --
+	(199.24, 54.74) --
+	(202.48, 54.74) --
+	(205.73, 54.74) --
+	(208.97, 54.74) --
+	(212.21, 54.73) --
+	(215.46, 54.73) --
+	(218.70, 54.73) --
+	(221.95, 54.73) --
+	(225.19, 54.73) --
+	(228.43, 54.72) --
+	(231.68, 54.72) --
+	(234.92, 54.72) --
+	(238.17, 54.72) --
+	(241.41, 54.71) --
+	(244.65, 54.71) --
+	(247.90, 54.71) --
+	(251.14, 54.71) --
+	(254.39, 54.70) --
+	(257.63, 54.70) --
+	(260.87, 54.70) --
+	(264.12, 54.70) --
+	(267.36, 54.70) --
+	(270.60, 54.70) --
+	(273.85, 54.70) --
+	(277.09, 54.70) --
+	(280.34, 54.70) --
+	(283.58, 54.70);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31, 55.83) --
-	( 30.56, 56.93) --
-	( 33.80, 58.02) --
-	( 37.04, 59.09) --
-	( 40.29, 60.16) --
-	( 43.53, 61.21) --
-	( 46.78, 62.25) --
-	( 50.02, 63.27) --
-	( 53.26, 64.29) --
-	( 56.51, 65.29) --
-	( 59.75, 66.28) --
-	( 63.00, 67.26) --
-	( 66.24, 68.22) --
-	( 69.48, 69.18) --
-	( 72.73, 70.12) --
-	( 75.97, 71.05) --
-	( 79.22, 71.97) --
-	( 82.46, 72.88) --
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31, 55.70) --
+	( 30.56, 56.81) --
+	( 33.80, 57.90) --
+	( 37.04, 58.98) --
+	( 40.29, 60.06) --
+	( 43.53, 61.12) --
+	( 46.78, 62.16) --
+	( 50.02, 63.20) --
+	( 53.26, 64.22) --
+	( 56.51, 65.23) --
+	( 59.75, 66.23) --
+	( 63.00, 67.21) --
+	( 66.24, 68.18) --
+	( 69.48, 69.14) --
+	( 72.73, 70.09) --
+	( 75.97, 71.03) --
+	( 79.22, 71.95) --
+	( 82.46, 72.86) --
 	( 85.70, 73.77) --
@@
 	( 92.19, 75.53) --
-	( 95.43, 76.38) --
-	( 98.68, 77.22) --
-	(101.92, 78.05) --
-	(105.17, 78.87) --
-	(108.41, 79.68) --
-	(111.65, 80.48) --
-	(114.90, 81.26) --
-	(118.14, 82.04) --
-	(121.39, 82.81) --
-	(124.63, 83.56) --
-	(127.87, 84.30) --
-	(131.12, 85.03) --
-	(134.36, 85.74) --
-	(137.61, 86.44) --
-	(140.85, 87.13) --
-	(144.09, 87.82) --
-	(147.34, 88.50) --
-	(150.58, 89.18) --
-	(153.82, 89.85) --
-	(157.07, 90.53) --
-	(160.31, 91.19) --
-	(163.56, 91.85) --
-	(166.80, 92.50) --
-	(170.04, 93.14) --
-	(173.29, 93.78) --
-	(176.53, 94.41) --
-	(179.78, 95.03) --
-	(183.02, 95.66) --
-	(186.26, 96.27) --
-	(189.51, 96.89) --
-	(192.75, 97.50) --
-	(196.00, 98.11) --
-	(199.24, 98.72) --
-	(202.48, 99.31) --
-	(205.73, 99.91) --
-	(208.97,100.50) --
-	(212.21,101.08) --
-	(215.46,101.66) --
-	(218.70,102.23) --
-	(221.95,102.80) --
-	(225.19,103.37) --
-	(228.43,103.93) --
-	(231.68,104.49) --
-	(234.92,105.04) --
-	(238.17,105.59) --
-	(241.41,106.13) --
-	(244.65,106.66) --
-	(247.90,107.20) --
-	(251.14,107.72) --
-	(254.39,108.25) --
-	(257.63,108.77) --
-	(260.87,109.28) --
-	(264.12,109.79) --
-	(267.36,110.29) --
-	(270.60,110.79) --
-	(273.85,111.29) --
-	(277.09,111.78) --
-	(280.34,112.27) --
-	(283.58,112.75);
+	( 95.43, 76.39) --
+	( 98.68, 77.24) --
+	(101.92, 78.07) --
+	(105.17, 78.90) --
+	(108.41, 79.71) --
+	(111.65, 80.51) --
+	(114.90, 81.30) --
+	(118.14, 82.08) --
+	(121.39, 82.85) --
+	(124.63, 83.61) --
+	(127.87, 84.35) --
+	(131.12, 85.08) --
+	(134.36, 85.79) --
+	(137.61, 86.49) --
+	(140.85, 87.19) --
+	(144.09, 87.87) --
+	(147.34, 88.55) --
+	(150.58, 89.23) --
+	(153.82, 89.91) --
+	(157.07, 90.59) --
+	(160.31, 91.26) --
+	(163.56, 91.92) --
+	(166.80, 92.57) --
+	(170.04, 93.22) --
+	(173.29, 93.86) --
+	(176.53, 94.49) --
+	(179.78, 95.12) --
+	(183.02, 95.75) --
+	(186.26, 96.37) --
+	(189.51, 96.99) --
+	(192.75, 97.61) --
+	(196.00, 98.22) --
+	(199.24, 98.82) --
+	(202.48, 99.42) --
+	(205.73,100.02) --
+	(208.97,100.61) --
+	(212.21,101.20) --
+	(215.46,101.78) --
+	(218.70,102.35) --
+	(221.95,102.93) --
+	(225.19,103.50) --
+	(228.43,104.06) --
+	(231.68,104.62) --
+	(234.92,105.17) --
+	(238.17,105.72) --
+	(241.41,106.27) --
+	(244.65,106.81) --
+	(247.90,107.34) --
+	(251.14,107.87) --
+	(254.39,108.40) --
+	(257.63,108.92) --
+	(260.87,109.43) --
+	(264.12,109.95) --
+	(267.36,110.45) --
+	(270.60,110.95) --
+	(273.85,111.45) --
+	(277.09,111.95) --
+	(280.34,112.43) --
+	(283.58,112.92);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31, 55.69) --
-	( 30.56, 57.48) --
-	( 33.80, 59.25) --
-	( 37.04, 61.00) --
-	( 40.29, 62.74) --
-	( 43.53, 64.46) --
-	( 46.78, 66.16) --
-	( 50.02, 67.84) --
-	( 53.26, 69.50) --
-	( 56.51, 71.15) --
-	( 59.75, 72.78) --
-	( 63.00, 74.39) --
-	( 66.24, 75.98) --
-	( 69.48, 77.56) --
-	( 72.73, 79.11) --
-	( 75.97, 80.65) --
-	( 79.22, 82.18) --
-	( 82.46, 83.68) --
-	( 85.70, 85.17) --
-	( 88.95, 86.65) --
-	( 92.19, 88.10) --
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31, 55.54) --
+	( 30.56, 57.34) --
+	( 33.80, 59.12) --
+	( 37.04, 60.88) --
+	( 40.29, 62.63) --
+	( 43.53, 64.35) --
+	( 46.78, 66.06) --
+	( 50.02, 67.75) --
+	( 53.26, 69.43) --
+	( 56.51, 71.08) --
+	( 59.75, 72.71) --
+	( 63.00, 74.33) --
+	( 66.24, 75.93) --
+	( 69.48, 77.51) --
+	( 72.73, 79.07) --
+	( 75.97, 80.62) --
+	( 79.22, 82.15) --
+	( 82.46, 83.66) --
+	( 85.70, 85.16) --
+	( 88.95, 86.63) --
+	( 92.19, 88.09) --
 	( 95.43, 89.53) --
@@
 	(101.92, 92.34) --
-	(105.17, 93.71) --
-	(108.41, 95.07) --
-	(111.65, 96.42) --
-	(114.90, 97.74) --
-	(118.14, 99.06) --
-	(121.39,100.36) --
-	(124.63,101.64) --
-	(127.87,102.90) --
-	(131.12,104.13) --
-	(134.36,105.34) --
-	(137.61,106.54) --
-	(140.85,107.73) --
-	(144.09,108.90) --
-	(147.34,110.07) --
-	(150.58,111.23) --
-	(153.82,112.39) --
-	(157.07,113.56) --
-	(160.31,114.71) --
-	(163.56,115.85) --
-	(166.80,116.97) --
-	(170.04,118.09) --
-	(173.29,119.20) --
-	(176.53,120.30) --
-	(179.78,121.39) --
-	(183.02,122.48) --
-	(186.26,123.56) --
-	(189.51,124.64) --
-	(192.75,125.71) --
-	(196.00,126.77) --
-	(199.24,127.83) --
-	(202.48,128.88) --
-	(205.73,129.92) --
-	(208.97,130.96) --
-	(212.21,131.98) --
-	(215.46,133.00) --
-	(218.70,134.02) --
-	(221.95,135.02) --
-	(225.19,136.02) --
-	(228.43,137.01) --
-	(231.68,137.99) --
-	(234.92,138.97) --
-	(238.17,139.94) --
-	(241.41,140.90) --
-	(244.65,141.85) --
-	(247.90,142.80) --
-	(251.14,143.74) --
-	(254.39,144.67) --
-	(257.63,145.59) --
-	(260.87,146.51) --
-	(264.12,147.42) --
-	(267.36,148.32) --
-	(270.60,149.21) --
-	(273.85,150.10) --
-	(277.09,150.98) --
-	(280.34,151.85) --
-	(283.58,152.72);
+	(105.17, 93.72) --
+	(108.41, 95.08) --
+	(111.65, 96.43) --
+	(114.90, 97.76) --
+	(118.14, 99.08) --
+	(121.39,100.38) --
+	(124.63,101.67) --
+	(127.87,102.92) --
+	(131.12,104.16) --
+	(134.36,105.37) --
+	(137.61,106.57) --
+	(140.85,107.76) --
+	(144.09,108.93) --
+	(147.34,110.10) --
+	(150.58,111.27) --
+	(153.82,112.43) --
+	(157.07,113.59) --
+	(160.31,114.75) --
+	(163.56,115.89) --
+	(166.80,117.02) --
+	(170.04,118.14) --
+	(173.29,119.26) --
+	(176.53,120.36) --
+	(179.78,121.46) --
+	(183.02,122.55) --
+	(186.26,123.63) --
+	(189.51,124.71) --
+	(192.75,125.78) --
+	(196.00,126.85) --
+	(199.24,127.91) --
+	(202.48,128.96) --
+	(205.73,130.00) --
+	(208.97,131.03) --
+	(212.21,132.06) --
+	(215.46,133.08) --
+	(218.70,134.09) --
+	(221.95,135.10) --
+	(225.19,136.09) --
+	(228.43,137.09) --
+	(231.68,138.07) --
+	(234.92,139.04) --
+	(238.17,140.01) --
+	(241.41,140.97) --
+	(244.65,141.92) --
+	(247.90,142.87) --
+	(251.14,143.81) --
+	(254.39,144.74) --
+	(257.63,145.66) --
+	(260.87,146.58) --
+	(264.12,147.48) --
+	(267.36,148.38) --
+	(270.60,149.28) --
+	(273.85,150.16) --
+	(277.09,151.04) --
+	(280.34,151.91) --
+	(283.58,152.77);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 55.36) --
-	( 30.56, 57.79) --
-	( 33.80, 60.21) --
-	( 37.04, 62.60) --
-	( 40.29, 64.97) --
-	( 43.53, 67.32) --
-	( 46.78, 69.65) --
-	( 50.02, 71.96) --
-	( 53.26, 74.25) --
-	( 56.51, 76.51) --
-	( 59.75, 78.75) --
-	( 63.00, 80.97) --
-	( 66.24, 83.17) --
-	( 69.48, 85.34) --
-	( 72.73, 87.50) --
-	( 75.97, 89.63) --
-	( 79.22, 91.75) --
-	( 82.46, 93.84) --
-	( 85.70, 95.91) --
-	( 88.95, 97.97) --
-	( 92.19, 99.99) --
-	( 95.43,102.00) --
-	( 98.68,103.98) --
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 55.20) --
+	( 30.56, 57.64) --
+	( 33.80, 60.07) --
+	( 37.04, 62.47) --
+	( 40.29, 64.85) --
+	( 43.53, 67.21) --
+	( 46.78, 69.55) --
+	( 50.02, 71.86) --
+	( 53.26, 74.15) --
+	( 56.51, 76.43) --
+	( 59.75, 78.67) --
+	( 63.00, 80.90) --
+	( 66.24, 83.10) --
+	( 69.48, 85.29) --
+	( 72.73, 87.45) --
+	( 75.97, 89.59) --
+	( 79.22, 91.71) --
+	( 82.46, 93.81) --
+	( 85.70, 95.89) --
+	( 88.95, 97.94) --
+	( 92.19, 99.98) --
+	( 95.43,101.98) --
+	( 98.68,103.97) --
 	(101.92,105.93) --
 	(105.17,107.87) --
-	(108.41,109.78) --
-	(111.65,111.68) --
-	(114.90,113.56) --
-	(118.14,115.41) --
-	(121.39,117.26) --
-	(124.63,119.08) --
-	(127.87,120.86) --
-	(131.12,122.62) --
-	(134.36,124.35) --
-	(137.61,126.07) --
-	(140.85,127.76) --
-	(144.09,129.45) --
-	(147.34,131.13) --
-	(150.58,132.80) --
-	(153.82,134.48) --
-	(157.07,136.16) --
-	(160.31,137.82) --
-	(163.56,139.47) --
-	(166.80,141.11) --
-	(170.04,142.73) --
-	(173.29,144.35) --
-	(176.53,145.95) --
-	(179.78,147.55) --
-	(183.02,149.14) --
-	(186.26,150.72) --
-	(189.51,152.30) --
-	(192.75,153.87) --
-	(196.00,155.43) --
-	(199.24,156.98) --
-	(202.48,158.52) --
-	(205.73,160.06) --
-	(208.97,161.58) --
-	(212.21,163.09) --
-	(215.46,164.60) --
-	(218.70,166.10) --
-	(221.95,167.58) --
-	(225.19,169.06) --
-	(228.43,170.53) --
-	(231.68,171.99) --
-	(234.92,173.44) --
-	(238.17,174.88) --
-	(241.41,176.31) --
-	(244.65,177.74) --
-	(247.90,179.15) --
-	(251.14,180.55) --
+	(108.41,109.79) --
+	(111.65,111.69) --
+	(114.90,113.57) --
+	(118.14,115.43) --
+	(121.39,117.28) --
+	(124.63,119.10) --
+	(127.87,120.88) --
+	(131.12,122.64) --
+	(134.36,124.37) --
+	(137.61,126.09) --
+	(140.85,127.78) --
+	(144.09,129.47) --
+	(147.34,131.15) --
+	(150.58,132.82) --
+	(153.82,134.50) --
+	(157.07,136.18) --
+	(160.31,137.85) --
+	(163.56,139.50) --
+	(166.80,141.14) --
+	(170.04,142.77) --
+	(173.29,144.39) --
+	(176.53,146.00) --
+	(179.78,147.60) --
+	(183.02,149.19) --
+	(186.26,150.78) --
+	(189.51,152.36) --
+	(192.75,153.93) --
+	(196.00,155.49) --
+	(199.24,157.04) --
+	(202.48,158.58) --
+	(205.73,160.11) --
+	(208.97,161.63) --
+	(212.21,163.15) --
+	(215.46,164.65) --
+	(218.70,166.14) --
+	(221.95,167.63) --
+	(225.19,169.10) --
+	(228.43,170.57) --
+	(231.68,172.02) --
+	(234.92,173.47) --
+	(238.17,174.91) --
+	(241.41,176.33) --
+	(244.65,177.75) --
+	(247.90,179.16) --
+	(251.14,180.56) --
 	(254.39,181.95) --
-	(257.63,183.34) --
-	(260.87,184.71) --
-	(264.12,186.08) --
-	(267.36,187.44) --
-	(270.60,188.79) --
-	(273.85,190.13) --
-	(277.09,191.46) --
-	(280.34,192.78) --
-	(283.58,194.09);
+	(257.63,183.33) --
+	(260.87,184.70) --
+	(264.12,186.06) --
+	(267.36,187.41) --
+	(270.60,188.75) --
+	(273.85,190.08) --
+	(277.09,191.40) --
+	(280.34,192.72) --
+	(283.58,194.02);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] ( 27.31, 59.72) --
-	( 30.68, 53.90) --
-	( 23.95, 53.90) --
-	cycle;
-
-\path[fill=fillColor] ( 35.86, 62.59) --
-	( 39.22, 56.77) --
-	( 32.49, 56.77) --
-	cycle;
-
-\path[fill=fillColor] ( 44.40, 65.16) --
-	( 47.76, 59.33) --
-	( 41.03, 59.33) --
-	cycle;
-
-\path[fill=fillColor] ( 52.94, 68.11) --
-	( 56.30, 62.29) --
-	( 49.58, 62.29) --
-	cycle;
-
-\path[fill=fillColor] ( 61.48, 70.80) --
-	( 64.85, 64.98) --
-	( 58.12, 64.98) --
-	cycle;
-
-\path[fill=fillColor] ( 70.02, 73.35) --
-	( 73.39, 67.53) --
-	( 66.66, 67.53) --
-	cycle;
-
-\path[fill=fillColor] ( 78.57, 75.71) --
-	( 81.93, 69.89) --
-	( 75.20, 69.89) --
-	cycle;
-
-\path[fill=fillColor] ( 87.11, 77.99) --
-	( 90.47, 72.17) --
-	( 83.75, 72.17) --
-	cycle;
-
-\path[fill=fillColor] ( 95.65, 80.38) --
-	( 99.01, 74.56) --
-	( 92.29, 74.56) --
-	cycle;
-
-\path[fill=fillColor] (104.19, 82.73) --
-	(107.56, 76.90) --
-	(100.83, 76.90) --
-	cycle;
-
-\path[fill=fillColor] (112.74, 84.79) --
-	(116.10, 78.96) --
-	(109.37, 78.96) --
-	cycle;
-
-\path[fill=fillColor] (121.28, 86.71) --
-	(124.64, 80.88) --
-	(117.91, 80.88) --
-	cycle;
-
-\path[fill=fillColor] (129.82, 88.52) --
-	(133.18, 82.69) --
-	(126.46, 82.69) --
-	cycle;
-
-\path[fill=fillColor] (138.36, 90.39) --
-	(141.73, 84.57) --
-	(135.00, 84.57) --
+\path[fill=fillColor] ( 27.31, 59.60) --
+	( 30.68, 53.77) --
+	( 23.95, 53.77) --
+	cycle;
+
+\path[fill=fillColor] ( 35.86, 62.47) --
+	( 39.22, 56.65) --
+	( 32.49, 56.65) --
+	cycle;
+
+\path[fill=fillColor] ( 44.40, 65.07) --
+	( 47.76, 59.25) --
+	( 41.03, 59.25) --
+	cycle;
+
+\path[fill=fillColor] ( 52.94, 68.02) --
+	( 56.30, 62.19) --
+	( 49.58, 62.19) --
+	cycle;
+
+\path[fill=fillColor] ( 61.48, 70.77) --
+	( 64.85, 64.95) --
+	( 58.12, 64.95) --
+	cycle;
+
+\path[fill=fillColor] ( 70.02, 73.26) --
+	( 73.39, 67.44) --
+	( 66.66, 67.44) --
+	cycle;
+
+\path[fill=fillColor] ( 78.57, 75.65) --
+	( 81.93, 69.83) --
+	( 75.20, 69.83) --
+	cycle;
+
+\path[fill=fillColor] ( 87.11, 78.08) --
+	( 90.47, 72.25) --
+	( 83.75, 72.25) --
+	cycle;
+
+\path[fill=fillColor] ( 95.65, 80.50) --
+	( 99.01, 74.67) --
+	( 92.29, 74.67) --
+	cycle;
+
+\path[fill=fillColor] (104.19, 82.71) --
+	(107.56, 76.88) --
+	(100.83, 76.88) --
+	cycle;
+
+\path[fill=fillColor] (112.74, 84.81) --
+	(116.10, 78.99) --
+	(109.37, 78.99) --
+	cycle;
+
+\path[fill=fillColor] (121.28, 86.66) --
+	(124.64, 80.84) --
+	(117.91, 80.84) --
+	cycle;
+
+\path[fill=fillColor] (129.82, 88.60) --
+	(133.18, 82.78) --
+	(126.46, 82.78) --
+	cycle;
+
+\path[fill=fillColor] (138.36, 90.48) --
+	(141.73, 84.65) --
+	(135.00, 84.65) --
 	cycle;
@@
 \path[fill=fillColor] (146.90, 92.35) --
-	(150.27, 86.52) --
-	(143.54, 86.52) --
-	cycle;
-
-\path[fill=fillColor] (155.45, 94.05) --
-	(158.81, 88.22) --
-	(152.08, 88.22) --
-	cycle;
-
-\path[fill=fillColor] (163.99, 95.73) --
-	(167.35, 89.90) --
-	(160.63, 89.90) --
-	cycle;
-
-\path[fill=fillColor] (172.53, 97.38) --
-	(175.89, 91.55) --
-	(169.17, 91.55) --
-	cycle;
-
-\path[fill=fillColor] (181.07, 99.22) --
-	(184.44, 93.40) --
-	(177.71, 93.40) --
-	cycle;
-
-\path[fill=fillColor] (189.62,100.84) --
-	(192.98, 95.02) --
-	(186.25, 95.02) --
-	cycle;
-
-\path[fill=fillColor] (198.16,102.49) --
-	(201.52, 96.67) --
-	(194.79, 96.67) --
-	cycle;
-
-\path[fill=fillColor] (206.70,103.90) --
-	(210.06, 98.08) --
-	(203.34, 98.08) --
-	cycle;
-
-\path[fill=fillColor] (215.24,105.43) --
-	(218.61, 99.60) --
-	(211.88, 99.60) --
-	cycle;
-
-\path[fill=fillColor] (223.78,107.01) --
-	(227.15,101.18) --
-	(220.42,101.18) --
-	cycle;
-
-\path[fill=fillColor] (232.33,108.48) --
-	(235.69,102.65) --
-	(228.96,102.65) --
-	cycle;
-
-\path[fill=fillColor] (240.87,109.92) --
-	(244.23,104.10) --
-	(237.51,104.10) --
-	cycle;
-
-\path[fill=fillColor] (249.41,111.32) --
-	(252.77,105.49) --
-	(246.05,105.49) --
-	cycle;
-
-\path[fill=fillColor] (257.95,112.65) --
-	(261.32,106.82) --
-	(254.59,106.82) --
-	cycle;
-
-\path[fill=fillColor] (266.50,114.09) --
-	(269.86,108.26) --
-	(263.13,108.26) --
-	cycle;
-
-\path[fill=fillColor] (275.04,115.30) --
-	(278.40,109.48) --
-	(271.67,109.48) --
-	cycle;
-
-\path[fill=fillColor] (283.58,116.69) --
-	(286.94,110.86) --
-	(280.22,110.86) --
+	(150.27, 86.53) --
+	(143.54, 86.53) --
+	cycle;
+
+\path[fill=fillColor] (155.45, 94.13) --
+	(158.81, 88.30) --
+	(152.08, 88.30) --
+	cycle;
+
+\path[fill=fillColor] (163.99, 95.79) --
+	(167.35, 89.97) --
+	(160.63, 89.97) --
+	cycle;
+
+\path[fill=fillColor] (172.53, 97.50) --
+	(175.89, 91.67) --
+	(169.17, 91.67) --
+	cycle;
+
+\path[fill=fillColor] (181.07, 99.31) --
+	(184.44, 93.48) --
+	(177.71, 93.48) --
+	cycle;
+
+\path[fill=fillColor] (189.62,100.91) --
+	(192.98, 95.09) --
+	(186.25, 95.09) --
+	cycle;
+
+\path[fill=fillColor] (198.16,102.55) --
+	(201.52, 96.72) --
+	(194.79, 96.72) --
+	cycle;
+
+\path[fill=fillColor] (206.70,104.08) --
+	(210.06, 98.25) --
+	(203.34, 98.25) --
+	cycle;
+
+\path[fill=fillColor] (215.24,105.58) --
+	(218.61, 99.75) --
+	(211.88, 99.75) --
+	cycle;
+
+\path[fill=fillColor] (223.78,107.13) --
+	(227.15,101.30) --
+	(220.42,101.30) --
+	cycle;
+
+\path[fill=fillColor] (232.33,108.61) --
+	(235.69,102.78) --
+	(228.96,102.78) --
+	cycle;
+
+\path[fill=fillColor] (240.87,109.99) --
+	(244.23,104.16) --
+	(237.51,104.16) --
+	cycle;
+
+\path[fill=fillColor] (249.41,111.47) --
+	(252.77,105.64) --
+	(246.05,105.64) --
+	cycle;
+
+\path[fill=fillColor] (257.95,112.80) --
+	(261.32,106.97) --
+	(254.59,106.97) --
+	cycle;
+
+\path[fill=fillColor] (266.50,114.25) --
+	(269.86,108.43) --
+	(263.13,108.43) --
+	cycle;
+
+\path[fill=fillColor] (275.04,115.51) --
+	(278.40,109.68) --
+	(271.67,109.68) --
+	cycle;
+
+\path[fill=fillColor] (283.58,116.83) --
+	(286.94,111.01) --
+	(280.22,111.01) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 24.82, 53.26) --
-	( 29.81, 53.26) --
-	( 29.81, 58.26) --
-	( 24.82, 58.26) --
-	cycle;
-
-\path[fill=fillColor] ( 33.36, 57.87) --
-	( 38.35, 57.87) --
-	( 38.35, 62.86) --
-	( 33.36, 62.86) --
-	cycle;
-
-\path[fill=fillColor] ( 41.90, 62.08) --
-	( 46.90, 62.08) --
-	( 46.90, 67.07) --
-	( 41.90, 67.07) --
-	cycle;
-
-\path[fill=fillColor] ( 50.44, 66.89) --
-	( 55.44, 66.89) --
-	( 55.44, 71.88) --
-	( 50.44, 71.88) --
-	cycle;
-
-\path[fill=fillColor] ( 58.98, 71.24) --
-	( 63.98, 71.24) --
-	( 63.98, 76.24) --
-	( 58.98, 76.24) --
-	cycle;
-
-\path[fill=fillColor] ( 67.53, 75.45) --
-	( 72.52, 75.45) --
-	( 72.52, 80.44) --
-	( 67.53, 80.44) --
-	cycle;
-
-\path[fill=fillColor] ( 76.07, 79.40) --
-	( 81.06, 79.40) --
-	( 81.06, 84.39) --
-	( 76.07, 84.39) --
-	cycle;
-
-\path[fill=fillColor] ( 84.61, 83.31) --
-	( 89.61, 83.31) --
-	( 89.61, 88.30) --
-	( 84.61, 88.30) --
-	cycle;
-
-\path[fill=fillColor] ( 93.15, 87.27) --
-	( 98.15, 87.27) --
-	( 98.15, 92.27) --
-	( 93.15, 92.27) --
-	cycle;
-
-\path[fill=fillColor] (101.70, 91.22) --
-	(106.69, 91.22) --
-	(106.69, 96.22) --
-	(101.70, 96.22) --
-	cycle;
-
-\path[fill=fillColor] (110.24, 94.52) --
-	(115.23, 94.52) --
-	(115.23, 99.52) --
-	(110.24, 99.52) --
-	cycle;
-
-\path[fill=fillColor] (118.78, 97.88) --
-	(123.78, 97.88) --
-	(123.78,102.87) --
-	(118.78,102.87) --
-	cycle;
-
-\path[fill=fillColor] (127.32,100.97) --
-	(132.32,100.97) --
-	(132.32,105.96) --
-	(127.32,105.96) --
-	cycle;
-
-\path[fill=fillColor] (135.86,104.20) --
-	(140.86,104.20) --
-	(140.86,109.20) --
-	(135.86,109.20) --
-	cycle;
-
-\path[fill=fillColor] (144.41,107.50) --
-	(149.40,107.50) --
-	(149.40,112.49) --
-	(144.41,112.49) --
-	cycle;
-
-\path[fill=fillColor] (152.95,110.47) --
-	(157.94,110.47) --
-	(157.94,115.46) --
-	(152.95,115.46) --
-	cycle;
-
-\path[fill=fillColor] (161.49,113.31) --
-	(166.49,113.31) --
-	(166.49,118.31) --
-	(161.49,118.31) --
-	cycle;
-
-\path[fill=fillColor] (170.03,116.16) --
-	(175.03,116.16) --
-	(175.03,121.15) --
-	(170.03,121.15) --
-	cycle;
-
-\path[fill=fillColor] (178.58,119.44) --
-	(183.57,119.44) --
-	(183.57,124.44) --
-	(178.58,124.44) --
-	cycle;
-
-\path[fill=fillColor] (187.12,122.22) --
-	(192.11,122.22) --
-	(192.11,127.22) --
-	(187.12,127.22) --
-	cycle;
-
-\path[fill=fillColor] (195.66,125.20) --
-	(200.66,125.20) --
-	(200.66,130.19) --
-	(195.66,130.19) --
-	cycle;
-
-\path[fill=fillColor] (204.20,127.62) --
-	(209.20,127.62) --
-	(209.20,132.62) --
-	(204.20,132.62) --
-	cycle;
-
-\path[fill=fillColor] (212.74,130.39) --
-	(217.74,130.39) --
-	(217.74,135.38) --
-	(212.74,135.38) --
-	cycle;
-
-\path[fill=fillColor] (221.29,133.11) --
-	(226.28,133.11) --
-	(226.28,138.11) --
-	(221.29,138.11) --
-	cycle;
-
-\path[fill=fillColor] (229.83,135.65) --
-	(234.82,135.65) --
-	(234.82,140.64) --
-	(229.83,140.64) --
-	cycle;
-
-\path[fill=fillColor] (238.37,138.18) --
-	(243.37,138.18) --
-	(243.37,143.18) --
-	(238.37,143.18) --
-	cycle;
-
-\path[fill=fillColor] (246.91,140.83) --
-	(251.91,140.83) --
-	(251.91,145.82) --
-	(246.91,145.82) --
-	cycle;
-
-\path[fill=fillColor] (255.46,143.10) --
-	(260.45,143.10) --
-	(260.45,148.10) --
-	(255.46,148.10) --
-	cycle;
-
-\path[fill=fillColor] (264.00,145.63) --
-	(268.99,145.63) --
-	(268.99,150.63) --
-	(264.00,150.63) --
-	cycle;
-
-\path[fill=fillColor] (272.54,147.86) --
-	(277.54,147.86) --
-	(277.54,152.86) --
-	(272.54,152.86) --
-	cycle;
-
-\path[fill=fillColor] (281.08,150.27) --
-	(286.08,150.27) --
-	(286.08,155.27) --
-	(281.08,155.27) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78, 55.53) -- ( 30.85, 55.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31, 52.00) -- ( 27.31, 59.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32, 61.72) -- ( 39.39, 61.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86, 58.18) -- ( 35.86, 65.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87, 67.50) -- ( 47.93, 67.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40, 63.97) -- ( 44.40, 71.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41, 74.08) -- ( 56.47, 74.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94, 70.55) -- ( 52.94, 77.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95, 79.95) -- ( 65.01, 79.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48, 76.42) -- ( 61.48, 83.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49, 85.82) -- ( 73.56, 85.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02, 82.28) -- ( 70.02, 89.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03, 91.32) -- ( 82.10, 91.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57, 87.79) -- ( 78.57, 94.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58, 96.85) -- ( 90.64, 96.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11, 93.32) -- ( 87.11,100.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,102.37) -- ( 99.18,102.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 98.84) -- ( 95.65,105.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,107.95) -- (107.73,107.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,104.42) -- (104.19,111.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,112.40) -- (116.27,112.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,108.86) -- (112.74,115.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,117.27) -- (124.81,117.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,113.74) -- (121.28,120.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,121.67) -- (133.35,121.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,118.13) -- (129.82,125.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,126.30) -- (141.89,126.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,122.76) -- (138.36,129.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,131.03) -- (150.44,131.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,127.50) -- (146.90,134.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,135.37) -- (158.98,135.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,131.84) -- (155.45,138.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,139.39) -- (167.52,139.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,135.86) -- (163.99,142.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,143.52) -- (176.06,143.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,139.99) -- (172.53,147.05);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,148.36) -- (184.61,148.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,144.83) -- (181.07,151.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,152.40) -- (193.15,152.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,148.86) -- (189.62,155.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,156.84) -- (201.69,156.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,153.31) -- (198.16,160.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,160.37) -- (210.23,160.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,156.84) -- (206.70,163.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,164.46) -- (218.77,164.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,160.93) -- (215.24,168.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,168.49) -- (227.32,168.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,164.96) -- (223.78,172.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,172.17) -- (235.86,172.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,168.64) -- (232.33,175.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,175.87) -- (244.40,175.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,172.34) -- (240.87,179.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,180.09) -- (252.94,180.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,176.56) -- (249.41,183.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,183.35) -- (261.49,183.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,179.81) -- (257.95,186.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,187.13) -- (270.03,187.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,183.60) -- (266.50,190.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,190.53) -- (278.57,190.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,187.00) -- (275.04,194.06);
+\path[fill=fillColor] ( 24.82, 53.14) --
+	( 29.81, 53.14) --
+	( 29.81, 58.14) --
+	( 24.82, 58.14) --
+	cycle;
+
+\path[fill=fillColor] ( 33.36, 57.75) --
+	( 38.35, 57.75) --
+	( 38.35, 62.75) --
+	( 33.36, 62.75) --
+	cycle;
+
+\path[fill=fillColor] ( 41.90, 61.97) --
+	( 46.90, 61.97) --
+	( 46.90, 66.96) --
+	( 41.90, 66.96) --
+	cycle;
+
+\path[fill=fillColor] ( 50.44, 66.76) --
+	( 55.44, 66.76) --
+	( 55.44, 71.75) --
+	( 50.44, 71.75) --
+	cycle;
+
+\path[fill=fillColor] ( 58.98, 71.20) --
+	( 63.98, 71.20) --
+	( 63.98, 76.19) --
+	( 58.98, 76.19) --
+	cycle;
+
+\path[fill=fillColor] ( 67.53, 75.33) --
+	( 72.52, 75.33) --
+	( 72.52, 80.32) --
+	( 67.53, 80.32) --
+	cycle;
+
+\path[fill=fillColor] ( 76.07, 79.35) --
+	( 81.06, 79.35) --
+	( 81.06, 84.34) --
+	( 76.07, 84.34) --
+	cycle;
+
+\path[fill=fillColor] ( 84.61, 83.44) --
+	( 89.61, 83.44) --
+	( 89.61, 88.43) --
+	( 84.61, 88.43) --
+	cycle;
+
+\path[fill=fillColor] ( 93.15, 87.44) --
+	( 98.15, 87.44) --
+	( 98.15, 92.44) --
+	( 93.15, 92.44) --
+	cycle;
+
+\path[fill=fillColor] (101.70, 91.12) --
+	(106.69, 91.12) --
+	(106.69, 96.12) --
+	(101.70, 96.12) --
+	cycle;
+
+\path[fill=fillColor] (110.24, 94.51) --
+	(115.23, 94.51) --
+	(115.23, 99.50) --
+	(110.24, 99.50) --
+	cycle;
+
+\path[fill=fillColor] (118.78, 97.80) --
+	(123.78, 97.80) --
+	(123.78,102.79) --
+	(118.78,102.79) --
+	cycle;
+
+\path[fill=fillColor] (127.32,101.03) --
+	(132.32,101.03) --
+	(132.32,106.02) --
+	(127.32,106.02) --
+	cycle;
+
+\path[fill=fillColor] (135.86,104.29) --
+	(140.86,104.29) --
+	(140.86,109.28) --
+	(135.86,109.28) --
+	cycle;
+
+\path[fill=fillColor] (144.41,107.42) --
+	(149.40,107.42) --
+	(149.40,112.41) --
+	(144.41,112.41) --
+	cycle;
+
+\path[fill=fillColor] (152.95,110.55) --
+	(157.94,110.55) --
+	(157.94,115.55) --
+	(152.95,115.55) --
+	cycle;
+
+\path[fill=fillColor] (161.49,113.41) --
+	(166.49,113.41) --
+	(166.49,118.40) --
+	(161.49,118.40) --
+	cycle;
+
+\path[fill=fillColor] (170.03,116.27) --
+	(175.03,116.27) --
+	(175.03,121.26) --
+	(170.03,121.26) --
+	cycle;
+
+\path[fill=fillColor] (178.58,119.47) --
+	(183.57,119.47) --
+	(183.57,124.47) --
+	(178.58,124.47) --
+	cycle;
+
+\path[fill=fillColor] (187.12,122.28) --
+	(192.11,122.28) --
+	(192.11,127.28) --
+	(187.12,127.28) --
+	cycle;
+
+\path[fill=fillColor] (195.66,125.17) --
+	(200.66,125.17) --
+	(200.66,130.16) --
+	(195.66,130.16) --
+	cycle;
+
+\path[fill=fillColor] (204.20,127.80) --
+	(209.20,127.80) --
+	(209.20,132.80) --
+	(204.20,132.80) --
+	cycle;
+
+\path[fill=fillColor] (212.74,130.49) --
+	(217.74,130.49) --
+	(217.74,135.48) --
+	(212.74,135.48) --
+	cycle;
+
+\path[fill=fillColor] (221.29,133.19) --
+	(226.28,133.19) --
+	(226.28,138.18) --
+	(221.29,138.18) --
+	cycle;
+
+\path[fill=fillColor] (229.83,135.74) --
+	(234.82,135.74) --
+	(234.82,140.73) --
+	(229.83,140.73) --
+	cycle;
+
+\path[fill=fillColor] (238.37,138.17) --
+	(243.37,138.17) --
+	(243.37,143.16) --
+	(238.37,143.16) --
+	cycle;
+
+\path[fill=fillColor] (246.91,140.85) --
+	(251.91,140.85) --
+	(251.91,145.85) --
+	(246.91,145.85) --
+	cycle;
+
+\path[fill=fillColor] (255.46,143.24) --
+	(260.45,143.24) --
+	(260.45,148.23) --
+	(255.46,148.23) --
+	cycle;
+
+\path[fill=fillColor] (264.00,145.71) --
+	(268.99,145.71) --
+	(268.99,150.71) --
+	(264.00,150.71) --
+	cycle;
+
+\path[fill=fillColor] (272.54,147.90) --
+	(277.54,147.90) --
+	(277.54,152.89) --
+	(272.54,152.89) --
+	cycle;
+
+\path[fill=fillColor] (281.08,150.34) --
+	(286.08,150.34) --
+	(286.08,155.34) --
+	(281.08,155.34) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78, 55.41) -- ( 30.85, 55.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31, 51.87) -- ( 27.31, 58.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32, 61.62) -- ( 39.39, 61.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86, 58.09) -- ( 35.86, 65.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87, 67.34) -- ( 47.93, 67.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40, 63.81) -- ( 44.40, 70.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41, 73.88) -- ( 56.47, 73.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94, 70.35) -- ( 52.94, 77.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95, 79.89) -- ( 65.01, 79.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48, 76.36) -- ( 61.48, 83.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49, 85.65) -- ( 73.56, 85.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02, 82.12) -- ( 70.02, 89.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03, 91.28) -- ( 82.10, 91.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57, 87.75) -- ( 78.57, 94.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58, 97.06) -- ( 90.64, 97.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11, 93.53) -- ( 87.11,100.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,102.60) -- ( 99.18,102.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 99.07) -- ( 95.65,106.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,107.76) -- (107.73,107.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,104.23) -- (104.19,111.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,112.34) -- (116.27,112.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,108.81) -- (112.74,115.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,117.19) -- (124.81,117.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,113.66) -- (121.28,120.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,121.71) -- (133.35,121.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,118.17) -- (129.82,125.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,126.41) -- (141.89,126.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,122.88) -- (138.36,129.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,130.85) -- (150.44,130.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,127.32) -- (146.90,134.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,135.49) -- (158.98,135.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,131.96) -- (155.45,139.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,139.55) -- (167.52,139.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,136.02) -- (163.99,143.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,143.62) -- (176.06,143.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,140.09) -- (172.53,147.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,148.33) -- (184.61,148.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,144.80) -- (181.07,151.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,152.45) -- (193.15,152.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,148.92) -- (189.62,155.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,156.73) -- (201.69,156.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,153.19) -- (198.16,160.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,160.57) -- (210.23,160.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,157.04) -- (206.70,164.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,164.54) -- (218.77,164.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,161.01) -- (215.24,168.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,168.54) -- (227.32,168.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,165.01) -- (223.78,172.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,172.25) -- (235.86,172.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,168.71) -- (232.33,175.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,175.81) -- (244.40,175.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,172.28) -- (240.87,179.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,179.95) -- (252.94,179.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,176.42) -- (249.41,183.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,183.53) -- (261.49,183.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,179.99) -- (257.95,187.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,187.15) -- (270.03,187.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,183.62) -- (266.50,190.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,190.32) -- (278.57,190.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,186.78) -- (275.04,193.85);
 
@@
 
-\path[fill=fillColor] ( 27.31, 53.86) circle (  2.50);
-
-\path[fill=fillColor] ( 35.86, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 44.40, 55.01) circle (  2.50);
-
-\path[fill=fillColor] ( 52.94, 54.11) circle (  2.50);
-
-\path[fill=fillColor] ( 61.48, 55.47) circle (  2.50);
-
-\path[fill=fillColor] ( 70.02, 54.78) circle (  2.50);
-
-\path[fill=fillColor] ( 78.57, 54.81) circle (  2.50);
-
-\path[fill=fillColor] ( 87.11, 55.37) circle (  2.50);
-
-\path[fill=fillColor] ( 95.65, 54.67) circle (  2.50);
-
-\path[fill=fillColor] (104.19, 55.03) circle (  2.50);
-
-\path[fill=fillColor] (112.74, 54.66) circle (  2.50);
-
-\path[fill=fillColor] (121.28, 54.19) circle (  2.50);
-
-\path[fill=fillColor] (129.82, 54.27) circle (  2.50);
-
-\path[fill=fillColor] (138.36, 55.20) circle (  2.50);
-
-\path[fill=fillColor] (146.90, 54.61) circle (  2.50);
-
-\path[fill=fillColor] (155.45, 55.25) circle (  2.50);
-
-\path[fill=fillColor] (163.99, 55.30) circle (  2.50);
-
-\path[fill=fillColor] (172.53, 55.03) circle (  2.50);
-
-\path[fill=fillColor] (181.07, 54.88) circle (  2.50);
-
-\path[fill=fillColor] (189.62, 54.77) circle (  2.50);
-
-\path[fill=fillColor] (198.16, 54.88) circle (  2.50);
-
-\path[fill=fillColor] (206.70, 54.44) circle (  2.50);
-
-\path[fill=fillColor] (215.24, 54.97) circle (  2.50);
-
-\path[fill=fillColor] (223.78, 54.48) circle (  2.50);
-
-\path[fill=fillColor] (232.33, 54.54) circle (  2.50);
-
-\path[fill=fillColor] (240.87, 55.09) circle (  2.50);
-
-\path[fill=fillColor] (249.41, 55.20) circle (  2.50);
-
-\path[fill=fillColor] (257.95, 54.91) circle (  2.50);
-
-\path[fill=fillColor] (266.50, 55.15) circle (  2.50);
-
-\path[fill=fillColor] (275.04, 54.72) circle (  2.50);
-
-\path[fill=fillColor] (283.58, 54.55) circle (  2.50);
+\path[fill=fillColor] ( 27.31, 53.74) circle (  2.50);
+
+\path[fill=fillColor] ( 35.86, 54.86) circle (  2.50);
+
+\path[fill=fillColor] ( 44.40, 54.88) circle (  2.50);
+
+\path[fill=fillColor] ( 52.94, 53.99) circle (  2.50);
+
+\path[fill=fillColor] ( 61.48, 55.34) circle (  2.50);
+
+\path[fill=fillColor] ( 70.02, 54.65) circle (  2.50);
+
+\path[fill=fillColor] ( 78.57, 54.68) circle (  2.50);
+
+\path[fill=fillColor] ( 87.11, 55.24) circle (  2.50);
+
+\path[fill=fillColor] ( 95.65, 54.54) circle (  2.50);
+
+\path[fill=fillColor] (104.19, 54.90) circle (  2.50);
+
+\path[fill=fillColor] (112.74, 54.54) circle (  2.50);
+
+\path[fill=fillColor] (121.28, 54.06) circle (  2.50);
+
+\path[fill=fillColor] (129.82, 54.15) circle (  2.50);
+
+\path[fill=fillColor] (138.36, 55.07) circle (  2.50);
+
+\path[fill=fillColor] (146.90, 54.49) circle (  2.50);
+
+\path[fill=fillColor] (155.45, 55.12) circle (  2.50);
+
+\path[fill=fillColor] (163.99, 55.17) circle (  2.50);
+
+\path[fill=fillColor] (172.53, 54.90) circle (  2.50);
+
+\path[fill=fillColor] (181.07, 54.75) circle (  2.50);
+
+\path[fill=fillColor] (189.62, 54.64) circle (  2.50);
+
+\path[fill=fillColor] (198.16, 54.75) circle (  2.50);
+
+\path[fill=fillColor] (206.70, 54.31) circle (  2.50);
+
+\path[fill=fillColor] (215.24, 54.85) circle (  2.50);
+
+\path[fill=fillColor] (223.78, 54.36) circle (  2.50);
+
+\path[fill=fillColor] (232.33, 54.41) circle (  2.50);
+
+\path[fill=fillColor] (240.87, 54.96) circle (  2.50);
+
+\path[fill=fillColor] (249.41, 55.07) circle (  2.50);
+
+\path[fill=fillColor] (257.95, 54.79) circle (  2.50);
+
+\path[fill=fillColor] (266.50, 55.03) circle (  2.50);
+
+\path[fill=fillColor] (275.04, 54.59) circle (  2.50);
+
+\path[fill=fillColor] (283.58, 54.42) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 52.35) {5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,134.65) {6};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 52.22) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,134.09) {6};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 55.38) --
-	( 27.31, 55.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,137.68) --
-	( 27.31,137.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 55.25) --
+	( 27.31, 55.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,137.12) --
+	( 27.31,137.12);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24,141.29) --
-	(326.39,140.30) --
-	(329.55,139.33) --
-	(332.71,138.37) --
-	(335.87,137.43) --
-	(339.02,136.50) --
-	(342.18,135.60) --
-	(345.34,134.71) --
-	(348.49,133.83) --
-	(351.65,132.97) --
-	(354.81,132.13) --
-	(357.97,131.31) --
-	(361.12,130.51) --
-	(364.28,129.71) --
-	(367.44,128.94) --
-	(370.60,128.18) --
-	(373.75,127.44) --
-	(376.91,126.71) --
-	(380.07,126.00) --
-	(383.22,125.30) --
-	(386.38,124.63) --
-	(389.54,123.97) --
-	(392.70,123.33) --
-	(395.85,122.72) --
-	(399.01,122.12) --
-	(402.17,121.53) --
-	(405.32,120.96) --
-	(408.48,120.39) --
-	(411.64,119.84) --
-	(414.80,119.30) --
-	(417.95,118.78) --
-	(421.11,118.27) --
-	(424.27,117.79) --
-	(427.43,117.32) --
-	(430.58,116.87) --
-	(433.74,116.43) --
-	(436.90,115.99) --
-	(440.05,115.56) --
-	(443.21,115.13) --
-	(446.37,114.70) --
-	(449.53,114.27) --
-	(452.68,113.85) --
-	(455.84,113.44) --
-	(459.00,113.04) --
-	(462.16,112.65) --
-	(465.31,112.27) --
-	(468.47,111.89) --
-	(471.63,111.52) --
-	(474.78,111.14) --
-	(477.94,110.78) --
-	(481.10,110.41) --
-	(484.26,110.04) --
-	(487.41,109.68) --
-	(490.57,109.32) --
-	(493.73,108.97) --
-	(496.89,108.62) --
-	(500.04,108.28) --
-	(503.20,107.94) --
-	(506.36,107.61) --
-	(509.51,107.28) --
-	(512.67,106.96) --
-	(515.83,106.63) --
-	(518.99,106.32) --
-	(522.14,106.01) --
-	(525.30,105.70) --
-	(528.46,105.39) --
-	(531.62,105.09) --
-	(534.77,104.80) --
-	(537.93,104.51) --
-	(541.09,104.23) --
-	(544.24,103.94) --
-	(547.40,103.67) --
-	(550.56,103.40) --
-	(553.72,103.13) --
-	(556.87,102.86) --
-	(560.03,102.60) --
-	(563.19,102.35) --
-	(566.35,102.10) --
-	(569.50,101.85) --
-	(572.66,101.61);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24,142.26) --
+	(326.39,141.25) --
+	(329.55,140.26) --
+	(332.71,139.28) --
+	(335.87,138.32) --
+	(339.02,137.38) --
+	(342.18,136.45) --
+	(345.34,135.55) --
+	(348.49,134.65) --
+	(351.65,133.78) --
+	(354.81,132.92) --
+	(357.97,132.09) --
+	(361.12,131.26) --
+	(364.28,130.46) --
+	(367.44,129.67) --
+	(370.60,128.90) --
+	(373.75,128.14) --
+	(376.91,127.40) --
+	(380.07,126.68) --
+	(383.22,125.97) --
+	(386.38,125.28) --
+	(389.54,124.61) --
+	(392.70,123.97) --
+	(395.85,123.34) --
+	(399.01,122.73) --
+	(402.17,122.13) --
+	(405.32,121.55) --
+	(408.48,120.98) --
+	(411.64,120.42) --
+	(414.80,119.87) --
+	(417.95,119.34) --
+	(421.11,118.83) --
+	(424.27,118.34) --
+	(427.43,117.87) --
+	(430.58,117.41) --
+	(433.74,116.96) --
+	(436.90,116.52) --
+	(440.05,116.09) --
+	(443.21,115.65) --
+	(446.37,115.22) --
+	(449.53,114.78) --
+	(452.68,114.36) --
+	(455.84,113.94) --
+	(459.00,113.54) --
+	(462.16,113.14) --
+	(465.31,112.75) --
+	(468.47,112.37) --
+	(471.63,111.99) --
+	(474.78,111.61) --
+	(477.94,111.24) --
+	(481.10,110.87) --
+	(484.26,110.49) --
+	(487.41,110.13) --
+	(490.57,109.77) --
+	(493.73,109.41) --
+	(496.89,109.06) --
+	(500.04,108.71) --
+	(503.20,108.37) --
+	(506.36,108.03) --
+	(509.51,107.70) --
+	(512.67,107.37) --
+	(515.83,107.04) --
+	(518.99,106.72) --
+	(522.14,106.40) --
+	(525.30,106.09) --
+	(528.46,105.78) --
+	(531.62,105.48) --
+	(534.77,105.18) --
+	(537.93,104.88) --
+	(541.09,104.59) --
+	(544.24,104.31) --
+	(547.40,104.03) --
+	(550.56,103.75) --
+	(553.72,103.48) --
+	(556.87,103.21) --
+	(560.03,102.94) --
+	(563.19,102.69) --
+	(566.35,102.43) --
+	(569.50,102.18) --
+	(572.66,101.93);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,185.67) --
-	(326.39,183.76) --
-	(329.55,181.89) --
-	(332.71,180.05) --
-	(335.87,178.24) --
-	(339.02,176.47) --
-	(342.18,174.73) --
-	(345.34,173.02) --
-	(348.49,171.35) --
-	(351.65,169.71) --
-	(354.81,168.11) --
-	(357.97,166.55) --
-	(361.12,165.01) --
-	(364.28,163.51) --
-	(367.44,162.05) --
-	(370.60,160.61) --
-	(373.75,159.21) --
-	(376.91,157.84) --
-	(380.07,156.49) --
-	(383.22,155.18) --
-	(386.38,153.92) --
-	(389.54,152.70) --
-	(392.70,151.52) --
-	(395.85,150.37) --
-	(399.01,149.26) --
-	(402.17,148.17) --
-	(405.32,147.12) --
-	(408.48,146.09) --
-	(411.64,145.08) --
-	(414.80,144.08) --
-	(417.95,143.12) --
-	(421.11,142.21) --
-	(424.27,141.33) --
-	(427.43,140.48) --
-	(430.58,139.67) --
-	(433.74,138.87) --
-	(436.90,138.09) --
-	(440.05,137.32) --
-	(443.21,136.56) --
-	(446.37,135.79) --
-	(449.53,135.02) --
-	(452.68,134.27) --
-	(455.84,133.54) --
-	(459.00,132.83) --
-	(462.16,132.14) --
-	(465.31,131.46) --
-	(468.47,130.80) --
-	(471.63,130.14) --
-	(474.78,129.49) --
-	(477.94,128.85) --
-	(481.10,128.20) --
-	(484.26,127.56) --
-	(487.41,126.93) --
-	(490.57,126.31) --
-	(493.73,125.70) --
-	(496.89,125.11) --
-	(500.04,124.52) --
-	(503.20,123.94) --
-	(506.36,123.36) --
-	(509.51,122.80) --
-	(512.67,122.24) --
-	(515.83,121.69) --
-	(518.99,121.15) --
-	(522.14,120.61) --
-	(525.30,120.09) --
-	(528.46,119.58) --
-	(531.62,119.07) --
-	(534.77,118.57) --
-	(537.93,118.08) --
-	(541.09,117.60) --
-	(544.24,117.13) --
-	(547.40,116.67) --
-	(550.56,116.22) --
-	(553.72,115.77) --
-	(556.87,115.33) --
-	(560.03,114.91) --
-	(563.19,114.49) --
-	(566.35,114.07) --
-	(569.50,113.67) --
-	(572.66,113.28);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,186.85) --
+	(326.39,184.91) --
+	(329.55,183.00) --
+	(332.71,181.13) --
+	(335.87,179.29) --
+	(339.02,177.48) --
+	(342.18,175.71) --
+	(345.34,173.98) --
+	(348.49,172.28) --
+	(351.65,170.62) --
+	(354.81,168.99) --
+	(357.97,167.40) --
+	(361.12,165.84) --
+	(364.28,164.32) --
+	(367.44,162.83) --
+	(370.60,161.37) --
+	(373.75,159.95) --
+	(376.91,158.56) --
+	(380.07,157.20) --
+	(383.22,155.87) --
+	(386.38,154.59) --
+	(389.54,153.35) --
+	(392.70,152.15) --
+	(395.85,150.99) --
+	(399.01,149.87) --
+	(402.17,148.77) --
+	(405.32,147.71) --
+	(408.48,146.66) --
+	(411.64,145.64) --
+	(414.80,144.64) --
+	(417.95,143.67) --
+	(421.11,142.74) --
+	(424.27,141.86) --
+	(427.43,141.01) --
+	(430.58,140.19) --
+	(433.74,139.39) --
+	(436.90,138.60) --
+	(440.05,137.83) --
+	(443.21,137.06) --
+	(446.37,136.28) --
+	(449.53,135.51) --
+	(452.68,134.75) --
+	(455.84,134.01) --
+	(459.00,133.30) --
+	(462.16,132.60) --
+	(465.31,131.92) --
+	(468.47,131.24) --
+	(471.63,130.58) --
+	(474.78,129.92) --
+	(477.94,129.27) --
+	(481.10,128.62) --
+	(484.26,127.97) --
+	(487.41,127.33) --
+	(490.57,126.70) --
+	(493.73,126.09) --
+	(496.89,125.48) --
+	(500.04,124.89) --
+	(503.20,124.30) --
+	(506.36,123.72) --
+	(509.51,123.14) --
+	(512.67,122.58) --
+	(515.83,122.02) --
+	(518.99,121.47) --
+	(522.14,120.93) --
+	(525.30,120.40) --
+	(528.46,119.87) --
+	(531.62,119.36) --
+	(534.77,118.86) --
+	(537.93,118.36) --
+	(541.09,117.87) --
+	(544.24,117.39) --
+	(547.40,116.92) --
+	(550.56,116.46) --
+	(553.72,116.00) --
+	(556.87,115.56) --
+	(560.03,115.12) --
+	(563.19,114.69) --
+	(566.35,114.27) --
+	(569.50,113.86) --
+	(572.66,113.46);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (364.81,191.74) --
-	(367.44,190.07) --
-	(370.07,188.42) --
-	(372.70,186.81) --
-	(375.33,185.22) --
-	(377.96,183.67) --
-	(380.59,182.13) --
-	(383.22,180.63) --
-	(385.86,179.15) --
-	(388.49,177.70) --
-	(391.12,176.27) --
-	(393.75,174.87) --
-	(396.38,173.50) --
-	(399.01,172.16) --
-	(401.64,170.85) --
-	(404.27,169.56) --
-	(406.90,168.29) --
-	(409.53,167.05) --
-	(412.17,165.83) --
-	(414.80,164.63) --
-	(417.43,163.47) --
-	(420.06,162.34) --
-	(422.69,161.26) --
-	(425.32,160.20) --
-	(427.95,159.18) --
-	(430.58,158.17) --
-	(433.21,157.19) --
-	(435.85,156.21) --
-	(438.48,155.25) --
-	(441.11,154.29) --
-	(443.74,153.36) --
-	(446.37,152.46) --
-	(449.00,151.59) --
-	(451.63,150.73) --
-	(454.26,149.89) --
-	(456.89,149.05) --
-	(459.52,148.23) --
-	(462.16,147.40) --
-	(464.79,146.58) --
-	(467.42,145.76) --
-	(470.05,144.95) --
-	(472.68,144.16) --
-	(475.31,143.38) --
-	(477.94,142.60) --
-	(480.57,141.84) --
-	(483.20,141.09) --
-	(485.84,140.34) --
-	(488.47,139.61) --
-	(491.10,138.89) --
-	(493.73,138.18) --
-	(496.36,137.48) --
-	(498.99,136.79) --
-	(501.62,136.11) --
-	(504.25,135.44) --
-	(506.88,134.78) --
-	(509.51,134.14) --
-	(512.15,133.50) --
-	(514.78,132.87) --
-	(517.41,132.25) --
-	(520.04,131.64) --
-	(522.67,131.03) --
-	(525.30,130.43) --
-	(527.93,129.84) --
-	(530.56,129.25) --
-	(533.19,128.68) --
-	(535.83,128.11) --
-	(538.46,127.56) --
-	(541.09,127.01) --
-	(543.72,126.47) --
-	(546.35,125.94) --
-	(548.98,125.42) --
-	(551.61,124.90) --
-	(554.24,124.39) --
-	(556.87,123.90) --
-	(559.50,123.41) --
-	(562.14,122.93) --
-	(564.77,122.45) --
-	(567.40,121.99) --
-	(570.03,121.53) --
-	(572.66,121.08);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (364.81,192.52) --
+	(367.44,190.83) --
+	(370.07,189.17) --
+	(372.70,187.54) --
+	(375.33,185.94) --
+	(377.96,184.36) --
+	(380.59,182.82) --
+	(383.22,181.30) --
+	(385.86,179.80) --
+	(388.49,178.34) --
+	(391.12,176.90) --
+	(393.75,175.49) --
+	(396.38,174.11) --
+	(399.01,172.76) --
+	(401.64,171.43) --
+	(404.27,170.13) --
+	(406.90,168.86) --
+	(409.53,167.61) --
+	(412.17,166.38) --
+	(414.80,165.18) --
+	(417.43,164.00) --
+	(420.06,162.88) --
+	(422.69,161.79) --
+	(425.32,160.73) --
+	(427.95,159.70) --
+	(430.58,158.69) --
+	(433.21,157.70) --
+	(435.85,156.73) --
+	(438.48,155.76) --
+	(441.11,154.80) --
+	(443.74,153.86) --
+	(446.37,152.96) --
+	(449.00,152.08) --
+	(451.63,151.21) --
+	(454.26,150.37) --
+	(456.89,149.53) --
+	(459.52,148.70) --
+	(462.16,147.87) --
+	(464.79,147.03) --
+	(467.42,146.20) --
+	(470.05,145.39) --
+	(472.68,144.58) --
+	(475.31,143.79) --
+	(477.94,143.00) --
+	(480.57,142.23) --
+	(483.20,141.46) --
+	(485.84,140.71) --
+	(488.47,139.96) --
+	(491.10,139.22) --
+	(493.73,138.50) --
+	(496.36,137.79) --
+	(498.99,137.08) --
+	(501.62,136.40) --
+	(504.25,135.72) --
+	(506.88,135.06) --
+	(509.51,134.41) --
+	(512.15,133.76) --
+	(514.78,133.13) --
+	(517.41,132.50) --
+	(520.04,131.88) --
+	(522.67,131.26) --
+	(525.30,130.65) --
+	(527.93,130.05) --
+	(530.56,129.46) --
+	(533.19,128.87) --
+	(535.83,128.30) --
+	(538.46,127.73) --
+	(541.09,127.17) --
+	(543.72,126.62) --
+	(546.35,126.08) --
+	(548.98,125.55) --
+	(551.61,125.02) --
+	(554.24,124.51) --
+	(556.87,124.00) --
+	(559.50,123.49) --
+	(562.14,123.00) --
+	(564.77,122.52) --
+	(567.40,122.04) --
+	(570.03,121.57) --
+	(572.66,121.12);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] (323.24,145.42) --
-	(326.60,139.59) --
-	(319.87,139.59) --
-	cycle;
-
-\path[fill=fillColor] (331.55,142.62) --
-	(334.91,136.79) --
-	(328.19,136.79) --
-	cycle;
-
-\path[fill=fillColor] (339.86,140.20) --
-	(343.23,134.37) --
-	(336.50,134.37) --
-	cycle;
-
-\path[fill=fillColor] (348.18,137.66) --
-	(351.54,131.83) --
-	(344.81,131.83) --
-	cycle;
-
-\path[fill=fillColor] (356.49,135.29) --
-	(359.86,129.47) --
-	(353.13,129.47) --
-	cycle;
-
-\path[fill=fillColor] (364.81,133.27) --
-	(368.17,127.44) --
-	(361.44,127.44) --
-	cycle;
-
-\path[fill=fillColor] (373.12,131.42) --
-	(376.48,125.59) --
-	(369.76,125.59) --
-	cycle;
-
-\path[fill=fillColor] (381.44,129.62) --
-	(384.80,123.79) --
-	(378.07,123.79) --
-	cycle;
-
-\path[fill=fillColor] (389.75,127.76) --
-	(393.11,121.93) --
-	(386.39,121.93) --
-	cycle;
-
-\path[fill=fillColor] (398.06,125.95) --
-	(401.43,120.13) --
-	(394.70,120.13) --
-	cycle;
-
-\path[fill=fillColor] (406.38,124.42) --
-	(409.74,118.60) --
-	(403.01,118.60) --
-	cycle;
-
-\path[fill=fillColor] (414.69,123.14) --
-	(418.06,117.32) --
-	(411.33,117.32) --
-	cycle;
-
-\path[fill=fillColor] (423.01,121.89) --
-	(426.37,116.06) --
-	(419.64,116.06) --
-	cycle;
-
-\path[fill=fillColor] (431.32,120.75) --
-	(434.68,114.92) --
-	(427.96,114.92) --
-	cycle;
-
-\path[fill=fillColor] (439.63,119.48) --
-	(443.00,113.66) --
-	(436.27,113.66) --
-	cycle;
-
-\path[fill=fillColor] (447.95,118.47) --
-	(451.31,112.64) --
-	(444.58,112.64) --
-	cycle;
-
-\path[fill=fillColor] (456.26,117.35) --
-	(459.63,111.52) --
-	(452.90,111.52) --
-	cycle;
-
-\path[fill=fillColor] (464.58,116.47) --
-	(467.94,110.64) --
-	(461.21,110.64) --
-	cycle;
-
-\path[fill=fillColor] (472.89,115.21) --
-	(476.25,109.39) --
-	(469.53,109.39) --
-	cycle;
-
-\path[fill=fillColor] (481.20,114.19) --
-	(484.57,108.37) --
-	(477.84,108.37) --
-	cycle;
-
-\path[fill=fillColor] (489.52,113.29) --
-	(492.88,107.46) --
-	(486.15,107.46) --
-	cycle;
-
-\path[fill=fillColor] (497.83,112.38) --
-	(501.20,106.55) --
-	(494.47,106.55) --
-	cycle;
-
-\path[fill=fillColor] (506.15,111.57) --
-	(509.51,105.74) --
-	(502.78,105.74) --
-	cycle;
-
-\path[fill=fillColor] (514.46,110.65) --
-	(517.82,104.82) --
-	(511.10,104.82) --
-	cycle;
-
-\path[fill=fillColor] (522.78,109.83) --
-	(526.14,104.01) --
-	(519.41,104.01) --
-	cycle;
-
-\path[fill=fillColor] (531.09,109.08) --
-	(534.45,103.25) --
-	(527.73,103.25) --
-	cycle;
-
-\path[fill=fillColor] (539.40,108.38) --
-	(542.77,102.55) --
-	(536.04,102.55) --
-	cycle;
-
-\path[fill=fillColor] (547.72,107.52) --
-	(551.08,101.70) --
-	(544.35,101.70) --
-	cycle;
-
-\path[fill=fillColor] (556.03,106.78) --
-	(559.40,100.96) --
-	(552.67,100.96) --
-	cycle;
-
-\path[fill=fillColor] (564.35,106.17) --
-	(567.71,100.34) --
-	(560.98,100.34) --
-	cycle;
-
-\path[fill=fillColor] (572.66,105.44) --
-	(576.02, 99.61) --
-	(569.30, 99.61) --
+\path[fill=fillColor] (323.24,146.40) --
+	(326.60,140.57) --
+	(319.87,140.57) --
+	cycle;
+
+\path[fill=fillColor] (331.55,143.56) --
+	(334.91,137.74) --
+	(328.19,137.74) --
+	cycle;
+
+\path[fill=fillColor] (339.86,141.07) --
+	(343.23,135.25) --
+	(336.50,135.25) --
+	cycle;
+
+\path[fill=fillColor] (348.18,138.44) --
+	(351.54,132.61) --
+	(344.81,132.61) --
+	cycle;
+
+\path[fill=fillColor] (356.49,136.06) --
+	(359.86,130.23) --
+	(353.13,130.23) --
+	cycle;
+
+\path[fill=fillColor] (364.81,134.02) --
+	(368.17,128.19) --
+	(361.44,128.19) --
+	cycle;
+
+\path[fill=fillColor] (373.12,132.12) --
+	(376.48,126.29) --
+	(369.76,126.29) --
+	cycle;
+
+\path[fill=fillColor] (381.44,130.29) --
+	(384.80,124.46) --
+	(378.07,124.46) --
+	cycle;
+
+\path[fill=fillColor] (389.75,128.36) --
+	(393.11,122.53) --
+	(386.39,122.53) --
+	cycle;
+
+\path[fill=fillColor] (398.06,126.62) --
+	(401.43,120.79) --
+	(394.70,120.79) --
+	cycle;
+
+\path[fill=fillColor] (406.38,125.06) --
+	(409.74,119.23) --
+	(403.01,119.23) --
+	cycle;
+
+\path[fill=fillColor] (414.69,123.72) --
+	(418.06,117.89) --
+	(411.33,117.89) --
+	cycle;
+
+\path[fill=fillColor] (423.01,122.40) --
+	(426.37,116.58) --
+	(419.64,116.58) --
+	cycle;
+
+\path[fill=fillColor] (431.32,121.22) --
+	(434.68,115.39) --
+	(427.96,115.39) --
+	cycle;
+
+\path[fill=fillColor] (439.63,120.06) --
+	(443.00,114.23) --
+	(436.27,114.23) --
+	cycle;
+
+\path[fill=fillColor] (447.95,118.96) --
+	(451.31,113.14) --
+	(444.58,113.14) --
+	cycle;
+
+\path[fill=fillColor] (456.26,117.95) --
+	(459.63,112.12) --
+	(452.90,112.12) --
+	cycle;
+
+\path[fill=fillColor] (464.58,116.87) --
+	(467.94,111.05) --
+	(461.21,111.05) --
+	cycle;
+
+\path[fill=fillColor] (472.89,115.69) --
+	(476.25,109.87) --
+	(469.53,109.87) --
+	cycle;
+
+\path[fill=fillColor] (481.20,114.67) --
+	(484.57,108.84) --
+	(477.84,108.84) --
+	cycle;
+
+\path[fill=fillColor] (489.52,113.75) --
+	(492.88,107.92) --
+	(486.15,107.92) --
+	cycle;
+
+\path[fill=fillColor] (497.83,112.81) --
+	(501.20,106.98) --
+	(494.47,106.98) --
+	cycle;
+
+\path[fill=fillColor] (506.15,111.96) --
+	(509.51,106.13) --
+	(502.78,106.13) --
+	cycle;
+
+\path[fill=fillColor] (514.46,111.02) --
+	(517.82,105.19) --
+	(511.10,105.19) --
+	cycle;
+
+\path[fill=fillColor] (522.78,110.24) --
+	(526.14,104.41) --
+	(519.41,104.41) --
+	cycle;
+
+\path[fill=fillColor] (531.09,109.50) --
+	(534.45,103.67) --
+	(527.73,103.67) --
+	cycle;
+
+\path[fill=fillColor] (539.40,108.72) --
+	(542.77,102.89) --
+	(536.04,102.89) --
+	cycle;
+
+\path[fill=fillColor] (547.72,107.92) --
+	(551.08,102.09) --
+	(544.35,102.09) --
+	cycle;
+
+\path[fill=fillColor] (556.03,107.13) --
+	(559.40,101.31) --
+	(552.67,101.31) --
+	cycle;
+
+\path[fill=fillColor] (564.35,106.48) --
+	(567.71,100.65) --
+	(560.98,100.65) --
+	cycle;
+
+\path[fill=fillColor] (572.66,105.76) --
+	(576.02, 99.93) --
+	(569.30, 99.93) --
 	cycle;
@@
 
-\path[fill=fillColor] (320.74,183.71) --
-	(325.73,183.71) --
-	(325.73,188.71) --
-	(320.74,188.71) --
-	cycle;
-
-\path[fill=fillColor] (329.05,178.25) --
-	(334.05,178.25) --
-	(334.05,183.24) --
-	(329.05,183.24) --
-	cycle;
-
-\path[fill=fillColor] (337.37,173.63) --
-	(342.36,173.63) --
-	(342.36,178.62) --
-	(337.37,178.62) --
-	cycle;
-
-\path[fill=fillColor] (345.68,168.76) --
-	(350.68,168.76) --
-	(350.68,173.76) --
-	(345.68,173.76) --
-	cycle;
-
-\path[fill=fillColor] (353.99,164.12) --
-	(358.99,164.12) --
-	(358.99,169.12) --
-	(353.99,169.12) --
-	cycle;
-
-\path[fill=fillColor] (362.31,160.33) --
-	(367.30,160.33) --
-	(367.30,165.33) --
-	(362.31,165.33) --
-	cycle;
-
-\path[fill=fillColor] (370.62,156.78) --
-	(375.62,156.78) --
-	(375.62,161.77) --
-	(370.62,161.77) --
-	cycle;
-
-\path[fill=fillColor] (378.94,153.43) --
-	(383.93,153.43) --
-	(383.93,158.43) --
-	(378.94,158.43) --
-	cycle;
-
-\path[fill=fillColor] (387.25,149.99) --
-	(392.25,149.99) --
-	(392.25,154.99) --
-	(387.25,154.99) --
-	cycle;
-
-\path[fill=fillColor] (395.57,146.71) --
-	(400.56,146.71) --
-	(400.56,151.71) --
-	(395.57,151.71) --
-	cycle;
-
-\path[fill=fillColor] (403.88,143.82) --
-	(408.88,143.82) --
-	(408.88,148.82) --
-	(403.88,148.82) --
-	cycle;
-
-\path[fill=fillColor] (412.19,141.55) --
-	(417.19,141.55) --
-	(417.19,146.55) --
-	(412.19,146.55) --
-	cycle;
-
-\path[fill=fillColor] (420.51,139.32) --
-	(425.50,139.32) --
-	(425.50,144.31) --
-	(420.51,144.31) --
-	cycle;
-
-\path[fill=fillColor] (428.82,137.17) --
-	(433.82,137.17) --
-	(433.82,142.17) --
-	(428.82,142.17) --
-	cycle;
-
-\path[fill=fillColor] (437.14,134.85) --
-	(442.13,134.85) --
-	(442.13,139.85) --
-	(437.14,139.85) --
-	cycle;
-
-\path[fill=fillColor] (445.45,133.06) --
-	(450.45,133.06) --
-	(450.45,138.05) --
-	(445.45,138.05) --
-	cycle;
-
-\path[fill=fillColor] (453.76,131.12) --
-	(458.76,131.12) --
-	(458.76,136.11) --
-	(453.76,136.11) --
-	cycle;
-
-\path[fill=fillColor] (462.08,129.46) --
-	(467.07,129.46) --
-	(467.07,134.45) --
-	(462.08,134.45) --
-	cycle;
-
-\path[fill=fillColor] (470.39,127.34) --
-	(475.39,127.34) --
-	(475.39,132.34) --
-	(470.39,132.34) --
-	cycle;
-
-\path[fill=fillColor] (478.71,125.54) --
-	(483.70,125.54) --
-	(483.70,130.54) --
-	(478.71,130.54) --
-	cycle;
-
-\path[fill=fillColor] (487.02,123.98) --
-	(492.02,123.98) --
-	(492.02,128.97) --
-	(487.02,128.97) --
-	cycle;
-
-\path[fill=fillColor] (495.34,122.45) --
-	(500.33,122.45) --
-	(500.33,127.44) --
-	(495.34,127.44) --
-	cycle;
-
-\path[fill=fillColor] (503.65,120.96) --
-	(508.64,120.96) --
-	(508.64,125.95) --
-	(503.65,125.95) --
-	cycle;
-
-\path[fill=fillColor] (511.96,119.41) --
-	(516.96,119.41) --
-	(516.96,124.40) --
-	(511.96,124.40) --
-	cycle;
-
-\path[fill=fillColor] (520.28,118.05) --
-	(525.27,118.05) --
-	(525.27,123.05) --
-	(520.28,123.05) --
-	cycle;
-
-\path[fill=fillColor] (528.59,116.70) --
-	(533.59,116.70) --
-	(533.59,121.70) --
-	(528.59,121.70) --
-	cycle;
-
-\path[fill=fillColor] (536.91,115.61) --
-	(541.90,115.61) --
-	(541.90,120.60) --
-	(536.91,120.60) --
-	cycle;
-
-\path[fill=fillColor] (545.22,114.22) --
-	(550.22,114.22) --
-	(550.22,119.22) --
-	(545.22,119.22) --
-	cycle;
-
-\path[fill=fillColor] (553.53,112.86) --
-	(558.53,112.86) --
-	(558.53,117.86) --
-	(553.53,117.86) --
-	cycle;
-
-\path[fill=fillColor] (561.85,111.89) --
-	(566.84,111.89) --
-	(566.84,116.88) --
-	(561.85,116.88) --
-	cycle;
-
-\path[fill=fillColor] (570.16,110.62) --
-	(575.16,110.62) --
-	(575.16,115.62) --
-	(570.16,115.62) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,192.11) -- (368.34,192.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,188.58) -- (364.81,195.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,186.73) -- (376.65,186.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,183.20) -- (373.12,190.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,181.78) -- (384.97,181.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,178.25) -- (381.44,185.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,176.74) -- (393.28,176.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,173.21) -- (389.75,180.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,171.94) -- (401.60,171.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,168.41) -- (398.06,175.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,167.61) -- (409.91,167.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,164.08) -- (406.38,171.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,164.39) -- (418.22,164.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,160.86) -- (414.69,167.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,161.21) -- (426.54,161.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,157.67) -- (423.01,164.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,157.99) -- (434.85,157.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,154.46) -- (431.32,161.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,154.70) -- (443.17,154.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,151.16) -- (439.63,158.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,152.12) -- (451.48,152.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,148.59) -- (447.95,155.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,149.36) -- (459.79,149.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,145.83) -- (456.26,152.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,146.94) -- (468.11,146.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,143.40) -- (464.58,150.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,144.00) -- (476.42,144.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,140.47) -- (472.89,147.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,141.47) -- (484.74,141.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,137.94) -- (481.20,145.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,139.29) -- (493.05,139.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,135.76) -- (489.52,142.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,137.22) -- (501.36,137.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,133.69) -- (497.83,140.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,134.96) -- (509.68,134.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,131.43) -- (506.15,138.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,132.89) -- (517.99,132.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,129.36) -- (514.46,136.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,131.00) -- (526.31,131.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,127.46) -- (522.78,134.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,129.08) -- (534.62,129.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,125.55) -- (531.09,132.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,127.75) -- (542.94,127.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,124.22) -- (539.40,131.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,125.86) -- (551.25,125.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72,122.33) -- (547.72,129.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,123.89) -- (559.56,123.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03,120.36) -- (556.03,127.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,122.63) -- (567.88,122.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35,119.09) -- (564.35,126.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,120.90) -- (576.19,120.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,117.37) -- (572.66,124.44);
+\path[fill=fillColor] (320.74,184.90) --
+	(325.73,184.90) --
+	(325.73,189.89) --
+	(320.74,189.89) --
+	cycle;
+
+\path[fill=fillColor] (329.05,179.38) --
+	(334.05,179.38) --
+	(334.05,184.38) --
+	(329.05,184.38) --
+	cycle;
+
+\path[fill=fillColor] (337.37,174.63) --
+	(342.36,174.63) --
+	(342.36,179.62) --
+	(337.37,179.62) --
+	cycle;
+
+\path[fill=fillColor] (345.68,169.62) --
+	(350.68,169.62) --
+	(350.68,174.62) --
+	(345.68,174.62) --
+	cycle;
+
+\path[fill=fillColor] (353.99,164.98) --
+	(358.99,164.98) --
+	(358.99,169.97) --
+	(353.99,169.97) --
+	cycle;
+
+\path[fill=fillColor] (362.31,161.16) --
+	(367.30,161.16) --
+	(367.30,166.16) --
+	(362.31,166.16) --
+	cycle;
+
+\path[fill=fillColor] (370.62,157.55) --
+	(375.62,157.55) --
+	(375.62,162.54) --
+	(370.62,162.54) --
+	cycle;
+
+\path[fill=fillColor] (378.94,154.05) --
+	(383.93,154.05) --
+	(383.93,159.04) --
+	(378.94,159.04) --
+	cycle;
+
+\path[fill=fillColor] (387.25,150.58) --
+	(392.25,150.58) --
+	(392.25,155.57) --
+	(387.25,155.57) --
+	cycle;
+
+\path[fill=fillColor] (395.57,147.37) --
+	(400.56,147.37) --
+	(400.56,152.36) --
+	(395.57,152.36) --
+	cycle;
+
+\path[fill=fillColor] (403.88,144.46) --
+	(408.88,144.46) --
+	(408.88,149.46) --
+	(403.88,149.46) --
+	cycle;
+
+\path[fill=fillColor] (412.19,142.16) --
+	(417.19,142.16) --
+	(417.19,147.15) --
+	(412.19,147.15) --
+	cycle;
+
+\path[fill=fillColor] (420.51,139.77) --
+	(425.50,139.77) --
+	(425.50,144.76) --
+	(420.51,144.76) --
+	cycle;
+
+\path[fill=fillColor] (428.82,137.57) --
+	(433.82,137.57) --
+	(433.82,142.56) --
+	(428.82,142.56) --
+	cycle;
+
+\path[fill=fillColor] (437.14,135.43) --
+	(442.13,135.43) --
+	(442.13,140.43) --
+	(437.14,140.43) --
+	cycle;
+
+\path[fill=fillColor] (445.45,133.56) --
+	(450.45,133.56) --
+	(450.45,138.56) --
+	(445.45,138.56) --
+	cycle;
+
+\path[fill=fillColor] (453.76,131.74) --
+	(458.76,131.74) --
+	(458.76,136.74) --
+	(453.76,136.74) --
+	cycle;
+
+\path[fill=fillColor] (462.08,129.78) --
+	(467.07,129.78) --
+	(467.07,134.77) --
+	(462.08,134.77) --
+	cycle;
+
+\path[fill=fillColor] (470.39,127.78) --
+	(475.39,127.78) --
+	(475.39,132.78) --
+	(470.39,132.78) --
+	cycle;
+
+\path[fill=fillColor] (478.71,126.01) --
+	(483.70,126.01) --
+	(483.70,131.01) --
+	(478.71,131.01) --
+	cycle;
+
+\path[fill=fillColor] (487.02,124.40) --
+	(492.02,124.40) --
+	(492.02,129.39) --
+	(487.02,129.39) --
+	cycle;
+
+\path[fill=fillColor] (495.34,122.77) --
+	(500.33,122.77) --
+	(500.33,127.77) --
+	(495.34,127.77) --
+	cycle;
+
+\path[fill=fillColor] (503.65,121.27) --
+	(508.64,121.27) --
+	(508.64,126.27) --
+	(503.65,126.27) --
+	cycle;
+
+\path[fill=fillColor] (511.96,119.69) --
+	(516.96,119.69) --
+	(516.96,124.69) --
+	(511.96,124.69) --
+	cycle;
+
+\path[fill=fillColor] (520.28,118.37) --
+	(525.27,118.37) --
+	(525.27,123.37) --
+	(520.28,123.37) --
+	cycle;
+
+\path[fill=fillColor] (528.59,117.08) --
+	(533.59,117.08) --
+	(533.59,122.07) --
+	(528.59,122.07) --
+	cycle;
+
+\path[fill=fillColor] (536.91,115.80) --
+	(541.90,115.80) --
+	(541.90,120.79) --
+	(536.91,120.79) --
+	cycle;
+
+\path[fill=fillColor] (545.22,114.56) --
+	(550.22,114.56) --
+	(550.22,119.56) --
+	(545.22,119.56) --
+	cycle;
+
+\path[fill=fillColor] (553.53,113.11) --
+	(558.53,113.11) --
+	(558.53,118.11) --
+	(553.53,118.11) --
+	cycle;
+
+\path[fill=fillColor] (561.85,112.00) --
+	(566.84,112.00) --
+	(566.84,116.99) --
+	(561.85,116.99) --
+	cycle;
+
+\path[fill=fillColor] (570.16,110.83) --
+	(575.16,110.83) --
+	(575.16,115.83) --
+	(570.16,115.83) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,192.97) -- (368.34,192.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,189.44) -- (364.81,196.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,187.54) -- (376.65,187.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,184.00) -- (373.12,191.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,182.28) -- (384.97,182.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,178.74) -- (381.44,185.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,177.28) -- (393.28,177.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,173.74) -- (389.75,180.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,172.56) -- (401.60,172.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,169.03) -- (398.06,176.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,168.23) -- (409.91,168.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,164.70) -- (406.38,171.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,165.07) -- (418.22,165.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,161.54) -- (414.69,168.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,161.58) -- (426.54,161.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,158.05) -- (423.01,165.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,158.33) -- (434.85,158.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,154.80) -- (431.32,161.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,155.26) -- (443.17,155.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,151.73) -- (439.63,158.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,152.71) -- (451.48,152.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,149.18) -- (447.95,156.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,150.06) -- (459.79,150.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,146.53) -- (456.26,153.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,147.16) -- (468.11,147.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,143.63) -- (464.58,150.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,144.40) -- (476.42,144.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,140.87) -- (472.89,147.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,141.94) -- (484.74,141.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,138.40) -- (481.20,145.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,139.68) -- (493.05,139.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,136.15) -- (489.52,143.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,137.43) -- (501.36,137.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,133.89) -- (497.83,140.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,135.23) -- (509.68,135.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,131.70) -- (506.15,138.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,133.11) -- (517.99,133.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,129.58) -- (514.46,136.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,131.25) -- (526.31,131.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,127.72) -- (522.78,134.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,129.44) -- (534.62,129.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,125.91) -- (531.09,132.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,127.77) -- (542.94,127.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,124.24) -- (539.40,131.30);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,126.17) -- (551.25,126.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72,122.64) -- (547.72,129.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,124.08) -- (559.56,124.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03,120.55) -- (556.03,127.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,122.46) -- (567.88,122.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35,118.92) -- (564.35,125.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,121.01) -- (576.19,121.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,117.48) -- (572.66,124.54);
 \definecolor{fillColor}{RGB}{0,0,0}

### 2020-04-15 serial.tex
th
almost done with the results section

@@
 	\textbf\newline{
-		Unraveling the paradox between generation and serial intervals: applications to COVID-19 pandemic
+		Unraveling the paradox between generation and serial intervals
 	}
-}\\
+}
+\newline\\
 Sang Woo Park
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!th]
 \includegraphics[width=\textwidth]{serial_guide.pdf}
@@
 \begin{equation}
-f_\ell(\tau) \propto \int_{0}^\infty \int_{0}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma
+f_\ell(\tau) \propto \int_{0}^\infty \int_{0}^\infty \mathcal R_c (\ell - x_0) i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma
 \end{equation}
@@
 Here, we assume that the forward incubation period distribution does not vary across cohorts over the course of an epidemic as it represents an intrinsic property of the natrual history of a disease.
+Finally, $\mathcal R_c (\ell - x_0)$ is the cohort reproduction number, which is the average secondary number of cases caused by an individual infected at time $\ell - x_0$.
+The cohort reproduction number plays a critical role in defining the forward serial interval because serial intervals can only be measured after the disease has been transmitted; 
+we revisit this point in the Results section.
 
@@
 i(t) = \mathcal R_0 S(t) \int_0^\infty i(t-\tau) g(\tau) \mathrm{d}\tau,
+\label{eq:renewal}
 \end{equation}
@@
 g(\tau) = \int_0^\infty h(x_0, \tau) \mathrm{d}x_0.
+\end{equation}
+Finally, the cohort reproduction is defined as follows:
+\begin{equation}
+\mathcal R_c(t) = \mathcal R_0 \int_0^\infty g(\tau) S(t+\tau) \mathrm{d} \tau.
 \end{equation}
@@
 We note that the forward serial-interval distribution depends on the exponential growth rate $r$.
-When the epidemic grows fast (high $r$), we expect the backward incubation period to be short, and therefore, the forward serial-interval distribution will generally have a larger mean than the forward generation-interval distribution.
+When the epidemic grows fast (high $r$), we expect the backward incubation period to be short, and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation-interval distribution.
 The Susceptible-Exposed-Infected-Recovered model, which assumes that incubation and exposed periods are equivalent, is a special case where the conditional forward generation-interval distribution cancels out with the backward generation-interval distribution exactly because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector;
@@
 
+\begin{table}[!th]
+\begin{center}
+\begin{tabular}{|l|l|r|}
+\hline
+Parameter & Values & Source\\
+\hline
+Mean forward incubation period & 5.5 days & \cite{lauer2020incubation} \\
+SD forward incubation period & 2.4 & \cite{lauer2020incubation} \\
+Mean intrinsic generation interval & 5 days & \cite{ferretti2020quantifying} \\
+SD intrinsic generation interval & 2 & \cite{ferretti2020quantifying} \\
+\hline
+\end{tabular}
+\end{center}
+\caption{
+\textbf{Parameter values used for simulations.}
+The intrinsic generation-interval distribution is parameterized using a log-normal distribution with log mean $\mu_G=1.54$ and log standard deviation $\sigma_G=0.37$.
+The forward incubation period distribution is parameterized using a log-normal distribution with log mean $\mu_I=1.62$ and log standard deviation $\sigma_I=0.42$.
+The joint probability distribution is modeled using a multivariate log-normal distribution with correlations $\rho=-0.5, 0, 0.5$.
+}
+\end{table}
+
 We use a simulation-based approach to compare the estimates of $\mathcal R$ based on the serial- and generation-interval distributions. 
-To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and correlation $\rho$.
-The multivariate log-normal distribution is parameterized based on pameter estimates for COVID-19.
-We construct the forward serial-interval distribution during the exponential growth period as follows:
+To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and correlation $\rho$;
+the multivariate log-normal distribution is parameterized based on pameter estimates for COVID-19 (Table 1).
+We construct forward serial intervals during the exponential growth period as follows:
 \begin{equation}
@@
 \end{equation}
-We compare this estimate with a naive estimate of $\mathcal R$ that assumes that the backward and the forward incubation periods are identically distributed:
+We compare this estimate with a naive estimate of ${\mathcal R}_{\textrm{\tiny naive}}$ that assumes that the backward and the forward incubation periods are identically distributed:
 \begin{equation}
@@
 On the other hand, using naive serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates $\mathcal R$;
-as $r$ increases, estimates of $\mathcal R$ eventually saturate and decrease because negative serial intervals are given too much weight (\fref{rR}B)
+as $r$ increases, ${\mathcal R}_{\textrm{\tiny naive}}$ saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
 While the forward serial intervals during the exponential growth phase can be also negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation period (and therefore less negative serial intervals).
 
-\begin{figure}[!ht]
+\begin{figure}[!th]
 \includegraphics[width=\textwidth]{rR.pdf}
@@
 Comapring the shapes of forward serial-interval distributions and the intrinsic generation-interval distribution allow us to better understand how they are able to give identical estimates of $\mathcal R$.
-Generation-interval distributions with higher means and less variability are generally expected to give higher $\mathcal R$ for a given $r$.
-The forward serial intervals during the exponential growth phase have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
+In general, generation-interval distributions with higher means and less variability are expected to give higher $\mathcal R$ for a given $r$.
+In this case, the forward serial intervals during the exponential growth phase have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
 The effects of higher means (which increases $\mathcal R$) and higher variability (which decreases $\mathcal R$) cancel out exactly;
-therefore, the estimates of $\mathcal R$ remain unchanged.
+therefore, we estimate the same $\mathcal R$ using both serial and generation intervals.
 
-\begin{figure}[!ht]
+\begin{figure}[!th]
 \includegraphics[width=\textwidth]{forward.pdf}
@@
 
-\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions.
+\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and the corresponding stochastic realization based on the Gillespie algorithm.
 The mean forward incubation period remains constant throughout an epidemic as expected (\fref{epi}B).
-The mean forward generation interval contracts as epidemic progresses because an infected individual is less likely to infect another person as the proportion of susceptible individuals decreases (\fref{epi}C; \cite{champredon2015intrinsic}).
+The mean forward generation interval contracts as the epidemic progresses because an infected individual is less likely to infect another person as the proportion of susceptible individuals decreases (\fref{epi}C; \cite{champredon2015intrinsic}).
 In contrast, the mean serial interval depends on previous incidence and therefore decreases over time (\fref{epi}D):
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!th]
+\includegraphics[width=\textwidth]{forward_tease.pdf}
+\caption{
+\textbf{Effects of dynamical correlations on serial intervals.}
+}
+\label{fig:tease}
+\end{figure}
+
+We further tease apart factors that affect the forward serial interval distribution, including the cohort reproduction number, as mentioned previously.
+
+\begin{figure}[!th]
 \includegraphics[width=\textwidth]{observedrR.pdf}
@@
 
-\begin{figure}
+\begin{figure}[!th]
 \includegraphics[width=\textwidth]{serial_analysis.pdf}

### 2020-04-15 forward.R

@@ -27,10 +27,6 @@ summfun <- function(dd) {
 }
 
 ## model parameters
-meanlog <- 1.621
-sdlog <- 0.418
-scale <- 5.5
-shape <- 4.1
 r <- rr$r
 
 detdata <- data.frame(
@@ -109,15 +105,12 @@ serdata0 <- data.frame(
 
 serdet <- data.frame(
   tvec=rr$tvec,
-  mf=rr$mfser
+  mf=rr$mfser2
 )
 
 g4 <- ggplot(serdata0) +
-  # geom_point(aes(cohort, tdiff), shape=1, col="#D55E00", size=2) +
-  geom_smooth(aes(cohort, tdiff), shape=1, col="#D55E00", size=2) +
-  geom_line(data=serdet, aes(tvec, mf), lwd=1) 
-  
-  
+  geom_line(data=serdet, aes(tvec, mf), lwd=1) +
+  geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
   geom_hline(yintercept=serdet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
   scale_y_continuous("Forward serial interval (days)", expand=c(0, 0), limits=c(0, 7)) +
@@ -144,7 +137,8 @@ g5 <- ggplot(incdata1) +
   geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
   geom_hline(yintercept=incdet$mf[1], lty=2) +
   scale_x_continuous("Secondary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_continuous("Backward incubation period (days)", expand=c(0, 0), limits=c(0, 8.6)) +
+  scale_y_continuous("Backward incubation period (days)", expand=c(0, 0), limits=c(0, 9.6),
+                     breaks=0:4*2) +
   scale_fill_gradientn(colors=c("white", "black")) +
   ggtitle("E") +
   theme(
@@ -168,7 +162,7 @@ g6 <- ggplot(gendata1) +
   geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
   geom_hline(yintercept=gendet$mf[1], lty=2) +
   scale_x_continuous("Secondary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
[…]

### 2020-04-15 forward_tease.R

@@ -1,0 +1,182 @@
+library(tidyr)
+library(dplyr)
+library(ggplot2); theme_set(theme_bw())
+library(gridExtra)
+library(tikzDevice)
+source("renewal_det.R")
+
+load("sir_sim.rda")
+
+rr <- renewal_det()
+
+tcut <- 0:40*2
+
+serdata0 <- data.frame(
+  cohort=sir_sim$t_symptomatic[sir_sim$infected_by],
+  tdiff=sir_sim$t_symptomatic-sir_sim$t_symptomatic[sir_sim$infected_by]
+) %>%
+  filter(!is.na(cohort), !is.na(tdiff), cohort > 0, cohort <= 100) %>%
+  mutate(
+    cc=cut(cohort, tcut)
+  ) %>%
+  group_by(cc) %>%
+  summarize(
+    mean=mean(tdiff)
+  ) %>%
+  ungroup %>%
+  mutate(
+    cc=as.character(cc),
+    cc=(as.numeric(gsub("\\(", "", gsub(",.*", "", cc)))+as.numeric(gsub("]", "", gsub(".*,", "", cc))))/2
+  )
+
+serdet <- data.frame(
+  tvec=rr$tvec,
+  mf=rr$mfser2,
+  type="Accounting for changes in $\\mathcal R_c$"
+)
+
+serdet2 <- data.frame(
+  tvec=rr$tvec,
+  mf=rr$mfser,
+  type="Not accounting for changes in $\\mathcal R_c$"
+)
+
+serdet_all <- bind_rows(serdet, serdet2)
+
+g1 <- ggplot(serdata0) +
+  geom_line(data=serdet_all, aes(tvec, mf, lty=type), lwd=1) +
+  geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
+  # geom_hline(yintercept=serdet$mf[1], lty=2) +
+  scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
+  scale_y_continuous("Forward serial interval (days)", expand=c(0, 0), limits=c(0, 7),
+                     breaks=c(0.0, 1.5, 3.0, 4.5, 6.0)) +
+  scale_fill_gradientn(colors=c("white", "black")) +
+  ggtitle("A") +
+  theme(
+    panel.grid = element_blank(),
+    legend.position = c(0.35, 0.15),
[…]

### 2020-04-15 rR.R

@@ -5,17 +5,20 @@ library(gridExtra)
 source("cpalette.R")
 
 ## incubation!
-meanlog1 <- 1.621
-sdlog1 <- 0.418
+meanlog1 <- 1.62
+sdlog1 <- 0.42
+mean(rlnorm(50000, meanlog = 1.62, sdlog=0.42)) ## 5.5 days
+sd(rlnorm(50000, meanlog = 1.62, sdlog=0.42)) ## 2.4
+
 ## generation
 ## moment matching
 mean(rlnorm(50000, meanlog = 1.54, sdlog=0.37)) ## 5 days
-sd(rlnorm(50000, meanlog = 1.54, sdlog=0.37)) ## 1.9 days
+sd(rlnorm(50000, meanlog = 1.54, sdlog=0.37)) ##
 
 serialR <- function(r=0.1,
                     rho=0.5,
-                    meanlog1=1.621,
-                    sdlog1=0.418,
+                    meanlog1=1.62,
+                    sdlog1=0.42,
                     meanlog2=1.54,
                     sdlog2=0.37,
                     nsim=100000,
@@ -44,8 +47,8 @@ serialR <- function(r=0.1,
 
 serialR2 <- function(r=0.1,
                     rho=0.5,
-                    meanlog1=1.621,
-                    sdlog1=0.418,
+                    meanlog1=1.62,
+                    sdlog1=0.42,
                     meanlog2=1.54,
                     sdlog2=0.37,
                     nsim=100000,
@@ -156,7 +159,7 @@ g2 <- ggplot(rRdata2) +
   geom_smooth(aes(r, R, col=type, lty=type), se=FALSE) +
   geom_point(aes(r, R, col=type, shape=type), size=2) +
   scale_x_continuous("Exponential growth rate $r$ (1/day)", limits=c(0, 0.3), expand=c(0, 0)) +
-  scale_y_continuous("Reproduction number $\\mathcal R$", limits=c(1, 4.5), expand=c(0, 0)) +
+  scale_y_continuous("Naive reproduction number ${\\mathcal R}_{\\textrm{\\tiny naive}}$", limits=c(1, 4.5), expand=c(0, 0)) +
   scale_color_manual(values=cpalette) +
   ggtitle("B") +
   theme(

### 2020-04-15 renewal_det.R

@@ -2,7 +2,7 @@ renewal_det <- function(R0=2.5,
                         N=40000,
                         S0=40000-10,
                         dt=0.025,
-                        incfun=function(x) dlnorm(x, meanlog=1.621, sdlog=0.418),
+                        incfun=function(x) dlnorm(x, meanlog=1.62, sdlog=0.42),
                         genfun=function(x) dlnorm(x, meanlog=1.54, sdlog=0.37),
                         I0=10,
                         tmax=200,
@@ -40,27 +40,21 @@ renewal_det <- function(R0=2.5,
   mfinc <- apply(forwardinc, 2, function(x) sum(x*0:genmax*dt)/sum(x))
   mbinc <- apply(backwardinc, 2, function(x) sum(x*0:genmax*dt)/sum(x))
   
-  ## Jensen's inequality!!!!!
-  # sum(backwardinc[,x-genmax]*rev(mfgen[(x-genmax):x]))-mbinc[1]
-  
-  #tmpmat <- matrix(0:(genmax)*dt, nrow=genmax+1, ncol=genmax+1) - t(matrix(0:genmax*dt, nrow=genmax+1, ncol=genmax+1))
-  
-  # mfser0 <- sapply((genmax+1):(length(Svec)-genmax), function(x) {
-  #  sum(t(backwardinc[,x-genmax] * t(forwardgen[,x:(x-genmax)])) * tmpmat)
-  #}) +
-  #  tail(mfinc, -genmax)
-
-  # sapply((genmax+1):(length(Svec)-genmax), function(x) sum(backwardinc[,x-genmax]*rev(mfgen[(x-genmax):x])))
-    
   mfser <- head(sapply((genmax+1):(length(Svec)), function(x) sum(backwardinc[,x-genmax]*rev(mfgen[(x-genmax):x]))),-genmax) +
     tail(mfinc, -genmax) - head(mbinc, -genmax)
-  
-  # plot(mfser, type="l")
   
   mbgentmp <- c(rep(mbgen[1], genmax), mbgen)
   
   mbser <- head(sapply((genmax+1):(length(Svec)), function(x) sum(backwardinc[,x-genmax]*rev(mbgentmp[(x-genmax):x])))+mbinc,-genmax) -
     tail(mfinc, -genmax)
+  
[…]

### 2020-04-15 sir.R

@@ -10,8 +10,8 @@ sample2 <- function(x, size) {
 
 sir.full <- function(size,
                      R0=2.5,
-                     meanlog=1.621,
-                     sdlog=0.418,
+                     meanlog=1.62,
+                     sdlog=0.42,
                      meanlog2=1.54,
                      sdlog2=0.37,
                      I0,

### 2020-04-15 sir_sim.R

@@ -1,5 +1,5 @@
 source("sir.R")
 
-sir_sim <- sir.full(size=40000, I0=10, seed=123, keep.intrinsic = TRUE)
+sir_sim <- sir.full(size=40000, I0=10, seed=101, keep.intrinsic = TRUE)
 
 save("sir_sim", file="sir_sim.rda")

### 2020-04-15 serial.tex
tweak

@@
 this defines the forward serial interval (\fref{diagram}A).
-Then, it is clear that $x_0$ represents the backward incubation period for secondary cohort $\ell$; 
-$\sigma$ represents the forward generation interval for a primary cohort $\ell - x_0$ conditional on the incubation period $x_0$ of the infector;
-and $x_1$ represents the forward incubation period for a primary cohort $\ell - x_0 + \sigma$.
+Then, it is clear that $x_0$ represents the backward incubation period of infectors who became symptomatic at time $\ell$; 
+$\sigma$ represents the forward generation interval for individuals who came infected at time $\ell - x_0$ conditional on their incubation period $x_0$;
+and $x_1$ represents the forward incubation period for the infectees who became infected at time $\ell - x_0 + \sigma$.
 Assuming that the forward incubation distribution does not vary across cohorts, the forward serial interval distribution of a primary cohort $\ell$ can be written as follows:
@@
 \end{equation}
-Here, we assume that the forward incubation period distribution does not vary across cohorts over the course of an epidemic as it represents an intrinsic property of the natrual history of a disease.
-Finally, $\mathcal R_c (\ell - x_0)$ is the cohort reproduction number, which is the average secondary number of cases caused by an individual infected at time $\ell - x_0$.
-The cohort reproduction number plays a critical role in defining the forward serial interval because serial intervals can only be measured after the disease has been transmitted; 
-we revisit this point in the Results section.
+Finally, $\mathcal R_c (\ell - x_0)$ is the cohort reproduction number, which is defined as the average secondary number of cases caused by an individual infected at time $\ell - x_0$.
+We have to multiply the joint forward distribution $h$ by $\mathcal R_c (t) i(t)$, which represents total infectiousness of individuals infected at time $t$, rather than incidence $i(t)$, because we are interested in the backward incubation period $x_0$ and the forward generation interval $\sigma$ of infectors, rather than all infected individuals.
+We revisit this idea in the Results section.
 
@@
 then, we have to go forward in time by asking when the infector became symptomatic.
-In this case, $x_1$ and $\sigma$ represent the backward incubation period and generation-interval distributions, respectively, and $x_0$ represents the forward incubation period distribution.
+In this case, $x_1$ and $\sigma$ represent the backward incubation period and generation interval, respectively, and $x_0$ represents the forward incubation period.
 Therefore, the backward serial interval distribution of a secondary cohort $\ell$ can be written as follows
@@
 
-We further tease apart factors that affect the forward serial interval distribution, including the cohort reproduction number, as mentioned previously.
+We further tease apart factors that affect the forward serial interval distribution, including the cohort reproduction number $\mathcal R_c$, as mentioned earlier.
+\fref{tease}A compares the mean forward serial interval calculated from a stochastic model (orange points) with their deterministically calculated values;
+failing to account for changes in $\mathcal R_c$ overestimates the mean forward serial interval.
+A key distinction that needs to be made is that the forward serial-interval distributions depends on the backward incubation period of infectors (i.e., those who were able to successfully spread the disease to another person), rather than the incubation period of all symptomatic cases (\fref{tease}B).
+Therefore, the cohort size of infectors must be calculated as a product of the cohort reproduction number and incidence.
+
+Comparing the backward incubation period of infectors and all symptomatic cases provides an important, but counterintuitive, insight (\fref{tease}B).
+Given a cohort of symptomatic cases, individuals who were able to successfully spread the disease to others have longer incubation periods, on average;
+individuals with longer incubation period are infected earlier and have a higher chance of infecting others (i.e., higher $\mathcal R_c$) during the susceptible depletion phase.
+Therefore, the backward incubation period of an infector and the number of secondary cases caused by that infector are dynamically correlated (\fref{tease}C).
+This correlation disappears when we take the forward perspective, demonstrating the importance of perspective-dependency in studying epidemiological delay distributions (\fref{tease}D).
 
@@
 
+Now, we turn to practical issues.
 When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms.
 \fref{obsrR} demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of $\mathcal R$.
-Notably, even if we can observe \emph{all} serial intervals after the epidemic has ended, we still underestimate $\mathcal R$ by a large amount because the observed serial-interval distribution does not account for changes in the forward serial-interval distribution.
+Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate $\mathcal R$ by a large amount because the observed serial-interval distribution does not account for changes in the forward serial-interval distribution.
 As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean forward serial-interval distribution during the exponential growth phase, which provides the correct linke between $r$ and $\mathcal R$.

### 2020-04-15 serial.tex
more

@@
 
+Characterizing generation- and serial-interval distributions are critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
+Generation intervals measure the time difference between infection of a transmission pair, whereas serial intervals measure the time difference between symptom onset of a transmission pair.
+Due to their similar definitions, there differences have been inaccurately captured and misunderstood.
+We provide a theoretical basis for understanding serial intervals and show that both generation and serial intervals provide a correct link between $r$ and $\mathcal R$.
+Our analysis further reveals gap in current understanding and practical approaches to studying serial intervals.
+
+First, we demonstrate the importance of defining a cohort for studying any epidemiological time delay distributions.
+Previous studies have shown that generation interval can be either measured forward or backward;
+we generalize their ideas and show that these ideas can be applied to all distributions.
+Changes in the backward delay distributions is particularly robust across all distributions because they depend on previous changes in cohort sizes, which, in turn, depend on incidence of infection.
+Several epidemic analyses have attempted to reconstruct symptom onset or infection dates for each case from the confirmed dates while assuming a constant delay distribution;
+these assumptions translate to assuming a constant backward delay distribution.
+Although such assumption may be able to approximately match the time scale of an epidemic, 
+our analysis reveals that it is not a safe assumption.
+
+Using cohort-based approaches, we can define forward and backward serial intervals.
+The forward serial-interval distribution describes the
+
+\pagebreak
+
 \section*{Appendix}

### 2020-04-15 serial.tex
a small push

@@
 	\textbf\newline{
-		Unraveling the paradox between generation and serial intervals
+		Unraveling the paradox between generation and serial intervals: applications to COVID-19 pandemic
 	}
@@
 
-Using cohort-based approaches, we can define forward and backward serial intervals.
-The forward serial-interval distribution describes the
+Using cohort-based approaches, we define forward and backward serial intervals.
+The forward serial-interval distribution describes the renewal process of the
 

### 2020-04-15 serial.tex
changes in order

@@
 Due to their similar definitions, there differences have been inaccurately captured and misunderstood.
-We provide a theoretical basis for understanding serial intervals and show that both generation and serial intervals provide a correct link between $r$ and $\mathcal R$.
-Our analysis further reveals gap in current understanding and practical approaches to studying serial intervals.
+Here, we provide a theoretical basis for understanding serial intervals.
 
@@
 Using cohort-based approaches, we define forward and backward serial intervals.
-The forward serial-interval distribution describes the renewal process of the
+The forward serial-interval distribution describes the renewal process of the symptomatic cases and therefore provides the correct link between $r$ and $\mathcal R$.
+While our results support the use of serial interval distributions for calculating $\mathcal R$, 
+they also reveal gaps in our current understanding and practical approaches to characterizing serial intervals.
 

### 2020-04-16 serial.tex
almost there?

--- 2020-04-15 serial.tex
@@
 Generation intervals measure the time difference between infection of a transmission pair, whereas serial intervals measure the time difference between symptom onset of a transmission pair.
-Due to their similar definitions, there differences have been inaccurately captured and misunderstood.
-We provide a theoretical basis for understanding serial intervals and show that both generation and serial intervals provide a correct link between $r$ and $\mathcal R$.
-Our analysis further reveals gap in current understanding and practical approaches to studying serial intervals.
+Due to their similar definitions, their differences have been inaccurately captured and misunderstood.
 
-First, we demonstrate the importance of defining a cohort for studying any epidemiological time delay distributions.
+Our study demonstrate the importance of defining a cohort for studying any epidemiological time delay distributions.
 Previous studies have shown that generation interval can be either measured forward or backward;
@@
 Changes in the backward delay distributions is particularly robust across all distributions because they depend on previous changes in cohort sizes, which, in turn, depend on incidence of infection.
-Several epidemic analyses have attempted to reconstruct symptom onset or infection dates for each case from the confirmed dates while assuming a constant delay distribution;
-these assumptions translate to assuming a constant backward delay distribution.
-Although such assumption may be able to approximately match the time scale of an epidemic, 
-our analysis reveals that it is not a safe assumption.
+Several epidemic analyses during the COVID-19 pandemic have attempted to reconstruct symptom onset or infection dates for each case from confirmed dates while assuming a constant backward delay distribution.
+Although such approaches may be able to match the time scale of an epidemic, we recommend future studies to consider deconvolution approaches instead for proper reconstruction of epidemic time series.
 
 Using cohort-based approaches, we define forward and backward serial intervals.
-The forward serial-interval distribution describes the renewal process of the
+The forward serial-interval distribution describes the renewal process of the symptomatic individuals and therefore provides the correct link between $r$ and $\mathcal R$.
+While our results support the use of serial interval distributions for calculating $\mathcal R$, 
+they also reveal gaps in current approaches to characterizing serial intervals.
+Previous studies have often (i) recommended using up-to-date serial intervals, (ii) assumed that the serial interval distribution remains constant, and (iii) applied serial interval distributions estimated from one location to analyzing epidemics in other locations;
+however, these approaches implicitly ignore spatiotemporal variation in incidence and may therefore give systemtatically biased estimates of $\mathcal R$. 
+For example, given geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the forward serial interval distributions will vary across different countries.
+Future studies should aim to characterize spatiotemporal variation in serial intervals and understanding the drivers of their differences.
+
+We also show that there are multiple serial-interval distributions that correspond to the same set of generation-interval and incubation period distributions depending on their correlations;
+not explicitly accounting for their correlations can bias the estimate of the intrinsic generation-interval distribution from the serial-interval distribution (see Appendix).
+Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the effect of right-censoring or differences between the backward incubation period of an infector and the forward incubation period of an infecteee.
+There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.
+
+Our study is not without limitations.
+Here, we assumed that all individuals develop symptoms and that the the entire transmission process (e.g., direction of transmission, symptom onset dates, infection dates, etc.) are observable.
+In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult.
+For example, symotom onset dates cannot be used as a reliable proxy for the direction of transmission as infectees may develop symptoms before their infectors.
+Based on the COVID-19 paramters (Table 1), we expect roughly 3\% of infectees to develop symptoms before their infectors during the exponential growth period; 
+this probability increases as epidemic progresses because backward incubation period of an infector increases.
+Biases in the observed serial intervals will necessarily bias the estimates of $\mathcal R$.
+Furthermore, serial intervals do not take into account asymptomatic transmission; 
+not explicitly accounting for asymptomatic transmission may also  bias the estimates of $\mathcal R$.
+
+Both generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating $\mathcal R$ --- yet important quantities in describing an outbreak.
 

### 2020-04-16 serial.tex
edits

@@
 }
-\newline\\
+\newline
 Sang Woo Park
@@
 
-%The key distributions for understanding the spread of COVID-19 include:
-%\begin{enumerate}
-%  \item Incubation period distribution: time between infection and symptom onset \citep{backer2020incubation, %li2020early, linton2020incubation, tian2020characteristics}
-%  \item Serial interval distribution: time between symptom onset of an infector and an infectee \citep{du2020s%erial, nishiura2020serial, zhao2020estimating}
-%  \item Generation interval distribution: time between infection of an infector and an infectee \citep{ganyani%2020estimating}
-%\end{enumerate}
-
 \section{Introduction}
@@
 the corresponding reproduction number in a fully susceptible population --- referred to as the basic reproduction number $\mathcal R_0$ --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
-Since the reproduction number cannot be measured directly, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions.
+Since reproduction numbers cannot be measured directly, particularly during the outset of an outbreak, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{du2020serial, jung2020real, li2020early, zhao2020preliminary}).
 
 The generation interval is defined as the time between when an individual (infector) is infected and when an individual infects another person (infectee);
-the generation-interval distributions plays a key role in shaping the relationship between the exponential growth rate $r$ and the reproduction number $\mathcal R$.
-On the other hand, the serial interval is defined as the time between when an infector and an infectee become symptomatic.
-While serial intervals are similar to generation intervals, previous studies noted that using serial intervals can give different estimates of $\mathcal R$ and have often alluded to differences in their variances, despite having seemingly identical expected values.
+the generation-interval distributions plays a key role in shaping the relationship between the exponential growth rate $r$ and the reproduction number $\mathcal R$ \citep{wallinga2007generation}.
+On the other hand, the serial interval is defined as the time between when an infector and an infectee become symptomatic \citep{svensson2007note}.
+While generation and serial intervals are conceptually similar,
+previously studies have often alluded to differences in their variances, despite having seemingly identical expected values \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence};
+some suggested that using serial intervals can give different estimates of $\mathcal R$ \citep{britton2019estimation}.
 Even though these distinctions were first made over a decade ago \citep{svensson2007note}, 
@@
 previous frameworks implicitly assume that incidence remains constant.
-Using our framework, we are able to show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ based on the exponential growth phase of an epidemic.
+We are show that both serial- and generation-interval distributions can give identical estimates of $\mathcal R$ based on the exponential growth phase of an epidemic if they are properly defined.
 However, failing to account for changes in the observed serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
@@
 where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\sigma$ represents the realized generation interval.
-Previous studies have often assumed that $x_0$ and $x_1$ have the same means and concluded that the serial and generation intervals have the same mean;
-however, these results implicitly assume that incidence stays constant.
+Previous studies have often assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
+however, they implicitly assume that incidence stays constant.
 
@@
 \caption{
-\textbf{Forward and backward serial intervals.}
+\textbf{Illustration of forward and backward serial intervals.}
+A. The forward serial interval for a primary cohort $\ell$ (i.e., an infector who became symptomatic at time $\ell$).
+In this case, $x_0$ represents the backward incubation period of the infector;
+$\sigma$ represents the forward generation interval;
+and $x_1$ represents the forward incubation period of the infectee.
+B. The backward serial interval for a secondary cohort $\ell$ (i.e., an infectee who became symptomatic at time $\ell$).
+In this case, $x_0$ represents the forward incubation period of the infector;
+$\sigma$ represents the backward generation interval;
+and $x_1$ represents the backward incubation period of the infectee.
 }
@@
 Finally, $\mathcal R_c (\ell - x_0)$ is the cohort reproduction number, which is defined as the average secondary number of cases caused by an individual infected at time $\ell - x_0$.
-We have to multiply the joint forward distribution $h$ by $\mathcal R_c (t) i(t)$, which represents total infectiousness of individuals infected at time $t$, rather than incidence $i(t)$, because we are interested in the backward incubation period $x_0$ and the forward generation interval $\sigma$ of infectors, rather than all infected individuals.
+We have to multiply the joint forward distribution $h$ by $\mathcal R_c (t) i(t)$, which represents total infectiousness of individuals infected at time $t$, rather than incidence $i(t)$, because we are interested in the backward incubation period $x_0$ and the forward generation interval $\sigma$ of infectors (i.e., those who transmitted successfully to at least one individual), rather than all infected individuals.
 We revisit this idea in the Results section.
@@
 b_\ell(\tau) &\propto j(\ell) f_{\ell}(\tau)\\
-&\propto \int_0^\infty i(\ell-x_0) k(x_0) f_{\ell}(\tau) \mathrm{d} x_0
+&\propto \int_0^\infty \mathcal R_c (\ell - x_0) i(\ell-x_0) k(x_0) f_{\ell}(\tau) \mathrm{d} x_0
 \end{aligned}
 \end{equation}
-where $j$ represents the incidence of symptomatic cases.
+where $j$ represents the incidence of symptomatic infectors.
 
@@
 
-Here, use a renewal equation to model the spread of disease in a population:
+Here, use a renewal equation to model the spread of disease in a population.
+Ignoring the dynamics of births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be written as:
 \begin{equation}
@@
 \end{equation}
-where $\mathcal R_0$ is the basic reproduction number (i.e., the average number of secondary cases caused by a primary case  in a fully susceptible population), $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population), $S(t)$ is the proportion of susceptible individuals.
+where $\mathcal R_0$ is the basic reproduction number, and $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
 Then, the forward generation-interval for a primary cohort $\ell$ follows \citep{champredon2015intrinsic}:
@@
 \end{equation}
-We compare this estimate with a naive estimate of ${\mathcal R}_{\textrm{\tiny naive}}$ that assumes that the backward and the forward incubation periods are identically distributed:
+We compare this with an estimate of $\mathcal R$ based on naive serial-interval distribution that assumes that the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
 \begin{equation}
@@
 
-Both generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating $\mathcal R$ --- yet important quantities in describing an outbreak.
+Both generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating $\mathcal R$ --- yet important quantities in characterizing an epidemic.
+Here, we provided a theoretical basis for understanding serial intervals and show that naively using the observed serial intervals may lead to biased conclusions in studying the COVID-19 pandemic.
+Concluding sentence.
 

### 2020-04-16 serial.tex
caption

@@
 \caption{
-\textbf{Estimates of the reproduction number from the exponential growth rate.}
+\textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
+A. The forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number $\mathcal R$.
+B.
+The serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and $\mathcal R$.
+C. The mean forward serial interval during the exponential growth phase depends on $r$.
+D. The squared coefficient of variation of forward serial intervals during the exponential growth phase depends on $r$.
 }

### 2020-04-16 serial.tex
time for a break

@@
 f_\ell(\tau) \propto \int_{0}^\infty \int_{0}^\infty \mathcal R_c (\ell - x_0) i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma
+\label{eq:forward}
 \end{equation}
@@
 \begin{equation}
-i(t) = \mathcal R_0 S(t) \int_0^\infty i(t-\tau) g(\tau) \mathrm{d}\tau,
+\begin{aligned}
+\frac{\mathrm{d}S}{\mathrm{d}t} &= - i(t)\\
+i(t) &= \mathcal R_0 S(t) \int_0^\infty i(t-\tau) g(\tau) \mathrm{d}\tau,
+\end{aligned}
 \label{eq:renewal}
@@
 
-First, we compare the estimates of the reproduction number $\mathcal R$ based on the intrinsic generation-interval distribution and the forward serial-interval distribution during the exponential growth phase (\fref{rR}A).
+First, we compare the estimates of the reproduction number $\mathcal R$ based on the intrinsic generation-interval distribution $g(\tau)$ and the forward serial-interval distribution during the exponential growth phase $f_{\textrm{\tiny exp}}(\tau)$ (\fref{rR}A).
 Both distributions provide identical estimates of $\mathcal R$ regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution.
@@
 \textbf{Epidemiological dynamics and changes in mean forward and backward delay distributions.}
+A. Cumulative incidence over time.
+B-D. Changes in the mean forward incubation period, generation interval, and serial interval.
+E-G. Changes in the mean backward incubation period, generation interval, and serial interval.
+Black lines represent the results of a deterministic simulation.
+Orange lines and points represent the results of a stochastic simulation.
+Forward incubation periods and intrinsic generation-intervals are assumed to be independent of each other: $h(x_0, \sigma) = k(x_0) g(\sigma)$.
+See Table 1 for parameter values.
 }
@@
 \caption{
-\textbf{Effects of dynamical correlations on serial intervals.}
+\textbf{Effects of dynamical correlations between incubation periods and the number of secondary cases on serial intervals.}
 }
@@
 
-We further tease apart factors that affect the forward serial interval distribution, including the cohort reproduction number $\mathcal R_c$, as mentioned earlier.
-\fref{tease}A compares the mean forward serial interval calculated from a stochastic model (orange points) with their deterministically calculated values;
-failing to account for changes in $\mathcal R_c$ overestimates the mean forward serial interval.
-A key distinction that needs to be made is that the forward serial-interval distributions depends on the backward incubation period of infectors (i.e., those who were able to successfully spread the disease to another person), rather than the incubation period of all symptomatic cases (\fref{tease}B).
+We further tease apart factors that affect the forward serial interval distribution.
+\fref{tease}A compares the mean forward serial interval calculated from a stochastic model (orange points) with their deterministically calculated values (black lines);
+failing to account for changes in $\mathcal R_c$ in \eref{forward} overestimates the mean forward serial interval.
+A key distinction that needs to be made is that the forward serial-interval distributions depends on the backward incubation period of symptomatic infectors (i.e., those who were able to successfully spread the disease to another person), rather than the incubation period of all symptomatic cases (\fref{tease}B).
 Therefore, the cohort size of infectors must be calculated as a product of the cohort reproduction number and incidence.
@@
 Comparing the backward incubation period of infectors and all symptomatic cases provides an important, but counterintuitive, insight (\fref{tease}B).
-Given a cohort of symptomatic cases, individuals who were able to successfully spread the disease to others have longer incubation periods, on average;
-individuals with longer incubation period are infected earlier and have a higher chance of infecting others (i.e., higher $\mathcal R_c$) during the susceptible depletion phase.
-Therefore, the backward incubation period of an infector and the number of secondary cases caused by that infector are dynamically correlated (\fref{tease}C).
-This correlation disappears when we take the forward perspective, demonstrating the importance of perspective-dependency in studying epidemiological delay distributions (\fref{tease}D).
+Given a cohort of symptomatic cases, individuals who were able to successfully spread the disease to others have longer incubation periods, on average,
+because individuals with longer incubation period are infected earlier and have a higher chance of infecting others (i.e., higher $\mathcal R_c$) during the susceptible depletion phase.
+Therefore, the backward incubation period of a symptomatic case and the number of secondary cases caused by that individual are dynamically correlated (\fref{tease}D).
+This correlation disappears when we take the forward perspective, demonstrating the importance of perspective-dependency in studying epidemiological delay distributions (\fref{tease}C).
 

### 2020-04-16 forward_tease.R

@@ -48,10 +48,10 @@ g1 <- ggplot(serdata0) +
   geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
   # geom_hline(yintercept=serdet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_continuous("Forward serial interval (days)", expand=c(0, 0), limits=c(0, 7),
+  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7),
                      breaks=c(0.0, 1.5, 3.0, 4.5, 6.0)) +
   scale_fill_gradientn(colors=c("white", "black")) +
-  ggtitle("A") +
+  ggtitle("A. Serial interval") +
   theme(
     panel.grid = element_blank(),
     legend.position = c(0.35, 0.15),
@@ -85,18 +85,21 @@ incdet <- data.frame(
 incdet2 <- data.frame(
   tvec=rr$tvec,
   mf=rr$mbinc2,
-  type="Infectors"
+  type="Symptomatic infectors"
 )
 
-incdet_all <- bind_rows(incdet, incdet2)
+incdet_all <- bind_rows(incdet, incdet2) %>%
+  mutate(
+    type=factor(type, levels=c("Symptomatic infectors", "All symptomatic cases"))
+  )
 
 g2 <- ggplot(incdata) +
   geom_line(data=incdet_all, aes(tvec, mf, lty=type), lwd=1) +
   geom_point(aes(cc, mean), shape=2, size=2, col="#D55E00") +
   scale_x_continuous("Secondary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_continuous("Backward incubation period (days)", expand=c(0, 0), limits=c(0, 9.6)) +
-  scale_linetype_manual(values=c(3, 1)) +
-  ggtitle("B") +
+  scale_y_continuous("Backward delay (days)", expand=c(0, 0), limits=c(0, 9.6)) +
+  scale_linetype_manual(values=c(1, 3)) +
+  ggtitle("B. Incubation period") +
   theme(
     panel.grid = element_blank(),
     legend.position = c(0.3, 0.15),
@@ -158,9 +161,9 @@ g3 <- ggplot(cordat) +
   geom_hline(yintercept = 0, lty=2) +
[…]

### 2020-04-17 serial.tex
caption

@@
 \caption{
-\textbf{Effects of dynamical correlations between incubation periods and the number of secondary cases on serial intervals.}
+\textbf{Dynamical correlations between incubation periods and the number of secondary cases.}
+A. The mean forward serial interval depends on changes in the cohort reproduction number.
+B. The mean backward incubation period of infectors is higher than the mean backward incubation period of all symptomatic cases.
+C. Correlation between the number of secondary cases and the incubation period for individuals who got infected within the same time preiod.
+D. Correlation between the number of secondary cases and the incubation period for individuals who developed symptoms within the same time preiod.
 }

### 2020-04-17 serial.tex
Intro; also removing automatically made files, sorry if that will mess you up.

--- 2020-04-16 serial.tex
@@
 }
-\newline
+\newline\\
 Sang Woo Park
@@
 
+%The key distributions for understanding the spread of COVID-19 include:
+%\begin{enumerate}
+%  \item Incubation period distribution: time between infection and symptom onset \citep{backer2020incubation, %li2020early, linton2020incubation, tian2020characteristics}
+%  \item Serial interval distribution: time between symptom onset of an infector and an infectee \citep{du2020s%erial, nishiura2020serial, zhao2020estimating}
+%  \item Generation interval distribution: time between infection of an infector and an infectee \citep{ganyani%2020estimating}
+%\end{enumerate}
+
 \section{Introduction}
@@
 the corresponding reproduction number in a fully susceptible population --- referred to as the basic reproduction number $\mathcal R_0$ --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
-Since reproduction numbers cannot be measured directly, particularly during the outset of an outbreak, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{du2020serial, jung2020real, li2020early, zhao2020preliminary}).
+Since the reproduction number cannot be measured directly, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions.
 
 The generation interval is defined as the time between when an individual (infector) is infected and when an individual infects another person (infectee);
-the generation-interval distributions plays a key role in shaping the relationship between the exponential growth rate $r$ and the reproduction number $\mathcal R$ \citep{wallinga2007generation}.
-On the other hand, the serial interval is defined as the time between when an infector and an infectee become symptomatic \citep{svensson2007note}.
-While generation and serial intervals are conceptually similar,
-previously studies have often alluded to differences in their variances, despite having seemingly identical expected values \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence};
-some suggested that using serial intervals can give different estimates of $\mathcal R$ \citep{britton2019estimation}.
-Even though these distinctions were first made over a decade ago \citep{svensson2007note}, 
+the generation-interval distributions plays a key role in shaping the relationship between the exponential growth rate $r$ and the reproduction number $\mathcal R$.
+Similarly, the serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic}.
+While serial intervals are similar to generation intervals, previous studies noted that using serial intervals can give different estimates of $\mathcal R$ and have noted that in many contexts serial intervals are expected to have larger variances than generation intervals (but the same mean).
+Even these distributions were clearly distinguished over a decade ago \citep{svensson2007note}, 
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds:
@@
 
-The lack of clear understanding of their differences can be largely attributed to an apparent paradox.
+One important source of confusion comes down to an apparent paradox.
 When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
 This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number $\mathcal R$.
-Likewise, since infection typically leads to symptoms, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
+Likewise, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
 Therefore, both generation- and serial-interval distributions should give us identical estimates of  $\mathcal R$ based the observed epidemic growth rate $r$.
-However, current theory suggests that using generation- and serial-interval distributions give different estimates of $\mathcal R$ and contradicts our biological intution.
+In contexts where the distributions are expected to be different, current theory has no explanation for how they might link $r$ to \Rx\ in the same way.
 
-Here, we provide an answer to the decade-old paradox between generation and serial intervals.
-We present a novel framework for understanding serial intervals and show that the serial-interval distribution must be defined with reference to disease incidence;
-previous frameworks implicitly assume that incidence remains constant.
-We are show that both serial- and generation-interval distributions can give identical estimates of $\mathcal R$ based on the exponential growth phase of an epidemic if they are properly defined.
-However, failing to account for changes in the observed serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
+Here, we provide an answer to this paradox, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
+We develop a new framework for understanding intervals and show that the forward serial-interval distribution gives the correct value of $\mathcal R$.
+We also show that \jd{Come back to this.
+Not just over time, right?} However, failing to account for changes in the observed serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
 We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of the ongoing pandemic.
@@
 
-We first begin by describing a general framework for characterizing a distribution of time delays between \emph{any} two epidemiological events;
-these events can be defined either within an infected individual (e.g., infection and symptom onset of an individual) or between infected individuals (e.g., symptom onsets of an infector and an infectee).
+We first begin by describing a general framework for characterizing a distribution of time delays between any two epidemiological events;
+these events can be defined either within an infected individual (e.g., infection and symptom onset of an individual, the incubation period) or between infected individuals (e.g., symptom onsets of an infector and an infectee, the serial interval).
 We can further divide these events into \emph{primary} and \emph{secondary} events.
 When we measure an epidemiological time delay within an infected individual (e.g., incubation period), the primary event always occurs before the secondary event.
+\jd{Rethink, or else rethink ``any'' above: the ``hidden'' time (my term) is the time between onset of infectiousness and onset of symptoms; it is within, but can be positive or negative.
+I'm not saying we should use it here\ldots}
 When we measure an epidemiological time delay between infected individuals (e.g., serial interval), 
@@
 where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\sigma$ represents the realized generation interval.
-Previous studies have often assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, they implicitly assume that incidence stays constant.
+Previous studies have often assumed that $x_0$ and $x_1$ have the same means and concluded that the serial and generation intervals have the same mean;
+however, these results implicitly assume that incidence stays constant.
 
@@
 \caption{
-\textbf{Illustration of forward and backward serial intervals.}
-A. The forward serial interval for a primary cohort $\ell$ (i.e., an infector who became symptomatic at time $\ell$).
-In this case, $x_0$ represents the backward incubation period of the infector;
-$\sigma$ represents the forward generation interval;
-and $x_1$ represents the forward incubation period of the infectee.
-B. The backward serial interval for a secondary cohort $\ell$ (i.e., an infectee who became symptomatic at time $\ell$).
-In this case, $x_0$ represents the forward incubation period of the infector;
-$\sigma$ represents the backward generation interval;
-and $x_1$ represents the backward incubation period of the infectee.
+\textbf{Forward and backward serial intervals.}
 }
@@
 Finally, $\mathcal R_c (\ell - x_0)$ is the cohort reproduction number, which is defined as the average secondary number of cases caused by an individual infected at time $\ell - x_0$.
-We have to multiply the joint forward distribution $h$ by $\mathcal R_c (t) i(t)$, which represents total infectiousness of individuals infected at time $t$, rather than incidence $i(t)$, because we are interested in the backward incubation period $x_0$ and the forward generation interval $\sigma$ of infectors (i.e., those who transmitted successfully to at least one individual), rather than all infected individuals.
+We have to multiply the joint forward distribution $h$ by $\mathcal R_c (t) i(t)$, which represents total infectiousness of individuals infected at time $t$, rather than incidence $i(t)$, because we are interested in the backward incubation period $x_0$ and the forward generation interval $\sigma$ of infectors, rather than all infected individuals.
 We revisit this idea in the Results section.
@@
 b_\ell(\tau) &\propto j(\ell) f_{\ell}(\tau)\\
-&\propto \int_0^\infty \mathcal R_c (\ell - x_0) i(\ell-x_0) k(x_0) f_{\ell}(\tau) \mathrm{d} x_0
+&\propto \int_0^\infty i(\ell-x_0) k(x_0) f_{\ell}(\tau) \mathrm{d} x_0
 \end{aligned}
 \end{equation}
-where $j$ represents the incidence of symptomatic infectors.
+where $j$ represents the incidence of symptomatic cases.
 
@@
 
-Here, use a renewal equation to model the spread of disease in a population.
-Ignoring the dynamics of births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be written as:
+Here, use a renewal equation to model the spread of disease in a population:
 \begin{equation}
@@
 \end{equation}
-where $\mathcal R_0$ is the basic reproduction number, and $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
+where $\mathcal R_0$ is the basic reproduction number (i.e., the average number of secondary cases caused by a primary case  in a fully susceptible population), $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population), $S(t)$ is the proportion of susceptible individuals.
 Then, the forward generation-interval for a primary cohort $\ell$ follows \citep{champredon2015intrinsic}:
@@
 \end{equation}
-We compare this with an estimate of $\mathcal R$ based on naive serial-interval distribution that assumes that the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
+We compare this estimate with a naive estimate of ${\mathcal R}_{\textrm{\tiny naive}}$ that assumes that the backward and the forward incubation periods are identically distributed:
 \begin{equation}
@@
 \caption{
-\textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
-A. The forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number $\mathcal R$.
-B.
-The serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and $\mathcal R$.
-C. The mean forward serial interval during the exponential growth phase depends on $r$.
-D. The squared coefficient of variation of forward serial intervals during the exponential growth phase depends on $r$.
+\textbf{Estimates of the reproduction number from the exponential growth rate.}
 }
@@
 
-Both generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating $\mathcal R$ --- yet important quantities in characterizing an epidemic.
-Here, we provided a theoretical basis for understanding serial intervals and show that naively using the observed serial intervals may lead to biased conclusions in studying the COVID-19 pandemic.
-Concluding sentence.
+Both generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating $\mathcal R$ --- yet important quantities in describing an outbreak.
 

### 2020-04-17 forward.R
update

@@ -34,11 +34,21 @@ detdata <- data.frame(
   ci=rr$cI
 )
 
-g1 <- ggplot(sir_sim$data) +
+sir_data <- lapply(simlist, "[[", "data") %>%
+  bind_rows(.id="sim")
+
+sir_data2 <- sir_data %>%
+  mutate(
+    time=ceiling(time*5)/5
+  ) %>%
+  group_by(sim, time) %>%
+  filter(infected==max(infected))
+
+g1 <- ggplot(sir_data2) +
+  geom_line(aes(time, infected, col="Stochastic", group=sim)) +
   geom_line(data=detdata, aes(tvec, ci, col="Deterministic"), lwd=1) +
-  geom_line(aes(time, infected, col="Stochastic"), lwd=1) +
   scale_x_continuous("Time (days)", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_continuous("Cumulative incidence", expand=c(0, 0), limits=c(10, 49999)) +
+  scale_y_log10("Cumulative incidence", expand=c(0, 0), limits=c(10, 49999)) +
   scale_color_manual(values=c(1, "#D55E00")) +
   ggtitle("A") +
   theme(
@@ -48,6 +58,18 @@ g1 <- ggplot(sir_sim$data) +
   )
 
 tcut <- 0:40*2
+
+sir_sim <- lapply(simlist, function(x) {
+  data.frame(
+    t_infected=x$t_infected,
+    t_symptomatic=x$t_symptomatic,
+    infected_by=x$infected_by
+  )
+}) %>%
+  bind_rows(.id="sim") %>%
+  mutate(
+    infected_by=infected_by+(as.numeric(sim)-1)*40000
+  )
 
 incdata0 <- data.frame(
   cohort=sir_sim$t_infected,

### 2020-04-17 observedrR.R

@@ -18,11 +18,11 @@ tcut <- seq(10, 80, by=2)
 serdata0 <- data_frame(
   cohort=sir_sim$t_symptomatic[sir_sim$infected_by],
   tdiff=sir_sim$t_symptomatic-sir_sim$t_symptomatic[sir_sim$infected_by],
-  tobs=cohort+tdiff
+  tobs=pmax(cohort, cohort+tdiff)
 )
 
 R0_obs <- lapply(tcut, function(x) {
-  set.seed(123)
+  set.seed(101)
   tmp <- serdata0 %>%
     filter(tobs < x)
   
@@ -45,7 +45,7 @@ R0_obs <- lapply(tcut, function(x) {
   )
 
 R0_cohort <- lapply(tcut, function(x) {
-  set.seed(123)
+  set.seed(101)
   tmp <- serdata0 %>%
     filter(cohort < x)
   
@@ -74,7 +74,7 @@ g1 <- ggplot(R0all) +
   geom_line(aes(t, R0, col=type, lty=type)) +
   geom_hline(yintercept=rr$R0, lty=2) +
   scale_x_continuous("Time (days)", limits=c(0, 80), expand=c(0, 0)) +
-  scale_y_continuous("Reproduction number $\\mathcal R$", expand=c(0, 0)) +
+  scale_y_continuous("Reproduction number $\\mathcal R$", expand=c(0, 0), limits=c(1.3, 2.6)) +
   scale_color_manual(values=tail(cpalette, 2)) +
   scale_fill_manual(values=tail(cpalette, 2)) +
   theme(
@@ -82,6 +82,33 @@ g1 <- ggplot(R0all) +
     legend.position = c(0.85, 0.15),
     legend.title = element_blank()
   )
+
+gen_obs <- lapply(tcut, function(x) {
+  set.seed(101)
+  tmp <- serdata0 %>%
+    filter(tobs < x)
+  
+  gensamp <- replicate(nboot, {
+    ss <- tmp$tdiff
+    ss <- sample(ss, replace=TRUE)
+    mean(ss, na.rm=TRUE)
+  })
+  
+  data.frame(
+    t=x,
+    est=mean(tmp$tdiff, na.rm=TRUE),
+    lwr=quantile(gensamp, 0.025),
+    upr=quantile(gensamp, 0.975)
+  )
+}) %>%
+  bind_rows %>%
+  mutate(
+    type="Observed"
+  )
+
[…]

### 2020-04-17 sir_sim.R

@@ -1,5 +1,19 @@
 source("sir.R")
 
-sir_sim <- sir.full(size=40000, I0=10, seed=101, keep.intrinsic = TRUE)
+nsim <- 10
 
-save("sir_sim", file="sir_sim.rda")
+simlist <- vector('list', nsim)
+
+i <- 1
+
+while (i <= nsim) {
+  print(i)
+  sir_sim <- sir.full(size=40000, I0=10, seed=i, keep.intrinsic = TRUE)
+  
+  if (nrow(sir_sim$data) > 100) {
+    simlist[[i]] <- sir_sim
+    i <- i +1
+  }
+}
+
+save("simlist", file="sir_sim.rda")

### 2020-04-18 serial.tex
tweaks

--- 2020-04-17 serial.tex
@@
 the generation-interval distributions plays a key role in shaping the relationship between the exponential growth rate $r$ and the reproduction number $\mathcal R$ \citep{wallinga2007generation}.
-On the other hand, the serial interval is defined as the time between when an infector and an infectee become symptomatic \citep{svensson2007note}.
-While generation and serial intervals are conceptually similar,
-previously studies have often alluded to differences in their variances, despite having seemingly identical expected values \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence};
-some suggested that using serial intervals can give different estimates of $\mathcal R$ \citep{britton2019estimation}.
-Even though these distinctions were first made over a decade ago \citep{svensson2007note}, 
+Similarly, the serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
+While serial intervals are similar to generation intervals, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence};
+some studies further suggested that using serial intervals can give different estimates of $\mathcal R$ \citep{britton2019estimation}.
+Even these distributions were clearly distinguished over a decade ago \citep{svensson2007note}, 
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds:
@@
 
-The lack of clear understanding of their differences can be largely attributed to an apparent paradox.
+One important source of confusion comes down to an apparent paradox.
 When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
-This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number $\mathcal R$.
-Likewise, since infection typically leads to symptoms, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
+This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number $\mathcal R$ \citep{wallinga2007generation}.
+Likewise, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
 Therefore, both generation- and serial-interval distributions should give us identical estimates of  $\mathcal R$ based the observed epidemic growth rate $r$.
-However, current theory suggests that using generation- and serial-interval distributions give different estimates of $\mathcal R$ and contradicts our biological intution.
+In contexts where the distributions are expected to be different, current theory has no explanation for how they might link $r$ to \Rx\ in the same way.
 
-Here, we provide an answer to the decade-old paradox between generation and serial intervals.
-We present a novel framework for understanding serial intervals and show that the serial-interval distribution must be defined with reference to disease incidence;
-previous frameworks implicitly assume that incidence remains constant.
-We are show that both serial- and generation-interval distributions can give identical estimates of $\mathcal R$ based on the exponential growth phase of an epidemic if they are properly defined.
+Here, we provide an answer to this paradox, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
+We develop a new framework for understanding serial intervals and show that the forward serial-interval distribution gives the correct value of $\mathcal R$.
+\jd{Come back to this. Not just over time, right?}
 However, failing to account for changes in the observed serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
@@
 
-We first begin by describing a general framework for characterizing a distribution of time delays between \emph{any} two epidemiological events;
-these events can be defined either within an infected individual (e.g., infection and symptom onset of an individual) or between infected individuals (e.g., symptom onsets of an infector and an infectee).
+We first begin by describing a general framework for characterizing a distribution of time delays between two epidemiological events;
+these events can be defined either within an infected individual (e.g., infection and symptom onset of an individual, the incubation period) or between infected individuals (e.g., symptom onsets of an infector and an infectee, the serial interval).
 We can further divide these events into \emph{primary} and \emph{secondary} events.
-When we measure an epidemiological time delay within an infected individual (e.g., incubation period), the primary event always occurs before the secondary event.
-When we measure an epidemiological time delay between infected individuals (e.g., serial interval), 
+When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event always occurs before the secondary event.
+\jd{Rethink, or else rethink ``any'' above: the ``hidden'' time (my term) is the time between onset of infectiousness and onset of symptoms; it is within, but can be positive or negative.
+I'm not saying we should use it here\ldots}
+When we measure an epidemiological time delay between infected individuals (e.g., the serial interval), 
 the primary and secondary events are defined in terms of the direction of transmission:
@@
 a secondary cohort can be defined similarly based on the secondary events.
-For example, when we are measurign serial intervals, a primary cohort $s$ consists of all infectors who became symptomatic at time $s$.
-Then, for each primary cohort $s$, we can define the expected time distribution between primary and secondary events.
-We refer to this distribution as the forward delay distribution and denote it as $f_s(\tau)$.
+For example, when we are measuring serial intervals, a primary cohort $s$ consists of all infectors who became symptomatic at time $\ell$.
+Then, for each primary cohort $\ell$, we can define the expected time distribution between primary and secondary events.
+We refer to this distribution as the forward delay distribution and denote it as $f_\ell(\tau)$.
 The forward delay distributions can vary across primary cohorts.
 
-Likewise, we can define the backward delay distribution $b_s(\tau)$ for a secondary cohort $s$:
-The backward delay distribution for secondary host $s$ describes the time delays between a primary and secondary host given that the secondary event occurred at time $s$.
+Likewise, we can define the backward delay distribution $b_\ell(\tau)$ for a secondary cohort $\ell$:
+The backward delay distribution for secondary host $\ell$ describes the time delays between a primary and secondary host given that the secondary event occurred at time $\ell$.
 It follows that:
 \begin{equation}
-b_s(\tau) \propto C(s-\tau) f_{s-\tau}(\tau)
+b_\ell(\tau) \propto C(\ell-\tau) f_{\ell-\tau}(\tau)
 \end{equation}
-where $C(s)$ is the size of the primary cohort $s$.
-Therefore, changes in the backward delay distribution depends on the changes in cohort size $C(s)$ (therefore incidence of infection) as well as changes in the forward delay distribution.
+where $C(\ell)$ is the size of the primary cohort $\ell$.
+Therefore, changes in the backward delay distribution depends on the changes in cohort size $C(\ell)$ (therefore incidence of infection) as well as changes in the forward delay distribution.
 These ideas apply to all epidemiological delay distributions and generalize the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
@@
 Previous studies have often assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, they implicitly assume that incidence stays constant.
+however, these models implicitly assume that incidence stays constant.
 
@@
 Using the cohort-based framework provides a clear way of understanding the serial-interval distribution.
-Given that an infector became symptomatic at time $\ell$, we have to first go backward in time by asking when the infector was infected and go forward in time by asking when the infector infected infectee and when the infectee became symptomatic;
+Given that an infector became symptomatic at time $\ell$, we have to first go backward in time by asking when the infector was infected and then go forward in time by asking when the infector infected infectee and when the infectee became symptomatic;
 this defines the forward serial interval (\fref{diagram}A).
@@
 
-Here, use a renewal equation to model the spread of disease in a population.
+Here, we use a renewal equation to model the spread of disease in a population \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
 Ignoring the dynamics of births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be written as:
@@
 \end{equation}
-which allows us to separate the joint probability distribution $h_\ell$ of the forward incubation period and the forward generation-interval distribution as a product of joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals and the proportion of susceptible individuals $S$:
+which allows us to separate the joint probability distribution $h_\ell$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
 \begin{equation}
@@
 \end{equation}
-Finally, the cohort reproduction is defined as follows:
+Finally, the cohort reproduction for this model is defined as follows:
 \begin{equation}
@@
 
-First, we compare the estimates of the reproduction number $\mathcal R$ based on the intrinsic generation-interval distribution $g(\tau)$ and the forward serial-interval distribution during the exponential growth phase $f_{\textrm{\tiny exp}}(\tau)$ (\fref{rR}A).
-Both distributions provide identical estimates of $\mathcal R$ regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution.
+First, we compare the estimates of the reproduction number $\mathcal R$ based on the intrinsic generation-interval distribution $g(\tau)$ and the forward serial-interval distribution during the exponential growth phase $f_{\textrm{\tiny exp}}(\tau)$.
+Both distributions provide identical estimates of $\mathcal R$ regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
 On the other hand, using naive serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates $\mathcal R$;
@@
 Black lines represent the results of a deterministic simulation.
-Orange lines and points represent the results of a stochastic simulation.
+Orange lines and points represent the average of 10 stochastic simulations;
+cumulative incidence from the stochastic simulations in panel A are shown without averaging.
 Forward incubation periods and intrinsic generation-intervals are assumed to be independent of each other: $h(x_0, \sigma) = k(x_0) g(\sigma)$.
@@
 
-\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and the corresponding stochastic realization based on the Gillespie algorithm.
+\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and the corresponding stochastic realizations based on the Gillespie algorithm.
 The mean forward incubation period remains constant throughout an epidemic as expected (\fref{epi}B).
@@
 D. Correlation between the number of secondary cases and the incubation period for individuals who developed symptoms within the same time preiod.
+Black lines represent the results of a deterministic simulation.
+Orange lines and points represent the average of 10 stochastic simulations.
+Orange ribbons represent the 95\% confidence intervals.
 }
@@
 We further tease apart factors that affect the forward serial interval distribution.
-\fref{tease}A compares the mean forward serial interval calculated from a stochastic model (orange points) with their deterministically calculated values (black lines);
+\fref{tease}A compares the mean forward serial interval calculated from a deterministic model and its corresponding stochastic simulations;
 failing to account for changes in $\mathcal R_c$ in \eref{forward} overestimates the mean forward serial interval.
-A key distinction that needs to be made is that the forward serial-interval distributions depends on the backward incubation period of symptomatic infectors (i.e., those who were able to successfully spread the disease to another person), rather than the incubation period of all symptomatic cases (\fref{tease}B).
-Therefore, the cohort size of infectors must be calculated as a product of the cohort reproduction number and incidence.
+A key distinction that needs to be made is that the forward serial-interval distributions depend on the backward incubation period of symptomatic infectors (i.e., those who were able to successfully spread the disease to another person), rather than the incubation period of all symptomatic cases (including those who were not able to spread the disease).
+Therefore, the cohort size of infectors must be calculated as a product of the cohort reproduction number and incidence because cohorts with higher cohort reproduction numbers are more infectiouss and therefore more likely to be infectors.
 

### 2020-04-18 forward_tease.R

@@ -11,6 +11,18 @@ rr <- renewal_det()
 
 tcut <- 0:40*2
 
+sir_sim <- lapply(simlist, function(x) {
+  data.frame(
+    t_infected=x$t_infected,
+    t_symptomatic=x$t_symptomatic,
+    infected_by=x$infected_by
+  )
+}) %>%
+  bind_rows(.id="sim") %>%
+  mutate(
+    infected_by=infected_by+(as.numeric(sim)-1)*40000
+  )
+
 serdata0 <- data.frame(
   cohort=sir_sim$t_symptomatic[sir_sim$infected_by],
   tdiff=sir_sim$t_symptomatic-sir_sim$t_symptomatic[sir_sim$infected_by]
@@ -113,14 +125,15 @@ tmp <- data.frame(
   offspring=0
 )
 
-tmp$offspring[match(tt$Var1, tmp$N)] <- tt$Freq
+tmp$offspring[match(tt$Var1[-153138], tmp$N)] <- tt$Freq[-153138]
+tmp$offspring[tmp$N==3e5] <- tt$Freq[153138]
 
 cordat <- data.frame(
   cohort=sir_sim$t_symptomatic,
   tdiff=sir_sim$t_symptomatic-sir_sim$t_infected,
   offspring=tmp$offspring
 ) %>%
-  filter(!is.na(cohort), !is.na(tdiff), cohort > 4, cohort <= 80) %>%
+  filter(!is.na(cohort), !is.na(tdiff), cohort > 0, cohort <= 80) %>%
   mutate(
     cc=cut(cohort, tcut)
   ) %>%
@@ -141,7 +154,7 @@ cordat2 <- data.frame(
   tdiff=sir_sim$t_symptomatic-sir_sim$t_infected,
   offspring=tmp$offspring
 ) %>%
-  filter(!is.na(cohort), !is.na(tdiff), cohort > 0, cohort <= 78) %>%
+  filter(!is.na(cohort), !is.na(tdiff), cohort > 2, cohort <= 78) %>%
   mutate(
     cc=cut(cohort, tcut)
   ) %>%
@@ -159,22 +172,22 @@ cordat2 <- data.frame(
 
 g3 <- ggplot(cordat) +
   geom_hline(yintercept = 0, lty=2) +
-  geom_ribbon(aes(cc, ymin=lwr, ymax=upr), alpha=0.2) +
-  geom_line(aes(cc, cor)) +
[…]

### 2020-04-18 serial.tex
really need to go to bed

@@
 
-\begin{figure}[!th]
-\includegraphics[width=\textwidth]{forward.pdf}
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=0.95\textwidth]{forward.pdf}
 \caption{
@@
 }
+\end{center}
 \label{fig:epi}
@@
 
-\begin{figure}[!th]
+\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{observedrR.pdf}
@@
 \textbf{Estimates of the reproduction number from the observed serial intervals.}
+A. Changes in the observed and cohort-averaged mean serial interval over time.
+B. Changes in the estimate of $\mathcal R$ based on the observed and cohort-averaged mean serial interval over time.
+Each line represents an independent stochastic realization.
 }
@@
 \fref{obsrR} demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of $\mathcal R$.
-Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate $\mathcal R$ by a large amount because the observed serial-interval distribution does not account for changes in the forward serial-interval distribution.
-As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean forward serial-interval distribution during the exponential growth phase, which provides the correct linke between $r$ and $\mathcal R$.
+Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate the initial mean forward serial interval (\fref{obsrR}A) and therefore $\mathcal R_0$ (\fref{obsrR}) by a large amount because the observed serial-interval distribution does not account for changes in the forward serial-interval distribution.
+As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean of the initial forward serial-interval distribution, which provides the correct linke between $r$ and $\mathcal R$.
 
-We provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ retrospctively.
-Once a set of serial intervals has been observed, we can group observed serial intervals by their primary cohort times.
-Then, we can compare how estimates of $\mathcal R$ change as we include more cohorts into the analysis (see `cohort-averaged' in \fref{obsrR}).
-During the exponential growth phase, the estimates of $\mathcal R$ are consistent with the true value;
-adding more data allows us to make more precise inference about $\mathcal R$ during this period.
-However, the cohort-averaged estimates of $\mathcal R$ decreases rapidly soon after the exponential growth period.
-Confidence intervals associated with the cohort-averaged estimates of $\mathcal R$ becomes narrower and do not overlap with earlier estimates.
+We provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ \emph{retrospctively}.
+Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can group observed serial intervals by their primary cohort times.
+Then, we can compare how estimates of the mean serial interval and $\mathcal R$ change as we include more cohorts into the analysis (see `cohort-averaged' in \fref{obsrR}).
+During the exponential growth phase, the estimates of the mean serial interval and $\mathcal R$ are consistent with the target value;
+adding more data allows us to make more precise inference during this period.
+However, the cohort-averaged estimates decreases rapidly soon after the exponential growth period.
 This approach allows us to detect how changes in the forward serial intervals bias the estimates of $\mathcal R$.

### 2020-04-18 observedrR.R

@@ -6,8 +6,6 @@ library(tikzDevice)
 source("renewal_det.R")
 source("cpalette.R")
 
-nboot <- 200
-
 load("sir_sim.rda")
 
 rr <- renewal_det()
@@ -15,33 +13,80 @@ r <- rr$r
 
 tcut <- seq(10, 80, by=2)
 
+sir_sim <- lapply(simlist, function(x) {
+  data.frame(
+    t_infected=x$t_infected,
+    t_symptomatic=x$t_symptomatic,
+    infected_by=x$infected_by
+  )
+}) %>%
+  bind_rows(.id="sim") %>%
+  mutate(
+    infected_by=infected_by+(as.numeric(sim)-1)*40000
+  )
+
 serdata0 <- data_frame(
   cohort=sir_sim$t_symptomatic[sir_sim$infected_by],
   tdiff=sir_sim$t_symptomatic-sir_sim$t_symptomatic[sir_sim$infected_by],
-  tobs=pmax(cohort, cohort+tdiff)
+  tobs=pmax(cohort, cohort+tdiff),
+  sim=sir_sim$sim
 )
+
+ser_obs <- lapply(tcut, function(x) {
+  set.seed(101)
+  tmp <- serdata0 %>%
+    filter(tobs < x)
+  
+  tmp %>%
+    group_by(sim) %>%
+    summarize(
+      ser=mean(tdiff, na.rm=TRUE)
+    ) %>%
+    mutate(
+      t=x
+    )
+}) %>%
+  bind_rows %>%
+  mutate(
+    type="Observed"
+  )
 
 R0_obs <- lapply(tcut, function(x) {
   set.seed(101)
   tmp <- serdata0 %>%
     filter(tobs < x)
   
-  R0samp <- replicate(nboot, {
-    ss <- tmp$tdiff
-    ss <- sample(ss, replace=TRUE)
-    1/mean(exp(-r*ss), na.rm=TRUE)
-  })
-  
-  data.frame(
-    t=x,
-    R0=1/mean(exp(-r*tmp$tdiff), na.rm=TRUE),
-    lwr=quantile(R0samp, 0.025),
-    upr=quantile(R0samp, 0.975)
-  )
+  tmp %>%
+    group_by(sim) %>%
+    summarize(
+      R0=1/mean(exp(-r*tdiff), na.rm=TRUE)
+    ) %>%
+    mutate(
+      t=x
+    )
 }) %>%
   bind_rows %>%
   mutate(
     type="Observed"
+  )
+
[…]

### 2020-04-18 serial.tex
lunch time

@@
 
-%% \newcommand{\comment}{\showcomment}
-\newcommand{\comment}{\nocomment}
+\newcommand{\comment}{\showcomment}
+%% \newcommand{\comment}{\nocomment}
 
@@
 We can further divide these events into \emph{primary} and \emph{secondary} events.
-When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event always occurs before the secondary event.
+When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event \jd{is the event that always or usually} always occurs before the secondary event.
 \jd{Rethink, or else rethink ``any'' above: the ``hidden'' time (my term) is the time between onset of infectiousness and onset of symptoms; it is within, but can be positive or negative.
@@
 A primary cohort consists of \emph{all} individuals whose primary event occurred at a given time; 
-a secondary cohort can be defined similarly based on the secondary events.
+a secondary cohort is defined similarly based on the secondary events.
 For example, when we are measuring serial intervals, a primary cohort $s$ consists of all infectors who became symptomatic at time $\ell$.
@@
 We refer to this distribution as the forward delay distribution and denote it as $f_\ell(\tau)$.
-The forward delay distributions can vary across primary cohorts.
+%% The forward delay distributions can vary across primary cohorts.
+%% \jd already implied, and may block the flow
 
-Likewise, we can define the backward delay distribution $b_\ell(\tau)$ for a secondary cohort $\ell$:
-The backward delay distribution for secondary host $\ell$ describes the time delays between a primary and secondary host given that the secondary event occurred at time $\ell$.
+\jd{Thinking a lot about notation.
+I kind of want to make it easier for people to follow the logic by giving $\ell$ and $C$ different names.
+Like maybe P(t) for the primary-event cohort and D(t) for the secondary-event cohort?
+And then $\pi$ and $\delta$ instead of $\ell$?}
+Likewise, we define the backward delay distribution $b_\ell(\tau)$ for a secondary cohort $\ell$:
+The backward delay distribution describes the time delays between a primary and secondary host given that the secondary event occurred at time $\ell$.
 It follows that:
@@
 \end{equation}
+\jd{Brilliant, but would be easier to follow if more symmetric.
+Maybe start from the idea that we can add up events in either direction.
+Using the proposed notation, I might start from $D(\delta) b_\delta(\delta-\pi)  = P(\pi) f_\pi(\delta-\pi)$}
 where $C(\ell)$ is the size of the primary cohort $\ell$.
-Therefore, changes in the backward delay distribution depends on the changes in cohort size $C(\ell)$ (therefore incidence of infection) as well as changes in the forward delay distribution.
+Therefore, changes in the backward delay distribution depend on the changes in cohort size $C(\ell)$ (therefore incidence of infection) as well as changes in the forward delay distribution.
 These ideas apply to all epidemiological delay distributions and generalize the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
@@
 however, these models implicitly assume that incidence stays constant.
+\jd{I would drop the last clause. I still argue that this is true for intrinsic SIs, and we don't want to get into that here. You can just keep rolling forward at this point.}
 
@@
 
-Using the cohort-based framework provides a clear way of understanding the serial-interval distribution.
-Given that an infector became symptomatic at time $\ell$, we have to first go backward in time by asking when the infector was infected and then go forward in time by asking when the infector infected infectee and when the infectee became symptomatic;
-this defines the forward serial interval (\fref{diagram}A).
-Then, it is clear that $x_0$ represents the backward incubation period of infectors who became symptomatic at time $\ell$; 
+The cohort-based framework allows us to understand the distribution of serial intervals we expect to observe when incidence is changing.
+Given that an infector became symptomatic at time $\ell$, we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when the infectee became symptomatic;
+this defines the forward serial interval.
+In \fref{diagram}A, we see that $x_0$ represents the backward incubation period of infectors who became symptomatic at time $\ell$; 
 $\sigma$ represents the forward generation interval for individuals who came infected at time $\ell - x_0$ conditional on their incubation period $x_0$;
 and $x_1$ represents the forward incubation period for the infectees who became infected at time $\ell - x_0 + \sigma$.
+\jd{This needs more unpacking of what is conditional and why.
+We should spend some words talking about the fact that we expect forward internal intervals to be independent of dynamics (but not necessarily biology, I guess).}
 Assuming that the forward incubation distribution does not vary across cohorts, the forward serial interval distribution of a primary cohort $\ell$ can be written as follows:
+\jd{We should clearly state that we're always going to assume that intervals don't change intrinsically (or however we say it, the point is we're only going to think about changes that are driven by dynamics).}
 \begin{equation}

### 2020-04-18 serial.tex
Events paradigm

@@
 where $i$ is the incidence of infection, $h$ is the joint probability distribution of the forward incubation period and forward generation interval of a primary cohort $\ell - x_0$, and $k$ is a marginal probability distribution of $h$ describing the forward incubation periods:
+\jd{So obviously I was wrong about $k$; I get it now.
+I feel like the way to make this clear is similar to what DC and I did.
+First calculate the density of \emph{events}: this is the same numerator for the forward and backward distributions, the number of intervals that start at the beginning and end at the end; it's only the denominators that differ.
+I'm struggling again with \Rc: what matters is the number of susceptibles when I actually infected the infectee; using \Rc\ seems like we're averaging over something we shouldn't be averaging over.}
 \begin{equation}
@@
 
+\jd{An alternative approach that I'm pretty sure produces a slightly different answer. I'm going to write it in a mixed notation:}
+The number of SIs that go from $\delta_1$ to $\delta_2$ is an integral over all of the possibilities for the infection times.
+\begin{equation}
+	N(\delta_1, \delta_2) = \int \int d\alpha_1 d\alpha_2
+	i(\alpha_1) h(\delta_1-\alpha_1, \alpha_2-\alpha_1)
+	S(\alpha_2)\theta(\delta_2-\alpha_2)
+\end{equation}
+To get the forward SI, we substitute $\delta_2 = \delta_1+\tau$ and normalize. And so on.
 Likewise, we can define the backward serial interval distribution for a secondary cohort $\ell$ (\fref{diagram}B).

### 2020-04-19 serial.tex
Finish the ¶
minor changes

@@
 \end{equation}
-To get the forward SI, we substitute $\delta_2 = \delta_1+\tau$ and normalize. And so on.
+To get the forward SI, we substitute $\delta_2 = \delta_1+\tau$ and normalize. And a similar trick (from the same starting point) to get the backward SI.
+
 Likewise, we can define the backward serial interval distribution for a secondary cohort $\ell$ (\fref{diagram}B).
@@
 
-Here, we use a renewal equation to model the spread of disease in a population \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
-Ignoring the dynamics of births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be written as:
+We validate the theory by applying it to a specific example of an epidemic model. 
+We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
+Ignoring births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be written as:
 \begin{equation}

### 2020-04-19 serial.tex
this is hard and I need to sleep...

@@
 \newcommand{\Ro}{\Rx{0}}
+\newcommand{\Rc}{\Rx{c}}
 \newcommand{\RR}{\ensuremath{{\mathcal R}}}
@@
 }
-\newline
-Sang Woo Park
 \end{flushleft}
@@
 We develop a new framework for understanding serial intervals and show that the forward serial-interval distribution gives the correct value of $\mathcal R$.
-\jd{Come back to this. Not just over time, right?}
-However, failing to account for changes in the observed serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
+%\jd{Come back to this. Not just over time, right?} \swp{What do you mean? Everything is about time here... you haven't read the results section so maybe that's why?}
+However, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can bias the estimate of $\mathcal R$.
 We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of the ongoing pandemic.
@@
 We can further divide these events into \emph{primary} and \emph{secondary} events.
-When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event \jd{is the event that always or usually} always occurs before the secondary event.
-\jd{Rethink, or else rethink ``any'' above: the ``hidden'' time (my term) is the time between onset of infectiousness and onset of symptoms; it is within, but can be positive or negative.
+When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event is the event that always or usually occurs before the secondary event ---
+most epidemiological events that can be observed within an individual have clear direction (e.g., infection and onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
+% \jd{Rethink, or else rethink ``any'' above: the ``hidden'' time (my term) is the time between onset of infectiousness and onset of symptoms; it is within, but can be positive or negative.
 I'm not saying we should use it here\ldots}
@@
 a secondary cohort is defined similarly based on the secondary events.
-For example, when we are measuring serial intervals, a primary cohort $s$ consists of all infectors who became symptomatic at time $\ell$.
-Then, for each primary cohort $\ell$, we can define the expected time distribution between primary and secondary events.
-We refer to this distribution as the forward delay distribution and denote it as $f_\ell(\tau)$.
+For example, when we are measuring serial intervals, a primary cohort $s$ consists of all infectors who became symptomatic at time $\pi$.
+Then, for each primary cohort $\pi$, we can define the expected time distribution between primary and secondary events.
+We refer to this distribution as the forward delay distribution and denote it as $f_\pi(\tau)$.
 %% The forward delay distributions can vary across primary cohorts.
@@
 
-\jd{Thinking a lot about notation.
-I kind of want to make it easier for people to follow the logic by giving $\ell$ and $C$ different names.
-Like maybe P(t) for the primary-event cohort and D(t) for the secondary-event cohort?
-And then $\pi$ and $\delta$ instead of $\ell$?}
-Likewise, we define the backward delay distribution $b_\ell(\tau)$ for a secondary cohort $\ell$:
-The backward delay distribution describes the time delays between a primary and secondary host given that the secondary event occurred at time $\ell$.
-It follows that:
+Likewise, we define the backward delay distribution $b_\delta(\tau)$ for a secondary cohort $\delta$:
+The backward delay distribution describes the time delays between a primary and secondary host given that the secondary event occurred at time $\delta$.
+Since both forward and backward perspectives provide valid ways of measuring time delays, we can express the total density of primary and secondary events occurring at time $\pi$ and $\delta$, respectively, using both forward and backward delay distributions:
 \begin{equation}
-b_\ell(\tau) \propto C(\ell-\tau) f_{\ell-\tau}(\tau)
+P(\pi) f_\pi(\delta-\pi) = D(\delta) b_\delta(\delta-\pi),
 \end{equation}
-\jd{Brilliant, but would be easier to follow if more symmetric.
-Maybe start from the idea that we can add up events in either direction.
-Using the proposed notation, I might start from $D(\delta) b_\delta(\delta-\pi)  = P(\pi) f_\pi(\delta-\pi)$}
-where $C(\ell)$ is the size of the primary cohort $\ell$.
-Therefore, changes in the backward delay distribution depend on the changes in cohort size $C(\ell)$ (therefore incidence of infection) as well as changes in the forward delay distribution.
+where $P$ and $D$ represent the sizes of primary and secondary cohorts, respectively.
+Substituting $\tau = \delta - \pi$, it follows that:
+\begin{equation}
+b_\delta(\tau) = \frac{P(\delta-\tau) f_{\delta-\tau}(\tau)}{D(\delta)}
+\end{equation}
+Therefore, the backward delay distribution depends on the changes in primary cohort size $P$ (therefore incidence of infection) as well as changes in the forward delay distribution.
 These ideas apply to all epidemiological delay distributions and generalize the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
@@
 where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\sigma$ represents the realized generation interval.
-Previous studies have often assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, these models implicitly assume that incidence stays constant.
-\jd{I would drop the last clause. I still argue that this is true for intrinsic SIs, and we don't want to get into that here. You can just keep rolling forward at this point.}
+Previous studies have often assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
+% \jd{I would drop the last clause. I still argue that this is true for intrinsic SIs, and we don't want to get into that here. You can just keep rolling forward at this point.}
 
@@
 The cohort-based framework allows us to understand the distribution of serial intervals we expect to observe when incidence is changing.
-Given that an infector became symptomatic at time $\ell$, we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when the infectee became symptomatic;
+Given that an infector became symptomatic at time $\pi$, we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when the infectee became symptomatic;
 this defines the forward serial interval.
-In \fref{diagram}A, we see that $x_0$ represents the backward incubation period of infectors who became symptomatic at time $\ell$; 
-$\sigma$ represents the forward generation interval for individuals who came infected at time $\ell - x_0$ conditional on their incubation period $x_0$;
-and $x_1$ represents the forward incubation period for the infectees who became infected at time $\ell - x_0 + \sigma$.
+In \fref{diagram}A, we see that $x_0$ represents the backward incubation period of infectors who became symptomatic at time $\pi$; 
+$\sigma$ represents the forward generation interval for individuals who came infected at time $\pi - x_0$ conditioned on their incubation period $x_0$ (because generation intervals and incubation periods can be correlated \cite{klinkenberg2011correlation});
+and $x_1$ represents the forward incubation period for the infectees who became infected at time $\pi - x_0 + \sigma$.
+
 \jd{This needs more unpacking of what is conditional and why.

### 2020-04-19 serial.tex
k i think i actually need sleep

@@
 a secondary cohort is defined similarly based on the secondary events.
-For example, when we are measuring serial intervals, a primary cohort $s$ consists of all infectors who became symptomatic at time $\pi$.
+For example, when we are measuring serial intervals, a primary cohort $\pi$ consists of all infectors who became symptomatic at time $\pi$.
 Then, for each primary cohort $\pi$, we can define the expected time distribution between primary and secondary events.
@@
 The serial interval is defined as the time between when an infector becomes symptomatic and when and infectee becomes symptomatic.
-Serial intervals $\tau$ are typically written as:
+Serial intervals $\tau$ have been typically written in the form of:
 \begin{equation}
@@
 this defines the forward serial interval.
-In \fref{diagram}A, we see that $x_0$ represents the backward incubation period of infectors who became symptomatic at time $\pi$; 
-$\sigma$ represents the forward generation interval for individuals who came infected at time $\pi - x_0$ conditioned on their incubation period $x_0$ (because generation intervals and incubation periods can be correlated \cite{klinkenberg2011correlation});
+In \fref{diagram}A, we see that $x_0$ represents the backward incubation period of the infector who became symptomatic at time $\pi$;
+$\sigma$ represents the forward generation interval of the infector who came infected at time $\pi - x_0$;
 and $x_1$ represents the forward incubation period for the infectees who became infected at time $\pi - x_0 + \sigma$.
+
+Likewise, we can define the backward serial interval distribution for a secondary cohort $\delta$ (\fref{diagram}B).
+Given that an infectee became symptomatic at time $\delta$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
+then, we have to go forward in time by asking when the infector became symptomatic.
+In this case, $x_1$ represents the backward incubation period of the infectee who became symptomatic at time $\delta$;
+$\sigma$ represents the backward generation interval of the infectee who became infected at time $\delta-x_1$;
+and $x_0$ represents the forward incubation period of the infector who became infected at time $\delta-x_1-\sigma$.
+This conceptual framework clearly demonstrates that the distributions of $x_0$, $\delta$, and $x_1$ depend on the perspective as well as time and therefore cannot be treated statically.
+
+Then, the total number of serial intervals
 

### 2020-04-19 serial_guide.tex
k i think i actually need sleep

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-14 02:04:29
+% Created by tikzDevice version 0.12.3 on 2020-04-19 04:34:34
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,257.88) {$\ell$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,257.88) {$\pi$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,257.88) {$\ell-x_0$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,257.88) {$\pi-x_0$};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,257.88) {$\ell-x_0+\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,257.88) {$\pi-x_0+\sigma$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,257.88) {$\ell-x_0+\sigma+x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,257.88) {$\pi-x_0+\sigma+x_1$};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 41.07) {$\ell$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 41.07) {$\delta$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 41.07) {$\ell-x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 41.07) {$\delta-x_1$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 41.07) {$\ell-x_1-\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 41.07) {$\delta-x_1-\sigma$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 41.07) {$\ell-x_1-\sigma+x_0$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 41.07) {$\delta-x_1-\sigma+x_0$};
 

### 2020-04-19 serial_guide.R

@@ -17,13 +17,13 @@ g1 <- ggplot(arrow) +
   geom_point(aes(0.5, 0.2), size=3) +
   geom_point(aes(1.5, 0.4), size=3) +
   geom_point(aes(2.5, 0.3), size=3) +
-  annotate("text", x=1.5, y=-0.05, label="$\\ell$") +
-  annotate("text", x=0.5, y=-0.05, label="$\\ell-x_0$") +
+  annotate("text", x=1.5, y=-0.05, label="$\\pi$") +
+  annotate("text", x=0.5, y=-0.05, label="$\\pi-x_0$") +
   annotate("text", x=0.5, y=-0.1, label="Infector") +
   annotate("text", x=1.5, y=-0.1, label="Primary cohort") +
   annotate("text", x=2.5, y=-0.1, label="Infectee") +
-  annotate("text", x=2.5, y=-0.05, label="$\\ell-x_0+\\sigma$") +
-  annotate("text", x=3.5, y=-0.05, label="$\\ell-x_0+\\sigma+x_1$") +
+  annotate("text", x=2.5, y=-0.05, label="$\\pi-x_0+\\sigma$") +
+  annotate("text", x=3.5, y=-0.05, label="$\\pi-x_0+\\sigma+x_1$") +
   geom_segment(aes(x, y, xend=x1, yend=y1), arrow = arrow(length = unit(0.2, "inches")), lwd=1) +
   geom_segment(aes(0.5, 0, xend=0.5, yend=0.2), lty=2) +
   geom_segment(aes(1.5, 0, xend=1.5, yend=0.4), lty=2) +
@@ -57,10 +57,10 @@ g2 <- ggplot(arrow) +
   geom_point(aes(0.5, 0.3), size=3) +
   geom_point(aes(3.5, 0.4), size=3) +
   geom_point(aes(2.5, 0.2), size=3) +
-  annotate("text", x=3.5, y=-0.05, label="$\\ell$") +
-  annotate("text", x=2.5, y=-0.05, label="$\\ell-x_1$") +
-  annotate("text", x=0.5, y=-0.05, label="$\\ell-x_1-\\sigma$") +
-  annotate("text", x=1.5, y=-0.05, label="$\\ell-x_1-\\sigma+x_0$") +
+  annotate("text", x=3.5, y=-0.05, label="$\\delta$") +
+  annotate("text", x=2.5, y=-0.05, label="$\\delta-x_1$") +
[…]

### 2020-04-19 serial.tex
new framework

@@
 and $x_0$ represents the forward incubation period of the infector who became infected at time $\delta-x_1-\sigma$.
-This conceptual framework clearly demonstrates that the distributions of $x_0$, $\delta$, and $x_1$ depend on the perspective as well as time and therefore cannot be treated statically.
+This conceptual framework clearly demonstrates that the distributions of $x_0$, $\delta$, and $x_1$ (and therefore the distributions of serial intervals) depend on the perspective as well as time and cannot be treated statically.
 
-Then, the total number of serial intervals
+In order to define forward and backward serial interval distributions, we begin by writing the total number of serial intervals between time $\pi$ (when the infector developed symptoms) and $\delta$ (when the infectee developed symptoms), which can be expressed as an integral over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
+\begin{equation}
+T(\pi,\delta) = \int_{-\infty}^{\pi} \int_{\alpha_1}^{\delta} \mathcal R_c (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\delta - \alpha_2) \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1,
+\end{equation}
+where $\mathcal R_c(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}), $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee).
+Then, the forward serial-interval distribution is proportional to $T(\pi, \pi+\tau)$. Substituting $x=\pi-\alpha_1$ and $\sigma=\alpha_2-\alpha_1$, we have:
+\begin{equation}
+f_\pi(\tau) \propto \int_{0}^{\infty} \int_{0}^{x+\tau} \mathcal R_c (\pi-x) i(\pi-x) h_{\pi-x}(x, \sigma) k_{\pi-x+\sigma}(x-\sigma+\tau) \mathrm{d}\sigma\,\mathrm{d}x
+\end{equation}
+Likewise, the backward serial-interval distribution is proportional to $T(\delta-\tau, \delta)$. 
+This time, we substitute $x=\delta-\alpha_2$ and $\sigma=\alpha_2-\alpha_1$ to get:
+\begin{equation}
+b_\delta(\tau) \propto \int_{0}^{\infty} \int_{\max(0, \tau-x)}^{\infty} \mathcal R_c (\delta-x-\sigma) i(\delta-x-\sigma) h_{\delta-x-\sigma}(x+\sigma-\tau, \sigma) k_{\delta-x}(x) \mathrm{d}\sigma\,\mathrm{d}x.
+\end{equation}
 
-\jd{This needs more unpacking of what is conditional and why.
-We should spend some words talking about the fact that we expect forward internal intervals to be independent of dynamics (but not necessarily biology, I guess).}
-Assuming that the forward incubation distribution does not vary across cohorts, the forward serial interval distribution of a primary cohort $\ell$ can be written as follows:
-\jd{We should clearly state that we're always going to assume that intervals don't change intrinsically (or however we say it, the point is we're only going to think about changes that are driven by dynamics).}
-\begin{equation}
-f_\ell(\tau) \propto \int_{0}^\infty \int_{0}^\infty \mathcal R_c (\ell - x_0) i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma
-\label{eq:forward}
-\end{equation}
-where $i$ is the incidence of infection, $h$ is the joint probability distribution of the forward incubation period and forward generation interval of a primary cohort $\ell - x_0$, and $k$ is a marginal probability distribution of $h$ describing the forward incubation periods:
-\jd{So obviously I was wrong about $k$; I get it now.
-I feel like the way to make this clear is similar to what DC and I did.
-First calculate the density of \emph{events}: this is the same numerator for the forward and backward distributions, the number of intervals that start at the beginning and end at the end; it's only the denominators that differ.
-I'm struggling again with \Rc: what matters is the number of susceptibles when I actually infected the infectee; using \Rc\ seems like we're averaging over something we shouldn't be averaging over.}
-\begin{equation}
-k(x_0) = \int_0^\infty h_\ell(x_0, \sigma) \mathrm{d}\sigma.
-\end{equation}
-Finally, $\mathcal R_c (\ell - x_0)$ is the cohort reproduction number, which is defined as the average secondary number of cases caused by an individual infected at time $\ell - x_0$.
-We have to multiply the joint forward distribution $h$ by $\mathcal R_c (t) i(t)$, which represents total infectiousness of individuals infected at time $t$, rather than incidence $i(t)$, because we are interested in the backward incubation period $x_0$ and the forward generation interval $\sigma$ of infectors (i.e., those who transmitted successfully to at least one individual), rather than all infected individuals.
-We revisit this idea in the Results section.
-
-\jd{An alternative approach that I'm pretty sure produces a slightly different answer. I'm going to write it in a mixed notation:}
-The number of SIs that go from $\delta_1$ to $\delta_2$ is an integral over all of the possibilities for the infection times.
-\begin{equation}
-	N(\delta_1, \delta_2) = \int \int d\alpha_1 d\alpha_2
-	i(\alpha_1) h(\delta_1-\alpha_1, \alpha_2-\alpha_1)
-	S(\alpha_2)\theta(\delta_2-\alpha_2)
-\end{equation}
-To get the forward SI, we substitute $\delta_2 = \delta_1+\tau$ and normalize. And a similar trick (from the same starting point) to get the backward SI.
-
-Likewise, we can define the backward serial interval distribution for a secondary cohort $\ell$ (\fref{diagram}B).
-Given that an infectee became symptomatic at time $\ell$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
-then, we have to go forward in time by asking when the infector became symptomatic.
-In this case, $x_1$ and $\sigma$ represent the backward incubation period and generation interval, respectively, and $x_0$ represents the forward incubation period.
-Therefore, the backward serial interval distribution of a secondary cohort $\ell$ can be written as follows
-\begin{equation}
-\begin{aligned}
-b_\ell(\tau) &\propto j(\ell) f_{\ell}(\tau)\\
-&\propto \int_0^\infty \mathcal R_c (\ell - x_0) i(\ell-x_0) k(x_0) f_{\ell}(\tau) \mathrm{d} x_0
-\end{aligned}
-\end{equation}
-where $j$ represents the incidence of symptomatic infectors.
+%Hereafter, we assume that the forward incubation period distributions does not vary across cohorts over the course of an epidemic, as they represent the natural history of a disease, and use $k$ without subscript instead:
+%\begin{equation}
+%k(x) = \int_0^\infty h_\pi(x, \sigma) \mathrm{d}\sigma.
+%\end{equation}
 

### 2020-04-19 serial.tex
more more more

@@
 Here, we provide an answer to this paradox, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
-We develop a new framework for understanding serial intervals and show that the forward serial-interval distribution gives the correct value of $\mathcal R$.
+We develop a new framework for understanding serial intervals and show that the initial forward serial-interval distribution gives the correct value of $\mathcal R$.
 %\jd{Come back to this. Not just over time, right?} \swp{What do you mean? Everything is about time here... you haven't read the results section so maybe that's why?}
@@
 \begin{equation}
-f_\pi(\tau) \propto \int_{0}^{\infty} \int_{0}^{x+\tau} \mathcal R_c (\pi-x) i(\pi-x) h_{\pi-x}(x, \sigma) k_{\pi-x+\sigma}(x-\sigma+\tau) \mathrm{d}\sigma\,\mathrm{d}x
+f_\pi(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \mathcal R_c (\pi-x) i(\pi-x) h_{\pi-x}(x, \sigma) k_{\pi-x+\sigma}(x-\sigma+\tau) \mathrm{d}\sigma\,\mathrm{d}x
 \end{equation}
@@
 \end{equation}
-
-%Hereafter, we assume that the forward incubation period distributions does not vary across cohorts over the course of an epidemic, as they represent the natural history of a disease, and use $k$ without subscript instead:
-%\begin{equation}
-%k(x) = \int_0^\infty h_\pi(x, \sigma) \mathrm{d}\sigma.
-%\end{equation}
 
@@
 where $\mathcal R_0$ is the basic reproduction number, and $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
-Then, the forward generation-interval for a primary cohort $\ell$ follows \citep{champredon2015intrinsic}:
+Then, the forward generation-interval for a primary cohort $\pi$ follows \citep{champredon2015intrinsic}:
 \begin{equation}
-g_\ell (\tau) \propto g(\tau) S(\ell + \tau),
+g_\pi (\tau) \propto g(\tau) S(\pi + \tau),
 \end{equation}
-which allows us to separate the joint probability distribution $h_\ell$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
+which allows us to separate the joint probability distribution $h_\pi$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
 \begin{equation}
-h_\ell (x_0, \tau) \propto h(x_0, \tau) S(\ell + \tau),
+h_\pi (x, \tau) \propto h(x, \tau) S(\pi + \tau).
 \end{equation}
-which satisfies the following:
+We further assume that the forward incubation period distributions does not vary across cohorts over the course of an epidemic, as they represent the natural history of a disease, and use $k$ without subscript instead.
+Then, we have:
 \begin{equation}
-g(\tau) = \int_0^\infty h(x_0, \tau) \mathrm{d}x_0.
+\begin{aligned}
+k(x) &= \int_0^\infty h(x, \tau) \mathrm{d}\tau\\
+g(\tau) &= \int_0^\infty h(x, \tau) \mathrm{d}x.
+\end{aligned}
 \end{equation}
-Finally, the cohort reproduction for this model is defined as follows:
+Finally, the case reproduction for this model is defined as follows:
 \begin{equation}
@@
 forward serial-interval distributions describe the renewal process of symptomatic cases.
-Therefore, the forward serial-interval distribution $f_{\textrm{\tiny exp}}(\tau)$ during the exponential growth phase provides the identical $r$--$\mathcal R$ link as the intrinsic generation-interval distribution:
+Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to provide the identical $r$--$\mathcal R$ link as the intrinsic generation-interval distribution:
 \begin{equation}
-\frac{1}{\mathcal R} = \int_{-\infty}^\infty \exp(-r\tau) f_{\textrm{\tiny exp}}(\tau) \mathrm{d} \tau,
+\frac{1}{\mathcal R} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
 \end{equation}
-where the forward serial-interval distribution during the exponential growth phase is defined as:
+where the initial forward serial-interval distribution is defined as:
 \begin{equation}
-f_{\textrm{\tiny exp}}(\tau) \propto \int_{0}^\infty \int_{0}^\infty \exp( -r x_0) h(x_0, \sigma) k(\tau-\sigma+x_0) \mathrm{d} x_0\, \mathrm{d}\sigma.
+f_{0}(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \exp(-rx) h(x, \sigma) k(x-\sigma+\tau) \mathrm{d}\sigma\,\mathrm{d}x
 \end{equation}
@@
 
-We note that the forward serial-interval distribution depends on the exponential growth rate $r$.
-When the epidemic grows fast (high $r$), we expect the backward incubation period to be short, and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation-interval distribution.
-The Susceptible-Exposed-Infected-Recovered model, which assumes that incubation and exposed periods are equivalent, is a special case where the conditional forward generation-interval distribution cancels out with the backward generation-interval distribution exactly because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector;
-in this case, the forward serial- and generation-intervals have the same distributions during the exponential growth phase.
+The initial forward serial-interval distribution depends on the exponential growth rate $r$.
+For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short, and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation-interval distribution.
+The Susceptible-Exposed-Infected-Recovered model, which assumes that incubation and exposed periods are equivalent, is a special case where the conditional forward generation-interval distribution cancels out with the backward incubation period distribution exactly because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector;
+in this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase.
 
@@
 \begin{equation}
-{\mathcal R}_{\textrm{\tiny naive}} = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r T_i)},
+{\mathcal R}_{\textrm{\tiny naive}} = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r Q_i)},
 \end{equation}
@@
 \begin{equation}
-T_i = -A_i + (G_i|A_i) + I_i.
+Q_i = -A_i + (G_i|A_i) + I_i.
 \end{equation}
@@
 
-First, we compare the estimates of the reproduction number $\mathcal R$ based on the intrinsic generation-interval distribution $g(\tau)$ and the forward serial-interval distribution during the exponential growth phase $f_{\textrm{\tiny exp}}(\tau)$.
-Both distributions provide identical estimates of $\mathcal R$ regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
-On the other hand, using naive serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates $\mathcal R$;
+The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $g(\tau)$ give identical estimates of $\mathcal R$ regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
+However, using naive serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates $\mathcal R$;
 as $r$ increases, ${\mathcal R}_{\textrm{\tiny naive}}$ saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
-While the forward serial intervals during the exponential growth phase can be also negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation period (and therefore less negative serial intervals).
+While the forward serial intervals during the exponential growth phase can be also negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation periods (and therefore a lower proportion of negative serial intervals).
 
@@
 
-Comapring the shapes of forward serial-interval distributions and the intrinsic generation-interval distribution allow us to better understand how they are able to give identical estimates of $\mathcal R$.
+Comapring the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different distributoins are able to give identical estimates of $\mathcal R$.
 In general, generation-interval distributions with higher means and less variability are expected to give higher $\mathcal R$ for a given $r$.
-In this case, the forward serial intervals during the exponential growth phase have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
+In this case, the initial forward serial intervals during the exponential growth phase have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
 The effects of higher means (which increases $\mathcal R$) and higher variability (which decreases $\mathcal R$) cancel out exactly;
-therefore, we estimate the same $\mathcal R$ using both serial and generation intervals.
+therefore, we can estimate the same $\mathcal R$ using both serial and generation intervals.
 
@@
 
-\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and the corresponding stochastic realizations based on the Gillespie algorithm.
-The mean forward incubation period remains constant throughout an epidemic as expected (\fref{epi}B).
-The mean forward generation interval contracts as the epidemic progresses because an infected individual is less likely to infect another person as the proportion of susceptible individuals decreases (\fref{epi}C; \cite{champredon2015intrinsic}).
-In contrast, the mean serial interval depends on previous incidence and therefore decreases over time (\fref{epi}D):
-When incidence is increasing, symptomatic individuals are more likely to have been infected more recently (shorter backward incubation period and therefore longer forward serial interval) whereas when incidence is decreasing, symptomatic individuals are more likely to have been infected later (longer backward incubation period and therefore shorter forward serial interval).
-Qualitative patterns in the changes in the mean backward delays is robust across all delay distributions because they are predominantly driven by the changes in incidence (\fref{epi}D).
+\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on the Gillespie algorithm.
+The mean forward incubation period remains constant throughout an epidemic as assumed (\fref{epi}B).
+The mean forward generation interval decreases slightly as the epidemic progresses because an infected individual is less likely to infect another person as the proportion of susceptible individuals decreases (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
+In contrast, the mean forward serial interval decreases over time (\fref{epi}D).
 
-\begin{figure}[!th]
-\includegraphics[width=\textwidth]{forward_tease.pdf}
-\caption{
-\textbf{Dynamical correlations between incubation periods and the number of secondary cases.}
-A. The mean forward serial interval depends on changes in the cohort reproduction number.
-B. The mean backward incubation period of infectors is higher than the mean backward incubation period of all symptomatic cases.
-C. Correlation between the number of secondary cases and the incubation period for individuals who got infected within the same time preiod.
-D. Correlation between the number of secondary cases and the incubation period for individuals who developed symptoms within the same time preiod.
-Black lines represent the results of a deterministic simulation.
-Orange lines and points represent the average of 10 stochastic simulations.
-Orange ribbons represent the 95\% confidence intervals.
-}
-\label{fig:tease}
-\end{figure}
+Earlier, we demonstrated that the forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation periods of infectors, (ii) the forward generation intervals, and (iii) the forward incubation periods of infectees.
+Since both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant, changes in the forward serial-interval distributions are predominantly driven by the changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
+In this case, the increase in the mean backward incubation period directly translates to the decrease in the mean forward serial interval.
 
-We further tease apart factors that affect the forward serial interval distribution.
-\fref{tease}A compares the mean forward serial interval calculated from a deterministic model and its corresponding stochastic simulations;
-failing to account for changes in $\mathcal R_c$ in \eref{forward} overestimates the mean forward serial interval.
-A key distinction that needs to be made is that the forward serial-interval distributions depend on the backward incubation period of symptomatic infectors (i.e., those who were able to successfully spread the disease to another person), rather than the incubation period of all symptomatic cases (including those who were not able to spread the disease).
-Therefore, the cohort size of infectors must be calculated as a product of the cohort reproduction number and incidence because cohorts with higher cohort reproduction numbers are more infectiouss and therefore more likely to be infectors.
-
-Comparing the backward incubation period of infectors and all symptomatic cases provides an important, but counterintuitive, insight (\fref{tease}B).
-Given a cohort of symptomatic cases, individuals who were able to successfully spread the disease to others have longer incubation periods, on average,
-because individuals with longer incubation period are infected earlier and have a higher chance of infecting others (i.e., higher $\mathcal R_c$) during the susceptible depletion phase.
-Therefore, the backward incubation period of a symptomatic case and the number of secondary cases caused by that individual are dynamically correlated (\fref{tease}D).
-This correlation disappears when we take the forward perspective, demonstrating the importance of perspective-dependency in studying epidemiological delay distributions (\fref{tease}C).
+Qualitative patterns in the changes in the mean backward delays is robust across all delay distributions because they are predominantly driven by the changes in incidence (\fref{epi}D--F).
+During the exponential growth phase, the backward delays are short: individuals are
 

### 2020-04-19 forward_tease.R

@@ -192,7 +192,10 @@ g4 <- ggplot(cordat2) +
     panel.grid = element_blank()
   )
 
-tikz(file = "forward_tease.tex", width = 8, height = 6, standAlone = T)
-grid.arrange(g1, g2, g4, g3, nrow=2)
+tikz(file = "forward_tease.tex", width = 8, height = 3, standAlone = T)
+grid.arrange(g2 +
+               ggtitle("A. Incubation period"),
+             g3 +
+               ggtitle("B. Backward correlation") , nrow=1)
 dev.off()
 tools::texi2dvi('forward_tease.tex', pdf = T, clean = T)

### 2020-04-19 renewal_det.R

@@ -56,6 +56,8 @@ renewal_det <- function(R0=2.5,
   mfser2 <- head(sapply((genmax+1):(length(Svec)), function(x) sum(backwardinc2[,x-genmax]*rev(mfgen[(x-genmax):x]))),-genmax) +
     tail(mfinc, -genmax) - head(mbinc2, -genmax)
   
+  
+  
   list(
     tvec=head(tvec, -2*genmax),
     cI=tail(head(cumsum(Ivec), -genmax), -genmax),

### 2020-04-19 serial.tex
first draft

@@
 
-During the initial phase of an epidemic, the proprotion susceptible remains constant ($S(t) = S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
+During the initial phase of an epidemic, the proportion susceptible remains constant ($S(t) = S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
 Then, we can estimate the reproduction number from the exponential growth rate $r$ via the Euler-Lotka equation:
@@
 To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and correlation $\rho$;
-the multivariate log-normal distribution is parameterized based on pameter estimates for COVID-19 (Table 1).
+the multivariate log-normal distribution is parameterized based on parameter estimates for COVID-19 (Table 1).
 We construct forward serial intervals during the exponential growth period as follows:
@@
 
-Comapring the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different distributoins are able to give identical estimates of $\mathcal R$.
+Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different distributions are able to give identical estimates of $\mathcal R$.
 In general, generation-interval distributions with higher means and less variability are expected to give higher $\mathcal R$ for a given $r$.
@@
 
-Earlier, we demonstrated that the forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation periods of infectors, (ii) the forward generation intervals, and (iii) the forward incubation periods of infectees.
+Earlier, we showed that the forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation periods of infectors, (ii) the forward generation intervals, and (iii) the forward incubation periods of infectees.
 Since both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant, changes in the forward serial-interval distributions are predominantly driven by the changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
@@
 Qualitative patterns in the changes in the mean backward delays is robust across all delay distributions because they are predominantly driven by the changes in incidence (\fref{epi}D--F).
-During the exponential growth phase, the backward delays are short: individuals are
+When incidence increases exponentially, individuals are more likely to have been infected more recently and therefore, we are more likely to observe shorter intervals.
+Similarly, when incidence decreases, we are more likely to observe longer intervals.
 
@@
 Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate the initial mean forward serial interval (\fref{obsrR}A) and therefore $\mathcal R_0$ (\fref{obsrR}) by a large amount because the observed serial-interval distribution does not account for changes in the forward serial-interval distribution.
-As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean of the initial forward serial-interval distribution, which provides the correct linke between $r$ and $\mathcal R$.
+As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean of the initial forward serial-interval distribution, which provides the correct link between $r$ and $\mathcal R$.
 
-We provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ \emph{retrospctively}.
+We provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ \emph{retrospectively}.
 Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can group observed serial intervals by their primary cohort times.
@@
 Previous studies have often (i) recommended using up-to-date serial intervals, (ii) assumed that the serial interval distribution remains constant, and (iii) applied serial interval distributions estimated from one location to analyzing epidemics in other locations;
-however, these approaches implicitly ignore spatiotemporal variation in incidence and may therefore give systemtatically biased estimates of $\mathcal R$. 
+however, these approaches implicitly ignore spatiotemporal variation in incidence and may therefore give systematically biased estimates of $\mathcal R$. 
 For example, given geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the forward serial interval distributions will vary across different countries.
@@
 not explicitly accounting for their correlations can bias the estimate of the intrinsic generation-interval distribution from the serial-interval distribution (see Appendix).
-Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the effect of right-censoring or differences between the backward incubation period of an infector and the forward incubation period of an infecteee.
+Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the effect of right-censoring or differences between the backward incubation period of an infector and the forward incubation period of an infectee.
 There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.
@@
 In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult.
-For example, symotom onset dates cannot be used as a reliable proxy for the direction of transmission as infectees may develop symptoms before their infectors.
-Based on the COVID-19 paramters (Table 1), we expect roughly 3\% of infectees to develop symptoms before their infectors during the exponential growth period; 
+For example, symptom onset dates cannot be used as a reliable proxy for the direction of transmission as infectees may develop symptoms before their infectors.
+Based on the COVID-19 parameters (Table 1), we expect roughly 3\% of infectees to develop symptoms before their infectors during the exponential growth period; 
 this probability increases as epidemic progresses because backward incubation period of an infector increases.

### 2020-04-20 serial.tex
no more dynamical correlation... doesn't seem too important for now

@@
 
+The initial forward serial interval distribution only applies to the exponential growth phase of an epidemic.
+Nowm, we characterize how forward and backward serial intervals vary over the course of an epidemic when incubation periods and generation intervals are independent.
 \fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on the Gillespie algorithm.
@@
 
-Earlier, we showed that the forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation periods of infectors, (ii) the forward generation intervals, and (iii) the forward incubation periods of infectees.
+The forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation periods of infectors, (ii) the forward generation intervals, and (iii) the forward incubation periods of infectees.
 Since both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant, changes in the forward serial-interval distributions are predominantly driven by the changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
 In this case, the increase in the mean backward incubation period directly translates to the decrease in the mean forward serial interval.
+We note that the relative contributions of the three distributions depend on their shapes and correlations between incubation periods and generation intervals --- as discussed earlier, the backward incubation period has ``no'' effect on the forward serial intervals in the SEIR model because transmission always occurs after symptom onset.
 
@@
 When incidence increases exponentially, individuals are more likely to have been infected more recently and therefore, we are more likely to observe shorter intervals.
-Similarly, when incidence decreases, we are more likely to observe longer intervals.
+When incidence decreases, we are more likely to observe longer intervals for similar but opposite reasons.
+Since changes in incidence can occur even in the absence of significant susceptible depletion (e.g., due to intervention), we expect the qualitative patterns in the changes of backward delay distributions to be robust across many outbreaks.
 

### 2020-04-20 forward_tease.R

@@ -122,26 +122,28 @@ tt <- as.data.frame(table(sir_sim$infected_by))
 
 tmp <- data.frame(
   N=1:length(sir_sim$t_infected),
-  offspring=0
+  offspring=0,
+  sim=sir_sim$sim
 )
 
 tmp$offspring[match(tt$Var1[-153138], tmp$N)] <- tt$Freq[-153138]
 tmp$offspring[tmp$N==3e5] <- tt$Freq[153138]
 
 cordat <- data.frame(
-  cohort=sir_sim$t_symptomatic,
-  tdiff=sir_sim$t_symptomatic-sir_sim$t_infected,
-  offspring=tmp$offspring
+  cohort=sir_sim$t_symptomatic[sir_sim$infected_by],
+  tdiff=sir_sim$t_symptomatic[sir_sim$infected_by]-sir_sim$t_infected[sir_sim$infected_by],
+  tgen=sir_sim$t_infected-sir_sim$t_infected[sir_sim$infected_by],
+  infected_by=sir_sim$infected_by
 ) %>%
-  filter(!is.na(cohort), !is.na(tdiff), cohort > 0, cohort <= 80) %>%
+  filter(!is.na(cohort), !is.na(tdiff), cohort > 10, cohort <= 76) %>%
   mutate(
     cc=cut(cohort, tcut)
   ) %>%
   group_by(cc) %>%
   summarize(
-    cor=cor(tdiff, offspring),
-    lwr=cor.test(tdiff, offspring)[[9]][1],
-    upr=cor.test(tdiff, offspring)[[9]][2]
+    cor=cor(tdiff, tgen),
+    lwr=cor.test(tdiff, tgen)[[9]][1],
+    upr=cor.test(tdiff, tgen)[[9]][2]
   ) %>%
   ungroup %>%
   mutate(
@@ -149,16 +151,17 @@ cordat <- data.frame(
     cc=(as.numeric(gsub("\\(", "", gsub(",.*", "", cc)))+as.numeric(gsub("]", "", gsub(".*,", "", cc))))/2
   )
 
-cordat2 <- data.frame(
-  cohort=sir_sim$t_infected,
+cordat <- data.frame(
+  cohort=sir_sim$t_symptomatic,
   tdiff=sir_sim$t_symptomatic-sir_sim$t_infected,
-  offspring=tmp$offspring
+  offspring=tmp$offspring,
+  sim=sir_sim$sim
 ) %>%
[…]

### 2020-04-20 serial.tex
stuff

@@
 Similarly, the serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
-While serial intervals are similar to generation intervals, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence};
+While serial intervals are similar to generation intervals, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence};
 some studies further suggested that using serial intervals can give different estimates of $\mathcal R$ \citep{britton2019estimation}.
@@
 \textbf{Illustration of forward and backward serial intervals.}
-A. The forward serial interval for a primary cohort $\ell$ (i.e., an infector who became symptomatic at time $\ell$).
+(A) The forward serial interval for a primary cohort $\ell$ (i.e., an infector who became symptomatic at time $\ell$).
 In this case, $x_0$ represents the backward incubation period of the infector;
@@
 and $x_1$ represents the forward incubation period of the infectee.
-B. The backward serial interval for a secondary cohort $\ell$ (i.e., an infectee who became symptomatic at time $\ell$).
+(B) The backward serial interval for a secondary cohort $\ell$ (i.e., an infectee who became symptomatic at time $\ell$).
 In this case, $x_0$ represents the forward incubation period of the infector;
@@
 \textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
-A. The forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number $\mathcal R$.
-B.
-The serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and $\mathcal R$.
-C. The mean forward serial interval during the exponential growth phase depends on $r$.
-D. The squared coefficient of variation of forward serial intervals during the exponential growth phase depends on $r$.
+(A). The forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number $\mathcal R$.
+(B) The serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and $\mathcal R$.
+(C) The mean forward serial interval during the exponential growth phase depends on $r$.
+(D) The squared coefficient of variation of forward serial intervals during the exponential growth phase depends on $r$.
 }
@@
 \textbf{Epidemiological dynamics and changes in mean forward and backward delay distributions.}
-A. Cumulative incidence over time.
-B-D. Changes in the mean forward incubation period, generation interval, and serial interval.
-E-G. Changes in the mean backward incubation period, generation interval, and serial interval.
+(A) Cumulative incidence over time.
+(B--D) Changes in the mean forward incubation period, generation interval, and serial interval.
+(E--G) Changes in the mean backward incubation period, generation interval, and serial interval.
 Black lines represent the results of a deterministic simulation.
@@
 \textbf{Estimates of the reproduction number from the observed serial intervals.}
-A. Changes in the observed and cohort-averaged mean serial interval over time.
-B. Changes in the estimate of $\mathcal R$ based on the observed and cohort-averaged mean serial interval over time.
+(A) Changes in the observed and cohort-averaged mean serial interval over time.
+(B) Changes in the estimate of $\mathcal R$ based on the observed and cohort-averaged mean serial interval over time.
 Each line represents an independent stochastic realization.
@@
 
-We provide a simple, heuristic way of assessing potential biases in the estimate of $\mathcal R$ \emph{retrospectively}.
-Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can group observed serial intervals by their primary cohort times.
-Then, we can compare how estimates of the mean serial interval and $\mathcal R$ change as we include more cohorts into the analysis (see `cohort-averaged' in \fref{obsrR}).
+We provide a simple, heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore $\mathcal R$ retrospectively.
+Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can group observed serial intervals by their primary cohort times (i.e., symptom onset times of infectors).
+Then, we can compare how estimates of the mean serial interval as well as $\mathcal R$ change as we include more recent cohorts into the analysis (see `cohort-averaged' in \fref{obsrR}).
 During the exponential growth phase, the estimates of the mean serial interval and $\mathcal R$ are consistent with the target value;
@@
 However, the cohort-averaged estimates decreases rapidly soon after the exponential growth period.
-This approach allows us to detect how changes in the forward serial intervals bias the estimates of $\mathcal R$.
+This approach allows us to characterize potential biases in the estimates of $\mathcal R$ cuased by changes in the forward serial-interval distributions.
 
@@
 \caption{
-\textbf{Observed serial intervals of COVID-19 and estimates of $\mathcal R$.}
+\textbf{Observed serial intervals of COVID-19 and cohort-averaged estimates of $\mathcal R$.}
+(A--B) forward and backward serial intervals over time.
+Points represent the means. Vertical error bars represent the observed maximum and minimum values.
+Solid lines and ribbons represent the estimated locally estimated scatterplot smoothing (LOESS) fits and associated 95\% confidence intervals.
+The dashed line represents the maximum observable delay calculated from the most recent observed symptom onset date.
+(C) Cohort-averaged estimates of $\mathcal R$ assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
+Ribbons represent the associated 95\% bootstrap confidence intervals.
 }
@@
 
-Finally, we revisit serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on transmission events reported between January 21--February 8, 2020;
-they estimated the mean serial of 3.96 days (95\% CI 3.53–4.39 days) and $\mathcal R_0$ of 1.32 (95\% CI 1.16–1.48).
-\fref{du}A shows changes in the forward serial-interval distribution across cohorts.
-While the observed serial intervals may be subject to right-censoring, increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution.
-\fref{du}B shows the cohort-averaged estimates of $\mathcal R_0$, which remain constant until day 7 and suddenly decreases.
-The early cohort-averaged estimates are also consistent with earlier estimates.
-This example clearly demonstrates the danger of naively averaging the observed serial intervals and calculating the reproduction number from them.
+Finally, we reanalyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on transmission events reported between January 21--February 8, 2020;
+\cite{du2020serial} estimated the mean serial of 3.96 days (95\% CI 3.53–4.39 days) and $\mathcal R_0$ of 1.32 (95\% CI 1.16–1.48).
+\fref{du}A shows that the mean forward serial interval decreases over time.
+While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the maximum observed serial intervals and maximum \emph{observable} serial intervals),  increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution.
+\fref{du}B shows that the mean backward serial interval increases over time.
+While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculate earlier based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
+These results indicate that previous estimates of incubation period and generation-intervals may have been underestimated as neither studies explicitly account for right-censoring (Table 1).
+We do not explicitly account for the right-censoring as it is beyond the scope of this study.
+
+\fref{du}C shows the cohort-averaged estimates of $\mathcal R_0$, which remain roughly constant until day 7 and suddenly decreases, as expected from our simulation study (\fref{obsrR}).
+The estimates of $\mathcal R_0$ based on the early forward serial intervals are also consistent with previous estimates of $\mathcal R_0$ of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}.
+We note that early cohort-averaged estimates of $\mathcal R_0$ are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
+This example clearly demonstrates the danger of naively averaging the observed serial intervals and calculating the reproduction number using them.
 
@@
 Characterizing generation- and serial-interval distributions are critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
-Generation intervals measure the time difference between infection of a transmission pair, whereas serial intervals measure the time difference between symptom onset of a transmission pair.
-Due to their similar definitions, their differences have been inaccurately captured and misunderstood.
+Generation intervals measure the time difference between infection of a transmission pair, whereas serial intervals measure the time difference between symptom onset of a transmission pair \citep{svensson2007note}.
+Due to their similar definitions, their differences have been inaccurately captured and misunderstood previously.
 
 Our study demonstrate the importance of defining a cohort for studying any epidemiological time delay distributions.
-Previous studies have shown that generation interval can be either measured forward or backward;
+Previous studies have shown that generation interval can be either measured forward or backward \citep{champredon2015intrinsic};
 we generalize their ideas and show that these ideas can be applied to all distributions.
 Changes in the backward delay distributions is particularly robust across all distributions because they depend on previous changes in cohort sizes, which, in turn, depend on incidence of infection.
-Several epidemic analyses during the COVID-19 pandemic have attempted to reconstruct symptom onset or infection dates for each case from confirmed dates while assuming a constant backward delay distribution.
-Although such approaches may be able to match the time scale of an epidemic, we recommend future studies to consider deconvolution approaches instead for proper reconstruction of epidemic time series.
+Previous analyses of COVID-19 epidemics have attempted to reconstruct the time series of symptomatic cases or infected cases from the reports of confirmed cases by assuming a constant backward delay distribution (e.g., \cite{tempvar, park2020potential, shim2020transmission}).
+Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using deconvolution approaches instead for proper reconstruction of epidemic time series \citep{goldstein2009reconstructing}.
 
 Using cohort-based approaches, we define forward and backward serial intervals.
-The forward serial-interval distribution describes the renewal process of the symptomatic individuals and therefore provides the correct link between $r$ and $\mathcal R$.
+The forward serial-interval distribution describes the renewal process of the symptomatic individuals, and therefore, its initial distribution  provides the correct link between $r$ and $\mathcal R$.
 While our results support the use of serial interval distributions for calculating $\mathcal R$, 
 they also reveal gaps in current approaches to characterizing serial intervals.
-Previous studies have often (i) recommended using up-to-date serial intervals, (ii) assumed that the serial interval distribution remains constant, and (iii) applied serial interval distributions estimated from one location to analyzing epidemics in other locations;
-however, these approaches implicitly ignore spatiotemporal variation in incidence and may therefore give systematically biased estimates of $\mathcal R$. 
-For example, given geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the forward serial interval distributions will vary across different countries.
-Future studies should aim to characterize spatiotemporal variation in serial intervals and understanding the drivers of their differences.
+Previous studies have (i) recommended using up-to-date serial intervals \citep{thompson2019improved}, (ii) assumed that the serial interval distribution remains constant throughout an epidemic \citep{wallinga2004different, cori2013new}, and (iii) applied serial interval distributions estimated from one location to analyzing epidemics in other locations \citep{tempvar};
+however, all of these approaches implicitly ignore spatiotemporal variation in incidence, which affects the serial-interval distributions, and may therefore give systematically biased estimates of $\mathcal R$.
+For example, given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic \citep{tempvar}, the initial forward serial interval distributions is likely to vary across different countries.
+Future studies should aim to characterize spatiotemporal variation in serial intervals and understand the drivers of their differences.
 
-We also show that there are multiple serial-interval distributions that correspond to the same set of generation-interval and incubation period distributions depending on their correlations;
-not explicitly accounting for their correlations can bias the estimate of the intrinsic generation-interval distribution from the serial-interval distribution (see Appendix).
-Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the effect of right-censoring or differences between the backward incubation period of an infector and the forward incubation period of an infectee.
+We also show that there are multiple serial-interval distributions that correspond to the same set of generation-interval and incubation period distributions depending on their correlations.
+Conversely, this means that not explicitly accounting for their correlations can bias the estimate of the intrinsic generation-interval distribution from the serial-interval distribution.
+Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the differences between the backward incubation period of an infector and the forward incubation period of an infectee (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
 There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.
@@
 Here, we assumed that all individuals develop symptoms and that the the entire transmission process (e.g., direction of transmission, symptom onset dates, infection dates, etc.) are observable.
-In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult.
+In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.
 For example, symptom onset dates cannot be used as a reliable proxy for the direction of transmission as infectees may develop symptoms before their infectors.
@@
 Furthermore, serial intervals do not take into account asymptomatic transmission; 
-not explicitly accounting for asymptomatic transmission may also  bias the estimates of $\mathcal R$.
+not explicitly accounting for asymptomatic transmission may also bias the estimates of $\mathcal R$ \citep{park2020time}.
 
 Both generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating $\mathcal R$ --- yet important quantities in characterizing an epidemic.
-Here, we provided a theoretical basis for understanding serial intervals and show that naively using the observed serial intervals may lead to biased conclusions in studying the COVID-19 pandemic.
-Concluding sentence.
+Here, we provided the first theoretical basis for understanding serial intervals and showed that naively using the observed serial intervals may lead to biased conclusions.
+Our re-analysis of the serial intervals of COVID-19 from China provided further support for our analysis.
 

### 2020-04-20 serial_analysis.tex
stuff

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-12 17:51:37
+% Created by tikzDevice version 0.12.3 on 2020-04-20 00:29:27
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,289.08);
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (650.43,216.81);
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (216.81,216.81);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,289.08);
-\end{scope}
-\begin{scope}
-\path[clip] ( 34.64, 30.69) rectangle (283.58,266.42);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (216.81,216.81);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 34.64, 30.69) rectangle (283.58,266.42);
+\path[fill=fillColor] ( 34.64, 30.69) rectangle (211.31,194.15);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (100.89,194.15) --
+	(106.42,189.20) --
+	(111.94,184.25) --
+	(117.46,179.29) --
+	(122.98,174.34) --
+	(128.50,169.39) --
+	(134.02,164.43) --
+	(139.54,159.48) --
+	(145.06,154.52) --
+	(150.58,149.57) --
+	(156.10,144.62) --
+	(161.62,139.66) --
+	(167.14,134.71) --
+	(172.66,129.76) --
+	(178.19,124.80) --
+	(183.71,119.85) --
+	(189.23,114.90) --
+	(194.75,109.94) --
+	(200.27,104.99) --
+	(205.79,100.04) --
+	(211.31, 95.08);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 34.64,104.99) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.69,161.34) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.21,136.36) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 56.73,144.62) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.25,144.62) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.77,164.43) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.29,164.43) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.81,144.62) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.33,159.48) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.85,137.19) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.37,120.06) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.89,120.16) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.42,124.02) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.94,113.45) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.46,121.02) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.98,112.94) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.50,109.78) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.02,113.37) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.54,101.81) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.06,105.30) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.58, 99.53) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.10, 97.67) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.62, 97.70) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.14, 92.46) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.66, 89.55) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.19, 95.98) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.71, 94.09) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.23, 85.17) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (200.27, 70.31) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.31, 60.41) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.64,104.99) --
+	( 34.64,104.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.64,104.99) --
+	( 34.64,104.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.64,104.99) --
+	( 34.64,104.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,139.66) --
+	( 45.69,139.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,139.66) --
+	( 45.69,174.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,174.34) --
+	( 45.69,174.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,114.90) --
+	( 51.21,114.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,114.90) --
+	( 51.21,169.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,169.39) --
+	( 51.21,169.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,134.71) --
+	( 56.73,134.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,134.71) --
+	( 56.73,154.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.52) --
+	( 56.73,154.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,104.99) --
+	( 62.25,104.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,104.99) --
+	( 62.25,174.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,174.34) --
+	( 62.25,174.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.77,164.43) --
+	( 67.77,164.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.77,164.43) --
+	( 67.77,164.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.77,164.43) --
+	( 67.77,164.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,139.66) --
+	( 73.29,139.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,139.66) --
+	( 73.29,189.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,189.20) --
+	( 73.29,189.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,134.71) --
+	( 78.81,134.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,134.71) --
+	( 78.81,154.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.52) --
+	( 78.81,154.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.33,159.48) --
+	( 84.33,159.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.33,159.48) --
+	( 84.33,159.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.33,159.48) --
+	( 84.33,159.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,119.85) --
+	( 89.85,119.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,119.85) --
+	( 89.85,159.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,159.48) --
+	( 89.85,159.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 80.22) --
+	( 95.37, 80.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 80.22) --
+	( 95.37,174.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,174.34) --
+	( 95.37,174.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 95.08) --
+	(100.89, 95.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 95.08) --
+	(100.89,164.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,164.43) --
+	(100.89,164.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 90.13) --
+	(106.42, 90.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 90.13) --
+	(106.42,149.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,149.57) --
+	(106.42,149.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94, 85.17) --
+	(111.94, 85.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94, 85.17) --
+	(111.94,159.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,159.48) --
+	(111.94,159.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 90.13) --
+	(117.46, 90.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 90.13) --
+	(117.46,164.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46,164.43) --
+	(117.46,164.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 45.55) --
+	(122.98, 45.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 45.55) --
+	(122.98,169.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,169.39) --
+	(122.98,169.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50, 85.17) --
+	(128.50, 85.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50, 85.17) --
+	(128.50,149.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,149.57) --
+	(128.50,149.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02, 90.13) --
+	(134.02, 90.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02, 90.13) --
+	(134.02,144.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,144.62) --
+	(134.02,144.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 65.36) --
+	(139.54, 65.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 65.36) --
+	(139.54,134.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,134.71) --
+	(139.54,134.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 60.41) --
+	(145.06, 60.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 60.41) --
+	(145.06,144.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,144.62) --
+	(145.06,144.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 65.36) --
+	(150.58, 65.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 65.36) --
+	(150.58,149.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,149.57) --
+	(150.58,149.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10, 40.59) --
+	(156.10, 40.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10, 40.59) --
+	(156.10,134.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,134.71) --
+	(156.10,134.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 50.50) --
+	(161.62, 50.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 50.50) --
+	(161.62,129.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,129.76) --
+	(161.62,129.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 60.41) --
+	(167.14, 60.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 60.41) --
+	(167.14,109.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14,109.94) --
+	(167.14,109.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 65.36) --
+	(172.66, 65.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 65.36) --
+	(172.66,109.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,109.94) --
+	(172.66,109.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 75.27) --
+	(178.19, 75.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 75.27) --
+	(178.19,109.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19,109.94) --
+	(178.19,109.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.17) --
+	(183.71, 85.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.17) --
+	(183.71,100.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71,100.04) --
+	(183.71,100.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
+	(189.23, 85.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
+	(189.23, 85.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
+	(189.23, 85.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.27, 70.31) --
+	(200.27, 70.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.27, 70.31) --
+	(200.27, 70.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.27, 70.31) --
+	(200.27, 70.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 35.64) --
+	(211.31, 35.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 35.64) --
+	(211.31, 85.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 85.17) --
+	(211.31, 85.17);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor,fill opacity=0.20] ( 34.64,171.01) --
+	( 36.88,169.05) --
+	( 39.12,167.14) --
+	( 41.35,165.27) --
+	( 43.59,163.46) --
+	( 45.83,161.68) --
+	( 48.06,159.96) --
+	( 50.30,158.29) --
+	( 52.54,156.67) --
+	( 54.77,155.10) --
+	( 57.01,153.59) --
+	( 59.24,152.12) --
+	( 61.48,150.70) --
+	( 63.72,149.32) --
+	( 65.95,147.97) --
+	( 68.19,146.66) --
+	( 70.43,145.37) --
+	( 72.66,144.09) --
+	( 74.90,142.81) --
+	( 77.13,141.54) --
+	( 79.37,140.25) --
+	( 81.61,138.94) --
+	( 83.84,137.61) --
+	( 86.08,136.26) --
+	( 88.32,134.88) --
+	( 90.55,133.47) --
+	( 92.79,132.04) --
+	( 95.02,130.59) --
+	( 97.26,129.14) --
+	( 99.50,127.74) --
+	(101.73,126.42) --
+	(103.97,125.19) --
+	(106.21,124.07) --
+	(108.44,123.07) --
+	(110.68,122.19) --
+	(112.91,121.41) --
+	(115.15,120.75) --
+	(117.39,120.02) --
+	(119.62,119.00) --
+	(121.86,117.91) --
+	(124.10,116.89) --
+	(126.33,115.70) --
+	(128.57,114.48) --
+	(130.80,113.34) --
+	(133.04,112.27) --
+	(135.28,111.11) --
+	(137.51,109.84) --
+	(139.75,108.69) --
+	(141.99,107.59) --
+	(144.22,106.58) --
+	(146.46,105.54) --
+	(148.69,104.57) --
+	(150.93,103.63) --
+	(153.17,102.62) --
+	(155.40,101.65) --
+	(157.64,100.75) --
+	(159.88, 99.93) --
+	(162.11, 99.20) --
+	(164.35, 98.48) --
+	(166.58, 97.75) --
+	(168.82, 97.00) --
+	(171.06, 96.23) --
+	(173.29, 95.46) --
+	(175.53, 94.69) --
+	(177.77, 93.95) --
+	(180.00, 93.23) --
+	(182.24, 92.56) --
+	(184.47, 91.94) --
+	(186.71, 91.37) --
+	(188.95, 90.85) --
+	(191.18, 90.39) --
+	(193.42, 89.99) --
+	(195.66, 89.64) --
+	(197.89, 89.34) --
+	(200.13, 89.10) --
+	(202.36, 88.91) --
+	(204.60, 88.77) --
+	(206.84, 88.68) --
+	(209.07, 88.64) --
+	(211.31, 88.65) --
+	(211.31, 46.93) --
+	(209.07, 50.41) --
+	(206.84, 53.75) --
+	(204.60, 56.97) --
+	(202.36, 60.04) --
+	(200.13, 62.98) --
+	(197.89, 65.79) --
+	(195.66, 68.45) --
+	(193.42, 70.97) --
+	(191.18, 73.35) --
+	(188.95, 75.58) --
+	(186.71, 77.67) --
+	(184.47, 79.62) --
+	(182.24, 81.42) --
+	(180.00, 83.08) --
+	(177.77, 84.60) --
+	(175.53, 86.01) --
+	(173.29, 87.29) --
+	(171.06, 88.48) --
+	(168.82, 89.58) --
+	(166.58, 90.59) --
+	(164.35, 91.53) --
+	(162.11, 92.39) --
+	(159.88, 93.23) --
+	(157.64, 94.16) --
+	(155.40, 95.15) --
+	(153.17, 96.16) --
+	(150.93, 97.18) --
+	(148.69, 98.28) --
+	(146.46, 99.36) --
+	(144.22,100.40) --
+	(141.99,101.43) --
+	(139.75,102.42) --
+	(137.51,103.58) --
+	(135.28,104.76) --
+	(133.04,105.87) --
+	(130.80,107.14) --
+	(128.57,108.40) --
+	(126.33,109.53) --
+	(124.10,110.53) --
+	(121.86,111.53) --
+	(119.62,112.53) --
+	(117.39,113.40) --
+	(115.15,114.13) --
+	(112.91,114.80) --
+	(110.68,115.58) --
+	(108.44,116.44) --
+	(106.21,117.32) --
+	(103.97,118.24) --
+	(101.73,119.19) --
+	( 99.50,120.18) --
+	( 97.26,121.23) --
+	( 95.02,122.36) --
+	( 92.79,123.51) --
+	( 90.55,124.65) --
+	( 88.32,125.78) --
+	( 86.08,126.91) --
+	( 83.84,128.03) --
+	( 81.61,129.15) --
+	( 79.37,130.26) --
+	( 77.13,131.35) --
+	( 74.90,132.43) --
+	( 72.66,133.48) --
+	( 70.43,134.49) --
+	( 68.19,135.47) --
+	( 65.95,136.39) --
+	( 63.72,137.26) --
+	( 61.48,138.06) --
+	( 59.24,138.79) --
+	( 57.01,139.45) --
+	( 54.77,140.04) --
+	( 52.54,140.55) --
+	( 50.30,140.98) --
+	( 48.06,141.33) --
+	( 45.83,141.61) --
+	( 43.59,141.82) --
+	( 41.35,141.95) --
+	( 39.12,142.01) --
+	( 36.88,142.01) --
+	( 34.64,141.94) --
+	cycle;
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 34.64,156.47) --
+	( 36.88,155.53) --
+	( 39.12,154.58) --
+	( 41.35,153.61) --
+	( 43.59,152.64) --
+	( 45.83,151.65) --
+	( 48.06,150.65) --
+	( 50.30,149.64) --
+	( 52.54,148.61) --
+	( 54.77,147.57) --
+	( 57.01,146.52) --
+	( 59.24,145.46) --
+	( 61.48,144.38) --
+	( 63.72,143.29) --
+	( 65.95,142.18) --
+	( 68.19,141.06) --
+	( 70.43,139.93) --
+	( 72.66,138.78) --
+	( 74.90,137.62) --
+	( 77.13,136.44) --
+	( 79.37,135.25) --
+	( 81.61,134.04) --
+	( 83.84,132.82) --
+	( 86.08,131.59) --
+	( 88.32,130.33) --
+	( 90.55,129.06) --
+	( 92.79,127.78) --
+	( 95.02,126.48) --
+	( 97.26,125.19) --
+	( 99.50,123.96) --
+	(101.73,122.80) --
+	(103.97,121.71) --
+	(106.21,120.70) --
+	(108.44,119.75) --
+	(110.68,118.89) --
+	(112.91,118.11) --
+	(115.15,117.44) --
+	(117.39,116.71) --
+	(119.62,115.77) --
+	(121.86,114.72) --
+	(124.10,113.71) --
+	(126.33,112.61) --
+	(128.57,111.44) --
+	(130.80,110.24) --
+	(133.04,109.07) --
+	(135.28,107.93) --
+	(137.51,106.71) --
+	(139.75,105.56) --
+	(141.99,104.51) --
+	(144.22,103.49) --
+	(146.46,102.45) --
+	(148.69,101.42) --
+	(150.93,100.41) --
+	(153.17, 99.39) --
+	(155.40, 98.40) --
+	(157.64, 97.46) --
+	(159.88, 96.58) --
+	(162.11, 95.79) --
+	(164.35, 95.01) --
+	(166.58, 94.17) --
+	(168.82, 93.29) --
+	(171.06, 92.35) --
+	(173.29, 91.38) --
+	(175.53, 90.35) --
+	(177.77, 89.28) --
+	(180.00, 88.16) --
+	(182.24, 86.99) --
+	(184.47, 85.78) --
+	(186.71, 84.52) --
+	(188.95, 83.22) --
+	(191.18, 81.87) --
+	(193.42, 80.48) --
+	(195.66, 79.04) --
+	(197.89, 77.57) --
+	(200.13, 76.04) --
+	(202.36, 74.48) --
+	(204.60, 72.87) --
+	(206.84, 71.22) --
+	(209.07, 69.53) --
+	(211.31, 67.79);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.97,138.18) -- ( 41.97,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.97,138.18) -- ( 41.97,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 39.22,138.18) --
-	( 39.22,138.18) --
-	( 44.71,138.18) --
-	( 44.71,138.18) --
-	( 39.22,138.18) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 39.22,138.18) -- ( 44.71,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.61,226.33) -- ( 56.61,234.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.61,209.04) -- ( 56.61,186.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 53.86,226.33) --
-	( 53.86,209.04) --
-	( 59.36,209.04) --
-	( 59.36,226.33) --
-	( 53.86,226.33) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 53.86,217.69) -- ( 59.36,217.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93,196.95) -- ( 63.93,228.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93,158.92) -- ( 63.93,152.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 61.19,196.95) --
-	( 61.19,158.92) --
-	( 66.68,158.92) --
-	( 66.68,196.95) --
-	( 61.19,196.95) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 61.19,165.84) -- ( 66.68,165.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 71.25,200.40) -- ( 71.25,207.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 71.25,186.58) -- ( 71.25,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.51,200.40) --
-	( 68.51,186.58) --
-	( 74.00,186.58) --
-	( 74.00,200.40) --
-	( 68.51,200.40) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.51,193.49) -- ( 74.00,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.57,221.14) -- ( 78.57,234.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.57,172.75) -- ( 78.57,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 75.83,221.14) --
-	( 75.83,172.75) --
-	( 81.32,172.75) --
-	( 81.32,221.14) --
-	( 75.83,221.14) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 75.83,207.32) -- ( 81.32,207.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.90,221.14) -- ( 85.90,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.90,221.14) -- ( 85.90,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 83.15,221.14) --
-	( 83.15,221.14) --
-	( 88.64,221.14) --
-	( 88.64,221.14) --
-	( 83.15,221.14) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 83.15,221.14) -- ( 88.64,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.22,238.42) -- ( 93.22,255.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.22,203.86) -- ( 93.22,186.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 90.47,238.42) --
-	( 90.47,203.86) --
-	( 95.96,203.86) --
-	( 95.96,238.42) --
-	( 90.47,238.42) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 90.47,221.14) -- ( 95.96,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,200.40) -- (100.54,207.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,186.58) -- (100.54,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 97.79,200.40) --
-	( 97.79,186.58) --
-	(103.29,186.58) --
-	(103.29,200.40) --
-	( 97.79,200.40) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 97.79,193.49) -- (103.29,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.86,214.23) -- (107.86,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.86,214.23) -- (107.86,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (105.12,214.23) --
-	(105.12,214.23) --
-	(110.61,214.23) --
-	(110.61,214.23) --
-	(105.12,214.23) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (105.12,214.23) -- (110.61,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (115.18,198.67) -- (115.18,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (115.18,164.11) -- (115.18,158.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.44,198.67) --
-	(112.44,164.11) --
-	(117.93,164.11) --
-	(117.93,198.67) --
-	(112.44,198.67) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (112.44,179.66) -- (117.93,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.50,186.58) -- (122.50,234.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.50,138.18) -- (122.50,103.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (119.76,186.58) --
-	(119.76,138.18) --
-	(125.25,138.18) --
-	(125.25,186.58) --
-	(119.76,186.58) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (119.76,158.92) -- (125.25,158.92);
-\definecolor{fillColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.83,221.14) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.83,171.02) -- (129.83,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.83,139.91) -- (129.83,124.36);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (127.08,171.02) --
-	(127.08,139.91) --
-	(132.57,139.91) --
-	(132.57,171.02) --
-	(127.08,171.02) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (127.08,155.47) -- (132.57,155.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15,183.12) -- (137.15,200.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15,148.55) -- (137.15,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (134.40,183.12) --
-	(134.40,148.55) --
-	(139.89,148.55) --
-	(139.89,183.12) --
-	(134.40,183.12) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (134.40,165.84) -- (139.89,165.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (144.47,172.75) -- (144.47,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (144.47,131.27) -- (144.47,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (141.72,172.75) --
-	(141.72,131.27) --
-	(147.21,131.27) --
-	(147.21,172.75) --
-	(141.72,172.75) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (141.72,152.01) -- (147.21,152.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.79,179.66) -- (151.79,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.79,138.18) -- (151.79,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (149.05,179.66) --
-	(149.05,138.18) --
-	(154.54,138.18) --
-	(154.54,179.66) --
-	(149.05,179.66) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (149.05,158.92) -- (154.54,158.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,184.85) -- (159.11,228.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,126.09) -- (159.11, 55.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (156.37,184.85) --
-	(156.37,126.09) --
-	(161.86,126.09) --
-	(161.86,184.85) --
-	(156.37,184.85) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (156.37,155.47) -- (161.86,155.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (166.43,174.48) -- (166.43,200.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (166.43,129.54) -- (166.43,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (163.69,174.48) --
-	(163.69,129.54) --
-	(169.18,129.54) --
-	(169.18,174.48) --
-	(163.69,174.48) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (163.69,152.01) -- (169.18,152.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (173.76,171.02) -- (173.76,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (173.76,133.00) -- (173.76,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (171.01,171.02) --
-	(171.01,133.00) --
-	(176.50,133.00) --
-	(176.50,171.02) --
-	(171.01,171.02) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (171.01,152.01) -- (176.50,152.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (181.08,152.01) -- (181.08,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (181.08,110.53) -- (181.08, 82.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (178.33,152.01) --
-	(178.33,110.53) --
-	(183.82,110.53) --
-	(183.82,152.01) --
-	(178.33,152.01) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (178.33,131.27) -- (183.82,131.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (188.40,165.84) -- (188.40,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (188.40,110.53) -- (188.40, 75.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (185.65,165.84) --
-	(185.65,110.53) --
-	(191.14,110.53) --
-	(191.14,165.84) --
-	(185.65,165.84) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (185.65,138.18) -- (191.14,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.72,160.65) -- (195.72,200.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.72,108.80) -- (195.72, 82.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (192.97,160.65) --
-	(192.97,108.80) --
-	(198.47,108.80) --
-	(198.47,160.65) --
-	(192.97,160.65) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (192.97,134.73) -- (198.47,134.73);
-\definecolor{fillColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.04, 48.31) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.04,155.47) -- (203.04,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.04,120.90) -- (203.04,103.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (200.30,155.47) --
-	(200.30,120.90) --
-	(205.79,120.90) --
-	(205.79,155.47) --
-	(200.30,155.47) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (200.30,138.18) -- (205.79,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36,143.37) -- (210.36,172.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36,107.08) -- (210.36, 62.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (207.62,143.37) --
-	(207.62,107.08) --
-	(213.11,107.08) --
-	(213.11,143.37) --
-	(207.62,143.37) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (207.62,127.81) -- (213.11,127.81);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (217.69,131.27) -- (217.69,145.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (217.69, 96.71) -- (217.69, 75.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (214.94,131.27) --
-	(214.94, 96.71) --
-	(220.43, 96.71) --
-	(220.43,131.27) --
-	(214.94,131.27) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (214.94,117.45) -- (220.43,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.01,134.73) -- (225.01,145.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.01,113.99) -- (225.01, 82.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (222.26,134.73) --
-	(222.26,113.99) --
-	(227.75,113.99) --
-	(227.75,134.73) --
-	(222.26,134.73) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (222.26,124.36) -- (227.75,124.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (232.33,134.73) -- (232.33,145.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (232.33,113.99) -- (232.33, 96.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (229.58,134.73) --
-	(229.58,113.99) --
-	(235.07,113.99) --
-	(235.07,134.73) --
-	(229.58,134.73) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (229.58,124.36) -- (235.07,124.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (239.65,126.09) -- (239.65,131.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (239.65,115.72) -- (239.65,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (236.90,126.09) --
-	(236.90,115.72) --
-	(242.40,115.72) --
-	(242.40,126.09) --
-	(236.90,126.09) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (236.90,120.90) -- (242.40,120.90);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (246.97,110.53) -- (246.97,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (246.97,110.53) -- (246.97,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (244.23,110.53) --
-	(244.23,110.53) --
-	(249.72,110.53) --
-	(249.72,110.53) --
-	(244.23,110.53) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (244.23,110.53) -- (249.72,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (261.62, 89.79) -- (261.62, 89.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (261.62, 89.79) -- (261.62, 89.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (258.87, 89.79) --
-	(258.87, 89.79) --
-	(264.36, 89.79) --
-	(264.36, 89.79) --
-	(258.87, 89.79) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (258.87, 89.79) -- (264.36, 89.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.26, 93.25) -- (276.26,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.26, 58.68) -- (276.26, 41.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (273.51, 93.25) --
-	(273.51, 58.68) --
-	(279.00, 58.68) --
-	(279.00, 93.25) --
-	(273.51, 93.25) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (273.51, 75.97) -- (279.00, 75.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.64, 30.69) rectangle (283.58,266.42);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.64, 30.69) rectangle (211.31,194.15);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69, 45.28) {-10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,114.41) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,183.55) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,252.68) {20};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69, 37.56) {-10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69, 87.10) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,136.63) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,186.17) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89, 48.31) --
-	( 34.64, 48.31);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,117.45) --
-	( 34.64,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,186.58) --
-	( 34.64,186.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,255.71) --
-	( 34.64,255.71);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89, 40.59) --
+	( 34.64, 40.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89, 90.13) --
+	( 34.64, 90.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,139.66) --
+	( 34.64,139.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,189.20) --
+	( 34.64,189.20);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93, 27.94) --
-	( 63.93, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15, 27.94) --
-	(137.15, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36, 27.94) --
-	(210.36, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (283.58, 27.94) --
-	(283.58, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21, 27.94) --
+	( 51.21, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 27.94) --
+	(106.42, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 27.94) --
+	(161.62, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 63.93, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (137.15, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (210.36, 19.68) {20};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (283.58, 19.68) {30};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 51.21, 19.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (106.42, 19.68) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (161.62, 19.68) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (159.11,  7.64) {Cohort time (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (122.98,  7.64) {Primary cohort time (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,148.55) {Forward serial intervals (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,112.42) {Forward delay (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.64,274.49) {A};
-\end{scope}
-\begin{scope}
-\path[clip] (289.08,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.64,202.22) {A. Forward serial interval};
+\end{scope}
+\begin{scope}
+\path[clip] (216.81,  0.00) rectangle (433.62,216.81);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.08,  0.00) rectangle (578.16,289.08);
-\end{scope}
-\begin{scope}
-\path[clip] (316.39, 30.69) rectangle (572.66,266.42);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (216.81,  0.00) rectangle (433.62,216.81);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (316.39, 30.69) rectangle (572.66,266.42);
+\path[fill=fillColor] (251.45, 30.69) rectangle (428.12,194.15);
+\definecolor{drawColor}{RGB}{0,0,0}
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (251.45,105.23) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (275.01, 47.70) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (280.90,110.02) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (286.79, 81.26) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (292.68,124.40) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (298.57, 90.85) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (304.45, 83.31) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.34, 98.52) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (316.23, 87.25) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (322.12, 95.32) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (328.01,102.53) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,105.54) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.79,106.72) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.68,105.89) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (351.57,100.32) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (357.45,107.92) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.34,112.15) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.23,113.22) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,111.54) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.01,112.98) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.90,115.62) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (392.79,121.14) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.68,124.15) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (404.56,122.56) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (410.45,139.38) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.34,133.19) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (422.23,167.55) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (428.12,148.37) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,105.23) --
+	(251.45,105.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,105.23) --
+	(251.45,105.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,105.23) --
+	(251.45,105.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 47.70) --
+	(275.01, 47.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 47.70) --
+	(275.01, 47.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 47.70) --
+	(275.01, 47.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,105.23) --
+	(280.90,105.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,105.23) --
+	(280.90,114.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,114.82) --
+	(280.90,114.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.26) --
+	(286.79, 81.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.26) --
+	(286.79, 81.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.26) --
+	(286.79, 81.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,124.40) --
+	(292.68,124.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,124.40) --
+	(292.68,124.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,124.40) --
+	(292.68,124.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 90.85) --
+	(298.57, 90.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 90.85) --
+	(298.57, 90.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 90.85) --
+	(298.57, 90.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45, 42.91) --
+	(304.45, 42.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45, 42.91) --
+	(304.45,138.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45,138.78) --
+	(304.45,138.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 86.05) --
+	(310.34, 86.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 86.05) --
+	(310.34,133.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34,133.99) --
+	(310.34,133.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23, 62.08) --
+	(316.23, 62.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23, 62.08) --
+	(316.23,105.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23,105.23) --
+	(316.23,105.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12, 52.50) --
+	(322.12, 52.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12, 52.50) --
+	(322.12,153.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12,153.17) --
+	(322.12,153.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01, 66.88) --
+	(328.01, 66.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01, 66.88) --
+	(328.01,157.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01,157.96) --
+	(328.01,157.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90, 71.67) --
+	(333.90, 71.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90, 71.67) --
+	(333.90,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,162.75) --
+	(333.90,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79, 62.08) --
+	(339.79, 62.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79, 62.08) --
+	(339.79,167.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79,167.55) --
+	(339.79,167.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68, 71.67) --
+	(345.68, 71.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68, 71.67) --
+	(345.68,172.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68,172.34) --
+	(345.68,172.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57, 66.88) --
+	(351.57, 66.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57, 66.88) --
+	(351.57,133.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57,133.99) --
+	(351.57,133.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45, 38.12) --
+	(357.45, 38.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45, 38.12) --
+	(357.45,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45,162.75) --
+	(357.45,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34, 90.85) --
+	(363.34, 90.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34, 90.85) --
+	(363.34,172.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34,172.34) --
+	(363.34,172.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23, 76.47) --
+	(369.23, 76.47);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23, 76.47) --
+	(369.23,157.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23,157.96) --
+	(369.23,157.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12, 86.05) --
+	(375.12, 86.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12, 86.05) --
+	(375.12,157.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12,157.96) --
+	(375.12,157.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01, 86.05) --
+	(381.01, 86.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01, 86.05) --
+	(381.01,148.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01,148.37) --
+	(381.01,148.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90, 71.67) --
+	(386.90, 71.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90, 71.67) --
+	(386.90,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90,162.75) --
+	(386.90,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79, 86.05) --
+	(392.79, 86.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79, 86.05) --
+	(392.79,186.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79,186.72) --
+	(392.79,186.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68, 95.64) --
+	(398.68, 95.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68, 95.64) --
+	(398.68,172.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68,172.34) --
+	(398.68,172.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,100.43) --
+	(404.56,100.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,100.43) --
+	(404.56,148.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,148.37) --
+	(404.56,148.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,110.02) --
+	(410.45,110.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,110.02) --
+	(410.45,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,162.75) --
+	(410.45,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34, 86.05) --
+	(416.34, 86.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34, 86.05) --
+	(416.34,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34,162.75) --
+	(416.34,162.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,167.55) --
+	(422.23,167.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,167.55) --
+	(422.23,167.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,167.55) --
+	(422.23,167.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,148.37) --
+	(428.12,148.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,148.37) --
+	(428.12,148.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,148.37) --
+	(428.12,148.37);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor,fill opacity=0.20] (251.45,121.15) --
+	(253.69,119.25) --
+	(255.93,117.44) --
+	(258.16,115.70) --
+	(260.40,114.05) --
+	(262.64,112.48) --
+	(264.87,111.00) --
+	(267.11,109.60) --
+	(269.35,108.28) --
+	(271.58,107.06) --
+	(273.82,105.92) --
+	(276.05,104.87) --
+	(278.29,103.92) --
+	(280.53,103.05) --
+	(282.76,102.27) --
+	(285.00,101.59) --
+	(287.24,101.00) --
+	(289.47,100.50) --
+	(291.71,100.09) --
+	(293.94, 99.78) --
+	(296.18, 99.55) --
+	(298.42, 99.42) --
+	(300.65, 99.37) --
+	(302.89, 99.40) --
+	(305.13, 99.50) --
+	(307.36, 99.68) --
+	(309.60, 99.93) --
+	(311.83,100.23) --
+	(314.07,100.59) --
+	(316.31,100.99) --
+	(318.54,101.45) --
+	(320.78,101.95) --
+	(323.02,102.50) --
+	(325.25,103.10) --
+	(327.49,103.76) --
+	(329.72,104.45) --
+	(331.96,105.11) --
+	(334.20,105.76) --
+	(336.43,106.39) --
+	(338.67,107.01) --
+	(340.91,107.56) --
+	(343.14,107.90) --
+	(345.38,108.14) --
+	(347.61,108.42) --
+	(349.85,108.79) --
+	(352.09,109.25) --
+	(354.32,109.74) --
+	(356.56,110.39) --
+	(358.80,111.15) --
+	(361.03,112.32) --
+	(363.27,113.45) --
+	(365.50,113.91) --
+	(367.74,114.29) --
+	(369.98,114.93) --
+	(372.21,115.63) --
+	(374.45,116.42) --
+	(376.69,117.13) --
+	(378.92,117.75) --
+	(381.16,118.39) --
+	(383.39,119.13) --
+	(385.63,120.01) --
+	(387.87,121.05) --
+	(390.10,122.20) --
+	(392.34,123.45) --
+	(394.58,124.82) --
+	(396.81,126.34) --
+	(399.05,128.02) --
+	(401.28,129.88) --
+	(403.52,131.95) --
+	(405.76,134.21) --
+	(407.99,136.68) --
+	(410.23,139.36) --
+	(412.47,142.24) --
+	(414.70,145.32) --
+	(416.94,148.60) --
+	(419.17,152.06) --
+	(421.41,155.72) --
+	(423.65,159.56) --
+	(425.88,163.59) --
+	(428.12,167.81) --
+	(428.12,134.79) --
+	(425.88,133.76) --
+	(423.65,132.73) --
+	(421.41,131.69) --
+	(419.17,130.64) --
+	(416.94,129.57) --
+	(414.70,128.50) --
+	(412.47,127.40) --
+	(410.23,126.29) --
+	(407.99,125.14) --
+	(405.76,123.97) --
+	(403.52,122.77) --
+	(401.28,121.53) --
+	(399.05,120.28) --
+	(396.81,119.01) --
+	(394.58,117.75) --
+	(392.34,116.53) --
+	(390.10,115.35) --
+	(387.87,114.24) --
+	(385.63,113.23) --
+	(383.39,112.40) --
+	(381.16,111.67) --
+	(378.92,110.96) --
+	(376.69,110.24) --
+	(374.45,109.51) --
+	(372.21,108.90) --
+	(369.98,108.23) --
+	(367.74,107.58) --
+	(365.50,106.98) --
+	(363.27,106.24) --
+	(361.03,105.28) --
+	(358.80,104.09) --
+	(356.56,103.31) --
+	(354.32,102.90) --
+	(352.09,102.47) --
+	(349.85,102.09) --
+	(347.61,101.83) --
+	(345.38,101.55) --
+	(343.14,101.17) --
+	(340.91,100.66) --
+	(338.67,100.06) --
+	(336.43, 99.41) --
+	(334.20, 98.70) --
+	(331.96, 97.92) --
+	(329.72, 97.09) --
+	(327.49, 96.21) --
+	(325.25, 95.32) --
+	(323.02, 94.44) --
+	(320.78, 93.58) --
+	(318.54, 92.75) --
+	(316.31, 91.93) --
+	(314.07, 91.14) --
+	(311.83, 90.37) --
+	(309.60, 89.60) --
+	(307.36, 88.85) --
+	(305.13, 88.09) --
+	(302.89, 87.33) --
+	(300.65, 86.56) --
+	(298.42, 85.77) --
+	(296.18, 84.96) --
+	(293.94, 84.13) --
+	(291.71, 83.27) --
+	(289.47, 82.38) --
+	(287.24, 81.46) --
+	(285.00, 80.51) --
+	(282.76, 79.53) --
+	(280.53, 78.51) --
+	(278.29, 77.47) --
+	(276.05, 76.39) --
+	(273.82, 75.29) --
+	(271.58, 74.15) --
+	(269.35, 72.98) --
+	(267.11, 71.79) --
+	(264.87, 70.56) --
+	(262.64, 69.31) --
+	(260.40, 68.03) --
+	(258.16, 66.72) --
+	(255.93, 65.38) --
+	(253.69, 64.01) --
+	(251.45, 62.62) --
+	cycle;
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (251.45, 91.89) --
+	(253.69, 91.63) --
+	(255.93, 91.41) --
+	(258.16, 91.21) --
+	(260.40, 91.04) --
+	(262.64, 90.89) --
+	(264.87, 90.78) --
+	(267.11, 90.69) --
+	(269.35, 90.63) --
+	(271.58, 90.60) --
+	(273.82, 90.60) --
+	(276.05, 90.63) --
+	(278.29, 90.69) --
+	(280.53, 90.78) --
+	(282.76, 90.90) --
+	(285.00, 91.05) --
+	(287.24, 91.23) --
+	(289.47, 91.44) --
+	(291.71, 91.68) --
+	(293.94, 91.95) --
+	(296.18, 92.26) --
+	(298.42, 92.60) --
+	(300.65, 92.96) --
+	(302.89, 93.37) --
+	(305.13, 93.80) --
+	(307.36, 94.27) --
+	(309.60, 94.76) --
+	(311.83, 95.30) --
+	(314.07, 95.86) --
+	(316.31, 96.46) --
+	(318.54, 97.10) --
+	(320.78, 97.77) --
+	(323.02, 98.47) --
+	(325.25, 99.21) --
+	(327.49, 99.98) --
+	(329.72,100.77) --
+	(331.96,101.52) --
+	(334.20,102.23) --
+	(336.43,102.90) --
+	(338.67,103.53) --
+	(340.91,104.11) --
+	(343.14,104.53) --
+	(345.38,104.85) --
+	(347.61,105.13) --
+	(349.85,105.44) --
+	(352.09,105.86) --
+	(354.32,106.32) --
+	(356.56,106.85) --
+	(358.80,107.62) --
+	(361.03,108.80) --
+	(363.27,109.84) --
+	(365.50,110.44) --
+	(367.74,110.94) --
+	(369.98,111.58) --
+	(372.21,112.27) --
+	(374.45,112.97) --
+	(376.69,113.68) --
+	(378.92,114.35) --
+	(381.16,115.03) --
+	(383.39,115.76) --
+	(385.63,116.62) --
+	(387.87,117.64) --
+	(390.10,118.77) --
+	(392.34,119.99) --
+	(394.58,121.29) --
+	(396.81,122.67) --
+	(399.05,124.15) --
+	(401.28,125.71) --
+	(403.52,127.36) --
+	(405.76,129.09) --
+	(407.99,130.91) --
+	(410.23,132.82) --
+	(412.47,134.82) --
+	(414.70,136.91) --
+	(416.94,139.09) --
+	(419.17,141.35) --
+	(421.41,143.70) --
+	(423.65,146.14) --
+	(425.88,148.68) --
+	(428.12,151.30);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.45, 30.69) rectangle (428.12,194.15);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50, 39.88) {-10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50, 87.82) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50,135.75) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50,183.69) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70, 42.91) --
+	(251.45, 42.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70, 90.85) --
+	(251.45, 90.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70,138.78) --
+	(251.45,138.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70,186.72) --
+	(251.45,186.72);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45, 27.94) --
+	(251.45, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 27.94) --
+	(310.34, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23, 27.94) --
+	(369.23, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12, 27.94) --
+	(428.12, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (251.45, 19.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (310.34, 19.68) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (369.23, 19.68) {20};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (428.12, 19.68) {30};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (339.79,  7.64) {Secondary cohort time (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (229.89,112.42) {Backward delay (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (251.45,202.22) {B. Backward serial interval};
+\end{scope}
+\begin{scope}
+\path[clip] (433.62,  0.00) rectangle (650.43,216.81);
+\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (433.62,  0.00) rectangle (650.43,216.81);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (460.93, 30.69) rectangle (644.93,194.15);
 \definecolor{drawColor}{RGB}{240,228,66}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (346.54,255.71) --
-	(354.08,234.51) --
-	(361.62,227.85) --
-	(369.15,224.34) --
-	(376.69,232.95) --
-	(384.23,225.18) --
-	(391.77,220.08) --
-	(399.30,212.60) --
-	(406.84,137.83) --
-	(414.38,119.60) --
-	(421.91,116.21) --
-	(429.45,104.34) --
-	(436.99,101.52) --
-	(444.53, 91.89) --
-	(452.06, 87.88) --
-	(459.60, 85.77) --
-	(467.14, 79.62) --
-	(474.68, 76.53) --
-	(482.21, 72.74) --
-	(489.75, 71.32) --
-	(497.29, 69.30) --
-	(504.82, 68.00) --
-	(512.36, 66.17) --
-	(519.90, 65.86) --
-	(527.44, 65.06) --
-	(534.97, 64.84) --
-	(542.51, 64.84) --
-	(550.05, 64.82) --
-	(557.59, 64.82) --
-	(565.12, 64.08) --
-	(565.12, 56.77) --
-	(557.59, 57.72) --
-	(550.05, 57.72) --
-	(542.51, 58.18) --
-	(534.97, 58.18) --
-	(527.44, 58.40) --
-	(519.90, 58.16) --
-	(512.36, 58.79) --
-	(504.82, 60.03) --
-	(497.29, 60.94) --
-	(489.75, 62.46) --
-	(482.21, 65.05) --
-	(474.68, 66.78) --
-	(467.14, 70.56) --
-	(459.60, 73.93) --
-	(452.06, 74.95) --
-	(444.53, 77.75) --
-	(436.99, 84.76) --
-	(429.45, 84.17) --
-	(421.91, 90.54) --
-	(414.38, 89.60) --
-	(406.84, 93.27) --
-	(399.30,129.71) --
-	(391.77,137.14) --
-	(384.23,136.34) --
-	(376.69,134.94) --
-	(369.15,135.04) --
-	(361.62,120.43) --
-	(354.08,124.23) --
-	(346.54,119.49) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (478.18,186.72) --
+	(483.93,172.02) --
+	(489.68,167.41) --
+	(495.43,164.97) --
+	(501.18,170.94) --
+	(506.93,165.55) --
+	(512.68,162.02) --
+	(518.43,156.83) --
+	(524.18,104.98) --
+	(529.93, 92.34) --
+	(535.68, 89.99) --
+	(541.43, 81.76) --
+	(547.18, 79.80) --
+	(552.93, 73.13) --
+	(558.68, 70.34) --
+	(564.43, 68.88) --
+	(570.18, 64.62) --
+	(575.93, 62.47) --
+	(581.68, 59.85) --
+	(587.43, 58.86) --
+	(593.18, 57.46) --
+	(598.93, 56.56) --
+	(604.68, 55.29) --
+	(610.43, 55.07) --
+	(616.18, 54.52) --
+	(621.93, 54.37) --
+	(627.68, 54.37) --
+	(633.43, 54.35) --
+	(639.18, 54.35) --
+	(644.93, 53.84) --
+	(644.93, 48.78) --
+	(639.18, 49.43) --
+	(633.43, 49.43) --
+	(627.68, 49.75) --
+	(621.93, 49.75) --
+	(616.18, 49.90) --
+	(610.43, 49.74) --
+	(604.68, 50.17) --
+	(598.93, 51.03) --
+	(593.18, 51.66) --
+	(587.43, 52.72) --
+	(581.68, 54.51) --
+	(575.93, 55.72) --
+	(570.18, 58.33) --
+	(564.43, 60.67) --
+	(558.68, 61.38) --
+	(552.93, 63.32) --
+	(547.18, 68.18) --
+	(541.43, 67.77) --
+	(535.68, 72.19) --
+	(529.93, 71.54) --
+	(524.18, 74.09) --
+	(518.43, 99.35) --
+	(512.68,104.50) --
+	(506.93,103.95) --
+	(501.18,102.98) --
+	(495.43,103.05) --
+	(489.68, 92.92) --
+	(483.93, 95.55) --
+	(478.18, 92.27) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (346.54,167.99) --
-	(354.08,158.37) --
-	(361.62,155.61) --
-	(369.15,153.41) --
-	(376.69,158.49) --
-	(384.23,154.03) --
-	(391.77,151.93) --
-	(399.30,148.30) --
-	(406.84,107.71) --
-	(414.38, 96.60) --
-	(421.91, 94.03) --
-	(429.45, 86.26) --
-	(436.99, 84.52) --
-	(444.53, 77.77) --
-	(452.06, 75.45) --
-	(459.60, 73.98) --
-	(467.14, 69.74) --
-	(474.68, 67.73) --
-	(482.21, 65.35) --
-	(489.75, 64.41) --
-	(497.29, 62.76) --
-	(504.82, 61.94) --
-	(512.36, 60.56) --
-	(519.90, 60.51) --
-	(527.44, 60.01) --
-	(534.97, 59.88) --
-	(542.51, 59.88) --
-	(550.05, 59.77) --
-	(557.59, 59.77) --
-	(565.12, 59.40) --
-	(565.12, 54.49) --
-	(557.59, 54.89) --
-	(550.05, 54.89) --
-	(542.51, 55.23) --
-	(534.97, 55.23) --
-	(527.44, 55.32) --
-	(519.90, 55.43) --
-	(512.36, 55.76) --
-	(504.82, 56.48) --
-	(497.29, 57.32) --
-	(489.75, 58.34) --
-	(482.21, 59.85) --
-	(474.68, 61.35) --
-	(467.14, 63.63) --
-	(459.60, 66.52) --
-	(452.06, 66.97) --
-	(444.53, 68.74) --
-	(436.99, 73.15) --
-	(429.45, 73.04) --
-	(421.91, 77.40) --
-	(414.38, 77.19) --
-	(406.84, 79.82) --
-	(399.30,101.35) --
-	(391.77,108.09) --
-	(384.23,107.05) --
-	(376.69,105.61) --
-	(369.15,105.29) --
-	(361.62, 96.62) --
-	(354.08, 98.80) --
-	(346.54, 95.78) --
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (478.18,125.90) --
+	(483.93,119.23) --
+	(489.68,117.31) --
+	(495.43,115.79) --
+	(501.18,119.31) --
+	(506.93,116.22) --
+	(512.68,114.76) --
+	(518.43,112.24) --
+	(524.18, 84.09) --
+	(529.93, 76.40) --
+	(535.68, 74.61) --
+	(541.43, 69.22) --
+	(547.18, 68.02) --
+	(552.93, 63.34) --
+	(558.68, 61.72) --
+	(564.43, 60.71) --
+	(570.18, 57.76) --
+	(575.93, 56.38) --
+	(581.68, 54.72) --
+	(587.43, 54.07) --
+	(593.18, 52.92) --
+	(598.93, 52.36) --
+	(604.68, 51.40) --
+	(610.43, 51.36) --
+	(616.18, 51.02) --
+	(621.93, 50.93) --
+	(627.68, 50.93) --
+	(633.43, 50.85) --
+	(639.18, 50.85) --
+	(644.93, 50.60) --
+	(644.93, 47.19) --
+	(639.18, 47.47) --
+	(633.43, 47.47) --
+	(627.68, 47.71) --
+	(621.93, 47.71) --
+	(616.18, 47.77) --
+	(610.43, 47.85) --
+	(604.68, 48.08) --
+	(598.93, 48.58) --
+	(593.18, 49.16) --
+	(587.43, 49.86) --
+	(581.68, 50.91) --
+	(575.93, 51.95) --
+	(570.18, 53.53) --
+	(564.43, 55.54) --
+	(558.68, 55.84) --
+	(552.93, 57.08) --
+	(547.18, 60.14) --
+	(541.43, 60.06) --
+	(535.68, 63.08) --
+	(529.93, 62.94) --
+	(524.18, 64.75) --
+	(518.43, 79.69) --
+	(512.68, 84.36) --
+	(506.93, 83.64) --
+	(501.18, 82.64) --
+	(495.43, 82.42) --
+	(489.68, 76.41) --
+	(483.93, 77.92) --
+	(478.18, 75.82) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (316.39, 41.40) -- (572.66, 41.40);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (460.93, 38.12) -- (644.93, 38.12);
 \definecolor{drawColor}{RGB}{240,228,66}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (346.54,170.94) --
-	(354.08,170.79) --
-	(361.62,163.30) --
-	(369.15,167.34) --
-	(376.69,172.68) --
-	(384.23,172.43) --
-	(391.77,174.86) --
-	(399.30,167.73) --
-	(406.84,112.65) --
-	(414.38,105.04) --
-	(421.91,102.84) --
-	(429.45, 93.38) --
-	(436.99, 91.84) --
-	(444.53, 83.99) --
-	(452.06, 80.95) --
-	(459.60, 80.00) --
-	(467.14, 75.18) --
-	(474.68, 71.77) --
-	(482.21, 68.56) --
-	(489.75, 66.30) --
-	(497.29, 65.11) --
-	(504.82, 63.71) --
-	(512.36, 62.37) --
-	(519.90, 61.91) --
-	(527.44, 61.69) --
-	(534.97, 61.52) --
-	(542.51, 61.52) --
-	(550.05, 61.33) --
-	(557.59, 61.33) --
-	(565.12, 60.65);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (478.18,127.94) --
+	(483.93,127.84) --
+	(489.68,122.64) --
+	(495.43,125.45) --
+	(501.18,129.15) --
+	(506.93,128.97) --
+	(512.68,130.66) --
+	(518.43,125.72) --
+	(524.18, 87.52) --
+	(529.93, 82.25) --
+	(535.68, 80.72) --
+	(541.43, 74.16) --
+	(547.18, 73.09) --
+	(552.93, 67.65) --
+	(558.68, 65.54) --
+	(564.43, 64.88) --
+	(570.18, 61.54) --
+	(575.93, 59.17) --
+	(581.68, 56.95) --
+	(587.43, 55.38) --
+	(593.18, 54.56) --
+	(598.93, 53.59) --
+	(604.68, 52.65) --
+	(610.43, 52.34) --
+	(616.18, 52.19) --
+	(621.93, 52.07) --
+	(627.68, 52.07) --
+	(633.43, 51.94) --
+	(639.18, 51.94) --
+	(644.93, 51.46);
 \definecolor{drawColor}{RGB}{0,114,178}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (346.54,126.39) --
-	(354.08,125.79) --
-	(361.62,122.09) --
-	(369.15,124.37) --
-	(376.69,127.48) --
-	(384.23,126.99) --
-	(391.77,128.28) --
-	(399.30,123.96) --
-	(406.84, 92.40) --
-	(414.38, 87.06) --
-	(421.91, 85.30) --
-	(429.45, 79.23) --
-	(436.99, 77.99) --
-	(444.53, 73.04) --
-	(452.06, 70.90) --
-	(459.60, 70.16) --
-	(467.14, 66.88) --
-	(474.68, 64.57) --
-	(482.21, 62.37) --
-	(489.75, 60.94) --
-	(497.29, 60.13) --
-	(504.82, 59.14) --
-	(512.36, 58.16) --
-	(519.90, 57.82) --
-	(527.44, 57.64) --
-	(534.97, 57.52) --
-	(542.51, 57.52) --
-	(550.05, 57.39) --
-	(557.59, 57.39) --
-	(565.12, 56.99);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (478.18, 97.05) --
+	(483.93, 96.63) --
+	(489.68, 94.07) --
+	(495.43, 95.65) --
+	(501.18, 97.81) --
+	(506.93, 97.47) --
+	(512.68, 98.36) --
+	(518.43, 95.36) --
+	(524.18, 73.48) --
+	(529.93, 69.78) --
+	(535.68, 68.56) --
+	(541.43, 64.35) --
+	(547.18, 63.49) --
+	(552.93, 60.05) --
+	(558.68, 58.57) --
+	(564.43, 58.06) --
+	(570.18, 55.78) --
+	(575.93, 54.18) --
+	(581.68, 52.66) --
+	(587.43, 51.66) --
+	(593.18, 51.10) --
+	(598.93, 50.42) --
+	(604.68, 49.74) --
+	(610.43, 49.50) --
+	(616.18, 49.38) --
+	(621.93, 49.29) --
+	(627.68, 49.29) --
+	(633.43, 49.20) --
+	(639.18, 49.20) --
+	(644.93, 48.92);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.39, 30.69) rectangle (572.66,266.42);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (460.93, 30.69) rectangle (644.93,194.15);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44, 38.37) {1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44, 90.38) {2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,142.40) {3};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,194.41) {4};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,246.42) {5};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98, 35.09) {1};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98, 71.15) {2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98,107.22) {3};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98,143.29) {4};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98,179.35) {5};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64, 41.40) --
-	(316.39, 41.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64, 93.41) --
-	(316.39, 93.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,145.43) --
-	(316.39,145.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,197.44) --
-	(316.39,197.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,249.45) --
-	(316.39,249.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18, 38.12) --
+	(460.93, 38.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18, 74.18) --
+	(460.93, 74.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18,110.25) --
+	(460.93,110.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18,146.32) --
+	(460.93,146.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18,182.38) --
+	(460.93,182.38);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (346.54, 27.94) --
-	(346.54, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (421.91, 27.94) --
-	(421.91, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.29, 27.94) --
-	(497.29, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (572.66, 27.94) --
-	(572.66, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (478.18, 27.94) --
+	(478.18, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (535.68, 27.94) --
+	(535.68, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (593.18, 27.94) --
+	(593.18, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (346.54, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (421.91, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (497.29, 19.68) {20};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.66, 19.68) {30};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (478.18, 19.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (535.68, 19.68) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (593.18, 19.68) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (444.53,  7.64) {Cohort time (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (552.93,  7.64) {Time (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,148.55) {Reproduction number $\mathcal R$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (446.70,112.42) {Reproduction number $\mathcal R$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (450.83,208.36) rectangle (566.36,253.77);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[fill=fillColor] (528.28,146.93) rectangle (643.82,192.34);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (456.33,228.31) rectangle (470.78,242.77);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[fill=fillColor] (533.78,166.88) rectangle (548.24,181.34);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{240,228,66}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor,fill opacity=0.50] (457.04,229.02) rectangle (470.07,242.05);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor,fill opacity=0.50] (534.49,167.59) rectangle (547.53,180.63);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{240,228,66}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (457.77,235.54) -- (469.33,235.54);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (535.23,174.11) -- (546.79,174.11);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (456.33,213.86) rectangle (470.78,228.31);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[fill=fillColor] (533.78,152.43) rectangle (548.24,166.88);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,114,178}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line cap=rect,fill=fillColor,fill opacity=0.50] (457.04,214.57) rectangle (470.07,227.60);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line cap=rect,fill=fillColor,fill opacity=0.50] (534.49,153.14) rectangle (547.53,166.17);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,114,178}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (457.77,221.09) -- (469.33,221.09);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (535.23,159.66) -- (546.79,159.66);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.28,232.51) {6 day doubling period};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (553.74,171.08) {6 day doubling period};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.28,218.05) {8 day doubling period};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (553.74,156.63) {8 day doubling period};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (316.39,274.49) {B};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (460.93,202.22) {C. Cohort-averaged estimates};
 \end{scope}

### 2020-04-20 serial_analysis.R

@@ -18,15 +18,20 @@ rr <- read_xlsx("Table S5.xlsx", skip=1) %>%
   )
 
 rr_summ <- rr %>%
-  group_by(cohort, serial) %>%
+  group_by(cohort) %>%
   summarize(
-    size=length(serial)
+    mean=mean(serial),
+    lwr=max(serial),
+    upr=min(serial)
   )
 
 rr_summ2 <- rr %>%
-  group_by(cohort) %>%
+  mutate(cohort=`Seconday - symptom onset date`) %>%
+  group_by(cohort)  %>%
   summarize(
-    mean=mean(serial)
+    mean=mean(serial),
+    lwr=max(serial),
+    upr=min(serial)
   )
 
 tcut <- seq(0, 29, by=1)
@@ -79,34 +84,58 @@ serdata2 <- lapply(tcut, function(x) {
 
 serall <- bind_rows(serdata1, serdata2)
 
-g1 <- ggplot(rr_summ) +
-  geom_boxplot(aes(cohort, serial, group=cohort)) +
-  # geom_point(data=rr_summ2, aes(cohort, mean), col=cpalette[2]) +
-  # geom_line(data=rr_summ2, aes(cohort, mean), col=cpalette[2], lty=2) +
-  scale_x_continuous("Cohort time (days)", limits=c(-4, 30), expand=c(0, 0)) +
-  scale_y_continuous("Forward serial intervals (days)") +
-  ggtitle("A") +
+mm <- max(c(rr$`Seconday - symptom onset date`, rr$`Index - symptom onset date`))
+
+cdata <- data.frame(
+  x=9:30,
+  y=30-9:30
+)
+
+g1 <- ggplot(rr) +
+  geom_line(data=cdata, aes(x, y), lty=2) +
+  geom_point(data=rr_summ, aes(cohort, mean)) +
+  geom_errorbar(data=rr_summ, aes(cohort, ymin=lwr, ymax=upr), width=0) +
+  geom_smooth(aes(cohort, serial), col=1, fill=1, fullrange=TRUE, alpha=0.2) +
+  scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(-3, 29)) +
+  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(-12, 21)) +
+  scale_size_area(max_size=4) +
+  coord_cartesian(clip="off", default=TRUE) +
+  ggtitle("A. Forward serial interval") +
   theme(
     panel.grid = element_blank(),
[…]

### 2020-04-20 serial.tex
final tweaks before sending off?

@@
 Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different distributions are able to give identical estimates of $\mathcal R$.
-In general, generation-interval distributions with higher means and less variability are expected to give higher $\mathcal R$ for a given $r$.
+In general, generation-interval distributions with higher means and less variability are expected to give higher $\mathcal R$ for a given $r$ \citep{wallinga2007generation, park2019practical}.
 In this case, the initial forward serial intervals during the exponential growth phase have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
@@
 Solid lines and ribbons represent the estimated locally estimated scatterplot smoothing (LOESS) fits and associated 95\% confidence intervals.
-The dashed line represents the maximum observable delay calculated from the most recent observed symptom onset date.
+The dashed line represents the maximum observable delay for each primary cohort calculated from the most recent observed symptom onset date.
 (C) Cohort-averaged estimates of $\mathcal R$ assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
@@
 
-Both generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating $\mathcal R$ --- yet important quantities in characterizing an epidemic.
-Here, we provided the first theoretical basis for understanding serial intervals and showed that naively using the observed serial intervals may lead to biased conclusions.
-Our re-analysis of the serial intervals of COVID-19 from China provided further support for our analysis.
+Desipte these limitations, our analysis of serial intervals of COVID-19 provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of $\mathcal R$.
+To our knowledge, most, if not all, existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
+Our study provides a rationale for reassessing estimates of serial-interval distributions of the COVID-19 pandemic.
 

### 2020-04-22 serial.tex
appendix

@@
 
-% \usepackage{lineno}
-% \linenumbers
+\usepackage{lineno}
+\linenumbers
 
@@
 	\textbf\newline{
-		Unraveling the paradox between generation and serial intervals: applications to COVID-19 pandemic
+		Unraveling the paradox between generation and serial intervals: applications to the COVID-19 pandemic
 	}
@@
 the corresponding reproduction number in a fully susceptible population --- referred to as the basic reproduction number $\mathcal R_0$ --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
-Since reproduction numbers cannot be measured directly, particularly during the outset of an outbreak, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{du2020serial, jung2020real, li2020early, zhao2020preliminary}).
+Since reproduction number cannot be measured directly, particularly during the outset of an outbreak, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{du2020serial, jung2020real, li2020early, zhao2020preliminary}).
 
@@
 We refer to this distribution as the forward delay distribution and denote it as $f_\pi(\tau)$.
-%% The forward delay distributions can vary across primary cohorts.
-%% \jd already implied, and may block the flow
 
@@
 The serial interval is defined as the time between when an infector becomes symptomatic and when and infectee becomes symptomatic.
-Serial intervals $\tau$ have been typically written in the form of:
+Serial intervals $\tau$ have been typically written in the form:
 \begin{equation}
@@
 \textbf{Illustration of forward and backward serial intervals.}
-(A) The forward serial interval for a primary cohort $\ell$ (i.e., an infector who became symptomatic at time $\ell$).
+(A) The forward serial interval for a primary cohort $\pi$ (i.e., an infector who became symptomatic at time $\pi$).
 In this case, $x_0$ represents the backward incubation period of the infector;
@@
 and $x_1$ represents the forward incubation period of the infectee.
-(B) The backward serial interval for a secondary cohort $\ell$ (i.e., an infectee who became symptomatic at time $\ell$).
+(B) The backward serial interval for a secondary cohort $\delta$ (i.e., an infectee who became symptomatic at time $\delta$).
 In this case, $x_0$ represents the forward incubation period of the infector;
@@
 \end{equation}
-In Appendix, we provide a mathematical proof that this relationship holds.
+In the Appendix, we provide a mathematical proof that this relationship holds.
 
@@
 
+\subsection{Realized serial interval distributions}
+
 The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $g(\tau)$ give identical estimates of $\mathcal R$ regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
@@
 as $r$ increases, ${\mathcal R}_{\textrm{\tiny naive}}$ saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
-While the forward serial intervals during the exponential growth phase can be also negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation periods (and therefore a lower proportion of negative serial intervals).
+While the forward serial intervals during the exponential growth phase can also be negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation periods (and therefore a lower proportion of negative serial intervals).
 
@@
 The initial forward serial interval distribution only applies to the exponential growth phase of an epidemic.
-Nowm, we characterize how forward and backward serial intervals vary over the course of an epidemic when incubation periods and generation intervals are independent.
+Now, we characterize how forward and backward serial intervals vary over the course of an epidemic when incubation periods and generation intervals are independent.
 \fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on the Gillespie algorithm.
@@
 The forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation periods of infectors, (ii) the forward generation intervals, and (iii) the forward incubation periods of infectees.
-Since both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant, changes in the forward serial-interval distributions are predominantly driven by the changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
+Since both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant, changes in the forward serial-interval distributions are predominantly driven by changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
 In this case, the increase in the mean backward incubation period directly translates to the decrease in the mean forward serial interval.
-We note that the relative contributions of the three distributions depend on their shapes and correlations between incubation periods and generation intervals --- as discussed earlier, the backward incubation period has ``no'' effect on the forward serial intervals in the SEIR model because transmission always occurs after symptom onset.
+We note that the relative contributions of the three distributions depend on their shapes and correlations between incubation periods and generation intervals --- as discussed earlier, the backward incubation period has \emph{no} effect on the forward serial intervals in the SEIR model, because transmission always occurs after symptom onset.
 
-Qualitative patterns in the changes in the mean backward delays is robust across all delay distributions because they are predominantly driven by the changes in incidence (\fref{epi}D--F).
+Qualitative patterns in the mean backward delays is robust across all delay distributions because they are predominantly driven by the changes in incidence (\fref{epi}D--F).
 When incidence increases exponentially, individuals are more likely to have been infected more recently and therefore, we are more likely to observe shorter intervals.
 When incidence decreases, we are more likely to observe longer intervals for similar but opposite reasons.
-Since changes in incidence can occur even in the absence of significant susceptible depletion (e.g., due to intervention), we expect the qualitative patterns in the changes of backward delay distributions to be robust across many outbreaks.
+Since changes in incidence can occur even in the absence of significant susceptible depletion (e.g., due to intervention), we expect qualitative patterns in the changes of backward delay distributions to be robust across many outbreaks.
 
@@
 \end{figure}
+
+\subsection{Observed serial interval distributions}
 
@@
 
+\subsection{Applications to the COVID-19 pandemic}
+
 Finally, we reanalyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on transmission events reported between January 21--February 8, 2020;
@@
 While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculate earlier based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
-These results indicate that previous estimates of incubation period and generation-intervals may have been underestimated as neither studies explicitly account for right-censoring (Table 1).
-We do not explicitly account for the right-censoring as it is beyond the scope of this study.
+These results indicate that previous estimates of incubation period and generation-intervals may have been underestimated as neither study explicitly accounts for right-censoring (Table 1).
+%We do not explicitly account for the right-censoring as it is beyond the scope of this study.
 
@@
 We note that early cohort-averaged estimates of $\mathcal R_0$ are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
-This example clearly demonstrates the danger of naively averaging the observed serial intervals and calculating the reproduction number using them.
+This example clearly demonstrates the danger of simply averaging the observed serial intervals and calculating the reproduction number using them.
 
@@
 
-Characterizing generation- and serial-interval distributions are critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
+Characterizing generation- and serial-interval distributions is critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
 Generation intervals measure the time difference between infection of a transmission pair, whereas serial intervals measure the time difference between symptom onset of a transmission pair \citep{svensson2007note}.
-Due to their similar definitions, their differences have been inaccurately captured and misunderstood previously.
+Due to their similar definitions, we show that their differences have been inaccurately captured previously.
 
@@
 
-\section*{Appendix}
+\section{Appendix}
 
-Recall that the forward serial interval can be written as:
-\begin{equation}
-- x_0 + \sigma + x_1
-\end{equation}
-Note that $x_1$ is independent of $x_0$ and $\sigma$. Then, we get:
-\begin{equation}
-M_{- x_0 + \sigma + x_1}(-r) = M_{- x_0 + \sigma}(-r) M_{x_1}(-r).
-\end{equation}
-We want to show that 
-\begin{equation}
-M_{- x_0 + \sigma}(-r)= \frac{M_\sigma(-r)}{M_{x_1}(-r)}
-\end{equation}
-for $r \geq 0$.
-Note that the time between symptom onset and infection of an infectee follows the following distribution:
-\begin{equation}
-z(\tau) \propto \int_{\max(0, -\tau)}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \tau+x_0) \mathrm{d} x_0.
-\end{equation}
-During the exponential growth phase, we have
+\subsection{Deterministic simulation}
+
+We simulate the renewal equation model using a discrete-time approximation:
 \begin{equation}
 \begin{aligned}
-z_{\textrm{\tiny exp}}(\tau) &= \frac{1}{N} \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\\
-% &= \frac{1}{N} \int_{0}^\infty \left[ \exp(- r x_0) k(x_0) \times \frac{h(x_0, \tau+x_0)}{k(x_0)}\right] \mathrm{d} x_0
+i(t) &= \mathcal R_0 S(t-\Delta t) \sum_{m=1}^{\ell} i(t-\Delta t m) \hat{g}(\Delta t m) \\
+S(t) &= S(t-\Delta t) - i(t)
 \end{aligned}
 \end{equation}
-where $N$ is the normalization factor:
+where $\hat{g}$ is a discrete-time intrinsic generation-interval distribution that satisfies the following:
+\begin{equation}
+\hat{g}(\Delta t m) = \frac{g(\Delta t m)}{\sum_{i=1}^\ell g(\Delta t m)}, \quad m=1, \dots, \ell
+\end{equation}
+The continuous-time intrinsic generation-interval distribution is parameterized using a log-normal distribution (Table 1). We define the forward incubation period distribution in a similar manner:
+\begin{equation}
+\hat{k}(\Delta t m) = \frac{k(\Delta t m)}{\sum_{i=1}^\ell k(\Delta t m)}, \quad m=1, \dots, \ell,
+\end{equation}
+where its continuous-time analog is also based on a log-normal distribution.
+For brevity, we assume that the forward incubation periods and intrisic generation intervals are independent:
+\begin{equation}
+\hat{h}(\Delta t m, \Delta t n) = \hat{k}(\Delta t m)\hat{g}(\Delta t n), \quad m,n=1, \dots, \ell.
+\end{equation}
+We use $\Delta t = 0.025\,\textrm{days}$ and $\ell=2001$ for discretization steps.
+
+We initialize the simulation with population size $N$=40,000 as follows:
 \begin{equation}
 \begin{aligned}
-N &= \int_{-\infty}^\infty \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\,\mathrm{d}\tau\\
-&= \int_{0}^\infty \int_{-x_0}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d}\tau\,\mathrm{d} x_0\\
-&= \int_{0}^\infty \exp(- r x_0) k(x_0) dx_0\\
-&= M_{x_1}(-r)
+i(\Delta t m) &= C \exp(r \Delta t m), \quad m=1, \dots, \ell\\
+S(\Delta t m) &= N - \sum_{n=1}^m i(\Delta t m), \quad m=1, \dots, \ell\\
 \end{aligned}
 \end{equation}
-Therefore,
+where $C$ is chosen such that $\sum_{n=1}^\ell i(\Delta t m)=10$.
+These initial conditions allow the model to follow exponentially growth from time $\Delta t (\ell + 1)$ without any transient behaviors.
+Results presented in the main text show simulations beginning from time $\Delta t (\ell + 1)$.
+
+\subsection{Stochastic simulation}
+
+We run stochastic simulations of the renewal equation model using an individual-based model on a fully connected network (i.e., homogeneous population) based on the Gillespie algorithm that we devloped earlier \citep{park2019inferring}.
+First, we initialize an epidemic with $I(0)$ infected individuals (nodes) in a fully connected network of size $N$. 
+For each initially infected individual, we draw number of infectious contacts from a Poisson distribution with the mean of $\mathcal R_0$ and the corresponding generation intervals for each contact from a log-normal distribution (Table 1).
+Contactees are uniformly sampled from the total population.
+All contactees are sorted into event queues based on their infection time.
+We update the current time to the infection time of the first person in the queue.
+Then, the first person in the queue makes contacts based on the Poisson offspring distribution described earlier and their contactees are added to the sorted queue.
+Whenever contactees are aded to the sorted queue, we remove all duplicated contacts (but keep the first one) as well as contacts made to individuals that have already been infected.
+Simulations continue until there are no more individuals in the queue.
+We simulate 10 epidemics with $I(0)=10$ and $N$=40,000.
+
+\subsection{Linking $r$ and $\mathcal R$ using serial-interval distributions}
+
+The intrinsic generation-interval distribution $g(\tau)$ provides a link between $r$ and $\mathcal R$ via the Euler-Lotka equation:
+\begin{equation}
+\frac{1}{\mathcal R} = \int_0^\infty \exp(-r\tau) g(\tau) \mathrm{d} \tau.
+\end{equation}
+Here, we prove that the initial forward serial-interval distribution $f_0$ also provides the same link:
+\begin{equation}
+\frac{1}{\mathcal R} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
+\end{equation}
+where the initial forward serial-interval distribution is defined as:
+\begin{equation}
+f_{0}(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \exp(-rx) h(x, \sigma) k(x-\sigma+\tau) \mathrm{d}\sigma\,\mathrm{d}x.
+\end{equation}
+
+First, we rewrite the initial forward serial-interval distribution in the following form:
 \begin{equation}
 \begin{aligned}
-&\int_{-\infty}^{\infty} \exp(-r\tau) z_{\textrm{\tiny exp}}(\tau) \mathrm{d}\tau\\
-&=\frac{1}{M_{-x_1}(-r)} \int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\, \mathrm{d}\tau
+f_{0}(\tau) &\propto \int_0^\infty \int_{-\alpha_1}^{\tau} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) k(\tau - \alpha_2) \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1\\
+&= \int_{-\infty}^{\tau} \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1)k(\tau - \alpha_2)\mathrm{d}\alpha_1\, \mathrm{d}\alpha_2\\
 \end{aligned}
 \end{equation}
-
-Finally, we are left to prove that 
+It follows that $z(\alpha_2)$ describes the time between symptom onset of infector and infection of infectee:
 \begin{equation}
-\int_0^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau = \int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\, \mathrm{d}\tau
+z(\alpha_2) \propto \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1.
 \end{equation}
-where $g$ is a marginal probability distribution of $h$ describing the forward generation intervals:
-\begin{equation}
-g(\tau) = \int_0^\infty h(x_0, \tau)  \mathrm{d} x_0.
-\end{equation}
-Let $a = x_0 + \tau$. Then, by change of variables, it immediately follows that
+The initial forward serial-interval distribution $f_0$ can be expressed as a convolution of $z$ and $k$:
 \begin{equation}
 \begin{aligned}
-&\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r x_0) h(x_0, \tau+x_0) \mathrm{d} x_0\, \mathrm{d}\tau\\
-&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r a) h(x_0, a) \mathrm{d} x_0\, \mathrm{d}a\\
+f_{0}(\tau) &\propto \int_{-\infty}^{\tau} z(\alpha_2) k(\tau - \alpha_2) \mathrm{d}\alpha_2.\\
+\end{aligned}
+\end{equation}
+Then, we have
+\begin{equation}
+\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau \int_{0}^\infty \exp(-r\tau) k(\tau) \mathrm{d} \tau
+\end{equation}
+
+Note that 
+\begin{equation}
+\begin{aligned}
+&\int_{-\infty}^\infty \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1 \mathrm{d}\alpha_2\\
+&= \int_{0}^\infty \int_{-\alpha_1}^\infty \exp(- r \alpha_1) h(\alpha_1, \alpha_2+\alpha_1) \mathrm{d}\alpha_2\,\mathrm{d} \alpha_1\\
+&= \int_{0}^\infty \exp(- r \alpha_1) k(\alpha_1) d\alpha_1
+\end{aligned}
+\end{equation}
+because $k$ is a marginal probability distribution of $h$.
+Since $\int_{0}^\infty \exp(- r \alpha_1) k(\alpha_1) d\alpha_1$ is a normalization factor for probability distribution $z$, we have:
+\begin{equation}
+\int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau = \frac{\int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1 \mathrm{d}\tau}{\int_{0}^\infty \exp(- r \alpha_1) k(\alpha_1) d\alpha_1}.
+\end{equation}
+Then, we have:
+\begin{equation}
+\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1 \mathrm{d}\tau.
+\end{equation}
+
+We are left to show that 
+\begin{equation}
+\int_0^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1 \mathrm{d}\tau,
+\end{equation}
+where the intrisic generation-interval distribution $g$ is also a marginal probability distribution of $f$:
+\begin{equation}
+g(\tau) = \int_0^\infty h(\alpha_1, \tau)  \mathrm{d} \alpha_1.
+\end{equation}
+Let $\sigma = \alpha_1 + \tau$. Then, by change of variables, it immediately follows that
+\begin{equation}
+\begin{aligned}
+&\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r \alpha_1) h(\alpha_1, \tau+\alpha_1) \mathrm{d} \alpha_1\, \mathrm{d}\tau\\
+&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \sigma) h(\alpha_1, \sigma) \mathrm{d} \alpha_1\, \mathrm{d}\sigma\\
 &=\int_{0}^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau
@@
 \end{equation}
-Therefore, the forward serial- and generation-interval distributions give the same link between $r$ and $\mathcal R$.
+Therefore, the initial forward serial--interval distribution and the intrinsic generation-interval distribution give the same link between $r$ and $\mathcal R$.
 

### 2020-04-22 renewal_det.R

@@ -7,14 +7,14 @@ renewal_det <- function(R0=2.5,
                         I0=10,
                         tmax=200,
                         genmax=2000) {
-  inc <- incfun(0:genmax*dt)
+  inc <- incfun(0:genmax*dt+dt)
   inc <- inc/sum(inc)
-  gen <- genfun(0:genmax*dt)
+  gen <- genfun(0:genmax*dt+dt)
   gen <- gen/sum(gen)
   tvec <- seq(0, tmax, by=dt)
   Ivec <- rep(0, dt*tmax)
   
-  r <- optim(0.19, function(x) (1/sum(exp(-x*(0:genmax*dt)) * gen)-R0)^2,
+  r <- optim(0.19, function(x) (1/sum(exp(-x*(0:genmax*dt+dt)) * gen)-R0)^2,
         lower=0.1,
         upper=0.3,
         method="Brent")[[1]]
@@ -35,10 +35,10 @@ renewal_det <- function(R0=2.5,
   forwardinc <- sapply(1:(length(Svec)-genmax), function(x) inc)
   backwardinc <- sapply((genmax+1):(length(Svec)), function(x) inc[1:(1+genmax)]*Ivec[x:(x-genmax)]/sum(inc[1:(1+genmax)]*Ivec[x:(x-genmax)]))
   
-  mfgen <- apply(forwardgen, 2, function(x) sum(x*0:genmax*dt)/sum(x))
-  mbgen <- apply(backwardgen, 2, function(x) sum(x*0:genmax*dt)/sum(x))
-  mfinc <- apply(forwardinc, 2, function(x) sum(x*0:genmax*dt)/sum(x))
-  mbinc <- apply(backwardinc, 2, function(x) sum(x*0:genmax*dt)/sum(x))
+  mfgen <- apply(forwardgen, 2, function(x) sum(x*(0:genmax*dt+dt))/sum(x))
+  mbgen <- apply(backwardgen, 2, function(x) sum(x*(0:genmax*dt+dt))/sum(x))
+  mfinc <- apply(forwardinc, 2, function(x) sum(x*(0:genmax*dt+dt))/sum(x))
+  mbinc <- apply(backwardinc, 2, function(x) sum(x*(0:genmax*dt+dt))/sum(x))
   
   mfser <- head(sapply((genmax+1):(length(Svec)), function(x) sum(backwardinc[,x-genmax]*rev(mfgen[(x-genmax):x]))),-genmax) +
[…]

### 2020-04-22 serial.tex
tex

@@
 \section*{Abstract}
+
+Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number $\mathcal R$ --- yet important quantities in understanding the outset of an outbreak.
+Due to their similar definitions, generation and serial intervals have been often used interchangeably even though two distributions are different.
+We argue that a part of the confusion can be attributed to an apparent paradox.
+As the generation-interval distribution describes the renewal process of infection, it provides a link between the epidemic growth rate $r$ and the reproduction number $\mathcal R$;
+likewise, the serial-interval distribution should describe the renewal process of symptomatic infection and therefore, should provide the same link between the epidemic growth rate $r$ and the reproduction number $\mathcal R$.
+However, the current theory does not explain how two different distributions can give the same link between $r$ and $\mathcal R$ link.
+We provide an answer to the paradox.
+We show that serial intervals have to be defined with a reference perspective and a reference time;
+the forward serial interval distribution during the exponential provides the correct link between $r$ and $\mathcal R$.
+We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references.
+Our study reveals gaps in the current understanding of serial intervals and provides rationale for reassessing serial intervals of COVID-19.
 

### 2020-04-22 serial_mli.tex
Con't on 2.3

--- 2020-04-22 serial.tex
@@
 \newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
+\newcommand{\mli}[1]{\comment{blue}{}{#1}}
 
@@
 Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number $\mathcal R$ --- yet important quantities in understanding the outset of an outbreak.
+\mli{Feels really harsh and unfair. People do care about ``time intervals''. In fact, from a selfish point of view, people care more how long they are going to be ill than how many people infect.}
 Due to their similar definitions, generation and serial intervals have been often used interchangeably even though two distributions are different.
@@
 Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its reproduction number $\mathcal R$ \citep{majumder2020early}.
+\mli{Isn't this true for every disease and every outbreak? Maybe put covid19 at the end of the sentence?}
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
@@
 Since reproduction number cannot be measured directly, particularly during the outset of an outbreak, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{du2020serial, jung2020real, li2020early, zhao2020preliminary}).
+\mli{The first part of the last sentence is false, if you have contact tracing, you know the reproduction number directly.
+If I know exactly who and how many people I infect, that is the reproduction number by definition.
+Gr-link is just a way to estimate R.
+Probably good to explain why we like it.
+I.e.
+based on reporting data, we can estimate little r, if we don't know much about G or S, we can use some prior or similar known thing as a first approximation proxy.}
 
@@
 the generation-interval distributions plays a key role in shaping the relationship between the exponential growth rate $r$ and the reproduction number $\mathcal R$ \citep{wallinga2007generation}.
+\mli{also cite park et al?
+generation paper?}
 Similarly, the serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
@@
 However, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can bias the estimate of $\mathcal R$.
+\mli{How bad can it be? Compared to all the other problems people are sweeping under the rug (I am defintely not saying it is okay to misuse it, but it is going to change by 1\%, 10\% ...)}
 We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of the ongoing pandemic.
@@
 most epidemiological events that can be observed within an individual have clear direction (e.g., infection and onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
+\mli{It sounds really confusing. Onset of symptoms appears in both clear direction and the latter (not clear direction?).}
 % \jd{Rethink, or else rethink ``any'' above: the ``hidden'' time (my term) is the time between onset of infectiousness and onset of symptoms; it is within, but can be positive or negative.
@@
 The primary event refers to the event that occurs within an infector and does not necessarily occur before the secondary event.
+\mli{Long text is hard to read.. I had to read it multiple times to see the difference. Maybe construct a within and between infected individuals table and have a side by side comparison.}
 
@@
 For example, when we are measuring serial intervals, a primary cohort $\pi$ consists of all infectors who became symptomatic at time $\pi$.
+\mli{$\pi$ has different units in the previous S. (1) a primary cohort of ``individuals'' and ... time ``$\pi$''}
+
 Then, for each primary cohort $\pi$, we can define the expected time distribution between primary and secondary events.
@@
 where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\sigma$ represents the realized generation interval.
+\mli{This equation is too compacted.
+$x_0$ is the incubation period of P; $x_1$ is the incubation period of S; $GI = \sigma = x_0 + waiting_time_P$.
+The $x_0$ cancels out and you are left with $waiting_time_P and x_1$.
+Maybe use the picture from my thesis, and start from the simple construction and show how to get it to equation 3.
+It is not at all an obvious until I took apart the pieces to validate this is true.}
 Previous studies have often assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
@@
 and $x_1$ represents the forward incubation period for the infectees who became infected at time $\pi - x_0 + \sigma$.
+\mli{Okay, I suggest switching places...
+explain this first before the first paragraph.
+All this forward and backwards thing is making your write backwards as well.
+In figure 1A, calling that a forward generation interval feels weird.
+The focal point is in the middle of the generation interval, it is only seeing the waiting time.}
 

### 2020-04-26 serial.tex
spell-checking

@@
 However, the cohort-averaged estimates decreases rapidly soon after the exponential growth period.
-This approach allows us to characterize potential biases in the estimates of $\mathcal R$ cuased by changes in the forward serial-interval distributions.
+This approach allows us to characterize potential biases in the estimates of $\mathcal R$ caused by changes in the forward serial-interval distributions.
 
@@
 
-Desipte these limitations, our analysis of serial intervals of COVID-19 provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of $\mathcal R$.
+Despite these limitations, our analysis of serial intervals of COVID-19 provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of $\mathcal R$.
 To our knowledge, most, if not all, existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
@@
 where its continuous-time analog is also based on a log-normal distribution.
-For brevity, we assume that the forward incubation periods and intrisic generation intervals are independent:
+For brevity, we assume that the forward incubation periods and intrinsic generation intervals are independent:
 \begin{equation}
@@
 
-We run stochastic simulations of the renewal equation model using an individual-based model on a fully connected network (i.e., homogeneous population) based on the Gillespie algorithm that we devloped earlier \citep{park2019inferring}.
+We run stochastic simulations of the renewal equation model using an individual-based model on a fully connected network (i.e., homogeneous population) based on the Gillespie algorithm that we developed earlier \citep{park2019inferring}.
 First, we initialize an epidemic with $I(0)$ infected individuals (nodes) in a fully connected network of size $N$. 
@@
 Then, the first person in the queue makes contacts based on the Poisson offspring distribution described earlier and their contactees are added to the sorted queue.
-Whenever contactees are aded to the sorted queue, we remove all duplicated contacts (but keep the first one) as well as contacts made to individuals that have already been infected.
+Whenever contactees are added to the sorted queue, we remove all duplicated contacts (but keep the first one) as well as contacts made to individuals that have already been infected.
 Simulations continue until there are no more individuals in the queue.
@@
 \end{equation}
-where the intrisic generation-interval distribution $g$ is also a marginal probability distribution of $f$:
+where the intrinsic generation-interval distribution $g$ is also a marginal probability distribution of $f$:
 \begin{equation}

### 2020-04-27 serial.tex
lots of notation, comments

@@
 \usepackage{graphicx}
+\usepackage{xspace}
 %\usepackage{adjustbox}
@@
 \newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
+\newcommand{\bmb}[1]{\comment{blue}{BMB}{#1}}
 
@@
 
-\newcommand{\Rx}[1]{\ensuremath{{\mathcal R}_{#1}}} 
+\newcommand{\Rx}[1]{\ensuremath{{\mathcal R}_{#1}}\xspace} 
 \newcommand{\Ro}{\Rx{0}}
 \newcommand{\Rc}{\Rx{c}}
-\newcommand{\RR}{\ensuremath{{\mathcal R}}}
+\newcommand{\RR}{\ensuremath{{\mathcal R}}\xspace}
 \newcommand{\Rhat}{\ensuremath{{\hat\RR}}}
+\newcommand{\Rnaive}{\ensuremath{{\mathcal R}_{\textrm{\tiny naive}}}\xspace}
 \newcommand{\tsub}[2]{#1_{{\textrm{\tiny #2}}}}
-
+\newcommand{\dd}[1]{\ensuremath{\, \mathrm{d}#1}}
+\newcommand{\dtau}{\dd{\tau}}
+\newcommand{\dx}{\dd{x}}
+\newcommand{\dsigma}{\dd{\sigma}}
 \begin{document}
@@
 
-Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number $\mathcal R$ --- yet important quantities in understanding the outset of an outbreak.
-Due to their similar definitions, generation and serial intervals have been often used interchangeably even though two distributions are different.
+Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number \RR --- yet important quantities in understanding the outset of an outbreak.
 We argue that a part of the confusion can be attributed to an apparent paradox.
-As the generation-interval distribution describes the renewal process of infection, it provides a link between the epidemic growth rate $r$ and the reproduction number $\mathcal R$;
-likewise, the serial-interval distribution should describe the renewal process of symptomatic infection and therefore, should provide the same link between the epidemic growth rate $r$ and the reproduction number $\mathcal R$.
-However, the current theory does not explain how two different distributions can give the same link between $r$ and $\mathcal R$ link.
-We provide an answer to the paradox.
-We show that serial intervals have to be defined with a reference perspective and a reference time;
-the forward serial interval distribution during the exponential provides the correct link between $r$ and $\mathcal R$.
+\bmb{need to define the paradox here, e.g.: ``although they cannot be used interchangeably in analyzing the behaviour of an epidemic, they give rise to nearly identical relationships between the epidemic growth rate $r$ and \RR''}
+As the generation-interval distribution describes the renewal process of infection, it provides a link between the epidemic growth rate $r$ and the reproduction number \RR;
+likewise, the serial-interval distribution should describe the renewal process of symptomatic infection and therefore, should provide the same link between the epidemic growth rate $r$ and the reproduction number \RR.
+%However, the current theory does not explain how two different distributions can give the same link between $r$ and $\mathcal R$ link.
+We provide an answer to the paradox by showing that if serial intervals are defined as \emph{forward-looking} intervals during the exponential phase, then the correct link between $r$ and \RR emerges.
 We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references.
@@
 
-Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its reproduction number $\mathcal R$ \citep{majumder2020early}.
+The reproduction number \RR is one of the most important characteristics of an emerging epidemic such as novel coronavirus disease (COVID-19) \citep{majumder2020early} \bmb{avoid starting a paper by saying ``X has been studied a lot''; instead, say it's important or interesting}
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
-the corresponding reproduction number in a fully susceptible population --- referred to as the basic reproduction number $\mathcal R_0$ --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
+the corresponding reproduction number in a fully susceptible population --- referred to as the basic reproduction number \Ro --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
 Since reproduction number cannot be measured directly, particularly during the outset of an outbreak, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{du2020serial, jung2020real, li2020early, zhao2020preliminary}).
@@
 The generation interval is defined as the time between when an individual (infector) is infected and when an individual infects another person (infectee);
-the generation-interval distributions plays a key role in shaping the relationship between the exponential growth rate $r$ and the reproduction number $\mathcal R$ \citep{wallinga2007generation}.
+the generation-interval distribution determines the relationship between the exponential growth rate $r$ and the reproduction number \RR \citep{wallinga2007generation}.
 Similarly, the serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
 While serial intervals are similar to generation intervals, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence};
-some studies further suggested that using serial intervals can give different estimates of $\mathcal R$ \citep{britton2019estimation}.
+some studies further suggested that using serial intervals can give different estimates of \RR \citep{britton2019estimation}.
 Even these distributions were clearly distinguished over a decade ago \citep{svensson2007note}, 
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds:
-Researchers continue to rely on both generation and serial intervals to estimate $\mathcal R$ for COVID-19 without making a clear distinction.
+Researchers continue to rely on both generation and serial intervals to estimate \RR for COVID-19 without making a clear distinction.
 
@@
 When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
-This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number $\mathcal R$ \citep{wallinga2007generation}.
+This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR \citep{wallinga2007generation}.
 Likewise, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
-Therefore, both generation- and serial-interval distributions should give us identical estimates of  $\mathcal R$ based the observed epidemic growth rate $r$.
+Therefore, both generation- and serial-interval distributions should give us identical estimates of  \RR based the observed epidemic growth rate $r$.
 In contexts where the distributions are expected to be different, current theory has no explanation for how they might link $r$ to \Rx\ in the same way.
@@
 Here, we provide an answer to this paradox, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
-We develop a new framework for understanding serial intervals and show that the initial forward serial-interval distribution gives the correct value of $\mathcal R$.
+We develop a new framework for understanding serial intervals and show that the initial forward serial-interval distribution gives the correct value of \RR.
 %\jd{Come back to this. Not just over time, right?} \swp{What do you mean? Everything is about time here... you haven't read the results section so maybe that's why?}
-However, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can bias the estimate of $\mathcal R$.
+However, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can bias the estimate of \RR.
 We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of the ongoing pandemic.
@@
 These ideas apply to all epidemiological delay distributions and generalize the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
+\bmb{need to work \textbf{really hard} to clarify the mechanisms driving various differences [backward vs forward, dependence on current $S$/epidemic phase, etc.]; which are caused by changes in cohort size over time (Euler-Lotka-type effects), which are caused by censoring/conditionality of observations, etc.
+?}
 
@@
 and $x_0$ represents the forward incubation period of the infector who became infected at time $\delta-x_1-\sigma$.
-This conceptual framework clearly demonstrates that the distributions of $x_0$, $\delta$, and $x_1$ (and therefore the distributions of serial intervals) depend on the perspective as well as time and cannot be treated statically.
+This conceptual framework clearly demonstrates that the distributions of $x_0$, $\delta$, and $x_1$ (and therefore the distributions of serial intervals) depend on the perspective \bmb{better/more consistent word than ``perspective''?} as well as time and cannot be treated statically.
+\bmb{please explain/clarify why the backward incubation period is not the same is as the forward}
 
-In order to define forward and backward serial interval distributions, we begin by writing the total number of serial intervals between time $\pi$ (when the infector developed symptoms) and $\delta$ (when the infectee developed symptoms), which can be expressed as an integral over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
+In order to define forward and backward serial interval distributions, we begin by writing the total number of serial intervals \bmb{explain more please \ldots} between time $\pi$ (when the infector developed symptoms) and $\delta$ (when the infectee developed symptoms), which can be expressed as an integral over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
 \begin{equation}
-T(\pi,\delta) = \int_{-\infty}^{\pi} \int_{\alpha_1}^{\delta} \mathcal R_c (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\delta - \alpha_2) \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1,
+T(\pi,\delta) = \int_{-\infty}^{\pi} \int_{\alpha_1}^{\delta} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\delta - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1,
 \end{equation}
-where $\mathcal R_c(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}), $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee).
+where $\Rc(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}) \bmb{is \Rc the same as ``forward \R measured at a particular time''?}, $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee).
 Then, the forward serial-interval distribution is proportional to $T(\pi, \pi+\tau)$. Substituting $x=\pi-\alpha_1$ and $\sigma=\alpha_2-\alpha_1$, we have:
 \begin{equation}
-f_\pi(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \mathcal R_c (\pi-x) i(\pi-x) h_{\pi-x}(x, \sigma) k_{\pi-x+\sigma}(x-\sigma+\tau) \mathrm{d}\sigma\,\mathrm{d}x
+f_\pi(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \Rc (\pi-x) i(\pi-x) h_{\pi-x}(x, \sigma) k_{\pi-x+\sigma}(x-\sigma+\tau) \dsigma \dx
 \end{equation}
@@
 \begin{equation}
-b_\delta(\tau) \propto \int_{0}^{\infty} \int_{\max(0, \tau-x)}^{\infty} \mathcal R_c (\delta-x-\sigma) i(\delta-x-\sigma) h_{\delta-x-\sigma}(x+\sigma-\tau, \sigma) k_{\delta-x}(x) \mathrm{d}\sigma\,\mathrm{d}x.
+b_\delta(\tau) \propto \int_{0}^{\infty} \int_{\max(0, \tau-x)}^{\infty} \Rc (\delta-x-\sigma) i(\delta-x-\sigma) h_{\delta-x-\sigma}(x+\sigma-\tau, \sigma) k_{\delta-x}(x) \dsigma \dx.
 \end{equation}
@@
 
-We validate the theory by applying it to a specific example of an epidemic model. 
+We validate \bmb{??} the theory by applying it to a specific example of an epidemic model. 
 We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
@@
 \frac{\mathrm{d}S}{\mathrm{d}t} &= - i(t)\\
-i(t) &= \mathcal R_0 S(t) \int_0^\infty i(t-\tau) g(\tau) \mathrm{d}\tau,
+i(t) &= \Ro S(t) \int_0^\infty i(t-\tau) g(\tau) \dtau,
 \end{aligned}
@@
 \end{equation}
-where $\mathcal R_0$ is the basic reproduction number, and $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
+where \Ro is the basic reproduction number, and $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
 Then, the forward generation-interval for a primary cohort $\pi$ follows \citep{champredon2015intrinsic}:
@@
 \begin{aligned}
-k(x) &= \int_0^\infty h(x, \tau) \mathrm{d}\tau\\
-g(\tau) &= \int_0^\infty h(x, \tau) \mathrm{d}x.
+k(x) &= \int_0^\infty h(x, \tau) \dtau\\
+g(\tau) &= \int_0^\infty h(x, \tau) \dx
 \end{aligned}
@@
 \begin{equation}
-\mathcal R_c(t) = \mathcal R_0 \int_0^\infty g(\tau) S(t+\tau) \mathrm{d} \tau.
+\Rc(t) = \Ro \int_0^\infty g(\tau) S(t+\tau) \dtau.
 \end{equation}
 
-\subsection{Linking $r$ and $\mathcal R$}
+\subsection{Linking $r$ and \RR}
 
-During the initial phase of an epidemic, the proportion susceptible remains constant ($S(t) = S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
-Then, we can estimate the reproduction number from the exponential growth rate $r$ via the Euler-Lotka equation:
+During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
+Then, we can use the Euler-Lotka equation to estimate the reproduction number from the exponential growth rate $r$ \bmb{ref??}:
 \begin{equation}
-\frac{1}{\mathcal R} = \int_0^\infty \exp(-r\tau) g(\tau) \mathrm{d} \tau.
+\frac{1}{\RR} = \int_0^\infty \exp(-r\tau) g(\tau) \dtau.
 \end{equation}
-Like forward generation-interval distributions, 
+Analogous to forward generation-interval distributions, 
 forward serial-interval distributions describe the renewal process of symptomatic cases.
-Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to provide the identical $r$--$\mathcal R$ link as the intrinsic generation-interval distribution:
+Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to provide the identical $r$--\RR link as the intrinsic generation-interval distribution:
 \begin{equation}
-\frac{1}{\mathcal R} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
+\frac{1}{\RR} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
 \end{equation}
@@
 \end{equation}
-In the Appendix, we provide a mathematical proof that this relationship holds.
+In the Appendix, we provide a mathematical proof of this relationship.
 
 The initial forward serial-interval distribution depends on the exponential growth rate $r$.
-For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short, and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation-interval distribution.
-The Susceptible-Exposed-Infected-Recovered model, which assumes that incubation and exposed periods are equivalent, is a special case where the conditional forward generation-interval distribution cancels out with the backward incubation period distribution exactly because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector;
+For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short \bmb{I \textbf{still} don't understand why backward incubation periods are dynamic as well as direction-sensitive \ldots}, and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation-interval distribution.
+The Susceptible-Exposed-Infected-Recovered model, which assumes that incubation and exposed periods are equivalent \bmb{note this is not generally how SEIR is defined.
+You need a special case}, is a special case where the conditional forward generation-interval distribution cancels out with \bmb{???} the backward incubation period distribution exactly because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector;
 in this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase.
@@
 The forward incubation period distribution is parameterized using a log-normal distribution with log mean $\mu_I=1.62$ and log standard deviation $\sigma_I=0.42$.
-The joint probability distribution is modeled using a multivariate log-normal distribution with correlations $\rho=-0.5, 0, 0.5$.
+The joint probability distribution is modeled using a multivariate log-normal distribution with correlations (on the log scale) $\rho=-0.5, 0, 0.5$.
 }
@@
 
-We use a simulation-based approach to compare the estimates of $\mathcal R$ based on the serial- and generation-interval distributions. 
+We use a simulation-based approach to compare the estimates of \RR based on the serial- and generation-interval distributions. 
 To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and correlation $\rho$;
@@
 the forward incubation period $I_i$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
-We then calculate the reproduction number $\mathcal R$ using the empirical estimator:
+We then calculate the reproduction number \RR using the empirical estimator:
 \begin{equation}
-\mathcal R = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r S_i)}.
+\RR = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r S_i)}.
 \end{equation}
-We compare this with an estimate of $\mathcal R$ based on naive serial-interval distribution that assumes that the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
+We compare this with an estimate of \RR based on naive serial-interval distribution that assumes that the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
 \begin{equation}
-{\mathcal R}_{\textrm{\tiny naive}} = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r Q_i)},
+  \Rnaive = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r Q_i)},
 \end{equation}
@@
 
-The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $g(\tau)$ give identical estimates of $\mathcal R$ regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
-However, using naive serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates $\mathcal R$;
-as $r$ increases, ${\mathcal R}_{\textrm{\tiny naive}}$ saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
+The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $g(\tau)$ give identical estimates of \RR regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
+However, using naive serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \RR;
+as $r$ increases, \Rnaive saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
 While the forward serial intervals during the exponential growth phase can also be negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation periods (and therefore a lower proportion of negative serial intervals).
@@
 \textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
-(A). The forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number $\mathcal R$.
-(B) The serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and $\mathcal R$.
+(A). The forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number \RR.
+(B) The serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and \RR.
 (C) The mean forward serial interval during the exponential growth phase depends on $r$.
@@
 
-Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different distributions are able to give identical estimates of $\mathcal R$.
-In general, generation-interval distributions with higher means and less variability are expected to give higher $\mathcal R$ for a given $r$ \citep{wallinga2007generation, park2019practical}.
+Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different distributions are able to give identical estimates of \RR.
+In general, generation-interval distributions with higher means and less variability are expected to give higher \RR for a given $r$ \citep{wallinga2007generation, park2019practical}.
 In this case, the initial forward serial intervals during the exponential growth phase have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
-The effects of higher means (which increases $\mathcal R$) and higher variability (which decreases $\mathcal R$) cancel out exactly;
-therefore, we can estimate the same $\mathcal R$ using both serial and generation intervals.
+The effects of higher means (which increases \RR) and higher variability (which decreases \RR) cancel out exactly;
+therefore, we can estimate the same \RR using both serial and generation intervals.
 
@@
 (A) Changes in the observed and cohort-averaged mean serial interval over time.
-(B) Changes in the estimate of $\mathcal R$ based on the observed and cohort-averaged mean serial interval over time.
+(B) Changes in the estimate of \RR based on the observed and cohort-averaged mean serial interval over time.
 Each line represents an independent stochastic realization.
@@
 When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms.
-\fref{obsrR} demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of $\mathcal R$.
-Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate the initial mean forward serial interval (\fref{obsrR}A) and therefore $\mathcal R_0$ (\fref{obsrR}) by a large amount because the observed serial-interval distribution does not account for changes in the forward serial-interval distribution.
-As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean of the initial forward serial-interval distribution, which provides the correct link between $r$ and $\mathcal R$.
+\fref{obsrR} demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of \RR.
+Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate the initial mean forward serial interval (\fref{obsrR}A) and therefore \Ro (\fref{obsrR}) by a large amount because the observed serial-interval distribution does not account for changes in the forward serial-interval distribution.
+As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean of the initial forward serial-interval distribution, which provides the correct link between $r$ and \RR.
 
-We provide a simple, heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore $\mathcal R$ retrospectively.
+We provide a simple, heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \RR retrospectively.
 Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can group observed serial intervals by their primary cohort times (i.e., symptom onset times of infectors).
-Then, we can compare how estimates of the mean serial interval as well as $\mathcal R$ change as we include more recent cohorts into the analysis (see `cohort-averaged' in \fref{obsrR}).
-During the exponential growth phase, the estimates of the mean serial interval and $\mathcal R$ are consistent with the target value;
+Then, we can compare how estimates of the mean serial interval as well as \RR change as we include more recent cohorts into the analysis (see `cohort-averaged' in \fref{obsrR}).
+During the exponential growth phase, the estimates of the mean serial interval and \RR are consistent with the target value;
 adding more data allows us to make more precise inference during this period.
 However, the cohort-averaged estimates decreases rapidly soon after the exponential growth period.
-This approach allows us to characterize potential biases in the estimates of $\mathcal R$ caused by changes in the forward serial-interval distributions.
+This approach allows us to characterize potential biases in the estimates of \RR caused by changes in the forward serial-interval distributions.
 
@@
 \caption{
-\textbf{Observed serial intervals of COVID-19 and cohort-averaged estimates of $\mathcal R$.}
+\textbf{Observed serial intervals of COVID-19 and cohort-averaged estimates of \RR.}
 (A--B) forward and backward serial intervals over time.
@@
 The dashed line represents the maximum observable delay for each primary cohort calculated from the most recent observed symptom onset date.
-(C) Cohort-averaged estimates of $\mathcal R$ assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
+(C) Cohort-averaged estimates of \RR assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
 Ribbons represent the associated 95\% bootstrap confidence intervals.
@@
 Finally, we reanalyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on transmission events reported between January 21--February 8, 2020;
-\cite{du2020serial} estimated the mean serial of 3.96 days (95\% CI 3.53–4.39 days) and $\mathcal R_0$ of 1.32 (95\% CI 1.16–1.48).
+\cite{du2020serial} estimated the mean serial of 3.96 days (95\% CI 3.53–4.39 days) and \Ro of 1.32 (95\% CI 1.16–1.48).
 \fref{du}A shows that the mean forward serial interval decreases over time.
@@
 
-\fref{du}C shows the cohort-averaged estimates of $\mathcal R_0$, which remain roughly constant until day 7 and suddenly decreases, as expected from our simulation study (\fref{obsrR}).
-The estimates of $\mathcal R_0$ based on the early forward serial intervals are also consistent with previous estimates of $\mathcal R_0$ of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}.
-We note that early cohort-averaged estimates of $\mathcal R_0$ are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
+\fref{du}C shows the cohort-averaged estimates of \Ro, which remain roughly constant until day 7 and suddenly decreases, as expected from our simulation study (\fref{obsrR}).
+The estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}.
+We note that early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
 This example clearly demonstrates the danger of simply averaging the observed serial intervals and calculating the reproduction number using them.
@@
 Using cohort-based approaches, we define forward and backward serial intervals.
-The forward serial-interval distribution describes the renewal process of the symptomatic individuals, and therefore, its initial distribution  provides the correct link between $r$ and $\mathcal R$.
-While our results support the use of serial interval distributions for calculating $\mathcal R$, 
+The forward serial-interval distribution describes the renewal process of the symptomatic individuals, and therefore, its initial distribution  provides the correct link between $r$ and \RR.
+While our results support the use of serial interval distributions for calculating \RR, 
 they also reveal gaps in current approaches to characterizing serial intervals.
 Previous studies have (i) recommended using up-to-date serial intervals \citep{thompson2019improved}, (ii) assumed that the serial interval distribution remains constant throughout an epidemic \citep{wallinga2004different, cori2013new}, and (iii) applied serial interval distributions estimated from one location to analyzing epidemics in other locations \citep{tempvar};
-however, all of these approaches implicitly ignore spatiotemporal variation in incidence, which affects the serial-interval distributions, and may therefore give systematically biased estimates of $\mathcal R$.
+however, all of these approaches implicitly ignore spatiotemporal variation in incidence, which affects the serial-interval distributions, and may therefore give systematically biased estimates of \RR.
 For example, given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic \citep{tempvar}, the initial forward serial interval distributions is likely to vary across different countries.
@@
 this probability increases as epidemic progresses because backward incubation period of an infector increases.
-Biases in the observed serial intervals will necessarily bias the estimates of $\mathcal R$. 
+Biases in the observed serial intervals will necessarily bias the estimates of \RR. 
 Furthermore, serial intervals do not take into account asymptomatic transmission; 
-not explicitly accounting for asymptomatic transmission may also bias the estimates of $\mathcal R$ \citep{park2020time}.
+not explicitly accounting for asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
 
-Despite these limitations, our analysis of serial intervals of COVID-19 provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of $\mathcal R$.
+Despite these limitations, our analysis of serial intervals of COVID-19 provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of \RR.
 To our knowledge, most, if not all, existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
@@
 \begin{aligned}
-i(t) &= \mathcal R_0 S(t-\Delta t) \sum_{m=1}^{\ell} i(t-\Delta t m) \hat{g}(\Delta t m) \\
+i(t) &= \Ro S(t-\Delta t) \sum_{m=1}^{\ell} i(t-m \Delta t) \hat{g}(m \Delta t) \\
 S(t) &= S(t-\Delta t) - i(t)
@@
 \begin{equation}
-\hat{g}(\Delta t m) = \frac{g(\Delta t m)}{\sum_{i=1}^\ell g(\Delta t m)}, \quad m=1, \dots, \ell
+\hat{g}(m \Delta t) = \frac{g(m \Delta t)}{\sum_{i=1}^\ell g(m \Delta t)}, \quad m=1, \dots, \ell
 \end{equation}
@@
 \begin{equation}
-\hat{k}(\Delta t m) = \frac{k(\Delta t m)}{\sum_{i=1}^\ell k(\Delta t m)}, \quad m=1, \dots, \ell,
+\hat{k}(m \Delta t) = \frac{k(m \Delta t)}{\sum_{i=1}^\ell k(m \Delta t)}, \quad m=1, \dots, \ell,
 \end{equation}
@@
 \begin{equation}
-\hat{h}(\Delta t m, \Delta t n) = \hat{k}(\Delta t m)\hat{g}(\Delta t n), \quad m,n=1, \dots, \ell.
+\hat{h}(m \Delta t, \Delta t n) = \hat{k}(m \Delta t)\hat{g}(\Delta t n), \quad m,n=1, \dots, \ell.
 \end{equation}
@@
 \begin{aligned}
-i(\Delta t m) &= C \exp(r \Delta t m), \quad m=1, \dots, \ell\\
-S(\Delta t m) &= N - \sum_{n=1}^m i(\Delta t m), \quad m=1, \dots, \ell\\
+i(m \Delta t) &= C \exp(r m \Delta t), \quad m=1, \dots, \ell\\
+S(m \Delta t) &= N - \sum_{n=1}^m i(m \Delta t), \quad m=1, \dots, \ell\\
 \end{aligned}
 \end{equation}
-where $C$ is chosen such that $\sum_{n=1}^\ell i(\Delta t m)=10$.
+where $C$ is chosen such that $\sum_{n=1}^\ell i(m \Delta t)=10$.
 These initial conditions allow the model to follow exponentially growth from time $\Delta t (\ell + 1)$ without any transient behaviors.
@@
 First, we initialize an epidemic with $I(0)$ infected individuals (nodes) in a fully connected network of size $N$. 
-For each initially infected individual, we draw number of infectious contacts from a Poisson distribution with the mean of $\mathcal R_0$ and the corresponding generation intervals for each contact from a log-normal distribution (Table 1).
+For each initially infected individual, we draw number of infectious contacts from a Poisson distribution with the mean of \Ro and the corresponding generation intervals for each contact from a log-normal distribution (Table 1).
 Contactees are uniformly sampled from the total population.
@@
 
-\subsection{Linking $r$ and $\mathcal R$ using serial-interval distributions}
+\subsection{Linking $r$ and \RR using serial-interval distributions}
 
-The intrinsic generation-interval distribution $g(\tau)$ provides a link between $r$ and $\mathcal R$ via the Euler-Lotka equation:
+The intrinsic generation-interval distribution $g(\tau)$ provides a link between $r$ and \RR via the Euler-Lotka equation:
 \begin{equation}
-\frac{1}{\mathcal R} = \int_0^\infty \exp(-r\tau) g(\tau) \mathrm{d} \tau.
+\frac{1}{\RR} = \int_0^\infty \exp(-r\tau) g(\tau) \mathrm{d} \tau.
 \end{equation}
@@
 \begin{equation}
-\frac{1}{\mathcal R} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
+\frac{1}{\RR} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
 \end{equation}
@@
 \end{equation}
-Therefore, the initial forward serial--interval distribution and the intrinsic generation-interval distribution give the same link between $r$ and $\mathcal R$.
+Therefore, the initial forward serial--interval distribution and the intrinsic generation-interval distribution give the same link between $r$ and \RR.
 

### 2020-04-28 serial.tex
undefined macro

@@
 \end{equation}
-where $\Rc(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}) \bmb{is \Rc the same as ``forward \R measured at a particular time''?}, $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee).
+where $\Rc(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}) \bmb{is \Rc the same as ``forward \Rx measured at a particular time''?}, $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee).
 Then, the forward serial-interval distribution is proportional to $T(\pi, \pi+\tau)$. Substituting $x=\pi-\alpha_1$ and $\sigma=\alpha_2-\alpha_1$, we have:

### 2020-04-28 serial.tex
macros

--- 2020-04-27 serial.tex
@@
 \newcommand{\dsigma}{\dd{\sigma}}
+
+\newcommand{\pt}{p} %% primary time
+\newcommand{\st}{s} %% secondary time
+
+\newcommand{\psize}{{\mathcal P}} %% primary cohort size
+\newcommand{\ssize}{{\mathcal S}} %% secondary cohort size
+
 \begin{document}
@@
 	\textbf\newline{
-		Unraveling the paradox between generation and serial intervals: applications to the COVID-19 pandemic
+		Unraveling the paradox between generation and serial intervals
 	}
@@
 We argue that a part of the confusion can be attributed to an apparent paradox.
-\bmb{need to define the paradox here, e.g.: ``although they cannot be used interchangeably in analyzing the behaviour of an epidemic, they give rise to nearly identical relationships between the epidemic growth rate $r$ and \RR''}
-As the generation-interval distribution describes the renewal process of infection, it provides a link between the epidemic growth rate $r$ and the reproduction number \RR;
-likewise, the serial-interval distribution should describe the renewal process of symptomatic infection and therefore, should provide the same link between the epidemic growth rate $r$ and the reproduction number \RR.
-%However, the current theory does not explain how two different distributions can give the same link between $r$ and $\mathcal R$ link.
+By definition, generation and serial intervals describe the renewal process between infection and symptom onset, respectively, and therefore, one might expect them to potentially provide the same link between the epidemic growth rate $r$ and the reproduction number \RR.
+However, current theory does not explain how two different distributions can give the same link between $r$ and $\mathcal R$ --- some studies have demonstrated that generation and serial intervals give different $r$--\RR link, contradicting our biological intuition.
 We provide an answer to the paradox by showing that if serial intervals are defined as \emph{forward-looking} intervals during the exponential phase, then the correct link between $r$ and \RR emerges.
@@
 
-The reproduction number \RR is one of the most important characteristics of an emerging epidemic such as novel coronavirus disease (COVID-19) \citep{majumder2020early} \bmb{avoid starting a paper by saying ``X has been studied a lot''; instead, say it's important or interesting}
+The reproduction number \RR is one of the most important characteristics of an emerging epidemic such as novel coronavirus disease (COVID-19) \citep{majumder2020early}.
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
@@
 some studies further suggested that using serial intervals can give different estimates of \RR \citep{britton2019estimation}.
-Even these distributions were clearly distinguished over a decade ago \citep{svensson2007note}, 
-the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds:
-Researchers continue to rely on both generation and serial intervals to estimate \RR for COVID-19 without making a clear distinction.
+
+Although these distributions were clearly distinguished over a decade ago \citep{svensson2007note}, 
+the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds.
+Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19, particularly for estimating its \RR, without making a clear distinction \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}.
+Some studies still refer to time between infection (i.e., generation intervals) as serial intervals \citep{anderson2020will,hellewell2020feasibility}.
 
@@
 When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
-This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR \citep{wallinga2007generation}.
-Likewise, we should be able to describe the renewal process of symptomatic cases using the serial-interval distribution.
-Therefore, both generation- and serial-interval distributions should give us identical estimates of  \RR based the observed epidemic growth rate $r$.
-In contexts where the distributions are expected to be different, current theory has no explanation for how they might link $r$ to \Rx\ in the same way.
+This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
+By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates;
+therefore, both generation- and serial-interval distributions should potentially give us identical estimates of  \RR based the observed epidemic growth rate $r$.
+In contexts where the distributions are expected to be different, current theory has no explanation for how they might provide identical estimates of \RR from $r$ (cf. \cite{britton2019estimation}).
 
 Here, we provide an answer to this paradox, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
-We develop a new framework for understanding serial intervals and show that the initial forward serial-interval distribution gives the correct value of \RR.
+We develop a new framework for understanding serial intervals and show that the initial forward serial-interval distribution correctly links $r$ and \RR.
 %\jd{Come back to this. Not just over time, right?} \swp{What do you mean? Everything is about time here... you haven't read the results section so maybe that's why?}
-However, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can bias the estimate of \RR.
+However, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can bias the estimate of \RR, as inferred from the observed growth rate $r$.
 We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of the ongoing pandemic.
@@
 a secondary cohort is defined similarly based on the secondary events.
-For example, when we are measuring serial intervals, a primary cohort $\pi$ consists of all infectors who became symptomatic at time $\pi$.
-Then, for each primary cohort $\pi$, we can define the expected time distribution between primary and secondary events.
-We refer to this distribution as the forward delay distribution and denote it as $f_\pi(\tau)$.
+For example, when we are measuring incubation periods, a \textbf{p}rimary cohort at time $\pt$ consists of all infected individuals who became infected at time $\pt$. 
+Similarly, when we are measuring serial intervals, a primary cohort at time $\pt$ consists of all infectors who became symptomatic at time $\pt$.
+Then, for each primary cohort $\pt$, we can define the expected time distribution between primary and secondary events.
+We refer to this distribution as the forward delay distribution and denote it as $f_\pt(\tau)$.
 
-Likewise, we define the backward delay distribution $b_\delta(\tau)$ for a secondary cohort $\delta$:
-The backward delay distribution describes the time delays between a primary and secondary host given that the secondary event occurred at time $\delta$.
-Since both forward and backward perspectives provide valid ways of measuring time delays, we can express the total density of primary and secondary events occurring at time $\pi$ and $\delta$, respectively, using both forward and backward delay distributions:
+Likewise, we define the backward delay distribution $b_\st(\tau)$ for a \textbf{s}econdary cohort at time $\st$:
+The backward delay distribution describes the time delays between a primary and secondary host given that the secondary event occurred at time $\st$.
+For example, the backward incubation period distribution at time $\st$ describes incubation periods for a \emph{cohort} of individuals who became symptomatic at time $\st$.
+Likewise, the backward serial-interval distribution at time $\st$ describes serial intervals for a \emph{cohort} of infectees who became symptomatic at time $\st$.
+
+At the individual-level, both forward and backward \emph{measurements} provide identical measures;
+in other words, we can express the total density of primary and secondary events occurring at time $\pt$ and $\st$, respectively, using both forward and backward delay \emph{distributions}:
 \begin{equation}
-P(\pi) f_\pi(\delta-\pi) = D(\delta) b_\delta(\delta-\pi),
+\psize(\pt) f_\pt(\st-\pt) = \ssize(\st) b_\st(\st-\pt),
 \end{equation}
-where $P$ and $D$ represent the sizes of primary and secondary cohorts, respectively.
-Substituting $\tau = \delta - \pi$, it follows that:
+where $\mathcal P$ and $\mathcal S$ represent the sizes of primary and secondary cohorts, respectively.
+Substituting $\tau = \st - \pt$, it follows that:
 \begin{equation}
-b_\delta(\tau) = \frac{P(\delta-\tau) f_{\delta-\tau}(\tau)}{D(\delta)}
+b_\st(\tau) = \frac{\psize(\st-\tau) f_{\st-\tau}(\tau)}{\ssize(\st)}
 \end{equation}
-Therefore, the backward delay distribution depends on the changes in primary cohort size $P$ (therefore incidence of infection) as well as changes in the forward delay distribution.
+Therefore, the backward delay distribution depends on the changes in primary cohort size $\tau$ time units ago from the reference time $\st$, $\psize(\st-\tau)$, as well as changes in the forward delay distribution, $f_{\st-\tau}(\tau)$.
 These ideas apply to all epidemiological delay distributions and generalize the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
-\bmb{need to work \textbf{really hard} to clarify the mechanisms driving various differences [backward vs forward, dependence on current $S$/epidemic phase, etc.]; which are caused by changes in cohort size over time (Euler-Lotka-type effects), which are caused by censoring/conditionality of observations, etc.
-?}
+
+There are multiple mechanisms that drive the changes in forward and backward delay distributions over time ---
+we being by describing factors that affect the forward delay distributions.
+Typically, within-individual delay distributions that reflect life-history of a disease is expected to remain constant over the course of an epidemic.
+
+\bmb{need to work \textbf{really hard} to clarify the mechanisms driving various differences [backward vs forward, dependence on current $S$/epidemic phase, etc.]; which are caused by changes in cohort size over time (Euler-Lotka-type effects), which are caused by censoring/conditionality of observations, etc.?}
 
@@
 \end{equation}
-where $\Rc(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}) \bmb{is \Rc the same as ``forward \R measured at a particular time''?}, $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee).
+where $\Rc(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}) \bmb{is \Rc the same as ``forward \RR measured at a particular time''?}, $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee).
 Then, the forward serial-interval distribution is proportional to $T(\pi, \pi+\tau)$. Substituting $x=\pi-\alpha_1$ and $\sigma=\alpha_2-\alpha_1$, we have:

### 2020-04-29 serial.tex
pushing

@@
 \newcommand{\ssize}{{\mathcal S}} %% secondary cohort size
+
+\newcommand{\gtime}{\sigma} %% generation interval
+\newcommand{\gdist}{g} %% generation-interval distribution
 
@@
 b_\st(\tau) = \frac{\psize(\st-\tau) f_{\st-\tau}(\tau)}{\ssize(\st)}
+\label{eq:backward}
 \end{equation}
 Therefore, the backward delay distribution depends on the changes in primary cohort size $\tau$ time units ago from the reference time $\st$, $\psize(\st-\tau)$, as well as changes in the forward delay distribution, $f_{\st-\tau}(\tau)$.
-These ideas apply to all epidemiological delay distributions and generalize the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
 
 There are multiple mechanisms that drive the changes in forward and backward delay distributions over time ---
-we being by describing factors that affect the forward delay distributions.
-Typically, within-individual delay distributions that reflect life-history of a disease is expected to remain constant over the course of an epidemic.
+we begin by describing factors that affect the forward delay distributions.
+Typically, within-individual forward delay distributions that reflect life-history of a disease is expected to remain invariant over the course of an epidemic; 
+these distributions include incubation period distribution.
+Within-individual forward delay distributions that depend on external interventions, such as time distribution of symptom onset to hospitalization, can change over the course of an epidemic.
+Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics;
+for example, the forward generation intervals to contract during the outbreak because infected individuals are less likely to infect others later due to susceptible depletion \citep{champredon2015intrinsic}.
 
-\bmb{need to work \textbf{really hard} to clarify the mechanisms driving various differences [backward vs forward, dependence on current $S$/epidemic phase, etc.]; which are caused by changes in cohort size over time (Euler-Lotka-type effects), which are caused by censoring/conditionality of observations, etc.?}
+Changes in the backward delay distributions are affected by the changes in the forward delay distributions as it is evident from \eref{backward}.
+Backward delay distributions also depend on changes in the primary cohort size over time due to conditionality of observations: 
+The backward delay distribution is measured for a cohort of individuals whose secondary events occurred at the same time.
+When the cohort size is increasing (or decreasing) over time, we are biased to observe shorter (or longer) delays if we look backward.
+Therefore, the backward delay distributions will be generally different from the forward delay distributions even if we are measuring time delays that are intrinsic to life-history of a disease (e.g., incubation period).
+These ideas apply to all epidemiological delay distributions and generalize the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
 
@@
 
-The serial interval is defined as the time between when an infector becomes symptomatic and when and infectee becomes symptomatic.
-Serial intervals $\tau$ have been typically written in the form:
+The serial interval is defined as the time between when an infector becomes symptomatic and when and infectee becomes symptomatic \citep{svensson2007note}.
+Previous studies have often expressed serial intervals $\tau$ in the form (\fref{diagram}A):
 \begin{equation}
-\tau = - x_0 + \sigma + x_1
+\tau = (\gtime + x_1) - x_0
 \end{equation}
-where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\sigma$ represents the realized generation interval.
-Previous studies have often assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
-% \jd{I would drop the last clause. I still argue that this is true for intrinsic SIs, and we don't want to get into that here. You can just keep rolling forward at this point.}
+where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\gtime$ represents the realized generation interval.
+These studies assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
+this conclusion is based on the implicit assumption that serial intervals are measured from the perspective of a cohort of infectors that share the same infection time.
+We refer to this definition of serial intervals as the intrinsic serial interval.
 
@@
 \caption{
-\textbf{Illustration of forward and backward serial intervals.}
-(A) The forward serial interval for a primary cohort $\pi$ (i.e., an infector who became symptomatic at time $\pi$).
-In this case, $x_0$ represents the backward incubation period of the infector;
+\textbf{Illustration of intrinsic, forward and backward serial intervals.}
+(A) The intrinsic serial interval for a cohort of individuals infected at time $\pt$.
+In this case, $x_0$ follows the forward incubation period distribution of the cohort of infectors who became infected at time $\pt$;
+$\gtime$ follows the forward generation interval of the cohort of infectors who became infected at time $\pt$;
+and $x_1$ follows the forward incubation period of the cohort of infectees who became infected at time $\pt+\gtime$.
+(B) The forward serial interval for a primary cohort $\pt$ (i.e., the cohort of infectors who became symptomatic at time $\pt$).
+In this case, $x_0$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\pt$;
 $\sigma$ represents the forward generation interval;
 and $x_1$ represents the forward incubation period of the infectee.
-(B) The backward serial interval for a secondary cohort $\delta$ (i.e., an infectee who became symptomatic at time $\delta$).
+(C) The backward serial interval for a secondary cohort $\delta$ (i.e., the cohort of infectees who became symptomatic at time $\delta$).
 In this case, $x_0$ represents the forward incubation period of the infector;
@@
 
+Since serial intervals describe the renewal process between symptomatic cases based on their symptom onset dates, we have to define serial intervals from the perspective of a cohort (of either infectors or infectees) that share the same symptom onset time.
 The cohort-based framework allows us to understand the distribution of serial intervals we expect to observe when incidence is changing.
-Given that an infector became symptomatic at time $\pi$, we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when the infectee became symptomatic;
+Given that an infector became symptomatic at time $\pt$, we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when the infectee became symptomatic;
 this defines the forward serial interval.
-In \fref{diagram}A, we see that $x_0$ represents the backward incubation period of the infector who became symptomatic at time $\pi$;
-$\sigma$ represents the forward generation interval of the infector who came infected at time $\pi - x_0$;
-and $x_1$ represents the forward incubation period for the infectees who became infected at time $\pi - x_0 + \sigma$.
+In \fref{diagram}B, we see that $x_0$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\pt$;
+$\gtime$ follows the forward generation-interval distribution of the cohort of infector who came infected at time $\pt - x_0$;
+and $x_1$ follows the forward incubation period distribution of the cohort of infectees who became infected at time $\pt - x_0 + \gtime$.
 
-Likewise, we can define the backward serial interval distribution for a secondary cohort $\delta$ (\fref{diagram}B).
-Given that an infectee became symptomatic at time $\delta$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
+Likewise, we can define the backward serial interval distribution for a secondary cohort $\st$ (\fref{diagram}C).
+Given that an infectee became symptomatic at time $\st$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
 then, we have to go forward in time by asking when the infector became symptomatic.
-In this case, $x_1$ represents the backward incubation period of the infectee who became symptomatic at time $\delta$;
-$\sigma$ represents the backward generation interval of the infectee who became infected at time $\delta-x_1$;
-and $x_0$ represents the forward incubation period of the infector who became infected at time $\delta-x_1-\sigma$.
-This conceptual framework clearly demonstrates that the distributions of $x_0$, $\delta$, and $x_1$ (and therefore the distributions of serial intervals) depend on the perspective \bmb{better/more consistent word than ``perspective''?} as well as time and cannot be treated statically.
-\bmb{please explain/clarify why the backward incubation period is not the same is as the forward}
+In this case, $x_1$ follows the backward incubation period distribution of the cohort of infectees who became symptomatic at time $\st$;
+$\gtime$ follows the backward generation-interval distribution of the cohort of infectees who became infected at time $\st-x_1$;
+and $x_0$ follows the forward incubation period distribution of the cohort of infectors who became infected at time $\st-x_1-\gtime$.
+This conceptual framework clearly demonstrates that the distributions of $x_0$, $\st$, and $x_1$ (and therefore the distributions of serial intervals) depend on the reference cohort and the corresponding cohort time.
 

### 2020-04-29 serial_guide.tex
pushing

--- 2020-04-14 serial_guide.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-04-14 02:04:29
+% Created by tikzDevice version 0.12.3 on 2020-04-28 19:38:14
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (722.70,433.62);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (722.70,578.16);
 \begin{scope}
-\path[clip] (  0.00,216.81) rectangle (722.70,433.62);
+\path[clip] (  0.00,385.44) rectangle (722.70,578.16);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,216.81) rectangle (722.70,433.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,385.44) rectangle (722.70,578.16);
 \end{scope}
 \begin{scope}
-\path[clip] (  8.25,225.06) rectangle (717.20,410.96);
+\path[clip] (  8.25,393.69) rectangle (717.20,555.50);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (  8.25,225.06) rectangle (717.20,410.96);
+\path[fill=fillColor] (  8.25,393.69) rectangle (717.20,555.50);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,275.76) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,437.82) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16,275.76) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16,437.82) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,275.76) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,437.82) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41,275.76) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41,437.82) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,332.09) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,486.85) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16,388.43) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16,535.89) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,360.26) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,511.37) circle (  3.57);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,257.88) {$\ell$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,462.34) circle (  3.57);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,257.88) {$\ell-x_0$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,421.76) {$p+x_0$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,243.79) {Infector};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,421.76) {$p$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,243.79) {Primary cohort};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,409.50) {Infector};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,243.79) {Infectee};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,409.50) {Infectee};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,257.88) {$\ell-x_0+\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,421.76) {$p+\sigma$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,257.88) {$\ell-x_0+\sigma+x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,421.76) {$p+\sigma+x_1$};
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 40.48,275.76) -- (684.98,275.76);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 40.48,437.82) -- (684.98,437.82);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (672.46,268.53) --
-	(684.98,275.76) --
-	(672.46,282.99);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (672.46,430.59) --
+	(684.98,437.82) --
+	(672.46,445.05);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (121.04,275.76) -- (121.04,332.09);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (121.04,437.82) -- (121.04,486.85);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.16,275.76) -- (282.16,388.43);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.16,437.82) -- (282.16,535.89);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (443.29,275.76) -- (443.29,360.26);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (443.29,437.82) -- (443.29,511.37);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (604.41,275.76) -- (604.41,388.43);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (604.41,437.82) -- (604.41,535.89);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,303.93) -- (121.04,303.93);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (121.04,462.34) -- (282.16,462.34);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (127.30,307.54) --
-	(121.04,303.93) --
-	(127.30,300.31);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (275.90,458.72) --
+	(282.16,462.34) --
+	(275.90,465.95);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (121.04,332.09) -- (443.29,332.09);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (121.04,486.85) -- (443.29,486.85);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (437.03,328.48) --
-	(443.29,332.09) --
-	(437.03,335.71);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (437.03,483.24) --
+	(443.29,486.85) --
+	(437.03,490.47);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (443.29,360.26) -- (604.41,360.26);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (443.29,511.37) -- (604.41,511.37);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,356.65) --
-	(604.41,360.26) --
-	(598.15,363.88);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,507.76) --
+	(604.41,511.37) --
+	(598.15,514.99);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,388.43) -- (604.41,388.43);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,535.89) -- (604.41,535.89);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,384.82) --
-	(604.41,388.43) --
-	(598.15,392.04);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,532.28) --
+	(604.41,535.89) --
+	(598.15,539.50);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,398.71) {Forward serial interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,544.35) {Intrinsic serial interval};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,314.21) {Backward incubation period};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,470.79) {Forward incubation period};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,342.38) {Forward generation interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,495.31) {Forward generation interval};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,370.54) {Forward incubation period};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,519.83) {Forward incubation period};
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16,275.76) circle (  5.71);
+\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16,437.82) circle (  5.71);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41,275.76) circle (  5.71);
+\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41,437.82) circle (  5.71);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,433.62);
+\path[clip] (  0.00,  0.00) rectangle (722.70,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  8.25,419.03) {A};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  8.25,563.57) {A. Intrinsic serial interval};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,216.81);
+\path[clip] (  0.00,192.72) rectangle (722.70,385.44);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,216.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,192.72) rectangle (722.70,385.44);
 \end{scope}
 \begin{scope}
-\path[clip] (  8.25,  8.25) rectangle (717.20,194.15);
+\path[clip] (  8.25,200.97) rectangle (717.20,362.78);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (  8.25,  8.25) rectangle (717.20,194.15);
+\path[fill=fillColor] (  8.25,200.97) rectangle (717.20,362.78);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04, 58.95) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,245.10) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16, 58.95) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16,245.10) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29, 58.95) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,245.10) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41, 58.95) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41,245.10) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,143.45) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,294.13) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41,171.62) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16,343.17) circle (  3.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,115.28) circle (  3.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,318.65) circle (  3.57);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 41.07) {$\ell$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16,269.62) circle (  3.57);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 41.07) {$\ell-x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,229.04) {$p$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 41.07) {$\ell-x_1-\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,229.04) {$p-x_0$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 41.07) {$\ell-x_1-\sigma+x_0$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,216.78) {Infector};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 26.98) {Infector};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,216.78) {Primary cohort};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 26.98) {Infectee};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,216.78) {Infectee};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 26.98) {Secondary cohort};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,229.04) {$p-x_0+\sigma$};
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 40.48, 58.95) -- (684.98, 58.95);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,229.04) {$p-x_0+\sigma+x_1$};
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (672.46, 51.72) --
-	(684.98, 58.95) --
-	(672.46, 66.18);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 40.48,245.10) -- (684.98,245.10);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (121.04, 58.95) -- (121.04,143.45);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (672.46,237.87) --
+	(684.98,245.10) --
+	(672.46,252.33);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.16, 58.95) -- (282.16,171.62);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (121.04,245.10) -- (121.04,294.13);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (443.29, 58.95) -- (443.29,115.28);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.16,245.10) -- (282.16,343.17);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (604.41, 58.95) -- (604.41,171.62);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (443.29,245.10) -- (443.29,318.65);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (604.41, 87.12) -- (443.29, 87.12);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (604.41,245.10) -- (604.41,343.17);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (449.55, 90.73) --
-	(443.29, 87.12) --
-	(449.55, 83.50);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,269.62) -- (121.04,269.62);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (443.29,115.28) -- (121.04,115.28);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (127.30,273.23) --
+	(121.04,269.62) --
+	(127.30,266.00);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (127.30,118.90) --
-	(121.04,115.28) --
-	(127.30,111.67);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (121.04,294.13) -- (443.29,294.13);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (121.04,143.45) -- (282.16,143.45);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (437.03,290.52) --
+	(443.29,294.13) --
+	(437.03,297.75);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (275.90,139.84) --
-	(282.16,143.45) --
-	(275.90,147.07);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (443.29,318.65) -- (604.41,318.65);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (604.41,171.62) -- (282.16,171.62);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,315.04) --
+	(604.41,318.65) --
+	(598.15,322.27);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (288.42,175.23) --
-	(282.16,171.62) --
-	(288.42,168.01);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,343.17) -- (604.41,343.17);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,181.90) {Backward serial interval};
+\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,339.56) --
+	(604.41,343.17) --
+	(598.15,346.78);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85, 97.40) {Backward incubation period};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,351.63) {Forward serial interval};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (362.72,125.57) {Backward generation interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,278.07) {Backward incubation period};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,153.73) {Forward incubation period};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,302.59) {Forward generation interval};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,327.11) {Forward incubation period};
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41, 58.95) circle (  5.71);
+\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16,245.10) circle (  5.71);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16, 58.95) circle (  5.71);
+\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41,245.10) circle (  5.71);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,433.62);
+\path[clip] (  0.00,  0.00) rectangle (722.70,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  8.25,202.22) {B};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  8.25,370.85) {B. Forward serial interval};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,192.72);
+\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,192.72);
+\end{scope}
+\begin{scope}
+\path[clip] (  8.25,  8.25) rectangle (717.20,170.06);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (  8.25,  8.25) rectangle (717.20,170.06);
+\definecolor{drawColor}{RGB}{0,0,0}
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04, 52.38) circle (  3.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.16, 52.38) circle (  3.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29, 52.38) circle (  3.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41, 52.38) circle (  3.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41, 76.90) circle (  3.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.04,125.93) circle (  3.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.41,150.45) circle (  3.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (443.29,101.41) circle (  3.57);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 36.32) {$s$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 36.32) {$s-x_1$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 36.32) {$s-x_1-\sigma$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 36.32) {$s-x_1-\sigma+x_0$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 24.06) {Infector};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 24.06) {Infectee};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 24.06) {Secondary cohort};
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 40.48, 52.38) -- (684.98, 52.38);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (672.46, 45.15) --
+	(684.98, 52.38) --
+	(672.46, 59.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (121.04, 52.38) -- (121.04,125.93);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.16, 52.38) -- (282.16,150.45);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (443.29, 52.38) -- (443.29,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (604.41, 52.38) -- (604.41,150.45);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (604.41, 76.90) -- (443.29, 76.90);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (449.55, 80.51) --
+	(443.29, 76.90) --
+	(449.55, 73.28);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (443.29,101.41) -- (121.04,101.41);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (127.30,105.03) --
+	(121.04,101.41) --
+	(127.30, 97.80);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (121.04,125.93) -- (282.16,125.93);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (275.90,122.32) --
+	(282.16,125.93) --
+	(275.90,129.55);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (604.41,150.45) -- (282.16,150.45);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (288.42,154.06) --
+	(282.16,150.45) --
+	(288.42,146.84);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,158.91) {Backward serial interval};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85, 85.35) {Backward incubation period};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (362.72,109.87) {Backward generation interval};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,134.39) {Forward incubation period};
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41, 52.38) circle (  5.71);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16, 52.38) circle (  5.71);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,578.16);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  8.25,178.13) {C. Backward serial interval};
 \end{scope}

### 2020-04-29 serial_guide.R

@@ -17,13 +17,54 @@ g1 <- ggplot(arrow) +
   geom_point(aes(0.5, 0.2), size=3) +
   geom_point(aes(1.5, 0.4), size=3) +
   geom_point(aes(2.5, 0.3), size=3) +
-  annotate("text", x=1.5, y=-0.05, label="$\\pi$") +
-  annotate("text", x=0.5, y=-0.05, label="$\\pi-x_0$") +
+  geom_point(aes(0.5, 0.1), size=3) +
+  annotate("text", x=1.5, y=-0.05, label="$p+x_0$") +
+  annotate("text", x=0.5, y=-0.05, label="$p$") +
+  annotate("text", x=0.5, y=-0.1, label="Infector") +
+  annotate("text", x=2.5, y=-0.1, label="Infectee") +
+  annotate("text", x=2.5, y=-0.05, label="$p+\\sigma$") +
+  annotate("text", x=3.5, y=-0.05, label="$p+\\sigma+x_1$") +
+  geom_segment(aes(x, y, xend=x1, yend=y1), arrow = arrow(length = unit(0.2, "inches")), lwd=1) +
+  geom_segment(aes(0.5, 0, xend=0.5, yend=0.2), lty=2) +
+  geom_segment(aes(1.5, 0, xend=1.5, yend=0.4), lty=2) +
+  geom_segment(aes(2.5, 0, xend=2.5, yend=0.3), lty=2) +
+  geom_segment(aes(3.5, 0, xend=3.5, yend=0.4), lty=2) +
+  geom_segment(aes(0.5, 0.1, xend=1.5, yend=0.1), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
+  geom_segment(aes(0.5, 0.2, xend=2.5, yend=0.2), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
+  geom_segment(aes(2.5, 0.3, xend=3.5, yend=0.3), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
+  geom_segment(aes(1.5, 0.4, xend=3.5, yend=0.4), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
+  annotate("text", x=2.5, y=0.45, label="Intrinsic serial interval") +
+  annotate("text", x=1, y=0.15, label="Forward incubation period") +
+  annotate("text", x=1, y=0.25, label="Forward generation interval") +
[…]

### 2020-04-29 serial_guide.tex
something broken???

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-28 19:38:14
+% Created by tikzDevice version 0.12.3 on 2020-04-28 20:48:42
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,409.50) {Infector};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,409.50) {Infector (reference cohort)};
 
@@
 
-\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16,437.82) circle (  5.71);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41,437.82) circle (  5.71);
+\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (121.04,437.82) circle (  5.71);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,216.78) {Primary cohort};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,216.78) {Reference cohort};
 
@@
 \path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16,245.10) circle (  5.71);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41,245.10) circle (  5.71);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 24.06) {Secondary cohort};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 24.06) {Reference cohort};
 
@@
 \path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (604.41, 52.38) circle (  5.71);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round,fill=fillColor] (282.16, 52.38) circle (  5.71);
 \end{scope}

### 2020-04-29 serial_guide.R

@@ -20,7 +20,7 @@ g1 <- ggplot(arrow) +
   geom_point(aes(0.5, 0.1), size=3) +
   annotate("text", x=1.5, y=-0.05, label="$p+x_0$") +
   annotate("text", x=0.5, y=-0.05, label="$p$") +
-  annotate("text", x=0.5, y=-0.1, label="Infector") +
+  annotate("text", x=0.5, y=-0.1, label="Infector (reference cohort)") +
   annotate("text", x=2.5, y=-0.1, label="Infectee") +
   annotate("text", x=2.5, y=-0.05, label="$p+\\sigma$") +
   annotate("text", x=3.5, y=-0.05, label="$p+\\sigma+x_1$") +
@@ -37,8 +37,7 @@ g1 <- ggplot(arrow) +
   annotate("text", x=1, y=0.15, label="Forward incubation period") +
   annotate("text", x=1, y=0.25, label="Forward generation interval") +
   annotate("text", x=3, y=0.35, label="Forward incubation period") +
-  geom_point(aes(1.5, 0), size=4, shape=21, fill="white", stroke=2) +
-  geom_point(aes(3.5, 0), size=4, shape=21, fill="black", stroke=2) +
+  geom_point(aes(0.5, 0), size=4, shape=21, fill="white", stroke=2) +
   scale_y_continuous(limits=c(-0.15, 0.45)) +
   ggtitle("A. Intrinsic serial interval") +
   theme(
@@ -61,7 +60,7 @@ g2 <- ggplot(arrow) +
   annotate("text", x=1.5, y=-0.05, label="$p$") +
   annotate("text", x=0.5, y=-0.05, label="$p-x_0$") +
   annotate("text", x=0.5, y=-0.1, label="Infector") +
-  annotate("text", x=1.5, y=-0.1, label="Primary cohort") +
+  annotate("text", x=1.5, y=-0.1, label="Reference cohort") +
   annotate("text", x=2.5, y=-0.1, label="Infectee") +
   annotate("text", x=2.5, y=-0.05, label="$p-x_0+\\sigma$") +
   annotate("text", x=3.5, y=-0.05, label="$p-x_0+\\sigma+x_1$") +
@@ -79,7 +78,6 @@ g2 <- ggplot(arrow) +
   annotate("text", x=1, y=0.25, label="Forward generation interval") +
   annotate("text", x=3, y=0.35, label="Forward incubation period") +
[…]

### 2020-04-29 serial.tex
i almost screwed up...

@@
 \newcommand{\gdist}{g} %% generation-interval distribution
+
+\newcommand{\total}{{\mathcal T}} %% total number of serial intervals
 
@@
 (A) The intrinsic serial interval for a cohort of individuals infected at time $\pt$.
-In this case, $x_0$ follows the forward incubation period distribution of the cohort of infectors who became infected at time $\pt$;
-$\gtime$ follows the forward generation interval of the cohort of infectors who became infected at time $\pt$;
-and $x_1$ follows the forward incubation period of the cohort of infectees who became infected at time $\pt+\gtime$.
+In this case, $x_0$ follows the forward incubation period distribution;
+$\gtime$ follows the forward generation-interval distribution;
+and $x_1$ follows the forward incubation period distribution.
 (B) The forward serial interval for a primary cohort $\pt$ (i.e., the cohort of infectors who became symptomatic at time $\pt$).
-In this case, $x_0$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\pt$;
-$\sigma$ represents the forward generation interval;
-and $x_1$ represents the forward incubation period of the infectee.
-(C) The backward serial interval for a secondary cohort $\delta$ (i.e., the cohort of infectees who became symptomatic at time $\delta$).
-In this case, $x_0$ represents the forward incubation period of the infector;
-$\sigma$ represents the backward generation interval;
-and $x_1$ represents the backward incubation period of the infectee.
+In this case, $x_0$ follows the backward incubation period distribution;
+$\gtime$ follows the forward generation-interval distribution;
+and $x_1$ follows the forward incubation period distribution.
+(C) The backward serial interval for a secondary cohort $\st$ (i.e., the cohort of infectees who became symptomatic at time $\st$).
+In this case, $x_0$ follows the forward incubation period distribution;
+$\gtime$ follows the backward generation-interval distribution;
+and $x_1$ follows the backward incubation period distribution.
 }
@@
 
-In order to define forward and backward serial interval distributions, we begin by writing the total number of serial intervals \bmb{explain more please \ldots} between time $\pi$ (when the infector developed symptoms) and $\delta$ (when the infectee developed symptoms), which can be expressed as an integral over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
+In order to define forward and backward serial interval distributions, we begin by modeling the total number of serial intervals $\total(\pt,\st)$ between time $\pt$ and $\st$ (i.e., total number of infection in which infectors develop symptom at time $\pt$ and infectees develop symptom at time $\st$).
+The number of serial intervals between time $\pt$ and $\st$ given that the infectors became infected at time $\alpha_1$ and the infectees became infected at time $\alpha_2$ is can be then expressed as a product of (i) incidence $i$ at time $\alpha_1$, (ii) their case reproduction number $\Rc(\alpha_1)$ (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}), (iii) the density of forward generation interval between $\alpha_1$ and $\alpha_2$, and (iv) the densities of forward incubation periods between $\alpha_1$ and $\pt$ (incubation periods of infectors) as well as $\alpha_2$ and $\st$ (incubation periods of infectees):
 \begin{equation}
-T(\pi,\delta) = \int_{-\infty}^{\pi} \int_{\alpha_1}^{\delta} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\delta - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1,
+\Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\st - \alpha_2),
 \end{equation}
-where $\Rc(\alpha_1)$ is the case reproduction number (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}) \bmb{is \Rc the same as ``forward \RR measured at a particular time''?}, $i(\alpha_1)$ is incidence, $h_{\alpha_1}(\pi-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pi-\alpha_1$ and forward generation interval $\alpha_2 - \alpha_1$ of an individual infected at time $\alpha_1$ (in this case, the infector), and $k_{\alpha_2}(\delta-\alpha_2)$ describes the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\delta-\alpha_2$ of an individual infected at time $\alpha_2$ (in this case, the infectee).
-Then, the forward serial-interval distribution is proportional to $T(\pi, \pi+\tau)$. Substituting $x=\pi-\alpha_1$ and $\sigma=\alpha_2-\alpha_1$, we have:
+where $h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pt-\alpha_1$ and the forward generation interval $\alpha_2 - \alpha_1$ of a cohort of individuals infected at time $\alpha_1$ (in this case, the infectors), and $k_{\alpha_2}(\st-\alpha_2)$ is the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\st-\alpha_2$ of a cohort of individuals infected at time $\alpha_2$ (in this case, the infectee).
+Then, the total number of serial intervals can be obtained by integrating over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
 \begin{equation}
-f_\pi(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \Rc (\pi-x) i(\pi-x) h_{\pi-x}(x, \sigma) k_{\pi-x+\sigma}(x-\sigma+\tau) \dsigma \dx
+\total (\pt,\st) = \int_{-\infty}^{\pt} \int_{\alpha_1}^{\st} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\st - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
 \end{equation}
-Likewise, the backward serial-interval distribution is proportional to $T(\delta-\tau, \delta)$. 
-This time, we substitute $x=\delta-\alpha_2$ and $\sigma=\alpha_2-\alpha_1$ to get:
+
+Then, the forward serial-interval distribution is proportional to $\total (\pt, \pt+\tau)$. Substituting $x=\pt-\alpha_1$ and $\gtime=\alpha_2-\alpha_1$, we have:
 \begin{equation}
-b_\delta(\tau) \propto \int_{0}^{\infty} \int_{\max(0, \tau-x)}^{\infty} \Rc (\delta-x-\sigma) i(\delta-x-\sigma) h_{\delta-x-\sigma}(x+\sigma-\tau, \sigma) k_{\delta-x}(x) \dsigma \dx.
+f_\pt(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \Rc (\pt-x) i(\pt-x) h_{\pt-x}(x, \gtime) k_{\pt-x+\gtime}(x-\gtime+\tau) \dsigma \dx
+\end{equation}
+Likewise, the backward serial-interval distribution is proportional to $\total (\st-\tau, \st)$. 
+This time, we substitute $x=\st-\alpha_2$ and $\gtime=\alpha_2-\alpha_1$ to get:
+\begin{equation}
+b_\st(\tau) \propto \int_{0}^{\infty} \int_{\max(0, \tau-x)}^{\infty} \Rc (\st-x-\gtime) i(\st-x-\gtime) h_{\st-x-\gtime}(x+\gtime-\tau, \gtime) k_{\st-x}(x) \dsigma \dx.
 \end{equation}

### 2020-04-29 serial.tex
so much to do!!!!!

@@
 In order to define forward and backward serial interval distributions, we begin by modeling the total number of serial intervals $\total(\pt,\st)$ between time $\pt$ and $\st$ (i.e., total number of infection in which infectors develop symptom at time $\pt$ and infectees develop symptom at time $\st$).
-The number of serial intervals between time $\pt$ and $\st$ given that the infectors became infected at time $\alpha_1$ and the infectees became infected at time $\alpha_2$ is can be then expressed as a product of (i) incidence $i$ at time $\alpha_1$, (ii) their case reproduction number $\Rc(\alpha_1)$ (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$, \cite{fraser2007estimating}), (iii) the density of forward generation interval between $\alpha_1$ and $\alpha_2$, and (iv) the densities of forward incubation periods between $\alpha_1$ and $\pt$ (incubation periods of infectors) as well as $\alpha_2$ and $\st$ (incubation periods of infectees):
+The number of serial intervals between time $\pt$ and $\st$ given that the infectors became infected at time $\alpha_1$ and the infectees became infected at time $\alpha_2$ is can be then expressed as a product of (i) incidence $i$ at time $\alpha_1$, (ii) their case reproduction number $\Rc(\alpha_1)$ (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$ over the course of their infection, \cite{fraser2007estimating}), (iii) the density of forward generation interval between $\alpha_1$ and $\alpha_2$, and (iv) the densities of forward incubation periods between $\alpha_1$ and $\pt$ (incubation periods of infectors) as well as $\alpha_2$ and $\st$ (incubation periods of infectees):
 \begin{equation}
-\Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\st - \alpha_2),
+\underbrace{\Rc (\alpha_1)}_{\substack{\text{case} \\ \text{reproduction} \\ \text{number}}} 
+\times 
+\underbrace{i(\alpha_1)}_{\text{incidence}} 
+\times 
+\underbrace{h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)}_{\substack{\text{joint density of} \\ \text{the forward incubation} \\ \text{period and the fowrard} \\ \text{generation interval}}}
+\times
+\underbrace{k_{\alpha_2}(\st - \alpha_2)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period}}},
 \end{equation}
 where $h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pt-\alpha_1$ and the forward generation interval $\alpha_2 - \alpha_1$ of a cohort of individuals infected at time $\alpha_1$ (in this case, the infectors), and $k_{\alpha_2}(\st-\alpha_2)$ is the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\st-\alpha_2$ of a cohort of individuals infected at time $\alpha_2$ (in this case, the infectee).
+It is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life-history of a disease;
+for example, if an infected individual can only transmit the disease after symptom onset, the forward generation interval will necessarily be longer than the forward incubation period.
 Then, the total number of serial intervals can be obtained by integrating over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
@@
 
-Then, the forward serial-interval distribution is proportional to $\total (\pt, \pt+\tau)$. Substituting $x=\pt-\alpha_1$ and $\gtime=\alpha_2-\alpha_1$, we have:
+Finally, the forward serial-interval distribution is proportional to $\total (\pt, \pt+\tau)$ because it is conditional on the cohort of infectors who become symptomatic at time $\pt$.
+Substituting $x=\pt-\alpha_1$ and $\gtime=\alpha_2-\alpha_1$, we have:
 \begin{equation}
@@
 \end{equation}
-Likewise, the backward serial-interval distribution is proportional to $\total (\st-\tau, \st)$. 
+Likewise, the backward serial-interval distribution is proportional to $\total (\st-\tau, \st)$ because it is conditional on the cohort of infectees who become symptomatic at time $\st$.  
 This time, we substitute $x=\st-\alpha_2$ and $\gtime=\alpha_2-\alpha_1$ to get:
@@
 
-We validate \bmb{??} the theory by applying it to a specific example of an epidemic model. 
+We illustrate the theory by applying it to a specific example of an epidemic model. 
 We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.

### 2020-04-29 serial.tex
more stuff

@@
 \newcommand{\Ro}{\Rx{0}}
-\newcommand{\Rc}{\Rx{c}}
+\newcommand{\Rc}{\Rx{\mathrm{c}}}
 \newcommand{\RR}{\ensuremath{{\mathcal R}}\xspace}
@@
 we begin by describing factors that affect the forward delay distributions.
-Typically, within-individual forward delay distributions that reflect life-history of a disease is expected to remain invariant over the course of an epidemic; 
+Typically, within-individual forward delay distributions that reflect life history of a disease is expected to remain invariant over the course of an epidemic; 
 these distributions include incubation period distribution.
@@
 The backward delay distribution is measured for a cohort of individuals whose secondary events occurred at the same time.
-When the cohort size is increasing (or decreasing) over time, we are biased to observe shorter (or longer) delays if we look backward.
-Therefore, the backward delay distributions will be generally different from the forward delay distributions even if we are measuring time delays that are intrinsic to life-history of a disease (e.g., incubation period).
-These ideas apply to all epidemiological delay distributions and generalize the work by \citep{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively.
+When the cohort size is increasing (or decreasing) over time, we are biased to observe shorter (or longer) delays when we look backward.
+In particular, when the incidence is growing exponentially, we can calculate the amount of bias exactly.
+Assuming that the forward delay distribution remains constant during the exponential growth phase ($\tsub{f}{exp}$), we have:
+\begin{equation}
+\tsub{b}{exp}(\tau) \propto \exp(-r\tau) \tsub{f}{exp}(\tau),
+\label{eq:backexp}
+\end{equation}
+where $r$ is the exponential growth rate.
+Therefore, the backward delay distributions will be generally different from the forward delay distributions even if we are measuring time delays that are intrinsic to life history of a disease (e.g., incubation period).
+These ideas apply to all epidemiological delay distributions and generalize the work by \cite{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively, as well as the work by \cite{britton2019estimation} who showed that \eref{backexp} holds for the backward generation-interval distributions.
 
@@
 These studies assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-this conclusion is based on the implicit assumption that serial intervals are measured from the perspective of a cohort of infectors that share the same infection time.
-We refer to this definition of serial intervals as the intrinsic serial interval.
+however, this conclusion is based on the implicit assumption that serial intervals are measured from the perspective of a cohort of infectors that share the same infection time.
+We refer to this definition as the intrinsic serial interval.
 
@@
 and $x_1$ follows the forward incubation period distribution.
-(B) The forward serial interval for a primary cohort $\pt$ (i.e., the cohort of infectors who became symptomatic at time $\pt$).
+(B) The forward serial interval for a cohort of infectors who became symptomatic at time $\pt$.
 In this case, $x_0$ follows the backward incubation period distribution;
@@
 and $x_1$ follows the forward incubation period distribution.
-(C) The backward serial interval for a secondary cohort $\st$ (i.e., the cohort of infectees who became symptomatic at time $\st$).
+(C) The backward serial interval for a cohort of infectees who became symptomatic at time $\st$.
 In this case, $x_0$ follows the forward incubation period distribution;
@@
 
-Since serial intervals describe the renewal process between symptomatic cases based on their symptom onset dates, we have to define serial intervals from the perspective of a cohort (of either infectors or infectees) that share the same symptom onset time.
+Since serial intervals describe the renewal process between symptomatic cases based on their symptom onset dates, we have to define serial intervals from the perspective of a cohort (of either infectors or infectees) of individuals that share the same symptom onset time.
 The cohort-based framework allows us to understand the distribution of serial intervals we expect to observe when incidence is changing.
@@
 where $h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pt-\alpha_1$ and the forward generation interval $\alpha_2 - \alpha_1$ of a cohort of individuals infected at time $\alpha_1$ (in this case, the infectors), and $k_{\alpha_2}(\st-\alpha_2)$ is the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\st-\alpha_2$ of a cohort of individuals infected at time $\alpha_2$ (in this case, the infectee).
-It is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life-history of a disease;
+It is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
 for example, if an infected individual can only transmit the disease after symptom onset, the forward generation interval will necessarily be longer than the forward incubation period.
@@
 
-Finally, the forward serial-interval distribution is proportional to $\total (\pt, \pt+\tau)$ because it is conditional on the cohort of infectors who become symptomatic at time $\pt$.
-Substituting $x=\pt-\alpha_1$ and $\gtime=\alpha_2-\alpha_1$, we have:
+Finally, the forward serial-interval distribution is proportional to $\total (\pt, \pt+\tau)$ because it is conditional on the cohort of infectors who became symptomatic at time $\pt$:
 \begin{equation}
-f_\pt(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \Rc (\pt-x) i(\pt-x) h_{\pt-x}(x, \gtime) k_{\pt-x+\gtime}(x-\gtime+\tau) \dsigma \dx
+f_\pt(\tau) \propto \int_{-\infty}^{\pt} \int_{\alpha_1}^{\pt+\tau} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\pt+\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
 \end{equation}
-Likewise, the backward serial-interval distribution is proportional to $\total (\st-\tau, \st)$ because it is conditional on the cohort of infectees who become symptomatic at time $\st$.  
-This time, we substitute $x=\st-\alpha_2$ and $\gtime=\alpha_2-\alpha_1$ to get:
+The constant of proportionality is then equal to the total number of infection caused by individuals who became symptomatic at time $\pt$.
+Likewise, the backward serial-interval distribution is proportional to $\total (\st-\tau, \st)$ because it is conditional on the cohort of infectees who became symptomatic at time $\st$:
 \begin{equation}
-b_\st(\tau) \propto \int_{0}^{\infty} \int_{\max(0, \tau-x)}^{\infty} \Rc (\st-x-\gtime) i(\st-x-\gtime) h_{\st-x-\gtime}(x+\gtime-\tau, \gtime) k_{\st-x}(x) \dsigma \dx.
+b_\st(\tau) \propto \int_{-\infty}^{\st-\tau} \int_{\alpha_1}^{\st} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\st-\tau-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\st - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
 \end{equation}
+The constant of proportionality is then equal to the total number of infectors that infected individuals who became symptomatic at time $\st$.
 
@@
 \frac{\mathrm{d}S}{\mathrm{d}t} &= - i(t)\\
-i(t) &= \Ro S(t) \int_0^\infty i(t-\tau) g(\tau) \dtau,
+i(t) &= \Ro S(t) \int_0^\infty i(t-\tau) \gdist(\tau) \dtau,
 \end{aligned}
@@
 \end{equation}
-where \Ro is the basic reproduction number, and $g(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
-Then, the forward generation-interval for a primary cohort $\pi$ follows \citep{champredon2015intrinsic}:
+where \Ro is the basic reproduction number, and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
+Then, the forward generation-interval for a cohort of individuals that were infected at time $\pt$ follows \citep{champredon2015intrinsic}:
 \begin{equation}
-g_\pi (\tau) \propto g(\tau) S(\pi + \tau),
+\gdist_\pt (\tau) \propto \gdist(\tau) S(\pt + \tau),
 \end{equation}
-which allows us to separate the joint probability distribution $h_\pi$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
+which allows us to separate the joint probability distribution $h_\pt$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
 \begin{equation}
-h_\pi (x, \tau) \propto h(x, \tau) S(\pi + \tau).
+h_\pt (x, \tau) \propto h(x, \tau) S(\pt + \tau).
 \end{equation}
-We further assume that the forward incubation period distributions does not vary across cohorts over the course of an epidemic, as they represent the natural history of a disease, and use $k$ without subscript instead.
+We further assume that the forward incubation period distributions does not vary across cohorts over the course of an epidemic, as they represent the life history of a disease, and use $k$ without subscript instead.
 Then, we have:
@@
 During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
-Then, we can use the Euler-Lotka equation to estimate the reproduction number from the exponential growth rate $r$ \bmb{ref??}:
+Then, we can use the Euler-Lotka equation to estimate the reproduction number from the exponential growth rate $r$ \citep{wallinga2007generation}:
 \begin{equation}
@@
 \begin{equation}
-f_{0}(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \exp(-rx) h(x, \sigma) k(x-\sigma+\tau) \mathrm{d}\sigma\,\mathrm{d}x
+f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) k(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
 \end{equation}
@@
 The initial forward serial-interval distribution depends on the exponential growth rate $r$.
-For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short \bmb{I \textbf{still} don't understand why backward incubation periods are dynamic as well as direction-sensitive \ldots}, and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation-interval distribution.
-The Susceptible-Exposed-Infected-Recovered model, which assumes that incubation and exposed periods are equivalent \bmb{note this is not generally how SEIR is defined.
-You need a special case}, is a special case where the conditional forward generation-interval distribution cancels out with \bmb{???} the backward incubation period distribution exactly because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector;
-in this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase.
+For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short (\eref{backexp}), and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation- and serial-interval distributions.
+The Susceptible-Exposed-Infected-Recovered model, with an additional assumption that incubation and exposed periods are equivalent, provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector (see Appendix).
 

### 2020-04-29 serial.tex
underbrace

@@
 }
+\newline
+\\
+Sang Woo Park\textsuperscript{1,*}
+Kaiyuan Sun\textsuperscript{2}
+Benjamin M.\ Bolker\textsuperscript{3,4,5}
+David Champredon\textsuperscript{6}
+David J.\,D.\ Earn\textsuperscript{4,5}
+Michael Li\textsuperscript{3}
+Joshua S.\ Weitz\textsuperscript{7, 8}
+Bryan T.\ Grenfell\textsuperscript{1,2,9}
+Jonathan Dushoff\textsuperscript{3,4,5,*}
+\\
+\bigskip
+\textbf{1} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, NJ, USA
+\\
+\textbf{2} Fogarty International Center, National Institutes of Health, Bethesda, MD, USA
+\\
+\textbf{3} Department of Biology, McMaster University, Hamilton, ON, Canada
+\\
+\textbf{4} Department of Mathematics and Statistics, McMaster University, Hamilton, ON, Canada
+\\
+\textbf{5} M.\,G.\,DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, ON, Canada
+\\
+\textbf{6} Department of Pathology and Laboratory Medicine, University of Western Ontario, London, Ontario, Canada
+\\
+\textbf{7} School of Biological Sciences, Georgia Institute of Technology, Atlanta, GA, USA
+\\
+\textbf{8} School of Physics, Georgia Institute of Technology, Atlanta, GA, USA
+\\
+\textbf{9} Woodrow Wilson School of Public and International Affairs, Princeton University, Princeton, NJ, USA
+\\
+\bigskip
+
+*Corresponding author: swp2@princeton.edu
 \end{flushleft}
@@
 Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number \RR --- yet important quantities in understanding the outset of an outbreak.
-We argue that a part of the confusion can be attributed to an apparent paradox.
+Even though their differences were clearly laid out over a decade ago, 
+A part of the confusion can be attributed to an apparent paradox.
 By definition, generation and serial intervals describe the renewal process between infection and symptom onset, respectively, and therefore, one might expect them to potentially provide the same link between the epidemic growth rate $r$ and the reproduction number \RR.
@@
 \times 
-\underbrace{h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)}_{\substack{\text{joint density of} \\ \text{the forward incubation} \\ \text{period and the fowrard} \\ \text{generation interval}}}
+\underbrace{h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)}_{\substack{\text{joint density of} \\ \text{the forward incubation} \\ \text{period and the forward} \\ \text{generation interval}\\ \text{(of infectors)}}}
 \times
-\underbrace{k_{\alpha_2}(\st - \alpha_2)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period}}},
+\underbrace{k_{\alpha_2}(\st - \alpha_2)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period (of infectees)}}},
 \end{equation}
@@
 \begin{equation}
-\Rc(t) = \Ro \int_0^\infty g(\tau) S(t+\tau) \dtau.
+\Rc(t) = \Ro \int_0^\infty \gdist(\tau) S(t+\tau) \dtau.
 \end{equation}

### 2020-04-29 serial.tex
still so much to do

@@
 \newcommand{\Rhat}{\ensuremath{{\hat\RR}}}
-\newcommand{\Rnaive}{\ensuremath{{\mathcal R}_{\textrm{\tiny naive}}}\xspace}
+\newcommand{\Rintrinsic}{\ensuremath{{\mathcal R}_{\textrm{\tiny intrinsic}}}\xspace}
 \newcommand{\tsub}[2]{#1_{{\textrm{\tiny #2}}}}
@@
 During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
-Then, we can use the Euler-Lotka equation to estimate the reproduction number from the exponential growth rate $r$ \citep{wallinga2007generation}:
+When incidence grows exponentially, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the reproduction number \RR based on the Euler-Lotka equation \citep{wallinga2007generation}:
 \begin{equation}
@@
 \end{equation}
-Analogous to forward generation-interval distributions, 
+Analogous to the intrinsic generation-interval distribution, 
 forward serial-interval distributions describe the renewal process of symptomatic cases.
@@
 \begin{equation}
-S_i = -B_i + (G_i|B_i) + I_i,
+F_i = -X_{0,i} + (G_i|X_{0,i}) + X_{1,i},
 \end{equation}
-where the backward incubation period $B_i$ of an infector is simulated by drawing random log-normal samples $A_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $A_i$, each weighted by the inverse of the exponential growth function $\exp(-rA_i)$;
-the intrinsic generation interval conditional on the incubation period of the infector $(G_i|B_i)$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(B_i) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
-the forward incubation period $I_i$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
+where the backward incubation period $X_{0,i}$ of an infector is simulated by drawing random log-normal samples $Y_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $Y_i$, each weighted by the inverse of the exponential growth function $\exp(-rY_i)$;
+the intrinsic generation interval conditional on the incubation period of the infector $(G_i|X_{0,i})$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(X_{0,i}) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
+the forward incubation period $X_{1,i}$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
 We then calculate the reproduction number \RR using the empirical estimator:
 \begin{equation}
-\RR = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r S_i)}.
+\RR = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r F_i)}.
 \end{equation}
-We compare this with an estimate of \RR based on naive serial-interval distribution that assumes that the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
+We compare this with an estimate of \RR based on the intrinsic serial-interval distribution in which the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
 \begin{equation}
-  \Rnaive = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r Q_i)},
+  \Rintrinsic = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r Q_i)},
 \end{equation}
@@
 \begin{equation}
-Q_i = -A_i + (G_i|A_i) + I_i.
+Q_i = -Y_i + (G_i|Y_i) + X_{1,i}.
 \end{equation}
@@
 However, using naive serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \RR;
-as $r$ increases, \Rnaive saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
+as $r$ increases, \Rintrinsic saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
 While the forward serial intervals during the exponential growth phase can also be negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation periods (and therefore a lower proportion of negative serial intervals).

### 2020-04-29 rR.tex
new fig

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-14 17:43:43
+% Created by tikzDevice version 0.12.3 on 2020-04-29 03:55:17
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.65) --
-	( 30.56,248.50) --
-	( 33.80,249.37) --
-	( 37.04,250.25) --
-	( 40.29,251.16) --
-	( 43.53,252.09) --
-	( 46.78,253.03) --
-	( 50.02,254.00) --
-	( 53.26,254.98) --
-	( 56.51,255.98) --
-	( 59.75,257.00) --
-	( 63.00,258.04) --
-	( 66.24,259.10) --
-	( 69.48,260.18) --
-	( 72.73,261.28) --
-	( 75.97,262.40) --
-	( 79.22,263.54) --
-	( 82.46,264.70) --
-	( 85.70,265.88) --
-	( 88.95,267.07) --
-	( 92.19,268.29) --
-	( 95.43,269.52) --
-	( 98.68,270.77) --
-	(101.92,272.04) --
-	(105.17,273.33) --
-	(108.41,274.63) --
-	(111.65,275.96) --
-	(114.90,277.31) --
-	(118.14,278.69) --
-	(121.39,280.08) --
-	(124.63,281.50) --
-	(127.87,282.94) --
-	(131.12,284.39) --
-	(134.36,285.86) --
-	(137.61,287.35) --
-	(140.85,288.87) --
-	(144.09,290.41) --
-	(147.34,291.97) --
-	(150.58,293.56) --
-	(153.82,295.18) --
-	(157.07,296.83) --
-	(160.31,298.49) --
-	(163.56,300.18) --
-	(166.80,301.88) --
-	(170.04,303.60) --
-	(173.29,305.35) --
-	(176.53,307.13) --
-	(179.78,308.93) --
-	(183.02,310.77) --
-	(186.26,312.64) --
-	(189.51,314.55) --
-	(192.75,316.48) --
-	(196.00,318.44) --
-	(199.24,320.43) --
-	(202.48,322.45) --
-	(205.73,324.49) --
-	(208.97,326.57) --
-	(212.21,328.67) --
-	(215.46,330.81) --
-	(218.70,332.98) --
-	(221.95,335.19) --
-	(225.19,337.43) --
-	(228.43,339.70) --
-	(231.68,342.00) --
-	(234.92,344.33) --
-	(238.17,346.69) --
-	(241.41,349.09) --
-	(244.65,351.51) --
-	(247.90,353.96) --
-	(251.14,356.45) --
-	(254.39,358.97) --
-	(257.63,361.51) --
-	(260.87,364.10) --
-	(264.12,366.71) --
-	(267.36,369.35) --
-	(270.60,372.03) --
-	(273.85,374.73) --
-	(277.09,377.47) --
-	(280.34,380.24) --
-	(283.58,383.04);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 52.94,254.97) --
+	( 55.54,255.77) --
+	( 58.13,256.58) --
+	( 60.73,257.40) --
+	( 63.32,258.23) --
+	( 65.92,259.08) --
+	( 68.51,259.94) --
+	( 71.11,260.81) --
+	( 73.70,261.69) --
+	( 76.30,262.59) --
+	( 78.89,263.49) --
+	( 81.49,264.42) --
+	( 84.08,265.35) --
+	( 86.68,266.30) --
+	( 89.27,267.26) --
+	( 91.87,268.23) --
+	( 94.46,269.21) --
+	( 97.06,270.20) --
+	( 99.65,271.21) --
+	(102.25,272.23) --
+	(104.84,273.26) --
+	(107.44,274.30) --
+	(110.03,275.36) --
+	(112.63,276.43) --
+	(115.22,277.51) --
+	(117.82,278.61) --
+	(120.41,279.72) --
+	(123.01,280.84) --
+	(125.60,281.98) --
+	(128.20,283.13) --
+	(130.79,284.29) --
+	(133.39,285.46) --
+	(135.98,286.65) --
+	(138.58,287.85) --
+	(141.17,289.07) --
+	(143.77,290.31) --
+	(146.36,291.55) --
+	(148.96,292.82) --
+	(151.55,294.10) --
+	(154.15,295.40) --
+	(156.74,296.71) --
+	(159.34,298.04) --
+	(161.93,299.39) --
+	(164.53,300.75) --
+	(167.12,302.12) --
+	(169.72,303.51) --
+	(172.31,304.92) --
+	(174.91,306.34) --
+	(177.51,307.78) --
+	(180.10,309.24) --
+	(182.70,310.71) --
+	(185.29,312.21) --
+	(187.89,313.72) --
+	(190.48,315.26) --
+	(193.08,316.81) --
+	(195.67,318.38) --
+	(198.27,319.97) --
+	(200.86,321.57) --
+	(203.46,323.20) --
+	(206.05,324.84) --
+	(208.65,326.51) --
+	(211.24,328.19) --
+	(213.84,329.89) --
+	(216.43,331.62) --
+	(219.03,333.36) --
+	(221.62,335.12) --
+	(224.22,336.91) --
+	(226.81,338.72) --
+	(229.41,340.54) --
+	(232.00,342.39) --
+	(234.60,344.25) --
+	(237.19,346.14) --
+	(239.79,348.04) --
+	(242.38,349.97) --
+	(244.98,351.91) --
+	(247.57,353.87) --
+	(250.17,355.85) --
+	(252.76,357.85) --
+	(255.36,359.88) --
+	(257.95,361.92);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.62) --
-	( 30.56,248.48) --
-	( 33.80,249.35) --
-	( 37.04,250.25) --
-	( 40.29,251.16) --
-	( 43.53,252.10) --
-	( 46.78,253.05) --
-	( 50.02,254.02) --
-	( 53.26,255.01) --
-	( 56.51,256.02) --
-	( 59.75,257.05) --
-	( 63.00,258.09) --
-	( 66.24,259.16) --
-	( 69.48,260.24) --
-	( 72.73,261.35) --
-	( 75.97,262.47) --
-	( 79.22,263.61) --
-	( 82.46,264.77) --
-	( 85.70,265.96) --
-	( 88.95,267.16) --
-	( 92.19,268.38) --
-	( 95.43,269.61) --
-	( 98.68,270.86) --
-	(101.92,272.13) --
-	(105.17,273.42) --
-	(108.41,274.73) --
-	(111.65,276.06) --
-	(114.90,277.41) --
-	(118.14,278.78) --
-	(121.39,280.18) --
-	(124.63,281.60) --
-	(127.87,283.02) --
-	(131.12,284.47) --
-	(134.36,285.93) --
-	(137.61,287.42) --
-	(140.85,288.92) --
-	(144.09,290.45) --
-	(147.34,292.01) --
-	(150.58,293.59) --
-	(153.82,295.21) --
-	(157.07,296.85) --
-	(160.31,298.51) --
-	(163.56,300.20) --
-	(166.80,301.90) --
-	(170.04,303.62) --
-	(173.29,305.37) --
-	(176.53,307.14) --
-	(179.78,308.95) --
-	(183.02,310.78) --
-	(186.26,312.65) --
-	(189.51,314.55) --
-	(192.75,316.49) --
-	(196.00,318.45) --
-	(199.24,320.44) --
-	(202.48,322.45) --
-	(205.73,324.49) --
-	(208.97,326.57) --
-	(212.21,328.67) --
-	(215.46,330.81) --
-	(218.70,332.98) --
-	(221.95,335.19) --
-	(225.19,337.43) --
-	(228.43,339.70) --
-	(231.68,342.01) --
-	(234.92,344.34) --
-	(238.17,346.71) --
-	(241.41,349.11) --
-	(244.65,351.53) --
-	(247.90,353.99) --
-	(251.14,356.48) --
-	(254.39,359.01) --
-	(257.63,361.56) --
-	(260.87,364.15) --
-	(264.12,366.77) --
-	(267.36,369.42) --
-	(270.60,372.10) --
-	(273.85,374.82) --
-	(277.09,377.56) --
-	(280.34,380.34) --
-	(283.58,383.15);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.52) --
+	( 30.34,248.34) --
+	( 33.37,249.16) --
+	( 36.40,250.01) --
+	( 39.42,250.87) --
+	( 42.45,251.74) --
+	( 45.48,252.64) --
+	( 48.51,253.54) --
+	( 51.53,254.47) --
+	( 54.56,255.41) --
+	( 57.59,256.36) --
+	( 60.62,257.34) --
+	( 63.64,258.32) --
+	( 66.67,259.33) --
+	( 69.70,260.35) --
+	( 72.73,261.38) --
+	( 75.76,262.43) --
+	( 78.78,263.50) --
+	( 81.81,264.58) --
+	( 84.84,265.68) --
+	( 87.87,266.80) --
+	( 90.89,267.93) --
+	( 93.92,269.08) --
+	( 96.95,270.25) --
+	( 99.98,271.42) --
+	(103.00,272.61) --
+	(106.03,273.81) --
+	(109.06,275.03) --
+	(112.09,276.26) --
+	(115.11,277.51) --
+	(118.14,278.77) --
+	(121.17,280.06) --
+	(124.20,281.37) --
+	(127.22,282.71) --
+	(130.25,284.06) --
+	(133.28,285.44) --
+	(136.31,286.83) --
+	(139.34,288.23) --
+	(142.36,289.64) --
+	(145.39,291.08) --
+	(148.42,292.53) --
+	(151.45,294.01) --
+	(154.47,295.51) --
+	(157.50,297.03) --
+	(160.53,298.59) --
+	(163.56,300.17) --
+	(166.58,301.77) --
+	(169.61,303.39) --
+	(172.64,305.02) --
+	(175.67,306.68) --
+	(178.69,308.35) --
+	(181.72,310.04) --
+	(184.75,311.76) --
+	(187.78,313.51) --
+	(190.80,315.28) --
+	(193.83,317.09) --
+	(196.86,318.92) --
+	(199.89,320.80) --
+	(202.92,322.69) --
+	(205.94,324.62) --
+	(208.97,326.56) --
+	(212.00,328.54) --
+	(215.03,330.54) --
+	(218.05,332.56) --
+	(221.08,334.62) --
+	(224.11,336.70) --
+	(227.14,338.80) --
+	(230.16,340.94) --
+	(233.19,343.10) --
+	(236.22,345.29) --
+	(239.25,347.50) --
+	(242.27,349.75) --
+	(245.30,352.02) --
+	(248.33,354.31) --
+	(251.36,356.63) --
+	(254.39,358.98) --
+	(257.41,361.36) --
+	(260.44,363.76) --
+	(263.47,366.19) --
+	(266.50,368.65);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.61) --
-	( 30.56,248.47) --
-	( 33.80,249.35) --
-	( 37.04,250.24) --
-	( 40.29,251.16) --
-	( 43.53,252.10) --
-	( 46.78,253.05) --
-	( 50.02,254.02) --
-	( 53.26,255.02) --
-	( 56.51,256.03) --
-	( 59.75,257.06) --
-	( 63.00,258.10) --
-	( 66.24,259.17) --
-	( 69.48,260.26) --
-	( 72.73,261.36) --
-	( 75.97,262.48) --
-	( 79.22,263.63) --
-	( 82.46,264.79) --
-	( 85.70,265.97) --
-	( 88.95,267.17) --
-	( 92.19,268.39) --
-	( 95.43,269.63) --
-	( 98.68,270.88) --
-	(101.92,272.15) --
-	(105.17,273.44) --
-	(108.41,274.75) --
-	(111.65,276.08) --
-	(114.90,277.43) --
-	(118.14,278.80) --
-	(121.39,280.20) --
-	(124.63,281.61) --
-	(127.87,283.04) --
-	(131.12,284.48) --
-	(134.36,285.94) --
-	(137.61,287.42) --
-	(140.85,288.92) --
-	(144.09,290.45) --
-	(147.34,292.00) --
-	(150.58,293.58) --
-	(153.82,295.19) --
-	(157.07,296.84) --
-	(160.31,298.49) --
-	(163.56,300.17) --
-	(166.80,301.87) --
-	(170.04,303.59) --
-	(173.29,305.33) --
-	(176.53,307.10) --
-	(179.78,308.90) --
-	(183.02,310.73) --
-	(186.26,312.60) --
-	(189.51,314.50) --
-	(192.75,316.44) --
-	(196.00,318.40) --
-	(199.24,320.39) --
-	(202.48,322.40) --
-	(205.73,324.45) --
-	(208.97,326.53) --
-	(212.21,328.63) --
-	(215.46,330.78) --
-	(218.70,332.95) --
-	(221.95,335.17) --
-	(225.19,337.42) --
-	(228.43,339.70) --
-	(231.68,342.01) --
-	(234.92,344.36) --
-	(238.17,346.74) --
-	(241.41,349.14) --
-	(244.65,351.58) --
-	(247.90,354.06) --
-	(251.14,356.56) --
-	(254.39,359.10) --
-	(257.63,361.67) --
-	(260.87,364.27) --
-	(264.12,366.91) --
-	(267.36,369.58) --
-	(270.60,372.28) --
-	(273.85,375.01) --
-	(277.09,377.78) --
-	(280.34,380.58) --
-	(283.58,383.41);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.86,249.91) --
+	( 38.88,250.76) --
+	( 41.91,251.62) --
+	( 44.94,252.51) --
+	( 47.97,253.41) --
+	( 50.99,254.32) --
+	( 54.02,255.26) --
+	( 57.05,256.21) --
+	( 60.08,257.17) --
+	( 63.10,258.15) --
+	( 66.13,259.15) --
+	( 69.16,260.17) --
+	( 72.19,261.20) --
+	( 75.21,262.25) --
+	( 78.24,263.31) --
+	( 81.27,264.39) --
+	( 84.30,265.48) --
+	( 87.33,266.60) --
+	( 90.35,267.72) --
+	( 93.38,268.87) --
+	( 96.41,270.03) --
+	( 99.44,271.21) --
+	(102.46,272.41) --
+	(105.49,273.62) --
+	(108.52,274.84) --
+	(111.55,276.08) --
+	(114.57,277.32) --
+	(117.60,278.59) --
+	(120.63,279.86) --
+	(123.66,281.16) --
+	(126.68,282.48) --
+	(129.71,283.81) --
+	(132.74,285.17) --
+	(135.77,286.56) --
+	(138.79,287.97) --
+	(141.82,289.39) --
+	(144.85,290.83) --
+	(147.88,292.29) --
+	(150.91,293.76) --
+	(153.93,295.24) --
+	(156.96,296.75) --
+	(159.99,298.28) --
+	(163.02,299.84) --
+	(166.04,301.42) --
+	(169.07,303.03) --
+	(172.10,304.67) --
+	(175.13,306.33) --
+	(178.15,308.01) --
+	(181.18,309.70) --
+	(184.21,311.42) --
+	(187.24,313.15) --
+	(190.26,314.90) --
+	(193.29,316.68) --
+	(196.32,318.49) --
+	(199.35,320.33) --
+	(202.37,322.21) --
+	(205.40,324.12) --
+	(208.43,326.06) --
+	(211.46,328.03) --
+	(214.49,330.03) --
+	(217.51,332.06) --
+	(220.54,334.11) --
+	(223.57,336.19) --
+	(226.60,338.30) --
+	(229.62,340.44) --
+	(232.65,342.61) --
+	(235.68,344.80) --
+	(238.71,347.02) --
+	(241.73,349.28) --
+	(244.76,351.56) --
+	(247.79,353.87) --
+	(250.82,356.21) --
+	(253.84,358.58) --
+	(256.87,360.97) --
+	(259.90,363.40) --
+	(262.93,365.85) --
+	(265.95,368.33) --
+	(268.98,370.84) --
+	(272.01,373.38) --
+	(275.04,375.95);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.60) --
-	( 30.56,248.46) --
-	( 33.80,249.34) --
-	( 37.04,250.24) --
-	( 40.29,251.16) --
-	( 43.53,252.09) --
-	( 46.78,253.05) --
-	( 50.02,254.02) --
-	( 53.26,255.02) --
-	( 56.51,256.03) --
-	( 59.75,257.06) --
-	( 63.00,258.11) --
-	( 66.24,259.18) --
-	( 69.48,260.26) --
-	( 72.73,261.37) --
-	( 75.97,262.49) --
-	( 79.22,263.64) --
-	( 82.46,264.80) --
-	( 85.70,265.98) --
-	( 88.95,267.19) --
-	( 92.19,268.40) --
-	( 95.43,269.64) --
-	( 98.68,270.89) --
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.40,252.39) --
+	( 47.43,253.28) --
+	( 50.45,254.18) --
+	( 53.48,255.11) --
+	( 56.51,256.05) --
+	( 59.54,257.00) --
+	( 62.56,257.98) --
+	( 65.59,258.97) --
+	( 68.62,259.97) --
+	( 71.65,261.00) --
+	( 74.67,262.04) --
+	( 77.70,263.10) --
+	( 80.73,264.17) --
+	( 83.76,265.26) --
+	( 86.78,266.37) --
+	( 89.81,267.49) --
+	( 92.84,268.63) --
+	( 95.87,269.79) --
+	( 98.89,270.97) --
 	(101.92,272.16) --
-	(105.17,273.45) --
-	(108.41,274.76) --
-	(111.65,276.09) --
-	(114.90,277.44) --
-	(118.14,278.81) --
-	(121.39,280.21) --
-	(124.63,281.62) --
-	(127.87,283.04) --
-	(131.12,284.48) --
-	(134.36,285.94) --
-	(137.61,287.42) --
-	(140.85,288.92) --
-	(144.09,290.44) --
-	(147.34,291.99) --
-	(150.58,293.57) --
-	(153.82,295.18) --
-	(157.07,296.82) --
-	(160.31,298.48) --
-	(163.56,300.15) --
-	(166.80,301.85) --
-	(170.04,303.56) --
-	(173.29,305.30) --
-	(176.53,307.07) --
-	(179.78,308.87) --
-	(183.02,310.70) --
-	(186.26,312.56) --
-	(189.51,314.47) --
-	(192.75,316.41) --
-	(196.00,318.37) --
-	(199.24,320.36) --
-	(202.48,322.38) --
-	(205.73,324.43) --
-	(208.97,326.51) --
-	(212.21,328.63) --
-	(215.46,330.77) --
-	(218.70,332.96) --
-	(221.95,335.18) --
-	(225.19,337.45) --
-	(228.43,339.74) --
-	(231.68,342.07) --
-	(234.92,344.42) --
-	(238.17,346.82) --
-	(241.41,349.24) --
-	(244.65,351.70) --
-	(247.90,354.18) --
-	(251.14,356.71) --
-	(254.39,359.26) --
-	(257.63,361.85) --
-	(260.87,364.48) --
-	(264.12,367.14) --
-	(267.36,369.83) --
-	(270.60,372.55) --
-	(273.85,375.31) --
-	(277.09,378.11) --
-	(280.34,380.93) --
-	(283.58,383.79);
+	(104.95,273.37) --
+	(107.98,274.60) --
+	(111.01,275.84) --
+	(114.03,277.11) --
+	(117.06,278.38) --
+	(120.09,279.67) --
+	(123.12,280.97) --
+	(126.14,282.28) --
+	(129.17,283.61) --
+	(132.20,284.96) --
+	(135.23,286.33) --
+	(138.25,287.72) --
+	(141.28,289.14) --
+	(144.31,290.58) --
+	(147.34,292.05) --
+	(150.36,293.53) --
+	(153.39,295.03) --
+	(156.42,296.54) --
+	(159.45,298.06) --
+	(162.48,299.61) --
+	(165.50,301.18) --
+	(168.53,302.77) --
+	(171.56,304.38) --
+	(174.59,306.03) --
+	(177.61,307.70) --
+	(180.64,309.41) --
+	(183.67,311.14) --
+	(186.70,312.89) --
+	(189.72,314.66) --
+	(192.75,316.45) --
+	(195.78,318.25) --
+	(198.81,320.09) --
+	(201.83,321.94) --
+	(204.86,323.83) --
+	(207.89,325.76) --
+	(210.92,327.71) --
+	(213.94,329.71) --
+	(216.97,331.74) --
+	(220.00,333.80) --
+	(223.03,335.89) --
+	(226.06,338.01) --
+	(229.08,340.16) --
+	(232.11,342.33) --
+	(235.14,344.54) --
+	(238.17,346.77) --
+	(241.19,349.04) --
+	(244.22,351.34) --
+	(247.25,353.67) --
+	(250.28,356.02) --
+	(253.30,358.41) --
+	(256.33,360.83) --
+	(259.36,363.28) --
+	(262.39,365.76) --
+	(265.41,368.27) --
+	(268.44,370.81) --
+	(271.47,373.38) --
+	(274.50,375.98) --
+	(277.52,378.61) --
+	(280.55,381.26) --
+	(283.58,383.95);
 \definecolor{fillColor}{RGB}{230,159,0}
@@
 
-\path[fill=fillColor] ( 35.86,253.77) --
-	( 39.22,247.94) --
-	( 32.49,247.94) --
-	cycle;
-
-\path[fill=fillColor] ( 44.40,256.26) --
-	( 47.76,250.43) --
-	( 41.03,250.43) --
-	cycle;
-
-\path[fill=fillColor] ( 52.94,258.86) --
-	( 56.30,253.03) --
-	( 49.58,253.03) --
-	cycle;
-
 \path[fill=fillColor] ( 61.48,261.57) --
@@
 
-\path[fill=fillColor] ( 70.02,264.40) --
-	( 73.39,258.57) --
-	( 66.66,258.57) --
-	cycle;
-
-\path[fill=fillColor] ( 78.57,267.34) --
-	( 81.93,261.52) --
-	( 75.20,261.52) --
-	cycle;
-
-\path[fill=fillColor] ( 87.11,270.42) --
-	( 90.47,264.59) --
-	( 83.75,264.59) --
-	cycle;
-
 \path[fill=fillColor] ( 95.65,273.63) --
@@
 
-\path[fill=fillColor] (104.19,276.97) --
-	(107.56,271.14) --
-	(100.83,271.14) --
-	cycle;
-
-\path[fill=fillColor] (112.74,280.44) --
-	(116.10,274.61) --
-	(109.37,274.61) --
-	cycle;
-
-\path[fill=fillColor] (121.28,284.03) --
-	(124.64,278.20) --
-	(117.91,278.20) --
-	cycle;
-
 \path[fill=fillColor] (129.82,287.78) --
@@
 
-\path[fill=fillColor] (138.36,291.67) --
-	(141.73,285.84) --
-	(135.00,285.84) --
-	cycle;
-
-\path[fill=fillColor] (146.90,295.72) --
-	(150.27,289.89) --
-	(143.54,289.89) --
-	cycle;
-
-\path[fill=fillColor] (155.45,299.91) --
-	(158.81,294.09) --
-	(152.08,294.09) --
-	cycle;
-
 \path[fill=fillColor] (163.99,304.26) --
@@
 
-\path[fill=fillColor] (172.53,308.81) --
-	(175.89,302.98) --
-	(169.17,302.98) --
-	cycle;
-
-\path[fill=fillColor] (181.07,313.60) --
-	(184.44,307.77) --
-	(177.71,307.77) --
-	cycle;
-
-\path[fill=fillColor] (189.62,318.53) --
-	(192.98,312.70) --
-	(186.25,312.70) --
-	cycle;
-
 \path[fill=fillColor] (198.16,323.63) --
@@
 
-\path[fill=fillColor] (206.70,328.95) --
-	(210.06,323.12) --
-	(203.34,323.12) --
-	cycle;
-
-\path[fill=fillColor] (215.24,334.48) --
-	(218.61,328.65) --
-	(211.88,328.65) --
-	cycle;
-
-\path[fill=fillColor] (223.78,340.26) --
-	(227.15,334.44) --
-	(220.42,334.44) --
-	cycle;
-
 \path[fill=fillColor] (232.33,346.20) --
@@
 
-\path[fill=fillColor] (240.87,352.35) --
-	(244.23,346.52) --
-	(237.51,346.52) --
-	cycle;
-
-\path[fill=fillColor] (249.41,358.83) --
-	(252.77,353.01) --
-	(246.05,353.01) --
-	cycle;
-
-\path[fill=fillColor] (257.95,365.61) --
-	(261.32,359.79) --
-	(254.59,359.79) --
-	cycle;
-
 \path[fill=fillColor] (266.50,372.59) --
@@
 	cycle;
-
-\path[fill=fillColor] (275.04,379.74) --
-	(278.40,373.92) --
-	(271.67,373.92) --
-	cycle;
-
-\path[fill=fillColor] (283.58,387.27) --
-	(286.94,381.45) --
-	(280.22,381.45) --
-	cycle;
 \definecolor{fillColor}{RGB}{86,180,233}
-
-\path[fill=fillColor] ( 24.82,245.00) --
-	( 29.81,245.00) --
-	( 29.81,249.99) --
-	( 24.82,249.99) --
-	cycle;
 
@@
 
-\path[fill=fillColor] ( 41.90,249.87) --
-	( 46.90,249.87) --
-	( 46.90,254.87) --
-	( 41.90,254.87) --
-	cycle;
-
-\path[fill=fillColor] ( 50.44,252.48) --
-	( 55.44,252.48) --
-	( 55.44,257.47) --
-	( 50.44,257.47) --
-	cycle;
-
-\path[fill=fillColor] ( 58.98,255.19) --
-	( 63.98,255.19) --
-	( 63.98,260.19) --
-	( 58.98,260.19) --
-	cycle;
-
 \path[fill=fillColor] ( 67.53,258.02) --
@@
 
-\path[fill=fillColor] ( 76.07,260.97) --
-	( 81.06,260.97) --
-	( 81.06,265.96) --
-	( 76.07,265.96) --
-	cycle;
-
-\path[fill=fillColor] ( 84.61,264.05) --
-	( 89.61,264.05) --
-	( 89.61,269.04) --
-	( 84.61,269.04) --
-	cycle;
-
-\path[fill=fillColor] ( 93.15,267.26) --
-	( 98.15,267.26) --
-	( 98.15,272.26) --
-	( 93.15,272.26) --
-	cycle;
-
 \path[fill=fillColor] (101.70,270.61) --
@@
 
-\path[fill=fillColor] (110.24,274.08) --
-	(115.23,274.08) --
-	(115.23,279.07) --
-	(110.24,279.07) --
-	cycle;
-
-\path[fill=fillColor] (118.78,277.67) --
-	(123.78,277.67) --
-	(123.78,282.67) --
-	(118.78,282.67) --
-	cycle;
-
-\path[fill=fillColor] (127.32,281.41) --
-	(132.32,281.41) --
-	(132.32,286.41) --
-	(127.32,286.41) --
-	cycle;
-
 \path[fill=fillColor] (135.86,285.30) --
@@
 
-\path[fill=fillColor] (144.41,289.34) --
-	(149.40,289.34) --
-	(149.40,294.33) --
-	(144.41,294.33) --
-	cycle;
-
-\path[fill=fillColor] (152.95,293.52) --
-	(157.94,293.52) --
-	(157.94,298.51) --
-	(152.95,298.51) --
-	cycle;
-
-\path[fill=fillColor] (161.49,297.83) --
-	(166.49,297.83) --
-	(166.49,302.82) --
-	(161.49,302.82) --
-	cycle;
-
 \path[fill=fillColor] (170.03,302.36) --
@@
 
-\path[fill=fillColor] (178.58,307.19) --
-	(183.57,307.19) --
-	(183.57,312.18) --
-	(178.58,312.18) --
-	cycle;
-
-\path[fill=fillColor] (187.12,312.12) --
-	(192.11,312.12) --
-	(192.11,317.12) --
-	(187.12,317.12) --
-	cycle;
-
-\path[fill=fillColor] (195.66,317.22) --
-	(200.66,317.22) --
-	(200.66,322.21) --
-	(195.66,322.21) --
-	cycle;
-
 \path[fill=fillColor] (204.20,322.52) --
@@
 
-\path[fill=fillColor] (212.74,328.07) --
-	(217.74,328.07) --
-	(217.74,333.06) --
-	(212.74,333.06) --
-	cycle;
-
-\path[fill=fillColor] (221.29,333.88) --
-	(226.28,333.88) --
-	(226.28,338.88) --
-	(221.29,338.88) --
-	cycle;
-
-\path[fill=fillColor] (229.83,339.76) --
-	(234.82,339.76) --
-	(234.82,344.75) --
-	(229.83,344.75) --
-	cycle;
-
 \path[fill=fillColor] (238.37,345.90) --
@@
 
-\path[fill=fillColor] (246.91,352.51) --
-	(251.91,352.51) --
-	(251.91,357.51) --
-	(246.91,357.51) --
-	cycle;
-
-\path[fill=fillColor] (255.46,359.41) --
-	(260.45,359.41) --
-	(260.45,364.40) --
-	(255.46,364.40) --
-	cycle;
-
-\path[fill=fillColor] (264.00,366.42) --
-	(268.99,366.42) --
-	(268.99,371.41) --
-	(264.00,371.41) --
-	cycle;
-
 \path[fill=fillColor] (272.54,373.53) --
@@
 
-\path[fill=fillColor] (281.08,381.15) --
-	(286.08,381.15) --
-	(286.08,386.15) --
-	(281.08,386.15) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78,247.50) -- ( 30.85,247.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31,243.96) -- ( 27.31,251.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32,249.88) -- ( 39.39,249.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86,246.35) -- ( 35.86,253.41);
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87,252.37) -- ( 47.93,252.37);
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41,254.97) -- ( 56.47,254.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94,251.44) -- ( 52.94,258.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95,257.69) -- ( 65.01,257.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48,254.15) -- ( 61.48,261.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.51) -- ( 73.56,260.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02,256.98) -- ( 70.02,264.05);
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,263.46) -- ( 82.10,263.46);
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.55) -- ( 90.64,266.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,263.02) -- ( 87.11,270.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.78) -- ( 99.18,269.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,266.24) -- ( 95.65,273.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,273.13) -- (107.73,273.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,269.60) -- (104.19,276.66);
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.59) -- (116.27,276.59);
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,280.19) -- (124.81,280.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.66) -- (121.28,283.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.92) -- (133.35,283.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.39) -- (129.82,287.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.81) -- (141.89,287.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,284.28) -- (138.36,291.35);
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.84) -- (150.44,291.84);
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,296.01) -- (158.98,296.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,292.47) -- (155.45,299.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.29) -- (167.52,300.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,296.75) -- (163.99,303.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.81) -- (176.06,304.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.27) -- (172.53,308.34);
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.66) -- (184.61,309.66);
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,314.61) -- (193.15,314.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.07) -- (189.62,318.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,319.70) -- (201.69,319.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,316.17) -- (198.16,323.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,324.99) -- (210.23,324.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,321.46) -- (206.70,328.52);
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.57) -- (218.77,330.57);
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,336.41) -- (227.32,336.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,332.88) -- (223.78,339.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,342.22) -- (235.86,342.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,338.69) -- (232.33,345.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,348.37) -- (244.40,348.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,344.84) -- (240.87,351.90);
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,355.17) -- (252.94,355.17);
@@
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,351.64) -- (249.41,358.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,362.17) -- (261.49,362.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,358.64) -- (257.95,365.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,369.21) -- (270.03,369.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,365.68) -- (266.50,372.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,376.31) -- (278.57,376.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,372.78) -- (275.04,379.84);
 
@@
 
-\path[fill=fillColor] ( 27.31,247.50) circle (  2.50);
-
-\path[fill=fillColor] ( 35.86,249.88) circle (  2.50);
-
-\path[fill=fillColor] ( 44.40,252.37) circle (  2.50);
-
-\path[fill=fillColor] ( 52.94,254.94) circle (  2.50);
-
-\path[fill=fillColor] ( 61.48,257.68) circle (  2.50);
-
-\path[fill=fillColor] ( 70.02,260.47) circle (  2.50);
-
-\path[fill=fillColor] ( 78.57,263.41) circle (  2.50);
+\path[fill=fillColor] ( 52.94,254.96) circle (  2.50);
 
@@
 
-\path[fill=fillColor] ( 95.65,269.65) circle (  2.50);
-
-\path[fill=fillColor] (104.19,273.00) circle (  2.50);
-
-\path[fill=fillColor] (112.74,276.42) circle (  2.50);
-
-\path[fill=fillColor] (121.28,279.99) circle (  2.50);
-
-\path[fill=fillColor] (129.82,283.76) circle (  2.50);
-
-\path[fill=fillColor] (138.36,287.74) circle (  2.50);
-
-\path[fill=fillColor] (146.90,291.70) circle (  2.50);
-
-\path[fill=fillColor] (155.45,296.03) circle (  2.50);
-
-\path[fill=fillColor] (163.99,300.46) circle (  2.50);
-
-\path[fill=fillColor] (172.53,304.98) circle (  2.50);
-
-\path[fill=fillColor] (181.07,309.73) circle (  2.50);
-
-\path[fill=fillColor] (189.62,314.62) circle (  2.50);
-
-\path[fill=fillColor] (198.16,319.79) circle (  2.50);
-
-\path[fill=fillColor] (206.70,324.93) circle (  2.50);
-
-\path[fill=fillColor] (215.24,330.66) circle (  2.50);
-
-\path[fill=fillColor] (223.78,336.18) circle (  2.50);
-
-\path[fill=fillColor] (232.33,342.09) circle (  2.50);
-
-\path[fill=fillColor] (240.87,348.75) circle (  2.50);
-
-\path[fill=fillColor] (249.41,355.20) circle (  2.50);
-
-\path[fill=fillColor] (257.95,361.58) circle (  2.50);
-
-\path[fill=fillColor] (266.50,368.62) circle (  2.50);
-
-\path[fill=fillColor] (275.04,375.76) circle (  2.50);
-
-\path[fill=fillColor] (283.58,383.22) circle (  2.50);
+\path[fill=fillColor] (121.28,280.09) circle (  2.50);
+
+\path[fill=fillColor] (155.45,296.05) circle (  2.50);
+
+\path[fill=fillColor] (189.62,314.74) circle (  2.50);
+
+\path[fill=fillColor] (223.78,336.55) circle (  2.50);
+
+\path[fill=fillColor] (257.95,361.93) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[fill=fillColor] ( 39.98,332.94) rectangle (168.41,407.25);
+\path[fill=fillColor] ( 31.06,332.94) rectangle (192.70,407.25);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 45.48,381.80) rectangle ( 59.93,396.25);
+\path[fill=fillColor] ( 36.56,381.80) rectangle ( 51.02,396.25);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.93,389.03) -- ( 58.49,389.03);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 38.01,389.03) -- ( 49.57,389.03);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 52.71,389.03) circle (  2.50);
+\path[fill=fillColor] ( 43.79,389.03) circle (  2.50);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 45.48,367.35) rectangle ( 59.93,381.80);
+\path[fill=fillColor] ( 36.56,367.35) rectangle ( 51.02,381.80);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 46.93,374.57) -- ( 58.49,374.57);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 38.01,374.57) -- ( 49.57,374.57);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 52.71,378.46) --
-	( 56.07,372.63) --
-	( 49.34,372.63) --
+\path[fill=fillColor] ( 43.79,378.46) --
+	( 47.15,372.63) --
+	( 40.43,372.63) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 45.48,352.89) rectangle ( 59.93,367.35);
+\path[fill=fillColor] ( 36.56,352.89) rectangle ( 51.02,367.35);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 46.93,360.12) -- ( 58.49,360.12);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 38.01,360.12) -- ( 49.57,360.12);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 50.21,357.62) --
-	( 55.20,357.62) --
-	( 55.20,362.62) --
-	( 50.21,362.62) --
+\path[fill=fillColor] ( 41.29,357.62) --
+	( 46.29,357.62) --
+	( 46.29,362.62) --
+	( 41.29,362.62) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 45.48,338.44) rectangle ( 59.93,352.89);
+\path[fill=fillColor] ( 36.56,338.44) rectangle ( 51.02,352.89);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 46.93,345.67) -- ( 58.49,345.67);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 38.01,345.67) -- ( 49.57,345.67);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.17,345.67) -- ( 56.24,345.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.71,342.13) -- ( 52.71,349.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.26,345.67) -- ( 47.32,345.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.79,342.13) -- ( 43.79,349.20);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 65.43,386.00) {Generation interval};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,386.00) {Intrinsic generation interval};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 65.43,371.54) {Serial interval ($\rho=0.5$)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,371.54) {Forward serial interval ($\rho=0.5$)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 65.43,357.09) {Serial interval ($\rho=0$)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,357.09) {Forward serial interval ($\rho=0$)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 65.43,342.63) {Serial interval ($\rho=-0.5$)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,342.63) {Forward serial interval ($\rho=-0.5$)};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (316.39,247.65) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] (316.39,247.64) --
 	(319.64,248.49) --
@@
 	(329.37,251.16) --
-	(332.61,252.08) --
+	(332.61,252.09) --
 	(335.86,253.03) --
 	(339.10,254.00) --
-	(342.34,254.98) --
-	(345.59,255.98) --
-	(348.83,257.00) --
-	(352.08,258.04) --
-	(355.32,259.10) --
-	(358.56,260.18) --
-	(361.81,261.28) --
-	(365.05,262.40) --
-	(368.30,263.54) --
-	(371.54,264.70) --
-	(374.78,265.88) --
-	(378.03,267.07) --
-	(381.27,268.29) --
-	(384.51,269.52) --
-	(387.76,270.77) --
-	(391.00,272.04) --
-	(394.25,273.32) --
-	(397.49,274.63) --
-	(400.73,275.96) --
-	(403.98,277.31) --
-	(407.22,278.68) --
-	(410.47,280.08) --
-	(413.71,281.49) --
-	(416.95,282.93) --
-	(420.20,284.38) --
-	(423.44,285.85) --
-	(426.69,287.34) --
-	(429.93,288.85) --
-	(433.17,290.39) --
-	(436.42,291.96) --
-	(439.66,293.55) --
-	(442.90,295.17) --
-	(446.15,296.82) --
-	(449.39,298.48) --
-	(452.64,300.17) --
-	(455.88,301.88) --
-	(459.12,303.61) --
-	(462.37,305.37) --
-	(465.61,307.15) --
-	(468.86,308.96) --
-	(472.10,310.80) --
-	(475.34,312.67) --
-	(478.59,314.58) --
-	(481.83,316.51) --
-	(485.08,318.47) --
-	(488.32,320.46) --
-	(491.56,322.47) --
-	(494.81,324.51) --
-	(498.05,326.58) --
-	(501.29,328.68) --
-	(504.54,330.81) --
-	(507.78,332.98) --
-	(511.03,335.19) --
-	(514.27,337.43) --
-	(517.51,339.70) --
-	(520.76,342.00) --
-	(524.00,344.33) --
-	(527.25,346.69) --
-	(530.49,349.09) --
-	(533.73,351.51) --
-	(536.98,353.97) --
-	(540.22,356.45) --
-	(543.47,358.97) --
-	(546.71,361.52) --
-	(549.95,364.10) --
-	(553.20,366.72) --
-	(556.44,369.36) --
-	(559.68,372.04) --
-	(562.93,374.75) --
-	(566.17,377.49) --
-	(569.42,380.26) --
-	(572.66,383.06);
-\definecolor{drawColor}{RGB}{230,159,0}
+	(342.34,254.99) --
+	(345.59,255.99) --
+	(348.83,257.01) --
+	(352.08,258.06) --
+	(355.32,259.12) --
+	(358.56,260.20) --
+	(361.81,261.30) --
+	(365.05,262.42) --
+	(368.30,263.56) --
+	(371.54,264.72) --
+	(374.78,265.90) --
+	(378.03,267.10) --
+	(381.27,268.32) --
+	(384.51,269.55) --
+	(387.76,270.81) --
+	(391.00,272.08) --
+	(394.25,273.37) --
+	(397.49,274.68) --
+	(400.73,276.01) --
+	(403.98,277.36) --
+	(407.22,278.74) --
+	(410.47,280.13) --
+	(413.71,281.55) --
+	(416.95,282.99) --
+	(420.20,284.44) --
+	(423.44,285.91) --
+	(426.69,287.40) --
+	(429.93,288.91) --
+	(433.17,290.45) --
+	(436.42,292.02) --
+	(439.66,293.61) --
+	(442.90,295.23) --
+	(446.15,296.88) --
+	(449.39,298.55) --
+	(452.64,300.24) --
+	(455.88,301.95) --
+	(459.12,303.68) --
+	(462.37,305.44) --
+	(465.61,307.23) --
+	(468.86,309.04) --
+	(472.10,310.89) --
+	(475.34,312.76) --
+	(478.59,314.68) --
+	(481.83,316.62) --
+	(485.08,318.59) --
+	(488.32,320.58) --
+	(491.56,322.60) --
+	(494.81,324.66) --
+	(498.05,326.74) --
+	(501.29,328.85) --
+	(504.54,330.99) --
+	(507.78,333.17) --
+	(511.03,335.39) --
+	(514.27,337.63) --
+	(517.51,339.91) --
+	(520.76,342.22) --
+	(524.00,344.56) --
+	(527.25,346.93) --
+	(530.49,349.33) --
+	(533.73,351.76) --
+	(536.98,354.22) --
+	(540.22,356.72) --
+	(543.47,359.24) --
+	(546.71,361.80) --
+	(549.95,364.38) --
+	(553.20,367.00) --
+	(556.44,369.66) --
+	(559.68,372.34) --
+	(562.93,375.05) --
+	(566.17,377.80) --
+	(569.42,380.57) --
+	(572.66,383.38);
+\definecolor{drawColor}{RGB}{0,158,115}
 
@@
 	(572.66,328.50);
-\definecolor{drawColor}{RGB}{86,180,233}
+\definecolor{drawColor}{RGB}{240,228,66}
 
@@
 	(572.66,294.80);
-\definecolor{drawColor}{RGB}{0,158,115}
+\definecolor{drawColor}{RGB}{0,114,178}
 
@@
 	(572.66,271.57);
-\definecolor{fillColor}{RGB}{230,159,0}
+\definecolor{fillColor}{RGB}{0,158,115}
 
@@
 	cycle;
-\definecolor{fillColor}{RGB}{86,180,233}
+\definecolor{fillColor}{RGB}{240,228,66}
 
@@
 
-\path[fill=fillColor] (333.48,252.36) circle (  2.50);
+\path[fill=fillColor] (333.48,252.37) circle (  2.50);
 
@@
 
-\path[fill=fillColor] (350.56,257.65) circle (  2.50);
-
-\path[fill=fillColor] (359.10,260.48) circle (  2.50);
-
-\path[fill=fillColor] (367.65,263.42) circle (  2.50);
-
-\path[fill=fillColor] (376.19,266.48) circle (  2.50);
-
-\path[fill=fillColor] (384.73,269.65) circle (  2.50);
-
-\path[fill=fillColor] (393.27,273.04) circle (  2.50);
-
-\path[fill=fillColor] (401.82,276.42) circle (  2.50);
-
-\path[fill=fillColor] (410.36,280.04) circle (  2.50);
-
-\path[fill=fillColor] (418.90,283.76) circle (  2.50);
-
-\path[fill=fillColor] (427.44,287.65) circle (  2.50);
-
-\path[fill=fillColor] (435.98,291.72) circle (  2.50);
+\path[fill=fillColor] (350.56,257.67) circle (  2.50);
+
+\path[fill=fillColor] (359.10,260.49) circle (  2.50);
+
+\path[fill=fillColor] (367.65,263.43) circle (  2.50);
+
+\path[fill=fillColor] (376.19,266.50) circle (  2.50);
+
+\path[fill=fillColor] (384.73,269.69) circle (  2.50);
+
+\path[fill=fillColor] (393.27,273.02) circle (  2.50);
+
+\path[fill=fillColor] (401.82,276.48) circle (  2.50);
+
+\path[fill=fillColor] (410.36,280.09) circle (  2.50);
+
+\path[fill=fillColor] (418.90,283.85) circle (  2.50);
+
+\path[fill=fillColor] (427.44,287.76) circle (  2.50);
+
+\path[fill=fillColor] (435.98,291.82) circle (  2.50);
 
@@
 
-\path[fill=fillColor] (453.07,300.28) circle (  2.50);
-
-\path[fill=fillColor] (461.61,305.03) circle (  2.50);
-
-\path[fill=fillColor] (470.15,309.81) circle (  2.50);
-
-\path[fill=fillColor] (478.70,314.71) circle (  2.50);
-
-\path[fill=fillColor] (487.24,319.74) circle (  2.50);
-
-\path[fill=fillColor] (495.78,324.97) circle (  2.50);
-
-\path[fill=fillColor] (504.32,330.80) circle (  2.50);
-
-\path[fill=fillColor] (512.86,336.10) circle (  2.50);
-
-\path[fill=fillColor] (521.41,342.50) circle (  2.50);
-
-\path[fill=fillColor] (529.95,348.19) circle (  2.50);
-
-\path[fill=fillColor] (538.49,354.89) circle (  2.50);
-
-\path[fill=fillColor] (547.03,361.68) circle (  2.50);
-
-\path[fill=fillColor] (555.58,368.79) circle (  2.50);
-
-\path[fill=fillColor] (564.12,375.90) circle (  2.50);
-
-\path[fill=fillColor] (572.66,383.19) circle (  2.50);
+\path[fill=fillColor] (453.07,300.46) circle (  2.50);
+
+\path[fill=fillColor] (461.61,305.04) circle (  2.50);
+
+\path[fill=fillColor] (470.15,309.80) circle (  2.50);
+
+\path[fill=fillColor] (478.70,314.74) circle (  2.50);
+
+\path[fill=fillColor] (487.24,319.89) circle (  2.50);
+
+\path[fill=fillColor] (495.78,325.23) circle (  2.50);
+
+\path[fill=fillColor] (504.32,330.79) circle (  2.50);
+
+\path[fill=fillColor] (512.86,336.55) circle (  2.50);
+
+\path[fill=fillColor] (521.41,342.55) circle (  2.50);
+
+\path[fill=fillColor] (529.95,348.77) circle (  2.50);
+
+\path[fill=fillColor] (538.49,355.23) circle (  2.50);
+
+\path[fill=fillColor] (547.03,361.93) circle (  2.50);
+
+\path[fill=fillColor] (555.58,368.89) circle (  2.50);
+
+\path[fill=fillColor] (564.12,376.12) circle (  2.50);
+
+\path[fill=fillColor] (572.66,383.61) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,329.23) {Naive reproduction number ${\mathcal R}_{\textrm{\tiny naive}}$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,329.23) {Reproduction number ${\mathcal R}_{\textrm{\tiny intrinsic}}$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (320.07,332.94) rectangle (481.85,407.25);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (325.57,381.80) rectangle (340.02,396.25);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (327.01,389.03) -- (338.58,389.03);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (332.80,389.03) circle (  2.50);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (325.57,367.35) rectangle (340.02,381.80);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,158,115}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (327.01,374.57) -- (338.58,374.57);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{0,158,115}
+
+\path[fill=fillColor] (332.80,378.46) --
+	(336.16,372.63) --
+	(329.43,372.63) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (325.57,352.89) rectangle (340.02,367.35);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (327.01,360.12) -- (338.58,360.12);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{240,228,66}
+
+\path[fill=fillColor] (330.30,357.62) --
+	(335.29,357.62) --
+	(335.29,362.62) --
+	(330.30,362.62) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (325.57,338.44) rectangle (340.02,352.89);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,114,178}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (327.01,345.67) -- (338.58,345.67);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,114,178}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.26,345.67) -- (336.33,345.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (332.80,342.13) -- (332.80,349.20);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,386.00) {Intrinsic generation interval};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,371.54) {Intrinsic serial interval ($\rho=0.5$)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,357.09) {Intrinsic serial interval ($\rho=0$)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,342.63) {Intrinsic serial interval ($\rho=-0.5$)};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 54.39) --
-	( 30.56, 54.42) --
-	( 33.80, 54.45) --
-	( 37.04, 54.47) --
-	( 40.29, 54.50) --
-	( 43.53, 54.52) --
-	( 46.78, 54.54) --
-	( 50.02, 54.56) --
-	( 53.26, 54.58) --
-	( 56.51, 54.59) --
-	( 59.75, 54.61) --
-	( 63.00, 54.62) --
-	( 66.24, 54.63) --
-	( 69.48, 54.64) --
-	( 72.73, 54.65) --
-	( 75.97, 54.66) --
-	( 79.22, 54.66) --
-	( 82.46, 54.67) --
-	( 85.70, 54.68) --
-	( 88.95, 54.68) --
-	( 92.19, 54.68) --
-	( 95.43, 54.68) --
-	( 98.68, 54.67) --
-	(101.92, 54.67) --
-	(105.17, 54.66) --
-	(108.41, 54.65) --
-	(111.65, 54.64) --
-	(114.90, 54.63) --
-	(118.14, 54.63) --
-	(121.39, 54.63) --
-	(124.63, 54.64) --
-	(127.87, 54.65) --
-	(131.12, 54.66) --
-	(134.36, 54.67) --
-	(137.61, 54.69) --
-	(140.85, 54.71) --
-	(144.09, 54.72) --
-	(147.34, 54.74) --
-	(150.58, 54.75) --
-	(153.82, 54.76) --
-	(157.07, 54.76) --
-	(160.31, 54.76) --
-	(163.56, 54.76) --
-	(166.80, 54.76) --
-	(170.04, 54.76) --
-	(173.29, 54.76) --
-	(176.53, 54.76) --
-	(179.78, 54.76) --
-	(183.02, 54.75) --
-	(186.26, 54.75) --
-	(189.51, 54.75) --
-	(192.75, 54.75) --
-	(196.00, 54.75) --
-	(199.24, 54.74) --
-	(202.48, 54.74) --
-	(205.73, 54.74) --
-	(208.97, 54.74) --
-	(212.21, 54.73) --
-	(215.46, 54.73) --
-	(218.70, 54.73) --
-	(221.95, 54.73) --
-	(225.19, 54.73) --
-	(228.43, 54.72) --
-	(231.68, 54.72) --
-	(234.92, 54.72) --
-	(238.17, 54.72) --
-	(241.41, 54.71) --
-	(244.65, 54.71) --
-	(247.90, 54.71) --
-	(251.14, 54.71) --
-	(254.39, 54.70) --
-	(257.63, 54.70) --
-	(260.87, 54.70) --
-	(264.12, 54.70) --
-	(267.36, 54.70) --
-	(270.60, 54.70) --
-	(273.85, 54.70) --
-	(277.09, 54.70) --
-	(280.34, 54.70) --
-	(283.58, 54.70);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 54.98) --
+	( 30.56, 54.98) --
+	( 33.80, 54.98) --
+	( 37.04, 54.98) --
+	( 40.29, 54.98) --
+	( 43.53, 54.98) --
+	( 46.78, 54.98) --
+	( 50.02, 54.98) --
+	( 53.26, 54.98) --
+	( 56.51, 54.98) --
+	( 59.75, 54.98) --
+	( 63.00, 54.98) --
+	( 66.24, 54.98) --
+	( 69.48, 54.98) --
+	( 72.73, 54.98) --
+	( 75.97, 54.98) --
+	( 79.22, 54.98) --
+	( 82.46, 54.98) --
+	( 85.70, 54.98) --
+	( 88.95, 54.98) --
+	( 92.19, 54.98) --
+	( 95.43, 54.98) --
+	( 98.68, 54.98) --
+	(101.92, 54.98) --
+	(105.17, 54.98) --
+	(108.41, 54.98) --
+	(111.65, 54.98) --
+	(114.90, 54.98) --
+	(118.14, 54.98) --
+	(121.39, 54.98) --
+	(124.63, 54.98) --
+	(127.87, 54.98) --
+	(131.12, 54.98) --
+	(134.36, 54.98) --
+	(137.61, 54.98) --
+	(140.85, 54.98) --
+	(144.09, 54.98) --
+	(147.34, 54.98) --
+	(150.58, 54.98) --
+	(153.82, 54.98) --
+	(157.07, 54.98) --
+	(160.31, 54.98) --
+	(163.56, 54.98) --
+	(166.80, 54.98) --
+	(170.04, 54.98) --
+	(173.29, 54.98) --
+	(176.53, 54.98) --
+	(179.78, 54.98) --
+	(183.02, 54.98) --
+	(186.26, 54.98) --
+	(189.51, 54.98) --
+	(192.75, 54.98) --
+	(196.00, 54.98) --
+	(199.24, 54.98) --
+	(202.48, 54.98) --
+	(205.73, 54.98) --
+	(208.97, 54.98) --
+	(212.21, 54.98) --
+	(215.46, 54.98) --
+	(218.70, 54.98) --
+	(221.95, 54.98) --
+	(225.19, 54.98) --
+	(228.43, 54.98) --
+	(231.68, 54.98) --
+	(234.92, 54.98) --
+	(238.17, 54.98) --
+	(241.41, 54.98) --
+	(244.65, 54.98) --
+	(247.90, 54.98) --
+	(251.14, 54.98) --
+	(254.39, 54.98) --
+	(257.63, 54.98) --
+	(260.87, 54.98) --
+	(264.12, 54.98) --
+	(267.36, 54.98) --
+	(270.60, 54.98) --
+	(273.85, 54.98) --
+	(277.09, 54.98) --
+	(280.34, 54.98) --
+	(283.58, 54.98);
 \definecolor{drawColor}{RGB}{230,159,0}
@@
 
-\path[fill=fillColor] ( 27.31, 53.74) circle (  2.50);
-
-\path[fill=fillColor] ( 35.86, 54.86) circle (  2.50);
-
-\path[fill=fillColor] ( 44.40, 54.88) circle (  2.50);
-
-\path[fill=fillColor] ( 52.94, 53.99) circle (  2.50);
-
-\path[fill=fillColor] ( 61.48, 55.34) circle (  2.50);
-
-\path[fill=fillColor] ( 70.02, 54.65) circle (  2.50);
-
-\path[fill=fillColor] ( 78.57, 54.68) circle (  2.50);
-
-\path[fill=fillColor] ( 87.11, 55.24) circle (  2.50);
-
-\path[fill=fillColor] ( 95.65, 54.54) circle (  2.50);
-
-\path[fill=fillColor] (104.19, 54.90) circle (  2.50);
-
-\path[fill=fillColor] (112.74, 54.54) circle (  2.50);
-
-\path[fill=fillColor] (121.28, 54.06) circle (  2.50);
-
-\path[fill=fillColor] (129.82, 54.15) circle (  2.50);
-
-\path[fill=fillColor] (138.36, 55.07) circle (  2.50);
-
-\path[fill=fillColor] (146.90, 54.49) circle (  2.50);
-
-\path[fill=fillColor] (155.45, 55.12) circle (  2.50);
-
-\path[fill=fillColor] (163.99, 55.17) circle (  2.50);
-
-\path[fill=fillColor] (172.53, 54.90) circle (  2.50);
-
-\path[fill=fillColor] (181.07, 54.75) circle (  2.50);
-
-\path[fill=fillColor] (189.62, 54.64) circle (  2.50);
-
-\path[fill=fillColor] (198.16, 54.75) circle (  2.50);
-
-\path[fill=fillColor] (206.70, 54.31) circle (  2.50);
-
-\path[fill=fillColor] (215.24, 54.85) circle (  2.50);
-
-\path[fill=fillColor] (223.78, 54.36) circle (  2.50);
-
-\path[fill=fillColor] (232.33, 54.41) circle (  2.50);
-
-\path[fill=fillColor] (240.87, 54.96) circle (  2.50);
-
-\path[fill=fillColor] (249.41, 55.07) circle (  2.50);
-
-\path[fill=fillColor] (257.95, 54.79) circle (  2.50);
-
-\path[fill=fillColor] (266.50, 55.03) circle (  2.50);
-
-\path[fill=fillColor] (275.04, 54.59) circle (  2.50);
-
-\path[fill=fillColor] (283.58, 54.42) circle (  2.50);
+\path[fill=fillColor] ( 27.31, 54.98) circle (  2.50);
+
+\path[fill=fillColor] ( 35.86, 54.98) circle (  2.50);
+
+\path[fill=fillColor] ( 44.40, 54.98) circle (  2.50);
+
+\path[fill=fillColor] ( 52.94, 54.98) circle (  2.50);
+
+\path[fill=fillColor] ( 61.48, 54.98) circle (  2.50);
+
+\path[fill=fillColor] ( 70.02, 54.98) circle (  2.50);
+
+\path[fill=fillColor] ( 78.57, 54.98) circle (  2.50);
+
+\path[fill=fillColor] ( 87.11, 54.98) circle (  2.50);
+
+\path[fill=fillColor] ( 95.65, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (104.19, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (112.74, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (121.28, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (129.82, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (138.36, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (146.90, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (155.45, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (163.99, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (172.53, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (181.07, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (189.62, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (198.16, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (206.70, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (215.24, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (223.78, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (232.33, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (240.87, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (249.41, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (257.95, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (266.50, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (275.04, 54.98) circle (  2.50);
+
+\path[fill=fillColor] (283.58, 54.98) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,112.42) {Mean generation/serial interval};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,112.42) {Mean interval (days)};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (323.24, 68.09) --
-	(326.39, 68.10) --
-	(329.55, 68.10) --
-	(332.71, 68.11) --
-	(335.87, 68.12) --
-	(339.02, 68.12) --
-	(342.18, 68.13) --
-	(345.34, 68.14) --
-	(348.49, 68.14) --
-	(351.65, 68.14) --
-	(354.81, 68.15) --
-	(357.97, 68.15) --
-	(361.12, 68.15) --
-	(364.28, 68.16) --
-	(367.44, 68.16) --
-	(370.60, 68.16) --
-	(373.75, 68.16) --
-	(376.91, 68.16) --
-	(380.07, 68.16) --
-	(383.22, 68.16) --
-	(386.38, 68.16) --
-	(389.54, 68.16) --
-	(392.70, 68.16) --
-	(395.85, 68.16) --
-	(399.01, 68.16) --
-	(402.17, 68.16) --
-	(405.32, 68.15) --
-	(408.48, 68.15) --
-	(411.64, 68.15) --
-	(414.80, 68.14) --
-	(417.95, 68.13) --
-	(421.11, 68.12) --
-	(424.27, 68.11) --
-	(427.43, 68.09) --
-	(430.58, 68.08) --
-	(433.74, 68.06) --
-	(436.90, 68.04) --
-	(440.05, 68.03) --
-	(443.21, 68.02) --
-	(446.37, 68.01) --
-	(449.53, 68.01) --
-	(452.68, 68.01) --
-	(455.84, 68.01) --
-	(459.00, 68.02) --
-	(462.16, 68.02) --
-	(465.31, 68.03) --
-	(468.47, 68.04) --
-	(471.63, 68.04) --
-	(474.78, 68.05) --
-	(477.94, 68.06) --
-	(481.10, 68.06) --
-	(484.26, 68.07) --
-	(487.41, 68.08) --
-	(490.57, 68.09) --
-	(493.73, 68.10) --
-	(496.89, 68.11) --
-	(500.04, 68.12) --
-	(503.20, 68.13) --
-	(506.36, 68.13) --
-	(509.51, 68.14) --
-	(512.67, 68.14) --
-	(515.83, 68.15) --
-	(518.99, 68.15) --
-	(522.14, 68.15) --
-	(525.30, 68.15) --
-	(528.46, 68.15) --
-	(531.62, 68.14) --
-	(534.77, 68.14) --
-	(537.93, 68.14) --
-	(541.09, 68.14) --
-	(544.24, 68.13) --
-	(547.40, 68.12) --
-	(550.56, 68.12) --
-	(553.72, 68.11) --
-	(556.87, 68.10) --
-	(560.03, 68.08) --
-	(563.19, 68.07) --
-	(566.35, 68.06) --
-	(569.50, 68.04) --
-	(572.66, 68.03);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (323.24, 58.94) --
+	(326.39, 58.94) --
+	(329.55, 58.94) --
+	(332.71, 58.94) --
+	(335.87, 58.94) --
+	(339.02, 58.94) --
+	(342.18, 58.94) --
+	(345.34, 58.94) --
+	(348.49, 58.94) --
+	(351.65, 58.94) --
+	(354.81, 58.94) --
+	(357.97, 58.94) --
+	(361.12, 58.94) --
+	(364.28, 58.94) --
+	(367.44, 58.94) --
+	(370.60, 58.94) --
+	(373.75, 58.94) --
+	(376.91, 58.94) --
+	(380.07, 58.94) --
+	(383.22, 58.94) --
+	(386.38, 58.94) --
+	(389.54, 58.94) --
+	(392.70, 58.94) --
+	(395.85, 58.94) --
+	(399.01, 58.94) --
+	(402.17, 58.94) --
+	(405.32, 58.94) --
+	(408.48, 58.94) --
+	(411.64, 58.94) --
+	(414.80, 58.94) --
+	(417.95, 58.94) --
+	(421.11, 58.94) --
+	(424.27, 58.94) --
+	(427.43, 58.94) --
+	(430.58, 58.94) --
+	(433.74, 58.94) --
+	(436.90, 58.94) --
+	(440.05, 58.94) --
+	(443.21, 58.94) --
+	(446.37, 58.94) --
+	(449.53, 58.94) --
+	(452.68, 58.94) --
+	(455.84, 58.94) --
+	(459.00, 58.94) --
+	(462.16, 58.94) --
+	(465.31, 58.94) --
+	(468.47, 58.94) --
+	(471.63, 58.94) --
+	(474.78, 58.94) --
+	(477.94, 58.94) --
+	(481.10, 58.94) --
+	(484.26, 58.94) --
+	(487.41, 58.94) --
+	(490.57, 58.94) --
+	(493.73, 58.94) --
+	(496.89, 58.94) --
+	(500.04, 58.94) --
+	(503.20, 58.94) --
+	(506.36, 58.94) --
+	(509.51, 58.94) --
+	(512.67, 58.94) --
+	(515.83, 58.94) --
+	(518.99, 58.94) --
+	(522.14, 58.94) --
+	(525.30, 58.94) --
+	(528.46, 58.94) --
+	(531.62, 58.94) --
+	(534.77, 58.94) --
+	(537.93, 58.94) --
+	(541.09, 58.94) --
+	(544.24, 58.94) --
+	(547.40, 58.94) --
+	(550.56, 58.94) --
+	(553.72, 58.94) --
+	(556.87, 58.94) --
+	(560.03, 58.94) --
+	(563.19, 58.94) --
+	(566.35, 58.94) --
+	(569.50, 58.94) --
+	(572.66, 58.94);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24,142.26) --
-	(326.39,141.25) --
-	(329.55,140.26) --
-	(332.71,139.28) --
-	(335.87,138.32) --
-	(339.02,137.38) --
-	(342.18,136.45) --
-	(345.34,135.55) --
-	(348.49,134.65) --
-	(351.65,133.78) --
-	(354.81,132.92) --
-	(357.97,132.09) --
-	(361.12,131.26) --
-	(364.28,130.46) --
-	(367.44,129.67) --
-	(370.60,128.90) --
-	(373.75,128.14) --
-	(376.91,127.40) --
-	(380.07,126.68) --
-	(383.22,125.97) --
-	(386.38,125.28) --
-	(389.54,124.61) --
-	(392.70,123.97) --
-	(395.85,123.34) --
-	(399.01,122.73) --
-	(402.17,122.13) --
-	(405.32,121.55) --
-	(408.48,120.98) --
-	(411.64,120.42) --
-	(414.80,119.87) --
-	(417.95,119.34) --
-	(421.11,118.83) --
-	(424.27,118.34) --
-	(427.43,117.87) --
-	(430.58,117.41) --
-	(433.74,116.96) --
-	(436.90,116.52) --
-	(440.05,116.09) --
-	(443.21,115.65) --
-	(446.37,115.22) --
-	(449.53,114.78) --
-	(452.68,114.36) --
-	(455.84,113.94) --
-	(459.00,113.54) --
-	(462.16,113.14) --
-	(465.31,112.75) --
-	(468.47,112.37) --
-	(471.63,111.99) --
-	(474.78,111.61) --
-	(477.94,111.24) --
-	(481.10,110.87) --
-	(484.26,110.49) --
-	(487.41,110.13) --
-	(490.57,109.77) --
-	(493.73,109.41) --
-	(496.89,109.06) --
-	(500.04,108.71) --
-	(503.20,108.37) --
-	(506.36,108.03) --
-	(509.51,107.70) --
-	(512.67,107.37) --
-	(515.83,107.04) --
-	(518.99,106.72) --
-	(522.14,106.40) --
-	(525.30,106.09) --
-	(528.46,105.78) --
-	(531.62,105.48) --
-	(534.77,105.18) --
-	(537.93,104.88) --
-	(541.09,104.59) --
-	(544.24,104.31) --
-	(547.40,104.03) --
-	(550.56,103.75) --
-	(553.72,103.48) --
-	(556.87,103.21) --
-	(560.03,102.94) --
-	(563.19,102.69) --
-	(566.35,102.43) --
-	(569.50,102.18) --
-	(572.66,101.93);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24,115.70) --
+	(326.39,114.93) --
+	(329.55,114.17) --
+	(332.71,113.43) --
+	(335.87,112.70) --
+	(339.02,111.98) --
+	(342.18,111.27) --
+	(345.34,110.58) --
+	(348.49,109.90) --
+	(351.65,109.23) --
+	(354.81,108.58) --
+	(357.97,107.94) --
+	(361.12,107.32) --
+	(364.28,106.70) --
+	(367.44,106.10) --
+	(370.60,105.51) --
+	(373.75,104.94) --
+	(376.91,104.37) --
+	(380.07,103.82) --
+	(383.22,103.28) --
+	(386.38,102.76) --
+	(389.54,102.25) --
+	(392.70,101.76) --
+	(395.85,101.28) --
+	(399.01,100.81) --
+	(402.17,100.36) --
+	(405.32, 99.92) --
+	(408.48, 99.48) --
+	(411.64, 99.06) --
+	(414.80, 98.64) --
+	(417.95, 98.23) --
+	(421.11, 97.85) --
+	(424.27, 97.47) --
+	(427.43, 97.11) --
+	(430.58, 96.76) --
+	(433.74, 96.42) --
+	(436.90, 96.09) --
+	(440.05, 95.75) --
+	(443.21, 95.42) --
+	(446.37, 95.09) --
+	(449.53, 94.76) --
+	(452.68, 94.43) --
+	(455.84, 94.12) --
+	(459.00, 93.81) --
+	(462.16, 93.51) --
+	(465.31, 93.21) --
+	(468.47, 92.92) --
+	(471.63, 92.63) --
+	(474.78, 92.34) --
+	(477.94, 92.06) --
+	(481.10, 91.77) --
+	(484.26, 91.49) --
+	(487.41, 91.21) --
+	(490.57, 90.94) --
+	(493.73, 90.67) --
+	(496.89, 90.40) --
+	(500.04, 90.13) --
+	(503.20, 89.87) --
+	(506.36, 89.61) --
+	(509.51, 89.36) --
+	(512.67, 89.11) --
+	(515.83, 88.86) --
+	(518.99, 88.61) --
+	(522.14, 88.37) --
+	(525.30, 88.13) --
+	(528.46, 87.90) --
+	(531.62, 87.67) --
+	(534.77, 87.44) --
+	(537.93, 87.22) --
+	(541.09, 87.00) --
+	(544.24, 86.78) --
+	(547.40, 86.56) --
+	(550.56, 86.35) --
+	(553.72, 86.14) --
+	(556.87, 85.94) --
+	(560.03, 85.74) --
+	(563.19, 85.54) --
+	(566.35, 85.35) --
+	(569.50, 85.16) --
+	(572.66, 84.97);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,186.85) --
-	(326.39,184.91) --
-	(329.55,183.00) --
-	(332.71,181.13) --
-	(335.87,179.29) --
-	(339.02,177.48) --
-	(342.18,175.71) --
-	(345.34,173.98) --
-	(348.49,172.28) --
-	(351.65,170.62) --
-	(354.81,168.99) --
-	(357.97,167.40) --
-	(361.12,165.84) --
-	(364.28,164.32) --
-	(367.44,162.83) --
-	(370.60,161.37) --
-	(373.75,159.95) --
-	(376.91,158.56) --
-	(380.07,157.20) --
-	(383.22,155.87) --
-	(386.38,154.59) --
-	(389.54,153.35) --
-	(392.70,152.15) --
-	(395.85,150.99) --
-	(399.01,149.87) --
-	(402.17,148.77) --
-	(405.32,147.71) --
-	(408.48,146.66) --
-	(411.64,145.64) --
-	(414.80,144.64) --
-	(417.95,143.67) --
-	(421.11,142.74) --
-	(424.27,141.86) --
-	(427.43,141.01) --
-	(430.58,140.19) --
-	(433.74,139.39) --
-	(436.90,138.60) --
-	(440.05,137.83) --
-	(443.21,137.06) --
-	(446.37,136.28) --
-	(449.53,135.51) --
-	(452.68,134.75) --
-	(455.84,134.01) --
-	(459.00,133.30) --
-	(462.16,132.60) --
-	(465.31,131.92) --
-	(468.47,131.24) --
-	(471.63,130.58) --
-	(474.78,129.92) --
-	(477.94,129.27) --
-	(481.10,128.62) --
-	(484.26,127.97) --
-	(487.41,127.33) --
-	(490.57,126.70) --
-	(493.73,126.09) --
-	(496.89,125.48) --
-	(500.04,124.89) --
-	(503.20,124.30) --
-	(506.36,123.72) --
-	(509.51,123.14) --
-	(512.67,122.58) --
-	(515.83,122.02) --
-	(518.99,121.47) --
-	(522.14,120.93) --
-	(525.30,120.40) --
-	(528.46,119.87) --
-	(531.62,119.36) --
-	(534.77,118.86) --
-	(537.93,118.36) --
-	(541.09,117.87) --
-	(544.24,117.39) --
-	(547.40,116.92) --
-	(550.56,116.46) --
-	(553.72,116.00) --
-	(556.87,115.56) --
-	(560.03,115.12) --
-	(563.19,114.69) --
-	(566.35,114.27) --
-	(569.50,113.86) --
-	(572.66,113.46);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,149.67) --
+	(326.39,148.19) --
+	(329.55,146.73) --
+	(332.71,145.31) --
+	(335.87,143.91) --
+	(339.02,142.53) --
+	(342.18,141.18) --
+	(345.34,139.86) --
+	(348.49,138.57) --
+	(351.65,137.30) --
+	(354.81,136.06) --
+	(357.97,134.85) --
+	(361.12,133.66) --
+	(364.28,132.50) --
+	(367.44,131.37) --
+	(370.60,130.26) --
+	(373.75,129.17) --
+	(376.91,128.11) --
+	(380.07,127.07) --
+	(383.22,126.06) --
+	(386.38,125.09) --
+	(389.54,124.14) --
+	(392.70,123.23) --
+	(395.85,122.35) --
+	(399.01,121.49) --
+	(402.17,120.66) --
+	(405.32,119.84) --
+	(408.48,119.05) --
+	(411.64,118.27) --
+	(414.80,117.51) --
+	(417.95,116.77) --
+	(421.11,116.06) --
+	(424.27,115.39) --
+	(427.43,114.74) --
+	(430.58,114.12) --
+	(433.74,113.51) --
+	(436.90,112.91) --
+	(440.05,112.32) --
+	(443.21,111.73) --
+	(446.37,111.14) --
+	(449.53,110.55) --
+	(452.68,109.97) --
+	(455.84,109.41) --
+	(459.00,108.87) --
+	(462.16,108.33) --
+	(465.31,107.81) --
+	(468.47,107.30) --
+	(471.63,106.80) --
+	(474.78,106.29) --
+	(477.94,105.80) --
+	(481.10,105.30) --
+	(484.26,104.81) --
+	(487.41,104.32) --
+	(490.57,103.84) --
+	(493.73,103.37) --
+	(496.89,102.91) --
+	(500.04,102.46) --
+	(503.20,102.01) --
+	(506.36,101.57) --
+	(509.51,101.13) --
+	(512.67,100.70) --
+	(515.83,100.27) --
+	(518.99, 99.86) --
+	(522.14, 99.44) --
+	(525.30, 99.04) --
+	(528.46, 98.64) --
+	(531.62, 98.25) --
+	(534.77, 97.86) --
+	(537.93, 97.48) --
+	(541.09, 97.11) --
+	(544.24, 96.75) --
+	(547.40, 96.39) --
+	(550.56, 96.04) --
+	(553.72, 95.69) --
+	(556.87, 95.35) --
+	(560.03, 95.02) --
+	(563.19, 94.69) --
+	(566.35, 94.37) --
+	(569.50, 94.06) --
+	(572.66, 93.75);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (364.81,192.52) --
-	(367.44,190.83) --
-	(370.07,189.17) --
-	(372.70,187.54) --
-	(375.33,185.94) --
-	(377.96,184.36) --
-	(380.59,182.82) --
-	(383.22,181.30) --
-	(385.86,179.80) --
-	(388.49,178.34) --
-	(391.12,176.90) --
-	(393.75,175.49) --
-	(396.38,174.11) --
-	(399.01,172.76) --
-	(401.64,171.43) --
-	(404.27,170.13) --
-	(406.90,168.86) --
-	(409.53,167.61) --
-	(412.17,166.38) --
-	(414.80,165.18) --
-	(417.43,164.00) --
-	(420.06,162.88) --
-	(422.69,161.79) --
-	(425.32,160.73) --
-	(427.95,159.70) --
-	(430.58,158.69) --
-	(433.21,157.70) --
-	(435.85,156.73) --
-	(438.48,155.76) --
-	(441.11,154.80) --
-	(443.74,153.86) --
-	(446.37,152.96) --
-	(449.00,152.08) --
-	(451.63,151.21) --
-	(454.26,150.37) --
-	(456.89,149.53) --
-	(459.52,148.70) --
-	(462.16,147.87) --
-	(464.79,147.03) --
-	(467.42,146.20) --
-	(470.05,145.39) --
-	(472.68,144.58) --
-	(475.31,143.79) --
-	(477.94,143.00) --
-	(480.57,142.23) --
-	(483.20,141.46) --
-	(485.84,140.71) --
-	(488.47,139.96) --
-	(491.10,139.22) --
-	(493.73,138.50) --
-	(496.36,137.79) --
-	(498.99,137.08) --
-	(501.62,136.40) --
-	(504.25,135.72) --
-	(506.88,135.06) --
-	(509.51,134.41) --
-	(512.15,133.76) --
-	(514.78,133.13) --
-	(517.41,132.50) --
-	(520.04,131.88) --
-	(522.67,131.26) --
-	(525.30,130.65) --
-	(527.93,130.05) --
-	(530.56,129.46) --
-	(533.19,128.87) --
-	(535.83,128.30) --
-	(538.46,127.73) --
-	(541.09,127.17) --
-	(543.72,126.62) --
-	(546.35,126.08) --
-	(548.98,125.55) --
-	(551.61,125.02) --
-	(554.24,124.51) --
-	(556.87,124.00) --
-	(559.50,123.49) --
-	(562.14,123.00) --
-	(564.77,122.52) --
-	(567.40,122.04) --
-	(570.03,121.57) --
-	(572.66,121.12);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (323.24,180.94) --
+	(326.39,178.70) --
+	(329.55,176.51) --
+	(332.71,174.35) --
+	(335.87,172.23) --
+	(339.02,170.16) --
+	(342.18,168.13) --
+	(345.34,166.14) --
+	(348.49,164.20) --
+	(351.65,162.29) --
+	(354.81,160.43) --
+	(357.97,158.62) --
+	(361.12,156.84) --
+	(364.28,155.11) --
+	(367.44,153.41) --
+	(370.60,151.76) --
+	(373.75,150.14) --
+	(376.91,148.56) --
+	(380.07,147.02) --
+	(383.22,145.52) --
+	(386.38,144.08) --
+	(389.54,142.68) --
+	(392.70,141.34) --
+	(395.85,140.05) --
+	(399.01,138.79) --
+	(402.17,137.57) --
+	(405.32,136.38) --
+	(408.48,135.23) --
+	(411.64,134.09) --
+	(414.80,132.98) --
+	(417.95,131.90) --
+	(421.11,130.89) --
+	(424.27,129.91) --
+	(427.43,128.98) --
+	(430.58,128.09) --
+	(433.74,127.21) --
+	(436.90,126.36) --
+	(440.05,125.52) --
+	(443.21,124.68) --
+	(446.37,123.84) --
+	(449.53,122.99) --
+	(452.68,122.16) --
+	(455.84,121.37) --
+	(459.00,120.59) --
+	(462.16,119.84) --
+	(465.31,119.10) --
+	(468.47,118.37) --
+	(471.63,117.66) --
+	(474.78,116.95) --
+	(477.94,116.25) --
+	(481.10,115.55) --
+	(484.26,114.85) --
+	(487.41,114.17) --
+	(490.57,113.50) --
+	(493.73,112.84) --
+	(496.89,112.20) --
+	(500.04,111.56) --
+	(503.20,110.94) --
+	(506.36,110.32) --
+	(509.51,109.72) --
+	(512.67,109.12) --
+	(515.83,108.53) --
+	(518.99,107.95) --
+	(522.14,107.38) --
+	(525.30,106.82) --
+	(528.46,106.27) --
+	(531.62,105.73) --
+	(534.77,105.20) --
+	(537.93,104.68) --
+	(541.09,104.17) --
+	(544.24,103.68) --
+	(547.40,103.19) --
+	(550.56,102.71) --
+	(553.72,102.24) --
+	(556.87,101.78) --
+	(560.03,101.33) --
+	(563.19,100.89) --
+	(566.35,100.46) --
+	(569.50,100.05) --
+	(572.66, 99.64);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] (323.24,146.40) --
-	(326.60,140.57) --
-	(319.87,140.57) --
-	cycle;
-
-\path[fill=fillColor] (331.55,143.56) --
-	(334.91,137.74) --
-	(328.19,137.74) --
-	cycle;
-
-\path[fill=fillColor] (339.86,141.07) --
-	(343.23,135.25) --
-	(336.50,135.25) --
-	cycle;
-
-\path[fill=fillColor] (348.18,138.44) --
-	(351.54,132.61) --
-	(344.81,132.61) --
-	cycle;
-
-\path[fill=fillColor] (356.49,136.06) --
-	(359.86,130.23) --
-	(353.13,130.23) --
-	cycle;
-
-\path[fill=fillColor] (364.81,134.02) --
-	(368.17,128.19) --
-	(361.44,128.19) --
-	cycle;
-
-\path[fill=fillColor] (373.12,132.12) --
-	(376.48,126.29) --
-	(369.76,126.29) --
-	cycle;
-
-\path[fill=fillColor] (381.44,130.29) --
-	(384.80,124.46) --
-	(378.07,124.46) --
-	cycle;
-
-\path[fill=fillColor] (389.75,128.36) --
-	(393.11,122.53) --
-	(386.39,122.53) --
-	cycle;
-
-\path[fill=fillColor] (398.06,126.62) --
-	(401.43,120.79) --
-	(394.70,120.79) --
-	cycle;
-
-\path[fill=fillColor] (406.38,125.06) --
-	(409.74,119.23) --
-	(403.01,119.23) --
-	cycle;
-
-\path[fill=fillColor] (414.69,123.72) --
-	(418.06,117.89) --
-	(411.33,117.89) --
-	cycle;
-
-\path[fill=fillColor] (423.01,122.40) --
-	(426.37,116.58) --
-	(419.64,116.58) --
-	cycle;
-
-\path[fill=fillColor] (431.32,121.22) --
-	(434.68,115.39) --
-	(427.96,115.39) --
-	cycle;
-
-\path[fill=fillColor] (439.63,120.06) --
-	(443.00,114.23) --
-	(436.27,114.23) --
-	cycle;
-
-\path[fill=fillColor] (447.95,118.96) --
-	(451.31,113.14) --
-	(444.58,113.14) --
-	cycle;
-
-\path[fill=fillColor] (456.26,117.95) --
-	(459.63,112.12) --
-	(452.90,112.12) --
-	cycle;
-
-\path[fill=fillColor] (464.58,116.87) --
-	(467.94,111.05) --
-	(461.21,111.05) --
-	cycle;
-
-\path[fill=fillColor] (472.89,115.69) --
-	(476.25,109.87) --
-	(469.53,109.87) --
-	cycle;
-
-\path[fill=fillColor] (481.20,114.67) --
-	(484.57,108.84) --
-	(477.84,108.84) --
-	cycle;
-
-\path[fill=fillColor] (489.52,113.75) --
-	(492.88,107.92) --
-	(486.15,107.92) --
-	cycle;
-
-\path[fill=fillColor] (497.83,112.81) --
-	(501.20,106.98) --
-	(494.47,106.98) --
-	cycle;
-
-\path[fill=fillColor] (506.15,111.96) --
-	(509.51,106.13) --
-	(502.78,106.13) --
-	cycle;
-
-\path[fill=fillColor] (514.46,111.02) --
-	(517.82,105.19) --
-	(511.10,105.19) --
-	cycle;
-
-\path[fill=fillColor] (522.78,110.24) --
-	(526.14,104.41) --
-	(519.41,104.41) --
-	cycle;
-
-\path[fill=fillColor] (531.09,109.50) --
-	(534.45,103.67) --
-	(527.73,103.67) --
-	cycle;
-
-\path[fill=fillColor] (539.40,108.72) --
-	(542.77,102.89) --
-	(536.04,102.89) --
-	cycle;
-
-\path[fill=fillColor] (547.72,107.92) --
-	(551.08,102.09) --
-	(544.35,102.09) --
-	cycle;
-
-\path[fill=fillColor] (556.03,107.13) --
-	(559.40,101.31) --
-	(552.67,101.31) --
-	cycle;
-
-\path[fill=fillColor] (564.35,106.48) --
-	(567.71,100.65) --
-	(560.98,100.65) --
-	cycle;
-
-\path[fill=fillColor] (572.66,105.76) --
-	(576.02, 99.93) --
-	(569.30, 99.93) --
+\path[fill=fillColor] (323.24,119.77) --
+	(326.60,113.94) --
+	(319.87,113.94) --
+	cycle;
+
+\path[fill=fillColor] (331.55,117.61) --
+	(334.91,111.79) --
+	(328.19,111.79) --
+	cycle;
+
+\path[fill=fillColor] (339.86,115.71) --
+	(343.23,109.89) --
+	(336.50,109.89) --
+	cycle;
+
+\path[fill=fillColor] (348.18,113.71) --
+	(351.54,107.88) --
+	(344.81,107.88) --
+	cycle;
+
+\path[fill=fillColor] (356.49,111.89) --
+	(359.86,106.07) --
+	(353.13,106.07) --
+	cycle;
+
+\path[fill=fillColor] (364.81,110.34) --
+	(368.17,104.52) --
+	(361.44,104.52) --
+	cycle;
+
+\path[fill=fillColor] (373.12,108.89) --
+	(376.48,103.06) --
+	(369.76,103.06) --
+	cycle;
+
+\path[fill=fillColor] (381.44,107.50) --
+	(384.80,101.67) --
+	(378.07,101.67) --
+	cycle;
+
+\path[fill=fillColor] (389.75,106.03) --
+	(393.11,100.20) --
+	(386.39,100.20) --
+	cycle;
+
+\path[fill=fillColor] (398.06,104.70) --
+	(401.43, 98.88) --
+	(394.70, 98.88) --
+	cycle;
+
+\path[fill=fillColor] (406.38,103.51) --
+	(409.74, 97.69) --
+	(403.01, 97.69) --
+	cycle;
+
+\path[fill=fillColor] (414.69,102.49) --
+	(418.06, 96.67) --
+	(411.33, 96.67) --
+	cycle;
+
+\path[fill=fillColor] (423.01,101.49) --
+	(426.37, 95.66) --
+	(419.64, 95.66) --
+	cycle;
+
+\path[fill=fillColor] (431.32,100.59) --
+	(434.68, 94.76) --
+	(427.96, 94.76) --
+	cycle;
+
+\path[fill=fillColor] (439.63, 99.70) --
+	(443.00, 93.88) --
+	(436.27, 93.88) --
+	cycle;
+
+\path[fill=fillColor] (447.95, 98.87) --
+	(451.31, 93.04) --
+	(444.58, 93.04) --
+	cycle;
+
+\path[fill=fillColor] (456.26, 98.10) --
+	(459.63, 92.27) --
+	(452.90, 92.27) --
+	cycle;
+
+\path[fill=fillColor] (464.58, 97.28) --
+	(467.94, 91.45) --
+	(461.21, 91.45) --
+	cycle;
+
+\path[fill=fillColor] (472.89, 96.38) --
+	(476.25, 90.55) --
+	(469.53, 90.55) --
+	cycle;
+
+\path[fill=fillColor] (481.20, 95.60) --
+	(484.57, 89.77) --
+	(477.84, 89.77) --
+	cycle;
+
+\path[fill=fillColor] (489.52, 94.90) --
+	(492.88, 89.07) --
+	(486.15, 89.07) --
+	cycle;
+
+\path[fill=fillColor] (497.83, 94.18) --
+	(501.20, 88.35) --
+	(494.47, 88.35) --
+	cycle;
+
+\path[fill=fillColor] (506.15, 93.53) --
+	(509.51, 87.70) --
+	(502.78, 87.70) --
+	cycle;
+
+\path[fill=fillColor] (514.46, 92.81) --
+	(517.82, 86.99) --
+	(511.10, 86.99) --
+	cycle;
+
+\path[fill=fillColor] (522.78, 92.22) --
+	(526.14, 86.39) --
+	(519.41, 86.39) --
+	cycle;
+
+\path[fill=fillColor] (531.09, 91.66) --
+	(534.45, 85.83) --
+	(527.73, 85.83) --
+	cycle;
+
+\path[fill=fillColor] (539.40, 91.06) --
+	(542.77, 85.24) --
+	(536.04, 85.24) --
+	cycle;
+
+\path[fill=fillColor] (547.72, 90.45) --
+	(551.08, 84.63) --
+	(544.35, 84.63) --
+	cycle;
+
+\path[fill=fillColor] (556.03, 89.86) --
+	(559.40, 84.03) --
+	(552.67, 84.03) --
+	cycle;
+
+\path[fill=fillColor] (564.35, 89.36) --
+	(567.71, 83.53) --
+	(560.98, 83.53) --
+	cycle;
+
+\path[fill=fillColor] (572.66, 88.81) --
+	(576.02, 82.98) --
+	(569.30, 82.98) --
 	cycle;
@@
 
-\path[fill=fillColor] (320.74,184.90) --
-	(325.73,184.90) --
-	(325.73,189.89) --
-	(320.74,189.89) --
-	cycle;
-
-\path[fill=fillColor] (329.05,179.38) --
-	(334.05,179.38) --
-	(334.05,184.38) --
-	(329.05,184.38) --
-	cycle;
-
-\path[fill=fillColor] (337.37,174.63) --
-	(342.36,174.63) --
-	(342.36,179.62) --
-	(337.37,179.62) --
-	cycle;
-
-\path[fill=fillColor] (345.68,169.62) --
-	(350.68,169.62) --
-	(350.68,174.62) --
-	(345.68,174.62) --
-	cycle;
-
-\path[fill=fillColor] (353.99,164.98) --
-	(358.99,164.98) --
-	(358.99,169.97) --
-	(353.99,169.97) --
-	cycle;
-
-\path[fill=fillColor] (362.31,161.16) --
-	(367.30,161.16) --
-	(367.30,166.16) --
-	(362.31,166.16) --
-	cycle;
-
-\path[fill=fillColor] (370.62,157.55) --
-	(375.62,157.55) --
-	(375.62,162.54) --
-	(370.62,162.54) --
-	cycle;
-
-\path[fill=fillColor] (378.94,154.05) --
-	(383.93,154.05) --
-	(383.93,159.04) --
-	(378.94,159.04) --
-	cycle;
-
-\path[fill=fillColor] (387.25,150.58) --
-	(392.25,150.58) --
-	(392.25,155.57) --
-	(387.25,155.57) --
-	cycle;
-
-\path[fill=fillColor] (395.57,147.37) --
-	(400.56,147.37) --
-	(400.56,152.36) --
-	(395.57,152.36) --
-	cycle;
-
-\path[fill=fillColor] (403.88,144.46) --
-	(408.88,144.46) --
-	(408.88,149.46) --
-	(403.88,149.46) --
-	cycle;
-
-\path[fill=fillColor] (412.19,142.16) --
-	(417.19,142.16) --
-	(417.19,147.15) --
-	(412.19,147.15) --
-	cycle;
-
-\path[fill=fillColor] (420.51,139.77) --
-	(425.50,139.77) --
-	(425.50,144.76) --
-	(420.51,144.76) --
-	cycle;
-
-\path[fill=fillColor] (428.82,137.57) --
-	(433.82,137.57) --
-	(433.82,142.56) --
-	(428.82,142.56) --
-	cycle;
-
-\path[fill=fillColor] (437.14,135.43) --
-	(442.13,135.43) --
-	(442.13,140.43) --
-	(437.14,140.43) --
-	cycle;
-
-\path[fill=fillColor] (445.45,133.56) --
-	(450.45,133.56) --
-	(450.45,138.56) --
-	(445.45,138.56) --
-	cycle;
-
-\path[fill=fillColor] (453.76,131.74) --
-	(458.76,131.74) --
-	(458.76,136.74) --
-	(453.76,136.74) --
-	cycle;
-
-\path[fill=fillColor] (462.08,129.78) --
-	(467.07,129.78) --
-	(467.07,134.77) --
-	(462.08,134.77) --
-	cycle;
-
-\path[fill=fillColor] (470.39,127.78) --
-	(475.39,127.78) --
-	(475.39,132.78) --
-	(470.39,132.78) --
-	cycle;
-
-\path[fill=fillColor] (478.71,126.01) --
-	(483.70,126.01) --
-	(483.70,131.01) --
-	(478.71,131.01) --
-	cycle;
-
-\path[fill=fillColor] (487.02,124.40) --
-	(492.02,124.40) --
-	(492.02,129.39) --
-	(487.02,129.39) --
-	cycle;
-
-\path[fill=fillColor] (495.34,122.77) --
-	(500.33,122.77) --
-	(500.33,127.77) --
-	(495.34,127.77) --
-	cycle;
-
-\path[fill=fillColor] (503.65,121.27) --
-	(508.64,121.27) --
-	(508.64,126.27) --
-	(503.65,126.27) --
-	cycle;
-
-\path[fill=fillColor] (511.96,119.69) --
-	(516.96,119.69) --
-	(516.96,124.69) --
-	(511.96,124.69) --
-	cycle;
-
-\path[fill=fillColor] (520.28,118.37) --
-	(525.27,118.37) --
-	(525.27,123.37) --
-	(520.28,123.37) --
-	cycle;
-
-\path[fill=fillColor] (528.59,117.08) --
-	(533.59,117.08) --
-	(533.59,122.07) --
-	(528.59,122.07) --
-	cycle;
-
-\path[fill=fillColor] (536.91,115.80) --
-	(541.90,115.80) --
-	(541.90,120.79) --
-	(536.91,120.79) --
-	cycle;
-
-\path[fill=fillColor] (545.22,114.56) --
-	(550.22,114.56) --
-	(550.22,119.56) --
-	(545.22,119.56) --
-	cycle;
-
-\path[fill=fillColor] (553.53,113.11) --
-	(558.53,113.11) --
-	(558.53,118.11) --
-	(553.53,118.11) --
-	cycle;
-
-\path[fill=fillColor] (561.85,112.00) --
-	(566.84,112.00) --
-	(566.84,116.99) --
-	(561.85,116.99) --
-	cycle;
-
-\path[fill=fillColor] (570.16,110.83) --
-	(575.16,110.83) --
-	(575.16,115.83) --
-	(570.16,115.83) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,192.97) -- (368.34,192.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,189.44) -- (364.81,196.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,187.54) -- (376.65,187.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,184.00) -- (373.12,191.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,182.28) -- (384.97,182.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,178.74) -- (381.44,185.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,177.28) -- (393.28,177.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,173.74) -- (389.75,180.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,172.56) -- (401.60,172.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,169.03) -- (398.06,176.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,168.23) -- (409.91,168.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,164.70) -- (406.38,171.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,165.07) -- (418.22,165.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,161.54) -- (414.69,168.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,161.58) -- (426.54,161.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,158.05) -- (423.01,165.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,158.33) -- (434.85,158.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,154.80) -- (431.32,161.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,155.26) -- (443.17,155.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,151.73) -- (439.63,158.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,152.71) -- (451.48,152.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,149.18) -- (447.95,156.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,150.06) -- (459.79,150.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,146.53) -- (456.26,153.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,147.16) -- (468.11,147.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,143.63) -- (464.58,150.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,144.40) -- (476.42,144.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,140.87) -- (472.89,147.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,141.94) -- (484.74,141.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,138.40) -- (481.20,145.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,139.68) -- (493.05,139.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,136.15) -- (489.52,143.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,137.43) -- (501.36,137.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,133.89) -- (497.83,140.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,135.23) -- (509.68,135.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,131.70) -- (506.15,138.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,133.11) -- (517.99,133.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,129.58) -- (514.46,136.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,131.25) -- (526.31,131.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,127.72) -- (522.78,134.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,129.44) -- (534.62,129.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,125.91) -- (531.09,132.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,127.77) -- (542.94,127.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,124.24) -- (539.40,131.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,126.17) -- (551.25,126.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72,122.64) -- (547.72,129.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,124.08) -- (559.56,124.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03,120.55) -- (556.03,127.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,122.46) -- (567.88,122.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35,118.92) -- (564.35,125.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,121.01) -- (576.19,121.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,117.48) -- (572.66,124.54);
+\path[fill=fillColor] (320.74,147.59) --
+	(325.73,147.59) --
+	(325.73,152.58) --
+	(320.74,152.58) --
+	cycle;
+
+\path[fill=fillColor] (329.05,143.39) --
+	(334.05,143.39) --
+	(334.05,148.38) --
+	(329.05,148.38) --
+	cycle;
+
+\path[fill=fillColor] (337.37,139.76) --
+	(342.36,139.76) --
+	(342.36,144.75) --
+	(337.37,144.75) --
+	cycle;
+
+\path[fill=fillColor] (345.68,135.95) --
+	(350.68,135.95) --
+	(350.68,140.94) --
+	(345.68,140.94) --
+	cycle;
+
+\path[fill=fillColor] (353.99,132.41) --
+	(358.99,132.41) --
+	(358.99,137.40) --
+	(353.99,137.40) --
+	cycle;
+
+\path[fill=fillColor] (362.31,129.50) --
+	(367.30,129.50) --
+	(367.30,134.50) --
+	(362.31,134.50) --
+	cycle;
+
+\path[fill=fillColor] (370.62,126.75) --
+	(375.62,126.75) --
+	(375.62,131.74) --
+	(370.62,131.74) --
+	cycle;
+
+\path[fill=fillColor] (378.94,124.08) --
+	(383.93,124.08) --
+	(383.93,129.08) --
+	(378.94,129.08) --
+	cycle;
+
+\path[fill=fillColor] (387.25,121.44) --
+	(392.25,121.44) --
+	(392.25,126.43) --
+	(387.25,126.43) --
+	cycle;
+
+\path[fill=fillColor] (395.57,118.99) --
+	(400.56,118.99) --
+	(400.56,123.99) --
+	(395.57,123.99) --
+	cycle;
+
+\path[fill=fillColor] (403.88,116.78) --
+	(408.88,116.78) --
+	(408.88,121.77) --
+	(403.88,121.77) --
+	cycle;
+
+\path[fill=fillColor] (412.19,115.02) --
+	(417.19,115.02) --
+	(417.19,120.02) --
+	(412.19,120.02) --
+	cycle;
+
+\path[fill=fillColor] (420.51,113.20) --
+	(425.50,113.20) --
+	(425.50,118.19) --
+	(420.51,118.19) --
+	cycle;
+
+\path[fill=fillColor] (428.82,111.53) --
+	(433.82,111.53) --
+	(433.82,116.52) --
+	(428.82,116.52) --
+	cycle;
+
+\path[fill=fillColor] (437.14,109.90) --
+	(442.13,109.90) --
+	(442.13,114.89) --
+	(437.14,114.89) --
+	cycle;
+
+\path[fill=fillColor] (445.45,108.47) --
+	(450.45,108.47) --
+	(450.45,113.47) --
+	(445.45,113.47) --
+	cycle;
+
+\path[fill=fillColor] (453.76,107.09) --
+	(458.76,107.09) --
+	(458.76,112.08) --
+	(453.76,112.08) --
+	cycle;
+
+\path[fill=fillColor] (462.08,105.59) --
+	(467.07,105.59) --
+	(467.07,110.58) --
+	(462.08,110.58) --
+	cycle;
+
+\path[fill=fillColor] (470.39,104.07) --
+	(475.39,104.07) --
+	(475.39,109.07) --
+	(470.39,109.07) --
+	cycle;
+
+\path[fill=fillColor] (478.71,102.72) --
+	(483.70,102.72) --
+	(483.70,107.72) --
+	(478.71,107.72) --
+	cycle;
+
+\path[fill=fillColor] (487.02,101.49) --
+	(492.02,101.49) --
+	(492.02,106.49) --
+	(487.02,106.49) --
+	cycle;
+
+\path[fill=fillColor] (495.34,100.25) --
+	(500.33,100.25) --
+	(500.33,105.25) --
+	(495.34,105.25) --
+	cycle;
+
+\path[fill=fillColor] (503.65, 99.11) --
+	(508.64, 99.11) --
+	(508.64,104.10) --
+	(503.65,104.10) --
+	cycle;
+
+\path[fill=fillColor] (511.96, 97.90) --
+	(516.96, 97.90) --
+	(516.96,102.90) --
+	(511.96,102.90) --
+	cycle;
+
+\path[fill=fillColor] (520.28, 96.90) --
+	(525.27, 96.90) --
+	(525.27,101.90) --
+	(520.28,101.90) --
+	cycle;
+
+\path[fill=fillColor] (528.59, 95.91) --
+	(533.59, 95.91) --
+	(533.59,100.91) --
+	(528.59,100.91) --
+	cycle;
+
+\path[fill=fillColor] (536.91, 94.94) --
+	(541.90, 94.94) --
+	(541.90, 99.93) --
+	(536.91, 99.93) --
+	cycle;
+
+\path[fill=fillColor] (545.22, 94.00) --
+	(550.22, 94.00) --
+	(550.22, 98.99) --
+	(545.22, 98.99) --
+	cycle;
+
+\path[fill=fillColor] (553.53, 92.89) --
+	(558.53, 92.89) --
+	(558.53, 97.89) --
+	(553.53, 97.89) --
+	cycle;
+
+\path[fill=fillColor] (561.85, 92.04) --
+	(566.84, 92.04) --
+	(566.84, 97.04) --
+	(561.85, 97.04) --
+	cycle;
+
+\path[fill=fillColor] (570.16, 91.16) --
+	(575.16, 91.16) --
+	(575.16, 96.15) --
+	(570.16, 96.15) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (319.70,181.63) -- (326.77,181.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.24,178.10) -- (323.24,185.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.02,175.24) -- (335.08,175.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.55,171.71) -- (331.55,178.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.33,169.74) -- (343.40,169.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.86,166.20) -- (339.86,173.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.65,163.98) -- (351.71,163.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.18,160.45) -- (348.18,167.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.96,158.64) -- (360.02,158.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.49,155.11) -- (356.49,162.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,154.33) -- (368.34,154.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,150.80) -- (364.81,157.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,150.19) -- (376.65,150.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,146.66) -- (373.12,153.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,146.18) -- (384.97,146.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,142.65) -- (381.44,149.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,142.37) -- (393.28,142.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,138.84) -- (389.75,145.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,138.78) -- (401.60,138.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,135.25) -- (398.06,142.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,135.48) -- (409.91,135.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,131.95) -- (406.38,139.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,133.07) -- (418.22,133.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,129.54) -- (414.69,136.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,130.41) -- (426.54,130.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,126.88) -- (423.01,133.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,127.94) -- (434.85,127.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,124.40) -- (431.32,131.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,125.60) -- (443.17,125.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,122.07) -- (439.63,129.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,123.66) -- (451.48,123.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,120.13) -- (447.95,127.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,121.64) -- (459.79,121.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,118.11) -- (456.26,125.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,119.43) -- (468.11,119.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,115.90) -- (464.58,122.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,117.33) -- (476.42,117.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,113.80) -- (472.89,120.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,115.45) -- (484.74,115.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,111.92) -- (481.20,118.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,113.73) -- (493.05,113.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,110.20) -- (489.52,117.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,112.01) -- (501.36,112.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,108.48) -- (497.83,115.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,110.34) -- (509.68,110.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,106.81) -- (506.15,113.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,108.72) -- (517.99,108.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,105.19) -- (514.46,112.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,107.30) -- (526.31,107.30);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,103.77) -- (522.78,110.84);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,105.93) -- (534.62,105.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,102.40) -- (531.09,109.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,104.65) -- (542.94,104.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,101.12) -- (539.40,108.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,103.44) -- (551.25,103.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72, 99.91) -- (547.72,106.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,101.84) -- (559.56,101.84);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03, 98.31) -- (556.03,105.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,100.61) -- (567.88,100.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35, 97.07) -- (564.35,104.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13, 99.50) -- (576.19, 99.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66, 95.97) -- (572.66,103.04);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[fill=fillColor] (323.24, 68.06) circle (  2.50);
-
-\path[fill=fillColor] (331.55, 68.24) circle (  2.50);
-
-\path[fill=fillColor] (339.86, 68.21) circle (  2.50);
-
-\path[fill=fillColor] (348.18, 67.81) circle (  2.50);
-
-\path[fill=fillColor] (356.49, 68.07) circle (  2.50);
-
-\path[fill=fillColor] (364.81, 68.35) circle (  2.50);
-
-\path[fill=fillColor] (373.12, 68.10) circle (  2.50);
-
-\path[fill=fillColor] (381.44, 68.30) circle (  2.50);
-
-\path[fill=fillColor] (389.75, 68.27) circle (  2.50);
-
-\path[fill=fillColor] (398.06, 68.02) circle (  2.50);
-
-\path[fill=fillColor] (406.38, 68.54) circle (  2.50);
-
-\path[fill=fillColor] (414.69, 67.86) circle (  2.50);
-
-\path[fill=fillColor] (423.01, 67.64) circle (  2.50);
-
-\path[fill=fillColor] (431.32, 68.15) circle (  2.50);
-
-\path[fill=fillColor] (439.63, 68.39) circle (  2.50);
-
-\path[fill=fillColor] (447.95, 68.19) circle (  2.50);
-
-\path[fill=fillColor] (456.26, 68.00) circle (  2.50);
-
-\path[fill=fillColor] (464.58, 68.03) circle (  2.50);
-
-\path[fill=fillColor] (472.89, 67.80) circle (  2.50);
-
-\path[fill=fillColor] (481.20, 67.94) circle (  2.50);
-
-\path[fill=fillColor] (489.52, 67.80) circle (  2.50);
-
-\path[fill=fillColor] (497.83, 68.37) circle (  2.50);
-
-\path[fill=fillColor] (506.15, 68.09) circle (  2.50);
-
-\path[fill=fillColor] (514.46, 68.40) circle (  2.50);
-
-\path[fill=fillColor] (522.78, 68.75) circle (  2.50);
-
-\path[fill=fillColor] (531.09, 67.59) circle (  2.50);
-
-\path[fill=fillColor] (539.40, 68.00) circle (  2.50);
-
-\path[fill=fillColor] (547.72, 68.44) circle (  2.50);
-
-\path[fill=fillColor] (556.03, 68.43) circle (  2.50);
-
-\path[fill=fillColor] (564.35, 67.96) circle (  2.50);
-
-\path[fill=fillColor] (572.66, 67.78) circle (  2.50);
+\path[fill=fillColor] (323.24, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (331.55, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (339.86, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (348.18, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (356.49, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (364.81, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (373.12, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (381.44, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (389.75, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (398.06, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (406.38, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (414.69, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (423.01, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (431.32, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (439.63, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (447.95, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (456.26, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (464.58, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (472.89, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (481.20, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (489.52, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (497.83, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (506.15, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (514.46, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (522.78, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (531.09, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (539.40, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (547.72, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (556.03, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (564.35, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (572.66, 58.94) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29, 78.74) {0.2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,129.82) {0.4};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,180.91) {0.6};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29, 66.58) {0.2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,105.50) {0.4};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,144.42) {0.6};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,183.34) {0.8};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49, 81.77) --
-	(323.24, 81.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,132.85) --
-	(323.24,132.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,183.94) --
-	(323.24,183.94);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49, 69.61) --
+	(323.24, 69.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,108.53) --
+	(323.24,108.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,147.45) --
+	(323.24,147.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,186.37) --
+	(323.24,186.37);
 \end{scope}

### 2020-04-29 serial.tex
new fig

@@
 k(x) &= \int_0^\infty h(x, \tau) \dtau\\
-g(\tau) &= \int_0^\infty h(x, \tau) \dx
+\gdist(\tau) &= \int_0^\infty h(x, \tau) \dx
 \end{aligned}
@@
 
-The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $g(\tau)$ give identical estimates of \RR regardless of the correlation $\rho$ between the incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
-However, using naive serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \RR;
+The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $\gdist(\tau)$ give identical estimates of \RR regardless of the correlation $\rho$ between the forward incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
+However, using the intrinsic serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \RR;
 as $r$ increases, \Rintrinsic saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
@@
 \textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
-(A). The forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number \RR.
-(B) The serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and \RR.
+(A). The initial forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number \RR.
+(B) The intrinsic serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and \RR.
 (C) The mean forward serial interval during the exponential growth phase depends on $r$.

### 2020-04-29 forward_tease.R

@@ -1,191 +1,0 @@
-library(tidyr)
-library(dplyr)
-library(ggplot2); theme_set(theme_bw())
-library(gridExtra)
-library(tikzDevice)
-source("renewal_det.R")
-
-load("sir_sim.rda")
-
-rr <- renewal_det()
-
-tcut <- 0:40*2
-
-sir_sim <- lapply(simlist, function(x) {
-  data.frame(
-    t_infected=x$t_infected,
-    t_symptomatic=x$t_symptomatic,
-    infected_by=x$infected_by
-  )
-}) %>%
-  bind_rows(.id="sim") %>%
-  mutate(
-    infected_by=infected_by+(as.numeric(sim)-1)*40000
-  )
-
-serdata0 <- data.frame(
-  cohort=sir_sim$t_symptomatic[sir_sim$infected_by],
-  tdiff=sir_sim$t_symptomatic-sir_sim$t_symptomatic[sir_sim$infected_by]
-) %>%
-  filter(!is.na(cohort), !is.na(tdiff), cohort > 0, cohort <= 100) %>%
-  mutate(
-    cc=cut(cohort, tcut)
-  ) %>%
-  group_by(cc) %>%
-  summarize(
-    mean=mean(tdiff)
-  ) %>%
-  ungroup %>%
-  mutate(
-    cc=as.character(cc),
-    cc=(as.numeric(gsub("\\(", "", gsub(",.*", "", cc)))+as.numeric(gsub("]", "", gsub(".*,", "", cc))))/2
-  )
-
-serdet <- data.frame(
-  tvec=rr$tvec,
-  mf=rr$mfser2,
-  type="Accounting for changes in $\\mathcal R_c$"
-)
-
-serdet2 <- data.frame(
-  tvec=rr$tvec,
-  mf=rr$mfser,
-  type="Not accounting for changes in $\\mathcal R_c$"
-)
-
-serdet_all <- bind_rows(serdet, serdet2)
-
-g1 <- ggplot(serdata0) +
-  geom_line(data=serdet_all, aes(tvec, mf, lty=type), lwd=1) +
-  geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
-  # geom_hline(yintercept=serdet$mf[1], lty=2) +
-  scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7),
[…]

### 2020-04-29 rR.R

@@ -76,7 +76,9 @@ serialR2 <- function(r=0.1,
 generationR <- function(r=0.1,
                         meanlog2=1.54,
                         sdlog2=0.37,
-                        nsim=100000) {
+                        nsim=100000,
+                        seed=101) {
+  set.seed(101)
   gen <- rlnorm(nsim, meanlog2, sdlog2)
                           
   list(
@@ -86,32 +88,34 @@ generationR <- function(r=0.1,
   )
 }
 
+ww <- c(1, 5, 9, 13, 17, 21, 25, 29)
+
 rRdata <- list(
   data.frame(
-    r=seq(0, 0.3, by=0.01),
-    R=sapply(seq(0, 0.3, by=0.01), function(x) serialR(x, rho=0.5)$R),
-    type="Serial interval ($\\rho=0.5$)"
+    r=seq(0, 0.3, by=0.01)[ww],
+    R=sapply(seq(0, 0.3, by=0.01)[ww], function(x) serialR(x, rho=0.5)$R),
+    type="Forward serial interval ($\\rho=0.5$)"
   ),
   data.frame(
-    r=seq(0, 0.3, by=0.01),
-    R=sapply(seq(0, 0.3, by=0.01), function(x) serialR(x, rho=0)$R),
-    type="Serial interval ($\\rho=0$)"
+    r=seq(0, 0.3, by=0.01)[ww+1],
+    R=sapply(seq(0, 0.3, by=0.01)[ww+1], function(x) serialR(x, rho=0)$R),
+    type="Forward serial interval ($\\rho=0$)"
   ),
   data.frame(
-    r=seq(0, 0.3, by=0.01),
-    R=sapply(seq(0, 0.3, by=0.01), function(x) serialR(x, rho=-0.5)$R),
-    type="Serial interval ($\\rho=-0.5$)"
+    r=seq(0, 0.3, by=0.01)[ww+2],
+    R=sapply(seq(0, 0.3, by=0.01)[ww+2], function(x) serialR(x, rho=-0.5)$R),
+    type="Forward serial interval ($\\rho=-0.5$)"
   ),
   data.frame(
-    r=seq(0, 0.3, by=0.01),
-    R=sapply(seq(0, 0.3, by=0.01), function(x) generationR(x)$R),
-    type="Generation interval"
+    r=seq(0, 0.3, by=0.01)[head(ww,-1)+3],
[…]

### 2020-04-29 serial.tex
4AM!!! going to sleep...

@@
 \textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
-(A). The initial forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number \RR.
-(B) The intrinsic serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and \RR.
-(C) The mean forward serial interval during the exponential growth phase depends on $r$.
-(D) The squared coefficient of variation of forward serial intervals during the exponential growth phase depends on $r$.
+(A). The initial forward serial-interval distribution give a correct link between the exponential growth rate $r$ and the reproduction number \RR.
+(B) The intrinsic serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and \RR (and underestimates \RR compared to the intrinsic generation-interval distribution).
+(C) The mean initial forward serial interval during the exponential growth phase depends on $r$.
+(D) The squared coefficient of variation of the initial forward serial intervals during the exponential growth phase depends on $r$.
 }
@@
 The effects of higher means (which increases \RR) and higher variability (which decreases \RR) cancel out exactly;
-therefore, we can estimate the same \RR using both serial and generation intervals.
+therefore, we can estimate the same \RR using both initial forward serial and intrinsic generation intervals.
+On the other hand, intrinsic serial intervals have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are wider (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
+therefore, we underestimate \RR when we use the intrinsic serial-interval distribution.
 
@@
 
-The initial forward serial interval distribution only applies to the exponential growth phase of an epidemic.
+The initial forward serial interval distribution captures the exponential growth phase of an epidemic.
 Now, we characterize how forward and backward serial intervals vary over the course of an epidemic when incubation periods and generation intervals are independent.

### 2020-04-29 observedrRa.tex
almost screwed up...

% Created by tikzDevice version 0.12.3 on 2020-04-29 11:23:23
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (476.98,238.49);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (238.49,238.49);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (238.49,238.49);
\end{scope}
\begin{scope}
\path[clip] ( 39.73, 44.63) rectangle (230.49,230.49);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 39.73, 44.63) rectangle (230.49,230.49);
\definecolor{drawColor}{RGB}{213,94,0}
\definecolor{fillColor}{RGB}{213,94,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.57,143.88) --
	( 68.34,139.29) --
	( 73.11,140.53) --
	( 77.88,150.20) --
	( 82.65,154.08) --
	( 87.42,143.97) --
	( 92.19,139.44) --
	( 96.96,133.42) --
	(101.73,128.90) --
	(106.50,130.19) --
	(111.26,129.29) --
	(116.03,128.66) --
	(120.80,129.54) --
	(125.57,129.47) --
	(130.34,131.33) --
	(135.11,132.16) --
	(139.88,134.43) --
	(144.65,137.48) --
	(149.42,140.76) --
	(154.19,144.33) --
	(158.95,147.92) --
	(163.72,151.35) --
	(168.49,154.62) --
	(173.26,157.17) --
	(178.03,159.07) --
	(182.80,160.66) --
	(187.57,161.69) --
	(192.34,162.67) --
	(197.11,163.06) --
	(201.88,163.57) --
	(206.65,163.99) --
	(211.41,164.16) --
	(216.18,164.23) --
	(220.95,164.28) --
	(225.72,164.28) --
	(230.49,164.29) --
	(230.49,162.31) --
	(225.72,162.28) --
	(220.95,162.24) --
	(216.18,162.14) --
	(211.41,162.02) --
	(206.65,161.88) --
	(201.88,161.46) --
	(197.11,160.90) --
	(192.34,160.03) --
	(187.57,158.72) --
	(182.80,157.34) --
	(178.03,154.74) --
	(173.26,151.99) --
	(168.49,148.41) --
	(163.72,144.63) --
	(158.95,140.85) --
	(154.19,137.05) --
	(149.42,134.58) --
	(144.65,131.84) --
	(139.88,128.62) --
	(135.11,126.02) --
	(130.34,124.20) --
	(125.57,121.71) --
	(120.80,118.52) --
	(116.03,117.29) --
	(111.26,113.04) --
	(106.50,114.56) --
	(101.73,112.74) --
	( 96.96,105.19) --
	( 92.19, 95.56) --
	( 87.42, 89.02) --
	( 82.65, 83.72) --
	( 77.88, 92.96) --
	( 73.11, 67.00) --
	( 68.34, 70.51) --
	( 63.57, 57.69) --
	cycle;

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.57, 93.76) --
	( 68.34,105.54) --
	( 73.11,108.96) --
	( 77.88,116.25) --
	( 82.65,115.66) --
	( 87.42,117.30) --
	( 92.19,119.86) --
	( 96.96,119.34) --
	(101.73,119.30) --
	(106.50,121.94) --
	(111.26,122.94) --
	(116.03,124.17) --
	(120.80,125.18) --
	(125.57,126.08) --
	(130.34,127.59) --
	(135.11,129.11) --
	(139.88,131.40) --
	(144.65,133.92) --
	(149.42,136.99) --
	(154.19,140.41) --
	(158.95,144.31) --
	(163.72,147.94) --
	(168.49,151.28) --
	(173.26,154.33) --
	(178.03,156.87) --
	(182.80,158.84) --
	(187.57,160.23) --
	(192.34,161.26) --
	(197.11,161.93) --
	(201.88,162.38) --
	(206.65,162.70) --
	(211.41,162.89) --
	(216.18,163.02) --
	(220.95,163.11) --
	(225.72,163.15) --
	(230.49,163.18);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 39.73,213.02) -- (230.49,213.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.73,174.96) -- (230.49,174.96);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.72,215.96) {Initial forward};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.72,177.90) {Intrinsic};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] ( 39.73, 44.63) rectangle (230.49,230.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53, 40.23) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53, 83.45) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53,126.67) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53,169.89) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53,213.12) {6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73, 44.63) --
	( 39.73, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73, 87.86) --
	( 39.73, 87.86);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73,131.08) --
	( 39.73,131.08);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73,174.30) --
	( 39.73,174.30);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73,217.52) --
	( 39.73,217.52);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 39.73, 40.63) --
	( 39.73, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 87.42, 40.63) --
	( 87.42, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (135.11, 40.63) --
	(135.11, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (182.80, 40.63) --
	(182.80, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (230.49, 40.63) --
	(230.49, 44.63);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 39.73, 28.62) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 87.42, 28.62) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (135.11, 28.62) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (182.80, 28.62) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (230.49, 28.62) {80};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (135.11, 11.11) {Time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 19.02,137.56) {Mean serial interval (days)};
\end{scope}
\begin{scope}
\path[clip] (238.49,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (238.49,  0.00) rectangle (476.98,238.49);
\end{scope}
\begin{scope}
\path[clip] (278.22, 44.63) rectangle (468.98,230.49);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (278.22, 44.63) rectangle (468.98,230.49);
\definecolor{drawColor}{RGB}{213,94,0}
\definecolor{fillColor}{RGB}{213,94,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (302.06,179.67) --
	(306.83,169.56) --
	(311.60,166.54) --
	(316.37,168.01) --
	(321.14,168.69) --
	(325.91,159.68) --
	(330.68,154.35) --
	(335.45,145.54) --
	(340.22,138.10) --
	(344.99,137.84) --
	(349.76,138.33) --
	(354.52,138.29) --
	(359.29,137.48) --
	(364.06,137.84) --
	(368.83,138.02) --
	(373.60,138.31) --
	(378.37,138.83) --
	(383.14,139.83) --
	(387.91,141.29) --
	(392.68,142.28) --
	(397.45,144.58) --
	(402.22,145.75) --
	(406.98,146.14) --
	(411.75,147.28) --
	(416.52,148.06) --
	(421.29,148.09) --
	(426.06,148.51) --
	(430.83,148.53) --
	(435.60,148.65) --
	(440.37,148.06) --
	(445.14,148.05) --
	(449.91,148.10) --
	(454.67,148.17) --
	(459.44,148.20) --
	(464.21,148.21) --
	(468.98,148.21) --
	(468.98,144.11) --
	(464.21,144.09) --
	(459.44,144.07) --
	(454.67,144.04) --
	(449.91,144.01) --
	(445.14,143.96) --
	(440.37,144.51) --
	(435.60,144.38) --
	(430.83,144.21) --
	(426.06,143.63) --
	(421.29,143.39) --
	(416.52,142.54) --
	(411.75,141.53) --
	(406.98,140.62) --
	(402.22,139.39) --
	(397.45,138.15) --
	(392.68,135.95) --
	(387.91,136.13) --
	(383.14,135.19) --
	(378.37,133.02) --
	(373.60,130.47) --
	(368.83,131.68) --
	(364.06,129.95) --
	(359.29,126.47) --
	(354.52,125.78) --
	(349.76,123.21) --
	(344.99,123.48) --
	(340.22,121.22) --
	(335.45,120.50) --
	(330.68,112.09) --
	(325.91,111.07) --
	(321.14,104.63) --
	(316.37,105.39) --
	(311.60, 87.60) --
	(306.83,102.09) --
	(302.06, 99.55) --
	cycle;

\path[draw=drawColor,line width= 0.6pt,line join=round] (302.06,132.56) --
	(306.83,131.77) --
	(311.60,126.61) --
	(316.37,132.19) --
	(321.14,130.95) --
	(325.91,131.38) --
	(330.68,132.53) --
	(335.45,131.74) --
	(340.22,130.16) --
	(344.99,131.94) --
	(349.76,132.19) --
	(354.52,133.66) --
	(359.29,133.85) --
	(364.06,134.27) --
	(368.83,135.09) --
	(373.60,135.16) --
	(378.37,136.39) --
	(383.14,137.43) --
	(387.91,138.56) --
	(392.68,139.61) --
	(397.45,141.29) --
	(402.22,142.41) --
	(406.98,143.44) --
	(411.75,144.40) --
	(416.52,145.19) --
	(421.29,145.74) --
	(426.06,146.08) --
	(430.83,146.24) --
	(435.60,146.25) --
	(440.37,146.28) --
	(445.14,146.24) --
	(449.91,146.14) --
	(454.67,145.91) --
	(459.44,145.90) --
	(464.21,145.92) --
	(468.98,145.92);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (278.22,209.84) -- (468.98,209.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (278.22,154.56) -- (468.98,154.56);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,212.78) {Initial forward};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,157.50) {Intrinsic};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (278.22, 44.63) rectangle (468.98,230.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02, 50.55) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02,153.81) {2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22, 54.96) --
	(278.22, 54.96);

\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22,158.21) --
	(278.22,158.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] (278.22, 40.63) --
	(278.22, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (325.91, 40.63) --
	(325.91, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (373.60, 40.63) --
	(373.60, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (421.29, 40.63) --
	(421.29, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (468.98, 40.63) --
	(468.98, 44.63);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (278.22, 28.62) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (325.91, 28.62) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (373.60, 28.62) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (421.29, 28.62) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (468.98, 28.62) {80};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (373.60, 11.11) {Time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (257.51,137.56) {Reproduction number $\mathcal R$};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-04-29 observedrRb.tex
almost screwed up...

% Created by tikzDevice version 0.12.3 on 2020-04-29 11:23:36
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (476.98,238.49);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (238.49,238.49);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (238.49,238.49);
\end{scope}
\begin{scope}
\path[clip] ( 49.68, 44.63) rectangle (230.49,230.49);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 49.68, 44.63) rectangle (230.49,230.49);
\definecolor{drawColor}{RGB}{204,121,167}
\definecolor{fillColor}{RGB}{204,121,167}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.28,208.07) --
	( 76.80,164.32) --
	( 81.32,167.89) --
	( 85.84,158.27) --
	( 90.36,161.18) --
	( 94.88,155.47) --
	( 99.40,155.84) --
	(103.92,152.83) --
	(108.44,147.52) --
	(112.96,144.06) --
	(117.49,141.75) --
	(122.01,135.58) --
	(126.53,129.99) --
	(131.05,127.94) --
	(135.57,121.76) --
	(140.09,114.68) --
	(144.61,107.88) --
	(149.13,100.74) --
	(153.65, 92.87) --
	(158.17, 84.99) --
	(162.69, 79.17) --
	(167.21, 73.72) --
	(171.73, 70.27) --
	(176.25, 67.93) --
	(180.77, 66.45) --
	(185.29, 65.22) --
	(189.81, 64.69) --
	(194.33, 64.39) --
	(198.85, 63.99) --
	(203.37, 63.64) --
	(207.89, 63.40) --
	(212.41, 63.31) --
	(216.93, 63.30) --
	(221.45, 63.27) --
	(225.97, 63.25) --
	(230.49, 63.23) --
	(230.49, 59.98) --
	(225.97, 59.99) --
	(221.45, 59.99) --
	(216.93, 59.99) --
	(212.41, 60.01) --
	(207.89, 60.06) --
	(203.37, 60.28) --
	(198.85, 60.37) --
	(194.33, 60.61) --
	(189.81, 60.97) --
	(185.29, 61.22) --
	(180.77, 61.94) --
	(176.25, 63.28) --
	(171.73, 64.96) --
	(167.21, 67.32) --
	(162.69, 70.74) --
	(158.17, 75.21) --
	(153.65, 80.74) --
	(149.13, 86.75) --
	(144.61, 93.83) --
	(140.09,101.11) --
	(135.57,107.97) --
	(131.05,114.84) --
	(126.53,119.84) --
	(122.01,121.79) --
	(117.49,123.07) --
	(112.96,127.78) --
	(108.44,125.50) --
	(103.92,127.66) --
	( 99.40,118.76) --
	( 94.88,120.68) --
	( 90.36,112.09) --
	( 85.84,111.94) --
	( 81.32,109.08) --
	( 76.80,127.52) --
	( 72.28,125.38) --
	cycle;

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.28,166.88) --
	( 76.80,144.70) --
	( 81.32,138.94) --
	( 85.84,139.23) --
	( 90.36,139.42) --
	( 94.88,138.52) --
	( 99.40,138.58) --
	(103.92,136.90) --
	(108.44,135.32) --
	(112.96,134.23) --
	(117.49,130.80) --
	(122.01,129.38) --
	(126.53,125.23) --
	(131.05,120.57) --
	(135.57,114.75) --
	(140.09,107.84) --
	(144.61,100.77) --
	(149.13, 93.23) --
	(153.65, 86.29) --
	(158.17, 80.06) --
	(162.69, 75.18) --
	(167.21, 71.07) --
	(171.73, 67.95) --
	(176.25, 65.68) --
	(180.77, 64.26) --
	(185.29, 63.27) --
	(189.81, 62.65) --
	(194.33, 62.22) --
	(198.85, 61.93) --
	(203.37, 61.76) --
	(207.89, 61.63) --
	(212.41, 61.56) --
	(216.93, 61.51) --
	(221.45, 61.49) --
	(225.97, 61.48) --
	(230.49, 61.47);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 49.68,140.72) -- (230.49,140.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.68, 80.10) -- (230.49, 80.10);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.97,143.66) {Initial forward};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.97, 83.04) {Intrinsic};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] ( 49.68, 44.63) rectangle (230.49,230.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48, 40.23) {4.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48, 74.64) {5.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,109.06) {5.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,143.48) {6.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,177.90) {6.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,212.32) {7.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68, 44.63) --
	( 49.68, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68, 79.05) --
	( 49.68, 79.05);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,113.47) --
	( 49.68,113.47);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,147.89) --
	( 49.68,147.89);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,182.31) --
	( 49.68,182.31);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,216.72) --
	( 49.68,216.72);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 49.68, 40.63) --
	( 49.68, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 94.88, 40.63) --
	( 94.88, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (140.09, 40.63) --
	(140.09, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (185.29, 40.63) --
	(185.29, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (230.49, 40.63) --
	(230.49, 44.63);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 49.68, 28.62) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 94.88, 28.62) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (140.09, 28.62) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (185.29, 28.62) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (230.49, 28.62) {80};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (140.09, 11.11) {Time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 19.02,137.56) {Mean serial interval (days)};
\end{scope}
\begin{scope}
\path[clip] (238.49,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (238.49,  0.00) rectangle (476.98,238.49);
\end{scope}
\begin{scope}
\path[clip] (278.22, 44.63) rectangle (468.98,230.49);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (278.22, 44.63) rectangle (468.98,230.49);
\definecolor{drawColor}{RGB}{204,121,167}
\definecolor{fillColor}{RGB}{204,121,167}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (302.06,220.91) --
	(306.83,186.06) --
	(311.60,184.29) --
	(316.37,180.56) --
	(321.14,171.77) --
	(325.91,171.49) --
	(330.68,168.64) --
	(335.45,166.60) --
	(340.22,160.21) --
	(344.99,158.84) --
	(349.76,159.16) --
	(354.52,154.78) --
	(359.29,150.97) --
	(364.06,149.69) --
	(368.83,146.44) --
	(373.60,141.11) --
	(378.37,135.50) --
	(383.14,131.30) --
	(387.91,126.00) --
	(392.68,119.60) --
	(397.45,115.57) --
	(402.22,111.47) --
	(406.98,107.65) --
	(411.75,106.09) --
	(416.52,104.82) --
	(421.29,103.30) --
	(426.06,102.79) --
	(430.83,102.24) --
	(435.60,101.92) --
	(440.37,101.04) --
	(445.14,100.74) --
	(449.91,100.71) --
	(454.67,100.71) --
	(459.44,100.71) --
	(464.21,100.71) --
	(468.98,100.70) --
	(468.98, 97.00) --
	(464.21, 97.00) --
	(459.44, 97.00) --
	(454.67, 97.00) --
	(449.91, 97.02) --
	(445.14, 97.05) --
	(440.37, 97.67) --
	(435.60, 97.80) --
	(430.83, 98.05) --
	(426.06, 98.33) --
	(421.29, 98.61) --
	(416.52, 99.34) --
	(411.75,100.93) --
	(406.98,102.92) --
	(402.22,105.37) --
	(397.45,108.32) --
	(392.68,112.30) --
	(387.91,116.70) --
	(383.14,122.38) --
	(378.37,127.38) --
	(373.60,131.82) --
	(368.83,137.05) --
	(364.06,140.82) --
	(359.29,143.36) --
	(354.52,143.56) --
	(349.76,142.51) --
	(344.99,144.89) --
	(340.22,141.25) --
	(335.45,145.85) --
	(330.68,140.31) --
	(325.91,142.20) --
	(321.14,135.02) --
	(316.37,142.00) --
	(311.60,128.88) --
	(306.83,145.02) --
	(302.06,169.68) --
	cycle;

\path[draw=drawColor,line width= 0.6pt,line join=round] (302.06,188.49) --
	(306.83,168.18) --
	(311.60,158.33) --
	(316.37,159.72) --
	(321.14,157.07) --
	(325.91,156.54) --
	(330.68,156.67) --
	(335.45,155.15) --
	(340.22,152.92) --
	(344.99,153.04) --
	(349.76,150.77) --
	(354.52,150.34) --
	(359.29,147.58) --
	(364.06,144.69) --
	(368.83,140.95) --
	(373.60,135.85) --
	(378.37,131.20) --
	(383.14,125.97) --
	(387.91,120.91) --
	(392.68,116.05) --
	(397.45,112.24) --
	(402.22,108.72) --
	(406.98,105.97) --
	(411.75,103.93) --
	(416.52,102.50) --
	(421.29,101.44) --
	(426.06,100.72) --
	(430.83,100.16) --
	(435.60, 99.70) --
	(440.37, 99.45) --
	(445.14, 99.21) --
	(449.91, 99.01) --
	(454.67, 98.73) --
	(459.44, 98.68) --
	(464.21, 98.67) --
	(468.98, 98.65);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (278.22,156.15) -- (468.98,156.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] (278.22,106.40) -- (468.98,106.40);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,159.09) {Initial forward};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,109.34) {Intrinsic};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (278.22, 44.63) rectangle (468.98,230.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02,105.28) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02,198.20) {3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22,109.68) --
	(278.22,109.68);

\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22,202.61) --
	(278.22,202.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] (278.22, 40.63) --
	(278.22, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (325.91, 40.63) --
	(325.91, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (373.60, 40.63) --
	(373.60, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (421.29, 40.63) --
	(421.29, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (468.98, 40.63) --
	(468.98, 44.63);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (278.22, 28.62) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (325.91, 28.62) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (373.60, 28.62) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (421.29, 28.62) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (468.98, 28.62) {80};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (373.60, 11.11) {Time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (257.51,137.56) {Reproduction number $\mathcal R$};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-04-29 serial.tex
almost screwed up...

@@
 Now, we characterize how forward and backward serial intervals vary over the course of an epidemic when incubation periods and generation intervals are independent.
-\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on the Gillespie algorithm.
+\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
 The mean forward incubation period remains constant throughout an epidemic as assumed (\fref{epi}B).
@@
 
-The forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation periods of infectors, (ii) the forward generation intervals, and (iii) the forward incubation periods of infectees.
+The forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation period distributions, (ii) the forward generation-interval distributions, and (iii) the forward incubation period distributions.
 Since both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant, changes in the forward serial-interval distributions are predominantly driven by changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
 In this case, the increase in the mean backward incubation period directly translates to the decrease in the mean forward serial interval.
-We note that the relative contributions of the three distributions depend on their shapes and correlations between incubation periods and generation intervals --- as discussed earlier, the backward incubation period has \emph{no} effect on the forward serial intervals in the SEIR model, because transmission always occurs after symptom onset.
+We note that the relative contributions of the three distributions depend on their shapes and correlations between incubation periods and generation intervals --- as discussed earlier, the backward incubation period has \emph{no} effect on the forward serial intervals in the special case of an SEIR model, because transmission always occurs after symptom onset.
 
@@
 When incidence decreases, we are more likely to observe longer intervals for similar but opposite reasons.
-Since changes in incidence can occur even in the absence of significant susceptible depletion (e.g., due to intervention), we expect qualitative patterns in the changes of backward delay distributions to be robust across many outbreaks.
 
 \begin{figure}[!ht]
-\includegraphics[width=\textwidth]{observedrR.pdf}
+\includegraphics[width=\textwidth]{diagram.pdf}
 \caption{

### 2020-04-29 observedrR.R

@@ -1,8 +1,9 @@
 library(tidyr)
 library(dplyr)
-library(ggplot2); theme_set(theme_bw())
+library(ggplot2); theme_set(theme_bw(base_size = 16))
 library(gridExtra)
 library(tikzDevice)
+source("rRfun.R")
 source("renewal_det.R")
 source("cpalette.R")
 
@@ -111,42 +112,103 @@ R0_cohort <- lapply(tcut, function(x) {
 ser_all <- bind_rows(ser_obs, ser_cohort) %>%
   mutate(
     type=factor(type, level=c("Observed", "Cohort-averaged"))
+  ) %>%
+  group_by(type, t) %>%
+  summarize(
+    mean=mean(ser),
+    lwr=min(ser),
+    upr=max(ser)
   )
 
-g1 <- ggplot(ser_all) +
-  geom_line(aes(t, ser, col=type, group=interaction(sim, type), lty=type)) +
+serialsim <- serialR2(r=r, rho=0) 
+
+g1a <- ggplot(filter(ser_all, type=="Observed")) +
+  geom_ribbon(aes(t, ymin=lwr, ymax=upr, fill=type, col=type, lty=type), alpha=0.5) +
+  geom_line(aes(t, mean, col=type, lty=type)) +
   geom_hline(yintercept=rr$mfser2[1], lty=2) +
+  geom_hline(yintercept=serialsim$mean, lty=1) +
+  annotate("text", x=78, y=rr$mfser2[1], label="Initial forward", hjust=1, vjust=-0.3, size=5) +
+  annotate("text", x=78, y=serialsim$mean, label="Intrinsic", hjust=1, vjust=-0.3, size=5) +
   scale_x_continuous("Time (days)", limits=c(0, 80), expand=c(0, 0)) +
-  scale_y_continuous("Mean serial interval (days)", expand=c(0, 0), limits=c(2, 7.2)) +
+  scale_y_continuous("Mean serial interval (days)", expand=c(0, 0), limits=c(2, 6.3)) +
   scale_color_manual(values=tail(cpalette, 2)) +
   scale_fill_manual(values=tail(cpalette, 2)) +
-  ggtitle("A") +
-  theme(
-    panel.grid = element_blank(),
-    legend.position = c(0.75, 0.2),
-    legend.title = element_blank()
-  )
-
-R0all <- bind_rows(R0_obs, R0_cohort) %>%
-  mutate(
[…]

### 2020-04-29 rR.R

@@ -3,6 +3,7 @@ library(ggplot2); theme_set(theme_bw())
 library(tikzDevice)
 library(gridExtra)
 source("cpalette.R")
+source("rRfun.R")
 
 ## incubation!
 meanlog1 <- 1.62
@@ -13,80 +14,7 @@ sd(rlnorm(50000, meanlog = 1.62, sdlog=0.42)) ## 2.4
 ## generation
 ## moment matching
 mean(rlnorm(50000, meanlog = 1.54, sdlog=0.37)) ## 5 days
-sd(rlnorm(50000, meanlog = 1.54, sdlog=0.37)) ##
-
-serialR <- function(r=0.1,
-                    rho=0.5,
-                    meanlog1=1.62,
-                    sdlog1=0.42,
-                    meanlog2=1.54,
-                    sdlog2=0.37,
-                    nsim=100000,
-                    seed=101) {
-  set.seed(seed)
-  backinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
-  
-  backinc <- sample(backinc, replace=TRUE, prob=exp(-r*backinc))
-  
-  logbackinc <- log(backinc)
-  
-  muloggen <- meanlog2 + sdlog2 * rho * (logbackinc - meanlog1)/sdlog1
-  sigmaloggen <- sqrt(sdlog2^2 * (1 - rho^2))
-  
-  forwardgen <- exp(rnorm(nsim, muloggen, sigmaloggen))
-  forwardinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
-  
-  ser <- -backinc + forwardgen + forwardinc
-  
-  list(
-    mean=mean(ser),
-    kappa=var(ser)/mean(ser)^2,
-    R=1/mean(exp(-r*ser))
-  )
-}
-
-serialR2 <- function(r=0.1,
-                    rho=0.5,
-                    meanlog1=1.62,
-                    sdlog1=0.42,
-                    meanlog2=1.54,
-                    sdlog2=0.37,
-                    nsim=100000,
-                    seed=101) {
-  set.seed(seed)
-  backinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
-  
-  logbackinc <- log(backinc)
-  
-  muloggen <- meanlog2 + sdlog2 * rho * (logbackinc - meanlog1)/sdlog1
[…]

### 2020-04-29 serial.tex
attempting to improve key explanation in Methods

@@
 the primary and secondary events are defined in terms of the direction of transmission:
-The primary event refers to the event that occurs within an infector and does not necessarily occur before the secondary event.
+The primary event refers to the event that occurs within the infector
+and does not necessarily occur before the secondary event (which
+occurs within the infectee).
 
@@
 
-At the individual-level, both forward and backward \emph{measurements} provide identical measures;
-in other words, we can express the total density of primary and secondary events occurring at time $\pt$ and $\st$, respectively, using both forward and backward delay \emph{distributions}:
-\begin{equation}
+\david{deleted ``At the individual-level, both forward and backward
+  \emph{measurements} provide identical measures; in other words, we
+  can express the total density of primary and secondary events
+  occurring at time $\pt$ and $\st$, respectively, using both forward
+  and backward delay \emph{distributions}:''}
+
+At the individual level, both forward and backward \emph{perspectives}
+must yield identical results (e.g., the length of the incubation
+period of a given individual is the same whether measured forward from
+the time of infection or backward from time of symptom onset).
+Consequently, we must obtain the same number if we count the number of
+individuals who became infected at time $\pt$ or the number of
+individuals who first showed symptoms at time $\st$; that is, we must
+have
+\begin{equation}\label{eq:match}
 \psize(\pt) f_\pt(\st-\pt) = \ssize(\st) b_\st(\st-\pt),
 \end{equation}
-where $\mathcal P$ and $\mathcal S$ represent the sizes of primary and secondary cohorts, respectively.
+where $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
+secondary cohorts, respectively.
+
+{\color{red}DE: IN THE MIDST OF EDITING THIS PARAGRAPH... WILL RETURN
+  TO THIS, HOPEFULLY LATER THIS EVENING...}
+
 Substituting $\tau = \st - \pt$, it follows that:

### 2020-04-30 serial.tex
hopefully no merge conflicts

--- 2020-04-29 serial.tex
@@
 Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number \RR --- yet important quantities in understanding the outset of an outbreak.
-Even though their differences were clearly laid out over a decade ago, 
+Even though their differences were clearly laid out over a decade ago, there is still a need for clear conceptual and theoretical understanding of their roles in shaping the epidemiological dynamics.
 A part of the confusion can be attributed to an apparent paradox.
-By definition, generation and serial intervals describe the renewal process between infection and symptom onset, respectively, and therefore, one might expect them to potentially provide the same link between the epidemic growth rate $r$ and the reproduction number \RR.
-However, current theory does not explain how two different distributions can give the same link between $r$ and $\mathcal R$ --- some studies have demonstrated that generation and serial intervals give different $r$--\RR link, contradicting our biological intuition.
+By definition, both generation and serial intervals describe how infection spreads between individuals, and therefore, one might expect them to potentially provide the same link between the epidemic growth rate $r$ and the reproduction number \RR based on the renewal process.
+However, current theory does not explain how two different distributions can give the same link between $r$ and \RR --- some studies have further demonstrated that generation and serial intervals give different $r$--\RR link.
 We provide an answer to the paradox by showing that if serial intervals are defined as \emph{forward-looking} intervals during the exponential phase, then the correct link between $r$ and \RR emerges.
-We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references.
+We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to analyze serial intervals of COVID-19.
 Our study reveals gaps in the current understanding of serial intervals and provides rationale for reassessing serial intervals of COVID-19.
@@
 
-\subsection{Backward and forward delay distributions}
+\subsection{Forward and backward delay distributions}
 
@@
 Mean forward incubation period & 5.5 days & \cite{lauer2020incubation} \\
-SD forward incubation period & 2.4 & \cite{lauer2020incubation} \\
+SD forward incubation period & 2.4 days & \cite{lauer2020incubation} \\
 Mean intrinsic generation interval & 5 days & \cite{ferretti2020quantifying} \\
-SD intrinsic generation interval & 2 & \cite{ferretti2020quantifying} \\
+SD intrinsic generation interval & 2 days & \cite{ferretti2020quantifying} \\
 \hline
@@
 Now, we turn to practical issues.
+Serial intervals are typically calculated from line-list data (\fref{obsrR}A).
 When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms.

### 2020-04-30 serial.tex
new figure and adding new explanation

@@
 \newcommand{\bmb}[1]{\comment{blue}{BMB}{#1}}
+\newcommand{\david}[1]{\comment{red}{DE}{#1}}
 
@@
 
+\subsection{Observed serial interval distributions}
+
 \begin{figure}[!ht]
@@
 
-\subsection{Observed serial interval distributions}
-
 Now, we turn to practical issues.
 Serial intervals are typically calculated from line-list data (\fref{obsrR}A).
-When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms.
-\fref{obsrR} demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of \RR.
-Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate the initial mean forward serial interval (\fref{obsrR}A) and therefore \Ro (\fref{obsrR}) by a large amount because the observed serial-interval distribution does not account for changes in the forward serial-interval distribution.
-As the mean forward serial-interval distribution decreases over time, taking the average of all observed serial intervals throughout an epidemic will underestimate the mean of the initial forward serial-interval distribution, which provides the correct link between $r$ and \RR.
+When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
+for example, if we were to measure serial intervals on Day 8 in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
+\fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of \RR.
+Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate the initial mean forward serial interval and therefore \Ro by a large amount because the observed serial-interval distribution converges to the intrinsic serial-interval distribution;
+we still underestimate the intrinsic value slightly due to contraction of the forward generation-interval distribution during the susceptible depletion phase (\fref{epi}C).
 

### 2020-04-30 serial.tex
losing focus

@@
 \caption{
-\textbf{Estimates of the reproduction number from the observed serial intervals.}
-(A) Changes in the observed and cohort-averaged mean serial interval over time.
-(B) Changes in the estimate of \RR based on the observed and cohort-averaged mean serial interval over time.
-Each line represents an independent stochastic realization.
+\textbf{Estimating the reproduction number from the observed serial intervals.}
+(A) Schematic representation of line list data collected during an epidemic.
+(B) Changes in the estimate of \RR based on the observed serial intervals over time.
+(C) Schematic representation of line list data rearranged by symptom onset date of infectors.
+(B) Changes in the estimate of \RR based on the cohort-averaged serial intervals over time.
 }
@@
 for example, if we were to measure serial intervals on Day 8 in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
-\fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of \RR.
+\fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of \RR in our stochastic simulations.
 Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate the initial mean forward serial interval and therefore \Ro by a large amount because the observed serial-interval distribution converges to the intrinsic serial-interval distribution;
@@
 We provide a simple, heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \RR retrospectively.
-Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can group observed serial intervals by their primary cohort times (i.e., symptom onset times of infectors).
-Then, we can compare how estimates of the mean serial interval as well as \RR change as we include more recent cohorts into the analysis (see `cohort-averaged' in \fref{obsrR}).
+Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can rearrange the line list and group observed serial intervals based on the symptom onset date of infectors (\fref{obsrR}C).
+Then, we can compare how estimates of the mean serial interval as well as \RR change as we incorporate more recent cohorts into the analysis;
+that is, we analyze observed serial intervals from infectors who became symptomatic before time $t$ and evaluate how the estimates change as we increase $t$
+(\fref{obsrR}D).
 During the exponential growth phase, the estimates of the mean serial interval and \RR are consistent with the target value;
 adding more data allows us to make more precise inference during this period.
-However, the cohort-averaged estimates decreases rapidly soon after the exponential growth period.
-This approach allows us to characterize potential biases in the estimates of \RR caused by changes in the forward serial-interval distributions.
+However, the cohort-averaged estimates decrease rapidly soon after the exponential growth period, reflecting changes in the forward serial-interval distributions.
+This approach allows us to detect dynamical changes in the forward serial-interval distributions and its effect on the estimates of \RR.
 
@@
 
-Finally, we reanalyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on transmission events reported between January 21--February 8, 2020;
+Finally, we re-analyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on transmission events reported between January 21--February 8, 2020;
 \cite{du2020serial} estimated the mean serial of 3.96 days (95\% CI 3.53–4.39 days) and \Ro of 1.32 (95\% CI 1.16–1.48).

### 2020-04-30 serial.tex
fussed a lot with the paragraph including eq (1), which I changed; hopefully this much longer version is also clearer to others

--- 2020-04-30 serial.tex
@@
 \newcommand{\bmb}[1]{\comment{blue}{BMB}{#1}}
+\newcommand{\djde}[1]{\comment{red}{DJDE}{#1}}
 
@@
 Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number \RR --- yet important quantities in understanding the outset of an outbreak.
-Even though their differences were clearly laid out over a decade ago, there is still a need for clear conceptual and theoretical understanding of their roles in shaping the epidemiological dynamics.
+Even though their differences were clearly laid out over a decade ago, 
 A part of the confusion can be attributed to an apparent paradox.
-By definition, both generation and serial intervals describe how infection spreads between individuals, and therefore, one might expect them to potentially provide the same link between the epidemic growth rate $r$ and the reproduction number \RR based on the renewal process.
-However, current theory does not explain how two different distributions can give the same link between $r$ and \RR --- some studies have further demonstrated that generation and serial intervals give different $r$--\RR link.
+By definition, generation and serial intervals describe the renewal process between infection and symptom onset, respectively, and therefore, one might expect them to potentially provide the same link between the epidemic growth rate $r$ and the reproduction number \RR.
+However, current theory does not explain how two different distributions can give the same link between $r$ and $\mathcal R$ --- some studies have demonstrated that generation and serial intervals give different $r$--\RR link, contradicting our biological intuition.
 We provide an answer to the paradox by showing that if serial intervals are defined as \emph{forward-looking} intervals during the exponential phase, then the correct link between $r$ and \RR emerges.
-We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to analyze serial intervals of COVID-19.
+We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references.
 Our study reveals gaps in the current understanding of serial intervals and provides rationale for reassessing serial intervals of COVID-19.
@@
 
-\subsection{Forward and backward delay distributions}
+\subsection{Backward and forward delay distributions}
 
@@
 
-\david{deleted ``At the individual-level, both forward and backward
+\djde{deleted ``At the individual-level, both forward and backward
   \emph{measurements} provide identical measures; in other words, we
@@
   occurring at time $\pt$ and $\st$, respectively, using both forward
-  and backward delay \emph{distributions}:''}
+  and backward delay \emph{distributions}:'' and ended up rewriting
+  the following paragraph...}
 
@@
 period of a given individual is the same whether measured forward from
-the time of infection or backward from time of symptom onset).
-Consequently, we must obtain the same number if we count the number of
-individuals who became infected at time $\pt$ or the number of
-individuals who first showed symptoms at time $\st$; that is, we must
-have
-\begin{equation}\label{eq:match}
-\psize(\pt) f_\pt(\st-\pt) = \ssize(\st) b_\st(\st-\pt),
+the time of infection or backward from the time of symptom onset).
+Consequently, if we restrict attention to individuals with a given
+incubation period, say $\tau$, and we count how many became infected at time $\pt$
+or how many first showed symptoms at time $\st=\pt+\tau$ then we must obtain
+the same number. In general, no matter how delays are distributed, if
+$\mathcal P$ and $\mathcal S$ represent the sizes of primary and
+secondary cohorts then we must have
+\begin{equation}
+\psize(\pt) f_\pt(\tau) = \ssize(\st) b_\st(\tau) \,.
+\label{eq:match}
 \end{equation}
-where $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
-secondary cohorts, respectively.
-
-{\color{red}DE: IN THE MIDST OF EDITING THIS PARAGRAPH... WILL RETURN
-  TO THIS, HOPEFULLY LATER THIS EVENING...}
-
-Substituting $\tau = \st - \pt$, it follows that:
+Substituting $\pt=\st-\tau$, it follows that
 \begin{equation}
-b_\st(\tau) = \frac{\psize(\st-\tau) f_{\st-\tau}(\tau)}{\ssize(\st)}
+b_\st(\tau)= \frac{\psize(\st-\tau) f_{\st-\tau} (\tau)}{\ssize(\st)}
 \label{eq:backward}
 \end{equation}
-Therefore, the backward delay distribution depends on the changes in primary cohort size $\tau$ time units ago from the reference time $\st$, $\psize(\st-\tau)$, as well as changes in the forward delay distribution, $f_{\st-\tau}(\tau)$.
+If we are thinking of incubation periods, then the left hand side of
+this equation is the probability density that there is an individual
+who became symptomatic at time $\st$ after an incubation period of
+length $\tau$. From the right hand side, we see that this probability
+density depends on how many individuals became infected at time
+$\st-\tau$ [$\psize(\st-\tau)$], how many individuals became
+symptomatic at time $\st$ [$\ssize(\st)$], and the probability density
+that someone who was infected at time $\st-\tau$ became symptomatic at
+time $\st$ [$f_{\st-\tau}(\tau)$]. In general, Eq.~\eqref{eq:backward}
+shows that the the backward delay distribution at reference time $\st$
+[$b_\st(\tau)$] depends not only on the secondary cohort size at time
+$\st$ [$\ssize(\st)$], but also on the primary cohort size at the
+earlier time $\st-\tau$ [$\psize(\st-\tau)$] and the forward delay
+distribution at that earlier time [$f_{\st-\tau}(\tau)$].
 
@@
 Mean forward incubation period & 5.5 days & \cite{lauer2020incubation} \\
-SD forward incubation period & 2.4 days & \cite{lauer2020incubation} \\
+SD forward incubation period & 2.4 & \cite{lauer2020incubation} \\
 Mean intrinsic generation interval & 5 days & \cite{ferretti2020quantifying} \\
-SD intrinsic generation interval & 2 days & \cite{ferretti2020quantifying} \\
+SD intrinsic generation interval & 2 & \cite{ferretti2020quantifying} \\
 \hline
@@
 Now, we turn to practical issues.
-Serial intervals are typically calculated from line-list data (\fref{obsrR}A).
 When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms.

### 2020-04-30 serial.tex

--- 2020-04-30 serial.tex
@@
 \newcommand{\bmb}[1]{\comment{blue}{BMB}{#1}}
-\newcommand{\david}[1]{\comment{red}{DE}{#1}}
+\newcommand{\djde}[1]{\comment{red}{DJDE}{#1}}
 

### 2020-04-30 serial.tex
cool

--- 2020-04-30 serial.tex
@@
 (A) Schematic representation of line list data collected during an epidemic.
-(B) Changes in the estimate of \RR based on the observed serial intervals over time.
+(B) Changes in the estimate of \Ro based on the observed serial intervals over time.
 (C) Schematic representation of line list data rearranged by symptom onset date of infectors.
-(B) Changes in the estimate of \RR based on the cohort-averaged serial intervals over time.
+(B) Changes in the estimate of \Ro based on the cohort-averaged serial intervals over time.
+Dashed lines represent \Ro.
 }
@@
 for example, if we were to measure serial intervals on Day 8 in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
-\fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of \RR in our stochastic simulations.
+\fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of the basic reproduction number \Ro in our stochastic simulations.
 Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate the initial mean forward serial interval and therefore \Ro by a large amount because the observed serial-interval distribution converges to the intrinsic serial-interval distribution;
@@
 
-We provide a simple, heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \RR retrospectively.
+We provide a simple, heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \Ro retrospectively.
 Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can rearrange the line list and group observed serial intervals based on the symptom onset date of infectors (\fref{obsrR}C).
-Then, we can compare how estimates of the mean serial interval as well as \RR change as we incorporate more recent cohorts into the analysis;
+Then, we can compare how estimates of the mean serial interval as well as \Ro change as we incorporate more recent cohorts into the analysis;
 that is, we analyze observed serial intervals from infectors who became symptomatic before time $t$ and evaluate how the estimates change as we increase $t$
 (\fref{obsrR}D).
-During the exponential growth phase, the estimates of the mean serial interval and \RR are consistent with the target value;
+During the exponential growth phase, the estimates of the mean serial interval and \Ro are consistent with the target value;
 adding more data allows us to make more precise inference during this period.
 However, the cohort-averaged estimates decrease rapidly soon after the exponential growth period, reflecting changes in the forward serial-interval distributions.
-This approach allows us to detect dynamical changes in the forward serial-interval distributions and its effect on the estimates of \RR.
+This approach allows us to detect dynamical changes in the forward serial-interval distributions and its effect on the estimates of \Ro.
 

### 2020-04-30 observedrRa.tex
still making so many changes!!

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-29 11:23:23
+% Created by tikzDevice version 0.12.3 on 2020-04-30 02:30:25
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (476.98,238.49);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (476.98,252.94);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (238.49,238.49);
+\path[clip] (  0.00,  0.00) rectangle (238.49,252.94);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (238.49,238.49);
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (238.49,252.94);
 \end{scope}
 \begin{scope}
-\path[clip] ( 39.73, 44.63) rectangle (230.49,230.49);
+\path[clip] ( 39.73, 44.63) rectangle (230.49,244.95);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 39.73, 44.63) rectangle (230.49,230.49);
+\path[fill=fillColor] ( 39.73, 44.63) rectangle (230.49,244.94);
 \definecolor{drawColor}{RGB}{213,94,0}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.57,143.88) --
-	( 68.34,139.29) --
-	( 73.11,140.53) --
-	( 77.88,150.20) --
-	( 82.65,154.08) --
-	( 87.42,143.97) --
-	( 92.19,139.44) --
-	( 96.96,133.42) --
-	(101.73,128.90) --
-	(106.50,130.19) --
-	(111.26,129.29) --
-	(116.03,128.66) --
-	(120.80,129.54) --
-	(125.57,129.47) --
-	(130.34,131.33) --
-	(135.11,132.16) --
-	(139.88,134.43) --
-	(144.65,137.48) --
-	(149.42,140.76) --
-	(154.19,144.33) --
-	(158.95,147.92) --
-	(163.72,151.35) --
-	(168.49,154.62) --
-	(173.26,157.17) --
-	(178.03,159.07) --
-	(182.80,160.66) --
-	(187.57,161.69) --
-	(192.34,162.67) --
-	(197.11,163.06) --
-	(201.88,163.57) --
-	(206.65,163.99) --
-	(211.41,164.16) --
-	(216.18,164.23) --
-	(220.95,164.28) --
-	(225.72,164.28) --
-	(230.49,164.29) --
-	(230.49,162.31) --
-	(225.72,162.28) --
-	(220.95,162.24) --
-	(216.18,162.14) --
-	(211.41,162.02) --
-	(206.65,161.88) --
-	(201.88,161.46) --
-	(197.11,160.90) --
-	(192.34,160.03) --
-	(187.57,158.72) --
-	(182.80,157.34) --
-	(178.03,154.74) --
-	(173.26,151.99) --
-	(168.49,148.41) --
-	(163.72,144.63) --
-	(158.95,140.85) --
-	(154.19,137.05) --
-	(149.42,134.58) --
-	(144.65,131.84) --
-	(139.88,128.62) --
-	(135.11,126.02) --
-	(130.34,124.20) --
-	(125.57,121.71) --
-	(120.80,118.52) --
-	(116.03,117.29) --
-	(111.26,113.04) --
-	(106.50,114.56) --
-	(101.73,112.74) --
-	( 96.96,105.19) --
-	( 92.19, 95.56) --
-	( 87.42, 89.02) --
-	( 82.65, 83.72) --
-	( 77.88, 92.96) --
-	( 73.11, 67.00) --
-	( 68.34, 70.51) --
-	( 63.57, 57.69) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 63.57,151.60) --
+	( 68.34,146.65) --
+	( 73.11,147.98) --
+	( 77.88,158.41) --
+	( 82.65,162.59) --
+	( 87.42,151.69) --
+	( 92.19,146.81) --
+	( 96.96,140.33) --
+	(101.73,135.45) --
+	(106.50,136.85) --
+	(111.26,135.88) --
+	(116.03,135.19) --
+	(120.80,136.14) --
+	(125.57,136.07) --
+	(130.34,138.08) --
+	(135.11,138.96) --
+	(139.88,141.42) --
+	(144.65,144.70) --
+	(149.42,148.23) --
+	(154.19,152.08) --
+	(158.95,155.95) --
+	(163.72,159.65) --
+	(168.49,163.18) --
+	(173.26,165.92) --
+	(178.03,167.97) --
+	(182.80,169.68) --
+	(187.57,170.79) --
+	(192.34,171.85) --
+	(197.11,172.27) --
+	(201.88,172.82) --
+	(206.65,173.27) --
+	(211.41,173.45) --
+	(216.18,173.54) --
+	(220.95,173.58) --
+	(225.72,173.59) --
+	(230.49,173.60) --
+	(230.49,171.46) --
+	(225.72,171.42) --
+	(220.95,171.39) --
+	(216.18,171.28) --
+	(211.41,171.15) --
+	(206.65,170.99) --
+	(201.88,170.55) --
+	(197.11,169.95) --
+	(192.34,169.00) --
+	(187.57,167.59) --
+	(182.80,166.10) --
+	(178.03,163.30) --
+	(173.26,160.34) --
+	(168.49,156.48) --
+	(163.72,152.40) --
+	(158.95,148.33) --
+	(154.19,144.23) --
+	(149.42,141.58) --
+	(144.65,138.62) --
+	(139.88,135.15) --
+	(135.11,132.35) --
+	(130.34,130.38) --
+	(125.57,127.70) --
+	(120.80,124.26) --
+	(116.03,122.94) --
+	(111.26,118.36) --
+	(106.50,120.00) --
+	(101.73,118.03) --
+	( 96.96,109.89) --
+	( 92.19, 99.52) --
+	( 87.42, 92.47) --
+	( 82.65, 86.76) --
+	( 77.88, 96.72) --
+	( 73.11, 68.74) --
+	( 68.34, 72.52) --
+	( 63.57, 58.70) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.57, 93.76) --
-	( 68.34,105.54) --
-	( 73.11,108.96) --
-	( 77.88,116.25) --
-	( 82.65,115.66) --
-	( 87.42,117.30) --
-	( 92.19,119.86) --
-	( 96.96,119.34) --
-	(101.73,119.30) --
-	(106.50,121.94) --
-	(111.26,122.94) --
-	(116.03,124.17) --
-	(120.80,125.18) --
-	(125.57,126.08) --
-	(130.34,127.59) --
-	(135.11,129.11) --
-	(139.88,131.40) --
-	(144.65,133.92) --
-	(149.42,136.99) --
-	(154.19,140.41) --
-	(158.95,144.31) --
-	(163.72,147.94) --
-	(168.49,151.28) --
-	(173.26,154.33) --
-	(178.03,156.87) --
-	(182.80,158.84) --
-	(187.57,160.23) --
-	(192.34,161.26) --
-	(197.11,161.93) --
-	(201.88,162.38) --
-	(206.65,162.70) --
-	(211.41,162.89) --
-	(216.18,163.02) --
-	(220.95,163.11) --
-	(225.72,163.15) --
-	(230.49,163.18);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.57, 97.58) --
+	( 68.34,110.27) --
+	( 73.11,113.96) --
+	( 77.88,121.82) --
+	( 82.65,121.18) --
+	( 87.42,122.95) --
+	( 92.19,125.71) --
+	( 96.96,125.15) --
+	(101.73,125.10) --
+	(106.50,127.96) --
+	(111.26,129.03) --
+	(116.03,130.35) --
+	(120.80,131.44) --
+	(125.57,132.42) --
+	(130.34,134.04) --
+	(135.11,135.68) --
+	(139.88,138.14) --
+	(144.65,140.86) --
+	(149.42,144.17) --
+	(154.19,147.86) --
+	(158.95,152.06) --
+	(163.72,155.97) --
+	(168.49,159.57) --
+	(173.26,162.86) --
+	(178.03,165.60) --
+	(182.80,167.72) --
+	(187.57,169.22) --
+	(192.34,170.33) --
+	(197.11,171.05) --
+	(201.88,171.54) --
+	(206.65,171.88) --
+	(211.41,172.09) --
+	(216.18,172.23) --
+	(220.95,172.32) --
+	(225.72,172.37) --
+	(230.49,172.40);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 39.73,213.02) -- (230.49,213.02);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 39.73,226.12) -- (230.49,226.12);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.73,174.96) -- (230.49,174.96);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.73,185.10) -- (230.49,185.10);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.72,215.96) {Initial forward};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.72,229.06) {Initial forward};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.72,177.90) {Intrinsic};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.72,188.04) {Intrinsic};
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] ( 39.73, 44.63) rectangle (230.49,230.49);
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] ( 39.73, 44.63) rectangle (230.49,244.94);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.30}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53, 83.45) {3};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53, 86.81) {3};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53,126.67) {4};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53,133.39) {4};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53,169.89) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53,179.98) {5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53,213.12) {6};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 32.53,226.56) {6};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73, 87.86) --
-	( 39.73, 87.86);
+\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73, 91.22) --
+	( 39.73, 91.22);
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73,131.08) --
-	( 39.73,131.08);
+\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73,137.80) --
+	( 39.73,137.80);
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73,174.30) --
-	( 39.73,174.30);
+\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73,184.39) --
+	( 39.73,184.39);
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73,217.52) --
-	( 39.73,217.52);
+\path[draw=drawColor,line width= 0.8pt,line join=round] ( 35.73,230.97) --
+	( 39.73,230.97);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.20}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.30}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 19.02,137.56) {Mean serial interval (days)};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 19.02,144.79) {Mean serial interval (days)};
 \end{scope}
 \begin{scope}
-\path[clip] (238.49,  0.00) rectangle (476.98,238.49);
+\path[clip] (238.49,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (238.49,  0.00) rectangle (476.98,238.49);
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (238.49,  0.00) rectangle (476.98,252.94);
 \end{scope}
 \begin{scope}
-\path[clip] (278.22, 44.63) rectangle (468.98,230.49);
+\path[clip] (278.22, 44.63) rectangle (468.98,244.95);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (278.22, 44.63) rectangle (468.98,230.49);
+\path[fill=fillColor] (278.22, 44.63) rectangle (468.98,244.94);
 \definecolor{drawColor}{RGB}{213,94,0}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (302.06,179.67) --
-	(306.83,169.56) --
-	(311.60,166.54) --
-	(316.37,168.01) --
-	(321.14,168.69) --
-	(325.91,159.68) --
-	(330.68,154.35) --
-	(335.45,145.54) --
-	(340.22,138.10) --
-	(344.99,137.84) --
-	(349.76,138.33) --
-	(354.52,138.29) --
-	(359.29,137.48) --
-	(364.06,137.84) --
-	(368.83,138.02) --
-	(373.60,138.31) --
-	(378.37,138.83) --
-	(383.14,139.83) --
-	(387.91,141.29) --
-	(392.68,142.28) --
-	(397.45,144.58) --
-	(402.22,145.75) --
-	(406.98,146.14) --
-	(411.75,147.28) --
-	(416.52,148.06) --
-	(421.29,148.09) --
-	(426.06,148.51) --
-	(430.83,148.53) --
-	(435.60,148.65) --
-	(440.37,148.06) --
-	(445.14,148.05) --
-	(449.91,148.10) --
-	(454.67,148.17) --
-	(459.44,148.20) --
-	(464.21,148.21) --
-	(468.98,148.21) --
-	(468.98,144.11) --
-	(464.21,144.09) --
-	(459.44,144.07) --
-	(454.67,144.04) --
-	(449.91,144.01) --
-	(445.14,143.96) --
-	(440.37,144.51) --
-	(435.60,144.38) --
-	(430.83,144.21) --
-	(426.06,143.63) --
-	(421.29,143.39) --
-	(416.52,142.54) --
-	(411.75,141.53) --
-	(406.98,140.62) --
-	(402.22,139.39) --
-	(397.45,138.15) --
-	(392.68,135.95) --
-	(387.91,136.13) --
-	(383.14,135.19) --
-	(378.37,133.02) --
-	(373.60,130.47) --
-	(368.83,131.68) --
-	(364.06,129.95) --
-	(359.29,126.47) --
-	(354.52,125.78) --
-	(349.76,123.21) --
-	(344.99,123.48) --
-	(340.22,121.22) --
-	(335.45,120.50) --
-	(330.68,112.09) --
-	(325.91,111.07) --
-	(321.14,104.63) --
-	(316.37,105.39) --
-	(311.60, 87.60) --
-	(306.83,102.09) --
-	(302.06, 99.55) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (302.06,190.17) --
+	(306.83,179.27) --
+	(311.60,176.02) --
+	(316.37,177.60) --
+	(321.14,178.34) --
+	(325.91,168.63) --
+	(330.68,162.88) --
+	(335.45,153.39) --
+	(340.22,145.37) --
+	(344.99,145.09) --
+	(349.76,145.62) --
+	(354.52,145.58) --
+	(359.29,144.70) --
+	(364.06,145.09) --
+	(368.83,145.28) --
+	(373.60,145.60) --
+	(378.37,146.15) --
+	(383.14,147.24) --
+	(387.91,148.81) --
+	(392.68,149.88) --
+	(397.45,152.35) --
+	(402.22,153.62) --
+	(406.98,154.03) --
+	(411.75,155.27) --
+	(416.52,156.10) --
+	(421.29,156.14) --
+	(426.06,156.59) --
+	(430.83,156.61) --
+	(435.60,156.74) --
+	(440.37,156.10) --
+	(445.14,156.09) --
+	(449.91,156.15) --
+	(454.67,156.22) --
+	(459.44,156.25) --
+	(464.21,156.27) --
+	(468.98,156.27) --
+	(468.98,151.85) --
+	(464.21,151.83) --
+	(459.44,151.81) --
+	(454.67,151.77) --
+	(449.91,151.73) --
+	(445.14,151.68) --
+	(440.37,152.28) --
+	(435.60,152.14) --
+	(430.83,151.96) --
+	(426.06,151.33) --
+	(421.29,151.07) --
+	(416.52,150.15) --
+	(411.75,149.07) --
+	(406.98,148.09) --
+	(402.22,146.76) --
+	(397.45,145.42) --
+	(392.68,143.05) --
+	(387.91,143.24) --
+	(383.14,142.23) --
+	(378.37,139.89) --
+	(373.60,137.14) --
+	(368.83,138.45) --
+	(364.06,136.58) --
+	(359.29,132.83) --
+	(354.52,132.09) --
+	(349.76,129.32) --
+	(344.99,129.61) --
+	(340.22,127.18) --
+	(335.45,126.40) --
+	(330.68,117.34) --
+	(325.91,116.24) --
+	(321.14,109.30) --
+	(316.37,110.12) --
+	(311.60, 90.94) --
+	(306.83,106.56) --
+	(302.06,103.82) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (302.06,132.56) --
-	(306.83,131.77) --
-	(311.60,126.61) --
-	(316.37,132.19) --
-	(321.14,130.95) --
-	(325.91,131.38) --
-	(330.68,132.53) --
-	(335.45,131.74) --
-	(340.22,130.16) --
-	(344.99,131.94) --
-	(349.76,132.19) --
-	(354.52,133.66) --
-	(359.29,133.85) --
-	(364.06,134.27) --
-	(368.83,135.09) --
-	(373.60,135.16) --
-	(378.37,136.39) --
-	(383.14,137.43) --
-	(387.91,138.56) --
-	(392.68,139.61) --
-	(397.45,141.29) --
-	(402.22,142.41) --
-	(406.98,143.44) --
-	(411.75,144.40) --
-	(416.52,145.19) --
-	(421.29,145.74) --
-	(426.06,146.08) --
-	(430.83,146.24) --
-	(435.60,146.25) --
-	(440.37,146.28) --
-	(445.14,146.24) --
-	(449.91,146.14) --
-	(454.67,145.91) --
-	(459.44,145.90) --
-	(464.21,145.92) --
-	(468.98,145.92);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (302.06,139.40) --
+	(306.83,138.55) --
+	(311.60,132.98) --
+	(316.37,139.00) --
+	(321.14,137.66) --
+	(325.91,138.12) --
+	(330.68,139.37) --
+	(335.45,138.52) --
+	(340.22,136.81) --
+	(344.99,138.73) --
+	(349.76,139.00) --
+	(354.52,140.58) --
+	(359.29,140.79) --
+	(364.06,141.24) --
+	(368.83,142.12) --
+	(373.60,142.20) --
+	(378.37,143.52) --
+	(383.14,144.65) --
+	(387.91,145.87) --
+	(392.68,146.99) --
+	(397.45,148.80) --
+	(402.22,150.01) --
+	(406.98,151.12) --
+	(411.75,152.16) --
+	(416.52,153.01) --
+	(421.29,153.61) --
+	(426.06,153.97) --
+	(430.83,154.14) --
+	(435.60,154.15) --
+	(440.37,154.19) --
+	(445.14,154.14) --
+	(449.91,154.03) --
+	(454.67,153.78) --
+	(459.44,153.77) --
+	(464.21,153.79) --
+	(468.98,153.80);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (278.22,209.84) -- (468.98,209.84);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (278.22,222.69) -- (468.98,222.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (278.22,154.56) -- (468.98,154.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (278.22,163.11) -- (468.98,163.11);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,212.78) {Initial forward};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,225.63) {Initial forward};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,157.50) {Intrinsic};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,166.05) {Intrinsic};
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (278.22, 44.63) rectangle (468.98,230.49);
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (278.22, 44.63) rectangle (468.98,244.94);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02, 50.55) {1};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02, 51.35) {1};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02,153.81) {2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02,162.64) {2};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22, 54.96) --
-	(278.22, 54.96);
+\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22, 55.76) --
+	(278.22, 55.76);
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22,158.21) --
-	(278.22,158.21);
+\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22,167.05) --
+	(278.22,167.05);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.20}
@@
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (257.51,137.56) {Reproduction number $\mathcal R$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (257.51,144.79) {Basic reproduction number $\mathcal R_0$};
 \end{scope}

### 2020-04-30 observedrRb.tex
still making so many changes!!

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-29 11:23:36
+% Created by tikzDevice version 0.12.3 on 2020-04-30 02:30:28
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (238.49,238.49);
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (238.49,252.94);
 \end{scope}
 \begin{scope}
-\path[clip] ( 49.68, 44.63) rectangle (230.49,230.49);
+\path[clip] ( 49.68, 44.63) rectangle (230.49,244.95);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 49.68, 44.63) rectangle (230.49,230.49);
+\path[fill=fillColor] ( 49.68, 44.63) rectangle (230.49,244.94);
 \definecolor{drawColor}{RGB}{204,121,167}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.28,208.07) --
-	( 76.80,164.32) --
-	( 81.32,167.89) --
-	( 85.84,158.27) --
-	( 90.36,161.18) --
-	( 94.88,155.47) --
-	( 99.40,155.84) --
-	(103.92,152.83) --
-	(108.44,147.52) --
-	(112.96,144.06) --
-	(117.49,141.75) --
-	(122.01,135.58) --
-	(126.53,129.99) --
-	(131.05,127.94) --
-	(135.57,121.76) --
-	(140.09,114.68) --
-	(144.61,107.88) --
-	(149.13,100.74) --
-	(153.65, 92.87) --
-	(158.17, 84.99) --
-	(162.69, 79.17) --
-	(167.21, 73.72) --
-	(171.73, 70.27) --
-	(176.25, 67.93) --
-	(180.77, 66.45) --
-	(185.29, 65.22) --
-	(189.81, 64.69) --
-	(194.33, 64.39) --
-	(198.85, 63.99) --
-	(203.37, 63.64) --
-	(207.89, 63.40) --
-	(212.41, 63.31) --
-	(216.93, 63.30) --
-	(221.45, 63.27) --
-	(225.97, 63.25) --
-	(230.49, 63.23) --
-	(230.49, 59.98) --
-	(225.97, 59.99) --
-	(221.45, 59.99) --
-	(216.93, 59.99) --
-	(212.41, 60.01) --
-	(207.89, 60.06) --
-	(203.37, 60.28) --
-	(198.85, 60.37) --
-	(194.33, 60.61) --
-	(189.81, 60.97) --
-	(185.29, 61.22) --
-	(180.77, 61.94) --
-	(176.25, 63.28) --
-	(171.73, 64.96) --
-	(167.21, 67.32) --
-	(162.69, 70.74) --
-	(158.17, 75.21) --
-	(153.65, 80.74) --
-	(149.13, 86.75) --
-	(144.61, 93.83) --
-	(140.09,101.11) --
-	(135.57,107.97) --
-	(131.05,114.84) --
-	(126.53,119.84) --
-	(122.01,121.79) --
-	(117.49,123.07) --
-	(112.96,127.78) --
-	(108.44,125.50) --
-	(103.92,127.66) --
-	( 99.40,118.76) --
-	( 94.88,120.68) --
-	( 90.36,112.09) --
-	( 85.84,111.94) --
-	( 81.32,109.08) --
-	( 76.80,127.52) --
-	( 72.28,125.38) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] ( 72.28,220.79) --
+	( 76.80,173.63) --
+	( 81.32,177.48) --
+	( 85.84,167.11) --
+	( 90.36,170.24) --
+	( 94.88,164.09) --
+	( 99.40,164.49) --
+	(103.92,161.24) --
+	(108.44,155.52) --
+	(112.96,151.79) --
+	(117.49,149.31) --
+	(122.01,142.65) --
+	(126.53,136.63) --
+	(131.05,134.42) --
+	(135.57,127.76) --
+	(140.09,120.12) --
+	(144.61,112.80) --
+	(149.13,105.10) --
+	(153.65, 96.62) --
+	(158.17, 88.12) --
+	(162.69, 81.85) --
+	(167.21, 75.98) --
+	(171.73, 72.26) --
+	(176.25, 69.75) --
+	(180.77, 68.15) --
+	(185.29, 66.82) --
+	(189.81, 66.25) --
+	(194.33, 65.92) --
+	(198.85, 65.50) --
+	(203.37, 65.12) --
+	(207.89, 64.85) --
+	(212.41, 64.77) --
+	(216.93, 64.76) --
+	(221.45, 64.72) --
+	(225.97, 64.70) --
+	(230.49, 64.68) --
+	(230.49, 61.17) --
+	(225.97, 61.18) --
+	(221.45, 61.18) --
+	(216.93, 61.18) --
+	(212.41, 61.21) --
+	(207.89, 61.26) --
+	(203.37, 61.49) --
+	(198.85, 61.59) --
+	(194.33, 61.86) --
+	(189.81, 62.24) --
+	(185.29, 62.51) --
+	(180.77, 63.29) --
+	(176.25, 64.73) --
+	(171.73, 66.54) --
+	(167.21, 69.08) --
+	(162.69, 72.77) --
+	(158.17, 77.59) --
+	(153.65, 83.55) --
+	(149.13, 90.03) --
+	(144.61, 97.66) --
+	(140.09,105.50) --
+	(135.57,112.90) --
+	(131.05,120.30) --
+	(126.53,125.69) --
+	(122.01,127.79) --
+	(117.49,129.17) --
+	(112.96,134.25) --
+	(108.44,131.79) --
+	(103.92,134.11) --
+	( 99.40,124.53) --
+	( 94.88,126.59) --
+	( 90.36,117.34) --
+	( 85.84,117.17) --
+	( 81.32,114.10) --
+	( 76.80,133.97) --
+	( 72.28,131.66) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.28,166.88) --
-	( 76.80,144.70) --
-	( 81.32,138.94) --
-	( 85.84,139.23) --
-	( 90.36,139.42) --
-	( 94.88,138.52) --
-	( 99.40,138.58) --
-	(103.92,136.90) --
-	(108.44,135.32) --
-	(112.96,134.23) --
-	(117.49,130.80) --
-	(122.01,129.38) --
-	(126.53,125.23) --
-	(131.05,120.57) --
-	(135.57,114.75) --
-	(140.09,107.84) --
-	(144.61,100.77) --
-	(149.13, 93.23) --
-	(153.65, 86.29) --
-	(158.17, 80.06) --
-	(162.69, 75.18) --
-	(167.21, 71.07) --
-	(171.73, 67.95) --
-	(176.25, 65.68) --
-	(180.77, 64.26) --
-	(185.29, 63.27) --
-	(189.81, 62.65) --
-	(194.33, 62.22) --
-	(198.85, 61.93) --
-	(203.37, 61.76) --
-	(207.89, 61.63) --
-	(212.41, 61.56) --
-	(216.93, 61.51) --
-	(221.45, 61.49) --
-	(225.97, 61.48) --
-	(230.49, 61.47);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.28,176.39) --
+	( 76.80,152.48) --
+	( 81.32,146.27) --
+	( 85.84,146.59) --
+	( 90.36,146.79) --
+	( 94.88,145.82) --
+	( 99.40,145.88) --
+	(103.92,144.07) --
+	(108.44,142.38) --
+	(112.96,141.20) --
+	(117.49,137.50) --
+	(122.01,135.97) --
+	(126.53,131.50) --
+	(131.05,126.47) --
+	(135.57,120.20) --
+	(140.09,112.76) --
+	(144.61,105.14) --
+	(149.13, 97.01) --
+	(153.65, 89.53) --
+	(158.17, 82.81) --
+	(162.69, 77.55) --
+	(167.21, 73.12) --
+	(171.73, 69.77) --
+	(176.25, 67.31) --
+	(180.77, 65.78) --
+	(185.29, 64.72) --
+	(189.81, 64.05) --
+	(194.33, 63.59) --
+	(198.85, 63.28) --
+	(203.37, 63.09) --
+	(207.89, 62.95) --
+	(212.41, 62.87) --
+	(216.93, 62.83) --
+	(221.45, 62.80) --
+	(225.97, 62.79) --
+	(230.49, 62.78);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 49.68,140.72) -- (230.49,140.72);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 49.68,148.19) -- (230.49,148.19);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.68, 80.10) -- (230.49, 80.10);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.68, 82.86) -- (230.49, 82.86);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.97,143.66) {Initial forward};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.97,151.13) {Initial forward};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.97, 83.04) {Intrinsic};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (225.97, 85.80) {Intrinsic};
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] ( 49.68, 44.63) rectangle (230.49,230.49);
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] ( 49.68, 44.63) rectangle (230.49,244.94);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.30}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48, 74.64) {5.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48, 77.32) {5.0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,109.06) {5.5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,114.42) {5.5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,143.48) {6.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,151.51) {6.0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,177.90) {6.5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,188.60) {6.5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,212.32) {7.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 42.48,225.70) {7.0};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68, 79.05) --
-	( 49.68, 79.05);
+\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68, 81.73) --
+	( 49.68, 81.73);
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,113.47) --
-	( 49.68,113.47);
+\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,118.82) --
+	( 49.68,118.82);
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,147.89) --
-	( 49.68,147.89);
+\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,155.92) --
+	( 49.68,155.92);
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,182.31) --
-	( 49.68,182.31);
+\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,193.01) --
+	( 49.68,193.01);
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,216.72) --
-	( 49.68,216.72);
+\path[draw=drawColor,line width= 0.8pt,line join=round] ( 45.68,230.11) --
+	( 49.68,230.11);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (238.49,  0.00) rectangle (476.98,238.49);
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round,fill=fillColor] (238.49,  0.00) rectangle (476.98,252.94);
 \end{scope}
 \begin{scope}
-\path[clip] (278.22, 44.63) rectangle (468.98,230.49);
+\path[clip] (278.22, 44.63) rectangle (468.98,244.95);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (278.22, 44.63) rectangle (468.98,230.49);
+\path[fill=fillColor] (278.22, 44.63) rectangle (468.98,244.94);
 \definecolor{drawColor}{RGB}{204,121,167}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (302.06,220.91) --
-	(306.83,186.06) --
-	(311.60,184.29) --
-	(316.37,180.56) --
-	(321.14,171.77) --
-	(325.91,171.49) --
-	(330.68,168.64) --
-	(335.45,166.60) --
-	(340.22,160.21) --
-	(344.99,158.84) --
-	(349.76,159.16) --
-	(354.52,154.78) --
-	(359.29,150.97) --
-	(364.06,149.69) --
-	(368.83,146.44) --
-	(373.60,141.11) --
-	(378.37,135.50) --
-	(383.14,131.30) --
-	(387.91,126.00) --
-	(392.68,119.60) --
-	(397.45,115.57) --
-	(402.22,111.47) --
-	(406.98,107.65) --
-	(411.75,106.09) --
-	(416.52,104.82) --
-	(421.29,103.30) --
-	(426.06,102.79) --
-	(430.83,102.24) --
-	(435.60,101.92) --
-	(440.37,101.04) --
-	(445.14,100.74) --
-	(449.91,100.71) --
-	(454.67,100.71) --
-	(459.44,100.71) --
-	(464.21,100.71) --
-	(468.98,100.70) --
-	(468.98, 97.00) --
-	(464.21, 97.00) --
-	(459.44, 97.00) --
-	(454.67, 97.00) --
-	(449.91, 97.02) --
-	(445.14, 97.05) --
-	(440.37, 97.67) --
-	(435.60, 97.80) --
-	(430.83, 98.05) --
-	(426.06, 98.33) --
-	(421.29, 98.61) --
-	(416.52, 99.34) --
-	(411.75,100.93) --
-	(406.98,102.92) --
-	(402.22,105.37) --
-	(397.45,108.32) --
-	(392.68,112.30) --
-	(387.91,116.70) --
-	(383.14,122.38) --
-	(378.37,127.38) --
-	(373.60,131.82) --
-	(368.83,137.05) --
-	(364.06,140.82) --
-	(359.29,143.36) --
-	(354.52,143.56) --
-	(349.76,142.51) --
-	(344.99,144.89) --
-	(340.22,141.25) --
-	(335.45,145.85) --
-	(330.68,140.31) --
-	(325.91,142.20) --
-	(321.14,135.02) --
-	(316.37,142.00) --
-	(311.60,128.88) --
-	(306.83,145.02) --
-	(302.06,169.68) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (302.06,234.62) --
+	(306.83,197.06) --
+	(311.60,195.15) --
+	(316.37,191.13) --
+	(321.14,181.66) --
+	(325.91,181.35) --
+	(330.68,178.29) --
+	(335.45,176.09) --
+	(340.22,169.20) --
+	(344.99,167.73) --
+	(349.76,168.07) --
+	(354.52,163.34) --
+	(359.29,159.24) --
+	(364.06,157.86) --
+	(368.83,154.36) --
+	(373.60,148.61) --
+	(378.37,142.57) --
+	(383.14,138.04) --
+	(387.91,132.32) --
+	(392.68,125.43) --
+	(397.45,121.09) --
+	(402.22,116.67) --
+	(406.98,112.55) --
+	(411.75,110.87) --
+	(416.52,109.50) --
+	(421.29,107.86) --
+	(426.06,107.31) --
+	(430.83,106.72) --
+	(435.60,106.37) --
+	(440.37,105.43) --
+	(445.14,105.10) --
+	(449.91,105.07) --
+	(454.67,105.07) --
+	(459.44,105.07) --
+	(464.21,105.07) --
+	(468.98,105.06) --
+	(468.98,101.07) --
+	(464.21,101.08) --
+	(459.44,101.08) --
+	(454.67,101.08) --
+	(449.91,101.09) --
+	(445.14,101.13) --
+	(440.37,101.79) --
+	(435.60,101.93) --
+	(430.83,102.21) --
+	(426.06,102.51) --
+	(421.29,102.81) --
+	(416.52,103.59) --
+	(411.75,105.30) --
+	(406.98,107.46) --
+	(402.22,110.09) --
+	(397.45,113.28) --
+	(392.68,117.56) --
+	(387.91,122.30) --
+	(383.14,128.42) --
+	(378.37,133.81) --
+	(373.60,138.60) --
+	(368.83,144.24) --
+	(364.06,148.30) --
+	(359.29,151.04) --
+	(354.52,151.25) --
+	(349.76,150.12) --
+	(344.99,152.69) --
+	(340.22,148.77) --
+	(335.45,153.72) --
+	(330.68,147.75) --
+	(325.91,149.79) --
+	(321.14,142.05) --
+	(316.37,149.57) --
+	(311.60,135.43) --
+	(306.83,152.82) --
+	(302.06,179.40) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (302.06,188.49) --
-	(306.83,168.18) --
-	(311.60,158.33) --
-	(316.37,159.72) --
-	(321.14,157.07) --
-	(325.91,156.54) --
-	(330.68,156.67) --
-	(335.45,155.15) --
-	(340.22,152.92) --
-	(344.99,153.04) --
-	(349.76,150.77) --
-	(354.52,150.34) --
-	(359.29,147.58) --
-	(364.06,144.69) --
-	(368.83,140.95) --
-	(373.60,135.85) --
-	(378.37,131.20) --
-	(383.14,125.97) --
-	(387.91,120.91) --
-	(392.68,116.05) --
-	(397.45,112.24) --
-	(402.22,108.72) --
-	(406.98,105.97) --
-	(411.75,103.93) --
-	(416.52,102.50) --
-	(421.29,101.44) --
-	(426.06,100.72) --
-	(430.83,100.16) --
-	(435.60, 99.70) --
-	(440.37, 99.45) --
-	(445.14, 99.21) --
-	(449.91, 99.01) --
-	(454.67, 98.73) --
-	(459.44, 98.68) --
-	(464.21, 98.67) --
-	(468.98, 98.65);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (302.06,199.67) --
+	(306.83,177.79) --
+	(311.60,167.17) --
+	(316.37,168.67) --
+	(321.14,165.81) --
+	(325.91,165.25) --
+	(330.68,165.39) --
+	(335.45,163.75) --
+	(340.22,161.34) --
+	(344.99,161.47) --
+	(349.76,159.03) --
+	(354.52,158.56) --
+	(359.29,155.58) --
+	(364.06,152.47) --
+	(368.83,148.44) --
+	(373.60,142.95) --
+	(378.37,137.94) --
+	(383.14,132.30) --
+	(387.91,126.84) --
+	(392.68,121.60) --
+	(397.45,117.50) --
+	(402.22,113.71) --
+	(406.98,110.74) --
+	(411.75,108.55) --
+	(416.52,107.00) --
+	(421.29,105.86) --
+	(426.06,105.08) --
+	(430.83,104.48) --
+	(435.60,103.98) --
+	(440.37,103.71) --
+	(445.14,103.46) --
+	(449.91,103.23) --
+	(454.67,102.94) --
+	(459.44,102.88) --
+	(464.21,102.87) --
+	(468.98,102.85);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (278.22,156.15) -- (468.98,156.15);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (278.22,164.82) -- (468.98,164.82);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (278.22,106.40) -- (468.98,106.40);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (278.22,111.20) -- (468.98,111.20);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,159.09) {Initial forward};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,167.76) {Initial forward};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,109.34) {Intrinsic};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.42] at (464.21,114.14) {Intrinsic};
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (278.22, 44.63) rectangle (468.98,230.49);
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (278.22, 44.63) rectangle (468.98,244.94);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02,105.28) {2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02,110.33) {2};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02,198.20) {3};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (271.02,210.49) {3};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22,109.68) --
-	(278.22,109.68);
+\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22,114.74) --
+	(278.22,114.74);
 
-\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22,202.61) --
-	(278.22,202.61);
+\path[draw=drawColor,line width= 0.8pt,line join=round] (274.22,214.90) --
+	(278.22,214.90);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (476.98,238.49);
+\path[clip] (  0.00,  0.00) rectangle (476.98,252.94);
 \definecolor{drawColor}{gray}{0.20}

### 2020-04-30 serial.tex
still making so many changes!!

@@
 
-\djde{deleted ``At the individual-level, both forward and backward
-  \emph{measurements} provide identical measures; in other words, we
-  can express the total density of primary and secondary events
-  occurring at time $\pt$ and $\st$, respectively, using both forward
-  and backward delay \emph{distributions}:'' and ended up rewriting
-  the following paragraph...}
-
 At the individual level, both forward and backward \emph{perspectives}
@@
 where $r$ is the exponential growth rate.
+For faster epidemic (higher $r$), the backward delay distributions will be shorter.
 Therefore, the backward delay distributions will be generally different from the forward delay distributions even if we are measuring time delays that are intrinsic to life history of a disease (e.g., incubation period).
@@
 
-Finally, the forward serial-interval distribution is proportional to $\total (\pt, \pt+\tau)$ because it is conditional on the cohort of infectors who became symptomatic at time $\pt$:
+Finally, the forward serial-interval distribution $f_\pt(\tau)$ is proportional to $\total (\pt, \pt+\tau)$ because it is conditional on the cohort of infectors who became symptomatic at time $\pt$:
 \begin{equation}
@@
 The constant of proportionality is then equal to the total number of infection caused by individuals who became symptomatic at time $\pt$.
-Likewise, the backward serial-interval distribution is proportional to $\total (\st-\tau, \st)$ because it is conditional on the cohort of infectees who became symptomatic at time $\st$:
+Likewise, the backward serial-interval distribution $b_\st(\tau)$ is proportional to $\total (\st-\tau, \st)$ because it is conditional on the cohort of infectees who became symptomatic at time $\st$:
 \begin{equation}
@@
 During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
-When incidence grows exponentially, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the reproduction number \RR based on the Euler-Lotka equation \citep{wallinga2007generation}:
+When incidence grows exponentially, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation};
+in this case, we focus on the estimates of the basic reproduction number \Ro (the value of \RR in a fully susceptible population):
 \begin{equation}
-\frac{1}{\RR} = \int_0^\infty \exp(-r\tau) g(\tau) \dtau.
+\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) g(\tau) \dtau.
 \end{equation}
 Analogous to the intrinsic generation-interval distribution, 
-forward serial-interval distributions describe the renewal process of symptomatic cases.
-Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to provide the identical $r$--\RR link as the intrinsic generation-interval distribution:
+forward serial-interval distributions, by definition, describe the renewal process of infection based on symptom onset dates.
+Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to provide the identical $r$--\Ro link as the intrinsic generation-interval distribution:
 \begin{equation}
-\frac{1}{\RR} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
+\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
 \end{equation}
@@
 
-We use a simulation-based approach to compare the estimates of \RR based on the serial- and generation-interval distributions. 
+We use a simulation-based approach to compare the estimates of \Ro based on the serial- and generation-interval distributions. 
 To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and correlation $\rho$;
@@
 the forward incubation period $X_{1,i}$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
-We then calculate the reproduction number \RR using the empirical estimator:
+We then calculate the basic reproduction number \Ro using the empirical estimator:
 \begin{equation}
-\RR = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r F_i)}.
+\Ro = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r F_i)}.
 \end{equation}
-We compare this with an estimate of \RR based on the intrinsic serial-interval distribution in which the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
+We compare this with an estimate of \Ro based on the intrinsic serial-interval distribution in which the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
 \begin{equation}
@@
 
-The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $\gdist(\tau)$ give identical estimates of \RR regardless of the correlation $\rho$ between the forward incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
-However, using the intrinsic serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \RR;
+The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $\gdist(\tau)$ give identical estimates of \Ro regardless of the correlation $\rho$ between the forward incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
+However, using the intrinsic serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \Ro;
 as $r$ increases, \Rintrinsic saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
@@
 \textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
-(A). The initial forward serial-interval distribution give a correct link between the exponential growth rate $r$ and the reproduction number \RR.
-(B) The intrinsic serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and \RR (and underestimates \RR compared to the intrinsic generation-interval distribution).
+(A). The initial forward serial-interval distributions give a correct link between the exponential growth rate $r$ and the reproduction number \Ro.
+(B) The intrinsic serial-interval distributions give an incorrect link between $r$ and \Ro.
 (C) The mean initial forward serial interval during the exponential growth phase depends on $r$.
@@
 
-Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different distributions are able to give identical estimates of \RR.
-In general, generation-interval distributions with higher means and less variability are expected to give higher \RR for a given $r$ \citep{wallinga2007generation, park2019practical}.
+Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different distributions are able to give identical estimates of \Ro.
+In general, generation-interval distributions with higher means and less variability are expected to give higher \Ro for a given $r$ \citep{wallinga2007generation, park2019practical}.
 In this case, the initial forward serial intervals during the exponential growth phase have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
-The effects of higher means (which increases \RR) and higher variability (which decreases \RR) cancel out exactly;
-therefore, we can estimate the same \RR using both initial forward serial and intrinsic generation intervals.
+The effects of higher means (which increases \Ro) and higher variability (which decreases \Ro) cancel out exactly;
+this allows us to estimate the same \Ro using both initial forward serial and intrinsic generation intervals.
 On the other hand, intrinsic serial intervals have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are wider (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
-therefore, we underestimate \RR when we use the intrinsic serial-interval distribution.
+therefore, we underestimate \Ro when we use the intrinsic serial-interval distribution.
 
@@
 cumulative incidence from the stochastic simulations in panel A are shown without averaging.
-Forward incubation periods and intrinsic generation-intervals are assumed to be independent of each other: $h(x_0, \sigma) = k(x_0) g(\sigma)$.
+Forward incubation periods and intrinsic generation-intervals are assumed to be independent of each other.
 See Table 1 for parameter values.
 }
+\label{fig:epi}
 \end{center}
-\label{fig:epi}
 \end{figure}
@@
 The mean forward incubation period remains constant throughout an epidemic as assumed (\fref{epi}B).
-The mean forward generation interval decreases slightly as the epidemic progresses because an infected individual is less likely to infect another person as the proportion of susceptible individuals decreases (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
+The mean forward generation interval decreases slightly as the epidemic progresses due to susceptible depletion (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
 In contrast, the mean forward serial interval decreases over time (\fref{epi}D).
@@
 In this case, the increase in the mean backward incubation period directly translates to the decrease in the mean forward serial interval.
-We note that the relative contributions of the three distributions depend on their shapes and correlations between incubation periods and generation intervals --- as discussed earlier, the backward incubation period has \emph{no} effect on the forward serial intervals in the special case of an SEIR model, because transmission always occurs after symptom onset.
+Therefore, the forward serial intervals can decrease over time even in the absence of significant depletion of the susceptible pool;
+decrease in incidence via intervention strategies can still cause the backward incubation period to increase, which in turn can decrease serial intervals. 
+In general, relative contributions of the three distributions depend on their shapes, correlations between incubation periods and generation intervals, and overall epidemiological dynamics.
 
-Qualitative patterns in the mean backward delays is robust across all delay distributions because they are predominantly driven by the changes in incidence (\fref{epi}D--F).
-When incidence increases exponentially, individuals are more likely to have been infected more recently and therefore, we are more likely to observe shorter intervals.
+Qualitative patterns in the mean backward delays is robust across all delay distributions because they are predominantly driven by the changes in incidence, which in turn affects cohort sizes (\fref{epi}D--F; \eref{backward}).
+When incidence increases exponentially, individuals are more likely to have been infected more recently and therefore, we are more likely to observe shorter intervals (\eref{backexp}).
 When incidence decreases, we are more likely to observe longer intervals for similar but opposite reasons.
@@
 (B) Changes in the estimate of \Ro based on the cohort-averaged serial intervals over time.
-Dashed lines represent \Ro.
+Black dashed lines represent the mean initial forward serial interval and \Ro.
+Black solid lines represent the mean intrinsic serial interval and \Rintrinsic.
+Colored solid lines represent the mean estimates of \Ro across 10 stochastic simulations.
+Colored ribbons represent the range of estimates of \Ro across 10 stochastic simulations.
 }
@@
 Now, we turn to practical issues.
-Serial intervals are typically calculated from line-list data (\fref{obsrR}A).
+Serial intervals are typically measured from line-list data (\fref{obsrR}A).
 When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
-for example, if we were to measure serial intervals on Day 8 in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
+for example, if we were to measure serial intervals on Day 8 as in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
 \fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of the basic reproduction number \Ro in our stochastic simulations.
@@
 (A--B) forward and backward serial intervals over time.
-Points represent the means. Vertical error bars represent the observed maximum and minimum values.
-Solid lines and ribbons represent the estimated locally estimated scatterplot smoothing (LOESS) fits and associated 95\% confidence intervals.
+Points represent the means. 
+Vertical error bars represent the 95\% equi-tailed quantiles.
+Solid lines represent the estimated locally estimated scatterplot smoothing (LOESS) fits.
 The dashed line represents the maximum observable delay for each primary cohort calculated from the most recent observed symptom onset date.
-(C) Cohort-averaged estimates of \RR assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
+(C) Cohort-averaged estimates of \Ro assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
 Ribbons represent the associated 95\% bootstrap confidence intervals.
+The data were taken from Supplementary Materials of \cite{du2020serial}.
 }
@@
 \fref{du}A shows that the mean forward serial interval decreases over time.
-While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the maximum observed serial intervals and maximum \emph{observable} serial intervals),  increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution.
-\fref{du}B shows that the mean backward serial interval increases over time.
+While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum \emph{observable} serial intervals), increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution.
+The decrease in the mean forward serial interval is likely to be cause by increase in the mean backward serial intervals as well as increase in mitigation efforts.
+\fref{du}B shows that the mean backward serial interval increases over time, reflecting decrease in incidence over time.
+
 While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculate earlier based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
 These results indicate that previous estimates of incubation period and generation-intervals may have been underestimated as neither study explicitly accounts for right-censoring (Table 1).
-%We do not explicitly account for the right-censoring as it is beyond the scope of this study.
 
-\fref{du}C shows the cohort-averaged estimates of \Ro, which remain roughly constant until day 7 and suddenly decreases, as expected from our simulation study (\fref{obsrR}).
+\fref{du}C shows the cohort-averaged estimates of \Ro, which remain roughly constant until day 7 and suddenly decreases;
+this sudden decrease is indicative of changes in the forward serial intervals as shown in our simulation study (\fref{obsrR}).
 The estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}.
 We note that early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
-This example clearly demonstrates the danger of simply averaging the observed serial intervals and calculating the reproduction number using them.
+This example clearly demonstrates the danger of using the observed serial intervals to calculate the basic reproduction number without integrating serial intervals into cohorts..
 
@@
 To our knowledge, most, if not all, existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
-Our study provides a rationale for reassessing estimates of serial-interval distributions of the COVID-19 pandemic.
+Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \Ro, of the COVID-19 pandemic.
 

### 2020-04-30 serial_analysis.tex
still making so many changes!!

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-20 00:29:27
+% Created by tikzDevice version 0.12.3 on 2020-04-30 02:40:57
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,139.66) --
-	( 45.69,139.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,139.66) --
-	( 45.69,174.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,174.34) --
-	( 45.69,174.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,114.90) --
-	( 51.21,114.90);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,114.90) --
-	( 51.21,169.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,169.39) --
-	( 51.21,169.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,134.71) --
-	( 56.73,134.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,134.71) --
-	( 56.73,154.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.52) --
-	( 56.73,154.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,104.99) --
-	( 62.25,104.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,104.99) --
-	( 62.25,174.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,174.34) --
-	( 62.25,174.34);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,173.47) --
+	( 45.69,173.47);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,173.47) --
+	( 45.69,142.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,142.26) --
+	( 45.69,142.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,167.16) --
+	( 51.21,167.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,167.16) --
+	( 51.21,115.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,115.39) --
+	( 51.21,115.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.03) --
+	( 56.73,154.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.03) --
+	( 56.73,135.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,135.21) --
+	( 56.73,135.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,173.35) --
+	( 62.25,173.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,173.35) --
+	( 62.25,107.47);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,107.47) --
+	( 62.25,107.47);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,139.66) --
-	( 73.29,139.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,139.66) --
-	( 73.29,189.20);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,189.20) --
-	( 73.29,189.20);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,134.71) --
-	( 78.81,134.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,134.71) --
-	( 78.81,154.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.52) --
-	( 78.81,154.52);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,187.96) --
+	( 73.29,187.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,187.96) --
+	( 73.29,140.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,140.90) --
+	( 73.29,140.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.03) --
+	( 78.81,154.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.03) --
+	( 78.81,135.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,135.21) --
+	( 78.81,135.21);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,119.85) --
-	( 89.85,119.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,119.85) --
-	( 89.85,159.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,159.48) --
-	( 89.85,159.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 80.22) --
-	( 95.37, 80.22);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 80.22) --
-	( 95.37,174.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,174.34) --
-	( 95.37,174.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 95.08) --
-	(100.89, 95.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 95.08) --
-	(100.89,164.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,164.43) --
-	(100.89,164.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 90.13) --
-	(106.42, 90.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 90.13) --
-	(106.42,149.57);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,149.57) --
-	(106.42,149.57);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,158.36) --
+	( 89.85,158.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,158.36) --
+	( 89.85,120.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,120.22) --
+	( 89.85,120.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,168.89) --
+	( 95.37,168.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,168.89) --
+	( 95.37, 85.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 85.67) --
+	( 95.37, 85.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,157.00) --
+	(100.89,157.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,157.00) --
+	(100.89, 96.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 96.94) --
+	(100.89, 96.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,147.34) --
+	(106.42,147.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,147.34) --
+	(106.42, 94.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 94.59) --
+	(106.42, 94.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,156.63) --
+	(111.94,156.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,156.63) --
+	(111.94, 85.17);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94, 85.17) --
-	(111.94,159.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,159.48) --
-	(111.94,159.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 90.13) --
-	(117.46, 90.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 90.13) --
-	(117.46,164.43);
-
 \path[draw=drawColor,line width= 0.6pt,line join=round] (117.46,164.43) --
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 45.55) --
-	(122.98, 45.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 45.55) --
-	(122.98,169.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,169.39) --
-	(122.98,169.39);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46,164.43) --
+	(117.46, 94.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 94.22) --
+	(117.46, 94.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,163.56) --
+	(122.98,163.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,163.56) --
+	(122.98, 72.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 72.91) --
+	(122.98, 72.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,142.39) --
+	(128.50,142.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,142.39) --
+	(128.50, 85.17);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50, 85.17) --
-	(128.50,149.57);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,149.57) --
-	(128.50,149.57);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,141.52) --
+	(134.02,141.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,141.52) --
+	(134.02, 90.13);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02, 90.13) --
-	(134.02,144.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,144.62) --
-	(134.02,144.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 65.36) --
-	(139.54, 65.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 65.36) --
-	(139.54,134.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,134.71) --
-	(139.54,134.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 60.41) --
-	(145.06, 60.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 60.41) --
-	(145.06,144.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,144.62) --
-	(145.06,144.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 65.36) --
-	(150.58, 65.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 65.36) --
-	(150.58,149.57);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,149.57) --
-	(150.58,149.57);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,125.30) --
+	(139.54,125.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,125.30) --
+	(139.54, 70.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 70.07) --
+	(139.54, 70.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,143.75) --
+	(145.06,143.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,143.75) --
+	(145.06, 65.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 65.36) --
+	(145.06, 65.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,135.45) --
+	(150.58,135.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,135.45) --
+	(150.58, 70.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 70.07) --
+	(150.58, 70.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,129.26) --
+	(156.10,129.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,129.26) --
+	(156.10, 40.59);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10, 40.59) --
-	(156.10,134.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,134.71) --
-	(156.10,134.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 50.50) --
-	(161.62, 50.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 50.50) --
-	(161.62,129.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,129.76) --
-	(161.62,129.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 60.41) --
-	(167.14, 60.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 60.41) --
-	(167.14,109.94);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,125.79) --
+	(161.62,125.79);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,125.79) --
+	(161.62, 58.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 58.43) --
+	(161.62, 58.43);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 65.36) --
-	(172.66, 65.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 65.36) --
-	(172.66,109.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,109.94) --
-	(172.66,109.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 75.27) --
-	(178.19, 75.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 75.27) --
-	(178.19,109.94);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14,109.94) --
+	(167.14, 64.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 64.37) --
+	(167.14, 64.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,107.96) --
+	(172.66,107.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,107.96) --
+	(172.66, 73.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 73.29) --
+	(172.66, 73.29);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.17) --
-	(183.71, 85.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.17) --
-	(183.71,100.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19,109.94) --
+	(178.19, 77.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 77.74) --
+	(178.19, 77.74);
 
@@
 
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71,100.04) --
+	(183.71, 85.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.67) --
+	(183.71, 85.67);
+
 \path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 35.64) --
-	(211.31, 35.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 35.64) --
-	(211.31, 85.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 85.17) --
-	(211.31, 85.17);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor,fill opacity=0.20] ( 34.64,171.01) --
-	( 36.88,169.05) --
-	( 39.12,167.14) --
-	( 41.35,165.27) --
-	( 43.59,163.46) --
-	( 45.83,161.68) --
-	( 48.06,159.96) --
-	( 50.30,158.29) --
-	( 52.54,156.67) --
-	( 54.77,155.10) --
-	( 57.01,153.59) --
-	( 59.24,152.12) --
-	( 61.48,150.70) --
-	( 63.72,149.32) --
-	( 65.95,147.97) --
-	( 68.19,146.66) --
-	( 70.43,145.37) --
-	( 72.66,144.09) --
-	( 74.90,142.81) --
-	( 77.13,141.54) --
-	( 79.37,140.25) --
-	( 81.61,138.94) --
-	( 83.84,137.61) --
-	( 86.08,136.26) --
-	( 88.32,134.88) --
-	( 90.55,133.47) --
-	( 92.79,132.04) --
-	( 95.02,130.59) --
-	( 97.26,129.14) --
-	( 99.50,127.74) --
-	(101.73,126.42) --
-	(103.97,125.19) --
-	(106.21,124.07) --
-	(108.44,123.07) --
-	(110.68,122.19) --
-	(112.91,121.41) --
-	(115.15,120.75) --
-	(117.39,120.02) --
-	(119.62,119.00) --
-	(121.86,117.91) --
-	(124.10,116.89) --
-	(126.33,115.70) --
-	(128.57,114.48) --
-	(130.80,113.34) --
-	(133.04,112.27) --
-	(135.28,111.11) --
-	(137.51,109.84) --
-	(139.75,108.69) --
-	(141.99,107.59) --
-	(144.22,106.58) --
-	(146.46,105.54) --
-	(148.69,104.57) --
-	(150.93,103.63) --
-	(153.17,102.62) --
-	(155.40,101.65) --
-	(157.64,100.75) --
-	(159.88, 99.93) --
-	(162.11, 99.20) --
-	(164.35, 98.48) --
-	(166.58, 97.75) --
-	(168.82, 97.00) --
-	(171.06, 96.23) --
-	(173.29, 95.46) --
-	(175.53, 94.69) --
-	(177.77, 93.95) --
-	(180.00, 93.23) --
-	(182.24, 92.56) --
-	(184.47, 91.94) --
-	(186.71, 91.37) --
-	(188.95, 90.85) --
-	(191.18, 90.39) --
-	(193.42, 89.99) --
-	(195.66, 89.64) --
-	(197.89, 89.34) --
-	(200.13, 89.10) --
-	(202.36, 88.91) --
-	(204.60, 88.77) --
-	(206.84, 88.68) --
-	(209.07, 88.64) --
-	(211.31, 88.65) --
-	(211.31, 46.93) --
-	(209.07, 50.41) --
-	(206.84, 53.75) --
-	(204.60, 56.97) --
-	(202.36, 60.04) --
-	(200.13, 62.98) --
-	(197.89, 65.79) --
-	(195.66, 68.45) --
-	(193.42, 70.97) --
-	(191.18, 73.35) --
-	(188.95, 75.58) --
-	(186.71, 77.67) --
-	(184.47, 79.62) --
-	(182.24, 81.42) --
-	(180.00, 83.08) --
-	(177.77, 84.60) --
-	(175.53, 86.01) --
-	(173.29, 87.29) --
-	(171.06, 88.48) --
-	(168.82, 89.58) --
-	(166.58, 90.59) --
-	(164.35, 91.53) --
-	(162.11, 92.39) --
-	(159.88, 93.23) --
-	(157.64, 94.16) --
-	(155.40, 95.15) --
-	(153.17, 96.16) --
-	(150.93, 97.18) --
-	(148.69, 98.28) --
-	(146.46, 99.36) --
-	(144.22,100.40) --
-	(141.99,101.43) --
-	(139.75,102.42) --
-	(137.51,103.58) --
-	(135.28,104.76) --
-	(133.04,105.87) --
-	(130.80,107.14) --
-	(128.57,108.40) --
-	(126.33,109.53) --
-	(124.10,110.53) --
-	(121.86,111.53) --
-	(119.62,112.53) --
-	(117.39,113.40) --
-	(115.15,114.13) --
-	(112.91,114.80) --
-	(110.68,115.58) --
-	(108.44,116.44) --
-	(106.21,117.32) --
-	(103.97,118.24) --
-	(101.73,119.19) --
-	( 99.50,120.18) --
-	( 97.26,121.23) --
-	( 95.02,122.36) --
-	( 92.79,123.51) --
-	( 90.55,124.65) --
-	( 88.32,125.78) --
-	( 86.08,126.91) --
-	( 83.84,128.03) --
-	( 81.61,129.15) --
-	( 79.37,130.26) --
-	( 77.13,131.35) --
-	( 74.90,132.43) --
-	( 72.66,133.48) --
-	( 70.43,134.49) --
-	( 68.19,135.47) --
-	( 65.95,136.39) --
-	( 63.72,137.26) --
-	( 61.48,138.06) --
-	( 59.24,138.79) --
-	( 57.01,139.45) --
-	( 54.77,140.04) --
-	( 52.54,140.55) --
-	( 50.30,140.98) --
-	( 48.06,141.33) --
-	( 45.83,141.61) --
-	( 43.59,141.82) --
-	( 41.35,141.95) --
-	( 39.12,142.01) --
-	( 36.88,142.01) --
-	( 34.64,141.94) --
-	cycle;
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 83.94) --
+	(211.31, 83.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 83.94) --
+	(211.31, 36.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 36.88) --
+	(211.31, 36.88);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (122.98,  7.64) {Primary cohort time (days)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (122.98,  7.64) {Symptom onset day (infector)};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (251.45,105.23) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (275.01, 47.70) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (280.90,110.02) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (286.79, 81.26) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (292.68,124.40) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (298.57, 90.85) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (304.45, 83.31) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.34, 98.52) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (316.23, 87.25) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (322.12, 95.32) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (328.01,102.53) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,105.54) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.79,106.72) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.68,105.89) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (351.57,100.32) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (357.45,107.92) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.34,112.15) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.23,113.22) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,111.54) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.01,112.98) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.90,115.62) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (392.79,121.14) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.68,124.15) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (404.56,122.56) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (410.45,139.38) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.34,133.19) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (422.23,167.55) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (428.12,148.37) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,105.23) --
-	(251.45,105.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,105.23) --
-	(251.45,105.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,105.23) --
-	(251.45,105.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 47.70) --
-	(275.01, 47.70);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 47.70) --
-	(275.01, 47.70);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 47.70) --
-	(275.01, 47.70);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,105.23) --
-	(280.90,105.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,105.23) --
-	(280.90,114.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,114.82) --
-	(280.90,114.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.26) --
-	(286.79, 81.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.26) --
-	(286.79, 81.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.26) --
-	(286.79, 81.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,124.40) --
-	(292.68,124.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,124.40) --
-	(292.68,124.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,124.40) --
-	(292.68,124.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 90.85) --
-	(298.57, 90.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 90.85) --
-	(298.57, 90.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 90.85) --
-	(298.57, 90.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45, 42.91) --
-	(304.45, 42.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45, 42.91) --
-	(304.45,138.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45,138.78) --
-	(304.45,138.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 86.05) --
-	(310.34, 86.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 86.05) --
-	(310.34,133.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34,133.99) --
-	(310.34,133.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23, 62.08) --
-	(316.23, 62.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23, 62.08) --
-	(316.23,105.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23,105.23) --
-	(316.23,105.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12, 52.50) --
-	(322.12, 52.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12, 52.50) --
-	(322.12,153.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12,153.17) --
-	(322.12,153.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01, 66.88) --
-	(328.01, 66.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01, 66.88) --
-	(328.01,157.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01,157.96) --
-	(328.01,157.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90, 71.67) --
-	(333.90, 71.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90, 71.67) --
-	(333.90,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,162.75) --
-	(333.90,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79, 62.08) --
-	(339.79, 62.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79, 62.08) --
-	(339.79,167.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79,167.55) --
-	(339.79,167.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68, 71.67) --
-	(345.68, 71.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68, 71.67) --
-	(345.68,172.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68,172.34) --
-	(345.68,172.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57, 66.88) --
-	(351.57, 66.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57, 66.88) --
-	(351.57,133.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57,133.99) --
-	(351.57,133.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45, 38.12) --
-	(357.45, 38.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45, 38.12) --
-	(357.45,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45,162.75) --
-	(357.45,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34, 90.85) --
-	(363.34, 90.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34, 90.85) --
-	(363.34,172.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34,172.34) --
-	(363.34,172.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23, 76.47) --
-	(369.23, 76.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23, 76.47) --
-	(369.23,157.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23,157.96) --
-	(369.23,157.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12, 86.05) --
-	(375.12, 86.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12, 86.05) --
-	(375.12,157.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12,157.96) --
-	(375.12,157.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01, 86.05) --
-	(381.01, 86.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01, 86.05) --
-	(381.01,148.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01,148.37) --
-	(381.01,148.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90, 71.67) --
-	(386.90, 71.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90, 71.67) --
-	(386.90,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90,162.75) --
-	(386.90,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79, 86.05) --
-	(392.79, 86.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79, 86.05) --
-	(392.79,186.72);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (251.45,108.69) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (275.01, 43.54) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (280.90,114.12) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (286.79, 81.54) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (292.68,130.40) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (298.57, 92.40) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (304.45, 83.87) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.34,101.09) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (316.23, 88.33) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (322.12, 97.47) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (328.01,105.63) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,109.04) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.79,110.37) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.68,109.44) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (351.57,103.13) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (357.45,111.73) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.34,116.53) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.23,117.73) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,115.83) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.01,117.47) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.90,120.45) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (392.79,126.70) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.68,130.12) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (404.56,128.31) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (410.45,147.37) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.34,140.35) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (422.23,179.26) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (428.12,157.54) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,108.69) --
+	(251.45,108.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,108.69) --
+	(251.45,108.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,108.69) --
+	(251.45,108.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 43.54) --
+	(275.01, 43.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 43.54) --
+	(275.01, 43.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 43.54) --
+	(275.01, 43.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,119.27) --
+	(280.90,119.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,119.27) --
+	(280.90,108.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,108.96) --
+	(280.90,108.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.54) --
+	(286.79, 81.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.54) --
+	(286.79, 81.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.54) --
+	(286.79, 81.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,130.40) --
+	(292.68,130.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,130.40) --
+	(292.68,130.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,130.40) --
+	(292.68,130.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 92.40) --
+	(298.57, 92.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 92.40) --
+	(298.57, 92.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 92.40) --
+	(298.57, 92.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45,139.36) --
+	(304.45,139.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45,139.36) --
+	(304.45, 38.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45, 38.12) --
+	(304.45, 38.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34,136.92) --
+	(310.34,136.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34,136.92) --
+	(310.34, 86.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 86.97) --
+	(310.34, 86.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23,107.74) --
+	(316.23,107.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23,107.74) --
+	(316.23, 60.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23, 60.78) --
+	(316.23, 60.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12,145.87) --
+	(322.12,145.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12,145.87) --
+	(322.12, 54.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12, 54.67) --
+	(322.12, 54.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01,168.40) --
+	(328.01,168.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01,168.40) --
+	(328.01, 69.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01, 69.33) --
+	(328.01, 69.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,165.69) --
+	(333.90,165.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,165.69) --
+	(333.90, 70.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90, 70.69) --
+	(333.90, 70.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79,179.26) --
+	(339.79,179.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79,179.26) --
+	(339.79, 71.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79, 71.23) --
+	(339.79, 71.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68,180.89) --
+	(345.68,180.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68,180.89) --
+	(345.68, 78.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68, 78.29) --
+	(345.68, 78.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57,141.26) --
+	(351.57,141.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57,141.26) --
+	(351.57, 70.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57, 70.69) --
+	(351.57, 70.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45,162.97) --
+	(357.45,162.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45,162.97) --
+	(357.45, 76.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45, 76.12) --
+	(357.45, 76.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34,156.19) --
+	(363.34,156.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34,156.19) --
+	(363.34, 92.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34, 92.40) --
+	(363.34, 92.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23,154.15) --
+	(369.23,154.15);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23,154.15) --
+	(369.23, 85.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23, 85.62) --
+	(369.23, 85.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12,153.34) --
+	(375.12,153.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12,153.34) --
+	(375.12, 86.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12, 86.97) --
+	(375.12, 86.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01,148.59) --
+	(381.01,148.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01,148.59) --
+	(381.01, 91.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01, 91.45) --
+	(381.01, 91.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90,164.47) --
+	(386.90,164.47);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90,164.47) --
+	(386.90, 80.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90, 80.05) --
+	(386.90, 80.05);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68, 95.64) --
-	(398.68, 95.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68, 95.64) --
-	(398.68,172.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68,172.34) --
-	(398.68,172.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,100.43) --
-	(404.56,100.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,100.43) --
-	(404.56,148.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,148.37) --
-	(404.56,148.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,110.02) --
-	(410.45,110.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,110.02) --
-	(410.45,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,162.75) --
-	(410.45,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34, 86.05) --
-	(416.34, 86.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34, 86.05) --
-	(416.34,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34,162.75) --
-	(416.34,162.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,167.55) --
-	(422.23,167.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,167.55) --
-	(422.23,167.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,167.55) --
-	(422.23,167.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,148.37) --
-	(428.12,148.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,148.37) --
-	(428.12,148.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,148.37) --
-	(428.12,148.37);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor,fill opacity=0.20] (251.45,121.15) --
-	(253.69,119.25) --
-	(255.93,117.44) --
-	(258.16,115.70) --
-	(260.40,114.05) --
-	(262.64,112.48) --
-	(264.87,111.00) --
-	(267.11,109.60) --
-	(269.35,108.28) --
-	(271.58,107.06) --
-	(273.82,105.92) --
-	(276.05,104.87) --
-	(278.29,103.92) --
-	(280.53,103.05) --
-	(282.76,102.27) --
-	(285.00,101.59) --
-	(287.24,101.00) --
-	(289.47,100.50) --
-	(291.71,100.09) --
-	(293.94, 99.78) --
-	(296.18, 99.55) --
-	(298.42, 99.42) --
-	(300.65, 99.37) --
-	(302.89, 99.40) --
-	(305.13, 99.50) --
-	(307.36, 99.68) --
-	(309.60, 99.93) --
-	(311.83,100.23) --
-	(314.07,100.59) --
-	(316.31,100.99) --
-	(318.54,101.45) --
-	(320.78,101.95) --
-	(323.02,102.50) --
-	(325.25,103.10) --
-	(327.49,103.76) --
-	(329.72,104.45) --
-	(331.96,105.11) --
-	(334.20,105.76) --
-	(336.43,106.39) --
-	(338.67,107.01) --
-	(340.91,107.56) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79,186.72) --
+	(392.79, 86.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79, 86.97) --
+	(392.79, 86.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68,177.36) --
+	(398.68,177.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68,177.36) --
+	(398.68,100.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68,100.27) --
+	(398.68,100.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,155.92) --
+	(404.56,155.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,155.92) --
+	(404.56,103.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,103.26) --
+	(404.56,103.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,173.83) --
+	(410.45,173.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,173.83) --
+	(410.45,114.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,114.12) --
+	(410.45,114.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34,171.12) --
+	(416.34,171.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34,171.12) --
+	(416.34, 93.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34, 93.08) --
+	(416.34, 93.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,179.26) --
+	(422.23,179.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,179.26) --
+	(422.23,179.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,179.26) --
+	(422.23,179.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,157.54) --
+	(428.12,157.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,157.54) --
+	(428.12,157.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,157.54) --
+	(428.12,157.54);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (251.45, 93.58) --
+	(253.69, 93.29) --
+	(255.93, 93.04) --
+	(258.16, 92.81) --
+	(260.40, 92.62) --
+	(262.64, 92.45) --
+	(264.87, 92.32) --
+	(267.11, 92.23) --
+	(269.35, 92.16) --
+	(271.58, 92.13) --
+	(273.82, 92.13) --
+	(276.05, 92.16) --
+	(278.29, 92.23) --
+	(280.53, 92.33) --
+	(282.76, 92.46) --
+	(285.00, 92.63) --
+	(287.24, 92.83) --
+	(289.47, 93.07) --
+	(291.71, 93.35) --
+	(293.94, 93.66) --
+	(296.18, 94.00) --
+	(298.42, 94.38) --
+	(300.65, 94.80) --
+	(302.89, 95.25) --
+	(305.13, 95.74) --
+	(307.36, 96.27) --
+	(309.60, 96.84) --
+	(311.83, 97.44) --
+	(314.07, 98.08) --
+	(316.31, 98.76) --
+	(318.54, 99.48) --
+	(320.78,100.24) --
+	(323.02,101.03) --
+	(325.25,101.87) --
+	(327.49,102.75) --
+	(329.72,103.64) --
+	(331.96,104.48) --
+	(334.20,105.29) --
+	(336.43,106.05) --
+	(338.67,106.77) --
+	(340.91,107.42) --
 	(343.14,107.90) --
-	(345.38,108.14) --
-	(347.61,108.42) --
-	(349.85,108.79) --
-	(352.09,109.25) --
-	(354.32,109.74) --
-	(356.56,110.39) --
-	(358.80,111.15) --
-	(361.03,112.32) --
-	(363.27,113.45) --
-	(365.50,113.91) --
-	(367.74,114.29) --
-	(369.98,114.93) --
-	(372.21,115.63) --
-	(374.45,116.42) --
-	(376.69,117.13) --
-	(378.92,117.75) --
-	(381.16,118.39) --
-	(383.39,119.13) --
-	(385.63,120.01) --
-	(387.87,121.05) --
-	(390.10,122.20) --
-	(392.34,123.45) --
-	(394.58,124.82) --
-	(396.81,126.34) --
-	(399.05,128.02) --
-	(401.28,129.88) --
-	(403.52,131.95) --
-	(405.76,134.21) --
-	(407.99,136.68) --
-	(410.23,139.36) --
-	(412.47,142.24) --
-	(414.70,145.32) --
-	(416.94,148.60) --
-	(419.17,152.06) --
-	(421.41,155.72) --
-	(423.65,159.56) --
-	(425.88,163.59) --
-	(428.12,167.81) --
-	(428.12,134.79) --
-	(425.88,133.76) --
-	(423.65,132.73) --
-	(421.41,131.69) --
-	(419.17,130.64) --
-	(416.94,129.57) --
-	(414.70,128.50) --
-	(412.47,127.40) --
-	(410.23,126.29) --
-	(407.99,125.14) --
-	(405.76,123.97) --
-	(403.52,122.77) --
-	(401.28,121.53) --
-	(399.05,120.28) --
-	(396.81,119.01) --
-	(394.58,117.75) --
-	(392.34,116.53) --
-	(390.10,115.35) --
-	(387.87,114.24) --
-	(385.63,113.23) --
-	(383.39,112.40) --
-	(381.16,111.67) --
-	(378.92,110.96) --
-	(376.69,110.24) --
-	(374.45,109.51) --
-	(372.21,108.90) --
-	(369.98,108.23) --
-	(367.74,107.58) --
-	(365.50,106.98) --
-	(363.27,106.24) --
-	(361.03,105.28) --
-	(358.80,104.09) --
-	(356.56,103.31) --
-	(354.32,102.90) --
-	(352.09,102.47) --
-	(349.85,102.09) --
-	(347.61,101.83) --
-	(345.38,101.55) --
-	(343.14,101.17) --
-	(340.91,100.66) --
-	(338.67,100.06) --
-	(336.43, 99.41) --
-	(334.20, 98.70) --
-	(331.96, 97.92) --
-	(329.72, 97.09) --
-	(327.49, 96.21) --
-	(325.25, 95.32) --
-	(323.02, 94.44) --
-	(320.78, 93.58) --
-	(318.54, 92.75) --
-	(316.31, 91.93) --
-	(314.07, 91.14) --
-	(311.83, 90.37) --
-	(309.60, 89.60) --
-	(307.36, 88.85) --
-	(305.13, 88.09) --
-	(302.89, 87.33) --
-	(300.65, 86.56) --
-	(298.42, 85.77) --
-	(296.18, 84.96) --
-	(293.94, 84.13) --
-	(291.71, 83.27) --
-	(289.47, 82.38) --
-	(287.24, 81.46) --
-	(285.00, 80.51) --
-	(282.76, 79.53) --
-	(280.53, 78.51) --
-	(278.29, 77.47) --
-	(276.05, 76.39) --
-	(273.82, 75.29) --
-	(271.58, 74.15) --
-	(269.35, 72.98) --
-	(267.11, 71.79) --
-	(264.87, 70.56) --
-	(262.64, 69.31) --
-	(260.40, 68.03) --
-	(258.16, 66.72) --
-	(255.93, 65.38) --
-	(253.69, 64.01) --
-	(251.45, 62.62) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (251.45, 91.89) --
-	(253.69, 91.63) --
-	(255.93, 91.41) --
-	(258.16, 91.21) --
-	(260.40, 91.04) --
-	(262.64, 90.89) --
-	(264.87, 90.78) --
-	(267.11, 90.69) --
-	(269.35, 90.63) --
-	(271.58, 90.60) --
-	(273.82, 90.60) --
-	(276.05, 90.63) --
-	(278.29, 90.69) --
-	(280.53, 90.78) --
-	(282.76, 90.90) --
-	(285.00, 91.05) --
-	(287.24, 91.23) --
-	(289.47, 91.44) --
-	(291.71, 91.68) --
-	(293.94, 91.95) --
-	(296.18, 92.26) --
-	(298.42, 92.60) --
-	(300.65, 92.96) --
-	(302.89, 93.37) --
-	(305.13, 93.80) --
-	(307.36, 94.27) --
-	(309.60, 94.76) --
-	(311.83, 95.30) --
-	(314.07, 95.86) --
-	(316.31, 96.46) --
-	(318.54, 97.10) --
-	(320.78, 97.77) --
-	(323.02, 98.47) --
-	(325.25, 99.21) --
-	(327.49, 99.98) --
-	(329.72,100.77) --
-	(331.96,101.52) --
-	(334.20,102.23) --
-	(336.43,102.90) --
-	(338.67,103.53) --
-	(340.91,104.11) --
-	(343.14,104.53) --
-	(345.38,104.85) --
-	(347.61,105.13) --
-	(349.85,105.44) --
-	(352.09,105.86) --
-	(354.32,106.32) --
-	(356.56,106.85) --
-	(358.80,107.62) --
-	(361.03,108.80) --
-	(363.27,109.84) --
-	(365.50,110.44) --
-	(367.74,110.94) --
-	(369.98,111.58) --
-	(372.21,112.27) --
-	(374.45,112.97) --
-	(376.69,113.68) --
-	(378.92,114.35) --
-	(381.16,115.03) --
-	(383.39,115.76) --
-	(385.63,116.62) --
-	(387.87,117.64) --
-	(390.10,118.77) --
-	(392.34,119.99) --
-	(394.58,121.29) --
-	(396.81,122.67) --
-	(399.05,124.15) --
-	(401.28,125.71) --
-	(403.52,127.36) --
-	(405.76,129.09) --
-	(407.99,130.91) --
-	(410.23,132.82) --
-	(412.47,134.82) --
-	(414.70,136.91) --
-	(416.94,139.09) --
-	(419.17,141.35) --
-	(421.41,143.70) --
-	(423.65,146.14) --
-	(425.88,148.68) --
-	(428.12,151.30);
+	(345.38,108.26) --
+	(347.61,108.57) --
+	(349.85,108.93) --
+	(352.09,109.40) --
+	(354.32,109.92) --
+	(356.56,110.52) --
+	(358.80,111.39) --
+	(361.03,112.74) --
+	(363.27,113.91) --
+	(365.50,114.59) --
+	(367.74,115.15) --
+	(369.98,115.88) --
+	(372.21,116.66) --
+	(374.45,117.45) --
+	(376.69,118.26) --
+	(378.92,119.02) --
+	(381.16,119.78) --
+	(383.39,120.62) --
+	(385.63,121.59) --
+	(387.87,122.75) --
+	(390.10,124.03) --
+	(392.34,125.40) --
+	(394.58,126.87) --
+	(396.81,128.44) --
+	(399.05,130.11) --
+	(401.28,131.88) --
+	(403.52,133.75) --
+	(405.76,135.71) --
+	(407.99,137.77) --
+	(410.23,139.94) --
+	(412.47,142.20) --
+	(414.70,144.56) --
+	(416.94,147.03) --
+	(419.17,149.59) --
+	(421.41,152.26) --
+	(423.65,155.02) --
+	(425.88,157.89) --
+	(428.12,160.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50, 39.88) {-10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50, 87.82) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50,135.75) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50,183.69) {20};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50, 35.09) {-10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50, 89.37) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50,143.66) {10};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70, 42.91) --
-	(251.45, 42.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70, 90.85) --
-	(251.45, 90.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70,138.78) --
-	(251.45,138.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70,186.72) --
-	(251.45,186.72);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70, 38.12) --
+	(251.45, 38.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70, 92.40) --
+	(251.45, 92.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70,146.69) --
+	(251.45,146.69);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (339.79,  7.64) {Secondary cohort time (days)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (339.79,  7.64) {Symptom onset day (infectee)};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (446.70,112.42) {Reproduction number $\mathcal R$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (446.70,112.42) {Basic reproduction number $\mathcal R_0$};
 \end{scope}

### 2020-04-30 observedrR.R

@@ -175,7 +175,7 @@ g2a <- ggplot(filter(R0all, type=="Observed")) +
   annotate("text", x=78, y=rr$R0, label="Initial forward", hjust=1, vjust=-0.3, size=5) +
   annotate("text", x=78, y=serialsim$R, label="Intrinsic", hjust=1, vjust=-0.3, size=5) +
   scale_x_continuous("Time (days)", limits=c(0, 80), expand=c(0, 0)) +
-  scale_y_continuous("Reproduction number $\\mathcal R$", expand=c(0, 0), limits=c(0.9, 2.7),
+  scale_y_continuous("Basic reproduction number $\\mathcal R_0$", expand=c(0, 0), limits=c(0.9, 2.7),
                      breaks=c(1, 2, 3)) +
   scale_color_manual(values=tail(cpalette, 2)) +
   scale_fill_manual(values=tail(cpalette, 2)) +
@@ -193,7 +193,7 @@ g2b <- ggplot(filter(R0all, type=="Cohort-averaged")) +
   annotate("text", x=78, y=rr$R0, label="Initial forward", hjust=1, vjust=-0.3, size=5) +
   annotate("text", x=78, y=serialsim$R, label="Intrinsic", hjust=1, vjust=-0.3, size=5) +
   scale_x_continuous("Time (days)", limits=c(0, 80), expand=c(0, 0)) +
-  scale_y_continuous("Reproduction number $\\mathcal R$", expand=c(0, 0), limits=c(1.3, 3.3),
+  scale_y_continuous("Basic reproduction number $\\mathcal R_0$", expand=c(0, 0), limits=c(1.3, 3.3),
                      breaks=c(1, 2, 3)) +
   scale_color_manual(values=tail(cpalette, 1)) +
   scale_fill_manual(values=tail(cpalette, 1)) +
@@ -203,12 +203,12 @@ g2b <- ggplot(filter(R0all, type=="Cohort-averaged")) +
     legend.title = element_blank()
   )
 
-tikz(file = "observedrRa.tex", width = 6.6, height = 3.3, standAlone = T)
+tikz(file = "observedrRa.tex", width = 6.6, height = 3.5, standAlone = T)
 grid.arrange(g1a, g2a, nrow=1)
 dev.off()
 tools::texi2dvi('observedrRa.tex', pdf = T, clean = T)
 
[…]

### 2020-04-30 rR.R

@@ -50,7 +50,7 @@ g1 <- ggplot(rRdata) +
   geom_smooth(aes(r, R, col=type, lty=type), se=FALSE) +
   geom_point(aes(r, R, col=type, shape=type), size=2) +
   scale_x_continuous("Exponential growth rate $r$ (1/day)", limits=c(0, 0.3), expand=c(0, 0)) +
-  scale_y_continuous("Reproduction number $\\mathcal R$", limits=c(1, 4.5), expand=c(0, 0)) +
+  scale_y_continuous("Basic reproduction number $\\mathcal R_0$", limits=c(1, 4.5), expand=c(0, 0)) +
   scale_color_manual(values=cpalette) +
   ggtitle("A") +
   theme(

### 2020-04-30 serial_analysis.R

@@ -21,8 +21,8 @@ rr_summ <- rr %>%
   group_by(cohort) %>%
   summarize(
     mean=mean(serial),
-    lwr=max(serial),
-    upr=min(serial)
+    lwr=quantile(serial, 0.025),
+    upr=quantile(serial, 0.975)
   )
 
 rr_summ2 <- rr %>%
@@ -30,8 +30,8 @@ rr_summ2 <- rr %>%
   group_by(cohort)  %>%
   summarize(
     mean=mean(serial),
-    lwr=max(serial),
-    upr=min(serial)
+    lwr=quantile(serial, 0.025),
+    upr=quantile(serial, 0.975)
   )
 
 tcut <- seq(0, 29, by=1)
@@ -95,8 +95,8 @@ g1 <- ggplot(rr) +
   geom_line(data=cdata, aes(x, y), lty=2) +
   geom_point(data=rr_summ, aes(cohort, mean)) +
   geom_errorbar(data=rr_summ, aes(cohort, ymin=lwr, ymax=upr), width=0) +
-  geom_smooth(aes(cohort, serial), col=1, fill=1, fullrange=TRUE, alpha=0.2) +
-  scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(-3, 29)) +
+  geom_smooth(aes(cohort, serial), col=1, fill=1, fullrange=TRUE, se=FALSE) +
+  scale_x_continuous("Symptom onset day (infector)", expand=c(0, 0), limits=c(-3, 29)) +
   scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(-12, 21)) +
   scale_size_area(max_size=4) +
   coord_cartesian(clip="off", default=TRUE) +
@@ -109,8 +109,8 @@ g1 <- ggplot(rr) +
 g2 <- ggplot(rr) +
   geom_point(data=rr_summ2, aes(cohort, mean)) +
   geom_errorbar(data=rr_summ2, aes(cohort, ymin=lwr, ymax=upr), width=0) +
-  geom_smooth(aes(`Seconday - symptom onset date`, serial), col=1, fill=1, alpha=0.2) +
-  scale_x_continuous("Secondary cohort time (days)", expand=c(0, 0)) +
+  geom_smooth(aes(`Seconday - symptom onset date`, serial), col=1, fill=1, se=FALSE) +
+  scale_x_continuous("Symptom onset day (infectee)", expand=c(0, 0)) +
[…]

### 2020-04-30 serial.tex
comments

@@
 \end{equation}
-where $h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pt-\alpha_1$ and the forward generation interval $\alpha_2 - \alpha_1$ of a cohort of individuals infected at time $\alpha_1$ (in this case, the infectors), and $k_{\alpha_2}(\st-\alpha_2)$ is the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\st-\alpha_2$ of a cohort of individuals infected at time $\alpha_2$ (in this case, the infectee).
+where $h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pt-\alpha_1$ and the forward generation interval $\alpha_2 - \alpha_1$ of a cohort of individuals infected at time $\alpha_1$ (in this case, the infectors), and $k_{\alpha_2}(\st-\alpha_2)$ is the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\st-\alpha_2$ of a cohort of individuals infected at time $\alpha_2$ (in this case, the infectees):
+\begin{equation}
+k_{\alpha_2}(\tau) = \int_0^\infty h_{\alpha_2}(\tau, \sigma) \dsigma.
+\end{equation}
 It is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
 for example, if an infected individual can only transmit the disease after symptom onset, the forward generation interval will necessarily be longer than the forward incubation period.
-Then, the total number of serial intervals can be obtained by integrating over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
+
+Finally, the total number of serial intervals can be obtained by integrating over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
 \begin{equation}
@@
 \end{equation}
-
-Finally, the forward serial-interval distribution $f_\pt(\tau)$ is proportional to $\total (\pt, \pt+\tau)$ because it is conditional on the cohort of infectors who became symptomatic at time $\pt$:
+Then, the forward serial-interval distribution $f_\pt(\tau)$ is proportional to $\total (\pt, \pt+\tau)$ because it is conditional on the cohort of infectors who became symptomatic at time $\pt$:
 \begin{equation}
@@
 The mean forward incubation period remains constant throughout an epidemic as assumed (\fref{epi}B).
-The mean forward generation interval decreases slightly as the epidemic progresses due to susceptible depletion (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
+The mean forward generation interval decreases slightly as incidence rate increases, causing the proportion of susceptible populaton to decrease (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
 In contrast, the mean forward serial interval decreases over time (\fref{epi}D).

### 2020-04-30 serial.tex
some key comments from Sunky

@@
 Now, we turn to practical issues.
-Serial intervals are typically measured from line-list data (\fref{obsrR}A).
-When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
+In order to have an unbiased estimate on \Ro, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e.
+initial forward serial-interval distribution).
+However, when an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
 for example, if we were to measure serial intervals on Day 8 as in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
@@
 While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum \emph{observable} serial intervals), increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution.
-The decrease in the mean forward serial interval is likely to be cause by increase in the mean backward serial intervals as well as increase in mitigation efforts.
+The decrease in the mean forward serial interval is likely to be cause by increase in the mean backward serial intervals as well as intervention efforts (e.g., case isolation will shorten the forward generation intervals).
 \fref{du}B shows that the mean backward serial interval increases over time, reflecting decrease in incidence over time.

### 2020-04-30 serial.tex
tweak

@@
 Characterizing generation- and serial-interval distributions is critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
-Generation intervals measure the time difference between infection of a transmission pair, whereas serial intervals measure the time difference between symptom onset of a transmission pair \citep{svensson2007note}.
+Generation intervals are defined as the time difference between infection time of a transmission pair, whereas serial intervals are defined as the time difference between symptom onset time of a transmission pair \citep{svensson2007note}.
 Due to their similar definitions, we show that their differences have been inaccurately captured previously.
 
-Our study demonstrate the importance of defining a cohort for studying any epidemiological time delay distributions.
-Previous studies have shown that generation interval can be either measured forward or backward \citep{champredon2015intrinsic};
-we generalize their ideas and show that these ideas can be applied to all distributions.
+Our study demonstrates the importance of defining a reference cohort for studying any epidemiological time delay distributions.
+Previous studies have shown that generation interval can be either measured forward or backward \citep{champredon2015intrinsic,britton2019estimation};
+we generalize their ideas by showing that these ideas can be applied to all distributions.
 Changes in the backward delay distributions is particularly robust across all distributions because they depend on previous changes in cohort sizes, which, in turn, depend on incidence of infection.

### 2020-04-30 serial.tex
tweaks

@@
 We provide an answer to the paradox by showing that if serial intervals are defined as \emph{forward-looking} intervals during the exponential phase, then the correct link between $r$ and \RR emerges.
-We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to analyze serial intervals of COVID-19.
-Our study reveals gaps in the current understanding of serial intervals and provides rationale for reassessing serial intervals of COVID-19.
+We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to re-analyze serial intervals of COVID-19 collected from China.
+Our study further reveals gaps in the current practices in outbreak analysis and provides rationale for reassessing serial intervals of COVID-19.
 
@@
 
-Characterizing generation- and serial-interval distributions is critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
+Estimating generation- and serial-interval distributions is critical to characterizing the outset of an outbreak as they determine the time scale of disease transmission.
 Generation intervals are defined as the time difference between infection time of a transmission pair, whereas serial intervals are defined as the time difference between symptom onset time of a transmission pair \citep{svensson2007note}.
-Due to their similar definitions, we show that their differences have been inaccurately captured previously.
+By definition, they both describe how infection spreads between individiauls;
 
 Our study demonstrates the importance of defining a reference cohort for studying any epidemiological time delay distributions.
-Previous studies have shown that generation interval can be either measured forward or backward \citep{champredon2015intrinsic,britton2019estimation};
+Previous studies have shown that generation interval can be either measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
 we generalize their ideas by showing that these ideas can be applied to all distributions.

### 2020-04-30 serial.tex
the
tweaks

@@
 We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to re-analyze serial intervals of COVID-19 collected from China.
-Our study further reveals gaps in the current practices in outbreak analysis and provides rationale for reassessing serial intervals of COVID-19.
+Our study further reveals gaps in current practices in outbreak analysis and provides rationale for reassessing serial intervals of COVID-19.
 
@@
 
-Estimating generation- and serial-interval distributions is critical to characterizing the outset of an outbreak as they determine the time scale of disease transmission.
-Generation intervals are defined as the time difference between infection time of a transmission pair, whereas serial intervals are defined as the time difference between symptom onset time of a transmission pair \citep{svensson2007note}.
-By definition, they both describe how infection spreads between individiauls;
+Characterizing generation- and serial-interval distributions is critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
+Here, we show that the initial forward serial-interval distributions --- measured during exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
 
@@
 \begin{aligned}
-i(t) &= \Ro S(t-\Delta t) \sum_{m=1}^{\ell} i(t-m \Delta t) \hat{g}(m \Delta t) \\
+i(t) &= \Ro S(t-\Delta t) \sum_{m=1}^{\ell} i(t-m \Delta t) \hat{\gdist}(m \Delta t) \\
 S(t) &= S(t-\Delta t) - i(t)
@@
 \end{equation}
-where $\hat{g}$ is a discrete-time intrinsic generation-interval distribution that satisfies the following:
+where $\hat{\gdist}$ is a discrete-time intrinsic generation-interval distribution that satisfies the following:
 \begin{equation}
-\hat{g}(m \Delta t) = \frac{g(m \Delta t)}{\sum_{i=1}^\ell g(m \Delta t)}, \quad m=1, \dots, \ell
+\hat{\gdist}(m \Delta t) = \frac{\gdist(m \Delta t)}{\sum_{i=1}^\ell \gdist(m \Delta t)}, \quad m=1, \dots, \ell
 \end{equation}
@@
 \begin{equation}
-\hat{h}(m \Delta t, \Delta t n) = \hat{k}(m \Delta t)\hat{g}(\Delta t n), \quad m,n=1, \dots, \ell.
+\hat{h}(m \Delta t, \Delta t n) = \hat{k}(m \Delta t)\hat{\gdist}(\Delta t n), \quad m,n=1, \dots, \ell.
 \end{equation}
@@
 
-The intrinsic generation-interval distribution $g(\tau)$ provides a link between $r$ and \RR via the Euler-Lotka equation:
+The intrinsic generation-interval distribution $\gdist(\tau)$ provides a link between $r$ and \Ro via the Euler-Lotka equation:
 \begin{equation}
-\frac{1}{\RR} = \int_0^\infty \exp(-r\tau) g(\tau) \mathrm{d} \tau.
+\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) \gdist(\tau) \dtau.
 \end{equation}
@@
 \begin{equation}
-\frac{1}{\RR} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
+\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \dtau,
 \end{equation}
@@
 \begin{equation}
-f_{0}(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \exp(-rx) h(x, \sigma) k(x-\sigma+\tau) \mathrm{d}\sigma\,\mathrm{d}x.
+f_{0}(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \exp(-rx) h(x, \sigma) k(x-\sigma+\tau) \dsigma\dx.
 \end{equation}

### 2020-04-30 serial.tex
still working on discussion

@@
 
-Characterizing generation- and serial-interval distributions is critical to understanding the outset of an outbreak as they determine the time scale of disease transmission.
+Characterizing generation- and serial-interval distributions is critical to understanding the course of an outbreak as they determine the time scale of disease transmission.
 Here, we show that the initial forward serial-interval distributions --- measured during exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
+We further illustrate that epidemiological dynamics can cause the mean backward incubation period to increase over time, which in turn decreases the mean forward serial interval.
+Failing to account for these changes can result in underestimation of \RR.
 
-Our study demonstrates the importance of defining a reference cohort for studying any epidemiological time delay distributions.
+Our study demonstrates the importance of defining a reference cohort for characterizing any epidemiological time distributions.
 Previous studies have shown that generation interval can be either measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
-we generalize their ideas by showing that these ideas can be applied to all distributions.
-Changes in the backward delay distributions is particularly robust across all distributions because they depend on previous changes in cohort sizes, which, in turn, depend on incidence of infection.
-Previous analyses of COVID-19 epidemics have attempted to reconstruct the time series of symptomatic cases or infected cases from the reports of confirmed cases by assuming a constant backward delay distribution (e.g., \cite{tempvar, park2020potential, shim2020transmission}).
-Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using deconvolution approaches instead for proper reconstruction of epidemic time series \citep{goldstein2009reconstructing}.
+we generalize their ideas and show that they can be applied to any distributions.
+Changes in the backward delay distributions is expected to be a robust feature across any outbreaks because they are primarily driven by changes in cohort sizes, which, in turn, depend on incidence of infection.
+Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series of symptomatic cases or infected cases from the reports of confirmed cases by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential, shim2020transmission});
+these studies effectively assume constant backward delay distributions.
+Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using deconvolution approaches \citep{goldstein2009reconstructing} or mechanstic modeling approaches for proper reconstruction of epidemic time series instead \citep{flaxman2020estimating}.
 
 Using cohort-based approaches, we define forward and backward serial intervals.
-The forward serial-interval distribution describes the renewal process of the symptomatic individuals, and therefore, its initial distribution  provides the correct link between $r$ and \RR.
+The forward serial-interval distribution describes the renewal process between symptomatic cases, and therefore, its initial distribution provides the correct link between $r$ and \RR.
 While our results support the use of serial interval distributions for calculating \RR, 
-they also reveal gaps in current approaches to characterizing serial intervals.
-Previous studies have (i) recommended using up-to-date serial intervals \citep{thompson2019improved}, (ii) assumed that the serial interval distribution remains constant throughout an epidemic \citep{wallinga2004different, cori2013new}, and (iii) applied serial interval distributions estimated from one location to analyzing epidemics in other locations \citep{tempvar};
-however, all of these approaches implicitly ignore spatiotemporal variation in incidence, which affects the serial-interval distributions, and may therefore give systematically biased estimates of \RR.
-For example, given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic \citep{tempvar}, the initial forward serial interval distributions is likely to vary across different countries.
+they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
+In particular, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial interval data for accurate estimation of time-varying reproduction numbers;
+however, our study demonstrates that early serial interval data is required to estimate \RR and using up-to-date serial interval data can, in fact, underestaimte \RR.
+Moreover, \cite{tempvar} recently analyzed case reports of COVID-19 from over 30 countries to estimate their time-varying reproduction numbers but relied on a serial-interval distribution;
+given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the initial forward serial interval distributions is likely to vary across different countries.
+
 Future studies should aim to characterize spatiotemporal variation in serial intervals and understand the drivers of their differences.

### 2020-04-30 serial.tex
ok

@@
 given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the initial forward serial interval distributions is likely to vary across different countries.
-
-Future studies should aim to characterize spatiotemporal variation in serial intervals and understand the drivers of their differences.
+We suggest that modelers should aim to characterize spatiotemporal variation in initial forward serial-interval distributions and understand their changes over time.
+These modeling approaches should be necessarily coupled with intensive epidemiological investigation through contact tracing at the very beginning of the outbreak in order to characterize the initial forward serial-interval distribution, particularly for an emerging epidemic such as COVID-19.
 
@@
 Despite these limitations, our analysis of serial intervals of COVID-19 provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of \RR.
-To our knowledge, most, if not all, existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
+To our knowledge, most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
 Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \Ro, of the COVID-19 pandemic.

### 2020-04-30 serial.tex
a bit more

@@
 
-We also show that there are multiple serial-interval distributions that correspond to the same set of generation-interval and incubation period distributions depending on their correlations.
+Our study also demonstrates that there are multiple serial-interval distributions that correspond to the same set of generation-interval and incubation period distributions depending on their correlations;
+all of them can provide the correct link between $r$--\RR (\fref{rR}).
 Conversely, this means that not explicitly accounting for their correlations can bias the estimate of the intrinsic generation-interval distribution from the serial-interval distribution.
-Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the differences between the backward incubation period of an infector and the forward incubation period of an infectee (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
+Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the differences between the incubation periods of infectors and those of infectees (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating});
+
 There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.
@@
 In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.
-For example, symptom onset dates cannot be used as a reliable proxy for the direction of transmission as infectees may develop symptoms before their infectors.
+For example, symptom onset dates cannot be used as a reliable proxy for determining the direction of transmission as infectees may develop symptoms before their infectors.
 Based on the COVID-19 parameters (Table 1), we expect roughly 3\% of infectees to develop symptoms before their infectors during the exponential growth period; 
-this probability increases as epidemic progresses because backward incubation period of an infector increases.
+this probability increases as epidemic progresses because the mean backward incubation period increases.
 Biases in the observed serial intervals will necessarily bias the estimates of \RR. 

### 2020-04-30 serial.tex
space

@@
 Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the differences between the incubation periods of infectors and those of infectees (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating});
-
 There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.

### 2020-05-01 serial.tex
tweaks to abstract

@@
 
-Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number \RR --- yet important quantities in understanding the outset of an outbreak.
+Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number \RR --- yet important quantities for charaterizing the outset of an outbreak.
 Even though their differences were clearly laid out over a decade ago, there is still a need for clear conceptual and theoretical understanding of their roles in shaping the epidemiological dynamics.
 A part of the confusion can be attributed to an apparent paradox.
-By definition, both generation and serial intervals describe how infection spreads between individuals, and therefore, one might expect them to potentially provide the same link between the epidemic growth rate $r$ and the reproduction number \RR based on the renewal process.
+By definition, both generation and serial intervals describe how infection spreads between individuals, and therefore, one would expect them to potentially provide the same link between the epidemic growth rate $r$ and the reproduction number \RR.
 However, current theory does not explain how two different distributions can give the same link between $r$ and \RR --- some studies have further demonstrated that generation and serial intervals give different $r$--\RR link.
 We provide an answer to the paradox by showing that if serial intervals are defined as \emph{forward-looking} intervals during the exponential phase, then the correct link between $r$ and \RR emerges.
-We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to re-analyze serial intervals of COVID-19 collected from China.
-Our study further reveals gaps in current practices in outbreak analysis and provides rationale for reassessing serial intervals of COVID-19.
+We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to serial intervals of COVID-19.
+Our study demonstrates the importance of early epidemiological investigation through contact tracing for characterizing initial serial intervals and further provides rationale for reassessing serial intervals of COVID-19.
 

### 2020-05-01 serial.tex
ok...

@@
 
-Despite these limitations, our analysis of serial intervals of COVID-19 provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of \RR.
+While we focused on the effect of epidemiological dynamics on the serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
+Individual-level interventions, such as case isolation, directly affect individual's ability to transmit and will shorten the forward generation- and serial-intervals.
+On the other hand, population-level interventions, such as social distancing, have qualitatively similar effects on epidemiogical dynamics as susceptible depletion;
+therefore, we expect these intervention efforts to also shorten the forward generation- and serial-intervals.
+
+Despite these limitations, our analysis of serial intervals of COVID-19 from China provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of \RR.
 To our knowledge, most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.

### 2020-05-01 serial.tex
minor tweaks

@@
 Individual-level interventions, such as case isolation, directly affect individual's ability to transmit and will shorten the forward generation- and serial-intervals.
-On the other hand, population-level interventions, such as social distancing, have qualitatively similar effects on epidemiogical dynamics as susceptible depletion;
-therefore, we expect these intervention efforts to also shorten the forward generation- and serial-intervals.
+Population-level interventions, such as social distancing, have qualitatively similar effects on epidemiogical dynamics as susceptible depletion;
+therefore, we expect these intervention efforts to also (indirectly) shorten the forward generation- and serial-intervals.
+\swp{Sunky suggested: ``Social distancing will squeeze the contacts into the household, thus introduce high degree of clustering, which will shorten the generation interval as well (running out of susceptible within the household before the infectious period ends).'' and I like the idea of mentioning this briefly and cite our previous contact\_trace paper...
+don't have a good sentence at the moment so I'm just going to leave it as is.}
 
@@
 To our knowledge, most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
-Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \Ro, of the COVID-19 pandemic.
+Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \RR, of the COVID-19 pandemic.
 

### 2020-05-03 serial.tex
Some thoughts and suggestions

@@
 
-Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number \RR --- yet important quantities for charaterizing the outset of an outbreak.
-Even though their differences were clearly laid out over a decade ago, there is still a need for clear conceptual and theoretical understanding of their roles in shaping the epidemiological dynamics.
-A part of the confusion can be attributed to an apparent paradox.
-By definition, both generation and serial intervals describe how infection spreads between individuals, and therefore, one would expect them to potentially provide the same link between the epidemic growth rate $r$ and the reproduction number \RR.
+Generation and serial intervals are under-appreciated yet important quantities for charaterizing the outset of an outbreak.
+Even though their definitions (and differences) were clearly laid out over a decade ago, there is still a need for clear conceptual and theoretical understanding of their roles in shaping the epidemiological dynamics.
+Part of the confusion can be attributed to an apparent paradox.
+By definition, both generation and serial intervals describe how infection spreads between individuals --- thus, one would expect them both to link between the epidemic growth rate $r$ and the reproduction number \RR.
 However, current theory does not explain how two different distributions can give the same link between $r$ and \RR --- some studies have further demonstrated that generation and serial intervals give different $r$--\RR link.
-We provide an answer to the paradox by showing that if serial intervals are defined as \emph{forward-looking} intervals during the exponential phase, then the correct link between $r$ and \RR emerges.
-We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to serial intervals of COVID-19.
-Our study demonstrates the importance of early epidemiological investigation through contact tracing for characterizing initial serial intervals and further provides rationale for reassessing serial intervals of COVID-19.
+\jd{Revisit}
+We provide an answer to the paradox by showing that \emph{forward-looking} serial intervals, which correctly link the two quantities, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
+We provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to serial intervals of COVID-19.
+This study demonstrates the importance of early epidemiological investigation through contact tracing for characterizing initial serial intervals and provides rationale for reassessing serial intervals, and \RR\ estimates, for COVID-19.
 
@@
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
-the corresponding reproduction number in a fully susceptible population --- referred to as the basic reproduction number \Ro --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
-Since reproduction number cannot be measured directly, particularly during the outset of an outbreak, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{du2020serial, jung2020real, li2020early, zhao2020preliminary}).
+the reproduction number in a fully susceptible population --- referred to as the basic reproduction number \Ro --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention necessary to eliminate disease \citep{anderson1991infectious}.
+Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{du2020serial, jung2020real, li2020early, zhao2020preliminary}).
 
-The generation interval is defined as the time between when an individual (infector) is infected and when an individual infects another person (infectee);
+The generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee);
 the generation-interval distribution determines the relationship between the exponential growth rate $r$ and the reproduction number \RR \citep{wallinga2007generation}.
+\jd{Is the the best starting citation for Euler-Lotka? It would be nice to have one or two older things.}
 Similarly, the serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
@@
 
-Although these distributions were clearly distinguished over a decade ago \citep{svensson2007note}, 
+Although these distributions were clearly and distinctly defined over a decade ago \citep{svensson2007note}, 
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds.
-Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19, particularly for estimating its \RR, without making a clear distinction \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}.
-Some studies still refer to time between infection (i.e., generation intervals) as serial intervals \citep{anderson2020will,hellewell2020feasibility}.
+Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19, particularly for estimating its \RR, either without making a clear distinction \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}, or explicitly conflating the two intervals
+\citep{anderson2020will,hellewell2020feasibility}.
 
-One important source of confusion comes down to an apparent paradox.
+One source of confusion comes down to an apparent paradox.
 When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
@@
 By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates;
-therefore, both generation- and serial-interval distributions should potentially give us identical estimates of  \RR based the observed epidemic growth rate $r$.
+therefore, both generation- and serial-interval distributions should give identical estimates of  \RR based the observed epidemic growth rate $r$.
 In contexts where the distributions are expected to be different, current theory has no explanation for how they might provide identical estimates of \RR from $r$ (cf. \cite{britton2019estimation}).
 
-Here, we provide an answer to this paradox, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
+Here, we resolve this paradox, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
 We develop a new framework for understanding serial intervals and show that the initial forward serial-interval distribution correctly links $r$ and \RR.
 %\jd{Come back to this. Not just over time, right?} \swp{What do you mean? Everything is about time here... you haven't read the results section so maybe that's why?}
-However, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can bias the estimate of \RR, as inferred from the observed growth rate $r$.
-We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of the ongoing pandemic.
+Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can bias estimates of \RR.
+We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of epidemics.
 
@@
 most epidemiological events that can be observed within an individual have clear direction (e.g., infection and onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
-% \jd{Rethink, or else rethink ``any'' above: the ``hidden'' time (my term) is the time between onset of infectiousness and onset of symptoms; it is within, but can be positive or negative.
-I'm not saying we should use it here\ldots}
 When we measure an epidemiological time delay between infected individuals (e.g., the serial interval), 
 the primary and secondary events are defined in terms of the direction of transmission:
-The primary event refers to the event that occurs within the infector
-and does not necessarily occur before the secondary event (which
-occurs within the infectee).
+the primary event refers to the event that occurs in the infector; again some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to report sysmptoms before the infector).
 
-We model time delays between a primary and a secondary event from a cohort perspective.
+\jd{I wonder if we should talk about intrinsic earlier. To what extent does it correspond to an individual perspective?}
+At the population level, we model time delays between a primary and a secondary event from a cohort perspective.
 A primary cohort consists of \emph{all} individuals whose primary event occurred at a given time; 
 a secondary cohort is defined similarly based on the secondary events.
-For example, when we are measuring incubation periods, a \textbf{p}rimary cohort at time $\pt$ consists of all infected individuals who became infected at time $\pt$. 
-Similarly, when we are measuring serial intervals, a primary cohort at time $\pt$ consists of all infectors who became symptomatic at time $\pt$.
+For example, when we are measuring incubation periods, a \textbf{p}rimary cohort consists of all individuals who became infected at time $\pt$. 
+Similarly, when we are measuring serial intervals, a primary cohort consists of all individuals who became symptomatic at time $\pt$.
 Then, for each primary cohort $\pt$, we can define the expected time distribution between primary and secondary events.
@@
 If we are thinking of incubation periods, then the left hand side of
-this equation is the probability density that there is an individual
-who became symptomatic at time $\st$ after an incubation period of
+this equation is the probability density that an individual
+who became symptomatic at time $\st$ had an incubation period of
 length $\tau$. From the right hand side, we see that this probability
@@
 
-There are multiple mechanisms that drive the changes in forward and backward delay distributions over time ---
-we begin by describing factors that affect the forward delay distributions.
-Typically, within-individual forward delay distributions that reflect life history of a disease is expected to remain invariant over the course of an epidemic; 
-these distributions include incubation period distribution.
-Within-individual forward delay distributions that depend on external interventions, such as time distribution of symptom onset to hospitalization, can change over the course of an epidemic.
+There are multiple mechanisms that drive the changes in forward and backward delay distributions over time.
+Typically, within-individual forward delay distributions are not affected by epidemic dynamics.
+Some, like incubation periods, may remain more or less invariant over the course of an epidemic.
+Others, like the time from symptom onset to testing, may change over the course of an epidemic due to changes in public health policies.
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics;
-for example, the forward generation intervals to contract during the outbreak because infected individuals are less likely to infect others later due to susceptible depletion \citep{champredon2015intrinsic}.
+for example, forward generation intervals contract during the outbreak because infected individuals are less likely to infect others later due to susceptible depletion \citep{champredon2015intrinsic}.
 
+\jd{How clear are we where the asymmetry emerges?
+\eref{match} is perfectly symmetric.
+Is there a good explanation to throw at people?
+We should start this \P with the answer to that question: the main thing we learn from \eref{backward} is that $b$ changes when $f$ \emph{doesn't} change.
+}
 Changes in the backward delay distributions are affected by the changes in the forward delay distributions as it is evident from \eref{backward}.
@@
 These studies assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, this conclusion is based on the implicit assumption that serial intervals are measured from the perspective of a cohort of infectors that share the same infection time.
+however, this conclusion is based on the implicit assumption that incubation times are intrinsic to individuals (and not dependent on disease dynamics) --- something that is true of forward but not backward incubation times.
 We refer to this definition as the intrinsic serial interval.
@@
 \textbf{Illustration of intrinsic, forward and backward serial intervals.}
+\jd{I think it would be nice to have intrinsic incubation periods, and to make the point somewhere that because of causality we expect the forward to equal intrinsic incubation.}
 (A) The intrinsic serial interval for a cohort of individuals infected at time $\pt$.
@@
 
-Since serial intervals describe the renewal process between symptomatic cases based on their symptom onset dates, we have to define serial intervals from the perspective of a cohort (of either infectors or infectees) of individuals that share the same symptom onset time.
-The cohort-based framework allows us to understand the distribution of serial intervals we expect to observe when incidence is changing.
-Given that an infector became symptomatic at time $\pt$, we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when the infectee became symptomatic;
+To correctly link serial intervals to the renewal process between cases based on symptom onset dates, we must use the forward serial interval (i.e., use the perspective of a cohort of infectors that share the same symptom onset time.
+\jd{I'm running out of time.
+If you read this before I get back to it, give some thought to whether we need to talk much at all about backward serial intervals here and right below.
+I guess there may be a correction coming later if that's what people measure, but for now a focus on forward serial intervals (and how they contain backward incubation periods) could be clarifying.}
+Given that an infector became symptomatic at time $\pt$, we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then became symptomatic;
 this defines the forward serial interval.
@@
 \end{equation}
-where \Ro is the basic reproduction number, and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population; \cite{champredon2015intrinsic}).
+where \Ro is the basic reproduction number, and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population.
 Then, the forward generation-interval for a cohort of individuals that were infected at time $\pt$ follows \citep{champredon2015intrinsic}:

### 2020-05-04 serial.tex
More suggestions. I feel like we need to talk about “intrinsic”

@@
 
-\newcommand{\pt}{p} %% primary time
-\newcommand{\st}{s} %% secondary time
+\newcommand{\psymp}{\ensuremath{\rho_1}} %% primary symptom time
+\newcommand{\ssymp}{\ensuremath{\rho_2}} %% secondary symptom time
+\newcommand{\pinf}{\ensuremath{\alpha_1}} %% primary infection time
+\newcommand{\sinf}{\ensuremath{\alpha_2}} %% secondary infection time
 
@@
 a secondary cohort is defined similarly based on the secondary events.
-For example, when we are measuring incubation periods, a \textbf{p}rimary cohort consists of all individuals who became infected at time $\pt$. 
-Similarly, when we are measuring serial intervals, a primary cohort consists of all individuals who became symptomatic at time $\pt$.
-Then, for each primary cohort $\pt$, we can define the expected time distribution between primary and secondary events.
-We refer to this distribution as the forward delay distribution and denote it as $f_\pt(\tau)$.
+For example, when we are measuring incubation periods, a \textbf{p}rimary cohort consists of all individuals who became infected at time $\psymp$. 
+Similarly, when we are measuring serial intervals, a primary cohort consists of all individuals who became symptomatic at time $\psymp$.
+Then, for each primary cohort $\psymp$, we can define the expected time distribution between primary and secondary events.
+We refer to this distribution as the forward delay distribution and denote it as $f_\psymp(\tau)$.
 
-Likewise, we define the backward delay distribution $b_\st(\tau)$ for a \textbf{s}econdary cohort at time $\st$:
-The backward delay distribution describes the time delays between a primary and secondary host given that the secondary event occurred at time $\st$.
-For example, the backward incubation period distribution at time $\st$ describes incubation periods for a \emph{cohort} of individuals who became symptomatic at time $\st$.
-Likewise, the backward serial-interval distribution at time $\st$ describes serial intervals for a \emph{cohort} of infectees who became symptomatic at time $\st$.
+Likewise, we define the backward delay distribution $b_\ssymp(\tau)$ for a \textbf{s}econdary cohort at time $\ssymp$:
+The backward delay distribution describes the time delays between a primary and secondary host given that the secondary event occurred at time $\ssymp$.
+For example, the backward incubation period distribution at time $\ssymp$ describes incubation periods for a \emph{cohort} of individuals who became symptomatic at time $\ssymp$.
+Likewise, the backward serial-interval distribution at time $\ssymp$ describes serial intervals for a \emph{cohort} of infectees who became symptomatic at time $\ssymp$.
 
@@
 Consequently, if we restrict attention to individuals with a given
-incubation period, say $\tau$, and we count how many became infected at time $\pt$
-or how many first showed symptoms at time $\st=\pt+\tau$ then we must obtain
+incubation period, say $\tau$, and we count how many became infected at time $\psymp$
+or how many first showed symptoms at time $\ssymp=\psymp+\tau$ then we must obtain
 the same number. In general, no matter how delays are distributed, if
@@
 \begin{equation}
-\psize(\pt) f_\pt(\tau) = \ssize(\st) b_\st(\tau) \,.
+\psize(\psymp) f_\psymp(\tau) = \ssize(\ssymp) b_\ssymp(\tau) \,.
 \label{eq:match}
 \end{equation}
-Substituting $\pt=\st-\tau$, it follows that
+Substituting $\psymp=\ssymp-\tau$, it follows that
 \begin{equation}
-b_\st(\tau)= \frac{\psize(\st-\tau) f_{\st-\tau} (\tau)}{\ssize(\st)}
+b_\ssymp(\tau)= \frac{\psize(\ssymp-\tau) f_{\ssymp-\tau} (\tau)}{\ssize(\ssymp)}
 \label{eq:backward}
@@
 this equation is the probability density that an individual
-who became symptomatic at time $\st$ had an incubation period of
+who became symptomatic at time $\ssymp$ had an incubation period of
 length $\tau$. From the right hand side, we see that this probability
 density depends on how many individuals became infected at time
-$\st-\tau$ [$\psize(\st-\tau)$], how many individuals became
-symptomatic at time $\st$ [$\ssize(\st)$], and the probability density
-that someone who was infected at time $\st-\tau$ became symptomatic at
-time $\st$ [$f_{\st-\tau}(\tau)$]. In general, Eq.~\eqref{eq:backward}
-shows that the the backward delay distribution at reference time $\st$
-[$b_\st(\tau)$] depends not only on the secondary cohort size at time
-$\st$ [$\ssize(\st)$], but also on the primary cohort size at the
-earlier time $\st-\tau$ [$\psize(\st-\tau)$] and the forward delay
-distribution at that earlier time [$f_{\st-\tau}(\tau)$].
+$\ssymp-\tau$ [$\psize(\ssymp-\tau)$], how many individuals became
+symptomatic at time $\ssymp$ [$\ssize(\ssymp)$], and the probability density
+that someone who was infected at time $\ssymp-\tau$ became symptomatic at
+time $\ssymp$ [$f_{\ssymp-\tau}(\tau)$]. In general, Eq.~\eqref{eq:backward}
+shows that the the backward delay distribution at reference time $\ssymp$
+[$b_\ssymp(\tau)$] depends not only on the secondary cohort size at time
+$\ssymp$ [$\ssize(\ssymp)$], but also on the primary cohort size at the
+earlier time $\ssymp-\tau$ [$\psize(\ssymp-\tau)$] and the forward delay
+distribution at that earlier time [$f_{\ssymp-\tau}(\tau)$].
 
@@
 \textbf{Illustration of intrinsic, forward and backward serial intervals.}
-\jd{I think it would be nice to have intrinsic incubation periods, and to make the point somewhere that because of causality we expect the forward to equal intrinsic incubation.}
-(A) The intrinsic serial interval for a cohort of individuals infected at time $\pt$.
+\jd{I think it would be nice to have intrinsic incubation periods, and to make the point somewhere that because of causality we expect the forward to equal intrinsic incubation.
+I also wonder if we should skip the }
+(A) The intrinsic serial interval for a cohort of individuals infected at time $\psymp$.
 In this case, $x_0$ follows the forward incubation period distribution;
@@
 and $x_1$ follows the forward incubation period distribution.
-(B) The forward serial interval for a cohort of infectors who became symptomatic at time $\pt$.
+(B) The forward serial interval for a cohort of infectors who became symptomatic at time $\psymp$.
 In this case, $x_0$ follows the backward incubation period distribution;
@@
 and $x_1$ follows the forward incubation period distribution.
-(C) The backward serial interval for a cohort of infectees who became symptomatic at time $\st$.
+(C) The backward serial interval for a cohort of infectees who became symptomatic at time $\ssymp$.
 In this case, $x_0$ follows the forward incubation period distribution;
@@
 
-To correctly link serial intervals to the renewal process between cases based on symptom onset dates, we must use the forward serial interval (i.e., use the perspective of a cohort of infectors that share the same symptom onset time.
-\jd{I'm running out of time.
-If you read this before I get back to it, give some thought to whether we need to talk much at all about backward serial intervals here and right below.
-I guess there may be a correction coming later if that's what people measure, but for now a focus on forward serial intervals (and how they contain backward incubation periods) could be clarifying.}
-Given that an infector became symptomatic at time $\pt$, we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then became symptomatic;
-this defines the forward serial interval.
-In \fref{diagram}B, we see that $x_0$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\pt$;
-$\gtime$ follows the forward generation-interval distribution of the cohort of infector who came infected at time $\pt - x_0$;
-and $x_1$ follows the forward incubation period distribution of the cohort of infectees who became infected at time $\pt - x_0 + \gtime$.
+To correctly link serial intervals to the renewal process between cases based on symptom onset dates, we must use the forward serial interval (i.e., use the perspective of a cohort of infectors that share the same symptom onset time).
+Given that an infector became symptomatic at time $\psymp$, to calculate the forward serial interval we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when they became symptomatic.
+In \fref{diagram}B, we see that $x_0$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\psymp$;
+$\gtime$ follows the forward generation-interval distribution of the cohort of infector who came infected at time $\psymp - x_0$;
+and $x_1$ follows the forward incubation period distribution of the cohort of infectees who became infected at time $\psymp - x_0 + \gtime$.
 
-Likewise, we can define the backward serial interval distribution for a secondary cohort $\st$ (\fref{diagram}C).
-Given that an infectee became symptomatic at time $\st$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
+\jd{Could we skip this \P?} Likewise, we can define the backward serial interval distribution for a secondary cohort $\ssymp$ (\fref{diagram}C).
+Given that an infectee became symptomatic at time $\ssymp$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
 then, we have to go forward in time by asking when the infector became symptomatic.
-In this case, $x_1$ follows the backward incubation period distribution of the cohort of infectees who became symptomatic at time $\st$;
-$\gtime$ follows the backward generation-interval distribution of the cohort of infectees who became infected at time $\st-x_1$;
-and $x_0$ follows the forward incubation period distribution of the cohort of infectors who became infected at time $\st-x_1-\gtime$.
-This conceptual framework clearly demonstrates that the distributions of $x_0$, $\st$, and $x_1$ (and therefore the distributions of serial intervals) depend on the reference cohort and the corresponding cohort time.
+In this case, $x_1$ follows the backward incubation period distribution of the cohort of infectees who became symptomatic at time $\ssymp$;
+$\gtime$ follows the backward generation-interval distribution of the cohort of infectees who became infected at time $\ssymp-x_1$;
+and $x_0$ follows the forward incubation period distribution of the cohort of infectors who became infected at time $\ssymp-x_1-\gtime$.
+This conceptual framework clearly demonstrates that the distributions of $x_0$, $\ssymp$, and $x_1$ (and therefore the distributions of serial intervals) depend on the reference cohort and the corresponding cohort time.
 
-In order to define forward and backward serial interval distributions, we begin by modeling the total number of serial intervals $\total(\pt,\st)$ between time $\pt$ and $\st$ (i.e., total number of infection in which infectors develop symptom at time $\pt$ and infectees develop symptom at time $\st$).
-The number of serial intervals between time $\pt$ and $\st$ given that the infectors became infected at time $\alpha_1$ and the infectees became infected at time $\alpha_2$ is can be then expressed as a product of (i) incidence $i$ at time $\alpha_1$, (ii) their case reproduction number $\Rc(\alpha_1)$ (i.e., the average number of secondary cases caused by a primary case infected at time $\alpha_1$ over the course of their infection, \cite{fraser2007estimating}), (iii) the density of forward generation interval between $\alpha_1$ and $\alpha_2$, and (iv) the densities of forward incubation periods between $\alpha_1$ and $\pt$ (incubation periods of infectors) as well as $\alpha_2$ and $\st$ (incubation periods of infectees):
+\jd{This exposition is repetitive.}
+To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total number of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end at time $\ssymp$).
+The number of serial intervals between time $\psymp$ and $\ssymp$ given that the infectors became infected at time $\pinf$ and the infectees became infected at time $\sinf$ is can be then expressed as a product of (i) incidence $i$ at time $\pinf$, (ii) their case reproduction number $\Rc(\pinf)$ (i.e., the average number of secondary cases caused by a primary case infected at time $\pinf$ over the course of their infection, \cite{fraser2007estimating}), (iii) the density of forward generation interval between $\pinf$ and $\sinf$, and (iv) the densities of forward incubation periods between $\pinf$ and $\psymp$ (incubation periods of infectors) as well as $\sinf$ and $\ssymp$ (incubation periods of infectees):
 \begin{equation}
-\underbrace{\Rc (\alpha_1)}_{\substack{\text{case} \\ \text{reproduction} \\ \text{number}}} 
+\underbrace{i(\pinf)}_{\text{incidence}} 
 \times 
-\underbrace{i(\alpha_1)}_{\text{incidence}} 
+\underbrace{\Rc (\pinf)}_{\substack{\text{case} \\ \text{reproduction} \\ \text{number}}} 
 \times 
-\underbrace{h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)}_{\substack{\text{joint density of} \\ \text{the forward incubation} \\ \text{period and the forward} \\ \text{generation interval}\\ \text{(of infectors)}}}
+\underbrace{h_{\pinf}(\psymp-\pinf, \sinf - \pinf)}_{\substack{\text{joint density of} \\ \text{the forward incubation} \\ \text{period and the forward} \\ \text{generation interval}\\ \text{(of infectors)}}}
 \times
-\underbrace{k_{\alpha_2}(\st - \alpha_2)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period (of infectees)}}},
+\underbrace{k_{\sinf}(\ssymp - \sinf)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period (of infectees)}}},
 \end{equation}
-where $h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1)$ is the joint probability distribution describing the forward incubation period $\pt-\alpha_1$ and the forward generation interval $\alpha_2 - \alpha_1$ of a cohort of individuals infected at time $\alpha_1$ (in this case, the infectors), and $k_{\alpha_2}(\st-\alpha_2)$ is the marginal probability distribution of $h_{\alpha_2}$ describing the forward incubation period $\st-\alpha_2$ of a cohort of individuals infected at time $\alpha_2$ (in this case, the infectees):
+\jd{We've already described all of these things twice.
+Could we just stop here?
+Including, skip the integral below.} where $h_{\pinf}(\psymp-\pinf, \sinf - \pinf)$ is the joint probability distribution describing the forward incubation period $\psymp-\pinf$ and the forward generation interval $\sinf - \pinf$ of a cohort of individuals infected at time $\pinf$ (in this case, the infectors), and $k_{\sinf}(\ssymp-\sinf)$ is the marginal probability distribution of $h_{\sinf}$ describing the forward incubation period $\ssymp-\sinf$ of a cohort of individuals infected at time $\sinf$ (in this case, the infectees):
 \begin{equation}
-k_{\alpha_2}(\tau) = \int_0^\infty h_{\alpha_2}(\tau, \sigma) \dsigma.
+k_{\sinf}(\tau) = \int_0^\infty h_{\sinf}(\tau, \sigma) \dsigma.
 \end{equation}
+
 It is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
@@
 
-Finally, the total number of serial intervals can be obtained by integrating over all of the possibilities for the infection times of the infector $\alpha_1$ and the infectee $\alpha_2$:
+The total number of serial intervals can now be obtained by integrating over all possible infection times for the infector and the infectee:
 \begin{equation}
-\total (\pt,\st) = \int_{-\infty}^{\pt} \int_{\alpha_1}^{\st} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\st - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
+\total (\psymp,\ssymp) = \int_{-\infty}^{\psymp} \int_{\pinf}^{\ssymp} \Rc (\pinf) i(\pinf) h_{\pinf}(\psymp-\pinf, \sinf - \pinf) k_{\sinf}(\ssymp - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
 \end{equation}
-Then, the forward serial-interval distribution $f_\pt(\tau)$ is proportional to $\total (\pt, \pt+\tau)$ because it is conditional on the cohort of infectors who became symptomatic at time $\pt$:
+Then, the forward serial-interval distribution $f_\psymp(\tau)$ is given by the density of intervals of length $\tau$ starting at \psymp, relative to the total number of serial intervals starting at \psymp:
 \begin{equation}
-f_\pt(\tau) \propto \int_{-\infty}^{\pt} \int_{\alpha_1}^{\pt+\tau} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\pt-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\pt+\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
+f_\psymp(\tau) 
+\frac{\total(\psymp, \psymp+\tau)}{\int \total(\psymp, \psymp+\tau') d\tau'}
 \end{equation}
-The constant of proportionality is then equal to the total number of infection caused by individuals who became symptomatic at time $\pt$.
-Likewise, the backward serial-interval distribution $b_\st(\tau)$ is proportional to $\total (\st-\tau, \st)$ because it is conditional on the cohort of infectees who became symptomatic at time $\st$:
-\begin{equation}
-b_\st(\tau) \propto \int_{-\infty}^{\st-\tau} \int_{\alpha_1}^{\st} \Rc (\alpha_1) i(\alpha_1) h_{\alpha_1}(\st-\tau-\alpha_1, \alpha_2 - \alpha_1) k_{\alpha_2}(\st - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
-\end{equation}
-The constant of proportionality is then equal to the total number of infectors that infected individuals who became symptomatic at time $\st$.
 
@@
 where \Ro is the basic reproduction number, and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population.
-Then, the forward generation-interval for a cohort of individuals that were infected at time $\pt$ follows \citep{champredon2015intrinsic}:
+Then, the forward generation-interval for a cohort of individuals that were infected at time $\psymp$ follows \citep{champredon2015intrinsic}:
 \begin{equation}
-\gdist_\pt (\tau) \propto \gdist(\tau) S(\pt + \tau),
+\gdist_\psymp (\tau) \propto \gdist(\tau) S(\psymp + \tau),
 \end{equation}
-which allows us to separate the joint probability distribution $h_\pt$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
+which allows us to separate the joint probability distribution $h_\psymp$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
 \begin{equation}
-h_\pt (x, \tau) \propto h(x, \tau) S(\pt + \tau).
+h_\psymp (x, \tau) \propto h(x, \tau) S(\psymp + \tau).
 \end{equation}
@@
 forward serial-interval distributions, by definition, describe the renewal process of infection based on symptom onset dates.
-Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to provide the identical $r$--\Ro link as the intrinsic generation-interval distribution:
+Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to link the same values of $r$ and \Ro as the intrinsic generation-interval distribution:
+\jd{I don't want to talk about the ``link'' here, because that to me implies the functional link, not just linking a single pair of values.}
 \begin{equation}
@@
 \begin{equation}
-f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) k(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
+f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) k(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
 \end{equation}
@@
 \begin{aligned}
-f_{0}(\tau) &\propto \int_0^\infty \int_{-\alpha_1}^{\tau} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) k(\tau - \alpha_2) \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1\\
-&= \int_{-\infty}^{\tau} \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1)k(\tau - \alpha_2)\mathrm{d}\alpha_1\, \mathrm{d}\alpha_2\\
+f_{0}(\tau) &\propto \int_0^\infty \int_{-\pinf}^{\tau} \exp(-r\pinf) h(\pinf, \sinf + \pinf) k(\tau - \sinf) \mathrm{d}\sinf\,\mathrm{d}\pinf\\
+&= \int_{-\infty}^{\tau} \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)k(\tau - \sinf)\mathrm{d}\pinf\, \mathrm{d}\sinf\\
 \end{aligned}
 \end{equation}
-It follows that $z(\alpha_2)$ describes the time between symptom onset of infector and infection of infectee:
+It follows that $z(\sinf)$ describes the time between symptom onset of infector and infection of infectee:
 \begin{equation}
-z(\alpha_2) \propto \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1.
+z(\sinf) \propto \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf.
 \end{equation}
@@
 \begin{aligned}
-f_{0}(\tau) &\propto \int_{-\infty}^{\tau} z(\alpha_2) k(\tau - \alpha_2) \mathrm{d}\alpha_2.\\
+f_{0}(\tau) &\propto \int_{-\infty}^{\tau} z(\sinf) k(\tau - \sinf) \mathrm{d}\sinf.\\
 \end{aligned}
@@
 \begin{aligned}
-&\int_{-\infty}^\infty \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1 \mathrm{d}\alpha_2\\
-&= \int_{0}^\infty \int_{-\alpha_1}^\infty \exp(- r \alpha_1) h(\alpha_1, \alpha_2+\alpha_1) \mathrm{d}\alpha_2\,\mathrm{d} \alpha_1\\
-&= \int_{0}^\infty \exp(- r \alpha_1) k(\alpha_1) d\alpha_1
+&\int_{-\infty}^\infty \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\sinf\\
+&= \int_{0}^\infty \int_{-\pinf}^\infty \exp(- r \pinf) h(\pinf, \sinf+\pinf) \mathrm{d}\sinf\,\mathrm{d} \pinf\\
+&= \int_{0}^\infty \exp(- r \pinf) k(\pinf) d\pinf
 \end{aligned}
@@
 because $k$ is a marginal probability distribution of $h$.
-Since $\int_{0}^\infty \exp(- r \alpha_1) k(\alpha_1) d\alpha_1$ is a normalization factor for probability distribution $z$, we have:
+Since $\int_{0}^\infty \exp(- r \pinf) k(\pinf) d\pinf$ is a normalization factor for probability distribution $z$, we have:
 \begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau = \frac{\int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1 \mathrm{d}\tau}{\int_{0}^\infty \exp(- r \alpha_1) k(\alpha_1) d\alpha_1}.
+\int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau = \frac{\int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\tau}{\int_{0}^\infty \exp(- r \pinf) k(\pinf) d\pinf}.
 \end{equation}
@@
 \begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1 \mathrm{d}\tau.
+\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\tau.
 \end{equation}
@@
 \begin{equation}
-\int_0^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\alpha_2)}}^{\infty} \exp(-r\alpha_1) h(\alpha_1, \alpha_2 + \alpha_1) \mathrm{d}\alpha_1 \mathrm{d}\tau,
+\int_0^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\tau,
 \end{equation}
@@
 \begin{equation}
-g(\tau) = \int_0^\infty h(\alpha_1, \tau)  \mathrm{d} \alpha_1.
+g(\tau) = \int_0^\infty h(\pinf, \tau)  \mathrm{d} \pinf.
 \end{equation}
-Let $\sigma = \alpha_1 + \tau$. Then, by change of variables, it immediately follows that
+Let $\sigma = \pinf + \tau$. Then, by change of variables, it immediately follows that
 \begin{equation}
 \begin{aligned}
-&\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r \alpha_1) h(\alpha_1, \tau+\alpha_1) \mathrm{d} \alpha_1\, \mathrm{d}\tau\\
-&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \sigma) h(\alpha_1, \sigma) \mathrm{d} \alpha_1\, \mathrm{d}\sigma\\
+&\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r \pinf) h(\pinf, \tau+\pinf) \mathrm{d} \pinf\, \mathrm{d}\tau\\
+&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \sigma) h(\pinf, \sigma) \mathrm{d} \pinf\, \mathrm{d}\sigma\\
 &=\int_{0}^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau

### 2020-05-06 serial.tex
forgot to push this..crap
some tweaks

@@
 
-\newcommand{\psymp}{\ensuremath{\rho_1}} %% primary symptom time
-\newcommand{\ssymp}{\ensuremath{\rho_2}} %% secondary symptom time
+\newcommand{\psymp}{\ensuremath{p}} %% primary symptom time
+\newcommand{\ssymp}{\ensuremath{s}} %% secondary symptom time
 \newcommand{\pinf}{\ensuremath{\alpha_1}} %% primary infection time
@@
 The generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee);
-the generation-interval distribution determines the relationship between the exponential growth rate $r$ and the reproduction number \RR \citep{wallinga2007generation}.
-\jd{Is the the best starting citation for Euler-Lotka? It would be nice to have one or two older things.}
+the generation-interval distribution determines the relationship between the exponential growth rate $r$ and the reproduction number \RR \citep{anderson1991infectious, ferguson2005strategies, wallinga2007generation}.
 Similarly, the serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
@@
 
-\subsection{Forward and backward delay distributions}
+\subsection{Intrinsic, forward, and backward delay distributions}
 
@@
 
-\jd{I wonder if we should talk about intrinsic earlier. To what extent does it correspond to an individual perspective?}
-At the population level, we model time delays between a primary and a secondary event from a cohort perspective.
+At the individual level, we can define the expected time distribution between a primary and a secondary event --- we refer to this distribution as the intrinsic distribution.
+For example, the intrinsic incubation period distribution describes the expected time from infection to symptom onset of an individual.
+Likewise, the intrinsic generation-interval distribution describes the expected time from infection of a primary case to infection of a secondary case in a fully susceptible population; 
+since this is a expected time distribution, it does not take into account dynamical factors such as susceptible depletion or intervention efforts.
+However, the intrinsic time distributions are not always equivalent to realized time distributions at the population level.
+
+At the population level, we model realized time delays between a primary and a secondary event from a cohort perspective.
 A primary cohort consists of \emph{all} individuals whose primary event occurred at a given time; 
@@
 Typically, within-individual forward delay distributions are not affected by epidemic dynamics.
-Some, like incubation periods, may remain more or less invariant over the course of an epidemic.
+Some, like incubation periods, are expected to be equivalent to their intrinsic distributions and remain invariant over the course of an epidemic.
 Others, like the time from symptom onset to testing, may change over the course of an epidemic due to changes in public health policies.
@@
 
-\jd{How clear are we where the asymmetry emerges?
-\eref{match} is perfectly symmetric.
-Is there a good explanation to throw at people?
-We should start this \P with the answer to that question: the main thing we learn from \eref{backward} is that $b$ changes when $f$ \emph{doesn't} change.
-}
-Changes in the backward delay distributions are affected by the changes in the forward delay distributions as it is evident from \eref{backward}.
-Backward delay distributions also depend on changes in the primary cohort size over time due to conditionality of observations: 
-The backward delay distribution is measured for a cohort of individuals whose secondary events occurred at the same time.
+\eref{backward} suggests that backward delay distributions change over time even if their corresponding forward delay distribution does not change:
+Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations (i.e., they are measured from a cohort of individuals whose secondary events occurred at160the same time).
 When the cohort size is increasing (or decreasing) over time, we are biased to observe shorter (or longer) delays when we look backward.
@@
 For faster epidemic (higher $r$), the backward delay distributions will be shorter.
+Changes in the backward delay distributions are also affected by the changes in the forward delay distributions by definition (\eref{backward}).
 Therefore, the backward delay distributions will be generally different from the forward delay distributions even if we are measuring time delays that are intrinsic to life history of a disease (e.g., incubation period).
@@
 
-The serial interval is defined as the time between when an infector becomes symptomatic and when and infectee becomes symptomatic \citep{svensson2007note}.
+The serial interval is defined as the time between when an infector becomes symptomatic and when an infectee becomes symptomatic \citep{svensson2007note}.
 Previous studies have often expressed serial intervals $\tau$ in the form (\fref{diagram}A):
@@
 These studies assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, this conclusion is based on the implicit assumption that incubation times are intrinsic to individuals (and not dependent on disease dynamics) --- something that is true of forward but not backward incubation times.
+however, this conclusion is based on the implicit assumption that incubation times, $x_0$ and $x_1$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on disease dynamics) --- something that is true of forward but not backward incubation times.
 We refer to this definition as the intrinsic serial interval.
@@
 \textbf{Illustration of intrinsic, forward and backward serial intervals.}
-\jd{I think it would be nice to have intrinsic incubation periods, and to make the point somewhere that because of causality we expect the forward to equal intrinsic incubation.
-I also wonder if we should skip the }
 (A) The intrinsic serial interval for a cohort of individuals infected at time $\psymp$.
-In this case, $x_0$ follows the forward incubation period distribution;
-$\gtime$ follows the forward generation-interval distribution;
-and $x_1$ follows the forward incubation period distribution.
+In this case, $x_0$ follows the intrinsic incubation period distribution;
+$\gtime$ follows the intrinsic generation-interval distribution;
+and $x_1$ follows the intrinsic incubation period distribution.
 (B) The forward serial interval for a cohort of infectors who became symptomatic at time $\psymp$.
@@
 and $x_1$ follows the forward incubation period distribution of the cohort of infectees who became infected at time $\psymp - x_0 + \gtime$.
-
-\jd{Could we skip this \P?} Likewise, we can define the backward serial interval distribution for a secondary cohort $\ssymp$ (\fref{diagram}C).
-Given that an infectee became symptomatic at time $\ssymp$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
-then, we have to go forward in time by asking when the infector became symptomatic.
-In this case, $x_1$ follows the backward incubation period distribution of the cohort of infectees who became symptomatic at time $\ssymp$;
-$\gtime$ follows the backward generation-interval distribution of the cohort of infectees who became infected at time $\ssymp-x_1$;
-and $x_0$ follows the forward incubation period distribution of the cohort of infectors who became infected at time $\ssymp-x_1-\gtime$.
+Likewise, we can define the backward serial interval distribution for a secondary cohort $\ssymp$ (\fref{diagram}C).
 This conceptual framework clearly demonstrates that the distributions of $x_0$, $\ssymp$, and $x_1$ (and therefore the distributions of serial intervals) depend on the reference cohort and the corresponding cohort time.
 
-\jd{This exposition is repetitive.}
-To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total number of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end at time $\ssymp$).
-The number of serial intervals between time $\psymp$ and $\ssymp$ given that the infectors became infected at time $\pinf$ and the infectees became infected at time $\sinf$ is can be then expressed as a product of (i) incidence $i$ at time $\pinf$, (ii) their case reproduction number $\Rc(\pinf)$ (i.e., the average number of secondary cases caused by a primary case infected at time $\pinf$ over the course of their infection, \cite{fraser2007estimating}), (iii) the density of forward generation interval between $\pinf$ and $\sinf$, and (iv) the densities of forward incubation periods between $\pinf$ and $\psymp$ (incubation periods of infectors) as well as $\sinf$ and $\ssymp$ (incubation periods of infectees):
+% \jd{Could we skip this \P?} 
+% Given that an infectee became symptomatic at time $\ssymp$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
+% then, we have to go forward in time by asking when the infector became symptomatic.
+% In this case, $x_1$ follows the backward incubation period distribution of the cohort of infectees who became symptomatic at time $\ssymp$;
+% $\gtime$ follows the backward generation-interval distribution of the cohort of infectees who became infected at time $\ssymp-x_1$;
+% and $x_0$ follows the forward incubation period distribution of the cohort of infectors who became infected at time $\ssymp-x_1-\gtime$.
+
+To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total number of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
+The number of serial intervals between time $\psymp$ and $\ssymp$ given that the infectors became infected at time $\pinf$ and the infectees became infected at time $\sinf$ depends on the amount of infection that occur between time $\pinf$ and $\sinf$ as well as the densities of forward incubation period between $\pinf$ and $\psymp$ (incubation periods of infectors) as well as $\sinf$ and $\ssymp$ (incubation periods of infectees):
 \begin{equation}
@@
 \times 
-\underbrace{h_{\pinf}(\psymp-\pinf, \sinf - \pinf)}_{\substack{\text{joint density of} \\ \text{the forward incubation} \\ \text{period and the forward} \\ \text{generation interval}\\ \text{(of infectors)}}}
+\underbrace{h_{\pinf}(\psymp-\pinf, \sinf - \pinf)}_{\substack{\text{joint density of} \\ \text{the forward incubation} \\ \text{period } p-\pinf \text{ and the forward} \\ \text{generation interval } \sinf-\pinf\\ \text{(of infectors)}}}
 \times
-\underbrace{k_{\sinf}(\ssymp - \sinf)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period (of infectees)}}},
+\underbrace{k_{\sinf}(\ssymp - \sinf)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period } \ssymp-\sinf \\ \text{(of infectees)}}},
 \end{equation}
-\jd{We've already described all of these things twice.
-Could we just stop here?
-Including, skip the integral below.} where $h_{\pinf}(\psymp-\pinf, \sinf - \pinf)$ is the joint probability distribution describing the forward incubation period $\psymp-\pinf$ and the forward generation interval $\sinf - \pinf$ of a cohort of individuals infected at time $\pinf$ (in this case, the infectors), and $k_{\sinf}(\ssymp-\sinf)$ is the marginal probability distribution of $h_{\sinf}$ describing the forward incubation period $\ssymp-\sinf$ of a cohort of individuals infected at time $\sinf$ (in this case, the infectees):
-\begin{equation}
-k_{\sinf}(\tau) = \int_0^\infty h_{\sinf}(\tau, \sigma) \dsigma.
-\end{equation}
-
-It is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
+where the case reproduction number $\Rc (\pinf)$ is defined as the average number of secondary cases caused by a primary case infected at time $\pinf$ over the course of their infection \citep{fraser2007estimating}.
+We note that it is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
 for example, if an infected individual can only transmit the disease after symptom onset, the forward generation interval will necessarily be longer than the forward incubation period.
@@
 \begin{equation}
-f_\psymp(\tau) 
-\frac{\total(\psymp, \psymp+\tau)}{\int \total(\psymp, \psymp+\tau') d\tau'}
+f_\psymp(\tau) = 
+\frac{\total(\psymp, \psymp+\tau)}{\int \total(\psymp, \psymp+\tau') d\tau'}.
+\end{equation}
+Likewise, the backward serial-interval distribution $b_\ssymp(\tau)$ is given by the density of intervals of length $\tau$ ending at \ssymp, relative to the total number of serial intervals ending at \ssymp:
+\begin{equation}
+b_\ssymp(\tau) = 
+\frac{\total(\ssymp-\tau, \ssymp)}{\int \total(\ssymp-\tau', \ssymp) d\tau'}.
 \end{equation}
@@
 \begin{equation}
-f_{0}(\tau) \propto \int_{0}^{\infty} \int_{0}^{\max(0,x+\tau)} \exp(-rx) h(x, \sigma) k(x-\sigma+\tau) \dsigma\dx.
+f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) k(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
 \end{equation}

### 2020-05-06 serial_guide.tex
some tweaks

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-28 20:48:42
+% Created by tikzDevice version 0.12.3 on 2020-05-05 20:39:06
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,470.79) {Forward incubation period};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,470.79) {Intrinsic incubation period};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,495.31) {Forward generation interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,495.31) {Intrinsic generation interval};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,519.83) {Forward incubation period};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,519.83) {Intrinsic incubation period};
 \definecolor{fillColor}{RGB}{255,255,255}

### 2020-05-06 serial_guide.R

@@ -34,9 +34,9 @@ g1 <- ggplot(arrow) +
   geom_segment(aes(2.5, 0.3, xend=3.5, yend=0.3), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
   geom_segment(aes(1.5, 0.4, xend=3.5, yend=0.4), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
   annotate("text", x=2.5, y=0.45, label="Intrinsic serial interval") +
-  annotate("text", x=1, y=0.15, label="Forward incubation period") +
-  annotate("text", x=1, y=0.25, label="Forward generation interval") +
-  annotate("text", x=3, y=0.35, label="Forward incubation period") +
+  annotate("text", x=1, y=0.15, label="Intrinsic incubation period") +
+  annotate("text", x=1, y=0.25, label="Intrinsic generation interval") +
+  annotate("text", x=3, y=0.35, label="Intrinsic incubation period") +
   geom_point(aes(0.5, 0), size=4, shape=21, fill="white", stroke=2) +
   scale_y_continuous(limits=c(-0.15, 0.45)) +
   ggtitle("A. Intrinsic serial interval") +

### 2020-05-06 serial.tex
tweaks

@@
 Here, we resolve this paradox, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
-We develop a new framework for understanding serial intervals and show that the initial forward serial-interval distribution correctly links $r$ and \RR.
-%\jd{Come back to this. Not just over time, right?} \swp{What do you mean? Everything is about time here... you haven't read the results section so maybe that's why?}
-Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can bias estimates of \RR.
+We develop a new framework for understanding serial intervals and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
+Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can significantly bias estimates of \RR.
 We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of epidemics.
@@
 forward serial-interval distributions, by definition, describe the renewal process of infection based on symptom onset dates.
-Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to link the same values of $r$ and \Ro as the intrinsic generation-interval distribution:
-\jd{I don't want to talk about the ``link'' here, because that to me implies the functional link, not just linking a single pair of values.}
+Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to estimate the same values of \Ro from $r$ as the intrinsic generation-interval distribution:
 \begin{equation}

### 2020-05-06 serial.tex
Trying to understand

--- 2020-05-06 serial.tex
@@
 During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
-When incidence grows exponentially, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation};
+During this period, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the initial reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation};
 in this case, we focus on the estimates of the basic reproduction number \Ro (the value of \RR in a fully susceptible population):
@@
 forward serial-interval distributions, by definition, describe the renewal process of infection based on symptom onset dates.
-Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to link the same values of $r$ and \Ro as the intrinsic generation-interval distribution:
-\jd{I don't want to talk about the ``link'' here, because that to me implies the functional link, not just linking a single pair of values.}
+Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to link $r$ and \Ro in the same way as the intrinsic generation-interval distribution (note, however, that the forward serial interval is not necessarily positive):
 \begin{equation}
@@
 \end{equation}
-where the initial forward serial-interval distribution is defined as:
+where the initial forward serial-interval distribution is given by:
 \begin{equation}
@@
 In the Appendix, we provide a mathematical proof of this relationship.
+\jd{$k$ for marginal density is really slowing me down (since Champredon uses k for Rg). Maybe that's just my problem, but maybe we can think of a better letter.}
 
@@
 
+\jd{I thought you were doing disease-model simulations (like DC does).
+I'm surprised we model the distribution of SIs instead of letting it emerge.
+I think I agree that it's still convincing because of the rR link, but it would be better to do the full-simulation way if that's practical.}
 We use a simulation-based approach to compare the estimates of \Ro based on the serial- and generation-interval distributions. 
-To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and correlation $\rho$;
+To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and log-scale correlation $\rho$;
 the multivariate log-normal distribution is parameterized based on parameter estimates for COVID-19 (Table 1).

### 2020-05-06 serial.tex

@@
 forward serial-interval distributions, by definition, describe the renewal process of infection based on symptom onset dates.
-Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to link $r$ and \Ro in the same way as the intrinsic generation-interval distribution (note, however, that the forward serial interval is not necessarily positive):
+Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to estimate the same value of \Ro for a given $r$ as the intrinsic generation-interval distribution (note, however, that the forward serial interval is not necessarily positive):
 \begin{equation}

### 2020-05-10 serial.tex
forgot to merge?

@@
 (B) The intrinsic serial-interval distributions give an incorrect link between $r$ and \Ro.
-(C) The mean initial forward serial interval during the exponential growth phase depends on $r$.
-(D) The squared coefficient of variation of the initial forward serial intervals during the exponential growth phase depends on $r$.
+(C) The mean initial forward serial interval during the exponential growth phase increases with $r$.
+(D) The squared coefficient of variation of the initial forward serial intervals during the exponential growth phase decreases with $r$.
 }
@@
 
-Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different distributions are able to give identical estimates of \Ro.
-In general, generation-interval distributions with higher means and less variability are expected to give higher \Ro for a given $r$ \citep{wallinga2007generation, park2019practical}.
-In this case, the initial forward serial intervals during the exponential growth phase have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
-The effects of higher means (which increases \Ro) and higher variability (which decreases \Ro) cancel out exactly;
-this allows us to estimate the same \Ro using both initial forward serial and intrinsic generation intervals.
-On the other hand, intrinsic serial intervals have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are wider (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
+Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different forward distributions lead to identical estimates of \Ro.
+In general, distributions with higher means and less variability give higher \Ro for a given $r$ \citep{wallinga2007generation, park2019practical}.
+When an outbreak is growing exponentially, forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
+The effects of higher means (which increases \Ro) exactly cancel those of higher variability (which decreases \Ro).
+On the other hand, \emph{intrinsic} serial intervals have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are wider (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
 therefore, we underestimate \Ro when we use the intrinsic serial-interval distribution.

### 2020-05-10 serial.tex
Dinner time

@@
 \textbf{Epidemiological dynamics and changes in mean forward and backward delay distributions.}
-(A) Cumulative incidence over time.
+(A) Cumulative incidence over time. \jd{Would it be easier for people to think about dynamics if we show incidence instead?}
 (B--D) Changes in the mean forward incubation period, generation interval, and serial interval.
@@
 
+\jd{This is hard to follow.
+We still haven't said much about why we're interested in backward intervals.
+And it's hard to think clearly about the assumption of incubation periods being independent of generation intervals.
+The dynamics are a potential complication.
+Presumably we mean that at any given time, we are assuming that these things are independent across individuals.}
 The initial forward serial interval distribution captures the exponential growth phase of an epidemic.
@@
 Since both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant, changes in the forward serial-interval distributions are predominantly driven by changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
+\jd{Are you saying that this is true in general, or for these parameters?
+Have we said enough about these parameters to make this clear to others?}
 In this case, the increase in the mean backward incubation period directly translates to the decrease in the mean forward serial interval.

### 2020-05-11 renewal_det.R
small changes to the code

@@ -12,7 +12,7 @@ renewal_det <- function(R0=2.5,
   gen <- genfun(0:genmax*dt+dt)
   gen <- gen/sum(gen)
   tvec <- seq(0, tmax, by=dt)
-  Ivec <- rep(0, dt*tmax)
+  Ivec <- rep(0, tmax/dt)
   
   r <- optim(0.19, function(x) (1/sum(exp(-x*(0:genmax*dt+dt)) * gen)-R0)^2,
         lower=0.1,
@@ -22,8 +22,8 @@ renewal_det <- function(R0=2.5,
   ## r=0.1904075 for R0=2.5
   Ivec[1:genmax] <- exp(r*1:genmax*dt)
   Ivec[1:genmax] <- I0*Ivec[1:genmax]/sum(Ivec[1:genmax])
-  Svec <- rep(0, dt*tmax)
-  Svec[1:genmax] <- N - cumsum(Ivec)
+  Svec <- rep(0, tmax/dt)
+  Svec[1:genmax] <- N - cumsum(Ivec)[1:genmax]
   
   for (i in (genmax+1):length(tvec)) {
     Ivec[i] <- Svec[i-1] * R0 * sum(Ivec[max(1, i-genmax):(i-1)] * gen[min(i, genmax+1):2])/N

### 2020-05-11 serial.tex
some thoughts and suggestions about Results

@@
 \end{equation}
-where \Ro is the basic reproduction number, and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a fully susceptible population.
+where \Ro is the basic reproduction number, and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a population where the number of susceptibles remains constant).
 Then, the forward generation-interval for a cohort of individuals that were infected at time $\psymp$ follows \citep{champredon2015intrinsic}:
@@
 cumulative incidence from the stochastic simulations in panel A are shown without averaging.
+\jd{I don't see orange lines, and the location of the dashed line is not explained. I guess you use the forward value at time 0? Would the intrinsic value be better?}
 Forward incubation periods and intrinsic generation-intervals are assumed to be independent of each other.
@@
 decrease in incidence via intervention strategies can still cause the backward incubation period to increase, which in turn can decrease serial intervals. 
+\jd{Bringing intervention in here is potentially confusing. If you want to do it, maybe try a bit more lead in?} 
 In general, relative contributions of the three distributions depend on their shapes, correlations between incubation periods and generation intervals, and overall epidemiological dynamics.
 
-Qualitative patterns in the mean backward delays is robust across all delay distributions because they are predominantly driven by the changes in incidence, which in turn affects cohort sizes (\fref{epi}D--F; \eref{backward}).
-When incidence increases exponentially, individuals are more likely to have been infected more recently and therefore, we are more likely to observe shorter intervals (\eref{backexp}).
-When incidence decreases, we are more likely to observe longer intervals for similar but opposite reasons.
+We see similar qualitative patterns in all three backward delays (\fref{epi}E--G; \eref{backward}), because they are predominantly driven by the rate of change in incidence, which in turn affects relative cohort sizes.
+When incidence is increasing, individuals are more likely to have been infected recently and therefore, we are more likely to observe shorter intervals (\eref{backexp}).
+Similarly, when incidence decreases, we are more likely to observe longer intervals.
 
@@
 (A) Schematic representation of line list data collected during an epidemic.
-(B) Changes in the estimate of \Ro based on the observed serial intervals over time.
+(B) Estimates of \Ro based on all observed serial intervals completed by a given time. \jd{Is this accurate?}
 (C) Schematic representation of line list data rearranged by symptom onset date of infectors.
-(B) Changes in the estimate of \Ro based on the cohort-averaged serial intervals over time.
+(D) Estimates of \Ro based on all observed serial intervals started by a given time. 
 Black dashed lines represent the mean initial forward serial interval and \Ro.
@@
 
-Now, we turn to practical issues.
-In order to have an unbiased estimate on \Ro, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e.
+Now we turn to practical issues.
+In order to have an unbiased estimate of \Ro, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e.
 initial forward serial-interval distribution).
@@
 \fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of the basic reproduction number \Ro in our stochastic simulations.
-Notably, even if we can observe \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we still underestimate the initial mean forward serial interval and therefore \Ro by a large amount because the observed serial-interval distribution converges to the intrinsic serial-interval distribution;
-we still underestimate the intrinsic value slightly due to contraction of the forward generation-interval distribution during the susceptible depletion phase (\fref{epi}C).
+Notably, even if we could observe, and average, \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we would still underestimate the initial mean forward serial interval (and therefore \Ro), likely by a large amount, because the observed serial-interval distribution converges to the intrinsic serial-interval distribution
+(in fact, we would even underestimate the intrinsic value slightly due to contraction of the forward generation-interval distribution during the susceptible depletion phase (\fref{epi}C)).
 
-We provide a simple, heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \Ro retrospectively.
+Here we provide a heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \Ro retrospectively.
 Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can rearrange the line list and group observed serial intervals based on the symptom onset date of infectors (\fref{obsrR}C).
 Then, we can compare how estimates of the mean serial interval as well as \Ro change as we incorporate more recent cohorts into the analysis;
-that is, we analyze observed serial intervals from infectors who became symptomatic before time $t$ and evaluate how the estimates change as we increase $t$
+that is, we analyze observed serial intervals from infectors who became symptomatic before time $t$ and evaluate how the estimates change as we increase $t$.
+This approach is analogous to averaging over a set of forward intervals, just as using all information up to a certain time is analogous to averaging over a set of backward intervals.
 (\fref{obsrR}D).
@@
 While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum \emph{observable} serial intervals), increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution.
-The decrease in the mean forward serial interval is likely to be cause by increase in the mean backward serial intervals as well as intervention efforts (e.g., case isolation will shorten the forward generation intervals).
+\jd{Is censoring relevant to negative values as well? We might not have (or can't?) observe events before a certain time? It's a bit confusing.}
+The decrease in the mean forward serial interval was likely caused by increase in the mean backward serial intervals \jd{incubation periods?
+is it obvious to the reader why these are increasing?} as well as intervention efforts which reduce generation intervals by preventing infections once cases are identified.
 \fref{du}B shows that the mean backward serial interval increases over time, reflecting decrease in incidence over time.
@@
 We note that early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
-This example clearly demonstrates the danger of using the observed serial intervals to calculate the basic reproduction number without integrating serial intervals into cohorts..
+This example demonstrates the danger of using the observed serial intervals to calculate the basic reproduction number without integrating serial intervals into cohorts..
 

### 2020-05-12 serial.tex
minor tweaks

@@
 By definition, both generation and serial intervals describe how infection spreads between individuals --- thus, one would expect them both to link between the epidemic growth rate $r$ and the reproduction number \RR.
-However, current theory does not explain how two different distributions can give the same link between $r$ and \RR --- some studies have further demonstrated that generation and serial intervals give different $r$--\RR link.
-\jd{Revisit}
-We provide an answer to the paradox by showing that \emph{forward-looking} serial intervals, which correctly link the two quantities, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
+However, current theory does not explain how two different distributions can estimate the same \RR from $r$ --- some studies have further demonstrated that generation and serial intervals give different estimates of \RR.
+We provide an answer to the paradox by showing that \emph{forward-looking} serial intervals, which correctly estimates \RR from $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
 We provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to serial intervals of COVID-19.
@@
 
-The reproduction number \RR is one of the most important characteristics of an emerging epidemic such as novel coronavirus disease (COVID-19) \citep{majumder2020early}.
+The reproduction number \RR is one of the most important characteristics of an emerging epidemic such as Coronavirus Disease 2019 (COVID-19) \citep{majumder2020early}.
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
@@
 
-At the individual level, we can define the expected time distribution between a primary and a secondary event --- we refer to this distribution as the intrinsic distribution.
-For example, the intrinsic incubation period distribution describes the expected time from infection to symptom onset of an individual.
-Likewise, the intrinsic generation-interval distribution describes the expected time from infection of a primary case to infection of a secondary case in a fully susceptible population; 
-since this is a expected time distribution, it does not take into account dynamical factors such as susceptible depletion or intervention efforts.
-However, the intrinsic time distributions are not always equivalent to realized time distributions at the population level.
+At the individual level, we can define the expected time distribution between a primary and a secondary event for an average infected individual --- we refer to this distribution as the intrinsic distribution.
+For example, the intrinsic incubation period distribution describes the expected time distribution from infection to symptom onset of an average infected individual.
+Likewise, the intrinsic generation-interval distribution describes the expected time distribution of infectious contacts made by an average infected individual.
+However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., distribution of time between primary and secondary events that occur during an epidemic).
+For example, an infectious contact may not result in infection if the contacted individual is not susceptible;
+therefore, the realized generation-interval distribution can be different from the intrinsic generation-interval distribution.
 
@@
 At the individual level, both forward and backward \emph{perspectives}
-must yield identical results (e.g., the length of the incubation
+must yield identical measurement (e.g., the length of the incubation
 period of a given individual is the same whether measured forward from
@@
 \end{equation}
-If we are thinking of incubation periods, then the left hand side of
+If we are thinking of realized incubation periods, then the left hand side of
 this equation is the probability density that an individual
@@
 \begin{equation}
+\underbrace{\Rc (\pinf)}_{\substack{\text{case} \\ \text{reproduction} \\ \text{number}}} 
+\times 
 \underbrace{i(\pinf)}_{\text{incidence}} 
-\times 
-\underbrace{\Rc (\pinf)}_{\substack{\text{case} \\ \text{reproduction} \\ \text{number}}} 
 \times 
@@
 \textbf{Epidemiological dynamics and changes in mean forward and backward delay distributions.}
-(A) Cumulative incidence over time. \jd{Would it be easier for people to think about dynamics if we show incidence instead?}
+(A) Daily incidence over time.
 (B--D) Changes in the mean forward incubation period, generation interval, and serial interval.
@@
 Black lines represent the results of a deterministic simulation.
-Orange lines and points represent the average of 10 stochastic simulations;
-cumulative incidence from the stochastic simulations in panel A are shown without averaging.
+Orange lines (A) represent the results of 10 stochastic simulations.
+Orange points (B-G) represent the average of 10 stochastic simulations.
 \jd{I don't see orange lines, and the location of the dashed line is not explained. I guess you use the forward value at time 0? Would the intrinsic value be better?}
-Forward incubation periods and intrinsic generation-intervals are assumed to be independent of each other.
+Intrinsic incubation periods and intrinsic generation-intervals are assumed to be independent of each other.
 See Table 1 for parameter values.

### 2020-05-12 forward.R

@@ -39,16 +39,27 @@ sir_data <- lapply(simlist, "[[", "data") %>%
 
 sir_data2 <- sir_data %>%
   mutate(
-    time=ceiling(time*5)/5
+    day=floor(time)
   ) %>%
-  group_by(sim, time) %>%
-  filter(infected==max(infected))
+  group_by(day, sim) %>%
+  summarize(
+    cases=tail(infected, 1)-head(infected,1)
+  )
+
+detdata2 <- detdata %>%
+  mutate(
+    day=floor(tvec)
+  ) %>%
+  group_by(day) %>%
+  summarize(
+    cases=tail(ci, 1)-head(ci,1)
+  )
 
 g1 <- ggplot(sir_data2) +
-  geom_line(aes(time, infected, col="Stochastic", group=sim)) +
-  geom_line(data=detdata, aes(tvec, ci, col="Deterministic"), lwd=1) +
+  geom_line(aes(day, cases, col="Stochastic", group=sim)) +
+  geom_line(data=detdata2, aes(day, cases, col="Deterministic"), lwd=1) +
   scale_x_continuous("Time (days)", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_log10("Cumulative incidence", expand=c(0, 0), limits=c(10, 49999)) +
+  scale_y_continuous("Daily incidence", expand=c(0, 0), limits=c(1, 2400)) +
   scale_color_manual(values=c(1, "#D55E00")) +
   ggtitle("A") +
   theme(

### 2020-05-13 serial.tex
Quickly through discussion b4 meeting

@@
 
-Characterizing generation- and serial-interval distributions is critical to understanding the course of an outbreak as they determine the time scale of disease transmission.
-Here, we show that the initial forward serial-interval distributions --- measured during exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
-We further illustrate that epidemiological dynamics can cause the mean backward incubation period to increase over time, which in turn decreases the mean forward serial interval.
-Failing to account for these changes can result in underestimation of \RR.
+Generation- and serial-interval distributions determine the time scale of disease transmission, and are therefore critical to dynamical modeling of infectious outbreaks.
+Here, we show that the initial \emph{forward} serial-interval distribution --- measured during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
+In general, this will not match the intrinsic or the backward serial interval.
+Further, this interval can decrease over time due to disease dynamics. 
+Failing to account for these differences can result in underestimation of \RR.
 
-Our study demonstrates the importance of defining a reference cohort for characterizing any epidemiological time distributions.
+Our study underlines the importance of carefully defining measured epidemiological time distributions.
 Previous studies have shown that generation interval can be either measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
-we generalize their ideas and show that they can be applied to any distributions.
-Changes in the backward delay distributions is expected to be a robust feature across any outbreaks because they are primarily driven by changes in cohort sizes, which, in turn, depend on incidence of infection.
+we generalize these ideas and show that they apply to other epidemiological distributions.
+Changes in the backward delay distributions due to changing cohort sizes is expected to be a pervasive feature of outbreak dynamics.
 Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series of symptomatic cases or infected cases from the reports of confirmed cases by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential, shim2020transmission});
@@
 Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using deconvolution approaches \citep{goldstein2009reconstructing} or mechanstic modeling approaches for proper reconstruction of epidemic time series instead \citep{flaxman2020estimating}.
+\jd{I'm not in love with Goldstein as a practical approach, even though it was more or less my idea! I'd like to learn more about Flaxman.}
 
-Using cohort-based approaches, we define forward and backward serial intervals.
-The forward serial-interval distribution describes the renewal process between symptomatic cases, and therefore, its initial distribution provides the correct link between $r$ and \RR.
 While our results support the use of serial interval distributions for calculating \RR, 
@@
 In particular, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial interval data for accurate estimation of time-varying reproduction numbers;
-however, our study demonstrates that early serial interval data is required to estimate \RR and using up-to-date serial interval data can, in fact, underestaimte \RR.
-Moreover, \cite{tempvar} recently analyzed case reports of COVID-19 from over 30 countries to estimate their time-varying reproduction numbers but relied on a serial-interval distribution;
+however, our study demonstrates that early serial interval data is required to estimate \RR and using up-to-date serial interval data can, in fact, underestimate \RR.
+\jd{I'm confused by this.
+We should be working towards methods that don't get the wrong answer just because you give them more information.
+Also, if \RR is assumed to be time-varying then of course you want to be up-to-date, no?}
+Moreover, \cite{tempvar} recently analyzed case reports of COVID-19 from over 30 countries to estimate their time-varying reproduction numbers but relied on a [fixed] serial-interval distribution;
 given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the initial forward serial interval distributions is likely to vary across different countries.
+\jd{Isn't it more interesting for our purposes whether they appropriately considered the \emph{forward} interval?}
 We suggest that modelers should aim to characterize spatiotemporal variation in initial forward serial-interval distributions and understand their changes over time.
@@
 
-Our study also demonstrates that there are multiple serial-interval distributions that correspond to the same set of generation-interval and incubation period distributions depending on their correlations;
-all of them can provide the correct link between $r$--\RR (\fref{rR}).
-Conversely, this means that not explicitly accounting for their correlations can bias the estimate of the intrinsic generation-interval distribution from the serial-interval distribution.
+Our study also underlines the fact that the serial-interval distribution depends not only on the generation-interval and incubation-period distributions, but also on their correlations.
+This implies that not considering this correlation can bias the estimates of the intrinsic generation-interval distribution from the serial-interval distribution.
 Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the differences between the incubation periods of infectors and those of infectees (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating});
+\jd{Need to be clearer what source of difference is relevant here.}
 There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.
@@
 Our study is not without limitations.
-Here, we assumed that all individuals develop symptoms and that the the entire transmission process (e.g., direction of transmission, symptom onset dates, infection dates, etc.) are observable.
+We assumed that all individuals develop symptoms and that the the entire transmission process (e.g., direction of transmission, symptom onset dates, infection dates, etc.) are observable.
+\jd{I don't think we quite assumed that infection dates are observable, we can discuss.}
 In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.
 For example, symptom onset dates cannot be used as a reliable proxy for determining the direction of transmission as infectees may develop symptoms before their infectors.
+\jd{Not an example, and not really something we don't consider.}
 Based on the COVID-19 parameters (Table 1), we expect roughly 3\% of infectees to develop symptoms before their infectors during the exponential growth period; 
@@
 While we focused on the effect of epidemiological dynamics on the serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
-Individual-level interventions, such as case isolation, directly affect individual's ability to transmit and will shorten the forward generation- and serial-intervals.
+Individual-level interventions, such as case isolation, directly affect individuals' ability to transmit and will shorten the forward generation- and serial-intervals.
 Population-level interventions, such as social distancing, have qualitatively similar effects on epidemiogical dynamics as susceptible depletion;
@@
 don't have a good sentence at the moment so I'm just going to leave it as is.}
+\jd{Maybe leave out the susceptible depletion and just jump straight to the sunky/trace stuff? }
 

### 2020-05-14 serial.tex
ok maybe better

@@
 \newcommand{\gdist}{g} %% generation-interval distribution
+\newcommand{\idist}{\ell} %% incubation period distribution
 
@@
 
-The reproduction number \RR is one of the most important characteristics of an emerging epidemic such as Coronavirus Disease 2019 (COVID-19) \citep{majumder2020early}.
+The reproduction number \RR is one of the most important characteristics of an emerging epidemic such as coronavirus disease 2019 (COVID-19) \citep{majumder2020early}.
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
@@
 While serial intervals are similar to generation intervals, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence};
-some studies further suggested that using serial intervals can give different estimates of \RR \citep{britton2019estimation}.
+some studies further suggested that using serial intervals can give different estimates of \RR \citep{britton2019estimation, ganyani2020estimating}.
 
@@
 Likewise, the intrinsic generation-interval distribution describes the expected time distribution of infectious contacts made by an average infected individual.
-However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., distribution of time between primary and secondary events that occur during an epidemic).
-For example, an infectious contact may not result in infection if the contacted individual is not susceptible;
+However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., distribution of time between realized primary and secondary events that occur during an epidemic).
+For example, an infectious contact may not result in infection if the contacted individual has already been infected;
 therefore, the realized generation-interval distribution can be different from the intrinsic generation-interval distribution.
@@
 a secondary cohort is defined similarly based on the secondary events.
-For example, when we are measuring incubation periods, a \textbf{p}rimary cohort consists of all individuals who became infected at time $\psymp$.
+For example, when we are measuring incubation periods, a primary cohort consists of all individuals who became infected at time $\psymp$.
 Similarly, when we are measuring serial intervals, a primary cohort consists of all individuals who became symptomatic at time $\psymp$.
-Then, for each primary cohort $\psymp$, we can define the expected time distribution between primary and secondary events.
+Then, for each primary cohort at time $\psymp$, we can define the expected time distribution between primary and secondary events.
 We refer to this distribution as the forward delay distribution and denote it as $f_\psymp(\tau)$.
 
-Likewise, we define the backward delay distribution $b_\ssymp(\tau)$ for a \textbf{s}econdary cohort at time $\ssymp$:
+Likewise, we define the backward delay distribution $b_\ssymp(\tau)$ for a secondary cohort at time $\ssymp$:
 The backward delay distribution describes the time delays between a primary and secondary host given that the secondary event occurred at time $\ssymp$.
@@
 
-At the individual level, both forward and backward \emph{perspectives}
-must yield identical measurement (e.g., the length of the incubation
+Both forward and backward perspectives
+must yield identical \emph{measurement} (e.g., the length of the incubation
 period of a given individual is the same whether measured forward from
@@
 \eref{backward} suggests that backward delay distributions change over time even if their corresponding forward delay distribution does not change:
-Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations (i.e., they are measured from a cohort of individuals whose secondary events occurred at160the same time).
+Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations (i.e., they are measured from a cohort of individuals whose secondary events occurred at the same time).
 When the cohort size is increasing (or decreasing) over time, we are biased to observe shorter (or longer) delays when we look backward.
@@
 \end{equation}
-where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\gtime$ represents the realized generation interval.
+where $x_0$ and $x_1$ represent incubation periods of an infector and an infectee, respectively, and $\gtime$ represents the generation interval.
 These studies assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
@@
 
-To correctly link serial intervals to the renewal process between cases based on symptom onset dates, we must use the forward serial interval (i.e., use the perspective of a cohort of infectors that share the same symptom onset time).
+To correctly link realized serial intervals to the renewal process between cases based on symptom onset dates, we must use the forward serial interval (i.e., use the perspective of a cohort of infectors that share the same symptom onset time).
 Given that an infector became symptomatic at time $\psymp$, to calculate the forward serial interval we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when they became symptomatic.
 In \fref{diagram}B, we see that $x_0$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\psymp$;
-$\gtime$ follows the forward generation-interval distribution of the cohort of infector who came infected at time $\psymp - x_0$;
+$\gtime$ follows the forward generation-interval distribution of the cohort of infectors who came infected at time $\psymp - x_0$;
 and $x_1$ follows the forward incubation period distribution of the cohort of infectees who became infected at time $\psymp - x_0 + \gtime$.
-Likewise, we can define the backward serial interval distribution for a secondary cohort $\ssymp$ (\fref{diagram}C).
-This conceptual framework clearly demonstrates that the distributions of $x_0$, $\ssymp$, and $x_1$ (and therefore the distributions of serial intervals) depend on the reference cohort and the corresponding cohort time.
-
-% \jd{Could we skip this \P?} 
-% Given that an infectee became symptomatic at time $\ssymp$, we have to first go backward in time by asking when the infectee became infected and when the infector became infected; 
-% then, we have to go forward in time by asking when the infector became symptomatic.
-% In this case, $x_1$ follows the backward incubation period distribution of the cohort of infectees who became symptomatic at time $\ssymp$;
-% $\gtime$ follows the backward generation-interval distribution of the cohort of infectees who became infected at time $\ssymp-x_1$;
-% and $x_0$ follows the forward incubation period distribution of the cohort of infectors who became infected at time $\ssymp-x_1-\gtime$.
+Likewise, we can define the backward serial interval distribution for a cohort of infectees who became symptomatic at time $\ssymp$ (\fref{diagram}C).
+This conceptual framework clearly demonstrates that the distributions of $x_0$, $\ssymp$, and $x_1$ (and therefore the distributions of realized serial intervals) depend on the reference cohort and the corresponding cohort time.
 
 To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total number of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
-The number of serial intervals between time $\psymp$ and $\ssymp$ given that the infectors became infected at time $\pinf$ and the infectees became infected at time $\sinf$ depends on the amount of infection that occur between time $\pinf$ and $\sinf$ as well as the densities of forward incubation period between $\pinf$ and $\psymp$ (incubation periods of infectors) as well as $\sinf$ and $\ssymp$ (incubation periods of infectees):
+The number of serial intervals between time $\psymp$ and $\ssymp$, given that the infectors became infected at time $\pinf$ and the infectees became infected at time $\sinf$, depends on the amount of infection that occur between time $\pinf$ and $\sinf$ as well as the densities of forward incubation periods between $\pinf$ and $\psymp$ (realized incubation periods of infectors) as well as $\sinf$ and $\ssymp$ (realized incubation periods of infectees):
 \begin{equation}
@@
 \times
-\underbrace{k_{\sinf}(\ssymp - \sinf)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period } \ssymp-\sinf \\ \text{(of infectees)}}},
+\underbrace{\idist_{\sinf}(\ssymp - \sinf)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period } \ssymp-\sinf \\ \text{(of infectees)}}},
 \end{equation}
@@
 \begin{equation}
-\total (\psymp,\ssymp) = \int_{-\infty}^{\psymp} \int_{\pinf}^{\ssymp} \Rc (\pinf) i(\pinf) h_{\pinf}(\psymp-\pinf, \sinf - \pinf) k_{\sinf}(\ssymp - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
+\total (\psymp,\ssymp) = \int_{-\infty}^{\psymp} \int_{\pinf}^{\ssymp} \Rc (\pinf) i(\pinf) h_{\pinf}(\psymp-\pinf, \sinf - \pinf) \idist_{\sinf}(\ssymp - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
 \end{equation}
@@
 \begin{aligned}
-k(x) &= \int_0^\infty h(x, \tau) \dtau\\
+\idist(x) &= \int_0^\infty h(x, \tau) \dtau\\
 \gdist(\tau) &= \int_0^\infty h(x, \tau) \dx
@@
 
+We use this framework to illustrate how the realized epidemiological time distributions vary over the course of an epidemic and depend on the perspective.
+We run deterministic as well as stochastic simulations based on the renewal equations (see Appendix) using previously estimated intrinsic incubation period and intrinsic generation-interval distributions for COVID-19 (Table 1) and compare both the forward and backward delay distributions;
+in particular, we focus on the realized incubation period, generation-interval, and serial-interval distributions.
+
 \subsection{Linking $r$ and \RR}
@@
 During this period, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the initial reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation};
-in this case, we focus on the estimates of the basic reproduction number \Ro (the value of \RR in a fully susceptible population):
+in this case, we focus on the estimates of the basic reproduction number \Ro (the value of \RR in a fully susceptible population, $S(t) \approx 1$):
 \begin{equation}
@@
 \begin{equation}
-f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) k(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
+f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
 \end{equation}
 In the Appendix, we provide a mathematical proof of this relationship.
-\jd{$k$ for marginal density is really slowing me down (since Champredon uses k for Rg). Maybe that's just my problem, but maybe we can think of a better letter.}
+We further compare this with the estimate of \Ro based on the intrinsic serial-interval distribution:
+\begin{equation}
+\frac{1}{\Rintrinsic} = \int_{-\infty}^\infty \exp(-r\tau) q(\tau) \mathrm{d} \tau,
+\end{equation}
+where the intrinsic serial-interval distribution does not depend on disease dynamics:
+\begin{equation}
+q(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
+\end{equation}
 
@@
 
-\jd{I thought you were doing disease-model simulations (like DC does).
-I'm surprised we model the distribution of SIs instead of letting it emerge.
-I think I agree that it's still convincing because of the rR link, but it would be better to do the full-simulation way if that's practical.}
-We use a simulation-based approach to compare the estimates of \Ro based on the serial- and generation-interval distributions. 
-To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and log-scale correlation $\rho$;
-the multivariate log-normal distribution is parameterized based on parameter estimates for COVID-19 (Table 1).
-We construct forward serial intervals during the exponential growth period as follows:
-\begin{equation}
-F_i = -X_{0,i} + (G_i|X_{0,i}) + X_{1,i},
-\end{equation}
-where the backward incubation period $X_{0,i}$ of an infector is simulated by drawing random log-normal samples $Y_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $Y_i$, each weighted by the inverse of the exponential growth function $\exp(-rY_i)$;
-the intrinsic generation interval conditional on the incubation period of the infector $(G_i|X_{0,i})$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(X_{0,i}) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
-the forward incubation period $X_{1,i}$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
-We then calculate the basic reproduction number \Ro using the empirical estimator:
-\begin{equation}
-\Ro = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r F_i)}.
-\end{equation}
-We compare this with an estimate of \Ro based on the intrinsic serial-interval distribution in which the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
-\begin{equation}
-  \Rintrinsic = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r Q_i)},
-\end{equation}
-where
-\begin{equation}
-Q_i = -Y_i + (G_i|Y_i) + X_{1,i}.
-\end{equation}
-
 \section{Results}
@@
 In general, distributions with higher means and less variability give higher \Ro for a given $r$ \citep{wallinga2007generation, park2019practical}.
-When an outbreak is growing exponentially, forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
+When incidence is growing exponentially, forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
 The effects of higher means (which increases \Ro) exactly cancel those of higher variability (which decreases \Ro).
@@
 
-\jd{This is hard to follow.
-We still haven't said much about why we're interested in backward intervals.
-And it's hard to think clearly about the assumption of incubation periods being independent of generation intervals.
-The dynamics are a potential complication.
-Presumably we mean that at any given time, we are assuming that these things are independent across individuals.}
 The initial forward serial interval distribution captures the exponential growth phase of an epidemic.
-Now, we characterize how forward and backward serial intervals vary over the course of an epidemic when incubation periods and generation intervals are independent.
+Now, we characterize how forward and backward serial intervals vary over the course of an epidemic.
+While the forward serial-interval distribution is our primary focus, characterizing the difference between the forward and the backward distributions are important because the observed intervals during on ongoing epidemic are like backward distributions:
+we typically identify infected individuals and ask when they were infected by whom.
+Similarly, when we are estimating the incubation period of an individual, we often observe their symptom onset date and try to estimate when they were infected.
+
 \fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
@@
 
-\subsection{Linking $r$ and \RR using serial-interval distributions}
+\subsection{Linking $r$ and \Ro using serial-interval distributions}
 
@@
 
+\subsection{Comparing the estimates of \Ro using the initial forward and the intrinsic serial-interval distributions}
+
+We use a simulation-based approach to compare the estimates of \Ro based on the serial- and generation-interval distributions. 
+To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and log-scale correlation $\rho$;
+the multivariate log-normal distribution is parameterized based on parameter estimates for COVID-19 (Table 1).
+We construct forward serial intervals during the exponential growth period as follows:
+\begin{equation}
+F_i = -X_{0,i} + (G_i|X_{0,i}) + X_{1,i},
+\end{equation}
+where the backward incubation period $X_{0,i}$ of an infector is simulated by drawing random log-normal samples $Y_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $Y_i$, each weighted by the inverse of the exponential growth function $\exp(-rY_i)$;
+the intrinsic generation interval conditional on the incubation period of the infector $(G_i|X_{0,i})$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(X_{0,i}) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
+the forward incubation period $X_{1,i}$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
+We then calculate the basic reproduction number \Ro using the empirical estimator:
+\begin{equation}
+\Ro = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r F_i)}.
+\end{equation}
+We compare this with an estimate of \Ro based on the intrinsic serial-interval distribution in which the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
+\begin{equation}
+  \Rintrinsic = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r Q_i)},
+\end{equation}
+where
+\begin{equation}
+Q_i = -Y_i + (G_i|Y_i) + X_{1,i}.
+\end{equation}
+
+\pagebreak
+
 \bibliography{serial}

### 2020-05-15 serial.tex
done

@@
 Bryan T.\ Grenfell\textsuperscript{1,2,9}
-Jonathan Dushoff\textsuperscript{3,4,5,*}
+Jonathan Dushoff\textsuperscript{3,4,5}
 \\
@@
 Orange points (B-G) represent the average of 10 stochastic simulations.
-\jd{I don't see orange lines, and the location of the dashed line is not explained. I guess you use the forward value at time 0? Would the intrinsic value be better?}
+Dashed lines represent the mean initial forward delay.
 Intrinsic incubation periods and intrinsic generation-intervals are assumed to be independent of each other.
@@
 Now, we characterize how forward and backward serial intervals vary over the course of an epidemic.
-While the forward serial-interval distribution is our primary focus, characterizing the difference between the forward and the backward distributions are important because the observed intervals during on ongoing epidemic are like backward distributions:
+While the forward serial-interval distribution is our primary focus, understanding the differences between the forward and the backward distributions are important because the observed intervals during on ongoing epidemic are like backward distributions:
 we typically identify infected individuals and ask when they were infected by whom.
-Similarly, when we are estimating the incubation period of an individual, we often observe their symptom onset date and try to estimate when they were infected.
+Similarly, when we are estimating the incubation period of an individual, we often observe their symptom onset date of infected individuals and try to estimate when they were infected (e.g., \cite{backer2020incubation}).
 
@@
 The forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation period distributions, (ii) the forward generation-interval distributions, and (iii) the forward incubation period distributions.
-Since both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant, changes in the forward serial-interval distributions are predominantly driven by changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
-\jd{Are you saying that this is true in general, or for these parameters?
-Have we said enough about these parameters to make this clear to others?}
+For COVID-19 parameters (Table 1), both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
+therefore, changes in the forward serial-interval distributions are predominantly driven by changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
 In this case, the increase in the mean backward incubation period directly translates to the decrease in the mean forward serial interval.
-Therefore, the forward serial intervals can decrease over time even in the absence of significant depletion of the susceptible pool;
-decrease in incidence via intervention strategies can still cause the backward incubation period to increase, which in turn can decrease serial intervals. 
-\jd{Bringing intervention in here is potentially confusing. If you want to do it, maybe try a bit more lead in?} 
-In general, relative contributions of the three distributions depend on their shapes, correlations between incubation periods and generation intervals, and overall epidemiological dynamics.
+Since the increase in the mean backward period is driven by the decreasing incidence, which can still occur in the absence of significant depletion of the susceptible pool via intervention, decrease in the mean forward serial interval may be a robust feature in COVID-19 outbreaks.
+In general, relative contributions of the three distributions depend on their shapes, correlations between intrinsic incubation periods and generation intervals, and overall epidemiological dynamics.
 
@@
 Similarly, when incidence decreases, we are more likely to observe longer intervals.
+Neglecting these changes in the backward distributions will necessarily bias the inference of the intrinsic distributions from the observed distributions.
 
@@
 (A) Schematic representation of line list data collected during an epidemic.
-(B) Estimates of \Ro based on all observed serial intervals completed by a given time. \jd{Is this accurate?}
+(B) Estimates of \Ro based on all observed serial intervals completed by a given time.
 (C) Schematic representation of line list data rearranged by symptom onset date of infectors.
@@
 Now we turn to practical issues.
-In order to have an unbiased estimate of \Ro, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e.
-initial forward serial-interval distribution).
+In order to have an unbiased estimate of \Ro, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e., initial forward serial-interval distribution).
 However, when an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
@@
 \fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of the basic reproduction number \Ro in our stochastic simulations.
-Notably, even if we could observe, and average, \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we would still underestimate the initial mean forward serial interval (and therefore \Ro), likely by a large amount, because the observed serial-interval distribution converges to the intrinsic serial-interval distribution
-(in fact, we would even underestimate the intrinsic value slightly due to contraction of the forward generation-interval distribution during the susceptible depletion phase (\fref{epi}C)).
+Notably, even if we could observe, and average, \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we would still underestimate the initial mean forward serial interval (and therefore \Ro), likely by a large amount, because the observed serial-interval distribution converges to the intrinsic serial-interval distribution;
+in fact, we would even underestimate the intrinsic value slightly due to contraction of the forward generation-interval distribution during the susceptible depletion phase (\fref{epi}C).
 
@@
 that is, we analyze observed serial intervals from infectors who became symptomatic before time $t$ and evaluate how the estimates change as we increase $t$.
-This approach is analogous to averaging over a set of forward intervals, just as using all information up to a certain time is analogous to averaging over a set of backward intervals.
-(\fref{obsrR}D).
+This approach is analogous to averaging over a set of forward intervals, just as using all information up to a certain time is analogous to averaging over a set of backward intervals (\fref{obsrR}D).
 During the exponential growth phase, the estimates of the mean serial interval and \Ro are consistent with the target value;
@@
 Solid lines represent the estimated locally estimated scatterplot smoothing (LOESS) fits.
-The dashed line represents the maximum observable delay for each primary cohort calculated from the most recent observed symptom onset date.
+The dashed line represents the maximum and minimum observable delays across the range of .
 (C) Cohort-averaged estimates of \Ro assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
@@
 \fref{du}A shows that the mean forward serial interval decreases over time.
-While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum \emph{observable} serial intervals), increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution.
-\jd{Is censoring relevant to negative values as well? We might not have (or can't?) observe events before a certain time? It's a bit confusing.}
-The decrease in the mean forward serial interval was likely caused by increase in the mean backward serial intervals \jd{incubation periods?
-is it obvious to the reader why these are increasing?} as well as intervention efforts which reduce generation intervals by preventing infections once cases are identified.
-\fref{du}B shows that the mean backward serial interval increases over time, reflecting decrease in incidence over time.
+While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and \emph{maximum observable} serial intervals), increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution;
+increase in the proportion of negative serial intervals is unlikely to be driven by the left-censoring (indicated by the farness between the quantiles of the observed serial intervals and \emph{minimum observable} serial intervals).
+The decrease in the mean forward serial interval was likely to be caused by increase in the mean backward incubation periods, reflecting decrease in COVID-19 cases in China, as well as intervention efforts which reduce generation intervals by preventing infections once cases are identified.
+\fref{du}B shows that the mean backward serial interval increases over time, also reflecting decrease in COVID-19 cases in China.
 
 While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculate earlier based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
-These results indicate that previous estimates of incubation period and generation-intervals may have been underestimated as neither study explicitly accounts for right-censoring (Table 1).
+These results indicate that previous estimates of incubation period and generation-intervals (Table 1) may have been underestimated as neither study explicitly accounts for the fact that the observed distributions are like backward distributions.
 
@@
 We note that early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
-This example demonstrates the danger of using the observed serial intervals to calculate the basic reproduction number without integrating serial intervals into cohorts..
+This example demonstrates the danger of using the observed serial intervals to calculate the basic reproduction number without integrating serial intervals into cohorts.
 
@@
 
-Generation- and serial-interval distributions determine the time scale of disease transmission, and are therefore critical to dynamical modeling of infectious outbreaks.
+Generation and serial intervals determine the time scale of disease transmission, and are therefore critical to dynamical modeling of infectious outbreaks.
 Here, we show that the initial \emph{forward} serial-interval distribution --- measured during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
@@
 these studies effectively assume constant backward delay distributions.
-Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using deconvolution approaches \citep{goldstein2009reconstructing} or mechanstic modeling approaches for proper reconstruction of epidemic time series instead \citep{flaxman2020estimating}.
-\jd{I'm not in love with Goldstein as a practical approach, even though it was more or less my idea! I'd like to learn more about Flaxman.}
+Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using dynamical approaches that model incidence as well as reporting delays explicitly (e.g., \citep{flaxman2020estimating}).
 
@@
 In particular, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial interval data for accurate estimation of time-varying reproduction numbers;
-however, our study demonstrates that early serial interval data is required to estimate \RR and using up-to-date serial interval data can, in fact, underestimate \RR.
-\jd{I'm confused by this.
-We should be working towards methods that don't get the wrong answer just because you give them more information.
-Also, if \RR is assumed to be time-varying then of course you want to be up-to-date, no?}
-Moreover, \cite{tempvar} recently analyzed case reports of COVID-19 from over 30 countries to estimate their time-varying reproduction numbers but relied on a [fixed] serial-interval distribution;
-given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the initial forward serial interval distributions is likely to vary across different countries.
-\jd{Isn't it more interesting for our purposes whether they appropriately considered the \emph{forward} interval?}
+however, our study demonstrates that early serial interval data is required to estimate \RR and that using up-to-date serial interval data (without accounting for changes in the forward serial-interval distribution) can, in fact, underestimate \RR.
+Many studies have already estimated the (time-varying) reproduction numbers for COVID-19 epidemics using aggregated serial interval data (e.g., \cite{tempvar,du2020serial,pan2020jama,zhang2020evolving});
+these studies should re-assess whether they appropriately considered the \emph{forward} serial interval.
+Given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the initial forward serial interval distributions are also likely to vary across different countries.
 We suggest that modelers should aim to characterize spatiotemporal variation in initial forward serial-interval distributions and understand their changes over time.
@@
 
-Our study also underlines the fact that the serial-interval distribution depends not only on the generation-interval and incubation-period distributions, but also on their correlations.
+Our study also underlines the fact that the serial-interval distribution depends not only on the generation-interval and incubation-period distributions, but also on their intrinsic correlations.
 This implies that not considering this correlation can bias the estimates of the intrinsic generation-interval distribution from the serial-interval distribution.
-Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the differences between the incubation periods of infectors and those of infectees (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating});
-\jd{Need to be clearer what source of difference is relevant here.}
+Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the dynamical differences between the realized incubation periods of infectors (backward-looking) and those of infectees (forward looking) (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
 There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.
@@
 Our study is not without limitations.
-We assumed that all individuals develop symptoms and that the the entire transmission process (e.g., direction of transmission, symptom onset dates, infection dates, etc.) are observable.
-\jd{I don't think we quite assumed that infection dates are observable, we can discuss.}
+We assumed that all individuals develop symptoms and that the the entire transmission process, including all relevant epidemiological delays, are known exactly.
 In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.
-For example, symptom onset dates cannot be used as a reliable proxy for determining the direction of transmission as infectees may develop symptoms before their infectors.
-\jd{Not an example, and not really something we don't consider.}
-Based on the COVID-19 parameters (Table 1), we expect roughly 3\% of infectees to develop symptoms before their infectors during the exponential growth period; 
-this probability increases as epidemic progresses because the mean backward incubation period increases.
 Biases in the observed serial intervals will necessarily bias the estimates of \RR. 
@@
 Individual-level interventions, such as case isolation, directly affect individuals' ability to transmit and will shorten the forward generation- and serial-intervals.
-Population-level interventions, such as social distancing, have qualitatively similar effects on epidemiogical dynamics as susceptible depletion;
-therefore, we expect these intervention efforts to also (indirectly) shorten the forward generation- and serial-intervals.
-\swp{Sunky suggested: ``Social distancing will squeeze the contacts into the household, thus introduce high degree of clustering, which will shorten the generation interval as well (running out of susceptible within the household before the infectious period ends).'' and I like the idea of mentioning this briefly and cite our previous contact\_trace paper...
-don't have a good sentence at the moment so I'm just going to leave it as is.}
-\jd{Maybe leave out the susceptible depletion and just jump straight to the sunky/trace stuff? }
+Population-level interventions, such as social distancing, can squeeze contacts into household and introduce high degree of clustering, which, in turn, will shorten the realized generation intervals due to local depletion of the susceptible pool within households \citep{park2019inferring}.
 
@@
 
+\subsection{Applications: SEIR model}
+
+Consider a Susceptible-Exposed-Infectious-Recovered model:
+\begin{equation}
+\begin{aligned}
+\frac{\mathrm{d}S}{\mathrm{d}t} &= - \beta S I\\
+\frac{\mathrm{d}E}{\mathrm{d}t} &= \beta S I - \sigma E\\
+\frac{\mathrm{d}I}{\mathrm{d}t} &= \sigma E - \gamma I \\
+\frac{\mathrm{d}R}{\mathrm{d}t} &= \gamma I \\
+\end{aligned}
+\end{equation}
+where $\beta$ is the transmission rate, $1/\sigma$ is the mean latent period, and $1/\gamma$ is the mean infectious period.
+We further assume that the latent period is equivalent to incubation period; in other words, infected individuals can only transmit after symptom onset.
+Then, the generation interval will be always longer than the incubation period.
+
+The joint probability distribution of the intrinsic incubation periods and intrinsic generation intervals for this model can be written as:
+\begin{equation}
+h(x, \tau) = \begin{cases}
+0 & x > \tau\\
+\gamma \sigma \exp(-\gamma (\tau-x)-\sigma x) & x \leq \tau
+\end{cases}
+\end{equation}
+Then, the intrinsic generation-interval distribution is given by:
+\begin{equation}
+\begin{aligned}
+g(\tau) &= \int_0^\tau h(x, \tau) \dx\\
+&= \frac{\gamma \sigma}{\sigma-\gamma} (\exp(-\gamma \tau) - \exp(-\sigma \tau))
+\end{aligned}
+\end{equation}
+On the other hand, the initial forward serial-interval distribution is given by:
+\begin{equation}
+\begin{aligned}
+f_{0}(\tau) &\propto \int_{-\infty}^{0} \int_{0}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
+&\propto \int_{-\infty}^{0} \int_{0}^{\tau}\exp(r \pinf) \exp(-\gamma \sinf+ \sigma \pinf) \exp(-\sigma(\tau-\sinf)) \, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
+&\propto  \exp(-\sigma \tau) \int_{-\infty}^{0} \int_{0}^{\tau} \exp((\sigma-\gamma) \sinf) \exp((r+ \sigma) \pinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
+&\propto  (\exp(-\gamma \tau) - \exp(-\sigma \tau)) \int_{-\infty}^{0} \exp((r+ \sigma) \pinf)\,\mathrm{d}\pinf\\
+&\propto  \exp(-\gamma \tau) - \exp(-\sigma \tau)
+\end{aligned}
+\end{equation}
+Therefore, both the intrinsic generation interval and the initial forward serial intervals are identically distributed.
+
 \pagebreak

### 2020-05-15 serial_analysis.tex
done

--- 2020-04-14 serial_analysis.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-04-12 17:51:37
+% Created by tikzDevice version 0.12.3 on 2020-05-14 21:20:58
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,289.08);
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (867.24,289.08);
+\begin{scope}
+\path[clip] ( 10.17,  0.00) rectangle (278.91,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,289.08);
-\end{scope}
-\begin{scope}
-\path[clip] ( 34.64, 30.69) rectangle (283.58,266.42);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 10.17,  0.00) rectangle (278.91,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 34.64, 30.69) rectangle (283.58,266.42);
+\path[fill=fillColor] ( 44.82, 30.69) rectangle (273.41,266.42);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (206.43,192.30) {maximum observable};
+
+\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 92.13, 70.86) {minimum observable};
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (130.54,266.42) --
+	(137.68,259.28) --
+	(144.83,252.14) --
+	(151.97,244.99) --
+	(159.11,237.85) --
+	(166.26,230.71) --
+	(173.40,223.56) --
+	(180.54,216.42) --
+	(187.69,209.27) --
+	(194.83,202.13) --
+	(201.97,194.99) --
+	(209.12,187.84) --
+	(216.26,180.70) --
+	(223.40,173.56) --
+	(230.55,166.41) --
+	(237.69,159.27) --
+	(244.83,152.13) --
+	(251.98,144.98) --
+	(259.12,137.84) --
+	(266.27,130.70) --
+	(273.41,123.55);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.82,116.41) --
+	( 51.96,109.26) --
+	( 59.10,102.12) --
+	( 66.25, 94.98) --
+	( 73.39, 87.83) --
+	( 80.53, 80.69) --
+	( 87.68, 73.55) --
+	( 94.82, 66.40) --
+	(101.96, 59.26) --
+	(109.11, 52.12) --
+	(116.25, 44.97) --
+	(123.39, 37.83) --
+	(130.54, 30.69);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 44.82,137.84) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.10,219.10) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.25,183.08) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.39,194.99) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.53,194.99) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.68,223.56) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.82,223.56) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.96,194.99) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.11,216.42) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,184.27) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.39,159.58) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.54,159.72) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.68,165.29) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.83,150.04) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.97,160.95) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.11,149.30) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.26,144.74) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.40,149.93) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.54,133.26) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.69,138.29) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.83,129.96) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.97,127.28) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.12,127.33) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.26,119.77) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (223.40,115.57) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.55,124.85) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (237.69,122.12) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (244.83,109.26) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (259.12, 87.83) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (273.41, 73.55) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
+	( 44.82,137.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
+	( 44.82,137.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
+	( 44.82,137.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,236.60) --
+	( 59.10,236.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,236.60) --
+	( 59.10,191.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,191.59) --
+	( 59.10,191.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,227.49) --
+	( 66.25,227.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,227.49) --
+	( 66.25,152.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,152.84) --
+	( 66.25,152.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,208.56) --
+	( 73.39,208.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,208.56) --
+	( 73.39,181.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,181.41) --
+	( 73.39,181.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,236.42) --
+	( 80.53,236.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,236.42) --
+	( 80.53,141.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,141.41) --
+	( 80.53,141.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
+	( 87.68,223.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
+	( 87.68,223.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
+	( 87.68,223.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,257.49) --
+	( 94.82,257.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,257.49) --
+	( 94.82,189.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,189.63) --
+	( 94.82,189.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,208.56) --
+	(101.96,208.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,208.56) --
+	(101.96,181.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,181.41) --
+	(101.96,181.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
+	(109.11,216.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
+	(109.11,216.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
+	(109.11,216.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,214.81) --
+	(116.25,214.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,214.81) --
+	(116.25,159.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,159.81) --
+	(116.25,159.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,229.99) --
+	(123.39,229.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,229.99) --
+	(123.39,109.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,109.98) --
+	(123.39,109.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,212.85) --
+	(130.54,212.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,212.85) --
+	(130.54,126.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,126.23) --
+	(130.54,126.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,198.92) --
+	(137.68,198.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,198.92) --
+	(137.68,122.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,122.84) --
+	(137.68,122.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,212.31) --
+	(144.83,212.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,212.31) --
+	(144.83,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,109.26) --
+	(144.83,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,223.56) --
+	(151.97,223.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,223.56) --
+	(151.97,122.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,122.30) --
+	(151.97,122.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,222.31) --
+	(159.11,222.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,222.31) --
+	(159.11, 91.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11, 91.58) --
+	(159.11, 91.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,191.77) --
+	(166.26,191.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,191.77) --
+	(166.26,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,109.26) --
+	(166.26,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,190.52) --
+	(173.40,190.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,190.52) --
+	(173.40,116.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,116.41) --
+	(173.40,116.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54,167.13) --
+	(180.54,167.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54,167.13) --
+	(180.54, 87.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54, 87.48) --
+	(180.54, 87.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69,193.74) --
+	(187.69,193.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69,193.74) --
+	(187.69, 80.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69, 80.69) --
+	(187.69, 80.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83,181.77) --
+	(194.83,181.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83,181.77) --
+	(194.83, 87.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83, 87.48) --
+	(194.83, 87.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97,172.84) --
+	(201.97,172.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97,172.84) --
+	(201.97, 44.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97, 44.97) --
+	(201.97, 44.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12,167.84) --
+	(209.12,167.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12,167.84) --
+	(209.12, 70.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12, 70.69) --
+	(209.12, 70.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26,144.98) --
+	(216.26,144.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26,144.98) --
+	(216.26, 79.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26, 79.26) --
+	(216.26, 79.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40,142.13) --
+	(223.40,142.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40,142.13) --
+	(223.40, 92.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40, 92.12) --
+	(223.40, 92.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55,144.98) --
+	(230.55,144.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55,144.98) --
+	(230.55, 98.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55, 98.55) --
+	(230.55, 98.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,130.70) --
+	(237.69,130.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,130.70) --
+	(237.69,109.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,109.98) --
+	(237.69,109.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
+	(244.83,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
+	(244.83,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
+	(244.83,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
+	(259.12, 87.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
+	(259.12, 87.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
+	(259.12, 87.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,107.48) --
+	(273.41,107.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,107.48) --
+	(273.41, 39.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41, 39.62) --
+	(273.41, 39.62);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 44.82,212.08) --
+	( 47.71,210.73) --
+	( 50.60,209.35) --
+	( 53.50,207.96) --
+	( 56.39,206.55) --
+	( 59.28,205.13) --
+	( 62.18,203.68) --
+	( 65.07,202.22) --
+	( 67.96,200.75) --
+	( 70.86,199.25) --
+	( 73.75,197.73) --
+	( 76.65,196.20) --
+	( 79.54,194.64) --
+	( 82.43,193.07) --
+	( 85.33,191.48) --
+	( 88.22,189.86) --
+	( 91.11,188.23) --
+	( 94.01,186.57) --
+	( 96.90,184.90) --
+	( 99.79,183.20) --
+	(102.69,181.48) --
+	(105.58,179.74) --
+	(108.47,177.98) --
+	(111.37,176.19) --
+	(114.26,174.39) --
+	(117.16,172.56) --
+	(120.05,170.70) --
+	(122.94,168.82) --
+	(125.84,166.96) --
+	(128.73,165.20) --
+	(131.62,163.53) --
+	(134.52,161.96) --
+	(137.41,160.49) --
+	(140.30,159.13) --
+	(143.20,157.88) --
+	(146.09,156.76) --
+	(148.98,155.79) --
+	(151.88,154.74) --
+	(154.77,153.38) --
+	(157.67,151.87) --
+	(160.56,150.42) --
+	(163.45,148.83) --
+	(166.35,147.14) --
+	(169.24,145.41) --
+	(172.13,143.73) --
+	(175.03,142.08) --
+	(177.92,140.32) --
+	(180.81,138.66) --
+	(183.71,137.15) --
+	(186.60,135.67) --
+	(189.50,134.18) --
+	(192.39,132.70) --
+	(195.28,131.23) --
+	(198.18,129.77) --
+	(201.07,128.34) --
+	(203.96,126.97) --
+	(206.86,125.71) --
+	(209.75,124.58) --
+	(212.64,123.44) --
+	(215.54,122.24) --
+	(218.43,120.96) --
+	(221.32,119.62) --
+	(224.22,118.21) --
+	(227.11,116.73) --
+	(230.01,115.18) --
+	(232.90,113.56) --
+	(235.79,111.88) --
+	(238.69,110.13) --
+	(241.58,108.32) --
+	(244.47,106.44) --
+	(247.37,104.50) --
+	(250.26,102.49) --
+	(253.15,100.42) --
+	(256.05, 98.29) --
+	(258.94, 96.10) --
+	(261.83, 93.84) --
+	(264.73, 91.52) --
+	(267.62, 89.14) --
+	(270.52, 86.70) --
+	(273.41, 84.20);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.97,138.18) -- ( 41.97,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.97,138.18) -- ( 41.97,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 39.22,138.18) --
-	( 39.22,138.18) --
-	( 44.71,138.18) --
-	( 44.71,138.18) --
-	( 39.22,138.18) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 39.22,138.18) -- ( 44.71,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.61,226.33) -- ( 56.61,234.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.61,209.04) -- ( 56.61,186.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 53.86,226.33) --
-	( 53.86,209.04) --
-	( 59.36,209.04) --
-	( 59.36,226.33) --
-	( 53.86,226.33) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 53.86,217.69) -- ( 59.36,217.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93,196.95) -- ( 63.93,228.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93,158.92) -- ( 63.93,152.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 61.19,196.95) --
-	( 61.19,158.92) --
-	( 66.68,158.92) --
-	( 66.68,196.95) --
-	( 61.19,196.95) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 61.19,165.84) -- ( 66.68,165.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 71.25,200.40) -- ( 71.25,207.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 71.25,186.58) -- ( 71.25,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.51,200.40) --
-	( 68.51,186.58) --
-	( 74.00,186.58) --
-	( 74.00,200.40) --
-	( 68.51,200.40) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.51,193.49) -- ( 74.00,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.57,221.14) -- ( 78.57,234.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.57,172.75) -- ( 78.57,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 75.83,221.14) --
-	( 75.83,172.75) --
-	( 81.32,172.75) --
-	( 81.32,221.14) --
-	( 75.83,221.14) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 75.83,207.32) -- ( 81.32,207.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.90,221.14) -- ( 85.90,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 85.90,221.14) -- ( 85.90,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 83.15,221.14) --
-	( 83.15,221.14) --
-	( 88.64,221.14) --
-	( 88.64,221.14) --
-	( 83.15,221.14) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 83.15,221.14) -- ( 88.64,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.22,238.42) -- ( 93.22,255.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.22,203.86) -- ( 93.22,186.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 90.47,238.42) --
-	( 90.47,203.86) --
-	( 95.96,203.86) --
-	( 95.96,238.42) --
-	( 90.47,238.42) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 90.47,221.14) -- ( 95.96,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,200.40) -- (100.54,207.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,186.58) -- (100.54,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 97.79,200.40) --
-	( 97.79,186.58) --
-	(103.29,186.58) --
-	(103.29,200.40) --
-	( 97.79,200.40) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 97.79,193.49) -- (103.29,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.86,214.23) -- (107.86,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.86,214.23) -- (107.86,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (105.12,214.23) --
-	(105.12,214.23) --
-	(110.61,214.23) --
-	(110.61,214.23) --
-	(105.12,214.23) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (105.12,214.23) -- (110.61,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (115.18,198.67) -- (115.18,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (115.18,164.11) -- (115.18,158.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.44,198.67) --
-	(112.44,164.11) --
-	(117.93,164.11) --
-	(117.93,198.67) --
-	(112.44,198.67) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (112.44,179.66) -- (117.93,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.50,186.58) -- (122.50,234.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.50,138.18) -- (122.50,103.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (119.76,186.58) --
-	(119.76,138.18) --
-	(125.25,138.18) --
-	(125.25,186.58) --
-	(119.76,186.58) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (119.76,158.92) -- (125.25,158.92);
-\definecolor{fillColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.83,221.14) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.83,171.02) -- (129.83,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.83,139.91) -- (129.83,124.36);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (127.08,171.02) --
-	(127.08,139.91) --
-	(132.57,139.91) --
-	(132.57,171.02) --
-	(127.08,171.02) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (127.08,155.47) -- (132.57,155.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15,183.12) -- (137.15,200.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15,148.55) -- (137.15,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (134.40,183.12) --
-	(134.40,148.55) --
-	(139.89,148.55) --
-	(139.89,183.12) --
-	(134.40,183.12) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (134.40,165.84) -- (139.89,165.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (144.47,172.75) -- (144.47,214.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (144.47,131.27) -- (144.47,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (141.72,172.75) --
-	(141.72,131.27) --
-	(147.21,131.27) --
-	(147.21,172.75) --
-	(141.72,172.75) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (141.72,152.01) -- (147.21,152.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.79,179.66) -- (151.79,221.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.79,138.18) -- (151.79,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (149.05,179.66) --
-	(149.05,138.18) --
-	(154.54,138.18) --
-	(154.54,179.66) --
-	(149.05,179.66) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (149.05,158.92) -- (154.54,158.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,184.85) -- (159.11,228.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,126.09) -- (159.11, 55.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (156.37,184.85) --
-	(156.37,126.09) --
-	(161.86,126.09) --
-	(161.86,184.85) --
-	(156.37,184.85) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (156.37,155.47) -- (161.86,155.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (166.43,174.48) -- (166.43,200.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (166.43,129.54) -- (166.43,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (163.69,174.48) --
-	(163.69,129.54) --
-	(169.18,129.54) --
-	(169.18,174.48) --
-	(163.69,174.48) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (163.69,152.01) -- (169.18,152.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (173.76,171.02) -- (173.76,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (173.76,133.00) -- (173.76,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (171.01,171.02) --
-	(171.01,133.00) --
-	(176.50,133.00) --
-	(176.50,171.02) --
-	(171.01,171.02) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (171.01,152.01) -- (176.50,152.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (181.08,152.01) -- (181.08,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (181.08,110.53) -- (181.08, 82.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (178.33,152.01) --
-	(178.33,110.53) --
-	(183.82,110.53) --
-	(183.82,152.01) --
-	(178.33,152.01) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (178.33,131.27) -- (183.82,131.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (188.40,165.84) -- (188.40,193.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (188.40,110.53) -- (188.40, 75.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (185.65,165.84) --
-	(185.65,110.53) --
-	(191.14,110.53) --
-	(191.14,165.84) --
-	(185.65,165.84) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (185.65,138.18) -- (191.14,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.72,160.65) -- (195.72,200.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (195.72,108.80) -- (195.72, 82.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (192.97,160.65) --
-	(192.97,108.80) --
-	(198.47,108.80) --
-	(198.47,160.65) --
-	(192.97,160.65) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (192.97,134.73) -- (198.47,134.73);
-\definecolor{fillColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.04, 48.31) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.04,155.47) -- (203.04,179.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (203.04,120.90) -- (203.04,103.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (200.30,155.47) --
-	(200.30,120.90) --
-	(205.79,120.90) --
-	(205.79,155.47) --
-	(200.30,155.47) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (200.30,138.18) -- (205.79,138.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36,143.37) -- (210.36,172.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36,107.08) -- (210.36, 62.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (207.62,143.37) --
-	(207.62,107.08) --
-	(213.11,107.08) --
-	(213.11,143.37) --
-	(207.62,143.37) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (207.62,127.81) -- (213.11,127.81);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (217.69,131.27) -- (217.69,145.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (217.69, 96.71) -- (217.69, 75.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (214.94,131.27) --
-	(214.94, 96.71) --
-	(220.43, 96.71) --
-	(220.43,131.27) --
-	(214.94,131.27) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (214.94,117.45) -- (220.43,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.01,134.73) -- (225.01,145.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (225.01,113.99) -- (225.01, 82.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (222.26,134.73) --
-	(222.26,113.99) --
-	(227.75,113.99) --
-	(227.75,134.73) --
-	(222.26,134.73) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (222.26,124.36) -- (227.75,124.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (232.33,134.73) -- (232.33,145.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (232.33,113.99) -- (232.33, 96.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (229.58,134.73) --
-	(229.58,113.99) --
-	(235.07,113.99) --
-	(235.07,134.73) --
-	(229.58,134.73) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (229.58,124.36) -- (235.07,124.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (239.65,126.09) -- (239.65,131.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (239.65,115.72) -- (239.65,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (236.90,126.09) --
-	(236.90,115.72) --
-	(242.40,115.72) --
-	(242.40,126.09) --
-	(236.90,126.09) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (236.90,120.90) -- (242.40,120.90);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (246.97,110.53) -- (246.97,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (246.97,110.53) -- (246.97,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (244.23,110.53) --
-	(244.23,110.53) --
-	(249.72,110.53) --
-	(249.72,110.53) --
-	(244.23,110.53) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (244.23,110.53) -- (249.72,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (261.62, 89.79) -- (261.62, 89.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (261.62, 89.79) -- (261.62, 89.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (258.87, 89.79) --
-	(258.87, 89.79) --
-	(264.36, 89.79) --
-	(264.36, 89.79) --
-	(258.87, 89.79) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (258.87, 89.79) -- (264.36, 89.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.26, 93.25) -- (276.26,110.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.26, 58.68) -- (276.26, 41.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (273.51, 93.25) --
-	(273.51, 58.68) --
-	(279.00, 58.68) --
-	(279.00, 93.25) --
-	(273.51, 93.25) --
-	cycle;
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (273.51, 75.97) -- (279.00, 75.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.64, 30.69) rectangle (283.58,266.42);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 44.82, 30.69) rectangle (273.41,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69, 45.28) {-10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,114.41) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,183.55) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,252.68) {20};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 39.87, 41.94) {-10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 39.87,113.38) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 39.87,184.81) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 39.87,256.25) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89, 48.31) --
-	( 34.64, 48.31);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,117.45) --
-	( 34.64,117.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,186.58) --
-	( 34.64,186.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,255.71) --
-	( 34.64,255.71);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 42.07, 44.97) --
+	( 44.82, 44.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 42.07,116.41) --
+	( 44.82,116.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 42.07,187.84) --
+	( 44.82,187.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 42.07,259.28) --
+	( 44.82,259.28);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.93, 27.94) --
-	( 63.93, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.15, 27.94) --
-	(137.15, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.36, 27.94) --
-	(210.36, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (283.58, 27.94) --
-	(283.58, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25, 27.94) --
+	( 66.25, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68, 27.94) --
+	(137.68, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12, 27.94) --
+	(209.12, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 63.93, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (137.15, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (210.36, 19.68) {20};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (283.58, 19.68) {30};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 66.25, 19.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (137.68, 19.68) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (209.12, 19.68) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (159.11,  7.64) {Cohort time (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (159.11,  7.64) {Symptom onset day (infector)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,148.55) {Forward serial intervals (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 23.25,148.55) {Forward delay (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.64,274.49) {A};
-\end{scope}
-\begin{scope}
-\path[clip] (289.08,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 44.82,274.49) {A. Forward serial interval};
+\end{scope}
+\begin{scope}
+\path[clip] (295.68,  0.00) rectangle (571.56,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.08,  0.00) rectangle (578.16,289.08);
-\end{scope}
-\begin{scope}
-\path[clip] (316.39, 30.69) rectangle (572.66,266.42);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (295.68,  0.00) rectangle (571.56,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (316.39, 30.69) rectangle (572.66,266.42);
+\path[fill=fillColor] (330.32, 30.69) rectangle (566.06,266.42);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (388.02,200.87) {maximum observable};
+
+\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (521.60, 75.14) {minimum observable};
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (330.32,140.70) --
+	(338.18,148.55) --
+	(346.04,156.41) --
+	(353.90,164.27) --
+	(361.76,172.13) --
+	(369.61,179.99) --
+	(377.47,187.84) --
+	(385.33,195.70) --
+	(393.19,203.56) --
+	(401.05,211.42) --
+	(408.90,219.28) --
+	(416.76,227.13) --
+	(424.62,234.99) --
+	(432.48,242.85) --
+	(440.33,250.71) --
+	(448.19,258.56) --
+	(456.05,266.42);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (479.62, 30.69) --
+	(487.48, 38.54) --
+	(495.34, 46.40) --
+	(503.20, 54.26) --
+	(511.06, 62.12) --
+	(518.91, 69.98) --
+	(526.77, 77.83) --
+	(534.63, 85.69) --
+	(542.49, 93.55) --
+	(550.35,101.41) --
+	(558.20,109.26) --
+	(566.06,117.12);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (330.32,140.70) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.76, 46.40) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.61,148.55) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.47,101.41) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (385.33,172.13) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (393.19,117.12) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (401.05,104.77) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (408.90,129.70) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.76,111.23) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (424.62,124.46) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (432.48,136.28) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (440.33,141.20) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (448.19,143.14) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (456.05,141.78) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (463.91,132.65) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (471.77,145.10) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (479.62,152.05) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.48,153.79) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (495.34,151.04) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (503.20,153.41) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (511.06,157.72) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (518.91,166.77) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (526.77,171.71) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (534.63,169.11) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (542.49,196.68) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (550.35,186.53) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (558.20,242.85) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (566.06,211.42) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (330.32,140.70) --
+	(330.32,140.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (330.32,140.70) --
+	(330.32,140.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (330.32,140.70) --
+	(330.32,140.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.76, 46.40) --
+	(361.76, 46.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.76, 46.40) --
+	(361.76, 46.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.76, 46.40) --
+	(361.76, 46.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,156.02) --
+	(369.61,156.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,156.02) --
+	(369.61,141.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,141.09) --
+	(369.61,141.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (377.47,101.41) --
+	(377.47,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (377.47,101.41) --
+	(377.47,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (377.47,101.41) --
+	(377.47,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (385.33,172.13) --
+	(385.33,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (385.33,172.13) --
+	(385.33,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (385.33,172.13) --
+	(385.33,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.19,117.12) --
+	(393.19,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.19,117.12) --
+	(393.19,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.19,117.12) --
+	(393.19,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (401.05,185.09) --
+	(401.05,185.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (401.05,185.09) --
+	(401.05, 38.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (401.05, 38.54) --
+	(401.05, 38.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (408.90,181.56) --
+	(408.90,181.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (408.90,181.56) --
+	(408.90,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (408.90,109.26) --
+	(408.90,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.76,139.32) --
+	(416.76,139.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.76,139.32) --
+	(416.76, 71.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.76, 71.35) --
+	(416.76, 71.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (424.62,194.52) --
+	(424.62,194.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (424.62,194.52) --
+	(424.62, 62.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (424.62, 62.51) --
+	(424.62, 62.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (432.48,227.13) --
+	(432.48,227.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (432.48,227.13) --
+	(432.48, 83.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (432.48, 83.73) --
+	(432.48, 83.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (440.33,223.20) --
+	(440.33,223.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (440.33,223.20) --
+	(440.33, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (440.33, 85.69) --
+	(440.33, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19,242.85) --
+	(448.19,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19,242.85) --
+	(448.19, 86.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19, 86.48) --
+	(448.19, 86.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (456.05,245.21) --
+	(456.05,245.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (456.05,245.21) --
+	(456.05, 96.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (456.05, 96.69) --
+	(456.05, 96.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.91,187.84) --
+	(463.91,187.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.91,187.84) --
+	(463.91, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.91, 85.69) --
+	(463.91, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (471.77,219.28) --
+	(471.77,219.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (471.77,219.28) --
+	(471.77, 93.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (471.77, 93.55) --
+	(471.77, 93.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (479.62,209.45) --
+	(479.62,209.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (479.62,209.45) --
+	(479.62,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (479.62,117.12) --
+	(479.62,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (487.48,206.51) --
+	(487.48,206.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (487.48,206.51) --
+	(487.48,107.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (487.48,107.30) --
+	(487.48,107.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (495.34,205.33) --
+	(495.34,205.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (495.34,205.33) --
+	(495.34,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (495.34,109.26) --
+	(495.34,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (503.20,198.45) --
+	(503.20,198.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (503.20,198.45) --
+	(503.20,115.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (503.20,115.75) --
+	(503.20,115.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (511.06,221.44) --
+	(511.06,221.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (511.06,221.44) --
+	(511.06, 99.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (511.06, 99.25) --
+	(511.06, 99.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (518.91,253.65) --
+	(518.91,253.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (518.91,253.65) --
+	(518.91,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (518.91,109.26) --
+	(518.91,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,240.10) --
+	(526.77,240.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,240.10) --
+	(526.77,128.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,128.52) --
+	(526.77,128.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (534.63,209.06) --
+	(534.63,209.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (534.63,209.06) --
+	(534.63,132.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (534.63,132.84) --
+	(534.63,132.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (542.49,234.99) --
+	(542.49,234.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (542.49,234.99) --
+	(542.49,148.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (542.49,148.55) --
+	(542.49,148.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (550.35,231.06) --
+	(550.35,231.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (550.35,231.06) --
+	(550.35,118.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (550.35,118.10) --
+	(550.35,118.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (558.20,242.85) --
+	(558.20,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (558.20,242.85) --
+	(558.20,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (558.20,242.85) --
+	(558.20,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (566.06,211.42) --
+	(566.06,211.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (566.06,211.42) --
+	(566.06,211.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (566.06,211.42) --
+	(566.06,211.42);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (330.32,118.83) --
+	(333.31,118.41) --
+	(336.29,118.04) --
+	(339.28,117.71) --
+	(342.26,117.43) --
+	(345.24,117.20) --
+	(348.23,117.01) --
+	(351.21,116.87) --
+	(354.20,116.77) --
+	(357.18,116.72) --
+	(360.16,116.72) --
+	(363.15,116.77) --
+	(366.13,116.87) --
+	(369.12,117.01) --
+	(372.10,117.21) --
+	(375.08,117.45) --
+	(378.07,117.75) --
+	(381.05,118.09) --
+	(384.04,118.49) --
+	(387.02,118.94) --
+	(390.00,119.44) --
+	(392.99,119.99) --
+	(395.97,120.59) --
+	(398.96,121.25) --
+	(401.94,121.96) --
+	(404.92,122.73) --
+	(407.91,123.54) --
+	(410.89,124.42) --
+	(413.88,125.35) --
+	(416.86,126.33) --
+	(419.84,127.37) --
+	(422.83,128.47) --
+	(425.81,129.62) --
+	(428.80,130.83) --
+	(431.78,132.10) --
+	(434.76,133.38) --
+	(437.75,134.61) --
+	(440.73,135.77) --
+	(443.72,136.88) --
+	(446.70,137.92) --
+	(449.68,138.87) --
+	(452.67,139.56) --
+	(455.65,140.07) --
+	(458.64,140.53) --
+	(461.62,141.04) --
+	(464.60,141.73) --
+	(467.59,142.49) --
+	(470.57,143.35) --
+	(473.56,144.61) --
+	(476.54,146.56) --
+	(479.52,148.26) --
+	(482.51,149.31) --
+	(485.49,150.22) --
+	(488.48,151.24) --
+	(491.46,152.28) --
+	(494.44,153.32) --
+	(497.43,154.37) --
+	(500.41,155.31) --
+	(503.40,156.26) --
+	(506.38,157.32) --
+	(509.36,158.61) --
+	(512.35,160.23) --
+	(515.33,162.05) --
+	(518.32,164.02) --
+	(521.30,166.15) --
+	(524.28,168.43) --
+	(527.27,170.87) --
+	(530.25,173.46) --
+	(533.24,176.21) --
+	(536.22,179.13) --
+	(539.20,182.20) --
+	(542.19,185.42) --
+	(545.17,188.81) --
+	(548.16,192.36) --
+	(551.14,196.07) --
+	(554.12,199.95) --
+	(557.11,203.98) --
+	(560.09,208.18) --
+	(563.08,212.54) --
+	(566.06,217.06);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.32, 30.69) rectangle (566.06,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (325.37, 35.51) {-10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (325.37,114.09) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (325.37,192.67) {10};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.57, 38.54) --
+	(330.32, 38.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.57,117.12) --
+	(330.32,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.57,195.70) --
+	(330.32,195.70);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (330.32, 27.94) --
+	(330.32, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (408.90, 27.94) --
+	(408.90, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (487.48, 27.94) --
+	(487.48, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (566.06, 27.94) --
+	(566.06, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (330.32, 19.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (408.90, 19.68) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (487.48, 19.68) {20};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (566.06, 19.68) {30};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (448.19,  7.64) {Symptom onset day (infectee)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (308.76,148.55) {Backward delay (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (330.32,274.49) {B. Backward serial interval};
+\end{scope}
+\begin{scope}
+\path[clip] (578.16,  0.00) rectangle (867.24,289.08);
+\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (578.16,  0.00) rectangle (867.24,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (605.47, 30.69) rectangle (861.74,266.42);
 \definecolor{drawColor}{RGB}{240,228,66}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (346.54,255.71) --
-	(354.08,234.51) --
-	(361.62,227.85) --
-	(369.15,224.34) --
-	(376.69,232.95) --
-	(384.23,225.18) --
-	(391.77,220.08) --
-	(399.30,212.60) --
-	(406.84,137.83) --
-	(414.38,119.60) --
-	(421.91,116.21) --
-	(429.45,104.34) --
-	(436.99,101.52) --
-	(444.53, 91.89) --
-	(452.06, 87.88) --
-	(459.60, 85.77) --
-	(467.14, 79.62) --
-	(474.68, 76.53) --
-	(482.21, 72.74) --
-	(489.75, 71.32) --
-	(497.29, 69.30) --
-	(504.82, 68.00) --
-	(512.36, 66.17) --
-	(519.90, 65.86) --
-	(527.44, 65.06) --
-	(534.97, 64.84) --
-	(542.51, 64.84) --
-	(550.05, 64.82) --
-	(557.59, 64.82) --
-	(565.12, 64.08) --
-	(565.12, 56.77) --
-	(557.59, 57.72) --
-	(550.05, 57.72) --
-	(542.51, 58.18) --
-	(534.97, 58.18) --
-	(527.44, 58.40) --
-	(519.90, 58.16) --
-	(512.36, 58.79) --
-	(504.82, 60.03) --
-	(497.29, 60.94) --
-	(489.75, 62.46) --
-	(482.21, 65.05) --
-	(474.68, 66.78) --
-	(467.14, 70.56) --
-	(459.60, 73.93) --
-	(452.06, 74.95) --
-	(444.53, 77.75) --
-	(436.99, 84.76) --
-	(429.45, 84.17) --
-	(421.91, 90.54) --
-	(414.38, 89.60) --
-	(406.84, 93.27) --
-	(399.30,129.71) --
-	(391.77,137.14) --
-	(384.23,136.34) --
-	(376.69,134.94) --
-	(369.15,135.04) --
-	(361.62,120.43) --
-	(354.08,124.23) --
-	(346.54,119.49) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (629.50,255.71) --
+	(637.51,234.51) --
+	(645.51,227.85) --
+	(653.52,224.34) --
+	(661.53,232.95) --
+	(669.54,225.18) --
+	(677.55,220.08) --
+	(685.56,212.60) --
+	(693.56,137.83) --
+	(701.57,119.60) --
+	(709.58,116.21) --
+	(717.59,104.34) --
+	(725.60,101.52) --
+	(733.61, 91.89) --
+	(741.61, 87.88) --
+	(749.62, 85.77) --
+	(757.63, 79.62) --
+	(765.64, 76.53) --
+	(773.65, 72.74) --
+	(781.66, 71.32) --
+	(789.66, 69.30) --
+	(797.67, 68.00) --
+	(805.68, 66.17) --
+	(813.69, 65.86) --
+	(821.70, 65.06) --
+	(829.71, 64.84) --
+	(837.71, 64.84) --
+	(845.72, 64.82) --
+	(853.73, 64.82) --
+	(861.74, 64.08) --
+	(861.74, 56.77) --
+	(853.73, 57.72) --
+	(845.72, 57.72) --
+	(837.71, 58.18) --
+	(829.71, 58.18) --
+	(821.70, 58.40) --
+	(813.69, 58.16) --
+	(805.68, 58.79) --
+	(797.67, 60.03) --
+	(789.66, 60.94) --
+	(781.66, 62.46) --
+	(773.65, 65.05) --
+	(765.64, 66.78) --
+	(757.63, 70.56) --
+	(749.62, 73.93) --
+	(741.61, 74.95) --
+	(733.61, 77.75) --
+	(725.60, 84.76) --
+	(717.59, 84.17) --
+	(709.58, 90.54) --
+	(701.57, 89.60) --
+	(693.56, 93.27) --
+	(685.56,129.71) --
+	(677.55,137.14) --
+	(669.54,136.34) --
+	(661.53,134.94) --
+	(653.52,135.04) --
+	(645.51,120.43) --
+	(637.51,124.23) --
+	(629.50,119.49) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (346.54,167.99) --
-	(354.08,158.37) --
-	(361.62,155.61) --
-	(369.15,153.41) --
-	(376.69,158.49) --
-	(384.23,154.03) --
-	(391.77,151.93) --
-	(399.30,148.30) --
-	(406.84,107.71) --
-	(414.38, 96.60) --
-	(421.91, 94.03) --
-	(429.45, 86.26) --
-	(436.99, 84.52) --
-	(444.53, 77.77) --
-	(452.06, 75.45) --
-	(459.60, 73.98) --
-	(467.14, 69.74) --
-	(474.68, 67.73) --
-	(482.21, 65.35) --
-	(489.75, 64.41) --
-	(497.29, 62.76) --
-	(504.82, 61.94) --
-	(512.36, 60.56) --
-	(519.90, 60.51) --
-	(527.44, 60.01) --
-	(534.97, 59.88) --
-	(542.51, 59.88) --
-	(550.05, 59.77) --
-	(557.59, 59.77) --
-	(565.12, 59.40) --
-	(565.12, 54.49) --
-	(557.59, 54.89) --
-	(550.05, 54.89) --
-	(542.51, 55.23) --
-	(534.97, 55.23) --
-	(527.44, 55.32) --
-	(519.90, 55.43) --
-	(512.36, 55.76) --
-	(504.82, 56.48) --
-	(497.29, 57.32) --
-	(489.75, 58.34) --
-	(482.21, 59.85) --
-	(474.68, 61.35) --
-	(467.14, 63.63) --
-	(459.60, 66.52) --
-	(452.06, 66.97) --
-	(444.53, 68.74) --
-	(436.99, 73.15) --
-	(429.45, 73.04) --
-	(421.91, 77.40) --
-	(414.38, 77.19) --
-	(406.84, 79.82) --
-	(399.30,101.35) --
-	(391.77,108.09) --
-	(384.23,107.05) --
-	(376.69,105.61) --
-	(369.15,105.29) --
-	(361.62, 96.62) --
-	(354.08, 98.80) --
-	(346.54, 95.78) --
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (629.50,167.99) --
+	(637.51,158.37) --
+	(645.51,155.61) --
+	(653.52,153.41) --
+	(661.53,158.49) --
+	(669.54,154.03) --
+	(677.55,151.93) --
+	(685.56,148.30) --
+	(693.56,107.71) --
+	(701.57, 96.60) --
+	(709.58, 94.03) --
+	(717.59, 86.26) --
+	(725.60, 84.52) --
+	(733.61, 77.77) --
+	(741.61, 75.45) --
+	(749.62, 73.98) --
+	(757.63, 69.74) --
+	(765.64, 67.73) --
+	(773.65, 65.35) --
+	(781.66, 64.41) --
+	(789.66, 62.76) --
+	(797.67, 61.94) --
+	(805.68, 60.56) --
+	(813.69, 60.51) --
+	(821.70, 60.01) --
+	(829.71, 59.88) --
+	(837.71, 59.88) --
+	(845.72, 59.77) --
+	(853.73, 59.77) --
+	(861.74, 59.40) --
+	(861.74, 54.49) --
+	(853.73, 54.89) --
+	(845.72, 54.89) --
+	(837.71, 55.23) --
+	(829.71, 55.23) --
+	(821.70, 55.32) --
+	(813.69, 55.43) --
+	(805.68, 55.76) --
+	(797.67, 56.48) --
+	(789.66, 57.32) --
+	(781.66, 58.34) --
+	(773.65, 59.85) --
+	(765.64, 61.35) --
+	(757.63, 63.63) --
+	(749.62, 66.52) --
+	(741.61, 66.97) --
+	(733.61, 68.74) --
+	(725.60, 73.15) --
+	(717.59, 73.04) --
+	(709.58, 77.40) --
+	(701.57, 77.19) --
+	(693.56, 79.82) --
+	(685.56,101.35) --
+	(677.55,108.09) --
+	(669.54,107.05) --
+	(661.53,105.61) --
+	(653.52,105.29) --
+	(645.51, 96.62) --
+	(637.51, 98.80) --
+	(629.50, 95.78) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (316.39, 41.40) -- (572.66, 41.40);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (605.47, 41.40) -- (861.74, 41.40);
 \definecolor{drawColor}{RGB}{240,228,66}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (346.54,170.94) --
-	(354.08,170.79) --
-	(361.62,163.30) --
-	(369.15,167.34) --
-	(376.69,172.68) --
-	(384.23,172.43) --
-	(391.77,174.86) --
-	(399.30,167.73) --
-	(406.84,112.65) --
-	(414.38,105.04) --
-	(421.91,102.84) --
-	(429.45, 93.38) --
-	(436.99, 91.84) --
-	(444.53, 83.99) --
-	(452.06, 80.95) --
-	(459.60, 80.00) --
-	(467.14, 75.18) --
-	(474.68, 71.77) --
-	(482.21, 68.56) --
-	(489.75, 66.30) --
-	(497.29, 65.11) --
-	(504.82, 63.71) --
-	(512.36, 62.37) --
-	(519.90, 61.91) --
-	(527.44, 61.69) --
-	(534.97, 61.52) --
-	(542.51, 61.52) --
-	(550.05, 61.33) --
-	(557.59, 61.33) --
-	(565.12, 60.65);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (629.50,170.94) --
+	(637.51,170.79) --
+	(645.51,163.30) --
+	(653.52,167.34) --
+	(661.53,172.68) --
+	(669.54,172.43) --
+	(677.55,174.86) --
+	(685.56,167.73) --
+	(693.56,112.65) --
+	(701.57,105.04) --
+	(709.58,102.84) --
+	(717.59, 93.38) --
+	(725.60, 91.84) --
+	(733.61, 83.99) --
+	(741.61, 80.95) --
+	(749.62, 80.00) --
+	(757.63, 75.18) --
+	(765.64, 71.77) --
+	(773.65, 68.56) --
+	(781.66, 66.30) --
+	(789.66, 65.11) --
+	(797.67, 63.71) --
+	(805.68, 62.37) --
+	(813.69, 61.91) --
+	(821.70, 61.69) --
+	(829.71, 61.52) --
+	(837.71, 61.52) --
+	(845.72, 61.33) --
+	(853.73, 61.33) --
+	(861.74, 60.65);
 \definecolor{drawColor}{RGB}{0,114,178}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (346.54,126.39) --
-	(354.08,125.79) --
-	(361.62,122.09) --
-	(369.15,124.37) --
-	(376.69,127.48) --
-	(384.23,126.99) --
-	(391.77,128.28) --
-	(399.30,123.96) --
-	(406.84, 92.40) --
-	(414.38, 87.06) --
-	(421.91, 85.30) --
-	(429.45, 79.23) --
-	(436.99, 77.99) --
-	(444.53, 73.04) --
-	(452.06, 70.90) --
-	(459.60, 70.16) --
-	(467.14, 66.88) --
-	(474.68, 64.57) --
-	(482.21, 62.37) --
-	(489.75, 60.94) --
-	(497.29, 60.13) --
-	(504.82, 59.14) --
-	(512.36, 58.16) --
-	(519.90, 57.82) --
-	(527.44, 57.64) --
-	(534.97, 57.52) --
-	(542.51, 57.52) --
-	(550.05, 57.39) --
-	(557.59, 57.39) --
-	(565.12, 56.99);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (629.50,126.39) --
+	(637.51,125.79) --
+	(645.51,122.09) --
+	(653.52,124.37) --
+	(661.53,127.48) --
+	(669.54,126.99) --
+	(677.55,128.28) --
+	(685.56,123.96) --
+	(693.56, 92.40) --
+	(701.57, 87.06) --
+	(709.58, 85.30) --
+	(717.59, 79.23) --
+	(725.60, 77.99) --
+	(733.61, 73.04) --
+	(741.61, 70.90) --
+	(749.62, 70.16) --
+	(757.63, 66.88) --
+	(765.64, 64.57) --
+	(773.65, 62.37) --
+	(781.66, 60.94) --
+	(789.66, 60.13) --
+	(797.67, 59.14) --
+	(805.68, 58.16) --
+	(813.69, 57.82) --
+	(821.70, 57.64) --
+	(829.71, 57.52) --
+	(837.71, 57.52) --
+	(845.72, 57.39) --
+	(853.73, 57.39) --
+	(861.74, 56.99);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.39, 30.69) rectangle (572.66,266.42);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (605.47, 30.69) rectangle (861.74,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44, 38.37) {1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44, 90.38) {2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,142.40) {3};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,194.41) {4};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,246.42) {5};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52, 38.37) {1};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52, 90.38) {2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52,142.40) {3};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52,194.41) {4};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52,246.42) {5};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64, 41.40) --
-	(316.39, 41.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64, 93.41) --
-	(316.39, 93.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,145.43) --
-	(316.39,145.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,197.44) --
-	(316.39,197.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,249.45) --
-	(316.39,249.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72, 41.40) --
+	(605.47, 41.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72, 93.41) --
+	(605.47, 93.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72,145.43) --
+	(605.47,145.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72,197.44) --
+	(605.47,197.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72,249.45) --
+	(605.47,249.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (346.54, 27.94) --
-	(346.54, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (421.91, 27.94) --
-	(421.91, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.29, 27.94) --
-	(497.29, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (572.66, 27.94) --
-	(572.66, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (629.50, 27.94) --
+	(629.50, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (709.58, 27.94) --
+	(709.58, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (789.66, 27.94) --
+	(789.66, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (346.54, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (421.91, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (497.29, 19.68) {20};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.66, 19.68) {30};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (629.50, 19.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (709.58, 19.68) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (789.66, 19.68) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (444.53,  7.64) {Cohort time (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (733.61,  7.64) {Time (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,148.55) {Reproduction number $\mathcal R$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (591.24,148.55) {Basic reproduction number $\mathcal R_0$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (450.83,208.36) rectangle (566.36,253.77);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[fill=fillColor] (721.97,208.36) rectangle (837.50,253.77);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (456.33,228.31) rectangle (470.78,242.77);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[fill=fillColor] (727.47,228.31) rectangle (741.92,242.77);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{240,228,66}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor,fill opacity=0.50] (457.04,229.02) rectangle (470.07,242.05);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor,fill opacity=0.50] (728.18,229.02) rectangle (741.21,242.05);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{240,228,66}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (457.77,235.54) -- (469.33,235.54);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (728.91,235.54) -- (740.48,235.54);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (456.33,213.86) rectangle (470.78,228.31);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[fill=fillColor] (727.47,213.86) rectangle (741.92,228.31);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,114,178}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line cap=rect,fill=fillColor,fill opacity=0.50] (457.04,214.57) rectangle (470.07,227.60);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line cap=rect,fill=fillColor,fill opacity=0.50] (728.18,214.57) rectangle (741.21,227.60);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,114,178}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (457.77,221.09) -- (469.33,221.09);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (728.91,221.09) -- (740.48,221.09);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.28,232.51) {6 day doubling period};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (747.42,232.51) {6 day doubling period};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.28,218.05) {8 day doubling period};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (747.42,218.05) {8 day doubling period};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (316.39,274.49) {B};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (605.47,274.49) {C. Cohort-averaged estimates};
 \end{scope}

### 2020-05-15 serial_analysis.R

@@ -85,34 +85,60 @@ serdata2 <- lapply(tcut, function(x) {
 serall <- bind_rows(serdata1, serdata2)
 
 mm <- max(c(rr$`Seconday - symptom onset date`, rr$`Index - symptom onset date`))
+mm2 <- min(c(rr$`Seconday - symptom onset date`, rr$`Index - symptom onset date`))
 
 cdata <- data.frame(
-  x=9:30,
-  y=30-9:30
+  x=9:29,
+  y=mm-9:29
+)
+
+cdata2 <- data.frame(
+  x=-3:9,
+  y=mm2-((-3):9)
 )
 
 g1 <- ggplot(rr) +
+  annotate("text", x=20, y=11, label="maximum observable", angle=-45) +
+  annotate("text", x=4, y=-6, label="minimum observable", angle=-45) +
   geom_line(data=cdata, aes(x, y), lty=2) +
+  geom_line(data=cdata2, aes(x, y), lty=2) +
   geom_point(data=rr_summ, aes(cohort, mean)) +
   geom_errorbar(data=rr_summ, aes(cohort, ymin=lwr, ymax=upr), width=0) +
   geom_smooth(aes(cohort, serial), col=1, fill=1, fullrange=TRUE, se=FALSE) +
   scale_x_continuous("Symptom onset day (infector)", expand=c(0, 0), limits=c(-3, 29)) +
   scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(-12, 21)) +
   scale_size_area(max_size=4) +
-  coord_cartesian(clip="off", default=TRUE) +
+  coord_fixed(clip="off") +
   ggtitle("A. Forward serial interval") +
   theme(
     panel.grid = element_blank(),
     legend.position = "none"
   )
 
+mm3 <- max(c(rr$`Seconday - symptom onset date`, rr$`Index - symptom onset date`))
+mm4 <- min(c(rr$`Seconday - symptom onset date`, rr$`Index - symptom onset date`))
+
+cdata3 <- data.frame(
+  x=0:16,
+  y=0:16-mm2
+)
+
+cdata4 <- data.frame(
+  x=19:30,
+  y=19:30-mm
+)
+
 g2 <- ggplot(rr) +
+  annotate("text", x=7, y=11, label="maximum observable", angle=45) +
+  annotate("text", x=24, y=-5, label="minimum observable", angle=45) +
+  geom_line(data=cdata3, aes(x, y), lty=2) +
[…]

### 2020-05-15 serial.tex
done???
done

@@
 
+\pagebreak
+
 \section*{Abstract}
 
-Generation and serial intervals are under-appreciated yet important quantities for charaterizing the outset of an outbreak.
+Generation and serial intervals are under-appreciated yet important quantities for characterizing the outset of an outbreak.
 Even though their definitions (and differences) were clearly laid out over a decade ago, there is still a need for clear conceptual and theoretical understanding of their roles in shaping the epidemiological dynamics.
@@
 This study demonstrates the importance of early epidemiological investigation through contact tracing for characterizing initial serial intervals and provides rationale for reassessing serial intervals, and \RR\ estimates, for COVID-19.
+
+\section*{Significance}
+
+The generation- and serial-interval distributions are key quantities in outbreak analyses.
+Recent theoretical studies suggest that two distributions give different estimates of \RR;
+however, both intervals, by definition, can equally describe the disease transmission at the individual level.
+Here, we show that the serial-interval distribution, defined from the correct reference time and cohort, gives the same estimate of \RR as the generation-interval distribution.
+We then apply our framework to serial interval data from the COVID-19 epidemic.
+While our study supports the use of serial-interval distributions in estimating \RR, it also reveals several gaps in the current understanding and applications of the serial-interval distributions.
 
@@
 the primary and secondary events are defined in terms of the direction of transmission:
-the primary event refers to the event that occurs in the infector; again some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to report sysmptoms before the infector).
+the primary event refers to the event that occurs in the infector; again some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to report symptoms before the infector).
 
@@
 The mean forward incubation period remains constant throughout an epidemic as assumed (\fref{epi}B).
-The mean forward generation interval decreases slightly as incidence rate increases, causing the proportion of susceptible populaton to decrease (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
+The mean forward generation interval decreases slightly as incidence rate increases, causing the proportion of susceptible population to decrease (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
 In contrast, the mean forward serial interval decreases over time (\fref{epi}D).
@@
 While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and \emph{maximum observable} serial intervals), increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution;
-increase in the proportion of negative serial intervals is unlikely to be driven by the left-censoring (indicated by the farness between the quantiles of the observed serial intervals and \emph{minimum observable} serial intervals).
+increase in the proportion of negative serial intervals is unlikely to be driven by the left-censoring (indicated by the ``farness'' between the quantiles of the observed serial intervals and \emph{minimum observable} serial intervals).
 The decrease in the mean forward serial interval was likely to be caused by increase in the mean backward incubation periods, reflecting decrease in COVID-19 cases in China, as well as intervention efforts which reduce generation intervals by preventing infections once cases are identified.
@@
 \end{equation}
-Therefore, both the intrinsic generation interval and the initial forward serial intervals are identically distributed.
+Therefore, both the intrinsic generation intervals and the initial forward serial intervals are identically distributed and have the same mean.
 

### 2020-05-22 serial.tex
tweaks

@@
 	\textbf\newline{
-		Unraveling the paradox between generation and serial intervals
+		Cohort-based approach to understanding the roles of generation and serial intervals in shaping epidemiological dynamics
 	}
@@
 
-Generation and serial intervals are under-appreciated yet important quantities for characterizing the outset of an outbreak.
-Even though their definitions (and differences) were clearly laid out over a decade ago, there is still a need for clear conceptual and theoretical understanding of their roles in shaping the epidemiological dynamics.
-Part of the confusion can be attributed to an apparent paradox.
-By definition, both generation and serial intervals describe how infection spreads between individuals --- thus, one would expect them both to link between the epidemic growth rate $r$ and the reproduction number \RR.
-However, current theory does not explain how two different distributions can estimate the same \RR from $r$ --- some studies have further demonstrated that generation and serial intervals give different estimates of \RR.
-We provide an answer to the paradox by showing that \emph{forward-looking} serial intervals, which correctly estimates \RR from $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
-We provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references and apply our framework to serial intervals of COVID-19.
-This study demonstrates the importance of early epidemiological investigation through contact tracing for characterizing initial serial intervals and provides rationale for reassessing serial intervals, and \RR\ estimates, for COVID-19.
+Generation intervals and serial intervals are critical quantities for characterizing outbreak dynamics.
+Generation intervals characterize the time between infection and transmission; whereas serial intervals characterize the time between the onset of symptoms in a chain of transmission.
+They are often used interchangeably, leading to misunderstanding of how to use either generation or serial intervals to establish a link between the epidemic growth rate $r$ and the reproduction number \RR.
+On one hand, generation intervals provide a mechanistic link between $r$ and \RR but are harder to measure via contact tracing.
+On the other hand, serial intervals are easier to measure from contact tracing but recent studies suggest that two intervals give different estimates of \RR from $r$.
+We present a general framework for characterizing \emph{any} epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly estimates \RR from $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
+We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial interval data --- our analysis shows that using incorrectly defined serial intervals can severely bias the estimate.
+This study demonstrates the importance of early epidemiological investigation through contact tracing and provides rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
 
@@
 
-The generation- and serial-interval distributions are key quantities in outbreak analyses.
-Recent theoretical studies suggest that two distributions give different estimates of \RR;
-however, both intervals, by definition, can equally describe the disease transmission at the individual level.
+The generation- and serial-interval distributions are key, but different, quantities in outbreak analyses.
+Recent theoretical studies suggest that two distributions give different estimates of the reproduction number \RR from the exponential growth rate $r$;
+however, both intervals, by definition, describe disease transmission at the individual level.
 Here, we show that the serial-interval distribution, defined from the correct reference time and cohort, gives the same estimate of \RR as the generation-interval distribution.
-We then apply our framework to serial interval data from the COVID-19 epidemic.
-While our study supports the use of serial-interval distributions in estimating \RR, it also reveals several gaps in the current understanding and applications of the serial-interval distributions.
+We then apply our framework to serial interval data from the COVID-19 outbreak in China.
+While our study supports the use of serial-interval distributions in estimating \RR, it also reveals necessary changes to the current understanding and applications of serial-interval distribution.
 
@@
 
-The reproduction number \RR is one of the most important characteristics of an emerging epidemic such as coronavirus disease 2019 (COVID-19) \citep{majumder2020early}.
+The reproduction number \RR is one of the most important characteristics of an emerging epidemic, including characterization of coronavirus disease 2019 (COVID-19) \citep{majumder2020early}.
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
@@
 Similarly, the serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
-While serial intervals are similar to generation intervals, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence};
-some studies further suggested that using serial intervals can give different estimates of \RR \citep{britton2019estimation, ganyani2020estimating}.
+While serial intervals are similar to generation intervals, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
 
@@
 
-One source of confusion comes down to an apparent paradox.
+One source of confusion comes down to an apparent discrepancy between biological intuition and mathematical theory.
 When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
@@
 By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates;
-therefore, both generation- and serial-interval distributions should give identical estimates of  \RR based the observed epidemic growth rate $r$.
-In contexts where the distributions are expected to be different, current theory has no explanation for how they might provide identical estimates of \RR from $r$ (cf. \cite{britton2019estimation}).
+therefore, we expect both generation- and serial-interval distributions to give identical estimates of  \RR based the observed epidemic growth rate $r$.
+In contexts where the distributions are expected to be different, current theory has no explanation for how they might provide identical estimates of \RR from $r$. 
+Some studies have further suggested that using serial intervals can give different estimates of \RR \citep{britton2019estimation, ganyani2020estimating}.
 
-Here, we resolve this paradox, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
-We develop a new framework for understanding serial intervals and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
+Here, we resolve this discrepancy, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
+We develop a new framework for understanding serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
 Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can significantly bias estimates of \RR.
-We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays in the analysis of epidemics.
+We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the reproduction number during the early stages of an outbreak.
 
@@
 
-We first begin by describing a general framework for characterizing a distribution of time delays between two epidemiological events;
-these events can be defined either within an infected individual (e.g., infection and symptom onset of an individual, the incubation period) or between infected individuals (e.g., symptom onsets of an infector and an infectee, the serial interval).
+The time delays between two epidemiological events can be defined either within an infected individual (e.g., infection and symptom onset of an individual, the incubation period) or between infected individuals (e.g., symptom onsets of an infector and an infectee, the serial interval).
 We can further divide these events into \emph{primary} and \emph{secondary} events.
@@
 the primary and secondary events are defined in terms of the direction of transmission:
-the primary event refers to the event that occurs in the infector; again some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to report symptoms before the infector).
+the primary event refers to the event that occurs in the infector. 
+Again, some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to develop symptoms before the infector \citep{he2020temporal}).
 
@@
 \begin{equation}
-b_\ssymp(\tau)= \frac{\psize(\ssymp-\tau) f_{\ssymp-\tau} (\tau)}{\ssize(\ssymp)}
+b_\ssymp(\tau)= \frac{\psize(\ssymp-\tau) f_{\ssymp-\tau} (\tau)}{\ssize(\ssymp)}\,.
 \label{eq:backward}
@@
 Typically, within-individual forward delay distributions are not affected by epidemic dynamics.
-Some, like incubation periods, are expected to be equivalent to their intrinsic distributions and remain invariant over the course of an epidemic.
-Others, like the time from symptom onset to testing, may change over the course of an epidemic due to changes in public health policies.
+Some realized distributions, like incubation period distributions, are expected to be equivalent to their intrinsic distributions and remain invariant over the course of an epidemic.
+Other realized distributions, like the distribution of time from symptom onset to testing, may change over the course of an epidemic due to changes in public health policies.
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics;
@@
 however, this conclusion is based on the implicit assumption that incubation times, $x_0$ and $x_1$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on disease dynamics) --- something that is true of forward but not backward incubation times.
-We refer to this definition as the intrinsic serial interval.
+We refer to this definition as the intrinsic serial interval (\fref{diagram}A).
 
@@
 \frac{\total(\psymp, \psymp+\tau)}{\int \total(\psymp, \psymp+\tau') d\tau'}.
+\label{eq:fserial}
 \end{equation}
@@
 \frac{\total(\ssymp-\tau, \ssymp)}{\int \total(\ssymp-\tau', \ssymp) d\tau'}.
+\label{eq:bserial}
 \end{equation}
+This framework allows us to understand changes in the realized serial intervals for any deterministic epidemic models.
 
@@
 
-We illustrate the theory by applying it to a specific example of an epidemic model. 
+We illustrate changes in the forward and backward serial intervals over the course of an epidemic by applying it to a specific example of an epidemic model. 
 We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
@@
 \end{equation}
-
+The forward and backward serial-interval distributions are then calculated by substituting these quantities into \eref{fserial} and \eref{bserial}.
 We use this framework to illustrate how the realized epidemiological time distributions vary over the course of an epidemic and depend on the perspective.
-We run deterministic as well as stochastic simulations based on the renewal equations (see Appendix) using previously estimated intrinsic incubation period and intrinsic generation-interval distributions for COVID-19 (Table 1) and compare both the forward and backward delay distributions;
-in particular, we focus on the realized incubation period, generation-interval, and serial-interval distributions.
 
@@
 In the Appendix, we provide a mathematical proof of this relationship.
-We further compare this with the estimate of \Ro based on the intrinsic serial-interval distribution:
+We further compare this with the estimate of \Ro based on the intrinsic serial-interval distribution $q(\tau)$:
 \begin{equation}
@@
 \end{equation}
-where the intrinsic serial-interval distribution does not depend on disease dynamics:
+where the intrinsic serial-interval distribution $q(\tau)$ does not depend on disease dynamics:
 \begin{equation}
@@
 \hline
-Mean forward incubation period & 5.5 days & \cite{lauer2020incubation} \\
-SD forward incubation period & 2.4 days & \cite{lauer2020incubation} \\
+Mean intrinsic incubation period & 5.5 days & \cite{lauer2020incubation} \\
+SD intrinsic incubation period & 2.4 days & \cite{lauer2020incubation} \\
 Mean intrinsic generation interval & 5 days & \cite{ferretti2020quantifying} \\
@@
 
+First, we compare the estimates of the basic reproduction number \Ro based on the initial forward serial-interval distributions and the intrinsic serial-interval distributions (see Appendix for calculation details.).
+In particular, we model the joint probability distribution of the intrinsic incubation periods and generation intervals using a bivariate lognormal distribution with correlation $\rho$ based on parameter estimates for COVID-19 (Table 1).
 The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $\gdist(\tau)$ give identical estimates of \Ro regardless of the correlation $\rho$ between the forward incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
@@
 Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different forward distributions lead to identical estimates of \Ro.
-In general, distributions with higher means and less variability give higher \Ro for a given $r$ \citep{wallinga2007generation, park2019practical}.
+In general, distributions with higher means and less variability give higher \Ro for a given $r$ \citep{wallinga2007generation, weitz2015modeling, park2019practical}.
 When incidence is growing exponentially, forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
@@
 The initial forward serial interval distribution captures the exponential growth phase of an epidemic.
-Now, we characterize how forward and backward serial intervals vary over the course of an epidemic.
+Next, we characterize how forward and backward serial intervals vary over the course of an epidemic by running deterministic as well as stochastic simulations based on the renewal equations (see Appendix) using parameters in Table 1;
+we further assume $\Ro=2.5$.
 While the forward serial-interval distribution is our primary focus, understanding the differences between the forward and the backward distributions are important because the observed intervals during on ongoing epidemic are like backward distributions:
@@
 
-Now we turn to practical issues.
+Now, we turn to issues of estimating \Ro from the observed serial interval data during on ongoing epidemic.
 In order to have an unbiased estimate of \Ro, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e., initial forward serial-interval distribution).
@@
 for example, if we were to measure serial intervals on Day 8 as in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
-\fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of the basic reproduction number \Ro in our stochastic simulations.
+\fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of the basic reproduction number \Ro in our stochastic simulations (assuming $\Ro = 2.5$ as in \fref{epi}).
 Notably, even if we could observe, and average, \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we would still underestimate the initial mean forward serial interval (and therefore \Ro), likely by a large amount, because the observed serial-interval distribution converges to the intrinsic serial-interval distribution;
@@
 Here we provide a heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \Ro retrospectively.
-Once serial intervals have been observed after the epidemic has been sufficiently progressed, we can rearrange the line list and group observed serial intervals based on the symptom onset date of infectors (\fref{obsrR}C).
+We can rearrange the line list and group observed serial intervals based on the symptom onset date of infectors (\fref{obsrR}C).
 Then, we can compare how estimates of the mean serial interval as well as \Ro change as we incorporate more recent cohorts into the analysis;
@@
 This approach is analogous to averaging over a set of forward intervals, just as using all information up to a certain time is analogous to averaging over a set of backward intervals (\fref{obsrR}D).
-During the exponential growth phase, the estimates of the mean serial interval and \Ro are consistent with the target value;
+During the exponential growth phase, the estimates of the mean serial interval and \Ro are consistent with the true value (see `initial forward' in \fref{obsrR}B,D);
 adding more data allows us to make more precise inference during this period.
@@
 This approach allows us to detect dynamical changes in the forward serial-interval distributions and its effect on the estimates of \Ro.
+
+\subsection{Applications to the COVID-19 pandemic}
 
@@
 
-\subsection{Applications to the COVID-19 pandemic}
-
 Finally, we re-analyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on transmission events reported between January 21--February 8, 2020;
-\cite{du2020serial} estimated the mean serial of 3.96 days (95\% CI 3.53–4.39 days) and \Ro of 1.32 (95\% CI 1.16–1.48).
+\cite{du2020serial} estimated the mean serial interval of 3.96 days (95\% CI 3.53–4.39 days) and \Ro of 1.32 (95\% CI 1.16–1.48).
 \fref{du}A shows that the mean forward serial interval decreases over time.
@@
 this sudden decrease is indicative of changes in the forward serial intervals as shown in our simulation study (\fref{obsrR}).
-The estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}.
-We note that early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
-This example demonstrates the danger of using the observed serial intervals to calculate the basic reproduction number without integrating serial intervals into cohorts.
+The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}:
+$\Ro = 2.6$ (95\% CI: 2.2--3.1) and $\Ro = 3.4$ (95\% CI: 2.7 -- 4.3) based on 8 and 6 doubling periods, respectively, using serial interval data from infectors who developed symptoms by day 7.
+These early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
+Therefore, \Ro estimate of 1.32 (95\% CI 1.16–1.48), which neglects the changes in the forward serial-interval distribution, is likely to be an underestimate.
+This example demonstrates the danger of using the observed serial intervals to calculate the reproduction number without integrating serial intervals into cohorts.
 
@@
 Here, we show that the initial \emph{forward} serial-interval distribution --- measured during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
-In general, this will not match the intrinsic or the backward serial interval.
-Further, this interval can decrease over time due to disease dynamics. 
+In general, the forward serial-interval distributions will not match the intrinsic or the backward serial-interval distributions.
+Further, the mean forward serial interval can decrease over time due to disease dynamics. 
 Failing to account for these differences can result in underestimation of \RR.

### 2020-05-22 observedrR.R

@@ -131,8 +131,6 @@ g1a <- ggplot(filter(ser_all, type=="Observed")) +
   annotate("text", x=78, y=serialsim$mean, label="Intrinsic", hjust=1, vjust=-0.3, size=5) +
   scale_x_continuous("Time (days)", limits=c(0, 80), expand=c(0, 0)) +
   scale_y_continuous("Mean serial interval (days)", expand=c(0, 0), limits=c(2, 6.3)) +
-  scale_color_manual(values=tail(cpalette, 2)) +
-  scale_fill_manual(values=tail(cpalette, 2)) +
   theme(
     panel.grid = element_blank(),
     legend.position = "none",
@@ -177,8 +175,6 @@ g2a <- ggplot(filter(R0all, type=="Observed")) +
   scale_x_continuous("Time (days)", limits=c(0, 80), expand=c(0, 0)) +
   scale_y_continuous("Basic reproduction number $\\mathcal R_0$", expand=c(0, 0), limits=c(0.9, 2.7),
                      breaks=c(1, 2, 3)) +
-  scale_color_manual(values=tail(cpalette, 2)) +
-  scale_fill_manual(values=tail(cpalette, 2)) +
   theme(
     panel.grid = element_blank(),
     legend.position = "none",

### 2020-05-22 serial.tex
a few changes to the notation

@@
 \end{equation}
-We further assume that the forward incubation period distributions does not vary across cohorts over the course of an epidemic, as they represent the life history of a disease, and use $k$ without subscript instead.
+We further assume that the forward incubation period distributions does not vary across cohorts over the course of an epidemic, as they represent the life history of a disease, and use $\idist$ without subscript instead.
 Then, we have:
@@
 \end{equation}
-The continuous-time intrinsic generation-interval distribution is parameterized using a log-normal distribution (Table 1). We define the forward incubation period distribution in a similar manner:
+The continuous-time intrinsic generation-interval distribution is parameterized using a log-normal distribution (Table 1). We define the intrinsic incubation period distribution in a similar manner:
 \begin{equation}
-\hat{k}(m \Delta t) = \frac{k(m \Delta t)}{\sum_{i=1}^\ell k(m \Delta t)}, \quad m=1, \dots, \ell,
+\hat{\idist}(m \Delta t) = \frac{\idist(m \Delta t)}{\sum_{i=1}^\ell \idist(m \Delta t)}, \quad m=1, \dots, \ell,
 \end{equation}
 where its continuous-time analog is also based on a log-normal distribution.
-For brevity, we assume that the forward incubation periods and intrinsic generation intervals are independent:
+For simplicity, we assume that the forward incubation periods and intrinsic generation intervals are independent:
 \begin{equation}
-\hat{h}(m \Delta t, \Delta t n) = \hat{k}(m \Delta t)\hat{\gdist}(\Delta t n), \quad m,n=1, \dots, \ell.
+\hat{h}(m \Delta t, \Delta t n) = \hat{\idist}(m \Delta t)\hat{\gdist}(\Delta t n), \quad m,n=1, \dots, \ell.
 \end{equation}
@@
 \begin{equation}
-f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) k(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
+f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
 \end{equation}
@@
 \begin{aligned}
-f_{0}(\tau) &\propto \int_0^\infty \int_{-\pinf}^{\tau} \exp(-r\pinf) h(\pinf, \sinf + \pinf) k(\tau - \sinf) \mathrm{d}\sinf\,\mathrm{d}\pinf\\
-&= \int_{-\infty}^{\tau} \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)k(\tau - \sinf)\mathrm{d}\pinf\, \mathrm{d}\sinf\\
+f_{0}(\tau) &\propto \int_0^\infty \int_{-\pinf}^{\tau} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \idist(\tau - \sinf) \mathrm{d}\sinf\,\mathrm{d}\pinf\\
+&= \int_{-\infty}^{\tau} \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\idist(\tau - \sinf)\mathrm{d}\pinf\, \mathrm{d}\sinf\\
 \end{aligned}
@@
 \end{equation}
-The initial forward serial-interval distribution $f_0$ can be expressed as a convolution of $z$ and $k$:
+The initial forward serial-interval distribution $f_0$ can be expressed as a convolution of $z$ and $\idist$:
 \begin{equation}
 \begin{aligned}
-f_{0}(\tau) &\propto \int_{-\infty}^{\tau} z(\sinf) k(\tau - \sinf) \mathrm{d}\sinf.\\
+f_{0}(\tau) &\propto \int_{-\infty}^{\tau} z(\sinf) \idist(\tau - \sinf) \mathrm{d}\sinf.\\
 \end{aligned}
@@
 \begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau \int_{0}^\infty \exp(-r\tau) k(\tau) \mathrm{d} \tau
+\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau \int_{0}^\infty \exp(-r\tau) \idist(\tau) \mathrm{d} \tau
 \end{equation}
@@
 &= \int_{0}^\infty \int_{-\pinf}^\infty \exp(- r \pinf) h(\pinf, \sinf+\pinf) \mathrm{d}\sinf\,\mathrm{d} \pinf\\
-&= \int_{0}^\infty \exp(- r \pinf) k(\pinf) d\pinf
+&= \int_{0}^\infty \exp(- r \pinf) \idist(\pinf) d\pinf
 \end{aligned}
 \end{equation}
-because $k$ is a marginal probability distribution of $h$.
-Since $\int_{0}^\infty \exp(- r \pinf) k(\pinf) d\pinf$ is a normalization factor for probability distribution $z$, we have:
+because $\idist$ is a marginal probability distribution of $h$.
+Since $\int_{0}^\infty \exp(- r \pinf) \idist(\pinf) d\pinf$ is a normalization factor for probability distribution $z$, we have:
 \begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau = \frac{\int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\tau}{\int_{0}^\infty \exp(- r \pinf) k(\pinf) d\pinf}.
+\int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau = \frac{\int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\tau}{\int_{0}^\infty \exp(- r \pinf) \idist(\pinf) d\pinf}.
 \end{equation}

### 2020-05-22 serial.tex
done for today

@@
 
-\newcommand{\eref}[1]{Eq.~\ref{eq:#1}}
+\newcommand{\eref}[1]{Eq.~(\ref{eq:#1})}
 \newcommand{\fref}[1]{Fig.~\ref{fig:#1}}
@@
 *Corresponding author: swp2@princeton.edu
+\bigskip
+
+Disclaimer: The findings and conclusions in this report are those of the authors and do not necessarily represent the official position of the U.S.
+National Institutes of Health or Department of Health and Human Services.
 \end{flushleft}
@@
 the reproduction number in a fully susceptible population --- referred to as the basic reproduction number \Ro --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention necessary to eliminate disease \citep{anderson1991infectious}.
-Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{du2020serial, jung2020real, li2020early, zhao2020preliminary}).
+Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{wallinga2007generation, fraser2009pandemic, hampson2009transmission, chunara2012social, chowell2014west, du2020serial, jung2020real}).
 
@@
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds.
-Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19, particularly for estimating its \RR, either without making a clear distinction \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}, or explicitly conflating the two intervals
+Researchers continue to rely on both generation and serial intervals to estimate the reproduction number \RR of COVID-19, either without making a clear distinction \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}, or explicitly conflating the two intervals
 \citep{anderson2020will,hellewell2020feasibility}.
@@
 By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates;
-therefore, we expect both generation- and serial-interval distributions to give identical estimates of  \RR based the observed epidemic growth rate $r$.
+therefore, we expect both generation- and serial-interval distributions to give identical estimates of \RR based on the observed epidemic growth rate $r$.
 In contexts where the distributions are expected to be different, current theory has no explanation for how they might provide identical estimates of \RR from $r$. 
@@
 
-The time delays between two epidemiological events can be defined either within an infected individual (e.g., infection and symptom onset of an individual, the incubation period) or between infected individuals (e.g., symptom onsets of an infector and an infectee, the serial interval).
+The time delays between two epidemiological events can be defined either within an infected individual (e.g., incubation period: infection and symptom onset of an individual) or between infected individuals (e.g., serial interval: symptom onsets of an infector and an infectee).
 We can further divide these events into \emph{primary} and \emph{secondary} events.
@@
 However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., distribution of time between realized primary and secondary events that occur during an epidemic).
-For example, an infectious contact may not result in infection if the contacted individual has already been infected;
+For example, an infectious contact results in infection only if the contacted individual is susceptible (and has already been infected);
 therefore, the realized generation-interval distribution can be different from the intrinsic generation-interval distribution.
@@
 For example, when we are measuring incubation periods, a primary cohort consists of all individuals who became infected at time $\psymp$.
-Similarly, when we are measuring serial intervals, a primary cohort consists of all individuals who became symptomatic at time $\psymp$.
+Similarly, when we are measuring serial intervals, a primary cohort consists of all infectors who became symptomatic at time $\psymp$.
 Then, for each primary cohort at time $\psymp$, we can define the expected time distribution between primary and secondary events.
@@
 In particular, when the incidence is growing exponentially, we can calculate the amount of bias exactly.
-Assuming that the forward delay distribution remains constant during the exponential growth phase ($\tsub{f}{exp}$), we have:
+Assuming that the forward delay distribution remains constant during the exponential growth phase ($f_p(\tau) \approx f_0(\tau)$), we can substitute $\psize(t) = \psize(0) \exp(rt)$ in \eref{backward} to obtain:
 \begin{equation}
-\tsub{b}{exp}(\tau) \propto \exp(-r\tau) \tsub{f}{exp}(\tau),
+b_0(\tau) \propto \exp(-r\tau) f_0(\tau),
 \label{eq:backexp}
@@
 Likewise, we can define the backward serial interval distribution for a cohort of infectees who became symptomatic at time $\ssymp$ (\fref{diagram}C).
-This conceptual framework clearly demonstrates that the distributions of $x_0$, $\ssymp$, and $x_1$ (and therefore the distributions of realized serial intervals) depend on the reference cohort and the corresponding cohort time.
+This conceptual framework clearly demonstrates that the distributions of $x_0$, $\gtime$, and $x_1$ (and therefore the distributions of realized serial intervals) depend on the reference cohort and the corresponding cohort time.
 
@@
 \frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) g(\tau) \dtau.
+\label{eq:Rgen}
 \end{equation}
@@
 \frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
+\label{eq:Rforward}
 \end{equation}
@@
 f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
+\label{eq:initialSI}
 \end{equation}
-In the Appendix, we provide a mathematical proof of this relationship.
+In Supplementary Materials, we provide a mathematical proof of this relationship.
 We further compare this with the estimate of \Ro based on the intrinsic serial-interval distribution $q(\tau)$:
@@
 \frac{1}{\Rintrinsic} = \int_{-\infty}^\infty \exp(-r\tau) q(\tau) \mathrm{d} \tau,
+\label{eq:Rintrinsic}
 \end{equation}
@@
 q(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
+\label{eq:intrinsicSI}
 \end{equation}
+Instead of numerically integrating over closed forms of $g$, $f_0$, and $q$ to estimate $\Ro$, we use simulation-based approaches for simplicity (Supplementary Materials).
 
@@
 For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short (\eref{backexp}), and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation- and serial-interval distributions.
-The Susceptible-Exposed-Infected-Recovered model, with an additional assumption that incubation and exposed periods are equivalent, provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector (see Appendix).
+The Susceptible-Exposed-Infected-Recovered model, with an additional assumption that incubation and exposed periods are equivalent, provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector (see Supplementary Materials).
 
@@
 
-First, we compare the estimates of the basic reproduction number \Ro based on the initial forward serial-interval distributions and the intrinsic serial-interval distributions (see Appendix for calculation details.).
+First, we compare the estimates of the basic reproduction number \Ro based on the initial forward serial-interval distributions and the intrinsic serial-interval distributions (see Supplementary Materials for calculation details.).
 In particular, we model the joint probability distribution of the intrinsic incubation periods and generation intervals using a bivariate lognormal distribution with correlation $\rho$ based on parameter estimates for COVID-19 (Table 1).
-The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $\gdist(\tau)$ give identical estimates of \Ro regardless of the correlation $\rho$ between the forward incubation period distribution and the intrinsic generation-interval distribution (\fref{rR}A).
-However, using the intrinsic serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \Ro;
+The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $\gdist(\tau)$ give identical estimates of \Ro (see \eref{Rgen} and \eref{Rforward}) regardless of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
+However, using the intrinsic serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \Ro (see \eref{Rintrinsic});
 as $r$ increases, \Rintrinsic saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
@@
 
-Comparing the shapes of initial forward serial-interval distributions and the intrinsic generation-interval distribution allows us to better understand how different forward distributions lead to identical estimates of \Ro.
+Comparing the shapes of initial forward serial-interval distributions (\eref{initialSI}) and the intrinsic generation-interval distribution allows us to better understand how different forward distributions lead to identical estimates of \Ro.
 In general, distributions with higher means and less variability give higher \Ro for a given $r$ \citep{wallinga2007generation, weitz2015modeling, park2019practical}.
@@
 The effects of higher means (which increases \Ro) exactly cancel those of higher variability (which decreases \Ro).
-On the other hand, \emph{intrinsic} serial intervals have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are wider (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
+On the other hand, \emph{intrinsic} serial intervals (\eref{intrinsicSI}) have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are wider (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
 therefore, we underestimate \Ro when we use the intrinsic serial-interval distribution.
@@
 The initial forward serial interval distribution captures the exponential growth phase of an epidemic.
-Next, we characterize how forward and backward serial intervals vary over the course of an epidemic by running deterministic as well as stochastic simulations based on the renewal equations (see Appendix) using parameters in Table 1;
+Next, we characterize how forward and backward serial intervals vary over the course of an epidemic by running deterministic as well as stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
 we further assume $\Ro=2.5$.
-While the forward serial-interval distribution is our primary focus, understanding the differences between the forward and the backward distributions are important because the observed intervals during on ongoing epidemic are like backward distributions:
+While the forward serial-interval distribution is our primary focus, understanding the differences between the forward and the backward distributions are important because the observed intervals during on ongoing epidemic are often the backward ones:
 we typically identify infected individuals and ask when they were infected by whom.
@@
 In this case, the increase in the mean backward incubation period directly translates to the decrease in the mean forward serial interval.
-Since the increase in the mean backward period is driven by the decreasing incidence, which can still occur in the absence of significant depletion of the susceptible pool via intervention, decrease in the mean forward serial interval may be a robust feature in COVID-19 outbreaks.
+% Since the increase in the mean backward period is driven by the decreasing incidence, which can still occur in the absence of significant depletion of the susceptible pool via intervention, decrease in the mean forward serial interval may be a robust feature in COVID-19 outbreaks.
 In general, relative contributions of the three distributions depend on their shapes, correlations between intrinsic incubation periods and generation intervals, and overall epidemiological dynamics.
@@
 
-Now, we turn to issues of estimating \Ro from the observed serial interval data during on ongoing epidemic.
-In order to have an unbiased estimate of \Ro, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e., initial forward serial-interval distribution).
-However, when an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
+Now, we turn to issues of estimating the reproduction number from the observed serial interval data during on ongoing epidemic.
+In order to have an unbiased estimate of the basic reproduction number, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e., initial forward serial-interval distribution).
+However, researchers typically use all available information to estimate epidemiological parameters;
+in particular, \citep{thompson2019improved} recently suggested that up-to-date serial interval data is necessary to accurately estimate the reproduction number.
+We explore the consequences of neglecting changes in the realized serial interval distributions on estimates of the basic reproduction number.
+
+When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
 for example, if we were to measure serial intervals on Day 8 as in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
@@
 they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
-In particular, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial interval data for accurate estimation of time-varying reproduction numbers;
-however, our study demonstrates that early serial interval data is required to estimate \RR and that using up-to-date serial interval data (without accounting for changes in the forward serial-interval distribution) can, in fact, underestimate \RR.
+\cite{thompson2019improved} recently emphasized the importance of using up-to-date serial interval data for accurate estimation of time-varying reproduction numbers.
+However, our study demonstrates that early serial interval data is required to estimate the initial \RR during the exponential growth phase and that using up-to-date serial interval data (without accounting for changes in the forward serial-interval distribution) can, in fact, underestimate the initial \RR.
+Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase and potentially re-asses existing estimates of \RR.
+
 Many studies have already estimated the (time-varying) reproduction numbers for COVID-19 epidemics using aggregated serial interval data (e.g., \cite{tempvar,du2020serial,pan2020jama,zhang2020evolving});
-these studies should re-assess whether they appropriately considered the \emph{forward} serial interval.
-Given large geographical differences in the observed exponential growth rates of the COVID-19 epidemic, the initial forward serial interval distributions are also likely to vary across different countries.
-We suggest that modelers should aim to characterize spatiotemporal variation in initial forward serial-interval distributions and understand their changes over time.
+these studies should also re-assess whether they appropriately considered the \emph{forward} serial interval.
+Given large geographical variation in the spread of the COVID-19, the forward serial interval distributions are also likely to vary across different countries.
+We suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions and understand their changes over time.
 These modeling approaches should be necessarily coupled with intensive epidemiological investigation through contact tracing at the very beginning of the outbreak in order to characterize the initial forward serial-interval distribution, particularly for an emerging epidemic such as COVID-19.
@@
 
-\section{Appendix}
+\section{Supplementary Materials}
 

### 2020-05-22 serial_guide.tex
diff

@@
-% Created by tikzDevice version 0.12.3 on 2020-05-05 20:39:06
+% Created by tikzDevice version 0.12.3 on 2020-05-22 09:42:54
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,421.76) {$p+x_0$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,421.76) {$p+x_1$};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,421.76) {$p+\sigma+x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,421.76) {$p+\sigma+x_2$};
 
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,535.89) -- (604.41,535.89);
+\path[draw=drawColor,line width= 1.7pt,line join=round] (282.16,535.89) -- (604.41,535.89);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,532.28) --
+\path[draw=drawColor,line width= 1.7pt,line join=round] (598.15,532.28) --
 	(604.41,535.89) --
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,229.04) {$p-x_0$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,229.04) {$p-x_1$};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,229.04) {$p-x_0+\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,229.04) {$p-x_1+\sigma$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,229.04) {$p-x_0+\sigma+x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,229.04) {$p-x_1+\sigma+x_2$};
 
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (282.16,343.17) -- (604.41,343.17);
+\path[draw=drawColor,line width= 1.7pt,line join=round] (282.16,343.17) -- (604.41,343.17);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (598.15,339.56) --
+\path[draw=drawColor,line width= 1.7pt,line join=round] (598.15,339.56) --
 	(604.41,343.17) --
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 36.32) {$s-x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 36.32) {$s-x_2$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 36.32) {$s-x_1-\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 36.32) {$s-x_2-\sigma$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 36.32) {$s-x_1-\sigma+x_0$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 36.32) {$s-x_2-\sigma+x_1$};
 
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (604.41,150.45) -- (282.16,150.45);
+\path[draw=drawColor,line width= 1.7pt,line join=round] (604.41,150.45) -- (282.16,150.45);
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (288.42,154.06) --
+\path[draw=drawColor,line width= 1.7pt,line join=round] (288.42,154.06) --
 	(282.16,150.45) --

### 2020-05-22 rRfun.R

@@ -1,0 +1,72 @@
+serialR <- function(r=0.1,
+                    rho=0.5,
+                    meanlog1=1.62,
+                    sdlog1=0.42,
+                    meanlog2=1.54,
+                    sdlog2=0.37,
+                    nsim=100000,
+                    seed=101) {
+  set.seed(seed)
+  backinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
+  
+  backinc <- sample(backinc, replace=TRUE, prob=exp(-r*backinc))
+  
+  logbackinc <- log(backinc)
+  
+  muloggen <- meanlog2 + sdlog2 * rho * (logbackinc - meanlog1)/sdlog1
+  sigmaloggen <- sqrt(sdlog2^2 * (1 - rho^2))
+  
+  forwardgen <- exp(rnorm(nsim, muloggen, sigmaloggen))
+  forwardinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
+  
+  ser <- -backinc + forwardgen + forwardinc
+  
+  list(
+    mean=mean(ser),
+    kappa=var(ser)/mean(ser)^2,
+    R=1/mean(exp(-r*ser))
+  )
+}
+
+serialR2 <- function(r=0.1,
+                     rho=0.5,
+                     meanlog1=1.62,
+                     sdlog1=0.42,
+                     meanlog2=1.54,
+                     sdlog2=0.37,
+                     nsim=100000,
+                     seed=101) {
+  set.seed(seed)
+  backinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
+  
+  logbackinc <- log(backinc)
+  
+  muloggen <- meanlog2 + sdlog2 * rho * (logbackinc - meanlog1)/sdlog1
+  sigmaloggen <- sqrt(sdlog2^2 * (1 - rho^2))
+  
+  forwardgen <- exp(rnorm(nsim, muloggen, sigmaloggen))
+  forwardinc <- rlnorm(nsim, meanlog=meanlog1, sdlog=sdlog1)
+  
+  ser <- -backinc + forwardgen + forwardinc
+  
+  list(
+    mean=mean(ser),
+    kappa=var(ser)/mean(ser)^2,
+    R=1/mean(exp(-r*ser))
+  )
+}
+
+generationR <- function(r=0.1,
+                        meanlog2=1.54,
+                        sdlog2=0.37,
[…]

### 2020-05-22 serial_guide.R

@@ -18,12 +18,12 @@ g1 <- ggplot(arrow) +
   geom_point(aes(1.5, 0.4), size=3) +
   geom_point(aes(2.5, 0.3), size=3) +
   geom_point(aes(0.5, 0.1), size=3) +
-  annotate("text", x=1.5, y=-0.05, label="$p+x_0$") +
+  annotate("text", x=1.5, y=-0.05, label="$p+x_1$") +
   annotate("text", x=0.5, y=-0.05, label="$p$") +
   annotate("text", x=0.5, y=-0.1, label="Infector (reference cohort)") +
   annotate("text", x=2.5, y=-0.1, label="Infectee") +
   annotate("text", x=2.5, y=-0.05, label="$p+\\sigma$") +
-  annotate("text", x=3.5, y=-0.05, label="$p+\\sigma+x_1$") +
+  annotate("text", x=3.5, y=-0.05, label="$p+\\sigma+x_2$") +
   geom_segment(aes(x, y, xend=x1, yend=y1), arrow = arrow(length = unit(0.2, "inches")), lwd=1) +
   geom_segment(aes(0.5, 0, xend=0.5, yend=0.2), lty=2) +
   geom_segment(aes(1.5, 0, xend=1.5, yend=0.4), lty=2) +
@@ -32,7 +32,7 @@ g1 <- ggplot(arrow) +
   geom_segment(aes(0.5, 0.1, xend=1.5, yend=0.1), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
   geom_segment(aes(0.5, 0.2, xend=2.5, yend=0.2), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
   geom_segment(aes(2.5, 0.3, xend=3.5, yend=0.3), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
-  geom_segment(aes(1.5, 0.4, xend=3.5, yend=0.4), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
+  geom_segment(aes(1.5, 0.4, xend=3.5, yend=0.4), arrow = arrow(length = unit(0.1, "inches")), lwd=1.5) +
   annotate("text", x=2.5, y=0.45, label="Intrinsic serial interval") +
   annotate("text", x=1, y=0.15, label="Intrinsic incubation period") +
   annotate("text", x=1, y=0.25, label="Intrinsic generation interval") +
[…]

### 2020-05-22 serial.tex
tweak

@@
 \begin{equation}
-\tau = (\gtime + x_1) - x_0
+\tau = (\gtime + x_2) - x_1
 \end{equation}
-where $x_0$ and $x_1$ represent incubation periods of an infector and an infectee, respectively, and $\gtime$ represents the generation interval.
-These studies assumed that $x_0$ and $x_1$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, this conclusion is based on the implicit assumption that incubation times, $x_0$ and $x_1$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on disease dynamics) --- something that is true of forward but not backward incubation times.
+where $x_1$ and $x_2$ represent incubation periods of an infector and an infectee, respectively, and $\gtime$ represents the generation interval.
+These studies assumed that $x_1$ and $x_2$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
+however, this conclusion is based on the implicit assumption that incubation times, $x_1$ and $x_2$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on disease dynamics) --- something that is true of forward but not backward incubation times.
 We refer to this definition as the intrinsic serial interval (\fref{diagram}A).
@@
 (A) The intrinsic serial interval for a cohort of individuals infected at time $\psymp$.
-In this case, $x_0$ follows the intrinsic incubation period distribution;
+In this case, $x_1$ follows the intrinsic incubation period distribution;
 $\gtime$ follows the intrinsic generation-interval distribution;
-and $x_1$ follows the intrinsic incubation period distribution.
+and $x_2$ follows the intrinsic incubation period distribution.
 (B) The forward serial interval for a cohort of infectors who became symptomatic at time $\psymp$.
-In this case, $x_0$ follows the backward incubation period distribution;
+In this case, $x_1$ follows the backward incubation period distribution;
 $\gtime$ follows the forward generation-interval distribution;
-and $x_1$ follows the forward incubation period distribution.
+and $x_2$ follows the forward incubation period distribution.
 (C) The backward serial interval for a cohort of infectees who became symptomatic at time $\ssymp$.
-In this case, $x_0$ follows the forward incubation period distribution;
+In this case, $x_1$ follows the forward incubation period distribution;
 $\gtime$ follows the backward generation-interval distribution;
-and $x_1$ follows the backward incubation period distribution.
+and $x_2$ follows the backward incubation period distribution.
 }
@@
 Given that an infector became symptomatic at time $\psymp$, to calculate the forward serial interval we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when they became symptomatic.
-In \fref{diagram}B, we see that $x_0$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\psymp$;
-$\gtime$ follows the forward generation-interval distribution of the cohort of infectors who came infected at time $\psymp - x_0$;
-and $x_1$ follows the forward incubation period distribution of the cohort of infectees who became infected at time $\psymp - x_0 + \gtime$.
+In \fref{diagram}B, we see that $x_1$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\psymp$;
+$\gtime$ follows the forward generation-interval distribution of the cohort of infectors who came infected at time $\psymp - x_1$;
+and $x_2$ follows the forward incubation period distribution of the cohort of infectees who became infected at time $\psymp - x_1 + \gtime$.
 Likewise, we can define the backward serial interval distribution for a cohort of infectees who became symptomatic at time $\ssymp$ (\fref{diagram}C).
-This conceptual framework clearly demonstrates that the distributions of $x_0$, $\gtime$, and $x_1$ (and therefore the distributions of realized serial intervals) depend on the reference cohort and the corresponding cohort time.
+This conceptual framework clearly demonstrates that the distributions of $x_1$, $\gtime$, and $x_2$ (and therefore the distributions of realized serial intervals) depend on the reference cohort and the corresponding cohort time.
 
@@
 f_\psymp(\tau) = 
-\frac{\total(\psymp, \psymp+\tau)}{\int \total(\psymp, \psymp+\tau') d\tau'}.
+\frac{\total(\psymp, \psymp+\tau)}{\int \total(\psymp, \psymp+\tau') \dtau'}.
 \label{eq:fserial}
@@
 b_\ssymp(\tau) = 
-\frac{\total(\ssymp-\tau, \ssymp)}{\int \total(\ssymp-\tau', \ssymp) d\tau'}.
+\frac{\total(\ssymp-\tau, \ssymp)}{\int \total(\ssymp-\tau', \ssymp) \dtau'}.
 \label{eq:bserial}
@@
 The intrinsic generation-interval distribution is parameterized using a log-normal distribution with log mean $\mu_G=1.54$ and log standard deviation $\sigma_G=0.37$.
-The forward incubation period distribution is parameterized using a log-normal distribution with log mean $\mu_I=1.62$ and log standard deviation $\sigma_I=0.42$.
+The intrinsic incubation period distribution is parameterized using a log-normal distribution with log mean $\mu_I=1.62$ and log standard deviation $\sigma_I=0.42$.
 The joint probability distribution is modeled using a multivariate log-normal distribution with correlations (on the log scale) $\rho=-0.5, 0, 0.5$.
@@
 \begin{aligned}
-i(t) &= \Ro S(t-\Delta t) \sum_{m=1}^{\ell} i(t-m \Delta t) \hat{\gdist}(m \Delta t) \\
+i(t) &= \Ro S(t-\Delta t) \sum_{m=1}^{\tsub{m}{max}} i(t-m \Delta t) \hat{\gdist}(m \Delta t) \\
 S(t) &= S(t-\Delta t) - i(t)
@@
 \begin{equation}
-\hat{\gdist}(m \Delta t) = \frac{\gdist(m \Delta t)}{\sum_{i=1}^\ell \gdist(m \Delta t)}, \quad m=1, \dots, \ell
+\hat{\gdist}(m \Delta t) = \frac{\gdist(m \Delta t)}{\sum_{i=1}^\ell \gdist(m \Delta t)}, \quad m=1, \dots, \tsub{m}{max}.
 \end{equation}
@@
 \begin{equation}
-\hat{\idist}(m \Delta t) = \frac{\idist(m \Delta t)}{\sum_{i=1}^\ell \idist(m \Delta t)}, \quad m=1, \dots, \ell,
+\hat{\idist}(m \Delta t) = \frac{\idist(m \Delta t)}{\sum_{i=1}^\ell \idist(m \Delta t)}, \quad m=1, \dots, \tsub{m}{max},
 \end{equation}
@@
 \begin{equation}
-\hat{h}(m \Delta t, \Delta t n) = \hat{\idist}(m \Delta t)\hat{\gdist}(\Delta t n), \quad m,n=1, \dots, \ell.
+\hat{h}(m \Delta t, n \Delta t) = \hat{\idist}(m \Delta t)\hat{\gdist}(n \Delta t), \quad m,n=1, \dots, \tsub{m}{max}.
 \end{equation}
-We use $\Delta t = 0.025\,\textrm{days}$ and $\ell=2001$ for discretization steps.
+We use $\Delta t = 0.025\,\textrm{days}$ and $\tsub{m}{max}=2001$ for discretization steps.
 
@@
 \begin{aligned}
-i(m \Delta t) &= C \exp(r m \Delta t), \quad m=1, \dots, \ell\\
-S(m \Delta t) &= N - \sum_{n=1}^m i(m \Delta t), \quad m=1, \dots, \ell\\
+i(m \Delta t) &= C \exp(r m \Delta t), \quad m=1, \dots, \tsub{m}{max}\\
+S(m \Delta t) &= N - \sum_{n=1}^m i(n \Delta t), \quad m=1, \dots, \tsub{m}{max}\\
 \end{aligned}
 \end{equation}
-where $C$ is chosen such that $\sum_{n=1}^\ell i(m \Delta t)=10$.
-These initial conditions allow the model to follow exponentially growth from time $\Delta t (\ell + 1)$ without any transient behaviors.
-Results presented in the main text show simulations beginning from time $\Delta t (\ell + 1)$.
+where $C$ is chosen such that $\sum_{n=1}^{\tsub{m}{max}} i(m \Delta t)=10$.
+These initial conditions allow the model to follow exponentially growth from time $\Delta t (\tsub{m}{max} + 1)$ without any transient behaviors.
+Results presented in the main text show simulations beginning from time $\Delta t (\tsub{m}{max} + 1)$.
 
@@
 \begin{equation}
-F_i = -X_{0,i} + (G_i|X_{0,i}) + X_{1,i},
+F_i = -X_{1,i} + (G_i|X_{1,i}) + X_{2,i},
 \end{equation}
-where the backward incubation period $X_{0,i}$ of an infector is simulated by drawing random log-normal samples $Y_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $Y_i$, each weighted by the inverse of the exponential growth function $\exp(-rY_i)$;
-the intrinsic generation interval conditional on the incubation period of the infector $(G_i|X_{0,i})$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(X_{0,i}) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
-the forward incubation period $X_{1,i}$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
+where the backward incubation period $X_{1,i}$ of an infector is simulated by drawing random log-normal samples $Y_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $Y_i$, each weighted by the inverse of the exponential growth function $\exp(-rY_i)$;
+the intrinsic generation interval conditional on the incubation period of the infector $(G_i|X_{1,i})$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(X_{1,i}) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
+the forward incubation period $X_{2,i}$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
 We then calculate the basic reproduction number \Ro using the empirical estimator:
@@
 \begin{equation}
-Q_i = -Y_i + (G_i|Y_i) + X_{1,i}.
+Q_i = -Y_i + (G_i|Y_i) + X_{2,i}.
 \end{equation}

### 2020-05-22 serial.tex
ok
minor tweaks

@@
 On one hand, generation intervals provide a mechanistic link between $r$ and \RR but are harder to measure via contact tracing.
-On the other hand, serial intervals are easier to measure from contact tracing but recent studies suggest that two intervals give different estimates of \RR from $r$.
+On the other hand, serial intervals are easier to measure from contact tracing but recent studies suggest that the two intervals give different estimates of \RR from $r$.
 We present a general framework for characterizing \emph{any} epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly estimates \RR from $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
 We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial interval data --- our analysis shows that using incorrectly defined serial intervals can severely bias the estimate.
-This study demonstrates the importance of early epidemiological investigation through contact tracing and provides rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
+This study demonstrates the importance of early epidemiological investigation through contact tracing and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
 
@@
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
-the reproduction number in a fully susceptible population --- referred to as the basic reproduction number \Ro --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention necessary to eliminate disease \citep{anderson1991infectious}.
+the value in a fully susceptible population --- referred to as the basic reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population and the amount of intervention necessary to eliminate it \citep{anderson1991infectious}.
 Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{wallinga2007generation, fraser2009pandemic, hampson2009transmission, chunara2012social, chowell2014west, du2020serial, jung2020real}).
@@
 \frac{\mathrm{d}S}{\mathrm{d}t} &= - \beta S I\\
-\frac{\mathrm{d}E}{\mathrm{d}t} &= \beta S I - \sigma E\\
-\frac{\mathrm{d}I}{\mathrm{d}t} &= \sigma E - \gamma I \\
-\frac{\mathrm{d}R}{\mathrm{d}t} &= \gamma I \\
+\frac{\mathrm{d}E}{\mathrm{d}t} &= \beta S I - \gamma_E E\\
+\frac{\mathrm{d}I}{\mathrm{d}t} &= \gamma_E E - \gamma_I I \\
+\frac{\mathrm{d}R}{\mathrm{d}t} &= \gamma_I I \\
 \end{aligned}
 \end{equation}
-where $\beta$ is the transmission rate, $1/\sigma$ is the mean latent period, and $1/\gamma$ is the mean infectious period.
+where $\beta$ is the transmission rate, $1/\gamma_E$ is the mean latent period, and $1/\gamma_I$ is the mean infectious period.
 We further assume that the latent period is equivalent to incubation period; in other words, infected individuals can only transmit after symptom onset.
@@
 0 & x > \tau\\
-\gamma \sigma \exp(-\gamma (\tau-x)-\sigma x) & x \leq \tau
+\gamma_I \gamma_E \exp(-\gamma_I (\tau-x)-\gamma_E x) & x \leq \tau
 \end{cases}
@@
 g(\tau) &= \int_0^\tau h(x, \tau) \dx\\
-&= \frac{\gamma \sigma}{\sigma-\gamma} (\exp(-\gamma \tau) - \exp(-\sigma \tau))
+&= \frac{\gamma_I \gamma_E}{\gamma_E-\gamma_I} (\exp(-\gamma_I \tau) - \exp(-\gamma_E \tau))
 \end{aligned}
@@
 f_{0}(\tau) &\propto \int_{-\infty}^{0} \int_{0}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
-&\propto \int_{-\infty}^{0} \int_{0}^{\tau}\exp(r \pinf) \exp(-\gamma \sinf+ \sigma \pinf) \exp(-\sigma(\tau-\sinf)) \, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
-&\propto  \exp(-\sigma \tau) \int_{-\infty}^{0} \int_{0}^{\tau} \exp((\sigma-\gamma) \sinf) \exp((r+ \sigma) \pinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
-&\propto  (\exp(-\gamma \tau) - \exp(-\sigma \tau)) \int_{-\infty}^{0} \exp((r+ \sigma) \pinf)\,\mathrm{d}\pinf\\
-&\propto  \exp(-\gamma \tau) - \exp(-\sigma \tau)
+&\propto \int_{-\infty}^{0} \int_{0}^{\tau}\exp(r \pinf) \exp(-\gamma_I \sinf+ \gamma_E \pinf) \exp(-\gamma_E(\tau-\sinf)) \, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
+&\propto  \exp(-\gamma_E \tau) \int_{-\infty}^{0} \int_{0}^{\tau} \exp((\gamma_E-\gamma_I) \sinf) \exp((r+ \gamma_E) \pinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
+&\propto  (\exp(-\gamma_I \tau) - \exp(-\gamma_E \tau)) \int_{-\infty}^{0} \exp((r+ \gamma_E) \pinf)\,\mathrm{d}\pinf\\
+&\propto  \exp(-\gamma_I \tau) - \exp(-\gamma_E \tau)
 \end{aligned}

### 2020-05-25 serial.tex
new proof

@@
 Ignoring births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be written as:
-\begin{equation}
-\begin{aligned}
-\frac{\mathrm{d}S}{\mathrm{d}t} &= - i(t)\\
+\begin{align}
+\frac{\mathrm{d}S}{\mathrm{d}t} &= - i(t)\nonumber\\
 i(t) &= \Ro S(t) \int_0^\infty i(t-\tau) \gdist(\tau) \dtau,
-\end{aligned}
 \label{eq:renewal}
-\end{equation}
+\end{align}
 where \Ro is the basic reproduction number, and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a population where the number of susceptibles remains constant).
@@
 Then, we have:
-\begin{equation}
-\begin{aligned}
-\idist(x) &= \int_0^\infty h(x, \tau) \dtau\\
+\begin{align}
+\idist(x) &= \int_0^\infty h(x, \tau) \dtau\nonumber\\
 \gdist(\tau) &= \int_0^\infty h(x, \tau) \dx
-\end{aligned}
-\end{equation}
+\label{eq:marginal}
+\end{align}
 Finally, the case reproduction for this model is defined as follows:
@@
 We simulate the renewal equation model using a discrete-time approximation:
-\begin{equation}
-\begin{aligned}
-i(t) &= \Ro S(t-\Delta t) \sum_{m=1}^{\tsub{m}{max}} i(t-m \Delta t) \hat{\gdist}(m \Delta t) \\
+\begin{align}
+i(t) &= \Ro S(t-\Delta t) \sum_{m=1}^{\tsub{m}{max}} i(t-m \Delta t) \hat{\gdist}(m \Delta t) \nonumber \\
 S(t) &= S(t-\Delta t) - i(t)
-\end{aligned}
-\end{equation}
+\end{align}
 where $\hat{\gdist}$ is a discrete-time intrinsic generation-interval distribution that satisfies the following:
@@
 We initialize the simulation with population size $N$=40,000 as follows:
-\begin{equation}
-\begin{aligned}
-i(m \Delta t) &= C \exp(r m \Delta t), \quad m=1, \dots, \tsub{m}{max}\\
-S(m \Delta t) &= N - \sum_{n=1}^m i(n \Delta t), \quad m=1, \dots, \tsub{m}{max}\\
-\end{aligned}
-\end{equation}
+\begin{align}
+i(m \Delta t) &= C \exp(r m \Delta t), \quad m=1, \dots, \tsub{m}{max}\nonumber \\
+S(m \Delta t) &= N - \sum_{n=1}^m i(n \Delta t), \quad m=1, \dots, \tsub{m}{max}
+\end{align}
 where $C$ is chosen such that $\sum_{n=1}^{\tsub{m}{max}} i(m \Delta t)=10$.
@@
 
-The intrinsic generation-interval distribution $\gdist(\tau)$ provides a link between $r$ and \Ro via the Euler-Lotka equation:
+The intrinsic generation-interval distribution $\gdist(\tau)$ provides a link between $r$ and \Ro via the Euler-Lotka equation \citep{wallinga2007generation}:
 \begin{equation}
-\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) \gdist(\tau) \dtau.
+\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) \gdist(\tau) \dtau\,.
 \end{equation}
-Here, we prove that the initial forward serial-interval distribution $f_0$ also provides the same link:
+In this section, we prove that the initial forward serial-interval distribution $f_0(\tau)$ also estimates the same \Ro from $r$, except that integral extends to $\tau=-\infty$ rather than beginning at $\tau=0$, because serial intervals can be negative:
 \begin{equation}
-\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \dtau,
+\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \dtau\,.
+\label{eq:ptarget}
 \end{equation}
-where the initial forward serial-interval distribution is defined as:
+Here, the initial forward serial-interval distribution $f_{0}(\tau)$ is defined as:
 \begin{equation}
-f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1.
+f_{0}(\tau) = \frac{\int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1}{\int_{-\infty}^\infty \int_{-\infty}^{0} \int_{\alpha_1}^{\tau'} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1 \dtau'},
+\label{eq:fdist}
+\end{equation}
+where $h$ is the joint probability distribution describing the the intrinsic generation-interval distribution $g$ and the intrinsic incubation period distribution $\idist$ (see \eref{marginal} in the main text).
+For brevity, we denote the constant of proportionality using $\phi$ such that
+\begin{equation}
+f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1\,.
 \end{equation}
 
-First, we rewrite the initial forward serial-interval distribution in the following form:
+In order to verify \eref{ptarget}, we first rewrite the integral in \eref{fdist} by substituting $-\alpha_1$ for $\alpha_1$, and then changing the order of integration:
+\begin{align}
+f_{0}(\tau) &= \frac{1}{\phi} \int_0^\infty \int_{-\pinf}^{\tau} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \idist(\tau - \sinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf\,,\nonumber \\
+&= \frac{1}{\phi} \int_{-\infty}^{\tau} \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\idist(\tau - \sinf)\,\mathrm{d}\pinf\, \mathrm{d}\sinf\,.
+\label{eq:newforward}
+\end{align}
+To further simplify the expression, we define $z(\sinf)$ as follows:
 \begin{equation}
-\begin{aligned}
-f_{0}(\tau) &\propto \int_0^\infty \int_{-\pinf}^{\tau} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \idist(\tau - \sinf) \mathrm{d}\sinf\,\mathrm{d}\pinf\\
-&= \int_{-\infty}^{\tau} \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\idist(\tau - \sinf)\mathrm{d}\pinf\, \mathrm{d}\sinf\\
-\end{aligned}
+z(\sinf) = \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \,\mathrm{d}\pinf\,.
 \end{equation}
-It follows that $z(\sinf)$ describes the time between symptom onset of infector and infection of infectee:
+We substitute $z(\sinf)$ into \eref{newforward} to obtain:
 \begin{equation}
-z(\sinf) \propto \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf.
+f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{\tau} z(\sinf) \idist(\tau - \sinf) \,\mathrm{d}\sinf\,,.
 \end{equation}
-The initial forward serial-interval distribution $f_0$ can be expressed as a convolution of $z$ and $\idist$:
+By normalizing $z(\sinf)$ such that $\hat{z}(\sinf) = z(\sinf)/\left[\int_{-\infty}^\infty z(x) \dx\right]$,
+we can now express the initial forward serial-interval distribution $f_0$ as a convolution of $\hat{z}$ and $\idist$:
 \begin{equation}
-\begin{aligned}
-f_{0}(\tau) &\propto \int_{-\infty}^{\tau} z(\sinf) \idist(\tau - \sinf) \mathrm{d}\sinf.\\
-\end{aligned}
+f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{\tau} \hat{z}(\sinf) \idist(\tau - \sinf)\, \mathrm{d}\sinf\,.
 \end{equation}
-Then, we have
+Since the right hand side of \eref{ptarget} is also a moment-generating function of $f_0$, we can express it as the product of the moment-generation functions of $\hat{z}$ and $\idist$:
 \begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau \int_{0}^\infty \exp(-r\tau) \idist(\tau) \mathrm{d} \tau
+\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) \hat{z}(\tau)\, \mathrm{d} \tau \int_{0}^\infty \exp(-r\tau) \idist(\tau) \dtau\,.
+\label{eq:newtarget}
 \end{equation}
 
-Note that 
+In order to derive an expression for $\int_{-\infty}^\infty \exp(-r\tau) \hat{z}(\tau) \mathrm{d} \tau$, we have to first derive an analytical expression for $\int_{-\infty}^\infty z(x) \dx$.
+By changing the order of integration, we have:
+\begin{align}
+\int_{-\infty}^\infty z(\sinf) \mathrm{d}\sinf &= \int_{-\infty}^\infty \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf \,\mathrm{d}\sinf\nonumber\,,\\
+&= \int_{0}^\infty \int_{-\pinf}^\infty \exp(- r \pinf) h(\pinf, \sinf+\pinf)\, \mathrm{d}\sinf\,\mathrm{d} \pinf\,.
+\end{align}
+Since $\idist$ is a marginal probability distribution of $h$, it follows that:
 \begin{equation}
-\begin{aligned}
-&\int_{-\infty}^\infty \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\sinf\\
-&= \int_{0}^\infty \int_{-\pinf}^\infty \exp(- r \pinf) h(\pinf, \sinf+\pinf) \mathrm{d}\sinf\,\mathrm{d} \pinf\\
-&= \int_{0}^\infty \exp(- r \pinf) \idist(\pinf) d\pinf
-\end{aligned}
-\end{equation}
-because $\idist$ is a marginal probability distribution of $h$.
-Since $\int_{0}^\infty \exp(- r \pinf) \idist(\pinf) d\pinf$ is a normalization factor for probability distribution $z$, we have:
-\begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) z(\tau) \mathrm{d} \tau = \frac{\int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\tau}{\int_{0}^\infty \exp(- r \pinf) \idist(\pinf) d\pinf}.
+\int_{-\infty}^\infty z(\sinf) \mathrm{d}\sinf = \int_{0}^\infty \exp(- r \pinf) \idist(\pinf)\, \mathrm{d}\pinf\,.
 \end{equation}
@@
 \begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\tau.
+\hat{z}(\sinf) = \frac{\int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf}{\int_{0}^\infty \exp(- r \pinf) \idist(\pinf)\, \mathrm{d}\pinf}\,.
+\end{equation}
+Substituting the expression into \eref{newtarget}, we have:
+\begin{equation}
+\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf \dtau\,.
+\label{eq:newtarget2}
 \end{equation}
 
-We are left to show that 
+Recall that $g$ is also a marginal probability distribution of $h$:
 \begin{equation}
-\int_0^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \mathrm{d}\pinf \mathrm{d}\tau,
+g(\tau) = \int_0^\infty h(\pinf, \tau) \,\mathrm{d} \pinf\,.
 \end{equation}
-where the intrinsic generation-interval distribution $g$ is also a marginal probability distribution of $f$:
-\begin{equation}
-g(\tau) = \int_0^\infty h(\pinf, \tau)  \mathrm{d} \pinf.
-\end{equation}
-Let $\sigma = \pinf + \tau$. Then, by change of variables, it immediately follows that
-\begin{equation}
-\begin{aligned}
-&\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r \pinf) h(\pinf, \tau+\pinf) \mathrm{d} \pinf\, \mathrm{d}\tau\\
-&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \sigma) h(\pinf, \sigma) \mathrm{d} \pinf\, \mathrm{d}\sigma\\
-&=\int_{0}^{\infty} \exp(-r\tau) g(\tau) \mathrm{d}\tau
-\end{aligned}
-\end{equation}
-Therefore, the initial forward serial--interval distribution and the intrinsic generation-interval distribution give the same link between $r$ and \RR.
+We can then substitute $\sigma = \pinf + \tau$ into \eref{newtarget2} and apply change of variables to obtain:
+\begin{align}
+&\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau\\
+&=\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r \pinf) h(\pinf, \tau+\pinf) \,\mathrm{d} \pinf \dtau\nonumber\\
+&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \sigma) h(\pinf, \sigma)\, \mathrm{d} \pinf\, \mathrm{d}\sigma\nonumber\\
+&=\int_{0}^{\infty} \exp(-r\tau) g(\tau) \dtau =\frac{1}{\Ro}
+\end{align}
+Therefore, the initial forward serial-interval distribution and the intrinsic generation-interval distribution give the same estimates of \Ro from $r$.
 
@@
 \end{equation}
-We compare this with an estimate of \Ro based on the intrinsic serial-interval distribution in which the backward and the forward incubation periods are identically distributed \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
+We compare this with an estimate of \Ro based on the intrinsic serial-interval distribution which has the same mean as the intrinsic geeneration-interval distribution \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
 \begin{equation}
@@
 Consider a Susceptible-Exposed-Infectious-Recovered model:
-\begin{equation}
-\begin{aligned}
-\frac{\mathrm{d}S}{\mathrm{d}t} &= - \beta S I\\
-\frac{\mathrm{d}E}{\mathrm{d}t} &= \beta S I - \gamma_E E\\
-\frac{\mathrm{d}I}{\mathrm{d}t} &= \gamma_E E - \gamma_I I \\
-\frac{\mathrm{d}R}{\mathrm{d}t} &= \gamma_I I \\
-\end{aligned}
-\end{equation}
+\begin{align}
+\frac{\mathrm{d}S}{\mathrm{d}t} &= - \beta S I \nonumber \\
+\frac{\mathrm{d}E}{\mathrm{d}t} &= \beta S I - \gamma_E E\nonumber\\
+\frac{\mathrm{d}I}{\mathrm{d}t} &= \gamma_E E - \gamma_I I\nonumber \\
+\frac{\mathrm{d}R}{\mathrm{d}t} &= \gamma_I I
+\end{align}
 where $\beta$ is the transmission rate, $1/\gamma_E$ is the mean latent period, and $1/\gamma_I$ is the mean infectious period.
@@
 Then, the intrinsic generation-interval distribution is given by:
-\begin{equation}
-\begin{aligned}
-g(\tau) &= \int_0^\tau h(x, \tau) \dx\\
+\begin{align}
+g(\tau) &= \int_0^\tau h(x, \tau) \dx\nonumber \\
 &= \frac{\gamma_I \gamma_E}{\gamma_E-\gamma_I} (\exp(-\gamma_I \tau) - \exp(-\gamma_E \tau))
-\end{aligned}
-\end{equation}
+\end{align}
 On the other hand, the initial forward serial-interval distribution is given by:
-\begin{equation}
-\begin{aligned}
-f_{0}(\tau) &\propto \int_{-\infty}^{0} \int_{0}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
-&\propto \int_{-\infty}^{0} \int_{0}^{\tau}\exp(r \pinf) \exp(-\gamma_I \sinf+ \gamma_E \pinf) \exp(-\gamma_E(\tau-\sinf)) \, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
-&\propto  \exp(-\gamma_E \tau) \int_{-\infty}^{0} \int_{0}^{\tau} \exp((\gamma_E-\gamma_I) \sinf) \exp((r+ \gamma_E) \pinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf\\
-&\propto  (\exp(-\gamma_I \tau) - \exp(-\gamma_E \tau)) \int_{-\infty}^{0} \exp((r+ \gamma_E) \pinf)\,\mathrm{d}\pinf\\
+\begin{align}
+f_{0}(\tau) &\propto \int_{-\infty}^{0} \int_{0}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf \nonumber \\
+&\propto \int_{-\infty}^{0} \int_{0}^{\tau}\exp(r \pinf) \exp(-\gamma_I \sinf+ \gamma_E \pinf) \exp(-\gamma_E(\tau-\sinf)) \, \mathrm{d}\sinf\,\mathrm{d}\pinf \nonumber \\
+&\propto  \exp(-\gamma_E \tau) \int_{-\infty}^{0} \int_{0}^{\tau} \exp((\gamma_E-\gamma_I) \sinf) \exp((r+ \gamma_E) \pinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf \nonumber \\
+&\propto  (\exp(-\gamma_I \tau) - \exp(-\gamma_E \tau)) \int_{-\infty}^{0} \exp((r+ \gamma_E) \pinf)\,\mathrm{d}\pinf \nonumber \\
 &\propto  \exp(-\gamma_I \tau) - \exp(-\gamma_E \tau)
-\end{aligned}
-\end{equation}
+\end{align}
 Therefore, both the intrinsic generation intervals and the initial forward serial intervals are identically distributed and have the same mean.

### 2020-05-25 serial.tex
general comments and plot tweaks

@@
 \usepackage{amsfonts}
+\usepackage[utf8]{inputenc} % make sure fancy dashes etc. don't get dropped
 
@@
 
-The reproduction number \RR is one of the most important characteristics of an emerging epidemic, including characterization of coronavirus disease 2019 (COVID-19) \citep{majumder2020early}.
+The reproduction number \RR is one of the most important characteristics of an emerging epidemic, including the current pandemic of coronavirus disease 2019 (COVID-19) \citep{majumder2020early}.
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
@@
 
-One source of confusion comes down to an apparent discrepancy between biological intuition and mathematical theory.
-When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
+\bmb{the next two paragraphs are much improved but they might be able to be improved still further by making the logical as explicit as possible (see ?
+below for points where I think the connections are not absolutely clear)}
+One source of confusion arises from an apparent discrepancy between biological intuition and mathematical theory.
+When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' \bmb{quotes or italic?} based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
 This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
 By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates;
-therefore, we expect both generation- and serial-interval distributions to give identical estimates of \RR based on the observed epidemic growth rate $r$.
-In contexts where the distributions are expected to be different, current theory has no explanation for how they might provide identical estimates of \RR from $r$. 
+therefore \bmb{why?
+(because both are renewal processes describing the same underlying system, where all components must be growing at the same rate?)}, we expect both generation- and serial-interval distributions to give identical estimates of \RR based on the observed epidemic growth rate $r$.
+In contexts where the distributions are expected to be different, current theory has no explanation for how these differing distributions could provide identical estimates of \RR from $r$. 
 Some studies have further suggested that using serial intervals can give different estimates of \RR \citep{britton2019estimation, ganyani2020estimating}.
 
-Here, we resolve this discrepancy, by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential-growth phase.
+Here, we resolve this discrepancy by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential growth phase  \bmb{?
+how exactly does this resolve the discrepancy?}
 We develop a new framework for understanding serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
@@
 We can further divide these events into \emph{primary} and \emph{secondary} events.
-When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event is the event that always or usually occurs before the secondary event ---
+When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event is the event that usually occurs before the secondary event ---
 most epidemiological events that can be observed within an individual have clear direction (e.g., infection and onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
@@
 
-At the individual level, we can define the expected time distribution between a primary and a secondary event for an average infected individual --- we refer to this distribution as the intrinsic distribution.
+At the individual level, we can define the expected \bmb{I'm not entirely clear what ``expected'' means in this section; it doesn't seem as though this is an expectation in the mathematical sense; what does it mean precisely?
+(I don't think you necessarily have to give the definition, but knowing the precise definition  will help clarify your usage of ``expected'').
+Similarly for ``realized'' \ldots} time distribution between a primary and a secondary event for an average infected individual --- we refer to this distribution as the intrinsic distribution.
 For example, the intrinsic incubation period distribution describes the expected time distribution from infection to symptom onset of an average infected individual.
 Likewise, the intrinsic generation-interval distribution describes the expected time distribution of infectious contacts made by an average infected individual.
-However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., distribution of time between realized primary and secondary events that occur during an epidemic).
+However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., the distribution of time between realized primary and secondary events that occur during an epidemic).
 For example, an infectious contact results in infection only if the contacted individual is susceptible (and has already been infected);
-therefore, the realized generation-interval distribution can be different from the intrinsic generation-interval distribution.
+this is one mechanism that drives differences between the realized and intrinsic generation-interval distributions.
 
@@
 
-There are multiple mechanisms that drive the changes in forward and backward delay distributions over time.
+Multiple \bmb{or ``Several different''} mechanisms drive the changes in forward and backward delay distributions over time.
 Typically, within-individual forward delay distributions are not affected by epidemic dynamics.
@@
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics;
-for example, forward generation intervals contract during the outbreak because infected individuals are less likely to infect others later due to susceptible depletion \citep{champredon2015intrinsic}.
+for example, forward generation intervals contract during the outbreak because infected individuals are less likely to infect others later in  the epidemic due to susceptible depletion \citep{champredon2015intrinsic} \bmb{behavioural change and interventions [i.e.
+anything that drives time-dependent decreases in transmission] also drive this process.
+I know you mention this later in the caveats; do you want to highlight it a little bit more up front since such a large fraction of the decreasing R(t) in COVID-19 could plausibly be driven by processes other than susceptible depletion \emph{per se}?}
 
 \eref{backward} suggests that backward delay distributions change over time even if their corresponding forward delay distribution does not change:
-Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations (i.e., they are measured from a cohort of individuals whose secondary events occurred at the same time).
+Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations (i.e., they are measured from a cohort of individuals whose secondary events occurred at the same time) \bmb{I think this is very important and deserves a few more words to clarify, e.g.
+``i.e., conditioning on individuals whose secondary events have already occurred means that we tend not to observe longer inter-event times, so that the distribution is truncated [censored??]'' (or something like that)?}.
 When the cohort size is increasing (or decreasing) over time, we are biased to observe shorter (or longer) delays when we look backward.
@@
 where $r$ is the exponential growth rate.
-For faster epidemic (higher $r$), the backward delay distributions will be shorter.
-Changes in the backward delay distributions are also affected by the changes in the forward delay distributions by definition (\eref{backward}).
-Therefore, the backward delay distributions will be generally different from the forward delay distributions even if we are measuring time delays that are intrinsic to life history of a disease (e.g., incubation period).
+For faster epidemics (higher $r$), the backward delay distribution will be shorter.
+\bmb{I'm not sure whether ``distribution'' should be singular or plural in general.  Singular reads better to me most of the time, but do whatever you want as long as it's consistent}
+Changes in the backward delay distribution are also by definition affected by the changes in the forward delay distribution (\eref{backward}).
+Therefore, the backward delay distribution will generally differ from the forward delay distribution even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
 These ideas apply to all epidemiological delay distributions and generalize the work by \cite{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively, as well as the work by \cite{britton2019estimation} who showed that \eref{backexp} holds for the backward generation-interval distributions.
@@
 These studies assumed that $x_1$ and $x_2$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, this conclusion is based on the implicit assumption that incubation times, $x_1$ and $x_2$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on disease dynamics) --- something that is true of forward but not backward incubation times.
+however, this conclusion is based on the implicit assumption that incubation times, $x_1$ and $x_2$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on disease \bmb{I think ``epidemic dynamics'' might be better than ``disease dynamics'' generally (search and replace?) --- emphasizes that it's a population-level effect} dynamics) --- something that is true of forward but not backward incubation times.
 We refer to this definition as the intrinsic serial interval (\fref{diagram}A).
@@
 In \fref{diagram}B, we see that $x_1$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\psymp$;
-$\gtime$ follows the forward generation-interval distribution of the cohort of infectors who came infected at time $\psymp - x_1$;
+$\gtime$ follows the forward generation-interval distribution of the cohort of infectors who became infected at time $\psymp - x_1$;
 and $x_2$ follows the forward incubation period distribution of the cohort of infectees who became infected at time $\psymp - x_1 + \gtime$.
 Likewise, we can define the backward serial interval distribution for a cohort of infectees who became symptomatic at time $\ssymp$ (\fref{diagram}C).
-This conceptual framework clearly demonstrates that the distributions of $x_1$, $\gtime$, and $x_2$ (and therefore the distributions of realized serial intervals) depend on the reference cohort and the corresponding cohort time.
+This conceptual framework clearly demonstrates that the distributions of $x_1$, $\gtime$, and $x_2$ (and therefore the distributions of realized serial intervals) depend on the reference cohort and the corresponding cohort time \bmb{have you defined what ``cohort time'' means?}.
 
 To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total number of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
-The number of serial intervals between time $\psymp$ and $\ssymp$, given that the infectors became infected at time $\pinf$ and the infectees became infected at time $\sinf$, depends on the amount of infection that occur between time $\pinf$ and $\sinf$ as well as the densities of forward incubation periods between $\pinf$ and $\psymp$ (realized incubation periods of infectors) as well as $\sinf$ and $\ssymp$ (realized incubation periods of infectees):
+The number of serial intervals between time $\psymp$ and $\ssymp$, given that the infectors became infected at time $\pinf$ and the infectees became infected at time $\sinf$, depends on the amount of infection that occurs between time $\pinf$ and $\sinf$ as well as the density of forward incubation periods between $\pinf$ and $\psymp$ (realized incubation periods of infectors) and between $\sinf$ and $\ssymp$ (realized incubation periods of infectees):
 \begin{equation}
@@
 where the case reproduction number $\Rc (\pinf)$ is defined as the average number of secondary cases caused by a primary case infected at time $\pinf$ over the course of their infection \citep{fraser2007estimating}.
-We note that it is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
+We note that \bmb{I always delete this if possible: maybe needed here though?} it is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
 for example, if an infected individual can only transmit the disease after symptom onset, the forward generation interval will necessarily be longer than the forward incubation period.
@@
 \end{equation}
-This framework allows us to understand changes in the realized serial intervals for any deterministic epidemic models.
+This framework allows us to understand changes in the realized serial intervals for any deterministic epidemic model.
 
@@
 \end{equation}
-We further assume that the forward incubation period distributions does not vary across cohorts over the course of an epidemic, as they represent the life history of a disease, and use $\idist$ without subscript instead.
+We further assume that the forward incubation period distribution does not vary across cohorts over the course of an epidemic, as it represents the life history of a disease; we denote it as $\idist$ (without subscript).
+\bmb{do we need ``without subscript''?}
 Then, we have:
@@
 The forward and backward serial-interval distributions are then calculated by substituting these quantities into \eref{fserial} and \eref{bserial}.
-We use this framework to illustrate how the realized epidemiological time distributions vary over the course of an epidemic and depend on the perspective.
+We use this framework to illustrate how the realized epidemiological time distributions vary over the course of an epidemic and depend on the perspective (i.e., forward vs. backward).
 
@@
 For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short (\eref{backexp}), and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation- and serial-interval distributions.
-The Susceptible-Exposed-Infected-Recovered model, with an additional assumption that incubation and exposed periods are equivalent, provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector (see Supplementary Materials).
+The Susceptible-Exposed-Infected-Recovered model, under the additional assumption that the incubation and exposed periods are equivalent (i.e.
+that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector (see Supplementary Materials).
 
@@
   \textbf{Parameter values used for simulations.}
+  \bmb{note that these are chosen to be characteristic of COVID19 (sort of obvious, but most of the paper so far has been general), to illustrate realistic magnitudes of time-varying/perspective effects in the current pandemic?}
 The intrinsic generation-interval distribution is parameterized using a log-normal distribution with log mean $\mu_G=1.54$ and log standard deviation $\sigma_G=0.37$.
@@
 
-Comparing the shapes of initial forward serial-interval distributions (\eref{initialSI}) and the intrinsic generation-interval distribution allows us to better understand how different forward distributions lead to identical estimates of \Ro.
-In general, distributions with higher means and less variability give higher \Ro for a given $r$ \citep{wallinga2007generation, weitz2015modeling, park2019practical}.
+Comparing the shapes of the initial forward serial-interval distribution (\eref{initialSI}) and the intrinsic generation-interval distribution allows us to better understand how different forward distributions lead to identical estimates of \Ro.
+In general, distributions with higher means and less variability lead to higher \Ro for a given $r$ \citep{wallinga2007generation, weitz2015modeling, park2019practical}.
 When incidence is growing exponentially, forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
-The effects of higher means (which increases \Ro) exactly cancel those of higher variability (which decreases \Ro).
+The effects of higher means (which increase \Ro) exactly cancel those of higher variability (which decrease \Ro).
 On the other hand, \emph{intrinsic} serial intervals (\eref{intrinsicSI}) have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are wider (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
@@
 See Table 1 for parameter values.
+\bmb{I added 50\% quantiles to one of the plots.  You can decide whether you think it's too ugly OR extend it to the other plots\ldots}
 }
@@
 The initial forward serial interval distribution captures the exponential growth phase of an epidemic.
-Next, we characterize how forward and backward serial intervals vary over the course of an epidemic by running deterministic as well as stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
+Next, we characterize how forward and backward serial intervals vary over the course of an epidemic by running deterministic and stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
 we further assume $\Ro=2.5$.
-While the forward serial-interval distribution is our primary focus, understanding the differences between the forward and the backward distributions are important because the observed intervals during on ongoing epidemic are often the backward ones:
-we typically identify infected individuals and ask when they were infected by whom.
-Similarly, when we are estimating the incubation period of an individual, we often observe their symptom onset date of infected individuals and try to estimate when they were infected (e.g., \cite{backer2020incubation}).
+While the forward serial-interval distribution is our primary focus, understanding the differences between the forward and the backward distributions is important because the observed intervals during an ongoing epidemic are often the backward ones:
+we typically identify infected individuals and ask when and by whom they were infected.
+Similarly, when we are estimating the incubation period of an individual, we typically observe their symptom onset date and try to estimate when they were infected (e.g., \cite{backer2020incubation}).
 
-\fref{epi} compares the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
+\fref{epi} juxtaposes \bmb{too fancy?
+technically we're not ``comparing'' the epi dynamics to the intervals (we're comparing the forward and backward intervals)} the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
 The mean forward incubation period remains constant throughout an epidemic as assumed (\fref{epi}B).
-The mean forward generation interval decreases slightly as incidence rate increases, causing the proportion of susceptible population to decrease (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
+The mean forward generation interval decreases slightly as incidence rate \bmb{``incidence'' or ``incidence rate''?} increases, causing the proportion of susceptible population to decrease (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
 In contrast, the mean forward serial interval decreases over time (\fref{epi}D).
 
-The forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation period distributions, (ii) the forward generation-interval distributions, and (iii) the forward incubation period distributions.
+The forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation period, \bmb{I deleted ``distributions'' in this sentence; seems to read better without hurting the meaning?
+could also do that for the next few sentences if appropriate} (ii) the forward generation interval, and (iii) the forward incubation period.
 For COVID-19 parameters (Table 1), both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
@@
 However, researchers typically use all available information to estimate epidemiological parameters;
-in particular, \citep{thompson2019improved} recently suggested that up-to-date serial interval data is necessary to accurately estimate the reproduction number.
-We explore the consequences of neglecting changes in the realized serial interval distributions on estimates of the basic reproduction number.
+in particular, \cite{thompson2019improved} recently suggested that up-to-date serial interval data is \bmb{is? are? https://xkcd.com/1429/} necessary to accurately estimate the reproduction number.
+We explore the consequences of neglecting changes in the realized serial interval distribution on estimates of the basic reproduction number.
 
@@
 Solid lines represent the estimated locally estimated scatterplot smoothing (LOESS) fits.
-The dashed line represents the maximum and minimum observable delays across the range of .
+The dashed line represents the maximum and minimum observable delays across the range of \bmb{???}.
 (C) Cohort-averaged estimates of \Ro assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
@@
 The data were taken from Supplementary Materials of \cite{du2020serial}.
+\bmb{I think this would be slightly more readable if you nudged the min/max labels up slightly so they were clear of the dashed lines}
 }
@@
 \fref{du}A shows that the mean forward serial interval decreases over time.
-While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and \emph{maximum observable} serial intervals), increase in the proportion of negative serial intervals are clearly indicative of the changes in the forward serial-interval distribution;
-increase in the proportion of negative serial intervals is unlikely to be driven by the left-censoring (indicated by the ``farness'' between the quantiles of the observed serial intervals and \emph{minimum observable} serial intervals).
-The decrease in the mean forward serial interval was likely to be caused by increase in the mean backward incubation periods, reflecting decrease in COVID-19 cases in China, as well as intervention efforts which reduce generation intervals by preventing infections once cases are identified.
-\fref{du}B shows that the mean backward serial interval increases over time, also reflecting decrease in COVID-19 cases in China.
+While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and \emph{maximum observable} \bmb{drop italics?} serial intervals), the increase in the proportion of negative serial intervals clearly indicates changes in the forward serial-interval distribution;
+the increase in the proportion of negative serial intervals is unlikely to be driven by left-censoring (indicated by the distance between the quantiles of the observed serial intervals and \emph{minimum observable} serial intervals).
+The decrease in the mean forward serial interval was probably caused by increase in the mean backward incubation period, reflecting decrease in COVID-19 cases in China, as well as intervention efforts which reduced generation intervals by preventing infections once cases were identified.
+\fref{du}B shows that the mean backward serial interval increased over time, also reflecting decrease in COVID-19 cases in China.
+\bmb{careful about tense consistency}
 
 While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculate earlier based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
-These results indicate that previous estimates of incubation period and generation-intervals (Table 1) may have been underestimated as neither study explicitly accounts for the fact that the observed distributions are like backward distributions.
+These results indicate that the incubation period and generation interval (Table 1) may previously have been underestimated as neither study explicitly accounts \bmb{accounted?} for the fact that the observed distributions are like \bmb{?delete ``like''?} backward distributions.
 
@@
 In general, the forward serial-interval distributions will not match the intrinsic or the backward serial-interval distributions.
-Further, the mean forward serial interval can decrease over time due to disease dynamics. 
+Further, the mean forward serial interval can decrease over time due to disease \bmb{epidemic? see previous note} dynamics. 
 Failing to account for these differences can result in underestimation of \RR.
@@
 Our study underlines the importance of carefully defining measured epidemiological time distributions.
-Previous studies have shown that generation interval can be either measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
+Previous studies have shown that generation interval can be measured either forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
 we generalize these ideas and show that they apply to other epidemiological distributions.
-Changes in the backward delay distributions due to changing cohort sizes is expected to be a pervasive feature of outbreak dynamics.
+Changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
 Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series of symptomatic cases or infected cases from the reports of confirmed cases by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential, shim2020transmission});
 these studies effectively assume constant backward delay distributions.
-Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using dynamical approaches that model incidence as well as reporting delays explicitly (e.g., \citep{flaxman2020estimating}).
+Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using dynamical approaches that model incidence as well as reporting delays explicitly (e.g., \cite{flaxman2020estimating}).
 
@@
 However, our study demonstrates that early serial interval data is required to estimate the initial \RR during the exponential growth phase and that using up-to-date serial interval data (without accounting for changes in the forward serial-interval distribution) can, in fact, underestimate the initial \RR.
-Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase and potentially re-asses existing estimates of \RR.
+Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase and potentially re-assess existing estimates of \RR.
 
@@
 these studies should also re-assess whether they appropriately considered the \emph{forward} serial interval.
-Given large geographical variation in the spread of the COVID-19, the forward serial interval distributions are also likely to vary across different countries.
+Given large geographical variation in the spread of the COVID-19, the forward serial interval distributions are also likely to vary across countries.
 We suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions and understand their changes over time.
@@
 Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the dynamical differences between the realized incubation periods of infectors (backward-looking) and those of infectees (forward looking) (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
-There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.
+Better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals are needed \bmb{usually avoid the passive voice, but here I think it works better}.
 
-Our study is not without limitations.
-We assumed that all individuals develop symptoms and that the the entire transmission process, including all relevant epidemiological delays, are known exactly.
+Our study has some limitations.
+We assumed that all individuals develop symptoms and that the the entire transmission process, including all relevant epidemiological delays, is known exactly.
 In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.
@@
 Furthermore, serial intervals do not take into account asymptomatic transmission; 
-not explicitly accounting for asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
+neglecting asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
 
@@
 Individual-level interventions, such as case isolation, directly affect individuals' ability to transmit and will shorten the forward generation- and serial-intervals.
-Population-level interventions, such as social distancing, can squeeze contacts into household and introduce high degree of clustering, which, in turn, will shorten the realized generation intervals due to local depletion of the susceptible pool within households \citep{park2019inferring}.
+\bmb{Do you want to mention/remind here that individual-level behavioural changes can either reduce transmission (like susceptible depletion) or shorten generation intervals?}
+Population-level interventions, such as social distancing, can squeeze contacts into household and induce clustering, which will in turn shorten the realized generation interval due to local depletion of the susceptible pool within households \citep{park2019inferring}.
 
-Despite these limitations, our analysis of serial intervals of COVID-19 from China provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of \RR.
-To our knowledge, most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
+Despite these limitations, our analysis of serial intervals of COVID-19 from China provides further support for our theoretical framework, demonstrating temporal variation in serial intervals and its effect on the estimates of \RR.
+Most \bmb{I don't think you need ``to our knowledge'' if you're going to hedge with ``most''} existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
 Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \RR, of the COVID-19 pandemic.
+\bmb{a little awkward; could probably move ``of the COVID-19 pandemic'' before the first comma}
 
@@
 \end{equation}
-We compare this with an estimate of \Ro based on the intrinsic serial-interval distribution which has the same mean as the intrinsic geeneration-interval distribution \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
+We compare this with an estimate of \Ro based on the intrinsic serial-interval distribution which has the same mean as the intrinsic generation-interval distribution \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
 \begin{equation}

### 2020-05-25 forward.R

@@ -9,6 +9,8 @@ load("sir_sim.rda")
 
 rr <- renewal_det()
 
+lvl <- 0.5  ## CI ribbon
+
 summfun <- function(dd) {
   dd %>%
     filter(!is.na(cohort), !is.na(tdiff), cohort > 0, cohort <= 100) %>%
@@ -17,7 +19,9 @@ summfun <- function(dd) {
     ) %>%
     group_by(cc) %>%
     summarize(
-      mean=mean(tdiff)
+        mean=mean(tdiff),
+        lwr=quantile(tdiff,(1-lvl)/2),
+        upr = quantile(tdiff,(1+lvl)/2)
     ) %>%
     ungroup %>%
     mutate(
@@ -95,10 +99,11 @@ incdet <- data.frame(
 
 g2 <- ggplot(incdata0) +
   geom_line(data=incdet, aes(tvec, mf), lwd=1) +
-  geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
+    geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
+    geom_ribbon(aes(cc, ymin=lwr, ymax=upr), colour=NA, fill="#D55E00", alpha=0.2) +
   geom_hline(yintercept=incdet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7)) +
+  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7), oob=scales::squish) +
   scale_fill_gradientn(colors=c("white", "black")) +
   ggtitle("B. Incubation period") +
   theme(

### 2020-05-26 serial.tex
'the the' --> 'the'

@@
 time $\ssymp$ [$f_{\ssymp-\tau}(\tau)$]. In general, Eq.~\eqref{eq:backward}
-shows that the the backward delay distribution at reference time $\ssymp$
+shows that the backward delay distribution at reference time $\ssymp$
 [$b_\ssymp(\tau)$] depends not only on the secondary cohort size at time
@@
 Our study has some limitations.
-We assumed that all individuals develop symptoms and that the the entire transmission process, including all relevant epidemiological delays, is known exactly.
+We assumed that all individuals develop symptoms and that the entire transmission process, including all relevant epidemiological delays, is known exactly.
 In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.
@@
 \end{equation}
-where $h$ is the joint probability distribution describing the the intrinsic generation-interval distribution $g$ and the intrinsic incubation period distribution $\idist$ (see \eref{marginal} in the main text).
+where $h$ is the joint probability distribution describing the intrinsic generation-interval distribution $g$ and the intrinsic incubation period distribution $\idist$ (see \eref{marginal} in the main text).
 For brevity, we denote the constant of proportionality using $\phi$ such that

### 2020-05-26 serial.tex
comment on eq (3)

@@
 \end{equation}
+\djde{I do not find it helpful to write $\propto$.
+It would be clearer to write it out exactly with the part that doesn't depend on $\tau$ in $[]$.
+Then you can follow with ``where $r$ is the exponential growth rate and the expression in square brackets is a constant since it does not depend on $\tau$.''  I think it is helpful to see what the constant is and not make the reader think it through.
+Alternatively, you could write the equality and then have your $\propto$ and then say afterwards that we write $\propto$ for convenience since the expression in $[]$ is constant wrt $\tau$.}
 where $r$ is the exponential growth rate.

### 2020-05-27 serial.tex
various comments up to Results

@@
 For faster epidemics (higher $r$), the backward delay distribution will be shorter.
+\djde{Is it correct to refer to the distribution as ``shorter''?  I
+  believe you mean squashed towards 0.  I'm blanking on the right phrase.}
 \bmb{I'm not sure whether ``distribution'' should be singular or plural in general.  Singular reads better to me most of the time, but do whatever you want as long as it's consistent}
@@
 \end{equation}
-where $x_1$ and $x_2$ represent incubation periods of an infector and an infectee, respectively, and $\gtime$ represents the generation interval.
-These studies assumed that $x_1$ and $x_2$ follow the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, this conclusion is based on the implicit assumption that incubation times, $x_1$ and $x_2$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on disease \bmb{I think ``epidemic dynamics'' might be better than ``disease dynamics'' generally (search and replace?) --- emphasizes that it's a population-level effect} dynamics) --- something that is true of forward but not backward incubation times.
-We refer to this definition as the intrinsic serial interval (\fref{diagram}A).
+where $x_1$ and $x_2$ represent incubation periods of an infector and
+an infectee, respectively, and $\gtime$ represents the generation
+interval.  These studies assumed that $x_1$ and $x_2$ follow the same
+distributions and concluded that the serial and generation intervals
+have the same mean
+\citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence,
+  britton2019estimation}; however, this conclusion is based on the
+implicit assumption that incubation times, $x_1$ and $x_2$, as well as
+generation interval, $\gtime$, are intrinsic to individuals (and not
+dependent on disease \bmb{I think ``epidemic dynamics'' might be
+  better than ``disease dynamics'' generally (search and replace?) ---
+  emphasizes that it's a population-level effect} dynamics) ---
+something that is true of forward but not backward \djde{distribution
+  of} incubation times.  \djde{Above is confusing and my suggested
+  change doesn't fix it.  Incubation times \underline{are} associated
+  with individuals.  It is the distributions that are
+  cohort-dependent.}  We refer to this definition as the intrinsic
+serial interval (\fref{diagram}A).
 
@@
 \includegraphics[width=\textwidth]{serial_guide.pdf}
-\caption{
-\textbf{Illustration of intrinsic, forward and backward serial intervals.}
-(A) The intrinsic serial interval for a cohort of individuals infected at time $\psymp$.
-In this case, $x_1$ follows the intrinsic incubation period distribution;
-$\gtime$ follows the intrinsic generation-interval distribution;
-and $x_2$ follows the intrinsic incubation period distribution.
-(B) The forward serial interval for a cohort of infectors who became symptomatic at time $\psymp$.
-In this case, $x_1$ follows the backward incubation period distribution;
-$\gtime$ follows the forward generation-interval distribution;
-and $x_2$ follows the forward incubation period distribution.
-(C) The backward serial interval for a cohort of infectees who became symptomatic at time $\ssymp$.
-In this case, $x_1$ follows the forward incubation period distribution;
-$\gtime$ follows the backward generation-interval distribution;
-and $x_2$ follows the backward incubation period distribution.
-}
+\caption{ \djde{I think this graph could be improved using colour.  In
+    particular, how about using a red-filled rather than white-filled
+    dot for the reference cohort, and using red text for the words
+    ``Reference cohort'' everywhere.  I would also put symbols in the
+    annotation of the intervals.  For example: ``Intrinsic generation
+    interval $\sigma$'' and ``Intrinsic serial interal
+    $\sigma+x_2-x_1$'' (though use $\tau_{\rm g}$ etc.
+    as discussed by e-mail).}  \textbf{Illustration of intrinsic,
+    forward and backward serial intervals.}  (A) The intrinsic serial
+  interval for a cohort of individuals infected at time $\psymp$.  In
+  this case, $x_1$ follows the intrinsic incubation period
+  distribution; $\gtime$ follows the intrinsic generation-interval
+  distribution; and $x_2$ follows the intrinsic incubation period
+  distribution.  (B) The forward serial interval for a cohort of
+  infectors who became symptomatic at time $\psymp$.  In this case,
+  $x_1$ follows the backward incubation period distribution; $\gtime$
+  follows the forward generation-interval distribution; and $x_2$
+  follows the forward incubation period distribution.  (C) The
+  backward serial interval for a cohort of infectees who became
+  symptomatic at time $\ssymp$.  In this case, $x_1$ follows the
+  forward incubation period distribution; $\gtime$ follows the
+  backward generation-interval distribution; and $x_2$ follows the
+  backward incubation period distribution.  }
 \label{fig:diagram}
@@
 
-To correctly link realized serial intervals to the renewal process between cases based on symptom onset dates, we must use the forward serial interval (i.e., use the perspective of a cohort of infectors that share the same symptom onset time).
-Given that an infector became symptomatic at time $\psymp$, to calculate the forward serial interval we first go backward in time by asking when the infector was infected, and then go forward in time by asking first when the infectee was infected and then when they became symptomatic.
-In \fref{diagram}B, we see that $x_1$ follows the backward incubation period distribution of the cohort of infectors who became symptomatic at time $\psymp$;
-$\gtime$ follows the forward generation-interval distribution of the cohort of infectors who became infected at time $\psymp - x_1$;
-and $x_2$ follows the forward incubation period distribution of the cohort of infectees who became infected at time $\psymp - x_1 + \gtime$.
-Likewise, we can define the backward serial interval distribution for a cohort of infectees who became symptomatic at time $\ssymp$ (\fref{diagram}C).
-This conceptual framework clearly demonstrates that the distributions of $x_1$, $\gtime$, and $x_2$ (and therefore the distributions of realized serial intervals) depend on the reference cohort and the corresponding cohort time \bmb{have you defined what ``cohort time'' means?}.
+To correctly link realized serial intervals to the renewal process
+between cases based on symptom onset dates, we must use the forward
+serial interval (i.e., use the perspective of a cohort of infectors
+that share the same symptom onset time).  Given that an infector
+became symptomatic at time $\psymp$, to calculate the forward serial
+interval we first go backward in time to when the infector was
+infected, and then forward in time to when the infectee was infected,
+and then forward to when they became symptomatic.\djde{I altered that
+  sentence} In \fref{diagram}B, we see that $x_1$ follows\djde{I think
+  ``is drawn from'' would be better than ``follows'' each time in this
+  sentence} the backward incubation period distribution of the cohort
+of infectors who became symptomatic at time $\psymp$; $\gtime$ follows
+the forward generation-interval distribution of the cohort of
+infectors who became infected at time $\psymp - x_1$; and $x_2$
+follows the forward incubation period distribution of the cohort of
+infectees who became infected at time $\psymp - x_1 + \gtime$.
+Likewise, we can define the backward serial interval distribution for
+a cohort of infectees who became symptomatic at time $\ssymp$
+(\fref{diagram}C).  This conceptual framework \djde{delete
+  ``clearly''; try to expunge this from your vocabulary; why insult
+  somebody for whom it isn't clear?} demonstrates
+that the distributions of $x_1$, $\gtime$, and $x_2$ (and therefore
+the distributions of realized serial intervals) depend on the
+reference cohort and the corresponding cohort time \bmb{have you
+  defined what ``cohort time'' means?}.  \djde{``reference time''
+  might be better.  How about saying ``reference cohort, which is
+  defined by an event type, temporal direction, and a particular
+  reference time''.}
 
 To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total number of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
-The number of serial intervals between time $\psymp$ and $\ssymp$, given that the infectors became infected at time $\pinf$ and the infectees became infected at time $\sinf$, depends on the amount of infection that occurs between time $\pinf$ and $\sinf$ as well as the density of forward incubation periods between $\pinf$ and $\psymp$ (realized incubation periods of infectors) and between $\sinf$ and $\ssymp$ (realized incubation periods of infectees):
+The number of serial intervals between time $\psymp$ and $\ssymp$,
+given that the infectors became infected at time $\pinf\le\psymp$ and
+the infectees became infected at time $\sinf\le\ssymp$, depends on the
+amount of infection that occurs between time $\pinf$ and $\sinf$ as
+well as the density of forward incubation periods between $\pinf$ and
+$\psymp$ (realized incubation periods of infectors) and between
+$\sinf$ and $\ssymp$ (realized incubation periods of infectees):
+\djde{why not use $t$ instead of $\alpha$?}
 \begin{equation}
@@
 
+\djde{The term ``total number'' of serial intervals is very peculiar,
+  because there are infinitely many.  It is more like a cumulative
+  distribution.  I'm not sure what the best jargon is.}
+
 The total number of serial intervals can now be obtained by integrating over all possible infection times for the infector and the infectee:
@@
 \end{equation}
+\djde{Don't leave out the limits of integration.  Ambiguity isn't
+  helpful to anyone.  This stuff is hard.  Be as precise as possible.}
 Likewise, the backward serial-interval distribution $b_\ssymp(\tau)$ is given by the density of intervals of length $\tau$ ending at \ssymp, relative to the total number of serial intervals ending at \ssymp:
@@
 \end{equation}
+\djde{I don't like $\propto$.  It is always clearer to state the
+  constant of proportionality.}
 which allows us to separate the joint probability distribution $h_\psymp$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
@@
 \end{equation}
-We further assume that the forward incubation period distribution does not vary across cohorts over the course of an epidemic, as it represents the life history of a disease; we denote it as $\idist$ (without subscript).
-\bmb{do we need ``without subscript''?}
+We further assume that the forward incubation period distribution does
+not vary across cohorts over the course of an epidemic, as it
+represents the life history of a disease; we denote it as $\idist$
+(without subscript). \bmb{do we need ``without subscript''?}
+\djde{perhaps ``without the subscript used in (5)''}
 Then, we have:
@@
 \end{equation}
-Instead of numerically integrating over closed forms of $g$, $f_0$, and $q$ to estimate $\Ro$, we use simulation-based approaches for simplicity (Supplementary Materials).
+Rather than numerically integrating over closed forms of $g$, $f_0$, and $q$ to estimate $\Ro$, we use simulation-based approaches for simplicity (Supplementary Materials).
 

### 2020-05-27 serial.tex
in the middle of the proof; calling it a night

@@
 \textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
-(A). The initial forward serial-interval distributions give a correct link between the exponential growth rate $r$ and the reproduction number \Ro.
+(A). The initial forward serial-interval distributions give a correct
+link between the exponential growth rate $r$ and the reproduction
+number \Ro,
+for any correlation $\rho$ between intrinsic incubation period and
+intrinsic generation interval.\djde{added definition of $\rho$ for the
+benefit of the many readers who will just poke through figures.}
 (B) The intrinsic serial-interval distributions give an incorrect link between $r$ and \Ro.
@@
 
-\fref{epi} juxtaposes \bmb{too fancy?
-technically we're not ``comparing'' the epi dynamics to the intervals (we're comparing the forward and backward intervals)} the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
+\fref{epi} juxtaposes \bmb{too fancy? technically we're not
+  ``comparing'' the epi dynamics to the intervals (we're comparing the
+  forward and backward intervals)}\djde{how about ``shows'' and then
+  say ``(A) together with'' rather than ``(A) with'' } the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
 The mean forward incubation period remains constant throughout an epidemic as assumed (\fref{epi}B).
@@
 
-The forward serial interval distributions depend on three intervals (\fref{diagram}): (i) the backward incubation period, \bmb{I deleted ``distributions'' in this sentence; seems to read better without hurting the meaning?
-could also do that for the next few sentences if appropriate} (ii) the forward generation interval, and (iii) the forward incubation period.
+The forward serial interval distributions depend on \djde{adding these
+two words so Ben's deletions are a little more palatable to me (but I
+don't like it because it goes back to talking about forward and
+backward periods rather than forward and backward distributions; I
+would go back to being precise):}distributions of three intervals
+(\fref{diagram}): (i) the backward incubation period, \bmb{I deleted
+  ``distributions'' in this sentence; seems to read better without
+  hurting the meaning? could also do that for the next few sentences
+  if appropriate} (ii) the forward generation interval, and (iii) the forward incubation period.
 For COVID-19 parameters (Table 1), both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
@@
 \fref{du}A shows that the mean forward serial interval decreases over time.
-While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and \emph{maximum observable} \bmb{drop italics?} serial intervals), the increase in the proportion of negative serial intervals clearly indicates changes in the forward serial-interval distribution;
+While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and \emph{maximum observable} \bmb{drop italics?} serial intervals), the increase in the proportion of negative serial intervals clearly\djde{unequivocally?} indicates changes in the forward serial-interval distribution;
 the increase in the proportion of negative serial intervals is unlikely to be driven by left-censoring (indicated by the distance between the quantiles of the observed serial intervals and \emph{minimum observable} serial intervals).
@@
 These early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
-Therefore, \Ro estimate of 1.32 (95\% CI 1.16–1.48), which neglects the changes in the forward serial-interval distribution, is likely to be an underestimate.
+Therefore, the \Ro estimate of 1.32 (95\% CI 1.16–1.48), which neglects the changes in the forward serial-interval distribution, is likely to be an underestimate.
 This example demonstrates the danger of using the observed serial intervals to calculate the reproduction number without integrating serial intervals into cohorts.
@@
 Our study underlines the importance of carefully defining measured epidemiological time distributions.
-Previous studies have shown that generation interval can be measured either forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
+\djde{altered the following sentence}
+Previous studies have shown that it matters whether generation
+intervals are measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
 we generalize these ideas and show that they apply to other epidemiological distributions.
@@
 We suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions and understand their changes over time.
-These modeling approaches should be necessarily coupled with intensive epidemiological investigation through contact tracing at the very beginning of the outbreak in order to characterize the initial forward serial-interval distribution, particularly for an emerging epidemic such as COVID-19.
+These modeling approaches should be necessarily coupled with intensive
+epidemiological investigation through contact tracing at the very
+beginning of the outbreak in order to characterize the initial forward
+serial-interval distribution, particularly for an epidemic of an
+emerging disease such as COVID-19.
 
@@
 Most \bmb{I don't think you need ``to our knowledge'' if you're going to hedge with ``most''} existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
-Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \RR, of the COVID-19 pandemic.
-\bmb{a little awkward; could probably move ``of the COVID-19 pandemic'' before the first comma}
+Our study provides a rationale for reassessing estimates of
+serial-interval distributions---and their use in estimating
+\RR---during the COVID-19 pandemic. \bmb{a little awkward; could
+  probably move ``of the COVID-19 pandemic'' before the first
+  comma}\djde{I used --- instead of commas and replaced ``of'' with
+  ``during'', which I think fixes the problem.}
 
@@
 where $C$ is chosen such that $\sum_{n=1}^{\tsub{m}{max}} i(m \Delta t)=10$.
-These initial conditions allow the model to follow exponentially growth from time $\Delta t (\tsub{m}{max} + 1)$ without any transient behaviors.
+These initial conditions allow the model to follow exponential growth from time $\Delta t (\tsub{m}{max} + 1)$ without any transient behaviors.
 Results presented in the main text show simulations beginning from time $\Delta t (\tsub{m}{max} + 1)$.
@@
 \begin{equation}
-f_{0}(\tau) = \frac{\int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1}{\int_{-\infty}^\infty \int_{-\infty}^{0} \int_{\alpha_1}^{\tau'} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1 \dtau'},
+f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1\,,
 \label{eq:fdist}
 \end{equation}
-where $h$ is the joint probability distribution describing the intrinsic generation-interval distribution $g$ and the intrinsic incubation period distribution $\idist$ (see \eref{marginal} in the main text).
-For brevity, we denote the constant of proportionality using $\phi$ such that
-\begin{equation}
-f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1\,.
-\end{equation}
+where $h$ is the joint probability distribution describing the
+intrinsic generation-interval distribution $g$ and the intrinsic
+incubation period distribution $\idist$ (see \eref{marginal} in the
+main text), and the normalization constant $\phi$ is determined by the
+requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
+\djde{a bit of tidying there}
 
@@
 \end{equation}
-We substitute $z(\sinf)$ into \eref{newforward} to obtain:
+Substituting $z(\sinf)$ into \eref{newforward} we obtain:
 \begin{equation}
@@
 \end{equation}
-By normalizing $z(\sinf)$ such that $\hat{z}(\sinf) = z(\sinf)/\left[\int_{-\infty}^\infty z(x) \dx\right]$,
-we can now express the initial forward serial-interval distribution $f_0$ as a convolution of $\hat{z}$ and $\idist$:
+Writing $\hat{z}$ for a normalized version of $z$,
+\begin{equation}\hat{z}(\sinf) = \frac{z(\sinf)}{\int_{-\infty}^\infty z(x) \dx}\,,\end{equation}
+we can now express the initial forward serial-interval distribution
+$f_0$ as a convolution of $\hat{z}$ and $\idist$:\djde{I think you
+  meant to remove $\phi$ below, but $\phi$ is not identical to $\int
+  z$; I'm missing something}
 \begin{equation}
@@
 \end{equation}
-Since the right hand side of \eref{ptarget} is also a moment-generating function of $f_0$, we can express it as the product of the moment-generation functions of $\hat{z}$ and $\idist$:
+Since the right hand side of \eref{ptarget} is also a
+moment-generating function of $f_0$, we can express it as the product
+of the moment-generation functions of $\hat{z}$ and $\idist$:
+\djde{That didn't make sense to me, probably just not quite what you
+  meant to say.  To me, it would be much simpler just to say that
+  you're taking Laplace transforms of $f_0=\hat{z}*\idist$.}
 \begin{equation}
@@
 \end{align}
-Therefore, the initial forward serial-interval distribution and the intrinsic generation-interval distribution give the same estimates of \Ro from $r$.
+Therefore, the initial forward serial-interval distribution and the intrinsic generation-interval distribution give the same estimates of \Ro from $r$.\qed
 

### 2020-05-28 serial.tex
done

@@
 
-\newcommand{\gtime}{\sigma} %% generation interval
+\newcommand{\gtime}{\tau_{\rm g}} %% generation interval
 \newcommand{\gdist}{g} %% generation-interval distribution
@@
 Kaiyuan Sun\textsuperscript{2}
-Benjamin M.\ Bolker\textsuperscript{3,4,5}
-David Champredon\textsuperscript{6}
-David J.\,D.\ Earn\textsuperscript{4,5}
-Michael Li\textsuperscript{3}
+David Champredon\textsuperscript{3}
+Michael Li\textsuperscript{4}
+Benjamin M.\ Bolker\textsuperscript{4,5,6}
+David J.\,D.\ Earn\textsuperscript{5,6}
 Joshua S.\ Weitz\textsuperscript{7, 8}
 Bryan T.\ Grenfell\textsuperscript{1,2,9}
-Jonathan Dushoff\textsuperscript{3,4,5}
+Jonathan Dushoff\textsuperscript{4,5,6}
 \\
@@
 \\
-\textbf{3} Department of Biology, McMaster University, Hamilton, ON, Canada
+\textbf{3} Department of Pathology and Laboratory Medicine, University of Western Ontario, London, Ontario, Canada
 \\
-\textbf{4} Department of Mathematics and Statistics, McMaster University, Hamilton, ON, Canada
+\textbf{4} Department of Biology, McMaster University, Hamilton, ON, Canada
 \\
-\textbf{5} M.\,G.\,DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, ON, Canada
+\textbf{5} Department of Mathematics and Statistics, McMaster University, Hamilton, ON, Canada
 \\
-\textbf{6} Department of Pathology and Laboratory Medicine, University of Western Ontario, London, Ontario, Canada
+\textbf{6} M.\,G.\,DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, ON, Canada
 \\
@@
 
-\bmb{the next two paragraphs are much improved but they might be able to be improved still further by making the logical as explicit as possible (see ?
-below for points where I think the connections are not absolutely clear)}
 One source of confusion arises from an apparent discrepancy between biological intuition and mathematical theory.
-When the epidemic is growing exponentially, the spread of infection can be characterized as a ``renewal process'' \bmb{quotes or italic?} based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
+When the epidemic is growing exponentially, the spread of infection can be characterized as a \emph{renewal process} based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
 This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
 By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates;
-therefore \bmb{why?
-(because both are renewal processes describing the same underlying system, where all components must be growing at the same rate?)}, we expect both generation- and serial-interval distributions to give identical estimates of \RR based on the observed epidemic growth rate $r$.
+since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system, where all components must be growing at the same rate, we expect both generation- and serial-interval distributions to give identical estimates of \RR based on the observed epidemic growth rate $r$.
 In contexts where the distributions are expected to be different, current theory has no explanation for how these differing distributions could provide identical estimates of \RR from $r$. 
@@
 
-Here, we resolve this discrepancy by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial (but not generation) interval is affected by the rate of growth $r$ during the exponential growth phase  \bmb{?
-how exactly does this resolve the discrepancy?}
+Here, we resolve this discrepancy by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
 We develop a new framework for understanding serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
-Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can significantly bias estimates of \RR.
+Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of \RR.
 We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the reproduction number during the early stages of an outbreak.
@@
 
-At the individual level, we can define the expected \bmb{I'm not entirely clear what ``expected'' means in this section; it doesn't seem as though this is an expectation in the mathematical sense; what does it mean precisely?
-(I don't think you necessarily have to give the definition, but knowing the precise definition  will help clarify your usage of ``expected'').
-Similarly for ``realized'' \ldots} time distribution between a primary and a secondary event for an average infected individual --- we refer to this distribution as the intrinsic distribution.
+At the individual level, we can define the time distribution between a primary and a secondary event that we expect to observe for an average infected individual --- we refer to this distribution as the intrinsic distribution.
 For example, the intrinsic incubation period distribution describes the expected time distribution from infection to symptom onset of an average infected individual.
 Likewise, the intrinsic generation-interval distribution describes the expected time distribution of infectious contacts made by an average infected individual.
-However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., the distribution of time between realized primary and secondary events that occur during an epidemic).
-For example, an infectious contact results in infection only if the contacted individual is susceptible (and has already been infected);
-this is one mechanism that drives differences between the realized and intrinsic generation-interval distributions.
+However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., the distribution of time between actual primary and secondary events that occur during an epidemic).
+For example, an infectious contact results in infection only if the contacted individual is susceptible (and has not already been infected);
+this is one mechanism that distinguishes the realized generation intervals (time between actual infection events) from the intrinsic generation intervals (time between infection and infectious contacts).
 
-At the population level, we model realized time delays between a primary and a secondary event from a cohort perspective.
+At the population level, we model realized time delays between a primary and a secondary event that occurs during an epidemic from a cohort perspective.
 A primary cohort consists of \emph{all} individuals whose primary event occurred at a given time; 
@@
 
-Multiple \bmb{or ``Several different''} mechanisms drive the changes in forward and backward delay distributions over time.
+Several different mechanisms drive the changes in forward and backward delay distributions over time.
 Typically, within-individual forward delay distributions are not affected by epidemic dynamics.
@@
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics;
-for example, forward generation intervals contract during the outbreak because infected individuals are less likely to infect others later in  the epidemic due to susceptible depletion \citep{champredon2015intrinsic} \bmb{behavioural change and interventions [i.e.
-anything that drives time-dependent decreases in transmission] also drive this process.
-I know you mention this later in the caveats; do you want to highlight it a little bit more up front since such a large fraction of the decreasing R(t) in COVID-19 could plausibly be driven by processes other than susceptible depletion \emph{per se}?}
+for example, forward generation intervals contract during the outbreak because infected individuals are less likely to infect others later in the epidemic due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.
 
-\eref{backward} suggests that backward delay distributions change over time even if their corresponding forward delay distribution does not change:
-Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations (i.e., they are measured from a cohort of individuals whose secondary events occurred at the same time) \bmb{I think this is very important and deserves a few more words to clarify, e.g.
-``i.e., conditioning on individuals whose secondary events have already occurred means that we tend not to observe longer inter-event times, so that the distribution is truncated [censored??]'' (or something like that)?}.
-When the cohort size is increasing (or decreasing) over time, we are biased to observe shorter (or longer) delays when we look backward.
+\eref{backward} suggests that backward delay distributions change over time even if their corresponding forward delay distribution does not change.
+Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations:
+Conditioning on individuals whose secondary events have occurred at the same time means that the distribution is truncated so that we tend to observe shorter (or longer) inter-event delays when incidence is  the cohort size has been increasing (or decreasing) over time.
 In particular, when the incidence is growing exponentially, we can calculate the amount of bias exactly.
@@
 \begin{equation}
-b_0(\tau) \propto \exp(-r\tau) f_0(\tau),
+b_0(\tau) = \frac{\exp(-r\tau) f_0(\tau)}{\left[\int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'\right]},
 \label{eq:backexp}
 \end{equation}
-\djde{I do not find it helpful to write $\propto$.
-It would be clearer to write it out exactly with the part that doesn't depend on $\tau$ in $[]$.
-Then you can follow with ``where $r$ is the exponential growth rate and the expression in square brackets is a constant since it does not depend on $\tau$.''  I think it is helpful to see what the constant is and not make the reader think it through.
-Alternatively, you could write the equality and then have your $\propto$ and then say afterwards that we write $\propto$ for convenience since the expression in $[]$ is constant wrt $\tau$.}
-where $r$ is the exponential growth rate.
-For faster epidemics (higher $r$), the backward delay distribution will be shorter.
-\djde{Is it correct to refer to the distribution as ``shorter''?  I
-  believe you mean squashed towards 0.  I'm blanking on the right phrase.}
-\bmb{I'm not sure whether ``distribution'' should be singular or plural in general.  Singular reads better to me most of the time, but do whatever you want as long as it's consistent}
+where $r$ is the exponential growth rate and the expression in square brackets is a constant since it does not depend on $\tau$.
+For faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.
 Changes in the backward delay distribution are also by definition affected by the changes in the forward delay distribution (\eref{backward}).
@@
 The serial interval is defined as the time between when an infector becomes symptomatic and when an infectee becomes symptomatic \citep{svensson2007note}.
-Previous studies have often expressed serial intervals $\tau$ in the form (\fref{diagram}A):
+Previous studies have often expressed serial intervals $\tau_{\rm s}$ in the form (\fref{diagram}A):
 \begin{equation}
-\tau = (\gtime + x_2) - x_1
+\tau_{\rm s} = (\gtime + \tau_{\rm i2}) - \tau_{\rm i1}
 \end{equation}
-where $x_1$ and $x_2$ represent incubation periods of an infector and
+where $\tau_{\rm i1}$ and $\tau_{\rm i2}$ represent incubation periods of an infector and
 an infectee, respectively, and $\gtime$ represents the generation
-interval.  These studies assumed that $x_1$ and $x_2$ follow the same
-distributions and concluded that the serial and generation intervals
-have the same mean
-\citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence,
-  britton2019estimation}; however, this conclusion is based on the
-implicit assumption that incubation times, $x_1$ and $x_2$, as well as
-generation interval, $\gtime$, are intrinsic to individuals (and not
-dependent on disease \bmb{I think ``epidemic dynamics'' might be
-  better than ``disease dynamics'' generally (search and replace?) ---
-  emphasizes that it's a population-level effect} dynamics) ---
-something that is true of forward but not backward \djde{distribution
-  of} incubation times.  \djde{Above is confusing and my suggested
-  change doesn't fix it.  Incubation times \underline{are} associated
-  with individuals.  It is the distributions that are
-  cohort-dependent.}  We refer to this definition as the intrinsic
+interval.  
+These studies assume that $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
+however, this conclusion is based on the implicit assumption that distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
+something that is true of forward but not backward distribution of incubation periods.
+We refer to this definition as the intrinsic
 serial interval (\fref{diagram}A).
@@
 \includegraphics[width=\textwidth]{serial_guide.pdf}
-\caption{ \djde{I think this graph could be improved using colour.  In
-    particular, how about using a red-filled rather than white-filled
-    dot for the reference cohort, and using red text for the words
-    ``Reference cohort'' everywhere.  I would also put symbols in the
-    annotation of the intervals.  For example: ``Intrinsic generation
-    interval $\sigma$'' and ``Intrinsic serial interal
-    $\sigma+x_2-x_1$'' (though use $\tau_{\rm g}$ etc.
-    as discussed by e-mail).}  \textbf{Illustration of intrinsic,
+\caption{\textbf{Illustration of intrinsic,
     forward and backward serial intervals.}  (A) The intrinsic serial
   interval for a cohort of individuals infected at time $\psymp$.  In
-  this case, $x_1$ follows the intrinsic incubation period
-  distribution; $\gtime$ follows the intrinsic generation-interval
-  distribution; and $x_2$ follows the intrinsic incubation period
+  this case, $\tau_{\rm i1}$ is drawn from the intrinsic incubation period
+  distribution; $\gtime$ is drawn from the intrinsic generation-interval
+  distribution; and $\tau_{\rm i2}$ is drawn from the intrinsic incubation period
   distribution.  (B) The forward serial interval for a cohort of
   infectors who became symptomatic at time $\psymp$.  In this case,
-  $x_1$ follows the backward incubation period distribution; $\gtime$
-  follows the forward generation-interval distribution; and $x_2$
-  follows the forward incubation period distribution.  (C) The
+  $\tau_{\rm i1}$ is drawn from the backward incubation period distribution; $\gtime$
+  is drawn from the forward generation-interval distribution; and $\tau_{\rm i2}$
+  is drawn from the forward incubation period distribution.  (C) The
   backward serial interval for a cohort of infectees who became
-  symptomatic at time $\ssymp$.  In this case, $x_1$ follows the
-  forward incubation period distribution; $\gtime$ follows the
-  backward generation-interval distribution; and $x_2$ follows the
-  backward incubation period distribution.  }
+  symptomatic at time $\ssymp$.  In this case, $\tau_{\rm i1}$ is drawn from the
+  forward incubation period distribution; $\gtime$ is drawn from the
+  backward generation-interval distribution; and $\tau_{\rm i2}$ is drawn from the
+  backward incubation period distribution.}
 \label{fig:diagram}
@@
 
-To correctly link realized serial intervals to the renewal process
+To correctly link the realized serial interval distribution to the renewal process
 between cases based on symptom onset dates, we must use the forward
@@
 infected, and then forward in time to when the infectee was infected,
-and then forward to when they became symptomatic.\djde{I altered that
-  sentence} In \fref{diagram}B, we see that $x_1$ follows\djde{I think
-  ``is drawn from'' would be better than ``follows'' each time in this
-  sentence} the backward incubation period distribution of the cohort
-of infectors who became symptomatic at time $\psymp$; $\gtime$ follows
+and then forward to when the infectee became symptomatic.
+In \fref{diagram}B, we see that $\tau_{\rm i1}$ is drawn from
+the backward incubation period distribution of the cohort
+of infectors who became symptomatic at time $\psymp$; $\gtime$ is drawn from
 the forward generation-interval distribution of the cohort of
-infectors who became infected at time $\psymp - x_1$; and $x_2$
-follows the forward incubation period distribution of the cohort of
-infectees who became infected at time $\psymp - x_1 + \gtime$.
+infectors who became infected at time $\psymp - \tau_{\rm i1}$; and $\tau_{\rm i2}$
+is drawn from the forward incubation period distribution of the cohort of
+infectees who became infected at time $\psymp - \tau_{\rm i1} + \gtime$.
 Likewise, we can define the backward serial interval distribution for
 a cohort of infectees who became symptomatic at time $\ssymp$
-(\fref{diagram}C).  This conceptual framework \djde{delete
-  ``clearly''; try to expunge this from your vocabulary; why insult
-  somebody for whom it isn't clear?} demonstrates
-that the distributions of $x_1$, $\gtime$, and $x_2$ (and therefore
+(\fref{diagram}C).  This conceptual framework demonstrates
+that the distributions of $\tau_{\rm i1}$, $\gtime$, and $\tau_{\rm i2}$ (and therefore
 the distributions of realized serial intervals) depend on the
-reference cohort and the corresponding cohort time \bmb{have you
-  defined what ``cohort time'' means?}.  \djde{``reference time''
-  might be better.  How about saying ``reference cohort, which is
-  defined by an event type, temporal direction, and a particular
-  reference time''.}
+reference cohort, which is defined by an event type (primary or secondary),
+temporal direction (forward or backward), and a particular reference time.
 
-To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total number of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
-The number of serial intervals between time $\psymp$ and $\ssymp$,
+To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total amount of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
+The amount of serial intervals between time $\psymp$ and $\ssymp$,
 given that the infectors became infected at time $\pinf\le\psymp$ and
@@
 $\sinf$ and $\ssymp$ (realized incubation periods of infectees):
-\djde{why not use $t$ instead of $\alpha$?}
 \begin{equation}
@@
 where the case reproduction number $\Rc (\pinf)$ is defined as the average number of secondary cases caused by a primary case infected at time $\pinf$ over the course of their infection \citep{fraser2007estimating}.
-We note that \bmb{I always delete this if possible: maybe needed here though?} it is necessary to describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
+We describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
 for example, if an infected individual can only transmit the disease after symptom onset, the forward generation interval will necessarily be longer than the forward incubation period.
 
-\djde{The term ``total number'' of serial intervals is very peculiar,
-  because there are infinitely many.  It is more like a cumulative
-  distribution.  I'm not sure what the best jargon is.}
-
-The total number of serial intervals can now be obtained by integrating over all possible infection times for the infector and the infectee:
+The total amount of serial intervals can now be obtained by integrating over all possible infection times for the infector and the infectee:
 \begin{equation}
@@
 f_\psymp(\tau) = 
-\frac{\total(\psymp, \psymp+\tau)}{\int \total(\psymp, \psymp+\tau') \dtau'}.
+\frac{\total(\psymp, \psymp+\tau)}{\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'}.
 \label{eq:fserial}
 \end{equation}
-\djde{Don't leave out the limits of integration.  Ambiguity isn't
-  helpful to anyone.  This stuff is hard.  Be as precise as possible.}
 Likewise, the backward serial-interval distribution $b_\ssymp(\tau)$ is given by the density of intervals of length $\tau$ ending at \ssymp, relative to the total number of serial intervals ending at \ssymp:
@@
 b_\ssymp(\tau) = 
-\frac{\total(\ssymp-\tau, \ssymp)}{\int \total(\ssymp-\tau', \ssymp) \dtau'}.
+\frac{\total(\ssymp-\tau, \ssymp)}{\int_{-\infty}^\infty \total(\ssymp-\tau', \ssymp) \dtau'}.
 \label{eq:bserial}
@@
 \begin{equation}
-\gdist_\psymp (\tau) \propto \gdist(\tau) S(\psymp + \tau),
+\gdist_\psymp (\tau) = \frac{ \gdist(\tau) S(\psymp + \tau)}{\int_0^\infty \gdist(\tau') S(\psymp + \tau') \dtau'},
 \end{equation}
@@
 \begin{equation}
-h_\psymp (x, \tau) \propto h(x, \tau) S(\psymp + \tau).
+h_\psymp (x, \tau) = \frac{h(x, \tau) S(\psymp + \tau)}{\int_0^\infty \int_0^\infty h(x', \tau') S(\psymp + \tau') \dtau' \dx'}.
 \end{equation}
@@
 not vary across cohorts over the course of an epidemic, as it
-represents the life history of a disease; we denote it as $\idist$
-(without subscript). \bmb{do we need ``without subscript''?}
-\djde{perhaps ``without the subscript used in (5)''}
+represents the life history of a disease; we denote it as $\idist$.
 Then, we have:
@@
 \end{equation}
-where the intrinsic serial-interval distribution $q(\tau)$ does not depend on disease dynamics:
+where the intrinsic serial-interval distribution $q(\tau)$ does not depend on epidemic dynamics:
 \begin{equation}
@@
   \textbf{Parameter values used for simulations.}
-  \bmb{note that these are chosen to be characteristic of COVID19 (sort of obvious, but most of the paper so far has been general), to illustrate realistic magnitudes of time-varying/perspective effects in the current pandemic?}
 The intrinsic generation-interval distribution is parameterized using a log-normal distribution with log mean $\mu_G=1.54$ and log standard deviation $\sigma_G=0.37$.
@@
 The joint probability distribution is modeled using a multivariate log-normal distribution with correlations (on the log scale) $\rho=-0.5, 0, 0.5$.
+The intrinsic generation-interval and incubation period distributions are chosen to match characteristic of COVID-19 to illustrate realistic magnitudes of time-varying/perspective effects in the current pandemic.
 }
@@
 The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $\gdist(\tau)$ give identical estimates of \Ro (see \eref{Rgen} and \eref{Rforward}) regardless of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
-However, using the intrinsic serial-interval distributions that do not account for disease dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \Ro (see \eref{Rintrinsic});
+However, using the intrinsic serial-interval distributions that do not account for epidemic dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \Ro (see \eref{Rintrinsic});
 as $r$ increases, \Rintrinsic saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
@@
 for any correlation $\rho$ between intrinsic incubation period and
-intrinsic generation interval.\djde{added definition of $\rho$ for the
-benefit of the many readers who will just poke through figures.}
+intrinsic generation interval of the underlying bivariate log-normal distribution.
 (B) The intrinsic serial-interval distributions give an incorrect link between $r$ and \Ro.
@@
 
-\fref{epi} juxtaposes \bmb{too fancy? technically we're not
-  ``comparing'' the epi dynamics to the intervals (we're comparing the
-  forward and backward intervals)}\djde{how about ``shows'' and then
-  say ``(A) together with'' rather than ``(A) with'' } the epidemiological dynamics (A) with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
+\fref{epi} shows the epidemiological dynamics (A) together with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
 The mean forward incubation period remains constant throughout an epidemic as assumed (\fref{epi}B).
-The mean forward generation interval decreases slightly as incidence rate \bmb{``incidence'' or ``incidence rate''?} increases, causing the proportion of susceptible population to decrease (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
+The mean forward generation interval decreases slightly as incidence increases, causing the proportion of susceptible population to decrease (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
 In contrast, the mean forward serial interval decreases over time (\fref{epi}D).
 
-The forward serial interval distributions depend on \djde{adding these
-two words so Ben's deletions are a little more palatable to me (but I
-don't like it because it goes back to talking about forward and
-backward periods rather than forward and backward distributions; I
-would go back to being precise):}distributions of three intervals
-(\fref{diagram}): (i) the backward incubation period, \bmb{I deleted
-  ``distributions'' in this sentence; seems to read better without
-  hurting the meaning? could also do that for the next few sentences
-  if appropriate} (ii) the forward generation interval, and (iii) the forward incubation period.
+The forward serial interval distributions depend on distributions of three intervals
+(\fref{diagram}): (i) the backward incubation period, (ii) the forward generation interval, and (iii) the forward incubation period.
 For COVID-19 parameters (Table 1), both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
@@
 However, researchers typically use all available information to estimate epidemiological parameters;
-in particular, \cite{thompson2019improved} recently suggested that up-to-date serial interval data is \bmb{is? are? https://xkcd.com/1429/} necessary to accurately estimate the reproduction number.
+in particular, \cite{thompson2019improved} recently suggested that up-to-date serial interval data are necessary to accurately estimate the reproduction number.
 We explore the consequences of neglecting changes in the realized serial interval distribution on estimates of the basic reproduction number.
@@
 \fref{du}A shows that the mean forward serial interval decreases over time.
-While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and \emph{maximum observable} \bmb{drop italics?} serial intervals), the increase in the proportion of negative serial intervals clearly\djde{unequivocally?} indicates changes in the forward serial-interval distribution;
-the increase in the proportion of negative serial intervals is unlikely to be driven by left-censoring (indicated by the distance between the quantiles of the observed serial intervals and \emph{minimum observable} serial intervals).
+While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum observable serial intervals), the increase in the proportion of negative serial intervals unequivocally indicates changes in the forward serial-interval distribution;
+the increase in the proportion of negative intervals is unlikely to be driven by left-censoring (indicated by the distance between the quantiles of the observed serial intervals and minimum observable serial intervals).
 The decrease in the mean forward serial interval was probably caused by increase in the mean backward incubation period, reflecting decrease in COVID-19 cases in China, as well as intervention efforts which reduced generation intervals by preventing infections once cases were identified.
 \fref{du}B shows that the mean backward serial interval increased over time, also reflecting decrease in COVID-19 cases in China.
-\bmb{careful about tense consistency}
 
 While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculate earlier based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
-These results indicate that the incubation period and generation interval (Table 1) may previously have been underestimated as neither study explicitly accounts \bmb{accounted?} for the fact that the observed distributions are like \bmb{?delete ``like''?} backward distributions.
+These results indicate that the incubation period and generation interval (Table 1) may previously have been underestimated as neither study explicitly accounted for the fact that the observed intervals were drawn from the backward distributions and were likely to have been truncated.
 
@@
 In general, the forward serial-interval distributions will not match the intrinsic or the backward serial-interval distributions.
-Further, the mean forward serial interval can decrease over time due to disease \bmb{epidemic? see previous note} dynamics. 
+Further, the mean forward serial interval can decrease over time due to epidemic dynamics. 
 Failing to account for these differences can result in underestimation of \RR.
@@
 Our study underlines the importance of carefully defining measured epidemiological time distributions.
-\djde{altered the following sentence}
 Previous studies have shown that it matters whether generation
@@
 Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the dynamical differences between the realized incubation periods of infectors (backward-looking) and those of infectees (forward looking) (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
-Better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals are needed \bmb{usually avoid the passive voice, but here I think it works better}.
+Better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals are needed.
 
@@
 While we focused on the effect of epidemiological dynamics on the serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
-Individual-level interventions, such as case isolation, directly affect individuals' ability to transmit and will shorten the forward generation- and serial-intervals.
-\bmb{Do you want to mention/remind here that individual-level behavioural changes can either reduce transmission (like susceptible depletion) or shorten generation intervals?}
+Individual-level interventions, such as case isolation, and behavioral responses directly affect individuals' ability to transmit and will shorten the forward generation- and serial-intervals.
 Population-level interventions, such as social distancing, can squeeze contacts into household and induce clustering, which will in turn shorten the realized generation interval due to local depletion of the susceptible pool within households \citep{park2019inferring}.
@@
 Despite these limitations, our analysis of serial intervals of COVID-19 from China provides further support for our theoretical framework, demonstrating temporal variation in serial intervals and its effect on the estimates of \RR.
-Most \bmb{I don't think you need ``to our knowledge'' if you're going to hedge with ``most''} existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
+Most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
 Our study provides a rationale for reassessing estimates of
 serial-interval distributions---and their use in estimating
-\RR---during the COVID-19 pandemic. \bmb{a little awkward; could
-  probably move ``of the COVID-19 pandemic'' before the first
-  comma}\djde{I used --- instead of commas and replaced ``of'' with
-  ``during'', which I think fixes the problem.}
+\RR---during the COVID-19 pandemic.
 
@@
 requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
-\djde{a bit of tidying there}
 
@@
 we can now express the initial forward serial-interval distribution
-$f_0$ as a convolution of $\hat{z}$ and $\idist$:\djde{I think you
-  meant to remove $\phi$ below, but $\phi$ is not identical to $\int
-  z$; I'm missing something}
+$f_0$ as a convolution of $\hat{z}$ and $\idist$:
 \begin{equation}
-f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{\tau} \hat{z}(\sinf) \idist(\tau - \sinf)\, \mathrm{d}\sinf\,.
+f_{0}(\tau) = \frac{1}{\hat{\phi}} \int_{-\infty}^{\tau} \hat{z}(\sinf) \idist(\tau - \sinf)\, \mathrm{d}\sinf\,,
 \end{equation}
+where $\hat{\phi} = \phi/\int_{-\infty}^\infty z(x) \dx$.
+
 Since the right hand side of \eref{ptarget} is also a
-moment-generating function of $f_0$, we can express it as the product
-of the moment-generation functions of $\hat{z}$ and $\idist$:
-\djde{That didn't make sense to me, probably just not quite what you
-  meant to say.  To me, it would be much simpler just to say that
-  you're taking Laplace transforms of $f_0=\hat{z}*\idist$.}
+Laplace transform of $f_0=\hat{z}*\idist$, we can express it as the product
+of Laplace transforms of $\hat{z}$ and $\idist$:
 \begin{equation}
@@
 \end{equation}
-
-In order to derive an expression for $\int_{-\infty}^\infty \exp(-r\tau) \hat{z}(\tau) \mathrm{d} \tau$, we have to first derive an analytical expression for $\int_{-\infty}^\infty z(x) \dx$.
+In order to derive an expression for a Laplace transform of $\hat{z}$, we have to first derive an analytical expression for $\int_{-\infty}^\infty z(x) \dx$.
 By changing the order of integration, we have:
@@
 \begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf \dtau\,.
+\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\tau)}}^{\infty} \exp(-r\pinf) h(\pinf, \tau + \pinf)\, \mathrm{d}\pinf \dtau\,.
 \label{eq:newtarget2}
@@
 &\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau\\
-&=\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r \pinf) h(\pinf, \tau+\pinf) \,\mathrm{d} \pinf \dtau\nonumber\\
-&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \sigma) h(\pinf, \sigma)\, \mathrm{d} \pinf\, \mathrm{d}\sigma\nonumber\\
+&=\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r \pinf) h(\pinf, \tau+\pinf) \,\mathrm{d} \pinf \dtau\\
+&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \sigma) h(\pinf, \sigma)\, \mathrm{d} \pinf\, \mathrm{d}\sigma\\
 &=\int_{0}^{\infty} \exp(-r\tau) g(\tau) \dtau =\frac{1}{\Ro}

### 2020-05-28 serial_guide.tex
done

@@
-% Created by tikzDevice version 0.12.3 on 2020-05-22 09:42:54
+% Created by tikzDevice version 0.12.3 on 2020-05-27 19:48:26
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,421.76) {$p+x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,421.76) {$p+\tau_{\rm i1}$};
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,421.76) {$p$};
+\definecolor{drawColor}{RGB}{255,0,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,409.50) {Infector (reference cohort)};
+\definecolor{drawColor}{RGB}{0,0,0}
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,421.76) {$p+\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,421.76) {$p+\tau_{\rm g}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,421.76) {$p+\sigma+x_2$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,421.76) {$p+\tau_{\rm g}+\tau_{\rm i2}$};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,544.35) {Intrinsic serial interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,544.35) {Intrinsic serial interval, $\tau_{\rm s} = (\tau_{\rm g} + \tau_{\rm i2}) - \tau_{\rm i1}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,470.79) {Intrinsic incubation period};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,470.79) {Intrinsic incubation period, $\tau_{\rm i1}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,495.31) {Intrinsic generation interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,495.31) {Intrinsic generation interval, $\tau_{\rm g}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,519.83) {Intrinsic incubation period};
-\definecolor{fillColor}{RGB}{255,255,255}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,519.83) {Intrinsic incubation period, $\tau_{\rm i2}$};
+\definecolor{fillColor}{RGB}{255,0,0}
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,229.04) {$p-x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,229.04) {$p-\tau_{\rm i1}$};
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,216.78) {Infector};
+\definecolor{drawColor}{RGB}{255,0,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,216.78) {Reference cohort};
+\definecolor{drawColor}{RGB}{0,0,0}
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,229.04) {$p-x_1+\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,229.04) {$p-\tau_{\rm i1}+\tau_{\rm g}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,229.04) {$p-x_1+\sigma+x_2$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,229.04) {$p-\tau_{\rm i1}+\tau_{\rm g}+\tau_{\rm i2}$};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,351.63) {Forward serial interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,351.63) {Forward serial interval, $\tau_{\rm s} = (\tau_{\rm g} + \tau_{\rm i2}) - \tau_{\rm i1}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,278.07) {Backward incubation period};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,278.07) {Backward incubation period, $\tau_{\rm i1}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,302.59) {Forward generation interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,302.59) {Forward generation interval, $\tau_{\rm g}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,327.11) {Forward incubation period};
-\definecolor{fillColor}{RGB}{255,255,255}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,327.11) {Forward incubation period, $\tau_{\rm i2}$};
+\definecolor{fillColor}{RGB}{255,0,0}
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 36.32) {$s-x_2$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 36.32) {$s-\tau_{\rm i2}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 36.32) {$s-x_2-\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 36.32) {$s-\tau_{\rm i2}-\tau_{\rm g}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 36.32) {$s-x_2-\sigma+x_1$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 36.32) {$s-\tau_{\rm i2}-\tau_{\rm g}+\tau_{\rm i1}$};
 
@@
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 24.06) {Infectee};
+\definecolor{drawColor}{RGB}{255,0,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 24.06) {Reference cohort};
+\definecolor{drawColor}{RGB}{0,0,0}
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,158.91) {Backward serial interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,158.91) {Backward serial interval, $\tau_{\rm s} = (\tau_{\rm g} + \tau_{\rm i2}) - \tau_{\rm i1}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85, 85.35) {Backward incubation period};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85, 85.35) {Backward incubation period, $\tau_{\rm i2}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (362.72,109.87) {Backward generation interval};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (362.72,109.87) {Backward generation interval, $\tau_{\rm g}$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,134.39) {Forward incubation period};
-\definecolor{fillColor}{RGB}{255,255,255}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,134.39) {Forward incubation period, $\tau_{\rm i1}$};
+\definecolor{fillColor}{RGB}{255,0,0}
 

### 2020-05-28 forward.R

@@ -125,9 +125,10 @@ gendet <- data.frame(
 g3 <- ggplot(gendata0) +
   geom_line(data=gendet, aes(tvec, mf), lwd=1) +
   geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
+  geom_ribbon(aes(cc, ymin=lwr, ymax=upr), colour=NA, fill="#D55E00", alpha=0.2) +
   geom_hline(yintercept=gendet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7), breaks=0:4*2) +
+  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7), breaks=0:4*2, oob=scales::squish) +
   scale_fill_gradientn(colors=c("white", "black")) +
   ggtitle("C. Generation interval") +
   theme(
@@ -149,6 +150,7 @@ serdet <- data.frame(
 g4 <- ggplot(serdata0) +
   geom_line(data=serdet, aes(tvec, mf), lwd=1) +
   geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
+  geom_ribbon(aes(cc, ymin=lwr, ymax=upr), colour=NA, fill="#D55E00", alpha=0.2) +
   geom_hline(yintercept=serdet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
   scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7)) +

### 2020-05-28 serial_guide.R

@@ -18,12 +18,12 @@ g1 <- ggplot(arrow) +
   geom_point(aes(1.5, 0.4), size=3) +
   geom_point(aes(2.5, 0.3), size=3) +
   geom_point(aes(0.5, 0.1), size=3) +
-  annotate("text", x=1.5, y=-0.05, label="$p+x_1$") +
+  annotate("text", x=1.5, y=-0.05, label="$p+\\tau_{\\rm i1}$") +
   annotate("text", x=0.5, y=-0.05, label="$p$") +
-  annotate("text", x=0.5, y=-0.1, label="Infector (reference cohort)") +
+  annotate("text", x=0.5, y=-0.1, label="Infector (reference cohort)", col="red") +
   annotate("text", x=2.5, y=-0.1, label="Infectee") +
-  annotate("text", x=2.5, y=-0.05, label="$p+\\sigma$") +
-  annotate("text", x=3.5, y=-0.05, label="$p+\\sigma+x_2$") +
+  annotate("text", x=2.5, y=-0.05, label="$p+\\tau_{\\rm g}$") +
+  annotate("text", x=3.5, y=-0.05, label="$p+\\tau_{\\rm g}+\\tau_{\\rm i2}$") +
   geom_segment(aes(x, y, xend=x1, yend=y1), arrow = arrow(length = unit(0.2, "inches")), lwd=1) +
   geom_segment(aes(0.5, 0, xend=0.5, yend=0.2), lty=2) +
   geom_segment(aes(1.5, 0, xend=1.5, yend=0.4), lty=2) +
@@ -33,11 +33,11 @@ g1 <- ggplot(arrow) +
   geom_segment(aes(0.5, 0.2, xend=2.5, yend=0.2), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
   geom_segment(aes(2.5, 0.3, xend=3.5, yend=0.3), arrow = arrow(length = unit(0.1, "inches")), lwd=1) +
   geom_segment(aes(1.5, 0.4, xend=3.5, yend=0.4), arrow = arrow(length = unit(0.1, "inches")), lwd=1.5) +
-  annotate("text", x=2.5, y=0.45, label="Intrinsic serial interval") +
-  annotate("text", x=1, y=0.15, label="Intrinsic incubation period") +
-  annotate("text", x=1, y=0.25, label="Intrinsic generation interval") +
-  annotate("text", x=3, y=0.35, label="Intrinsic incubation period") +
[…]

### 2020-05-28 serial.tex
almost done

@@
 Generation intervals characterize the time between infection and transmission; whereas serial intervals characterize the time between the onset of symptoms in a chain of transmission.
-They are often used interchangeably, leading to misunderstanding of how to use either generation or serial intervals to establish a link between the epidemic growth rate $r$ and the reproduction number \RR.
-On one hand, generation intervals provide a mechanistic link between $r$ and \RR but are harder to measure via contact tracing.
-On the other hand, serial intervals are easier to measure from contact tracing but recent studies suggest that the two intervals give different estimates of \RR from $r$.
+They are often used interchangeably, leading to ongoing misunderstanding of how to use either generation or serial intervals to establish a link between the epidemic growth rate $r$ and the reproduction number \RR.
+Generation intervals provide a mechanistic link between $r$ and \RR but are harder to measure via contact tracing.
+While serial intervals are easier to measure from contact tracing, recent studies suggest that the two intervals give different estimates of \RR from $r$.
 We present a general framework for characterizing \emph{any} epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly estimates \RR from $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
@@
 the value in a fully susceptible population --- referred to as the basic reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population and the amount of intervention necessary to eliminate it \citep{anderson1991infectious}.
-Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{wallinga2007generation, fraser2009pandemic, hampson2009transmission, chunara2012social, chowell2014west, du2020serial, jung2020real}).
+Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{wallinga2007generation, fraser2009pandemic, hampson2009transmission, chunara2012social, chowell2014west, du2020serial, jung2020real}) but the differences in the distributions are often neglected.
 
@@
 When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event is the event that usually occurs before the secondary event ---
-most epidemiological events that can be observed within an individual have clear direction (e.g., infection and onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
+most epidemiological events that can be observed within an individual have clear direction (e.g., infection to onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
 When we measure an epidemiological time delay between infected individuals (e.g., the serial interval), 
@@
 Consequently, if we restrict attention to individuals with a given
-incubation period, say $\tau$, and we count how many became infected at time $\psymp$
+incubation period, say $\tau$ days, and we count how many became infected at time $\psymp$
 or how many first showed symptoms at time $\ssymp=\psymp+\tau$ then we must obtain
@@
 Typically, within-individual forward delay distributions are not affected by epidemic dynamics.
-Some realized distributions, like incubation period distributions, are expected to be equivalent to their intrinsic distributions and remain invariant over the course of an epidemic.
+Some realized distributions, like incubation period distributions, are expected to be equivalent to their intrinsic distributions and remain invariant at time time scale of an outbreak.
 Other realized distributions, like the distribution of time from symptom onset to testing, may change over the course of an epidemic due to changes in public health policies.
@@
 Assuming that the forward delay distribution remains constant during the exponential growth phase ($f_p(\tau) \approx f_0(\tau)$), we can substitute $\psize(t) = \psize(0) \exp(rt)$ in \eref{backward} to obtain:
-\begin{equation}
-b_0(\tau) = \frac{\exp(-r\tau) f_0(\tau)}{\left[\int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'\right]},
+\begin{align}
+b_0(\tau) &= \exp(-r\tau) f_0(\tau) \left[\psize(0)/\ssize(0)\right]\\
+&=\frac{\exp(-r\tau) f_0(\tau)}{\int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'},
 \label{eq:backexp}
-\end{equation}
-where $r$ is the exponential growth rate and the expression in square brackets is a constant since it does not depend on $\tau$.
+\end{align}
+where $r$ is the exponential growth rate and the denominator is a constant since it does not depend on $\tau$.
 For faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.
@@
 \end{equation}
-\djde{I don't like $\propto$.  It is always clearer to state the
-  constant of proportionality.}
 which allows us to separate the joint probability distribution $h_\psymp$ of the forward incubation period and the forward generation-interval distribution as a product of the proportion of susceptible individuals $S$ and the joint probability distribution $h$ of the forward incubation period and the intrinsic generation intervals:
@@
 See Table 1 for parameter values.
-\bmb{I added 50\% quantiles to one of the plots.  You can decide whether you think it's too ugly OR extend it to the other plots\ldots}
 }
@@
 Solid lines represent the estimated locally estimated scatterplot smoothing (LOESS) fits.
-The dashed line represents the maximum and minimum observable delays across the range of \bmb{???}.
+The dashed line represents the maximum and minimum observable delays across the range of reported sypmtom onset dates.
 (C) Cohort-averaged estimates of \Ro assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
@@
 The data were taken from Supplementary Materials of \cite{du2020serial}.
-\bmb{I think this would be slightly more readable if you nudged the min/max labels up slightly so they were clear of the dashed lines}
 }
@@
 \begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau = \int_{-\infty}^\infty \exp(-r\tau) \int_{\max{(0,-\tau)}}^{\infty} \exp(-r\pinf) h(\pinf, \tau + \pinf)\, \mathrm{d}\pinf \dtau\,.
+\int_{-\infty}^\infty \exp(-r\sinf) f_{0}(\tau)\dtau = \int_{-\infty}^\infty \exp(-r\sinf) \int_{\max{(0,-\tau)}}^{\infty} \exp(-r\pinf) h(\pinf, \tau + \pinf)\, \mathrm{d}\pinf\,\mathrm{d}\sinf\,.
 \label{eq:newtarget2}
@@
 \begin{equation}
-g(\tau) = \int_0^\infty h(\pinf, \tau) \,\mathrm{d} \pinf\,.
+g(\tau) = \int_0^\infty h(x, \tau) \,\mathrm{d}x\,.
 \end{equation}
-We can then substitute $\sigma = \pinf + \tau$ into \eref{newtarget2} and apply change of variables to obtain:
+We can then substitute $\tau = \pinf + \sinf$ into \eref{newtarget2} and apply change of variables to obtain:
 \begin{align}
 &\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau\\
-&=\int_{-\infty}^{\infty} \exp(-r\tau) \int_{\max(0, -\tau)}^\infty \exp(- r \pinf) h(\pinf, \tau+\pinf) \,\mathrm{d} \pinf \dtau\\
-&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \sigma) h(\pinf, \sigma)\, \mathrm{d} \pinf\, \mathrm{d}\sigma\\
+&=\int_{-\infty}^{\infty} \exp(-r\sinf) \int_{\max(0, -\sinf)}^\infty \exp(- r \pinf) h(\pinf, \tau+\pinf) \,\mathrm{d} \pinf \,\mathrm{d}\sinf \\
+&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \tau) h(\pinf, \tau)\, \mathrm{d} \pinf\, \mathrm{d}\tau\\
 &=\int_{0}^{\infty} \exp(-r\tau) g(\tau) \dtau =\frac{1}{\Ro}

### 2020-05-28 serial_analysis.tex
tweaks
almost done

@@
-% Created by tikzDevice version 0.12.3 on 2020-05-14 21:20:58
+% Created by tikzDevice version 0.12.3 on 2020-05-27 22:31:58
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (206.43,192.30) {maximum observable};
-
-\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 92.13, 70.86) {minimum observable};
+\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (210.00,195.87) {maximum observable};
+
+\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 95.70, 74.43) {minimum observable};
 
@@
 
-\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (388.02,200.87) {maximum observable};
-
-\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (521.60, 75.14) {minimum observable};
+\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (384.09,204.80) {maximum observable};
+
+\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (517.67, 79.07) {minimum observable};
 

### 2020-05-28 forward.R

@@ -9,8 +9,6 @@ load("sir_sim.rda")
 
 rr <- renewal_det()
 
-lvl <- 0.5  ## CI ribbon
-
 summfun <- function(dd) {
   dd %>%
     filter(!is.na(cohort), !is.na(tdiff), cohort > 0, cohort <= 100) %>%
@@ -19,9 +17,7 @@ summfun <- function(dd) {
     ) %>%
     group_by(cc) %>%
     summarize(
-        mean=mean(tdiff),
-        lwr=quantile(tdiff,(1-lvl)/2),
-        upr = quantile(tdiff,(1+lvl)/2)
+        mean=mean(tdiff)
     ) %>%
     ungroup %>%
     mutate(
@@ -99,8 +95,7 @@ incdet <- data.frame(
 
 g2 <- ggplot(incdata0) +
   geom_line(data=incdet, aes(tvec, mf), lwd=1) +
-    geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
-    geom_ribbon(aes(cc, ymin=lwr, ymax=upr), colour=NA, fill="#D55E00", alpha=0.2) +
+  geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
   geom_hline(yintercept=incdet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
   scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7), oob=scales::squish) +
@@ -125,10 +120,9 @@ gendet <- data.frame(
 g3 <- ggplot(gendata0) +
   geom_line(data=gendet, aes(tvec, mf), lwd=1) +
   geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
-  geom_ribbon(aes(cc, ymin=lwr, ymax=upr), colour=NA, fill="#D55E00", alpha=0.2) +
   geom_hline(yintercept=gendet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(0, 82)) +
-  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7), breaks=0:4*2, oob=scales::squish) +
+  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7), breaks=0:4*2) +
[…]

### 2020-05-28 serial_analysis.R

@@ -98,8 +98,8 @@ cdata2 <- data.frame(
 )
 
 g1 <- ggplot(rr) +
-  annotate("text", x=20, y=11, label="maximum observable", angle=-45) +
-  annotate("text", x=4, y=-6, label="minimum observable", angle=-45) +
+  annotate("text", x=20.5, y=11.5, label="maximum observable", angle=-45) +
+  annotate("text", x=4.5, y=-5.5, label="minimum observable", angle=-45) +
   geom_line(data=cdata, aes(x, y), lty=2) +
   geom_line(data=cdata2, aes(x, y), lty=2) +
   geom_point(data=rr_summ, aes(cohort, mean)) +
@@ -129,8 +129,8 @@ cdata4 <- data.frame(
 )
 
 g2 <- ggplot(rr) +
-  annotate("text", x=7, y=11, label="maximum observable", angle=45) +
-  annotate("text", x=24, y=-5, label="minimum observable", angle=45) +
+  annotate("text", x=6.5, y=11.5, label="maximum observable", angle=45) +
+  annotate("text", x=23.5, y=-4.5, label="minimum observable", angle=45) +
   geom_line(data=cdata3, aes(x, y), lty=2) +
   geom_line(data=cdata4, aes(x, y), lty=2) +
   geom_point(data=rr_summ2, aes(cohort, mean)) +

### 2020-05-28 serial.tex
done!!!
tweak

@@
 the value in a fully susceptible population --- referred to as the basic reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population and the amount of intervention necessary to eliminate it \citep{anderson1991infectious}.
-Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{wallinga2007generation, fraser2009pandemic, hampson2009transmission, chunara2012social, chowell2014west, du2020serial, jung2020real}) but the differences in the distributions are often neglected.
+Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{wallinga2007generation, fraser2009pandemic, hampson2009transmission, chunara2012social, chowell2014west, du2020serial, jung2020real}) but the differences among two distributions are often neglected.
 
@@
 \begin{equation}
-\int_{-\infty}^\infty \exp(-r\sinf) f_{0}(\tau)\dtau = \int_{-\infty}^\infty \exp(-r\sinf) \int_{\max{(0,-\tau)}}^{\infty} \exp(-r\pinf) h(\pinf, \tau + \pinf)\, \mathrm{d}\pinf\,\mathrm{d}\sinf\,.
+\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau = \int_{-\infty}^\infty \exp(-r\sinf) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf\,\mathrm{d}\sinf\,.
 \label{eq:newtarget2}
@@
 &\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau\\
-&=\int_{-\infty}^{\infty} \exp(-r\sinf) \int_{\max(0, -\sinf)}^\infty \exp(- r \pinf) h(\pinf, \tau+\pinf) \,\mathrm{d} \pinf \,\mathrm{d}\sinf \\
+&=\int_{-\infty}^{\infty} \exp(-r\sinf) \int_{\max(0, -\sinf)}^\infty \exp(- r \pinf) h(\pinf, \sinf+\pinf) \,\mathrm{d} \pinf \,\mathrm{d}\sinf \\
 &=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \tau) h(\pinf, \tau)\, \mathrm{d} \pinf\, \mathrm{d}\tau\\

### 2020-05-28 serial.tex
ok done

@@
 \begin{align}
-b_0(\tau) &= \exp(-r\tau) f_0(\tau) \left[\psize(0)/\ssize(0)\right]\\
-&=\frac{\exp(-r\tau) f_0(\tau)}{\int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'},
+b_0(\tau) &= \left[\psize(0)/\ssize(0)\right] \exp(-r\tau) f_0(\tau)
 \label{eq:backexp}
 \end{align}
-where $r$ is the exponential growth rate and the denominator is a constant since it does not depend on $\tau$.
+where $r$ is the exponential growth rate (and $\psize(0)/\ssize(0) = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
 For faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.

### 2020-05-28 serial.tex
done

@@
 \end{align}
-where $r$ is the exponential growth rate (and $\psize(0)/\ssize(0) = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
+where $r$ is the exponential growth rate (and $\left[\psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
 For faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.

### 2020-05-28 serial.tex
super-minor changes

@@
 Therefore, the \Ro estimate of 1.32 (95\% CI 1.16–1.48), which neglects the changes in the forward serial-interval distribution, is likely to be an underestimate.
-This example demonstrates the danger of using the observed serial intervals to calculate the reproduction number without integrating serial intervals into cohorts.
+This example demonstrates the danger of using the observed serial intervals to calculate the reproduction number without organizing serial intervals into cohorts.
 
@@
 
-Our study has some limitations.
-We assumed that all individuals develop symptoms and that the entire transmission process, including all relevant epidemiological delays, is known exactly.
+Here, we assume that all individuals develop symptoms and that the entire transmission process, including all relevant epidemiological delays, is known exactly.
 In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.

### 2020-05-28 serial.tex
tweak

@@
 We can further divide these events into \emph{primary} and \emph{secondary} events.
-When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event is the event that usually occurs before the secondary event ---
+When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event usually occurs before the secondary event ---
 most epidemiological events that can be observed within an individual have clear direction (e.g., infection to onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).

### 2020-05-28 serial.tex
dropcap

@@
 
+\usepackage{lettrine}
+
+\newcommand{\dropcapfont}{\fontfamily{lmss}\bfseries\fontsize{26pt}{28pt}\selectfont}
+\newcommand{\dropcap}[1]{\lettrine[lines=2,lraise=0.05,findent=0.1em, nindent=0em]{{\dropcapfont{#1}}}{}}
+
 \begin{document}
@@
 
-Generation intervals and serial intervals are critical quantities for characterizing outbreak dynamics.
+\dropcap{G}eneration intervals and serial intervals are critical quantities for characterizing outbreak dynamics.
 Generation intervals characterize the time between infection and transmission; whereas serial intervals characterize the time between the onset of symptoms in a chain of transmission.
@@
 
-\section*{Significance}
+\section*{Significance Statement}
 

### 2020-05-28 serial.tex
bibtweak

@@
 Changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
-Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series of symptomatic cases or infected cases from the reports of confirmed cases by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential, shim2020transmission});
+Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series of symptomatic cases or infected cases from the reports of confirmed cases by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential,scire2020reproductive,shim2020transmission});
 these studies effectively assume constant backward delay distributions.

### 2020-05-29 serial.tex
Once through Intro, see what you think.

@@
 \dropcap{G}eneration intervals and serial intervals are critical quantities for characterizing outbreak dynamics.
-Generation intervals characterize the time between infection and transmission; whereas serial intervals characterize the time between the onset of symptoms in a chain of transmission.
-They are often used interchangeably, leading to ongoing misunderstanding of how to use either generation or serial intervals to establish a link between the epidemic growth rate $r$ and the reproduction number \RR.
+Generation intervals characterize the time between infection and transmission, while serial intervals characterize the time between the onset of symptoms in a chain of transmission.
+They are often used interchangeably, leading to misunderstanding of how these intervals link the epidemic growth rate $r$ and the reproduction number \RR.
 Generation intervals provide a mechanistic link between $r$ and \RR but are harder to measure via contact tracing.
 While serial intervals are easier to measure from contact tracing, recent studies suggest that the two intervals give different estimates of \RR from $r$.
-We present a general framework for characterizing \emph{any} epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly estimates \RR from $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
-We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial interval data --- our analysis shows that using incorrectly defined serial intervals can severely bias the estimate.
+We present a general framework for characterizing epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly link \RR with $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
+We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial-interval data --- our analysis shows that using incorrectly defined serial intervals can severely bias estimates.
 This study demonstrates the importance of early epidemiological investigation through contact tracing and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
@@
 Here, we show that the serial-interval distribution, defined from the correct reference time and cohort, gives the same estimate of \RR as the generation-interval distribution.
-We then apply our framework to serial interval data from the COVID-19 outbreak in China.
+We then apply our framework to serial-interval data from the COVID-19 outbreak in China.
 While our study supports the use of serial-interval distributions in estimating \RR, it also reveals necessary changes to the current understanding and applications of serial-interval distribution.
@@
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
-the value in a fully susceptible population --- referred to as the basic reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population and the amount of intervention necessary to eliminate it \citep{anderson1991infectious}.
+the value in a fully susceptible population --- the ``basic'' reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population, and the amount of intervention necessary to eliminate it \citep{anderson1991infectious}.
 Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{wallinga2007generation, fraser2009pandemic, hampson2009transmission, chunara2012social, chowell2014west, du2020serial, jung2020real}) but the differences among two distributions are often neglected.
@@
 
-One source of confusion arises from an apparent discrepancy between biological intuition and mathematical theory.
+One source of confusion arises from an apparent discrepancy between the serial-interval and generation-interval viewpoints.
 When the epidemic is growing exponentially, the spread of infection can be characterized as a \emph{renewal process} based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
-This renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
+It is well established that this renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
 By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates;
-since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system, where all components must be growing at the same rate, we expect both generation- and serial-interval distributions to give identical estimates of \RR based on the observed epidemic growth rate $r$.
+since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system of exponential growth, both should provide the same correct link between \RR and the epidemic growth rate $r$.
 In contexts where the distributions are expected to be different, current theory has no explanation for how these differing distributions could provide identical estimates of \RR from $r$. 
@@
 
-Here, we resolve this discrepancy by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
-We develop a new framework for understanding serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
+Here, we resolve this apparent paradox by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
+We develop a new framework for characterizing and comparing serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
 Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of \RR.
@@
 
-Now, we turn to issues of estimating the reproduction number from the observed serial interval data during on ongoing epidemic.
+Now, we turn to issues of estimating the reproduction number from the observed serial-interval data during on ongoing epidemic.
 In order to have an unbiased estimate of the basic reproduction number, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e., initial forward serial-interval distribution).
 However, researchers typically use all available information to estimate epidemiological parameters;
-in particular, \cite{thompson2019improved} recently suggested that up-to-date serial interval data are necessary to accurately estimate the reproduction number.
+in particular, \cite{thompson2019improved} recently suggested that up-to-date serial-interval data are necessary to accurately estimate the reproduction number.
 We explore the consequences of neglecting changes in the realized serial interval distribution on estimates of the basic reproduction number.
@@
 The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}:
-$\Ro = 2.6$ (95\% CI: 2.2--3.1) and $\Ro = 3.4$ (95\% CI: 2.7 -- 4.3) based on 8 and 6 doubling periods, respectively, using serial interval data from infectors who developed symptoms by day 7.
+$\Ro = 2.6$ (95\% CI: 2.2--3.1) and $\Ro = 3.4$ (95\% CI: 2.7 -- 4.3) based on 8 and 6 doubling periods, respectively, using serial-interval data from infectors who developed symptoms by day 7.
 These early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
@@
 they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
-\cite{thompson2019improved} recently emphasized the importance of using up-to-date serial interval data for accurate estimation of time-varying reproduction numbers.
-However, our study demonstrates that early serial interval data is required to estimate the initial \RR during the exponential growth phase and that using up-to-date serial interval data (without accounting for changes in the forward serial-interval distribution) can, in fact, underestimate the initial \RR.
+\cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
+However, our study demonstrates that early serial-interval data is required to estimate the initial \RR during the exponential growth phase and that using up-to-date serial-interval data (without accounting for changes in the forward serial-interval distribution) can, in fact, underestimate the initial \RR.
 Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase and potentially re-assess existing estimates of \RR.
 
-Many studies have already estimated the (time-varying) reproduction numbers for COVID-19 epidemics using aggregated serial interval data (e.g., \cite{tempvar,du2020serial,pan2020jama,zhang2020evolving});
+Many studies have already estimated the (time-varying) reproduction numbers for COVID-19 epidemics using aggregated serial-interval data (e.g., \cite{tempvar,du2020serial,pan2020jama,zhang2020evolving});
 these studies should also re-assess whether they appropriately considered the \emph{forward} serial interval.

### 2020-05-29 serial.tex
trying to merge in case Daniel has anything

@@
 For example, an infectious contact results in infection only if the contacted individual is susceptible (and has not already been infected);
-this is one mechanism that distinguishes the realized generation intervals (time between actual infection events) from the intrinsic generation intervals (time between infection and infectious contacts).
+this is one mechanism that causes realized generation intervals (time between actual infection events) to differ from from the intrinsic generation intervals (time between infection and infectious contacts).
 
-At the population level, we model realized time delays between a primary and a secondary event that occurs during an epidemic from a cohort perspective.
-A primary cohort consists of \emph{all} individuals whose primary event occurred at a given time; 
-a secondary cohort is defined similarly based on the secondary events.
-For example, when we are measuring incubation periods, a primary cohort consists of all individuals who became infected at time $\psymp$.
+At the population level, we model realized time delays between a primary and a secondary event from a cohort perspective.
+A cohort consists of \emph{all} individuals whose (primary or secondary) event occurred at a given time. 
+For example, when we are measuring incubation periods, a primary cohort consists of all individuals who became infected at time \psymp, while a secondary cohort consists of all individuals whose symptom onset occurred at time $\ssymp$.
 Similarly, when we are measuring serial intervals, a primary cohort consists of all infectors who became symptomatic at time $\psymp$.
@@
 \end{equation}
-If we are thinking of realized incubation periods, then the left hand side of
+If we are considering incubation periods, the left hand side of
 this equation is the probability density that an individual
@@
 length $\tau$. From the right hand side, we see that this probability
-density depends on how many individuals became infected at time
-$\ssymp-\tau$ [$\psize(\ssymp-\tau)$], how many individuals became
-symptomatic at time $\ssymp$ [$\ssize(\ssymp)$], and the probability density
-that someone who was infected at time $\ssymp-\tau$ became symptomatic at
-time $\ssymp$ [$f_{\ssymp-\tau}(\tau)$]. In general, Eq.~\eqref{eq:backward}
-shows that the backward delay distribution at reference time $\ssymp$
-[$b_\ssymp(\tau)$] depends not only on the secondary cohort size at time
-$\ssymp$ [$\ssize(\ssymp)$], but also on the primary cohort size at the
-earlier time $\ssymp-\tau$ [$\psize(\ssymp-\tau)$] and the forward delay
-distribution at that earlier time [$f_{\ssymp-\tau}(\tau)$].
+density depends on both the forward distribution $f_{\ssymp-\tau}(\tau)$], and the time-varying number of people becoming infected $\psize(\ssymp-\tau)$].
 
 Several different mechanisms drive the changes in forward and backward delay distributions over time.
-Typically, within-individual forward delay distributions are not affected by epidemic dynamics.
+Typically, within-individual forward delay distributions are not directly affected by epidemic dynamics.
 Some realized distributions, like incubation period distributions, are expected to be equivalent to their intrinsic distributions and remain invariant at time time scale of an outbreak.
@@
 Backward delay distributions depend on changes in the primary cohort size over time due to conditionality of observations:
-Conditioning on individuals whose secondary events have occurred at the same time means that the distribution is truncated so that we tend to observe shorter (or longer) inter-event delays when incidence is  the cohort size has been increasing (or decreasing) over time.
-In particular, when the incidence is growing exponentially, we can calculate the amount of bias exactly.
+Conditioning on individuals whose secondary events have occurred at the same time means that we tend to observe shorter (or longer) inter-event delays when cohort size has been increasing (decreasing) through time.
+When incidence is growing exponentially, we can calculate the amount of bias exactly.
 Assuming that the forward delay distribution remains constant during the exponential growth phase ($f_p(\tau) \approx f_0(\tau)$), we can substitute $\psize(t) = \psize(0) \exp(rt)$ in \eref{backward} to obtain:

### 2020-05-29 serial.tex
methods

@@
 
+\jd{It's a shame not to mention the idea that serial intervals are wider, and should therefore predict smaller \RR.
+That would also help with understanding the resolution.
+Or maybe we get to these ideas later?
+It helps with the paradox framing, but I guess you really don't like that.}
 One source of confusion arises from an apparent discrepancy between the serial-interval and generation-interval viewpoints.
@@
 where $r$ is the exponential growth rate (and $\left[\psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
-For faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.
-Changes in the backward delay distribution are also by definition affected by the changes in the forward delay distribution (\eref{backward}).
-Therefore, the backward delay distribution will generally differ from the forward delay distribution even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
-These ideas apply to all epidemiological delay distributions and generalize the work by \cite{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe the realized generation intervals from the perspective of an infector and an infectee, respectively, as well as the work by \cite{britton2019estimation} who showed that \eref{backexp} holds for the backward generation-interval distributions.
+Thus, for faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.
+In general, the backward delay distribution will differ from the forward delay distribution (unless the disease is at equilibrium), even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
+These ideas apply to all epidemiological delay distributions and generalize the work by \cite{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe realized generation intervals from the perspective of an infector and an infectee, respectively, as well as the work by \cite{britton2019estimation} who showed that \eref{backexp} holds for the backward generation-interval distributions.
 
-\subsection{Realized serial interval distributions}
+\subsection{Realized serial-interval distributions}
 
@@
 \tau_{\rm s} = (\gtime + \tau_{\rm i2}) - \tau_{\rm i1}
+\label{eq:intser}
 \end{equation}
@@
 an infectee, respectively, and $\gtime$ represents the generation
-interval.  
+interval of the infector.  
 These studies assume that $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
 however, this conclusion is based on the implicit assumption that distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
-something that is true of forward but not backward distribution of incubation periods.
-We refer to this definition as the intrinsic
+something that is generally true of forward but not backward incubation-period distributions.
+We refer to the definition \eref{intser} as the intrinsic
 serial interval (\fref{diagram}A).
@@
 
-To correctly link the realized serial interval distribution to the renewal process
+To correctly link the realized serial-interval distribution to the renewal process
 between cases based on symptom onset dates, we must use the forward
@@
 infectees who became infected at time $\psymp - \tau_{\rm i1} + \gtime$.
-Likewise, we can define the backward serial interval distribution for
+Likewise, we can define the backward serial-interval distribution for
 a cohort of infectees who became symptomatic at time $\ssymp$
@@
 $\sinf$ and $\ssymp$ (realized incubation periods of infectees):
+\jd{I feel that $R_c$ should group with h (i.e., after i()), for comprehension.}
 \begin{equation}
@@
 
-During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t)=i_0\exp(rt)$.
+During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t) \approx i_0\exp(rt)$.
 During this period, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the initial reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation};
@@
 Analogous to the intrinsic generation-interval distribution, 
-forward serial-interval distributions, by definition, describe the renewal process of infection based on symptom onset dates.
+forward serial-interval distributions describe the renewal process of infection based on symptom onset dates.
 Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to estimate the same value of \Ro for a given $r$ as the intrinsic generation-interval distribution (note, however, that the forward serial interval is not necessarily positive):
@@
 Rather than numerically integrating over closed forms of $g$, $f_0$, and $q$ to estimate $\Ro$, we use simulation-based approaches for simplicity (Supplementary Materials).
+Our parameter values are shown in the Table.
 
@@
 The Susceptible-Exposed-Infected-Recovered model, under the additional assumption that the incubation and exposed periods are equivalent (i.e.
-that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset to infection is independent of the incubation period of an infector (see Supplementary Materials).
+that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
 
@@
 
-\subsection{Realized serial interval distributions}
+\subsection{Realized serial-interval distributions}
 
@@
 
-The initial forward serial interval distribution captures the exponential growth phase of an epidemic.
+The initial forward serial-interval distribution captures the exponential growth phase of an epidemic.
 Next, we characterize how forward and backward serial intervals vary over the course of an epidemic by running deterministic and stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
@@
 
-The forward serial interval distributions depend on distributions of three intervals
+The forward serial-interval distributions depend on distributions of three intervals
 (\fref{diagram}): (i) the backward incubation period, (ii) the forward generation interval, and (iii) the forward incubation period.
@@
 
-\subsection{Observed serial interval distributions}
+\subsection{Observed serial-interval distributions}
 
@@
 in particular, \cite{thompson2019improved} recently suggested that up-to-date serial-interval data are necessary to accurately estimate the reproduction number.
-We explore the consequences of neglecting changes in the realized serial interval distribution on estimates of the basic reproduction number.
+We explore the consequences of neglecting changes in the realized serial-interval distribution on estimates of the basic reproduction number.
 
@@
 
-While our results support the use of serial interval distributions for calculating \RR, 
+While our results support the use of serial-interval distributions for calculating \RR, 
 they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
@@
 these studies should also re-assess whether they appropriately considered the \emph{forward} serial interval.
-Given large geographical variation in the spread of the COVID-19, the forward serial interval distributions are also likely to vary across countries.
+Given large geographical variation in the spread of the COVID-19, the forward serial-interval distributions are also likely to vary across countries.
 We suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions and understand their changes over time.

### 2020-05-29 serial.tex
push for Daniel

@@
 
+\jd{Results could start sharper. I don't think $\rho$ is ``based on parameter estimates'' --  I think you mean the other stuff. The lognormal details etc., should be merged into Methods.}
 First, we compare the estimates of the basic reproduction number \Ro based on the initial forward serial-interval distributions and the intrinsic serial-interval distributions (see Supplementary Materials for calculation details.).
 In particular, we model the joint probability distribution of the intrinsic incubation periods and generation intervals using a bivariate lognormal distribution with correlation $\rho$ based on parameter estimates for COVID-19 (Table 1).
-The initial forward serial-interval distributions $f_0(\tau)$ and the intrinsic generation-interval distribution $\gdist(\tau)$ give identical estimates of \Ro (see \eref{Rgen} and \eref{Rforward}) regardless of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
-However, using the intrinsic serial-interval distributions that do not account for epidemic dynamics (i.e., assuming that the backward and the forward incubation period distributions are identical) underestimates \Ro (see \eref{Rintrinsic});
+
+\fref{rR} shows Euler-Lotka estimates of \Ro\ on different definitions of the serial interval. 
+When the initial forward serial-interval distributions $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen} for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
+When the intrinsic distributions are used, however, estimates based on the serial interval (\eref{Rintrinsic});
 as $r$ increases, \Rintrinsic saturates and eventually decreases due to negative serial intervals (\fref{rR}B).

### 2020-05-29 serial.tex
take break!

@@
 When the initial forward serial-interval distributions $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen} for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
-When the intrinsic distributions are used, however, estimates based on the serial interval (\eref{Rintrinsic});
-as $r$ increases, \Rintrinsic saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
-While the forward serial intervals during the exponential growth phase can also be negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation periods (and therefore a lower proportion of negative serial intervals).
+When the intrinsic distributions are used, however, estimates based on the serial interval (\eref{Rintrinsic}) underestimate \Ro; as $r$ increases, \Rintrinsic saturates and eventually \emph{decreases} due to the increasing inferred importance of negative serial intervals (\fref{rR}B).
+While the forward serial intervals during the exponential growth phase can also be negative, their effects are appropriately balanced because faster epidemic growth leads to longer serial intervals (and a corresponding lower proportion of negative intervals).
 

### 2020-05-29 serial.tex
commit

--- 2020-05-29 serial.tex
@@
 
-\jd{It's a shame not to mention the idea that serial intervals are wider, and should therefore predict smaller \RR.
-That would also help with understanding the resolution.
-Or maybe we get to these ideas later?
-It helps with the paradox framing, but I guess you really don't like that.}
 One source of confusion arises from an apparent discrepancy between the serial-interval and generation-interval viewpoints.
@@
 In contexts where the distributions are expected to be different, current theory has no explanation for how these differing distributions could provide identical estimates of \RR from $r$. 
-Some studies have further suggested that using serial intervals can give different estimates of \RR \citep{britton2019estimation, ganyani2020estimating}.
+Some studies have further suggested that using serial intervals can underestimate \RR because the serial-interval distribution is wider than the generation-interval distribution \citep{britton2019estimation, ganyani2020estimating}.
 
-Here, we resolve this apparent paradox by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
+Here, we resolve this apparent discrepancy by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
 We develop a new framework for characterizing and comparing serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
@@
 $\sinf$ and $\ssymp$ (realized incubation periods of infectees):
-\jd{I feel that $R_c$ should group with h (i.e., after i()), for comprehension.}
 \begin{equation}
@@
 We use this framework to illustrate how the realized epidemiological time distributions vary over the course of an epidemic and depend on the perspective (i.e., forward vs. backward).
+We parameterize the model based on parameter estimates for COVID-19 (Table);
+we use a bivariate lognormal distribution
 
@@
 Rather than numerically integrating over closed forms of $g$, $f_0$, and $q$ to estimate $\Ro$, we use simulation-based approaches for simplicity (Supplementary Materials).
-Our parameter values are shown in the Table.
+Our parameter values are shown in the Table 1.
 

### 2020-05-29 serial.tex
not sure how to start results sharper, ugh..

@@
 who became symptomatic at time $\ssymp$ had an incubation period of
-length $\tau$. From the right hand side, we see that this probability
-density depends on both the forward distribution $f_{\ssymp-\tau}(\tau)$], and the time-varying number of people becoming infected $\psize(\ssymp-\tau)$].
+length $\tau$. 
+From the right hand side, we see that this probability density depends on both the time-varying primary cohort size at the earlier time $\psize(\ssymp-\tau)$ (in this case, the number of individuals became infected at time $\ssymp-\tau$) and the forward delay distribution $f_{\ssymp-\tau}(\tau)$ (in this case, the probability density that someone who was infected at time $\ssymp-\tau$ became symptomatic at time $\ssymp$).
 
@@
 an infectee, respectively, and $\gtime$ represents the generation
-interval of the infector.  
+interval between the infector and the infectee.
 These studies assume that $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
@@
 We use this framework to illustrate how the realized epidemiological time distributions vary over the course of an epidemic and depend on the perspective (i.e., forward vs. backward).
-We parameterize the model based on parameter estimates for COVID-19 (Table);
-we use a bivariate lognormal distribution
 
@@
 Rather than numerically integrating over closed forms of $g$, $f_0$, and $q$ to estimate $\Ro$, we use simulation-based approaches for simplicity (Supplementary Materials).
-Our parameter values are shown in the Table 1.
 
@@
 that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
+
+\subsection{Model parameterization}
+
+We parameterize our model based on parameter estimates for COVID-19 (Table 1).
+We use a bivariate lognormal distribution to model the joint probability distribution of the intrinsic incubation periods and the intrinsic generation intervals while allowing for the possibility that they might be correlated.
+For simplicity, we consider three values for the correlation coefficients (on the log scale) of the bivariate lognormal distribution: $\rho = -0.5, 0, 0.5$.
 
@@
 The intrinsic incubation period distribution is parameterized using a log-normal distribution with log mean $\mu_I=1.62$ and log standard deviation $\sigma_I=0.42$.
-The joint probability distribution is modeled using a multivariate log-normal distribution with correlations (on the log scale) $\rho=-0.5, 0, 0.5$.
+The joint probability distribution is modeled using a bivariate log-normal distribution with correlations (on the log scale) $\rho=-0.5, 0, 0.5$.
 The intrinsic generation-interval and incubation period distributions are chosen to match characteristic of COVID-19 to illustrate realistic magnitudes of time-varying/perspective effects in the current pandemic.
@@
 \jd{Results could start sharper. I don't think $\rho$ is ``based on parameter estimates'' --  I think you mean the other stuff. The lognormal details etc., should be merged into Methods.}
-First, we compare the estimates of the basic reproduction number \Ro based on the initial forward serial-interval distributions and the intrinsic serial-interval distributions (see Supplementary Materials for calculation details.).
-In particular, we model the joint probability distribution of the intrinsic incubation periods and generation intervals using a bivariate lognormal distribution with correlation $\rho$ based on parameter estimates for COVID-19 (Table 1).
 

### 2020-05-29 serial.tex
hopefully sharper?

@@
 
+We use parameter estimates for COVID-19 to characterize the degree to which the serial-interval distribution can change over the course of the epidemic and evaluate how different definitions of the serial-interval distribution can affect the Euler-Lotka estimates of \Ro.
+We further address how the observed serial intervals are affected by the right truncation during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial interval data to estimate \Ro.
+Finally, we analyze the serial interval data from the COVID-19 epidemic in China under our framework.
+
 \subsection{Realized serial-interval distributions}
 
-\jd{Results could start sharper. I don't think $\rho$ is ``based on parameter estimates'' --  I think you mean the other stuff. The lognormal details etc., should be merged into Methods.}
-
 \fref{rR} shows Euler-Lotka estimates of \Ro\ on different definitions of the serial interval. 
-When the initial forward serial-interval distributions $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen} for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
+When the initial forward serial-interval distributions $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen}) for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
 When the intrinsic distributions are used, however, estimates based on the serial interval (\eref{Rintrinsic}) underestimate \Ro; as $r$ increases, \Rintrinsic saturates and eventually \emph{decreases} due to the increasing inferred importance of negative serial intervals (\fref{rR}B).
-While the forward serial intervals during the exponential growth phase can also be negative, their effects are appropriately balanced because faster epidemic growth leads to longer serial intervals (and a corresponding lower proportion of negative intervals).
+While the initial forward serial intervals during the exponential growth phase can also be negative, their effects are appropriately balanced because faster epidemic growth leads to longer serial intervals (and a corresponding lower proportion of negative intervals).
 

### 2020-05-31 serial.tex
done!

@@
 \begin{equation}
-\psize(\psymp) f_\psymp(\tau) = \ssize(\ssymp) b_\ssymp(\tau) \,.
+W(\psymp) \psize(\psymp) f_\psymp(\tau) = \ssize(\ssymp) b_\ssymp(\tau) \,,
 \label{eq:match}
 \end{equation}
+where $W(\psymp)$, the ``weight'' of the primary cohort $\psize(\psymp)$, represents the average number of forward intervals that an individual in cohort $\psize(\psymp)$ produces over the course of their infection.
+When we measure within-individual delays, we expect $W(\psymp) \leq 1$ because only a subset of individuals who experience the primary event (e.g., infection) will eventually experience the secondary event (e.g., symptom onset).
+When we measure between-individual delays, we expect $W(\psymp)$ to change throughout an epidemic because individuals infected in the beginning of an epidemic will infect more than one individual, on average, over the course of their infection, whereas those infected later will infect less than one individual, on average.
+
 Substituting $\psymp=\ssymp-\tau$, it follows that
 \begin{equation}
-b_\ssymp(\tau)= \frac{\psize(\ssymp-\tau) f_{\ssymp-\tau} (\tau)}{\ssize(\ssymp)}\,.
+b_\ssymp(\tau)= \frac{W(\ssymp-\tau) \psize(\ssymp-\tau) f_{\ssymp-\tau} (\tau)}{\ssize(\ssymp)}\,.
 \label{eq:backward}
@@
 length $\tau$. 
-From the right hand side, we see that this probability density depends on both the time-varying primary cohort size at the earlier time $\psize(\ssymp-\tau)$ (in this case, the number of individuals became infected at time $\ssymp-\tau$) and the forward delay distribution $f_{\ssymp-\tau}(\tau)$ (in this case, the probability density that someone who was infected at time $\ssymp-\tau$ became symptomatic at time $\ssymp$).
+From the right hand side, we see that this probability density depends on the weight parameter $W(\psymp-\tau)$ (in this case, the proportion of symptomatic infection),
+the time-varying primary cohort size at the earlier time $\psize(\ssymp-\tau)$ (in this case, the number of individuals became infected at time $\ssymp-\tau$),
+and the forward delay distribution $f_{\ssymp-\tau}(\tau)$ (in this case, the probability density that someone who was infected at time $\ssymp-\tau$ became symptomatic at time $\ssymp$).
 
@@
 When incidence is growing exponentially, we can calculate the amount of bias exactly.
-Assuming that the forward delay distribution remains constant during the exponential growth phase ($f_p(\tau) \approx f_0(\tau)$), we can substitute $\psize(t) = \psize(0) \exp(rt)$ in \eref{backward} to obtain:
+Assuming that the forward delay distribution ($f_\psymp(\tau) \approx f_0(\tau)$) and the weight parameter ($W(\psymp) \approx W(0)$) remain constant during the exponential growth phase, we can substitute $\psize(t) = \psize(0) \exp(rt)$ in \eref{backward} to obtain:
 \begin{align}
-b_0(\tau) &= \left[\psize(0)/\ssize(0)\right] \exp(-r\tau) f_0(\tau)
+b_0(\tau) &= \left[ W(0) \psize(0)/\ssize(0)\right] \exp(-r\tau) f_0(\tau)
 \label{eq:backexp}
 \end{align}
-where $r$ is the exponential growth rate (and $\left[\psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
+where $r$ is the exponential growth rate (and $\left[W(0) \psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
 Thus, for faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.

### 2020-06-03 serial.tex
Not done but see comment about W.

@@
 \end{equation}
-where $W(\psymp)$, the ``weight'' of the primary cohort $\psize(\psymp)$, represents the average number of forward intervals that an individual in cohort $\psize(\psymp)$ produces over the course of their infection.
+where $W(\psymp)$, the ``weight'' of the primary cohort, represents the average number of forward intervals that an individual in cohort $\psize(\psymp)$ produces over the course of their infection.
 When we measure within-individual delays, we expect $W(\psymp) \leq 1$ because only a subset of individuals who experience the primary event (e.g., infection) will eventually experience the secondary event (e.g., symptom onset).
-When we measure between-individual delays, we expect $W(\psymp)$ to change throughout an epidemic because individuals infected in the beginning of an epidemic will infect more than one individual, on average, over the course of their infection, whereas those infected later will infect less than one individual, on average.
+For between-individual delays, we expect $W(\psymp)$ to change throughout an epidemic, because individuals infected earlier in an epidemic will infect more individuals on average than those infected later.
 
@@
 length $\tau$. 
+\jd{I need to keep thinking about what a cohort is for incubation period.
+Here, you seem to be putting people who don't show symptoms into the forward but not the backward cohort.
+How sure are you that this is right?
+The non-symptomatic people also seem to have $\tau$s?}
 From the right hand side, we see that this probability density depends on the weight parameter $W(\psymp-\tau)$ (in this case, the proportion of symptomatic infection),
@@
 In general, the forward serial-interval distributions will not match the intrinsic or the backward serial-interval distributions.
-Further, the mean forward serial interval can decrease over time due to epidemic dynamics. 
-Failing to account for these differences can result in underestimation of \RR.
+In particular, the mean forward serial interval can decrease over time due to epidemic dynamics. 
+Failing to account for these effects can result in underestimation of \RR.
 
@@
 Changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
-Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series of symptomatic cases or infected cases from the reports of confirmed cases by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential,scire2020reproductive,shim2020transmission});
+Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series from by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential,scire2020reproductive,shim2020transmission});
 these studies effectively assume constant backward delay distributions.
-Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using dynamical approaches that model incidence as well as reporting delays explicitly (e.g., \cite{flaxman2020estimating}).
+Although such approaches may be able to roughly match the time scale of an epidemic, we show here that they are subject to bias.
+Dynamical approaches that model explicitly model incidence as well as reporting delays (e.g., \cite{flaxman2020estimating}) can avoid this problem, but at the cost of more complexity in estimation.
+There is a need for simple methods that can complement more explicit approaches of addressing this problem.
 
@@
 \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
-However, our study demonstrates that early serial-interval data is required to estimate the initial \RR during the exponential growth phase and that using up-to-date serial-interval data (without accounting for changes in the forward serial-interval distribution) can, in fact, underestimate the initial \RR.
+We show here, however, that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can, in fact, exacerbate the underestimation of initial \RR.
 Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase and potentially re-assess existing estimates of \RR.
@@
 these studies should also re-assess whether they appropriately considered the \emph{forward} serial interval.
-Given large geographical variation in the spread of the COVID-19, the forward serial-interval distributions are also likely to vary across countries.
+Forward serial-interval distributions are also likely to vary across countries.
 We suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions and understand their changes over time.
-These modeling approaches should be necessarily coupled with intensive
-epidemiological investigation through contact tracing at the very
-beginning of the outbreak in order to characterize the initial forward
-serial-interval distribution, particularly for an epidemic of an
-emerging disease such as COVID-19.
+These modeling approaches should be coupled with epidemiological investigation through contact tracing. 
+Going forward, an additional advantage of early, intensive contact tracing of emerging diseases is that this is the best way to characterize the initial forward serial-interval distribution.
 
@@
 This implies that not considering this correlation can bias the estimates of the intrinsic generation-interval distribution from the serial-interval distribution.
-Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the dynamical differences between the realized incubation periods of infectors (backward-looking) and those of infectees (forward looking) (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
+Previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the dynamical differences between the realized incubation periods of infectors (backward-looking) and those of infectees (forward looking) (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
 Better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals are needed.
@@
 Here, we assume that all individuals develop symptoms and that the entire transmission process, including all relevant epidemiological delays, is known exactly.
-In practice, asymptomatic and presymptomatic transmission of COVID-19 makes measuring serial intervals difficult \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.
+In practice, identifying who infected whom is difficult in general, and asymptomatic and presymptomatic transmission of COVID-19 exacerbates this difficulty \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.
 Biases in the observed serial intervals will necessarily bias the estimates of \RR. 
-Furthermore, serial intervals do not take into account asymptomatic transmission; 
-neglecting asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
+Furthermore, when one of the individuals is asymptomatic, there is no symptom-based serial interval; 
+neglecting the time scale asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
 
-While we focused on the effect of epidemiological dynamics on the serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
+While we focus here on the effect of epidemiological dynamics on the serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
 Individual-level interventions, such as case isolation, and behavioral responses directly affect individuals' ability to transmit and will shorten the forward generation- and serial-intervals.

### 2020-06-03 serial.tex
Interrupted! Will try to get back this evening and finish

@@
 When the initial forward serial-interval distributions $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen}) for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
-When the intrinsic distributions are used, however, estimates based on the serial interval (\eref{Rintrinsic}) underestimate \Ro; as $r$ increases, \Rintrinsic saturates and eventually \emph{decreases} due to the increasing inferred importance of negative serial intervals (\fref{rR}B).
+When the intrinsic distributions are used, however, estimates based on the serial interval (\eref{Rintrinsic}) underestimate \Ro: as $r$ increases, \Rintrinsic saturates and eventually \emph{decreases} due to the increasing inferred importance of negative serial intervals (\fref{rR}B).
 While the initial forward serial intervals during the exponential growth phase can also be negative, their effects are appropriately balanced because faster epidemic growth leads to longer serial intervals (and a corresponding lower proportion of negative intervals).
@@
 The initial forward serial-interval distribution captures the exponential growth phase of an epidemic.
-Next, we characterize how forward and backward serial intervals vary over the course of an epidemic by running deterministic and stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
+We explore how forward and backward serial intervals can vary over the course of an epidemic using deterministic and stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
 we further assume $\Ro=2.5$.
@@
 
-While we focus here on the effect of epidemiological dynamics on the serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
+While we focus here on the effect of epidemiological dynamics on serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
 Individual-level interventions, such as case isolation, and behavioral responses directly affect individuals' ability to transmit and will shorten the forward generation- and serial-intervals.

### 2020-06-03 serial.tex
lunch

@@
 
-\fref{epi} shows the epidemiological dynamics (A) together with the mean forward (B--D) and the mean backward (E--F) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
-The mean forward incubation period remains constant throughout an epidemic as assumed (\fref{epi}B).
-The mean forward generation interval decreases slightly as incidence increases, causing the proportion of susceptible population to decrease (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
+\fref{epi} shows the epidemiological dynamics (A) together with the mean forward (B--D) and the mean backward (E--G) delay distributions of a deterministic model based on the renewal equation (\eref{renewal}) and of the corresponding stochastic realizations based on individual-based simulations.
+The mean forward incubation period remains constant throughout an epidemic by assumption (\fref{epi}B).
+The mean forward generation interval decreases slightly when incidence is high, which is when the susceptible population declines rapidly (\fref{epi}C; \cite{kenah2008generation, champredon2015intrinsic}).
 In contrast, the mean forward serial interval decreases over time (\fref{epi}D).
@@
 (\fref{diagram}): (i) the backward incubation period, (ii) the forward generation interval, and (iii) the forward incubation period.
-For COVID-19 parameters (Table 1), both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
+In these simulations, both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
 therefore, changes in the forward serial-interval distributions are predominantly driven by changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
-In this case, the increase in the mean backward incubation period directly translates to the decrease in the mean forward serial interval.
 % Since the increase in the mean backward period is driven by the decreasing incidence, which can still occur in the absence of significant depletion of the susceptible pool via intervention, decrease in the mean forward serial interval may be a robust feature in COVID-19 outbreaks.
 In general, relative contributions of the three distributions depend on their shapes, correlations between intrinsic incubation periods and generation intervals, and overall epidemiological dynamics.
+\jd{Am I right that the main thing going on here is the decrease in $r(t)$, which should be a robust feature of outbreaks in general? Can we explain that?}
 

### 2020-06-03 serial.tex
done

@@
 Similarly, when we are measuring serial intervals, a primary cohort consists of all infectors who became symptomatic at time $\psymp$.
-Then, for each primary cohort at time $\psymp$, we can define the expected time distribution between primary and secondary events.
+Then, for \swp{an average individual in} primary cohort at time $\psymp$, we can define the expected time distribution between primary and secondary events. 
 We refer to this distribution as the forward delay distribution and denote it as $f_\psymp(\tau)$.
+\swp{Since the forward delay distribution is defined for an average individual, we do not assume that all individuals who experience the primary event must experience the secondary event.}
 
@@
 the time of infection or backward from the time of symptom onset).
-Consequently, if we restrict attention to individuals with a given
-incubation period, say $\tau$ days, and we count how many became infected at time $\psymp$
-or how many first showed symptoms at time $\ssymp=\psymp+\tau$ then we must obtain
-the same number. In general, no matter how delays are distributed, if
+% Consequently, if we restrict attention to individuals with a given
+% incubation period, say $\tau$ days, and we count how many became infected at time $\psymp$
+% or how many first showed symptoms at time $\ssymp=\psymp+\tau$ then we must obtain
+% the same number. 
+Consequently, no matter how delays are distributed, if
 $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
-secondary cohorts then we must have
+secondary cohorts then we \swp{can express the total density of intervals between time $\psymp$ and $\ssymp$ as follows:}
 \begin{equation}
@@
 \end{equation}
-where $W(\psymp)$, the ``weight'' of the primary cohort, represents the average number of forward intervals that an individual in cohort $\psize(\psymp)$ produces over the course of their infection.
+where $W(\psymp)$, the ``weight'' of the primary cohort, represents the average number of forward intervals that an \swp{average} individual in cohort $\psize(\psymp)$ produces over the course of their infection.
 When we measure within-individual delays, we expect $W(\psymp) \leq 1$ because only a subset of individuals who experience the primary event (e.g., infection) will eventually experience the secondary event (e.g., symptom onset).
@@
 If we are considering incubation periods, the left hand side of
-this equation is the probability density that an individual
+this equation is the probability density that an \swp{average} individual
 who became symptomatic at time $\ssymp$ had an incubation period of
 length $\tau$.
-\jd{I need to keep thinking about what a cohort is for incubation period.
-Here, you seem to be putting people who don't show symptoms into the forward but not the backward cohort.
-How sure are you that this is right?
-The non-symptomatic people also seem to have $\tau$s?}
 From the right hand side, we see that this probability density depends on the weight parameter $W(\psymp-\tau)$ (in this case, the proportion of symptomatic infection),
 the time-varying primary cohort size at the earlier time $\psize(\ssymp-\tau)$ (in this case, the number of individuals became infected at time $\ssymp-\tau$),
-and the forward delay distribution $f_{\ssymp-\tau}(\tau)$ (in this case, the probability density that someone who was infected at time $\ssymp-\tau$ became symptomatic at time $\ssymp$).
+and the forward delay distribution $f_{\ssymp-\tau}(\tau)$ (in this case, the probability density that \swp{an average individual} who was infected at time $\ssymp-\tau$ became symptomatic at time $\ssymp$).
 
@@
 \jd{Am I right that the main thing going on here is the decrease in $r(t)$, which should be a robust feature of outbreaks in general? Can we explain that?}
+\swp{You mean decrease in $i(t)$. I had explained that previously (see what's commented out above; Since the increase ...) but DC complained that he didn't like it. I'd be OK with keeping it in.}
 

### 2020-06-04 serial.tex
Dushoff all the way through

--- 2020-06-03 serial.tex
@@
 Similarly, when we are measuring serial intervals, a primary cohort consists of all infectors who became symptomatic at time $\psymp$.
-Then, for each primary cohort at time $\psymp$, we can define the expected time distribution between primary and secondary events.
+Then, for primary cohort at time $\psymp$, we can define the expected time distribution between primary and secondary events. 
 We refer to this distribution as the forward delay distribution and denote it as $f_\psymp(\tau)$.
@@
 the time of infection or backward from the time of symptom onset).
-Consequently, if we restrict attention to individuals with a given
-incubation period, say $\tau$ days, and we count how many became infected at time $\psymp$
-or how many first showed symptoms at time $\ssymp=\psymp+\tau$ then we must obtain
-the same number. In general, no matter how delays are distributed, if
+% Consequently, if we restrict attention to individuals with a given
+% incubation period, say $\tau$ days, and we count how many became infected at time $\psymp$
+% or how many first showed symptoms at time $\ssymp=\psymp+\tau$ then we must obtain
+% the same number. 
+Consequently, no matter how delays are distributed, if
 $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
-secondary cohorts then we must have
+secondary cohorts then we can express the total density of intervals between time $\psymp$ and $\ssymp$ as follows:
 \begin{equation}
@@
 length $\tau$.
-\jd{I need to keep thinking about what a cohort is for incubation period.
-Here, you seem to be putting people who don't show symptoms into the forward but not the backward cohort.
-How sure are you that this is right?
-The non-symptomatic people also seem to have $\tau$s?}
 From the right hand side, we see that this probability density depends on the weight parameter $W(\psymp-\tau)$ (in this case, the proportion of symptomatic infection),
-the time-varying primary cohort size at the earlier time $\psize(\ssymp-\tau)$ (in this case, the number of individuals became infected at time $\ssymp-\tau$),
-and the forward delay distribution $f_{\ssymp-\tau}(\tau)$ (in this case, the probability density that someone who was infected at time $\ssymp-\tau$ became symptomatic at time $\ssymp$).
+the time-varying primary cohort size at the earlier time $\psize(\ssymp-\tau)$ (in this case, the number of individuals infected at time $\ssymp-\tau$),
+and the forward delay distribution $f_{\ssymp-\tau}(\tau)$ (in this case, the probability density that an incubation period that starts at time $\ssymp-\tau$ ends at time $\ssymp$).
 
@@
 In these simulations, both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
-therefore, changes in the forward serial-interval distributions are predominantly driven by changes in the backward incubation period distributions, whose mean increases over time (\fref{epi}D).
-% Since the increase in the mean backward period is driven by the decreasing incidence, which can still occur in the absence of significant depletion of the susceptible pool via intervention, decrease in the mean forward serial interval may be a robust feature in COVID-19 outbreaks.
+therefore, changes in the forward serial-interval distributions (\fref{epi}D) are predominantly driven by changes in the backward incubation period distribution, whose mean increases over time as the growth rate of disease incidence slows, then becomes negative.
 In general, relative contributions of the three distributions depend on their shapes, correlations between intrinsic incubation periods and generation intervals, and overall epidemiological dynamics.
-\jd{Am I right that the main thing going on here is the decrease in $r(t)$, which should be a robust feature of outbreaks in general? Can we explain that?}
 
@@
 Now, we turn to issues of estimating the reproduction number from the observed serial-interval data during on ongoing epidemic.
-In order to have an unbiased estimate of the basic reproduction number, we need to use serial-interval distributions estimated based on primary cohorts (i.e., infectors who share the same symptom onset time) at the early stage of the epidemic (i.e., initial forward serial-interval distribution).
+In order to have an unbiased estimate of the basic reproduction number, we need to estimate the initial forward serial-interval distribution -- i.e., estimate based on cohorts of infectors who share the same symptom onset time, at the early stage of the epidemic.
 However, researchers typically use all available information to estimate epidemiological parameters;
@@
 
+\jd{Are we worried about censoring vs.\ truncation?}
 When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
@@
 \fref{du}A shows that the mean forward serial interval decreases over time.
-While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum observable serial intervals), the increase in the proportion of negative serial intervals unequivocally indicates changes in the forward serial-interval distribution;
-the increase in the proportion of negative intervals is unlikely to be driven by left-censoring (indicated by the distance between the quantiles of the observed serial intervals and minimum observable serial intervals).
-The decrease in the mean forward serial interval was probably caused by increase in the mean backward incubation period, reflecting decrease in COVID-19 cases in China, as well as intervention efforts which reduced generation intervals by preventing infections once cases were identified.
-\fref{du}B shows that the mean backward serial interval increased over time, also reflecting decrease in COVID-19 cases in China.
+While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum observable serial intervals), the increase in the proportion of negative serial intervals clearly indicates changes in the forward serial-interval distribution;
+this proportion is unlikely to be affected by left-censoring (based on the gap between the quantiles of the observed serial intervals and minimum observable serial intervals).
+The decrease in the mean forward serial interval was probably driven by interventions against spread.
+Interventions during this time period both decreased (and then reversed) the exponential growth of COVID-19 cases --- thus increasing the backward incubation period --- and also reduced generation intervals, by preventing infections once cases were identified.
+\jd{GI shortening does not act through backward incubation primarily, so I took that out.}
+Both of these would have acted to reduce the forward serial interval.
+\fref{du}B shows that the mean backward serial interval increased over time, likely driven directly by the decrease in COVID-19 cases.
 
-While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculate earlier based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
-These results indicate that the incubation period and generation interval (Table 1) may previously have been underestimated as neither study explicitly accounted for the fact that the observed intervals were drawn from the backward distributions and were likely to have been truncated.
+While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculated based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
+These may imply that the incubation period and generation interval (Table 1) were underestimated, as neither study explicitly accounted for the fact that the observed intervals were drawn from the backward distributions and were likely to have been truncated.
 
 \fref{du}C shows the cohort-averaged estimates of \Ro, which remain roughly constant until day 7 and suddenly decreases;
-this sudden decrease is indicative of changes in the forward serial intervals as shown in our simulation study (\fref{obsrR}).
+this sudden decrease is due changes in the forward serial intervals consistent with the dynamics seen in our simulations (\fref{obsrR}).
 The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}:

### 2020-06-04 serial.tex
done!!!!

@@
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds.
-Researchers continue to rely on both generation and serial intervals to estimate the reproduction number \RR of COVID-19, either without making a clear distinction \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}, or explicitly conflating the two intervals
+Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19, either without making a clear distinction \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}, or explicitly conflating the two intervals
 \citep{anderson2020will,hellewell2020feasibility}.
@@
 By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates;
-since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system of exponential growth, both should provide the same correct link between \RR and the epidemic growth rate $r$.
+since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system of exponential growth, both should provide the same correct link between the reproduction number \RR and the epidemic growth rate $r$.
 In contexts where the distributions are expected to be different, current theory has no explanation for how these differing distributions could provide identical estimates of \RR from $r$. 
@@
 
-At the individual level, we can define the time distribution between a primary and a secondary event that we expect to observe for an average infected individual --- we refer to this distribution as the intrinsic distribution.
-For example, the intrinsic incubation period distribution describes the expected time distribution from infection to symptom onset of an average infected individual.
-Likewise, the intrinsic generation-interval distribution describes the expected time distribution of infectious contacts made by an average infected individual.
+At the individual level, we can define the time distribution between a primary and a secondary event that we expect to observe (averaged across individual characteristics) for an infected individual --- we refer to this distribution as the intrinsic distribution.
+For example, the intrinsic incubation period distribution describes the expected time distribution from infection to symptom onset of an infected individual.
+Likewise, the intrinsic generation-interval distribution describes the expected time distribution of infectious contacts made by an infected individual.
 However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., the distribution of time between actual primary and secondary events that occur during an epidemic).
@@
 Typically, within-individual forward delay distributions are not directly affected by epidemic dynamics.
-Some realized distributions, like incubation period distributions, are expected to be equivalent to their intrinsic distributions and remain invariant at time time scale of an outbreak.
+Some realized distributions, like incubation period distributions, are expected to be equivalent to their intrinsic distributions and remain invariant at the time scale of an outbreak.
 Other realized distributions, like the distribution of time from symptom onset to testing, may change over the course of an epidemic due to changes in public health policies.
@@
 
-To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total amount of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
-The amount of serial intervals between time $\psymp$ and $\ssymp$,
+To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total density of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
+The density of serial intervals between time $\psymp$ and $\ssymp$,
 given that the infectors became infected at time $\pinf\le\psymp$ and
@@
 During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t) \approx i_0\exp(rt)$.
-During this period, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the initial reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation};
-in this case, we focus on the estimates of the basic reproduction number \Ro (the value of \RR in a fully susceptible population, $S(t) \approx 1$):
+During this period, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the initial reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation}.
+Here, we focus on the estimates of the basic reproduction number \Ro (the value of \RR in a fully susceptible population, $S(t) \approx 1$):
 \begin{equation}
@@
 \begin{equation}
-f_{0}(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
+f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{0} \int_{\pinf}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf,
 \label{eq:initialSI}
 \end{equation}
+where the normalization constant $\phi$ is determined by the
+requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
 In Supplementary Materials, we provide a mathematical proof of this relationship.
@@
 \begin{equation}
-\frac{1}{\Rintrinsic} = \int_{-\infty}^\infty \exp(-r\tau) q(\tau) \mathrm{d} \tau,
+\frac{1}{\Rintrinsic} = \int_{-\infty}^\infty \exp(-r\tau) q(\tau) \mathrm{d} \tau.
 \label{eq:Rintrinsic}
 \end{equation}
-where the intrinsic serial-interval distribution $q(\tau)$ does not depend on epidemic dynamics:
+Here, the intrinsic serial-interval distribution $q(\tau)$ does not depend on epidemic dynamics:
 \begin{equation}
-q(\tau) \propto \int_{-\infty}^{0} \int_{\pinf}^{\tau} h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
+q(\tau) = \frac{1}{\phi_q} \int_{-\infty}^{0} \int_{\pinf}^{\tau} h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf,
 \label{eq:intrinsicSI}
 \end{equation}
+where the normalization constant $\phi_q$ is determined by the
+requirement that $\int_{-\infty}^\infty q(\tau)\,\dtau=1$.
 Rather than numerically integrating over closed forms of $g$, $f_0$, and $q$ to estimate $\Ro$, we use simulation-based approaches for simplicity (Supplementary Materials).
@@
 
-\begin{table}[!th]
+\begin{table}[!ht]
 \begin{center}
@@
 
-We use parameter estimates for COVID-19 to characterize the degree to which the serial-interval distribution can change over the course of the epidemic and evaluate how different definitions of the serial-interval distribution can affect the Euler-Lotka estimates of \Ro.
-We further address how the observed serial intervals are affected by the right truncation during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial interval data to estimate \Ro.
+We use parameter estimates for COVID-19 to characterize the degree to which the realized serial-interval distribution can change over the course of the epidemic and evaluate how different definitions of the serial-interval distribution can affect the Euler-Lotka estimates of \Ro.
+We further address how the observed serial intervals, measured through contact tracing, are affected by the right censoring during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial interval data to estimate \Ro.
 Finally, we analyze the serial interval data from the COVID-19 epidemic in China under our framework.
@@
 The effects of higher means (which increase \Ro) exactly cancel those of higher variability (which decrease \Ro).
-On the other hand, \emph{intrinsic} serial intervals (\eref{intrinsicSI}) have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are wider (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
+On the other hand, \emph{intrinsic} serial intervals (\eref{intrinsicSI}) have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are more variable (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
 therefore, we underestimate \Ro when we use the intrinsic serial-interval distribution.
@@
 Now, we turn to issues of estimating the reproduction number from the observed serial-interval data during on ongoing epidemic.
-In order to have an unbiased estimate of the basic reproduction number, we need to estimate the initial forward serial-interval distribution -- i.e., estimate based on cohorts of infectors who share the same symptom onset time, at the early stage of the epidemic.
+In order to have an unbiased estimate of the basic reproduction number, we need to estimate the initial forward serial-interval distribution --- i.e., estimate based on cohorts of infectors who share the same symptom onset time, at the early stage of the epidemic.
 However, researchers typically use all available information to estimate epidemiological parameters;
@@
 
-\jd{Are we worried about censoring vs.\ truncation?}
 When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
@@
 
-Here we provide a heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \Ro retrospectively.
+Here, we provide a heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \Ro retrospectively.
 We can rearrange the line list and group observed serial intervals based on the symptom onset date of infectors (\fref{obsrR}C).
@@
 However, the cohort-averaged estimates decrease rapidly soon after the exponential growth period, reflecting changes in the forward serial-interval distributions.
-This approach allows us to detect dynamical changes in the forward serial-interval distributions and its effect on the estimates of \Ro.
+This approach allows us to detect dynamical changes in the forward serial-interval distributions and their effect on the estimates of \Ro.
 
@@
 Solid lines represent the estimated locally estimated scatterplot smoothing (LOESS) fits.
-The dashed line represents the maximum and minimum observable delays across the range of reported sypmtom onset dates.
+The dashed line represents the maximum and minimum observable delays across the range of reported symptom onset dates.
 (C) Cohort-averaged estimates of \Ro assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
@@
 \fref{du}A shows that the mean forward serial interval decreases over time.
-While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum observable serial intervals), the increase in the proportion of negative serial intervals clearly indicates changes in the forward serial-interval distribution;
+While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum observable serial intervals), the increase in the proportion of negative serial intervals indicates changes in the forward serial-interval distribution;
 this proportion is unlikely to be affected by left-censoring (based on the gap between the quantiles of the observed serial intervals and minimum observable serial intervals).
 The decrease in the mean forward serial interval was probably driven by interventions against spread.
-Interventions during this time period both decreased (and then reversed) the exponential growth of COVID-19 cases --- thus increasing the backward incubation period --- and also reduced generation intervals, by preventing infections once cases were identified.
-\jd{GI shortening does not act through backward incubation primarily, so I took that out.}
+Interventions during this time period both decreased (and then reversed) the growth rate of COVID-19 cases --- thus increasing the backward incubation period --- and also reduced generation intervals, by preventing infections once cases were identified.
 Both of these would have acted to reduce the forward serial interval.
@@
 While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculated based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
-These may imply that the incubation period and generation interval (Table 1) were underestimated, as neither study explicitly accounted for the fact that the observed intervals were drawn from the backward distributions and were likely to have been truncated.
+These may imply that the incubation period and generation interval (Table 1) were underestimated, as neither study explicitly accounted for the fact that the observed intervals were drawn from the backward distributions and were likely to have been censored.
 

### 2020-08-26 serial.tex
update

@@
 $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
-secondary cohorts then we can express the total density of intervals between time $\psymp$ and $\ssymp$ as follows:
+secondary cohorts then we can express the total density of intervals $\tau$ between calendar time $\psymp$ and $\ssymp$ (i.e., $\tau=\ssymp-\psymp$) as follows:
 \begin{equation}
@@
 length $\tau$.
-From the right hand side, we see that this probability density depends on the weight parameter $W(\psymp-\tau)$ (in this case, the proportion of symptomatic infection),
+From the right hand side, we see that this probability density depends on the weight parameter $W(\ssymp-\tau)$ (in this case, the proportion of symptomatic infection),
 the time-varying primary cohort size at the earlier time $\psize(\ssymp-\tau)$ (in this case, the number of individuals infected at time $\ssymp-\tau$),
@@
 Other realized distributions, like the distribution of time from symptom onset to testing, may change over the course of an epidemic due to changes in public health policies.
-Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics;
-for example, forward generation intervals contract during the outbreak because infected individuals are less likely to infect others later in the epidemic due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.
+Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics.
+For example, shorter generation intervals are more likely to be realized later in the \emph{epidemic} (therefore, leading to ``contraction'' of generation intervals) because infected individuals are less likely to infect others later in their \emph{infection} due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.
 
@@
 where $r$ is the exponential growth rate (and $\left[W(0) \psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
-Thus, for faster epidemics (higher $r$), the backward delay distribution will have a shorter mean.
+Thus, as the growth rate $r$ of an epidemic increases, the mean backward delay distribution will decrease, leading to stronger bias.
 In general, the backward delay distribution will differ from the forward delay distribution (unless the disease is at equilibrium), even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
@@
 interval between the infector and the infectee.
-These studies assume that $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions and concluded that the serial and generation intervals have the same mean \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, this conclusion is based on the implicit assumption that distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$, as well as generation interval, $\gtime$, are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
+These studies concluded that the serial and generation intervals have the same mean when $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
+however, distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$ will be identical only if we assume that they are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
 something that is generally true of forward but not backward incubation-period distributions.
-We refer to the definition \eref{intser} as the intrinsic
-serial interval (\fref{diagram}A).
+We refer to the definition \eref{intser} as the intrinsic serial interval (\fref{diagram}A).
 
@@
 \end{equation}
-This framework allows us to understand changes in the realized serial intervals for any deterministic epidemic model.
+This framework allows us to understand changes in the realized serial intervals for any epidemic model.
 
@@
 The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}:
-$\Ro = 2.6$ (95\% CI: 2.2--3.1) and $\Ro = 3.4$ (95\% CI: 2.7 -- 4.3) based on 8 and 6 doubling periods, respectively, using serial-interval data from infectors who developed symptoms by day 7.
+$\Ro = 2.6$ (95\% CI: 2.2--3.1) and $\Ro = 3.4$ (95\% CI: 2.7 -- 4.3) based on a doubling period of 8 or 6 days, respectively, using serial-interval data from infectors who developed symptoms by day 7.
 These early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
@@
 they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
-\cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
-We show here, however, that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can, in fact, exacerbate the underestimation of initial \RR.
+For example, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
+However, our results show that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can, in fact, exacerbate the underestimation of initial \RR.
 Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase and potentially re-assess existing estimates of \RR.

### 2020-08-28 serial.tex
push

@@
 \newcommand{\Rc}{\Rx{\mathrm{c}}}
+\newcommand{\Rs}{\Rx{\mathrm{s}}}
 \newcommand{\RR}{\ensuremath{{\mathcal R}}\xspace}
@@
 the value in a fully susceptible population --- the ``basic'' reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population, and the amount of intervention necessary to eliminate it \citep{anderson1991infectious}.
-Near the beginning of an outbreak, \RR is often estimated from the observed exponential growth rate using generation- and serial-interval distributions (e.g., \cite{wallinga2007generation, fraser2009pandemic, hampson2009transmission, chunara2012social, chowell2014west, du2020serial, jung2020real}) but the differences among two distributions are often neglected.
+Since the reproduction number represents an average \citep{diekmann1990definition, anderson1991infectious}, it does not capture heterogeneity among individuals or across space.
+The reproduction number also does not provide any information about the time scale of disease transmission.
 
-The generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee);
-the generation-interval distribution determines the relationship between the exponential growth rate $r$ and the reproduction number \RR \citep{anderson1991infectious, ferguson2005strategies, wallinga2007generation}.
-Similarly, the serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
-While serial intervals are similar to generation intervals, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
+Estimating the reproduction number \RR is challenging because it cannot be measured directly.
+It often requires a detailed knowledge of the disease history and reliable incidence data.
+Instead, near the beginning of an epidemic, \RR can be estimated from the population-level exponential growth rate.
+This approach is convenient because the growth rate can be estimated robustly from case reports \citep{mills2004transmissibility, ma2014estimating}.
+These two quantities, representing the speed $r$ and strength $\RR$ of an epidemic, are linked by the generation-interval distribution \cite{wallinga2007generation}, where the generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee) \citep{svensson2007note}.
+
+Since generation intervals measure time between infection events, which can be difficult to observe in practice, generation intervals are often replaced with serial intervals.
+The serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
+While generation and serial intervals both measure the time scale of disease transmission, they measure fundamentally different quantities. 
+In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean, assuming that the incubation periods of the infector and infectee are identically distributed \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
+Serial intervals can also take negative values due to presymptomatic transmission \citep{he2020temporal}, whereas generation intervals are confinsed to positive values.
 
@@
 It is well established that this renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
-By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates;
-since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system of exponential growth, both should provide the same correct link between the reproduction number \RR and the epidemic growth rate $r$.
+By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates.
+Since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system of exponential growth, both should provide the same correct link between the reproduction number \RR and the epidemic growth rate $r$.
+
 In contexts where the distributions are expected to be different, current theory has no explanation for how these differing distributions could provide identical estimates of \RR from $r$.
-Some studies have further suggested that using serial intervals can underestimate \RR because the serial-interval distribution is wider than the generation-interval distribution \citep{britton2019estimation, ganyani2020estimating}.
+In fact, recent theory suggest that using serial-interval can underestimate the reproduction number \citep{britton2019estimation, ganyani2020estimating}.
+However, these studies rely on imprecise definitions of the serial-interval distribution, relying on \emph{intrinsic} distributions of incubation periods and generation intervals that neglect the population-level dynamics of the disease spread.
+During an ongoing epidemic, \emph{all} observed epidemiological delays between primary and secondary events (e.g., infection and symptom onset) are subject to backward biases: when incidence of primary events is increasing (or decreasing), we are more likely to observe shorter (or longer) intervals.
+Since serial intervals depend on three distinct intervals (i.e., incubation period of the infector, incubation period of the infectee, and the generation interval between them), any of these intervals can be subject to backward biases depending on our perspective.
+Therefore, it is not always safe to assume that the incubation periods of the infector and the infectee are drawn from the same distribution.
 
 Here, we resolve this apparent discrepancy by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
-We develop a new framework for characterizing and comparing serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
+We develop a cohort-based framework for characterizing and comparing serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
 Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of \RR.
-We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the reproduction number during the early stages of an outbreak.
+We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the initial reproduction number during the early stages of an outbreak.
 
@@
 Similarly, when we are measuring serial intervals, a primary cohort consists of all infectors who became symptomatic at time $\psymp$.
-Then, for primary cohort at time $\psymp$, we can define the expected time distribution between primary and secondary events. 
+Then, for a primary cohort at time $\psymp$, we can define the expected time distribution between primary and secondary events. 
 We refer to this distribution as the forward delay distribution and denote it as $f_\psymp(\tau)$.
@@
 the time of infection or backward from the time of symptom onset).
-% Consequently, if we restrict attention to individuals with a given
-% incubation period, say $\tau$ days, and we count how many became infected at time $\psymp$
-% or how many first showed symptoms at time $\ssymp=\psymp+\tau$ then we must obtain
-% the same number. 
 Consequently, no matter how delays are distributed, if
@@
 \end{equation}
-where the case reproduction number $\Rc (\pinf)$ is defined as the average number of secondary cases caused by a primary case infected at time $\pinf$ over the course of their infection \citep{fraser2007estimating}.
+where the case reproduction number $\Rc (\pinf)$ is defined as the average number of secondary cases that a primary case infected at time $\pinf$ will generate over the course of their infection \citep{fraser2007estimating}.
 We describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
@@
 
-The total amount of serial intervals can now be obtained by integrating over all possible infection times for the infector and the infectee:
+The total density of serial intervals can now be obtained by integrating over all possible infection times for the infector and the infectee:
 \begin{equation}
@@
 \end{equation}
-Then, the forward serial-interval distribution $f_\psymp(\tau)$ is given by the density of intervals of length $\tau$ starting at \psymp, relative to the total number of serial intervals starting at \psymp:
+Then, the forward serial-interval distribution $f_\psymp(\tau)$ is given by the density of intervals of length $\tau$ starting at time \psymp, relative to the total number of serial intervals starting at time \psymp:
 \begin{equation}
@@
 \end{equation}
-Likewise, the backward serial-interval distribution $b_\ssymp(\tau)$ is given by the density of intervals of length $\tau$ ending at \ssymp, relative to the total number of serial intervals ending at \ssymp:
+The denominator, $\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'$, then corresponds to the total number of symptomatic cases generated by primary cases who developed at time \psymp;
+dividing it by the incidence of symptomatic cases (also infected by symptomatic cases) at time \psymp, $j(\psymp) = \int_{-\infty}^\infty \total(\psymp-\tau', \psymp) \dtau'$, we obtain the serial reproduction number:
+\begin{equation}
+\Rs(\psymp) = \frac{\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'}{j(\psymp)},
+\end{equation}
+which we define as the average number of symptomatic cases generated by individuals who developed symptoms at time \psymp (and were also infected by sympmtomatic cases).
+Combining the forward serial-interval distribution with the serial reproduction number allows us to express the renewal process between symptomatic cases:
+\begin{equation}
+j(t) = \int_{-\infty}^\infty \Rs(t-\tau) j(t-\tau) f_{t-\tau}(\tau) \dtau.
+\label{eq:jrenew}
+\end{equation}
+In Supplementary Materials, we show that estimating the serial reproduction number requires the backward serial-interval distribution $b_\ssymp(\tau)$, which is given by the density of intervals of length $\tau$ ending at \ssymp, relative to the total number of serial intervals ending at \ssymp:
 \begin{equation}
@@
 \end{equation}
-This framework allows us to understand changes in the realized serial intervals for any epidemic model.
+This framework allows us to understand changes in the realized serial intervals for any epidemic model and link serial-interval distributions with the renewal process.
 
@@
 We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
-Ignoring births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be written as:
+Ignoring births and deaths, general changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be described as:
 \begin{align}
 \frac{\mathrm{d}S}{\mathrm{d}t} &= - i(t)\nonumber\\
-i(t) &= \Ro S(t) \int_0^\infty i(t-\tau) \gdist(\tau) \dtau,
+i(t) &= \RR(t) \int_0^\infty i(t-\tau) \gdist(\tau) \dtau,
 \label{eq:renewal}
 \end{align}
-where \Ro is the basic reproduction number, and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a population where the number of susceptibles remains constant).
+where $\RR(t)$ is the instantaneous reproduction number (i.e., the average number of secondary cases that a primary case infected at time $t$ will generate if conditions at time $t$ remains unchanged \citep{fraser2007estimating}), and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a population where changes in $\RR(t)$ is negligible \citep{champredon2015intrinsic}).
+This model effectively assumes that epidemic dynamics are driven by changes in transmission rate, which may not hold under individual-based intervention such as case isolation \citep{fraser2007estimating};
+nonetheless, this form has been widely used in the literature and has been successfully applied in modeling the current COVID-19 pandemic.
+
+Here, we consider a specific example where changes in the reproduction number is driven by susceptible depletion: $\RR(t) = \Ro S(t)$, where \Ro represents the basic reproduction number.
 Then, the forward generation-interval for a cohort of individuals that were infected at time $\psymp$ follows \citep{champredon2015intrinsic}:
@@
 \begin{align}
-\idist(x) &= \int_0^\infty h(x, \tau) \dtau\nonumber\\
-\gdist(\tau) &= \int_0^\infty h(x, \tau) \dx
+\idist(x) &= \int_0^\infty h(x, \tau) \dtau\nonumber,\\
+\gdist(\tau) &= \int_0^\infty h(x, \tau) \dx.
 \label{eq:marginal}
@@
 requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
-In Supplementary Materials, we provide a mathematical proof of this relationship.
+Since we have not yet made any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, this conclusion is robust, regardless of whether presymptomatic is possible or not.
+It is straightforward to see this relationship from \eref{jrenew} (by substituting $j(t) \approx j(0) \exp(rt)$ and $\Rs(t) \approx \Ro$);
+in Supplementary Materials, we provide a more detailed mathematical proof of this relationship.
 We further compare this with the estimate of \Ro based on the intrinsic serial-interval distribution $q(\tau)$:
@@
 The initial forward serial-interval distribution depends on the exponential growth rate $r$.
-For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short (\eref{backexp}), and therefore, the forward serial-interval distribution will generally have a larger mean than the intrinsic generation- and serial-interval distributions.
-The Susceptible-Exposed-Infected-Recovered model, under the additional assumption that the incubation and exposed periods are equivalent (i.e.
+For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short (\eref{backexp}), meaning that presymptomatic transmission is less likely to occur; 
+therefore, the initial forward serial-interval distribution will generally have a larger mean than the intrinsic generation- and serial-interval distributions.
+However, the exact shape of the initial forward serial-interval distribution depends on the shape of the joint distribution.
+For example, the Susceptible-Exposed-Infected-Recovered model, under the additional assumption that the incubation and exposed periods are equivalent (i.e.
 that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
+Throughout the paper, we allow for presymptomatic transmission to match the transmission dynamics of COVID-19.a
 
@@
 
-We parameterize our model based on parameter estimates for COVID-19 (Table 1).
+The dynamics of the serial-interval distribution depends heavily on the joint distribution between incubation periods and generation intervals.
+Here, we use a bivariate lognormal distribution to model the joint probability distribution of the intrinsic incubation periods and the intrinsic generation intervals while allowing for the possibility that they might be correlated.
+Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset, we generally expect the generation intervals to be positively correlated with the incubation period;
+that is, individuals who develop symptoms later are more likely to transmit later.
+The marginal lognormal distributions are parameterized based on parameter estimates for COVID-19 (Table 1).
 We use a bivariate lognormal distribution to model the joint probability distribution of the intrinsic incubation periods and the intrinsic generation intervals while allowing for the possibility that they might be correlated.

### 2020-08-28 serial.tex
update

@@
 that is, individuals who develop symptoms later are more likely to transmit later.
-The marginal lognormal distributions are parameterized based on parameter estimates for COVID-19 (Table 1).
-We use a bivariate lognormal distribution to model the joint probability distribution of the intrinsic incubation periods and the intrinsic generation intervals while allowing for the possibility that they might be correlated.
+Marginal distributions of incubation periods and generation intervals are parameterized based on parameter estimates for COVID-19 (Table 1).
 For simplicity, we consider three values for the correlation coefficients (on the log scale) of the bivariate lognormal distribution: $\rho = -0.5, 0, 0.5$.

### 2020-08-28 rR.R

@@ -16,13 +16,23 @@ sd(rlnorm(50000, meanlog = 1.62, sdlog=0.42)) ## 2.4
 mean(rlnorm(50000, meanlog = 1.54, sdlog=0.37)) ## 5 days
 sd(rlnorm(50000, meanlog = 1.54, sdlog=0.37)) ## 1.9 days
 
-ww <- c(1, 5, 9, 13, 17, 21, 25, 29)
+ww <- c(1, 6, 11, 16, 21, 26)
 
 rRdata <- list(
   data.frame(
-    r=seq(0, 0.3, by=0.01)[ww],
-    R=sapply(seq(0, 0.3, by=0.01)[ww], function(x) serialR(x, rho=0.5)$R),
+    r=seq(0, 0.3, by=0.01)[ww+4],
+    R=sapply(seq(0, 0.3, by=0.01)[ww+4], function(x) serialR(x, rho=0.75)$R),
+    type="Forward serial interval ($\\rho=0.75$)"
+  ),
+  data.frame(
+    r=seq(0, 0.3, by=0.01)[ww+3],
+    R=sapply(seq(0, 0.3, by=0.01)[ww+3], function(x) serialR(x, rho=0.5)$R),
     type="Forward serial interval ($\\rho=0.5$)"
+  ),
+  data.frame(
+    r=seq(0, 0.3, by=0.01)[ww+2],
+    R=sapply(seq(0, 0.3, by=0.01)[ww+2], function(x) serialR(x, rho=0.25)$R),
+    type="Forward serial interval ($\\rho=0.25$)"
   ),
   data.frame(
     r=seq(0, 0.3, by=0.01)[ww+1],
@@ -30,25 +40,22 @@ rRdata <- list(
     type="Forward serial interval ($\\rho=0$)"
   ),
   data.frame(
-    r=seq(0, 0.3, by=0.01)[ww+2],
-    R=sapply(seq(0, 0.3, by=0.01)[ww+2], function(x) serialR(x, rho=-0.5)$R),
-    type="Forward serial interval ($\\rho=-0.5$)"
-  ),
-  data.frame(
-    r=seq(0, 0.3, by=0.01)[head(ww,-1)+3],
-    R=sapply(seq(0, 0.3, by=0.01)[head(ww,-1)+3], function(x) generationR(x)$R),
+    r=seq(0, 0.3, by=0.01)[ww],
+    R=sapply(seq(0, 0.3, by=0.01)[ww], function(x) generationR(x)$R),
[…]

### 2020-08-28 rR.tex
still making so many changes!!
update

@@
-% Created by tikzDevice version 0.12.3 on 2020-04-29 03:55:17
+% Created by tikzDevice version 0.12.3 on 2020-08-27 23:38:11
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 52.94,254.97) --
-	( 55.54,255.77) --
-	( 58.13,256.58) --
-	( 60.73,257.40) --
-	( 63.32,258.23) --
-	( 65.92,259.08) --
-	( 68.51,259.94) --
-	( 71.11,260.81) --
-	( 73.70,261.69) --
-	( 76.30,262.59) --
-	( 78.89,263.49) --
-	( 81.49,264.42) --
-	( 84.08,265.35) --
-	( 86.68,266.30) --
-	( 89.27,267.26) --
-	( 91.87,268.23) --
-	( 94.46,269.21) --
-	( 97.06,270.20) --
-	( 99.65,271.21) --
-	(102.25,272.23) --
-	(104.84,273.26) --
-	(107.44,274.30) --
-	(110.03,275.36) --
-	(112.63,276.43) --
-	(115.22,277.51) --
-	(117.82,278.61) --
-	(120.41,279.72) --
-	(123.01,280.84) --
-	(125.60,281.98) --
-	(128.20,283.13) --
-	(130.79,284.29) --
-	(133.39,285.46) --
-	(135.98,286.65) --
-	(138.58,287.85) --
-	(141.17,289.07) --
-	(143.77,290.31) --
-	(146.36,291.55) --
-	(148.96,292.82) --
-	(151.55,294.10) --
-	(154.15,295.40) --
-	(156.74,296.71) --
-	(159.34,298.04) --
-	(161.93,299.39) --
-	(164.53,300.75) --
-	(167.12,302.12) --
-	(169.72,303.51) --
-	(172.31,304.92) --
-	(174.91,306.34) --
-	(177.51,307.78) --
-	(180.10,309.24) --
-	(182.70,310.71) --
-	(185.29,312.21) --
-	(187.89,313.72) --
-	(190.48,315.26) --
-	(193.08,316.81) --
-	(195.67,318.38) --
-	(198.27,319.97) --
-	(200.86,321.57) --
-	(203.46,323.20) --
-	(206.05,324.84) --
-	(208.65,326.51) --
-	(211.24,328.19) --
-	(213.84,329.89) --
-	(216.43,331.62) --
-	(219.03,333.36) --
-	(221.62,335.12) --
-	(224.22,336.91) --
-	(226.81,338.72) --
-	(229.41,340.54) --
-	(232.00,342.39) --
-	(234.60,344.25) --
-	(237.19,346.14) --
-	(239.79,348.04) --
-	(242.38,349.97) --
-	(244.98,351.91) --
-	(247.57,353.87) --
-	(250.17,355.85) --
-	(252.76,357.85) --
-	(255.36,359.88) --
-	(257.95,361.92);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.50) --
+	( 30.02,248.23) --
+	( 32.72,248.97) --
+	( 35.42,249.73) --
+	( 38.13,250.50) --
+	( 40.83,251.28) --
+	( 43.53,252.08) --
+	( 46.24,252.88) --
+	( 48.94,253.70) --
+	( 51.64,254.53) --
+	( 54.35,255.37) --
+	( 57.05,256.23) --
+	( 59.75,257.09) --
+	( 62.46,257.97) --
+	( 65.16,258.86) --
+	( 67.86,259.76) --
+	( 70.57,260.67) --
+	( 73.27,261.60) --
+	( 75.97,262.53) --
+	( 78.67,263.48) --
+	( 81.38,264.43) --
+	( 84.08,265.40) --
+	( 86.78,266.38) --
+	( 89.49,267.37) --
+	( 92.19,268.38) --
+	( 94.89,269.40) --
+	( 97.60,270.43) --
+	(100.30,271.47) --
+	(103.00,272.54) --
+	(105.71,273.61) --
+	(108.41,274.70) --
+	(111.11,275.81) --
+	(113.82,276.93) --
+	(116.52,278.07) --
+	(119.22,279.22) --
+	(121.93,280.38) --
+	(124.63,281.55) --
+	(127.33,282.74) --
+	(130.04,283.95) --
+	(132.74,285.16) --
+	(135.44,286.40) --
+	(138.15,287.65) --
+	(140.85,288.91) --
+	(143.55,290.20) --
+	(146.26,291.50) --
+	(148.96,292.81) --
+	(151.66,294.15) --
+	(154.37,295.51) --
+	(157.07,296.88) --
+	(159.77,298.27) --
+	(162.48,299.67) --
+	(165.18,301.09) --
+	(167.88,302.53) --
+	(170.58,303.98) --
+	(173.29,305.45) --
+	(175.99,306.94) --
+	(178.69,308.45) --
+	(181.40,309.97) --
+	(184.10,311.51) --
+	(186.80,313.08) --
+	(189.51,314.67) --
+	(192.21,316.27) --
+	(194.91,317.90) --
+	(197.62,319.55) --
+	(200.32,321.23) --
+	(203.02,322.92) --
+	(205.73,324.64) --
+	(208.43,326.37) --
+	(211.13,328.13) --
+	(213.84,329.90) --
+	(216.54,331.70) --
+	(219.24,333.51) --
+	(221.95,335.35) --
+	(224.65,337.21) --
+	(227.35,339.08) --
+	(230.06,340.98) --
+	(232.76,342.90) --
+	(235.46,344.83) --
+	(238.17,346.79) --
+	(240.87,348.77);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.52) --
-	( 30.34,248.34) --
-	( 33.37,249.16) --
-	( 36.40,250.01) --
-	( 39.42,250.87) --
-	( 42.45,251.74) --
-	( 45.48,252.64) --
-	( 48.51,253.54) --
-	( 51.53,254.47) --
-	( 54.56,255.41) --
-	( 57.59,256.36) --
-	( 60.62,257.34) --
-	( 63.64,258.32) --
-	( 66.67,259.33) --
-	( 69.70,260.35) --
-	( 72.73,261.38) --
-	( 75.76,262.43) --
-	( 78.78,263.50) --
-	( 81.81,264.58) --
-	( 84.84,265.68) --
-	( 87.87,266.80) --
-	( 90.89,267.93) --
-	( 93.92,269.08) --
-	( 96.95,270.25) --
-	( 99.98,271.42) --
-	(103.00,272.61) --
-	(106.03,273.81) --
-	(109.06,275.03) --
-	(112.09,276.26) --
-	(115.11,277.51) --
-	(118.14,278.77) --
-	(121.17,280.06) --
-	(124.20,281.37) --
-	(127.22,282.71) --
-	(130.25,284.06) --
-	(133.28,285.44) --
-	(136.31,286.83) --
-	(139.34,288.23) --
-	(142.36,289.64) --
-	(145.39,291.08) --
-	(148.42,292.53) --
-	(151.45,294.01) --
-	(154.47,295.51) --
-	(157.50,297.03) --
-	(160.53,298.59) --
-	(163.56,300.17) --
-	(166.58,301.77) --
-	(169.61,303.39) --
-	(172.64,305.02) --
-	(175.67,306.68) --
-	(178.69,308.35) --
-	(181.72,310.04) --
-	(184.75,311.76) --
-	(187.78,313.51) --
-	(190.80,315.28) --
-	(193.83,317.09) --
-	(196.86,318.92) --
-	(199.89,320.80) --
-	(202.92,322.69) --
-	(205.94,324.62) --
-	(208.97,326.56) --
-	(212.00,328.54) --
-	(215.03,330.54) --
-	(218.05,332.56) --
-	(221.08,334.62) --
-	(224.11,336.70) --
-	(227.14,338.80) --
-	(230.16,340.94) --
-	(233.19,343.10) --
-	(236.22,345.29) --
-	(239.25,347.50) --
-	(242.27,349.75) --
-	(245.30,352.02) --
-	(248.33,354.31) --
-	(251.36,356.63) --
-	(254.39,358.98) --
-	(257.41,361.36) --
-	(260.44,363.76) --
-	(263.47,366.19) --
-	(266.50,368.65);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 61.48,257.69) --
+	( 64.19,258.56) --
+	( 66.89,259.45) --
+	( 69.59,260.35) --
+	( 72.30,261.26) --
+	( 75.00,262.19) --
+	( 77.70,263.13) --
+	( 80.40,264.08) --
+	( 83.11,265.05) --
+	( 85.81,266.03) --
+	( 88.51,267.03) --
+	( 91.22,268.04) --
+	( 93.92,269.06) --
+	( 96.62,270.09) --
+	( 99.33,271.14) --
+	(102.03,272.21) --
+	(104.73,273.28) --
+	(107.44,274.37) --
+	(110.14,275.47) --
+	(112.84,276.58) --
+	(115.55,277.71) --
+	(118.25,278.84) --
+	(120.95,279.99) --
+	(123.66,281.16) --
+	(126.36,282.34) --
+	(129.06,283.53) --
+	(131.77,284.74) --
+	(134.47,285.97) --
+	(137.17,287.21) --
+	(139.88,288.47) --
+	(142.58,289.75) --
+	(145.28,291.04) --
+	(147.99,292.36) --
+	(150.69,293.69) --
+	(153.39,295.03) --
+	(156.10,296.39) --
+	(158.80,297.76) --
+	(161.50,299.15) --
+	(164.21,300.55) --
+	(166.91,301.97) --
+	(169.61,303.41) --
+	(172.31,304.87) --
+	(175.02,306.34) --
+	(177.72,307.84) --
+	(180.42,309.35) --
+	(183.13,310.89) --
+	(185.83,312.45) --
+	(188.53,314.03) --
+	(191.24,315.62) --
+	(193.94,317.24) --
+	(196.64,318.87) --
+	(199.35,320.53) --
+	(202.05,322.19) --
+	(204.75,323.88) --
+	(207.46,325.59) --
+	(210.16,327.32) --
+	(212.86,329.07) --
+	(215.57,330.84) --
+	(218.27,332.63) --
+	(220.97,334.45) --
+	(223.68,336.29) --
+	(226.38,338.15) --
+	(229.08,340.04) --
+	(231.79,341.96) --
+	(234.49,343.90) --
+	(237.19,345.87) --
+	(239.90,347.86) --
+	(242.60,349.87) --
+	(245.30,351.90) --
+	(248.01,353.96) --
+	(250.71,356.04) --
+	(253.41,358.15) --
+	(256.12,360.28) --
+	(258.82,362.43) --
+	(261.52,364.60) --
+	(264.22,366.80) --
+	(266.93,369.02) --
+	(269.63,371.27) --
+	(272.33,373.53) --
+	(275.04,375.82);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.86,249.91) --
-	( 38.88,250.76) --
-	( 41.91,251.62) --
-	( 44.94,252.51) --
-	( 47.97,253.41) --
-	( 50.99,254.32) --
-	( 54.02,255.26) --
-	( 57.05,256.21) --
-	( 60.08,257.17) --
-	( 63.10,258.15) --
-	( 66.13,259.15) --
-	( 69.16,260.17) --
-	( 72.19,261.20) --
-	( 75.21,262.25) --
-	( 78.24,263.31) --
-	( 81.27,264.39) --
-	( 84.30,265.48) --
-	( 87.33,266.60) --
-	( 90.35,267.72) --
-	( 93.38,268.87) --
-	( 96.41,270.03) --
-	( 99.44,271.21) --
-	(102.46,272.41) --
-	(105.49,273.62) --
-	(108.52,274.84) --
-	(111.55,276.08) --
-	(114.57,277.32) --
-	(117.60,278.59) --
-	(120.63,279.86) --
-	(123.66,281.16) --
-	(126.68,282.48) --
-	(129.71,283.81) --
-	(132.74,285.17) --
-	(135.77,286.56) --
-	(138.79,287.97) --
-	(141.82,289.39) --
-	(144.85,290.83) --
-	(147.88,292.29) --
-	(150.91,293.76) --
-	(153.93,295.24) --
-	(156.96,296.75) --
-	(159.99,298.28) --
-	(163.02,299.84) --
-	(166.04,301.42) --
-	(169.07,303.03) --
-	(172.10,304.67) --
-	(175.13,306.33) --
-	(178.15,308.01) --
-	(181.18,309.70) --
-	(184.21,311.42) --
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 52.94,254.98) --
+	( 55.64,255.81) --
+	( 58.35,256.66) --
+	( 61.05,257.53) --
+	( 63.75,258.41) --
+	( 66.46,259.30) --
+	( 69.16,260.20) --
+	( 71.86,261.12) --
+	( 74.57,262.04) --
+	( 77.27,262.99) --
+	( 79.97,263.94) --
+	( 82.68,264.91) --
+	( 85.38,265.89) --
+	( 88.08,266.89) --
+	( 90.79,267.90) --
+	( 93.49,268.92) --
+	( 96.19,269.95) --
+	( 98.89,271.00) --
+	(101.60,272.05) --
+	(104.30,273.12) --
+	(107.00,274.20) --
+	(109.71,275.30) --
+	(112.41,276.40) --
+	(115.11,277.52) --
+	(117.82,278.66) --
+	(120.52,279.81) --
+	(123.22,280.97) --
+	(125.93,282.15) --
+	(128.63,283.34) --
+	(131.33,284.55) --
+	(134.04,285.78) --
+	(136.74,287.03) --
+	(139.44,288.29) --
+	(142.15,289.56) --
+	(144.85,290.85) --
+	(147.55,292.16) --
+	(150.26,293.48) --
+	(152.96,294.81) --
+	(155.66,296.16) --
+	(158.37,297.52) --
+	(161.07,298.90) --
+	(163.77,300.30) --
+	(166.48,301.72) --
+	(169.18,303.16) --
+	(171.88,304.61) --
+	(174.59,306.09) --
+	(177.29,307.58) --
+	(179.99,309.10) --
+	(182.70,310.64) --
+	(185.40,312.20) --
+	(188.10,313.77) --
+	(190.80,315.36) --
+	(193.51,316.96) --
+	(196.21,318.59) --
+	(198.91,320.23) --
+	(201.62,321.89) --
+	(204.32,323.58) --
+	(207.02,325.28) --
+	(209.73,327.01) --
+	(212.43,328.76) --
+	(215.13,330.54) --
+	(217.84,332.33) --
+	(220.54,334.16) --
+	(223.24,336.01) --
+	(225.95,337.88) --
+	(228.65,339.78) --
+	(231.35,341.70) --
+	(234.06,343.64) --
+	(236.76,345.60) --
+	(239.46,347.59) --
+	(242.17,349.60) --
+	(244.87,351.63) --
+	(247.57,353.69) --
+	(250.28,355.76) --
+	(252.98,357.86) --
+	(255.68,359.99) --
+	(258.39,362.13) --
+	(261.09,364.30) --
+	(263.79,366.49) --
+	(266.50,368.71);
+\definecolor{drawColor}{RGB}{0,158,115}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.40,252.37) --
+	( 47.10,253.17) --
+	( 49.80,253.99) --
+	( 52.51,254.82) --
+	( 55.21,255.66) --
+	( 57.91,256.51) --
+	( 60.62,257.37) --
+	( 63.32,258.25) --
+	( 66.02,259.14) --
+	( 68.73,260.05) --
+	( 71.43,260.97) --
+	( 74.13,261.90) --
+	( 76.84,262.84) --
+	( 79.54,263.79) --
+	( 82.24,264.76) --
+	( 84.95,265.74) --
+	( 87.65,266.74) --
+	( 90.35,267.74) --
+	( 93.06,268.76) --
+	( 95.76,269.79) --
+	( 98.46,270.83) --
+	(101.17,271.88) --
+	(103.87,272.95) --
+	(106.57,274.03) --
+	(109.28,275.12) --
+	(111.98,276.23) --
+	(114.68,277.35) --
+	(117.39,278.49) --
+	(120.09,279.64) --
+	(122.79,280.80) --
+	(125.49,281.98) --
+	(128.20,283.18) --
+	(130.90,284.39) --
+	(133.60,285.61) --
+	(136.31,286.85) --
+	(139.01,288.09) --
+	(141.71,289.35) --
+	(144.42,290.63) --
+	(147.12,291.92) --
+	(149.82,293.22) --
+	(152.53,294.54) --
+	(155.23,295.88) --
+	(157.93,297.23) --
+	(160.64,298.61) --
+	(163.34,300.00) --
+	(166.04,301.41) --
+	(168.75,302.85) --
+	(171.45,304.30) --
+	(174.15,305.78) --
+	(176.86,307.28) --
+	(179.56,308.79) --
+	(182.26,310.32) --
+	(184.97,311.86) --
+	(187.67,313.42) --
+	(190.37,315.01) --
+	(193.08,316.61) --
+	(195.78,318.23) --
+	(198.48,319.88) --
+	(201.19,321.54) --
+	(203.89,323.23) --
+	(206.59,324.94) --
+	(209.30,326.68) --
+	(212.00,328.43) --
+	(214.70,330.22) --
+	(217.40,332.02) --
+	(220.11,333.85) --
+	(222.81,335.71) --
+	(225.51,337.58) --
+	(228.22,339.48) --
+	(230.92,341.40) --
+	(233.62,343.34) --
+	(236.33,345.30) --
+	(239.03,347.28) --
+	(241.73,349.29) --
+	(244.44,351.32) --
+	(247.14,353.37) --
+	(249.84,355.45) --
+	(252.55,357.54) --
+	(255.25,359.66) --
+	(257.95,361.80);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 35.86,249.88) --
+	( 38.56,250.65) --
+	( 41.26,251.43) --
+	( 43.97,252.22) --
+	( 46.67,253.03) --
+	( 49.37,253.84) --
+	( 52.07,254.67) --
+	( 54.78,255.51) --
+	( 57.48,256.37) --
+	( 60.18,257.24) --
+	( 62.89,258.11) --
+	( 65.59,259.01) --
+	( 68.29,259.91) --
+	( 71.00,260.83) --
+	( 73.70,261.76) --
+	( 76.40,262.70) --
+	( 79.11,263.65) --
+	( 81.81,264.62) --
+	( 84.51,265.60) --
+	( 87.22,266.59) --
+	( 89.92,267.59) --
+	( 92.62,268.60) --
+	( 95.33,269.63) --
+	( 98.03,270.67) --
+	(100.73,271.72) --
+	(103.44,272.79) --
+	(106.14,273.87) --
+	(108.84,274.96) --
+	(111.55,276.07) --
+	(114.25,277.19) --
+	(116.95,278.32) --
+	(119.66,279.47) --
+	(122.36,280.64) --
+	(125.06,281.81) --
+	(127.77,283.00) --
+	(130.47,284.20) --
+	(133.17,285.41) --
+	(135.88,286.63) --
+	(138.58,287.87) --
+	(141.28,289.12) --
+	(143.98,290.39) --
+	(146.69,291.67) --
+	(149.39,292.97) --
+	(152.09,294.29) --
+	(154.80,295.63) --
+	(157.50,296.98) --
+	(160.20,298.36) --
+	(162.91,299.76) --
+	(165.61,301.18) --
+	(168.31,302.62) --
+	(171.02,304.07) --
+	(173.72,305.54) --
+	(176.42,307.02) --
+	(179.13,308.53) --
+	(181.83,310.05) --
+	(184.53,311.59) --
 	(187.24,313.15) --
-	(190.26,314.90) --
-	(193.29,316.68) --
-	(196.32,318.49) --
-	(199.35,320.33) --
-	(202.37,322.21) --
-	(205.40,324.12) --
-	(208.43,326.06) --
-	(211.46,328.03) --
-	(214.49,330.03) --
-	(217.51,332.06) --
-	(220.54,334.11) --
-	(223.57,336.19) --
-	(226.60,338.30) --
-	(229.62,340.44) --
-	(232.65,342.61) --
-	(235.68,344.80) --
-	(238.71,347.02) --
-	(241.73,349.28) --
-	(244.76,351.56) --
-	(247.79,353.87) --
-	(250.82,356.21) --
-	(253.84,358.58) --
-	(256.87,360.97) --
-	(259.90,363.40) --
-	(262.93,365.85) --
-	(265.95,368.33) --
-	(268.98,370.84) --
-	(272.01,373.38) --
-	(275.04,375.95);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.40,252.39) --
-	( 47.43,253.28) --
-	( 50.45,254.18) --
-	( 53.48,255.11) --
-	( 56.51,256.05) --
-	( 59.54,257.00) --
-	( 62.56,257.98) --
-	( 65.59,258.97) --
-	( 68.62,259.97) --
-	( 71.65,261.00) --
-	( 74.67,262.04) --
-	( 77.70,263.10) --
-	( 80.73,264.17) --
-	( 83.76,265.26) --
-	( 86.78,266.37) --
-	( 89.81,267.49) --
-	( 92.84,268.63) --
-	( 95.87,269.79) --
-	( 98.89,270.97) --
-	(101.92,272.16) --
-	(104.95,273.37) --
-	(107.98,274.60) --
-	(111.01,275.84) --
-	(114.03,277.11) --
-	(117.06,278.38) --
-	(120.09,279.67) --
-	(123.12,280.97) --
-	(126.14,282.28) --
-	(129.17,283.61) --
-	(132.20,284.96) --
-	(135.23,286.33) --
-	(138.25,287.72) --
-	(141.28,289.14) --
-	(144.31,290.58) --
-	(147.34,292.05) --
-	(150.36,293.53) --
-	(153.39,295.03) --
-	(156.42,296.54) --
-	(159.45,298.06) --
-	(162.48,299.61) --
-	(165.50,301.18) --
-	(168.53,302.77) --
-	(171.56,304.38) --
-	(174.59,306.03) --
-	(177.61,307.70) --
-	(180.64,309.41) --
-	(183.67,311.14) --
-	(186.70,312.89) --
-	(189.72,314.66) --
-	(192.75,316.45) --
-	(195.78,318.25) --
-	(198.81,320.09) --
-	(201.83,321.94) --
-	(204.86,323.83) --
-	(207.89,325.76) --
-	(210.92,327.71) --
-	(213.94,329.71) --
+	(189.94,314.73) --
+	(192.64,316.33) --
+	(195.35,317.95) --
+	(198.05,319.60) --
+	(200.75,321.27) --
+	(203.46,322.96) --
+	(206.16,324.67) --
+	(208.86,326.41) --
+	(211.57,328.16) --
+	(214.27,329.94) --
 	(216.97,331.74) --
-	(220.00,333.80) --
-	(223.03,335.89) --
-	(226.06,338.01) --
-	(229.08,340.16) --
-	(232.11,342.33) --
-	(235.14,344.54) --
-	(238.17,346.77) --
-	(241.19,349.04) --
-	(244.22,351.34) --
-	(247.25,353.67) --
-	(250.28,356.02) --
-	(253.30,358.41) --
-	(256.33,360.83) --
-	(259.36,363.28) --
-	(262.39,365.76) --
-	(265.41,368.27) --
-	(268.44,370.81) --
-	(271.47,373.38) --
-	(274.50,375.98) --
-	(277.52,378.61) --
-	(280.55,381.26) --
-	(283.58,383.95);
+	(219.68,333.57) --
+	(222.38,335.41) --
+	(225.08,337.27) --
+	(227.79,339.16) --
+	(230.49,341.07) --
+	(233.19,342.99) --
+	(235.89,344.94) --
+	(238.60,346.91) --
+	(241.30,348.91) --
+	(244.00,350.92) --
+	(246.71,352.95) --
+	(249.41,355.01);
 \definecolor{fillColor}{RGB}{230,159,0}
-
-\path[fill=fillColor] ( 27.31,251.38) --
-	( 30.68,245.55) --
-	( 23.95,245.55) --
-	cycle;
 
@@
 
-\path[fill=fillColor] ( 95.65,273.63) --
-	( 99.01,267.80) --
-	( 92.29,267.80) --
-	cycle;
-
-\path[fill=fillColor] (129.82,287.78) --
-	(133.18,281.95) --
-	(126.46,281.95) --
-	cycle;
-
-\path[fill=fillColor] (163.99,304.26) --
-	(167.35,298.43) --
-	(160.63,298.43) --
-	cycle;
-
-\path[fill=fillColor] (198.16,323.63) --
-	(201.52,317.81) --
-	(194.79,317.81) --
-	cycle;
-
-\path[fill=fillColor] (232.33,346.20) --
-	(235.69,340.37) --
-	(228.96,340.37) --
-	cycle;
-
-\path[fill=fillColor] (266.50,372.59) --
-	(269.86,366.77) --
-	(263.13,366.77) --
+\path[fill=fillColor] (104.19,276.95) --
+	(107.56,271.12) --
+	(100.83,271.12) --
+	cycle;
+
+\path[fill=fillColor] (146.90,295.71) --
+	(150.27,289.89) --
+	(143.54,289.89) --
+	cycle;
+
+\path[fill=fillColor] (189.62,318.55) --
+	(192.98,312.72) --
+	(186.25,312.72) --
+	cycle;
+
+\path[fill=fillColor] (232.33,346.23) --
+	(235.69,340.41) --
+	(228.96,340.41) --
+	cycle;
+
+\path[fill=fillColor] (275.04,379.71) --
+	(278.40,373.88) --
+	(271.67,373.88) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 33.36,247.39) --
-	( 38.35,247.39) --
-	( 38.35,252.38) --
-	( 33.36,252.38) --
-	cycle;
-
-\path[fill=fillColor] ( 67.53,258.02) --
-	( 72.52,258.02) --
-	( 72.52,263.01) --
-	( 67.53,263.01) --
-	cycle;
-
-\path[fill=fillColor] (101.70,270.61) --
-	(106.69,270.61) --
-	(106.69,275.61) --
-	(101.70,275.61) --
-	cycle;
-
-\path[fill=fillColor] (135.86,285.30) --
-	(140.86,285.30) --
-	(140.86,290.30) --
-	(135.86,290.30) --
-	cycle;
-
-\path[fill=fillColor] (170.03,302.36) --
-	(175.03,302.36) --
-	(175.03,307.36) --
-	(170.03,307.36) --
-	cycle;
-
-\path[fill=fillColor] (204.20,322.52) --
-	(209.20,322.52) --
-	(209.20,327.51) --
-	(204.20,327.51) --
-	cycle;
-
-\path[fill=fillColor] (238.37,345.90) --
-	(243.37,345.90) --
-	(243.37,350.89) --
-	(238.37,350.89) --
-	cycle;
-
-\path[fill=fillColor] (272.54,373.53) --
-	(277.54,373.53) --
-	(277.54,378.53) --
-	(272.54,378.53) --
-	cycle;
+\path[fill=fillColor] ( 50.44,252.48) --
+	( 55.44,252.48) --
+	( 55.44,257.47) --
+	( 50.44,257.47) --
+	cycle;
+
+\path[fill=fillColor] ( 93.15,267.25) --
+	( 98.15,267.25) --
+	( 98.15,272.24) --
+	( 93.15,272.24) --
+	cycle;
+
+\path[fill=fillColor] (135.86,285.28) --
+	(140.86,285.28) --
+	(140.86,290.28) --
+	(135.86,290.28) --
+	cycle;
+
+\path[fill=fillColor] (178.58,307.22) --
+	(183.57,307.22) --
+	(183.57,312.21) --
+	(178.58,312.21) --
+	cycle;
+
+\path[fill=fillColor] (221.29,333.88) --
+	(226.28,333.88) --
+	(226.28,338.88) --
+	(221.29,338.88) --
+	cycle;
+
+\path[fill=fillColor] (264.00,366.21) --
+	(268.99,366.21) --
+	(268.99,371.20) --
+	(264.00,371.20) --
+	cycle;
+\definecolor{drawColor}{RGB}{0,158,115}
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.83) -- ( 44.40,255.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,263.46) -- ( 82.10,263.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57,259.93) -- ( 78.57,266.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.59) -- (116.27,276.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,273.06) -- (112.74,280.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.84) -- (150.44,291.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.31) -- (146.90,295.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.66) -- (184.61,309.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.13) -- (181.07,313.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.57) -- (218.77,330.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,327.04) -- (215.24,334.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,355.17) -- (252.94,355.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,351.64) -- (249.41,358.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,384.02) -- (287.11,384.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,380.49) -- (283.58,387.55);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.84) -- ( 44.40,255.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.54) -- ( 90.64,266.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,263.01) -- ( 87.11,270.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.90) -- (133.35,283.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.37) -- (129.82,287.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.89) -- (176.06,304.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.36) -- (172.53,308.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.58) -- (218.77,330.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,327.04) -- (215.24,334.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,361.80) -- (261.49,361.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,358.27) -- (257.95,365.33);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.36,247.39) rectangle ( 38.35,252.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.36,247.39) -- ( 38.35,252.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.36,252.38) -- ( 38.35,247.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.07,260.97) rectangle ( 81.06,265.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.07,260.97) -- ( 81.06,265.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.07,265.96) -- ( 81.06,260.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.78,277.67) rectangle (123.78,282.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.78,277.67) -- (123.78,282.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.78,282.67) -- (123.78,277.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.49,297.83) rectangle (166.49,302.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.49,297.83) -- (166.49,302.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.49,302.82) -- (166.49,297.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.20,322.52) rectangle (209.20,327.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.20,322.52) -- (209.20,327.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.20,327.51) -- (209.20,322.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.91,352.51) rectangle (251.91,357.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.91,352.51) -- (251.91,357.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.91,357.51) -- (251.91,352.51);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[fill=fillColor] ( 52.94,254.96) circle (  2.50);
-
-\path[fill=fillColor] ( 87.11,266.50) circle (  2.50);
-
-\path[fill=fillColor] (121.28,280.09) circle (  2.50);
+\path[fill=fillColor] ( 27.31,247.50) circle (  2.50);
+
+\path[fill=fillColor] ( 70.02,260.49) circle (  2.50);
+
+\path[fill=fillColor] (112.74,276.48) circle (  2.50);
 
@@
 
-\path[fill=fillColor] (189.62,314.74) circle (  2.50);
-
-\path[fill=fillColor] (223.78,336.55) circle (  2.50);
-
-\path[fill=fillColor] (257.95,361.93) circle (  2.50);
+\path[fill=fillColor] (198.16,319.89) circle (  2.50);
+
+\path[fill=fillColor] (240.87,348.77) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,329.23) {Reproduction number $\mathcal R$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,329.23) {Basic reproduction number $\mathcal R_0$};
 \end{scope}
@@
 
-\path[fill=fillColor] ( 31.06,332.94) rectangle (192.70,407.25);
+\path[fill=fillColor] ( 37.78,389.03) rectangle ( 52.24,403.48);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 39.23,396.25) -- ( 50.79,396.25);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] ( 45.01,396.25) circle (  2.50);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 36.56,381.80) rectangle ( 51.02,396.25);
+\path[fill=fillColor] ( 37.78,374.57) rectangle ( 52.24,389.03);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{230,159,0}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 39.23,381.80) -- ( 50.79,381.80);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{230,159,0}
+
+\path[fill=fillColor] ( 45.01,385.68) --
+	( 48.37,379.86) --
+	( 41.65,379.86) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 37.78,360.12) rectangle ( 52.24,374.57);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{86,180,233}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 39.23,367.35) -- ( 50.79,367.35);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{86,180,233}
+
+\path[fill=fillColor] ( 42.51,364.85) --
+	( 47.51,364.85) --
+	( 47.51,369.84) --
+	( 42.51,369.84) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 37.78,345.67) rectangle ( 52.24,360.12);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,158,115}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 39.23,352.89) -- ( 50.79,352.89);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,158,115}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.48,352.89) -- ( 48.54,352.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.01,349.36) -- ( 45.01,356.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 37.78,331.21) rectangle ( 52.24,345.67);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 39.23,338.44) -- ( 50.79,338.44);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.51,335.94) rectangle ( 47.51,340.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.51,335.94) -- ( 47.51,340.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.51,340.94) -- ( 47.51,335.94);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 38.01,389.03) -- ( 49.57,389.03);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] ( 43.79,389.03) circle (  2.50);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 36.56,367.35) rectangle ( 51.02,381.80);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{230,159,0}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 38.01,374.57) -- ( 49.57,374.57);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{230,159,0}
-
-\path[fill=fillColor] ( 43.79,378.46) --
-	( 47.15,372.63) --
-	( 40.43,372.63) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 36.56,352.89) rectangle ( 51.02,367.35);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{86,180,233}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 38.01,360.12) -- ( 49.57,360.12);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{86,180,233}
-
-\path[fill=fillColor] ( 41.29,357.62) --
-	( 46.29,357.62) --
-	( 46.29,362.62) --
-	( 41.29,362.62) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 36.56,338.44) rectangle ( 51.02,352.89);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 38.01,345.67) -- ( 49.57,345.67);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.26,345.67) -- ( 47.32,345.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.79,342.13) -- ( 43.79,349.20);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 57.74,393.22) {Intrinsic generation interval};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,386.00) {Intrinsic generation interval};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 57.74,378.77) {Forward serial interval ($\rho=0.75$)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,371.54) {Forward serial interval ($\rho=0.5$)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 57.74,364.32) {Forward serial interval ($\rho=0.5$)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,357.09) {Forward serial interval ($\rho=0$)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 57.74,349.86) {Forward serial interval ($\rho=0.25$)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,342.63) {Forward serial interval ($\rho=-0.5$)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 57.74,335.41) {Forward serial interval ($\rho=0$)};
 \end{scope}
@@
 \path[fill=fillColor] (316.39,247.50) rectangle (572.66,410.96);
-\definecolor{drawColor}{RGB}{0,0,0}
+\definecolor{drawColor}{RGB}{13,8,135}
 
@@
 	(572.66,383.38);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (319.64,248.30) --
+\definecolor{drawColor}{RGB}{126,3,168}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (319.64,248.37) --
+	(322.88,249.29) --
+	(326.12,250.21) --
+	(329.37,251.14) --
+	(332.61,252.09) --
+	(335.86,253.04) --
+	(339.10,254.01) --
+	(342.34,254.98) --
+	(345.59,255.97) --
+	(348.83,256.97) --
+	(352.08,257.98) --
+	(355.32,259.00) --
+	(358.56,260.04) --
+	(361.81,261.08) --
+	(365.05,262.13) --
+	(368.30,263.20) --
+	(371.54,264.27) --
+	(374.78,265.36) --
+	(378.03,266.46) --
+	(381.27,267.57) --
+	(384.51,268.69) --
+	(387.76,269.82) --
+	(391.00,270.96) --
+	(394.25,272.12) --
+	(397.49,273.28) --
+	(400.73,274.45) --
+	(403.98,275.64) --
+	(407.22,276.84) --
+	(410.47,278.04) --
+	(413.71,279.26) --
+	(416.95,280.49) --
+	(420.20,281.73) --
+	(423.44,282.98) --
+	(426.69,284.25) --
+	(429.93,285.52) --
+	(433.17,286.81) --
+	(436.42,288.10) --
+	(439.66,289.40) --
+	(442.90,290.71) --
+	(446.15,292.02) --
+	(449.39,293.35) --
+	(452.64,294.69) --
+	(455.88,296.04) --
+	(459.12,297.40) --
+	(462.37,298.77) --
+	(465.61,300.15) --
+	(468.86,301.54) --
+	(472.10,302.93) --
+	(475.34,304.32) --
+	(478.59,305.72) --
+	(481.83,307.12) --
+	(485.08,308.54) --
+	(488.32,309.96) --
+	(491.56,311.39) --
+	(494.81,312.82) --
+	(498.05,314.26) --
+	(501.29,315.71) --
+	(504.54,317.16) --
+	(507.78,318.61) --
+	(511.03,320.07) --
+	(514.27,321.53) --
+	(517.51,322.99) --
+	(520.76,324.45) --
+	(524.00,325.93) --
+	(527.25,327.40) --
+	(530.49,328.89) --
+	(533.73,330.37) --
+	(536.98,331.86) --
+	(540.22,333.36) --
+	(543.47,334.86) --
+	(546.71,336.37) --
+	(549.95,337.88) --
+	(553.20,339.39) --
+	(556.44,340.91) --
+	(559.68,342.43) --
+	(562.93,343.96) --
+	(566.17,345.49) --
+	(569.42,347.03) --
+	(572.66,348.57);
+\definecolor{drawColor}{RGB}{204,70,120}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (319.64,248.30) --
 	(322.88,249.24) --
@@
 	(572.66,328.50);
-\definecolor{drawColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (319.64,248.18) --
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (319.64,248.24) --
+	(322.88,249.19) --
+	(326.12,250.15) --
+	(329.37,251.11) --
+	(332.61,252.07) --
+	(335.86,253.03) --
+	(339.10,254.00) --
+	(342.34,254.96) --
+	(345.59,255.93) --
+	(348.83,256.91) --
+	(352.08,257.88) --
+	(355.32,258.86) --
+	(358.56,259.84) --
+	(361.81,260.82) --
+	(365.05,261.80) --
+	(368.30,262.78) --
+	(371.54,263.77) --
+	(374.78,264.75) --
+	(378.03,265.74) --
+	(381.27,266.73) --
+	(384.51,267.73) --
+	(387.76,268.73) --
+	(391.00,269.73) --
+	(394.25,270.74) --
+	(397.49,271.75) --
+	(400.73,272.76) --
+	(403.98,273.76) --
+	(407.22,274.76) --
+	(410.47,275.76) --
+	(413.71,276.76) --
+	(416.95,277.77) --
+	(420.20,278.79) --
+	(423.44,279.81) --
+	(426.69,280.83) --
+	(429.93,281.84) --
+	(433.17,282.85) --
+	(436.42,283.85) --
+	(439.66,284.83) --
+	(442.90,285.80) --
+	(446.15,286.75) --
+	(449.39,287.70) --
+	(452.64,288.67) --
+	(455.88,289.63) --
+	(459.12,290.59) --
+	(462.37,291.54) --
+	(465.61,292.47) --
+	(468.86,293.39) --
+	(472.10,294.29) --
+	(475.34,295.16) --
+	(478.59,295.99) --
+	(481.83,296.81) --
+	(485.08,297.61) --
+	(488.32,298.41) --
+	(491.56,299.19) --
+	(494.81,299.95) --
+	(498.05,300.69) --
+	(501.29,301.40) --
+	(504.54,302.09) --
+	(507.78,302.75) --
+	(511.03,303.37) --
+	(514.27,303.96) --
+	(517.51,304.52) --
+	(520.76,305.06) --
+	(524.00,305.58) --
+	(527.25,306.08) --
+	(530.49,306.56) --
+	(533.73,307.01) --
+	(536.98,307.43) --
+	(540.22,307.83) --
+	(543.47,308.21) --
+	(546.71,308.56) --
+	(549.95,308.88) --
+	(553.20,309.18) --
+	(556.44,309.45) --
+	(559.68,309.69) --
+	(562.93,309.91) --
+	(566.17,310.11) --
+	(569.42,310.28) --
+	(572.66,310.43);
+\definecolor{drawColor}{RGB}{240,249,33}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (319.64,248.18) --
 	(322.88,249.15) --
@@
 	(572.66,294.80);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (319.64,248.10) --
-	(322.88,249.10) --
-	(326.12,250.09) --
-	(329.37,251.07) --
-	(332.61,252.04) --
-	(335.86,253.00) --
-	(339.10,253.95) --
-	(342.34,254.90) --
-	(345.59,255.84) --
-	(348.83,256.77) --
-	(352.08,257.69) --
-	(355.32,258.60) --
-	(358.56,259.51) --
-	(361.81,260.40) --
-	(365.05,261.29) --
-	(368.30,262.16) --
-	(371.54,263.02) --
-	(374.78,263.87) --
-	(378.03,264.71) --
-	(381.27,265.55) --
-	(384.51,266.39) --
-	(387.76,267.23) --
-	(391.00,268.05) --
-	(394.25,268.87) --
-	(397.49,269.68) --
-	(400.73,270.47) --
-	(403.98,271.25) --
-	(407.22,272.00) --
-	(410.47,272.74) --
-	(413.71,273.47) --
-	(416.95,274.20) --
-	(420.20,274.93) --
-	(423.44,275.65) --
-	(426.69,276.36) --
-	(429.93,277.05) --
-	(433.17,277.72) --
-	(436.42,278.35) --
-	(439.66,278.95) --
-	(442.90,279.51) --
-	(446.15,280.03) --
-	(449.39,280.54) --
-	(452.64,281.05) --
-	(455.88,281.54) --
-	(459.12,282.01) --
-	(462.37,282.46) --
-	(465.61,282.87) --
-	(468.86,283.25) --
-	(472.10,283.58) --
-	(475.34,283.86) --
-	(478.59,284.08) --
-	(481.83,284.25) --
-	(485.08,284.40) --
-	(488.32,284.51) --
-	(491.56,284.59) --
-	(494.81,284.63) --
-	(498.05,284.63) --
-	(501.29,284.58) --
-	(504.54,284.48) --
-	(507.78,284.34) --
-	(511.03,284.13) --
-	(514.27,283.88) --
-	(517.51,283.57) --
-	(520.76,283.23) --
-	(524.00,282.84) --
-	(527.25,282.40) --
-	(530.49,281.93) --
-	(533.73,281.41) --
-	(536.98,280.84) --
-	(540.22,280.23) --
-	(543.47,279.57) --
-	(546.71,278.87) --
-	(549.95,278.12) --
-	(553.20,277.32) --
-	(556.44,276.47) --
-	(559.68,275.58) --
-	(562.93,274.65) --
-	(566.17,273.66) --
-	(569.42,272.64) --
-	(572.66,271.57);
-\definecolor{fillColor}{RGB}{0,158,115}
+\definecolor{fillColor}{RGB}{126,3,168}
 
@@
 \path[fill=fillColor] (324.94,253.76) --
-	(328.30,247.93) --
-	(321.57,247.93) --
-	cycle;
-
-\path[fill=fillColor] (333.48,256.20) --
-	(336.84,250.37) --
-	(330.11,250.37) --
-	cycle;
-
-\path[fill=fillColor] (342.02,258.70) --
-	(345.38,252.88) --
-	(338.66,252.88) --
-	cycle;
-
-\path[fill=fillColor] (350.56,261.27) --
-	(353.93,255.44) --
-	(347.20,255.44) --
-	cycle;
-
-\path[fill=fillColor] (359.10,263.89) --
-	(362.47,258.07) --
-	(355.74,258.07) --
-	cycle;
-
-\path[fill=fillColor] (367.65,266.57) --
-	(371.01,260.75) --
-	(364.28,260.75) --
-	cycle;
-
-\path[fill=fillColor] (376.19,269.31) --
-	(379.55,263.48) --
-	(372.83,263.48) --
-	cycle;
-
-\path[fill=fillColor] (384.73,272.09) --
-	(388.09,266.27) --
-	(381.37,266.27) --
-	cycle;
-
-\path[fill=fillColor] (393.27,274.93) --
-	(396.64,269.10) --
-	(389.91,269.10) --
-	cycle;
-
-\path[fill=fillColor] (401.82,277.80) --
-	(405.18,271.97) --
-	(398.45,271.97) --
-	cycle;
-
-\path[fill=fillColor] (410.36,280.71) --
-	(413.72,274.89) --
-	(406.99,274.89) --
-	cycle;
-
-\path[fill=fillColor] (418.90,283.66) --
-	(422.26,277.83) --
-	(415.54,277.83) --
-	cycle;
-
-\path[fill=fillColor] (427.44,286.63) --
-	(430.81,280.80) --
-	(424.08,280.80) --
-	cycle;
-
-\path[fill=fillColor] (435.98,289.62) --
-	(439.35,283.79) --
-	(432.62,283.79) --
-	cycle;
-
-\path[fill=fillColor] (444.53,292.62) --
-	(447.89,286.79) --
-	(441.16,286.79) --
-	cycle;
-
-\path[fill=fillColor] (453.07,295.63) --
-	(456.43,289.80) --
-	(449.71,289.80) --
-	cycle;
-
-\path[fill=fillColor] (461.61,298.63) --
-	(464.97,292.81) --
-	(458.25,292.81) --
-	cycle;
-
-\path[fill=fillColor] (470.15,301.63) --
-	(473.52,295.80) --
-	(466.79,295.80) --
-	cycle;
-
-\path[fill=fillColor] (478.70,304.60) --
-	(482.06,298.77) --
-	(475.33,298.77) --
-	cycle;
-
-\path[fill=fillColor] (487.24,307.54) --
-	(490.60,301.71) --
-	(483.87,301.71) --
-	cycle;
-
-\path[fill=fillColor] (495.78,310.43) --
-	(499.14,304.60) --
-	(492.42,304.60) --
-	cycle;
-
-\path[fill=fillColor] (504.32,313.26) --
-	(507.69,307.44) --
-	(500.96,307.44) --
-	cycle;
-
-\path[fill=fillColor] (512.86,316.03) --
-	(516.23,310.20) --
-	(509.50,310.20) --
-	cycle;
-
-\path[fill=fillColor] (521.41,318.70) --
-	(524.77,312.87) --
-	(518.04,312.87) --
-	cycle;
-
-\path[fill=fillColor] (529.95,321.27) --
-	(533.31,315.44) --
-	(526.59,315.44) --
-	cycle;
-
-\path[fill=fillColor] (538.49,323.72) --
-	(541.85,317.89) --
-	(535.13,317.89) --
-	cycle;
-
-\path[fill=fillColor] (547.03,326.03) --
-	(550.40,320.20) --
-	(543.67,320.20) --
-	cycle;
-
-\path[fill=fillColor] (555.58,328.18) --
-	(558.94,322.35) --
-	(552.21,322.35) --
-	cycle;
-
-\path[fill=fillColor] (564.12,330.14) --
-	(567.48,324.32) --
-	(560.75,324.32) --
-	cycle;
-
-\path[fill=fillColor] (572.66,331.91) --
-	(576.02,326.08) --
-	(569.30,326.08) --
-	cycle;
-\definecolor{fillColor}{RGB}{240,228,66}
+	(328.30,247.94) --
+	(321.57,247.94) --
+	cycle;
+
+\path[fill=fillColor] (333.48,256.22) --
+	(336.84,250.40) --
+	(330.11,250.40) --
+	cycle;
+
+\path[fill=fillColor] (342.02,258.76) --
+	(345.38,252.93) --
+	(338.66,252.93) --
+	cycle;
+
+\path[fill=fillColor] (350.56,261.38) --
+	(353.93,255.55) --
+	(347.20,255.55) --
+	cycle;
+
+\path[fill=fillColor] (359.10,264.07) --
+	(362.47,258.25) --
+	(355.74,258.25) --
+	cycle;
+
+\path[fill=fillColor] (367.65,266.85) --
+	(371.01,261.02) --
+	(364.28,261.02) --
+	cycle;
+
+\path[fill=fillColor] (376.19,269.70) --
+	(379.55,263.87) --
+	(372.83,263.87) --
+	cycle;
+
+\path[fill=fillColor] (384.73,272.63) --
+	(388.09,266.80) --
+	(381.37,266.80) --
+	cycle;
+
+\path[fill=fillColor] (393.27,275.64) --
+	(396.64,269.81) --
+	(389.91,269.81) --
+	cycle;
+
+\path[fill=fillColor] (401.82,278.72) --
+	(405.18,272.89) --
+	(398.45,272.89) --
+	cycle;
+
+\path[fill=fillColor] (410.36,281.88) --
+	(413.72,276.05) --
+	(406.99,276.05) --
+	cycle;
+
+\path[fill=fillColor] (418.90,285.11) --
+	(422.26,279.29) --
+	(415.54,279.29) --
+	cycle;
+
+\path[fill=fillColor] (427.44,288.42) --
+	(430.81,282.59) --
+	(424.08,282.59) --
+	cycle;
+
+\path[fill=fillColor] (435.98,291.80) --
+	(439.35,285.97) --
+	(432.62,285.97) --
+	cycle;
+
+\path[fill=fillColor] (444.53,295.24) --
+	(447.89,289.41) --
+	(441.16,289.41) --
+	cycle;
+
+\path[fill=fillColor] (453.07,298.75) --
+	(456.43,292.92) --
+	(449.71,292.92) --
+	cycle;
+
+\path[fill=fillColor] (461.61,302.32) --
+	(464.97,296.50) --
+	(458.25,296.50) --
+	cycle;
+
+\path[fill=fillColor] (470.15,305.95) --
+	(473.52,300.13) --
+	(466.79,300.13) --
+	cycle;
+
+\path[fill=fillColor] (478.70,309.64) --
+	(482.06,303.81) --
+	(475.33,303.81) --
+	cycle;
+
+\path[fill=fillColor] (487.24,313.38) --
+	(490.60,307.55) --
+	(483.87,307.55) --
+	cycle;
+
+\path[fill=fillColor] (495.78,317.16) --
+	(499.14,311.34) --
+	(492.42,311.34) --
+	cycle;
+
+\path[fill=fillColor] (504.32,320.99) --
+	(507.69,315.16) --
+	(500.96,315.16) --
+	cycle;
+
+\path[fill=fillColor] (512.86,324.85) --
+	(516.23,319.03) --
+	(509.50,319.03) --
+	cycle;
+
+\path[fill=fillColor] (521.41,328.74) --
+	(524.77,322.92) --
+	(518.04,322.92) --
+	cycle;
+
+\path[fill=fillColor] (529.95,332.66) --
+	(533.31,326.83) --
+	(526.59,326.83) --
+	cycle;
+
+\path[fill=fillColor] (538.49,336.58) --
+	(541.85,330.76) --
+	(535.13,330.76) --
+	cycle;
+
+\path[fill=fillColor] (547.03,340.52) --
+	(550.40,334.69) --
+	(543.67,334.69) --
+	cycle;
+
+\path[fill=fillColor] (555.58,344.44) --
+	(558.94,338.62) --
+	(552.21,338.62) --
+	cycle;
+
+\path[fill=fillColor] (564.12,348.36) --
+	(567.48,342.53) --
+	(560.75,342.53) --
+	cycle;
+
+\path[fill=fillColor] (572.66,352.25) --
+	(576.02,346.42) --
+	(569.30,346.42) --
+	cycle;
+\definecolor{fillColor}{RGB}{204,70,120}
 
@@
 
-\path[fill=fillColor] (322.44,247.36) --
-	(327.43,247.36) --
-	(327.43,252.36) --
-	(322.44,252.36) --
-	cycle;
-
-\path[fill=fillColor] (330.98,249.77) --
-	(335.98,249.77) --
-	(335.98,254.76) --
-	(330.98,254.76) --
-	cycle;
-
-\path[fill=fillColor] (339.52,252.21) --
-	(344.52,252.21) --
-	(344.52,257.20) --
-	(339.52,257.20) --
-	cycle;
-
-\path[fill=fillColor] (348.06,254.68) --
-	(353.06,254.68) --
-	(353.06,259.67) --
-	(348.06,259.67) --
-	cycle;
-
-\path[fill=fillColor] (356.61,257.17) --
-	(361.60,257.17) --
-	(361.60,262.16) --
-	(356.61,262.16) --
-	cycle;
-
-\path[fill=fillColor] (365.15,259.67) --
-	(370.14,259.67) --
-	(370.14,264.67) --
-	(365.15,264.67) --
-	cycle;
-
-\path[fill=fillColor] (373.69,262.19) --
-	(378.69,262.19) --
-	(378.69,267.19) --
-	(373.69,267.19) --
-	cycle;
-
-\path[fill=fillColor] (382.23,264.71) --
-	(387.23,264.71) --
-	(387.23,269.70) --
-	(382.23,269.70) --
-	cycle;
-
-\path[fill=fillColor] (390.78,267.21) --
-	(395.77,267.21) --
-	(395.77,272.21) --
-	(390.78,272.21) --
-	cycle;
-
-\path[fill=fillColor] (399.32,269.70) --
-	(404.31,269.70) --
-	(404.31,274.69) --
-	(399.32,274.69) --
-	cycle;
-
-\path[fill=fillColor] (407.86,272.15) --
-	(412.86,272.15) --
-	(412.86,277.15) --
-	(407.86,277.15) --
-	cycle;
-
-\path[fill=fillColor] (416.40,274.57) --
-	(421.40,274.57) --
-	(421.40,279.56) --
-	(416.40,279.56) --
-	cycle;
-
-\path[fill=fillColor] (424.94,276.93) --
-	(429.94,276.93) --
-	(429.94,281.93) --
-	(424.94,281.93) --
-	cycle;
-
-\path[fill=fillColor] (433.49,279.22) --
-	(438.48,279.22) --
-	(438.48,284.22) --
-	(433.49,284.22) --
-	cycle;
-
-\path[fill=fillColor] (442.03,281.44) --
-	(447.02,281.44) --
-	(447.02,286.43) --
-	(442.03,286.43) --
-	cycle;
-
-\path[fill=fillColor] (450.57,283.55) --
-	(455.57,283.55) --
-	(455.57,288.55) --
-	(450.57,288.55) --
-	cycle;
-
-\path[fill=fillColor] (459.11,285.55) --
-	(464.11,285.55) --
-	(464.11,290.55) --
-	(459.11,290.55) --
-	cycle;
-
-\path[fill=fillColor] (467.66,287.42) --
-	(472.65,287.42) --
-	(472.65,292.42) --
-	(467.66,292.42) --
-	cycle;
-
-\path[fill=fillColor] (476.20,289.14) --
-	(481.19,289.14) --
-	(481.19,294.14) --
-	(476.20,294.14) --
-	cycle;
-
-\path[fill=fillColor] (484.74,290.69) --
-	(489.74,290.69) --
-	(489.74,295.69) --
-	(484.74,295.69) --
-	cycle;
-
-\path[fill=fillColor] (493.28,292.05) --
-	(498.28,292.05) --
-	(498.28,297.04) --
-	(493.28,297.04) --
-	cycle;
-
-\path[fill=fillColor] (501.82,293.19) --
-	(506.82,293.19) --
-	(506.82,298.19) --
-	(501.82,298.19) --
-	cycle;
-
-\path[fill=fillColor] (510.37,294.09) --
-	(515.36,294.09) --
-	(515.36,299.09) --
-	(510.37,299.09) --
-	cycle;
-
-\path[fill=fillColor] (518.91,294.73) --
-	(523.90,294.73) --
-	(523.90,299.73) --
-	(518.91,299.73) --
-	cycle;
-
-\path[fill=fillColor] (527.45,295.08) --
-	(532.45,295.08) --
-	(532.45,300.07) --
-	(527.45,300.07) --
-	cycle;
-
-\path[fill=fillColor] (535.99,295.11) --
-	(540.99,295.11) --
-	(540.99,300.11) --
-	(535.99,300.11) --
-	cycle;
-
-\path[fill=fillColor] (544.54,294.80) --
-	(549.53,294.80) --
-	(549.53,299.79) --
-	(544.54,299.79) --
-	cycle;
-
-\path[fill=fillColor] (553.08,294.12) --
-	(558.07,294.12) --
-	(558.07,299.12) --
-	(553.08,299.12) --
-	cycle;
-
-\path[fill=fillColor] (561.62,293.05) --
-	(566.62,293.05) --
-	(566.62,298.05) --
-	(561.62,298.05) --
-	cycle;
-
-\path[fill=fillColor] (570.16,291.57) --
-	(575.16,291.57) --
-	(575.16,296.57) --
-	(570.16,296.57) --
-	cycle;
+\path[fill=fillColor] (322.44,247.37) --
+	(327.43,247.37) --
+	(327.43,252.37) --
+	(322.44,252.37) --
+	cycle;
+
+\path[fill=fillColor] (330.98,249.82) --
+	(335.98,249.82) --
+	(335.98,254.81) --
+	(330.98,254.81) --
+	cycle;
+
+\path[fill=fillColor] (339.52,252.32) --
+	(344.52,252.32) --
+	(344.52,257.32) --
+	(339.52,257.32) --
+	cycle;
+
+\path[fill=fillColor] (348.06,254.89) --
+	(353.06,254.89) --
+	(353.06,259.88) --
+	(348.06,259.88) --
+	cycle;
+
+\path[fill=fillColor] (356.61,257.51) --
+	(361.60,257.51) --
+	(361.60,262.51) --
+	(356.61,262.51) --
+	cycle;
+
+\path[fill=fillColor] (365.15,260.19) --
+	(370.14,260.19) --
+	(370.14,265.19) --
+	(365.15,265.19) --
+	cycle;
+
+\path[fill=fillColor] (373.69,262.93) --
+	(378.69,262.93) --
+	(378.69,267.92) --
+	(373.69,267.92) --
+	cycle;
+
+\path[fill=fillColor] (382.23,265.71) --
+	(387.23,265.71) --
+	(387.23,270.71) --
+	(382.23,270.71) --
+	cycle;
+
+\path[fill=fillColor] (390.78,268.54) --
+	(395.77,268.54) --
+	(395.77,273.54) --
+	(390.78,273.54) --
+	cycle;
+
+\path[fill=fillColor] (399.32,271.42) --
+	(404.31,271.42) --
+	(404.31,276.41) --
+	(399.32,276.41) --
+	cycle;
+
+\path[fill=fillColor] (407.86,274.33) --
+	(412.86,274.33) --
+	(412.86,279.32) --
+	(407.86,279.32) --
+	cycle;
+
+\path[fill=fillColor] (416.40,277.27) --
+	(421.40,277.27) --
+	(421.40,282.27) --
+	(416.40,282.27) --
+	cycle;
+
+\path[fill=fillColor] (424.94,280.24) --
+	(429.94,280.24) --
+	(429.94,285.24) --
+	(424.94,285.24) --
+	cycle;
+
+\path[fill=fillColor] (433.49,283.23) --
+	(438.48,283.23) --
+	(438.48,288.23) --
+	(433.49,288.23) --
+	cycle;
+
+\path[fill=fillColor] (442.03,286.24) --
+	(447.02,286.24) --
+	(447.02,291.23) --
+	(442.03,291.23) --
+	cycle;
+
+\path[fill=fillColor] (450.57,289.25) --
+	(455.57,289.25) --
+	(455.57,294.24) --
+	(450.57,294.24) --
+	cycle;
+
+\path[fill=fillColor] (459.11,292.25) --
+	(464.11,292.25) --
+	(464.11,297.25) --
+	(459.11,297.25) --
+	cycle;
+
+\path[fill=fillColor] (467.66,295.25) --
+	(472.65,295.25) --
+	(472.65,300.24) --
+	(467.66,300.24) --
+	cycle;
+
+\path[fill=fillColor] (476.20,298.22) --
+	(481.19,298.22) --
+	(481.19,303.21) --
+	(476.20,303.21) --
+	cycle;
+
+\path[fill=fillColor] (484.74,301.15) --
+	(489.74,301.15) --
+	(489.74,306.15) --
+	(484.74,306.15) --
+	cycle;
+
+\path[fill=fillColor] (493.28,304.05) --
+	(498.28,304.05) --
+	(498.28,309.04) --
+	(493.28,309.04) --
+	cycle;
+
+\path[fill=fillColor] (501.82,306.88) --
+	(506.82,306.88) --
+	(506.82,311.88) --
+	(501.82,311.88) --
+	cycle;
+
+\path[fill=fillColor] (510.37,309.64) --
+	(515.36,309.64) --
+	(515.36,314.64) --
+	(510.37,314.64) --
+	cycle;
+
+\path[fill=fillColor] (518.91,312.32) --
+	(523.90,312.32) --
+	(523.90,317.31) --
+	(518.91,317.31) --
+	cycle;
+
+\path[fill=fillColor] (527.45,314.89) --
+	(532.45,314.89) --
+	(532.45,319.88) --
+	(527.45,319.88) --
+	cycle;
+
+\path[fill=fillColor] (535.99,317.34) --
+	(540.99,317.34) --
+	(540.99,322.33) --
+	(535.99,322.33) --
+	cycle;
+
+\path[fill=fillColor] (544.54,319.65) --
+	(549.53,319.65) --
+	(549.53,324.64) --
+	(544.54,324.64) --
+	cycle;
+
+\path[fill=fillColor] (553.08,321.80) --
+	(558.07,321.80) --
+	(558.07,326.79) --
+	(553.08,326.79) --
+	cycle;
+
+\path[fill=fillColor] (561.62,323.76) --
+	(566.62,323.76) --
+	(566.62,328.76) --
+	(561.62,328.76) --
+	cycle;
+
+\path[fill=fillColor] (570.16,325.52) --
+	(575.16,325.52) --
+	(575.16,330.52) --
+	(570.16,330.52) --
+	cycle;
+\definecolor{drawColor}{RGB}{248,148,65}
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.40,249.85) -- (328.47,249.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.94,246.32) -- (324.94,253.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.95,252.22) -- (337.01,252.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.48,248.69) -- (333.48,255.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.49,254.60) -- (345.55,254.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.02,251.07) -- (342.02,258.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.03,256.98) -- (354.09,256.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.45) -- (350.56,260.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,259.35) -- (362.64,259.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,255.81) -- (359.10,262.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,261.70) -- (371.18,261.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,258.16) -- (367.65,265.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,264.01) -- (379.72,264.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,260.48) -- (376.19,267.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,266.28) -- (388.26,266.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,262.75) -- (384.73,269.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,268.50) -- (396.81,268.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,264.97) -- (393.27,272.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,270.64) -- (405.35,270.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,267.11) -- (401.82,274.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,272.70) -- (413.89,272.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,269.17) -- (410.36,276.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,274.66) -- (422.43,274.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,271.13) -- (418.90,278.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,276.50) -- (430.97,276.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,272.97) -- (427.44,280.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,278.21) -- (439.52,278.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,274.67) -- (435.98,281.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,279.76) -- (448.06,279.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,276.23) -- (444.53,283.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,281.15) -- (456.60,281.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,277.61) -- (453.07,284.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,282.34) -- (465.14,282.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,278.81) -- (461.61,285.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,283.32) -- (473.69,283.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,279.79) -- (470.15,286.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,284.08) -- (482.23,284.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,280.55) -- (478.70,287.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,284.58) -- (490.77,284.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,281.04) -- (487.24,288.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,284.80) -- (499.31,284.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,281.27) -- (495.78,288.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,284.72) -- (507.85,284.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,281.19) -- (504.32,288.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,284.32) -- (516.40,284.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,280.79) -- (512.86,287.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,283.58) -- (524.94,283.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,280.04) -- (521.41,287.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,282.47) -- (533.48,282.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,278.94) -- (529.95,286.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,280.98) -- (542.02,280.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,277.44) -- (538.49,284.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,279.09) -- (550.57,279.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,275.56) -- (547.03,282.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,276.80) -- (559.11,276.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,273.26) -- (555.58,280.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,274.10) -- (567.65,274.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,270.57) -- (564.12,277.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,271.01) -- (576.19,271.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,267.47) -- (572.66,274.54);
-\definecolor{fillColor}{RGB}{0,0,0}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.40,249.87) -- (328.47,249.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.94,246.33) -- (324.94,253.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.95,252.29) -- (337.01,252.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.48,248.76) -- (333.48,255.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.49,254.76) -- (345.55,254.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.02,251.23) -- (342.02,258.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.03,257.28) -- (354.09,257.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.74) -- (350.56,260.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,259.83) -- (362.64,259.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,256.30) -- (359.10,263.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,262.43) -- (371.18,262.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,258.89) -- (367.65,265.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,265.05) -- (379.72,265.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,261.52) -- (376.19,268.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,267.70) -- (388.26,267.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,264.16) -- (384.73,271.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,270.36) -- (396.81,270.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,266.83) -- (393.27,273.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,273.03) -- (405.35,273.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,269.50) -- (401.82,276.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,275.71) -- (413.89,275.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,272.18) -- (410.36,279.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,278.38) -- (422.43,278.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,274.85) -- (418.90,281.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,281.04) -- (430.97,281.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,277.51) -- (427.44,284.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,283.67) -- (439.52,283.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,280.13) -- (435.98,287.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,286.26) -- (448.06,286.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,282.73) -- (444.53,289.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,288.80) -- (456.60,288.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,285.27) -- (453.07,292.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,291.28) -- (465.14,291.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,287.75) -- (461.61,294.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,293.69) -- (473.69,293.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,290.15) -- (470.15,297.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,296.00) -- (482.23,296.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,292.47) -- (478.70,299.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,298.20) -- (490.77,298.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,294.67) -- (487.24,301.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,300.28) -- (499.31,300.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,296.75) -- (495.78,303.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,302.21) -- (507.85,302.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,298.68) -- (504.32,305.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,303.98) -- (516.40,303.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,300.45) -- (512.86,307.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,305.56) -- (524.94,305.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,302.03) -- (521.41,309.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,306.93) -- (533.48,306.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,303.40) -- (529.95,310.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,308.07) -- (542.02,308.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,304.54) -- (538.49,311.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,308.95) -- (550.57,308.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,305.42) -- (547.03,312.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,309.54) -- (559.11,309.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,306.01) -- (555.58,313.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,309.82) -- (567.65,309.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,306.29) -- (564.12,313.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,309.77) -- (576.19,309.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,306.24) -- (572.66,313.30);
+\definecolor{drawColor}{RGB}{240,249,33}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (313.90,245.00) rectangle (318.89,249.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (313.90,245.00) -- (318.89,249.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (313.90,249.99) -- (318.89,245.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.44,247.36) rectangle (327.43,252.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.44,247.36) -- (327.43,252.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.44,252.36) -- (327.43,247.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.98,249.77) rectangle (335.98,254.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.98,249.77) -- (335.98,254.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.98,254.76) -- (335.98,249.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.52,252.21) rectangle (344.52,257.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.52,252.21) -- (344.52,257.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.52,257.20) -- (344.52,252.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.06,254.68) rectangle (353.06,259.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.06,254.68) -- (353.06,259.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.06,259.67) -- (353.06,254.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.61,257.17) rectangle (361.60,262.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.61,257.17) -- (361.60,262.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.61,262.16) -- (361.60,257.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.15,259.67) rectangle (370.14,264.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.15,259.67) -- (370.14,264.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.15,264.67) -- (370.14,259.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.69,262.19) rectangle (378.69,267.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.69,262.19) -- (378.69,267.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.69,267.19) -- (378.69,262.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (382.23,264.71) rectangle (387.23,269.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (382.23,264.71) -- (387.23,269.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (382.23,269.70) -- (387.23,264.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.78,267.21) rectangle (395.77,272.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.78,267.21) -- (395.77,272.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.78,272.21) -- (395.77,267.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (399.32,269.70) rectangle (404.31,274.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (399.32,269.70) -- (404.31,274.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (399.32,274.69) -- (404.31,269.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (407.86,272.15) rectangle (412.86,277.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (407.86,272.15) -- (412.86,277.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (407.86,277.15) -- (412.86,272.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.40,274.57) rectangle (421.40,279.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.40,274.57) -- (421.40,279.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.40,279.56) -- (421.40,274.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.94,276.93) rectangle (429.94,281.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.94,276.93) -- (429.94,281.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.94,281.93) -- (429.94,276.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.49,279.22) rectangle (438.48,284.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.49,279.22) -- (438.48,284.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.49,284.22) -- (438.48,279.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.03,281.44) rectangle (447.02,286.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.03,281.44) -- (447.02,286.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.03,286.43) -- (447.02,281.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.57,283.55) rectangle (455.57,288.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.57,283.55) -- (455.57,288.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.57,288.55) -- (455.57,283.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.11,285.55) rectangle (464.11,290.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.11,285.55) -- (464.11,290.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.11,290.55) -- (464.11,285.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.66,287.42) rectangle (472.65,292.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.66,287.42) -- (472.65,292.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.66,292.42) -- (472.65,287.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.20,289.14) rectangle (481.19,294.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.20,289.14) -- (481.19,294.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.20,294.14) -- (481.19,289.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.74,290.69) rectangle (489.74,295.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.74,290.69) -- (489.74,295.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.74,295.69) -- (489.74,290.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.28,292.05) rectangle (498.28,297.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.28,292.05) -- (498.28,297.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.28,297.04) -- (498.28,292.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.82,293.19) rectangle (506.82,298.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.82,293.19) -- (506.82,298.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.82,298.19) -- (506.82,293.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.37,294.09) rectangle (515.36,299.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.37,294.09) -- (515.36,299.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.37,299.09) -- (515.36,294.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.91,294.73) rectangle (523.90,299.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.91,294.73) -- (523.90,299.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.91,299.73) -- (523.90,294.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.45,295.08) rectangle (532.45,300.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.45,295.08) -- (532.45,300.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.45,300.07) -- (532.45,295.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.99,295.11) rectangle (540.99,300.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.99,295.11) -- (540.99,300.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.99,300.11) -- (540.99,295.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.54,294.80) rectangle (549.53,299.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.54,294.80) -- (549.53,299.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.54,299.79) -- (549.53,294.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.08,294.12) rectangle (558.07,299.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.08,294.12) -- (558.07,299.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.08,299.12) -- (558.07,294.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.62,293.05) rectangle (566.62,298.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.62,293.05) -- (566.62,298.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.62,298.05) -- (566.62,293.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16,291.57) rectangle (575.16,296.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16,291.57) -- (575.16,296.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16,296.57) -- (575.16,291.57);
+\definecolor{fillColor}{RGB}{13,8,135}
 
@@
 
-\path[fill=fillColor] (320.07,332.94) rectangle (481.85,407.25);
+\path[fill=fillColor] (326.79,389.03) rectangle (341.24,403.48);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{13,8,135}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (328.24,396.25) -- (339.80,396.25);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{13,8,135}
+
+\path[fill=fillColor] (334.02,396.25) circle (  2.50);
 \end{scope}
@@
 
-\path[fill=fillColor] (325.57,381.80) rectangle (340.02,396.25);
+\path[fill=fillColor] (326.79,374.57) rectangle (341.24,389.03);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{126,3,168}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (328.24,381.80) -- (339.80,381.80);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{126,3,168}
+
+\path[fill=fillColor] (334.02,385.68) --
+	(337.38,379.86) --
+	(330.65,379.86) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (326.79,360.12) rectangle (341.24,374.57);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{204,70,120}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (328.24,367.35) -- (339.80,367.35);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{204,70,120}
+
+\path[fill=fillColor] (331.52,364.85) --
+	(336.52,364.85) --
+	(336.52,369.84) --
+	(331.52,369.84) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (326.79,345.67) rectangle (341.24,360.12);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (328.24,352.89) -- (339.80,352.89);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.49,352.89) -- (337.55,352.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.02,349.36) -- (334.02,356.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (326.79,331.21) rectangle (341.24,345.67);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{240,249,33}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (328.24,338.44) -- (339.80,338.44);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{240,249,33}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.52,335.94) rectangle (336.52,340.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.52,335.94) -- (336.52,340.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.52,340.94) -- (336.52,335.94);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (327.01,389.03) -- (338.58,389.03);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] (332.80,389.03) circle (  2.50);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (325.57,367.35) rectangle (340.02,381.80);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (327.01,374.57) -- (338.58,374.57);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{0,158,115}
-
-\path[fill=fillColor] (332.80,378.46) --
-	(336.16,372.63) --
-	(329.43,372.63) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (325.57,352.89) rectangle (340.02,367.35);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (327.01,360.12) -- (338.58,360.12);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{240,228,66}
-
-\path[fill=fillColor] (330.30,357.62) --
-	(335.29,357.62) --
-	(335.29,362.62) --
-	(330.30,362.62) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (325.57,338.44) rectangle (340.02,352.89);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (327.01,345.67) -- (338.58,345.67);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.26,345.67) -- (336.33,345.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (332.80,342.13) -- (332.80,349.20);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (346.74,393.22) {Intrinsic generation interval};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,386.00) {Intrinsic generation interval};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (346.74,378.77) {Intrinsic serial interval ($\rho=0.75$)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,371.54) {Intrinsic serial interval ($\rho=0.5$)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (346.74,364.32) {Intrinsic serial interval ($\rho=0.5$)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,357.09) {Intrinsic serial interval ($\rho=0$)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (346.74,349.86) {Intrinsic serial interval ($\rho=0.25$)};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,342.63) {Intrinsic serial interval ($\rho=-0.5$)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (346.74,335.41) {Intrinsic serial interval ($\rho=0$)};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 54.98) --
-	( 30.56, 54.98) --
-	( 33.80, 54.98) --
-	( 37.04, 54.98) --
-	( 40.29, 54.98) --
-	( 43.53, 54.98) --
-	( 46.78, 54.98) --
-	( 50.02, 54.98) --
-	( 53.26, 54.98) --
-	( 56.51, 54.98) --
-	( 59.75, 54.98) --
-	( 63.00, 54.98) --
-	( 66.24, 54.98) --
-	( 69.48, 54.98) --
-	( 72.73, 54.98) --
-	( 75.97, 54.98) --
-	( 79.22, 54.98) --
-	( 82.46, 54.98) --
-	( 85.70, 54.98) --
-	( 88.95, 54.98) --
-	( 92.19, 54.98) --
-	( 95.43, 54.98) --
-	( 98.68, 54.98) --
-	(101.92, 54.98) --
-	(105.17, 54.98) --
-	(108.41, 54.98) --
-	(111.65, 54.98) --
-	(114.90, 54.98) --
-	(118.14, 54.98) --
-	(121.39, 54.98) --
-	(124.63, 54.98) --
-	(127.87, 54.98) --
-	(131.12, 54.98) --
-	(134.36, 54.98) --
-	(137.61, 54.98) --
-	(140.85, 54.98) --
-	(144.09, 54.98) --
-	(147.34, 54.98) --
-	(150.58, 54.98) --
-	(153.82, 54.98) --
-	(157.07, 54.98) --
-	(160.31, 54.98) --
-	(163.56, 54.98) --
-	(166.80, 54.98) --
-	(170.04, 54.98) --
-	(173.29, 54.98) --
-	(176.53, 54.98) --
-	(179.78, 54.98) --
-	(183.02, 54.98) --
-	(186.26, 54.98) --
-	(189.51, 54.98) --
-	(192.75, 54.98) --
-	(196.00, 54.98) --
-	(199.24, 54.98) --
-	(202.48, 54.98) --
-	(205.73, 54.98) --
-	(208.97, 54.98) --
-	(212.21, 54.98) --
-	(215.46, 54.98) --
-	(218.70, 54.98) --
-	(221.95, 54.98) --
-	(225.19, 54.98) --
-	(228.43, 54.98) --
-	(231.68, 54.98) --
-	(234.92, 54.98) --
-	(238.17, 54.98) --
-	(241.41, 54.98) --
-	(244.65, 54.98) --
-	(247.90, 54.98) --
-	(251.14, 54.98) --
-	(254.39, 54.98) --
-	(257.63, 54.98) --
-	(260.87, 54.98) --
-	(264.12, 54.98) --
-	(267.36, 54.98) --
-	(270.60, 54.98) --
-	(273.85, 54.98) --
-	(277.09, 54.98) --
-	(280.34, 54.98) --
-	(283.58, 54.98);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 63.20) --
+	( 30.56, 63.20) --
+	( 33.80, 63.20) --
+	( 37.04, 63.20) --
+	( 40.29, 63.20) --
+	( 43.53, 63.20) --
+	( 46.78, 63.20) --
+	( 50.02, 63.20) --
+	( 53.26, 63.20) --
+	( 56.51, 63.20) --
+	( 59.75, 63.20) --
+	( 63.00, 63.20) --
+	( 66.24, 63.20) --
+	( 69.48, 63.20) --
+	( 72.73, 63.20) --
+	( 75.97, 63.20) --
+	( 79.22, 63.20) --
+	( 82.46, 63.20) --
+	( 85.70, 63.20) --
+	( 88.95, 63.20) --
+	( 92.19, 63.20) --
+	( 95.43, 63.20) --
+	( 98.68, 63.20) --
+	(101.92, 63.20) --
+	(105.17, 63.20) --
+	(108.41, 63.20) --
+	(111.65, 63.20) --
+	(114.90, 63.20) --
+	(118.14, 63.20) --
+	(121.39, 63.20) --
+	(124.63, 63.20) --
+	(127.87, 63.20) --
+	(131.12, 63.20) --
+	(134.36, 63.20) --
+	(137.61, 63.20) --
+	(140.85, 63.20) --
+	(144.09, 63.20) --
+	(147.34, 63.20) --
+	(150.58, 63.20) --
+	(153.82, 63.20) --
+	(157.07, 63.20) --
+	(160.31, 63.20) --
+	(163.56, 63.20) --
+	(166.80, 63.20) --
+	(170.04, 63.20) --
+	(173.29, 63.20) --
+	(176.53, 63.20) --
+	(179.78, 63.20) --
+	(183.02, 63.20) --
+	(186.26, 63.20) --
+	(189.51, 63.20) --
+	(192.75, 63.20) --
+	(196.00, 63.20) --
+	(199.24, 63.20) --
+	(202.48, 63.20) --
+	(205.73, 63.20) --
+	(208.97, 63.20) --
+	(212.21, 63.20) --
+	(215.46, 63.20) --
+	(218.70, 63.20) --
+	(221.95, 63.20) --
+	(225.19, 63.20) --
+	(228.43, 63.20) --
+	(231.68, 63.20) --
+	(234.92, 63.20) --
+	(238.17, 63.20) --
+	(241.41, 63.20) --
+	(244.65, 63.20) --
+	(247.90, 63.20) --
+	(251.14, 63.20) --
+	(254.39, 63.20) --
+	(257.63, 63.20) --
+	(260.87, 63.20) --
+	(264.12, 63.20) --
+	(267.36, 63.20) --
+	(270.60, 63.20) --
+	(273.85, 63.20) --
+	(277.09, 63.20) --
+	(280.34, 63.20) --
+	(283.58, 63.20);
 \definecolor{drawColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31, 55.70) --
-	( 30.56, 56.81) --
-	( 33.80, 57.90) --
-	( 37.04, 58.98) --
-	( 40.29, 60.06) --
-	( 43.53, 61.12) --
-	( 46.78, 62.16) --
-	( 50.02, 63.20) --
-	( 53.26, 64.22) --
-	( 56.51, 65.23) --
-	( 59.75, 66.23) --
-	( 63.00, 67.21) --
-	( 66.24, 68.18) --
-	( 69.48, 69.14) --
-	( 72.73, 70.09) --
-	( 75.97, 71.03) --
-	( 79.22, 71.95) --
-	( 82.46, 72.86) --
-	( 85.70, 73.77) --
-	( 88.95, 74.66) --
-	( 92.19, 75.53) --
-	( 95.43, 76.39) --
-	( 98.68, 77.24) --
-	(101.92, 78.07) --
-	(105.17, 78.90) --
-	(108.41, 79.71) --
-	(111.65, 80.51) --
-	(114.90, 81.30) --
-	(118.14, 82.08) --
-	(121.39, 82.85) --
-	(124.63, 83.61) --
-	(127.87, 84.35) --
-	(131.12, 85.08) --
-	(134.36, 85.79) --
-	(137.61, 86.49) --
-	(140.85, 87.19) --
-	(144.09, 87.87) --
-	(147.34, 88.55) --
-	(150.58, 89.23) --
-	(153.82, 89.91) --
-	(157.07, 90.59) --
-	(160.31, 91.26) --
-	(163.56, 91.92) --
-	(166.80, 92.57) --
-	(170.04, 93.22) --
-	(173.29, 93.86) --
-	(176.53, 94.49) --
-	(179.78, 95.12) --
-	(183.02, 95.75) --
-	(186.26, 96.37) --
-	(189.51, 96.99) --
-	(192.75, 97.61) --
-	(196.00, 98.22) --
-	(199.24, 98.82) --
-	(202.48, 99.42) --
-	(205.73,100.02) --
-	(208.97,100.61) --
-	(212.21,101.20) --
-	(215.46,101.78) --
-	(218.70,102.35) --
-	(221.95,102.93) --
-	(225.19,103.50) --
-	(228.43,104.06) --
-	(231.68,104.62) --
-	(234.92,105.17) --
-	(238.17,105.72) --
-	(241.41,106.27) --
-	(244.65,106.81) --
-	(247.90,107.34) --
-	(251.14,107.87) --
-	(254.39,108.40) --
-	(257.63,108.92) --
-	(260.87,109.43) --
-	(264.12,109.95) --
-	(267.36,110.45) --
-	(270.60,110.95) --
-	(273.85,111.45) --
-	(277.09,111.95) --
-	(280.34,112.43) --
-	(283.58,112.92);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31, 64.16) --
+	( 30.56, 65.16) --
+	( 33.80, 66.15) --
+	( 37.04, 67.13) --
+	( 40.29, 68.09) --
+	( 43.53, 69.05) --
+	( 46.78, 69.99) --
+	( 50.02, 70.92) --
+	( 53.26, 71.84) --
+	( 56.51, 72.75) --
+	( 59.75, 73.64) --
+	( 63.00, 74.53) --
+	( 66.24, 75.40) --
+	( 69.48, 76.26) --
+	( 72.73, 77.11) --
+	( 75.97, 77.95) --
+	( 79.22, 78.78) --
+	( 82.46, 79.59) --
+	( 85.70, 80.40) --
+	( 88.95, 81.20) --
+	( 92.19, 81.98) --
+	( 95.43, 82.75) --
+	( 98.68, 83.50) --
+	(101.92, 84.24) --
+	(105.17, 84.98) --
+	(108.41, 85.70) --
+	(111.65, 86.41) --
+	(114.90, 87.11) --
+	(118.14, 87.80) --
+	(121.39, 88.49) --
+	(124.63, 89.16) --
+	(127.87, 89.82) --
+	(131.12, 90.46) --
+	(134.36, 91.09) --
+	(137.61, 91.71) --
+	(140.85, 92.33) --
+	(144.09, 92.93) --
+	(147.34, 93.54) --
+	(150.58, 94.13) --
+	(153.82, 94.73) --
+	(157.07, 95.33) --
+	(160.31, 95.92) --
+	(163.56, 96.50) --
+	(166.80, 97.08) --
+	(170.04, 97.64) --
+	(173.29, 98.20) --
+	(176.53, 98.76) --
+	(179.78, 99.31) --
+	(183.02, 99.86) --
+	(186.26,100.41) --
+	(189.51,100.95) --
+	(192.75,101.49) --
+	(196.00,102.03) --
+	(199.24,102.56) --
+	(202.48,103.08) --
+	(205.73,103.60) --
+	(208.97,104.12) --
+	(212.21,104.63) --
+	(215.46,105.14) --
+	(218.70,105.65) --
+	(221.95,106.15) --
+	(225.19,106.65) --
+	(228.43,107.14) --
+	(231.68,107.63) --
+	(234.92,108.12) --
+	(238.17,108.60) --
+	(241.41,109.07) --
+	(244.65,109.54) --
+	(247.90,110.01) --
+	(251.14,110.48) --
+	(254.39,110.94) --
+	(257.63,111.39) --
+	(260.87,111.84) --
+	(264.12,112.29) --
+	(267.36,112.73) --
+	(270.60,113.17) --
+	(273.85,113.61) --
+	(277.09,114.04) --
+	(280.34,114.46) --
+	(283.58,114.89);
 \definecolor{drawColor}{RGB}{86,180,233}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31, 55.54) --
-	( 30.56, 57.34) --
-	( 33.80, 59.12) --
-	( 37.04, 60.88) --
-	( 40.29, 62.63) --
-	( 43.53, 64.35) --
-	( 46.78, 66.06) --
-	( 50.02, 67.75) --
-	( 53.26, 69.43) --
-	( 56.51, 71.08) --
-	( 59.75, 72.71) --
-	( 63.00, 74.33) --
-	( 66.24, 75.93) --
-	( 69.48, 77.51) --
-	( 72.73, 79.07) --
-	( 75.97, 80.62) --
-	( 79.22, 82.15) --
-	( 82.46, 83.66) --
-	( 85.70, 85.16) --
-	( 88.95, 86.63) --
-	( 92.19, 88.09) --
-	( 95.43, 89.53) --
-	( 98.68, 90.94) --
-	(101.92, 92.34) --
-	(105.17, 93.72) --
-	(108.41, 95.08) --
-	(111.65, 96.43) --
-	(114.90, 97.76) --
-	(118.14, 99.08) --
-	(121.39,100.38) --
-	(124.63,101.67) --
-	(127.87,102.92) --
-	(131.12,104.16) --
-	(134.36,105.37) --
-	(137.61,106.57) --
-	(140.85,107.76) --
-	(144.09,108.93) --
-	(147.34,110.10) --
-	(150.58,111.27) --
-	(153.82,112.43) --
-	(157.07,113.59) --
-	(160.31,114.75) --
-	(163.56,115.89) --
-	(166.80,117.02) --
-	(170.04,118.14) --
-	(173.29,119.26) --
-	(176.53,120.36) --
-	(179.78,121.46) --
-	(183.02,122.55) --
-	(186.26,123.63) --
-	(189.51,124.71) --
-	(192.75,125.78) --
-	(196.00,126.85) --
-	(199.24,127.91) --
-	(202.48,128.96) --
-	(205.73,130.00) --
-	(208.97,131.03) --
-	(212.21,132.06) --
-	(215.46,133.08) --
-	(218.70,134.09) --
-	(221.95,135.10) --
-	(225.19,136.09) --
-	(228.43,137.09) --
-	(231.68,138.07) --
-	(234.92,139.04) --
-	(238.17,140.01) --
-	(241.41,140.97) --
-	(244.65,141.92) --
-	(247.90,142.87) --
-	(251.14,143.81) --
-	(254.39,144.74) --
-	(257.63,145.66) --
-	(260.87,146.58) --
-	(264.12,147.48) --
-	(267.36,148.38) --
-	(270.60,149.28) --
-	(273.85,150.16) --
-	(277.09,151.04) --
-	(280.34,151.91) --
-	(283.58,152.77);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31, 64.16) --
+	( 30.56, 65.64) --
+	( 33.80, 67.11) --
+	( 37.04, 68.56) --
+	( 40.29, 69.99) --
+	( 43.53, 71.41) --
+	( 46.78, 72.81) --
+	( 50.02, 74.19) --
+	( 53.26, 75.56) --
+	( 56.51, 76.91) --
+	( 59.75, 78.25) --
+	( 63.00, 79.56) --
+	( 66.24, 80.86) --
+	( 69.48, 82.15) --
+	( 72.73, 83.42) --
+	( 75.97, 84.67) --
+	( 79.22, 85.91) --
+	( 82.46, 87.13) --
+	( 85.70, 88.34) --
+	( 88.95, 89.53) --
+	( 92.19, 90.70) --
+	( 95.43, 91.85) --
+	( 98.68, 92.98) --
+	(101.92, 94.10) --
+	(105.17, 95.20) --
+	(108.41, 96.29) --
+	(111.65, 97.36) --
+	(114.90, 98.41) --
+	(118.14, 99.46) --
+	(121.39,100.49) --
+	(124.63,101.51) --
+	(127.87,102.50) --
+	(131.12,103.47) --
+	(134.36,104.43) --
+	(137.61,105.37) --
+	(140.85,106.29) --
+	(144.09,107.21) --
+	(147.34,108.12) --
+	(150.58,109.03) --
+	(153.82,109.94) --
+	(157.07,110.85) --
+	(160.31,111.75) --
+	(163.56,112.63) --
+	(166.80,113.50) --
+	(170.04,114.37) --
+	(173.29,115.22) --
+	(176.53,116.07) --
+	(179.78,116.92) --
+	(183.02,117.75) --
+	(186.26,118.59) --
+	(189.51,119.42) --
+	(192.75,120.24) --
+	(196.00,121.06) --
+	(199.24,121.87) --
+	(202.48,122.67) --
+	(205.73,123.47) --
+	(208.97,124.26) --
+	(212.21,125.04) --
+	(215.46,125.82) --
+	(218.70,126.59) --
+	(221.95,127.36) --
+	(225.19,128.12) --
+	(228.43,128.87) --
+	(231.68,129.62) --
+	(234.92,130.36) --
+	(238.17,131.10) --
+	(241.41,131.83) --
+	(244.65,132.55) --
+	(247.90,133.26) --
+	(251.14,133.97) --
+	(254.39,134.68) --
+	(257.63,135.37) --
+	(260.87,136.07) --
+	(264.12,136.75) --
+	(267.36,137.43) --
+	(270.60,138.10) --
+	(273.85,138.77) --
+	(277.09,139.43) --
+	(280.34,140.08) --
+	(283.58,140.73);
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 55.20) --
-	( 30.56, 57.64) --
-	( 33.80, 60.07) --
-	( 37.04, 62.47) --
-	( 40.29, 64.85) --
-	( 43.53, 67.21) --
-	( 46.78, 69.55) --
-	( 50.02, 71.86) --
-	( 53.26, 74.15) --
-	( 56.51, 76.43) --
-	( 59.75, 78.67) --
-	( 63.00, 80.90) --
-	( 66.24, 83.10) --
-	( 69.48, 85.29) --
-	( 72.73, 87.45) --
-	( 75.97, 89.59) --
-	( 79.22, 91.71) --
-	( 82.46, 93.81) --
-	( 85.70, 95.89) --
-	( 88.95, 97.94) --
-	( 92.19, 99.98) --
-	( 95.43,101.98) --
-	( 98.68,103.97) --
-	(101.92,105.93) --
-	(105.17,107.87) --
-	(108.41,109.79) --
-	(111.65,111.69) --
-	(114.90,113.57) --
-	(118.14,115.43) --
-	(121.39,117.28) --
-	(124.63,119.10) --
-	(127.87,120.88) --
-	(131.12,122.64) --
-	(134.36,124.37) --
-	(137.61,126.09) --
-	(140.85,127.78) --
-	(144.09,129.47) --
-	(147.34,131.15) --
-	(150.58,132.82) --
-	(153.82,134.50) --
-	(157.07,136.18) --
-	(160.31,137.85) --
-	(163.56,139.50) --
-	(166.80,141.14) --
-	(170.04,142.77) --
-	(173.29,144.39) --
-	(176.53,146.00) --
-	(179.78,147.60) --
-	(183.02,149.19) --
-	(186.26,150.78) --
-	(189.51,152.36) --
-	(192.75,153.93) --
-	(196.00,155.49) --
-	(199.24,157.04) --
-	(202.48,158.58) --
-	(205.73,160.11) --
-	(208.97,161.63) --
-	(212.21,163.15) --
-	(215.46,164.65) --
-	(218.70,166.14) --
-	(221.95,167.63) --
-	(225.19,169.10) --
-	(228.43,170.57) --
-	(231.68,172.02) --
-	(234.92,173.47) --
-	(238.17,174.91) --
-	(241.41,176.33) --
-	(244.65,177.75) --
-	(247.90,179.16) --
-	(251.14,180.56) --
-	(254.39,181.95) --
-	(257.63,183.33) --
-	(260.87,184.70) --
-	(264.12,186.06) --
-	(267.36,187.41) --
-	(270.60,188.75) --
-	(273.85,190.08) --
-	(277.09,191.40) --
-	(280.34,192.72) --
-	(283.58,194.02);
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 64.08) --
+	( 30.56, 66.04) --
+	( 33.80, 67.97) --
+	( 37.04, 69.88) --
+	( 40.29, 71.77) --
+	( 43.53, 73.64) --
+	( 46.78, 75.49) --
+	( 50.02, 77.31) --
+	( 53.26, 79.12) --
+	( 56.51, 80.91) --
+	( 59.75, 82.67) --
+	( 63.00, 84.42) --
+	( 66.24, 86.14) --
+	( 69.48, 87.84) --
+	( 72.73, 89.53) --
+	( 75.97, 91.19) --
+	( 79.22, 92.83) --
+	( 82.46, 94.46) --
+	( 85.70, 96.06) --
+	( 88.95, 97.65) --
+	( 92.19, 99.21) --
+	( 95.43,100.75) --
+	( 98.68,102.26) --
+	(101.92,103.75) --
+	(105.17,105.23) --
+	(108.41,106.68) --
+	(111.65,108.11) --
+	(114.90,109.53) --
+	(118.14,110.93) --
+	(121.39,112.32) --
+	(124.63,113.68) --
+	(127.87,115.02) --
+	(131.12,116.33) --
+	(134.36,117.61) --
+	(137.61,118.88) --
+	(140.85,120.13) --
+	(144.09,121.37) --
+	(147.34,122.61) --
+	(150.58,123.84) --
+	(153.82,125.07) --
+	(157.07,126.29) --
+	(160.31,127.51) --
+	(163.56,128.71) --
+	(166.80,129.90) --
+	(170.04,131.07) --
+	(173.29,132.24) --
+	(176.53,133.40) --
+	(179.78,134.54) --
+	(183.02,135.68) --
+	(186.26,136.82) --
+	(189.51,137.95) --
+	(192.75,139.07) --
+	(196.00,140.19) --
+	(199.24,141.29) --
+	(202.48,142.39) --
+	(205.73,143.48) --
+	(208.97,144.56) --
+	(212.21,145.63) --
+	(215.46,146.69) --
+	(218.70,147.75) --
+	(221.95,148.80) --
+	(225.19,149.84) --
+	(228.43,150.87) --
+	(231.68,151.89) --
+	(234.92,152.91) --
+	(238.17,153.91) --
+	(241.41,154.91) --
+	(244.65,155.90) --
+	(247.90,156.88) --
+	(251.14,157.85) --
+	(254.39,158.82) --
+	(257.63,159.78) --
+	(260.87,160.73) --
+	(264.12,161.67) --
+	(267.36,162.60) --
+	(270.60,163.52) --
+	(273.85,164.44) --
+	(277.09,165.35) --
+	(280.34,166.24) --
+	(283.58,167.14);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 27.31, 63.95) --
+	( 30.56, 66.36) --
+	( 33.80, 68.74) --
+	( 37.04, 71.10) --
+	( 40.29, 73.43) --
+	( 43.53, 75.74) --
+	( 46.78, 78.03) --
+	( 50.02, 80.29) --
+	( 53.26, 82.53) --
+	( 56.51, 84.74) --
+	( 59.75, 86.93) --
+	( 63.00, 89.09) --
+	( 66.24, 91.23) --
+	( 69.48, 93.35) --
+	( 72.73, 95.44) --
+	( 75.97, 97.51) --
+	( 79.22, 99.55) --
+	( 82.46,101.58) --
+	( 85.70,103.58) --
+	( 88.95,105.56) --
+	( 92.19,107.51) --
+	( 95.43,109.43) --
+	( 98.68,111.32) --
+	(101.92,113.19) --
+	(105.17,115.04) --
+	(108.41,116.86) --
+	(111.65,118.67) --
+	(114.90,120.45) --
+	(118.14,122.21) --
+	(121.39,123.96) --
+	(124.63,125.67) --
+	(127.87,127.35) --
+	(131.12,129.01) --
+	(134.36,130.63) --
+	(137.61,132.24) --
+	(140.85,133.82) --
+	(144.09,135.39) --
+	(147.34,136.96) --
+	(150.58,138.52) --
+	(153.82,140.07) --
+	(157.07,141.63) --
+	(160.31,143.18) --
+	(163.56,144.71) --
+	(166.80,146.22) --
+	(170.04,147.72) --
+	(173.29,149.21) --
+	(176.53,150.69) --
+	(179.78,152.15) --
+	(183.02,153.61) --
+	(186.26,155.06) --
+	(189.51,156.51) --
+	(192.75,157.94) --
+	(196.00,159.37) --
+	(199.24,160.79) --
+	(202.48,162.19) --
+	(205.73,163.58) --
+	(208.97,164.97) --
+	(212.21,166.34) --
+	(215.46,167.71) --
+	(218.70,169.06) --
+	(221.95,170.41) --
+	(225.19,171.74) --
+	(228.43,173.07) --
+	(231.68,174.38) --
+	(234.92,175.69) --
+	(238.17,176.98) --
+	(241.41,178.27) --
+	(244.65,179.54) --
+	(247.90,180.81) --
+	(251.14,182.06) --
+	(254.39,183.31) --
+	(257.63,184.54) --
+	(260.87,185.77) --
+	(264.12,186.98) --
+	(267.36,188.19) --
+	(270.60,189.38) --
+	(273.85,190.57) --
+	(277.09,191.74) --
+	(280.34,192.91) --
+	(283.58,194.06);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[fill=fillColor] ( 27.31, 59.60) --
-	( 30.68, 53.77) --
-	( 23.95, 53.77) --
-	cycle;
-
-\path[fill=fillColor] ( 35.86, 62.47) --
-	( 39.22, 56.65) --
-	( 32.49, 56.65) --
-	cycle;
-
-\path[fill=fillColor] ( 44.40, 65.07) --
-	( 47.76, 59.25) --
-	( 41.03, 59.25) --
-	cycle;
-
-\path[fill=fillColor] ( 52.94, 68.02) --
-	( 56.30, 62.19) --
-	( 49.58, 62.19) --
-	cycle;
-
-\path[fill=fillColor] ( 61.48, 70.77) --
-	( 64.85, 64.95) --
-	( 58.12, 64.95) --
-	cycle;
-
-\path[fill=fillColor] ( 70.02, 73.26) --
-	( 73.39, 67.44) --
-	( 66.66, 67.44) --
-	cycle;
-
-\path[fill=fillColor] ( 78.57, 75.65) --
-	( 81.93, 69.83) --
-	( 75.20, 69.83) --
-	cycle;
-
-\path[fill=fillColor] ( 87.11, 78.08) --
-	( 90.47, 72.25) --
-	( 83.75, 72.25) --
-	cycle;
-
-\path[fill=fillColor] ( 95.65, 80.50) --
-	( 99.01, 74.67) --
-	( 92.29, 74.67) --
-	cycle;
-
-\path[fill=fillColor] (104.19, 82.71) --
-	(107.56, 76.88) --
-	(100.83, 76.88) --
-	cycle;
-
-\path[fill=fillColor] (112.74, 84.81) --
-	(116.10, 78.99) --
-	(109.37, 78.99) --
-	cycle;
-
-\path[fill=fillColor] (121.28, 86.66) --
-	(124.64, 80.84) --
-	(117.91, 80.84) --
-	cycle;
-
-\path[fill=fillColor] (129.82, 88.60) --
-	(133.18, 82.78) --
-	(126.46, 82.78) --
-	cycle;
-
-\path[fill=fillColor] (138.36, 90.48) --
-	(141.73, 84.65) --
-	(135.00, 84.65) --
-	cycle;
-
-\path[fill=fillColor] (146.90, 92.35) --
-	(150.27, 86.53) --
-	(143.54, 86.53) --
-	cycle;
-
-\path[fill=fillColor] (155.45, 94.13) --
-	(158.81, 88.30) --
-	(152.08, 88.30) --
-	cycle;
-
-\path[fill=fillColor] (163.99, 95.79) --
-	(167.35, 89.97) --
-	(160.63, 89.97) --
-	cycle;
-
-\path[fill=fillColor] (172.53, 97.50) --
-	(175.89, 91.67) --
-	(169.17, 91.67) --
-	cycle;
-
-\path[fill=fillColor] (181.07, 99.31) --
-	(184.44, 93.48) --
-	(177.71, 93.48) --
-	cycle;
-
-\path[fill=fillColor] (189.62,100.91) --
-	(192.98, 95.09) --
-	(186.25, 95.09) --
-	cycle;
-
-\path[fill=fillColor] (198.16,102.55) --
-	(201.52, 96.72) --
-	(194.79, 96.72) --
-	cycle;
-
-\path[fill=fillColor] (206.70,104.08) --
-	(210.06, 98.25) --
-	(203.34, 98.25) --
-	cycle;
-
-\path[fill=fillColor] (215.24,105.58) --
-	(218.61, 99.75) --
-	(211.88, 99.75) --
-	cycle;
-
-\path[fill=fillColor] (223.78,107.13) --
-	(227.15,101.30) --
-	(220.42,101.30) --
-	cycle;
-
-\path[fill=fillColor] (232.33,108.61) --
-	(235.69,102.78) --
-	(228.96,102.78) --
-	cycle;
-
-\path[fill=fillColor] (240.87,109.99) --
-	(244.23,104.16) --
-	(237.51,104.16) --
-	cycle;
-
-\path[fill=fillColor] (249.41,111.47) --
-	(252.77,105.64) --
-	(246.05,105.64) --
-	cycle;
-
-\path[fill=fillColor] (257.95,112.80) --
-	(261.32,106.97) --
-	(254.59,106.97) --
-	cycle;
-
-\path[fill=fillColor] (266.50,114.25) --
-	(269.86,108.43) --
-	(263.13,108.43) --
-	cycle;
-
-\path[fill=fillColor] (275.04,115.51) --
-	(278.40,109.68) --
-	(271.67,109.68) --
-	cycle;
-
-\path[fill=fillColor] (283.58,116.83) --
-	(286.94,111.01) --
-	(280.22,111.01) --
+\path[fill=fillColor] ( 27.31, 68.04) --
+	( 30.68, 62.21) --
+	( 23.95, 62.21) --
+	cycle;
+
+\path[fill=fillColor] ( 35.86, 70.65) --
+	( 39.22, 64.82) --
+	( 32.49, 64.82) --
+	cycle;
+
+\path[fill=fillColor] ( 44.40, 73.00) --
+	( 47.76, 67.17) --
+	( 41.03, 67.17) --
+	cycle;
+
+\path[fill=fillColor] ( 52.94, 75.66) --
+	( 56.30, 69.83) --
+	( 49.58, 69.83) --
+	cycle;
+
+\path[fill=fillColor] ( 61.48, 78.15) --
+	( 64.85, 72.32) --
+	( 58.12, 72.32) --
+	cycle;
+
+\path[fill=fillColor] ( 70.02, 80.38) --
+	( 73.39, 74.55) --
+	( 66.66, 74.55) --
+	cycle;
+
+\path[fill=fillColor] ( 78.57, 82.50) --
+	( 81.93, 76.67) --
+	( 75.20, 76.67) --
+	cycle;
+
+\path[fill=fillColor] ( 87.11, 84.65) --
+	( 90.47, 78.82) --
+	( 83.75, 78.82) --
+	cycle;
+
+\path[fill=fillColor] ( 95.65, 86.82) --
+	( 99.01, 80.99) --
+	( 92.29, 80.99) --
+	cycle;
+
+\path[fill=fillColor] (104.19, 88.79) --
+	(107.56, 82.96) --
+	(100.83, 82.96) --
+	cycle;
+
+\path[fill=fillColor] (112.74, 90.70) --
+	(116.10, 84.87) --
+	(109.37, 84.87) --
+	cycle;
+
+\path[fill=fillColor] (121.28, 92.30) --
+	(124.64, 86.48) --
+	(117.91, 86.48) --
+	cycle;
+
+\path[fill=fillColor] (129.82, 94.04) --
+	(133.18, 88.21) --
+	(126.46, 88.21) --
+	cycle;
+
+\path[fill=fillColor] (138.36, 95.68) --
+	(141.73, 89.85) --
+	(135.00, 89.85) --
+	cycle;
+
+\path[fill=fillColor] (146.90, 97.35) --
+	(150.27, 91.53) --
+	(143.54, 91.53) --
+	cycle;
+
+\path[fill=fillColor] (155.45, 98.90) --
+	(158.81, 93.07) --
+	(152.08, 93.07) --
+	cycle;
+
+\path[fill=fillColor] (163.99,100.37) --
+	(167.35, 94.54) --
+	(160.63, 94.54) --
+	cycle;
+
+\path[fill=fillColor] (172.53,101.89) --
+	(175.89, 96.06) --
+	(169.17, 96.06) --
+	cycle;
+
+\path[fill=fillColor] (181.07,103.46) --
+	(184.44, 97.64) --
+	(177.71, 97.64) --
+	cycle;
+
+\path[fill=fillColor] (189.62,104.87) --
+	(192.98, 99.04) --
+	(186.25, 99.04) --
+	cycle;
+
+\path[fill=fillColor] (198.16,106.29) --
+	(201.52,100.47) --
+	(194.79,100.47) --
+	cycle;
+
+\path[fill=fillColor] (206.70,107.65) --
+	(210.06,101.82) --
+	(203.34,101.82) --
+	cycle;
+
+\path[fill=fillColor] (215.24,108.93) --
+	(218.61,103.11) --
+	(211.88,103.11) --
+	cycle;
+
+\path[fill=fillColor] (223.78,110.30) --
+	(227.15,104.48) --
+	(220.42,104.48) --
+	cycle;
+
+\path[fill=fillColor] (232.33,111.62) --
+	(235.69,105.79) --
+	(228.96,105.79) --
+	cycle;
+
+\path[fill=fillColor] (240.87,112.82) --
+	(244.23,106.99) --
+	(237.51,106.99) --
+	cycle;
+
+\path[fill=fillColor] (249.41,114.10) --
+	(252.77,108.28) --
+	(246.05,108.28) --
+	cycle;
+
+\path[fill=fillColor] (257.95,115.26) --
+	(261.32,109.43) --
+	(254.59,109.43) --
+	cycle;
+
+\path[fill=fillColor] (266.50,116.55) --
+	(269.86,110.72) --
+	(263.13,110.72) --
+	cycle;
+
+\path[fill=fillColor] (275.04,117.65) --
+	(278.40,111.83) --
+	(271.67,111.83) --
+	cycle;
+
+\path[fill=fillColor] (283.58,118.80) --
+	(286.94,112.97) --
+	(280.22,112.97) --
 	cycle;
@@
 
-\path[fill=fillColor] ( 24.82, 53.14) --
-	( 29.81, 53.14) --
-	( 29.81, 58.14) --
-	( 24.82, 58.14) --
-	cycle;
-
-\path[fill=fillColor] ( 33.36, 57.75) --
-	( 38.35, 57.75) --
-	( 38.35, 62.75) --
-	( 33.36, 62.75) --
-	cycle;
-
-\path[fill=fillColor] ( 41.90, 61.97) --
-	( 46.90, 61.97) --
-	( 46.90, 66.96) --
-	( 41.90, 66.96) --
-	cycle;
-
-\path[fill=fillColor] ( 50.44, 66.76) --
-	( 55.44, 66.76) --
-	( 55.44, 71.75) --
-	( 50.44, 71.75) --
-	cycle;
-
-\path[fill=fillColor] ( 58.98, 71.20) --
-	( 63.98, 71.20) --
-	( 63.98, 76.19) --
-	( 58.98, 76.19) --
-	cycle;
-
-\path[fill=fillColor] ( 67.53, 75.33) --
-	( 72.52, 75.33) --
-	( 72.52, 80.32) --
-	( 67.53, 80.32) --
-	cycle;
-
-\path[fill=fillColor] ( 76.07, 79.35) --
-	( 81.06, 79.35) --
-	( 81.06, 84.34) --
-	( 76.07, 84.34) --
-	cycle;
-
-\path[fill=fillColor] ( 84.61, 83.44) --
-	( 89.61, 83.44) --
-	( 89.61, 88.43) --
-	( 84.61, 88.43) --
-	cycle;
-
-\path[fill=fillColor] ( 93.15, 87.44) --
-	( 98.15, 87.44) --
-	( 98.15, 92.44) --
-	( 93.15, 92.44) --
-	cycle;
-
-\path[fill=fillColor] (101.70, 91.12) --
-	(106.69, 91.12) --
-	(106.69, 96.12) --
-	(101.70, 96.12) --
-	cycle;
-
-\path[fill=fillColor] (110.24, 94.51) --
-	(115.23, 94.51) --
-	(115.23, 99.50) --
-	(110.24, 99.50) --
-	cycle;
-
-\path[fill=fillColor] (118.78, 97.80) --
-	(123.78, 97.80) --
-	(123.78,102.79) --
-	(118.78,102.79) --
-	cycle;
-
-\path[fill=fillColor] (127.32,101.03) --
-	(132.32,101.03) --
-	(132.32,106.02) --
-	(127.32,106.02) --
-	cycle;
-
-\path[fill=fillColor] (135.86,104.29) --
-	(140.86,104.29) --
-	(140.86,109.28) --
-	(135.86,109.28) --
-	cycle;
-
-\path[fill=fillColor] (144.41,107.42) --
-	(149.40,107.42) --
-	(149.40,112.41) --
-	(144.41,112.41) --
-	cycle;
-
-\path[fill=fillColor] (152.95,110.55) --
-	(157.94,110.55) --
-	(157.94,115.55) --
-	(152.95,115.55) --
-	cycle;
-
-\path[fill=fillColor] (161.49,113.41) --
-	(166.49,113.41) --
-	(166.49,118.40) --
-	(161.49,118.40) --
-	cycle;
-
-\path[fill=fillColor] (170.03,116.27) --
-	(175.03,116.27) --
-	(175.03,121.26) --
-	(170.03,121.26) --
-	cycle;
-
-\path[fill=fillColor] (178.58,119.47) --
-	(183.57,119.47) --
-	(183.57,124.47) --
-	(178.58,124.47) --
-	cycle;
-
-\path[fill=fillColor] (187.12,122.28) --
-	(192.11,122.28) --
-	(192.11,127.28) --
-	(187.12,127.28) --
-	cycle;
-
-\path[fill=fillColor] (195.66,125.17) --
-	(200.66,125.17) --
-	(200.66,130.16) --
-	(195.66,130.16) --
-	cycle;
-
-\path[fill=fillColor] (204.20,127.80) --
-	(209.20,127.80) --
-	(209.20,132.80) --
-	(204.20,132.80) --
-	cycle;
-
-\path[fill=fillColor] (212.74,130.49) --
-	(217.74,130.49) --
-	(217.74,135.48) --
-	(212.74,135.48) --
-	cycle;
-
-\path[fill=fillColor] (221.29,133.19) --
-	(226.28,133.19) --
-	(226.28,138.18) --
-	(221.29,138.18) --
-	cycle;
-
-\path[fill=fillColor] (229.83,135.74) --
-	(234.82,135.74) --
-	(234.82,140.73) --
-	(229.83,140.73) --
-	cycle;
-
-\path[fill=fillColor] (238.37,138.17) --
-	(243.37,138.17) --
-	(243.37,143.16) --
-	(238.37,143.16) --
-	cycle;
-
-\path[fill=fillColor] (246.91,140.85) --
-	(251.91,140.85) --
-	(251.91,145.85) --
-	(246.91,145.85) --
-	cycle;
-
-\path[fill=fillColor] (255.46,143.24) --
-	(260.45,143.24) --
-	(260.45,148.23) --
-	(255.46,148.23) --
-	cycle;
-
-\path[fill=fillColor] (264.00,145.71) --
-	(268.99,145.71) --
-	(268.99,150.71) --
-	(264.00,150.71) --
-	cycle;
-
-\path[fill=fillColor] (272.54,147.90) --
-	(277.54,147.90) --
-	(277.54,152.89) --
-	(272.54,152.89) --
-	cycle;
-
-\path[fill=fillColor] (281.08,150.34) --
-	(286.08,150.34) --
-	(286.08,155.34) --
-	(281.08,155.34) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78, 55.41) -- ( 30.85, 55.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31, 51.87) -- ( 27.31, 58.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32, 61.62) -- ( 39.39, 61.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86, 58.09) -- ( 35.86, 65.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87, 67.34) -- ( 47.93, 67.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40, 63.81) -- ( 44.40, 70.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41, 73.88) -- ( 56.47, 73.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94, 70.35) -- ( 52.94, 77.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95, 79.89) -- ( 65.01, 79.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48, 76.36) -- ( 61.48, 83.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49, 85.65) -- ( 73.56, 85.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02, 82.12) -- ( 70.02, 89.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03, 91.28) -- ( 82.10, 91.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57, 87.75) -- ( 78.57, 94.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58, 97.06) -- ( 90.64, 97.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11, 93.53) -- ( 87.11,100.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,102.60) -- ( 99.18,102.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 99.07) -- ( 95.65,106.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,107.76) -- (107.73,107.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,104.23) -- (104.19,111.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,112.34) -- (116.27,112.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,108.81) -- (112.74,115.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,117.19) -- (124.81,117.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,113.66) -- (121.28,120.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,121.71) -- (133.35,121.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,118.17) -- (129.82,125.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,126.41) -- (141.89,126.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,122.88) -- (138.36,129.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,130.85) -- (150.44,130.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,127.32) -- (146.90,134.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,135.49) -- (158.98,135.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,131.96) -- (155.45,139.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,139.55) -- (167.52,139.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,136.02) -- (163.99,143.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,143.62) -- (176.06,143.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,140.09) -- (172.53,147.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,148.33) -- (184.61,148.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,144.80) -- (181.07,151.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,152.45) -- (193.15,152.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,148.92) -- (189.62,155.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,156.73) -- (201.69,156.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,153.19) -- (198.16,160.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,160.57) -- (210.23,160.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,157.04) -- (206.70,164.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,164.54) -- (218.77,164.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,161.01) -- (215.24,168.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,168.54) -- (227.32,168.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,165.01) -- (223.78,172.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,172.25) -- (235.86,172.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,168.71) -- (232.33,175.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,175.81) -- (244.40,175.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,172.28) -- (240.87,179.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,179.95) -- (252.94,179.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,176.42) -- (249.41,183.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,183.53) -- (261.49,183.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,179.99) -- (257.95,187.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,187.15) -- (270.03,187.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,183.62) -- (266.50,190.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,190.32) -- (278.57,190.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,186.78) -- (275.04,193.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,194.15) -- (287.11,194.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,190.62) -- (283.58,197.68);
+\path[fill=fillColor] ( 24.82, 61.68) --
+	( 29.81, 61.68) --
+	( 29.81, 66.68) --
+	( 24.82, 66.68) --
+	cycle;
+
+\path[fill=fillColor] ( 33.36, 65.53) --
+	( 38.35, 65.53) --
+	( 38.35, 70.52) --
+	( 33.36, 70.52) --
+	cycle;
+
+\path[fill=fillColor] ( 41.90, 69.01) --
+	( 46.90, 69.01) --
+	( 46.90, 74.00) --
+	( 41.90, 74.00) --
+	cycle;
+
+\path[fill=fillColor] ( 50.44, 72.95) --
+	( 55.44, 72.95) --
+	( 55.44, 77.95) --
+	( 50.44, 77.95) --
+	cycle;
+
+\path[fill=fillColor] ( 58.98, 76.64) --
+	( 63.98, 76.64) --
+	( 63.98, 81.63) --
+	( 58.98, 81.63) --
+	cycle;
+
+\path[fill=fillColor] ( 67.53, 79.97) --
+	( 72.52, 79.97) --
+	( 72.52, 84.96) --
+	( 67.53, 84.96) --
+	cycle;
+
+\path[fill=fillColor] ( 76.07, 83.16) --
+	( 81.06, 83.16) --
+	( 81.06, 88.16) --
+	( 76.07, 88.16) --
+	cycle;
+
+\path[fill=fillColor] ( 84.61, 86.41) --
+	( 89.61, 86.41) --
+	( 89.61, 91.41) --
+	( 84.61, 91.41) --
+	cycle;
+
+\path[fill=fillColor] ( 93.15, 89.65) --
+	( 98.15, 89.65) --
+	( 98.15, 94.65) --
+	( 93.15, 94.65) --
+	cycle;
+
+\path[fill=fillColor] (101.70, 92.60) --
+	(106.69, 92.60) --
+	(106.69, 97.60) --
+	(101.70, 97.60) --
+	cycle;
+
+\path[fill=fillColor] (110.24, 95.42) --
+	(115.23, 95.42) --
+	(115.23,100.42) --
+	(110.24,100.42) --
+	cycle;
+
+\path[fill=fillColor] (118.78, 97.90) --
+	(123.78, 97.90) --
+	(123.78,102.89) --
+	(118.78,102.89) --
+	cycle;
+
+\path[fill=fillColor] (127.32,100.49) --
+	(132.32,100.49) --
+	(132.32,105.49) --
+	(127.32,105.49) --
+	cycle;
+
+\path[fill=fillColor] (135.86,103.01) --
+	(140.86,103.01) --
+	(140.86,108.00) --
+	(135.86,108.00) --
+	cycle;
+
+\path[fill=fillColor] (144.41,105.51) --
+	(149.40,105.51) --
+	(149.40,110.51) --
+	(144.41,110.51) --
+	cycle;
+
+\path[fill=fillColor] (152.95,107.88) --
+	(157.94,107.88) --
+	(157.94,112.88) --
+	(152.95,112.88) --
+	cycle;
+
+\path[fill=fillColor] (161.49,110.12) --
+	(166.49,110.12) --
+	(166.49,115.11) --
+	(161.49,115.11) --
+	cycle;
+
+\path[fill=fillColor] (170.03,112.40) --
+	(175.03,112.40) --
+	(175.03,117.39) --
+	(170.03,117.39) --
+	cycle;
+
+\path[fill=fillColor] (178.58,114.82) --
+	(183.57,114.82) --
+	(183.57,119.82) --
+	(178.58,119.82) --
+	cycle;
+
+\path[fill=fillColor] (187.12,116.97) --
+	(192.11,116.97) --
+	(192.11,121.96) --
+	(187.12,121.96) --
+	cycle;
+
+\path[fill=fillColor] (195.66,119.16) --
+	(200.66,119.16) --
+	(200.66,124.15) --
+	(195.66,124.15) --
+	cycle;
+
+\path[fill=fillColor] (204.20,121.21) --
+	(209.20,121.21) --
+	(209.20,126.20) --
+	(204.20,126.20) --
+	cycle;
+
+\path[fill=fillColor] (212.74,123.21) --
+	(217.74,123.21) --
+	(217.74,128.21) --
+	(212.74,128.21) --
+	cycle;
+
+\path[fill=fillColor] (221.29,125.29) --
+	(226.28,125.29) --
+	(226.28,130.28) --
+	(221.29,130.28) --
+	cycle;
+
+\path[fill=fillColor] (229.83,127.27) --
+	(234.82,127.27) --
+	(234.82,132.26) --
+	(229.83,132.26) --
+	cycle;
+
+\path[fill=fillColor] (238.37,129.12) --
+	(243.37,129.12) --
+	(243.37,134.11) --
+	(238.37,134.11) --
+	cycle;
+
+\path[fill=fillColor] (246.91,131.10) --
+	(251.91,131.10) --
+	(251.91,136.09) --
+	(246.91,136.09) --
+	cycle;
+
+\path[fill=fillColor] (255.46,132.88) --
+	(260.45,132.88) --
+	(260.45,137.87) --
+	(255.46,137.87) --
+	cycle;
+
+\path[fill=fillColor] (264.00,134.82) --
+	(268.99,134.82) --
+	(268.99,139.81) --
+	(264.00,139.81) --
+	cycle;
+
+\path[fill=fillColor] (272.54,136.50) --
+	(277.54,136.50) --
+	(277.54,141.49) --
+	(272.54,141.49) --
+	cycle;
+
+\path[fill=fillColor] (281.08,138.27) --
+	(286.08,138.27) --
+	(286.08,143.27) --
+	(281.08,143.27) --
+	cycle;
+\definecolor{drawColor}{RGB}{0,158,115}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78, 64.15) -- ( 30.85, 64.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31, 60.62) -- ( 27.31, 67.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32, 69.18) -- ( 39.39, 69.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86, 65.65) -- ( 35.86, 72.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87, 73.76) -- ( 47.93, 73.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40, 70.23) -- ( 44.40, 77.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41, 78.96) -- ( 56.47, 78.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94, 75.42) -- ( 52.94, 82.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95, 83.79) -- ( 65.01, 83.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48, 80.26) -- ( 61.48, 87.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49, 88.22) -- ( 73.56, 88.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02, 84.69) -- ( 70.02, 91.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03, 92.50) -- ( 82.10, 92.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57, 88.97) -- ( 78.57, 96.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58, 96.86) -- ( 90.64, 96.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11, 93.33) -- ( 87.11,100.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,101.17) -- ( 99.18,101.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 97.63) -- ( 95.65,104.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,105.11) -- (107.73,105.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,101.57) -- (104.19,108.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,108.80) -- (116.27,108.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,105.26) -- (112.74,112.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,112.21) -- (124.81,112.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,108.68) -- (121.28,115.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,115.67) -- (133.35,115.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,112.14) -- (129.82,119.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,119.09) -- (141.89,119.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,115.56) -- (138.36,122.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,122.43) -- (150.44,122.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,118.90) -- (146.90,125.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,125.69) -- (158.98,125.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,122.16) -- (155.45,129.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,128.71) -- (167.52,128.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,125.18) -- (163.99,132.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,131.76) -- (176.06,131.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,128.22) -- (172.53,135.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,135.09) -- (184.61,135.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,131.55) -- (181.07,138.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,138.02) -- (193.15,138.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,134.49) -- (189.62,141.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,141.02) -- (201.69,141.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,137.49) -- (198.16,144.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,143.80) -- (210.23,143.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,140.26) -- (206.70,147.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,146.57) -- (218.77,146.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,143.04) -- (215.24,150.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,149.39) -- (227.32,149.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,145.86) -- (223.78,152.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,152.08) -- (235.86,152.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,148.55) -- (232.33,155.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,154.61) -- (244.40,154.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,151.07) -- (240.87,158.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,157.36) -- (252.94,157.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,153.83) -- (249.41,160.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,159.82) -- (261.49,159.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,156.28) -- (257.95,163.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,162.43) -- (270.03,162.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,158.90) -- (266.50,165.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,164.72) -- (278.57,164.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,161.19) -- (275.04,168.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,167.20) -- (287.11,167.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,163.67) -- (283.58,170.73);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 24.82, 61.58) rectangle ( 29.81, 66.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 24.82, 61.58) -- ( 29.81, 66.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 24.82, 66.58) -- ( 29.81, 61.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.36, 67.75) rectangle ( 38.35, 72.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.36, 67.75) -- ( 38.35, 72.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.36, 72.74) -- ( 38.35, 67.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.90, 73.39) rectangle ( 46.90, 78.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.90, 73.39) -- ( 46.90, 78.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.90, 78.39) -- ( 46.90, 73.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.44, 79.80) rectangle ( 55.44, 84.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.44, 79.80) -- ( 55.44, 84.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.44, 84.80) -- ( 55.44, 79.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.98, 85.74) rectangle ( 63.98, 90.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.98, 85.74) -- ( 63.98, 90.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.98, 90.74) -- ( 63.98, 85.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 67.53, 91.27) rectangle ( 72.52, 96.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 67.53, 91.27) -- ( 72.52, 96.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 67.53, 96.26) -- ( 72.52, 91.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.07, 96.65) rectangle ( 81.06,101.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.07, 96.65) -- ( 81.06,101.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.07,101.64) -- ( 81.06, 96.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.61,102.12) rectangle ( 89.61,107.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.61,102.12) -- ( 89.61,107.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.61,107.12) -- ( 89.61,102.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.15,107.48) rectangle ( 98.15,112.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.15,107.48) -- ( 98.15,112.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.15,112.48) -- ( 98.15,107.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.70,112.41) rectangle (106.69,117.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.70,112.41) -- (106.69,117.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.70,117.40) -- (106.69,112.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.24,116.94) rectangle (115.23,121.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.24,116.94) -- (115.23,121.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.24,121.93) -- (115.23,116.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.78,121.34) rectangle (123.78,126.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.78,121.34) -- (123.78,126.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.78,126.34) -- (123.78,121.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.32,125.66) rectangle (132.32,130.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.32,125.66) -- (132.32,130.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.32,130.66) -- (132.32,125.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.86,130.03) rectangle (140.86,135.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.86,130.03) -- (140.86,135.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.86,135.02) -- (140.86,130.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.41,134.21) rectangle (149.40,139.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.41,134.21) -- (149.40,139.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.41,139.21) -- (149.40,134.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.95,138.41) rectangle (157.94,143.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.95,138.41) -- (157.94,143.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.95,143.40) -- (157.94,138.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.49,142.23) rectangle (166.49,147.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.49,142.23) -- (166.49,147.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.49,147.22) -- (166.49,142.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.03,146.06) rectangle (175.03,151.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.03,146.06) -- (175.03,151.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.03,151.05) -- (175.03,146.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.58,150.34) rectangle (183.57,155.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.58,150.34) -- (183.57,155.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.58,155.34) -- (183.57,150.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.12,154.10) rectangle (192.11,159.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.12,154.10) -- (192.11,159.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.12,159.10) -- (192.11,154.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.66,157.97) rectangle (200.66,162.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.66,157.97) -- (200.66,162.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.66,162.96) -- (200.66,157.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.20,161.49) rectangle (209.20,166.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.20,161.49) -- (209.20,166.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.20,166.49) -- (209.20,161.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.74,165.09) rectangle (217.74,170.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.74,165.09) -- (217.74,170.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.74,170.08) -- (217.74,165.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.29,168.70) rectangle (226.28,173.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.29,168.70) -- (226.28,173.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.29,173.69) -- (226.28,168.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.83,172.11) rectangle (234.82,177.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.83,172.11) -- (234.82,177.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.83,177.11) -- (234.82,172.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.37,175.36) rectangle (243.37,180.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.37,175.36) -- (243.37,180.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.37,180.35) -- (243.37,175.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.91,178.96) rectangle (251.91,183.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.91,178.96) -- (251.91,183.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.91,183.95) -- (251.91,178.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.46,182.15) rectangle (260.45,187.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.46,182.15) -- (260.45,187.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.46,187.14) -- (260.45,182.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.00,185.46) rectangle (268.99,190.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.00,185.46) -- (268.99,190.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.00,190.45) -- (268.99,185.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (272.54,188.38) rectangle (277.54,193.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (272.54,188.38) -- (277.54,193.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (272.54,193.38) -- (277.54,188.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.08,191.66) rectangle (286.08,196.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.08,191.66) -- (286.08,196.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.08,196.65) -- (286.08,191.66);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[fill=fillColor] ( 27.31, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 35.86, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 44.40, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 52.94, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 61.48, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 70.02, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 78.57, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 87.11, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 95.65, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (104.19, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (112.74, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (121.28, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (129.82, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (138.36, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (146.90, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (155.45, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (163.99, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (172.53, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (181.07, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (189.62, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (198.16, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (206.70, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (215.24, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (223.78, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (232.33, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (240.87, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (249.41, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (257.95, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (266.50, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (275.04, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (283.58, 54.98) circle (  2.50);
+\path[fill=fillColor] ( 27.31, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 35.86, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 44.40, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 52.94, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 61.48, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 70.02, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 78.57, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 87.11, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 95.65, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (104.19, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (112.74, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (121.28, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (129.82, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (138.36, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (146.90, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (155.45, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (163.99, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (172.53, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (181.07, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (189.62, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (198.16, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (206.70, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (215.24, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (223.78, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (232.33, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (240.87, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (249.41, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (257.95, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (266.50, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (275.04, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (283.58, 63.20) circle (  2.50);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 52.22) {5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,134.09) {6};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 60.52) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,170.08) {6};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 55.25) --
-	( 27.31, 55.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,137.12) --
-	( 27.31,137.12);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 63.55) --
+	( 27.31, 63.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,173.11) --
+	( 27.31,173.11);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24,115.70) --
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24, 97.64) --
+	(326.39, 97.20) --
+	(329.55, 96.77) --
+	(332.71, 96.35) --
+	(335.87, 95.93) --
+	(339.02, 95.52) --
+	(342.18, 95.12) --
+	(345.34, 94.73) --
+	(348.49, 94.34) --
+	(351.65, 93.96) --
+	(354.81, 93.58) --
+	(357.97, 93.22) --
+	(361.12, 92.86) --
+	(364.28, 92.51) --
+	(367.44, 92.16) --
+	(370.60, 91.82) --
+	(373.75, 91.49) --
+	(376.91, 91.17) --
+	(380.07, 90.85) --
+	(383.22, 90.54) --
+	(386.38, 90.23) --
+	(389.54, 89.94) --
+	(392.70, 89.65) --
+	(395.85, 89.37) --
+	(399.01, 89.10) --
+	(402.17, 88.84) --
+	(405.32, 88.58) --
+	(408.48, 88.32) --
+	(411.64, 88.07) --
+	(414.80, 87.82) --
+	(417.95, 87.59) --
+	(421.11, 87.36) --
+	(424.27, 87.14) --
+	(427.43, 86.92) --
+	(430.58, 86.72) --
+	(433.74, 86.51) --
+	(436.90, 86.31) --
+	(440.05, 86.12) --
+	(443.21, 85.92) --
+	(446.37, 85.72) --
+	(449.53, 85.52) --
+	(452.68, 85.33) --
+	(455.84, 85.14) --
+	(459.00, 84.95) --
+	(462.16, 84.77) --
+	(465.31, 84.59) --
+	(468.47, 84.41) --
+	(471.63, 84.24) --
+	(474.78, 84.07) --
+	(477.94, 83.89) --
+	(481.10, 83.72) --
+	(484.26, 83.55) --
+	(487.41, 83.38) --
+	(490.57, 83.21) --
+	(493.73, 83.04) --
+	(496.89, 82.88) --
+	(500.04, 82.72) --
+	(503.20, 82.56) --
+	(506.36, 82.40) --
+	(509.51, 82.25) --
+	(512.67, 82.09) --
+	(515.83, 81.94) --
+	(518.99, 81.79) --
+	(522.14, 81.64) --
+	(525.30, 81.49) --
+	(528.46, 81.35) --
+	(531.62, 81.20) --
+	(534.77, 81.06) --
+	(537.93, 80.92) --
+	(541.09, 80.79) --
+	(544.24, 80.65) --
+	(547.40, 80.52) --
+	(550.56, 80.39) --
+	(553.72, 80.26) --
+	(556.87, 80.13) --
+	(560.03, 80.00) --
+	(563.19, 79.88) --
+	(566.35, 79.76) --
+	(569.50, 79.64) --
+	(572.66, 79.52);
+\definecolor{drawColor}{RGB}{86,180,233}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,115.70) --
 	(326.39,114.93) --
@@
 	(572.66, 84.97);
-\definecolor{drawColor}{RGB}{86,180,233}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,149.67) --
+\definecolor{drawColor}{RGB}{0,158,115}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (323.24,133.03) --
+	(326.39,131.91) --
+	(329.55,130.81) --
+	(332.71,129.73) --
+	(335.87,128.67) --
+	(339.02,127.63) --
+	(342.18,126.61) --
+	(345.34,125.61) --
+	(348.49,124.63) --
+	(351.65,123.67) --
+	(354.81,122.72) --
+	(357.97,121.80) --
+	(361.12,120.90) --
+	(364.28,120.02) --
+	(367.44,119.15) --
+	(370.60,118.31) --
+	(373.75,117.48) --
+	(376.91,116.67) --
+	(380.07,115.88) --
+	(383.22,115.11) --
+	(386.38,114.36) --
+	(389.54,113.63) --
+	(392.70,112.93) --
+	(395.85,112.25) --
+	(399.01,111.59) --
+	(402.17,110.95) --
+	(405.32,110.32) --
+	(408.48,109.71) --
+	(411.64,109.11) --
+	(414.80,108.52) --
+	(417.95,107.94) --
+	(421.11,107.40) --
+	(424.27,106.87) --
+	(427.43,106.37) --
+	(430.58,105.88) --
+	(433.74,105.40) --
+	(436.90,104.94) --
+	(440.05,104.47) --
+	(443.21,104.01) --
+	(446.37,103.55) --
+	(449.53,103.09) --
+	(452.68,102.64) --
+	(455.84,102.20) --
+	(459.00,101.77) --
+	(462.16,101.35) --
+	(465.31,100.94) --
+	(468.47,100.54) --
+	(471.63,100.14) --
+	(474.78, 99.74) --
+	(477.94, 99.35) --
+	(481.10, 98.96) --
+	(484.26, 98.57) --
+	(487.41, 98.18) --
+	(490.57, 97.81) --
+	(493.73, 97.43) --
+	(496.89, 97.07) --
+	(500.04, 96.71) --
+	(503.20, 96.35) --
+	(506.36, 96.00) --
+	(509.51, 95.65) --
+	(512.67, 95.31) --
+	(515.83, 94.97) --
+	(518.99, 94.63) --
+	(522.14, 94.31) --
+	(525.30, 93.98) --
+	(528.46, 93.66) --
+	(531.62, 93.35) --
+	(534.77, 93.04) --
+	(537.93, 92.74) --
+	(541.09, 92.44) --
+	(544.24, 92.14) --
+	(547.40, 91.86) --
+	(550.56, 91.57) --
+	(553.72, 91.29) --
+	(556.87, 91.02) --
+	(560.03, 90.75) --
+	(563.19, 90.48) --
+	(566.35, 90.23) --
+	(569.50, 89.97) --
+	(572.66, 89.72);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (323.24,149.67) --
 	(326.39,148.19) --
@@
 	(572.66, 93.75);
+\definecolor{fillColor}{RGB}{230,159,0}
+
+\path[fill=fillColor] (323.24,101.62) --
+	(326.60, 95.79) --
+	(319.87, 95.79) --
+	cycle;
+
+\path[fill=fillColor] (331.55,100.41) --
+	(334.91, 94.58) --
+	(328.19, 94.58) --
+	cycle;
+
+\path[fill=fillColor] (339.86, 99.32) --
+	(343.23, 93.49) --
+	(336.50, 93.49) --
+	cycle;
+
+\path[fill=fillColor] (348.18, 98.18) --
+	(351.54, 92.35) --
+	(344.81, 92.35) --
+	cycle;
+
+\path[fill=fillColor] (356.49, 97.16) --
+	(359.86, 91.33) --
+	(353.13, 91.33) --
+	cycle;
+
+\path[fill=fillColor] (364.81, 96.27) --
+	(368.17, 90.44) --
+	(361.44, 90.44) --
+	cycle;
+
+\path[fill=fillColor] (373.12, 95.43) --
+	(376.48, 89.61) --
+	(369.76, 89.61) --
+	cycle;
+
+\path[fill=fillColor] (381.44, 94.63) --
+	(384.80, 88.80) --
+	(378.07, 88.80) --
+	cycle;
+
+\path[fill=fillColor] (389.75, 93.76) --
+	(393.11, 87.94) --
+	(386.39, 87.94) --
+	cycle;
+
+\path[fill=fillColor] (398.06, 92.98) --
+	(401.43, 87.16) --
+	(394.70, 87.16) --
+	cycle;
+
+\path[fill=fillColor] (406.38, 92.29) --
+	(409.74, 86.46) --
+	(403.01, 86.46) --
+	cycle;
+
+\path[fill=fillColor] (414.69, 91.68) --
+	(418.06, 85.86) --
+	(411.33, 85.86) --
+	cycle;
+
+\path[fill=fillColor] (423.01, 91.09) --
+	(426.37, 85.26) --
+	(419.64, 85.26) --
+	cycle;
+
+\path[fill=fillColor] (431.32, 90.57) --
+	(434.68, 84.74) --
+	(427.96, 84.74) --
+	cycle;
+
+\path[fill=fillColor] (439.63, 90.05) --
+	(443.00, 84.22) --
+	(436.27, 84.22) --
+	cycle;
+
+\path[fill=fillColor] (447.95, 89.54) --
+	(451.31, 83.72) --
+	(444.58, 83.72) --
+	cycle;
+
+\path[fill=fillColor] (456.26, 89.09) --
+	(459.63, 83.26) --
+	(452.90, 83.26) --
+	cycle;
+
+\path[fill=fillColor] (464.58, 88.59) --
+	(467.94, 82.77) --
+	(461.21, 82.77) --
+	cycle;
+
+\path[fill=fillColor] (472.89, 88.04) --
+	(476.25, 82.21) --
+	(469.53, 82.21) --
+	cycle;
+
+\path[fill=fillColor] (481.20, 87.56) --
+	(484.57, 81.73) --
+	(477.84, 81.73) --
+	cycle;
+
+\path[fill=fillColor] (489.52, 87.14) --
+	(492.88, 81.31) --
+	(486.15, 81.31) --
+	cycle;
+
+\path[fill=fillColor] (497.83, 86.70) --
+	(501.20, 80.87) --
+	(494.47, 80.87) --
+	cycle;
+
+\path[fill=fillColor] (506.15, 86.30) --
+	(509.51, 80.48) --
+	(502.78, 80.48) --
+	cycle;
+
+\path[fill=fillColor] (514.46, 85.86) --
+	(517.82, 80.04) --
+	(511.10, 80.04) --
+	cycle;
+
+\path[fill=fillColor] (522.78, 85.49) --
+	(526.14, 79.67) --
+	(519.41, 79.67) --
+	cycle;
+
+\path[fill=fillColor] (531.09, 85.15) --
+	(534.45, 79.33) --
+	(527.73, 79.33) --
+	cycle;
+
+\path[fill=fillColor] (539.40, 84.78) --
+	(542.77, 78.96) --
+	(536.04, 78.96) --
+	cycle;
+
+\path[fill=fillColor] (547.72, 84.39) --
+	(551.08, 78.57) --
+	(544.35, 78.57) --
+	cycle;
+
+\path[fill=fillColor] (556.03, 84.03) --
+	(559.40, 78.21) --
+	(552.67, 78.21) --
+	cycle;
+
+\path[fill=fillColor] (564.35, 83.73) --
+	(567.71, 77.90) --
+	(560.98, 77.90) --
+	cycle;
+
+\path[fill=fillColor] (572.66, 83.38) --
+	(576.02, 77.56) --
+	(569.30, 77.56) --
+	cycle;
+\definecolor{fillColor}{RGB}{86,180,233}
+
+\path[fill=fillColor] (320.74,113.39) --
+	(325.73,113.39) --
+	(325.73,118.38) --
+	(320.74,118.38) --
+	cycle;
+
+\path[fill=fillColor] (329.05,111.23) --
+	(334.05,111.23) --
+	(334.05,116.23) --
+	(329.05,116.23) --
+	cycle;
+
+\path[fill=fillColor] (337.37,109.33) --
+	(342.36,109.33) --
+	(342.36,114.33) --
+	(337.37,114.33) --
+	cycle;
+
+\path[fill=fillColor] (345.68,107.33) --
+	(350.68,107.33) --
+	(350.68,112.32) --
+	(345.68,112.32) --
+	cycle;
+
+\path[fill=fillColor] (353.99,105.51) --
+	(358.99,105.51) --
+	(358.99,110.51) --
+	(353.99,110.51) --
+	cycle;
+
+\path[fill=fillColor] (362.31,103.96) --
+	(367.30,103.96) --
+	(367.30,108.96) --
+	(362.31,108.96) --
+	cycle;
+
+\path[fill=fillColor] (370.62,102.51) --
+	(375.62,102.51) --
+	(375.62,107.50) --
+	(370.62,107.50) --
+	cycle;
+
+\path[fill=fillColor] (378.94,101.12) --
+	(383.93,101.12) --
+	(383.93,106.11) --
+	(378.94,106.11) --
+	cycle;
+
+\path[fill=fillColor] (387.25, 99.64) --
+	(392.25, 99.64) --
+	(392.25,104.64) --
+	(387.25,104.64) --
+	cycle;
+
+\path[fill=fillColor] (395.57, 98.32) --
+	(400.56, 98.32) --
+	(400.56,103.31) --
+	(395.57,103.31) --
+	cycle;
+
+\path[fill=fillColor] (403.88, 97.13) --
+	(408.88, 97.13) --
+	(408.88,102.13) --
+	(403.88,102.13) --
+	cycle;
+
+\path[fill=fillColor] (412.19, 96.11) --
+	(417.19, 96.11) --
+	(417.19,101.11) --
+	(412.19,101.11) --
+	cycle;
+
+\path[fill=fillColor] (420.51, 95.11) --
+	(425.50, 95.11) --
+	(425.50,100.10) --
+	(420.51,100.10) --
+	cycle;
+
+\path[fill=fillColor] (428.82, 94.21) --
+	(433.82, 94.21) --
+	(433.82, 99.20) --
+	(428.82, 99.20) --
+	cycle;
+
+\path[fill=fillColor] (437.14, 93.32) --
+	(442.13, 93.32) --
+	(442.13, 98.32) --
+	(437.14, 98.32) --
+	cycle;
+
+\path[fill=fillColor] (445.45, 92.49) --
+	(450.45, 92.49) --
+	(450.45, 97.48) --
+	(445.45, 97.48) --
+	cycle;
+
+\path[fill=fillColor] (453.76, 91.72) --
+	(458.76, 91.72) --
+	(458.76, 96.71) --
+	(453.76, 96.71) --
+	cycle;
+
+\path[fill=fillColor] (462.08, 90.90) --
+	(467.07, 90.90) --
+	(467.07, 95.89) --
+	(462.08, 95.89) --
+	cycle;
+
+\path[fill=fillColor] (470.39, 90.00) --
+	(475.39, 90.00) --
+	(475.39, 94.99) --
+	(470.39, 94.99) --
+	cycle;
+
+\path[fill=fillColor] (478.71, 89.22) --
+	(483.70, 89.22) --
+	(483.70, 94.21) --
+	(478.71, 94.21) --
+	cycle;
+
+\path[fill=fillColor] (487.02, 88.51) --
+	(492.02, 88.51) --
+	(492.02, 93.51) --
+	(487.02, 93.51) --
+	cycle;
+
+\path[fill=fillColor] (495.34, 87.80) --
+	(500.33, 87.80) --
+	(500.33, 92.79) --
+	(495.34, 92.79) --
+	cycle;
+
+\path[fill=fillColor] (503.65, 87.15) --
+	(508.64, 87.15) --
+	(508.64, 92.14) --
+	(503.65, 92.14) --
+	cycle;
+
+\path[fill=fillColor] (511.96, 86.43) --
+	(516.96, 86.43) --
+	(516.96, 91.43) --
+	(511.96, 91.43) --
+	cycle;
+
+\path[fill=fillColor] (520.28, 85.84) --
+	(525.27, 85.84) --
+	(525.27, 90.83) --
+	(520.28, 90.83) --
+	cycle;
+
+\path[fill=fillColor] (528.59, 85.28) --
+	(533.59, 85.28) --
+	(533.59, 90.27) --
+	(528.59, 90.27) --
+	cycle;
+
+\path[fill=fillColor] (536.91, 84.68) --
+	(541.90, 84.68) --
+	(541.90, 89.67) --
+	(536.91, 89.67) --
+	cycle;
+
+\path[fill=fillColor] (545.22, 84.07) --
+	(550.22, 84.07) --
+	(550.22, 89.07) --
+	(545.22, 89.07) --
+	cycle;
+
+\path[fill=fillColor] (553.53, 83.47) --
+	(558.53, 83.47) --
+	(558.53, 88.47) --
+	(553.53, 88.47) --
+	cycle;
+
+\path[fill=fillColor] (561.85, 82.98) --
+	(566.84, 82.98) --
+	(566.84, 87.97) --
+	(561.85, 87.97) --
+	cycle;
+
+\path[fill=fillColor] (570.16, 82.43) --
+	(575.16, 82.43) --
+	(575.16, 87.42) --
+	(570.16, 87.42) --
+	cycle;
 \definecolor{drawColor}{RGB}{0,158,115}
 
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (323.24,180.94) --
-	(326.39,178.70) --
-	(329.55,176.51) --
-	(332.71,174.35) --
-	(335.87,172.23) --
-	(339.02,170.16) --
-	(342.18,168.13) --
-	(345.34,166.14) --
-	(348.49,164.20) --
-	(351.65,162.29) --
-	(354.81,160.43) --
-	(357.97,158.62) --
-	(361.12,156.84) --
-	(364.28,155.11) --
-	(367.44,153.41) --
-	(370.60,151.76) --
-	(373.75,150.14) --
-	(376.91,148.56) --
-	(380.07,147.02) --
-	(383.22,145.52) --
-	(386.38,144.08) --
-	(389.54,142.68) --
-	(392.70,141.34) --
-	(395.85,140.05) --
-	(399.01,138.79) --
-	(402.17,137.57) --
-	(405.32,136.38) --
-	(408.48,135.23) --
-	(411.64,134.09) --
-	(414.80,132.98) --
-	(417.95,131.90) --
-	(421.11,130.89) --
-	(424.27,129.91) --
-	(427.43,128.98) --
-	(430.58,128.09) --
-	(433.74,127.21) --
-	(436.90,126.36) --
-	(440.05,125.52) --
-	(443.21,124.68) --
-	(446.37,123.84) --
-	(449.53,122.99) --
-	(452.68,122.16) --
-	(455.84,121.37) --
-	(459.00,120.59) --
-	(462.16,119.84) --
-	(465.31,119.10) --
-	(468.47,118.37) --
-	(471.63,117.66) --
-	(474.78,116.95) --
-	(477.94,116.25) --
-	(481.10,115.55) --
-	(484.26,114.85) --
-	(487.41,114.17) --
-	(490.57,113.50) --
-	(493.73,112.84) --
-	(496.89,112.20) --
-	(500.04,111.56) --
-	(503.20,110.94) --
-	(506.36,110.32) --
-	(509.51,109.72) --
-	(512.67,109.12) --
-	(515.83,108.53) --
-	(518.99,107.95) --
-	(522.14,107.38) --
-	(525.30,106.82) --
-	(528.46,106.27) --
-	(531.62,105.73) --
-	(534.77,105.20) --
-	(537.93,104.68) --
-	(541.09,104.17) --
-	(544.24,103.68) --
-	(547.40,103.19) --
-	(550.56,102.71) --
-	(553.72,102.24) --
-	(556.87,101.78) --
-	(560.03,101.33) --
-	(563.19,100.89) --
-	(566.35,100.46) --
-	(569.50,100.05) --
-	(572.66, 99.64);
-\definecolor{fillColor}{RGB}{230,159,0}
-
-\path[fill=fillColor] (323.24,119.77) --
-	(326.60,113.94) --
-	(319.87,113.94) --
-	cycle;
-
-\path[fill=fillColor] (331.55,117.61) --
-	(334.91,111.79) --
-	(328.19,111.79) --
-	cycle;
-
-\path[fill=fillColor] (339.86,115.71) --
-	(343.23,109.89) --
-	(336.50,109.89) --
-	cycle;
-
-\path[fill=fillColor] (348.18,113.71) --
-	(351.54,107.88) --
-	(344.81,107.88) --
-	cycle;
-
-\path[fill=fillColor] (356.49,111.89) --
-	(359.86,106.07) --
-	(353.13,106.07) --
-	cycle;
-
-\path[fill=fillColor] (364.81,110.34) --
-	(368.17,104.52) --
-	(361.44,104.52) --
-	cycle;
-
-\path[fill=fillColor] (373.12,108.89) --
-	(376.48,103.06) --
-	(369.76,103.06) --
-	cycle;
-
-\path[fill=fillColor] (381.44,107.50) --
-	(384.80,101.67) --
-	(378.07,101.67) --
-	cycle;
-
-\path[fill=fillColor] (389.75,106.03) --
-	(393.11,100.20) --
-	(386.39,100.20) --
-	cycle;
-
-\path[fill=fillColor] (398.06,104.70) --
-	(401.43, 98.88) --
-	(394.70, 98.88) --
-	cycle;
-
-\path[fill=fillColor] (406.38,103.51) --
-	(409.74, 97.69) --
-	(403.01, 97.69) --
-	cycle;
-
-\path[fill=fillColor] (414.69,102.49) --
-	(418.06, 96.67) --
-	(411.33, 96.67) --
-	cycle;
-
-\path[fill=fillColor] (423.01,101.49) --
-	(426.37, 95.66) --
-	(419.64, 95.66) --
-	cycle;
-
-\path[fill=fillColor] (431.32,100.59) --
-	(434.68, 94.76) --
-	(427.96, 94.76) --
-	cycle;
-
-\path[fill=fillColor] (439.63, 99.70) --
-	(443.00, 93.88) --
-	(436.27, 93.88) --
-	cycle;
-
-\path[fill=fillColor] (447.95, 98.87) --
-	(451.31, 93.04) --
-	(444.58, 93.04) --
-	cycle;
-
-\path[fill=fillColor] (456.26, 98.10) --
-	(459.63, 92.27) --
-	(452.90, 92.27) --
-	cycle;
-
-\path[fill=fillColor] (464.58, 97.28) --
-	(467.94, 91.45) --
-	(461.21, 91.45) --
-	cycle;
-
-\path[fill=fillColor] (472.89, 96.38) --
-	(476.25, 90.55) --
-	(469.53, 90.55) --
-	cycle;
-
-\path[fill=fillColor] (481.20, 95.60) --
-	(484.57, 89.77) --
-	(477.84, 89.77) --
-	cycle;
-
-\path[fill=fillColor] (489.52, 94.90) --
-	(492.88, 89.07) --
-	(486.15, 89.07) --
-	cycle;
-
-\path[fill=fillColor] (497.83, 94.18) --
-	(501.20, 88.35) --
-	(494.47, 88.35) --
-	cycle;
-
-\path[fill=fillColor] (506.15, 93.53) --
-	(509.51, 87.70) --
-	(502.78, 87.70) --
-	cycle;
-
-\path[fill=fillColor] (514.46, 92.81) --
-	(517.82, 86.99) --
-	(511.10, 86.99) --
-	cycle;
-
-\path[fill=fillColor] (522.78, 92.22) --
-	(526.14, 86.39) --
-	(519.41, 86.39) --
-	cycle;
-
-\path[fill=fillColor] (531.09, 91.66) --
-	(534.45, 85.83) --
-	(527.73, 85.83) --
-	cycle;
-
-\path[fill=fillColor] (539.40, 91.06) --
-	(542.77, 85.24) --
-	(536.04, 85.24) --
-	cycle;
-
-\path[fill=fillColor] (547.72, 90.45) --
-	(551.08, 84.63) --
-	(544.35, 84.63) --
-	cycle;
-
-\path[fill=fillColor] (556.03, 89.86) --
-	(559.40, 84.03) --
-	(552.67, 84.03) --
-	cycle;
-
-\path[fill=fillColor] (564.35, 89.36) --
-	(567.71, 83.53) --
-	(560.98, 83.53) --
-	cycle;
-
-\path[fill=fillColor] (572.66, 88.81) --
-	(576.02, 82.98) --
-	(569.30, 82.98) --
-	cycle;
-\definecolor{fillColor}{RGB}{86,180,233}
-
-\path[fill=fillColor] (320.74,147.59) --
-	(325.73,147.59) --
-	(325.73,152.58) --
-	(320.74,152.58) --
-	cycle;
-
-\path[fill=fillColor] (329.05,143.39) --
-	(334.05,143.39) --
-	(334.05,148.38) --
-	(329.05,148.38) --
-	cycle;
-
-\path[fill=fillColor] (337.37,139.76) --
-	(342.36,139.76) --
-	(342.36,144.75) --
-	(337.37,144.75) --
-	cycle;
-
-\path[fill=fillColor] (345.68,135.95) --
-	(350.68,135.95) --
-	(350.68,140.94) --
-	(345.68,140.94) --
-	cycle;
-
-\path[fill=fillColor] (353.99,132.41) --
-	(358.99,132.41) --
-	(358.99,137.40) --
-	(353.99,137.40) --
-	cycle;
-
-\path[fill=fillColor] (362.31,129.50) --
-	(367.30,129.50) --
-	(367.30,134.50) --
-	(362.31,134.50) --
-	cycle;
-
-\path[fill=fillColor] (370.62,126.75) --
-	(375.62,126.75) --
-	(375.62,131.74) --
-	(370.62,131.74) --
-	cycle;
-
-\path[fill=fillColor] (378.94,124.08) --
-	(383.93,124.08) --
-	(383.93,129.08) --
-	(378.94,129.08) --
-	cycle;
-
-\path[fill=fillColor] (387.25,121.44) --
-	(392.25,121.44) --
-	(392.25,126.43) --
-	(387.25,126.43) --
-	cycle;
-
-\path[fill=fillColor] (395.57,118.99) --
-	(400.56,118.99) --
-	(400.56,123.99) --
-	(395.57,123.99) --
-	cycle;
-
-\path[fill=fillColor] (403.88,116.78) --
-	(408.88,116.78) --
-	(408.88,121.77) --
-	(403.88,121.77) --
-	cycle;
-
-\path[fill=fillColor] (412.19,115.02) --
-	(417.19,115.02) --
-	(417.19,120.02) --
-	(412.19,120.02) --
-	cycle;
-
-\path[fill=fillColor] (420.51,113.20) --
-	(425.50,113.20) --
-	(425.50,118.19) --
-	(420.51,118.19) --
-	cycle;
-
-\path[fill=fillColor] (428.82,111.53) --
-	(433.82,111.53) --
-	(433.82,116.52) --
-	(428.82,116.52) --
-	cycle;
-
-\path[fill=fillColor] (437.14,109.90) --
-	(442.13,109.90) --
-	(442.13,114.89) --
-	(437.14,114.89) --
-	cycle;
-
-\path[fill=fillColor] (445.45,108.47) --
-	(450.45,108.47) --
-	(450.45,113.47) --
-	(445.45,113.47) --
-	cycle;
-
-\path[fill=fillColor] (453.76,107.09) --
-	(458.76,107.09) --
-	(458.76,112.08) --
-	(453.76,112.08) --
-	cycle;
-
-\path[fill=fillColor] (462.08,105.59) --
-	(467.07,105.59) --
-	(467.07,110.58) --
-	(462.08,110.58) --
-	cycle;
-
-\path[fill=fillColor] (470.39,104.07) --
-	(475.39,104.07) --
-	(475.39,109.07) --
-	(470.39,109.07) --
-	cycle;
-
-\path[fill=fillColor] (478.71,102.72) --
-	(483.70,102.72) --
-	(483.70,107.72) --
-	(478.71,107.72) --
-	cycle;
-
-\path[fill=fillColor] (487.02,101.49) --
-	(492.02,101.49) --
-	(492.02,106.49) --
-	(487.02,106.49) --
-	cycle;
-
-\path[fill=fillColor] (495.34,100.25) --
-	(500.33,100.25) --
-	(500.33,105.25) --
-	(495.34,105.25) --
-	cycle;
-
-\path[fill=fillColor] (503.65, 99.11) --
-	(508.64, 99.11) --
-	(508.64,104.10) --
-	(503.65,104.10) --
-	cycle;
-
-\path[fill=fillColor] (511.96, 97.90) --
-	(516.96, 97.90) --
-	(516.96,102.90) --
-	(511.96,102.90) --
-	cycle;
-
-\path[fill=fillColor] (520.28, 96.90) --
-	(525.27, 96.90) --
-	(525.27,101.90) --
-	(520.28,101.90) --
-	cycle;
-
-\path[fill=fillColor] (528.59, 95.91) --
-	(533.59, 95.91) --
-	(533.59,100.91) --
-	(528.59,100.91) --
-	cycle;
-
-\path[fill=fillColor] (536.91, 94.94) --
-	(541.90, 94.94) --
-	(541.90, 99.93) --
-	(536.91, 99.93) --
-	cycle;
-
-\path[fill=fillColor] (545.22, 94.00) --
-	(550.22, 94.00) --
-	(550.22, 98.99) --
-	(545.22, 98.99) --
-	cycle;
-
-\path[fill=fillColor] (553.53, 92.89) --
-	(558.53, 92.89) --
-	(558.53, 97.89) --
-	(553.53, 97.89) --
-	cycle;
-
-\path[fill=fillColor] (561.85, 92.04) --
-	(566.84, 92.04) --
-	(566.84, 97.04) --
-	(561.85, 97.04) --
-	cycle;
-
-\path[fill=fillColor] (570.16, 91.16) --
-	(575.16, 91.16) --
-	(575.16, 96.15) --
-	(570.16, 96.15) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (319.70,181.63) -- (326.77,181.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.24,178.10) -- (323.24,185.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.02,175.24) -- (335.08,175.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.55,171.71) -- (331.55,178.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.33,169.74) -- (343.40,169.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.86,166.20) -- (339.86,173.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.65,163.98) -- (351.71,163.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.18,160.45) -- (348.18,167.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.96,158.64) -- (360.02,158.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.49,155.11) -- (356.49,162.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,154.33) -- (368.34,154.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,150.80) -- (364.81,157.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,150.19) -- (376.65,150.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,146.66) -- (373.12,153.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,146.18) -- (384.97,146.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,142.65) -- (381.44,149.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,142.37) -- (393.28,142.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,138.84) -- (389.75,145.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,138.78) -- (401.60,138.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,135.25) -- (398.06,142.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,135.48) -- (409.91,135.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,131.95) -- (406.38,139.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,133.07) -- (418.22,133.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,129.54) -- (414.69,136.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,130.41) -- (426.54,130.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,126.88) -- (423.01,133.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,127.94) -- (434.85,127.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,124.40) -- (431.32,131.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,125.60) -- (443.17,125.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,122.07) -- (439.63,129.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,123.66) -- (451.48,123.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,120.13) -- (447.95,127.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,121.64) -- (459.79,121.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,118.11) -- (456.26,125.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,119.43) -- (468.11,119.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,115.90) -- (464.58,122.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,117.33) -- (476.42,117.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,113.80) -- (472.89,120.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,115.45) -- (484.74,115.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,111.92) -- (481.20,118.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,113.73) -- (493.05,113.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,110.20) -- (489.52,117.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,112.01) -- (501.36,112.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,108.48) -- (497.83,115.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,110.34) -- (509.68,110.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,106.81) -- (506.15,113.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,108.72) -- (517.99,108.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,105.19) -- (514.46,112.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,107.30) -- (526.31,107.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,103.77) -- (522.78,110.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,105.93) -- (534.62,105.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,102.40) -- (531.09,109.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,104.65) -- (542.94,104.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,101.12) -- (539.40,108.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,103.44) -- (551.25,103.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72, 99.91) -- (547.72,106.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,101.84) -- (559.56,101.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03, 98.31) -- (556.03,105.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,100.61) -- (567.88,100.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35, 97.07) -- (564.35,104.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13, 99.50) -- (576.19, 99.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66, 95.97) -- (572.66,103.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (319.70,133.33) -- (326.77,133.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.24,129.79) -- (323.24,136.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.02,130.17) -- (335.08,130.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.55,126.64) -- (331.55,133.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.33,127.42) -- (343.40,127.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.86,123.89) -- (339.86,130.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.65,124.53) -- (351.71,124.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.18,121.00) -- (348.18,128.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.96,121.87) -- (360.02,121.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.49,118.34) -- (356.49,125.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,119.65) -- (368.34,119.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,116.11) -- (364.81,123.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,117.55) -- (376.65,117.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,114.02) -- (373.12,121.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,115.54) -- (384.97,115.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,112.01) -- (381.44,119.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,113.47) -- (393.28,113.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,109.94) -- (389.75,117.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,111.60) -- (401.60,111.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,108.06) -- (398.06,115.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,109.91) -- (409.91,109.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,106.37) -- (406.38,113.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,108.50) -- (418.22,108.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,104.97) -- (414.69,112.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,107.09) -- (426.54,107.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,103.56) -- (423.01,110.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,105.80) -- (434.85,105.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,102.27) -- (431.32,109.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,104.55) -- (443.17,104.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,101.02) -- (439.63,108.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,103.41) -- (451.48,103.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95, 99.87) -- (447.95,106.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,102.33) -- (459.79,102.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26, 98.80) -- (456.26,105.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,101.17) -- (468.11,101.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58, 97.64) -- (464.58,104.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36, 99.96) -- (476.42, 99.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89, 96.42) -- (472.89,103.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67, 98.89) -- (484.74, 98.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20, 95.35) -- (481.20,102.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99, 97.92) -- (493.05, 97.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52, 94.38) -- (489.52,101.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30, 96.93) -- (501.36, 96.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83, 93.40) -- (497.83,100.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61, 96.04) -- (509.68, 96.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15, 92.51) -- (506.15, 99.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93, 95.07) -- (517.99, 95.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46, 91.53) -- (514.46, 98.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24, 94.27) -- (526.31, 94.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78, 90.73) -- (522.78, 97.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56, 93.49) -- (534.62, 93.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09, 89.96) -- (531.09, 97.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87, 92.69) -- (542.94, 92.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40, 89.16) -- (539.40, 96.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19, 91.90) -- (551.25, 91.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72, 88.37) -- (547.72, 95.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50, 91.05) -- (559.56, 91.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03, 87.52) -- (556.03, 94.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81, 90.38) -- (567.88, 90.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35, 86.85) -- (564.35, 93.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13, 89.65) -- (576.19, 89.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66, 86.12) -- (572.66, 93.18);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.74,147.59) rectangle (325.73,152.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.74,147.59) -- (325.73,152.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.74,152.58) -- (325.73,147.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.05,143.39) rectangle (334.05,148.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.05,143.39) -- (334.05,148.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.05,148.38) -- (334.05,143.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.37,139.76) rectangle (342.36,144.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.37,139.76) -- (342.36,144.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.37,144.75) -- (342.36,139.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.68,135.95) rectangle (350.68,140.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.68,135.95) -- (350.68,140.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.68,140.94) -- (350.68,135.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.99,132.41) rectangle (358.99,137.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.99,132.41) -- (358.99,137.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.99,137.40) -- (358.99,132.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (362.31,129.50) rectangle (367.30,134.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (362.31,129.50) -- (367.30,134.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (362.31,134.50) -- (367.30,129.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.62,126.75) rectangle (375.62,131.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.62,126.75) -- (375.62,131.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.62,131.74) -- (375.62,126.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.94,124.08) rectangle (383.93,129.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.94,124.08) -- (383.93,129.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.94,129.08) -- (383.93,124.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.25,121.44) rectangle (392.25,126.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.25,121.44) -- (392.25,126.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.25,126.43) -- (392.25,121.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.57,118.99) rectangle (400.56,123.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.57,118.99) -- (400.56,123.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.57,123.99) -- (400.56,118.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.88,116.78) rectangle (408.88,121.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.88,116.78) -- (408.88,121.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.88,121.77) -- (408.88,116.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.19,115.02) rectangle (417.19,120.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.19,115.02) -- (417.19,120.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.19,120.02) -- (417.19,115.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.51,113.20) rectangle (425.50,118.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.51,113.20) -- (425.50,118.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.51,118.19) -- (425.50,113.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.82,111.53) rectangle (433.82,116.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.82,111.53) -- (433.82,116.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.82,116.52) -- (433.82,111.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.14,109.90) rectangle (442.13,114.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.14,109.90) -- (442.13,114.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.14,114.89) -- (442.13,109.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.45,108.47) rectangle (450.45,113.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.45,108.47) -- (450.45,113.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.45,113.47) -- (450.45,108.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.76,107.09) rectangle (458.76,112.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.76,107.09) -- (458.76,112.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.76,112.08) -- (458.76,107.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.08,105.59) rectangle (467.07,110.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.08,105.59) -- (467.07,110.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.08,110.58) -- (467.07,105.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.39,104.07) rectangle (475.39,109.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.39,104.07) -- (475.39,109.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.39,109.07) -- (475.39,104.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.71,102.72) rectangle (483.70,107.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.71,102.72) -- (483.70,107.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.71,107.72) -- (483.70,102.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.02,101.49) rectangle (492.02,106.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.02,101.49) -- (492.02,106.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.02,106.49) -- (492.02,101.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.34,100.25) rectangle (500.33,105.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.34,100.25) -- (500.33,105.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.34,105.25) -- (500.33,100.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.65, 99.11) rectangle (508.64,104.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.65, 99.11) -- (508.64,104.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.65,104.10) -- (508.64, 99.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.96, 97.90) rectangle (516.96,102.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.96, 97.90) -- (516.96,102.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.96,102.90) -- (516.96, 97.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.28, 96.90) rectangle (525.27,101.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.28, 96.90) -- (525.27,101.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.28,101.90) -- (525.27, 96.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.59, 95.91) rectangle (533.59,100.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.59, 95.91) -- (533.59,100.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.59,100.91) -- (533.59, 95.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.91, 94.94) rectangle (541.90, 99.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.91, 94.94) -- (541.90, 99.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.91, 99.93) -- (541.90, 94.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (545.22, 94.00) rectangle (550.22, 98.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (545.22, 94.00) -- (550.22, 98.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (545.22, 98.99) -- (550.22, 94.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.53, 92.89) rectangle (558.53, 97.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.53, 92.89) -- (558.53, 97.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.53, 97.89) -- (558.53, 92.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.85, 92.04) rectangle (566.84, 97.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.85, 92.04) -- (566.84, 97.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.85, 97.04) -- (566.84, 92.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16, 91.16) rectangle (575.16, 96.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16, 91.16) -- (575.16, 96.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16, 96.15) -- (575.16, 91.16);
 \definecolor{fillColor}{RGB}{0,0,0}

### 2020-08-28 rR.R

@@ -55,7 +55,7 @@ rRdata <- list(
 
 g1 <- ggplot(rRdata) +
   geom_smooth(aes(r, R, col=type, lty=type), se=FALSE) +
-  geom_point(aes(r, R, col=type, shape=type), size=3) +
+  geom_point(aes(r, R, col=type, shape=type), size=2) +
   scale_x_continuous("Exponential growth rate $r$ (1/day)", limits=c(0, 0.3), expand=c(0, 0)) +
   scale_y_continuous("Basic reproduction number $\\mathcal R_0$", limits=c(1, 4.5), expand=c(0, 0)) +
   scale_color_manual(values=cpalette) +
@@ -63,7 +63,8 @@ g1 <- ggplot(rRdata) +
   theme(
     panel.grid = element_blank(),
     legend.position = c(0.33, 0.75),
-    legend.title = element_blank()
+    legend.title = element_blank(),
+    legend.background = element_blank()
   )
 
 rRdata2 <- list(
@@ -103,7 +104,7 @@ rRdata2 <- list(
 
 g2 <- ggplot(rRdata2) +
   geom_smooth(aes(r, R, col=type, lty=type), se=FALSE) +
-  geom_point(aes(r, R, col=type, shape=type), size=3) +
+  geom_point(aes(r, R, col=type, shape=type), size=2) +
   scale_x_continuous("Exponential growth rate $r$ (1/day)", limits=c(0, 0.3), expand=c(0, 0)) +
   scale_y_continuous("Reproduction number ${\\mathcal R}_{\\textrm{\\tiny intrinsic}}$", limits=c(1, 4.5), expand=c(0, 0)) +
   scale_color_viridis_d(option="C") +
@@ -111,7 +112,8 @@ g2 <- ggplot(rRdata2) +
   theme(
     panel.grid = element_blank(),
     legend.position = c(0.33, 0.75),
-    legend.title = element_blank()
+    legend.title = element_blank(),
+    legend.background = element_blank()
   )
 
 rGdata <- list(
@@ -151,7 +153,7 @@ rGdata <- list(
 
 g3 <- ggplot(rGdata) +
   geom_smooth(aes(r, mean, col=type, lty=type), se=FALSE) +
-  geom_point(aes(r, mean, col=type, shape=type), size=3) +
+  geom_point(aes(r, mean, col=type, shape=type), size=2) +
[…]

### 2020-08-28 serial.tex
tweaks

@@
 \end{equation}
-The denominator, $\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'$, then corresponds to the total number of symptomatic cases generated by primary cases who developed at time \psymp;
+Likewise, the backward serial-interval distribution $b_\ssymp(\tau)$ is given by the density of intervals of length $\tau$ ending at \ssymp, relative to the total number of serial intervals ending at \ssymp:
+\begin{equation}
+b_\ssymp(\tau) = 
+\frac{\total(\ssymp-\tau, \ssymp)}{\int_{-\infty}^\infty \total(\ssymp-\tau', \ssymp) \dtau'}.
+\label{eq:bserial}
+\end{equation}
+
+We see that the denominator of the forward serial-interval distribution, $\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'$, then corresponds to the total number of symptomatic cases generated by primary cases who developed at time \psymp (\eref{fserial});
 dividing it by the incidence of symptomatic cases (also infected by symptomatic cases) at time \psymp, $j(\psymp) = \int_{-\infty}^\infty \total(\psymp-\tau', \psymp) \dtau'$, we obtain the serial reproduction number:
@@
 which we define as the average number of symptomatic cases generated by individuals who developed symptoms at time \psymp (and were also infected by sympmtomatic cases).
-Combining the forward serial-interval distribution with the serial reproduction number allows us to express the renewal process between symptomatic cases:
+Combining the forward serial-interval distribution with the serial reproduction number completes the renewal process between symptomatic cases:
 \begin{equation}
@@
 \end{equation}
-In Supplementary Materials, we show that estimating the serial reproduction number requires the backward serial-interval distribution $b_\ssymp(\tau)$, which is given by the density of intervals of length $\tau$ ending at \ssymp, relative to the total number of serial intervals ending at \ssymp:
-\begin{equation}
-b_\ssymp(\tau) = 
-\frac{\total(\ssymp-\tau, \ssymp)}{\int_{-\infty}^\infty \total(\ssymp-\tau', \ssymp) \dtau'}.
-\label{eq:bserial}
-\end{equation}
-This framework allows us to understand changes in the realized serial intervals for any epidemic model and link serial-interval distributions with the renewal process.
+This framework allows us to understand changes in the realized serial intervals for any epidemic model and properly link serial-interval distributions with the renewal process.
 
@@
 that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
-Throughout the paper, we allow for presymptomatic transmission to match the transmission dynamics of COVID-19.a
+Throughout the paper, we allow for presymptomatic transmission to match the transmission dynamics of COVID-19.
 
@@
 
-The dynamics of the serial-interval distribution depends heavily on the joint distribution between incubation periods and generation intervals.
-Here, we use a bivariate lognormal distribution to model the joint probability distribution of the intrinsic incubation periods and the intrinsic generation intervals while allowing for the possibility that they might be correlated.
-Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset, we generally expect the generation intervals to be positively correlated with the incubation period;
+We have shown that the dynamics of the serial-interval distribution depends on the joint distribution between incubation periods and generation intervals.
+Here, we use a bivariate lognormal distribution to model the joint probability distribution $h$ of intrinsic incubation periods and intrinsic generation intervals (in the renewal equation model, \eref{renewal}) while allowing for the possibility that they might be correlated.
+Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset, we generally expect the generation intervals to be positively correlated with the incubation period:
 that is, individuals who develop symptoms later are more likely to transmit later.
 Marginal distributions of incubation periods and generation intervals are parameterized based on parameter estimates for COVID-19 (Table 1).
-For simplicity, we consider three values for the correlation coefficients (on the log scale) of the bivariate lognormal distribution: $\rho = -0.5, 0, 0.5$.
+For simplicity, we consider four values for the correlation coefficients (on the log scale) of the bivariate lognormal distribution: $\rho = 0, 0.25, 0.5, 0.75$.
+This parameterization allows for generation intervals to be shorter than the incubation period, allowing for presymptomatic transmission.
 
@@
 The intrinsic incubation period distribution is parameterized using a log-normal distribution with log mean $\mu_I=1.62$ and log standard deviation $\sigma_I=0.42$.
-The joint probability distribution is modeled using a bivariate log-normal distribution with correlations (on the log scale) $\rho=-0.5, 0, 0.5$.
+The joint probability distribution is modeled using a bivariate log-normal distribution with correlations (on the log scale) $\rho=0, 0.25, 0.5, 0.75$.
 The intrinsic generation-interval and incubation period distributions are chosen to match characteristic of COVID-19 to illustrate realistic magnitudes of time-varying/perspective effects in the current pandemic.
@@
 The initial forward serial-interval distribution captures the exponential growth phase of an epidemic.
-We explore how forward and backward serial intervals can vary over the course of an epidemic using deterministic and stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
-we further assume $\Ro=2.5$.
+We now explore how forward and backward serial intervals can vary over the course of an epidemic using deterministic and stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
+we further assume $\Ro=2.5$ to reflect the transmission dynamics of COVID-19 \citep{doi:10.1098/rsif.2020.0144}.
 While the forward serial-interval distribution is our primary focus, understanding the differences between the forward and the backward distributions is important because the observed intervals during an ongoing epidemic are often the backward ones:

### 2020-09-01 response.tex
response

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{color}

\usepackage{xspace}

\usepackage{lmodern}
\usepackage{amssymb,amsmath}

\usepackage[pdfencoding=auto, psdextra]{hyperref}

\usepackage{natbib}
\bibliographystyle{chicago}

\newcommand{\rR}{\mbox{$r$--$\cal R$}}
\newcommand{\RR}{\ensuremath{{\cal R}}}
\newcommand{\RRhat}{\ensuremath{{\hat \cal R}}}
\newcommand{\Rx}[1]{\ensuremath{{\cal R}_{#1}}} 
\newcommand{\Ro}{\ensuremath{{\mathcal R}_{0}}\xspace}
\newcommand{\Rpool}{\ensuremath{{\mathcal R}_{\textrm{\tiny{pool}}}}\xspace}
\newcommand{\Reff}{\Rx{\mathit{eff}}}
\newcommand{\Tc}{\ensuremath{C}}

\newcommand{\rev}{\subsection*}
\newcommand{\revtext}{\textsf}
\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0em}

\newcommand{\comment}[3]{\textcolor{#1}{\textbf{[#2: }\textsl{#3}\textbf{]}}}
\newcommand{\jd}[1]{\comment{cyan}{JD}{#1}}
\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
\newcommand{\dc}[1]{\comment{blue}{DC}{#1}}
\newcommand{\jsw}[1]{\comment{green}{JSW}{#1}}
\newcommand{\hotcomment}[1]{\comment{red}{HOT}{#1}}

\newcommand{\psymp}{\ensuremath{p}} %% primary symptom time
\newcommand{\ssymp}{\ensuremath{s}} %% secondary symptom time
\newcommand{\pinf}{\ensuremath{\alpha_1}} %% primary infection time
\newcommand{\sinf}{\ensuremath{\alpha_2}} %% secondary infection time

\newcommand{\psize}{{\mathcal P}} %% primary cohort size
\newcommand{\ssize}{{\mathcal S}} %% secondary cohort size

\newcommand{\gtime}{\tau_{\rm g}} %% generation interval
\newcommand{\gdist}{g} %% generation-interval distribution
\newcommand{\idist}{\ell} %% incubation period distribution

\newcommand{\total}{{\mathcal T}} %% total number of serial intervals

\begin{document}

\noindent Dear Editor:

Thank you for the chance to revise and resubmit our manuscript. 
We have made major revisions to our manuscript to address the reviewers' comments.
We were apparently not clear in our writing. Reviewers 1 and 3 both pointed out that we assume that the latent and incubation periods are equivalent (and thus not allowing for presymptomatic transmission). 
However, we only present this result in the appendix as a special case.
We do not assume this in the main text and allow for presymptomatic transmission.
Below please find our responses to reviewers.

\rev{Reviewer \#1}

\revtext{I have one main concern, and this concerns the model. First a very general model is discussed, then a very special version is mentioned (mid p11) in which the latent period and incubation periods are always identical. For this model the General interval and Serial interval have exactly the same distribution. My concern is whether the stated results are valid only for this special case or if they apply also in general. I doubt the results hold in general, but at least think arguments for it are missing.}

The special version is only presented in the supplementary material. We do not assume this in the main text. We have made this distinction clear. Also Figure 2C--D shows that the initial forward serial-interval distribution is different from the intrinsic generation-interval distribution.

\revtext{Regarding my main concern above I note that you write "should" on p3, line 91, and "expect" on p 10, line 273. I don't see any proof for the statement to hold in general and am not sure the statement is even true in general. }

We provide a mathematical proof of this using a general model in the supplementary file. Figure 2A also demonstrates that this holds. We tried to make this clear in the main text.

\revtext{p4, bottom: refer to Fig 1 }

\revtext{p5, middle: emphasize that s and p are calendar times whereas $\tau$ is a duration }

\revtext{p5, line 158: clarify that $\tau = s-p$}

Done.

``Consequently, no matter how delays are distributed, if
$\mathcal P$ and $\mathcal S$ represent the sizes of primary and
secondary cohorts then we can express the total density of intervals $\tau$ between calendar time $\psymp$ and $\ssymp$ (i.e., $\tau=\ssymp-\psymp$) as follows:
\begin{equation}
W(\psymp) \psize(\psymp) f_\psymp(\tau) = \ssize(\ssymp) b_\ssymp(\tau) \,,
\label{eq:match}
\end{equation}''

\revtext{p5, line 170: should be $W(s-\tau)$?}

Done.

\revtext{p6, line 181-183: why will it contract during the outbreak? I understand why fewer will be materialized, but not why they will get shorter}

We have tried to clarify this:

``For example, shorter generation intervals are more likely to be realized later in the \emph{epidemic} (therefore, leading to ``contraction'' of generation intervals) because infected individuals are less likely to infect others later in their \emph{infection} due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.''

We also demonstrate this phenomenon in Figure 3C.

\revtext{p6, line 188: shorter than what? If you mean compared to the forward delay distribution it is always true when r>0 and not necessary that r is higher (than what?).}

We have rephrased this sentence:

``Thus, as the growth rate $r$ of an epidemic increases, the mean backward delay distribution will decrease, leading to stronger bias.''

\revtext{p7, line 203-205. Several of these papers acknowledge that the means are identical only if the tau's have the same distribution. On p11 (cf my main concern) you study an even more restrictive situation so in a sense you also implicitly assume this to hold or have I misunderstood?}

The restrictive is presented in the supplementary file as a special case. The main results do not depend on the restrictive assumption. We have tried to clarify this. We have also re-phrased the sentence now to acknoweldge what other studies have said more carefully:

``These studies concluded that the serial and generation intervals have the same mean when $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
however, distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$ will be identical only if we assume that they are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
something that is generally true of forward but not backward incubation-period distributions.''

\revtext{Section 3: be specific which model you are assuming. I think it is the SEIR where incubation is identical to latent period, i.e. individuals become infectious the same instance as their onset of symptoms.}

We are not assuming this. We have tried to clarify this in the main text.

\revtext{p19, line 470: something missing}

We have re-phrased the sentence to make it clearer:

``For example, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
However, our results show that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can, in fact, exacerbate the underestimation of initial \RR.''

\revtext{p19, line 485: you are assuming generation and serial intervals have the same distribution.}

We do not assume this. Also, Figure 2--3 illustrate that generation and serial intervals have different means, and therefore different distributions. We have tried to highlight these differences in the main text.

\rev{Reviewer \#2}

\revtext{The authors show how methods for estimating the reproduction number R from the growth rate r based on incorrectly defined disease transmission intervals can lead to biased estimates. They explain where the biases come from and present an unbiased heuristic to derive R from r, which they apply to the COVID-19 outbreak in China. Because the reproduction number has become part of everyday vocabulary this spring, the explanation of the source of biases is sound and clear, and the presented heuristic likely useful, their analysis may be sufficiently important to warrant publication in PNAS. However, then the authors must substantiate their criticism of previous work and present the reproduction number in a nuanced context.}

\revtext{The methods and results sections do excellent jobs explaining the source of confusion and biases, and how to overcome them. The discussion section synthesizes the insights into suggestions and good practices. However, I miss examples of how far off - if off at all - criticized application papers are when estimating the reproduction number.}

\revtext{The authors can improve their manuscript by responding to the following issues:}

\revtext{What is the manuscript about - generation and serial intervals or the reproduction number R? The title and abstract suggest the intervals and the introduction the reproduction number. I think opening with the well-known reproduction number will give the most transparent and coherent story.}

It is about both. Generation and serial intervals are key quantities in describing epidemic dynamics; their differences have long been misunderstood. These intervals also play critical role in estimating the reproduction number. We have made major revisions to the writing of the manuscript to provide a transparent and coherent story.

\revtext{The reproduction number is not put in a nuanced context. The presentation of the reproduction number as "one of the most important characteristics of an emerging epidemic ... [definition] ... [that] allows us to predict the extent to which an infection will spread in the population, and the amount of intervention necessary to eliminate it" that then leads directly into how it is estimated leaves no room for its shortcomings. A more nuanced picture includes its inability to, for example, account for individual variation, including superspreaders and spatial variations in regions.}

\revtext{The introduction presents previous methodological work on the R-r relationship based on generation and serial intervals and recent applications that confuse the two intervals. The presentation goes back and forth between the two and does not clarify the shortcomings of each work or application. My suggestion for a stronger introduction: A funnel focusing on the methods that ends with the knowledge gap "In contexts where the distributions are expected to be different, current theory has no explanation for how these differing distributions could provide identical estimates of R from r" (and further specified by the gaps indicated at the end of section 2.1 and beginning of section 2.2) followed by concrete examples of how off R estimates are in applications to substantiate the problem.}

\revtext{I also lack a discussion of standard software to estimate the reproduction number such as the widely used R package EpiEstim.}

\revtext{The abstract states that "recent studies suggest that the two intervals give different estimates of R from r" and "our analysis shows that using incorrectly defined serial intervals can severely bias estimates" Exemplify by numbers to substantiate the severity.}

\revtext{Same vagueness at the end of the introduction: "Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of R." By how much?}

\revtext{Figure 1 clearly illustrates the different intervals from different perspectives but does not explain the source of biases. Consider ways to visually communicate the important insights at the end of section 3.1.}

\revtext{Section 3.3 provides one example of a biased R estimate. The authors should substantiate their critique of several papers in the introduction by listing their estimated R estimates and the revised estimates - or not accusing those papers in the introduction. I think "these studies should also re-assess whether they appropriately considered the forward serial interval" is weak.}

\rev{Reviewr \#3}

\revtext{Throughout the paper becoming symptomatic seems equivalent to becoming infectious? This is a little confusing in context of Covid-19.}

We do not assume this. This is only assumed in the supplementary file as a special case. We now make this clear in the main text.

\revtext{Define s=p+tau before eq. 1.}

Done.

``Consequently, no matter how delays are distributed, if
$\mathcal P$ and $\mathcal S$ represent the sizes of primary and
secondary cohorts then we can express the total density of intervals $\tau$ between calendar time $\psymp$ and $\ssymp$ (i.e., $\tau=\ssymp-\psymp$) as follows:
\begin{equation}
W(\psymp) \psize(\psymp) f_\psymp(\tau) = \ssize(\ssymp) b_\ssymp(\tau) \,,
\label{eq:match}
\end{equation}''

\revtext{On page 9, ``any deterministic epidemic model"...Guess it should be just as important for a stochastic model?}

We removed the word ``deterministic'' from the sentence.

\revtext{On page 11, the important parameter rho =-0.5, 0 or 0.5 is obscure. What does these correlations means? partly anti-correlated, non correlated or positive correlated, but by how much? Which disease could have anti-correlation between these quantities? It make interpretation of Fig. 2B difficult. }

\revtext{Page 4, figure 3A: Why are stochastic trajectories systematically shifted toward earlier time compared to deterministic trajectory. Was the deterministic trajectory not simulated with same serial interval distribution?}

\revtext{Page 18, ``based on 8 and 6 doubling periods" guess it should be "based on a doubling period of 8 or 6 days"??}

Thank you. We have changed this as suggested.

\revtext{Page 17, figure 5 is difficult to judge. It needs to be supplemented with a trajectory of the epidemic curve in the days that is shown.}

\revtext{Figure 5, what is on the y axis? Which delay is plotted and how does it relate to the forward/backward serial intervals. Why not plot serial intervals directly?}

\revtext{Could the results be simplified to an extend that medical doctors that actually "measure" backward serial intervals directly could recalculate the intrinsic serial intervals (in some simple approximation). As a technical paper it should provide some direct applicable results.}

\revtext{Overall, I find the work interesting and believe it could contribute to current discussions on intrinsic time scales for Covid-19. It is a technical read, that would gain by being made easier accessible.}

Thank you. We have made substantial edits to the manuscript to make it more accessible.

\bibliography{serial}

\end{document}

### 2020-09-15 response.tex
update

@@
 
+\newcommand{\eref}[1]{Eq.~(\ref{eq:#1})}
+\newcommand{\fref}[1]{Fig.~\ref{fig:#1}}
+
 \newcommand{\rR}{\mbox{$r$--$\cal R$}}
@@
 \newcommand{\Ro}{\ensuremath{{\mathcal R}_{0}}\xspace}
+\newcommand{\Rs}{\Rx{\mathrm{s}}}
 \newcommand{\Rpool}{\ensuremath{{\mathcal R}_{\textrm{\tiny{pool}}}}\xspace}
@@
 \newcommand{\Tc}{\ensuremath{C}}
+
+\newcommand{\dd}[1]{\ensuremath{\, \mathrm{d}#1}}
+\newcommand{\dtau}{\dd{\tau}}
+\newcommand{\dx}{\dd{x}}
+\newcommand{\dsigma}{\dd{\sigma}}
 
@@
 
-The special version is only presented in the supplementary material.
-We do not assume this in the main text.
-We have made this distinction clear.
-Also Figure 2C--D shows that the initial forward serial-interval distribution is different from the intrinsic generation-interval distribution.
+The special version is only presented in the supplementary material. We do not assume this in the main text. We have made this distinction clear:
+
+``For example, the Susceptible-Exposed-Infected-Recovered model, under the additional assumption that the incubation and exposed periods are equivalent (i.e.
+that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
+Throughout the paper, we allow for presymptomatic transmission to match the transmission dynamics of COVID-19.''
+
+Figure 2 further shows that the initial forward serial-interval distribution is different from the intrinsic generation-interval distribution but gives identical \Ro estimates given $r$.
 
@@
 
-We provide a mathematical proof of this using a general model in the supplementary file. Figure 2A also demonstrates that this holds. We tried to make this clear in the main text.
+We provide a mathematical proof of this using a general model in the supplementary file. Figure 2A also demonstrates that this holds. We tried to make this clear in the main text:
+
+``Analogous to the intrinsic generation-interval distribution, 
+forward serial-interval distributions describe the renewal process of infection based on symptom onset dates.
+Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to estimate the same value of \Ro for a given $r$ as the intrinsic generation-interval distribution (note, however, that the forward serial interval is not necessarily positive):
+\begin{equation}
+\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
+\label{eq:Rforward}
+\end{equation}
+where the initial forward serial-interval distribution is given by:
+\begin{equation}
+f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{0} \int_{\pinf}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf,
+\label{eq:initialSI}
+\end{equation}
+where the normalization constant $\phi$ is determined by the
+requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
+Since we have not yet made any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, this conclusion is robust, regardless of whether presymptomatic is possible or not.
+It is straightforward to see this relationship from \eref{jrenew} (by substituting $j(t) \approx j(0) \exp(rt)$ and $\Rs(t) \approx \Ro$);
+in Supplementary Materials, we provide a more detailed mathematical proof of this relationship.''
 
@@
 
-The restrictive is presented in the supplementary file as a special case.
+The restrictive situation is presented in the supplementary file as a special case.
 The main results do not depend on the restrictive assumption.
@@
 We do not assume this.
-Also, Figure 2--3 illustrate that generation and serial intervals have different means, and therefore different distributions.
-We have tried to highlight these differences in the main text.
+Also, Figure 2--3 illustrate that generation and serial intervals have different means, and therefore are different distributions.
+We have tried to highlight these differences throughout the main text.
 
@@
 
+We initially considered anti-correlations for demonstration purposes (that regardless of choices of correlations, we can still obtain an unbiased estimate of \Ro using the initial forward serial-interval distributions).
+We agree that it is unrealistic.
+We have removed the negative correlation example and added the following text:
+
+``We have shown that the dynamics of the serial-interval distribution depends on the joint distribution between incubation periods and generation intervals.
+Here, we use a bivariate lognormal distribution to model the joint probability distribution $h$ of intrinsic incubation periods and intrinsic generation intervals (in the renewal equation model, \eref{renewal}) while allowing for the possibility that they might be correlated.
+Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset, we generally expect the generation intervals to be positively correlated with the incubation period:
+that is, individuals who develop symptoms later are more likely to transmit later.
+Marginal distributions of incubation periods and generation intervals are parameterized based on parameter estimates for COVID-19 (Table 1).
+For simplicity, we consider four values for the correlation coefficients (on the log scale) of the bivariate lognormal distribution: $\rho = 0, 0.25, 0.5, 0.75$.
+This parameterization allows for generation intervals to be shorter than the incubation period, allowing for presymptomatic transmission.''
+
 \revtext{Page 4, figure 3A: Why are stochastic trajectories systematically shifted toward earlier time compared to deterministic trajectory.
 Was the deterministic trajectory not simulated with same serial interval distribution?}
+
+We now comment on this:
+
+``Stochastic simulations confirm our deterministic calculations albeit minor differences due to transient dynamics.
+Incidence trajectories of stochastic simulations are slightly shifted (\fref{epi}A) due to differences in initial conditions. 
+We set the distribution of infection time of initially infected individuals (beginning from a small number of infected individuals) for deterministic simulations such that the system can exhibit exponential growth immediately (Supplementary Materials).
+This is not possible for stochastic simulations because the number of initially infected individuals cannot be smaller than 1; instead, we begin with 10 infected indiivduals who are infected at time $t=0$.
+In addition, the mean backward intervals of stochastic simulations begins from smaller values due to left-censoring.''
 
@@
 
+Thank you for pointing this out. We have now added an epidemic trajectory.
+
 \revtext{Figure 5, what is on the y axis? Which delay is plotted and how does it relate to the forward/backward serial intervals. Why not plot serial intervals directly?}
+
+We are plotting serial intervals, after grouping them based on the symptom onset dates of primary (forward) and secondary (backward) cases. We have added the following sentence to further clarify:
+
+``In order to quantify changes in serial intervals, we group them by the symptom onset dates of the primary (\fref{du}B) and secondary (\fref{du}C) cases---correspoding to forward and backward serial-interval distributions, respectively---and compute their mean and 95\% quantiles.''
 
@@
 As a technical paper it should provide some direct applicable results.}
+
+We believe that section 3.2 does this.
+We show that, instead of aggregating all measured serial intervals, one could rearrange them based on symptom onset date of a primary case and take the cohort-based average.
+We further demonstrate how this could be done with an illusrative line list (Figure 4).
+In addition, there is a simple way to calculate the intrinsic serial interval distribution.
+As we show in our simulations, even if we could observe all serial intervals throughout an epidemic (in the absence of non-pharmaceutical interventions), we cannot estimate the intrinsic distribution.
+Instead, we recommend analyzing serial intervals through a cohort-based perspective.
+We have now added a paragraph in the discussion section, summarizing and providing practical guidance.
 

### 2020-09-15 serial.tex
update

@@
 To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total density of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
-The density of serial intervals between time $\psymp$ and $\ssymp$,
+For simplicity, we assume that all infected individuals eventually develop symptoms.
+Then, the density of serial intervals between time $\psymp$ and $\ssymp$,
 given that the infectors became infected at time $\pinf\le\psymp$ and
 the infectees became infected at time $\sinf\le\ssymp$, depends on the
-amount of infection that occurs between time $\pinf$ and $\sinf$ as
-well as the density of forward incubation periods between $\pinf$ and
+amount of infection that occurs between time $\pinf$ and $\sinf$ as well as
+the density of forward incubation periods between $\pinf$ and
 $\psymp$ (realized incubation periods of infectors) and between
@@
 \times 
-\underbrace{i(\pinf)}_{\text{incidence}} 
+\underbrace{i(\pinf)}_{\substack{\text{incidence} \\ \text{of} \\ \text{infection}}} 
 \times 
-\underbrace{h_{\pinf}(\psymp-\pinf, \sinf - \pinf)}_{\substack{\text{joint density of} \\ \text{the forward incubation} \\ \text{period } p-\pinf \text{ and the forward} \\ \text{generation interval } \sinf-\pinf\\ \text{(of infectors)}}}
+\underbrace{h_{\pinf}(\psymp-\pinf, \sinf - \pinf)}_{\substack{\text{joint density of} \\ \text{forward incubation} \\ \text{periods } p-\pinf \text{ and forward} \\ \text{generation intervals } \sinf-\pinf\\ \text{(of infectors)}}}
 \times
-\underbrace{\idist_{\sinf}(\ssymp - \sinf)}_{\substack{\text{marginal density of} \\ \text{the forward incubation} \\ \text{period } \ssymp-\sinf \\ \text{(of infectees)}}},
+\underbrace{\idist_{\sinf}(\ssymp - \sinf)}_{\substack{\text{marginal density of} \\ \text{forward incubation} \\ \text{periods } \ssymp-\sinf \\ \text{(of infectees)}}},
 \end{equation}
@@
 
-We see that the denominator of the forward serial-interval distribution, $\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'$, then corresponds to the total number of symptomatic cases generated by primary cases who developed at time \psymp (\eref{fserial});
-dividing it by the incidence of symptomatic cases (also infected by symptomatic cases) at time \psymp, $j(\psymp) = \int_{-\infty}^\infty \total(\psymp-\tau', \psymp) \dtau'$, we obtain the serial reproduction number:
+We see that the denominator of the forward serial-interval distribution, $\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'$, then corresponds to the total number of symptomatic cases generated by primary cases who themselves developed symptoms at time \psymp\ (\eref{fserial}).
+Dividing this quantity by the number of individuals who developed symptoms at time at time \psymp, $j(\psymp) = \int_{-\infty}^\infty \total(\psymp-\tau', \psymp) \dtau'$, we obtain the serial reproduction number:
 \begin{equation}
@@
 \end{equation}
-which we define as the average number of symptomatic cases generated by individuals who developed symptoms at time \psymp (and were also infected by sympmtomatic cases).
+which we define as the average number of symptomatic cases generated by individuals who developed symptoms at time \psymp.
 Combining the forward serial-interval distribution with the serial reproduction number completes the renewal process between symptomatic cases:
@@
 
-We illustrate changes in the forward and backward serial intervals over the course of an epidemic by applying it to a specific example of an epidemic model.
+We illustrate changes in forward and backward serial intervals over the course of an epidemic by applying it to a specific example of an epidemic model.
 We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
@@
 This model effectively assumes that epidemic dynamics are driven by changes in transmission rate, which may not hold under individual-based intervention such as case isolation \citep{fraser2007estimating};
-nonetheless, this form has been widely used in the literature and has been successfully applied in modeling the current COVID-19 pandemic.
+nonetheless, this form has been widely used in the literature and has been successfully applied in modeling the current COVID-19 pandemic \citep{gostic2020practical}.
 
 Here, we consider a specific example where changes in the reproduction number is driven by susceptible depletion: $\RR(t) = \Ro S(t)$, where \Ro represents the basic reproduction number.
+Although we do not consider non-pharmaceutical interventions explicitly, the effect of susceptible depletion is mathematically equivalent to the effect of interventions that reduce transmission rate.
 Then, the forward generation-interval for a cohort of individuals that were infected at time $\psymp$ follows \citep{champredon2015intrinsic}:
@@
 in Supplementary Materials, we provide a more detailed mathematical proof of this relationship.
+
 We further compare this with the estimate of \Ro based on the intrinsic serial-interval distribution $q(\tau)$:
@@
 We now explore how forward and backward serial intervals can vary over the course of an epidemic using deterministic and stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
-we further assume $\Ro=2.5$ to reflect the transmission dynamics of COVID-19 \citep{doi:10.1098/rsif.2020.0144}.
+we further assume $\Ro=2.5$ to reflect the transmission dynamics of COVID-19 in China \citep{doi:10.1098/rsif.2020.0144}.
 While the forward serial-interval distribution is our primary focus, understanding the differences between the forward and the backward distributions is important because the observed intervals during an ongoing epidemic are often the backward ones:
@@
 
+Stochastic simulations confirm our deterministic calculations albeit minor differences due to transient dynamics.
+Incidence trajectories of stochastic simulations are slightly shifted (\fref{epi}A) due to differences in initial conditions. 
+We set the distribution of infection time of initially infected individuals (beginning from a small number of infected individuals) for deterministic simulations such that the system can exhibit exponential growth immediately (Supplementary Materials).
+This is not possible for stochastic simulations because the number of initially infected individuals cannot be smaller than 1; instead, we begin with 10 infected indiivduals who are infected at time $t=0$.
+In addition, the mean backward intervals of stochastic simulations begins from smaller values due to left-censoring.
+
 \subsection{Observed serial-interval distributions}
@@
 
-Now, we turn to issues of estimating the reproduction number from the observed serial-interval data during on ongoing epidemic.
-In order to have an unbiased estimate of the basic reproduction number, we need to estimate the initial forward serial-interval distribution --- i.e., estimate based on cohorts of infectors who share the same symptom onset time, at the early stage of the epidemic.
-However, researchers typically use all available information to estimate epidemiological parameters;
-in particular, \cite{thompson2019improved} recently suggested that up-to-date serial-interval data are necessary to accurately estimate the reproduction number.
+Now, we turn to practical issues of estimating the reproduction number from the observed serial-interval data during on ongoing epidemic.
+In order to have an unbiased estimate of the basic reproduction number, we need to estimate the initial forward serial-interval distribution --- i.e., serial intervals based on cohorts of infectors who share the same symptom onset time, at the early stage of the epidemic.
+However, researchers typically use all available information to estimate epidemiological parameters (e.g., aggregating all serial intervals observed until certain time of an epidemic);
+for example, \cite{thompson2019improved} recently suggested that up-to-date serial-interval data are necessary to accurately estimate the reproduction number.
 We explore the consequences of neglecting changes in the realized serial-interval distribution on estimates of the basic reproduction number.
@@
 \fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of the basic reproduction number \Ro in our stochastic simulations (assuming $\Ro = 2.5$ as in \fref{epi}).
-Notably, even if we could observe, and average, \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we would still underestimate the initial mean forward serial interval (and therefore \Ro), likely by a large amount, because the observed serial-interval distribution converges to the intrinsic serial-interval distribution;
+Notably, even if we could observe, and aggregate, \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we would still underestimate the initial mean forward serial interval (and therefore \Ro), likely by a large amount, because the observed serial-interval distribution converges to the intrinsic serial-interval distribution (as the incubation periods and generation intervals will no longer be subject to backward biases);
 in fact, we would even underestimate the intrinsic value slightly due to contraction of the forward generation-interval distribution during the susceptible depletion phase (\fref{epi}C).
+Therefore, aggregated distributions of serial intervals that have been collected throughout different periods of an epidemic should be interpreted with care.
 
 Here, we provide a heuristic way of assessing potential biases in the estimate of the mean initial forward serial interval and therefore \Ro retrospectively.
-We can rearrange the line list and group observed serial intervals based on the symptom onset date of infectors (\fref{obsrR}C).
-Then, we can compare how estimates of the mean serial interval as well as \Ro change as we incorporate more recent cohorts into the analysis;
+We can rearrange the line list and group observed serial intervals based on the symptom onset date of infectors (\fref{obsrR}C)---as we showed earlier, serial intervals that share the same symptom onset date of a primary case give us the forward serial-interval distribution.
+Then, we can compare how the shape of the serial-interval distribution (particularly its mean) as well as the estimate of \Ro change as we incorporate more recent cohorts into the analysis:
 that is, we analyze observed serial intervals from infectors who became symptomatic before time $t$ and evaluate how the estimates change as we increase $t$.
-This approach is analogous to averaging over a set of forward intervals, just as using all information up to a certain time is analogous to averaging over a set of backward intervals (\fref{obsrR}D).
+This approach is analogous to averaging over a set of forward intervals, just as using all information up to a certain time is analogous to averaging over a set of backward intervals (\fref{obsrR}D);
+the major difference is that we we focus on serial intervals that begin in a certain period, rather than those that end in a certain period.
 During the exponential growth phase, the estimates of the mean serial interval and \Ro are consistent with the true value (see `initial forward' in \fref{obsrR}B,D);
@@
 \textbf{Observed serial intervals of COVID-19 and cohort-averaged estimates of \RR.}
-(A--B) forward and backward serial intervals over time.
+(A) Symptom onset dates of all individuals within 468 transmission pairs in the data.
+(B--C) forward and backward serial intervals over time.
+Serial interval data have been grouped based on the symptom onset dates of primary (B) and secondary (C) cases.
 Points represent the means. 
@@
 The dashed line represents the maximum and minimum observable delays across the range of reported symptom onset dates.
-(C) Cohort-averaged estimates of \Ro assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
+(D) Cohort-averaged estimates of \Ro assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
 Ribbons represent the associated 95\% bootstrap confidence intervals.
@@
 
-Finally, we re-analyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on transmission events reported between January 21--February 8, 2020;
+Finally, we re-analyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on 468 transmission events reported between January 21--February 8, 2020;
 \cite{du2020serial} estimated the mean serial interval of 3.96 days (95\% CI 3.53–4.39 days) and \Ro of 1.32 (95\% CI 1.16–1.48).
-\fref{du}A shows that the mean forward serial interval decreases over time.
+\fref{du}A shows the distribution of symptom onset dates of all individuals within 468 transmission pairs (consisting a total of 752 unique individuals), resembling a COVID-19 epidemic curve in China (cf.
+Fig.
+1 in \citep{pan2020jama}).
+In order to quantify changes in serial intervals, we group them by the symptom onset dates of the primary (\fref{du}B) and secondary (\fref{du}C) cases---correspoding to forward and backward serial-interval distributions, respectively---and compute their mean and 95\% quantiles.
+\fref{du}B shows that the mean forward serial interval decreases over time.
 While the decrease is likely to be affected by the right-censoring (indicated by the closeness between the quantiles of the observed serial intervals and maximum observable serial intervals), the increase in the proportion of negative serial intervals indicates changes in the forward serial-interval distribution;
@@
 Both of these would have acted to reduce the forward serial interval.
-\fref{du}B shows that the mean backward serial interval increased over time, likely driven directly by the decrease in COVID-19 cases.
+\fref{du}C shows that the mean backward serial interval increased over time, also likely driven directly by the decrease in COVID-19 infections.
 
-While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}A) appears to be larger than what we calculated based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
+While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}B) appears to be larger than what we calculated based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
 These may imply that the incubation period and generation interval (Table 1) were underestimated, as neither study explicitly accounted for the fact that the observed intervals were drawn from the backward distributions and were likely to have been censored.
 
-\fref{du}C shows the cohort-averaged estimates of \Ro, which remain roughly constant until day 7 and suddenly decreases;
+\fref{du}D shows the cohort-averaged estimates of \Ro, which remain roughly constant until day 7 and suddenly decreases;
 this sudden decrease is due changes in the forward serial intervals consistent with the dynamics seen in our simulations (\fref{obsrR}).
-The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, park2020reconciling}:
+The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, doi:10.1098/rsif.2020.0144}:
 $\Ro = 2.6$ (95\% CI: 2.2--3.1) and $\Ro = 3.4$ (95\% CI: 2.7 -- 4.3) based on a doubling period of 8 or 6 days, respectively, using serial-interval data from infectors who developed symptoms by day 7.
@@
 Generation and serial intervals determine the time scale of disease transmission, and are therefore critical to dynamical modeling of infectious outbreaks.
-Here, we show that the initial \emph{forward} serial-interval distribution --- measured during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
+Here, we show that the initial \emph{forward} serial-interval distribution --- measured from the cohort of infectors who developed symptoms during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
 In general, the forward serial-interval distributions will not match the intrinsic or the backward serial-interval distributions.

### 2020-09-15 serial_analysis.tex
update

--- 2020-04-30 serial_analysis.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-04-30 02:40:57
+% Created by tikzDevice version 0.12.3 on 2020-09-14 16:14:30
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (650.43,216.81);
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (216.81,216.81);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (1156.32,289.08);
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (216.81,216.81);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.71, 30.69) rectangle (283.58,266.42);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 34.64, 30.69) rectangle (211.31,194.15);
+\path[fill=fillColor] ( 31.71, 30.69) rectangle (283.58,266.42);
+\definecolor{fillColor}{gray}{0.35}
+
+\path[fill=fillColor] ( 31.71, 30.69) rectangle ( 38.40, 34.10);
+
+\path[fill=fillColor] ( 46.57, 30.69) rectangle ( 53.26, 37.52);
+
+\path[fill=fillColor] ( 54.00, 30.69) rectangle ( 60.69, 40.94);
+
+\path[fill=fillColor] ( 61.43, 30.69) rectangle ( 68.12, 37.52);
+
+\path[fill=fillColor] ( 68.86, 30.69) rectangle ( 75.55, 40.94);
+
+\path[fill=fillColor] ( 76.29, 30.69) rectangle ( 82.98, 34.10);
+
+\path[fill=fillColor] ( 83.72, 30.69) rectangle ( 90.41, 37.52);
+
+\path[fill=fillColor] ( 91.15, 30.69) rectangle ( 97.84, 40.94);
+
+\path[fill=fillColor] ( 98.58, 30.69) rectangle (105.27, 37.52);
+
+\path[fill=fillColor] (106.01, 30.69) rectangle (112.70, 44.35);
+
+\path[fill=fillColor] (113.44, 30.69) rectangle (120.13, 85.35);
+
+\path[fill=fillColor] (120.87, 30.69) rectangle (127.56, 85.35);
+
+\path[fill=fillColor] (128.30, 30.69) rectangle (134.99, 92.18);
+
+\path[fill=fillColor] (135.73, 30.69) rectangle (142.42, 95.60);
+
+\path[fill=fillColor] (143.16, 30.69) rectangle (149.84,150.26);
+
+\path[fill=fillColor] (150.59, 30.69) rectangle (157.27,194.68);
+
+\path[fill=fillColor] (158.02, 30.69) rectangle (164.70,204.93);
+
+\path[fill=fillColor] (165.45, 30.69) rectangle (172.13,198.09);
+
+\path[fill=fillColor] (172.88, 30.69) rectangle (179.56,218.59);
+
+\path[fill=fillColor] (180.31, 30.69) rectangle (186.99,245.92);
+
+\path[fill=fillColor] (187.74, 30.69) rectangle (194.42,256.17);
+
+\path[fill=fillColor] (195.17, 30.69) rectangle (201.85,198.09);
+
+\path[fill=fillColor] (202.60, 30.69) rectangle (209.28,187.84);
+
+\path[fill=fillColor] (210.03, 30.69) rectangle (216.71,191.26);
+
+\path[fill=fillColor] (217.46, 30.69) rectangle (224.14,177.59);
+
+\path[fill=fillColor] (224.89, 30.69) rectangle (231.57,136.60);
+
+\path[fill=fillColor] (232.31, 30.69) rectangle (239.00,116.10);
+
+\path[fill=fillColor] (239.74, 30.69) rectangle (246.43,102.43);
+
+\path[fill=fillColor] (247.17, 30.69) rectangle (253.86, 75.10);
+
+\path[fill=fillColor] (254.60, 30.69) rectangle (261.29, 61.43);
+
+\path[fill=fillColor] (262.03, 30.69) rectangle (268.72, 51.18);
+
+\path[fill=fillColor] (269.46, 30.69) rectangle (276.15, 37.52);
+
+\path[fill=fillColor] (276.89, 30.69) rectangle (283.58, 34.10);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71, 30.69) rectangle (283.58,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 27.66) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76, 95.98) {20};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,164.31) {40};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,232.64) {60};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 30.69) --
+	( 31.71, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 99.02) --
+	( 31.71, 99.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,167.34) --
+	( 31.71,167.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,235.67) --
+	( 31.71,235.67);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.63, 27.94) --
+	( 79.63, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (131.64, 27.94) --
+	(131.64, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.65, 27.94) --
+	(183.65, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (235.66, 27.94) --
+	(235.66, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 79.63, 19.68) {Jan 13};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (131.64, 19.68) {Jan 20};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (183.65, 19.68) {Jan 27};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (235.66, 19.68) {Feb 03};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (100.89,194.15) --
-	(106.42,189.20) --
-	(111.94,184.25) --
-	(117.46,179.29) --
-	(122.98,174.34) --
-	(128.50,169.39) --
-	(134.02,164.43) --
-	(139.54,159.48) --
-	(145.06,154.52) --
-	(150.58,149.57) --
-	(156.10,144.62) --
-	(161.62,139.66) --
-	(167.14,134.71) --
-	(172.66,129.76) --
-	(178.19,124.80) --
-	(183.71,119.85) --
-	(189.23,114.90) --
-	(194.75,109.94) --
-	(200.27,104.99) --
-	(205.79,100.04) --
-	(211.31, 95.08);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 34.64,104.99) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.69,161.34) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.21,136.36) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 56.73,144.62) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.25,144.62) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.77,164.43) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.29,164.43) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.81,144.62) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.33,159.48) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.85,137.19) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.37,120.06) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.89,120.16) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.42,124.02) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.94,113.45) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.46,121.02) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.98,112.94) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.50,109.78) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.02,113.37) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.54,101.81) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.06,105.30) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.58, 99.53) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.10, 97.67) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.62, 97.70) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.14, 92.46) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.66, 89.55) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.19, 95.98) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.71, 94.09) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.23, 85.17) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (200.27, 70.31) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.31, 60.41) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.64,104.99) --
-	( 34.64,104.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.64,104.99) --
-	( 34.64,104.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.64,104.99) --
-	( 34.64,104.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,173.47) --
-	( 45.69,173.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,173.47) --
-	( 45.69,142.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,142.26) --
-	( 45.69,142.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,167.16) --
-	( 51.21,167.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,167.16) --
-	( 51.21,115.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,115.39) --
-	( 51.21,115.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.03) --
-	( 56.73,154.03);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.03) --
-	( 56.73,135.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,135.21) --
-	( 56.73,135.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,173.35) --
-	( 62.25,173.35);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,173.35) --
-	( 62.25,107.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,107.47) --
-	( 62.25,107.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.77,164.43) --
-	( 67.77,164.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.77,164.43) --
-	( 67.77,164.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.77,164.43) --
-	( 67.77,164.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,187.96) --
-	( 73.29,187.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,187.96) --
-	( 73.29,140.90);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,140.90) --
-	( 73.29,140.90);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.03) --
-	( 78.81,154.03);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.03) --
-	( 78.81,135.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,135.21) --
-	( 78.81,135.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.33,159.48) --
-	( 84.33,159.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.33,159.48) --
-	( 84.33,159.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.33,159.48) --
-	( 84.33,159.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,158.36) --
-	( 89.85,158.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,158.36) --
-	( 89.85,120.22);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,120.22) --
-	( 89.85,120.22);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,168.89) --
-	( 95.37,168.89);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,168.89) --
-	( 95.37, 85.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 85.67) --
-	( 95.37, 85.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,157.00) --
-	(100.89,157.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,157.00) --
-	(100.89, 96.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 96.94) --
-	(100.89, 96.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,147.34) --
-	(106.42,147.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,147.34) --
-	(106.42, 94.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 94.59) --
-	(106.42, 94.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,156.63) --
-	(111.94,156.63);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,156.63) --
-	(111.94, 85.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94, 85.17) --
-	(111.94, 85.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46,164.43) --
-	(117.46,164.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46,164.43) --
-	(117.46, 94.22);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 94.22) --
-	(117.46, 94.22);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,163.56) --
-	(122.98,163.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,163.56) --
-	(122.98, 72.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 72.91) --
-	(122.98, 72.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,142.39) --
-	(128.50,142.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,142.39) --
-	(128.50, 85.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50, 85.17) --
-	(128.50, 85.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,141.52) --
-	(134.02,141.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,141.52) --
-	(134.02, 90.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02, 90.13) --
-	(134.02, 90.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,125.30) --
-	(139.54,125.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,125.30) --
-	(139.54, 70.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 70.07) --
-	(139.54, 70.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,143.75) --
-	(145.06,143.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,143.75) --
-	(145.06, 65.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 65.36) --
-	(145.06, 65.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,135.45) --
-	(150.58,135.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,135.45) --
-	(150.58, 70.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 70.07) --
-	(150.58, 70.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,129.26) --
-	(156.10,129.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,129.26) --
-	(156.10, 40.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10, 40.59) --
-	(156.10, 40.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,125.79) --
-	(161.62,125.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,125.79) --
-	(161.62, 58.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 58.43) --
-	(161.62, 58.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14,109.94) --
-	(167.14,109.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14,109.94) --
-	(167.14, 64.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 64.37) --
-	(167.14, 64.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,107.96) --
-	(172.66,107.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,107.96) --
-	(172.66, 73.29);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 73.29) --
-	(172.66, 73.29);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19,109.94) --
-	(178.19,109.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19,109.94) --
-	(178.19, 77.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 77.74) --
-	(178.19, 77.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71,100.04) --
-	(183.71,100.04);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71,100.04) --
-	(183.71, 85.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.67) --
-	(183.71, 85.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
-	(189.23, 85.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
-	(189.23, 85.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.23, 85.17) --
-	(189.23, 85.17);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.27, 70.31) --
-	(200.27, 70.31);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.27, 70.31) --
-	(200.27, 70.31);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (200.27, 70.31) --
-	(200.27, 70.31);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 83.94) --
-	(211.31, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 83.94) --
-	(211.31, 36.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 36.88) --
-	(211.31, 36.88);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 34.64,156.47) --
-	( 36.88,155.53) --
-	( 39.12,154.58) --
-	( 41.35,153.61) --
-	( 43.59,152.64) --
-	( 45.83,151.65) --
-	( 48.06,150.65) --
-	( 50.30,149.64) --
-	( 52.54,148.61) --
-	( 54.77,147.57) --
-	( 57.01,146.52) --
-	( 59.24,145.46) --
-	( 61.48,144.38) --
-	( 63.72,143.29) --
-	( 65.95,142.18) --
-	( 68.19,141.06) --
-	( 70.43,139.93) --
-	( 72.66,138.78) --
-	( 74.90,137.62) --
-	( 77.13,136.44) --
-	( 79.37,135.25) --
-	( 81.61,134.04) --
-	( 83.84,132.82) --
-	( 86.08,131.59) --
-	( 88.32,130.33) --
-	( 90.55,129.06) --
-	( 92.79,127.78) --
-	( 95.02,126.48) --
-	( 97.26,125.19) --
-	( 99.50,123.96) --
-	(101.73,122.80) --
-	(103.97,121.71) --
-	(106.21,120.70) --
-	(108.44,119.75) --
-	(110.68,118.89) --
-	(112.91,118.11) --
-	(115.15,117.44) --
-	(117.39,116.71) --
-	(119.62,115.77) --
-	(121.86,114.72) --
-	(124.10,113.71) --
-	(126.33,112.61) --
-	(128.57,111.44) --
-	(130.80,110.24) --
-	(133.04,109.07) --
-	(135.28,107.93) --
-	(137.51,106.71) --
-	(139.75,105.56) --
-	(141.99,104.51) --
-	(144.22,103.49) --
-	(146.46,102.45) --
-	(148.69,101.42) --
-	(150.93,100.41) --
-	(153.17, 99.39) --
-	(155.40, 98.40) --
-	(157.64, 97.46) --
-	(159.88, 96.58) --
-	(162.11, 95.79) --
-	(164.35, 95.01) --
-	(166.58, 94.17) --
-	(168.82, 93.29) --
-	(171.06, 92.35) --
-	(173.29, 91.38) --
-	(175.53, 90.35) --
-	(177.77, 89.28) --
-	(180.00, 88.16) --
-	(182.24, 86.99) --
-	(184.47, 85.78) --
-	(186.71, 84.52) --
-	(188.95, 83.22) --
-	(191.18, 81.87) --
-	(193.42, 80.48) --
-	(195.66, 79.04) --
-	(197.89, 77.57) --
-	(200.13, 76.04) --
-	(202.36, 74.48) --
-	(204.60, 72.87) --
-	(206.84, 71.22) --
-	(209.07, 69.53) --
-	(211.31, 67.79);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.64, 30.69) rectangle (211.31,194.15);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69, 37.56) {-10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69, 87.10) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,136.63) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.69,186.17) {20};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89, 40.59) --
-	( 34.64, 40.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89, 90.13) --
-	( 34.64, 90.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,139.66) --
-	( 34.64,139.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.89,189.20) --
-	( 34.64,189.20);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21, 27.94) --
-	( 51.21, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 27.94) --
-	(106.42, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 27.94) --
-	(161.62, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 51.21, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (106.42, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (161.62, 19.68) {20};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (157.65,  7.64) {Symptom onset date};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (122.98,  7.64) {Symptom onset day (infector)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,148.55) {Number of cases with a known infector/infectee pair};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,112.42) {Forward delay (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.64,202.22) {A. Forward serial interval};
-\end{scope}
-\begin{scope}
-\path[clip] (216.81,  0.00) rectangle (433.62,216.81);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 31.71,274.49) {A. Epidemic curve};
+\end{scope}
+\begin{scope}
+\path[clip] (299.25,  0.00) rectangle (567.99,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (216.81,  0.00) rectangle (433.62,216.81);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (299.25,  0.00) rectangle (567.99,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (251.45, 30.69) rectangle (428.12,194.15);
+\path[fill=fillColor] (333.90, 30.69) rectangle (562.49,266.42);
 \definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (499.08,195.87) {maximum observable};
+
+\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (384.78, 74.43) {minimum observable};
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (419.62,266.42) --
+	(426.76,259.28) --
+	(433.91,252.14) --
+	(441.05,244.99) --
+	(448.19,237.85) --
+	(455.34,230.71) --
+	(462.48,223.56) --
+	(469.62,216.42) --
+	(476.77,209.27) --
+	(483.91,202.13) --
+	(491.05,194.99) --
+	(498.20,187.84) --
+	(505.34,180.70) --
+	(512.48,173.56) --
+	(519.63,166.41) --
+	(526.77,159.27) --
+	(533.91,152.13) --
+	(541.06,144.98) --
+	(548.20,137.84) --
+	(555.35,130.70) --
+	(562.49,123.55);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (333.90,116.41) --
+	(341.04,109.26) --
+	(348.18,102.12) --
+	(355.33, 94.98) --
+	(362.47, 87.83) --
+	(369.61, 80.69) --
+	(376.76, 73.55) --
+	(383.90, 66.40) --
+	(391.04, 59.26) --
+	(398.19, 52.12) --
+	(405.33, 44.97) --
+	(412.47, 37.83) --
+	(419.62, 30.69);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (251.45,108.69) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (275.01, 43.54) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (280.90,114.12) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (286.79, 81.54) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (292.68,130.40) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (298.57, 92.40) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (304.45, 83.87) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.34,101.09) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (316.23, 88.33) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (322.12, 97.47) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (328.01,105.63) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,109.04) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.79,110.37) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.68,109.44) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (351.57,103.13) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (357.45,111.73) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.34,116.53) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.23,117.73) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,115.83) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.01,117.47) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.90,120.45) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (392.79,126.70) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.68,130.12) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (404.56,128.31) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (410.45,147.37) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.34,140.35) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (422.23,179.26) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (428.12,157.54) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,108.69) --
-	(251.45,108.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,108.69) --
-	(251.45,108.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,108.69) --
-	(251.45,108.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 43.54) --
-	(275.01, 43.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 43.54) --
-	(275.01, 43.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 43.54) --
-	(275.01, 43.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,119.27) --
-	(280.90,119.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,119.27) --
-	(280.90,108.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,108.96) --
-	(280.90,108.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.54) --
-	(286.79, 81.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.54) --
-	(286.79, 81.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.54) --
-	(286.79, 81.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,130.40) --
-	(292.68,130.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,130.40) --
-	(292.68,130.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,130.40) --
-	(292.68,130.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 92.40) --
-	(298.57, 92.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 92.40) --
-	(298.57, 92.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 92.40) --
-	(298.57, 92.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45,139.36) --
-	(304.45,139.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45,139.36) --
-	(304.45, 38.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45, 38.12) --
-	(304.45, 38.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34,136.92) --
-	(310.34,136.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34,136.92) --
-	(310.34, 86.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 86.97) --
-	(310.34, 86.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23,107.74) --
-	(316.23,107.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23,107.74) --
-	(316.23, 60.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23, 60.78) --
-	(316.23, 60.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12,145.87) --
-	(322.12,145.87);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12,145.87) --
-	(322.12, 54.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (322.12, 54.67) --
-	(322.12, 54.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01,168.40) --
-	(328.01,168.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01,168.40) --
-	(328.01, 69.33);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (328.01, 69.33) --
-	(328.01, 69.33);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,165.69) --
-	(333.90,165.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,165.69) --
-	(333.90, 70.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90, 70.69) --
-	(333.90, 70.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79,179.26) --
-	(339.79,179.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79,179.26) --
-	(339.79, 71.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.79, 71.23) --
-	(339.79, 71.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68,180.89) --
-	(345.68,180.89);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68,180.89) --
-	(345.68, 78.29);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (345.68, 78.29) --
-	(345.68, 78.29);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57,141.26) --
-	(351.57,141.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57,141.26) --
-	(351.57, 70.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (351.57, 70.69) --
-	(351.57, 70.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45,162.97) --
-	(357.45,162.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45,162.97) --
-	(357.45, 76.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (357.45, 76.12) --
-	(357.45, 76.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34,156.19) --
-	(363.34,156.19);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34,156.19) --
-	(363.34, 92.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (363.34, 92.40) --
-	(363.34, 92.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23,154.15) --
-	(369.23,154.15);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23,154.15) --
-	(369.23, 85.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23, 85.62) --
-	(369.23, 85.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12,153.34) --
-	(375.12,153.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12,153.34) --
-	(375.12, 86.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.12, 86.97) --
-	(375.12, 86.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01,148.59) --
-	(381.01,148.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01,148.59) --
-	(381.01, 91.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (381.01, 91.45) --
-	(381.01, 91.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90,164.47) --
-	(386.90,164.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90,164.47) --
-	(386.90, 80.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (386.90, 80.05) --
-	(386.90, 80.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79,186.72) --
-	(392.79,186.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79,186.72) --
-	(392.79, 86.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (392.79, 86.97) --
-	(392.79, 86.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68,177.36) --
-	(398.68,177.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68,177.36) --
-	(398.68,100.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (398.68,100.27) --
-	(398.68,100.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,155.92) --
-	(404.56,155.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,155.92) --
-	(404.56,103.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.56,103.26) --
-	(404.56,103.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,173.83) --
-	(410.45,173.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,173.83) --
-	(410.45,114.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.45,114.12) --
-	(410.45,114.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34,171.12) --
-	(416.34,171.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34,171.12) --
-	(416.34, 93.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.34, 93.08) --
-	(416.34, 93.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,179.26) --
-	(422.23,179.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,179.26) --
-	(422.23,179.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (422.23,179.26) --
-	(422.23,179.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,157.54) --
-	(428.12,157.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,157.54) --
-	(428.12,157.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12,157.54) --
-	(428.12,157.54);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (251.45, 93.58) --
-	(253.69, 93.29) --
-	(255.93, 93.04) --
-	(258.16, 92.81) --
-	(260.40, 92.62) --
-	(262.64, 92.45) --
-	(264.87, 92.32) --
-	(267.11, 92.23) --
-	(269.35, 92.16) --
-	(271.58, 92.13) --
-	(273.82, 92.13) --
-	(276.05, 92.16) --
-	(278.29, 92.23) --
-	(280.53, 92.33) --
-	(282.76, 92.46) --
-	(285.00, 92.63) --
-	(287.24, 92.83) --
-	(289.47, 93.07) --
-	(291.71, 93.35) --
-	(293.94, 93.66) --
-	(296.18, 94.00) --
-	(298.42, 94.38) --
-	(300.65, 94.80) --
-	(302.89, 95.25) --
-	(305.13, 95.74) --
-	(307.36, 96.27) --
-	(309.60, 96.84) --
-	(311.83, 97.44) --
-	(314.07, 98.08) --
-	(316.31, 98.76) --
-	(318.54, 99.48) --
-	(320.78,100.24) --
-	(323.02,101.03) --
-	(325.25,101.87) --
-	(327.49,102.75) --
-	(329.72,103.64) --
-	(331.96,104.48) --
-	(334.20,105.29) --
-	(336.43,106.05) --
-	(338.67,106.77) --
-	(340.91,107.42) --
-	(343.14,107.90) --
-	(345.38,108.26) --
-	(347.61,108.57) --
-	(349.85,108.93) --
-	(352.09,109.40) --
-	(354.32,109.92) --
-	(356.56,110.52) --
-	(358.80,111.39) --
-	(361.03,112.74) --
-	(363.27,113.91) --
-	(365.50,114.59) --
-	(367.74,115.15) --
-	(369.98,115.88) --
-	(372.21,116.66) --
-	(374.45,117.45) --
-	(376.69,118.26) --
-	(378.92,119.02) --
-	(381.16,119.78) --
-	(383.39,120.62) --
-	(385.63,121.59) --
-	(387.87,122.75) --
-	(390.10,124.03) --
-	(392.34,125.40) --
-	(394.58,126.87) --
-	(396.81,128.44) --
-	(399.05,130.11) --
-	(401.28,131.88) --
-	(403.52,133.75) --
-	(405.76,135.71) --
-	(407.99,137.77) --
-	(410.23,139.94) --
-	(412.47,142.20) --
-	(414.70,144.56) --
-	(416.94,147.03) --
-	(419.17,149.59) --
-	(421.41,152.26) --
-	(423.65,155.02) --
-	(425.88,157.89) --
-	(428.12,160.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,137.84) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (348.18,219.10) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (355.33,183.08) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.47,194.99) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.61,194.99) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (376.76,223.56) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (383.90,223.56) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (391.04,194.99) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.19,216.42) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (405.33,184.27) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (412.47,159.58) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (419.62,159.72) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (426.76,165.29) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (433.91,150.04) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (441.05,160.95) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (448.19,149.30) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (455.34,144.74) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (462.48,149.93) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (469.62,133.26) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (476.77,138.29) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (483.91,129.96) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (491.05,127.28) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.20,127.33) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (505.34,119.77) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (512.48,115.57) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (519.63,124.85) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (526.77,122.12) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (533.91,109.26) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (548.20, 87.83) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (562.49, 73.55) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,137.84) --
+	(333.90,137.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,137.84) --
+	(333.90,137.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,137.84) --
+	(333.90,137.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,236.60) --
+	(348.18,236.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,236.60) --
+	(348.18,191.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,191.59) --
+	(348.18,191.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,227.49) --
+	(355.33,227.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,227.49) --
+	(355.33,152.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,152.84) --
+	(355.33,152.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,208.56) --
+	(362.47,208.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,208.56) --
+	(362.47,181.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,181.41) --
+	(362.47,181.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,236.42) --
+	(369.61,236.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,236.42) --
+	(369.61,141.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,141.41) --
+	(369.61,141.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,223.56) --
+	(376.76,223.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,223.56) --
+	(376.76,223.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,223.56) --
+	(376.76,223.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,257.49) --
+	(383.90,257.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,257.49) --
+	(383.90,189.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,189.63) --
+	(383.90,189.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,208.56) --
+	(391.04,208.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,208.56) --
+	(391.04,181.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,181.41) --
+	(391.04,181.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,216.42) --
+	(398.19,216.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,216.42) --
+	(398.19,216.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,216.42) --
+	(398.19,216.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,214.81) --
+	(405.33,214.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,214.81) --
+	(405.33,159.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,159.81) --
+	(405.33,159.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,229.99) --
+	(412.47,229.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,229.99) --
+	(412.47,109.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,109.98) --
+	(412.47,109.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,212.85) --
+	(419.62,212.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,212.85) --
+	(419.62,126.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,126.23) --
+	(419.62,126.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,198.92) --
+	(426.76,198.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,198.92) --
+	(426.76,122.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,122.84) --
+	(426.76,122.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (433.91,212.31) --
+	(433.91,212.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (433.91,212.31) --
+	(433.91,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (433.91,109.26) --
+	(433.91,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (441.05,223.56) --
+	(441.05,223.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (441.05,223.56) --
+	(441.05,122.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (441.05,122.30) --
+	(441.05,122.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19,222.31) --
+	(448.19,222.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19,222.31) --
+	(448.19, 91.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19, 91.58) --
+	(448.19, 91.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (455.34,191.77) --
+	(455.34,191.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (455.34,191.77) --
+	(455.34,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (455.34,109.26) --
+	(455.34,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.48,190.52) --
+	(462.48,190.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.48,190.52) --
+	(462.48,116.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.48,116.41) --
+	(462.48,116.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.62,167.13) --
+	(469.62,167.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.62,167.13) --
+	(469.62, 87.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.62, 87.48) --
+	(469.62, 87.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.77,193.74) --
+	(476.77,193.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.77,193.74) --
+	(476.77, 80.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.77, 80.69) --
+	(476.77, 80.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (483.91,181.77) --
+	(483.91,181.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (483.91,181.77) --
+	(483.91, 87.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (483.91, 87.48) --
+	(483.91, 87.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.05,172.84) --
+	(491.05,172.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.05,172.84) --
+	(491.05, 44.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.05, 44.97) --
+	(491.05, 44.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (498.20,167.84) --
+	(498.20,167.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (498.20,167.84) --
+	(498.20, 70.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (498.20, 70.69) --
+	(498.20, 70.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (505.34,144.98) --
+	(505.34,144.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (505.34,144.98) --
+	(505.34, 79.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (505.34, 79.26) --
+	(505.34, 79.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (512.48,142.13) --
+	(512.48,142.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (512.48,142.13) --
+	(512.48, 92.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (512.48, 92.12) --
+	(512.48, 92.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (519.63,144.98) --
+	(519.63,144.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (519.63,144.98) --
+	(519.63, 98.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (519.63, 98.55) --
+	(519.63, 98.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,130.70) --
+	(526.77,130.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,130.70) --
+	(526.77,109.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,109.98) --
+	(526.77,109.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.91,109.26) --
+	(533.91,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.91,109.26) --
+	(533.91,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.91,109.26) --
+	(533.91,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (548.20, 87.83) --
+	(548.20, 87.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (548.20, 87.83) --
+	(548.20, 87.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (548.20, 87.83) --
+	(548.20, 87.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (562.49,107.48) --
+	(562.49,107.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (562.49,107.48) --
+	(562.49, 39.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (562.49, 39.62) --
+	(562.49, 39.62);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (333.90,212.08) --
+	(336.79,210.73) --
+	(339.68,209.35) --
+	(342.58,207.96) --
+	(345.47,206.55) --
+	(348.36,205.13) --
+	(351.26,203.68) --
+	(354.15,202.22) --
+	(357.04,200.75) --
+	(359.94,199.25) --
+	(362.83,197.73) --
+	(365.73,196.20) --
+	(368.62,194.64) --
+	(371.51,193.07) --
+	(374.41,191.48) --
+	(377.30,189.86) --
+	(380.19,188.23) --
+	(383.09,186.57) --
+	(385.98,184.90) --
+	(388.87,183.20) --
+	(391.77,181.48) --
+	(394.66,179.74) --
+	(397.55,177.98) --
+	(400.45,176.19) --
+	(403.34,174.39) --
+	(406.24,172.56) --
+	(409.13,170.70) --
+	(412.02,168.82) --
+	(414.92,166.96) --
+	(417.81,165.20) --
+	(420.70,163.53) --
+	(423.60,161.96) --
+	(426.49,160.49) --
+	(429.38,159.13) --
+	(432.28,157.88) --
+	(435.17,156.76) --
+	(438.06,155.79) --
+	(440.96,154.74) --
+	(443.85,153.38) --
+	(446.75,151.87) --
+	(449.64,150.42) --
+	(452.53,148.83) --
+	(455.43,147.14) --
+	(458.32,145.41) --
+	(461.21,143.73) --
+	(464.11,142.08) --
+	(467.00,140.32) --
+	(469.89,138.66) --
+	(472.79,137.15) --
+	(475.68,135.67) --
+	(478.58,134.18) --
+	(481.47,132.70) --
+	(484.36,131.23) --
+	(487.26,129.77) --
+	(490.15,128.34) --
+	(493.04,126.97) --
+	(495.94,125.71) --
+	(498.83,124.58) --
+	(501.72,123.44) --
+	(504.62,122.24) --
+	(507.51,120.96) --
+	(510.40,119.62) --
+	(513.30,118.21) --
+	(516.19,116.73) --
+	(519.09,115.18) --
+	(521.98,113.56) --
+	(524.87,111.88) --
+	(527.77,110.13) --
+	(530.66,108.32) --
+	(533.55,106.44) --
+	(536.45,104.50) --
+	(539.34,102.49) --
+	(542.23,100.42) --
+	(545.13, 98.29) --
+	(548.02, 96.10) --
+	(550.91, 93.84) --
+	(553.81, 91.52) --
+	(556.70, 89.14) --
+	(559.60, 86.70) --
+	(562.49, 84.20);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.45, 30.69) rectangle (428.12,194.15);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.90, 30.69) rectangle (562.49,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50, 35.09) {-10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50, 89.37) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (246.50,143.66) {10};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (328.95, 41.94) {-10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (328.95,113.38) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (328.95,184.81) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (328.95,256.25) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70, 38.12) --
-	(251.45, 38.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70, 92.40) --
-	(251.45, 92.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (248.70,146.69) --
-	(251.45,146.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.15, 44.97) --
+	(333.90, 44.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.15,116.41) --
+	(333.90,116.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.15,187.84) --
+	(333.90,187.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.15,259.28) --
+	(333.90,259.28);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45, 27.94) --
-	(251.45, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 27.94) --
-	(310.34, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.23, 27.94) --
-	(369.23, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (428.12, 27.94) --
-	(428.12, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76, 27.94) --
+	(376.76, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76, 27.94) --
+	(426.76, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.77, 27.94) --
+	(476.77, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77, 27.94) --
+	(526.77, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (251.45, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (310.34, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (369.23, 19.68) {20};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (428.12, 19.68) {30};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (376.76, 19.68) {Jan 13};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (426.76, 19.68) {Jan 20};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.77, 19.68) {Jan 27};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (526.77, 19.68) {Feb 03};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (339.79,  7.64) {Symptom onset day (infectee)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (448.19,  7.64) {Symptom onset date (infector)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (229.89,112.42) {Backward delay (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (312.33,148.55) {Forward delay (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (251.45,202.22) {B. Backward serial interval};
-\end{scope}
-\begin{scope}
-\path[clip] (433.62,  0.00) rectangle (650.43,216.81);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (333.90,274.49) {B. Forward serial interval};
+\end{scope}
+\begin{scope}
+\path[clip] (584.76,  0.00) rectangle (860.64,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (433.62,  0.00) rectangle (650.43,216.81);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (584.76,  0.00) rectangle (860.64,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (460.93, 30.69) rectangle (644.93,194.15);
+\path[fill=fillColor] (619.40, 30.69) rectangle (855.14,266.42);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (673.17,204.80) {maximum observable};
+
+\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (806.75, 79.07) {minimum observable};
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (619.40,140.70) --
+	(627.26,148.55) --
+	(635.12,156.41) --
+	(642.98,164.27) --
+	(650.84,172.13) --
+	(658.69,179.99) --
+	(666.55,187.84) --
+	(674.41,195.70) --
+	(682.27,203.56) --
+	(690.13,211.42) --
+	(697.98,219.28) --
+	(705.84,227.13) --
+	(713.70,234.99) --
+	(721.56,242.85) --
+	(729.41,250.71) --
+	(737.27,258.56) --
+	(745.13,266.42);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (768.70, 30.69) --
+	(776.56, 38.54) --
+	(784.42, 46.40) --
+	(792.28, 54.26) --
+	(800.14, 62.12) --
+	(807.99, 69.98) --
+	(815.85, 77.83) --
+	(823.71, 85.69) --
+	(831.57, 93.55) --
+	(839.43,101.41) --
+	(847.28,109.26) --
+	(855.14,117.12);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.40,140.70) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (650.84, 46.40) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (658.69,148.55) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (666.55,101.41) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (674.41,172.13) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (682.27,117.12) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (690.13,104.77) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (697.98,129.70) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (705.84,111.23) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (713.70,124.46) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (721.56,136.28) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (729.41,141.20) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (737.27,143.14) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (745.13,141.78) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (752.99,132.65) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (760.85,145.10) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (768.70,152.05) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (776.56,153.79) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (784.42,151.04) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (792.28,153.41) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (800.14,157.72) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (807.99,166.77) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (815.85,171.71) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (823.71,169.11) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (831.57,196.68) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (839.43,186.53) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (847.28,242.85) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (855.14,211.42) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.40,140.70) --
+	(619.40,140.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.40,140.70) --
+	(619.40,140.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.40,140.70) --
+	(619.40,140.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (650.84, 46.40) --
+	(650.84, 46.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (650.84, 46.40) --
+	(650.84, 46.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (650.84, 46.40) --
+	(650.84, 46.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (658.69,156.02) --
+	(658.69,156.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (658.69,156.02) --
+	(658.69,141.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (658.69,141.09) --
+	(658.69,141.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.55,101.41) --
+	(666.55,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.55,101.41) --
+	(666.55,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.55,101.41) --
+	(666.55,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.41,172.13) --
+	(674.41,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.41,172.13) --
+	(674.41,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.41,172.13) --
+	(674.41,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (682.27,117.12) --
+	(682.27,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (682.27,117.12) --
+	(682.27,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (682.27,117.12) --
+	(682.27,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.13,185.09) --
+	(690.13,185.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.13,185.09) --
+	(690.13, 38.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.13, 38.54) --
+	(690.13, 38.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (697.98,181.56) --
+	(697.98,181.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (697.98,181.56) --
+	(697.98,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (697.98,109.26) --
+	(697.98,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (705.84,139.32) --
+	(705.84,139.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (705.84,139.32) --
+	(705.84, 71.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (705.84, 71.35) --
+	(705.84, 71.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (713.70,194.52) --
+	(713.70,194.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (713.70,194.52) --
+	(713.70, 62.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (713.70, 62.51) --
+	(713.70, 62.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (721.56,227.13) --
+	(721.56,227.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (721.56,227.13) --
+	(721.56, 83.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (721.56, 83.73) --
+	(721.56, 83.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (729.41,223.20) --
+	(729.41,223.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (729.41,223.20) --
+	(729.41, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (729.41, 85.69) --
+	(729.41, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (737.27,242.85) --
+	(737.27,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (737.27,242.85) --
+	(737.27, 86.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (737.27, 86.48) --
+	(737.27, 86.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (745.13,245.21) --
+	(745.13,245.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (745.13,245.21) --
+	(745.13, 96.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (745.13, 96.69) --
+	(745.13, 96.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (752.99,187.84) --
+	(752.99,187.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (752.99,187.84) --
+	(752.99, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (752.99, 85.69) --
+	(752.99, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (760.85,219.28) --
+	(760.85,219.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (760.85,219.28) --
+	(760.85, 93.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (760.85, 93.55) --
+	(760.85, 93.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (768.70,209.45) --
+	(768.70,209.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (768.70,209.45) --
+	(768.70,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (768.70,117.12) --
+	(768.70,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (776.56,206.51) --
+	(776.56,206.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (776.56,206.51) --
+	(776.56,107.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (776.56,107.30) --
+	(776.56,107.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (784.42,205.33) --
+	(784.42,205.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (784.42,205.33) --
+	(784.42,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (784.42,109.26) --
+	(784.42,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (792.28,198.45) --
+	(792.28,198.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (792.28,198.45) --
+	(792.28,115.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (792.28,115.75) --
+	(792.28,115.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (800.14,221.44) --
+	(800.14,221.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (800.14,221.44) --
+	(800.14, 99.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (800.14, 99.25) --
+	(800.14, 99.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (807.99,253.65) --
+	(807.99,253.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (807.99,253.65) --
+	(807.99,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (807.99,109.26) --
+	(807.99,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (815.85,240.10) --
+	(815.85,240.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (815.85,240.10) --
+	(815.85,128.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (815.85,128.52) --
+	(815.85,128.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (823.71,209.06) --
+	(823.71,209.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (823.71,209.06) --
+	(823.71,132.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (823.71,132.84) --
+	(823.71,132.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (831.57,234.99) --
+	(831.57,234.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (831.57,234.99) --
+	(831.57,148.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (831.57,148.55) --
+	(831.57,148.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (839.43,231.06) --
+	(839.43,231.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (839.43,231.06) --
+	(839.43,118.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (839.43,118.10) --
+	(839.43,118.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (847.28,242.85) --
+	(847.28,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (847.28,242.85) --
+	(847.28,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (847.28,242.85) --
+	(847.28,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (855.14,211.42) --
+	(855.14,211.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (855.14,211.42) --
+	(855.14,211.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (855.14,211.42) --
+	(855.14,211.42);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (619.40,118.83) --
+	(622.39,118.41) --
+	(625.37,118.04) --
+	(628.36,117.71) --
+	(631.34,117.43) --
+	(634.32,117.20) --
+	(637.31,117.01) --
+	(640.29,116.87) --
+	(643.28,116.77) --
+	(646.26,116.72) --
+	(649.24,116.72) --
+	(652.23,116.77) --
+	(655.21,116.87) --
+	(658.20,117.01) --
+	(661.18,117.21) --
+	(664.16,117.45) --
+	(667.15,117.75) --
+	(670.13,118.09) --
+	(673.12,118.49) --
+	(676.10,118.94) --
+	(679.08,119.44) --
+	(682.07,119.99) --
+	(685.05,120.59) --
+	(688.04,121.25) --
+	(691.02,121.96) --
+	(694.00,122.73) --
+	(696.99,123.54) --
+	(699.97,124.42) --
+	(702.96,125.35) --
+	(705.94,126.33) --
+	(708.92,127.37) --
+	(711.91,128.47) --
+	(714.89,129.62) --
+	(717.88,130.83) --
+	(720.86,132.10) --
+	(723.84,133.38) --
+	(726.83,134.61) --
+	(729.81,135.77) --
+	(732.80,136.88) --
+	(735.78,137.92) --
+	(738.76,138.87) --
+	(741.75,139.56) --
+	(744.73,140.07) --
+	(747.72,140.53) --
+	(750.70,141.04) --
+	(753.68,141.73) --
+	(756.67,142.49) --
+	(759.65,143.35) --
+	(762.64,144.61) --
+	(765.62,146.56) --
+	(768.60,148.26) --
+	(771.59,149.31) --
+	(774.57,150.22) --
+	(777.56,151.24) --
+	(780.54,152.28) --
+	(783.52,153.32) --
+	(786.51,154.37) --
+	(789.49,155.31) --
+	(792.48,156.26) --
+	(795.46,157.32) --
+	(798.44,158.61) --
+	(801.43,160.23) --
+	(804.41,162.05) --
+	(807.40,164.02) --
+	(810.38,166.15) --
+	(813.36,168.43) --
+	(816.35,170.87) --
+	(819.33,173.46) --
+	(822.32,176.21) --
+	(825.30,179.13) --
+	(828.28,182.20) --
+	(831.27,185.42) --
+	(834.25,188.81) --
+	(837.24,192.36) --
+	(840.22,196.07) --
+	(843.20,199.95) --
+	(846.19,203.98) --
+	(849.17,208.18) --
+	(852.16,212.54) --
+	(855.14,217.06);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (619.40, 30.69) rectangle (855.14,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (614.45, 35.51) {-10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (614.45,114.09) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (614.45,192.67) {10};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.65, 38.54) --
+	(619.40, 38.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.65,117.12) --
+	(619.40,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.65,195.70) --
+	(619.40,195.70);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (642.98, 27.94) --
+	(642.98, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (697.98, 27.94) --
+	(697.98, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (752.99, 27.94) --
+	(752.99, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (807.99, 27.94) --
+	(807.99, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (642.98, 19.68) {Jan 13};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (697.98, 19.68) {Jan 20};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (752.99, 19.68) {Jan 27};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (807.99, 19.68) {Feb 03};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (737.27,  7.64) {Symptom onset date (infectee)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (597.84,148.55) {Backward delay (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (619.40,274.49) {C. Backward serial interval};
+\end{scope}
+\begin{scope}
+\path[clip] (867.24,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (867.24,  0.00) rectangle (1156.32,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (894.55, 30.69) rectangle (1150.82,266.42);
+\definecolor{fillColor}{RGB}{240,228,66}
+
+\path[fill=fillColor,fill opacity=0.50] (918.58,255.71) --
+	(926.59,234.51) --
+	(934.59,227.85) --
+	(942.60,224.34) --
+	(950.61,232.95) --
+	(958.62,225.18) --
+	(966.63,220.08) --
+	(974.64,212.60) --
+	(982.64,137.83) --
+	(990.65,119.60) --
+	(998.66,116.21) --
+	(1006.67,104.34) --
+	(1014.68,101.52) --
+	(1022.69, 91.89) --
+	(1030.69, 87.88) --
+	(1038.70, 85.77) --
+	(1046.71, 79.62) --
+	(1054.72, 76.53) --
+	(1062.73, 72.74) --
+	(1070.74, 71.32) --
+	(1078.74, 69.30) --
+	(1086.75, 68.00) --
+	(1094.76, 66.17) --
+	(1102.77, 65.86) --
+	(1110.78, 65.06) --
+	(1118.79, 64.84) --
+	(1126.79, 64.84) --
+	(1134.80, 64.82) --
+	(1142.81, 64.82) --
+	(1150.82, 64.08) --
+	(1150.82, 56.77) --
+	(1142.81, 57.72) --
+	(1134.80, 57.72) --
+	(1126.79, 58.18) --
+	(1118.79, 58.18) --
+	(1110.78, 58.40) --
+	(1102.77, 58.16) --
+	(1094.76, 58.79) --
+	(1086.75, 60.03) --
+	(1078.74, 60.94) --
+	(1070.74, 62.46) --
+	(1062.73, 65.05) --
+	(1054.72, 66.78) --
+	(1046.71, 70.56) --
+	(1038.70, 73.93) --
+	(1030.69, 74.95) --
+	(1022.69, 77.75) --
+	(1014.68, 84.76) --
+	(1006.67, 84.17) --
+	(998.66, 90.54) --
+	(990.65, 89.60) --
+	(982.64, 93.27) --
+	(974.64,129.71) --
+	(966.63,137.14) --
+	(958.62,136.34) --
+	(950.61,134.94) --
+	(942.60,135.04) --
+	(934.59,120.43) --
+	(926.59,124.23) --
+	(918.58,119.49) --
+	cycle;
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (918.58,255.71) --
+	(926.59,234.51) --
+	(934.59,227.85) --
+	(942.60,224.34) --
+	(950.61,232.95) --
+	(958.62,225.18) --
+	(966.63,220.08) --
+	(974.64,212.60) --
+	(982.64,137.83) --
+	(990.65,119.60) --
+	(998.66,116.21) --
+	(1006.67,104.34) --
+	(1014.68,101.52) --
+	(1022.69, 91.89) --
+	(1030.69, 87.88) --
+	(1038.70, 85.77) --
+	(1046.71, 79.62) --
+	(1054.72, 76.53) --
+	(1062.73, 72.74) --
+	(1070.74, 71.32) --
+	(1078.74, 69.30) --
+	(1086.75, 68.00) --
+	(1094.76, 66.17) --
+	(1102.77, 65.86) --
+	(1110.78, 65.06) --
+	(1118.79, 64.84) --
+	(1126.79, 64.84) --
+	(1134.80, 64.82) --
+	(1142.81, 64.82) --
+	(1150.82, 64.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (1150.82, 56.77) --
+	(1142.81, 57.72) --
+	(1134.80, 57.72) --
+	(1126.79, 58.18) --
+	(1118.79, 58.18) --
+	(1110.78, 58.40) --
+	(1102.77, 58.16) --
+	(1094.76, 58.79) --
+	(1086.75, 60.03) --
+	(1078.74, 60.94) --
+	(1070.74, 62.46) --
+	(1062.73, 65.05) --
+	(1054.72, 66.78) --
+	(1046.71, 70.56) --
+	(1038.70, 73.93) --
+	(1030.69, 74.95) --
+	(1022.69, 77.75) --
+	(1014.68, 84.76) --
+	(1006.67, 84.17) --
+	(998.66, 90.54) --
+	(990.65, 89.60) --
+	(982.64, 93.27) --
+	(974.64,129.71) --
+	(966.63,137.14) --
+	(958.62,136.34) --
+	(950.61,134.94) --
+	(942.60,135.04) --
+	(934.59,120.43) --
+	(926.59,124.23) --
+	(918.58,119.49);
+\definecolor{fillColor}{RGB}{0,114,178}
+
+\path[fill=fillColor,fill opacity=0.50] (918.58,167.99) --
+	(926.59,158.37) --
+	(934.59,155.61) --
+	(942.60,153.41) --
+	(950.61,158.49) --
+	(958.62,154.03) --
+	(966.63,151.93) --
+	(974.64,148.30) --
+	(982.64,107.71) --
+	(990.65, 96.60) --
+	(998.66, 94.03) --
+	(1006.67, 86.26) --
+	(1014.68, 84.52) --
+	(1022.69, 77.77) --
+	(1030.69, 75.45) --
+	(1038.70, 73.98) --
+	(1046.71, 69.74) --
+	(1054.72, 67.73) --
+	(1062.73, 65.35) --
+	(1070.74, 64.41) --
+	(1078.74, 62.76) --
+	(1086.75, 61.94) --
+	(1094.76, 60.56) --
+	(1102.77, 60.51) --
+	(1110.78, 60.01) --
+	(1118.79, 59.88) --
+	(1126.79, 59.88) --
+	(1134.80, 59.77) --
+	(1142.81, 59.77) --
+	(1150.82, 59.40) --
+	(1150.82, 54.49) --
+	(1142.81, 54.89) --
+	(1134.80, 54.89) --
+	(1126.79, 55.23) --
+	(1118.79, 55.23) --
+	(1110.78, 55.32) --
+	(1102.77, 55.43) --
+	(1094.76, 55.76) --
+	(1086.75, 56.48) --
+	(1078.74, 57.32) --
+	(1070.74, 58.34) --
+	(1062.73, 59.85) --
+	(1054.72, 61.35) --
+	(1046.71, 63.63) --
+	(1038.70, 66.52) --
+	(1030.69, 66.97) --
+	(1022.69, 68.74) --
+	(1014.68, 73.15) --
+	(1006.67, 73.04) --
+	(998.66, 77.40) --
+	(990.65, 77.19) --
+	(982.64, 79.82) --
+	(974.64,101.35) --
+	(966.63,108.09) --
+	(958.62,107.05) --
+	(950.61,105.61) --
+	(942.60,105.29) --
+	(934.59, 96.62) --
+	(926.59, 98.80) --
+	(918.58, 95.78) --
+	cycle;
+\definecolor{drawColor}{RGB}{0,114,178}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round] (918.58,167.99) --
+	(926.59,158.37) --
+	(934.59,155.61) --
+	(942.60,153.41) --
+	(950.61,158.49) --
+	(958.62,154.03) --
+	(966.63,151.93) --
+	(974.64,148.30) --
+	(982.64,107.71) --
+	(990.65, 96.60) --
+	(998.66, 94.03) --
+	(1006.67, 86.26) --
+	(1014.68, 84.52) --
+	(1022.69, 77.77) --
+	(1030.69, 75.45) --
+	(1038.70, 73.98) --
+	(1046.71, 69.74) --
+	(1054.72, 67.73) --
+	(1062.73, 65.35) --
+	(1070.74, 64.41) --
+	(1078.74, 62.76) --
+	(1086.75, 61.94) --
+	(1094.76, 60.56) --
+	(1102.77, 60.51) --
+	(1110.78, 60.01) --
+	(1118.79, 59.88) --
+	(1126.79, 59.88) --
+	(1134.80, 59.77) --
+	(1142.81, 59.77) --
+	(1150.82, 59.40);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round] (1150.82, 54.49) --
+	(1142.81, 54.89) --
+	(1134.80, 54.89) --
+	(1126.79, 55.23) --
+	(1118.79, 55.23) --
+	(1110.78, 55.32) --
+	(1102.77, 55.43) --
+	(1094.76, 55.76) --
+	(1086.75, 56.48) --
+	(1078.74, 57.32) --
+	(1070.74, 58.34) --
+	(1062.73, 59.85) --
+	(1054.72, 61.35) --
+	(1046.71, 63.63) --
+	(1038.70, 66.52) --
+	(1030.69, 66.97) --
+	(1022.69, 68.74) --
+	(1014.68, 73.15) --
+	(1006.67, 73.04) --
+	(998.66, 77.40) --
+	(990.65, 77.19) --
+	(982.64, 79.82) --
+	(974.64,101.35) --
+	(966.63,108.09) --
+	(958.62,107.05) --
+	(950.61,105.61) --
+	(942.60,105.29) --
+	(934.59, 96.62) --
+	(926.59, 98.80) --
+	(918.58, 95.78);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (894.55, 41.40) -- (1150.82, 41.40);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (918.58,170.94) --
+	(926.59,170.79) --
+	(934.59,163.30) --
+	(942.60,167.34) --
+	(950.61,172.68) --
+	(958.62,172.43) --
+	(966.63,174.86) --
+	(974.64,167.73) --
+	(982.64,112.65) --
+	(990.65,105.04) --
+	(998.66,102.84) --
+	(1006.67, 93.38) --
+	(1014.68, 91.84) --
+	(1022.69, 83.99) --
+	(1030.69, 80.95) --
+	(1038.70, 80.00) --
+	(1046.71, 75.18) --
+	(1054.72, 71.77) --
+	(1062.73, 68.56) --
+	(1070.74, 66.30) --
+	(1078.74, 65.11) --
+	(1086.75, 63.71) --
+	(1094.76, 62.37) --
+	(1102.77, 61.91) --
+	(1110.78, 61.69) --
+	(1118.79, 61.52) --
+	(1126.79, 61.52) --
+	(1134.80, 61.33) --
+	(1142.81, 61.33) --
+	(1150.82, 60.65);
+\definecolor{drawColor}{RGB}{0,114,178}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (918.58,126.39) --
+	(926.59,125.79) --
+	(934.59,122.09) --
+	(942.60,124.37) --
+	(950.61,127.48) --
+	(958.62,126.99) --
+	(966.63,128.28) --
+	(974.64,123.96) --
+	(982.64, 92.40) --
+	(990.65, 87.06) --
+	(998.66, 85.30) --
+	(1006.67, 79.23) --
+	(1014.68, 77.99) --
+	(1022.69, 73.04) --
+	(1030.69, 70.90) --
+	(1038.70, 70.16) --
+	(1046.71, 66.88) --
+	(1054.72, 64.57) --
+	(1062.73, 62.37) --
+	(1070.74, 60.94) --
+	(1078.74, 60.13) --
+	(1086.75, 59.14) --
+	(1094.76, 58.16) --
+	(1102.77, 57.82) --
+	(1110.78, 57.64) --
+	(1118.79, 57.52) --
+	(1126.79, 57.52) --
+	(1134.80, 57.39) --
+	(1142.81, 57.39) --
+	(1150.82, 56.99);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (894.55, 30.69) rectangle (1150.82,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (889.60, 38.37) {1};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (889.60, 90.38) {2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (889.60,142.40) {3};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (889.60,194.41) {4};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (889.60,246.42) {5};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (891.80, 41.40) --
+	(894.55, 41.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (891.80, 93.41) --
+	(894.55, 93.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (891.80,145.43) --
+	(894.55,145.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (891.80,197.44) --
+	(894.55,197.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (891.80,249.45) --
+	(894.55,249.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (918.58, 27.94) --
+	(918.58, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (998.66, 27.94) --
+	(998.66, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (1078.74, 27.94) --
+	(1078.74, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (918.58, 19.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (998.66, 19.68) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (1078.74, 19.68) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (1022.69,  7.64) {Time (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (880.32,148.55) {Basic reproduction number $\mathcal R_0$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (1011.05,208.36) rectangle (1126.58,253.77);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (1016.55,228.31) rectangle (1031.00,242.77);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{240,228,66}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (478.18,186.72) --
-	(483.93,172.02) --
-	(489.68,167.41) --
-	(495.43,164.97) --
-	(501.18,170.94) --
-	(506.93,165.55) --
-	(512.68,162.02) --
-	(518.43,156.83) --
-	(524.18,104.98) --
-	(529.93, 92.34) --
-	(535.68, 89.99) --
-	(541.43, 81.76) --
-	(547.18, 79.80) --
-	(552.93, 73.13) --
-	(558.68, 70.34) --
-	(564.43, 68.88) --
-	(570.18, 64.62) --
-	(575.93, 62.47) --
-	(581.68, 59.85) --
-	(587.43, 58.86) --
-	(593.18, 57.46) --
-	(598.93, 56.56) --
-	(604.68, 55.29) --
-	(610.43, 55.07) --
-	(616.18, 54.52) --
-	(621.93, 54.37) --
-	(627.68, 54.37) --
-	(633.43, 54.35) --
-	(639.18, 54.35) --
-	(644.93, 53.84) --
-	(644.93, 48.78) --
-	(639.18, 49.43) --
-	(633.43, 49.43) --
-	(627.68, 49.75) --
-	(621.93, 49.75) --
-	(616.18, 49.90) --
-	(610.43, 49.74) --
-	(604.68, 50.17) --
-	(598.93, 51.03) --
-	(593.18, 51.66) --
-	(587.43, 52.72) --
-	(581.68, 54.51) --
-	(575.93, 55.72) --
-	(570.18, 58.33) --
-	(564.43, 60.67) --
-	(558.68, 61.38) --
-	(552.93, 63.32) --
-	(547.18, 68.18) --
-	(541.43, 67.77) --
-	(535.68, 72.19) --
-	(529.93, 71.54) --
-	(524.18, 74.09) --
-	(518.43, 99.35) --
-	(512.68,104.50) --
-	(506.93,103.95) --
-	(501.18,102.98) --
-	(495.43,103.05) --
-	(489.68, 92.92) --
-	(483.93, 95.55) --
-	(478.18, 92.27) --
-	cycle;
+\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor,fill opacity=0.50] (1017.26,229.02) rectangle (1030.29,242.05);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (1017.99,235.54) -- (1029.56,235.54);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (1016.55,213.86) rectangle (1031.00,228.31);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,114,178}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (478.18,125.90) --
-	(483.93,119.23) --
-	(489.68,117.31) --
-	(495.43,115.79) --
-	(501.18,119.31) --
-	(506.93,116.22) --
-	(512.68,114.76) --
-	(518.43,112.24) --
-	(524.18, 84.09) --
-	(529.93, 76.40) --
-	(535.68, 74.61) --
-	(541.43, 69.22) --
-	(547.18, 68.02) --
-	(552.93, 63.34) --
-	(558.68, 61.72) --
-	(564.43, 60.71) --
-	(570.18, 57.76) --
-	(575.93, 56.38) --
-	(581.68, 54.72) --
-	(587.43, 54.07) --
-	(593.18, 52.92) --
-	(598.93, 52.36) --
-	(604.68, 51.40) --
-	(610.43, 51.36) --
-	(616.18, 51.02) --
-	(621.93, 50.93) --
-	(627.68, 50.93) --
-	(633.43, 50.85) --
-	(639.18, 50.85) --
-	(644.93, 50.60) --
-	(644.93, 47.19) --
-	(639.18, 47.47) --
-	(633.43, 47.47) --
-	(627.68, 47.71) --
-	(621.93, 47.71) --
-	(616.18, 47.77) --
-	(610.43, 47.85) --
-	(604.68, 48.08) --
-	(598.93, 48.58) --
-	(593.18, 49.16) --
-	(587.43, 49.86) --
-	(581.68, 50.91) --
-	(575.93, 51.95) --
-	(570.18, 53.53) --
-	(564.43, 55.54) --
-	(558.68, 55.84) --
-	(552.93, 57.08) --
-	(547.18, 60.14) --
-	(541.43, 60.06) --
-	(535.68, 63.08) --
-	(529.93, 62.94) --
-	(524.18, 64.75) --
-	(518.43, 79.69) --
-	(512.68, 84.36) --
-	(506.93, 83.64) --
-	(501.18, 82.64) --
-	(495.43, 82.42) --
-	(489.68, 76.41) --
-	(483.93, 77.92) --
-	(478.18, 75.82) --
-	cycle;
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line cap=rect,fill=fillColor,fill opacity=0.50] (1017.26,214.57) rectangle (1030.29,227.60);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
+\definecolor{drawColor}{RGB}{0,114,178}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (1017.99,221.09) -- (1029.56,221.09);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (460.93, 38.12) -- (644.93, 38.12);
-\definecolor{drawColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (478.18,127.94) --
-	(483.93,127.84) --
-	(489.68,122.64) --
-	(495.43,125.45) --
-	(501.18,129.15) --
-	(506.93,128.97) --
-	(512.68,130.66) --
-	(518.43,125.72) --
-	(524.18, 87.52) --
-	(529.93, 82.25) --
-	(535.68, 80.72) --
-	(541.43, 74.16) --
-	(547.18, 73.09) --
-	(552.93, 67.65) --
-	(558.68, 65.54) --
-	(564.43, 64.88) --
-	(570.18, 61.54) --
-	(575.93, 59.17) --
-	(581.68, 56.95) --
-	(587.43, 55.38) --
-	(593.18, 54.56) --
-	(598.93, 53.59) --
-	(604.68, 52.65) --
-	(610.43, 52.34) --
-	(616.18, 52.19) --
-	(621.93, 52.07) --
-	(627.68, 52.07) --
-	(633.43, 51.94) --
-	(639.18, 51.94) --
-	(644.93, 51.46);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (478.18, 97.05) --
-	(483.93, 96.63) --
-	(489.68, 94.07) --
-	(495.43, 95.65) --
-	(501.18, 97.81) --
-	(506.93, 97.47) --
-	(512.68, 98.36) --
-	(518.43, 95.36) --
-	(524.18, 73.48) --
-	(529.93, 69.78) --
-	(535.68, 68.56) --
-	(541.43, 64.35) --
-	(547.18, 63.49) --
-	(552.93, 60.05) --
-	(558.68, 58.57) --
-	(564.43, 58.06) --
-	(570.18, 55.78) --
-	(575.93, 54.18) --
-	(581.68, 52.66) --
-	(587.43, 51.66) --
-	(593.18, 51.10) --
-	(598.93, 50.42) --
-	(604.68, 49.74) --
-	(610.43, 49.50) --
-	(616.18, 49.38) --
-	(621.93, 49.29) --
-	(627.68, 49.29) --
-	(633.43, 49.20) --
-	(639.18, 49.20) --
-	(644.93, 48.92);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (460.93, 30.69) rectangle (644.93,194.15);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98, 35.09) {1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98, 71.15) {2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98,107.22) {3};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98,143.29) {4};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.98,179.35) {5};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18, 38.12) --
-	(460.93, 38.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18, 74.18) --
-	(460.93, 74.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18,110.25) --
-	(460.93,110.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18,146.32) --
-	(460.93,146.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (458.18,182.38) --
-	(460.93,182.38);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (478.18, 27.94) --
-	(478.18, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (535.68, 27.94) --
-	(535.68, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.18, 27.94) --
-	(593.18, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (478.18, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (535.68, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (593.18, 19.68) {20};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (1036.50,232.51) {6 day doubling period};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (552.93,  7.64) {Time (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (1036.50,218.05) {8 day doubling period};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (1156.32,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (446.70,112.42) {Basic reproduction number $\mathcal R_0$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (528.28,146.93) rectangle (643.82,192.34);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (533.78,166.88) rectangle (548.24,181.34);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{RGB}{240,228,66}
-\definecolor{fillColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor,fill opacity=0.50] (534.49,167.59) rectangle (547.53,180.63);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (535.23,174.11) -- (546.79,174.11);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (533.78,152.43) rectangle (548.24,166.88);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{RGB}{0,114,178}
-\definecolor{fillColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line cap=rect,fill=fillColor,fill opacity=0.50] (534.49,153.14) rectangle (547.53,166.17);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (535.23,159.66) -- (546.79,159.66);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (553.74,171.08) {6 day doubling period};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (553.74,156.63) {8 day doubling period};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (460.93,202.22) {C. Cohort-averaged estimates};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (894.55,274.49) {D. Cohort-averaged $\mathcal R_0$ estimates};
 \end{scope}

### 2020-09-15 serial_analysis.R

@@ -11,11 +11,20 @@ nboot <- 200
 r1 <- log(2)/8
 r2 <- log(2)/6
 
+## day 12 corresponds to 2020-01-22
+## figured out based on https://github.com/MeyersLabUTexas/COVID-19/blob/master/Table%20S5%20medrxiv.xlsx
+
 rr <- read_xlsx("Table S5.xlsx", skip=1) %>%
   mutate(
     cohort=`Index - symptom onset date`,
+    cohort2=`Seconday - symptom onset date`,
     serial=`Seconday - symptom onset date`- `Index - symptom onset date`
   )
+
+date_range <- range(c(rr$`Index - symptom onset date`, rr$`Seconday - symptom onset date`))
+
+date_numeric <- seq(date_range[1], date_range[2], by=1)
+date_actual <- as.Date("2020-01-22") + date_numeric - 12
 
 rr_summ <- rr %>%
   group_by(cohort) %>%
@@ -23,6 +32,9 @@ rr_summ <- rr %>%
     mean=mean(serial),
     lwr=quantile(serial, 0.025),
     upr=quantile(serial, 0.975)
+  ) %>%
+  mutate(
+    cohort=date_actual[match(cohort, date_numeric)]
   )
 
 rr_summ2 <- rr %>%
@@ -32,6 +44,9 @@ rr_summ2 <- rr %>%
     mean=mean(serial),
     lwr=quantile(serial, 0.025),
     upr=quantile(serial, 0.975)
+  ) %>%
+  mutate(
+    cohort=date_actual[match(cohort, date_numeric)]
   )
 
 tcut <- seq(0, 29, by=1)
@@ -84,32 +99,51 @@ serdata2 <- lapply(tcut, function(x) {
 
 serall <- bind_rows(serdata1, serdata2)
 
+ww <- duplicated(c(rr$`Index ID`, rr$`Secondary ID`))
+
+dd <- c(rr$`Index - symptom onset date`, rr$`Seconday - symptom onset date`)[!ww]
+
+sdate <- data.frame(
+  date=date_actual[match(dd, date_numeric)]
+)
+
+g1 <- ggplot(sdate) +
+  geom_bar(aes(date)) +
+  scale_x_date("Symptom onset date", expand=c(0, 0)) +
+  scale_y_continuous("Number of cases with a known infector/infectee pair", expand=c(0, 0), limits=c(0, 69)) +
+  ggtitle("A. Epidemic curve") +
+  theme(
+    panel.grid = element_blank()
+  )
[…]

### 2020-09-15 serial.tex
update

@@
 Here, we show that the initial \emph{forward} serial-interval distribution --- measured from the cohort of infectors who developed symptoms during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
-In general, the forward serial-interval distributions will not match the intrinsic or the backward serial-interval distributions.
-In particular, the mean forward serial interval can decrease over time due to epidemic dynamics. 
+In general, the forward serial-interval distributions will not match the intrinsic serial-interval distribution (which has the same mean as the intrinsic generation-interval distribution) because the incubation period of the infectors (conditional on their symptom onset date of the infector) will be subject to backward biases.
+In particular, the mean forward serial interval can decrease over time for COVID-19 as individuals who develop symptoms later are more likely to have longer incubation periods, and therefore have greater opportunity to transmit presymptomatically.
 Failing to account for these effects can result in underestimation of \RR.
 
-Our study underlines the importance of carefully defining measured epidemiological time distributions.
+Recently, \cite{ali2020serial} also showed that serial intervals of COVID-19 decreased in China.
+
+Our study underlines the importance of carefully defining measured epidemiological time distributions in general.
 Previous studies have shown that it matters whether generation
@@
 we generalize these ideas and show that they apply to other epidemiological distributions.
+Some studies during the early phases of the COVID-19 epidemics
+
 Changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.

### 2020-09-16 serial.tex
almost there

@@
 Recently, \cite{ali2020serial} also showed that serial intervals of COVID-19 decreased in China.
+Analogous to our apporach, they also grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean serial interval decreased from 7.8 days to 2.6 days.
+They attributed the decrease in serial intervals to reduction of the isolation delay period and showed that isolation delays can explain 51.5\% of the variation in serial intervals through a regression analysis.
 
-Our study underlines the importance of carefully defining measured epidemiological time distributions in general.
+More broadly, our study underlines the importance of carefully defining measured epidemiological time distributions.
 Previous studies have shown that it matters whether generation

### 2020-09-19 response.tex
almost

@@
 
-The special version is only presented in the supplementary material. We do not assume this in the main text. We have made this distinction clear:
+Thank you for pointing this out. The special version is only presented in the supplementary material. We do not assume this in the main text. We have made this distinction clear:
 
@@
 
-Figure 2 further shows that the initial forward serial-interval distribution is different from the intrinsic generation-interval distribution but gives identical \Ro estimates given $r$.
+Figure 2 further shows that the initial forward serial-interval distribution is different from the intrinsic generation-interval distribution but gives identical \Ro estimates given $r$ using parameter estimates for COVID-19.
 
@@
 It is about both.
-Generation and serial intervals are key quantities in describing epidemic dynamics; their differences have long been misunderstood.
+Generation and serial intervals are key quantities in describing epidemic dynamics; their differences have long been misunderstood and our paper provides a theoretical basis for linking them properly.
 These intervals also play critical role in estimating the reproduction number.
-We have made major revisions to the writing of the manuscript to provide a transparent and coherent story.
+We have made major revisions to the writing of the manuscript based on the suggestions to provide a transparent and coherent story.
 
@@
 
+We have added the following limiations of the reproduction number:
+
+``Since the reproduction number represents an average \citep{diekmann1990definition, anderson1991infectious}, it does not capture heterogeneity among individuals or across space.
+The reproduction number also does not provide any information about the time scale of disease transmission.''
+
 \revtext{The introduction presents previous methodological work on the R-r relationship based on generation and serial intervals and recent applications that confuse the two intervals.
@@
 My suggestion for a stronger introduction: A funnel focusing on the methods that ends with the knowledge gap "In contexts where the distributions are expected to be different, current theory has no explanation for how these differing distributions could provide identical estimates of R from r" (and further specified by the gaps indicated at the end of section 2.1 and beginning of section 2.2) followed by concrete examples of how off R estimates are in applications to substantiate the problem.}
+
+We have rewritten a large proportion of the introduction section based on these suggestions.
 

### 2020-09-19 serial.tex
almost

@@
 Analogous to our apporach, they also grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean serial interval decreased from 7.8 days to 2.6 days.
-They attributed the decrease in serial intervals to reduction of the isolation delay period and showed that isolation delays can explain 51.5\% of the variation in serial intervals through a regression analysis.
+They attributed the decrease in serial intervals to reduction of the isolation delay; however, their regression analysis shows that isolation delays explain only 51.5\% of the variation in serial intervals (and explaining up to 72\% of the variance including other intervention measures).
+Our framework provides an explanation for the remaining variation: changes in the backward incubation period during the decreasing phase of an epidemic also shorten serial intervals (even in the absence of nonpharmaceutical interventions).
+Since isolation delays and other intervention measures affect the amount of onward transmission, and therefore the distribution of realize (forward) generation intervals, it cannot explain all variation in forward serial intervals, which depend on (i) backward incubation period of the infector, (ii) the forward generation interval, and (iii) the forward incubation period of the infectee (\fref{diagram}B).
+
+Here, we lay out a few practical principles for analyzing the serial interval data.
+First, serial intervals should be cohorted based on the symptom onset date whenever possible.
+Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval, but their distributions are expected to change due to epidemic dynamics \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
+Even when all realzied serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR})---something true of realzied generation intervals as well \citep{park2020inferring}.
+Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases.
+Often, the amount serial interval data can be limited due to difficulties in collecting them and the aggregation cannot be avoided; in these situations, the aggregated serial-interval distributions should be interpreted with care, providing an order-of-magnitude estimates for the time scale of disease transmission.
+Finally, these biases should be explicitly taken into account when inferring other epidemiological parameters (e.g., the amount of presymptomatic transmission) from serial interval data.
 
@@
 intervals are measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
-we generalize these ideas and show that they apply to other epidemiological distributions.
-Some studies during the early phases of the COVID-19 epidemics
+we generalize these ideas and show that they apply to any other epidemiological distributions.
+Some studies during the early phases of the COVID-19 epidemics have tried to correct for the backward biases, but changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
+Cohorting epidemiological delays by the primary event time can help avoid backward biases (although censoring biases can still exist) as well as detect potential changes in the distribution.
 
-Changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
-Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series from by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential,scire2020reproductive,shim2020transmission});
-these studies effectively assume constant backward delay distributions.
-Although such approaches may be able to roughly match the time scale of an epidemic, we show here that they are subject to bias.
-Dynamical approaches that model explicitly model incidence as well as reporting delays (e.g., \cite{flaxman2020estimating}) can avoid this problem, but at the cost of more complexity in estimation.
-There is a need for simple methods that can complement more explicit approaches of addressing this problem.
+While our results support the use of serial-interval distributions for calculating the initial \RR during the exponential growth phase,  
+they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
 
-While our results support the use of serial-interval distributions for calculating \RR, 
-they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
 For example, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
@@
 Individual-level interventions, such as case isolation, and behavioral responses directly affect individuals' ability to transmit and will shorten the forward generation- and serial-intervals.
-Population-level interventions, such as social distancing, can squeeze contacts into household and induce clustering, which will in turn shorten the realized generation interval due to local depletion of the susceptible pool within households \citep{park2019inferring}.
+Population-level interventions, such as social distancing, can squeeze contacts into household and induce clustering, which will in turn shorten the realized generation interval due to local depletion of the susceptible pool within households \citep{park2020inferring}.
 
@@
 
-We run stochastic simulations of the renewal equation model using an individual-based model on a fully connected network (i.e., homogeneous population) based on the Gillespie algorithm that we developed earlier \citep{park2019inferring}.
+We run stochastic simulations of the renewal equation model using an individual-based model on a fully connected network (i.e., homogeneous population) based on the Gillespie algorithm that we developed earlier \citep{park2020inferring}.
 First, we initialize an epidemic with $I(0)$ infected individuals (nodes) in a fully connected network of size $N$. 

### 2020-09-20 response.tex
updae

@@
 
+We have added the following sentence:
+
+``The lack of distinction is apparent even in standard softwares for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.''
+
 \revtext{The abstract states that "recent studies suggest that the two intervals give different estimates of R from r" and "our analysis shows that using incorrectly defined serial intervals can severely bias estimates" Exemplify by numbers to substantiate the severity.}
@@
 
+\swp{?????}
+
 \revtext{Section 3.3 provides one example of a biased R estimate.
@@
 I think "these studies should also re-assess whether they appropriately considered the forward serial interval" is weak.}
+
+We think that it is important to emphasize that nont distinguishing generation and serial intervals is a commonly made mistake in the field. 
+However, we agree that our critique is weak.
+We have tried to remove any unfair accusations from the paper (but still provide a few examples to illustrate that this is a common practice without accusing those papers).
 

### 2020-09-20 serial.tex
updae

@@
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds.
-Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19, either without making a clear distinction \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}, or explicitly conflating the two intervals
-\citep{anderson2020will,hellewell2020feasibility}.
+Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19 without making a clear distinction (e.g., \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}), and explicitly conflate the definitions of two intervals (e.g., \citep{anderson2020will,hellewell2020feasibility}).
+The lack of distinction is apparent even in standard softwares for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
+However, these studies should not be accused of their practices; until now, it has been a common practice use serial and generation intervals interchangeably.
 
@@
 Generation and serial intervals determine the time scale of disease transmission, and are therefore critical to dynamical modeling of infectious outbreaks.
-Here, we show that the initial \emph{forward} serial-interval distribution --- measured from the cohort of infectors who developed symptoms during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the reproduction number \RR.
+Here, we show that the initial \emph{forward} serial-interval distribution --- measured from the cohort of infectors who developed symptoms during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the initial reproduction number \RR.
 In general, the forward serial-interval distributions will not match the intrinsic serial-interval distribution (which has the same mean as the intrinsic generation-interval distribution) because the incubation period of the infectors (conditional on their symptom onset date of the infector) will be subject to backward biases.
-In particular, the mean forward serial interval can decrease over time for COVID-19 as individuals who develop symptoms later are more likely to have longer incubation periods, and therefore have greater opportunity to transmit presymptomatically.
-Failing to account for these effects can result in underestimation of \RR.
+In particular, the mean forward serial interval can decrease over time for COVID-19 as individuals who develop symptoms later in an epidemic are more likely to have longer incubation periods, and therefore have greater opportunity to transmit presymptomatically.
+Failing to account for these effects can result in underestimation of initial \RR.
 
 Recently, \cite{ali2020serial} also showed that serial intervals of COVID-19 decreased in China.
-Analogous to our apporach, they also grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean serial interval decreased from 7.8 days to 2.6 days.
-They attributed the decrease in serial intervals to reduction of the isolation delay; however, their regression analysis shows that isolation delays explain only 51.5\% of the variation in serial intervals (and explaining up to 72\% of the variance including other intervention measures).
-Our framework provides an explanation for the remaining variation: changes in the backward incubation period during the decreasing phase of an epidemic also shorten serial intervals (even in the absence of nonpharmaceutical interventions).
+Analogous to our apporach, they also grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean forward serial interval decreased from 7.8 days to 2.6 days.
+While they attributed the decrease in serial intervals to reduction of the isolation delay, their regression analysis showed that isolation delays explain only 51.5\% of the variation in serial intervals (and explaining up to 72\% of the variance including other intervention measures).
+Our framework provides an explanation for the remaining variation: changes in the backward incubation period during the decreasing phase of an epidemic also shorten serial intervals due to increased amount of presymptomatic transmission (even in the absence of nonpharmaceutical interventions).
 Since isolation delays and other intervention measures affect the amount of onward transmission, and therefore the distribution of realize (forward) generation intervals, it cannot explain all variation in forward serial intervals, which depend on (i) backward incubation period of the infector, (ii) the forward generation interval, and (iii) the forward incubation period of the infectee (\fref{diagram}B).
+
+Our results support the use of serial-interval distributions for calculating the initial \RR during the exponential growth phase,  
+but they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
+For example, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
+However, our results show that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can, in fact, exacerbate the underestimation of initial \RR.
+Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase and potentially re-assess existing estimates of \RR.
+We also suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions and understand their changes over time.
+These modeling approaches should be coupled with epidemiological investigation through contact tracing. 
+Going forward, an additional advantage of early, intensive contact tracing of emerging diseases is that this is the best way to characterize the initial forward serial-interval distribution.
+
+Our study also underlines the fact that the serial-interval distribution depends not only on the generation-interval and incubation-period distributions, but also on their intrinsic correlations.
+Here, we use a bivariate lognormal distribution to capture their correlations phenomenologically but their true correlations will depend on viral load dynamics;
+nonetheless, we expect our conclusions about decreasing serial intervals of COVID-19 to be robust as individuals with longer incubation periods have longer time window to transmit before symptom onset.
+Otherwise, the impact of increasing backward incubation periods on the forward serial intervals are likely to be disease specific---for example, we show in Supplementary Materials that the initial forward serial-interval distribution can be equivalent to the intrinsic generation-interval distribution, regardless of the growth rate $r$, due to independence between the incubation period and time from symptom onset to transmission (assuming no transmission occurs during the incubation period).
+This implies that not considering this correlation can potentially bias the estimates of the intrinsic generation-interval distribution from the serial-interval distribution.
+% Previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the dynamical differences between the realized incubation periods of infectors (backward-looking) and those of infectees (forward looking) (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
+Better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals are needed.
 
@@
 Cohorting epidemiological delays by the primary event time can help avoid backward biases (although censoring biases can still exist) as well as detect potential changes in the distribution.
-
-While our results support the use of serial-interval distributions for calculating the initial \RR during the exponential growth phase,  
-they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
-
-For example, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
-However, our results show that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can, in fact, exacerbate the underestimation of initial \RR.
-Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase and potentially re-assess existing estimates of \RR.
-
-Many studies have already estimated the (time-varying) reproduction numbers for COVID-19 epidemics using aggregated serial-interval data (e.g., \cite{tempvar,du2020serial,pan2020jama,zhang2020evolving});
-these studies should also re-assess whether they appropriately considered the \emph{forward} serial interval.
-Forward serial-interval distributions are also likely to vary across countries.
-We suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions and understand their changes over time.
-These modeling approaches should be coupled with epidemiological investigation through contact tracing. 
-Going forward, an additional advantage of early, intensive contact tracing of emerging diseases is that this is the best way to characterize the initial forward serial-interval distribution.
-
-Our study also underlines the fact that the serial-interval distribution depends not only on the generation-interval and incubation-period distributions, but also on their intrinsic correlations.
-This implies that not considering this correlation can bias the estimates of the intrinsic generation-interval distribution from the serial-interval distribution.
-Previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the dynamical differences between the realized incubation periods of infectors (backward-looking) and those of infectees (forward looking) (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
-Better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals are needed.
 

### 2020-09-20 serial.tex
more

@@
 In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean, assuming that the incubation periods of the infector and infectee are identically distributed \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
-Serial intervals can also take negative values due to presymptomatic transmission \citep{he2020temporal}, whereas generation intervals are confinsed to positive values.
+Serial intervals can also take negative values due to presymptomatic transmission \citep{he2020temporal}, whereas generation intervals are confined to positive values.
 
@@
 Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19 without making a clear distinction (e.g., \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}), and explicitly conflate the definitions of two intervals (e.g., \citep{anderson2020will,hellewell2020feasibility}).
-The lack of distinction is apparent even in standard softwares for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
+The lack of distinction is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
 However, these studies should not be accused of their practices; until now, it has been a common practice use serial and generation intervals interchangeably.
@@
 We set the distribution of infection time of initially infected individuals (beginning from a small number of infected individuals) for deterministic simulations such that the system can exhibit exponential growth immediately (Supplementary Materials).
-This is not possible for stochastic simulations because the number of initially infected individuals cannot be smaller than 1; instead, we begin with 10 infected indiivduals who are infected at time $t=0$.
+This is not possible for stochastic simulations because the number of initially infected individuals cannot be smaller than 1; instead, we begin with 10 infected individuals who are infected at time $t=0$.
 In addition, the mean backward intervals of stochastic simulations begins from smaller values due to left-censoring.
@@
 1 in \citep{pan2020jama}).
-In order to quantify changes in serial intervals, we group them by the symptom onset dates of the primary (\fref{du}B) and secondary (\fref{du}C) cases---correspoding to forward and backward serial-interval distributions, respectively---and compute their mean and 95\% quantiles.
+In order to quantify changes in serial intervals, we group them by the symptom onset dates of the primary (\fref{du}B) and secondary (\fref{du}C) cases---corresponding to forward and backward serial-interval distributions, respectively---and compute their mean and 95\% quantiles.
 \fref{du}B shows that the mean forward serial interval decreases over time.
@@
 Recently, \cite{ali2020serial} also showed that serial intervals of COVID-19 decreased in China.
-Analogous to our apporach, they also grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean forward serial interval decreased from 7.8 days to 2.6 days.
+Analogous to our approach, they also grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean forward serial interval decreased from 7.8 days to 2.6 days.
 While they attributed the decrease in serial intervals to reduction of the isolation delay, their regression analysis showed that isolation delays explain only 51.5\% of the variation in serial intervals (and explaining up to 72\% of the variance including other intervention measures).
@@
 
-Here, we lay out a few practical principles for analyzing the serial interval data.
+Here, we lay out a few practical principles for analyzing and interpreting the serial interval data.
 First, serial intervals should be cohorted based on the symptom onset date whenever possible.
 Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval, but their distributions are expected to change due to epidemic dynamics \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
-Even when all realzied serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR})---something true of realzied generation intervals as well \citep{park2020inferring}.
+Even when all realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR})---something true of realized generation intervals as well \citep{park2020inferring}.
 Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases.
@@
 neglecting the time scale asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
-
-While we focus here on the effect of epidemiological dynamics on serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
-Individual-level interventions, such as case isolation, and behavioral responses directly affect individuals' ability to transmit and will shorten the forward generation- and serial-intervals.
-Population-level interventions, such as social distancing, can squeeze contacts into household and induce clustering, which will in turn shorten the realized generation interval due to local depletion of the susceptible pool within households \citep{park2020inferring}.
 

### 2020-09-20 response.tex
done now?

@@
 
-Thank you for pointing this out. The special version is only presented in the supplementary material. We do not assume this in the main text. We have made this distinction clear:
+Thank you for pointing this out. The special version is only presented in the supplementary material. We do not assume this in the main text. We have now made this distinction clear in the text:
 
@@
 Figure 2 further shows that the initial forward serial-interval distribution is different from the intrinsic generation-interval distribution but gives identical \Ro estimates given $r$ using parameter estimates for COVID-19.
+We also show that the main result (initial forward serial-interval distribution provides the same link as the intrinsic generation-interval distribution) hold in general and provide a mathematical proof for it.
+But we acknowledge that changes in serial intervals throughout the epidemic and their exact shape depends on the joint distribution of intrinsic generation intervals and incubation periods.
 
 \revtext{Regarding my main concern above I note that you write "should" on p3, line 91, and "expect" on p 10, line 273.
-I don't see any proof for the statement to hold in general and am not sure the statement is even true in general.
-}
+I don't see any proof for the statement to hold in general and am not sure the statement is even true in general.}
 
@@
 
+Done.
+
 \revtext{p5, middle: emphasize that s and p are calendar times whereas $\tau$ is a duration }
@@
 
-``For example, shorter generation intervals are more likely to be realized later in the \emph{epidemic} (therefore, leading to ``contraction'' of generation intervals) because infected individuals are less likely to infect others later in their \emph{infection} due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.''
+``For example, infected individuals can become less likely to infect others during late stages of their infection as the epidemic progresses (therefore, leading to ``contraction'' of generation intervals) due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.''
 
@@
 
-``Thus, as the growth rate $r$ of an epidemic increases, the mean backward delay distribution will decrease, leading to stronger bias.''
+``Thus, even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), assuming all else being equal.''
 
@@
 
+We have revised the abstract according to previous suggestions and have added the following sentence to substantiate the severity: ``our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by up to 50\%--60\%.''
+
 \revtext{Same vagueness at the end of the introduction: "Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of R." By how much?}
+
+Done:
+
+``For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro esimates based on aggregated serial interval data underestimated \Ro by 50\%--60\%.''
 
@@
 Instead, we recommend analyzing serial intervals through a cohort-based perspective.
-We have now added a paragraph in the discussion section, summarizing and providing practical guidance.
+We have now added a paragraph in the discussion section, summarizing and providing practical guidance:
+
+``Here, we lay out a few practical principles for analyzing and interpreting the serial interval data.
+First, serial intervals should be cohorted based on the symptom onset date whenever possible.
+Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but their distributions are expected to change due to epidemic dynamics.
+Even when all realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR})---something true of realized generation intervals as well \citep{park2020inferring}.
+Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases.
+Third, applying serial interval information from one epidemic to another should be avoided, even for same diseases, because serial intervals are epidemic-specific, rather than disease-specific.
+Finally, serial interval data should be accompanied by a trajectory of the epidemic curve, whenever possible, to properly assess them within the epidemiological context.
+In practice, these recommendations can be still difficult to follow due to limited serial interval information;
+nonetheless, we believe that following these approaches will help interpret serial interval data and understand transmission dynamics at the individual-level.''
 

### 2020-09-20 serial.tex
done now?

@@
 
-\dropcap{G}eneration intervals and serial intervals are critical quantities for characterizing outbreak dynamics.
-Generation intervals characterize the time between infection and transmission, while serial intervals characterize the time between the onset of symptoms in a chain of transmission.
-They are often used interchangeably, leading to misunderstanding of how these intervals link the epidemic growth rate $r$ and the reproduction number \RR.
-Generation intervals provide a mechanistic link between $r$ and \RR but are harder to measure via contact tracing.
+The reproduction number \RR and the exponential growth rate $r$ are critical quantities for characterizing outbreak dynamics.
+These quantities are linked by generation intervals---defined as the time between infection and transmission.
+Because generation intervals are difficult to measure directly, they are often substituted with serial intervals---defined as the onset of symptoms in a chain of transmission.
 While serial intervals are easier to measure from contact tracing, recent studies suggest that the two intervals give different estimates of \RR from $r$.
 We present a general framework for characterizing epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly link \RR with $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
-We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial-interval data --- our analysis shows that using incorrectly defined serial intervals can severely bias estimates.
+We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial-interval data --- our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by up to 50\%--60\%.
 This study demonstrates the importance of early epidemiological investigation through contact tracing and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
@@
 Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of \RR.
-We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the initial reproduction number during the early stages of an outbreak.
+For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro esimates based on aggregated serial interval data underestimated \Ro by 50\%--60\%.
+We further lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the initial reproduction number during the early stages of an outbreak.
 
@@
 Likewise, the intrinsic generation-interval distribution describes the expected time distribution of infectious contacts made by an infected individual.
-However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., the distribution of time between actual primary and secondary events that occur during an epidemic).
+However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., the distribution of time between actual primary and secondary events that occur during an epidemic; see \fref{diagram}).
 For example, an infectious contact results in infection only if the contacted individual is susceptible (and has not already been infected);
@@
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics.
-For example, shorter generation intervals are more likely to be realized later in the \emph{epidemic} (therefore, leading to ``contraction'' of generation intervals) because infected individuals are less likely to infect others later in their \emph{infection} due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.
+For example, infected individuals can become less likely to infect others during late stages of their infection as the epidemic progresses (therefore, leading to ``contraction'' of generation intervals) due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.
 
@@
 where $r$ is the exponential growth rate (and $\left[W(0) \psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
-Thus, as the growth rate $r$ of an epidemic increases, the mean backward delay distribution will decrease, leading to stronger bias.
+Thus, even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), assuming all else being equal.
 In general, the backward delay distribution will differ from the forward delay distribution (unless the disease is at equilibrium), even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
@@
 These early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
-Therefore, the \Ro estimate of 1.32 (95\% CI 1.16–1.48), which neglects the changes in the forward serial-interval distribution, is likely to be an underestimate.
+Therefore, the original \Ro estimate of 1.32 (95\% CI 1.16-–1.48), which neglects the changes in the forward serial-interval distribution, underestimates \Ro by 50\%--60\%.
 This example demonstrates the danger of using the observed serial intervals to calculate the reproduction number without organizing serial intervals into cohorts.
@@
 First, serial intervals should be cohorted based on the symptom onset date whenever possible.
-Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval, but their distributions are expected to change due to epidemic dynamics \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
+Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but their distributions are expected to change due to epidemic dynamics.
 Even when all realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR})---something true of realized generation intervals as well \citep{park2020inferring}.
 Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases.
-Often, the amount serial interval data can be limited due to difficulties in collecting them and the aggregation cannot be avoided; in these situations, the aggregated serial-interval distributions should be interpreted with care, providing an order-of-magnitude estimates for the time scale of disease transmission.
-Finally, these biases should be explicitly taken into account when inferring other epidemiological parameters (e.g., the amount of presymptomatic transmission) from serial interval data.
+Third, applying serial interval information from one epidemic to another should be avoided, even for same diseases, because serial intervals are epidemic-specific, rather than disease-specific.
+Finally, serial interval data should be accompanied by a trajectory of the epidemic curve, whenever possible, to properly assess them within the epidemiological context.
+In practice, these recommendations can be still difficult to follow due to limited serial interval information;
+nonetheless, we believe that following these approaches will help interpret serial interval data and understand transmission dynamics at the individual-level.
 

### 2020-09-20 serial.tex
basically done

@@
 While serial intervals are easier to measure from contact tracing, recent studies suggest that the two intervals give different estimates of \RR from $r$.
-We present a general framework for characterizing epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly link \RR with $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
+We present a general framework for characterizing epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly link \RR with $r$, are not the same as \emph{intrinsic} serial intervals (defined by averaging across individual-level characteristics while neglecting population-level dynamics), but instead change with $r$.
 We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial-interval data --- our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by up to 50\%--60\%.
@@
 however, both intervals, by definition, describe disease transmission at the individual level.
-Here, we show that the serial-interval distribution, defined from the correct reference time and cohort, gives the same estimate of \RR as the generation-interval distribution.
+Here, we show that the serial-interval distribution, defined from the correct reference time and cohort, gives the same estimate of \RR as the generation-interval distribution from $r$.
 We then apply our framework to serial-interval data from the COVID-19 outbreak in China.
@@
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds.
-Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19 without making a clear distinction (e.g., \citep{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}), and explicitly conflate the definitions of two intervals (e.g., \citep{anderson2020will,hellewell2020feasibility}).
+Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19 without making a clear distinction (e.g., \cite{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}), and explicitly conflate the definitions of two intervals (e.g., \cite{anderson2020will,hellewell2020feasibility}).
 The lack of distinction is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
-However, these studies should not be accused of their practices; until now, it has been a common practice use serial and generation intervals interchangeably.
+However, these studies are not meant to be accused of their practices; until now, it has been a common practice use serial and generation intervals interchangeably.
 
-One source of confusion arises from an apparent discrepancy between the serial-interval and generation-interval viewpoints.
+One source of confusion arises from an apparent discrepancy between the generation-interval and serial-interval viewpoints.
 When the epidemic is growing exponentially, the spread of infection can be characterized as a \emph{renewal process} based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
@@
 However, these studies rely on imprecise definitions of the serial-interval distribution, relying on \emph{intrinsic} distributions of incubation periods and generation intervals that neglect the population-level dynamics of the disease spread.
-During an ongoing epidemic, \emph{all} observed epidemiological delays between primary and secondary events (e.g., infection and symptom onset) are subject to backward biases: when incidence of primary events is increasing (or decreasing), we are more likely to observe shorter (or longer) intervals.
-Since serial intervals depend on three distinct intervals (i.e., incubation period of the infector, incubation period of the infectee, and the generation interval between them), any of these intervals can be subject to backward biases depending on our perspective.
-Therefore, it is not always safe to assume that the incubation periods of the infector and the infectee are drawn from the same distribution.
+During an ongoing epidemic, \emph{all} observed epidemiological delays (e.g., incubation period) between primary (e.g., infection) and secondary (e.g., symptom onset) events are subject to backward biases: when the incidence of primary events is increasing (or decreasing), we are more likely to observe shorter (or longer) intervals.
+Since realized serial intervals depend on three distinct intervals (i.e., incubation period of the infector, incubation period of the infectee, and the generation interval between them), any of these intervals can be subject to backward biases depending on our perspective.
+For example, when we consider ``forward'' serial-interval distributions (i.e., serial intervals from a cohort of infectors that developed symptoms at the same time), the incubation periods of the infectors are subject to backward biases because we have to look backward in time from their symptom onset to infection.
+Therefore, the realized incubation period distributions of the infector and the infectee can differ dynamically, even if they are expected to be equivalent intrinsically.
 
-Here, we resolve this apparent discrepancy by showing that the relevant interval for the renewal framework is what is called the ``forward'' interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
+Here, we resolve the apparent discrepancy between generation-interval and serial-interval viewpoints by showing that the relevant interval for the renewal framework is the forward interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
 We develop a cohort-based framework for characterizing and comparing serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
 Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of \RR.
-For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro esimates based on aggregated serial interval data underestimated \Ro by 50\%--60\%.
+For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro estimates based on aggregated serial interval data underestimated \Ro by 50\%--60\%.
 We further lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the initial reproduction number during the early stages of an outbreak.
@@
 the primary event refers to the event that occurs in the infector. 
-Again, some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to develop symptoms before the infector \citep{he2020temporal}).
+Again, some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to develop symptoms before the infector).
 
@@
 Similarly, when we are measuring serial intervals, a primary cohort consists of all infectors who became symptomatic at time $\psymp$.
-Then, for a primary cohort at time $\psymp$, we can define the expected time distribution between primary and secondary events. 
+Then, for a primary cohort at time $\psymp$, we can define the distribution of realized delays between primary and secondary events. 
 We refer to this distribution as the forward delay distribution and denote it as $f_\psymp(\tau)$.
@@
 
-We see that the denominator of the forward serial-interval distribution, $\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'$, then corresponds to the total number of symptomatic cases generated by primary cases who themselves developed symptoms at time \psymp\ (\eref{fserial}).
+We see that the denominator of the forward serial-interval distribution, $\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'$, then corresponds to the total number of infections generated by primary cases who themselves developed symptoms at time \psymp\ (\eref{fserial}).
 Dividing this quantity by the number of individuals who developed symptoms at time at time \psymp, $j(\psymp) = \int_{-\infty}^\infty \total(\psymp-\tau', \psymp) \dtau'$, we obtain the serial reproduction number:
@@
 \end{equation}
-which we define as the average number of symptomatic cases generated by individuals who developed symptoms at time \psymp.
+which we define as the average number of infections generated by an individual who developed symptoms at time \psymp.
 Combining the forward serial-interval distribution with the serial reproduction number completes the renewal process between symptomatic cases:
@@
 
-We use parameter estimates for COVID-19 to characterize the degree to which the realized serial-interval distribution can change over the course of the epidemic and evaluate how different definitions of the serial-interval distribution can affect the Euler-Lotka estimates of \Ro.
+We use parameter estimates for COVID-19 to characterize the degree to which the realized serial-interval distribution can change over the course of an epidemic and evaluate how different definitions of the serial-interval distribution can affect the Euler-Lotka estimates of \Ro.
 We further address how the observed serial intervals, measured through contact tracing, are affected by the right censoring during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial interval data to estimate \Ro.
@@
 
-\fref{rR} shows Euler-Lotka estimates of \Ro\ on different definitions of the serial interval. 
+\fref{rR} shows Euler-Lotka estimates of \Ro\ based on different definitions of the serial interval. 
 When the initial forward serial-interval distributions $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen}) for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
@@
 Stochastic simulations confirm our deterministic calculations albeit minor differences due to transient dynamics.
-Incidence trajectories of stochastic simulations are slightly shifted (\fref{epi}A) due to differences in initial conditions. 
-We set the distribution of infection time of initially infected individuals (beginning from a small number of infected individuals) for deterministic simulations such that the system can exhibit exponential growth immediately (Supplementary Materials).
+Incidence trajectories of stochastic simulations are slightly shifted to earlier time (\fref{epi}A) due to differences in initial conditions. 
+We set the distribution of infection time of initially infected individuals (beginning from a very small number of infected individuals, $<<1$) for deterministic simulations such that the system can exhibit exponential growth immediately (Supplementary Materials).
 This is not possible for stochastic simulations because the number of initially infected individuals cannot be smaller than 1; instead, we begin with 10 infected individuals who are infected at time $t=0$.
@@
 in fact, we would even underestimate the intrinsic value slightly due to contraction of the forward generation-interval distribution during the susceptible depletion phase (\fref{epi}C).
-Therefore, aggregated distributions of serial intervals that have been collected throughout different periods of an epidemic should be interpreted with care.
+Therefore, aggregated distributions of serial intervals that have been collected throughout different periods of an epidemic must be interpreted with care.
 
@@
 \begin{figure}[!th]
-\includegraphics[width=\textwidth]{serial_analysis.pdf}
+\begin{center}
+\includegraphics[width=0.85\textwidth]{serial_analysis.pdf}
 \caption{
 \textbf{Observed serial intervals of COVID-19 and cohort-averaged estimates of \RR.}
-(A) Symptom onset dates of all individuals within 468 transmission pairs in the data.
+(A) Symptom onset dates of all individuals within 468 transmission pairs included in the contact tracing data.
 (B--C) forward and backward serial intervals over time.
@@
 }
+\end{center}
 \label{fig:du}
@@
 Fig.
-1 in \citep{pan2020jama}).
+1 in \cite{pan2020jama}).
 In order to quantify changes in serial intervals, we group them by the symptom onset dates of the primary (\fref{du}B) and secondary (\fref{du}C) cases---corresponding to forward and backward serial-interval distributions, respectively---and compute their mean and 95\% quantiles.
@@
 
-\fref{du}D shows the cohort-averaged estimates of \Ro, which remain roughly constant until day 7 and suddenly decreases;
+\fref{du}D shows the cohort-averaged estimates of \Ro, which remain roughly constant until day January 17th and suddenly decreases;
 this sudden decrease is due changes in the forward serial intervals consistent with the dynamics seen in our simulations (\fref{obsrR}).
 The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, doi:10.1098/rsif.2020.0144}:
-$\Ro = 2.6$ (95\% CI: 2.2--3.1) and $\Ro = 3.4$ (95\% CI: 2.7 -- 4.3) based on a doubling period of 8 or 6 days, respectively, using serial-interval data from infectors who developed symptoms by day 7.
+$\Ro = 2.6$ (95\% CI: 2.2--3.1) and $\Ro = 3.4$ (95\% CI: 2.7 -- 4.3) based on a doubling period of 8 or 6 days, respectively, using serial-interval data from infectors who developed symptoms by January 17th.
 These early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).

### 2020-09-20 serial_analysis.R

@@ -181,11 +181,13 @@ g3 <- ggplot(rr) +
     legend.position = "none"
   )
 
+serall$date <- serall$t + as.Date("2020-01-22") - 12
+
 g4 <- ggplot(serall) +
-  geom_ribbon(aes(t, ymin=lwr, ymax=upr, fill=type, lty=type, col=type), alpha=0.5) +
+  geom_ribbon(aes(date, ymin=lwr, ymax=upr, fill=type, lty=type, col=type), alpha=0.5) +
   geom_hline(yintercept=1, lty=2) +
-  geom_line(aes(t, R0, col=type, lty=type)) +
-  scale_x_continuous("Time (days)", limits=c(-3, 29), expand=c(0, 0)) +
+  geom_line(aes(date, R0, col=type, lty=type)) +
+  scale_x_date("Symptom onset date (infector)", limits=as.Date(c("2020-01-07", "2020-02-08")), expand=c(0, 0)) +
   scale_y_continuous("Basic reproduction number $\\mathcal R_0$") +
   scale_color_manual(values=cpalette[5:6]) +
   scale_fill_manual(values=cpalette[5:6]) +
@@ -197,7 +199,7 @@ g4 <- ggplot(serall) +
     legend.title = element_blank()
   )
 
-tikz(file = "serial_analysis.tex", width = 16, height = 4, standAlone = T)
-grid.arrange(g1, g2, g3, g4, nrow=1)
+tikz(file = "serial_analysis.tex", width = 8, height = 8, standAlone = T)
+grid.arrange(g1, g2, g3, g4, nrow=2)
 dev.off()
 tools::texi2dvi('serial_analysis.tex', pdf = T, clean = T)

### 2020-09-20 serial_analysis.tex
forgot to commit

--- 2020-05-28 serial_analysis.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-05-27 22:31:58
+% Created by tikzDevice version 0.12.3 on 2020-09-20 18:46:20
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (867.24,289.08);
-\begin{scope}
-\path[clip] ( 10.17,  0.00) rectangle (278.91,289.08);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
+\begin{scope}
+\path[clip] (  0.00,289.08) rectangle (289.08,578.16);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 10.17,  0.00) rectangle (278.91,289.08);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,289.08) rectangle (289.08,578.16);
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.71,319.77) rectangle (283.58,555.50);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 44.82, 30.69) rectangle (273.41,266.42);
+\path[fill=fillColor] ( 31.71,319.77) rectangle (283.58,555.50);
+\definecolor{fillColor}{gray}{0.35}
+
+\path[fill=fillColor] ( 31.71,319.77) rectangle ( 38.40,323.18);
+
+\path[fill=fillColor] ( 46.57,319.77) rectangle ( 53.26,326.60);
+
+\path[fill=fillColor] ( 54.00,319.77) rectangle ( 60.69,330.02);
+
+\path[fill=fillColor] ( 61.43,319.77) rectangle ( 68.12,326.60);
+
+\path[fill=fillColor] ( 68.86,319.77) rectangle ( 75.55,330.02);
+
+\path[fill=fillColor] ( 76.29,319.77) rectangle ( 82.98,323.18);
+
+\path[fill=fillColor] ( 83.72,319.77) rectangle ( 90.41,326.60);
+
+\path[fill=fillColor] ( 91.15,319.77) rectangle ( 97.84,330.02);
+
+\path[fill=fillColor] ( 98.58,319.77) rectangle (105.27,326.60);
+
+\path[fill=fillColor] (106.01,319.77) rectangle (112.70,333.43);
+
+\path[fill=fillColor] (113.44,319.77) rectangle (120.13,374.43);
+
+\path[fill=fillColor] (120.87,319.77) rectangle (127.56,374.43);
+
+\path[fill=fillColor] (128.30,319.77) rectangle (134.99,381.26);
+
+\path[fill=fillColor] (135.73,319.77) rectangle (142.42,384.68);
+
+\path[fill=fillColor] (143.16,319.77) rectangle (149.84,439.34);
+
+\path[fill=fillColor] (150.59,319.77) rectangle (157.27,483.76);
+
+\path[fill=fillColor] (158.02,319.77) rectangle (164.70,494.01);
+
+\path[fill=fillColor] (165.45,319.77) rectangle (172.13,487.17);
+
+\path[fill=fillColor] (172.88,319.77) rectangle (179.56,507.67);
+
+\path[fill=fillColor] (180.31,319.77) rectangle (186.99,535.00);
+
+\path[fill=fillColor] (187.74,319.77) rectangle (194.42,545.25);
+
+\path[fill=fillColor] (195.17,319.77) rectangle (201.85,487.17);
+
+\path[fill=fillColor] (202.60,319.77) rectangle (209.28,476.92);
+
+\path[fill=fillColor] (210.03,319.77) rectangle (216.71,480.34);
+
+\path[fill=fillColor] (217.46,319.77) rectangle (224.14,466.67);
+
+\path[fill=fillColor] (224.89,319.77) rectangle (231.57,425.68);
+
+\path[fill=fillColor] (232.31,319.77) rectangle (239.00,405.18);
+
+\path[fill=fillColor] (239.74,319.77) rectangle (246.43,391.51);
+
+\path[fill=fillColor] (247.17,319.77) rectangle (253.86,364.18);
+
+\path[fill=fillColor] (254.60,319.77) rectangle (261.29,350.51);
+
+\path[fill=fillColor] (262.03,319.77) rectangle (268.72,340.26);
+
+\path[fill=fillColor] (269.46,319.77) rectangle (276.15,326.60);
+
+\path[fill=fillColor] (276.89,319.77) rectangle (283.58,323.18);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.71,319.77) rectangle (283.58,555.50);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,316.74) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,385.06) {20};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,453.39) {40};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 26.76,521.72) {60};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,319.77) --
+	( 31.71,319.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,388.10) --
+	( 31.71,388.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,456.42) --
+	( 31.71,456.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,524.75) --
+	( 31.71,524.75);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.63,317.02) --
+	( 79.63,319.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (131.64,317.02) --
+	(131.64,319.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (183.65,317.02) --
+	(183.65,319.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (235.66,317.02) --
+	(235.66,319.77);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 79.63,308.76) {Jan 13};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (131.64,308.76) {Jan 20};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (183.65,308.76) {Jan 27};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (235.66,308.76) {Feb 03};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (210.00,195.87) {maximum observable};
-
-\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 95.70, 74.43) {minimum observable};
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (130.54,266.42) --
-	(137.68,259.28) --
-	(144.83,252.14) --
-	(151.97,244.99) --
-	(159.11,237.85) --
-	(166.26,230.71) --
-	(173.40,223.56) --
-	(180.54,216.42) --
-	(187.69,209.27) --
-	(194.83,202.13) --
-	(201.97,194.99) --
-	(209.12,187.84) --
-	(216.26,180.70) --
-	(223.40,173.56) --
-	(230.55,166.41) --
-	(237.69,159.27) --
-	(244.83,152.13) --
-	(251.98,144.98) --
-	(259.12,137.84) --
-	(266.27,130.70) --
-	(273.41,123.55);
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.82,116.41) --
-	( 51.96,109.26) --
-	( 59.10,102.12) --
-	( 66.25, 94.98) --
-	( 73.39, 87.83) --
-	( 80.53, 80.69) --
-	( 87.68, 73.55) --
-	( 94.82, 66.40) --
-	(101.96, 59.26) --
-	(109.11, 52.12) --
-	(116.25, 44.97) --
-	(123.39, 37.83) --
-	(130.54, 30.69);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 44.82,137.84) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.10,219.10) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.25,183.08) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.39,194.99) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.53,194.99) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.68,223.56) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.82,223.56) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.96,194.99) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.11,216.42) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,184.27) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.39,159.58) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.54,159.72) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.68,165.29) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.83,150.04) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.97,160.95) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.11,149.30) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.26,144.74) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.40,149.93) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.54,133.26) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.69,138.29) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.83,129.96) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.97,127.28) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.12,127.33) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.26,119.77) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (223.40,115.57) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.55,124.85) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (237.69,122.12) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (244.83,109.26) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (259.12, 87.83) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (273.41, 73.55) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
-	( 44.82,137.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
-	( 44.82,137.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.82,137.84) --
-	( 44.82,137.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,236.60) --
-	( 59.10,236.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,236.60) --
-	( 59.10,191.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.10,191.59) --
-	( 59.10,191.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,227.49) --
-	( 66.25,227.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,227.49) --
-	( 66.25,152.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25,152.84) --
-	( 66.25,152.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,208.56) --
-	( 73.39,208.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,208.56) --
-	( 73.39,181.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.39,181.41) --
-	( 73.39,181.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,236.42) --
-	( 80.53,236.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,236.42) --
-	( 80.53,141.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,141.41) --
-	( 80.53,141.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
-	( 87.68,223.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
-	( 87.68,223.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.68,223.56) --
-	( 87.68,223.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,257.49) --
-	( 94.82,257.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,257.49) --
-	( 94.82,189.63);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.82,189.63) --
-	( 94.82,189.63);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,208.56) --
-	(101.96,208.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,208.56) --
-	(101.96,181.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.96,181.41) --
-	(101.96,181.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
-	(109.11,216.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
-	(109.11,216.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (109.11,216.42) --
-	(109.11,216.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,214.81) --
-	(116.25,214.81);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,214.81) --
-	(116.25,159.81);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.25,159.81) --
-	(116.25,159.81);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,229.99) --
-	(123.39,229.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,229.99) --
-	(123.39,109.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (123.39,109.98) --
-	(123.39,109.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,212.85) --
-	(130.54,212.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,212.85) --
-	(130.54,126.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,126.23) --
-	(130.54,126.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,198.92) --
-	(137.68,198.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,198.92) --
-	(137.68,122.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68,122.84) --
-	(137.68,122.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,212.31) --
-	(144.83,212.31);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,212.31) --
-	(144.83,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (144.83,109.26) --
-	(144.83,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,223.56) --
-	(151.97,223.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,223.56) --
-	(151.97,122.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.97,122.30) --
-	(151.97,122.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,222.31) --
-	(159.11,222.31);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,222.31) --
-	(159.11, 91.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11, 91.58) --
-	(159.11, 91.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,191.77) --
-	(166.26,191.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,191.77) --
-	(166.26,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (166.26,109.26) --
-	(166.26,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,190.52) --
-	(173.40,190.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,190.52) --
-	(173.40,116.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (173.40,116.41) --
-	(173.40,116.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54,167.13) --
-	(180.54,167.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54,167.13) --
-	(180.54, 87.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (180.54, 87.48) --
-	(180.54, 87.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69,193.74) --
-	(187.69,193.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69,193.74) --
-	(187.69, 80.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (187.69, 80.69) --
-	(187.69, 80.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83,181.77) --
-	(194.83,181.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83,181.77) --
-	(194.83, 87.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (194.83, 87.48) --
-	(194.83, 87.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97,172.84) --
-	(201.97,172.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97,172.84) --
-	(201.97, 44.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (201.97, 44.97) --
-	(201.97, 44.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12,167.84) --
-	(209.12,167.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12,167.84) --
-	(209.12, 70.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12, 70.69) --
-	(209.12, 70.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26,144.98) --
-	(216.26,144.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26,144.98) --
-	(216.26, 79.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.26, 79.26) --
-	(216.26, 79.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40,142.13) --
-	(223.40,142.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40,142.13) --
-	(223.40, 92.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (223.40, 92.12) --
-	(223.40, 92.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55,144.98) --
-	(230.55,144.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55,144.98) --
-	(230.55, 98.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.55, 98.55) --
-	(230.55, 98.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,130.70) --
-	(237.69,130.70);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,130.70) --
-	(237.69,109.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,109.98) --
-	(237.69,109.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
-	(244.83,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
-	(244.83,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.83,109.26) --
-	(244.83,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
-	(259.12, 87.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
-	(259.12, 87.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (259.12, 87.83) --
-	(259.12, 87.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,107.48) --
-	(273.41,107.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,107.48) --
-	(273.41, 39.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41, 39.62) --
-	(273.41, 39.62);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 44.82,212.08) --
-	( 47.71,210.73) --
-	( 50.60,209.35) --
-	( 53.50,207.96) --
-	( 56.39,206.55) --
-	( 59.28,205.13) --
-	( 62.18,203.68) --
-	( 65.07,202.22) --
-	( 67.96,200.75) --
-	( 70.86,199.25) --
-	( 73.75,197.73) --
-	( 76.65,196.20) --
-	( 79.54,194.64) --
-	( 82.43,193.07) --
-	( 85.33,191.48) --
-	( 88.22,189.86) --
-	( 91.11,188.23) --
-	( 94.01,186.57) --
-	( 96.90,184.90) --
-	( 99.79,183.20) --
-	(102.69,181.48) --
-	(105.58,179.74) --
-	(108.47,177.98) --
-	(111.37,176.19) --
-	(114.26,174.39) --
-	(117.16,172.56) --
-	(120.05,170.70) --
-	(122.94,168.82) --
-	(125.84,166.96) --
-	(128.73,165.20) --
-	(131.62,163.53) --
-	(134.52,161.96) --
-	(137.41,160.49) --
-	(140.30,159.13) --
-	(143.20,157.88) --
-	(146.09,156.76) --
-	(148.98,155.79) --
-	(151.88,154.74) --
-	(154.77,153.38) --
-	(157.67,151.87) --
-	(160.56,150.42) --
-	(163.45,148.83) --
-	(166.35,147.14) --
-	(169.24,145.41) --
-	(172.13,143.73) --
-	(175.03,142.08) --
-	(177.92,140.32) --
-	(180.81,138.66) --
-	(183.71,137.15) --
-	(186.60,135.67) --
-	(189.50,134.18) --
-	(192.39,132.70) --
-	(195.28,131.23) --
-	(198.18,129.77) --
-	(201.07,128.34) --
-	(203.96,126.97) --
-	(206.86,125.71) --
-	(209.75,124.58) --
-	(212.64,123.44) --
-	(215.54,122.24) --
-	(218.43,120.96) --
-	(221.32,119.62) --
-	(224.22,118.21) --
-	(227.11,116.73) --
-	(230.01,115.18) --
-	(232.90,113.56) --
-	(235.79,111.88) --
-	(238.69,110.13) --
-	(241.58,108.32) --
-	(244.47,106.44) --
-	(247.37,104.50) --
-	(250.26,102.49) --
-	(253.15,100.42) --
-	(256.05, 98.29) --
-	(258.94, 96.10) --
-	(261.83, 93.84) --
-	(264.73, 91.52) --
-	(267.62, 89.14) --
-	(270.52, 86.70) --
-	(273.41, 84.20);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 44.82, 30.69) rectangle (273.41,266.42);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 39.87, 41.94) {-10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 39.87,113.38) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 39.87,184.81) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 39.87,256.25) {20};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 42.07, 44.97) --
-	( 44.82, 44.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 42.07,116.41) --
-	( 44.82,116.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 42.07,187.84) --
-	( 44.82,187.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 42.07,259.28) --
-	( 44.82,259.28);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.25, 27.94) --
-	( 66.25, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (137.68, 27.94) --
-	(137.68, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.12, 27.94) --
-	(209.12, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 66.25, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (137.68, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (209.12, 19.68) {20};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (157.65,296.72) {Symptom onset date};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (159.11,  7.64) {Symptom onset day (infector)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,437.63) {Number of cases with a known infector/infectee pair};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 23.25,148.55) {Forward delay (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 44.82,274.49) {A. Forward serial interval};
-\end{scope}
-\begin{scope}
-\path[clip] (295.68,  0.00) rectangle (571.56,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 31.71,563.57) {A. Epidemic curve};
+\end{scope}
+\begin{scope}
+\path[clip] (299.25,289.08) rectangle (567.99,578.16);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (295.68,  0.00) rectangle (571.56,289.08);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (299.25,289.08) rectangle (567.99,578.16);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (330.32, 30.69) rectangle (566.06,266.42);
+\path[fill=fillColor] (333.90,319.77) rectangle (562.49,555.50);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (384.09,204.80) {maximum observable};
-
-\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (517.67, 79.07) {minimum observable};
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (330.32,140.70) --
-	(338.18,148.55) --
-	(346.04,156.41) --
-	(353.90,164.27) --
-	(361.76,172.13) --
-	(369.61,179.99) --
-	(377.47,187.84) --
-	(385.33,195.70) --
-	(393.19,203.56) --
-	(401.05,211.42) --
-	(408.90,219.28) --
-	(416.76,227.13) --
-	(424.62,234.99) --
-	(432.48,242.85) --
-	(440.33,250.71) --
-	(448.19,258.56) --
-	(456.05,266.42);
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (479.62, 30.69) --
-	(487.48, 38.54) --
-	(495.34, 46.40) --
-	(503.20, 54.26) --
-	(511.06, 62.12) --
-	(518.91, 69.98) --
-	(526.77, 77.83) --
-	(534.63, 85.69) --
-	(542.49, 93.55) --
-	(550.35,101.41) --
-	(558.20,109.26) --
-	(566.06,117.12);
+\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (499.08,484.95) {maximum observable};
+
+\node[text=drawColor,rotate=-45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (384.78,363.51) {minimum observable};
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (419.62,555.50) --
+	(426.76,548.36) --
+	(433.91,541.22) --
+	(441.05,534.07) --
+	(448.19,526.93) --
+	(455.34,519.79) --
+	(462.48,512.64) --
+	(469.62,505.50) --
+	(476.77,498.35) --
+	(483.91,491.21) --
+	(491.05,484.07) --
+	(498.20,476.92) --
+	(505.34,469.78) --
+	(512.48,462.64) --
+	(519.63,455.49) --
+	(526.77,448.35) --
+	(533.91,441.21) --
+	(541.06,434.06) --
+	(548.20,426.92) --
+	(555.35,419.78) --
+	(562.49,412.63);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (333.90,405.49) --
+	(341.04,398.34) --
+	(348.18,391.20) --
+	(355.33,384.06) --
+	(362.47,376.91) --
+	(369.61,369.77) --
+	(376.76,362.63) --
+	(383.90,355.48) --
+	(391.04,348.34) --
+	(398.19,341.20) --
+	(405.33,334.05) --
+	(412.47,326.91) --
+	(419.62,319.77);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (330.32,140.70) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.76, 46.40) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.61,148.55) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.47,101.41) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (385.33,172.13) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (393.19,117.12) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (401.05,104.77) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (408.90,129.70) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.76,111.23) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (424.62,124.46) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (432.48,136.28) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (440.33,141.20) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (448.19,143.14) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (456.05,141.78) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (463.91,132.65) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (471.77,145.10) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (479.62,152.05) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.48,153.79) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (495.34,151.04) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (503.20,153.41) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (511.06,157.72) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (518.91,166.77) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (526.77,171.71) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (534.63,169.11) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (542.49,196.68) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (550.35,186.53) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (558.20,242.85) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (566.06,211.42) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (330.32,140.70) --
-	(330.32,140.70);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (330.32,140.70) --
-	(330.32,140.70);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (330.32,140.70) --
-	(330.32,140.70);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.76, 46.40) --
-	(361.76, 46.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.76, 46.40) --
-	(361.76, 46.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.76, 46.40) --
-	(361.76, 46.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,156.02) --
-	(369.61,156.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,156.02) --
-	(369.61,141.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,141.09) --
-	(369.61,141.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.47,101.41) --
-	(377.47,101.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.47,101.41) --
-	(377.47,101.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.47,101.41) --
-	(377.47,101.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (385.33,172.13) --
-	(385.33,172.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (385.33,172.13) --
-	(385.33,172.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (385.33,172.13) --
-	(385.33,172.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.19,117.12) --
-	(393.19,117.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.19,117.12) --
-	(393.19,117.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.19,117.12) --
-	(393.19,117.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (401.05,185.09) --
-	(401.05,185.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (401.05,185.09) --
-	(401.05, 38.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (401.05, 38.54) --
-	(401.05, 38.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (408.90,181.56) --
-	(408.90,181.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (408.90,181.56) --
-	(408.90,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (408.90,109.26) --
-	(408.90,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.76,139.32) --
-	(416.76,139.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.76,139.32) --
-	(416.76, 71.35);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.76, 71.35) --
-	(416.76, 71.35);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (424.62,194.52) --
-	(424.62,194.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (424.62,194.52) --
-	(424.62, 62.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (424.62, 62.51) --
-	(424.62, 62.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (432.48,227.13) --
-	(432.48,227.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (432.48,227.13) --
-	(432.48, 83.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (432.48, 83.73) --
-	(432.48, 83.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (440.33,223.20) --
-	(440.33,223.20);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (440.33,223.20) --
-	(440.33, 85.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (440.33, 85.69) --
-	(440.33, 85.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19,242.85) --
-	(448.19,242.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19,242.85) --
-	(448.19, 86.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19, 86.48) --
-	(448.19, 86.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (456.05,245.21) --
-	(456.05,245.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (456.05,245.21) --
-	(456.05, 96.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (456.05, 96.69) --
-	(456.05, 96.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (463.91,187.84) --
-	(463.91,187.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (463.91,187.84) --
-	(463.91, 85.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (463.91, 85.69) --
-	(463.91, 85.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (471.77,219.28) --
-	(471.77,219.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (471.77,219.28) --
-	(471.77, 93.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (471.77, 93.55) --
-	(471.77, 93.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (479.62,209.45) --
-	(479.62,209.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (479.62,209.45) --
-	(479.62,117.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (479.62,117.12) --
-	(479.62,117.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (487.48,206.51) --
-	(487.48,206.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (487.48,206.51) --
-	(487.48,107.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (487.48,107.30) --
-	(487.48,107.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (495.34,205.33) --
-	(495.34,205.33);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (495.34,205.33) --
-	(495.34,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (495.34,109.26) --
-	(495.34,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (503.20,198.45) --
-	(503.20,198.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (503.20,198.45) --
-	(503.20,115.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (503.20,115.75) --
-	(503.20,115.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (511.06,221.44) --
-	(511.06,221.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (511.06,221.44) --
-	(511.06, 99.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (511.06, 99.25) --
-	(511.06, 99.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (518.91,253.65) --
-	(518.91,253.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (518.91,253.65) --
-	(518.91,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (518.91,109.26) --
-	(518.91,109.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,240.10) --
-	(526.77,240.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,240.10) --
-	(526.77,128.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,128.52) --
-	(526.77,128.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (534.63,209.06) --
-	(534.63,209.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (534.63,209.06) --
-	(534.63,132.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (534.63,132.84) --
-	(534.63,132.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (542.49,234.99) --
-	(542.49,234.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (542.49,234.99) --
-	(542.49,148.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (542.49,148.55) --
-	(542.49,148.55);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (550.35,231.06) --
-	(550.35,231.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (550.35,231.06) --
-	(550.35,118.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (550.35,118.10) --
-	(550.35,118.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (558.20,242.85) --
-	(558.20,242.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (558.20,242.85) --
-	(558.20,242.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (558.20,242.85) --
-	(558.20,242.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (566.06,211.42) --
-	(566.06,211.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (566.06,211.42) --
-	(566.06,211.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (566.06,211.42) --
-	(566.06,211.42);
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (330.32,118.83) --
-	(333.31,118.41) --
-	(336.29,118.04) --
-	(339.28,117.71) --
-	(342.26,117.43) --
-	(345.24,117.20) --
-	(348.23,117.01) --
-	(351.21,116.87) --
-	(354.20,116.77) --
-	(357.18,116.72) --
-	(360.16,116.72) --
-	(363.15,116.77) --
-	(366.13,116.87) --
-	(369.12,117.01) --
-	(372.10,117.21) --
-	(375.08,117.45) --
-	(378.07,117.75) --
-	(381.05,118.09) --
-	(384.04,118.49) --
-	(387.02,118.94) --
-	(390.00,119.44) --
-	(392.99,119.99) --
-	(395.97,120.59) --
-	(398.96,121.25) --
-	(401.94,121.96) --
-	(404.92,122.73) --
-	(407.91,123.54) --
-	(410.89,124.42) --
-	(413.88,125.35) --
-	(416.86,126.33) --
-	(419.84,127.37) --
-	(422.83,128.47) --
-	(425.81,129.62) --
-	(428.80,130.83) --
-	(431.78,132.10) --
-	(434.76,133.38) --
-	(437.75,134.61) --
-	(440.73,135.77) --
-	(443.72,136.88) --
-	(446.70,137.92) --
-	(449.68,138.87) --
-	(452.67,139.56) --
-	(455.65,140.07) --
-	(458.64,140.53) --
-	(461.62,141.04) --
-	(464.60,141.73) --
-	(467.59,142.49) --
-	(470.57,143.35) --
-	(473.56,144.61) --
-	(476.54,146.56) --
-	(479.52,148.26) --
-	(482.51,149.31) --
-	(485.49,150.22) --
-	(488.48,151.24) --
-	(491.46,152.28) --
-	(494.44,153.32) --
-	(497.43,154.37) --
-	(500.41,155.31) --
-	(503.40,156.26) --
-	(506.38,157.32) --
-	(509.36,158.61) --
-	(512.35,160.23) --
-	(515.33,162.05) --
-	(518.32,164.02) --
-	(521.30,166.15) --
-	(524.28,168.43) --
-	(527.27,170.87) --
-	(530.25,173.46) --
-	(533.24,176.21) --
-	(536.22,179.13) --
-	(539.20,182.20) --
-	(542.19,185.42) --
-	(545.17,188.81) --
-	(548.16,192.36) --
-	(551.14,196.07) --
-	(554.12,199.95) --
-	(557.11,203.98) --
-	(560.09,208.18) --
-	(563.08,212.54) --
-	(566.06,217.06);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,426.92) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (348.18,508.18) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (355.33,472.16) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.47,484.07) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.61,484.07) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (376.76,512.64) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (383.90,512.64) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (391.04,484.07) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.19,505.50) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (405.33,473.35) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (412.47,448.66) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (419.62,448.80) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (426.76,454.37) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (433.91,439.12) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (441.05,450.03) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (448.19,438.38) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (455.34,433.82) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (462.48,439.01) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (469.62,422.34) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (476.77,427.37) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (483.91,419.04) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (491.05,416.36) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.20,416.41) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (505.34,408.85) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (512.48,404.65) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (519.63,413.93) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (526.77,411.20) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (533.91,398.34) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (548.20,376.91) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (562.49,362.63) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,426.92) --
+	(333.90,426.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,426.92) --
+	(333.90,426.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.90,426.92) --
+	(333.90,426.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,525.68) --
+	(348.18,525.68);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,525.68) --
+	(348.18,480.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.18,480.67) --
+	(348.18,480.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,516.57) --
+	(355.33,516.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,516.57) --
+	(355.33,441.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (355.33,441.92) --
+	(355.33,441.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,497.64) --
+	(362.47,497.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,497.64) --
+	(362.47,470.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.47,470.49) --
+	(362.47,470.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,525.50) --
+	(369.61,525.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,525.50) --
+	(369.61,430.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.61,430.49) --
+	(369.61,430.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,512.64) --
+	(376.76,512.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,512.64) --
+	(376.76,512.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,512.64) --
+	(376.76,512.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,546.57) --
+	(383.90,546.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,546.57) --
+	(383.90,478.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,478.71) --
+	(383.90,478.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,497.64) --
+	(391.04,497.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,497.64) --
+	(391.04,470.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (391.04,470.49) --
+	(391.04,470.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,505.50) --
+	(398.19,505.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,505.50) --
+	(398.19,505.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.19,505.50) --
+	(398.19,505.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,503.89) --
+	(405.33,503.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,503.89) --
+	(405.33,448.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.33,448.89) --
+	(405.33,448.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,519.07) --
+	(412.47,519.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,519.07) --
+	(412.47,399.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (412.47,399.06) --
+	(412.47,399.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,501.93) --
+	(419.62,501.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,501.93) --
+	(419.62,415.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (419.62,415.31) --
+	(419.62,415.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,488.00) --
+	(426.76,488.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,488.00) --
+	(426.76,411.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,411.92) --
+	(426.76,411.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (433.91,501.39) --
+	(433.91,501.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (433.91,501.39) --
+	(433.91,398.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (433.91,398.34) --
+	(433.91,398.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (441.05,512.64) --
+	(441.05,512.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (441.05,512.64) --
+	(441.05,411.38);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (441.05,411.38) --
+	(441.05,411.38);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19,511.39) --
+	(448.19,511.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19,511.39) --
+	(448.19,380.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (448.19,380.66) --
+	(448.19,380.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (455.34,480.85) --
+	(455.34,480.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (455.34,480.85) --
+	(455.34,398.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (455.34,398.34) --
+	(455.34,398.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.48,479.60) --
+	(462.48,479.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.48,479.60) --
+	(462.48,405.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.48,405.49) --
+	(462.48,405.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.62,456.21) --
+	(469.62,456.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.62,456.21) --
+	(469.62,376.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.62,376.56) --
+	(469.62,376.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.77,482.82) --
+	(476.77,482.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.77,482.82) --
+	(476.77,369.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.77,369.77) --
+	(476.77,369.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (483.91,470.85) --
+	(483.91,470.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (483.91,470.85) --
+	(483.91,376.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (483.91,376.56) --
+	(483.91,376.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.05,461.92) --
+	(491.05,461.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.05,461.92) --
+	(491.05,334.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.05,334.05) --
+	(491.05,334.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (498.20,456.92) --
+	(498.20,456.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (498.20,456.92) --
+	(498.20,359.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (498.20,359.77) --
+	(498.20,359.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (505.34,434.06) --
+	(505.34,434.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (505.34,434.06) --
+	(505.34,368.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (505.34,368.34) --
+	(505.34,368.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (512.48,431.21) --
+	(512.48,431.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (512.48,431.21) --
+	(512.48,381.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (512.48,381.20) --
+	(512.48,381.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (519.63,434.06) --
+	(519.63,434.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (519.63,434.06) --
+	(519.63,387.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (519.63,387.63) --
+	(519.63,387.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,419.78) --
+	(526.77,419.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,419.78) --
+	(526.77,399.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,399.06) --
+	(526.77,399.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.91,398.34) --
+	(533.91,398.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.91,398.34) --
+	(533.91,398.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.91,398.34) --
+	(533.91,398.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (548.20,376.91) --
+	(548.20,376.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (548.20,376.91) --
+	(548.20,376.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (548.20,376.91) --
+	(548.20,376.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (562.49,396.56) --
+	(562.49,396.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (562.49,396.56) --
+	(562.49,328.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (562.49,328.70) --
+	(562.49,328.70);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (333.90,501.16) --
+	(336.79,499.81) --
+	(339.68,498.43) --
+	(342.58,497.04) --
+	(345.47,495.63) --
+	(348.36,494.21) --
+	(351.26,492.76) --
+	(354.15,491.30) --
+	(357.04,489.83) --
+	(359.94,488.33) --
+	(362.83,486.81) --
+	(365.73,485.28) --
+	(368.62,483.72) --
+	(371.51,482.15) --
+	(374.41,480.56) --
+	(377.30,478.94) --
+	(380.19,477.31) --
+	(383.09,475.65) --
+	(385.98,473.98) --
+	(388.87,472.28) --
+	(391.77,470.56) --
+	(394.66,468.82) --
+	(397.55,467.06) --
+	(400.45,465.27) --
+	(403.34,463.47) --
+	(406.24,461.64) --
+	(409.13,459.78) --
+	(412.02,457.90) --
+	(414.92,456.04) --
+	(417.81,454.28) --
+	(420.70,452.61) --
+	(423.60,451.04) --
+	(426.49,449.57) --
+	(429.38,448.21) --
+	(432.28,446.96) --
+	(435.17,445.84) --
+	(438.06,444.87) --
+	(440.96,443.82) --
+	(443.85,442.46) --
+	(446.75,440.95) --
+	(449.64,439.50) --
+	(452.53,437.91) --
+	(455.43,436.22) --
+	(458.32,434.49) --
+	(461.21,432.81) --
+	(464.11,431.16) --
+	(467.00,429.40) --
+	(469.89,427.74) --
+	(472.79,426.23) --
+	(475.68,424.75) --
+	(478.58,423.26) --
+	(481.47,421.78) --
+	(484.36,420.31) --
+	(487.26,418.85) --
+	(490.15,417.42) --
+	(493.04,416.05) --
+	(495.94,414.79) --
+	(498.83,413.66) --
+	(501.72,412.52) --
+	(504.62,411.32) --
+	(507.51,410.04) --
+	(510.40,408.70) --
+	(513.30,407.29) --
+	(516.19,405.81) --
+	(519.09,404.26) --
+	(521.98,402.64) --
+	(524.87,400.96) --
+	(527.77,399.21) --
+	(530.66,397.40) --
+	(533.55,395.52) --
+	(536.45,393.58) --
+	(539.34,391.57) --
+	(542.23,389.50) --
+	(545.13,387.37) --
+	(548.02,385.18) --
+	(550.91,382.92) --
+	(553.81,380.60) --
+	(556.70,378.22) --
+	(559.60,375.78) --
+	(562.49,373.28);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (330.32, 30.69) rectangle (566.06,266.42);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.90,319.77) rectangle (562.49,555.50);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (325.37, 35.51) {-10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (325.37,114.09) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (325.37,192.67) {10};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (328.95,331.02) {-10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (328.95,402.46) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (328.95,473.89) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (328.95,545.33) {20};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (327.57, 38.54) --
-	(330.32, 38.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (327.57,117.12) --
-	(330.32,117.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (327.57,195.70) --
-	(330.32,195.70);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.15,334.05) --
+	(333.90,334.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.15,405.49) --
+	(333.90,405.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.15,476.92) --
+	(333.90,476.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.15,548.36) --
+	(333.90,548.36);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (330.32, 27.94) --
-	(330.32, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (408.90, 27.94) --
-	(408.90, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (487.48, 27.94) --
-	(487.48, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (566.06, 27.94) --
-	(566.06, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.76,317.02) --
+	(376.76,319.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (426.76,317.02) --
+	(426.76,319.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.77,317.02) --
+	(476.77,319.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (526.77,317.02) --
+	(526.77,319.77);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{gray}{0.30}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (330.32, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (408.90, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (487.48, 19.68) {20};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (566.06, 19.68) {30};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (376.76,308.76) {Jan 13};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (426.76,308.76) {Jan 20};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.77,308.76) {Jan 27};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (526.77,308.76) {Feb 03};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (448.19,  7.64) {Symptom onset day (infectee)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (448.19,296.72) {Symptom onset date (infector)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (308.76,148.55) {Backward delay (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (312.33,437.63) {Forward delay (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (330.32,274.49) {B. Backward serial interval};
-\end{scope}
-\begin{scope}
-\path[clip] (578.16,  0.00) rectangle (867.24,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (333.90,563.57) {B. Forward serial interval};
+\end{scope}
+\begin{scope}
+\path[clip] (  6.60,  0.00) rectangle (282.48,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (578.16,  0.00) rectangle (867.24,289.08);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  6.60,  0.00) rectangle (282.48,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (605.47, 30.69) rectangle (861.74,266.42);
+\path[fill=fillColor] ( 41.24, 30.69) rectangle (276.98,266.42);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 95.01,204.80) {maximum observable};
+
+\node[text=drawColor,rotate= 45.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (228.59, 79.07) {minimum observable};
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 41.24,140.70) --
+	( 49.10,148.55) --
+	( 56.96,156.41) --
+	( 64.82,164.27) --
+	( 72.68,172.13) --
+	( 80.53,179.99) --
+	( 88.39,187.84) --
+	( 96.25,195.70) --
+	(104.11,203.56) --
+	(111.97,211.42) --
+	(119.82,219.28) --
+	(127.68,227.13) --
+	(135.54,234.99) --
+	(143.40,242.85) --
+	(151.25,250.71) --
+	(159.11,258.56) --
+	(166.97,266.42);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (190.54, 30.69) --
+	(198.40, 38.54) --
+	(206.26, 46.40) --
+	(214.12, 54.26) --
+	(221.98, 62.12) --
+	(229.83, 69.98) --
+	(237.69, 77.83) --
+	(245.55, 85.69) --
+	(253.41, 93.55) --
+	(261.27,101.41) --
+	(269.12,109.26) --
+	(276.98,117.12);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 41.24,140.70) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.68, 46.40) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.53,148.55) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 88.39,101.41) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.25,172.13) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.11,117.12) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.97,104.77) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.82,129.70) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.68,111.23) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.54,124.46) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.40,136.28) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.25,141.20) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.11,143.14) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.97,141.78) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.83,132.65) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.69,145.10) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.54,152.05) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (198.40,153.79) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.26,151.04) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (214.12,153.41) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (221.98,157.72) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.83,166.77) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (237.69,171.71) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (245.55,169.11) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (253.41,196.68) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (261.27,186.53) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (269.12,242.85) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (276.98,211.42) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.24,140.70) --
+	( 41.24,140.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.24,140.70) --
+	( 41.24,140.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.24,140.70) --
+	( 41.24,140.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.68, 46.40) --
+	( 72.68, 46.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.68, 46.40) --
+	( 72.68, 46.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 72.68, 46.40) --
+	( 72.68, 46.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,156.02) --
+	( 80.53,156.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,156.02) --
+	( 80.53,141.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.53,141.09) --
+	( 80.53,141.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.39,101.41) --
+	( 88.39,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.39,101.41) --
+	( 88.39,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.39,101.41) --
+	( 88.39,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.25,172.13) --
+	( 96.25,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.25,172.13) --
+	( 96.25,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.25,172.13) --
+	( 96.25,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (104.11,117.12) --
+	(104.11,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (104.11,117.12) --
+	(104.11,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (104.11,117.12) --
+	(104.11,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.97,185.09) --
+	(111.97,185.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.97,185.09) --
+	(111.97, 38.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.97, 38.54) --
+	(111.97, 38.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (119.82,181.56) --
+	(119.82,181.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (119.82,181.56) --
+	(119.82,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (119.82,109.26) --
+	(119.82,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (127.68,139.32) --
+	(127.68,139.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (127.68,139.32) --
+	(127.68, 71.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (127.68, 71.35) --
+	(127.68, 71.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (135.54,194.52) --
+	(135.54,194.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (135.54,194.52) --
+	(135.54, 62.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (135.54, 62.51) --
+	(135.54, 62.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (143.40,227.13) --
+	(143.40,227.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (143.40,227.13) --
+	(143.40, 83.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (143.40, 83.73) --
+	(143.40, 83.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.25,223.20) --
+	(151.25,223.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.25,223.20) --
+	(151.25, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.25, 85.69) --
+	(151.25, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,242.85) --
+	(159.11,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11,242.85) --
+	(159.11, 86.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.11, 86.48) --
+	(159.11, 86.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (166.97,245.21) --
+	(166.97,245.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (166.97,245.21) --
+	(166.97, 96.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (166.97, 96.69) --
+	(166.97, 96.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (174.83,187.84) --
+	(174.83,187.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (174.83,187.84) --
+	(174.83, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (174.83, 85.69) --
+	(174.83, 85.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (182.69,219.28) --
+	(182.69,219.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (182.69,219.28) --
+	(182.69, 93.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (182.69, 93.55) --
+	(182.69, 93.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (190.54,209.45) --
+	(190.54,209.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (190.54,209.45) --
+	(190.54,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (190.54,117.12) --
+	(190.54,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.40,206.51) --
+	(198.40,206.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.40,206.51) --
+	(198.40,107.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (198.40,107.30) --
+	(198.40,107.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.26,205.33) --
+	(206.26,205.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.26,205.33) --
+	(206.26,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.26,109.26) --
+	(206.26,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.12,198.45) --
+	(214.12,198.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.12,198.45) --
+	(214.12,115.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.12,115.75) --
+	(214.12,115.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.98,221.44) --
+	(221.98,221.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.98,221.44) --
+	(221.98, 99.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.98, 99.25) --
+	(221.98, 99.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.83,253.65) --
+	(229.83,253.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.83,253.65) --
+	(229.83,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.83,109.26) --
+	(229.83,109.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,240.10) --
+	(237.69,240.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,240.10) --
+	(237.69,128.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (237.69,128.52) --
+	(237.69,128.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (245.55,209.06) --
+	(245.55,209.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (245.55,209.06) --
+	(245.55,132.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (245.55,132.84) --
+	(245.55,132.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (253.41,234.99) --
+	(253.41,234.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (253.41,234.99) --
+	(253.41,148.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (253.41,148.55) --
+	(253.41,148.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.27,231.06) --
+	(261.27,231.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.27,231.06) --
+	(261.27,118.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.27,118.10) --
+	(261.27,118.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (269.12,242.85) --
+	(269.12,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (269.12,242.85) --
+	(269.12,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (269.12,242.85) --
+	(269.12,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (276.98,211.42) --
+	(276.98,211.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (276.98,211.42) --
+	(276.98,211.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (276.98,211.42) --
+	(276.98,211.42);
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 41.24,118.83) --
+	( 44.23,118.41) --
+	( 47.21,118.04) --
+	( 50.20,117.71) --
+	( 53.18,117.43) --
+	( 56.16,117.20) --
+	( 59.15,117.01) --
+	( 62.13,116.87) --
+	( 65.12,116.77) --
+	( 68.10,116.72) --
+	( 71.08,116.72) --
+	( 74.07,116.77) --
+	( 77.05,116.87) --
+	( 80.04,117.01) --
+	( 83.02,117.21) --
+	( 86.00,117.45) --
+	( 88.99,117.75) --
+	( 91.97,118.09) --
+	( 94.96,118.49) --
+	( 97.94,118.94) --
+	(100.92,119.44) --
+	(103.91,119.99) --
+	(106.89,120.59) --
+	(109.88,121.25) --
+	(112.86,121.96) --
+	(115.84,122.73) --
+	(118.83,123.54) --
+	(121.81,124.42) --
+	(124.80,125.35) --
+	(127.78,126.33) --
+	(130.76,127.37) --
+	(133.75,128.47) --
+	(136.73,129.62) --
+	(139.72,130.83) --
+	(142.70,132.10) --
+	(145.68,133.38) --
+	(148.67,134.61) --
+	(151.65,135.77) --
+	(154.64,136.88) --
+	(157.62,137.92) --
+	(160.60,138.87) --
+	(163.59,139.56) --
+	(166.57,140.07) --
+	(169.56,140.53) --
+	(172.54,141.04) --
+	(175.52,141.73) --
+	(178.51,142.49) --
+	(181.49,143.35) --
+	(184.48,144.61) --
+	(187.46,146.56) --
+	(190.44,148.26) --
+	(193.43,149.31) --
+	(196.41,150.22) --
+	(199.40,151.24) --
+	(202.38,152.28) --
+	(205.36,153.32) --
+	(208.35,154.37) --
+	(211.33,155.31) --
+	(214.32,156.26) --
+	(217.30,157.32) --
+	(220.28,158.61) --
+	(223.27,160.23) --
+	(226.25,162.05) --
+	(229.24,164.02) --
+	(232.22,166.15) --
+	(235.20,168.43) --
+	(238.19,170.87) --
+	(241.17,173.46) --
+	(244.16,176.21) --
+	(247.14,179.13) --
+	(250.12,182.20) --
+	(253.11,185.42) --
+	(256.09,188.81) --
+	(259.08,192.36) --
+	(262.06,196.07) --
+	(265.04,199.95) --
+	(268.03,203.98) --
+	(271.01,208.18) --
+	(274.00,212.54) --
+	(276.98,217.06);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.24, 30.69) rectangle (276.98,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.29, 35.51) {-10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.29,114.09) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.29,192.67) {10};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.49, 38.54) --
+	( 41.24, 38.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.49,117.12) --
+	( 41.24,117.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 38.49,195.70) --
+	( 41.24,195.70);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.82, 27.94) --
+	( 64.82, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (119.82, 27.94) --
+	(119.82, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (174.83, 27.94) --
+	(174.83, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.83, 27.94) --
+	(229.83, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 64.82, 19.68) {Jan 13};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (119.82, 19.68) {Jan 20};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (174.83, 19.68) {Jan 27};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (229.83, 19.68) {Feb 03};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (159.11,  7.64) {Symptom onset date (infectee)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 19.68,148.55) {Backward delay (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 41.24,274.49) {C. Backward serial interval};
+\end{scope}
+\begin{scope}
+\path[clip] (289.08,  0.00) rectangle (578.16,289.08);
+\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.08,  0.00) rectangle (578.16,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (316.39, 30.69) rectangle (572.66,266.42);
+\definecolor{fillColor}{RGB}{240,228,66}
+
+\path[fill=fillColor,fill opacity=0.50] (340.42,255.71) --
+	(348.43,234.51) --
+	(356.43,227.85) --
+	(364.44,224.34) --
+	(372.45,232.95) --
+	(380.46,225.18) --
+	(388.47,220.08) --
+	(396.48,212.60) --
+	(404.48,137.83) --
+	(412.49,119.60) --
+	(420.50,116.21) --
+	(428.51,104.34) --
+	(436.52,101.52) --
+	(444.53, 91.89) --
+	(452.53, 87.88) --
+	(460.54, 85.77) --
+	(468.55, 79.62) --
+	(476.56, 76.53) --
+	(484.57, 72.74) --
+	(492.58, 71.32) --
+	(500.58, 69.30) --
+	(508.59, 68.00) --
+	(516.60, 66.17) --
+	(524.61, 65.86) --
+	(532.62, 65.06) --
+	(540.63, 64.84) --
+	(548.63, 64.84) --
+	(556.64, 64.82) --
+	(564.65, 64.82) --
+	(572.66, 64.08) --
+	(572.66, 56.77) --
+	(564.65, 57.72) --
+	(556.64, 57.72) --
+	(548.63, 58.18) --
+	(540.63, 58.18) --
+	(532.62, 58.40) --
+	(524.61, 58.16) --
+	(516.60, 58.79) --
+	(508.59, 60.03) --
+	(500.58, 60.94) --
+	(492.58, 62.46) --
+	(484.57, 65.05) --
+	(476.56, 66.78) --
+	(468.55, 70.56) --
+	(460.54, 73.93) --
+	(452.53, 74.95) --
+	(444.53, 77.75) --
+	(436.52, 84.76) --
+	(428.51, 84.17) --
+	(420.50, 90.54) --
+	(412.49, 89.60) --
+	(404.48, 93.27) --
+	(396.48,129.71) --
+	(388.47,137.14) --
+	(380.46,136.34) --
+	(372.45,134.94) --
+	(364.44,135.04) --
+	(356.43,120.43) --
+	(348.43,124.23) --
+	(340.42,119.49) --
+	cycle;
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.42,255.71) --
+	(348.43,234.51) --
+	(356.43,227.85) --
+	(364.44,224.34) --
+	(372.45,232.95) --
+	(380.46,225.18) --
+	(388.47,220.08) --
+	(396.48,212.60) --
+	(404.48,137.83) --
+	(412.49,119.60) --
+	(420.50,116.21) --
+	(428.51,104.34) --
+	(436.52,101.52) --
+	(444.53, 91.89) --
+	(452.53, 87.88) --
+	(460.54, 85.77) --
+	(468.55, 79.62) --
+	(476.56, 76.53) --
+	(484.57, 72.74) --
+	(492.58, 71.32) --
+	(500.58, 69.30) --
+	(508.59, 68.00) --
+	(516.60, 66.17) --
+	(524.61, 65.86) --
+	(532.62, 65.06) --
+	(540.63, 64.84) --
+	(548.63, 64.84) --
+	(556.64, 64.82) --
+	(564.65, 64.82) --
+	(572.66, 64.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (572.66, 56.77) --
+	(564.65, 57.72) --
+	(556.64, 57.72) --
+	(548.63, 58.18) --
+	(540.63, 58.18) --
+	(532.62, 58.40) --
+	(524.61, 58.16) --
+	(516.60, 58.79) --
+	(508.59, 60.03) --
+	(500.58, 60.94) --
+	(492.58, 62.46) --
+	(484.57, 65.05) --
+	(476.56, 66.78) --
+	(468.55, 70.56) --
+	(460.54, 73.93) --
+	(452.53, 74.95) --
+	(444.53, 77.75) --
+	(436.52, 84.76) --
+	(428.51, 84.17) --
+	(420.50, 90.54) --
+	(412.49, 89.60) --
+	(404.48, 93.27) --
+	(396.48,129.71) --
+	(388.47,137.14) --
+	(380.46,136.34) --
+	(372.45,134.94) --
+	(364.44,135.04) --
+	(356.43,120.43) --
+	(348.43,124.23) --
+	(340.42,119.49);
+\definecolor{fillColor}{RGB}{0,114,178}
+
+\path[fill=fillColor,fill opacity=0.50] (340.42,167.99) --
+	(348.43,158.37) --
+	(356.43,155.61) --
+	(364.44,153.41) --
+	(372.45,158.49) --
+	(380.46,154.03) --
+	(388.47,151.93) --
+	(396.48,148.30) --
+	(404.48,107.71) --
+	(412.49, 96.60) --
+	(420.50, 94.03) --
+	(428.51, 86.26) --
+	(436.52, 84.52) --
+	(444.53, 77.77) --
+	(452.53, 75.45) --
+	(460.54, 73.98) --
+	(468.55, 69.74) --
+	(476.56, 67.73) --
+	(484.57, 65.35) --
+	(492.58, 64.41) --
+	(500.58, 62.76) --
+	(508.59, 61.94) --
+	(516.60, 60.56) --
+	(524.61, 60.51) --
+	(532.62, 60.01) --
+	(540.63, 59.88) --
+	(548.63, 59.88) --
+	(556.64, 59.77) --
+	(564.65, 59.77) --
+	(572.66, 59.40) --
+	(572.66, 54.49) --
+	(564.65, 54.89) --
+	(556.64, 54.89) --
+	(548.63, 55.23) --
+	(540.63, 55.23) --
+	(532.62, 55.32) --
+	(524.61, 55.43) --
+	(516.60, 55.76) --
+	(508.59, 56.48) --
+	(500.58, 57.32) --
+	(492.58, 58.34) --
+	(484.57, 59.85) --
+	(476.56, 61.35) --
+	(468.55, 63.63) --
+	(460.54, 66.52) --
+	(452.53, 66.97) --
+	(444.53, 68.74) --
+	(436.52, 73.15) --
+	(428.51, 73.04) --
+	(420.50, 77.40) --
+	(412.49, 77.19) --
+	(404.48, 79.82) --
+	(396.48,101.35) --
+	(388.47,108.09) --
+	(380.46,107.05) --
+	(372.45,105.61) --
+	(364.44,105.29) --
+	(356.43, 96.62) --
+	(348.43, 98.80) --
+	(340.42, 95.78) --
+	cycle;
+\definecolor{drawColor}{RGB}{0,114,178}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round] (340.42,167.99) --
+	(348.43,158.37) --
+	(356.43,155.61) --
+	(364.44,153.41) --
+	(372.45,158.49) --
+	(380.46,154.03) --
+	(388.47,151.93) --
+	(396.48,148.30) --
+	(404.48,107.71) --
+	(412.49, 96.60) --
+	(420.50, 94.03) --
+	(428.51, 86.26) --
+	(436.52, 84.52) --
+	(444.53, 77.77) --
+	(452.53, 75.45) --
+	(460.54, 73.98) --
+	(468.55, 69.74) --
+	(476.56, 67.73) --
+	(484.57, 65.35) --
+	(492.58, 64.41) --
+	(500.58, 62.76) --
+	(508.59, 61.94) --
+	(516.60, 60.56) --
+	(524.61, 60.51) --
+	(532.62, 60.01) --
+	(540.63, 59.88) --
+	(548.63, 59.88) --
+	(556.64, 59.77) --
+	(564.65, 59.77) --
+	(572.66, 59.40);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round] (572.66, 54.49) --
+	(564.65, 54.89) --
+	(556.64, 54.89) --
+	(548.63, 55.23) --
+	(540.63, 55.23) --
+	(532.62, 55.32) --
+	(524.61, 55.43) --
+	(516.60, 55.76) --
+	(508.59, 56.48) --
+	(500.58, 57.32) --
+	(492.58, 58.34) --
+	(484.57, 59.85) --
+	(476.56, 61.35) --
+	(468.55, 63.63) --
+	(460.54, 66.52) --
+	(452.53, 66.97) --
+	(444.53, 68.74) --
+	(436.52, 73.15) --
+	(428.51, 73.04) --
+	(420.50, 77.40) --
+	(412.49, 77.19) --
+	(404.48, 79.82) --
+	(396.48,101.35) --
+	(388.47,108.09) --
+	(380.46,107.05) --
+	(372.45,105.61) --
+	(364.44,105.29) --
+	(356.43, 96.62) --
+	(348.43, 98.80) --
+	(340.42, 95.78);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (316.39, 41.40) -- (572.66, 41.40);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (340.42,170.94) --
+	(348.43,170.79) --
+	(356.43,163.30) --
+	(364.44,167.34) --
+	(372.45,172.68) --
+	(380.46,172.43) --
+	(388.47,174.86) --
+	(396.48,167.73) --
+	(404.48,112.65) --
+	(412.49,105.04) --
+	(420.50,102.84) --
+	(428.51, 93.38) --
+	(436.52, 91.84) --
+	(444.53, 83.99) --
+	(452.53, 80.95) --
+	(460.54, 80.00) --
+	(468.55, 75.18) --
+	(476.56, 71.77) --
+	(484.57, 68.56) --
+	(492.58, 66.30) --
+	(500.58, 65.11) --
+	(508.59, 63.71) --
+	(516.60, 62.37) --
+	(524.61, 61.91) --
+	(532.62, 61.69) --
+	(540.63, 61.52) --
+	(548.63, 61.52) --
+	(556.64, 61.33) --
+	(564.65, 61.33) --
+	(572.66, 60.65);
+\definecolor{drawColor}{RGB}{0,114,178}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (340.42,126.39) --
+	(348.43,125.79) --
+	(356.43,122.09) --
+	(364.44,124.37) --
+	(372.45,127.48) --
+	(380.46,126.99) --
+	(388.47,128.28) --
+	(396.48,123.96) --
+	(404.48, 92.40) --
+	(412.49, 87.06) --
+	(420.50, 85.30) --
+	(428.51, 79.23) --
+	(436.52, 77.99) --
+	(444.53, 73.04) --
+	(452.53, 70.90) --
+	(460.54, 70.16) --
+	(468.55, 66.88) --
+	(476.56, 64.57) --
+	(484.57, 62.37) --
+	(492.58, 60.94) --
+	(500.58, 60.13) --
+	(508.59, 59.14) --
+	(516.60, 58.16) --
+	(524.61, 57.82) --
+	(532.62, 57.64) --
+	(540.63, 57.52) --
+	(548.63, 57.52) --
+	(556.64, 57.39) --
+	(564.65, 57.39) --
+	(572.66, 56.99);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.39, 30.69) rectangle (572.66,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44, 38.37) {1};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44, 90.38) {2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,142.40) {3};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,194.41) {4};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,246.42) {5};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64, 41.40) --
+	(316.39, 41.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64, 93.41) --
+	(316.39, 93.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,145.43) --
+	(316.39,145.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,197.44) --
+	(316.39,197.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,249.45) --
+	(316.39,249.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (364.44, 27.94) --
+	(364.44, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (420.50, 27.94) --
+	(420.50, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.56, 27.94) --
+	(476.56, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (532.62, 27.94) --
+	(532.62, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (364.44, 19.68) {Jan 13};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (420.50, 19.68) {Jan 20};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.56, 19.68) {Jan 27};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (532.62, 19.68) {Feb 03};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (444.53,  7.64) {Symptom onset date (infector)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,148.55) {Basic reproduction number $\mathcal R_0$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (432.89,208.36) rectangle (548.42,253.77);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (438.39,228.31) rectangle (452.84,242.77);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{240,228,66}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (629.50,255.71) --
-	(637.51,234.51) --
-	(645.51,227.85) --
-	(653.52,224.34) --
-	(661.53,232.95) --
-	(669.54,225.18) --
-	(677.55,220.08) --
-	(685.56,212.60) --
-	(693.56,137.83) --
-	(701.57,119.60) --
-	(709.58,116.21) --
-	(717.59,104.34) --
-	(725.60,101.52) --
-	(733.61, 91.89) --
-	(741.61, 87.88) --
-	(749.62, 85.77) --
-	(757.63, 79.62) --
-	(765.64, 76.53) --
-	(773.65, 72.74) --
-	(781.66, 71.32) --
-	(789.66, 69.30) --
-	(797.67, 68.00) --
-	(805.68, 66.17) --
-	(813.69, 65.86) --
-	(821.70, 65.06) --
-	(829.71, 64.84) --
-	(837.71, 64.84) --
-	(845.72, 64.82) --
-	(853.73, 64.82) --
-	(861.74, 64.08) --
-	(861.74, 56.77) --
-	(853.73, 57.72) --
-	(845.72, 57.72) --
-	(837.71, 58.18) --
-	(829.71, 58.18) --
-	(821.70, 58.40) --
-	(813.69, 58.16) --
-	(805.68, 58.79) --
-	(797.67, 60.03) --
-	(789.66, 60.94) --
-	(781.66, 62.46) --
-	(773.65, 65.05) --
-	(765.64, 66.78) --
-	(757.63, 70.56) --
-	(749.62, 73.93) --
-	(741.61, 74.95) --
-	(733.61, 77.75) --
-	(725.60, 84.76) --
-	(717.59, 84.17) --
-	(709.58, 90.54) --
-	(701.57, 89.60) --
-	(693.56, 93.27) --
-	(685.56,129.71) --
-	(677.55,137.14) --
-	(669.54,136.34) --
-	(661.53,134.94) --
-	(653.52,135.04) --
-	(645.51,120.43) --
-	(637.51,124.23) --
-	(629.50,119.49) --
-	cycle;
+\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor,fill opacity=0.50] (439.10,229.02) rectangle (452.13,242.05);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{RGB}{240,228,66}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (439.83,235.54) -- (451.40,235.54);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (438.39,213.86) rectangle (452.84,228.31);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,114,178}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round,line cap=round,fill=fillColor,fill opacity=0.50] (629.50,167.99) --
-	(637.51,158.37) --
-	(645.51,155.61) --
-	(653.52,153.41) --
-	(661.53,158.49) --
-	(669.54,154.03) --
-	(677.55,151.93) --
-	(685.56,148.30) --
-	(693.56,107.71) --
-	(701.57, 96.60) --
-	(709.58, 94.03) --
-	(717.59, 86.26) --
-	(725.60, 84.52) --
-	(733.61, 77.77) --
-	(741.61, 75.45) --
-	(749.62, 73.98) --
-	(757.63, 69.74) --
-	(765.64, 67.73) --
-	(773.65, 65.35) --
-	(781.66, 64.41) --
-	(789.66, 62.76) --
-	(797.67, 61.94) --
-	(805.68, 60.56) --
-	(813.69, 60.51) --
-	(821.70, 60.01) --
-	(829.71, 59.88) --
-	(837.71, 59.88) --
-	(845.72, 59.77) --
-	(853.73, 59.77) --
-	(861.74, 59.40) --
-	(861.74, 54.49) --
-	(853.73, 54.89) --
-	(845.72, 54.89) --
-	(837.71, 55.23) --
-	(829.71, 55.23) --
-	(821.70, 55.32) --
-	(813.69, 55.43) --
-	(805.68, 55.76) --
-	(797.67, 56.48) --
-	(789.66, 57.32) --
-	(781.66, 58.34) --
-	(773.65, 59.85) --
-	(765.64, 61.35) --
-	(757.63, 63.63) --
-	(749.62, 66.52) --
-	(741.61, 66.97) --
-	(733.61, 68.74) --
-	(725.60, 73.15) --
-	(717.59, 73.04) --
-	(709.58, 77.40) --
-	(701.57, 77.19) --
-	(693.56, 79.82) --
-	(685.56,101.35) --
-	(677.55,108.09) --
-	(669.54,107.05) --
-	(661.53,105.61) --
-	(653.52,105.29) --
-	(645.51, 96.62) --
-	(637.51, 98.80) --
-	(629.50, 95.78) --
-	cycle;
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line cap=rect,fill=fillColor,fill opacity=0.50] (439.10,214.57) rectangle (452.13,227.60);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{RGB}{0,114,178}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (439.83,221.09) -- (451.40,221.09);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (605.47, 41.40) -- (861.74, 41.40);
-\definecolor{drawColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (629.50,170.94) --
-	(637.51,170.79) --
-	(645.51,163.30) --
-	(653.52,167.34) --
-	(661.53,172.68) --
-	(669.54,172.43) --
-	(677.55,174.86) --
-	(685.56,167.73) --
-	(693.56,112.65) --
-	(701.57,105.04) --
-	(709.58,102.84) --
-	(717.59, 93.38) --
-	(725.60, 91.84) --
-	(733.61, 83.99) --
-	(741.61, 80.95) --
-	(749.62, 80.00) --
-	(757.63, 75.18) --
-	(765.64, 71.77) --
-	(773.65, 68.56) --
-	(781.66, 66.30) --
-	(789.66, 65.11) --
-	(797.67, 63.71) --
-	(805.68, 62.37) --
-	(813.69, 61.91) --
-	(821.70, 61.69) --
-	(829.71, 61.52) --
-	(837.71, 61.52) --
-	(845.72, 61.33) --
-	(853.73, 61.33) --
-	(861.74, 60.65);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (629.50,126.39) --
-	(637.51,125.79) --
-	(645.51,122.09) --
-	(653.52,124.37) --
-	(661.53,127.48) --
-	(669.54,126.99) --
-	(677.55,128.28) --
-	(685.56,123.96) --
-	(693.56, 92.40) --
-	(701.57, 87.06) --
-	(709.58, 85.30) --
-	(717.59, 79.23) --
-	(725.60, 77.99) --
-	(733.61, 73.04) --
-	(741.61, 70.90) --
-	(749.62, 70.16) --
-	(757.63, 66.88) --
-	(765.64, 64.57) --
-	(773.65, 62.37) --
-	(781.66, 60.94) --
-	(789.66, 60.13) --
-	(797.67, 59.14) --
-	(805.68, 58.16) --
-	(813.69, 57.82) --
-	(821.70, 57.64) --
-	(829.71, 57.52) --
-	(837.71, 57.52) --
-	(845.72, 57.39) --
-	(853.73, 57.39) --
-	(861.74, 56.99);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (605.47, 30.69) rectangle (861.74,266.42);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52, 38.37) {1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52, 90.38) {2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52,142.40) {3};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52,194.41) {4};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.52,246.42) {5};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72, 41.40) --
-	(605.47, 41.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72, 93.41) --
-	(605.47, 93.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72,145.43) --
-	(605.47,145.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72,197.44) --
-	(605.47,197.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.72,249.45) --
-	(605.47,249.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (629.50, 27.94) --
-	(629.50, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (709.58, 27.94) --
-	(709.58, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (789.66, 27.94) --
-	(789.66, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (629.50, 19.68) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (709.58, 19.68) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (789.66, 19.68) {20};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (458.34,232.51) {6 day doubling period};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (733.61,  7.64) {Time (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (458.34,218.05) {8 day doubling period};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (591.24,148.55) {Basic reproduction number $\mathcal R_0$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (721.97,208.36) rectangle (837.50,253.77);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (727.47,228.31) rectangle (741.92,242.77);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{RGB}{240,228,66}
-\definecolor{fillColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor,fill opacity=0.50] (728.18,229.02) rectangle (741.21,242.05);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (728.91,235.54) -- (740.48,235.54);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (727.47,213.86) rectangle (741.92,228.31);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{RGB}{0,114,178}
-\definecolor{fillColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line cap=rect,fill=fillColor,fill opacity=0.50] (728.18,214.57) rectangle (741.21,227.60);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (728.91,221.09) -- (740.48,221.09);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (747.42,232.51) {6 day doubling period};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (747.42,218.05) {8 day doubling period};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (867.24,289.08);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (605.47,274.49) {C. Cohort-averaged estimates};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (316.39,274.49) {D. Cohort-averaged $\mathcal R_0$ estimates};
 \end{scope}

### 2020-09-22 response.tex
updating more
amsync

@@
 We have made major revisions to our manuscript to address the reviewers' comments.
-We were apparently not clear in our writing.
-Reviewers 1 and 3 both pointed out that we assume that the latent and incubation periods are equivalent (and thus not allowing for presymptomatic transmission).
-However, we only present this result in the appendix as a special case.
-We do not assume this in the main text and allow for presymptomatic transmission.
-Below please find our responses to reviewers.
+In particular, we have tried to clarify our exposition.
+Reviewers 1 and 3 both mention that we assume that the latent and incubation periods are equivalent (thus not allowing for presymptomatic transmission). 
+However, we only present this scenario in the appendix as a special case.
+We do not assume this in the main text.
+We have thus tried to make our assumptions clear and our results more accessible.
+Below please find our detailed responses to reviewers.
 
@@
 
-Thank you for pointing this out. The special version is only presented in the supplementary material. We do not assume this in the main text. We have now made this distinction clear in the text:
+Thank you for pointing this out. Our results do apply in general. We have clarified this assertion and tried to make the arguments more clear as well.
+
+JD: The reviewers' main concern is that they don't feel we have made a strong argument in the general case.
+Your response seems to focus more on the clarity of our claim than the clarity of our arguments.
+
+The special version is only presented in the supplementary material. We do not assume this in the main text. We have now made this distinction clear in the text:
 
@@
 
-We provide a mathematical proof of this using a general model in the supplementary file. Figure 2A also demonstrates that this holds. We tried to make this clear in the main text:
+This statement is proved in the supplement and illustrated in a general context in Figure 2A. We now say this explicitly in the main text:
+
+JD: In early drafts, it's probably better to just list line numbers for a clearly specified MS version than to put quotes that may change.
 
@@
 
-Done.
+Fixed, thank you.
 
@@
 
-We have tried to clarify this:
+We have tried to clarify this point:
 
@@
 
-\revtext{p6, line 188: shorter than what? If you mean compared to the forward delay distribution it is always true when r>0 and not necessary that r is higher (than what?).}
+\revtext{p6, line 188: shorter than what? If you mean compared to the forward delay distribution it is always true when $r>0$ and not necessary that r is higher (than what?).}
 

### 2020-09-22 response.tex
working through revisions

@@
 
-The restrictive situation is presented in the supplementary file as a special case.
-The main results do not depend on the restrictive assumption.
-We have tried to clarify this.
-We have also re-phrased the sentence now to acknoweldge what other studies have said more carefully:
+This result also does not depend on the restrictive assumption. We have tried to clarify this. We also re-phrased to describe the earlier studies more carefully:
 
@@
 
-We are not assuming this. We have tried to clarify this in the main text.
+We are not assuming this, as discussed above. We have tried to clarify.
 
@@
 
-We have re-phrased the sentence to make it clearer:
+We have clarified this sentence:
 

### 2020-09-22 serial.tex
updating more
working through revisions

@@
 It is well established that this renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
-By definition, the serial-interval distribution describes the renewal process between symptomatic cases based on their symptom onset dates.
+However, the serial-interval distribution describes also describes a renewal process -- in this case, linking symptomatic cases based on their symptom onset dates.
 Since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system of exponential growth, both should provide the same correct link between the reproduction number \RR and the epidemic growth rate $r$.
@@
 In fact, recent theory suggest that using serial-interval can underestimate the reproduction number \citep{britton2019estimation, ganyani2020estimating}.
-However, these studies rely on imprecise definitions of the serial-interval distribution, relying on \emph{intrinsic} distributions of incubation periods and generation intervals that neglect the population-level dynamics of the disease spread.
+These studies rely on \emph{intrinsic} distributions of incubation periods and generation intervals that neglect the population-level dynamics of the disease spread.
+Here we show that, by correctly defining and calculating the ``forward'' serial distribution that connects symptom onset dates, we can resolve this discrepancy.
 During an ongoing epidemic, \emph{all} observed epidemiological delays (e.g., incubation period) between primary (e.g., infection) and secondary (e.g., symptom onset) events are subject to backward biases: when the incidence of primary events is increasing (or decreasing), we are more likely to observe shorter (or longer) intervals.
 Since realized serial intervals depend on three distinct intervals (i.e., incubation period of the infector, incubation period of the infectee, and the generation interval between them), any of these intervals can be subject to backward biases depending on our perspective.
-For example, when we consider ``forward'' serial-interval distributions (i.e., serial intervals from a cohort of infectors that developed symptoms at the same time), the incubation periods of the infectors are subject to backward biases because we have to look backward in time from their symptom onset to infection.
+For example, when we consider forward serial-interval distributions (i.e., serial intervals from a cohort of infectors that developed symptoms at the same time), the incubation periods of the infectors are subject to backward biases because we have to look backward in time from their symptom onset to infection.
 Therefore, the realized incubation period distributions of the infector and the infectee can differ dynamically, even if they are expected to be equivalent intrinsically.
 
-Here, we resolve the apparent discrepancy between generation-interval and serial-interval viewpoints by showing that the relevant interval for the renewal framework is the forward interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
+\jd{I have added a version of this sentence further up, where I feel it goes nicely.
+But I guess some merging will be necessary.} Here, we resolve the apparent discrepancy between generation-interval and serial-interval viewpoints by showing that the relevant interval for the renewal framework is the forward interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
 We develop a cohort-based framework for characterizing and comparing serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
@@
 
-The time delays between two epidemiological events can be defined either within an infected individual (e.g., incubation period: infection and symptom onset of an individual) or between infected individuals (e.g., serial interval: symptom onsets of an infector and an infectee).
-We can further divide these events into \emph{primary} and \emph{secondary} events.
-When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event usually occurs before the secondary event ---
-most epidemiological events that can be observed within an individual have clear direction (e.g., infection to onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
-When we measure an epidemiological time delay between infected individuals (e.g., the serial interval), 
-the primary and secondary events are defined in terms of the direction of transmission:
-the primary event refers to the event that occurs in the infector. 
-Again, some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to develop symptoms before the infector).
+A time delay between two epidemiological events can involve either one infected individual (e.g., incubation period: infection and symptom onset of an individual) or two -- an infector and an infectee (e.g., the serial interval).
+We define the delay as the time difference between one event (the \emph{primary} event) and the other (the \emph{secondary} event).
+In some cases, the primary event always occurs before the secondary event (e.g., the time from infection to onset of symptoms in a single individual, or the generation interval between two individuals.)
+In other cases, the delay can sometimes be negative (e.g., the time from onset of infectiousness to onset of symptoms in a single individuals, or the serial interval between two individuals).
+\jd{Drastically simplified here, hope that's OK.}
 
@@
 Dashed lines represent the mean initial forward delay.
-Intrinsic incubation periods and intrinsic generation-intervals are assumed to be independent of each other.
+Intrinsic incubation periods and intrinsic generation-intervals are assumed to be independent of each other for simplicity.
 See Table 1 for parameter values.

### 2020-09-24 response.tex
morning makeup

@@
 W(\psymp) \psize(\psymp) f_\psymp(\tau) = \ssize(\ssymp) b_\ssymp(\tau) \,,
-\label{eq:match}
+%% \label{eq:match}
 \end{equation}''
@@
 These intervals also play critical role in estimating the reproduction number.
-We have made major revisions to the writing of the manuscript based on the suggestions to provide a transparent and coherent story.
+We have made major revisions to the writing of the manuscript based on these suggestions to provide a transparent and coherent story.
+\jd{We now bridge better with the Abstract, but there's still a gulf between title and intro.
+The last s.~here reads as vague and may trouble the reviewer, unless it's obvious changes are big.
+Do we need rR in the title?}
 
@@
 
-\swp{?????}
+We believe it would be premature to try to explain the biases in Figure 1: the goal of this figure is to explain the intervals (to readers who are likely to be less familiar than the reviewer).
+
+\jd{
+We have, however, added some visual aids to the figure: we color the backward incubation periods (the main driver of differences), and we have made them a little shorter to reflect what happens early in the epidemic.
+We explain this briefly in the caption.
+}
 

### 2020-09-24 serial.tex
morning makeup

@@
 Typically, within-individual forward delay distributions are not directly affected by epidemic dynamics.
-Some realized distributions, like incubation period distributions, are expected to be equivalent to their intrinsic distributions and remain invariant at the time scale of an outbreak.
-Other realized distributions, like the distribution of time from symptom onset to testing, may change over the course of an epidemic due to changes in public health policies.
+Some realized forward distributions, like incubation period distributions, are expected to be equivalent to their intrinsic distributions and remain invariant at the time scale of an outbreak.
+Other realized distributions, like the distribution of time from symptom onset to testing, may change over the course of an epidemic due to changes in public-health policies or individual behavior.
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics.
-For example, infected individuals can become less likely to infect others during late stages of their infection as the epidemic progresses (therefore, leading to ``contraction'' of generation intervals) due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.
+For example, infected individuals forward generation intervals often contract as an epidemic progresses due to the dynamical facto of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{champredon2015intrinsic}.
 
@@
 Conditioning on individuals whose secondary events have occurred at the same time means that we tend to observe shorter (or longer) inter-event delays when cohort size has been increasing (decreasing) through time.
-When incidence is growing exponentially, we can calculate the amount of bias exactly.
+When incidence is growing exponentially, we can calculate the amount of bias directly.
 Assuming that the forward delay distribution ($f_\psymp(\tau) \approx f_0(\tau)$) and the weight parameter ($W(\psymp) \approx W(0)$) remain constant during the exponential growth phase, we can substitute $\psize(t) = \psize(0) \exp(rt)$ in \eref{backward} to obtain:
@@
 where $r$ is the exponential growth rate (and $\left[W(0) \psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
-Thus, even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), assuming all else being equal.
+Thus, even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.
 In general, the backward delay distribution will differ from the forward delay distribution (unless the disease is at equilibrium), even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
@@
 became symptomatic at time $\psymp$, to calculate the forward serial
-interval we first go backward in time to when the infector was
+interval we first go \emph{backward} in time to when the infector was
 infected, and then forward in time to when the infectee was infected,
-and then forward to when the infectee became symptomatic.
+and then forward again to when the infectee became symptomatic.
 In \fref{diagram}B, we see that $\tau_{\rm i1}$ is drawn from
@@
 (\fref{diagram}C).  This conceptual framework demonstrates
-that the distributions of $\tau_{\rm i1}$, $\gtime$, and $\tau_{\rm i2}$ (and therefore
-the distributions of realized serial intervals) depend on the
+\jd{Can we take out event type below? It makes things seem complicated and seems redundant with direction. If I say forward serial interval, do you need to ask primary or secondary?}
+that the distributions of $\tau_{\rm i1}$, $\gtime$, and $\tau_{\rm i2}$ (and therefore the distributions of realized serial intervals) depend on the
 reference cohort, which is defined by an event type (primary or secondary),
@@
 $\sinf$ and $\ssymp$ (realized incubation periods of infectees):
+\jd{Would it be easier to follow if we put a LHS on this equation? 
+$\total (\psymp,\ssymp | \alpha_1, \alpha_2)$?}
 \begin{equation}
@@
 
-We see that the denominator of the forward serial-interval distribution, $\int_{-\infty}^\infty \total(\psymp, \psymp+\tau') \dtau'$, then corresponds to the total number of infections generated by primary cases who themselves developed symptoms at time \psymp\ (\eref{fserial}).
+The denominator of the forward serial-interval distribution (\eref{fserial}) then corresponds to the total number of infections generated by primary cases who themselves developed symptoms at time \psymp.
 Dividing this quantity by the number of individuals who developed symptoms at time at time \psymp, $j(\psymp) = \int_{-\infty}^\infty \total(\psymp-\tau', \psymp) \dtau'$, we obtain the serial reproduction number:
@@
 We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
-Ignoring births and deaths, general changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be described as:
+Ignoring births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be described as:
 \begin{align}
@@
 \end{equation}
-Here, the intrinsic serial-interval distribution $q(\tau)$ does not depend on epidemic dynamics:
+The intrinsic serial-interval distribution $q(\tau)$ does not depend on epidemic dynamics, and is given by:
 \begin{equation}
@@
 We further address how the observed serial intervals, measured through contact tracing, are affected by the right censoring during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial interval data to estimate \Ro.
-Finally, we analyze the serial interval data from the COVID-19 epidemic in China under our framework.
+Finally, we analyze serial-interval data from the COVID-19 epidemic in China under our framework.
 
@@
 Dashed lines represent the mean initial forward delay.
-Intrinsic incubation periods and intrinsic generation-intervals are assumed to be independent of each other for simplicity.
+Intrinsic incubation periods and intrinsic generation intervals are assumed to be independent of each other for simplicity.
 See Table 1 for parameter values.
@@
 In these simulations, both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
-therefore, changes in the forward serial-interval distributions (\fref{epi}D) are predominantly driven by changes in the backward incubation period distribution, whose mean increases over time as the growth rate of disease incidence slows, then becomes negative.
+therefore, changes in the forward serial-interval distributions (\fref{epi}D) are predominantly driven by changes in the backward incubation period distribution, whose mean increases over time as the growth rate of disease incidence slows and then reverses.
 In general, relative contributions of the three distributions depend on their shapes, correlations between intrinsic incubation periods and generation intervals, and overall epidemiological dynamics.
@@
 Similarly, when incidence decreases, we are more likely to observe longer intervals.
-Neglecting these changes in the backward distributions will necessarily bias the inference of the intrinsic distributions from the observed distributions.
+Neglecting these changes will bias the inference of intrinsic distributions from observed distributions.
 

### 2020-09-25 response.tex
friday reboot

--- 2020-09-22 response.tex
@@
 These intervals also play critical role in estimating the reproduction number.
-We have made major revisions to the writing of the manuscript based on the suggestions to provide a transparent and coherent story.
+We have made major revisions to the Introduction to clarify this point and make our story more clear.
+\jd{Do we need to change the title?}
 
@@
 
-\swp{?????}
+\jd{
+One possibility: We have added some visual aids to Figure 1: we color the backward incubation periods (the main driver of differences), and we have made them a little shorter to reflect what happens early in the epidemic.
+We explain this briefly in the caption.
+This does not seem to cover the whole suggestion, though.
+We could add text in S3 referring back to this -- it's hard to think of anything else that wouldn't be a pain, but suggestions are welcome.
+}
 

### 2020-09-25 serial.tex
update
friday reboot

@@
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics.
-For example, infected individuals forward generation intervals often contract as an epidemic progresses due to the dynamical facto of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{champredon2015intrinsic}.
+For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical fact of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.
 
@@
 a cohort of infectees who became symptomatic at time $\ssymp$
-(\fref{diagram}C).  This conceptual framework demonstrates
-\jd{Can we take out event type below? It makes things seem complicated and seems redundant with direction. If I say forward serial interval, do you need to ask primary or secondary?}
-that the distributions of $\tau_{\rm i1}$, $\gtime$, and $\tau_{\rm i2}$ (and therefore the distributions of realized serial intervals) depend on the
-reference cohort, which is defined by an event type (primary or secondary),
-temporal direction (forward or backward), and a particular reference time.
+(\fref{diagram}C).  
+This conceptual framework demonstrates that the distributions of $\tau_{\rm i1}$, $\gtime$, and $\tau_{\rm i2}$ (and therefore the distributions of realized serial intervals) depend on the reference cohort, which is defined by temporal direction (forward or backward) and a particular reference time.
 

### 2020-09-27 response.tex
update

--- 2020-09-22 response.tex
@@
 
-JD: The reviewers' main concern is that they don't feel we have made a strong argument in the general case.
-Your response seems to focus more on the clarity of our claim than the clarity of our arguments.
-
 The special version is only presented in the supplementary material. We do not assume this in the main text. We have now made this distinction clear in the text:
@@
 This statement is proved in the supplement and illustrated in a general context in Figure 2A. We now say this explicitly in the main text:
-
-JD: In early drafts, it's probably better to just list line numbers for a clearly specified MS version than to put quotes that may change.
 
@@
 
-\swp{?????}
+We have added some visual aids to Figure 1: we color intrinsic, backward, and forward intervals and explain them breifly in the caption:
+
+``
+Intrinsic intervals (black) reflect average of individual characteristics and are not dependent on population-level dynamics.
+  Forward intervals (green) can change due to epidemiological dynamics (e.g., contraction of generation intervals through susceptible depletion).
+  Backward intervals (blue) can change due to changes in cohort sizes even when forward intervals remain time-invariant.
+''
+
+\swp{Doesn't this paragraph visually communicate the insights???? It was already there in the previous version...}
+
+``The forward serial-interval distributions depend on distributions of three intervals
+(\fref{diagram}B): (i) the backward incubation period, (ii) the forward generation interval, and (iii) the forward incubation period.
+In these simulations, both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
+therefore, changes in the forward serial-interval distributions (\fref{epi}D) are predominantly driven by changes in the backward incubation period distribution, whose mean increases over time as the growth rate of disease incidence slows and then reverses.
+In general, relative contributions of the three distributions depend on their shapes, correlations between intrinsic incubation periods and generation intervals, and overall epidemiological dynamics.''
 

### 2020-09-27 serial.tex
update

@@
 It is well established that this renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
-However, the serial-interval distribution describes also describes a renewal process -- in this case, linking symptomatic cases based on their symptom onset dates.
+However, the serial-interval distribution also describes a renewal process --- in this case, linking symptomatic cases based on their symptom onset dates.
 Since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system of exponential growth, both should provide the same correct link between the reproduction number \RR and the epidemic growth rate $r$.
@@
 In fact, recent theory suggest that using serial-interval can underestimate the reproduction number \citep{britton2019estimation, ganyani2020estimating}.
-These studies rely on \emph{intrinsic} distributions of incubation periods and generation intervals that neglect the population-level dynamics of the disease spread.
-Here we show that, by correctly defining and calculating the ``forward'' serial distribution that connects symptom onset dates, we can resolve this discrepancy.
+However, these studies rely on \emph{intrinsic} distributions of incubation periods and generation intervals that neglect the population-level dynamics of the disease spread.
+
+Here we show that, by correctly defining and calculating the ``forward'' serial-interval distribution (i.e., a distribution of serial intervals from a cohort of infectors that developed symptoms at the same time) that connects symptom onset dates, we can resolve this discrepancy;
+these intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
 During an ongoing epidemic, \emph{all} observed epidemiological delays (e.g., incubation period) between primary (e.g., infection) and secondary (e.g., symptom onset) events are subject to backward biases: when the incidence of primary events is increasing (or decreasing), we are more likely to observe shorter (or longer) intervals.
 Since realized serial intervals depend on three distinct intervals (i.e., incubation period of the infector, incubation period of the infectee, and the generation interval between them), any of these intervals can be subject to backward biases depending on our perspective.
-For example, when we consider forward serial-interval distributions (i.e., serial intervals from a cohort of infectors that developed symptoms at the same time), the incubation periods of the infectors are subject to backward biases because we have to look backward in time from their symptom onset to infection.
+In particular, when we consider forward serial-interval distributions, the incubation periods of the infectors are subject to backward biases because we have to look backward in time from their symptom onset to infection.
 Therefore, the realized incubation period distributions of the infector and the infectee can differ dynamically, even if they are expected to be equivalent intrinsically.
 
-\jd{I have added a version of this sentence further up, where I feel it goes nicely.
-But I guess some merging will be necessary.} Here, we resolve the apparent discrepancy between generation-interval and serial-interval viewpoints by showing that the relevant interval for the renewal framework is the forward interval, and that the forward serial intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
-We develop a cohort-based framework for characterizing and comparing serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
+We develop a cohort-based framework for characterizing and comparing realized serial intervals, as well as any other epidemiological delays, and show that the initial forward serial-interval distribution correctly estimates \RR from $r$.
 Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of \RR.
@@
 We define the delay as the time difference between one event (the \emph{primary} event) and the other (the \emph{secondary} event).
-In some cases, the primary event always occurs before the secondary event (e.g., the time from infection to onset of symptoms in a single individual, or the generation interval between two individuals.)
+In some cases, the primary event always occurs before the secondary event (e.g., the time from infection to onset of symptoms in a single individual, or the generation interval between two individuals).
 In other cases, the delay can sometimes be negative (e.g., the time from onset of infectiousness to onset of symptoms in a single individuals, or the serial interval between two individuals).
-\jd{Drastically simplified here, hope that's OK.}
 
@@
 For example, an infectious contact results in infection only if the contacted individual is susceptible (and has not already been infected);
-this is one mechanism that causes realized generation intervals (time between actual infection events) to differ from from the intrinsic generation intervals (time between infection and infectious contacts).
+this is one mechanism that causes realized generation intervals (time between actual infection events) to differ from from the intrinsic generation intervals (time between infection and infectious contacts) \citep{park2020inferring}.
 
@@
 Likewise, we define the backward delay distribution $b_\ssymp(\tau)$ for a secondary cohort at time $\ssymp$:
-The backward delay distribution describes the time delays between a primary and secondary host given that the secondary event occurred at time $\ssymp$.
+The backward delay distribution describes the time delays between a primary and secondary events given that the secondary event occurred at time $\ssymp$.
 For example, the backward incubation period distribution at time $\ssymp$ describes incubation periods for a \emph{cohort} of individuals who became symptomatic at time $\ssymp$.
@@
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics.
-For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical fact of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.
+For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical fact of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{kenah2008generation, nishiura2010time, champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.
 
@@
 \includegraphics[width=\textwidth]{serial_guide.pdf}
-\caption{\textbf{Illustration of intrinsic,
+\caption{
+\textbf{Illustration of intrinsic,
     forward and backward serial intervals.}  (A) The intrinsic serial
@@
   backward generation-interval distribution; and $\tau_{\rm i2}$ is drawn from the
-  backward incubation period distribution.}
+  backward incubation period distribution.
+  Intrinsic intervals (black) reflect average of individual characteristics and are not dependent on population-level dynamics.
+  Forward intervals (green) can change due to epidemiological dynamics (e.g., contraction of generation intervals through susceptible depletion).
+  Backward intervals (blue) can change due to changes in cohort sizes even when forward intervals remain time-invariant.
+}
 \label{fig:diagram}
@@
 $\sinf$ and $\ssymp$ (realized incubation periods of infectees):
-\jd{Would it be easier to follow if we put a LHS on this equation? 
-$\total (\psymp,\ssymp | \alpha_1, \alpha_2)$?}
 \begin{equation}
-\underbrace{\Rc (\pinf)}_{\substack{\text{case} \\ \text{reproduction} \\ \text{number}}} 
+\total (\psymp,\ssymp | \alpha_1, \alpha_2)=\underbrace{\Rc (\pinf)}_{\substack{\text{case} \\ \text{reproduction} \\ \text{number}}} 
 \times 
@@
 \begin{equation}
-\total (\psymp,\ssymp) = \int_{-\infty}^{\psymp} \int_{\pinf}^{\ssymp} \Rc (\pinf) i(\pinf) h_{\pinf}(\psymp-\pinf, \sinf - \pinf) \idist_{\sinf}(\ssymp - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
+\total (\psymp,\ssymp) = \int_{-\infty}^{\psymp} \int_{\pinf}^{\ssymp} \total (\psymp,\ssymp | \alpha_1, \alpha_2) \, \mathrm{d}\sinf\,\mathrm{d}\pinf.
 \end{equation}
@@
 The forward serial-interval distributions depend on distributions of three intervals
-(\fref{diagram}): (i) the backward incubation period, (ii) the forward generation interval, and (iii) the forward incubation period.
+(\fref{diagram}B): (i) the backward incubation period, (ii) the forward generation interval, and (iii) the forward incubation period.
 In these simulations, both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;

### 2020-09-27 serial_guide.R

@@ -49,14 +49,18 @@ g1 <- ggplot(arrow) +
   )
 
 g2 <- ggplot(arrow) +
+  geom_segment(aes(0.5, 0, xend=0.5, yend=0.2), lty=2) +
+  geom_segment(aes(1.5, 0, xend=1.5, yend=0.4), lty=2) +
+  geom_segment(aes(2.5, 0, xend=2.5, yend=0.3), lty=2) +
+  geom_segment(aes(3.5, 0, xend=3.5, yend=0.4), lty=2) +
   geom_point(aes(0.5, 0), size=3) +
   geom_point(aes(1.5, 0), size=3) +
   geom_point(aes(2.5, 0), size=3) +
   geom_point(aes(3.5, 0), size=3) +
-  geom_point(aes(0.5, 0.2), size=3) +
-  geom_point(aes(1.5, 0.4), size=3) +
-  geom_point(aes(2.5, 0.3), size=3) +
-  geom_point(aes(1.5, 0.1), size=3) +
+  geom_point(aes(0.5, 0.2), size=3, col="green") +
+  geom_point(aes(1.5, 0.4), size=3, col="green") +
+  geom_point(aes(2.5, 0.3), size=3, col="green") +
+  geom_point(aes(1.5, 0.1), size=3, col="blue") +
   annotate("text", x=1.5, y=-0.05, label="$p$") +
   annotate("text", x=0.5, y=-0.05, label="$p-\\tau_{\\rm i1}$") +
   annotate("text", x=0.5, y=-0.1, label="Infector") +
@@ -65,14 +69,10 @@ g2 <- ggplot(arrow) +
   annotate("text", x=2.5, y=-0.05, label="$p-\\tau_{\\rm i1}+\\tau_{\\rm g}$") +
   annotate("text", x=3.5, y=-0.05, label="$p-\\tau_{\\rm i1}+\\tau_{\\rm g}+\\tau_{\\rm i2}$") +
   geom_segment(aes(x, y, xend=x1, yend=y1), arrow = arrow(length = unit(0.2, "inches")), lwd=1) +
-  geom_segment(aes(0.5, 0, xend=0.5, yend=0.2), lty=2) +
-  geom_segment(aes(1.5, 0, xend=1.5, yend=0.4), lty=2) +
-  geom_segment(aes(2.5, 0, xend=2.5, yend=0.3), lty=2) +
-  geom_segment(aes(3.5, 0, xend=3.5, yend=0.4), lty=2) +
[…]

### 2020-09-27 response.tex
Handing back for now.

@@
 
-\rev{Reviewr \#3}
+\rev{Reviewer \#3}
 
@@
 Incidence trajectories of stochastic simulations are slightly shifted (\fref{epi}A) due to differences in initial conditions. 
+\jd{This s. does not make a lot of sense. How hard would it be to start from the appropriate number in a deterministic simulation instead of making this awkward explanation?}
 We set the distribution of infection time of initially infected individuals (beginning from a small number of infected individuals) for deterministic simulations such that the system can exhibit exponential growth immediately (Supplementary Materials).
@@
 
+\jd{Pretty sure the question here is why does it say ``delay'' instead of ``serial interval'' on the y axis of B and C.}
 We are plotting serial intervals, after grouping them based on the symptom onset dates of primary (forward) and secondary (backward) cases. We have added the following sentence to further clarify:
@@
 We show that, instead of aggregating all measured serial intervals, one could rearrange them based on symptom onset date of a primary case and take the cohort-based average.
-We further demonstrate how this could be done with an illusrative line list (Figure 4).
+We further demonstrate how this could be done with an illustrative line list (Figure 4).
 In addition, there is a simple way to calculate the intrinsic serial interval distribution.
@@
 
+\jd{I will edit this in the MS.}
 ``Here, we lay out a few practical principles for analyzing and interpreting the serial interval data.

### 2020-09-27 serial.tex
Handing back for now.

@@
 Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of \RR.
-For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro estimates based on aggregated serial interval data underestimated \Ro by 50\%--60\%.
+For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro estimates based on aggregated serial-interval data underestimated \Ro by 50\%--60\%.
 We further lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the initial reproduction number during the early stages of an outbreak.
@@
 We use parameter estimates for COVID-19 to characterize the degree to which the realized serial-interval distribution can change over the course of an epidemic and evaluate how different definitions of the serial-interval distribution can affect the Euler-Lotka estimates of \Ro.
-We further address how the observed serial intervals, measured through contact tracing, are affected by the right censoring during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial interval data to estimate \Ro.
+We further address how the observed serial intervals, measured through contact tracing, are affected by the right censoring during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial-interval data to estimate \Ro.
 Finally, we analyze serial-interval data from the COVID-19 epidemic in China under our framework.
@@
 
-Here, we lay out a few practical principles for analyzing and interpreting the serial interval data.
+Here, we lay out a few practical principles for analyzing and interpreting serial-interval data.
 First, serial intervals should be cohorted based on the symptom onset date whenever possible.
-Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but their distributions are expected to change due to epidemic dynamics.
-Even when all realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR})---something true of realized generation intervals as well \citep{park2020inferring}.
+Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals is expected to differ from this expectation, and to change through time due to epidemic dynamics.
+\jd{Maybe leave out this s., it's not highly relevant and we're trying to be practical.
+}Even when all realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR})---something true of realized generation intervals as well \citep{park2020inferring}.
 Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases.
-Third, applying serial interval information from one epidemic to another should be avoided, even for same diseases, because serial intervals are epidemic-specific, rather than disease-specific.
-Finally, serial interval data should be accompanied by a trajectory of the epidemic curve, whenever possible, to properly assess them within the epidemiological context.
-In practice, these recommendations can be still difficult to follow due to limited serial interval information;
-nonetheless, we believe that following these approaches will help interpret serial interval data and understand transmission dynamics at the individual-level.
+Third, applying serial interval information from one epidemic of a given disease to another should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.
+Finally, serial-interval data should be accompanied by a trajectory of the epidemic curve, whenever possible, to provide epidemiological context.
+In practice, these recommendations will sometimes be hard to follow, due to limited data about serial intervals, but these issues should be kept in mind when interpreting serial-interval data and understand transmission dynamics at the individual-level.
 

### 2020-09-28 response.tex
update

--- 2020-09-27 response.tex
@@
 
-We now comment on this:
+These differences were driven by stochasticity due to small number of initial infections. We were starting deterministic simulations with a very small number to avoid initial transient dynamics.
+We now set $t=0$ to the first time point when daily incidence is greater than 100 in order to make a fair comparison and comment on this in figure caption:
 
-``Stochastic simulations confirm our deterministic calculations albeit minor differences due to transient dynamics.
-Incidence trajectories of stochastic simulations are slightly shifted (\fref{epi}A) due to differences in initial conditions. 
-We set the distribution of infection time of initially infected individuals (beginning from a small number of infected individuals) for deterministic simulations such that the system can exhibit exponential growth immediately (Supplementary Materials).
-This is not possible for stochastic simulations because the number of initially infected individuals cannot be smaller than 1; instead, we begin with 10 infected indiivduals who are infected at time $t=0$.
-In addition, the mean backward intervals of stochastic simulations begins from smaller values due to left-censoring.''
+``In order to remove possible transient dynamics (e.g., left-censoring of time delays and initial stochasticity due to low number of infections), we set $t=0$ to the first time point when daily incidence is greater than 100.''
 
@@
 
+We have also changed the figure axis title to avoid confusion (from ``delay'' to ``serial interval'').
+
 \revtext{Could the results be simplified to an extend that medical doctors that actually "measure" backward serial intervals directly could recalculate the intrinsic serial intervals (in some simple approximation).
@@
 
-``Here, we lay out a few practical principles for analyzing and interpreting the serial interval data.
+``Here, we lay out a few practical principles for analyzing and interpreting serial-interval data.
 First, serial intervals should be cohorted based on the symptom onset date whenever possible.
-Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but their distributions are expected to change due to epidemic dynamics.
-Even when all realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR})---something true of realized generation intervals as well \citep{park2020inferring}.
-Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases.
-Third, applying serial interval information from one epidemic to another should be avoided, even for same diseases, because serial intervals are epidemic-specific, rather than disease-specific.
-Finally, serial interval data should be accompanied by a trajectory of the epidemic curve, whenever possible, to properly assess them within the epidemiological context.
-In practice, these recommendations can be still difficult to follow due to limited serial interval information;
-nonetheless, we believe that following these approaches will help interpret serial interval data and understand transmission dynamics at the individual-level.''
+Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals is expected to differ from this expectation, and to change through time due to epidemic dynamics.
+Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases:
+Even when \emph{all} realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR}).
+Third, applying serial interval information from one epidemic of a given disease to another should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.
+Finally, serial-interval data should be accompanied by a trajectory of the epidemic curve, whenever possible, to provide epidemiological context.
+In practice, these recommendations will sometimes be hard to follow, due to limited data about serial intervals, but these issues should be kept in mind when interpreting serial-interval data and understand transmission dynamics at the individual-level.''
 

### 2020-09-28 serial.tex
update

@@
 Dashed lines represent the mean initial forward delay.
-Intrinsic incubation periods and intrinsic generation intervals are assumed to be independent of each other for simplicity.
+In order to remove possible transient dynamics (e.g., left-censoring of time delays and initial stochasticity due to low number of infections), we set $t=0$ to the first time point when daily incidence is greater than 100.
+Intrinsic incubation periods and intrinsic generation intervals are assumed to be independent of each other for simplicity; simulations with correlated intrinsic incubation periods and intrinsic generation intervals are provided in Supplementary Materials.
 See Table 1 for parameter values.
@@
 Neglecting these changes will bias the inference of intrinsic distributions from observed distributions.
-
-Stochastic simulations confirm our deterministic calculations albeit minor differences due to transient dynamics.
-Incidence trajectories of stochastic simulations are slightly shifted to earlier time (\fref{epi}A) due to differences in initial conditions. 
-We set the distribution of infection time of initially infected individuals (beginning from a very small number of infected individuals, $<<1$) for deterministic simulations such that the system can exhibit exponential growth immediately (Supplementary Materials).
-This is not possible for stochastic simulations because the number of initially infected individuals cannot be smaller than 1; instead, we begin with 10 infected individuals who are infected at time $t=0$.
-In addition, the mean backward intervals of stochastic simulations begins from smaller values due to left-censoring.
 
@@
 Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals is expected to differ from this expectation, and to change through time due to epidemic dynamics.
-\jd{Maybe leave out this s., it's not highly relevant and we're trying to be practical.
-}Even when all realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR})---something true of realized generation intervals as well \citep{park2020inferring}.
-Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases.
+Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases:
+Even when \emph{all} realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR}).
 Third, applying serial interval information from one epidemic of a given disease to another should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.

### 2020-09-28 serial_analysis.tex
update

@@
-% Created by tikzDevice version 0.12.3 on 2020-09-20 18:46:20
+% Created by tikzDevice version 0.12.3 on 2020-09-27 20:19:45
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (312.33,437.63) {Forward delay (days)};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (312.33,437.63) {Serial interval (days)};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 19.68,148.55) {Backward delay (days)};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 19.68,148.55) {Serial interval(days)};
 \end{scope}

### 2020-09-28 forward.R

@@ -11,7 +11,7 @@ rr <- renewal_det()
 
 summfun <- function(dd) {
   dd %>%
-    filter(!is.na(cohort), !is.na(tdiff), cohort > 0, cohort <= 100) %>%
+    filter(!is.na(cohort), !is.na(tdiff), cohort <= 100) %>%
     mutate(
       cc=cut(cohort, tcut)
     ) %>%
@@ -46,6 +46,19 @@ sir_data2 <- sir_data %>%
     cases=tail(infected, 1)-head(infected,1)
   )
 
+sir_data2_time <- sir_data2 %>%
+  filter(cases >= 100) %>%
+  group_by(sim) %>%
+  summarize(
+    min=min(day)
+  )
+
+sir_data3 <- sir_data2 %>%
+  merge(sir_data2_time) %>%
+  mutate(
+    day=day-min
+  )
+
 detdata2 <- detdata %>%
   mutate(
     day=floor(tvec)
@@ -53,12 +66,18 @@ detdata2 <- detdata %>%
   group_by(day) %>%
   summarize(
     cases=tail(ci, 1)-head(ci,1)
+  ) %>%
+  mutate(
+    min=min(day[cases >= 100])
+  ) %>%
+  mutate(
+    day=day-min
   )
 
-g1 <- ggplot(sir_data2) +
+g1 <- ggplot(sir_data3) +
   geom_line(aes(day, cases, col="Stochastic", group=sim)) +
   geom_line(data=detdata2, aes(day, cases, col="Deterministic"), lwd=1) +
-  scale_x_continuous("Time (days)", expand=c(0, 0), limits=c(0, 82)) +
+  scale_x_continuous("Time (days)", expand=c(0, 0), limits=c(-10, 52)) +
   scale_y_continuous("Daily incidence", expand=c(0, 0), limits=c(1, 2400)) +
   scale_color_manual(values=c(1, "#D55E00")) +
   ggtitle("A") +
@@ -68,7 +87,7 @@ g1 <- ggplot(sir_data2) +
     legend.position = c(0.1, 0.7)
   )
 
-tcut <- 0:40*2
+tcut <- (-20):20*4
 
 sir_sim <- lapply(simlist, function(x) {
   data.frame(
@@ -84,12 +103,17 @@ sir_sim <- lapply(simlist, function(x) {
 
 incdata0 <- data.frame(
   cohort=sir_sim$t_infected,
[…]

### 2020-09-28 serial_analysis.R

@@ -140,7 +140,7 @@ g2 <- ggplot(rr) +
   geom_errorbar(data=rr_summ, aes(cohort, ymin=lwr, ymax=upr), width=0) +
   geom_smooth(aes(cohort, serial), col=1, fill=1, fullrange=TRUE, se=FALSE) +
   scale_x_date("Symptom onset date (infector)", expand=c(0, 0)) +
-  scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(-12, 21)) +
+  scale_y_continuous("Serial interval (days)", expand=c(0, 0), limits=c(-12, 21)) +
   scale_size_area(max_size=4) +
   coord_fixed(clip="off") +
   ggtitle("B. Forward serial interval") +
@@ -173,7 +173,7 @@ g3 <- ggplot(rr) +
   geom_errorbar(data=rr_summ2, aes(cohort, ymin=lwr, ymax=upr), width=0) +
   geom_smooth(aes(cohort2, serial), col=1, fill=1, se=FALSE) +
   scale_x_date("Symptom onset date (infectee)", expand=c(0, 0)) +
-  scale_y_continuous("Backward delay (days)", expand=c(0, 0), limits=c(-11, 19)) +
+  scale_y_continuous("Serial interval(days)", expand=c(0, 0), limits=c(-11, 19)) +
   coord_fixed(clip="off") +
   ggtitle("C. Backward serial interval") +
   theme(

### 2020-09-28 forward_corr.tex
update

% Created by tikzDevice version 0.12.3 on 2020-09-28 00:14:35
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.95}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,  0.00) -- (  0.00,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 30.43,  0.00) -- ( 30.43,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.86,  0.00) -- ( 60.86,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.29,  0.00) -- ( 91.29,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.72,  0.00) -- (121.72,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.15,  0.00) -- (152.15,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.58,  0.00) -- (182.58,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.01,  0.00) -- (213.01,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.44,  0.00) -- (243.44,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.87,  0.00) -- (273.87,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.29,  0.00) -- (304.29,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.72,  0.00) -- (334.72,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.15,  0.00) -- (365.15,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.58,  0.00) -- (395.58,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.01,  0.00) -- (426.01,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.44,  0.00) -- (456.44,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.87,  0.00) -- (486.87,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.30,  0.00) -- (517.30,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.73,  0.00) -- (547.73,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (578.16,  0.00) -- (578.16,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,  0.00) -- (578.16,  0.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 30.43) -- (578.16, 30.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 60.86) -- (578.16, 60.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 91.29) -- (578.16, 91.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,121.72) -- (578.16,121.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,152.15) -- (578.16,152.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,182.58) -- (578.16,182.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,213.01) -- (578.16,213.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,243.44) -- (578.16,243.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,273.87) -- (578.16,273.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,304.29) -- (578.16,304.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,334.72) -- (578.16,334.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,365.15) -- (578.16,365.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,395.58) -- (578.16,395.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,426.01) -- (578.16,426.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,456.44) -- (578.16,456.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,486.87) -- (578.16,486.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,517.30) -- (578.16,517.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,547.73) -- (578.16,547.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,578.16) -- (578.16,578.16);
\end{scope}
\begin{scope}
\path[clip] (  0.00,412.97) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,412.97) rectangle (578.16,578.16);
\end{scope}
\begin{scope}
\path[clip] ( 40.70,443.99) rectangle (572.66,555.28);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.70,443.99) rectangle (572.66,555.28);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.87) --
	( 49.28,444.83) --
	( 57.86,444.83) --
	( 66.44,445.43) --
	( 75.02,445.66) --
	( 83.60,446.22) --
	( 92.18,446.31) --
	(100.76,447.61) --
	(109.34,447.61) --
	(117.92,448.49) --
	(126.50,449.19) --
	(135.08,450.49) --
	(143.66,451.74) --
	(152.24,454.24) --
	(160.82,455.12) --
	(169.40,458.60) --
	(177.98,460.51) --
	(186.56,463.75) --
	(195.14,469.23) --
	(203.72,472.61) --
	(212.30,477.86) --
	(220.88,481.80) --
	(229.46,489.82) --
	(238.04,497.94) --
	(246.62,502.53) --
	(255.20,508.10) --
	(263.78,517.98) --
	(272.36,523.55) --
	(280.94,528.79) --
	(289.52,534.22) --
	(298.10,533.76) --
	(306.68,535.43) --
	(315.26,531.67) --
	(323.84,527.31) --
	(332.42,522.81) --
	(341.00,515.11) --
	(349.58,506.34) --
	(358.16,499.06) --
	(366.74,490.57) --
	(375.32,481.01) --
	(383.90,474.65) --
	(392.48,471.50) --
	(401.06,463.52) --
	(409.64,462.18) --
	(418.22,456.66) --
	(426.80,454.47) --
	(435.38,452.02) --
	(443.96,450.86) --
	(452.54,449.28) --
	(461.12,448.63) --
	(469.70,447.61) --
	(478.28,446.68) --
	(486.86,445.61) --
	(495.44,445.89) --
	(504.02,445.15) --
	(512.60,444.87) --
	(521.18,444.55) --
	(529.76,444.50) --
	(538.34,444.36) --
	(546.92,444.13) --
	(555.50,444.22) --
	(564.08,444.08) --
	(572.66,443.99);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
	( 49.28,444.73) --
	( 57.86,444.92) --
	( 66.44,444.92) --
	( 75.02,444.96) --
	( 83.60,445.71) --
	( 92.18,446.68) --
	(100.76,445.85) --
	(109.34,447.19) --
	(117.92,447.52) --
	(126.50,448.72) --
	(135.08,449.14) --
	(143.66,449.79) --
	(152.24,451.41) --
	(160.82,453.64) --
	(169.40,455.17) --
	(177.98,458.28) --
	(186.56,459.44) --
	(195.14,462.45) --
	(203.72,467.93) --
	(212.30,471.41) --
	(220.88,478.46) --
	(229.46,479.53) --
	(238.04,488.11) --
	(246.62,497.48) --
	(255.20,501.28) --
	(263.78,507.22) --
	(272.36,516.82) --
	(280.94,521.69) --
	(289.52,526.84) --
	(298.10,534.27) --
	(306.68,533.80) --
	(315.26,534.22) --
	(323.84,531.53) --
	(332.42,529.67) --
	(341.00,522.16) --
	(349.58,514.60) --
	(358.16,508.15) --
	(366.74,500.45) --
	(375.32,493.03) --
	(383.90,479.80) --
	(392.48,475.16) --
	(401.06,472.94) --
	(409.64,463.98) --
	(418.22,462.55) --
	(426.80,458.60) --
	(435.38,455.54) --
	(443.96,452.99) --
	(452.54,451.51) --
	(461.12,449.65) --
	(469.70,448.30) --
	(478.28,448.03) --
	(486.86,447.47) --
	(495.44,446.36) --
	(504.02,445.20) --
	(512.60,445.61) --
	(521.18,444.92) --
	(529.76,444.69) --
	(538.34,444.87) --
	(546.92,444.22) --
	(555.50,444.22) --
	(564.08,444.22) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
	( 49.28,444.59) --
	( 57.86,444.87) --
	( 66.44,444.87) --
	( 75.02,444.92) --
	( 83.60,445.48) --
	( 92.18,446.26) --
	(100.76,445.85) --
	(109.34,446.77) --
	(117.92,447.38) --
	(126.50,448.91) --
	(135.08,448.86) --
	(143.66,449.74) --
	(152.24,450.67) --
	(160.82,451.97) --
	(169.40,455.68) --
	(177.98,456.98) --
	(186.56,459.21) --
	(195.14,461.57) --
	(203.72,466.81) --
	(212.30,469.97) --
	(220.88,475.30) --
	(229.46,480.13) --
	(238.04,486.11) --
	(246.62,494.09) --
	(255.20,499.75) --
	(263.78,504.90) --
	(272.36,514.92) --
	(280.94,519.79) --
	(289.52,525.64) --
	(298.10,533.43) --
	(306.68,530.37) --
	(315.26,535.47) --
	(323.84,535.52) --
	(332.42,528.79) --
	(341.00,524.29) --
	(349.58,518.26) --
	(358.16,510.98) --
	(366.74,502.95) --
	(375.32,492.24) --
	(383.90,485.97) --
	(392.48,475.16) --
	(401.06,471.04) --
	(409.64,468.58) --
	(418.22,464.03) --
	(426.80,458.19) --
	(435.38,456.47) --
	(443.96,453.59) --
	(452.54,451.69) --
	(461.12,449.93) --
	(469.70,448.86) --
	(478.28,447.38) --
	(486.86,447.38) --
	(495.44,446.31) --
	(504.02,445.52) --
	(512.60,445.89) --
	(521.18,444.78) --
	(529.76,444.92) --
	(538.34,444.73) --
	(546.92,444.45) --
	(555.50,444.55) --
	(564.08,444.22) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
	( 49.28,445.29) --
	( 57.86,444.73) --
	( 66.44,445.52) --
	( 75.02,445.71) --
	( 83.60,445.94) --
	( 92.18,446.54) --
	(100.76,447.19) --
	(109.34,448.44) --
	(117.92,448.49) --
	(126.50,449.60) --
	(135.08,450.39) --
	(143.66,451.32) --
	(152.24,453.78) --
	(160.82,456.89) --
	(169.40,458.56) --
	(177.98,461.06) --
	(186.56,464.08) --
	(195.14,467.79) --
	(203.72,472.85) --
	(212.30,479.62) --
	(220.88,482.40) --
	(229.46,491.59) --
	(238.04,496.88) --
	(246.62,500.63) --
	(255.20,511.67) --
	(263.78,517.61) --
	(272.36,521.51) --
	(280.94,527.91) --
	(289.52,532.83) --
	(298.10,533.94) --
	(306.68,534.73) --
	(315.26,530.42) --
	(323.84,527.91) --
	(332.42,524.11) --
	(341.00,513.39) --
	(349.58,508.89) --
	(358.16,496.69) --
	(366.74,489.92) --
	(375.32,482.45) --
	(383.90,471.78) --
	(392.48,470.99) --
	(401.06,464.40) --
	(409.64,460.04) --
	(418.22,456.10) --
	(426.80,454.66) --
	(435.38,452.62) --
	(443.96,450.35) --
	(452.54,449.19) --
	(461.12,448.21) --
	(469.70,446.73) --
	(478.28,446.82) --
	(486.86,445.99) --
	(495.44,445.61) --
	(504.02,445.01) --
	(512.60,445.01) --
	(521.18,444.87) --
	(529.76,444.64) --
	(538.34,444.50) --
	(546.92,444.27) --
	(555.50,444.04) --
	(564.08,444.18) --
	(572.66,443.99);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
	( 49.28,444.64) --
	( 57.86,444.83) --
	( 66.44,444.96) --
	( 75.02,445.24) --
	( 83.60,445.52) --
	( 92.18,446.03) --
	(100.76,445.85) --
	(109.34,447.52) --
	(117.92,447.70) --
	(126.50,448.72) --
	(135.08,448.72) --
	(143.66,450.95) --
	(152.24,450.72) --
	(160.82,453.41) --
	(169.40,455.12) --
	(177.98,457.86) --
	(186.56,461.20) --
	(195.14,463.24) --
	(203.72,465.70) --
	(212.30,470.25) --
	(220.88,478.55) --
	(229.46,483.05) --
	(238.04,487.83) --
	(246.62,496.09) --
	(255.20,498.78) --
	(263.78,507.68) --
	(272.36,517.98) --
	(280.94,520.07) --
	(289.52,524.38) --
	(298.10,531.39) --
	(306.68,534.13) --
	(315.26,534.27) --
	(323.84,531.67) --
	(332.42,528.65) --
	(341.00,526.29) --
	(349.58,513.62) --
	(358.16,507.31) --
	(366.74,502.02) --
	(375.32,490.57) --
	(383.90,484.35) --
	(392.48,477.02) --
	(401.06,473.22) --
	(409.64,465.52) --
	(418.22,460.97) --
	(426.80,458.37) --
	(435.38,454.89) --
	(443.96,452.85) --
	(452.54,451.32) --
	(461.12,448.63) --
	(469.70,448.58) --
	(478.28,447.42) --
	(486.86,446.68) --
	(495.44,446.31) --
	(504.02,445.75) --
	(512.60,445.29) --
	(521.18,445.15) --
	(529.76,444.64) --
	(538.34,444.32) --
	(546.92,444.50) --
	(555.50,444.41) --
	(564.08,444.36) --
	(572.66,444.22);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.32) --
	( 49.28,444.73) --
	( 57.86,444.83) --
	( 66.44,445.29) --
	( 75.02,445.10) --
	( 83.60,445.43) --
	( 92.18,446.08) --
	(100.76,446.54) --
	(109.34,446.82) --
	(117.92,448.26) --
	(126.50,448.63) --
	(135.08,449.42) --
	(143.66,450.44) --
	(152.24,451.92) --
	(160.82,454.38) --
	(169.40,456.28) --
	(177.98,457.21) --
	(186.56,461.43) --
	(195.14,465.10) --
	(203.72,468.62) --
	(212.30,472.06) --
	(220.88,476.60) --
	(229.46,482.68) --
	(238.04,491.35) --
	(246.62,496.64) --
	(255.20,505.78) --
	(263.78,511.49) --
	(272.36,516.17) --
	(280.94,525.50) --
	(289.52,528.14) --
	(298.10,530.69) --
	(306.68,535.15) --
	(315.26,535.66) --
	(323.84,530.42) --
	(332.42,526.05) --
	(341.00,520.02) --
	(349.58,514.46) --
	(358.16,504.16) --
	(366.74,498.50) --
	(375.32,490.84) --
	(383.90,481.06) --
	(392.48,474.24) --
	(401.06,468.35) --
	(409.64,466.49) --
	(418.22,461.11) --
	(426.80,456.70) --
	(435.38,454.34) --
	(443.96,452.67) --
	(452.54,451.92) --
	(461.12,449.74) --
	(469.70,448.21) --
	(478.28,447.28) --
	(486.86,447.01) --
	(495.44,445.71) --
	(504.02,445.52) --
	(512.60,445.20) --
	(521.18,445.34) --
	(529.76,444.55) --
	(538.34,444.41) --
	(546.92,444.18) --
	(555.50,444.13) --
	(564.08,444.27) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
	( 49.28,444.83) --
	( 57.86,445.20) --
	( 66.44,444.96) --
	( 75.02,445.61) --
	( 83.60,445.75) --
	( 92.18,446.59) --
	(100.76,446.91) --
	(109.34,447.79) --
	(117.92,447.93) --
	(126.50,449.65) --
	(135.08,450.53) --
	(143.66,451.13) --
	(152.24,454.38) --
	(160.82,454.80) --
	(169.40,458.70) --
	(177.98,460.32) --
	(186.56,462.87) --
	(195.14,467.37) --
	(203.72,472.06) --
	(212.30,476.60) --
	(220.88,480.13) --
	(229.46,489.04) --
	(238.04,495.25) --
	(246.62,502.53) --
	(255.20,509.35) --
	(263.78,515.52) --
	(272.36,523.60) --
	(280.94,528.37) --
	(289.52,530.23) --
	(298.10,534.64) --
	(306.68,537.42) --
	(315.26,530.55) --
	(323.84,529.86) --
	(332.42,520.72) --
	(341.00,515.20) --
	(349.58,504.21) --
	(358.16,501.47) --
	(366.74,492.33) --
	(375.32,480.92) --
	(383.90,476.88) --
	(392.48,471.45) --
	(401.06,463.98) --
	(409.64,462.41) --
	(418.22,457.68) --
	(426.80,454.52) --
	(435.38,453.59) --
	(443.96,452.02) --
	(452.54,451.13) --
	(461.12,447.79) --
	(469.70,447.33) --
	(478.28,446.91) --
	(486.86,446.22) --
	(495.44,445.48) --
	(504.02,445.34) --
	(512.60,445.15) --
	(521.18,444.55) --
	(529.76,444.69) --
	(538.34,444.45) --
	(546.92,444.22) --
	(555.50,444.13) --
	(564.08,444.13) --
	(572.66,444.08);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
	( 49.28,444.64) --
	( 57.86,445.15) --
	( 66.44,445.15) --
	( 75.02,445.29) --
	( 83.60,446.03) --
	( 92.18,446.12) --
	(100.76,447.05) --
	(109.34,447.79) --
	(117.92,447.61) --
	(126.50,449.05) --
	(135.08,450.07) --
	(143.66,450.76) --
	(152.24,453.32) --
	(160.82,455.03) --
	(169.40,457.95) --
	(177.98,459.07) --
	(186.56,462.04) --
	(195.14,466.58) --
	(203.72,469.83) --
	(212.30,475.16) --
	(220.88,479.90) --
	(229.46,485.28) --
	(238.04,494.51) --
	(246.62,499.52) --
	(255.20,510.70) --
	(263.78,510.89) --
	(272.36,521.93) --
	(280.94,525.73) --
	(289.52,530.42) --
	(298.10,534.08) --
	(306.68,534.96) --
	(315.26,533.43) --
	(323.84,529.77) --
	(332.42,525.87) --
	(341.00,516.45) --
	(349.58,507.31) --
	(358.16,501.98) --
	(366.74,494.79) --
	(375.32,484.58) --
	(383.90,480.27) --
	(392.48,470.80) --
	(401.06,468.30) --
	(409.64,462.08) --
	(418.22,458.28) --
	(426.80,456.79) --
	(435.38,452.94) --
	(443.96,452.34) --
	(452.54,450.81) --
	(461.12,448.86) --
	(469.70,447.79) --
	(478.28,447.01) --
	(486.86,446.73) --
	(495.44,445.38) --
	(504.02,446.08) --
	(512.60,445.15) --
	(521.18,444.92) --
	(529.76,444.41) --
	(538.34,444.45) --
	(546.92,444.45) --
	(555.50,444.45) --
	(564.08,444.55) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.27) --
	( 49.28,444.73) --
	( 57.86,444.96) --
	( 66.44,445.34) --
	( 75.02,445.06) --
	( 83.60,445.85) --
	( 92.18,446.12) --
	(100.76,447.01) --
	(109.34,447.28) --
	(117.92,447.61) --
	(126.50,449.05) --
	(135.08,449.46) --
	(143.66,450.81) --
	(152.24,452.29) --
	(160.82,455.31) --
	(169.40,455.87) --
	(177.98,459.67) --
	(186.56,461.20) --
	(195.14,466.17) --
	(203.72,468.44) --
	(212.30,473.36) --
	(220.88,478.74) --
	(229.46,485.65) --
	(238.04,492.05) --
	(246.62,498.08) --
	(255.20,507.96) --
	(263.78,512.32) --
	(272.36,521.74) --
	(280.94,525.87) --
	(289.52,529.21) --
	(298.10,535.19) --
	(306.68,534.17) --
	(315.26,536.63) --
	(323.84,529.39) --
	(332.42,526.24) --
	(341.00,518.03) --
	(349.58,511.63) --
	(358.16,502.77) --
	(366.74,497.76) --
	(375.32,484.40) --
	(383.90,479.57) --
	(392.48,472.47) --
	(401.06,469.51) --
	(409.64,463.20) --
	(418.22,458.05) --
	(426.80,456.24) --
	(435.38,453.22) --
	(443.96,451.97) --
	(452.54,449.70) --
	(461.12,449.51) --
	(469.70,448.03) --
	(478.28,447.28) --
	(486.86,446.91) --
	(495.44,445.43) --
	(504.02,445.94) --
	(512.60,445.24) --
	(521.18,444.92) --
	(529.76,444.22) --
	(538.34,444.50) --
	(546.92,444.55) --
	(555.50,444.36) --
	(564.08,444.36) --
	(572.66,444.27);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
	( 49.28,445.01) --
	( 57.86,445.34) --
	( 66.44,444.83) --
	( 75.02,445.66) --
	( 83.60,446.63) --
	( 92.18,446.40) --
	(100.76,447.28) --
	(109.34,447.33) --
	(117.92,448.30) --
	(126.50,449.84) --
	(135.08,450.30) --
	(143.66,451.92) --
	(152.24,454.10) --
	(160.82,457.17) --
	(169.40,457.30) --
	(177.98,461.11) --
	(186.56,465.65) --
	(195.14,468.02) --
	(203.72,472.06) --
	(212.30,478.41) --
	(220.88,482.77) --
	(229.46,491.26) --
	(238.04,497.71) --
	(246.62,503.14) --
	(255.20,512.88) --
	(263.78,520.12) --
	(272.36,523.32) --
	(280.94,528.14) --
	(289.52,530.09) --
	(298.10,536.77) --
	(306.68,538.21) --
	(315.26,526.57) --
	(323.84,528.75) --
	(332.42,518.96) --
	(341.00,515.99) --
	(349.58,503.51) --
	(358.16,497.20) --
	(366.74,488.11) --
	(375.32,480.31) --
	(383.90,476.00) --
	(392.48,470.15) --
	(401.06,464.59) --
	(409.64,460.37) --
	(418.22,456.19) --
	(426.80,453.83) --
	(435.38,453.96) --
	(443.96,450.72) --
	(452.54,449.93) --
	(461.12,448.44) --
	(469.70,447.56) --
	(478.28,446.59) --
	(486.86,445.71) --
	(495.44,445.61) --
	(504.02,444.96) --
	(512.60,444.83) --
	(521.18,444.78) --
	(529.76,444.55) --
	(538.34,444.36) --
	(546.92,444.36) --
	(555.50,444.13) --
	(564.08,444.32);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.18) --
	( 49.28,444.96) --
	( 57.86,445.01) --
	( 66.44,444.96) --
	( 75.02,445.80) --
	( 83.60,445.57) --
	( 92.18,445.80) --
	(100.76,446.59) --
	(109.34,447.38) --
	(117.92,448.35) --
	(126.50,448.63) --
	(135.08,448.82) --
	(143.66,451.55) --
	(152.24,451.88) --
	(160.82,453.64) --
	(169.40,455.54) --
	(177.98,459.11) --
	(186.56,460.92) --
	(195.14,465.42) --
	(203.72,470.99) --
	(212.30,473.54) --
	(220.88,477.44) --
	(229.46,483.65) --
	(238.04,494.00) --
	(246.62,500.17) --
	(255.20,503.23) --
	(263.78,512.09) --
	(272.36,523.46) --
	(280.94,526.15) --
	(289.52,535.01) --
	(298.10,532.64) --
	(306.68,532.73) --
	(315.26,540.06) --
	(323.84,533.85) --
	(332.42,522.81) --
	(341.00,518.35) --
	(349.58,512.00) --
	(358.16,502.16) --
	(366.74,495.99) --
	(375.32,486.62) --
	(383.90,477.76) --
	(392.48,472.98) --
	(401.06,470.11) --
	(409.64,463.15) --
	(418.22,457.17) --
	(426.80,457.54) --
	(435.38,454.01) --
	(443.96,451.13) --
	(452.54,449.88) --
	(461.12,448.49) --
	(469.70,447.42) --
	(478.28,446.96) --
	(486.86,446.59) --
	(495.44,445.61) --
	(504.02,445.52) --
	(512.60,444.87) --
	(521.18,444.55) --
	(529.76,444.64) --
	(538.34,444.59) --
	(546.92,444.41) --
	(555.50,444.50) --
	(564.08,444.22) --
	(572.66,444.32);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.36) --
	( 49.28,444.69) --
	( 57.86,444.64) --
	( 66.44,445.24) --
	( 75.02,445.43) --
	( 83.60,445.66) --
	( 92.18,445.24) --
	(100.76,446.17) --
	(109.34,446.73) --
	(117.92,447.84) --
	(126.50,448.72) --
	(135.08,448.26) --
	(143.66,449.56) --
	(152.24,451.78) --
	(160.82,452.29) --
	(169.40,453.73) --
	(177.98,457.58) --
	(186.56,458.79) --
	(195.14,463.10) --
	(203.72,466.30) --
	(212.30,471.27) --
	(220.88,473.82) --
	(229.46,479.48) --
	(238.04,487.09) --
	(246.62,495.90) --
	(255.20,500.35) --
	(263.78,505.78) --
	(272.36,514.18) --
	(280.94,523.78) --
	(289.52,526.43) --
	(298.10,537.23) --
	(306.68,532.55) --
	(315.26,533.20) --
	(323.84,538.63) --
	(332.42,529.67) --
	(341.00,520.63) --
	(349.58,521.28) --
	(358.16,506.57) --
	(366.74,500.68) --
	(375.32,494.14) --
	(383.90,483.89) --
	(392.48,475.68) --
	(401.06,470.99) --
	(409.64,467.00) --
	(418.22,460.37) --
	(426.80,459.02) --
	(435.38,455.68) --
	(443.96,453.59) --
	(452.54,451.37) --
	(461.12,449.51) --
	(469.70,448.54) --
	(478.28,447.93) --
	(486.86,447.28) --
	(495.44,445.85) --
	(504.02,445.89) --
	(512.60,445.66) --
	(521.18,444.73) --
	(529.76,444.96) --
	(538.34,444.73) --
	(546.92,444.36) --
	(555.50,444.08) --
	(564.08,444.18) --
	(572.66,444.27);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
	( 49.28,444.45) --
	( 57.86,444.96) --
	( 66.44,445.38) --
	( 75.02,445.38) --
	( 83.60,445.66) --
	( 92.18,445.52) --
	(100.76,446.08) --
	(109.34,447.15) --
	(117.92,448.03) --
	(126.50,448.91) --
	(135.08,448.72) --
	(143.66,450.39) --
	(152.24,451.78) --
	(160.82,453.32) --
	(169.40,455.12) --
	(177.98,457.77) --
	(186.56,459.86) --
	(195.14,463.80) --
	(203.72,468.53) --
	(212.30,472.80) --
	(220.88,475.58) --
	(229.46,481.24) --
	(238.04,487.88) --
	(246.62,500.08) --
	(255.20,500.82) --
	(263.78,508.61) --
	(272.36,516.31) --
	(280.94,525.64) --
	(289.52,527.63) --
	(298.10,534.40) --
	(306.68,534.31) --
	(315.26,534.87) --
	(323.84,538.77) --
	(332.42,527.54) --
	(341.00,518.91) --
	(349.58,515.29) --
	(358.16,509.03) --
	(366.74,501.10) --
	(375.32,488.01) --
	(383.90,480.59) --
	(392.48,475.95) --
	(401.06,470.99) --
	(409.64,465.89) --
	(418.22,460.55) --
	(426.80,458.14) --
	(435.38,454.99) --
	(443.96,453.50) --
	(452.54,451.69) --
	(461.12,449.93) --
	(469.70,447.70) --
	(478.28,447.52) --
	(486.86,446.63) --
	(495.44,446.08) --
	(504.02,445.34) --
	(512.60,445.24) --
	(521.18,445.10) --
	(529.76,445.01) --
	(538.34,444.87) --
	(546.92,444.27) --
	(555.50,444.36) --
	(564.08,444.22) --
	(572.66,444.27);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
	( 49.28,444.36) --
	( 57.86,445.06) --
	( 66.44,445.57) --
	( 75.02,445.43) --
	( 83.60,445.48) --
	( 92.18,446.22) --
	(100.76,445.71) --
	(109.34,447.93) --
	(117.92,448.03) --
	(126.50,448.58) --
	(135.08,449.88) --
	(143.66,450.44) --
	(152.24,452.16) --
	(160.82,453.55) --
	(169.40,456.79) --
	(177.98,458.97) --
	(186.56,461.29) --
	(195.14,464.63) --
	(203.72,468.62) --
	(212.30,473.77) --
	(220.88,477.44) --
	(229.46,482.08) --
	(238.04,493.30) --
	(246.62,499.71) --
	(255.20,505.23) --
	(263.78,512.97) --
	(272.36,518.77) --
	(280.94,526.70) --
	(289.52,531.76) --
	(298.10,532.69) --
	(306.68,536.12) --
	(315.26,534.59) --
	(323.84,536.12) --
	(332.42,524.38) --
	(341.00,520.77) --
	(349.58,510.98) --
	(358.16,503.00) --
	(366.74,497.71) --
	(375.32,486.67) --
	(383.90,479.06) --
	(392.48,473.31) --
	(401.06,468.72) --
	(409.64,464.17) --
	(418.22,459.44) --
	(426.80,456.38) --
	(435.38,453.92) --
	(443.96,452.11) --
	(452.54,450.21) --
	(461.12,449.74) --
	(469.70,447.70) --
	(478.28,447.24) --
	(486.86,446.17) --
	(495.44,445.89) --
	(504.02,445.24) --
	(512.60,445.34) --
	(521.18,444.73) --
	(529.76,444.92) --
	(538.34,444.87) --
	(546.92,444.41) --
	(555.50,444.13) --
	(564.08,444.18) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.22) --
	( 49.28,444.83) --
	( 57.86,445.34) --
	( 66.44,445.34) --
	( 75.02,445.24) --
	( 83.60,445.89) --
	( 92.18,445.85) --
	(100.76,446.87) --
	(109.34,447.24) --
	(117.92,448.49) --
	(126.50,449.51) --
	(135.08,450.44) --
	(143.66,450.30) --
	(152.24,452.57) --
	(160.82,454.43) --
	(169.40,458.09) --
	(177.98,459.58) --
	(186.56,461.20) --
	(195.14,467.97) --
	(203.72,468.11) --
	(212.30,476.09) --
	(220.88,479.48) --
	(229.46,484.12) --
	(238.04,495.67) --
	(246.62,500.68) --
	(255.20,507.36) --
	(263.78,513.34) --
	(272.36,520.26) --
	(280.94,529.81) --
	(289.52,533.25) --
	(298.10,532.36) --
	(306.68,537.10) --
	(315.26,533.29) --
	(323.84,531.99) --
	(332.42,524.66) --
	(341.00,517.75) --
	(349.58,508.01) --
	(358.16,500.35) --
	(366.74,493.67) --
	(375.32,485.37) --
	(383.90,478.41) --
	(392.48,470.53) --
	(401.06,466.86) --
	(409.64,461.71) --
	(418.22,458.56) --
	(426.80,455.40) --
	(435.38,452.94) --
	(443.96,451.23) --
	(452.54,449.46) --
	(461.12,449.05) --
	(469.70,447.47) --
	(478.28,446.26) --
	(486.86,446.40) --
	(495.44,445.29) --
	(504.02,445.48) --
	(512.60,444.73) --
	(521.18,444.55) --
	(529.76,444.55) --
	(538.34,444.45) --
	(546.92,444.22) --
	(555.50,444.18) --
	(564.08,444.18) --
	(572.66,444.18);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.36) --
	( 49.28,444.50) --
	( 57.86,444.45) --
	( 66.44,444.83) --
	( 75.02,445.34) --
	( 83.60,445.29) --
	( 92.18,445.66) --
	(100.76,445.75) --
	(109.34,446.36) --
	(117.92,447.05) --
	(126.50,448.72) --
	(135.08,448.58) --
	(143.66,449.46) --
	(152.24,450.53) --
	(160.82,453.50) --
	(169.40,454.24) --
	(177.98,456.24) --
	(186.56,459.58) --
	(195.14,461.85) --
	(203.72,463.80) --
	(212.30,469.55) --
	(220.88,474.24) --
	(229.46,479.25) --
	(238.04,482.96) --
	(246.62,491.87) --
	(255.20,496.74) --
	(263.78,504.02) --
	(272.36,511.26) --
	(280.94,519.00) --
	(289.52,527.63) --
	(298.10,526.75) --
	(306.68,532.04) --
	(315.26,536.03) --
	(323.84,530.83) --
	(332.42,531.34) --
	(341.00,525.73) --
	(349.58,518.68) --
	(358.16,510.98) --
	(366.74,503.18) --
	(375.32,495.85) --
	(383.90,487.18) --
	(392.48,479.57) --
	(401.06,476.14) --
	(409.64,470.48) --
	(418.22,463.61) --
	(426.80,459.35) --
	(435.38,457.44) --
	(443.96,455.50) --
	(452.54,451.69) --
	(461.12,451.00) --
	(469.70,449.19) --
	(478.28,447.47) --
	(486.86,447.10) --
	(495.44,445.99) --
	(504.02,446.03) --
	(512.60,445.43) --
	(521.18,445.10) --
	(529.76,444.64) --
	(538.34,444.64) --
	(546.92,444.36) --
	(555.50,444.32) --
	(564.08,444.22) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
	( 49.28,444.78) --
	( 57.86,445.38) --
	( 66.44,445.43) --
	( 75.02,445.48) --
	( 83.60,445.85) --
	( 92.18,446.31) --
	(100.76,447.70) --
	(109.34,448.54) --
	(117.92,448.17) --
	(126.50,449.88) --
	(135.08,451.32) --
	(143.66,452.76) --
	(152.24,455.40) --
	(160.82,456.33) --
	(169.40,459.02) --
	(177.98,462.87) --
	(186.56,464.08) --
	(195.14,469.04) --
	(203.72,476.74) --
	(212.30,480.69) --
	(220.88,482.73) --
	(229.46,491.96) --
	(238.04,497.90) --
	(246.62,505.13) --
	(255.20,512.42) --
	(263.78,520.02) --
	(272.36,528.33) --
	(280.94,527.12) --
	(289.52,532.92) --
	(298.10,535.52) --
	(306.68,533.06) --
	(315.26,533.66) --
	(323.84,524.20) --
	(332.42,516.08) --
	(341.00,512.51) --
	(349.58,500.59) --
	(358.16,496.88) --
	(366.74,487.18) --
	(375.32,478.60) --
	(383.90,472.80) --
	(392.48,467.51) --
	(401.06,462.87) --
	(409.64,459.95) --
	(418.22,457.54) --
	(426.80,453.36) --
	(435.38,451.60) --
	(443.96,450.39) --
	(452.54,448.40) --
	(461.12,447.70) --
	(469.70,446.59) --
	(478.28,445.80) --
	(486.86,445.80) --
	(495.44,445.38) --
	(504.02,445.38) --
	(512.60,444.59) --
	(521.18,444.45) --
	(529.76,444.32) --
	(538.34,444.41) --
	(546.92,444.27) --
	(555.50,444.08) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
	( 49.28,445.01) --
	( 57.86,445.20) --
	( 66.44,445.48) --
	( 75.02,445.38) --
	( 83.60,445.94) --
	( 92.18,446.08) --
	(100.76,447.56) --
	(109.34,448.49) --
	(117.92,448.54) --
	(126.50,449.88) --
	(135.08,450.90) --
	(143.66,453.92) --
	(152.24,455.08) --
	(160.82,456.38) --
	(169.40,459.53) --
	(177.98,462.59) --
	(186.56,464.82) --
	(195.14,468.76) --
	(203.72,476.93) --
	(212.30,481.89) --
	(220.88,483.79) --
	(229.46,490.33) --
	(238.04,500.22) --
	(246.62,504.30) --
	(255.20,514.23) --
	(263.78,520.07) --
	(272.36,525.27) --
	(280.94,527.08) --
	(289.52,532.97) --
	(298.10,531.48) --
	(306.68,535.89) --
	(315.26,529.12) --
	(323.84,523.09) --
	(332.42,517.06) --
	(341.00,509.86) --
	(349.58,500.73) --
	(358.16,495.44) --
	(366.74,489.31) --
	(375.32,477.44) --
	(383.90,472.61) --
	(392.48,467.79) --
	(401.06,462.08) --
	(409.64,459.81) --
	(418.22,456.84) --
	(426.80,453.83) --
	(435.38,452.11) --
	(443.96,449.98) --
	(452.54,449.23) --
	(461.12,448.07) --
	(469.70,447.28) --
	(478.28,446.12) --
	(486.86,445.57) --
	(495.44,445.71) --
	(504.02,444.96) --
	(512.60,444.87) --
	(521.18,444.45) --
	(529.76,444.50) --
	(538.34,444.36) --
	(546.92,444.08) --
	(555.50,444.08) --
	(564.08,444.08);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.78) --
	( 49.28,444.73) --
	( 57.86,445.29) --
	( 66.44,445.34) --
	( 75.02,445.24) --
	( 83.60,446.12) --
	( 92.18,446.03) --
	(100.76,447.56) --
	(109.34,448.17) --
	(117.92,448.03) --
	(126.50,450.25) --
	(135.08,451.32) --
	(143.66,453.13) --
	(152.24,455.22) --
	(160.82,456.42) --
	(169.40,457.95) --
	(177.98,464.40) --
	(186.56,463.43) --
	(195.14,468.76) --
	(203.72,476.05) --
	(212.30,483.47) --
	(220.88,482.96) --
	(229.46,488.94) --
	(238.04,499.66) --
	(246.62,504.76) --
	(255.20,512.69) --
	(263.78,522.11) --
	(272.36,523.64) --
	(280.94,528.98) --
	(289.52,533.29) --
	(298.10,533.25) --
	(306.68,535.66) --
	(315.26,531.58) --
	(323.84,523.69) --
	(332.42,517.29) --
	(341.00,510.24) --
	(349.58,503.83) --
	(358.16,496.83) --
	(366.74,490.01) --
	(375.32,478.50) --
	(383.90,474.84) --
	(392.48,468.86) --
	(401.06,462.69) --
	(409.64,460.00) --
	(418.22,456.05) --
	(426.80,454.94) --
	(435.38,451.37) --
	(443.96,450.02) --
	(452.54,449.00) --
	(461.12,447.38) --
	(469.70,446.82) --
	(478.28,446.03) --
	(486.86,445.99) --
	(495.44,445.06) --
	(504.02,445.20) --
	(512.60,445.01) --
	(521.18,444.27) --
	(529.76,444.27) --
	(538.34,444.32) --
	(546.92,444.18) --
	(555.50,444.04) --
	(564.08,444.18) --
	(572.66,444.08);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
	( 49.28,444.83) --
	( 57.86,445.43) --
	( 66.44,444.96) --
	( 75.02,445.20) --
	( 83.60,446.31) --
	( 92.18,446.08) --
	(100.76,447.56) --
	(109.34,448.12) --
	(117.92,448.30) --
	(126.50,449.84) --
	(135.08,451.41) --
	(143.66,452.67) --
	(152.24,455.36) --
	(160.82,456.24) --
	(169.40,459.62) --
	(177.98,462.92) --
	(186.56,463.47) --
	(195.14,469.13) --
	(203.72,477.58) --
	(212.30,482.26) --
	(220.88,484.16) --
	(229.46,489.08) --
	(238.04,502.44) --
	(246.62,502.07) --
	(255.20,514.27) --
	(263.78,521.32) --
	(272.36,523.74) --
	(280.94,530.37) --
	(289.52,536.45) --
	(298.10,531.16) --
	(306.68,537.14) --
	(315.26,532.73) --
	(323.84,520.86) --
	(332.42,519.98) --
	(341.00,511.30) --
	(349.58,503.51) --
	(358.16,494.97) --
	(366.74,485.74) --
	(375.32,480.22) --
	(383.90,472.24) --
	(392.48,467.09) --
	(401.06,462.18) --
	(409.64,460.09) --
	(418.22,456.33) --
	(426.80,452.85) --
	(435.38,452.20) --
	(443.96,450.72) --
	(452.54,449.05) --
	(461.12,446.96) --
	(469.70,446.82) --
	(478.28,446.40) --
	(486.86,445.80) --
	(495.44,445.66) --
	(504.02,445.10) --
	(512.60,444.78) --
	(521.18,444.69) --
	(529.76,444.50) --
	(538.34,444.41) --
	(546.92,444.22) --
	(555.50,444.27);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.87) --
	( 49.28,445.01) --
	( 57.86,445.10) --
	( 66.44,445.38) --
	( 75.02,445.66) --
	( 83.60,446.45) --
	( 92.18,446.17) --
	(100.76,447.28) --
	(109.34,448.03) --
	(117.92,448.30) --
	(126.50,450.25) --
	(135.08,450.76) --
	(143.66,452.34) --
	(152.24,453.04) --
	(160.82,455.45) --
	(169.40,458.28) --
	(177.98,462.13) --
	(186.56,465.14) --
	(195.14,469.04) --
	(203.72,471.18) --
	(212.30,478.69) --
	(220.88,484.35) --
	(229.46,489.36) --
	(238.04,496.27) --
	(246.62,502.95) --
	(255.20,510.79) --
	(263.78,514.60) --
	(272.36,524.43) --
	(280.94,525.08) --
	(289.52,530.51) --
	(298.10,535.56) --
	(306.68,534.87) --
	(315.26,531.02) --
	(323.84,526.01) --
	(332.42,522.81) --
	(341.00,513.07) --
	(349.58,505.32) --
	(358.16,499.19) --
	(366.74,489.45) --
	(375.32,481.84) --
	(383.90,478.60) --
	(392.48,469.32) --
	(401.06,465.47) --
	(409.64,460.60) --
	(418.22,457.63) --
	(426.80,455.17) --
	(435.38,453.41) --
	(443.96,451.09) --
	(452.54,449.74) --
	(461.12,448.26) --
	(469.70,446.87) --
	(478.28,445.75) --
	(486.86,446.22) --
	(495.44,445.75) --
	(504.02,445.24) --
	(512.60,444.92) --
	(521.18,444.83) --
	(529.76,444.64) --
	(538.34,444.41) --
	(546.92,444.64) --
	(555.50,444.13) --
	(564.08,444.04) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
	( 49.28,445.34) --
	( 57.86,444.96) --
	( 66.44,445.20) --
	( 75.02,445.61) --
	( 83.60,445.89) --
	( 92.18,446.40) --
	(100.76,447.47) --
	(109.34,447.61) --
	(117.92,448.21) --
	(126.50,449.33) --
	(135.08,450.25) --
	(143.66,452.80) --
	(152.24,452.43) --
	(160.82,453.87) --
	(169.40,458.00) --
	(177.98,460.88) --
	(186.56,465.33) --
	(195.14,466.72) --
	(203.72,471.45) --
	(212.30,475.86) --
	(220.88,483.52) --
	(229.46,489.36) --
	(238.04,493.12) --
	(246.62,501.14) --
	(255.20,509.54) --
	(263.78,513.16) --
	(272.36,522.30) --
	(280.94,527.63) --
	(289.52,529.81) --
	(298.10,532.60) --
	(306.68,535.98) --
	(315.26,530.23) --
	(323.84,528.47) --
	(332.42,522.90) --
	(341.00,517.33) --
	(349.58,509.17) --
	(358.16,498.82) --
	(366.74,490.94) --
	(375.32,483.38) --
	(383.90,479.90) --
	(392.48,470.34) --
	(401.06,466.17) --
	(409.64,462.27) --
	(418.22,457.81) --
	(426.80,456.33) --
	(435.38,452.25) --
	(443.96,451.51) --
	(452.54,450.21) --
	(461.12,448.44) --
	(469.70,447.38) --
	(478.28,446.77) --
	(486.86,445.89) --
	(495.44,445.71) --
	(504.02,445.57) --
	(512.60,444.73) --
	(521.18,444.83) --
	(529.76,444.45) --
	(538.34,444.59) --
	(546.92,444.18) --
	(555.50,444.18) --
	(564.08,444.18) --
	(572.66,443.99);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.87) --
	( 49.28,445.10) --
	( 57.86,445.20) --
	( 66.44,445.06) --
	( 75.02,445.57) --
	( 83.60,445.57) --
	( 92.18,446.50) --
	(100.76,446.87) --
	(109.34,448.03) --
	(117.92,447.79) --
	(126.50,448.77) --
	(135.08,449.98) --
	(143.66,451.60) --
	(152.24,452.99) --
	(160.82,454.10) --
	(169.40,455.91) --
	(177.98,460.51) --
	(186.56,464.63) --
	(195.14,465.84) --
	(203.72,470.11) --
	(212.30,473.73) --
	(220.88,482.08) --
	(229.46,487.69) --
	(238.04,491.26) --
	(246.62,500.03) --
	(255.20,507.87) --
	(263.78,511.67) --
	(272.36,518.59) --
	(280.94,527.17) --
	(289.52,525.92) --
	(298.10,535.98) --
	(306.68,533.29) --
	(315.26,536.07) --
	(323.84,527.49) --
	(332.42,523.55) --
	(341.00,521.14) --
	(349.58,511.67) --
	(358.16,500.73) --
	(366.74,492.42) --
	(375.32,486.11) --
	(383.90,480.45) --
	(392.48,473.59) --
	(401.06,467.93) --
	(409.64,463.52) --
	(418.22,460.09) --
	(426.80,456.28) --
	(435.38,453.50) --
	(443.96,451.83) --
	(452.54,450.53) --
	(461.12,449.65) --
	(469.70,447.89) --
	(478.28,447.19) --
	(486.86,446.36) --
	(495.44,445.38) --
	(504.02,445.38) --
	(512.60,445.34) --
	(521.18,444.78) --
	(529.76,444.73) --
	(538.34,444.41) --
	(546.92,444.45) --
	(555.50,444.04) --
	(564.08,444.22) --
	(572.66,444.08);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
	( 49.28,445.24) --
	( 57.86,444.92) --
	( 66.44,445.24) --
	( 75.02,445.48) --
	( 83.60,445.48) --
	( 92.18,446.08) --
	(100.76,446.87) --
	(109.34,447.84) --
	(117.92,447.61) --
	(126.50,449.14) --
	(135.08,449.23) --
	(143.66,451.09) --
	(152.24,452.85) --
	(160.82,453.83) --
	(169.40,454.99) --
	(177.98,459.21) --
	(186.56,463.15) --
	(195.14,466.26) --
	(203.72,469.27) --
	(212.30,473.68) --
	(220.88,479.99) --
	(229.46,484.63) --
	(238.04,492.00) --
	(246.62,499.57) --
	(255.20,505.09) --
	(263.78,510.70) --
	(272.36,517.38) --
	(280.94,524.66) --
	(289.52,528.88) --
	(298.10,531.20) --
	(306.68,533.57) --
	(315.26,536.26) --
	(323.84,528.61) --
	(332.42,524.94) --
	(341.00,521.93) --
	(349.58,513.67) --
	(358.16,504.34) --
	(366.74,493.72) --
	(375.32,485.60) --
	(383.90,481.47) --
	(392.48,475.49) --
	(401.06,467.93) --
	(409.64,464.45) --
	(418.22,461.29) --
	(426.80,457.91) --
	(435.38,453.92) --
	(443.96,453.55) --
	(452.54,450.76) --
	(461.12,449.42) --
	(469.70,448.30) --
	(478.28,447.05) --
	(486.86,446.73) --
	(495.44,445.99) --
	(504.02,445.48) --
	(512.60,445.01) --
	(521.18,445.01) --
	(529.76,444.69) --
	(538.34,444.64) --
	(546.92,444.32) --
	(555.50,444.36) --
	(564.08,444.22) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.73) --
	( 49.28,445.20) --
	( 57.86,444.96) --
	( 66.44,445.52) --
	( 75.02,445.43) --
	( 83.60,445.94) --
	( 92.18,446.54) --
	(100.76,447.89) --
	(109.34,447.70) --
	(117.92,448.54) --
	(126.50,449.46) --
	(135.08,450.11) --
	(143.66,452.06) --
	(152.24,453.04) --
	(160.82,455.22) --
	(169.40,458.14) --
	(177.98,461.20) --
	(186.56,464.96) --
	(195.14,468.16) --
	(203.72,472.75) --
	(212.30,478.46) --
	(220.88,483.14) --
	(229.46,489.87) --
	(238.04,495.99) --
	(246.62,504.16) --
	(255.20,507.73) --
	(263.78,519.42) --
	(272.36,523.32) --
	(280.94,524.71) --
	(289.52,532.64) --
	(298.10,534.54) --
	(306.68,534.82) --
	(315.26,531.06) --
	(323.84,527.63) --
	(332.42,521.69) --
	(341.00,515.52) --
	(349.58,506.80) --
	(358.16,498.04) --
	(366.74,488.94) --
	(375.32,481.01) --
	(383.90,478.27) --
	(392.48,469.18) --
	(401.06,463.80) --
	(409.64,460.55) --
	(418.22,458.74) --
	(426.80,456.14) --
	(435.38,452.71) --
	(443.96,450.90) --
	(452.54,449.19) --
	(461.12,449.19) --
	(469.70,448.49) --
	(478.28,446.96) --
	(486.86,446.26) --
	(495.44,446.22) --
	(504.02,445.24) --
	(512.60,445.24) --
	(521.18,445.01) --
	(529.76,444.69) --
	(538.34,444.13) --
	(546.92,444.55) --
	(555.50,444.08) --
	(564.08,444.08) --
	(572.66,444.08);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
	( 49.28,444.73) --
	( 57.86,445.06) --
	( 66.44,444.92) --
	( 75.02,445.52) --
	( 83.60,445.15) --
	( 92.18,446.22) --
	(100.76,446.45) --
	(109.34,446.26) --
	(117.92,447.70) --
	(126.50,449.33) --
	(135.08,449.93) --
	(143.66,450.67) --
	(152.24,451.04) --
	(160.82,452.76) --
	(169.40,456.38) --
	(177.98,457.12) --
	(186.56,459.48) --
	(195.14,462.83) --
	(203.72,466.81) --
	(212.30,471.78) --
	(220.88,474.42) --
	(229.46,480.92) --
	(238.04,487.74) --
	(246.62,493.81) --
	(255.20,498.41) --
	(263.78,504.67) --
	(272.36,515.20) --
	(280.94,519.79) --
	(289.52,525.64) --
	(298.10,529.58) --
	(306.68,529.44) --
	(315.26,537.65) --
	(323.84,533.85) --
	(332.42,526.98) --
	(341.00,524.89) --
	(349.58,515.43) --
	(358.16,510.47) --
	(366.74,501.14) --
	(375.32,494.18) --
	(383.90,486.30) --
	(392.48,477.30) --
	(401.06,473.59) --
	(409.64,466.35) --
	(418.22,464.54) --
	(426.80,458.42) --
	(435.38,456.05) --
	(443.96,453.08) --
	(452.54,451.51) --
	(461.12,449.28) --
	(469.70,449.14) --
	(478.28,447.89) --
	(486.86,447.28) --
	(495.44,446.12) --
	(504.02,445.61) --
	(512.60,445.24) --
	(521.18,444.87) --
	(529.76,444.83) --
	(538.34,444.41) --
	(546.92,444.45) --
	(555.50,444.45) --
	(564.08,444.08) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
	( 49.28,444.69) --
	( 57.86,445.10) --
	( 66.44,444.96) --
	( 75.02,445.24) --
	( 83.60,445.52) --
	( 92.18,446.17) --
	(100.76,446.54) --
	(109.34,446.77) --
	(117.92,447.89) --
	(126.50,448.72) --
	(135.08,450.58) --
	(143.66,450.95) --
	(152.24,450.53) --
	(160.82,454.38) --
	(169.40,456.79) --
	(177.98,456.75) --
	(186.56,460.55) --
	(195.14,463.61) --
	(203.72,468.39) --
	(212.30,473.36) --
	(220.88,475.30) --
	(229.46,483.61) --
	(238.04,488.06) --
	(246.62,496.64) --
	(255.20,499.89) --
	(263.78,507.13) --
	(272.36,518.73) --
	(280.94,520.44) --
	(289.52,526.61) --
	(298.10,529.07) --
	(306.68,532.41) --
	(315.26,533.85) --
	(323.84,531.44) --
	(332.42,525.68) --
	(341.00,521.88) --
	(349.58,512.74) --
	(358.16,507.55) --
	(366.74,498.55) --
	(375.32,491.45) --
	(383.90,485.70) --
	(392.48,475.16) --
	(401.06,471.27) --
	(409.64,467.14) --
	(418.22,463.52) --
	(426.80,458.23) --
	(435.38,454.61) --
	(443.96,453.92) --
	(452.54,451.83) --
	(461.12,450.25) --
	(469.70,449.00) --
	(478.28,448.40) --
	(486.86,447.05) --
	(495.44,446.22) --
	(504.02,445.57) --
	(512.60,445.57) --
	(521.18,445.34) --
	(529.76,445.43) --
	(538.34,444.64) --
	(546.92,444.55) --
	(555.50,444.41) --
	(564.08,444.50) --
	(572.66,444.22);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.69) --
	( 49.28,445.06) --
	( 57.86,444.92) --
	( 66.44,445.61) --
	( 75.02,445.48) --
	( 83.60,446.22) --
	( 92.18,446.45) --
	(100.76,447.01) --
	(109.34,448.17) --
	(117.92,448.54) --
	(126.50,450.86) --
	(135.08,451.00) --
	(143.66,450.90) --
	(152.24,455.22) --
	(160.82,456.56) --
	(169.40,457.44) --
	(177.98,461.06) --
	(186.56,464.36) --
	(195.14,470.02) --
	(203.72,473.40) --
	(212.30,478.32) --
	(220.88,482.59) --
	(229.46,489.13) --
	(238.04,496.92) --
	(246.62,501.00) --
	(255.20,508.47) --
	(263.78,518.03) --
	(272.36,522.07) --
	(280.94,527.31) --
	(289.52,530.37) --
	(298.10,531.39) --
	(306.68,535.24) --
	(315.26,532.13) --
	(323.84,526.47) --
	(332.42,519.42) --
	(341.00,512.74) --
	(349.58,507.03) --
	(358.16,497.94) --
	(366.74,490.24) --
	(375.32,482.68) --
	(383.90,475.54) --
	(392.48,469.92) --
	(401.06,467.28) --
	(409.64,460.78) --
	(418.22,457.21) --
	(426.80,455.36) --
	(435.38,451.41) --
	(443.96,450.95) --
	(452.54,449.79) --
	(461.12,448.54) --
	(469.70,447.61) --
	(478.28,447.05) --
	(486.86,446.36) --
	(495.44,445.66) --
	(504.02,445.48) --
	(512.60,444.92) --
	(521.18,444.83) --
	(529.76,444.50) --
	(538.34,444.04) --
	(546.92,444.45) --
	(555.50,444.50) --
	(564.08,444.08) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.83) --
	( 49.28,444.92) --
	( 57.86,445.06) --
	( 66.44,445.66) --
	( 75.02,445.38) --
	( 83.60,446.22) --
	( 92.18,446.59) --
	(100.76,447.42) --
	(109.34,448.17) --
	(117.92,448.54) --
	(126.50,450.72) --
	(135.08,451.55) --
	(143.66,452.16) --
	(152.24,455.17) --
	(160.82,456.38) --
	(169.40,458.70) --
	(177.98,461.20) --
	(186.56,466.40) --
	(195.14,469.88) --
	(203.72,473.82) --
	(212.30,479.94) --
	(220.88,486.72) --
	(229.46,487.41) --
	(238.04,498.55) --
	(246.62,503.88) --
	(255.20,509.77) --
	(263.78,516.45) --
	(272.36,521.60) --
	(280.94,529.16) --
	(289.52,533.52) --
	(298.10,531.06) --
	(306.68,531.99) --
	(315.26,529.67) --
	(323.84,527.08) --
	(332.42,517.66) --
	(341.00,511.44) --
	(349.58,503.14) --
	(358.16,498.36) --
	(366.74,486.34) --
	(375.32,481.10) --
	(383.90,475.21) --
	(392.48,468.99) --
	(401.06,464.68) --
	(409.64,461.39) --
	(418.22,457.30) --
	(426.80,454.99) --
	(435.38,452.90) --
	(443.96,452.02) --
	(452.54,449.23) --
	(461.12,449.00) --
	(469.70,446.68) --
	(478.28,447.24) --
	(486.86,446.77) --
	(495.44,445.61) --
	(504.02,444.96) --
	(512.60,444.96) --
	(521.18,445.10) --
	(529.76,444.59) --
	(538.34,444.55) --
	(546.92,444.18) --
	(555.50,444.27) --
	(564.08,444.13) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
	( 49.28,444.83) --
	( 57.86,445.10) --
	( 66.44,445.24) --
	( 75.02,445.57) --
	( 83.60,445.15) --
	( 92.18,446.45) --
	(100.76,446.82) --
	(109.34,447.52) --
	(117.92,448.49) --
	(126.50,448.63) --
	(135.08,450.16) --
	(143.66,452.16) --
	(152.24,452.43) --
	(160.82,455.40) --
	(169.40,457.86) --
	(177.98,458.33) --
	(186.56,462.36) --
	(195.14,467.74) --
	(203.72,469.55) --
	(212.30,474.28) --
	(220.88,482.03) --
	(229.46,485.32) --
	(238.04,491.35) --
	(246.62,499.43) --
	(255.20,506.57) --
	(263.78,512.79) --
	(272.36,515.66) --
	(280.94,525.92) --
	(289.52,529.58) --
	(298.10,533.52) --
	(306.68,528.84) --
	(315.26,533.15) --
	(323.84,530.23) --
	(332.42,520.86) --
	(341.00,518.35) --
	(349.58,509.45) --
	(358.16,501.93) --
	(366.74,493.21) --
	(375.32,486.99) --
	(383.90,479.71) --
	(392.48,473.31) --
	(401.06,468.90) --
	(409.64,462.83) --
	(418.22,460.13) --
	(426.80,456.38) --
	(435.38,453.78) --
	(443.96,452.16) --
	(452.54,450.25) --
	(461.12,449.19) --
	(469.70,447.98) --
	(478.28,447.66) --
	(486.86,446.54) --
	(495.44,446.96) --
	(504.02,445.71) --
	(512.60,445.71) --
	(521.18,445.20) --
	(529.76,444.59) --
	(538.34,444.45) --
	(546.92,444.96) --
	(555.50,444.18) --
	(564.08,444.04) --
	(572.66,444.22);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.87) --
	( 49.28,444.69) --
	( 57.86,445.24) --
	( 66.44,445.29) --
	( 75.02,445.66) --
	( 83.60,446.26) --
	( 92.18,446.45) --
	(100.76,446.59) --
	(109.34,447.89) --
	(117.92,448.54) --
	(126.50,449.23) --
	(135.08,451.04) --
	(143.66,451.65) --
	(152.24,453.69) --
	(160.82,455.68) --
	(169.40,457.21) --
	(177.98,460.64) --
	(186.56,463.98) --
	(195.14,467.79) --
	(203.72,473.31) --
	(212.30,477.16) --
	(220.88,480.82) --
	(229.46,489.08) --
	(238.04,496.32) --
	(246.62,502.21) --
	(255.20,508.38) --
	(263.78,515.71) --
	(272.36,520.77) --
	(280.94,529.02) --
	(289.52,531.30) --
	(298.10,531.30) --
	(306.68,531.16) --
	(315.26,530.32) --
	(323.84,530.04) --
	(332.42,520.72) --
	(341.00,513.25) --
	(349.58,506.99) --
	(358.16,498.92) --
	(366.74,488.53) --
	(375.32,481.15) --
	(383.90,476.42) --
	(392.48,473.31) --
	(401.06,468.39) --
	(409.64,461.94) --
	(418.22,457.63) --
	(426.80,454.61) --
	(435.38,454.52) --
	(443.96,452.06) --
	(452.54,450.44) --
	(461.12,448.40) --
	(469.70,447.42) --
	(478.28,447.05) --
	(486.86,446.36) --
	(495.44,445.34) --
	(504.02,445.57) --
	(512.60,445.20) --
	(521.18,444.78) --
	(529.76,444.87) --
	(538.34,444.27) --
	(546.92,444.50) --
	(555.50,444.18) --
	(564.08,444.04) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.73) --
	( 49.28,444.96) --
	( 57.86,444.69) --
	( 66.44,445.29) --
	( 75.02,445.15) --
	( 83.60,445.94) --
	( 92.18,446.77) --
	(100.76,446.36) --
	(109.34,446.45) --
	(117.92,448.07) --
	(126.50,449.14) --
	(135.08,449.98) --
	(143.66,451.27) --
	(152.24,452.16) --
	(160.82,454.38) --
	(169.40,455.40) --
	(177.98,458.56) --
	(186.56,460.69) --
	(195.14,465.38) --
	(203.72,468.48) --
	(212.30,474.79) --
	(220.88,477.86) --
	(229.46,482.59) --
	(238.04,490.89) --
	(246.62,495.81) --
	(255.20,503.05) --
	(263.78,510.65) --
	(272.36,515.94) --
	(280.94,523.04) --
	(289.52,528.14) --
	(298.10,529.12) --
	(306.68,532.73) --
	(315.26,531.48) --
	(323.84,527.45) --
	(332.42,524.89) --
	(341.00,516.03) --
	(349.58,512.97) --
	(358.16,506.43) --
	(366.74,495.81) --
	(375.32,488.39) --
	(383.90,480.41) --
	(392.48,475.91) --
	(401.06,473.26) --
	(409.64,467.05) --
	(418.22,460.27) --
	(426.80,457.44) --
	(435.38,456.33) --
	(443.96,453.22) --
	(452.54,451.13) --
	(461.12,449.60) --
	(469.70,448.21) --
	(478.28,447.42) --
	(486.86,446.63) --
	(495.44,446.31) --
	(504.02,446.03) --
	(512.60,445.34) --
	(521.18,444.87) --
	(529.76,445.06) --
	(538.34,444.59) --
	(546.92,444.36) --
	(555.50,444.32) --
	(564.08,444.36) --
	(572.66,444.18);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.83) --
	( 49.28,444.83) --
	( 57.86,444.92) --
	( 66.44,445.06) --
	( 75.02,445.29) --
	( 83.60,445.94) --
	( 92.18,447.05) --
	(100.76,446.45) --
	(109.34,446.59) --
	(117.92,448.03) --
	(126.50,449.56) --
	(135.08,450.58) --
	(143.66,450.86) --
	(152.24,452.94) --
	(160.82,454.15) --
	(169.40,456.33) --
	(177.98,459.48) --
	(186.56,461.29) --
	(195.14,465.75) --
	(203.72,470.53) --
	(212.30,474.28) --
	(220.88,478.78) --
	(229.46,485.56) --
	(238.04,491.59) --
	(246.62,496.41) --
	(255.20,506.34) --
	(263.78,511.53) --
	(272.36,517.47) --
	(280.94,525.08) --
	(289.52,529.16) --
	(298.10,528.47) --
	(306.68,534.27) --
	(315.26,531.95) --
	(323.84,527.12) --
	(332.42,522.48) --
	(341.00,518.77) --
	(349.58,513.48) --
	(358.16,503.83) --
	(366.74,492.75) --
	(375.32,487.46) --
	(383.90,479.02) --
	(392.48,476.00) --
	(401.06,470.15) --
	(409.64,464.63) --
	(418.22,459.76) --
	(426.80,456.66) --
	(435.38,455.36) --
	(443.96,452.53) --
	(452.54,450.39) --
	(461.12,448.82) --
	(469.70,448.77) --
	(478.28,447.01) --
	(486.86,445.94) --
	(495.44,445.71) --
	(504.02,445.85) --
	(512.60,445.38) --
	(521.18,444.87) --
	(529.76,444.55) --
	(538.34,444.41) --
	(546.92,444.27) --
	(555.50,444.27) --
	(564.08,444.32) --
	(572.66,443.99);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.36) --
	( 49.28,444.96) --
	( 57.86,444.64) --
	( 66.44,445.10) --
	( 75.02,444.78) --
	( 83.60,445.57) --
	( 92.18,446.08) --
	(100.76,447.24) --
	(109.34,446.54) --
	(117.92,446.54) --
	(126.50,448.77) --
	(135.08,449.74) --
	(143.66,450.16) --
	(152.24,451.65) --
	(160.82,453.73) --
	(169.40,454.61) --
	(177.98,457.26) --
	(186.56,459.62) --
	(195.14,462.64) --
	(203.72,466.54) --
	(212.30,472.34) --
	(220.88,474.93) --
	(229.46,482.45) --
	(238.04,487.18) --
	(246.62,491.45) --
	(255.20,499.01) --
	(263.78,509.26) --
	(272.36,514.41) --
	(280.94,519.19) --
	(289.52,526.52) --
	(298.10,529.35) --
	(306.68,531.58) --
	(315.26,535.47) --
	(323.84,529.44) --
	(332.42,524.99) --
	(341.00,520.86) --
	(349.58,520.49) --
	(358.16,506.85) --
	(366.74,501.28) --
	(375.32,494.18) --
	(383.90,483.70) --
	(392.48,479.99) --
	(401.06,473.36) --
	(409.64,468.11) --
	(418.22,463.24) --
	(426.80,459.16) --
	(435.38,455.91) --
	(443.96,453.64) --
	(452.54,450.44) --
	(461.12,449.88) --
	(469.70,448.86) --
	(478.28,448.12) --
	(486.86,446.68) --
	(495.44,446.50) --
	(504.02,445.52) --
	(512.60,445.89) --
	(521.18,444.69) --
	(529.76,445.06) --
	(538.34,444.83) --
	(546.92,444.27) --
	(555.50,444.41) --
	(564.08,444.55) --
	(572.66,444.08);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
	( 49.28,444.92) --
	( 57.86,444.69) --
	( 66.44,444.87) --
	( 75.02,445.24) --
	( 83.60,445.66) --
	( 92.18,446.03) --
	(100.76,446.87) --
	(109.34,447.28) --
	(117.92,446.82) --
	(126.50,448.63) --
	(135.08,449.33) --
	(143.66,451.41) --
	(152.24,451.46) --
	(160.82,453.92) --
	(169.40,454.85) --
	(177.98,457.58) --
	(186.56,459.95) --
	(195.14,463.20) --
	(203.72,468.07) --
	(212.30,471.87) --
	(220.88,476.37) --
	(229.46,482.26) --
	(238.04,486.07) --
	(246.62,492.51) --
	(255.20,501.61) --
	(263.78,510.47) --
	(272.36,516.03) --
	(280.94,522.25) --
	(289.52,524.89) --
	(298.10,531.44) --
	(306.68,534.45) --
	(315.26,534.36) --
	(323.84,528.14) --
	(332.42,522.71) --
	(341.00,519.47) --
	(349.58,515.34) --
	(358.16,509.03) --
	(366.74,499.75) --
	(375.32,493.03) --
	(383.90,485.51) --
	(392.48,474.98) --
	(401.06,472.66) --
	(409.64,468.25) --
	(418.22,463.01) --
	(426.80,458.14) --
	(435.38,455.91) --
	(443.96,454.52) --
	(452.54,450.39) --
	(461.12,449.51) --
	(469.70,449.28) --
	(478.28,447.19) --
	(486.86,446.82) --
	(495.44,446.08) --
	(504.02,445.66) --
	(512.60,445.71) --
	(521.18,444.64) --
	(529.76,444.87) --
	(538.34,444.83) --
	(546.92,444.36) --
	(555.50,444.27) --
	(564.08,444.27) --
	(572.66,443.99);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.96) --
	( 49.28,444.36) --
	( 57.86,444.78) --
	( 66.44,445.20) --
	( 75.02,445.66) --
	( 83.60,446.17) --
	( 92.18,446.26) --
	(100.76,447.10) --
	(109.34,447.93) --
	(117.92,448.03) --
	(126.50,448.86) --
	(135.08,450.16) --
	(143.66,451.88) --
	(152.24,452.80) --
	(160.82,455.36) --
	(169.40,457.40) --
	(177.98,460.04) --
	(186.56,462.83) --
	(195.14,466.72) --
	(203.72,472.06) --
	(212.30,478.09) --
	(220.88,482.87) --
	(229.46,485.74) --
	(238.04,496.64) --
	(246.62,501.65) --
	(255.20,511.44) --
	(263.78,515.57) --
	(272.36,524.48) --
	(280.94,530.28) --
	(289.52,533.11) --
	(298.10,537.51) --
	(306.68,535.94) --
	(315.26,535.10) --
	(323.84,528.93) --
	(332.42,522.90) --
	(341.00,515.57) --
	(349.58,508.61) --
	(358.16,500.22) --
	(366.74,490.84) --
	(375.32,482.49) --
	(383.90,476.05) --
	(392.48,469.41) --
	(401.06,464.68) --
	(409.64,460.23) --
	(418.22,457.58) --
	(426.80,454.75) --
	(435.38,452.06) --
	(443.96,450.44) --
	(452.54,449.56) --
	(461.12,448.63) --
	(469.70,446.91) --
	(478.28,446.03) --
	(486.86,446.03) --
	(495.44,445.80) --
	(504.02,444.92) --
	(512.60,445.01) --
	(521.18,445.01) --
	(529.76,444.45) --
	(538.34,444.59) --
	(546.92,444.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (564.08,444.13) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,445.01) --
	( 49.28,444.59) --
	( 57.86,444.50) --
	( 66.44,445.29) --
	( 75.02,445.20) --
	( 83.60,446.17) --
	( 92.18,446.26) --
	(100.76,446.87) --
	(109.34,447.05) --
	(117.92,448.21) --
	(126.50,448.63) --
	(135.08,449.93) --
	(143.66,450.95) --
	(152.24,452.71) --
	(160.82,454.71) --
	(169.40,455.82) --
	(177.98,460.37) --
	(186.56,461.62) --
	(195.14,464.63) --
	(203.72,471.27) --
	(212.30,475.63) --
	(220.88,480.13) --
	(229.46,486.02) --
	(238.04,494.37) --
	(246.62,499.66) --
	(255.20,508.06) --
	(263.78,514.69) --
	(272.36,521.83) --
	(280.94,526.19) --
	(289.52,532.97) --
	(298.10,534.36) --
	(306.68,536.17) --
	(315.26,532.60) --
	(323.84,532.55) --
	(332.42,526.29) --
	(341.00,519.84) --
	(349.58,509.82) --
	(358.16,498.59) --
	(366.74,494.51) --
	(375.32,486.02) --
	(383.90,478.55) --
	(392.48,471.59) --
	(401.06,467.79) --
	(409.64,463.38) --
	(418.22,459.07) --
	(426.80,456.47) --
	(435.38,452.76) --
	(443.96,451.27) --
	(452.54,449.56) --
	(461.12,449.70) --
	(469.70,448.17) --
	(478.28,446.68) --
	(486.86,446.12) --
	(495.44,445.80) --
	(504.02,445.52) --
	(512.60,445.15) --
	(521.18,444.83) --
	(529.76,444.55) --
	(538.34,444.59) --
	(546.92,444.41) --
	(555.50,444.36) --
	(564.08,444.27) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.78) --
	( 49.28,444.78) --
	( 57.86,444.36) --
	( 66.44,445.24) --
	( 75.02,445.06) --
	( 83.60,445.57) --
	( 92.18,446.59) --
	(100.76,446.87) --
	(109.34,446.40) --
	(117.92,447.89) --
	(126.50,448.58) --
	(135.08,449.65) --
	(143.66,450.53) --
	(152.24,451.78) --
	(160.82,453.83) --
	(169.40,455.17) --
	(177.98,458.33) --
	(186.56,461.48) --
	(195.14,462.96) --
	(203.72,468.53) --
	(212.30,472.20) --
	(220.88,478.88) --
	(229.46,484.44) --
	(238.04,488.94) --
	(246.62,496.18) --
	(255.20,504.53) --
	(263.78,512.83) --
	(272.36,518.31) --
	(280.94,524.80) --
	(289.52,528.00) --
	(298.10,536.31) --
	(306.68,534.45) --
	(315.26,535.61) --
	(323.84,532.73) --
	(332.42,528.10) --
	(341.00,519.88) --
	(349.58,514.64) --
	(358.16,502.86) --
	(366.74,498.87) --
	(375.32,490.38) --
	(383.90,481.38) --
	(392.48,475.21) --
	(401.06,467.23) --
	(409.64,466.35) --
	(418.22,461.20) --
	(426.80,456.61) --
	(435.38,453.59) --
	(443.96,452.94) --
	(452.54,450.86) --
	(461.12,449.56) --
	(469.70,447.42) --
	(478.28,447.93) --
	(486.86,446.31) --
	(495.44,446.12) --
	(504.02,445.06) --
	(512.60,445.57) --
	(521.18,444.78) --
	(529.76,444.59) --
	(538.34,444.41) --
	(546.92,444.18) --
	(555.50,444.32) --
	(564.08,444.32) --
	(572.66,444.18);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.92) --
	( 49.28,444.55) --
	( 57.86,444.78) --
	( 66.44,445.38) --
	( 75.02,445.24) --
	( 83.60,446.17) --
	( 92.18,446.96) --
	(100.76,446.45) --
	(109.34,447.15) --
	(117.92,448.54) --
	(126.50,449.88) --
	(135.08,450.16) --
	(143.66,451.13) --
	(152.24,452.94) --
	(160.82,454.75) --
	(169.40,457.72) --
	(177.98,461.16) --
	(186.56,463.01) --
	(195.14,466.07) --
	(203.72,472.38) --
	(212.30,477.07) --
	(220.88,482.08) --
	(229.46,488.90) --
	(238.04,495.48) --
	(246.62,504.76) --
	(255.20,508.01) --
	(263.78,514.78) --
	(272.36,526.84) --
	(280.94,526.29) --
	(289.52,536.82) --
	(298.10,534.78) --
	(306.68,535.24) --
	(315.26,536.03) --
	(323.84,528.05) --
	(332.42,521.23) --
	(341.00,515.71) --
	(349.58,507.64) --
	(358.16,502.58) --
	(366.74,488.48) --
	(375.32,483.75) --
	(383.90,474.47) --
	(392.48,469.23) --
	(401.06,467.32) --
	(409.64,461.80) --
	(418.22,456.70) --
	(426.80,456.33) --
	(435.38,451.88) --
	(443.96,451.83) --
	(452.54,449.79) --
	(461.12,447.93) --
	(469.70,447.24) --
	(478.28,446.08) --
	(486.86,445.99) --
	(495.44,445.75) --
	(504.02,445.06) --
	(512.60,444.73) --
	(521.18,444.83) --
	(529.76,444.50) --
	(538.34,444.18) --
	(546.92,444.18) --
	(555.50,444.27) --
	(564.08,444.04) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.83) --
	( 49.28,444.59) --
	( 57.86,444.83) --
	( 66.44,445.38) --
	( 75.02,445.24) --
	( 83.60,445.89) --
	( 92.18,446.50) --
	(100.76,446.91) --
	(109.34,446.54) --
	(117.92,448.03) --
	(126.50,450.07) --
	(135.08,449.74) --
	(143.66,450.72) --
	(152.24,452.94) --
	(160.82,454.34) --
	(169.40,456.66) --
	(177.98,459.76) --
	(186.56,461.48) --
	(195.14,465.33) --
	(203.72,471.18) --
	(212.30,473.87) --
	(220.88,479.29) --
	(229.46,487.60) --
	(238.04,493.95) --
	(246.62,499.89) --
	(255.20,505.60) --
	(263.78,512.97) --
	(272.36,522.62) --
	(280.94,524.15) --
	(289.52,531.58) --
	(298.10,534.31) --
	(306.68,537.61) --
	(315.26,533.66) --
	(323.84,533.85) --
	(332.42,525.08) --
	(341.00,519.19) --
	(349.58,509.77) --
	(358.16,505.36) --
	(366.74,492.38) --
	(375.32,484.67) --
	(383.90,478.88) --
	(392.48,472.01) --
	(401.06,467.37) --
	(409.64,464.08) --
	(418.22,457.63) --
	(426.80,455.96) --
	(435.38,451.78) --
	(443.96,451.41) --
	(452.54,449.84) --
	(461.12,448.17) --
	(469.70,447.52) --
	(478.28,446.59) --
	(486.86,446.17) --
	(495.44,445.61) --
	(504.02,445.24) --
	(512.60,444.96) --
	(521.18,444.36) --
	(529.76,444.69) --
	(538.34,444.45) --
	(546.92,444.45) --
	(555.50,443.99) --
	(564.08,444.18) --
	(572.66,444.18);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.73) --
	( 49.28,444.73) --
	( 57.86,445.15) --
	( 66.44,445.24) --
	( 75.02,445.52) --
	( 83.60,446.08) --
	( 92.18,446.31) --
	(100.76,447.61) --
	(109.34,447.42) --
	(117.92,448.03) --
	(126.50,449.79) --
	(135.08,450.44) --
	(143.66,451.97) --
	(152.24,453.22) --
	(160.82,454.15) --
	(169.40,458.33) --
	(177.98,460.32) --
	(186.56,463.80) --
	(195.14,467.05) --
	(203.72,472.06) --
	(212.30,477.67) --
	(220.88,480.50) --
	(229.46,488.48) --
	(238.04,493.44) --
	(246.62,503.18) --
	(255.20,513.30) --
	(263.78,514.13) --
	(272.36,520.44) --
	(280.94,527.40) --
	(289.52,533.66) --
	(298.10,532.73) --
	(306.68,535.61) --
	(315.26,532.78) --
	(323.84,527.96) --
	(332.42,517.80) --
	(341.00,518.73) --
	(349.58,504.95) --
	(358.16,499.66) --
	(366.74,491.54) --
	(375.32,482.96) --
	(383.90,475.26) --
	(392.48,470.48) --
	(401.06,467.05) --
	(409.64,460.00) --
	(418.22,457.35) --
	(426.80,454.75) --
	(435.38,452.71) --
	(443.96,450.86) --
	(452.54,449.93) --
	(461.12,448.21) --
	(469.70,447.10) --
	(478.28,447.10) --
	(486.86,446.31) --
	(495.44,445.34) --
	(504.02,445.29) --
	(512.60,444.83) --
	(521.18,444.59) --
	(529.76,444.36) --
	(538.34,444.59) --
	(546.92,444.08) --
	(555.50,444.13);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.69) --
	( 49.28,444.64) --
	( 57.86,444.92) --
	( 66.44,444.83) --
	( 75.02,445.34) --
	( 83.60,445.48) --
	( 92.18,446.26) --
	(100.76,446.22) --
	(109.34,447.84) --
	(117.92,447.42) --
	(126.50,449.00) --
	(135.08,448.95) --
	(143.66,450.86) --
	(152.24,452.94) --
	(160.82,452.94) --
	(169.40,454.06) --
	(177.98,458.33) --
	(186.56,461.29) --
	(195.14,464.87) --
	(203.72,466.91) --
	(212.30,472.80) --
	(220.88,476.79) --
	(229.46,482.96) --
	(238.04,489.64) --
	(246.62,495.07) --
	(255.20,504.39) --
	(263.78,511.72) --
	(272.36,515.01) --
	(280.94,521.97) --
	(289.52,531.48) --
	(298.10,531.81) --
	(306.68,536.54) --
	(315.26,533.85) --
	(323.84,530.28) --
	(332.42,528.42) --
	(341.00,520.07) --
	(349.58,512.56) --
	(358.16,503.56) --
	(366.74,500.03) --
	(375.32,490.94) --
	(383.90,482.73) --
	(392.48,477.53) --
	(401.06,469.64) --
	(409.64,465.75) --
	(418.22,459.76) --
	(426.80,457.07) --
	(435.38,453.50) --
	(443.96,452.16) --
	(452.54,450.81) --
	(461.12,449.09) --
	(469.70,447.98) --
	(478.28,447.05) --
	(486.86,446.36) --
	(495.44,446.31) --
	(504.02,445.24) --
	(512.60,445.29) --
	(521.18,444.59) --
	(529.76,444.73) --
	(538.34,444.55) --
	(546.92,444.45) --
	(555.50,444.04) --
	(564.08,444.13) --
	(572.66,444.08);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
	( 49.28,444.96) --
	( 57.86,444.64) --
	( 66.44,445.01) --
	( 75.02,445.15) --
	( 83.60,445.75) --
	( 92.18,445.94) --
	(100.76,446.54) --
	(109.34,447.75) --
	(117.92,447.15) --
	(126.50,449.51) --
	(135.08,448.95) --
	(143.66,451.32) --
	(152.24,452.76) --
	(160.82,452.71) --
	(169.40,454.66) --
	(177.98,457.95) --
	(186.56,462.69) --
	(195.14,464.03) --
	(203.72,467.74) --
	(212.30,473.54) --
	(220.88,476.97) --
	(229.46,482.40) --
	(238.04,491.08) --
	(246.62,497.39) --
	(255.20,503.28) --
	(263.78,510.51) --
	(272.36,517.29) --
	(280.94,521.74) --
	(289.52,529.77) --
	(298.10,532.64) --
	(306.68,537.61) --
	(315.26,534.82) --
	(323.84,530.97) --
	(332.42,526.70) --
	(341.00,521.93) --
	(349.58,509.17) --
	(358.16,504.25) --
	(366.74,495.81) --
	(375.32,487.83) --
	(383.90,479.29) --
	(392.48,476.37) --
	(401.06,469.64) --
	(409.64,465.79) --
	(418.22,460.37) --
	(426.80,457.12) --
	(435.38,455.36) --
	(443.96,451.78) --
	(452.54,450.81) --
	(461.12,448.68) --
	(469.70,448.17) --
	(478.28,446.91) --
	(486.86,446.91) --
	(495.44,445.94) --
	(504.02,445.80) --
	(512.60,445.06) --
	(521.18,444.59) --
	(529.76,444.32) --
	(538.34,444.36) --
	(546.92,444.50) --
	(555.50,444.18) --
	(564.08,444.27) --
	(572.66,444.08);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
	( 49.28,444.96) --
	( 57.86,444.83) --
	( 66.44,445.01) --
	( 75.02,445.29) --
	( 83.60,445.85) --
	( 92.18,446.08) --
	(100.76,446.59) --
	(109.34,447.42) --
	(117.92,448.35) --
	(126.50,448.77) --
	(135.08,449.05) --
	(143.66,451.41) --
	(152.24,453.27) --
	(160.82,453.04) --
	(169.40,455.36) --
	(177.98,459.21) --
	(186.56,462.13) --
	(195.14,465.19) --
	(203.72,467.93) --
	(212.30,475.35) --
	(220.88,478.18) --
	(229.46,482.63) --
	(238.04,492.56) --
	(246.62,500.40) --
	(255.20,503.09) --
	(263.78,510.37) --
	(272.36,517.52) --
	(280.94,526.43) --
	(289.52,529.49) --
	(298.10,535.56) --
	(306.68,534.45) --
	(315.26,533.57) --
	(323.84,531.06) --
	(332.42,524.25) --
	(341.00,518.31) --
	(349.58,511.30) --
	(358.16,502.86) --
	(366.74,494.23) --
	(375.32,487.92) --
	(383.90,480.96) --
	(392.48,474.84) --
	(401.06,470.80) --
	(409.64,463.01) --
	(418.22,459.21) --
	(426.80,457.77) --
	(435.38,453.59) --
	(443.96,451.69) --
	(452.54,451.88) --
	(461.12,448.26) --
	(469.70,447.70) --
	(478.28,447.98) --
	(486.86,446.17) --
	(495.44,446.17) --
	(504.02,445.94) --
	(512.60,444.73) --
	(521.18,445.10) --
	(529.76,444.55) --
	(538.34,444.83) --
	(546.92,444.08) --
	(555.50,444.04) --
	(564.08,444.22) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
	( 49.28,444.64) --
	( 57.86,444.96) --
	( 66.44,445.24) --
	( 75.02,445.24) --
	( 83.60,445.66) --
	( 92.18,446.17) --
	(100.76,446.82) --
	(109.34,447.52) --
	(117.92,448.03) --
	(126.50,448.72) --
	(135.08,449.42) --
	(143.66,451.92) --
	(152.24,452.20) --
	(160.82,453.83) --
	(169.40,456.10) --
	(177.98,458.74) --
	(186.56,461.25) --
	(195.14,465.65) --
	(203.72,468.81) --
	(212.30,473.87) --
	(220.88,478.18) --
	(229.46,485.97) --
	(238.04,492.05) --
	(246.62,498.96) --
	(255.20,504.99) --
	(263.78,510.42) --
	(272.36,518.82) --
	(280.94,527.68) --
	(289.52,527.35) --
	(298.10,536.86) --
	(306.68,535.19) --
	(315.26,535.84) --
	(323.84,528.93) --
	(332.42,525.96) --
	(341.00,518.45) --
	(349.58,511.67) --
	(358.16,501.05) --
	(366.74,495.11) --
	(375.32,485.46) --
	(383.90,479.90) --
	(392.48,473.12) --
	(401.06,469.51) --
	(409.64,463.75) --
	(418.22,460.00) --
	(426.80,455.82) --
	(435.38,452.94) --
	(443.96,451.74) --
	(452.54,450.72) --
	(461.12,448.21) --
	(469.70,447.28) --
	(478.28,447.01) --
	(486.86,446.22) --
	(495.44,446.12) --
	(504.02,445.94) --
	(512.60,445.06) --
	(521.18,444.55) --
	(529.76,444.64) --
	(538.34,444.45) --
	(546.92,444.64) --
	(555.50,444.13) --
	(564.08,444.13) --
	(572.66,444.04);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.96) --
	( 49.28,444.22) --
	( 57.86,445.29) --
	( 66.44,445.34) --
	( 75.02,445.71) --
	( 83.60,445.75) --
	( 92.18,446.91) --
	(100.76,446.17) --
	(109.34,447.47) --
	(117.92,448.35) --
	(126.50,449.42) --
	(135.08,449.79) --
	(143.66,450.49) --
	(152.24,453.64) --
	(160.82,455.50) --
	(169.40,456.75) --
	(177.98,460.18) --
	(186.56,462.50) --
	(195.14,467.28) --
	(203.72,471.36) --
	(212.30,478.13) --
	(220.88,480.87) --
	(229.46,489.59) --
	(238.04,494.42) --
	(246.62,502.21) --
	(255.20,512.97) --
	(263.78,513.85) --
	(272.36,525.64) --
	(280.94,527.26) --
	(289.52,534.31) --
	(298.10,539.65) --
	(306.68,533.43) --
	(315.26,532.41) --
	(323.84,530.69) --
	(332.42,526.61) --
	(341.00,513.16) --
	(349.58,507.73) --
	(358.16,497.48) --
	(366.74,492.42) --
	(375.32,481.01) --
	(383.90,476.88) --
	(392.48,469.46) --
	(401.06,465.10) --
	(409.64,461.99) --
	(418.22,458.14) --
	(426.80,454.71) --
	(435.38,452.71) --
	(443.96,450.86) --
	(452.54,449.93) --
	(461.12,448.86) --
	(469.70,447.10) --
	(478.28,447.05) --
	(486.86,445.29) --
	(495.44,445.38) --
	(504.02,445.24) --
	(512.60,444.92) --
	(521.18,445.01) --
	(529.76,444.32) --
	(538.34,444.55) --
	(546.92,444.08) --
	(555.50,444.13) --
	(564.08,444.13);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.73) --
	( 49.28,444.36) --
	( 57.86,445.20) --
	( 66.44,445.52) --
	( 75.02,445.29) --
	( 83.60,446.40) --
	( 92.18,446.45) --
	(100.76,446.73) --
	(109.34,447.42) --
	(117.92,448.26) --
	(126.50,449.05) --
	(135.08,450.16) --
	(143.66,451.18) --
	(152.24,453.04) --
	(160.82,455.82) --
	(169.40,457.35) --
	(177.98,460.09) --
	(186.56,462.50) --
	(195.14,466.72) --
	(203.72,473.36) --
	(212.30,477.76) --
	(220.88,480.96) --
	(229.46,487.69) --
	(238.04,494.93) --
	(246.62,500.08) --
	(255.20,512.04) --
	(263.78,514.78) --
	(272.36,523.27) --
	(280.94,527.49) --
	(289.52,534.03) --
	(298.10,538.58) --
	(306.68,535.15) --
	(315.26,529.67) --
	(323.84,530.55) --
	(332.42,527.35) --
	(341.00,514.74) --
	(349.58,507.64) --
	(358.16,497.25) --
	(366.74,493.30) --
	(375.32,482.45) --
	(383.90,472.89) --
	(392.48,470.80) --
	(401.06,466.03) --
	(409.64,461.71) --
	(418.22,455.77) --
	(426.80,456.38) --
	(435.38,452.29) --
	(443.96,450.67) --
	(452.54,449.56) --
	(461.12,448.82) --
	(469.70,447.52) --
	(478.28,447.10) --
	(486.86,445.85) --
	(495.44,445.24) --
	(504.02,445.43) --
	(512.60,445.48) --
	(521.18,444.73) --
	(529.76,444.13) --
	(538.34,444.73) --
	(546.92,444.32) --
	(555.50,444.08) --
	(564.08,444.22);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
	( 49.28,444.55) --
	( 57.86,445.29) --
	( 66.44,445.57) --
	( 75.02,445.48) --
	( 83.60,446.12) --
	( 92.18,446.26) --
	(100.76,447.24) --
	(109.34,447.52) --
	(117.92,448.12) --
	(126.50,449.42) --
	(135.08,449.93) --
	(143.66,451.13) --
	(152.24,453.41) --
	(160.82,455.22) --
	(169.40,457.35) --
	(177.98,460.37) --
	(186.56,463.85) --
	(195.14,466.17) --
	(203.72,474.05) --
	(212.30,476.46) --
	(220.88,481.75) --
	(229.46,488.94) --
	(238.04,495.58) --
	(246.62,501.33) --
	(255.20,511.67) --
	(263.78,519.24) --
	(272.36,521.93) --
	(280.94,528.61) --
	(289.52,534.27) --
	(298.10,536.77) --
	(306.68,534.96) --
	(315.26,533.06) --
	(323.84,528.61) --
	(332.42,522.95) --
	(341.00,514.36) --
	(349.58,509.26) --
	(358.16,497.71) --
	(366.74,490.47) --
	(375.32,481.33) --
	(383.90,474.98) --
	(392.48,467.42) --
	(401.06,464.96) --
	(409.64,460.69) --
	(418.22,457.91) --
	(426.80,454.47) --
	(435.38,452.29) --
	(443.96,450.62) --
	(452.54,449.46) --
	(461.12,448.12) --
	(469.70,447.70) --
	(478.28,446.73) --
	(486.86,446.50) --
	(495.44,445.01) --
	(504.02,445.24) --
	(512.60,444.78) --
	(521.18,444.45) --
	(529.76,444.55) --
	(538.34,444.27) --
	(546.92,444.45) --
	(555.50,444.32) --
	(564.08,444.08) --
	(572.66,444.13);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
	( 49.28,444.87) --
	( 57.86,445.01) --
	( 66.44,445.43) --
	( 75.02,445.38) --
	( 83.60,446.40) --
	( 92.18,446.63) --
	(100.76,446.96) --
	(109.34,447.42) --
	(117.92,447.70) --
	(126.50,449.56) --
	(135.08,450.58) --
	(143.66,450.86) --
	(152.24,453.69) --
	(160.82,454.29) --
	(169.40,459.02) --
	(177.98,459.62) --
	(186.56,463.34) --
	(195.14,466.77) --
	(203.72,472.66) --
	(212.30,475.63) --
	(220.88,482.77) --
	(229.46,489.08) --
	(238.04,493.54) --
	(246.62,503.28) --
	(255.20,506.20) --
	(263.78,518.86) --
	(272.36,521.74) --
	(280.94,527.86) --
	(289.52,533.01) --
	(298.10,537.93) --
	(306.68,536.03) --
	(315.26,529.44) --
	(323.84,530.46) --
	(332.42,525.50) --
	(341.00,515.01) --
	(349.58,506.80) --
	(358.16,500.45) --
	(366.74,491.87) --
	(375.32,482.31) --
	(383.90,476.37) --
	(392.48,469.64) --
	(401.06,464.96) --
	(409.64,460.55) --
	(418.22,457.49) --
	(426.80,454.89) --
	(435.38,454.38) --
	(443.96,450.72) --
	(452.54,448.91) --
	(461.12,447.79) --
	(469.70,448.07) --
	(478.28,446.87) --
	(486.86,445.99) --
	(495.44,445.24) --
	(504.02,445.34) --
	(512.60,444.73) --
	(521.18,444.69) --
	(529.76,444.41) --
	(538.34,444.41) --
	(546.92,444.27) --
	(555.50,444.18) --
	(564.08,444.32) --
	(572.66,444.08);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.27) --
	( 49.28,444.55) --
	( 57.86,445.38) --
	( 66.44,445.24) --
	( 75.02,445.61) --
	( 83.60,446.31) --
	( 92.18,446.40) --
	(100.76,446.73) --
	(109.34,447.61) --
	(117.92,448.40) --
	(126.50,449.37) --
	(135.08,450.58) --
	(143.66,451.18) --
	(152.24,452.90) --
	(160.82,454.06) --
	(169.40,458.65) --
	(177.98,459.72) --
	(186.56,463.52) --
	(195.14,466.26) --
	(203.72,472.15) --
	(212.30,476.83) --
	(220.88,479.94) --
	(229.46,488.71) --
	(238.04,494.46) --
	(246.62,501.93) --
	(255.20,506.01) --
	(263.78,517.43) --
	(272.36,523.50) --
	(280.94,527.35) --
	(289.52,533.38) --
	(298.10,535.66) --
	(306.68,535.52) --
	(315.26,533.99) --
	(323.84,530.69) --
	(332.42,524.94) --
	(341.00,516.50) --
	(349.58,506.43) --
	(358.16,501.70) --
	(366.74,493.72) --
	(375.32,481.15) --
	(383.90,474.14) --
	(392.48,470.76) --
	(401.06,465.28) --
	(409.64,461.76) --
	(418.22,457.40) --
	(426.80,455.82) --
	(435.38,452.71) --
	(443.96,450.02) --
	(452.54,448.54) --
	(461.12,448.86) --
	(469.70,448.21) --
	(478.28,446.54) --
	(486.86,446.08) --
	(495.44,445.29) --
	(504.02,445.10) --
	(512.60,445.06) --
	(521.18,444.78) --
	(529.76,444.50) --
	(538.34,444.50) --
	(546.92,444.27) --
	(555.50,444.41) --
	(564.08,444.08) --
	(572.66,444.18);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.70,443.99) rectangle (572.66,555.28);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.75,464.11) {500};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.75,487.30) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.75,510.50) {1500};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.75,533.69) {2000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.95,467.14) --
	( 40.70,467.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.95,490.33) --
	( 40.70,490.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.95,513.53) --
	( 40.70,513.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.95,536.72) --
	( 40.70,536.72);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,441.24) --
	( 40.70,443.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.50,441.24) --
	(126.50,443.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.30,441.24) --
	(212.30,443.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (298.10,441.24) --
	(298.10,443.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (383.90,441.24) --
	(383.90,443.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (469.70,441.24) --
	(469.70,443.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (555.50,441.24) --
	(555.50,443.99);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 40.70,432.98) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (126.50,432.98) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (212.30,432.98) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (298.10,432.98) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (383.90,432.98) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (469.70,432.98) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (555.50,432.98) {50};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (306.68,420.80) {Time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,499.64) {Daily incidence};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);

\path[] ( 45.09,453.59) rectangle (121.42,556.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);

\path[] ( 45.09,453.59) rectangle (121.42,556.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 50.59,528.47) rectangle ( 67.93,545.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,537.14) -- ( 66.20,537.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 50.59,511.12) rectangle ( 67.93,528.47);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,519.79) -- ( 66.20,519.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 50.59,493.78) rectangle ( 67.93,511.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,502.45) -- ( 66.20,502.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 50.59,476.43) rectangle ( 67.93,493.78);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,485.11) -- ( 66.20,485.11);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 50.59,459.09) rectangle ( 67.93,476.43);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,467.76) -- ( 66.20,467.76);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,534.11) {$\rho=0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,516.76) {$\rho=0.2$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,499.42) {$\rho=0.4$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,482.07) {$\rho=0.6$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,464.73) {$\rho=0.8$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 40.70,563.57) {A};
\end{scope}
\begin{scope}
\path[clip] (  0.00,206.49) rectangle (192.72,412.97);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,206.49) rectangle (192.72,412.97);
\end{scope}
\begin{scope}
\path[clip] ( 27.50,237.50) rectangle (187.22,390.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.50,237.50) rectangle (187.22,390.09);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,356.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,356.89) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,358.01) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.20) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,357.80) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.23) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.98) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.73) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.72) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.59) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.48) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.72) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.49) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,354.92) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,356.93) circle (  2.50);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,356.64) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.22) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,357.59) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.23) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,357.86) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.20) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.90) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.88) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.66) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.56) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.51) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.78) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.07) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,357.24) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,355.42) circle (  2.50);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,357.11) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.46) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,357.42) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.37) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.66) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,357.98) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.20) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.87) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.88) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.62) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.67) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.38) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.37) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,359.12) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,355.67) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,356.17) circle (  2.50);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,357.29) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.65) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,357.48) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.69) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.34) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,358.05) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.17) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.90) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.90) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.55) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.74) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.36) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.69) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.30) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,357.14) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,357.74) circle (  2.50);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,358.36) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.14) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,357.19) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.54) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.47) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,358.07) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.17) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.84) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.95) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.55) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.66) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.50) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.80) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,357.56) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,358.55) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,356.45) circle (  2.50);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,356.77) --
	( 29.46,356.84) --
	( 31.41,356.90) --
	( 33.37,356.97) --
	( 35.32,357.03) --
	( 37.28,357.09) --
	( 39.24,357.15) --
	( 41.19,357.21) --
	( 43.15,357.27) --
	( 45.11,357.32) --
	( 47.06,357.37) --
	( 49.02,357.42) --
	( 50.98,357.47) --
	( 52.93,357.51) --
	( 54.89,357.56) --
	( 56.85,357.60) --
	( 58.80,357.64) --
	( 60.76,357.67) --
	( 62.72,357.71) --
	( 64.67,357.74) --
	( 66.63,357.77) --
	( 68.59,357.79) --
	( 70.54,357.82) --
	( 72.50,357.84) --
	( 74.46,357.86) --
	( 76.41,357.88) --
	( 78.37,357.89) --
	( 80.33,357.91) --
	( 82.28,357.91) --
	( 84.24,357.92) --
	( 86.20,357.92) --
	( 88.15,357.92) --
	( 90.11,357.91) --
	( 92.07,357.91) --
	( 94.02,357.91) --
	( 95.98,357.90) --
	( 97.94,357.90) --
	( 99.89,357.91) --
	(101.85,357.91) --
	(103.80,357.91) --
	(105.76,357.91) --
	(107.72,357.91) --
	(109.67,357.91) --
	(111.63,357.91) --
	(113.59,357.91) --
	(115.54,357.91) --
	(117.50,357.91) --
	(119.46,357.90) --
	(121.41,357.90) --
	(123.37,357.91) --
	(125.33,357.92) --
	(127.28,357.93) --
	(129.24,357.94) --
	(131.20,357.94) --
	(133.15,357.95) --
	(135.11,357.95) --
	(137.07,357.94) --
	(139.02,357.92) --
	(140.98,357.88) --
	(142.94,357.84) --
	(144.89,357.80) --
	(146.85,357.75) --
	(148.81,357.70) --
	(150.76,357.65) --
	(152.72,357.59) --
	(154.68,357.53) --
	(156.63,357.46) --
	(158.59,357.39) --
	(160.55,357.32) --
	(162.50,357.24) --
	(164.46,357.16) --
	(166.42,357.07) --
	(168.37,356.98) --
	(170.33,356.88) --
	(172.28,356.78) --
	(174.24,356.68) --
	(176.20,356.57) --
	(178.15,356.46) --
	(180.11,356.34) --
	(182.07,356.22);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,356.74) --
	( 29.46,356.81) --
	( 31.41,356.88) --
	( 33.37,356.94) --
	( 35.32,357.00) --
	( 37.28,357.06) --
	( 39.24,357.12) --
	( 41.19,357.18) --
	( 43.15,357.24) --
	( 45.11,357.29) --
	( 47.06,357.34) --
	( 49.02,357.39) --
	( 50.98,357.44) --
	( 52.93,357.48) --
	( 54.89,357.53) --
	( 56.85,357.57) --
	( 58.80,357.61) --
	( 60.76,357.64) --
	( 62.72,357.68) --
	( 64.67,357.71) --
	( 66.63,357.74) --
	( 68.59,357.77) --
	( 70.54,357.79) --
	( 72.50,357.82) --
	( 74.46,357.84) --
	( 76.41,357.86) --
	( 78.37,357.88) --
	( 80.33,357.89) --
	( 82.28,357.91) --
	( 84.24,357.91) --
	( 86.20,357.92) --
	( 88.15,357.92) --
	( 90.11,357.92) --
	( 92.07,357.92) --
	( 94.02,357.92) --
	( 95.98,357.91) --
	( 97.94,357.92) --
	( 99.89,357.92) --
	(101.85,357.92) --
	(103.80,357.92) --
	(105.76,357.91) --
	(107.72,357.91) --
	(109.67,357.90) --
	(111.63,357.89) --
	(113.59,357.88) --
	(115.54,357.87) --
	(117.50,357.87) --
	(119.46,357.86) --
	(121.41,357.87) --
	(123.37,357.88) --
	(125.33,357.90) --
	(127.28,357.93) --
	(129.24,357.96) --
	(131.20,357.99) --
	(133.15,358.01) --
	(135.11,358.03) --
	(137.07,358.03) --
	(139.02,358.03) --
	(140.98,358.00) --
	(142.94,357.97) --
	(144.89,357.93) --
	(146.85,357.89) --
	(148.81,357.85) --
	(150.76,357.80) --
	(152.72,357.75) --
	(154.68,357.68) --
	(156.63,357.62) --
	(158.59,357.54) --
	(160.55,357.45) --
	(162.50,357.36) --
	(164.46,357.26) --
	(166.42,357.15) --
	(168.37,357.03) --
	(170.33,356.91) --
	(172.28,356.78) --
	(174.24,356.64) --
	(176.20,356.49) --
	(178.15,356.34) --
	(180.11,356.18) --
	(182.07,356.02);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,357.12) --
	( 29.46,357.15) --
	( 31.41,357.19) --
	( 33.37,357.22) --
	( 35.32,357.26) --
	( 37.28,357.29) --
	( 39.24,357.33) --
	( 41.19,357.36) --
	( 43.15,357.40) --
	( 45.11,357.43) --
	( 47.06,357.46) --
	( 49.02,357.50) --
	( 50.98,357.53) --
	( 52.93,357.56) --
	( 54.89,357.59) --
	( 56.85,357.61) --
	( 58.80,357.64) --
	( 60.76,357.67) --
	( 62.72,357.69) --
	( 64.67,357.72) --
	( 66.63,357.75) --
	( 68.59,357.77) --
	( 70.54,357.80) --
	( 72.50,357.82) --
	( 74.46,357.84) --
	( 76.41,357.86) --
	( 78.37,357.88) --
	( 80.33,357.89) --
	( 82.28,357.90) --
	( 84.24,357.91) --
	( 86.20,357.92) --
	( 88.15,357.92) --
	( 90.11,357.93) --
	( 92.07,357.93) --
	( 94.02,357.93) --
	( 95.98,357.93) --
	( 97.94,357.93) --
	( 99.89,357.94) --
	(101.85,357.93) --
	(103.80,357.93) --
	(105.76,357.92) --
	(107.72,357.91) --
	(109.67,357.89) --
	(111.63,357.88) --
	(113.59,357.86) --
	(115.54,357.85) --
	(117.50,357.84) --
	(119.46,357.84) --
	(121.41,357.84) --
	(123.37,357.85) --
	(125.33,357.87) --
	(127.28,357.89) --
	(129.24,357.92) --
	(131.20,357.95) --
	(133.15,357.97) --
	(135.11,357.98) --
	(137.07,357.98) --
	(139.02,357.97) --
	(140.98,357.95) --
	(142.94,357.91) --
	(144.89,357.87) --
	(146.85,357.83) --
	(148.81,357.78) --
	(150.76,357.73) --
	(152.72,357.68) --
	(154.68,357.62) --
	(156.63,357.55) --
	(158.59,357.47) --
	(160.55,357.39) --
	(162.50,357.30) --
	(164.46,357.21) --
	(166.42,357.11) --
	(168.37,357.00) --
	(170.33,356.89) --
	(172.28,356.77) --
	(174.24,356.65) --
	(176.20,356.52) --
	(178.15,356.38) --
	(180.11,356.24) --
	(182.07,356.10);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,357.34) --
	( 29.46,357.36) --
	( 31.41,357.39) --
	( 33.37,357.41) --
	( 35.32,357.43) --
	( 37.28,357.45) --
	( 39.24,357.48) --
	( 41.19,357.50) --
	( 43.15,357.52) --
	( 45.11,357.55) --
	( 47.06,357.57) --
	( 49.02,357.59) --
	( 50.98,357.61) --
	( 52.93,357.63) --
	( 54.89,357.65) --
	( 56.85,357.67) --
	( 58.80,357.69) --
	( 60.76,357.71) --
	( 62.72,357.73) --
	( 64.67,357.75) --
	( 66.63,357.76) --
	( 68.59,357.78) --
	( 70.54,357.80) --
	( 72.50,357.82) --
	( 74.46,357.83) --
	( 76.41,357.85) --
	( 78.37,357.86) --
	( 80.33,357.87) --
	( 82.28,357.88) --
	( 84.24,357.89) --
	( 86.20,357.89) --
	( 88.15,357.90) --
	( 90.11,357.90) --
	( 92.07,357.90) --
	( 94.02,357.90) --
	( 95.98,357.91) --
	( 97.94,357.91) --
	( 99.89,357.91) --
	(101.85,357.91) --
	(103.80,357.91) --
	(105.76,357.90) --
	(107.72,357.90) --
	(109.67,357.89) --
	(111.63,357.88) --
	(113.59,357.87) --
	(115.54,357.86) --
	(117.50,357.85) --
	(119.46,357.85) --
	(121.41,357.85) --
	(123.37,357.85) --
	(125.33,357.86) --
	(127.28,357.87) --
	(129.24,357.87) --
	(131.20,357.88) --
	(133.15,357.88) --
	(135.11,357.89) --
	(137.07,357.89) --
	(139.02,357.89) --
	(140.98,357.89) --
	(142.94,357.88) --
	(144.89,357.87) --
	(146.85,357.87) --
	(148.81,357.86) --
	(150.76,357.85) --
	(152.72,357.85) --
	(154.68,357.84) --
	(156.63,357.83) --
	(158.59,357.82) --
	(160.55,357.80) --
	(162.50,357.79) --
	(164.46,357.77) --
	(166.42,357.75) --
	(168.37,357.74) --
	(170.33,357.72) --
	(172.28,357.70) --
	(174.24,357.67) --
	(176.20,357.65) --
	(178.15,357.63) --
	(180.11,357.60) --
	(182.07,357.58);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,357.81) --
	( 29.46,357.77) --
	( 31.41,357.74) --
	( 33.37,357.71) --
	( 35.32,357.69) --
	( 37.28,357.66) --
	( 39.24,357.64) --
	( 41.19,357.63) --
	( 43.15,357.62) --
	( 45.11,357.61) --
	( 47.06,357.60) --
	( 49.02,357.59) --
	( 50.98,357.59) --
	( 52.93,357.59) --
	( 54.89,357.59) --
	( 56.85,357.59) --
	( 58.80,357.59) --
	( 60.76,357.60) --
	( 62.72,357.62) --
	( 64.67,357.64) --
	( 66.63,357.67) --
	( 68.59,357.70) --
	( 70.54,357.74) --
	( 72.50,357.77) --
	( 74.46,357.80) --
	( 76.41,357.83) --
	( 78.37,357.85) --
	( 80.33,357.86) --
	( 82.28,357.88) --
	( 84.24,357.89) --
	( 86.20,357.89) --
	( 88.15,357.90) --
	( 90.11,357.90) --
	( 92.07,357.91) --
	( 94.02,357.91) --
	( 95.98,357.91) --
	( 97.94,357.92) --
	( 99.89,357.92) --
	(101.85,357.92) --
	(103.80,357.92) --
	(105.76,357.91) --
	(107.72,357.90) --
	(109.67,357.89) --
	(111.63,357.88) --
	(113.59,357.87) --
	(115.54,357.87) --
	(117.50,357.86) --
	(119.46,357.85) --
	(121.41,357.85) --
	(123.37,357.86) --
	(125.33,357.87) --
	(127.28,357.88) --
	(129.24,357.90) --
	(131.20,357.92) --
	(133.15,357.93) --
	(135.11,357.94) --
	(137.07,357.95) --
	(139.02,357.95) --
	(140.98,357.94) --
	(142.94,357.93) --
	(144.89,357.92) --
	(146.85,357.91) --
	(148.81,357.90) --
	(150.76,357.88) --
	(152.72,357.87) --
	(154.68,357.85) --
	(156.63,357.82) --
	(158.59,357.79) --
	(160.55,357.76) --
	(162.50,357.72) --
	(164.46,357.68) --
	(166.42,357.63) --
	(168.37,357.58) --
	(170.33,357.52) --
	(172.28,357.46) --
	(174.24,357.40) --
	(176.20,357.34) --
	(178.15,357.27) --
	(180.11,357.20) --
	(182.07,357.12);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.50,237.50) rectangle (187.22,390.09);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.55,234.47) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.55,278.07) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.55,321.67) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.55,365.26) {6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.75,237.50) --
	( 27.50,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.75,281.10) --
	( 27.50,281.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.75,324.70) --
	( 27.50,324.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.75,368.29) --
	( 27.50,368.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.50,234.75) --
	( 27.50,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 53.26,234.75) --
	( 53.26,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.02,234.75) --
	( 79.02,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.78,234.75) --
	(104.78,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54,234.75) --
	(130.54,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.31,234.75) --
	(156.31,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (182.07,234.75) --
	(182.07,237.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.50,226.49) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 53.26,226.49) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 79.02,226.49) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (104.78,226.49) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (130.54,226.49) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (156.31,226.49) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (182.07,226.49) {50};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (107.36,214.31) {Primary cohort time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,313.80) {Forward delay (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.50,398.38) {B. Incubation period};
\end{scope}
\begin{scope}
\path[clip] (192.72,206.49) rectangle (385.44,412.97);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (192.72,206.49) rectangle (385.44,412.97);
\end{scope}
\begin{scope}
\path[clip] (220.22,237.50) rectangle (379.94,390.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (220.22,237.50) rectangle (379.94,390.09);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,345.69) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.39) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.59) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.70) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.86) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.54) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.69) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,338.91) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.45) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,340.23) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,342.59) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.54) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,343.75) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,343.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,344.37) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,346.69) circle (  2.50);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,345.65) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.38) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.55) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.62) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.89) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.75) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.83) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,338.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.85) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.79) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,342.27) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.42) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,344.80) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,342.61) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,343.07) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,342.06) circle (  2.50);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,346.03) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.59) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.12) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.74) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.80) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.66) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.87) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,339.00) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.83) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,342.34) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.86) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,343.44) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,343.43) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,338.93) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,340.60) circle (  2.50);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,346.05) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.74) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.09) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.73) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.62) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.87) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,341.03) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,339.16) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.90) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.83) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,342.50) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.60) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,344.19) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,344.00) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,340.09) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,350.98) circle (  2.50);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,347.09) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.85) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,345.51) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.62) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.79) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,341.14) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,339.03) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.61) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,341.84) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.33) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,346.47) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,344.80) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,343.58) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,347.56) circle (  2.50);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.12) --
	(222.18,346.10) --
	(224.13,346.08) --
	(226.09,346.04) --
	(228.04,346.00) --
	(230.00,345.94) --
	(231.96,345.87) --
	(233.91,345.78) --
	(235.87,345.68) --
	(237.83,345.57) --
	(239.78,345.45) --
	(241.74,345.33) --
	(243.70,345.19) --
	(245.65,345.05) --
	(247.61,344.91) --
	(249.57,344.76) --
	(251.52,344.60) --
	(253.48,344.43) --
	(255.44,344.23) --
	(257.39,344.01) --
	(259.35,343.78) --
	(261.31,343.53) --
	(263.26,343.28) --
	(265.22,343.03) --
	(267.18,342.78) --
	(269.13,342.54) --
	(271.09,342.32) --
	(273.05,342.09) --
	(275.00,341.83) --
	(276.96,341.53) --
	(278.92,341.22) --
	(280.87,340.89) --
	(282.83,340.57) --
	(284.79,340.28) --
	(286.74,340.01) --
	(288.70,339.79) --
	(290.66,339.63) --
	(292.61,339.54) --
	(294.57,339.51) --
	(296.52,339.53) --
	(298.48,339.59) --
	(300.44,339.69) --
	(302.39,339.80) --
	(304.35,339.94) --
	(306.31,340.09) --
	(308.26,340.24) --
	(310.22,340.38) --
	(312.18,340.52) --
	(314.13,340.65) --
	(316.09,340.81) --
	(318.05,341.00) --
	(320.00,341.22) --
	(321.96,341.45) --
	(323.92,341.70) --
	(325.87,341.94) --
	(327.83,342.18) --
	(329.79,342.41) --
	(331.74,342.61) --
	(333.70,342.79) --
	(335.66,342.95) --
	(337.61,343.12) --
	(339.57,343.29) --
	(341.53,343.46) --
	(343.48,343.63) --
	(345.44,343.80) --
	(347.40,343.97) --
	(349.35,344.13) --
	(351.31,344.30) --
	(353.27,344.45) --
	(355.22,344.61) --
	(357.18,344.76) --
	(359.14,344.90) --
	(361.09,345.05) --
	(363.05,345.19) --
	(365.00,345.34) --
	(366.96,345.48) --
	(368.92,345.61) --
	(370.87,345.75) --
	(372.83,345.88) --
	(374.79,346.02);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.05) --
	(222.18,346.03) --
	(224.13,346.02) --
	(226.09,345.99) --
	(228.04,345.95) --
	(230.00,345.90) --
	(231.96,345.83) --
	(233.91,345.76) --
	(235.87,345.67) --
	(237.83,345.57) --
	(239.78,345.46) --
	(241.74,345.34) --
	(243.70,345.21) --
	(245.65,345.08) --
	(247.61,344.94) --
	(249.57,344.80) --
	(251.52,344.65) --
	(253.48,344.48) --
	(255.44,344.29) --
	(257.39,344.08) --
	(259.35,343.86) --
	(261.31,343.62) --
	(263.26,343.38) --
	(265.22,343.14) --
	(267.18,342.90) --
	(269.13,342.67) --
	(271.09,342.45) --
	(273.05,342.23) --
	(275.00,341.96) --
	(276.96,341.66) --
	(278.92,341.34) --
	(280.87,341.01) --
	(282.83,340.69) --
	(284.79,340.38) --
	(286.74,340.11) --
	(288.70,339.88) --
	(290.66,339.71) --
	(292.61,339.62) --
	(294.57,339.58) --
	(296.52,339.60) --
	(298.48,339.65) --
	(300.44,339.74) --
	(302.39,339.85) --
	(304.35,339.98) --
	(306.31,340.12) --
	(308.26,340.27) --
	(310.22,340.40) --
	(312.18,340.53) --
	(314.13,340.65) --
	(316.09,340.82) --
	(318.05,341.04) --
	(320.00,341.28) --
	(321.96,341.54) --
	(323.92,341.82) --
	(325.87,342.08) --
	(327.83,342.33) --
	(329.79,342.54) --
	(331.74,342.71) --
	(333.70,342.83) --
	(335.66,342.91) --
	(337.61,343.00) --
	(339.57,343.08) --
	(341.53,343.16) --
	(343.48,343.22) --
	(345.44,343.28) --
	(347.40,343.33) --
	(349.35,343.36) --
	(351.31,343.37) --
	(353.27,343.36) --
	(355.22,343.33) --
	(357.18,343.29) --
	(359.14,343.23) --
	(361.09,343.16) --
	(363.05,343.08) --
	(365.00,342.98) --
	(366.96,342.87) --
	(368.92,342.75) --
	(370.87,342.61) --
	(372.83,342.46) --
	(374.79,342.30);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.34) --
	(222.18,346.29) --
	(224.13,346.24) --
	(226.09,346.18) --
	(228.04,346.11) --
	(230.00,346.03) --
	(231.96,345.94) --
	(233.91,345.84) --
	(235.87,345.72) --
	(237.83,345.60) --
	(239.78,345.47) --
	(241.74,345.34) --
	(243.70,345.20) --
	(245.65,345.05) --
	(247.61,344.90) --
	(249.57,344.74) --
	(251.52,344.58) --
	(253.48,344.41) --
	(255.44,344.21) --
	(257.39,344.00) --
	(259.35,343.78) --
	(261.31,343.55) --
	(263.26,343.31) --
	(265.22,343.07) --
	(267.18,342.83) --
	(269.13,342.61) --
	(271.09,342.39) --
	(273.05,342.17) --
	(275.00,341.92) --
	(276.96,341.63) --
	(278.92,341.32) --
	(280.87,341.00) --
	(282.83,340.69) --
	(284.79,340.40) --
	(286.74,340.13) --
	(288.70,339.92) --
	(290.66,339.76) --
	(292.61,339.66) --
	(294.57,339.64) --
	(296.52,339.67) --
	(298.48,339.74) --
	(300.44,339.84) --
	(302.39,339.97) --
	(304.35,340.12) --
	(306.31,340.27) --
	(308.26,340.42) --
	(310.22,340.57) --
	(312.18,340.69) --
	(314.13,340.80) --
	(316.09,340.96) --
	(318.05,341.16) --
	(320.00,341.39) --
	(321.96,341.64) --
	(323.92,341.89) --
	(325.87,342.13) --
	(327.83,342.35) --
	(329.79,342.52) --
	(331.74,342.65) --
	(333.70,342.70) --
	(335.66,342.72) --
	(337.61,342.73) --
	(339.57,342.74) --
	(341.53,342.73) --
	(343.48,342.71) --
	(345.44,342.68) --
	(347.40,342.63) --
	(349.35,342.56) --
	(351.31,342.47) --
	(353.27,342.35) --
	(355.22,342.22) --
	(357.18,342.06) --
	(359.14,341.88) --
	(361.09,341.69) --
	(363.05,341.48) --
	(365.00,341.25) --
	(366.96,341.00) --
	(368.92,340.74) --
	(370.87,340.45) --
	(372.83,340.15) --
	(374.79,339.83);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.38) --
	(222.18,346.33) --
	(224.13,346.28) --
	(226.09,346.22) --
	(228.04,346.14) --
	(230.00,346.06) --
	(231.96,345.97) --
	(233.91,345.86) --
	(235.87,345.75) --
	(237.83,345.63) --
	(239.78,345.50) --
	(241.74,345.37) --
	(243.70,345.22) --
	(245.65,345.08) --
	(247.61,344.93) --
	(249.57,344.77) --
	(251.52,344.62) --
	(253.48,344.44) --
	(255.44,344.25) --
	(257.39,344.04) --
	(259.35,343.82) --
	(261.31,343.59) --
	(263.26,343.36) --
	(265.22,343.13) --
	(267.18,342.89) --
	(269.13,342.67) --
	(271.09,342.46) --
	(273.05,342.24) --
	(275.00,341.99) --
	(276.96,341.70) --
	(278.92,341.40) --
	(280.87,341.08) --
	(282.83,340.78) --
	(284.79,340.49) --
	(286.74,340.23) --
	(288.70,340.02) --
	(290.66,339.86) --
	(292.61,339.76) --
	(294.57,339.73) --
	(296.52,339.75) --
	(298.48,339.81) --
	(300.44,339.89) --
	(302.39,340.01) --
	(304.35,340.13) --
	(306.31,340.27) --
	(308.26,340.41) --
	(310.22,340.55) --
	(312.18,340.67) --
	(314.13,340.78) --
	(316.09,340.91) --
	(318.05,341.05) --
	(320.00,341.21) --
	(321.96,341.38) --
	(323.92,341.56) --
	(325.87,341.74) --
	(327.83,341.93) --
	(329.79,342.11) --
	(331.74,342.28) --
	(333.70,342.45) --
	(335.66,342.61) --
	(337.61,342.78) --
	(339.57,342.95) --
	(341.53,343.12) --
	(343.48,343.31) --
	(345.44,343.50) --
	(347.40,343.70) --
	(349.35,343.90) --
	(351.31,344.12) --
	(353.27,344.34) --
	(355.22,344.58) --
	(357.18,344.82) --
	(359.14,345.07) --
	(361.09,345.33) --
	(363.05,345.59) --
	(365.00,345.86) --
	(366.96,346.14) --
	(368.92,346.43) --
	(370.87,346.72) --
	(372.83,347.02) --
	(374.79,347.33);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,347.01) --
	(222.18,346.89) --
	(224.13,346.78) --
	(226.09,346.65) --
	(228.04,346.52) --
	(230.00,346.39) --
	(231.96,346.25) --
	(233.91,346.10) --
	(235.87,345.94) --
	(237.83,345.78) --
	(239.78,345.62) --
	(241.74,345.45) --
	(243.70,345.28) --
	(245.65,345.10) --
	(247.61,344.92) --
	(249.57,344.74) --
	(251.52,344.56) --
	(253.48,344.37) --
	(255.44,344.17) --
	(257.39,343.96) --
	(259.35,343.74) --
	(261.31,343.52) --
	(263.26,343.29) --
	(265.22,343.07) --
	(267.18,342.85) --
	(269.13,342.63) --
	(271.09,342.42) --
	(273.05,342.20) --
	(275.00,341.94) --
	(276.96,341.65) --
	(278.92,341.33) --
	(280.87,341.01) --
	(282.83,340.69) --
	(284.79,340.38) --
	(286.74,340.11) --
	(288.70,339.89) --
	(290.66,339.72) --
	(292.61,339.62) --
	(294.57,339.58) --
	(296.52,339.57) --
	(298.48,339.59) --
	(300.44,339.65) --
	(302.39,339.73) --
	(304.35,339.82) --
	(306.31,339.94) --
	(308.26,340.06) --
	(310.22,340.20) --
	(312.18,340.33) --
	(314.13,340.48) --
	(316.09,340.68) --
	(318.05,340.92) --
	(320.00,341.19) --
	(321.96,341.48) --
	(323.92,341.78) --
	(325.87,342.09) --
	(327.83,342.38) --
	(329.79,342.65) --
	(331.74,342.90) --
	(333.70,343.10) --
	(335.66,343.28) --
	(337.61,343.47) --
	(339.57,343.66) --
	(341.53,343.86) --
	(343.48,344.05) --
	(345.44,344.24) --
	(347.40,344.43) --
	(349.35,344.62) --
	(351.31,344.80) --
	(353.27,344.97) --
	(355.22,345.14) --
	(357.18,345.30) --
	(359.14,345.45) --
	(361.09,345.60) --
	(363.05,345.75) --
	(365.00,345.89) --
	(366.96,346.03) --
	(368.92,346.17) --
	(370.87,346.30) --
	(372.83,346.43) --
	(374.79,346.55);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (220.22,237.50) rectangle (379.94,390.09);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (215.27,234.47) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (215.27,278.07) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (215.27,321.67) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (215.27,365.26) {6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.47,237.50) --
	(220.22,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.47,281.10) --
	(220.22,281.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.47,324.70) --
	(220.22,324.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.47,368.29) --
	(220.22,368.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.22,234.75) --
	(220.22,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (245.98,234.75) --
	(245.98,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.74,234.75) --
	(271.74,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.50,234.75) --
	(297.50,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.26,234.75) --
	(323.26,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (349.03,234.75) --
	(349.03,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.79,234.75) --
	(374.79,237.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (220.22,226.49) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.98,226.49) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.74,226.49) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (297.50,226.49) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (323.26,226.49) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (349.03,226.49) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (374.79,226.49) {50};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (300.08,214.31) {Primary cohort time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (205.80,313.80) {Forward delay (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (220.22,398.38) {C. Generation interval};
\end{scope}
\begin{scope}
\path[clip] (385.44,206.49) rectangle (578.16,412.97);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (385.44,206.49) rectangle (578.16,412.97);
\end{scope}
\begin{scope}
\path[clip] (412.94,237.50) rectangle (572.66,390.09);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (412.94,237.50) rectangle (572.66,390.09);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,369.28) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,362.39) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,365.59) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,365.00) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,362.95) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,361.48) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,357.71) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,351.53) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,342.52) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,332.39) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,321.34) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,310.19) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,301.60) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,297.53) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,287.48) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,279.29) circle (  2.50);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,365.64) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,358.37) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,361.32) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,361.46) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,361.50) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,359.26) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,356.35) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,351.11) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,343.69) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,334.90) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,325.46) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,316.50) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,309.10) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,302.82) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,299.01) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,295.21) circle (  2.50);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,363.32) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,355.97) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,357.79) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,359.54) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,358.46) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,357.46) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,354.60) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,350.94) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,345.09) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,337.45) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,329.93) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,322.82) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,316.14) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,314.22) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,301.62) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,299.44) circle (  2.50);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,357.59) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,354.25) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,355.79) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,356.74) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,355.19) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,355.24) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,352.83) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,350.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,345.94) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,340.67) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,334.78) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,329.05) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,324.01) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,320.28) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,315.23) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,312.23) circle (  2.50);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,354.57) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,351.30) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,352.97) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,353.67) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,352.63) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,352.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,351.69) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,350.19) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,346.97) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,343.86) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,339.79) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,336.17) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,332.07) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,329.75) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,326.98) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,318.93) circle (  2.50);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,365.83) --
	(414.90,366.04) --
	(416.85,366.21) --
	(418.81,366.36) --
	(420.76,366.47) --
	(422.72,366.56) --
	(424.68,366.62) --
	(426.63,366.66) --
	(428.59,366.66) --
	(430.55,366.64) --
	(432.50,366.59) --
	(434.46,366.50) --
	(436.42,366.37) --
	(438.37,366.21) --
	(440.33,366.01) --
	(442.29,365.77) --
	(444.24,365.49) --
	(446.20,365.20) --
	(448.16,364.91) --
	(450.11,364.61) --
	(452.07,364.30) --
	(454.03,363.95) --
	(455.98,363.57) --
	(457.94,363.13) --
	(459.90,362.64) --
	(461.85,362.08) --
	(463.81,361.44) --
	(465.77,360.72) --
	(467.72,359.95) --
	(469.68,359.12) --
	(471.64,358.25) --
	(473.59,357.31) --
	(475.55,356.32) --
	(477.51,355.27) --
	(479.46,354.16) --
	(481.42,352.99) --
	(483.38,351.76) --
	(485.33,350.46) --
	(487.29,349.03) --
	(489.24,347.46) --
	(491.20,345.76) --
	(493.16,343.97) --
	(495.11,342.11) --
	(497.07,340.21) --
	(499.03,338.30) --
	(500.98,336.40) --
	(502.94,334.54) --
	(504.90,332.75) --
	(506.85,331.01) --
	(508.81,329.22) --
	(510.77,327.36) --
	(512.72,325.46) --
	(514.68,323.53) --
	(516.64,321.60) --
	(518.59,319.67) --
	(520.55,317.77) --
	(522.51,315.90) --
	(524.46,314.10) --
	(526.42,312.37) --
	(528.38,310.69) --
	(530.33,309.00) --
	(532.29,307.33) --
	(534.25,305.66) --
	(536.20,304.00) --
	(538.16,302.35) --
	(540.12,300.72) --
	(542.07,299.11) --
	(544.03,297.51) --
	(545.99,295.94) --
	(547.94,294.38) --
	(549.90,292.85) --
	(551.86,291.33) --
	(553.81,289.83) --
	(555.77,288.34) --
	(557.72,286.86) --
	(559.68,285.41) --
	(561.64,283.97) --
	(563.59,282.54) --
	(565.55,281.13) --
	(567.51,279.73);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,361.86) --
	(414.90,362.08) --
	(416.85,362.26) --
	(418.81,362.42) --
	(420.76,362.55) --
	(422.72,362.67) --
	(424.68,362.76) --
	(426.63,362.83) --
	(428.59,362.89) --
	(430.55,362.91) --
	(432.50,362.91) --
	(434.46,362.88) --
	(436.42,362.82) --
	(438.37,362.73) --
	(440.33,362.61) --
	(442.29,362.45) --
	(444.24,362.25) --
	(446.20,362.06) --
	(448.16,361.88) --
	(450.11,361.69) --
	(452.07,361.49) --
	(454.03,361.27) --
	(455.98,361.02) --
	(457.94,360.72) --
	(459.90,360.37) --
	(461.85,359.95) --
	(463.81,359.46) --
	(465.77,358.89) --
	(467.72,358.26) --
	(469.68,357.59) --
	(471.64,356.86) --
	(473.59,356.07) --
	(475.55,355.24) --
	(477.51,354.35) --
	(479.46,353.41) --
	(481.42,352.42) --
	(483.38,351.38) --
	(485.33,350.29) --
	(487.29,349.09) --
	(489.24,347.77) --
	(491.20,346.34) --
	(493.16,344.83) --
	(495.11,343.27) --
	(497.07,341.67) --
	(499.03,340.05) --
	(500.98,338.44) --
	(502.94,336.87) --
	(504.90,335.34) --
	(506.85,333.86) --
	(508.81,332.29) --
	(510.77,330.66) --
	(512.72,328.97) --
	(514.68,327.25) --
	(516.64,325.52) --
	(518.59,323.81) --
	(520.55,322.14) --
	(522.51,320.53) --
	(524.46,319.00) --
	(526.42,317.58) --
	(528.38,316.22) --
	(530.33,314.87) --
	(532.29,313.53) --
	(534.25,312.20) --
	(536.20,310.90) --
	(538.16,309.62) --
	(540.12,308.37) --
	(542.07,307.15) --
	(544.03,305.96) --
	(545.99,304.82) --
	(547.94,303.71) --
	(549.90,302.63) --
	(551.86,301.58) --
	(553.81,300.56) --
	(555.77,299.57) --
	(557.72,298.61) --
	(559.68,297.68) --
	(561.64,296.77) --
	(563.59,295.90) --
	(565.55,295.05) --
	(567.51,294.23);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,359.64) --
	(414.90,359.75) --
	(416.85,359.84) --
	(418.81,359.91) --
	(420.76,359.96) --
	(422.72,360.01) --
	(424.68,360.04) --
	(426.63,360.06) --
	(428.59,360.07) --
	(430.55,360.05) --
	(432.50,360.03) --
	(434.46,359.98) --
	(436.42,359.91) --
	(438.37,359.82) --
	(440.33,359.70) --
	(442.29,359.56) --
	(444.24,359.39) --
	(446.20,359.24) --
	(448.16,359.09) --
	(450.11,358.96) --
	(452.07,358.82) --
	(454.03,358.67) --
	(455.98,358.49) --
	(457.94,358.28) --
	(459.90,358.03) --
	(461.85,357.72) --
	(463.81,357.34) --
	(465.77,356.90) --
	(467.72,356.41) --
	(469.68,355.89) --
	(471.64,355.32) --
	(473.59,354.70) --
	(475.55,354.05) --
	(477.51,353.35) --
	(479.46,352.61) --
	(481.42,351.82) --
	(483.38,350.99) --
	(485.33,350.11) --
	(487.29,349.15) --
	(489.24,348.09) --
	(491.20,346.94) --
	(493.16,345.73) --
	(495.11,344.48) --
	(497.07,343.19) --
	(499.03,341.89) --
	(500.98,340.59) --
	(502.94,339.32) --
	(504.90,338.09) --
	(506.85,336.90) --
	(508.81,335.67) --
	(510.77,334.39) --
	(512.72,333.08) --
	(514.68,331.75) --
	(516.64,330.41) --
	(518.59,329.07) --
	(520.55,327.73) --
	(522.51,326.42) --
	(524.46,325.12) --
	(526.42,323.87) --
	(528.38,322.63) --
	(530.33,321.38) --
	(532.29,320.14) --
	(534.25,318.89) --
	(536.20,317.64) --
	(538.16,316.39) --
	(540.12,315.15) --
	(542.07,313.92) --
	(544.03,312.69) --
	(545.99,311.47) --
	(547.94,310.26) --
	(549.90,309.06) --
	(551.86,307.86) --
	(553.81,306.66) --
	(555.77,305.47) --
	(557.72,304.28) --
	(559.68,303.10) --
	(561.64,301.92) --
	(563.59,300.75) --
	(565.55,299.58) --
	(567.51,298.41);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,355.71) --
	(414.90,355.88) --
	(416.85,356.03) --
	(418.81,356.17) --
	(420.76,356.28) --
	(422.72,356.39) --
	(424.68,356.49) --
	(426.63,356.57) --
	(428.59,356.63) --
	(430.55,356.68) --
	(432.50,356.71) --
	(434.46,356.72) --
	(436.42,356.72) --
	(438.37,356.70) --
	(440.33,356.65) --
	(442.29,356.59) --
	(444.24,356.50) --
	(446.20,356.41) --
	(448.16,356.32) --
	(450.11,356.23) --
	(452.07,356.13) --
	(454.03,356.01) --
	(455.98,355.88) --
	(457.94,355.71) --
	(459.90,355.52) --
	(461.85,355.29) --
	(463.81,355.01) --
	(465.77,354.69) --
	(467.72,354.35) --
	(469.68,353.98) --
	(471.64,353.58) --
	(473.59,353.16) --
	(475.55,352.70) --
	(477.51,352.21) --
	(479.46,351.68) --
	(481.42,351.12) --
	(483.38,350.52) --
	(485.33,349.88) --
	(487.29,349.17) --
	(489.24,348.40) --
	(491.20,347.56) --
	(493.16,346.67) --
	(495.11,345.75) --
	(497.07,344.80) --
	(499.03,343.84) --
	(500.98,342.88) --
	(502.94,341.92) --
	(504.90,340.99) --
	(506.85,340.07) --
	(508.81,339.10) --
	(510.77,338.09) --
	(512.72,337.04) --
	(514.68,335.97) --
	(516.64,334.89) --
	(518.59,333.82) --
	(520.55,332.75) --
	(522.51,331.71) --
	(524.46,330.71) --
	(526.42,329.76) --
	(528.38,328.83) --
	(530.33,327.90) --
	(532.29,326.97) --
	(534.25,326.04) --
	(536.20,325.11) --
	(538.16,324.19) --
	(540.12,323.28) --
	(542.07,322.38) --
	(544.03,321.49) --
	(545.99,320.61) --
	(547.94,319.75) --
	(549.90,318.90) --
	(551.86,318.05) --
	(553.81,317.22) --
	(555.77,316.39) --
	(557.72,315.57) --
	(559.68,314.76) --
	(561.64,313.96) --
	(563.59,313.16) --
	(565.55,312.38) --
	(567.51,311.60);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,352.93) --
	(414.90,353.03) --
	(416.85,353.12) --
	(418.81,353.20) --
	(420.76,353.27) --
	(422.72,353.33) --
	(424.68,353.39) --
	(426.63,353.44) --
	(428.59,353.48) --
	(430.55,353.52) --
	(432.50,353.54) --
	(434.46,353.55) --
	(436.42,353.56) --
	(438.37,353.55) --
	(440.33,353.53) --
	(442.29,353.50) --
	(444.24,353.45) --
	(446.20,353.41) --
	(448.16,353.37) --
	(450.11,353.33) --
	(452.07,353.29) --
	(454.03,353.24) --
	(455.98,353.18) --
	(457.94,353.10) --
	(459.90,353.00) --
	(461.85,352.88) --
	(463.81,352.72) --
	(465.77,352.54) --
	(467.72,352.33) --
	(469.68,352.12) --
	(471.64,351.88) --
	(473.59,351.63) --
	(475.55,351.35) --
	(477.51,351.05) --
	(479.46,350.73) --
	(481.42,350.39) --
	(483.38,350.01) --
	(485.33,349.61) --
	(487.29,349.16) --
	(489.24,348.67) --
	(491.20,348.14) --
	(493.16,347.57) --
	(495.11,346.98) --
	(497.07,346.37) --
	(499.03,345.76) --
	(500.98,345.13) --
	(502.94,344.51) --
	(504.90,343.90) --
	(506.85,343.30) --
	(508.81,342.68) --
	(510.77,342.05) --
	(512.72,341.39) --
	(514.68,340.73) --
	(516.64,340.06) --
	(518.59,339.38) --
	(520.55,338.69) --
	(522.51,338.00) --
	(524.46,337.32) --
	(526.42,336.63) --
	(528.38,335.94) --
	(530.33,335.25) --
	(532.29,334.55) --
	(534.25,333.84) --
	(536.20,333.12) --
	(538.16,332.39) --
	(540.12,331.66) --
	(542.07,330.91) --
	(544.03,330.16) --
	(545.99,329.40) --
	(547.94,328.62) --
	(549.90,327.84) --
	(551.86,327.05) --
	(553.81,326.25) --
	(555.77,325.44) --
	(557.72,324.63) --
	(559.68,323.80) --
	(561.64,322.97) --
	(563.59,322.13) --
	(565.55,321.28) --
	(567.51,320.42);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (412.94,237.50) rectangle (572.66,390.09);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (407.99,234.47) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (407.99,278.07) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (407.99,321.67) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (407.99,365.26) {6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.19,237.50) --
	(412.94,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.19,281.10) --
	(412.94,281.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.19,324.70) --
	(412.94,324.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.19,368.29) --
	(412.94,368.29);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.94,234.75) --
	(412.94,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (438.70,234.75) --
	(438.70,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.46,234.75) --
	(464.46,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (490.22,234.75) --
	(490.22,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (515.98,234.75) --
	(515.98,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (541.75,234.75) --
	(541.75,237.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (567.51,234.75) --
	(567.51,237.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (412.94,226.49) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (438.70,226.49) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (464.46,226.49) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (490.22,226.49) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (515.98,226.49) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (541.75,226.49) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (567.51,226.49) {50};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (492.80,214.31) {Primary cohort time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (398.52,313.80) {Forward delay (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (412.94,398.38) {D. Serial interval};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (192.72,206.49);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (192.72,206.49);
\end{scope}
\begin{scope}
\path[clip] ( 27.50, 31.02) rectangle (187.22,183.61);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.50, 31.02) rectangle (187.22,183.61);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.82) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.84) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,104.72) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.43) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.08) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.28) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.06) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.98) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.85) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.53) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,122.02) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.26) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.54) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.77) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.65) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,156.29) circle (  2.50);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,102.25) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.79) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,104.60) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.51) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,104.85) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.33) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.11) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.94) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.88) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.51) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,122.04) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.29) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.47) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.64) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.10) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,155.45) circle (  2.50);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,102.39) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.44) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,104.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.28) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.03) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.20) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.16) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.89) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.88) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.42) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.89) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.30) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.44) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.62) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.12) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,156.03) circle (  2.50);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.75) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.84) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,105.21) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,103.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.04) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.24) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.15) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.89) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.83) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.39) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.85) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.18) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.51) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.75) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.23) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,156.30) circle (  2.50);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.62) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,107.17) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,105.21) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.04) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.02) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.37) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.15) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.82) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.81) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.37) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.75) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.04) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.60) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.25) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,155.48) circle (  2.50);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.12) --
	( 29.46,104.08) --
	( 31.41,104.06) --
	( 33.37,104.04) --
	( 35.32,104.03) --
	( 37.28,104.02) --
	( 39.24,104.01) --
	( 41.19,104.00) --
	( 43.15,104.00) --
	( 45.11,104.01) --
	( 47.06,104.02) --
	( 49.02,104.05) --
	( 50.98,104.08) --
	( 52.93,104.12) --
	( 54.89,104.17) --
	( 56.85,104.23) --
	( 58.80,104.31) --
	( 60.76,104.37) --
	( 62.72,104.42) --
	( 64.67,104.46) --
	( 66.63,104.50) --
	( 68.59,104.54) --
	( 70.54,104.60) --
	( 72.50,104.67) --
	( 74.46,104.77) --
	( 76.41,104.90) --
	( 78.37,105.07) --
	( 80.33,105.27) --
	( 82.28,105.45) --
	( 84.24,105.62) --
	( 86.20,105.80) --
	( 88.15,105.99) --
	( 90.11,106.21) --
	( 92.07,106.47) --
	( 94.02,106.77) --
	( 95.98,107.14) --
	( 97.94,107.58) --
	( 99.89,108.10) --
	(101.85,108.68) --
	(103.80,109.32) --
	(105.76,109.99) --
	(107.72,110.71) --
	(109.67,111.47) --
	(111.63,112.28) --
	(113.59,113.12) --
	(115.54,114.00) --
	(117.50,114.93) --
	(119.46,115.88) --
	(121.41,116.89) --
	(123.37,117.99) --
	(125.33,119.17) --
	(127.28,120.41) --
	(129.24,121.70) --
	(131.20,123.03) --
	(133.15,124.37) --
	(135.11,125.71) --
	(137.07,127.04) --
	(139.02,128.34) --
	(140.98,129.58) --
	(142.94,130.82) --
	(144.89,132.09) --
	(146.85,133.37) --
	(148.81,134.67) --
	(150.76,135.99) --
	(152.72,137.32) --
	(154.68,138.65) --
	(156.63,139.99) --
	(158.59,141.33) --
	(160.55,142.67) --
	(162.50,144.00) --
	(164.46,145.34) --
	(166.42,146.68) --
	(168.37,148.03) --
	(170.33,149.39) --
	(172.28,150.75) --
	(174.24,152.12) --
	(176.20,153.50) --
	(178.15,154.88) --
	(180.11,156.26) --
	(182.07,157.66);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.38) --
	( 29.46,104.31) --
	( 31.41,104.26) --
	( 33.37,104.22) --
	( 35.32,104.18) --
	( 37.28,104.14) --
	( 39.24,104.11) --
	( 41.19,104.09) --
	( 43.15,104.07) --
	( 45.11,104.06) --
	( 47.06,104.05) --
	( 49.02,104.06) --
	( 50.98,104.08) --
	( 52.93,104.10) --
	( 54.89,104.14) --
	( 56.85,104.20) --
	( 58.80,104.26) --
	( 60.76,104.32) --
	( 62.72,104.37) --
	( 64.67,104.41) --
	( 66.63,104.44) --
	( 68.59,104.49) --
	( 70.54,104.55) --
	( 72.50,104.62) --
	( 74.46,104.73) --
	( 76.41,104.86) --
	( 78.37,105.03) --
	( 80.33,105.23) --
	( 82.28,105.42) --
	( 84.24,105.59) --
	( 86.20,105.78) --
	( 88.15,105.97) --
	( 90.11,106.20) --
	( 92.07,106.46) --
	( 94.02,106.77) --
	( 95.98,107.14) --
	( 97.94,107.58) --
	( 99.89,108.10) --
	(101.85,108.69) --
	(103.80,109.33) --
	(105.76,110.01) --
	(107.72,110.73) --
	(109.67,111.50) --
	(111.63,112.30) --
	(113.59,113.15) --
	(115.54,114.03) --
	(117.50,114.95) --
	(119.46,115.91) --
	(121.41,116.92) --
	(123.37,118.01) --
	(125.33,119.19) --
	(127.28,120.44) --
	(129.24,121.73) --
	(131.20,123.06) --
	(133.15,124.40) --
	(135.11,125.74) --
	(137.07,127.06) --
	(139.02,128.34) --
	(140.98,129.58) --
	(142.94,130.80) --
	(144.89,132.04) --
	(146.85,133.31) --
	(148.81,134.59) --
	(150.76,135.88) --
	(152.72,137.18) --
	(154.68,138.48) --
	(156.63,139.79) --
	(158.59,141.10) --
	(160.55,142.40) --
	(162.50,143.70) --
	(164.46,145.00) --
	(166.42,146.30) --
	(168.37,147.61) --
	(170.33,148.92) --
	(172.28,150.23) --
	(174.24,151.55) --
	(176.20,152.87) --
	(178.15,154.20) --
	(180.11,155.53) --
	(182.07,156.86);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.38) --
	( 29.46,104.32) --
	( 31.41,104.27) --
	( 33.37,104.22) --
	( 35.32,104.18) --
	( 37.28,104.15) --
	( 39.24,104.12) --
	( 41.19,104.09) --
	( 43.15,104.08) --
	( 45.11,104.06) --
	( 47.06,104.06) --
	( 49.02,104.07) --
	( 50.98,104.08) --
	( 52.93,104.11) --
	( 54.89,104.15) --
	( 56.85,104.20) --
	( 58.80,104.27) --
	( 60.76,104.33) --
	( 62.72,104.37) --
	( 64.67,104.41) --
	( 66.63,104.45) --
	( 68.59,104.50) --
	( 70.54,104.56) --
	( 72.50,104.63) --
	( 74.46,104.74) --
	( 76.41,104.87) --
	( 78.37,105.04) --
	( 80.33,105.24) --
	( 82.28,105.42) --
	( 84.24,105.60) --
	( 86.20,105.77) --
	( 88.15,105.96) --
	( 90.11,106.18) --
	( 92.07,106.44) --
	( 94.02,106.74) --
	( 95.98,107.11) --
	( 97.94,107.55) --
	( 99.89,108.07) --
	(101.85,108.65) --
	(103.80,109.29) --
	(105.76,109.96) --
	(107.72,110.68) --
	(109.67,111.44) --
	(111.63,112.25) --
	(113.59,113.09) --
	(115.54,113.97) --
	(117.50,114.89) --
	(119.46,115.85) --
	(121.41,116.85) --
	(123.37,117.94) --
	(125.33,119.12) --
	(127.28,120.36) --
	(129.24,121.65) --
	(131.20,122.97) --
	(133.15,124.31) --
	(135.11,125.64) --
	(137.07,126.97) --
	(139.02,128.25) --
	(140.98,129.49) --
	(142.94,130.72) --
	(144.89,131.98) --
	(146.85,133.25) --
	(148.81,134.54) --
	(150.76,135.85) --
	(152.72,137.16) --
	(154.68,138.49) --
	(156.63,139.81) --
	(158.59,141.14) --
	(160.55,142.46) --
	(162.50,143.78) --
	(164.46,145.11) --
	(166.42,146.44) --
	(168.37,147.77) --
	(170.33,149.11) --
	(172.28,150.46) --
	(174.24,151.81) --
	(176.20,153.17) --
	(178.15,154.53) --
	(180.11,155.90) --
	(182.07,157.27);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.14) --
	( 29.46,104.10) --
	( 31.41,104.08) --
	( 33.37,104.06) --
	( 35.32,104.04) --
	( 37.28,104.03) --
	( 39.24,104.02) --
	( 41.19,104.01) --
	( 43.15,104.01) --
	( 45.11,104.01) --
	( 47.06,104.02) --
	( 49.02,104.04) --
	( 50.98,104.07) --
	( 52.93,104.11) --
	( 54.89,104.16) --
	( 56.85,104.22) --
	( 58.80,104.29) --
	( 60.76,104.35) --
	( 62.72,104.40) --
	( 64.67,104.44) --
	( 66.63,104.47) --
	( 68.59,104.51) --
	( 70.54,104.56) --
	( 72.50,104.63) --
	( 74.46,104.72) --
	( 76.41,104.85) --
	( 78.37,105.01) --
	( 80.33,105.21) --
	( 82.28,105.39) --
	( 84.24,105.57) --
	( 86.20,105.75) --
	( 88.15,105.94) --
	( 90.11,106.16) --
	( 92.07,106.42) --
	( 94.02,106.73) --
	( 95.98,107.10) --
	( 97.94,107.54) --
	( 99.89,108.06) --
	(101.85,108.65) --
	(103.80,109.28) --
	(105.76,109.95) --
	(107.72,110.66) --
	(109.67,111.41) --
	(111.63,112.21) --
	(113.59,113.05) --
	(115.54,113.92) --
	(117.50,114.84) --
	(119.46,115.79) --
	(121.41,116.80) --
	(123.37,117.89) --
	(125.33,119.07) --
	(127.28,120.31) --
	(129.24,121.60) --
	(131.20,122.92) --
	(133.15,124.26) --
	(135.11,125.61) --
	(137.07,126.93) --
	(139.02,128.23) --
	(140.98,129.47) --
	(142.94,130.71) --
	(144.89,131.97) --
	(146.85,133.25) --
	(148.81,134.55) --
	(150.76,135.87) --
	(152.72,137.19) --
	(154.68,138.52) --
	(156.63,139.86) --
	(158.59,141.20) --
	(160.55,142.54) --
	(162.50,143.87) --
	(164.46,145.21) --
	(166.42,146.56) --
	(168.37,147.91) --
	(170.33,149.26) --
	(172.28,150.63) --
	(174.24,152.00) --
	(176.20,153.37) --
	(178.15,154.76) --
	(180.11,156.14) --
	(182.07,157.54);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.16) --
	( 29.46,104.13) --
	( 31.41,104.11) --
	( 33.37,104.10) --
	( 35.32,104.09) --
	( 37.28,104.08) --
	( 39.24,104.08) --
	( 41.19,104.07) --
	( 43.15,104.07) --
	( 45.11,104.08) --
	( 47.06,104.09) --
	( 49.02,104.11) --
	( 50.98,104.14) --
	( 52.93,104.18) --
	( 54.89,104.23) --
	( 56.85,104.29) --
	( 58.80,104.37) --
	( 60.76,104.43) --
	( 62.72,104.47) --
	( 64.67,104.50) --
	( 66.63,104.53) --
	( 68.59,104.56) --
	( 70.54,104.61) --
	( 72.50,104.67) --
	( 74.46,104.76) --
	( 76.41,104.88) --
	( 78.37,105.04) --
	( 80.33,105.23) --
	( 82.28,105.41) --
	( 84.24,105.58) --
	( 86.20,105.76) --
	( 88.15,105.95) --
	( 90.11,106.17) --
	( 92.07,106.42) --
	( 94.02,106.73) --
	( 95.98,107.10) --
	( 97.94,107.53) --
	( 99.89,108.05) --
	(101.85,108.63) --
	(103.80,109.25) --
	(105.76,109.91) --
	(107.72,110.62) --
	(109.67,111.36) --
	(111.63,112.15) --
	(113.59,112.98) --
	(115.54,113.85) --
	(117.50,114.76) --
	(119.46,115.71) --
	(121.41,116.72) --
	(123.37,117.82) --
	(125.33,119.01) --
	(127.28,120.26) --
	(129.24,121.57) --
	(131.20,122.91) --
	(133.15,124.26) --
	(135.11,125.62) --
	(137.07,126.95) --
	(139.02,128.25) --
	(140.98,129.49) --
	(142.94,130.72) --
	(144.89,131.98) --
	(146.85,133.25) --
	(148.81,134.54) --
	(150.76,135.85) --
	(152.72,137.16) --
	(154.68,138.48) --
	(156.63,139.81) --
	(158.59,141.13) --
	(160.55,142.44) --
	(162.50,143.75) --
	(164.46,145.06) --
	(166.42,146.38) --
	(168.37,147.70) --
	(170.33,149.02) --
	(172.28,150.35) --
	(174.24,151.68) --
	(176.20,153.01) --
	(178.15,154.35) --
	(180.11,155.70) --
	(182.07,157.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.50, 31.02) rectangle (187.22,183.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.55, 27.99) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.55, 59.78) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.55, 91.57) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.55,123.36) {6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.55,155.14) {8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.75, 31.02) --
	( 27.50, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.75, 62.81) --
	( 27.50, 62.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.75, 94.60) --
	( 27.50, 94.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.75,126.39) --
	( 27.50,126.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.75,158.18) --
	( 27.50,158.18);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.50, 28.27) --
	( 27.50, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 53.26, 28.27) --
	( 53.26, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 79.02, 28.27) --
	( 79.02, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.78, 28.27) --
	(104.78, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.54, 28.27) --
	(130.54, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.31, 28.27) --
	(156.31, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (182.07, 28.27) --
	(182.07, 31.02);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 27.50, 20.01) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 53.26, 20.01) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 79.02, 20.01) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (104.78, 20.01) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (130.54, 20.01) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (156.31, 20.01) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (182.07, 20.01) {50};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (107.36,  7.82) {Secondary cohort time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,107.31) {Backward delay (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.50,191.89) {E. Incubation period};
\end{scope}
\begin{scope}
\path[clip] (192.72,  0.00) rectangle (385.44,206.49);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (192.72,  0.00) rectangle (385.44,206.49);
\end{scope}
\begin{scope}
\path[clip] (220.22, 31.02) rectangle (379.94,183.61);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (220.22, 31.02) rectangle (379.94,183.61);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.30) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,101.67) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.43) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,101.12) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.62) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.58) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.97) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.26) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.38) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.65) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.62) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.88) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.70) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,126.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,127.48) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,125.68) circle (  2.50);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.73) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,101.93) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.46) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,101.05) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.63) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.60) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.98) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.39) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.43) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.79) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.65) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.85) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.55) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,126.05) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,128.36) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,123.16) circle (  2.50);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,102.22) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.56) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,100.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.75) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.45) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.92) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.46) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.36) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.49) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,119.03) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.70) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,126.40) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,127.86) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,127.28) circle (  2.50);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.08) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,102.87) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.83) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,100.86) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.71) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.37) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.95) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.47) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.55) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.81) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.57) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.85) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.22) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,127.21) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,127.27) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,128.95) circle (  2.50);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.01) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,102.91) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,101.10) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,100.89) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.45) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.43) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.49) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.54) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.52) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.38) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.43) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.35) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,127.24) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,126.77) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,128.39) circle (  2.50);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,101.69) --
	(222.18,101.56) --
	(224.13,101.44) --
	(226.09,101.33) --
	(228.04,101.23) --
	(230.00,101.13) --
	(231.96,101.05) --
	(233.91,100.97) --
	(235.87,100.90) --
	(237.83,100.84) --
	(239.78,100.79) --
	(241.74,100.75) --
	(243.70,100.72) --
	(245.65,100.71) --
	(247.61,100.70) --
	(249.57,100.71) --
	(251.52,100.73) --
	(253.48,100.75) --
	(255.44,100.78) --
	(257.39,100.81) --
	(259.35,100.85) --
	(261.31,100.90) --
	(263.26,100.97) --
	(265.22,101.04) --
	(267.18,101.13) --
	(269.13,101.24) --
	(271.09,101.38) --
	(273.05,101.52) --
	(275.00,101.65) --
	(276.96,101.77) --
	(278.92,101.90) --
	(280.87,102.03) --
	(282.83,102.18) --
	(284.79,102.36) --
	(286.74,102.57) --
	(288.70,102.82) --
	(290.66,103.12) --
	(292.61,103.49) --
	(294.57,103.91) --
	(296.52,104.37) --
	(298.48,104.88) --
	(300.44,105.42) --
	(302.39,106.00) --
	(304.35,106.60) --
	(306.31,107.22) --
	(308.26,107.86) --
	(310.22,108.50) --
	(312.18,109.16) --
	(314.13,109.83) --
	(316.09,110.59) --
	(318.05,111.43) --
	(320.00,112.32) --
	(321.96,113.24) --
	(323.92,114.18) --
	(325.87,115.11) --
	(327.83,116.01) --
	(329.79,116.85) --
	(331.74,117.63) --
	(333.70,118.31) --
	(335.66,118.95) --
	(337.61,119.59) --
	(339.57,120.22) --
	(341.53,120.85) --
	(343.48,121.47) --
	(345.44,122.06) --
	(347.40,122.64) --
	(349.35,123.19) --
	(351.31,123.71) --
	(353.27,124.20) --
	(355.22,124.65) --
	(357.18,125.07) --
	(359.14,125.48) --
	(361.09,125.86) --
	(363.05,126.22) --
	(365.00,126.55) --
	(366.96,126.86) --
	(368.92,127.15) --
	(370.87,127.41) --
	(372.83,127.65) --
	(374.79,127.87);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.09) --
	(222.18,101.92) --
	(224.13,101.77) --
	(226.09,101.62) --
	(228.04,101.49) --
	(230.00,101.37) --
	(231.96,101.26) --
	(233.91,101.16) --
	(235.87,101.07) --
	(237.83,100.99) --
	(239.78,100.92) --
	(241.74,100.86) --
	(243.70,100.81) --
	(245.65,100.78) --
	(247.61,100.76) --
	(249.57,100.76) --
	(251.52,100.76) --
	(253.48,100.78) --
	(255.44,100.80) --
	(257.39,100.82) --
	(259.35,100.86) --
	(261.31,100.91) --
	(263.26,100.97) --
	(265.22,101.04) --
	(267.18,101.13) --
	(269.13,101.24) --
	(271.09,101.37) --
	(273.05,101.52) --
	(275.00,101.66) --
	(276.96,101.79) --
	(278.92,101.92) --
	(280.87,102.06) --
	(282.83,102.22) --
	(284.79,102.41) --
	(286.74,102.63) --
	(288.70,102.89) --
	(290.66,103.20) --
	(292.61,103.57) --
	(294.57,103.99) --
	(296.52,104.46) --
	(298.48,104.97) --
	(300.44,105.51) --
	(302.39,106.08) --
	(304.35,106.68) --
	(306.31,107.30) --
	(308.26,107.94) --
	(310.22,108.58) --
	(312.18,109.23) --
	(314.13,109.90) --
	(316.09,110.66) --
	(318.05,111.50) --
	(320.00,112.40) --
	(321.96,113.33) --
	(323.92,114.27) --
	(325.87,115.20) --
	(327.83,116.10) --
	(329.79,116.94) --
	(331.74,117.70) --
	(333.70,118.36) --
	(335.66,118.97) --
	(337.61,119.58) --
	(339.57,120.18) --
	(341.53,120.77) --
	(343.48,121.35) --
	(345.44,121.90) --
	(347.40,122.43) --
	(349.35,122.93) --
	(351.31,123.39) --
	(353.27,123.81) --
	(355.22,124.19) --
	(357.18,124.54) --
	(359.14,124.86) --
	(361.09,125.15) --
	(363.05,125.41) --
	(365.00,125.65) --
	(366.96,125.86) --
	(368.92,126.03) --
	(370.87,126.19) --
	(372.83,126.31) --
	(374.79,126.41);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.24) --
	(222.18,102.06) --
	(224.13,101.90) --
	(226.09,101.75) --
	(228.04,101.61) --
	(230.00,101.48) --
	(231.96,101.36) --
	(233.91,101.25) --
	(235.87,101.15) --
	(237.83,101.06) --
	(239.78,100.99) --
	(241.74,100.92) --
	(243.70,100.87) --
	(245.65,100.83) --
	(247.61,100.80) --
	(249.57,100.79) --
	(251.52,100.79) --
	(253.48,100.80) --
	(255.44,100.81) --
	(257.39,100.83) --
	(259.35,100.86) --
	(261.31,100.90) --
	(263.26,100.95) --
	(265.22,101.02) --
	(267.18,101.10) --
	(269.13,101.21) --
	(271.09,101.34) --
	(273.05,101.48) --
	(275.00,101.61) --
	(276.96,101.74) --
	(278.92,101.87) --
	(280.87,102.01) --
	(282.83,102.17) --
	(284.79,102.36) --
	(286.74,102.58) --
	(288.70,102.84) --
	(290.66,103.15) --
	(292.61,103.52) --
	(294.57,103.94) --
	(296.52,104.41) --
	(298.48,104.92) --
	(300.44,105.46) --
	(302.39,106.04) --
	(304.35,106.64) --
	(306.31,107.27) --
	(308.26,107.91) --
	(310.22,108.56) --
	(312.18,109.21) --
	(314.13,109.88) --
	(316.09,110.63) --
	(318.05,111.45) --
	(320.00,112.32) --
	(321.96,113.22) --
	(323.92,114.13) --
	(325.87,115.04) --
	(327.83,115.92) --
	(329.79,116.76) --
	(331.74,117.53) --
	(333.70,118.23) --
	(335.66,118.89) --
	(337.61,119.55) --
	(339.57,120.20) --
	(341.53,120.86) --
	(343.48,121.50) --
	(345.44,122.13) --
	(347.40,122.75) --
	(349.35,123.34) --
	(351.31,123.91) --
	(353.27,124.45) --
	(355.22,124.96) --
	(357.18,125.45) --
	(359.14,125.92) --
	(361.09,126.38) --
	(363.05,126.81) --
	(365.00,127.23) --
	(366.96,127.63) --
	(368.92,128.00) --
	(370.87,128.37) --
	(372.83,128.71) --
	(374.79,129.03);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.10) --
	(222.18,101.94) --
	(224.13,101.80) --
	(226.09,101.67) --
	(228.04,101.55) --
	(230.00,101.44) --
	(231.96,101.34) --
	(233.91,101.24) --
	(235.87,101.15) --
	(237.83,101.08) --
	(239.78,101.01) --
	(241.74,100.95) --
	(243.70,100.91) --
	(245.65,100.88) --
	(247.61,100.86) --
	(249.57,100.85) --
	(251.52,100.85) --
	(253.48,100.86) --
	(255.44,100.87) --
	(257.39,100.88) --
	(259.35,100.90) --
	(261.31,100.92) --
	(263.26,100.96) --
	(265.22,101.02) --
	(267.18,101.09) --
	(269.13,101.19) --
	(271.09,101.31) --
	(273.05,101.45) --
	(275.00,101.58) --
	(276.96,101.72) --
	(278.92,101.86) --
	(280.87,102.02) --
	(282.83,102.19) --
	(284.79,102.39) --
	(286.74,102.62) --
	(288.70,102.90) --
	(290.66,103.21) --
	(292.61,103.58) --
	(294.57,104.00) --
	(296.52,104.47) --
	(298.48,104.98) --
	(300.44,105.52) --
	(302.39,106.09) --
	(304.35,106.69) --
	(306.31,107.30) --
	(308.26,107.94) --
	(310.22,108.58) --
	(312.18,109.23) --
	(314.13,109.90) --
	(316.09,110.64) --
	(318.05,111.44) --
	(320.00,112.29) --
	(321.96,113.17) --
	(323.92,114.06) --
	(325.87,114.95) --
	(327.83,115.82) --
	(329.79,116.65) --
	(331.74,117.43) --
	(333.70,118.14) --
	(335.66,118.81) --
	(337.61,119.49) --
	(339.57,120.16) --
	(341.53,120.84) --
	(343.48,121.51) --
	(345.44,122.16) --
	(347.40,122.81) --
	(349.35,123.44) --
	(351.31,124.05) --
	(353.27,124.64) --
	(355.22,125.20) --
	(357.18,125.75) --
	(359.14,126.29) --
	(361.09,126.81) --
	(363.05,127.32) --
	(365.00,127.81) --
	(366.96,128.29) --
	(368.92,128.75) --
	(370.87,129.20) --
	(372.83,129.64) --
	(374.79,130.06);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.10) --
	(222.18,101.95) --
	(224.13,101.82) --
	(226.09,101.69) --
	(228.04,101.57) --
	(230.00,101.46) --
	(231.96,101.36) --
	(233.91,101.27) --
	(235.87,101.18) --
	(237.83,101.10) --
	(239.78,101.04) --
	(241.74,100.98) --
	(243.70,100.94) --
	(245.65,100.91) --
	(247.61,100.89) --
	(249.57,100.88) --
	(251.52,100.88) --
	(253.48,100.89) --
	(255.44,100.89) --
	(257.39,100.90) --
	(259.35,100.91) --
	(261.31,100.94) --
	(263.26,100.97) --
	(265.22,101.02) --
	(267.18,101.09) --
	(269.13,101.18) --
	(271.09,101.30) --
	(273.05,101.43) --
	(275.00,101.57) --
	(276.96,101.70) --
	(278.92,101.84) --
	(280.87,101.99) --
	(282.83,102.16) --
	(284.79,102.36) --
	(286.74,102.59) --
	(288.70,102.86) --
	(290.66,103.18) --
	(292.61,103.54) --
	(294.57,103.95) --
	(296.52,104.41) --
	(298.48,104.90) --
	(300.44,105.43) --
	(302.39,105.98) --
	(304.35,106.57) --
	(306.31,107.17) --
	(308.26,107.79) --
	(310.22,108.42) --
	(312.18,109.07) --
	(314.13,109.73) --
	(316.09,110.47) --
	(318.05,111.27) --
	(320.00,112.13) --
	(321.96,113.01) --
	(323.92,113.91) --
	(325.87,114.80) --
	(327.83,115.67) --
	(329.79,116.50) --
	(331.74,117.28) --
	(333.70,117.98) --
	(335.66,118.64) --
	(337.61,119.31) --
	(339.57,119.98) --
	(341.53,120.65) --
	(343.48,121.31) --
	(345.44,121.96) --
	(347.40,122.59) --
	(349.35,123.21) --
	(351.31,123.81) --
	(353.27,124.38) --
	(355.22,124.93) --
	(357.18,125.47) --
	(359.14,125.98) --
	(361.09,126.49) --
	(363.05,126.97) --
	(365.00,127.45) --
	(366.96,127.90) --
	(368.92,128.34) --
	(370.87,128.77) --
	(372.83,129.18) --
	(374.79,129.58);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (220.22, 31.02) rectangle (379.94,183.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (215.27, 27.99) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (215.27, 59.78) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (215.27, 91.57) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (215.27,123.36) {6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (215.27,155.14) {8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.47, 31.02) --
	(220.22, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.47, 62.81) --
	(220.22, 62.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.47, 94.60) --
	(220.22, 94.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.47,126.39) --
	(220.22,126.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.47,158.18) --
	(220.22,158.18);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.22, 28.27) --
	(220.22, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (245.98, 28.27) --
	(245.98, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.74, 28.27) --
	(271.74, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.50, 28.27) --
	(297.50, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.26, 28.27) --
	(323.26, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (349.03, 28.27) --
	(349.03, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.79, 28.27) --
	(374.79, 31.02);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (220.22, 20.01) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (245.98, 20.01) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (271.74, 20.01) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (297.50, 20.01) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (323.26, 20.01) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (349.03, 20.01) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (374.79, 20.01) {50};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (300.08,  7.82) {Secondary cohort time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (205.80,107.31) {Backward delay (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (220.22,191.89) {F. Generation interval};
\end{scope}
\begin{scope}
\path[clip] (385.44,  0.00) rectangle (578.16,206.49);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (385.44,  0.00) rectangle (578.16,206.49);
\end{scope}
\begin{scope}
\path[clip] (412.94, 31.02) rectangle (572.66,183.61);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (412.94, 31.02) rectangle (572.66,183.61);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 76.98) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 86.83) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 85.55) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 86.31) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 86.44) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 88.43) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 88.90) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 91.38) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38, 94.91) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,101.20) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,110.57) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,122.63) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,135.35) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,145.96) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,153.70) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,162.89) circle (  2.50);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 76.53) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 87.79) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 88.68) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 89.22) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 89.67) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 90.63) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 91.04) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 93.34) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38, 96.81) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,102.70) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,111.21) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,122.45) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,133.90) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,143.31) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,151.06) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,157.71) circle (  2.50);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 80.80) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 92.10) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 91.50) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 90.92) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 92.43) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 92.32) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 93.28) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 95.39) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38, 98.80) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,103.90) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,111.72) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,122.19) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,133.10) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,141.14) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,148.25) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,156.21) circle (  2.50);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 85.03) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 94.32) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 94.35) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 92.82) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 94.57) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 94.98) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 95.66) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 97.29) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,100.66) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,105.31) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,112.94) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,121.90) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,131.34) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,138.75) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,145.17) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,151.07) circle (  2.50);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 88.35) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 97.39) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 96.60) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 95.29) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 96.55) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 97.57) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 97.67) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 99.36) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,102.45) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,106.99) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,113.52) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,121.76) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,130.25) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,136.75) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,141.69) circle (  2.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,147.05) circle (  2.50);
\definecolor{drawColor}{RGB}{68,1,84}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 80.73) --
	(414.90, 81.08) --
	(416.85, 81.42) --
	(418.81, 81.77) --
	(420.76, 82.11) --
	(422.72, 82.43) --
	(424.68, 82.74) --
	(426.63, 83.04) --
	(428.59, 83.33) --
	(430.55, 83.62) --
	(432.50, 83.90) --
	(434.46, 84.18) --
	(436.42, 84.45) --
	(438.37, 84.73) --
	(440.33, 85.01) --
	(442.29, 85.29) --
	(444.24, 85.58) --
	(446.20, 85.84) --
	(448.16, 86.05) --
	(450.11, 86.23) --
	(452.07, 86.38) --
	(454.03, 86.53) --
	(455.98, 86.69) --
	(457.94, 86.85) --
	(459.90, 87.05) --
	(461.85, 87.28) --
	(463.81, 87.56) --
	(465.77, 87.87) --
	(467.72, 88.13) --
	(469.68, 88.36) --
	(471.64, 88.56) --
	(473.59, 88.78) --
	(475.55, 89.03) --
	(477.51, 89.32) --
	(479.46, 89.69) --
	(481.42, 90.15) --
	(483.38, 90.73) --
	(485.33, 91.44) --
	(487.29, 92.24) --
	(489.24, 93.08) --
	(491.20, 93.96) --
	(493.16, 94.90) --
	(495.11, 95.90) --
	(497.07, 96.95) --
	(499.03, 98.08) --
	(500.98, 99.27) --
	(502.94,100.53) --
	(504.90,101.88) --
	(506.85,103.32) --
	(508.81,104.91) --
	(510.77,106.62) --
	(512.72,108.43) --
	(514.68,110.31) --
	(516.64,112.26) --
	(518.59,114.23) --
	(520.55,116.21) --
	(522.51,118.17) --
	(524.46,120.09) --
	(526.42,121.95) --
	(528.38,123.80) --
	(530.33,125.70) --
	(532.29,127.63) --
	(534.25,129.59) --
	(536.20,131.58) --
	(538.16,133.59) --
	(540.12,135.62) --
	(542.07,137.66) --
	(544.03,139.71) --
	(545.99,141.76) --
	(547.94,143.81) --
	(549.90,145.87) --
	(551.86,147.95) --
	(553.81,150.04) --
	(555.77,152.14) --
	(557.72,154.26) --
	(559.68,156.39) --
	(561.64,158.54) --
	(563.59,160.70) --
	(565.55,162.87) --
	(567.51,165.06);
\definecolor{drawColor}{RGB}{59,82,139}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 80.69) --
	(414.90, 81.29) --
	(416.85, 81.89) --
	(418.81, 82.47) --
	(420.76, 83.03) --
	(422.72, 83.56) --
	(424.68, 84.07) --
	(426.63, 84.55) --
	(428.59, 85.01) --
	(430.55, 85.45) --
	(432.50, 85.87) --
	(434.46, 86.29) --
	(436.42, 86.68) --
	(438.37, 87.07) --
	(440.33, 87.46) --
	(442.29, 87.83) --
	(444.24, 88.21) --
	(446.20, 88.53) --
	(448.16, 88.79) --
	(450.11, 89.00) --
	(452.07, 89.17) --
	(454.03, 89.32) --
	(455.98, 89.47) --
	(457.94, 89.62) --
	(459.90, 89.79) --
	(461.85, 90.00) --
	(463.81, 90.26) --
	(465.77, 90.55) --
	(467.72, 90.77) --
	(469.68, 90.95) --
	(471.64, 91.10) --
	(473.59, 91.25) --
	(475.55, 91.43) --
	(477.51, 91.65) --
	(479.46, 91.94) --
	(481.42, 92.33) --
	(483.38, 92.84) --
	(485.33, 93.48) --
	(487.29, 94.22) --
	(489.24, 95.00) --
	(491.20, 95.82) --
	(493.16, 96.71) --
	(495.11, 97.64) --
	(497.07, 98.63) --
	(499.03, 99.69) --
	(500.98,100.80) --
	(502.94,101.98) --
	(504.90,103.23) --
	(506.85,104.56) --
	(508.81,106.02) --
	(510.77,107.61) --
	(512.72,109.29) --
	(514.68,111.04) --
	(516.64,112.84) --
	(518.59,114.66) --
	(520.55,116.49) --
	(522.51,118.29) --
	(524.46,120.05) --
	(526.42,121.75) --
	(528.38,123.43) --
	(530.33,125.15) --
	(532.29,126.90) --
	(534.25,128.68) --
	(536.20,130.48) --
	(538.16,132.30) --
	(540.12,134.12) --
	(542.07,135.96) --
	(544.03,137.79) --
	(545.99,139.63) --
	(547.94,141.45) --
	(549.90,143.29) --
	(551.86,145.13) --
	(553.81,146.98) --
	(555.77,148.84) --
	(557.72,150.71) --
	(559.68,152.59) --
	(561.64,154.48) --
	(563.59,156.38) --
	(565.55,158.29) --
	(567.51,160.20);
\definecolor{drawColor}{RGB}{33,144,140}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 85.11) --
	(414.90, 85.56) --
	(416.85, 86.01) --
	(418.81, 86.45) --
	(420.76, 86.87) --
	(422.72, 87.27) --
	(424.68, 87.65) --
	(426.63, 88.01) --
	(428.59, 88.36) --
	(430.55, 88.69) --
	(432.50, 89.01) --
	(434.46, 89.32) --
	(436.42, 89.62) --
	(438.37, 89.92) --
	(440.33, 90.22) --
	(442.29, 90.51) --
	(444.24, 90.80) --
	(446.20, 91.05) --
	(448.16, 91.24) --
	(450.11, 91.39) --
	(452.07, 91.51) --
	(454.03, 91.61) --
	(455.98, 91.71) --
	(457.94, 91.82) --
	(459.90, 91.96) --
	(461.85, 92.13) --
	(463.81, 92.35) --
	(465.77, 92.60) --
	(467.72, 92.81) --
	(469.68, 92.99) --
	(471.64, 93.14) --
	(473.59, 93.31) --
	(475.55, 93.50) --
	(477.51, 93.73) --
	(479.46, 94.03) --
	(481.42, 94.41) --
	(483.38, 94.89) --
	(485.33, 95.49) --
	(487.29, 96.17) --
	(489.24, 96.90) --
	(491.20, 97.67) --
	(493.16, 98.49) --
	(495.11, 99.36) --
	(497.07,100.28) --
	(499.03,101.25) --
	(500.98,102.29) --
	(502.94,103.38) --
	(504.90,104.53) --
	(506.85,105.76) --
	(508.81,107.10) --
	(510.77,108.55) --
	(512.72,110.08) --
	(514.68,111.67) --
	(516.64,113.31) --
	(518.59,114.97) --
	(520.55,116.64) --
	(522.51,118.29) --
	(524.46,119.92) --
	(526.42,121.49) --
	(528.38,123.05) --
	(530.33,124.65) --
	(532.29,126.27) --
	(534.25,127.93) --
	(536.20,129.61) --
	(538.16,131.30) --
	(540.12,133.01) --
	(542.07,134.73) --
	(544.03,136.46) --
	(545.99,138.19) --
	(547.94,139.92) --
	(549.90,141.66) --
	(551.86,143.41) --
	(553.81,145.17) --
	(555.77,146.95) --
	(557.72,148.74) --
	(559.68,150.54) --
	(561.64,152.35) --
	(563.59,154.17) --
	(565.55,156.01) --
	(567.51,157.86);
\definecolor{drawColor}{RGB}{93,200,99}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 88.68) --
	(414.90, 89.03) --
	(416.85, 89.38) --
	(418.81, 89.72) --
	(420.76, 90.06) --
	(422.72, 90.37) --
	(424.68, 90.67) --
	(426.63, 90.96) --
	(428.59, 91.23) --
	(430.55, 91.50) --
	(432.50, 91.76) --
	(434.46, 92.01) --
	(436.42, 92.26) --
	(438.37, 92.50) --
	(440.33, 92.75) --
	(442.29, 92.99) --
	(444.24, 93.24) --
	(446.20, 93.45) --
	(448.16, 93.61) --
	(450.11, 93.74) --
	(452.07, 93.85) --
	(454.03, 93.94) --
	(455.98, 94.03) --
	(457.94, 94.14) --
	(459.90, 94.26) --
	(461.85, 94.42) --
	(463.81, 94.63) --
	(465.77, 94.86) --
	(467.72, 95.06) --
	(469.68, 95.23) --
	(471.64, 95.40) --
	(473.59, 95.57) --
	(475.55, 95.76) --
	(477.51, 95.99) --
	(479.46, 96.28) --
	(481.42, 96.64) --
	(483.38, 97.10) --
	(485.33, 97.66) --
	(487.29, 98.29) --
	(489.24, 98.96) --
	(491.20, 99.67) --
	(493.16,100.43) --
	(495.11,101.23) --
	(497.07,102.08) --
	(499.03,102.98) --
	(500.98,103.92) --
	(502.94,104.92) --
	(504.90,105.96) --
	(506.85,107.07) --
	(508.81,108.29) --
	(510.77,109.61) --
	(512.72,111.00) --
	(514.68,112.45) --
	(516.64,113.94) --
	(518.59,115.45) --
	(520.55,116.96) --
	(522.51,118.45) --
	(524.46,119.90) --
	(526.42,121.30) --
	(528.38,122.69) --
	(530.33,124.11) --
	(532.29,125.55) --
	(534.25,127.01) --
	(536.20,128.49) --
	(538.16,129.99) --
	(540.12,131.49) --
	(542.07,132.99) --
	(544.03,134.50) --
	(545.99,136.01) --
	(547.94,137.51) --
	(549.90,139.01) --
	(551.86,140.52) --
	(553.81,142.04) --
	(555.77,143.57) --
	(557.72,145.10) --
	(559.68,146.64) --
	(561.64,148.19) --
	(563.59,149.74) --
	(565.55,151.30) --
	(567.51,152.87);
\definecolor{drawColor}{RGB}{253,231,37}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 91.91) --
	(414.90, 92.20) --
	(416.85, 92.48) --
	(418.81, 92.77) --
	(420.76, 93.04) --
	(422.72, 93.30) --
	(424.68, 93.55) --
	(426.63, 93.78) --
	(428.59, 94.01) --
	(430.55, 94.23) --
	(432.50, 94.44) --
	(434.46, 94.65) --
	(436.42, 94.86) --
	(438.37, 95.06) --
	(440.33, 95.27) --
	(442.29, 95.48) --
	(444.24, 95.69) --
	(446.20, 95.86) --
	(448.16, 96.00) --
	(450.11, 96.10) --
	(452.07, 96.18) --
	(454.03, 96.26) --
	(455.98, 96.33) --
	(457.94, 96.42) --
	(459.90, 96.52) --
	(461.85, 96.66) --
	(463.81, 96.84) --
	(465.77, 97.06) --
	(467.72, 97.25) --
	(469.68, 97.41) --
	(471.64, 97.58) --
	(473.59, 97.75) --
	(475.55, 97.94) --
	(477.51, 98.17) --
	(479.46, 98.45) --
	(481.42, 98.80) --
	(483.38, 99.22) --
	(485.33, 99.74) --
	(487.29,100.32) --
	(489.24,100.94) --
	(491.20,101.59) --
	(493.16,102.29) --
	(495.11,103.03) --
	(497.07,103.81) --
	(499.03,104.63) --
	(500.98,105.50) --
	(502.94,106.40) --
	(504.90,107.36) --
	(506.85,108.36) --
	(508.81,109.47) --
	(510.77,110.66) --
	(512.72,111.92) --
	(514.68,113.24) --
	(516.64,114.59) --
	(518.59,115.95) --
	(520.55,117.31) --
	(522.51,118.65) --
	(524.46,119.95) --
	(526.42,121.20) --
	(528.38,122.43) --
	(530.33,123.68) --
	(532.29,124.95) --
	(534.25,126.24) --
	(536.20,127.54) --
	(538.16,128.85) --
	(540.12,130.16) --
	(542.07,131.48) --
	(544.03,132.79) --
	(545.99,134.10) --
	(547.94,135.40) --
	(549.90,136.70) --
	(551.86,138.00) --
	(553.81,139.31) --
	(555.77,140.62) --
	(557.72,141.94) --
	(559.68,143.26) --
	(561.64,144.58) --
	(563.59,145.90) --
	(565.55,147.23) --
	(567.51,148.56);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (412.94, 31.02) rectangle (572.66,183.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (407.99, 27.99) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (407.99, 59.78) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (407.99, 91.57) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (407.99,123.36) {6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (407.99,155.14) {8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.19, 31.02) --
	(412.94, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.19, 62.81) --
	(412.94, 62.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.19, 94.60) --
	(412.94, 94.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.19,126.39) --
	(412.94,126.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.19,158.18) --
	(412.94,158.18);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.94, 28.27) --
	(412.94, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (438.70, 28.27) --
	(438.70, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.46, 28.27) --
	(464.46, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (490.22, 28.27) --
	(490.22, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (515.98, 28.27) --
	(515.98, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (541.75, 28.27) --
	(541.75, 31.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (567.51, 28.27) --
	(567.51, 31.02);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (412.94, 20.01) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (438.70, 20.01) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (464.46, 20.01) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (490.22, 20.01) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (515.98, 20.01) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (541.75, 20.01) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (567.51, 20.01) {50};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (492.80,  7.82) {Secondary cohort time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (398.52,107.31) {Backward delay (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (412.94,191.89) {G. Serial interval};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-09-28 serial.tex
update

@@
 These initial conditions allow the model to follow exponential growth from time $\Delta t (\tsub{m}{max} + 1)$ without any transient behaviors.
-Results presented in the main text show simulations beginning from time $\Delta t (\tsub{m}{max} + 1)$.
 
@@
 
+\subsection{Simulations with correlated intrinsic incubation periods and intrinsc generation intervals.}
+
+\begin{figure}[!pht]
+\begin{center}
+\includegraphics[width=0.95\textwidth]{forward_corr.pdf}
+\caption{
+\textbf{Epidemiological dynamics and changes in mean forward and backward delay distributions.}
+(A) Daily incidence over time.
+(B--D) Changes in the mean forward incubation period, generation interval, and serial interval.
+(E--G) Changes in the mean backward incubation period, generation interval, and serial interval.
+Intrinsic incubation periods and intrinsic generation intervals are modeled using a correlated bivariate lognormal distribution; 
+therefore, generation intervals are drawn from the corresponding conditional distributions (given a incubation period), instead of the marginal distribution.
+Higher correlation reduces the amount of changes in the mean forward serial interval because shorter (longer) backward incubation periods of infectors during the increasing (decreasing) phase of an epidemic are associated with shorter (longer) forward generation intervals.
+See Figure 3 in the main text for a detailed description.
+}
+\end{center}
+\end{figure}
+
 \pagebreak

### 2020-09-28 forward.R

@@ -275,7 +275,7 @@ g7 <- ggplot(serdata1) +
 gtot <- arrangeGrob(g1, g2, g3, g4, g5, g6, g7, layout_matrix = matrix(c(1, 1, 1, 2, 3, 4, 5, 6, 7), nrow=3, byrow=TRUE),
                     heights=c(0.8, 1, 1))
 
-tikz(file = "forward.tex", width = 8, height = 8, standAlone = T)
+tikz(file = "forward.tex", width = 8, height = 7, standAlone = T)
 plot(gtot)
 dev.off()
 tools::texi2dvi('forward.tex', pdf = T, clean = T)

### 2020-09-28 forward_corr.R

@@ -1,0 +1,272 @@
+library(tidyr)
+library(dplyr)
+library(ggplot2); theme_set(theme_bw())
+library(gridExtra)
+library(tikzDevice)
+
+load("sir_sim_corr.rda")
+
+corr_data <- data.frame(
+  corr=1:5,
+  type=paste0("$\\rho=", c(0, 0.2, 0.4, 0.6, 0.8), "$")
+) %>%
+  mutate(
+    type=factor(type, levels=type)
+  )
+
+summfun <- function(dd) {
+  dd %>%
+    filter(!is.na(cohort), !is.na(tdiff), cohort <= 100) %>%
+    mutate(
+      cc=cut(cohort, tcut)
+    ) %>%
+    group_by(cc) %>%
+    summarize(
+        mean=mean(tdiff)
+    ) %>%
+    ungroup %>%
+    mutate(
+      cc=as.character(cc),
+      cc=(as.numeric(gsub("\\(", "", gsub(",.*", "", cc)))+as.numeric(gsub("]", "", gsub(".*,", "", cc))))/2
+    )
+}
+
+sir_data <- lapply(simlist_corr, function(x) {
+  lapply(x, "[[", "data") %>%
+    bind_rows(.id="sim")
+}) %>%
+  bind_rows(.id='corr')
+
+sir_data2 <- sir_data %>%
+  mutate(
+    day=floor(time)
+  ) %>%
+  group_by(corr, day, sim) %>%
+  summarize(
+    cases=tail(infected, 1)-head(infected,1)
+  )
+
+sir_data2_time <- sir_data2 %>%
+  filter(cases >= 100) %>%
+  group_by(corr, sim) %>%
+  summarize(
+    min=min(day)
+  )
+
+sir_data3 <- sir_data2 %>%
+  merge(sir_data2_time) %>%
+  mutate(
+    day=day-min
+  ) %>%
+  merge(corr_data)
+
+g1 <- ggplot(sir_data3) +
+  geom_line(aes(day, cases, col=type, group=interaction(type, sim))) +
+  # geom_line(data=detdata2, aes(day, cases, col="Deterministic"), lwd=1) +
+  scale_x_continuous("Time (days)", expand=c(0, 0), limits=c(-10, 52)) +
+  scale_y_continuous("Daily incidence", expand=c(0, 0), limits=c(1, 2400)) +
+  scale_color_viridis_d() +
+  ggtitle("A") +
+  theme(
+    panel.grid = element_blank(),
+    legend.title = element_blank(),
[…]

### 2020-09-28 sir_corr.R

@@ -1,0 +1,113 @@
+##' @param x a vector of nodes
+##' @param size number of nodes to pick at random
+sample2 <- function(x, size) {
+  if(length(x)==1) {
+    rep(x, size)
+  } else{
+    sample(x, size, replace=TRUE)
+  }
+}
+
+sir.full2 <- function(size,
+                     R0=2.5,
+                     meanlog=1.62,
+                     sdlog=0.42,
+                     meanlog2=1.54,
+                     sdlog2=0.37,
+                     rho=0,
+                     I0,
+                     seed = NULL,
+                     imax,
+                     keep.intrinsic=FALSE){
+  
+  if (!is.null(seed)) set.seed(seed)
+  
+  V <- 1:size
+  
+  if (missing(I0)) {
+    if (missing(I0)) stop("specify the initial conditions")
+    
+  }
+  initial_infected <- 1:I0
+  
+  if (missing(imax)) imax <- size
+  
+  queue_v <- queue_t <- queue_infector <- rep(NA, I0)
+  
+  queue_v[1:I0] <- initial_infected 
+  queue_t[1:I0] <- 0
+  
+  t_infected <- t_symptomatic <- rep(NA, size)
+  t_infected[initial_infected] <- 0
+  
+  t_gillespie <- NULL
+  c_infected <- 0
+  
+  if (keep.intrinsic) {
+    intrinsic_generation <- vector('list', length(V))
+  } else {
+    intrinsic_generation <- NULL
+  }
+  
+  done <- rep(FALSE, size)
+  infected_by <- rep(NA, size)
+  
+  stop <- FALSE
+  
+  while (!stop) {
+    j.index <- which.min(queue_t)
+    j <- queue_v[j.index]
+    
+    infected_by[j] <- queue_infector[j.index]
+    t_infected[j] <- queue_t[j.index]
+    
+    t <- queue_t[j.index]; t_gillespie <- c(t_gillespie, t)
+    
+    incubation <- rlnorm(1, meanlog, sdlog)
+    t_symptomatic[j] <- t+incubation
+    
+    c_infected <- c_infected +1
+    
+    ncontact <- rpois(1, R0)
+    
+    n <- V[V != j]
+    
+    if (ncontact > 0) {
+      queue_v <- c(queue_v, sample2(n, ncontact))
+      queue_infector <- c(queue_infector, rep(j, ncontact))
+    }
+    
[…]

### 2020-09-28 sir_sim_corr.R

@@ -1,0 +1,28 @@
+source("sir_corr.R")
+
+nsim <- 10
+
+corr <- c(0, 0.2, 0.4, 0.6, 0.8)
+
+simlist_corr <- vector('list', length(corr))
+
+for (j in 1:length(corr)) {
+  print(j)
+  simlist <- vector('list', nsim)
+  
+  i <- 1
+  
+  while (i <= nsim) {
+    print(i)
+    sir_sim <- sir.full2(size=40000, I0=10, seed=i, rho=corr[j], keep.intrinsic = FALSE)
+    
+    if (nrow(sir_sim$data) > 100) {
+      simlist[[i]] <- sir_sim
+      i <- i +1
+    }
+  }
+  
+  simlist_corr[[j]] <- simlist
+}
+
+save("simlist_corr", file="sir_sim_corr.rda")

### 2020-09-28 response.tex
done for now

@@
 
-``For example, infected individuals can become less likely to infect others during late stages of their infection as the epidemic progresses (therefore, leading to ``contraction'' of generation intervals) due to factors that drive time-dependent decreases in transmission such as susceptible depletion, behavioral change, and interventions \citep{champredon2015intrinsic}.''
+``For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical fact of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{kenah2008generation, nishiura2010time, champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.''
 
@@
 
-``Thus, even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), assuming all else being equal.''
+``Thus, even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.''
 
@@
 
-``The lack of distinction is apparent even in standard softwares for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.''
+``The lack of distinction is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.''
 

### 2020-09-29 response.tex
respond to comments in response

@@
 
-We have added some visual aids to Figure 1: we color intrinsic, backward, and forward intervals and explain them breifly in the caption:
+We are not positive we understand this comment.
+Figure 1 is not really intended to communicate the source of biases: that comes later in the course of our exposition.
+We have made the following changes to attempt to improve our visual communication.
+
+\jd{I notice that you didn't fiddle the lengths. This might be worth doing.}
+
+We have added some visual aids to Figure 1: we color intrinsic, backward, and forward intervals and explain them briefly in the caption:
 
@@
 \swp{Doesn't this paragraph visually communicate the insights???? It was already there in the previous version...}
+
+\jd{We can add some text to the bottom of this \P, and maybe also refer back to Fig. 1 here.}
 

### 2020-09-29 response.tex
trivial typos

@@
 
-We have added the following limiations of the reproduction number:
+We have added the following limitations of the reproduction number:
 
@@
 
-``For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro esimates based on aggregated serial interval data underestimated \Ro by 50\%--60\%.''
+``For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro estimates based on aggregated serial interval data underestimated \Ro by 50\%--60\%.''
 
@@
 
-We think that it is important to emphasize that nont distinguishing generation and serial intervals is a commonly made mistake in the field. 
+We think that it is important to emphasize that not distinguishing generation and serial intervals is a commonly made mistake in the field. 
 However, we agree that our critique is weak.
@@
 
-``In order to quantify changes in serial intervals, we group them by the symptom onset dates of the primary (\fref{du}B) and secondary (\fref{du}C) cases---correspoding to forward and backward serial-interval distributions, respectively---and compute their mean and 95\% quantiles.''
+``In order to quantify changes in serial intervals, we group them by the symptom onset dates of the primary (\fref{du}B) and secondary (\fref{du}C) cases---corresponding to forward and backward serial-interval distributions, respectively---and compute their mean and 95\% quantiles.''
 

### 2020-09-29 serial.tex
wordsmithing and comments up to end of methods

@@
 The reproduction number \RR and the exponential growth rate $r$ are critical quantities for characterizing outbreak dynamics.
-These quantities are linked by generation intervals---defined as the time between infection and transmission.
-Because generation intervals are difficult to measure directly, they are often substituted with serial intervals---defined as the onset of symptoms in a chain of transmission.
+These quantities are linked by generation intervals, defined as the time between infection and transmission.
+Because generation intervals are difficult to measure directly, serial intervals---defined as the onset of symptoms in a chain of transmission---are often substituted.
 While serial intervals are easier to measure from contact tracing, recent studies suggest that the two intervals give different estimates of \RR from $r$.
 We present a general framework for characterizing epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly link \RR with $r$, are not the same as \emph{intrinsic} serial intervals (defined by averaging across individual-level characteristics while neglecting population-level dynamics), but instead change with $r$.
-We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial-interval data --- our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by up to 50\%--60\%.
+\bmb{I can't quite parse the meaning of the last clause (``but instead \ldots'').
+Clarify?}
+We provide a heuristic method for addressing biases that can arise from failing to account for changes in serial intervals across cohorts; we apply the method to estimation of \RR for the COVID-19 outbreak in China using serial-interval data.
+Our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by as much as 50\%--60\%.
+\bmb{if it's ``up to/as much as'', why give the range and not just the max?}
 This study demonstrates the importance of early epidemiological investigation through contact tracing and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
@@
 however, both intervals, by definition, describe disease transmission at the individual level.
-Here, we show that the serial-interval distribution, defined from the correct reference time and cohort, gives the same estimate of \RR as the generation-interval distribution from $r$.
-We then apply our framework to serial-interval data from the COVID-19 outbreak in China.
-While our study supports the use of serial-interval distributions in estimating \RR, it also reveals necessary changes to the current understanding and applications of serial-interval distribution.
+Here, we show that estimating \RR based on $r$ and the serial-interval distribution, defined from the correct reference time and cohort, gives the same estimate as using $r$ and the generation-interval distribution.
+We apply our framework to serial-interval data from the COVID-19 outbreak in China.
+While our study supports the use of serial-interval distributions in estimating \RR, it also highlights necessary changes to ourr current understanding and application of serial-interval distributions.
 
@@
 
-The reproduction number \RR is one of the most important characteristics of an emerging epidemic, including the current pandemic of coronavirus disease 2019 (COVID-19) \citep{majumder2020early}.
+The reproduction number \RR is one of the most important characteristics of an emerging epidemic, such as the current pandemic of coronavirus disease 2019 (COVID-19) \citep{majumder2020early}.
 The reproduction number is defined as the average number of secondary cases caused by a primary case;
-the value in a fully susceptible population --- the ``basic'' reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population, and the amount of intervention necessary to eliminate it \citep{anderson1991infectious}.
-Since the reproduction number represents an average \citep{diekmann1990definition, anderson1991infectious}, it does not capture heterogeneity among individuals or across space.
-The reproduction number also does not provide any information about the time scale of disease transmission.
+the value in a fully susceptible population --- the ``basic'' reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population, and the amount of intervention necessary to eliminate it in simple cases \citep{anderson1991infectious}.
+Since the reproduction number represents an average \citep{diekmann1990definition, anderson1991infectious}, it fails to capture heterogeneity among individuals or across space.
+The reproduction number also fails to provide any information about the time scale of disease transmission.
 
 Estimating the reproduction number \RR is challenging because it cannot be measured directly.
-It often requires a detailed knowledge of the disease history and reliable incidence data.
-Instead, near the beginning of an epidemic, \RR can be estimated from the population-level exponential growth rate.
-This approach is convenient because the growth rate can be estimated robustly from case reports \citep{mills2004transmissibility, ma2014estimating}.
-These two quantities, representing the speed $r$ and strength $\RR$ of an epidemic, are linked by the generation-interval distribution \cite{wallinga2007generation}, where the generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee) \citep{svensson2007note}.
+Most methods of \RR estimation require a detailed knowledge of the disease history \bmb{does ``disease history'' here mean $\approx$ life history?
+This might be misconstrued as history in the regular sense (e.g.
+``cholera first appeared in Europe in the 19th century \ldots'')} along with reliable incidence data.
+Alternatively, near the beginning of an epidemic, \RR can be estimated from the population-level exponential growth rate.
+This rate-based approach is convenient because the growth rate can be estimated robustly from case reports \citep{mills2004transmissibility, ma2014estimating}.
+The growth rate $r$, representing the speed of an epidemic, and \RR, reprenting its strength,
+\bmb{this is nice but will people who don't know speed/strength defs get hung up? Is there a spreed/strength ms out there we can ref?}
+are linked by the generation-interval distribution \cite{wallinga2007generation}, where the generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee) \citep{svensson2007note}.
 
@@
 In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean, assuming that the incubation periods of the infector and infectee are identically distributed \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
-Serial intervals can also take negative values due to presymptomatic transmission \citep{he2020temporal}, whereas generation intervals are confined to positive values.
+Serial intervals can also take negative values due to presymptomatic transmission \citep{he2020temporal}, whereas generation intervals must be positive.
 
@@
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds.
-Researchers continue to rely on both generation and serial intervals to make inferences about COVID-19 without making a clear distinction (e.g., \cite{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}), and explicitly conflate the definitions of two intervals (e.g., \cite{anderson2020will,hellewell2020feasibility}).
-The lack of distinction is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
+Researchers continue to base inferences about COVID-19 on both generation and serial intervals without clearly distinguishing between them (e.g., \cite{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}), sometimes explicitly conflating the definitions of the two intervals (e.g., \cite{anderson2020will,hellewell2020feasibility}).
+This lack of distinction \bmb{confusion?} is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
 However, these studies are not meant to be accused of their practices; until now, it has been a common practice use serial and generation intervals interchangeably.
@@
 One source of confusion arises from an apparent discrepancy between the generation-interval and serial-interval viewpoints.
-When the epidemic is growing exponentially, the spread of infection can be characterized as a \emph{renewal process} based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
+While the epidemic is growing exponentially, the spread of infection can be characterized as a \emph{renewal process} based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
 It is well established that this renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
-However, the serial-interval distribution also describes a renewal process --- in this case, linking symptomatic cases based on their symptom onset dates.
-Since both renewal processes, based on generation- and serial-interval distributions, describe the same underlying system of exponential growth, both should provide the same correct link between the reproduction number \RR and the epidemic growth rate $r$.
+However, the serial-interval distribution also describes a renewal process --- in this case, linking symptomatic cases based on their symptom onset dates \bmb{rephrase?
+``in this case, the creation of a new \emph{symptomatic} case based on a symptomatic case in the previous generation''.
+Is it important to talk about symptom onset dates at this point?}
+Since both renewal processes, based on either generation- or serial-interval distributions, describe the same underlying exponentially growing system, both should provide the same correct link between the reproduction number \RR and the epidemic growth rate $r$.
 
-In contexts where the distributions are expected to be different, current theory has no explanation for how these differing distributions could provide identical estimates of \RR from $r$. 
-In fact, recent theory suggest that using serial-interval can underestimate the reproduction number \citep{britton2019estimation, ganyani2020estimating}.
-However, these studies rely on \emph{intrinsic} distributions of incubation periods and generation intervals that neglect the population-level dynamics of the disease spread.
+In contexts where the serial- and generation-interval distributions differ, current theory has no explanation for how two different distributions could provide identical estimates of \RR from $r$. 
+In fact, recent theory suggest that using the serial-interval can underestimate the reproduction number \citep{britton2019estimation, ganyani2020estimating}.
+However, these studies rely on \emph{intrinsic} distributions of incubation periods and generation intervals that neglect the population-level dynamics of disease spread.
 
@@
 these intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
-During an ongoing epidemic, \emph{all} observed epidemiological delays (e.g., incubation period) between primary (e.g., infection) and secondary (e.g., symptom onset) events are subject to backward biases: when the incidence of primary events is increasing (or decreasing), we are more likely to observe shorter (or longer) intervals.
-Since realized serial intervals depend on three distinct intervals (i.e., incubation period of the infector, incubation period of the infectee, and the generation interval between them), any of these intervals can be subject to backward biases depending on our perspective.
+During an ongoing epidemic, all observed epidemiological delays (e.g., incubation period) between primary (e.g., infection) and secondary (e.g., symptom onset) events are subject to backward biases: when the incidence of primary events is increasing (or decreasing), we are more likely to observe shorter (respectively longer) intervals.
+Since realized serial intervals combine three distinct intervals (i.e., incubation period of the infector, incubation period of the infectee, and the generation interval between them), any of these intervals can be subject to backward biases depending on our perspective.
+\bmb{``depending on our perspective'' is a little unclear at this point but hopefully resolves quickly as reader moves forward}
 In particular, when we consider forward serial-interval distributions, the incubation periods of the infectors are subject to backward biases because we have to look backward in time from their symptom onset to infection.
-Therefore, the realized incubation period distributions of the infector and the infectee can differ dynamically, even if they are expected to be equivalent intrinsically.
+Therefore, the realized incubation period distributions of the infector and the infectee can differ dynamically, even if the intrinsic analogues of the same distributions are expected to be equivalent.
+\bmb{check to make sure I didn't screw this up?}
 
@@
 
-A time delay between two epidemiological events can involve either one infected individual (e.g., incubation period: infection and symptom onset of an individual) or two -- an infector and an infectee (e.g., the serial interval).
-We define the delay as the time difference between one event (the \emph{primary} event) and the other (the \emph{secondary} event).
+A time delay between two epidemiological events can involve either one infected individual (e.g., incubation period: infection and symptom onset of an individual) or two --- an infector and an infectee (e.g., the serial interval).
+We define the delay as the time difference between the \emph{primary} event and the \emph{secondary} event.
 In some cases, the primary event always occurs before the secondary event (e.g., the time from infection to onset of symptoms in a single individual, or the generation interval between two individuals).
-In other cases, the delay can sometimes be negative (e.g., the time from onset of infectiousness to onset of symptoms in a single individuals, or the serial interval between two individuals).
+In other cases, the delay can sometimes be negative (e.g., the time from onset of infectiousness to onset of symptoms in a single individual, or the serial interval between two individuals).
 
-At the individual level, we can define the time distribution between a primary and a secondary event that we expect to observe (averaged across individual characteristics) for an infected individual --- we refer to this distribution as the intrinsic distribution.
+At the individual level, we can define the time distribution between a primary and a secondary event that we expect to observe (averaged across individual characteristics) for an infected individual --- we refer to this distribution as the \emph{intrinsic distribution}.
 For example, the intrinsic incubation period distribution describes the expected time distribution from infection to symptom onset of an infected individual.
@@
 At the population level, we model realized time delays between a primary and a secondary event from a cohort perspective.
-A cohort consists of \emph{all} individuals whose (primary or secondary) event occurred at a given time. 
-For example, when we are measuring incubation periods, a primary cohort consists of all individuals who became infected at time \psymp, while a secondary cohort consists of all individuals whose symptom onset occurred at time $\ssymp$.
-Similarly, when we are measuring serial intervals, a primary cohort consists of all infectors who became symptomatic at time $\psymp$.
-Then, for a primary cohort at time $\psymp$, we can define the distribution of realized delays between primary and secondary events. 
+A cohort consists of all individuals whose (primary or secondary) event occurred at a given time.
+%% \psymp, \ssymp have \ensuremath in def so don't need $$ when used in isolation
+For example, when we are measuring incubation periods, a primary cohort consists of all individuals who became infected at time \psymp, while a secondary cohort consists of all individuals whose symptom onset occurred at time \ssymp.
+Similarly, when we are measuring serial intervals, a primary cohort consists of all infectors who became symptomatic at time \psymp.
+Then, for a primary cohort at time \psymp, we can define the distribution of realized delays between primary and secondary events. 
 We refer to this distribution as the forward delay distribution and denote it as $f_\psymp(\tau)$.
 
-Likewise, we define the backward delay distribution $b_\ssymp(\tau)$ for a secondary cohort at time $\ssymp$:
-The backward delay distribution describes the time delays between a primary and secondary events given that the secondary event occurred at time $\ssymp$.
-For example, the backward incubation period distribution at time $\ssymp$ describes incubation periods for a \emph{cohort} of individuals who became symptomatic at time $\ssymp$.
-Likewise, the backward serial-interval distribution at time $\ssymp$ describes serial intervals for a \emph{cohort} of infectees who became symptomatic at time $\ssymp$.
+Likewise, we define the backward delay distribution $b_\ssymp(\tau)$ for a secondary cohort at time \ssymp:
+The backward delay distribution describes the time delays between a primary and secondary events given that the secondary event occurred at time \ssymp.
+For example, the backward incubation period distribution at time \ssymp describes incubation periods for a \emph{cohort} of individuals who became symptomatic at time \ssymp.
+Likewise, the backward serial-interval distribution at time \ssymp describes serial intervals for a \emph{cohort} of infectees who became symptomatic at time \ssymp.
 
@@
 $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
-secondary cohorts then we can express the total density of intervals $\tau$ between calendar time $\psymp$ and $\ssymp$ (i.e., $\tau=\ssymp-\psymp$) as follows:
+secondary cohorts then we can express the total density of intervals $\tau$ between calendar time \psymp and \ssymp (i.e., $\tau=\ssymp-\psymp$) as follows:
 \begin{equation}
@@
 this equation is the probability density that an individual
-who became symptomatic at time $\ssymp$ had an incubation period of
+who became symptomatic at time \ssymp had an incubation period of
 length $\tau$.
@@
 the time-varying primary cohort size at the earlier time $\psize(\ssymp-\tau)$ (in this case, the number of individuals infected at time $\ssymp-\tau$),
-and the forward delay distribution $f_{\ssymp-\tau}(\tau)$ (in this case, the probability density that an incubation period that starts at time $\ssymp-\tau$ ends at time $\ssymp$).
+and the forward delay distribution $f_{\ssymp-\tau}(\tau)$ (in this case, the probability density that an incubation period that starts at time $\ssymp-\tau$ ends at time \ssymp).
 
@@
 Typically, within-individual forward delay distributions are not directly affected by epidemic dynamics.
-Some realized forward distributions, like incubation period distributions, are expected to be equivalent to their intrinsic distributions and remain invariant at the time scale of an outbreak.
+Some realized forward distributions, like incubation period distributions, are equivalent to their intrinsic distributions and remain invariant at the time scale of an outbreak.
 Other realized distributions, like the distribution of time from symptom onset to testing, may change over the course of an epidemic due to changes in public-health policies or individual behavior.
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics.
-For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical fact of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{kenah2008generation, nishiura2010time, champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.
+For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical process of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{kenah2008generation, nishiura2010time, champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.
 
@@
 In general, the backward delay distribution will differ from the forward delay distribution (unless the disease is at equilibrium), even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
-These ideas apply to all epidemiological delay distributions and generalize the work by \cite{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe realized generation intervals from the perspective of an infector and an infectee, respectively, as well as the work by \cite{britton2019estimation} who showed that \eref{backexp} holds for the backward generation-interval distributions.
+These ideas apply to all epidemiological delay distributions and generalize the work by \cite{champredon2015intrinsic} who compared forward and backward generation-interval distributions to describe realized generation intervals from the perspective of an infector and an infectee, respectively, as well as the work by \cite{britton2019estimation} who showed that \eref{backexp} holds for the backward generation-interval distribution.
 
@@
 
-The serial interval is defined as the time between when an infector becomes symptomatic and when an infectee becomes symptomatic \citep{svensson2007note}.
+The serial interval is defined as the time between when an infector becomes symptomatic and when their infectee becomes symptomatic \citep{svensson2007note}.
 Previous studies have often expressed serial intervals $\tau_{\rm s}$ in the form (\fref{diagram}A):
@@
   backward serial interval for a cohort of infectees who became
-  symptomatic at time $\ssymp$.  In this case, $\tau_{\rm i1}$ is drawn from the
+  symptomatic at time \ssymp.  In this case, $\tau_{\rm i1}$ is drawn from the
   forward incubation period distribution; $\gtime$ is drawn from the
@@
 Likewise, we can define the backward serial-interval distribution for
-a cohort of infectees who became symptomatic at time $\ssymp$
+a cohort of infectees who became symptomatic at time \ssymp
 (\fref{diagram}C).  
@@
 
-To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total density of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time $\ssymp$.
+To calculate realized serial-interval distributions, we begin by modeling $\total(\psymp,\ssymp)$: the total density of serial intervals that start (when infectors develop symptoms) at time $\psymp$ and end (when infectees develop symptoms) at time \ssymp.
 For simplicity, we assume that all infected individuals eventually develop symptoms.
-Then, the density of serial intervals between time $\psymp$ and $\ssymp$,
+Then, the density of serial intervals between time $\psymp$ and \ssymp,
 given that the infectors became infected at time $\pinf\le\psymp$ and
@@
 $\psymp$ (realized incubation periods of infectors) and between
-$\sinf$ and $\ssymp$ (realized incubation periods of infectees):
+$\sinf$ and \ssymp (realized incubation periods of infectees):
 \begin{equation}
@@
 The denominator of the forward serial-interval distribution (\eref{fserial}) then corresponds to the total number of infections generated by primary cases who themselves developed symptoms at time \psymp.
-Dividing this quantity by the number of individuals who developed symptoms at time at time \psymp, $j(\psymp) = \int_{-\infty}^\infty \total(\psymp-\tau', \psymp) \dtau'$, we obtain the serial reproduction number:
+Dividing this quantity by the number of individuals who developed symptoms at time \psymp, $j(\psymp) = \int_{-\infty}^\infty \total(\psymp-\tau', \psymp) \dtau'$, we obtain the serial reproduction number:
 \begin{equation}
@@
 \end{align}
-where $\RR(t)$ is the instantaneous reproduction number (i.e., the average number of secondary cases that a primary case infected at time $t$ will generate if conditions at time $t$ remains unchanged \citep{fraser2007estimating}), and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a population where changes in $\RR(t)$ is negligible \citep{champredon2015intrinsic}).
+where $\RR(t)$ is the instantaneous reproduction number (i.e., the average number of secondary cases that a primary case infected at time $t$ will generate if conditions at time $t$ remain unchanged \citep{fraser2007estimating}), and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a population where changes in $\RR(t)$ is negligible \citep{champredon2015intrinsic}).
 This model effectively assumes that epidemic dynamics are driven by changes in transmission rate, which may not hold under individual-based intervention such as case isolation \citep{fraser2007estimating};
@@
 
-Here, we consider a specific example where changes in the reproduction number is driven by susceptible depletion: $\RR(t) = \Ro S(t)$, where \Ro represents the basic reproduction number.
+Here, we consider a specific example where changes in the reproduction number are driven by susceptible depletion: $\RR(t) = \Ro S(t)$, where \Ro represents the basic reproduction number.
 Although we do not consider non-pharmaceutical interventions explicitly, the effect of susceptible depletion is mathematically equivalent to the effect of interventions that reduce transmission rate.
@@
 requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
-Since we have not yet made any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, this conclusion is robust, regardless of whether presymptomatic is possible or not.
+Since we have not yet made any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, this conclusion \bmb{what conclusion specifically?
+or do you mean this ``formulation'' is robust?
+Do you need to be more explicit about the inferential status of ``Therefore, we expect \ldots'' above?
+Is } is robust, regardless of whether presymptomatic transmission
+is possible or not.
 It is straightforward to see this relationship from \eref{jrenew} (by substituting $j(t) \approx j(0) \exp(rt)$ and $\Rs(t) \approx \Ro$);
@@
 that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
-Throughout the paper, we allow for presymptomatic transmission to match the transmission dynamics of COVID-19.
+Everywhere else in this paper, however, we allow for presymptomatic transmission in the model in order to match the transmission dynamics of COVID-19.
 
@@
 
-\subsection{Simulations with correlated intrinsic incubation periods and intrinsc generation intervals.}
+\subsection{Simulations with correlated intrinsic incubation periods and intrinsic generation intervals.}
 

### 2020-09-30 serial.tex
miscellaneous edits

@@
 The intrinsic incubation period distribution is parameterized using a log-normal distribution with log mean $\mu_I=1.62$ and log standard deviation $\sigma_I=0.42$.
-The joint probability distribution is modeled using a bivariate log-normal distribution with correlations (on the log scale) $\rho=0, 0.25, 0.5, 0.75$.
+The joint probability distribution is modeled using a bivariate log-normal distribution with correlations (on the log scale) $\rho=\{0, 0.25, 0.5, 0.75\}$.
 The intrinsic generation-interval and incubation period distributions are chosen to match characteristic of COVID-19 to illustrate realistic magnitudes of time-varying/perspective effects in the current pandemic.
@@
 
-We use parameter estimates for COVID-19 to characterize the degree to which the realized serial-interval distribution can change over the course of an epidemic and evaluate how different definitions of the serial-interval distribution can affect the Euler-Lotka estimates of \Ro.
-We further address how the observed serial intervals, measured through contact tracing, are affected by the right censoring during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial-interval data to estimate \Ro.
+We use parameter estimates for COVID-19 to characterize the degree to which the realized serial-interval distribution can change over the course of an epidemic and to evaluate how different definitions of the serial-interval distribution can affect the Euler-Lotka estimates of \Ro.
+We further address how the observed serial intervals, measured through contact tracing, are affected by right censoring during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial-interval data to estimate \Ro.
 Finally, we analyze serial-interval data from the COVID-19 epidemic in China under our framework.
@@
 \fref{rR} shows Euler-Lotka estimates of \Ro\ based on different definitions of the serial interval. 
-When the initial forward serial-interval distributions $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen}) for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
+When the initial forward serial-interval distribution $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen}) for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
 When the intrinsic distributions are used, however, estimates based on the serial interval (\eref{Rintrinsic}) underestimate \Ro: as $r$ increases, \Rintrinsic saturates and eventually \emph{decreases} due to the increasing inferred importance of negative serial intervals (\fref{rR}B).
@@
 (D) The squared coefficient of variation of the initial forward serial intervals during the exponential growth phase decreases with $r$.
+\bmb{x-axes of B and D don't exactly line up (I realize that's \emph{extremely} fussy)}
 }
@@
 The effects of higher means (which increase \Ro) exactly cancel those of higher variability (which decrease \Ro).
-On the other hand, \emph{intrinsic} serial intervals (\eref{intrinsicSI}) have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are more variable (also see squared coefficient of variation of the initial forward serials at $r=0$ in \fref{rR}D);
+On the other hand, \emph{intrinsic} serial intervals (\eref{intrinsicSI}) have the same mean (equal to the mean initial forward serial at $r=0$ in \fref{rR}C) as the intrinsic generation intervals but are more variable (also see squared coefficient of variation of the initial forward serial-interval distribution at $r=0$ in \fref{rR}D);
 therefore, we underestimate \Ro when we use the intrinsic serial-interval distribution.
@@
 In order to remove possible transient dynamics (e.g., left-censoring of time delays and initial stochasticity due to low number of infections), we set $t=0$ to the first time point when daily incidence is greater than 100.
-Intrinsic incubation periods and intrinsic generation intervals are assumed to be independent of each other for simplicity; simulations with correlated intrinsic incubation periods and intrinsic generation intervals are provided in Supplementary Materials.
+Intrinsic incubation periods and intrinsic generation intervals are assumed to be independent of each other for simplicity; see Supplementary Materials for simulations with correlated intrinsic incubation periods and intrinsic generation intervals.
 See Table 1 for parameter values.
+\bmb{identical plot titles B/E etc could be confusing at first glance?}
 }
@@
 We see similar qualitative patterns in all three backward delays (\fref{epi}E--G; \eref{backward}), because they are predominantly driven by the rate of change in incidence, which in turn affects relative cohort sizes.
-When incidence is increasing, individuals are more likely to have been infected recently and therefore, we are more likely to observe shorter intervals (\eref{backexp}).
+When incidence is increasing, individuals are more likely to have been infected recently, and therefore we are more likely to observe shorter intervals (\eref{backexp}).
 Similarly, when incidence decreases, we are more likely to observe longer intervals.
@@
 While the qualitative changes in the mean forward and backward serial interval are consistent with our earlier simulations (\fref{epi}), the initial mean forward serial interval (\fref{du}B) appears to be larger than what we calculated based on previously estimated incubation period and generation-interval distributions (\fref{rR}C).
-These may imply that the incubation period and generation interval (Table 1) were underestimated, as neither study explicitly accounted for the fact that the observed intervals were drawn from the backward distributions and were likely to have been censored.
+This difference may imply that the incubation period and generation interval (Table 1) were underestimated, as neither study explicitly accounted for the fact that the observed intervals were drawn from the backward distributions and were likely to have been censored.
 
 \fref{du}D shows the cohort-averaged estimates of \Ro, which remain roughly constant until day January 17th and suddenly decreases;
-this sudden decrease is due changes in the forward serial intervals consistent with the dynamics seen in our simulations (\fref{obsrR}).
+this sudden decrease is due to changes in the forward serial intervals consistent with the dynamics seen in our simulations (\fref{obsrR}).
 The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, doi:10.1098/rsif.2020.0144}:
@@
 Analogous to our approach, they also grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean forward serial interval decreased from 7.8 days to 2.6 days.
-While they attributed the decrease in serial intervals to reduction of the isolation delay, their regression analysis showed that isolation delays explain only 51.5\% of the variation in serial intervals (and explaining up to 72\% of the variance including other intervention measures).
+While they attributed the decrease in serial intervals to reduction of the isolation delay, their regression analysis showed that isolation delays explain only 51.5\% of the variation in serial intervals (they could explain up to 72\% of the variance by including other intervention measures).
 Our framework provides an explanation for the remaining variation: changes in the backward incubation period during the decreasing phase of an epidemic also shorten serial intervals due to increased amount of presymptomatic transmission (even in the absence of nonpharmaceutical interventions).
-Since isolation delays and other intervention measures affect the amount of onward transmission, and therefore the distribution of realize (forward) generation intervals, it cannot explain all variation in forward serial intervals, which depend on (i) backward incubation period of the infector, (ii) the forward generation interval, and (iii) the forward incubation period of the infectee (\fref{diagram}B).
+Since isolation delays and other intervention measures affect the amount of onward transmission, and therefore the distribution of realized (forward) generation intervals, it cannot explain all variation in forward serial intervals, which depend on (i) backward incubation period of the infector, (ii) the forward generation interval, and (iii) the forward incubation period of the infectee (\fref{diagram}B).
 
@@
 For example, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
-However, our results show that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can, in fact, exacerbate the underestimation of initial \RR.
-Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase and potentially re-assess existing estimates of \RR.
+However, our results show that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can actually exacerbate the underestimation of initial \RR.
+Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase, and potentially re-assess existing estimates of \RR.
 We also suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions and understand their changes over time.
 These modeling approaches should be coupled with epidemiological investigation through contact tracing. 
-Going forward, an additional advantage of early, intensive contact tracing of emerging diseases is that this is the best way to characterize the initial forward serial-interval distribution.
+Going forward, an additional advantage of early, intensive contact tracing of emerging diseases is that it provides the best information to characterize the initial forward serial-interval distribution.
 
@@
 Here, we use a bivariate lognormal distribution to capture their correlations phenomenologically but their true correlations will depend on viral load dynamics;
-nonetheless, we expect our conclusions about decreasing serial intervals of COVID-19 to be robust as individuals with longer incubation periods have longer time window to transmit before symptom onset.
-Otherwise, the impact of increasing backward incubation periods on the forward serial intervals are likely to be disease specific---for example, we show in Supplementary Materials that the initial forward serial-interval distribution can be equivalent to the intrinsic generation-interval distribution, regardless of the growth rate $r$, due to independence between the incubation period and time from symptom onset to transmission (assuming no transmission occurs during the incubation period).
-This implies that not considering this correlation can potentially bias the estimates of the intrinsic generation-interval distribution from the serial-interval distribution.
+\bmb{don't understand the connection between these two clauses?}
+nonetheless, we expect our conclusions about decreasing serial intervals of COVID-19 to be robust as individuals with longer incubation periods have a longer time window to transmit before symptom onset.
+Otherwise \bmb{??}, the impact of increasing backward incubation periods on the forward serial intervals are likely to be disease specific---for example, we show in Supplementary Materials that the initial forward serial-interval distribution can be equivalent to the intrinsic generation-interval distribution, regardless of the growth rate $r$, due to independence between the incubation period and time from symptom onset to transmission (assuming no transmission occurs during the incubation period).
+This \bmb{(?antecedent?)} implies that not considering this correlation can potentially bias the estimates of the intrinsic generation-interval distribution from the serial-interval distribution.
 % Previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the dynamical differences between the realized incubation periods of infectors (backward-looking) and those of infectees (forward looking) (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
@@
 
-Here, we lay out a few practical principles for analyzing and interpreting serial-interval data.
+Finally, we lay out a few practical principles for analyzing and interpreting serial-interval data.
 First, serial intervals should be cohorted based on the symptom onset date whenever possible.
-Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals is expected to differ from this expectation, and to change through time due to epidemic dynamics.
-Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases:
+Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals differs from this expectation, and changes through time due to epidemic dynamics.
+Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they \bmb{??} can be subject to different censoring and epidemiological biases:
 Even when \emph{all} realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR}).
-Third, applying serial interval information from one epidemic of a given disease to another should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.
+Third, applying serial interval information across epidemics of a given disease should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.
 Finally, serial-interval data should be accompanied by a trajectory of the epidemic curve, whenever possible, to provide epidemiological context.
@@
 More broadly, our study underlines the importance of carefully defining measured epidemiological time distributions. 
-Previous studies have shown that it matters whether generation
-intervals are measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
+Previous studies have shown the importance of forward vs. backward
+measurement of generation intervals \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
 we generalize these ideas and show that they apply to any other epidemiological distributions.
-Some studies during the early phases of the COVID-19 epidemics have tried to correct for the backward biases, but changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
+Some studies during the early phases of the COVID-19 epidemics have tried to correct for the backward biases \bmb{refs?}, but changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
 Cohorting epidemiological delays by the primary event time can help avoid backward biases (although censoring biases can still exist) as well as detect potential changes in the distribution.
@@
 Biases in the observed serial intervals will necessarily bias the estimates of \RR. 
-Furthermore, when one of the individuals is asymptomatic, there is no symptom-based serial interval; 
-neglecting the time scale asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
+Furthermore, when one of the individuals in a transmission pair is asymptomatic, there is no symptom-based serial interval; 
+neglecting the time scale of asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
 

### 2020-09-30 rR.R

@@ -102,12 +102,20 @@ rRdata2 <- list(
                               "Intrinsic serial interval ($\\rho=0$)"))
     )
 
+
+## viridis/C colours; manually extracted (see commented code below)
+vcpal <- c("#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF", "#0D0887FF")
+## reduce luminanance of too-light yellow
+vcpal[4] <- adjustcolor(vcpal[4], red.f = 0.9, green.f = 0.9, blue.f = 0.9)
+vcpal <- vcpal[c(5,1:4)] ## shuffle
+    
 g2 <- ggplot(rRdata2) +
   geom_smooth(aes(r, R, col=type, lty=type), se=FALSE) +
   geom_point(aes(r, R, col=type, shape=type), size=2) +
   scale_x_continuous("Exponential growth rate $r$ (1/day)", limits=c(0, 0.3), expand=c(0, 0)) +
   scale_y_continuous("Reproduction number ${\\mathcal R}_{\\textrm{\\tiny intrinsic}}$", limits=c(1, 4.5), expand=c(0, 0)) +
-  scale_color_viridis_d(option="C") +
+  ## scale_color_viridis_d(option="C") +
+  scale_colour_manual(values=vcpal) +
   ggtitle("B") +
   theme(
     panel.grid = element_blank(),
@@ -115,6 +123,9 @@ g2 <- ggplot(rRdata2) +
     legend.title = element_blank(),
     legend.background = element_blank()
   )
+
+## dput(unique(ggplot_build(g2)$data[[2]]$colour))
+## plot(1:5,1:5,cex=5,col=vcpal,pch=16)
 
 rGdata <- list(
   data.frame(

### 2020-10-04 response.tex
wordsmithing and comments up to end of methods
so close...

@@
 Reviewers 1 and 3 both mention that we assume that the latent and incubation periods are equivalent (thus not allowing for presymptomatic transmission). 
-However, we only present this scenario in the appendix as a special case.
-We do not assume this in the main text.
+However, we only present this scenario in the appendix as a special case; We do not make this assumption in the main text.
 We have thus tried to make our assumptions clear and our results more accessible.
@@
 
-The special version is only presented in the supplementary material. We do not assume this in the main text. We have now made this distinction clear in the text:
+The special version, in which the latent period and incubation period are assumed to be equivalent, is only presented in the supplementary material.
+We do not assume this in the main text.
+We have now made this distinction clear in the text:
 
 ``For example, the Susceptible-Exposed-Infected-Recovered model, under the additional assumption that the incubation and exposed periods are equivalent (i.e.
-that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
-Throughout the paper, we allow for presymptomatic transmission to match the transmission dynamics of COVID-19.''
+that onset of symptoms and infectiousness occur simultaneously), provides a special case.
+In this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
+Everywhere else in this paper, however, we do not assume that the incubation and exposed periods are equivalent---instead, we allow for presymptomatic transmission in the model in order to reflect the transmission dynamics of COVID-19.''
+
+We have also added section 2.3 which describes the parameterization of our model.
 
 Figure 2 further shows that the initial forward serial-interval distribution is different from the intrinsic generation-interval distribution but gives identical \Ro estimates given $r$ using parameter estimates for COVID-19.
-We also show that the main result (initial forward serial-interval distribution provides the same link as the intrinsic generation-interval distribution) hold in general and provide a mathematical proof for it.
-But we acknowledge that changes in serial intervals throughout the epidemic and their exact shape depends on the joint distribution of intrinsic generation intervals and incubation periods.
+We also show that the main result (initial forward serial-interval distribution provides the same link as the intrinsic generation-interval distribution) hold in general.
+We provide a mathematical proof for this in Supplementary Materials (and breifly describe the intuition in Section 2.4).
+We acknowledge that changes in serial intervals throughout the epidemic and their exact shape depends on the joint distribution of intrinsic generation intervals and incubation periods.
+Therefore, the main result regarding the initial forward serial interval is robust, and other results should be interpreted in the context of COVID-19.
 
@@
 
-This statement is proved in the supplement and illustrated in a general context in Figure 2A. We now say this explicitly in the main text:
+This statement is proved in the Supplementary Materials Section 5.3 and illustrated in a general context in Figure 2A. We now say this explicitly in the main text:
 
@@
 Since we have not yet made any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, this conclusion is robust, regardless of whether presymptomatic is possible or not.
-It is straightforward to see this relationship from \eref{jrenew} (by substituting $j(t) \approx j(0) \exp(rt)$ and $\Rs(t) \approx \Ro$);
+It is straightforward to see this relationship from Eq. (10) (by substituting $j(t) \approx j(0) \exp(rt)$ and $\Rs(t) \approx \Ro$);
 in Supplementary Materials, we provide a more detailed mathematical proof of this relationship.''
@@
 
-We have tried to clarify this point:
+We have clarified point:
 
@@
 
-``Thus, even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.''
+``Thus, the mean backward interval will be always shorter than the mean forward interval as long as $r > 0$---even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.''
 
@@
 
-This result also does not depend on the restrictive assumption. We have tried to clarify this. We also re-phrased to describe the earlier studies more carefully:
+This result does not depend on the restrictive assumption. We have clarified this. We also re-phrased to describe the earlier studies more carefully:
 
@@
 
-We are not assuming this, as discussed above. We have tried to clarify.
+We thank the reviewer for the recommendation on being specific on model assumptions.
+In Section 3, we do not use the SEIR model.
+We make our assumptions in Section 2.
+We have also added Section 2.5 (model parameterization).
 
@@
 ``For example, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
-However, our results show that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can, in fact, exacerbate the underestimation of initial \RR.''
+However, our results show that if observational biases in the forward serial interval through time are not accounted for, using up-to-date serial-interval data can actually exacerbate the underestimation of \RR in the initial growth phase of an outbreak.''
 
@@
 Also, Figure 2--3 illustrate that generation and serial intervals have different means, and therefore are different distributions.
-We have tried to highlight these differences throughout the main text.
+We highlight these differences throughout the main text.
 
@@
 
-It is about both.
+The manuscript is about the relationship between the reproduction number $\RR$, growth rate $r$, and interval distributions.
 Generation and serial intervals are key quantities in describing epidemic dynamics; their differences have long been misunderstood and our paper provides a theoretical basis for linking them properly.
@@
 We have rewritten a large proportion of the introduction section based on these suggestions.
+We now begin with the definition of $\RR$ (including its limitations). 
+Then, we discuss the method of inferring $\RR$ from $r$ and generation-interval distribution. 
+Then, we discuss the relationship between generation and serial intervals, ending with the knowledge gap.
+We end the introduction by providing examples of how off $\RR$ estimates are in applications.
 
@@
 
-We think that it is important to emphasize that not distinguishing generation and serial intervals is a commonly made mistake in the field. 
-However, we agree that our critique is weak.
-We have tried to remove any unfair accusations from the paper (but still provide a few examples to illustrate that this is a common practice without accusing those papers).
+We think that it is important to emphasize that not distinguishing generation and serial intervals is a commonly made compromise in the field. 
+However, we agree that the wording of our prior critique was too vague.
+We have tried to remove any unfair accusations from the paper (but still provide a few examples to illustrate that this is a common practice without accusing those particular authors of what we contend is a broader shortcoming in the field).
 
@@
 
-We do not assume this. This is only assumed in the supplementary file as a special case. We now make this clear in the main text.
+We do not assume this. This is only assumed in the supplementary file as a special case. We now make this clear in the main text:
+
+``For example, the Susceptible-Exposed-Infected-Recovered model, under the additional assumption that the incubation and exposed periods are equivalent (i.e.
+that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
+Everywhere else in this paper, however, we allow for presymptomatic transmission in the model in order to match the transmission dynamics of COVID-19.''
 

### 2020-10-04 serial.tex
so close...

@@
 Because generation intervals are difficult to measure directly, serial intervals---defined as the onset of symptoms in a chain of transmission---are often substituted.
-While serial intervals are easier to measure from contact tracing, recent studies suggest that the two intervals give different estimates of \RR from $r$.
-We present a general framework for characterizing epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly link \RR with $r$, are not the same as \emph{intrinsic} serial intervals (defined by averaging across individual-level characteristics while neglecting population-level dynamics), but instead change with $r$.
-\bmb{I can't quite parse the meaning of the last clause (``but instead \ldots'').
-Clarify?}
-We provide a heuristic method for addressing biases that can arise from failing to account for changes in serial intervals across cohorts; we apply the method to estimation of \RR for the COVID-19 outbreak in China using serial-interval data.
-Our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by as much as 50\%--60\%.
-\bmb{if it's ``up to/as much as'', why give the range and not just the max?}
+However, recent studies suggest that the two intervals give different estimates of \RR from $r$.
+We present a general framework for characterizing epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly link \RR with $r$, are not the same as \emph{intrinsic} serial intervals---defined by averaging across individual-level characteristics while neglecting population-level dynamics.
+Instead, the forward serial-interval distribution depends on $r$: 
+When an epidemic is growing exponenially, infectors that develop symptoms on a given day will have shorter incubation periods, on average, than their infectees, thereby affecting the realized serial-interval distribution.
+We provide a heuristic method for addressing biases that can arise from failing to account for changes in serial intervals across cohorts; we apply the method to estimation of \RR for the COVID-19 outbreak in China, outside Hubei province, using serial-interval data (collected between January  21--February  8,  2020).
+Our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by a factor of 2.0--2.6 in the context of COVID-19.
 This study demonstrates the importance of early epidemiological investigation through contact tracing and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
@@
 The generation- and serial-interval distributions are key, but different, quantities in outbreak analyses.
-Recent theoretical studies suggest that two distributions give different estimates of the reproduction number \RR from the exponential growth rate $r$;
+Recent theoretical studies suggest that the two distributions give different estimates of the reproduction number \RR as inferred from the observed exponential growth rate $r$;
 however, both intervals, by definition, describe disease transmission at the individual level.
-Here, we show that estimating \RR based on $r$ and the serial-interval distribution, defined from the correct reference time and cohort, gives the same estimate as using $r$ and the generation-interval distribution.
-We apply our framework to serial-interval data from the COVID-19 outbreak in China.
-While our study supports the use of serial-interval distributions in estimating \RR, it also highlights necessary changes to ourr current understanding and application of serial-interval distributions.
+Here, we show that estimating \RR based on $r$ and the serial-interval distribution, when defined from the correct reference time and cohort, gives the same estimate as using $r$ and the generation-interval distribution.
+We apply our framework to serial-interval data from the COVID-19 outbreak in China, outside Hubei province, reported between January  21--February 8, 2020, revealing systematic biases in prior inference methods.
+Our study provides the theoretical basis for practical changes to the principled use of serial interval distributions in estimating \RR during epidemics.
 
@@
 Estimating the reproduction number \RR is challenging because it cannot be measured directly.
-Most methods of \RR estimation require a detailed knowledge of the disease history \bmb{does ``disease history'' here mean $\approx$ life history?
-This might be misconstrued as history in the regular sense (e.g.
-``cholera first appeared in Europe in the 19th century \ldots'')} along with reliable incidence data.
-Alternatively, near the beginning of an epidemic, \RR can be estimated from the population-level exponential growth rate.
+Most methods of \RR estimation require a detailed knowledge of the life history along with reliable incidence data.
+Alternatively, near the beginning of an epidemic, \RR can be estimated from the population-level exponential growth rate $r$.
 This rate-based approach is convenient because the growth rate can be estimated robustly from case reports \citep{mills2004transmissibility, ma2014estimating}.
-The growth rate $r$, representing the speed of an epidemic, and \RR, reprenting its strength,
-\bmb{this is nice but will people who don't know speed/strength defs get hung up? Is there a spreed/strength ms out there we can ref?}
-are linked by the generation-interval distribution \cite{wallinga2007generation}, where the generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee) \citep{svensson2007note}.
+The growth rate $r$ and the reproduction number \RR are linked by the generation-interval distribution \cite{wallinga2007generation}, where the generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee) \citep{svensson2007note}.
 
@@
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds.
-Researchers continue to base inferences about COVID-19 on both generation and serial intervals without clearly distinguishing between them (e.g., \cite{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}), sometimes explicitly conflating the definitions of the two intervals (e.g., \cite{anderson2020will,hellewell2020feasibility}).
-This lack of distinction \bmb{confusion?} is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
-However, these studies are not meant to be accused of their practices; until now, it has been a common practice use serial and generation intervals interchangeably.
+Researchers continue to base inferences about COVID-19 on both generation and serial intervals without clearly distinguishing between them (e.g., \cite{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}), and, in some cases, explicitly conflate the definitions of the two intervals (e.g., \cite{anderson2020will,hellewell2020feasibility}).
+This confusion is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
+These studies are exampels of many---indeed, it is a common practice to use the serial and generation intervals interchangeably.
 
@@
 It is well established that this renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
-However, the serial-interval distribution also describes a renewal process --- in this case, linking symptomatic cases based on their symptom onset dates \bmb{rephrase?
-``in this case, the creation of a new \emph{symptomatic} case based on a symptomatic case in the previous generation''.
-Is it important to talk about symptom onset dates at this point?}
+However, the serial-interval distribution also describes a renewal process --- in this case, the creation of a new \emph{symptomatic} case based on a symptomatic case in the previous generation.
 Since both renewal processes, based on either generation- or serial-interval distributions, describe the same underlying exponentially growing system, both should provide the same correct link between the reproduction number \RR and the epidemic growth rate $r$.
@@
 
-Here we show that, by correctly defining and calculating the ``forward'' serial-interval distribution (i.e., a distribution of serial intervals from a cohort of infectors that developed symptoms at the same time) that connects symptom onset dates, we can resolve this discrepancy;
-these intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
+Here we show that, by correctly defining and calculating the ``forward'' serial-interval distribution (i.e., a distribution of serial intervals from a cohort of infectors that developed symptoms at the same time) that connects symptom onset dates, we can resolve this discrepancy.
+These forward intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
 During an ongoing epidemic, all observed epidemiological delays (e.g., incubation period) between primary (e.g., infection) and secondary (e.g., symptom onset) events are subject to backward biases: when the incidence of primary events is increasing (or decreasing), we are more likely to observe shorter (respectively longer) intervals.
-Since realized serial intervals combine three distinct intervals (i.e., incubation period of the infector, incubation period of the infectee, and the generation interval between them), any of these intervals can be subject to backward biases depending on our perspective.
-\bmb{``depending on our perspective'' is a little unclear at this point but hopefully resolves quickly as reader moves forward}
 In particular, when we consider forward serial-interval distributions, the incubation periods of the infectors are subject to backward biases because we have to look backward in time from their symptom onset to infection.
 Therefore, the realized incubation period distributions of the infector and the infectee can differ dynamically, even if the intrinsic analogues of the same distributions are expected to be equivalent.
-\bmb{check to make sure I didn't screw this up?}
 
@@
 Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of \RR.
-For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro estimates based on aggregated serial-interval data underestimated \Ro by 50\%--60\%.
+For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro estimates based on aggregated serial-interval data underestimated \Ro by a factor of 2.0--2.6.
 We further lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the initial reproduction number during the early stages of an outbreak.
@@
 
-At the individual level, we can define the time distribution between a primary and a secondary event that we expect to observe (averaged across individual characteristics) for an infected individual --- we refer to this distribution as the \emph{intrinsic distribution}.
+At the individual level, we can define the time distribution between a primary and a secondary event that we expect to observe for a single infected individual by averaging across individual characteristics --- we refer to this distribution as the \emph{intrinsic distribution}.
 For example, the intrinsic incubation period distribution describes the expected time distribution from infection to symptom onset of an infected individual.
@@
 However, the intrinsic time distributions are not always equivalent to the corresponding realized time distributions at the population level (i.e., the distribution of time between actual primary and secondary events that occur during an epidemic; see \fref{diagram}).
-For example, an infectious contact results in infection only if the contacted individual is susceptible (and has not already been infected);
+For example, an infectious contact results in infection only if the contacted individual is susceptible (and has not already been infected) ---
 this is one mechanism that causes realized generation intervals (time between actual infection events) to differ from from the intrinsic generation intervals (time between infection and infectious contacts) \citep{park2020inferring}.
+In this example, the difference between intrinsic and realized time distributions can be attributed to the fact that the fraction of susceptible individuals is itself dynamic.
 
@@
 where $r$ is the exponential growth rate (and $\left[W(0) \psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
-Thus, even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.
+\swp{JSW: If this is what you mean by 'direct', it's still opaque!  How do you humans interpret this.  It's non trivial!}
+Thus, the mean backward interval will be always shorter than the mean forward interval as long as $r > 0$---even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.
 In general, the backward delay distribution will differ from the forward delay distribution (unless the disease is at equilibrium), even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
@@
 This framework allows us to understand changes in the realized serial intervals for any epidemic model and properly link serial-interval distributions with the renewal process.
+In particular, we see that the initial forward serial-interval distribution, $f_0(\tau)$, provides a correct link between the exponential growth rate $r$ and the initial serial reproduction number $\Rs(0)$ by substituting $j(t) \approx j(0) \exp(rt)$, $\Rs(t) \approx \Rs(0)$, and $f_{t-\tau}(\tau) \approx f_0(\tau)$:
+\begin{equation}
+\frac{1}{\Rs(0)} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau.
+\label{eq:Rforward0}
+\end{equation}
+\swp{OK to add this here? Do we needs a concluding sentence for this section?}
 
@@
 Here, we consider a specific example where changes in the reproduction number are driven by susceptible depletion: $\RR(t) = \Ro S(t)$, where \Ro represents the basic reproduction number.
-Although we do not consider non-pharmaceutical interventions explicitly, the effect of susceptible depletion is mathematically equivalent to the effect of interventions that reduce transmission rate.
+Although we do not consider non-pharmaceutical interventions or behavioral changes explicitly, the effect of susceptible depletion is mathematically equivalent to the effect of interventions that reduce transmission rate, and therefore \RR(t).
+\swp{JSW: Should say we do not consider NPI and/or behavior explicitly.
+I'm not sure that it's all exactly equivalent; because then R0 would vary and I don't see what the last part of this sentence really means anyway.
+Also, I think Sang Woo would argue this is true even when peaks/declines occur in the absence of susceptible depletion which is the most likely thing happening for COvid-19.
+Write this sentence carefully!}
 Then, the forward generation-interval for a cohort of individuals that were infected at time $\psymp$ follows \citep{champredon2015intrinsic}:
@@
 Analogous to the intrinsic generation-interval distribution, 
-forward serial-interval distributions describe the renewal process of infection based on symptom onset dates.
+forward serial-interval distributions describe the renewal process between symptomatic cases.
 Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to estimate the same value of \Ro for a given $r$ as the intrinsic generation-interval distribution (note, however, that the forward serial interval is not necessarily positive):
@@
 requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
-Since we have not yet made any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, this conclusion \bmb{what conclusion specifically?
-or do you mean this ``formulation'' is robust?
-Do you need to be more explicit about the inferential status of ``Therefore, we expect \ldots'' above?
-Is } is robust, regardless of whether presymptomatic transmission
-is possible or not.
-It is straightforward to see this relationship from \eref{jrenew} (by substituting $j(t) \approx j(0) \exp(rt)$ and $\Rs(t) \approx \Ro$);
-in Supplementary Materials, we provide a more detailed mathematical proof of this relationship.
+While it is straightforward to see this relationship from the renewal equation (see \eref{Rforward0}),
+we provide a more detailed mathematical proof of this relationship in Supplementary Materials.
+Since we do not make any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, \eref{Rforward} holds in general whether presymptomatic transmission is possible or not.
+\bmb{what conclusion specifically? or do you mean this ``formulation'' is robust? Do you need to be more explicit about the inferential status of ``Therefore, we expect \ldots'' above? Is }
+\swp{I tried to deal with the first one. Not sure what he means by the second question?}
 
@@
 For example, the Susceptible-Exposed-Infected-Recovered model, under the additional assumption that the incubation and exposed periods are equivalent (i.e.
-that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
-Everywhere else in this paper, however, we allow for presymptomatic transmission in the model in order to match the transmission dynamics of COVID-19.
+that onset of symptoms and infectiousness occur simultaneously), provides a special case.
+In this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
+Everywhere else in this paper, however, we do not assume that the incubation and exposed periods are equivalent---instead, we allow for presymptomatic transmission in the model in order to reflect the transmission dynamics of COVID-19.
 
@@
 Here, we use a bivariate lognormal distribution to model the joint probability distribution $h$ of intrinsic incubation periods and intrinsic generation intervals (in the renewal equation model, \eref{renewal}) while allowing for the possibility that they might be correlated.
-Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset, we generally expect the generation intervals to be positively correlated with the incubation period:
+Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset \citep{he2020temporal}, we generally expect the generation intervals to be positively correlated with the incubation period:
 that is, individuals who develop symptoms later are more likely to transmit later.
@@
 SD intrinsic incubation period & 2.4 days & \cite{lauer2020incubation} \\
-Mean intrinsic generation interval & 5 days & \cite{ferretti2020quantifying} \\
-SD intrinsic generation interval & 2 days & \cite{ferretti2020quantifying} \\
+Mean intrinsic generation interval & 5.0 days & \cite{ferretti2020quantifying} \\
+SD intrinsic generation interval & 1.9 days & \cite{ferretti2020quantifying} \\
 \hline
@@
   \textbf{Parameter values used for simulations.}
+The intrinsic incubation period distribution is parameterized using a log-normal distribution with log mean $\mu_I=1.62$ and log standard deviation $\sigma_I=0.42$.
 The intrinsic generation-interval distribution is parameterized using a log-normal distribution with log mean $\mu_G=1.54$ and log standard deviation $\sigma_G=0.37$.
-The intrinsic incubation period distribution is parameterized using a log-normal distribution with log mean $\mu_I=1.62$ and log standard deviation $\sigma_I=0.42$.
+Log mean and log standard deviations represent the mean and standard deviations of the underlying normal distributions, which are later exponentiated.
 The joint probability distribution is modeled using a bivariate log-normal distribution with correlations (on the log scale) $\rho=\{0, 0.25, 0.5, 0.75\}$.
-The intrinsic generation-interval and incubation period distributions are chosen to match characteristic of COVID-19 to illustrate realistic magnitudes of time-varying/perspective effects in the current pandemic.
+The intrinsic  incubation period and generation-interval distributions are chosen to match characteristic of COVID-19 to illustrate realistic magnitudes of time-varying/perspective effects in the current pandemic.
+\swp{JSW is confused because exp(1.54)=4.66 but that's because those are parameters of the not log of the mean but rather mean of the normal.
+I tried to clarify that.
+He also wanted me to add $\mu_I$ and $\sigma$ but I think that's confusing because it won't be $\exp(\mu)$...}
 }
@@
 We further address how the observed serial intervals, measured through contact tracing, are affected by right censoring during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial-interval data to estimate \Ro.
-Finally, we analyze serial-interval data from the COVID-19 epidemic in China under our framework.
+Finally, we analyze serial-interval data from the COVID-19 epidemic in China, outside Hubei province based on 468 transmission events reported between January 21--February 8, 2020, under our framework.
 
-\subsection{Realized serial-interval distributions}
+\subsection{Realized serial-interval distributions during the exponential growth phase}
 
@@
 
+\subsection{Realized serial-interval distributions during an ongoing epidemic}
+
 The initial forward serial-interval distribution captures the exponential growth phase of an epidemic.
@@
 
-When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms;
-for example, if we were to measure serial intervals on Day 8 as in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
+When an epidemic is ongoing, the observed serial intervals are subject to right-censoring because we cannot observe a serial interval if either an infector or an infectee has not yet developed symptoms.
+For example, if we were to measure serial intervals on Day 8 as in \fref{obsrR}A, we will only be able to observe the first 6 events (ID 1--6).
 \fref{obsrR}B demonstrates how the effect of right-censoring in the observed serial intervals translates to the underestimation of the basic reproduction number \Ro in our stochastic simulations (assuming $\Ro = 2.5$ as in \fref{epi}).
-Notably, even if we could observe, and aggregate, \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we would still underestimate the initial mean forward serial interval (and therefore \Ro), likely by a large amount, because the observed serial-interval distribution converges to the intrinsic serial-interval distribution (as the incubation periods and generation intervals will no longer be subject to backward biases);
-in fact, we would even underestimate the intrinsic value slightly due to contraction of the forward generation-interval distribution during the susceptible depletion phase (\fref{epi}C).
+Notably, even if we could observe and aggregate \emph{all} serial intervals across all transmission pairs after the epidemic has ended, we would still underestimate the initial mean forward serial interval (and therefore \Ro), likely by a large amount.
+The observed serial-interval distribution converges to the intrinsic serial-interval distribution as the incubation periods and generation intervals will no longer be subject to backward biases.
+In fact, we would even underestimate the intrinsic value slightly due to contraction of the forward generation-interval distribution during the susceptible depletion phase (\fref{epi}C).
 Therefore, aggregated distributions of serial intervals that have been collected throughout different periods of an epidemic must be interpreted with care.
@@
 These early cohort-averaged estimates of \Ro are unlikely to be affected by the right-censoring as we expect the degree of right-censoring to be low (\fref{du}A).
-Therefore, the original \Ro estimate of 1.32 (95\% CI 1.16-–1.48), which neglects the changes in the forward serial-interval distribution, underestimates \Ro by 50\%--60\%.
+Therefore, the original \Ro estimate of 1.32 (95\% CI 1.16-–1.48), which neglects the changes in the forward serial-interval distribution, underestimates \Ro by a factor of 2.0--2.6.
 This example demonstrates the danger of using the observed serial intervals to calculate the reproduction number without organizing serial intervals into cohorts.
@@
 
-Our results support the use of serial-interval distributions for calculating the initial \RR during the exponential growth phase,  
+Our results support the use of serial-interval distributions for calculating the \RR during the exponential growth phase,  
 but they also reveal gaps in current practices in incorporating serial-interval distributions into outbreak analyses.
 For example, \cite{thompson2019improved} recently emphasized the importance of using up-to-date serial-interval data for accurate estimation of time-varying reproduction numbers.
-However, our results show that if changes the forward serial interval through time are not accounted for, using up-to-date serial-interval data can actually exacerbate the underestimation of initial \RR.
+However, our results show that if observational biases in the forward serial interval through time are not accounted for, using up-to-date serial-interval data can actually exacerbate the underestimation of \RR in the initial growth phase of an outbreak.
 Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase, and potentially re-assess existing estimates of \RR.
@@
 
-Finally, we lay out a few practical principles for analyzing and interpreting serial-interval data.
-First, serial intervals should be cohorted based on the symptom onset date whenever possible.
+In closing, we lay out a few practical principles for analyzing and interpreting serial-interval data.
+First, serial intervals should be cohorted based on the symptom onset date of the infector (and not of the infectee) whenever possible.
 Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals differs from this expectation, and changes through time due to epidemic dynamics.

### 2020-10-04 serial.tex
still editing

@@
 Our study also underlines the fact that the serial-interval distribution depends not only on the generation-interval and incubation-period distributions, but also on their intrinsic correlations.
-Here, we use a bivariate lognormal distribution to capture their correlations phenomenologically but their true correlations will depend on viral load dynamics;
-\bmb{don't understand the connection between these two clauses?}
-nonetheless, we expect our conclusions about decreasing serial intervals of COVID-19 to be robust as individuals with longer incubation periods have a longer time window to transmit before symptom onset.
-Otherwise \bmb{??}, the impact of increasing backward incubation periods on the forward serial intervals are likely to be disease specific---for example, we show in Supplementary Materials that the initial forward serial-interval distribution can be equivalent to the intrinsic generation-interval distribution, regardless of the growth rate $r$, due to independence between the incubation period and time from symptom onset to transmission (assuming no transmission occurs during the incubation period).
-This \bmb{(?antecedent?)} implies that not considering this correlation can potentially bias the estimates of the intrinsic generation-interval distribution from the serial-interval distribution.
-% Previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the dynamical differences between the realized incubation periods of infectors (backward-looking) and those of infectees (forward looking) (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating}).
-Better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals are needed.
+Here, we use a bivariate lognormal distribution to capture their correlations phenomenologically and to show that realized serial intervals can decrease over time in the context of COVID-19.
+Although their true correlation will depend on viral load dynamics, we expect our conclusions about decreasing serial intervals of COVID-19 to be robust as individuals with longer incubation periods will generally have a longer time window to transmit before symptom onset.
+In general, the impact of increasing backward incubation periods on the forward serial intervals are likely to be disease specific---for example, we show in Supplementary Materials that the initial forward serial-interval distribution can be equivalent to the intrinsic generation-interval distribution, regardless of the growth rate $r$, due to independence between the incubation period and time from symptom onset to transmission and the lack of presymptomatic transmission.
+Future studies trying to model realized serial intervals should consider carefully the joint distribution between the generation intervals and incubation periods.
+\swp{Is this para OK?}
 
@@
 Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals differs from this expectation, and changes through time due to epidemic dynamics.
-Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they \bmb{??} can be subject to different censoring and epidemiological biases:
+Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided because the realized serial-interval distribution can be subject to different censoring and epidemiological biases:
 Even when \emph{all} realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR}).
@@
 we generalize these ideas and show that they apply to any other epidemiological distributions.
-Some studies during the early phases of the COVID-19 epidemics have tried to correct for the backward biases \bmb{refs?}, but changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
+Some studies during the early phases of the COVID-19 epidemics have tried to correct for the backward biases \citep{verity2020estimates}, but changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
 Cohorting epidemiological delays by the primary event time can help avoid backward biases (although censoring biases can still exist) as well as detect potential changes in the distribution.

### 2020-10-05 rR.tex
so close

--- 2020-04-29 rR.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-04-29 03:55:17
+% Created by tikzDevice version 0.12.3 on 2020-10-04 14:51:35
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] (  0.00,216.81) rectangle (289.08,433.62);
-\definecolor{drawColor}{RGB}{255,255,255}
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,216.81) rectangle (289.08,433.62);
-\end{scope}
-\begin{scope}
-\path[clip] ( 27.31,247.50) rectangle (283.58,410.96);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 27.31,247.50) rectangle (283.58,410.96);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 52.94,254.97) --
-	( 55.54,255.77) --
-	( 58.13,256.58) --
-	( 60.73,257.40) --
-	( 63.32,258.23) --
-	( 65.92,259.08) --
-	( 68.51,259.94) --
-	( 71.11,260.81) --
-	( 73.70,261.69) --
-	( 76.30,262.59) --
-	( 78.89,263.49) --
-	( 81.49,264.42) --
-	( 84.08,265.35) --
-	( 86.68,266.30) --
-	( 89.27,267.26) --
-	( 91.87,268.23) --
-	( 94.46,269.21) --
-	( 97.06,270.20) --
-	( 99.65,271.21) --
-	(102.25,272.23) --
-	(104.84,273.26) --
-	(107.44,274.30) --
-	(110.03,275.36) --
-	(112.63,276.43) --
-	(115.22,277.51) --
-	(117.82,278.61) --
-	(120.41,279.72) --
-	(123.01,280.84) --
-	(125.60,281.98) --
-	(128.20,283.13) --
-	(130.79,284.29) --
-	(133.39,285.46) --
-	(135.98,286.65) --
-	(138.58,287.85) --
-	(141.17,289.07) --
-	(143.77,290.31) --
-	(146.36,291.55) --
-	(148.96,292.82) --
-	(151.55,294.10) --
-	(154.15,295.40) --
-	(156.74,296.71) --
-	(159.34,298.04) --
-	(161.93,299.39) --
-	(164.53,300.75) --
-	(167.12,302.12) --
-	(169.72,303.51) --
-	(172.31,304.92) --
-	(174.91,306.34) --
-	(177.51,307.78) --
-	(180.10,309.24) --
-	(182.70,310.71) --
-	(185.29,312.21) --
-	(187.89,313.72) --
-	(190.48,315.26) --
-	(193.08,316.81) --
-	(195.67,318.38) --
-	(198.27,319.97) --
-	(200.86,321.57) --
-	(203.46,323.20) --
-	(206.05,324.84) --
-	(208.65,326.51) --
-	(211.24,328.19) --
-	(213.84,329.89) --
-	(216.43,331.62) --
-	(219.03,333.36) --
-	(221.62,335.12) --
-	(224.22,336.91) --
-	(226.81,338.72) --
-	(229.41,340.54) --
-	(232.00,342.39) --
-	(234.60,344.25) --
-	(237.19,346.14) --
-	(239.79,348.04) --
-	(242.38,349.97) --
-	(244.98,351.91) --
-	(247.57,353.87) --
-	(250.17,355.85) --
-	(252.76,357.85) --
-	(255.36,359.88) --
-	(257.95,361.92);
-\definecolor{drawColor}{RGB}{230,159,0}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.52) --
-	( 30.34,248.34) --
-	( 33.37,249.16) --
-	( 36.40,250.01) --
-	( 39.42,250.87) --
-	( 42.45,251.74) --
-	( 45.48,252.64) --
-	( 48.51,253.54) --
-	( 51.53,254.47) --
-	( 54.56,255.41) --
-	( 57.59,256.36) --
-	( 60.62,257.34) --
-	( 63.64,258.32) --
-	( 66.67,259.33) --
-	( 69.70,260.35) --
-	( 72.73,261.38) --
-	( 75.76,262.43) --
-	( 78.78,263.50) --
-	( 81.81,264.58) --
-	( 84.84,265.68) --
-	( 87.87,266.80) --
-	( 90.89,267.93) --
-	( 93.92,269.08) --
-	( 96.95,270.25) --
-	( 99.98,271.42) --
-	(103.00,272.61) --
-	(106.03,273.81) --
-	(109.06,275.03) --
-	(112.09,276.26) --
-	(115.11,277.51) --
-	(118.14,278.77) --
-	(121.17,280.06) --
-	(124.20,281.37) --
-	(127.22,282.71) --
-	(130.25,284.06) --
-	(133.28,285.44) --
-	(136.31,286.83) --
-	(139.34,288.23) --
-	(142.36,289.64) --
-	(145.39,291.08) --
-	(148.42,292.53) --
-	(151.45,294.01) --
-	(154.47,295.51) --
-	(157.50,297.03) --
-	(160.53,298.59) --
-	(163.56,300.17) --
-	(166.58,301.77) --
-	(169.61,303.39) --
-	(172.64,305.02) --
-	(175.67,306.68) --
-	(178.69,308.35) --
-	(181.72,310.04) --
-	(184.75,311.76) --
-	(187.78,313.51) --
-	(190.80,315.28) --
-	(193.83,317.09) --
-	(196.86,318.92) --
-	(199.89,320.80) --
-	(202.92,322.69) --
-	(205.94,324.62) --
-	(208.97,326.56) --
-	(212.00,328.54) --
-	(215.03,330.54) --
-	(218.05,332.56) --
-	(221.08,334.62) --
-	(224.11,336.70) --
-	(227.14,338.80) --
-	(230.16,340.94) --
-	(233.19,343.10) --
-	(236.22,345.29) --
-	(239.25,347.50) --
-	(242.27,349.75) --
-	(245.30,352.02) --
-	(248.33,354.31) --
-	(251.36,356.63) --
-	(254.39,358.98) --
-	(257.41,361.36) --
-	(260.44,363.76) --
-	(263.47,366.19) --
-	(266.50,368.65);
-\definecolor{drawColor}{RGB}{86,180,233}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.86,249.91) --
-	( 38.88,250.76) --
-	( 41.91,251.62) --
-	( 44.94,252.51) --
-	( 47.97,253.41) --
-	( 50.99,254.32) --
-	( 54.02,255.26) --
-	( 57.05,256.21) --
-	( 60.08,257.17) --
-	( 63.10,258.15) --
-	( 66.13,259.15) --
-	( 69.16,260.17) --
-	( 72.19,261.20) --
-	( 75.21,262.25) --
-	( 78.24,263.31) --
-	( 81.27,264.39) --
-	( 84.30,265.48) --
-	( 87.33,266.60) --
-	( 90.35,267.72) --
-	( 93.38,268.87) --
-	( 96.41,270.03) --
-	( 99.44,271.21) --
-	(102.46,272.41) --
-	(105.49,273.62) --
-	(108.52,274.84) --
-	(111.55,276.08) --
-	(114.57,277.32) --
-	(117.60,278.59) --
-	(120.63,279.86) --
-	(123.66,281.16) --
-	(126.68,282.48) --
-	(129.71,283.81) --
-	(132.74,285.17) --
-	(135.77,286.56) --
-	(138.79,287.97) --
-	(141.82,289.39) --
-	(144.85,290.83) --
-	(147.88,292.29) --
-	(150.91,293.76) --
-	(153.93,295.24) --
-	(156.96,296.75) --
-	(159.99,298.28) --
-	(163.02,299.84) --
-	(166.04,301.42) --
-	(169.07,303.03) --
-	(172.10,304.67) --
-	(175.13,306.33) --
-	(178.15,308.01) --
-	(181.18,309.70) --
-	(184.21,311.42) --
-	(187.24,313.15) --
-	(190.26,314.90) --
-	(193.29,316.68) --
-	(196.32,318.49) --
-	(199.35,320.33) --
-	(202.37,322.21) --
-	(205.40,324.12) --
-	(208.43,326.06) --
-	(211.46,328.03) --
-	(214.49,330.03) --
-	(217.51,332.06) --
-	(220.54,334.11) --
-	(223.57,336.19) --
-	(226.60,338.30) --
-	(229.62,340.44) --
-	(232.65,342.61) --
-	(235.68,344.80) --
-	(238.71,347.02) --
-	(241.73,349.28) --
-	(244.76,351.56) --
-	(247.79,353.87) --
-	(250.82,356.21) --
-	(253.84,358.58) --
-	(256.87,360.97) --
-	(259.90,363.40) --
-	(262.93,365.85) --
-	(265.95,368.33) --
-	(268.98,370.84) --
-	(272.01,373.38) --
-	(275.04,375.95);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.40,252.39) --
-	( 47.43,253.28) --
-	( 50.45,254.18) --
-	( 53.48,255.11) --
-	( 56.51,256.05) --
-	( 59.54,257.00) --
-	( 62.56,257.98) --
-	( 65.59,258.97) --
-	( 68.62,259.97) --
-	( 71.65,261.00) --
-	( 74.67,262.04) --
-	( 77.70,263.10) --
-	( 80.73,264.17) --
-	( 83.76,265.26) --
-	( 86.78,266.37) --
-	( 89.81,267.49) --
-	( 92.84,268.63) --
-	( 95.87,269.79) --
-	( 98.89,270.97) --
-	(101.92,272.16) --
-	(104.95,273.37) --
-	(107.98,274.60) --
-	(111.01,275.84) --
-	(114.03,277.11) --
-	(117.06,278.38) --
-	(120.09,279.67) --
-	(123.12,280.97) --
-	(126.14,282.28) --
-	(129.17,283.61) --
-	(132.20,284.96) --
-	(135.23,286.33) --
-	(138.25,287.72) --
-	(141.28,289.14) --
-	(144.31,290.58) --
-	(147.34,292.05) --
-	(150.36,293.53) --
-	(153.39,295.03) --
-	(156.42,296.54) --
-	(159.45,298.06) --
-	(162.48,299.61) --
-	(165.50,301.18) --
-	(168.53,302.77) --
-	(171.56,304.38) --
-	(174.59,306.03) --
-	(177.61,307.70) --
-	(180.64,309.41) --
-	(183.67,311.14) --
-	(186.70,312.89) --
-	(189.72,314.66) --
-	(192.75,316.45) --
-	(195.78,318.25) --
-	(198.81,320.09) --
-	(201.83,321.94) --
-	(204.86,323.83) --
-	(207.89,325.76) --
-	(210.92,327.71) --
-	(213.94,329.71) --
-	(216.97,331.74) --
-	(220.00,333.80) --
-	(223.03,335.89) --
-	(226.06,338.01) --
-	(229.08,340.16) --
-	(232.11,342.33) --
-	(235.14,344.54) --
-	(238.17,346.77) --
-	(241.19,349.04) --
-	(244.22,351.34) --
-	(247.25,353.67) --
-	(250.28,356.02) --
-	(253.30,358.41) --
-	(256.33,360.83) --
-	(259.36,363.28) --
-	(262.39,365.76) --
-	(265.41,368.27) --
-	(268.44,370.81) --
-	(271.47,373.38) --
-	(274.50,375.98) --
-	(277.52,378.61) --
-	(280.55,381.26) --
-	(283.58,383.95);
-\definecolor{fillColor}{RGB}{230,159,0}
-
-\path[fill=fillColor] ( 27.31,251.38) --
-	( 30.68,245.55) --
-	( 23.95,245.55) --
-	cycle;
-
-\path[fill=fillColor] ( 61.48,261.57) --
-	( 64.85,255.75) --
-	( 58.12,255.75) --
-	cycle;
-
-\path[fill=fillColor] ( 95.65,273.63) --
-	( 99.01,267.80) --
-	( 92.29,267.80) --
-	cycle;
-
-\path[fill=fillColor] (129.82,287.78) --
-	(133.18,281.95) --
-	(126.46,281.95) --
-	cycle;
-
-\path[fill=fillColor] (163.99,304.26) --
-	(167.35,298.43) --
-	(160.63,298.43) --
-	cycle;
-
-\path[fill=fillColor] (198.16,323.63) --
-	(201.52,317.81) --
-	(194.79,317.81) --
-	cycle;
-
-\path[fill=fillColor] (232.33,346.20) --
-	(235.69,340.37) --
-	(228.96,340.37) --
-	cycle;
-
-\path[fill=fillColor] (266.50,372.59) --
-	(269.86,366.77) --
-	(263.13,366.77) --
-	cycle;
-\definecolor{fillColor}{RGB}{86,180,233}
-
-\path[fill=fillColor] ( 33.36,247.39) --
-	( 38.35,247.39) --
-	( 38.35,252.38) --
-	( 33.36,252.38) --
-	cycle;
-
-\path[fill=fillColor] ( 67.53,258.02) --
-	( 72.52,258.02) --
-	( 72.52,263.01) --
-	( 67.53,263.01) --
-	cycle;
-
-\path[fill=fillColor] (101.70,270.61) --
-	(106.69,270.61) --
-	(106.69,275.61) --
-	(101.70,275.61) --
-	cycle;
-
-\path[fill=fillColor] (135.86,285.30) --
-	(140.86,285.30) --
-	(140.86,290.30) --
-	(135.86,290.30) --
-	cycle;
-
-\path[fill=fillColor] (170.03,302.36) --
-	(175.03,302.36) --
-	(175.03,307.36) --
-	(170.03,307.36) --
-	cycle;
-
-\path[fill=fillColor] (204.20,322.52) --
-	(209.20,322.52) --
-	(209.20,327.51) --
-	(204.20,327.51) --
-	cycle;
-
-\path[fill=fillColor] (238.37,345.90) --
-	(243.37,345.90) --
-	(243.37,350.89) --
-	(238.37,350.89) --
-	cycle;
-
-\path[fill=fillColor] (272.54,373.53) --
-	(277.54,373.53) --
-	(277.54,378.53) --
-	(272.54,378.53) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87,252.37) -- ( 47.93,252.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.83) -- ( 44.40,255.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,263.46) -- ( 82.10,263.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57,259.93) -- ( 78.57,266.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.59) -- (116.27,276.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,273.06) -- (112.74,280.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.84) -- (150.44,291.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.31) -- (146.90,295.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.66) -- (184.61,309.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.13) -- (181.07,313.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.57) -- (218.77,330.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,327.04) -- (215.24,334.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,355.17) -- (252.94,355.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,351.64) -- (249.41,358.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,384.02) -- (287.11,384.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,380.49) -- (283.58,387.55);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] ( 52.94,254.96) circle (  2.50);
-
-\path[fill=fillColor] ( 87.11,266.50) circle (  2.50);
-
-\path[fill=fillColor] (121.28,280.09) circle (  2.50);
-
-\path[fill=fillColor] (155.45,296.05) circle (  2.50);
-
-\path[fill=fillColor] (189.62,314.74) circle (  2.50);
-
-\path[fill=fillColor] (223.78,336.55) circle (  2.50);
-
-\path[fill=fillColor] (257.95,361.93) circle (  2.50);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.31,247.50) rectangle (283.58,410.96);
-\end{scope}
-\begin{scope}
 \path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
@@
 \path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,329.23) {Basic reproduction number $\mathcal R_0$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,244.47) {1};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,291.17) {2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,337.88) {3};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,384.58) {4};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,247.50) --
+	(319.81,247.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,294.20) --
+	(319.81,294.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,340.91) --
+	(319.81,340.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,387.61) --
+	(319.81,387.61);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (305.58,329.23) {Reproduction number ${\mathcal R}_{\textrm{\tiny intrinsic}}$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 60.52) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,170.08) {6};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 63.55) --
+	( 27.31, 63.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,173.11) --
+	( 27.31,173.11);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,112.42) {Mean interval (days)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86, 27.66) {0.0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86, 66.58) {0.2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,105.50) {0.4};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,144.42) {0.6};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,183.34) {0.8};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06, 30.69) --
+	(319.81, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06, 69.61) --
+	(319.81, 69.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,108.53) --
+	(319.81,108.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,147.45) --
+	(319.81,147.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,186.37) --
+	(319.81,186.37);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (298.73,112.42) {Squared coefficient of variation};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.31,419.03) {A};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (319.81,419.03) {B};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.31,202.22) {C};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (319.81,202.22) {D};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.31,247.50) rectangle (280.16,410.96);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 27.31,247.50) rectangle (280.16,410.96);
+\definecolor{drawColor}{RGB}{13,8,135}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.50) --
+	( 29.98,248.23) --
+	( 32.65,248.97) --
+	( 35.31,249.73) --
+	( 37.98,250.50) --
+	( 40.65,251.28) --
+	( 43.32,252.08) --
+	( 45.98,252.88) --
+	( 48.65,253.70) --
+	( 51.32,254.53) --
+	( 53.98,255.37) --
+	( 56.65,256.23) --
+	( 59.32,257.09) --
+	( 61.99,257.97) --
+	( 64.65,258.86) --
+	( 67.32,259.76) --
+	( 69.99,260.67) --
+	( 72.65,261.60) --
+	( 75.32,262.53) --
+	( 77.99,263.48) --
+	( 80.66,264.43) --
+	( 83.32,265.40) --
+	( 85.99,266.38) --
+	( 88.66,267.37) --
+	( 91.32,268.38) --
+	( 93.99,269.40) --
+	( 96.66,270.43) --
+	( 99.33,271.47) --
+	(101.99,272.54) --
+	(104.66,273.61) --
+	(107.33,274.70) --
+	(109.99,275.81) --
+	(112.66,276.93) --
+	(115.33,278.07) --
+	(118.00,279.22) --
+	(120.66,280.38) --
+	(123.33,281.55) --
+	(126.00,282.74) --
+	(128.66,283.95) --
+	(131.33,285.16) --
+	(134.00,286.40) --
+	(136.67,287.65) --
+	(139.33,288.91) --
+	(142.00,290.20) --
+	(144.67,291.50) --
+	(147.33,292.81) --
+	(150.00,294.15) --
+	(152.67,295.51) --
+	(155.34,296.88) --
+	(158.00,298.27) --
+	(160.67,299.67) --
+	(163.34,301.09) --
+	(166.00,302.53) --
+	(168.67,303.98) --
+	(171.34,305.45) --
+	(174.01,306.94) --
+	(176.67,308.45) --
+	(179.34,309.97) --
+	(182.01,311.51) --
+	(184.67,313.08) --
+	(187.34,314.67) --
+	(190.01,316.27) --
+	(192.68,317.90) --
+	(195.34,319.55) --
+	(198.01,321.23) --
+	(200.68,322.92) --
+	(203.34,324.64) --
+	(206.01,326.37) --
+	(208.68,328.13) --
+	(211.35,329.90) --
+	(214.01,331.70) --
+	(216.68,333.51) --
+	(219.35,335.35) --
+	(222.01,337.21) --
+	(224.68,339.08) --
+	(227.35,340.98) --
+	(230.02,342.90) --
+	(232.68,344.83) --
+	(235.35,346.79) --
+	(238.02,348.77);
+\definecolor{drawColor}{RGB}{126,3,168}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 61.03,257.69) --
+	( 63.69,258.56) --
+	( 66.36,259.45) --
+	( 69.03,260.35) --
+	( 71.69,261.26) --
+	( 74.36,262.19) --
+	( 77.03,263.13) --
+	( 79.70,264.08) --
+	( 82.36,265.05) --
+	( 85.03,266.03) --
+	( 87.70,267.03) --
+	( 90.36,268.04) --
+	( 93.03,269.06) --
+	( 95.70,270.09) --
+	( 98.37,271.14) --
+	(101.03,272.21) --
+	(103.70,273.28) --
+	(106.37,274.37) --
+	(109.03,275.47) --
+	(111.70,276.58) --
+	(114.37,277.71) --
+	(117.04,278.84) --
+	(119.70,279.99) --
+	(122.37,281.16) --
+	(125.04,282.34) --
+	(127.70,283.53) --
+	(130.37,284.74) --
+	(133.04,285.97) --
+	(135.71,287.21) --
+	(138.37,288.47) --
+	(141.04,289.75) --
+	(143.71,291.04) --
+	(146.37,292.36) --
+	(149.04,293.69) --
+	(151.71,295.03) --
+	(154.38,296.39) --
+	(157.04,297.76) --
+	(159.71,299.15) --
+	(162.38,300.55) --
+	(165.04,301.97) --
+	(167.71,303.41) --
+	(170.38,304.87) --
+	(173.05,306.34) --
+	(175.71,307.84) --
+	(178.38,309.35) --
+	(181.05,310.89) --
+	(183.71,312.45) --
+	(186.38,314.03) --
+	(189.05,315.62) --
+	(191.72,317.24) --
+	(194.38,318.87) --
+	(197.05,320.53) --
+	(199.72,322.19) --
+	(202.38,323.88) --
+	(205.05,325.59) --
+	(207.72,327.32) --
+	(210.39,329.07) --
+	(213.05,330.84) --
+	(215.72,332.63) --
+	(218.39,334.45) --
+	(221.05,336.29) --
+	(223.72,338.15) --
+	(226.39,340.04) --
+	(229.06,341.96) --
+	(231.72,343.90) --
+	(234.39,345.87) --
+	(237.06,347.86) --
+	(239.72,349.87) --
+	(242.39,351.90) --
+	(245.06,353.96) --
+	(247.73,356.04) --
+	(250.39,358.15) --
+	(253.06,360.28) --
+	(255.73,362.43) --
+	(258.39,364.60) --
+	(261.06,366.80) --
+	(263.73,369.02) --
+	(266.40,371.27) --
+	(269.06,373.53) --
+	(271.73,375.82);
+\definecolor{drawColor}{RGB}{204,70,120}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 52.60,254.98) --
+	( 55.26,255.81) --
+	( 57.93,256.66) --
+	( 60.60,257.53) --
+	( 63.27,258.41) --
+	( 65.93,259.30) --
+	( 68.60,260.20) --
+	( 71.27,261.12) --
+	( 73.93,262.04) --
+	( 76.60,262.99) --
+	( 79.27,263.94) --
+	( 81.94,264.91) --
+	( 84.60,265.89) --
+	( 87.27,266.89) --
+	( 89.94,267.90) --
+	( 92.60,268.92) --
+	( 95.27,269.95) --
+	( 97.94,271.00) --
+	(100.61,272.05) --
+	(103.27,273.12) --
+	(105.94,274.20) --
+	(108.61,275.30) --
+	(111.27,276.40) --
+	(113.94,277.52) --
+	(116.61,278.66) --
+	(119.28,279.81) --
+	(121.94,280.97) --
+	(124.61,282.15) --
+	(127.28,283.34) --
+	(129.94,284.55) --
+	(132.61,285.78) --
+	(135.28,287.03) --
+	(137.95,288.29) --
+	(140.61,289.56) --
+	(143.28,290.85) --
+	(145.95,292.16) --
+	(148.62,293.48) --
+	(151.28,294.81) --
+	(153.95,296.16) --
+	(156.62,297.52) --
+	(159.28,298.90) --
+	(161.95,300.30) --
+	(164.62,301.72) --
+	(167.29,303.16) --
+	(169.95,304.61) --
+	(172.62,306.09) --
+	(175.29,307.58) --
+	(177.95,309.10) --
+	(180.62,310.64) --
+	(183.29,312.20) --
+	(185.96,313.77) --
+	(188.62,315.36) --
+	(191.29,316.96) --
+	(193.96,318.59) --
+	(196.62,320.23) --
+	(199.29,321.89) --
+	(201.96,323.58) --
+	(204.63,325.28) --
+	(207.29,327.01) --
+	(209.96,328.76) --
+	(212.63,330.54) --
+	(215.29,332.33) --
+	(217.96,334.16) --
+	(220.63,336.01) --
+	(223.30,337.88) --
+	(225.96,339.78) --
+	(228.63,341.70) --
+	(231.30,343.64) --
+	(233.96,345.60) --
+	(236.63,347.59) --
+	(239.30,349.60) --
+	(241.97,351.63) --
+	(244.63,353.69) --
+	(247.30,355.76) --
+	(249.97,357.86) --
+	(252.63,359.99) --
+	(255.30,362.13) --
+	(257.97,364.30) --
+	(260.64,366.49) --
+	(263.30,368.71);
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.17,252.37) --
+	( 46.84,253.17) --
+	( 49.50,253.99) --
+	( 52.17,254.82) --
+	( 54.84,255.66) --
+	( 57.51,256.51) --
+	( 60.17,257.37) --
+	( 62.84,258.25) --
+	( 65.51,259.14) --
+	( 68.17,260.05) --
+	( 70.84,260.97) --
+	( 73.51,261.90) --
+	( 76.18,262.84) --
+	( 78.84,263.79) --
+	( 81.51,264.76) --
+	( 84.18,265.74) --
+	( 86.84,266.74) --
+	( 89.51,267.74) --
+	( 92.18,268.76) --
+	( 94.85,269.79) --
+	( 97.51,270.83) --
+	(100.18,271.88) --
+	(102.85,272.95) --
+	(105.51,274.03) --
+	(108.18,275.12) --
+	(110.85,276.23) --
+	(113.52,277.35) --
+	(116.18,278.49) --
+	(118.85,279.64) --
+	(121.52,280.80) --
+	(124.18,281.98) --
+	(126.85,283.18) --
+	(129.52,284.39) --
+	(132.19,285.61) --
+	(134.85,286.85) --
+	(137.52,288.09) --
+	(140.19,289.35) --
+	(142.85,290.63) --
+	(145.52,291.92) --
+	(148.19,293.22) --
+	(150.86,294.54) --
+	(153.52,295.88) --
+	(156.19,297.23) --
+	(158.86,298.61) --
+	(161.52,300.00) --
+	(164.19,301.41) --
+	(166.86,302.85) --
+	(169.53,304.30) --
+	(172.19,305.78) --
+	(174.86,307.28) --
+	(177.53,308.79) --
+	(180.19,310.32) --
+	(182.86,311.86) --
+	(185.53,313.42) --
+	(188.20,315.01) --
+	(190.86,316.61) --
+	(193.53,318.23) --
+	(196.20,319.88) --
+	(198.86,321.54) --
+	(201.53,323.23) --
+	(204.20,324.94) --
+	(206.87,326.68) --
+	(209.53,328.43) --
+	(212.20,330.22) --
+	(214.87,332.02) --
+	(217.53,333.85) --
+	(220.20,335.71) --
+	(222.87,337.58) --
+	(225.54,339.48) --
+	(228.20,341.40) --
+	(230.87,343.34) --
+	(233.54,345.30) --
+	(236.20,347.28) --
+	(238.87,349.29) --
+	(241.54,351.32) --
+	(244.21,353.37) --
+	(246.87,355.45) --
+	(249.54,357.54) --
+	(252.21,359.66) --
+	(254.87,361.80);
+\definecolor{drawColor}{RGB}{216,224,30}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 35.74,249.88) --
+	( 38.41,250.65) --
+	( 41.08,251.43) --
+	( 43.74,252.22) --
+	( 46.41,253.03) --
+	( 49.08,253.84) --
+	( 51.74,254.67) --
+	( 54.41,255.51) --
+	( 57.08,256.37) --
+	( 59.75,257.24) --
+	( 62.41,258.11) --
+	( 65.08,259.01) --
+	( 67.75,259.91) --
+	( 70.41,260.83) --
+	( 73.08,261.76) --
+	( 75.75,262.70) --
+	( 78.42,263.65) --
+	( 81.08,264.62) --
+	( 83.75,265.60) --
+	( 86.42,266.59) --
+	( 89.08,267.59) --
+	( 91.75,268.60) --
+	( 94.42,269.63) --
+	( 97.09,270.67) --
+	( 99.75,271.72) --
+	(102.42,272.79) --
+	(105.09,273.87) --
+	(107.75,274.96) --
+	(110.42,276.07) --
+	(113.09,277.19) --
+	(115.76,278.32) --
+	(118.42,279.47) --
+	(121.09,280.64) --
+	(123.76,281.81) --
+	(126.42,283.00) --
+	(129.09,284.20) --
+	(131.76,285.41) --
+	(134.43,286.63) --
+	(137.09,287.87) --
+	(139.76,289.12) --
+	(142.43,290.39) --
+	(145.09,291.67) --
+	(147.76,292.97) --
+	(150.43,294.29) --
+	(153.10,295.63) --
+	(155.76,296.98) --
+	(158.43,298.36) --
+	(161.10,299.76) --
+	(163.76,301.18) --
+	(166.43,302.62) --
+	(169.10,304.07) --
+	(171.77,305.54) --
+	(174.43,307.02) --
+	(177.10,308.53) --
+	(179.77,310.05) --
+	(182.43,311.59) --
+	(185.10,313.15) --
+	(187.77,314.73) --
+	(190.44,316.33) --
+	(193.10,317.95) --
+	(195.77,319.60) --
+	(198.44,321.27) --
+	(201.10,322.96) --
+	(203.77,324.67) --
+	(206.44,326.41) --
+	(209.11,328.16) --
+	(211.77,329.94) --
+	(214.44,331.74) --
+	(217.11,333.57) --
+	(219.77,335.41) --
+	(222.44,337.27) --
+	(225.11,339.16) --
+	(227.78,341.07) --
+	(230.44,342.99) --
+	(233.11,344.94) --
+	(235.78,346.91) --
+	(238.44,348.91) --
+	(241.11,350.92) --
+	(243.78,352.95) --
+	(246.45,355.01);
+\definecolor{fillColor}{RGB}{126,3,168}
+
+\path[fill=fillColor] ( 61.03,261.57) --
+	( 64.39,255.75) --
+	( 57.66,255.75) --
+	cycle;
+
+\path[fill=fillColor] (103.17,276.95) --
+	(106.53,271.12) --
+	( 99.80,271.12) --
+	cycle;
+
+\path[fill=fillColor] (145.31,295.71) --
+	(148.67,289.89) --
+	(141.94,289.89) --
+	cycle;
+
+\path[fill=fillColor] (187.45,318.55) --
+	(190.81,312.72) --
+	(184.08,312.72) --
+	cycle;
+
+\path[fill=fillColor] (229.59,346.23) --
+	(232.95,340.41) --
+	(226.23,340.41) --
+	cycle;
+
+\path[fill=fillColor] (271.73,379.71) --
+	(275.09,373.88) --
+	(268.37,373.88) --
+	cycle;
+\definecolor{fillColor}{RGB}{204,70,120}
+
+\path[fill=fillColor] ( 50.10,252.48) --
+	( 55.10,252.48) --
+	( 55.10,257.47) --
+	( 50.10,257.47) --
+	cycle;
+
+\path[fill=fillColor] ( 92.24,267.25) --
+	( 97.24,267.25) --
+	( 97.24,272.24) --
+	( 92.24,272.24) --
+	cycle;
+
+\path[fill=fillColor] (134.38,285.28) --
+	(139.38,285.28) --
+	(139.38,290.28) --
+	(134.38,290.28) --
+	cycle;
+
+\path[fill=fillColor] (176.52,307.22) --
+	(181.52,307.22) --
+	(181.52,312.21) --
+	(176.52,312.21) --
+	cycle;
+
+\path[fill=fillColor] (218.66,333.88) --
+	(223.66,333.88) --
+	(223.66,338.88) --
+	(218.66,338.88) --
+	cycle;
+
+\path[fill=fillColor] (260.80,366.21) --
+	(265.80,366.21) --
+	(265.80,371.20) --
+	(260.80,371.20) --
+	cycle;
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.64,252.37) -- ( 47.70,252.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.17,248.84) -- ( 44.17,255.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 82.78,266.54) -- ( 89.84,266.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.31,263.01) -- ( 86.31,270.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.92,283.90) -- (131.98,283.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.45,280.37) -- (128.45,287.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.06,304.89) -- (174.12,304.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.59,301.36) -- (170.59,308.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.20,330.58) -- (216.27,330.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.73,327.04) -- (212.73,334.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.34,361.80) -- (258.41,361.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.87,358.27) -- (254.87,365.33);
+\definecolor{drawColor}{RGB}{216,224,30}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.24,247.39) rectangle ( 38.24,252.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.24,247.39) -- ( 38.24,252.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.24,252.38) -- ( 38.24,247.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.38,260.97) rectangle ( 80.38,265.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.38,260.97) -- ( 80.38,265.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.38,265.96) -- ( 80.38,260.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.53,277.67) rectangle (122.52,282.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.53,277.67) -- (122.52,282.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.53,282.67) -- (122.52,277.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.67,297.83) rectangle (164.66,302.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.67,297.83) -- (164.66,302.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.67,302.82) -- (164.66,297.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.81,322.52) rectangle (206.80,327.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.81,322.52) -- (206.80,327.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.81,327.51) -- (206.80,322.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.95,352.51) rectangle (248.94,357.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.95,352.51) -- (248.94,357.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.95,357.51) -- (248.94,352.51);
+\definecolor{fillColor}{RGB}{13,8,135}
+
+\path[fill=fillColor] ( 27.31,247.50) circle (  2.50);
+
+\path[fill=fillColor] ( 69.45,260.49) circle (  2.50);
+
+\path[fill=fillColor] (111.60,276.48) circle (  2.50);
+
+\path[fill=fillColor] (153.74,296.05) circle (  2.50);
+
+\path[fill=fillColor] (195.88,319.89) circle (  2.50);
+
+\path[fill=fillColor] (238.02,348.77) circle (  2.50);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.31,247.50) rectangle (280.16,410.96);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 36.66,389.03) rectangle ( 51.11,403.48);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{13,8,135}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 38.10,396.25) -- ( 49.66,396.25);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{13,8,135}
+
+\path[fill=fillColor] ( 43.88,396.25) circle (  2.50);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 36.66,374.57) rectangle ( 51.11,389.03);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{126,3,168}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 38.10,381.80) -- ( 49.66,381.80);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{126,3,168}
+
+\path[fill=fillColor] ( 43.88,385.68) --
+	( 47.25,379.86) --
+	( 40.52,379.86) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 36.66,360.12) rectangle ( 51.11,374.57);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{204,70,120}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 38.10,367.35) -- ( 49.66,367.35);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{204,70,120}
+
+\path[fill=fillColor] ( 41.38,364.85) --
+	( 46.38,364.85) --
+	( 46.38,369.84) --
+	( 41.38,369.84) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 36.66,345.67) rectangle ( 51.11,360.12);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 38.10,352.89) -- ( 49.66,352.89);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.35,352.89) -- ( 47.41,352.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.88,349.36) -- ( 43.88,356.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 36.66,331.21) rectangle ( 51.11,345.67);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{216,224,30}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 38.10,338.44) -- ( 49.66,338.44);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{216,224,30}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.38,335.94) rectangle ( 46.38,340.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.38,335.94) -- ( 46.38,340.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.38,340.94) -- ( 46.38,335.94);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.61,393.22) {Intrinsic generation interval};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.61,378.77) {Forward serial interval ($\rho=0.75$)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.61,364.32) {Forward serial interval ($\rho=0.5$)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.61,349.86) {Forward serial interval ($\rho=0.25$)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.61,335.41) {Forward serial interval ($\rho=0$)};
+\end{scope}
+\begin{scope}
+\path[clip] (319.81,247.50) rectangle (572.66,410.96);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (319.81,247.50) rectangle (572.66,410.96);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (319.81,247.64) --
+	(323.02,248.49) --
+	(326.22,249.36) --
+	(329.42,250.25) --
+	(332.62,251.16) --
+	(335.82,252.09) --
+	(339.02,253.03) --
+	(342.22,254.00) --
+	(345.42,254.99) --
+	(348.62,255.99) --
+	(351.82,257.01) --
+	(355.02,258.06) --
+	(358.22,259.12) --
+	(361.42,260.20) --
+	(364.62,261.30) --
+	(367.82,262.42) --
+	(371.02,263.56) --
+	(374.22,264.72) --
+	(377.43,265.90) --
+	(380.63,267.10) --
+	(383.83,268.32) --
+	(387.03,269.55) --
+	(390.23,270.81) --
+	(393.43,272.08) --
+	(396.63,273.37) --
+	(399.83,274.68) --
+	(403.03,276.01) --
+	(406.23,277.36) --
+	(409.43,278.74) --
+	(412.63,280.13) --
+	(415.83,281.55) --
+	(419.03,282.99) --
+	(422.23,284.44) --
+	(425.43,285.91) --
+	(428.63,287.40) --
+	(431.83,288.91) --
+	(435.04,290.45) --
+	(438.24,292.02) --
+	(441.44,293.61) --
+	(444.64,295.23) --
+	(447.84,296.88) --
+	(451.04,298.55) --
+	(454.24,300.24) --
+	(457.44,301.95) --
+	(460.64,303.68) --
+	(463.84,305.44) --
+	(467.04,307.23) --
+	(470.24,309.04) --
+	(473.44,310.89) --
+	(476.64,312.76) --
+	(479.84,314.68) --
+	(483.04,316.62) --
+	(486.24,318.59) --
+	(489.45,320.58) --
+	(492.65,322.60) --
+	(495.85,324.66) --
+	(499.05,326.74) --
+	(502.25,328.85) --
+	(505.45,330.99) --
+	(508.65,333.17) --
+	(511.85,335.39) --
+	(515.05,337.63) --
+	(518.25,339.91) --
+	(521.45,342.22) --
+	(524.65,344.56) --
+	(527.85,346.93) --
+	(531.05,349.33) --
+	(534.25,351.76) --
+	(537.45,354.22) --
+	(540.65,356.72) --
+	(543.85,359.24) --
+	(547.06,361.80) --
+	(550.26,364.38) --
+	(553.46,367.00) --
+	(556.66,369.66) --
+	(559.86,372.34) --
+	(563.06,375.05) --
+	(566.26,377.80) --
+	(569.46,380.57) --
+	(572.66,383.38);
+\definecolor{drawColor}{RGB}{109,109,109}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.02,248.37) --
+	(326.22,249.29) --
+	(329.42,250.21) --
+	(332.62,251.14) --
+	(335.82,252.09) --
+	(339.02,253.04) --
+	(342.22,254.01) --
+	(345.42,254.98) --
+	(348.62,255.97) --
+	(351.82,256.97) --
+	(355.02,257.98) --
+	(358.22,259.00) --
+	(361.42,260.04) --
+	(364.62,261.08) --
+	(367.82,262.13) --
+	(371.02,263.20) --
+	(374.22,264.27) --
+	(377.43,265.36) --
+	(380.63,266.46) --
+	(383.83,267.57) --
+	(387.03,268.69) --
+	(390.23,269.82) --
+	(393.43,270.96) --
+	(396.63,272.12) --
+	(399.83,273.28) --
+	(403.03,274.45) --
+	(406.23,275.64) --
+	(409.43,276.84) --
+	(412.63,278.04) --
+	(415.83,279.26) --
+	(419.03,280.49) --
+	(422.23,281.73) --
+	(425.43,282.98) --
+	(428.63,284.25) --
+	(431.83,285.52) --
+	(435.04,286.81) --
+	(438.24,288.10) --
+	(441.44,289.40) --
+	(444.64,290.71) --
+	(447.84,292.02) --
+	(451.04,293.35) --
+	(454.24,294.69) --
+	(457.44,296.04) --
+	(460.64,297.40) --
+	(463.84,298.77) --
+	(467.04,300.15) --
+	(470.24,301.54) --
+	(473.44,302.93) --
+	(476.64,304.32) --
+	(479.84,305.72) --
+	(483.04,307.12) --
+	(486.24,308.54) --
+	(489.45,309.96) --
+	(492.65,311.39) --
+	(495.85,312.82) --
+	(499.05,314.26) --
+	(502.25,315.71) --
+	(505.45,317.16) --
+	(508.65,318.61) --
+	(511.85,320.07) --
+	(515.05,321.53) --
+	(518.25,322.99) --
+	(521.45,324.45) --
+	(524.65,325.93) --
+	(527.85,327.40) --
+	(531.05,328.89) --
+	(534.25,330.37) --
+	(537.45,331.86) --
+	(540.65,333.36) --
+	(543.85,334.86) --
+	(547.06,336.37) --
+	(550.26,337.88) --
+	(553.46,339.39) --
+	(556.66,340.91) --
+	(559.86,342.43) --
+	(563.06,343.96) --
+	(566.26,345.49) --
+	(569.46,347.03) --
+	(572.66,348.57);
+\definecolor{drawColor}{RGB}{149,149,149}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.02,248.30) --
+	(326.22,249.24) --
+	(329.42,250.18) --
+	(332.62,251.12) --
+	(335.82,252.08) --
+	(339.02,253.04) --
+	(342.22,254.00) --
+	(345.42,254.98) --
+	(348.62,255.96) --
+	(351.82,256.94) --
+	(355.02,257.93) --
+	(358.22,258.93) --
+	(361.42,259.94) --
+	(364.62,260.95) --
+	(367.82,261.97) --
+	(371.02,262.99) --
+	(374.22,264.02) --
+	(377.43,265.05) --
+	(380.63,266.09) --
+	(383.83,267.14) --
+	(387.03,268.20) --
+	(390.23,269.26) --
+	(393.43,270.34) --
+	(396.63,271.42) --
+	(399.83,272.50) --
+	(403.03,273.59) --
+	(406.23,274.68) --
+	(409.43,275.78) --
+	(412.63,276.87) --
+	(415.83,277.98) --
+	(419.03,279.10) --
+	(422.23,280.22) --
+	(425.43,281.36) --
+	(428.63,282.50) --
+	(431.83,283.64) --
+	(435.04,284.78) --
+	(438.24,285.92) --
+	(441.44,287.06) --
+	(444.64,288.19) --
+	(447.84,289.31) --
+	(451.04,290.45) --
+	(454.24,291.59) --
+	(457.44,292.74) --
+	(460.64,293.89) --
+	(463.84,295.05) --
+	(467.04,296.19) --
+	(470.24,297.34) --
+	(473.44,298.47) --
+	(476.64,299.59) --
+	(479.84,300.69) --
+	(483.04,301.79) --
+	(486.24,302.89) --
+	(489.45,303.98) --
+	(492.65,305.07) --
+	(495.85,306.15) --
+	(499.05,307.23) --
+	(502.25,308.29) --
+	(505.45,309.34) --
+	(508.65,310.37) --
+	(511.85,311.39) --
+	(515.05,312.39) --
+	(518.25,313.37) --
+	(521.45,314.35) --
+	(524.65,315.32) --
+	(527.85,316.28) --
+	(531.05,317.22) --
+	(534.25,318.16) --
+	(537.45,319.09) --
+	(540.65,320.00) --
+	(543.85,320.91) --
+	(547.06,321.80) --
+	(550.26,322.67) --
+	(553.46,323.54) --
+	(556.66,324.40) --
+	(559.86,325.24) --
+	(563.06,326.07) --
+	(566.26,326.89) --
+	(569.46,327.70) --
+	(572.66,328.50);
+\definecolor{drawColor}{gray}{0.70}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (323.02,248.24) --
+	(326.22,249.19) --
+	(329.42,250.15) --
+	(332.62,251.11) --
+	(335.82,252.07) --
+	(339.02,253.03) --
+	(342.22,254.00) --
+	(345.42,254.96) --
+	(348.62,255.93) --
+	(351.82,256.91) --
+	(355.02,257.88) --
+	(358.22,258.86) --
+	(361.42,259.84) --
+	(364.62,260.82) --
+	(367.82,261.80) --
+	(371.02,262.78) --
+	(374.22,263.77) --
+	(377.43,264.75) --
+	(380.63,265.74) --
+	(383.83,266.73) --
+	(387.03,267.73) --
+	(390.23,268.73) --
+	(393.43,269.73) --
+	(396.63,270.74) --
+	(399.83,271.75) --
+	(403.03,272.76) --
+	(406.23,273.76) --
+	(409.43,274.76) --
+	(412.63,275.76) --
+	(415.83,276.76) --
+	(419.03,277.77) --
+	(422.23,278.79) --
+	(425.43,279.81) --
+	(428.63,280.83) --
+	(431.83,281.84) --
+	(435.04,282.85) --
+	(438.24,283.85) --
+	(441.44,284.83) --
+	(444.64,285.80) --
+	(447.84,286.75) --
+	(451.04,287.70) --
+	(454.24,288.67) --
+	(457.44,289.63) --
+	(460.64,290.59) --
+	(463.84,291.54) --
+	(467.04,292.47) --
+	(470.24,293.39) --
+	(473.44,294.29) --
+	(476.64,295.16) --
+	(479.84,295.99) --
+	(483.04,296.81) --
+	(486.24,297.61) --
+	(489.45,298.41) --
+	(492.65,299.19) --
+	(495.85,299.95) --
+	(499.05,300.69) --
+	(502.25,301.40) --
+	(505.45,302.09) --
+	(508.65,302.75) --
+	(511.85,303.37) --
+	(515.05,303.96) --
+	(518.25,304.52) --
+	(521.45,305.06) --
+	(524.65,305.58) --
+	(527.85,306.08) --
+	(531.05,306.56) --
+	(534.25,307.01) --
+	(537.45,307.43) --
+	(540.65,307.83) --
+	(543.85,308.21) --
+	(547.06,308.56) --
+	(550.26,308.88) --
+	(553.46,309.18) --
+	(556.66,309.45) --
+	(559.86,309.69) --
+	(563.06,309.91) --
+	(566.26,310.11) --
+	(569.46,310.28) --
+	(572.66,310.43);
+\definecolor{drawColor}{gray}{0.80}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (323.02,248.18) --
+	(326.22,249.15) --
+	(329.42,250.12) --
+	(332.62,251.09) --
+	(335.82,252.06) --
+	(339.02,253.02) --
+	(342.22,253.99) --
+	(345.42,254.95) --
+	(348.62,255.91) --
+	(351.82,256.87) --
+	(355.02,257.82) --
+	(358.22,258.78) --
+	(361.42,259.73) --
+	(364.62,260.68) --
+	(367.82,261.63) --
+	(371.02,262.58) --
+	(374.22,263.52) --
+	(377.43,264.45) --
+	(380.63,265.39) --
+	(383.83,266.33) --
+	(387.03,267.27) --
+	(390.23,268.21) --
+	(393.43,269.15) --
+	(396.63,270.09) --
+	(399.83,271.03) --
+	(403.03,271.96) --
+	(406.23,272.88) --
+	(409.43,273.79) --
+	(412.63,274.70) --
+	(415.83,275.60) --
+	(419.03,276.51) --
+	(422.23,277.43) --
+	(425.43,278.34) --
+	(428.63,279.25) --
+	(431.83,280.15) --
+	(435.04,281.03) --
+	(438.24,281.90) --
+	(441.44,282.74) --
+	(444.64,283.56) --
+	(447.84,284.35) --
+	(451.04,285.14) --
+	(454.24,285.93) --
+	(457.44,286.72) --
+	(460.64,287.50) --
+	(463.84,288.26) --
+	(467.04,289.01) --
+	(470.24,289.72) --
+	(473.44,290.40) --
+	(476.64,291.04) --
+	(479.84,291.64) --
+	(483.04,292.21) --
+	(486.24,292.76) --
+	(489.45,293.29) --
+	(492.65,293.79) --
+	(495.85,294.27) --
+	(499.05,294.72) --
+	(502.25,295.13) --
+	(505.45,295.51) --
+	(508.65,295.84) --
+	(511.85,296.12) --
+	(515.05,296.36) --
+	(518.25,296.57) --
+	(521.45,296.74) --
+	(524.65,296.88) --
+	(527.85,296.99) --
+	(531.05,297.06) --
+	(534.25,297.10) --
+	(537.45,297.11) --
+	(540.65,297.08) --
+	(543.85,297.02) --
+	(547.06,296.91) --
+	(550.26,296.77) --
+	(553.46,296.60) --
+	(556.66,296.39) --
+	(559.86,296.14) --
+	(563.06,295.86) --
+	(566.26,295.54) --
+	(569.46,295.19) --
+	(572.66,294.80);
+\definecolor{fillColor}{RGB}{109,109,109}
+
+\path[fill=fillColor] (319.81,251.38) --
+	(323.18,245.55) --
+	(316.45,245.55) --
+	cycle;
+
+\path[fill=fillColor] (328.24,253.76) --
+	(331.61,247.94) --
+	(324.88,247.94) --
+	cycle;
+
+\path[fill=fillColor] (336.67,256.22) --
+	(340.03,250.40) --
+	(333.31,250.40) --
+	cycle;
+
+\path[fill=fillColor] (345.10,258.76) --
+	(348.46,252.93) --
+	(341.74,252.93) --
+	cycle;
+
+\path[fill=fillColor] (353.53,261.38) --
+	(356.89,255.55) --
+	(350.16,255.55) --
+	cycle;
+
+\path[fill=fillColor] (361.96,264.07) --
+	(365.32,258.25) --
+	(358.59,258.25) --
+	cycle;
+
+\path[fill=fillColor] (370.38,266.85) --
+	(373.75,261.02) --
+	(367.02,261.02) --
+	cycle;
+
+\path[fill=fillColor] (378.81,269.70) --
+	(382.18,263.87) --
+	(375.45,263.87) --
+	cycle;
+
+\path[fill=fillColor] (387.24,272.63) --
+	(390.60,266.80) --
+	(383.88,266.80) --
+	cycle;
+
+\path[fill=fillColor] (395.67,275.64) --
+	(399.03,269.81) --
+	(392.30,269.81) --
+	cycle;
+
+\path[fill=fillColor] (404.10,278.72) --
+	(407.46,272.89) --
+	(400.73,272.89) --
+	cycle;
+
+\path[fill=fillColor] (412.52,281.88) --
+	(415.89,276.05) --
+	(409.16,276.05) --
+	cycle;
+
+\path[fill=fillColor] (420.95,285.11) --
+	(424.32,279.29) --
+	(417.59,279.29) --
+	cycle;
+
+\path[fill=fillColor] (429.38,288.42) --
+	(432.74,282.59) --
+	(426.02,282.59) --
+	cycle;
+
+\path[fill=fillColor] (437.81,291.80) --
+	(441.17,285.97) --
+	(434.45,285.97) --
+	cycle;
+
+\path[fill=fillColor] (446.24,295.24) --
+	(449.60,289.41) --
+	(442.87,289.41) --
+	cycle;
+
+\path[fill=fillColor] (454.67,298.75) --
+	(458.03,292.92) --
+	(451.30,292.92) --
+	cycle;
+
+\path[fill=fillColor] (463.09,302.32) --
+	(466.46,296.50) --
+	(459.73,296.50) --
+	cycle;
+
+\path[fill=fillColor] (471.52,305.95) --
+	(474.89,300.13) --
+	(468.16,300.13) --
+	cycle;
+
+\path[fill=fillColor] (479.95,309.64) --
+	(483.31,303.81) --
+	(476.59,303.81) --
+	cycle;
+
+\path[fill=fillColor] (488.38,313.38) --
+	(491.74,307.55) --
+	(485.01,307.55) --
+	cycle;
+
+\path[fill=fillColor] (496.81,317.16) --
+	(500.17,311.34) --
+	(493.44,311.34) --
+	cycle;
+
+\path[fill=fillColor] (505.23,320.99) --
+	(508.60,315.16) --
+	(501.87,315.16) --
+	cycle;
+
+\path[fill=fillColor] (513.66,324.85) --
+	(517.03,319.03) --
+	(510.30,319.03) --
+	cycle;
+
+\path[fill=fillColor] (522.09,328.74) --
+	(525.45,322.92) --
+	(518.73,322.92) --
+	cycle;
+
+\path[fill=fillColor] (530.52,332.66) --
+	(533.88,326.83) --
+	(527.16,326.83) --
+	cycle;
+
+\path[fill=fillColor] (538.95,336.58) --
+	(542.31,330.76) --
+	(535.58,330.76) --
+	cycle;
+
+\path[fill=fillColor] (547.38,340.52) --
+	(550.74,334.69) --
+	(544.01,334.69) --
+	cycle;
+
+\path[fill=fillColor] (555.80,344.44) --
+	(559.17,338.62) --
+	(552.44,338.62) --
+	cycle;
+
+\path[fill=fillColor] (564.23,348.36) --
+	(567.60,342.53) --
+	(560.87,342.53) --
+	cycle;
+
+\path[fill=fillColor] (572.66,352.25) --
+	(576.02,346.42) --
+	(569.30,346.42) --
+	cycle;
+\definecolor{fillColor}{RGB}{149,149,149}
+
+\path[fill=fillColor] (317.32,245.00) --
+	(322.31,245.00) --
+	(322.31,249.99) --
+	(317.32,249.99) --
+	cycle;
+
+\path[fill=fillColor] (325.75,247.37) --
+	(330.74,247.37) --
+	(330.74,252.37) --
+	(325.75,252.37) --
+	cycle;
+
+\path[fill=fillColor] (334.17,249.82) --
+	(339.17,249.82) --
+	(339.17,254.81) --
+	(334.17,254.81) --
+	cycle;
+
+\path[fill=fillColor] (342.60,252.32) --
+	(347.60,252.32) --
+	(347.60,257.32) --
+	(342.60,257.32) --
+	cycle;
+
+\path[fill=fillColor] (351.03,254.89) --
+	(356.03,254.89) --
+	(356.03,259.88) --
+	(351.03,259.88) --
+	cycle;
+
+\path[fill=fillColor] (359.46,257.51) --
+	(364.45,257.51) --
+	(364.45,262.51) --
+	(359.46,262.51) --
+	cycle;
+
+\path[fill=fillColor] (367.89,260.19) --
+	(372.88,260.19) --
+	(372.88,265.19) --
+	(367.89,265.19) --
+	cycle;
+
+\path[fill=fillColor] (376.31,262.93) --
+	(381.31,262.93) --
+	(381.31,267.92) --
+	(376.31,267.92) --
+	cycle;
+
+\path[fill=fillColor] (384.74,265.71) --
+	(389.74,265.71) --
+	(389.74,270.71) --
+	(384.74,270.71) --
+	cycle;
+
+\path[fill=fillColor] (393.17,268.54) --
+	(398.17,268.54) --
+	(398.17,273.54) --
+	(393.17,273.54) --
+	cycle;
+
+\path[fill=fillColor] (401.60,271.42) --
+	(406.59,271.42) --
+	(406.59,276.41) --
+	(401.60,276.41) --
+	cycle;
+
+\path[fill=fillColor] (410.03,274.33) --
+	(415.02,274.33) --
+	(415.02,279.32) --
+	(410.03,279.32) --
+	cycle;
+
+\path[fill=fillColor] (418.46,277.27) --
+	(423.45,277.27) --
+	(423.45,282.27) --
+	(418.46,282.27) --
+	cycle;
+
+\path[fill=fillColor] (426.88,280.24) --
+	(431.88,280.24) --
+	(431.88,285.24) --
+	(426.88,285.24) --
+	cycle;
+
+\path[fill=fillColor] (435.31,283.23) --
+	(440.31,283.23) --
+	(440.31,288.23) --
+	(435.31,288.23) --
+	cycle;
+
+\path[fill=fillColor] (443.74,286.24) --
+	(448.73,286.24) --
+	(448.73,291.23) --
+	(443.74,291.23) --
+	cycle;
+
+\path[fill=fillColor] (452.17,289.25) --
+	(457.16,289.25) --
+	(457.16,294.24) --
+	(452.17,294.24) --
+	cycle;
+
+\path[fill=fillColor] (460.60,292.25) --
+	(465.59,292.25) --
+	(465.59,297.25) --
+	(460.60,297.25) --
+	cycle;
+
+\path[fill=fillColor] (469.02,295.25) --
+	(474.02,295.25) --
+	(474.02,300.24) --
+	(469.02,300.24) --
+	cycle;
+
+\path[fill=fillColor] (477.45,298.22) --
+	(482.45,298.22) --
+	(482.45,303.21) --
+	(477.45,303.21) --
+	cycle;
+
+\path[fill=fillColor] (485.88,301.15) --
+	(490.88,301.15) --
+	(490.88,306.15) --
+	(485.88,306.15) --
+	cycle;
+
+\path[fill=fillColor] (494.31,304.05) --
+	(499.30,304.05) --
+	(499.30,309.04) --
+	(494.31,309.04) --
+	cycle;
+
+\path[fill=fillColor] (502.74,306.88) --
+	(507.73,306.88) --
+	(507.73,311.88) --
+	(502.74,311.88) --
+	cycle;
+
+\path[fill=fillColor] (511.17,309.64) --
+	(516.16,309.64) --
+	(516.16,314.64) --
+	(511.17,314.64) --
+	cycle;
+
+\path[fill=fillColor] (519.59,312.32) --
+	(524.59,312.32) --
+	(524.59,317.31) --
+	(519.59,317.31) --
+	cycle;
+
+\path[fill=fillColor] (528.02,314.89) --
+	(533.02,314.89) --
+	(533.02,319.88) --
+	(528.02,319.88) --
+	cycle;
+
+\path[fill=fillColor] (536.45,317.34) --
+	(541.44,317.34) --
+	(541.44,322.33) --
+	(536.45,322.33) --
+	cycle;
+
+\path[fill=fillColor] (544.88,319.65) --
+	(549.87,319.65) --
+	(549.87,324.64) --
+	(544.88,324.64) --
+	cycle;
+
+\path[fill=fillColor] (553.31,321.80) --
+	(558.30,321.80) --
+	(558.30,326.79) --
+	(553.31,326.79) --
+	cycle;
+
+\path[fill=fillColor] (561.73,323.76) --
+	(566.73,323.76) --
+	(566.73,328.76) --
+	(561.73,328.76) --
+	cycle;
+
+\path[fill=fillColor] (570.16,325.52) --
+	(575.16,325.52) --
+	(575.16,330.52) --
+	(570.16,330.52) --
+	cycle;
+\definecolor{drawColor}{gray}{0.70}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.28,247.50) -- (323.35,247.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (319.81,243.96) -- (319.81,251.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.71,249.87) -- (331.78,249.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.24,246.33) -- (328.24,253.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.14,252.29) -- (340.20,252.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.67,248.76) -- (336.67,255.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.57,254.76) -- (348.63,254.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.10,251.23) -- (345.10,258.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.00,257.28) -- (357.06,257.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.53,253.74) -- (353.53,260.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (358.42,259.83) -- (365.49,259.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.96,256.30) -- (361.96,263.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (366.85,262.43) -- (373.92,262.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.38,258.89) -- (370.38,265.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (375.28,265.05) -- (382.34,265.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.81,261.52) -- (378.81,268.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.71,267.70) -- (390.77,267.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.24,264.16) -- (387.24,271.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.14,270.36) -- (399.20,270.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.67,266.83) -- (395.67,273.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (400.56,273.03) -- (407.63,273.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (404.10,269.50) -- (404.10,276.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.99,275.71) -- (416.06,275.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.52,272.18) -- (412.52,279.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.42,278.38) -- (424.48,278.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.95,274.85) -- (420.95,281.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.85,281.04) -- (432.91,281.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.38,277.51) -- (429.38,284.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.28,283.67) -- (441.34,283.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.81,280.13) -- (437.81,287.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.71,286.26) -- (449.77,286.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.24,282.73) -- (446.24,289.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.13,288.80) -- (458.20,288.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.67,285.27) -- (454.67,292.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.56,291.28) -- (466.63,291.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.09,287.75) -- (463.09,294.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.99,293.69) -- (475.05,293.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (471.52,290.15) -- (471.52,297.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.42,296.00) -- (483.48,296.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.95,292.47) -- (479.95,299.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.85,298.20) -- (491.91,298.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.38,294.67) -- (488.38,301.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.27,300.28) -- (500.34,300.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.81,296.75) -- (496.81,303.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.70,302.21) -- (508.77,302.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.23,298.68) -- (505.23,305.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.13,303.98) -- (517.19,303.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (513.66,300.45) -- (513.66,307.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.56,305.56) -- (525.62,305.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.09,302.03) -- (522.09,309.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.99,306.93) -- (534.05,306.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (530.52,303.40) -- (530.52,310.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.42,308.07) -- (542.48,308.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.95,304.54) -- (538.95,311.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.84,308.95) -- (550.91,308.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.38,305.42) -- (547.38,312.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.27,309.54) -- (559.34,309.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.80,306.01) -- (555.80,313.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.70,309.82) -- (567.76,309.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.23,306.29) -- (564.23,313.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,309.77) -- (576.19,309.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,306.24) -- (572.66,313.30);
+\definecolor{drawColor}{gray}{0.80}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (317.32,245.00) rectangle (322.31,249.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (317.32,245.00) -- (322.31,249.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (317.32,249.99) -- (322.31,245.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (325.75,247.36) rectangle (330.74,252.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (325.75,247.36) -- (330.74,252.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (325.75,252.36) -- (330.74,247.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.17,249.77) rectangle (339.17,254.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.17,249.77) -- (339.17,254.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.17,254.76) -- (339.17,249.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.60,252.21) rectangle (347.60,257.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.60,252.21) -- (347.60,257.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.60,257.20) -- (347.60,252.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.03,254.68) rectangle (356.03,259.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.03,254.68) -- (356.03,259.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.03,259.67) -- (356.03,254.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.46,257.17) rectangle (364.45,262.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.46,257.17) -- (364.45,262.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.46,262.16) -- (364.45,257.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.89,259.67) rectangle (372.88,264.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.89,259.67) -- (372.88,264.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.89,264.67) -- (372.88,259.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.31,262.19) rectangle (381.31,267.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.31,262.19) -- (381.31,267.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.31,267.19) -- (381.31,262.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.74,264.71) rectangle (389.74,269.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.74,264.71) -- (389.74,269.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.74,269.70) -- (389.74,264.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.17,267.21) rectangle (398.17,272.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.17,267.21) -- (398.17,272.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.17,272.21) -- (398.17,267.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.60,269.70) rectangle (406.59,274.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.60,269.70) -- (406.59,274.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.60,274.69) -- (406.59,269.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.03,272.15) rectangle (415.02,277.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.03,272.15) -- (415.02,277.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.03,277.15) -- (415.02,272.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.46,274.57) rectangle (423.45,279.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.46,274.57) -- (423.45,279.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.46,279.56) -- (423.45,274.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.88,276.93) rectangle (431.88,281.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.88,276.93) -- (431.88,281.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.88,281.93) -- (431.88,276.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.31,279.22) rectangle (440.31,284.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.31,279.22) -- (440.31,284.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.31,284.22) -- (440.31,279.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.74,281.44) rectangle (448.73,286.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.74,281.44) -- (448.73,286.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.74,286.43) -- (448.73,281.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.17,283.55) rectangle (457.16,288.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.17,283.55) -- (457.16,288.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.17,288.55) -- (457.16,283.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.60,285.55) rectangle (465.59,290.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.60,285.55) -- (465.59,290.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.60,290.55) -- (465.59,285.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.02,287.42) rectangle (474.02,292.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.02,287.42) -- (474.02,292.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.02,292.42) -- (474.02,287.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.45,289.14) rectangle (482.45,294.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.45,289.14) -- (482.45,294.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.45,294.14) -- (482.45,289.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.88,290.69) rectangle (490.88,295.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.88,290.69) -- (490.88,295.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.88,295.69) -- (490.88,290.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,292.05) rectangle (499.30,297.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,292.05) -- (499.30,297.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,297.04) -- (499.30,292.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.74,293.19) rectangle (507.73,298.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.74,293.19) -- (507.73,298.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.74,298.19) -- (507.73,293.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.17,294.09) rectangle (516.16,299.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.17,294.09) -- (516.16,299.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.17,299.09) -- (516.16,294.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.59,294.73) rectangle (524.59,299.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.59,294.73) -- (524.59,299.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.59,299.73) -- (524.59,294.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.02,295.08) rectangle (533.02,300.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.02,295.08) -- (533.02,300.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.02,300.07) -- (533.02,295.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.45,295.11) rectangle (541.44,300.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.45,295.11) -- (541.44,300.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.45,300.11) -- (541.44,295.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.88,294.80) rectangle (549.87,299.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.88,294.80) -- (549.87,299.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.88,299.79) -- (549.87,294.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.31,294.12) rectangle (558.30,299.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.31,294.12) -- (558.30,299.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.31,299.12) -- (558.30,294.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.73,293.05) rectangle (566.73,298.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.73,293.05) -- (566.73,298.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.73,298.05) -- (566.73,293.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16,291.57) rectangle (575.16,296.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16,291.57) -- (575.16,296.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16,296.57) -- (575.16,291.57);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (319.81,247.50) circle (  2.50);
+
+\path[fill=fillColor] (328.24,249.88) circle (  2.50);
+
+\path[fill=fillColor] (336.67,252.37) circle (  2.50);
+
+\path[fill=fillColor] (345.10,254.96) circle (  2.50);
+
+\path[fill=fillColor] (353.53,257.67) circle (  2.50);
+
+\path[fill=fillColor] (361.96,260.49) circle (  2.50);
+
+\path[fill=fillColor] (370.38,263.43) circle (  2.50);
+
+\path[fill=fillColor] (378.81,266.50) circle (  2.50);
+
+\path[fill=fillColor] (387.24,269.69) circle (  2.50);
+
+\path[fill=fillColor] (395.67,273.02) circle (  2.50);
+
+\path[fill=fillColor] (404.10,276.48) circle (  2.50);
+
+\path[fill=fillColor] (412.52,280.09) circle (  2.50);
+
+\path[fill=fillColor] (420.95,283.85) circle (  2.50);
+
+\path[fill=fillColor] (429.38,287.76) circle (  2.50);
+
+\path[fill=fillColor] (437.81,291.82) circle (  2.50);
+
+\path[fill=fillColor] (446.24,296.05) circle (  2.50);
+
+\path[fill=fillColor] (454.67,300.46) circle (  2.50);
+
+\path[fill=fillColor] (463.09,305.04) circle (  2.50);
+
+\path[fill=fillColor] (471.52,309.80) circle (  2.50);
+
+\path[fill=fillColor] (479.95,314.74) circle (  2.50);
+
+\path[fill=fillColor] (488.38,319.89) circle (  2.50);
+
+\path[fill=fillColor] (496.81,325.23) circle (  2.50);
+
+\path[fill=fillColor] (505.23,330.79) circle (  2.50);
+
+\path[fill=fillColor] (513.66,336.55) circle (  2.50);
+
+\path[fill=fillColor] (522.09,342.55) circle (  2.50);
+
+\path[fill=fillColor] (530.52,348.77) circle (  2.50);
+
+\path[fill=fillColor] (538.95,355.23) circle (  2.50);
+
+\path[fill=fillColor] (547.38,361.93) circle (  2.50);
+
+\path[fill=fillColor] (555.80,368.89) circle (  2.50);
+
+\path[fill=fillColor] (564.23,376.12) circle (  2.50);
+
+\path[fill=fillColor] (572.66,383.61) circle (  2.50);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.81,247.50) rectangle (572.66,410.96);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (329.08,389.03) rectangle (343.54,403.48);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (330.53,396.25) -- (342.09,396.25);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (336.31,396.25) circle (  2.50);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (329.08,374.57) rectangle (343.54,389.03);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{109,109,109}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (330.53,381.80) -- (342.09,381.80);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{109,109,109}
+
+\path[fill=fillColor] (336.31,385.68) --
+	(339.67,379.86) --
+	(332.95,379.86) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (329.08,360.12) rectangle (343.54,374.57);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{149,149,149}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (330.53,367.35) -- (342.09,367.35);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{149,149,149}
+
+\path[fill=fillColor] (333.81,364.85) --
+	(338.81,364.85) --
+	(338.81,369.84) --
+	(333.81,369.84) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (329.08,345.67) rectangle (343.54,360.12);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.70}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (330.53,352.89) -- (342.09,352.89);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.70}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (332.78,352.89) -- (339.84,352.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.31,349.36) -- (336.31,356.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (329.08,331.21) rectangle (343.54,345.67);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.80}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (330.53,338.44) -- (342.09,338.44);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.80}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.81,335.94) rectangle (338.81,340.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.81,335.94) -- (338.81,340.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.81,340.94) -- (338.81,335.94);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (349.04,393.22) {Intrinsic generation interval};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (349.04,378.77) {Intrinsic serial interval ($\rho=0.75$)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (349.04,364.32) {Intrinsic serial interval ($\rho=0.5$)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (349.04,349.86) {Intrinsic serial interval ($\rho=0.25$)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (349.04,335.41) {Intrinsic serial interval ($\rho=0$)};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.31, 30.69) rectangle (280.16,194.15);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 27.31, 30.69) rectangle (280.16,194.15);
+\definecolor{drawColor}{RGB}{13,8,135}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 63.20) --
+	( 30.51, 63.20) --
+	( 33.71, 63.20) --
+	( 36.91, 63.20) --
+	( 40.12, 63.20) --
+	( 43.32, 63.20) --
+	( 46.52, 63.20) --
+	( 49.72, 63.20) --
+	( 52.92, 63.20) --
+	( 56.12, 63.20) --
+	( 59.32, 63.20) --
+	( 62.52, 63.20) --
+	( 65.72, 63.20) --
+	( 68.92, 63.20) --
+	( 72.12, 63.20) --
+	( 75.32, 63.20) --
+	( 78.52, 63.20) --
+	( 81.72, 63.20) --
+	( 84.92, 63.20) --
+	( 88.12, 63.20) --
+	( 91.32, 63.20) --
+	( 94.53, 63.20) --
+	( 97.73, 63.20) --
+	(100.93, 63.20) --
+	(104.13, 63.20) --
+	(107.33, 63.20) --
+	(110.53, 63.20) --
+	(113.73, 63.20) --
+	(116.93, 63.20) --
+	(120.13, 63.20) --
+	(123.33, 63.20) --
+	(126.53, 63.20) --
+	(129.73, 63.20) --
+	(132.93, 63.20) --
+	(136.13, 63.20) --
+	(139.33, 63.20) --
+	(142.53, 63.20) --
+	(145.73, 63.20) --
+	(148.94, 63.20) --
+	(152.14, 63.20) --
+	(155.34, 63.20) --
+	(158.54, 63.20) --
+	(161.74, 63.20) --
+	(164.94, 63.20) --
+	(168.14, 63.20) --
+	(171.34, 63.20) --
+	(174.54, 63.20) --
+	(177.74, 63.20) --
+	(180.94, 63.20) --
+	(184.14, 63.20) --
+	(187.34, 63.20) --
+	(190.54, 63.20) --
+	(193.74, 63.20) --
+	(196.94, 63.20) --
+	(200.14, 63.20) --
+	(203.34, 63.20) --
+	(206.55, 63.20) --
+	(209.75, 63.20) --
+	(212.95, 63.20) --
+	(216.15, 63.20) --
+	(219.35, 63.20) --
+	(222.55, 63.20) --
+	(225.75, 63.20) --
+	(228.95, 63.20) --
+	(232.15, 63.20) --
+	(235.35, 63.20) --
+	(238.55, 63.20) --
+	(241.75, 63.20) --
+	(244.95, 63.20) --
+	(248.15, 63.20) --
+	(251.35, 63.20) --
+	(254.55, 63.20) --
+	(257.75, 63.20) --
+	(260.96, 63.20) --
+	(264.16, 63.20) --
+	(267.36, 63.20) --
+	(270.56, 63.20) --
+	(273.76, 63.20) --
+	(276.96, 63.20) --
+	(280.16, 63.20);
+\definecolor{drawColor}{RGB}{126,3,168}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31, 64.16) --
+	( 30.51, 65.16) --
+	( 33.71, 66.15) --
+	( 36.91, 67.13) --
+	( 40.12, 68.09) --
+	( 43.32, 69.05) --
+	( 46.52, 69.99) --
+	( 49.72, 70.92) --
+	( 52.92, 71.84) --
+	( 56.12, 72.75) --
+	( 59.32, 73.64) --
+	( 62.52, 74.53) --
+	( 65.72, 75.40) --
+	( 68.92, 76.26) --
+	( 72.12, 77.11) --
+	( 75.32, 77.95) --
+	( 78.52, 78.78) --
+	( 81.72, 79.59) --
+	( 84.92, 80.40) --
+	( 88.12, 81.20) --
+	( 91.32, 81.98) --
+	( 94.53, 82.75) --
+	( 97.73, 83.50) --
+	(100.93, 84.24) --
+	(104.13, 84.98) --
+	(107.33, 85.70) --
+	(110.53, 86.41) --
+	(113.73, 87.11) --
+	(116.93, 87.80) --
+	(120.13, 88.49) --
+	(123.33, 89.16) --
+	(126.53, 89.82) --
+	(129.73, 90.46) --
+	(132.93, 91.09) --
+	(136.13, 91.71) --
+	(139.33, 92.33) --
+	(142.53, 92.93) --
+	(145.73, 93.54) --
+	(148.94, 94.13) --
+	(152.14, 94.73) --
+	(155.34, 95.33) --
+	(158.54, 95.92) --
+	(161.74, 96.50) --
+	(164.94, 97.08) --
+	(168.14, 97.64) --
+	(171.34, 98.20) --
+	(174.54, 98.76) --
+	(177.74, 99.31) --
+	(180.94, 99.86) --
+	(184.14,100.41) --
+	(187.34,100.95) --
+	(190.54,101.49) --
+	(193.74,102.03) --
+	(196.94,102.56) --
+	(200.14,103.08) --
+	(203.34,103.60) --
+	(206.55,104.12) --
+	(209.75,104.63) --
+	(212.95,105.14) --
+	(216.15,105.65) --
+	(219.35,106.15) --
+	(222.55,106.65) --
+	(225.75,107.14) --
+	(228.95,107.63) --
+	(232.15,108.12) --
+	(235.35,108.60) --
+	(238.55,109.07) --
+	(241.75,109.54) --
+	(244.95,110.01) --
+	(248.15,110.48) --
+	(251.35,110.94) --
+	(254.55,111.39) --
+	(257.75,111.84) --
+	(260.96,112.29) --
+	(264.16,112.73) --
+	(267.36,113.17) --
+	(270.56,113.61) --
+	(273.76,114.04) --
+	(276.96,114.46) --
+	(280.16,114.89);
+\definecolor{drawColor}{RGB}{204,70,120}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31, 64.16) --
+	( 30.51, 65.64) --
+	( 33.71, 67.11) --
+	( 36.91, 68.56) --
+	( 40.12, 69.99) --
+	( 43.32, 71.41) --
+	( 46.52, 72.81) --
+	( 49.72, 74.19) --
+	( 52.92, 75.56) --
+	( 56.12, 76.91) --
+	( 59.32, 78.25) --
+	( 62.52, 79.56) --
+	( 65.72, 80.86) --
+	( 68.92, 82.15) --
+	( 72.12, 83.42) --
+	( 75.32, 84.67) --
+	( 78.52, 85.91) --
+	( 81.72, 87.13) --
+	( 84.92, 88.34) --
+	( 88.12, 89.53) --
+	( 91.32, 90.70) --
+	( 94.53, 91.85) --
+	( 97.73, 92.98) --
+	(100.93, 94.10) --
+	(104.13, 95.20) --
+	(107.33, 96.29) --
+	(110.53, 97.36) --
+	(113.73, 98.41) --
+	(116.93, 99.46) --
+	(120.13,100.49) --
+	(123.33,101.51) --
+	(126.53,102.50) --
+	(129.73,103.47) --
+	(132.93,104.43) --
+	(136.13,105.37) --
+	(139.33,106.29) --
+	(142.53,107.21) --
+	(145.73,108.12) --
+	(148.94,109.03) --
+	(152.14,109.94) --
+	(155.34,110.85) --
+	(158.54,111.75) --
+	(161.74,112.63) --
+	(164.94,113.50) --
+	(168.14,114.37) --
+	(171.34,115.22) --
+	(174.54,116.07) --
+	(177.74,116.92) --
+	(180.94,117.75) --
+	(184.14,118.59) --
+	(187.34,119.42) --
+	(190.54,120.24) --
+	(193.74,121.06) --
+	(196.94,121.87) --
+	(200.14,122.67) --
+	(203.34,123.47) --
+	(206.55,124.26) --
+	(209.75,125.04) --
+	(212.95,125.82) --
+	(216.15,126.59) --
+	(219.35,127.36) --
+	(222.55,128.12) --
+	(225.75,128.87) --
+	(228.95,129.62) --
+	(232.15,130.36) --
+	(235.35,131.10) --
+	(238.55,131.83) --
+	(241.75,132.55) --
+	(244.95,133.26) --
+	(248.15,133.97) --
+	(251.35,134.68) --
+	(254.55,135.37) --
+	(257.75,136.07) --
+	(260.96,136.75) --
+	(264.16,137.43) --
+	(267.36,138.10) --
+	(270.56,138.77) --
+	(273.76,139.43) --
+	(276.96,140.08) --
+	(280.16,140.73);
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 64.08) --
+	( 30.51, 66.04) --
+	( 33.71, 67.97) --
+	( 36.91, 69.88) --
+	( 40.12, 71.77) --
+	( 43.32, 73.64) --
+	( 46.52, 75.49) --
+	( 49.72, 77.31) --
+	( 52.92, 79.12) --
+	( 56.12, 80.91) --
+	( 59.32, 82.67) --
+	( 62.52, 84.42) --
+	( 65.72, 86.14) --
+	( 68.92, 87.84) --
+	( 72.12, 89.53) --
+	( 75.32, 91.19) --
+	( 78.52, 92.83) --
+	( 81.72, 94.46) --
+	( 84.92, 96.06) --
+	( 88.12, 97.65) --
+	( 91.32, 99.21) --
+	( 94.53,100.75) --
+	( 97.73,102.26) --
+	(100.93,103.75) --
+	(104.13,105.23) --
+	(107.33,106.68) --
+	(110.53,108.11) --
+	(113.73,109.53) --
+	(116.93,110.93) --
+	(120.13,112.32) --
+	(123.33,113.68) --
+	(126.53,115.02) --
+	(129.73,116.33) --
+	(132.93,117.61) --
+	(136.13,118.88) --
+	(139.33,120.13) --
+	(142.53,121.37) --
+	(145.73,122.61) --
+	(148.94,123.84) --
+	(152.14,125.07) --
+	(155.34,126.29) --
+	(158.54,127.51) --
+	(161.74,128.71) --
+	(164.94,129.90) --
+	(168.14,131.07) --
+	(171.34,132.24) --
+	(174.54,133.40) --
+	(177.74,134.54) --
+	(180.94,135.68) --
+	(184.14,136.82) --
+	(187.34,137.95) --
+	(190.54,139.07) --
+	(193.74,140.19) --
+	(196.94,141.29) --
+	(200.14,142.39) --
+	(203.34,143.48) --
+	(206.55,144.56) --
+	(209.75,145.63) --
+	(212.95,146.69) --
+	(216.15,147.75) --
+	(219.35,148.80) --
+	(222.55,149.84) --
+	(225.75,150.87) --
+	(228.95,151.89) --
+	(232.15,152.91) --
+	(235.35,153.91) --
+	(238.55,154.91) --
+	(241.75,155.90) --
+	(244.95,156.88) --
+	(248.15,157.85) --
+	(251.35,158.82) --
+	(254.55,159.78) --
+	(257.75,160.73) --
+	(260.96,161.67) --
+	(264.16,162.60) --
+	(267.36,163.52) --
+	(270.56,164.44) --
+	(273.76,165.35) --
+	(276.96,166.24) --
+	(280.16,167.14);
+\definecolor{drawColor}{RGB}{216,224,30}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 27.31, 63.95) --
+	( 30.51, 66.36) --
+	( 33.71, 68.74) --
+	( 36.91, 71.10) --
+	( 40.12, 73.43) --
+	( 43.32, 75.74) --
+	( 46.52, 78.03) --
+	( 49.72, 80.29) --
+	( 52.92, 82.53) --
+	( 56.12, 84.74) --
+	( 59.32, 86.93) --
+	( 62.52, 89.09) --
+	( 65.72, 91.23) --
+	( 68.92, 93.35) --
+	( 72.12, 95.44) --
+	( 75.32, 97.51) --
+	( 78.52, 99.55) --
+	( 81.72,101.58) --
+	( 84.92,103.58) --
+	( 88.12,105.56) --
+	( 91.32,107.51) --
+	( 94.53,109.43) --
+	( 97.73,111.32) --
+	(100.93,113.19) --
+	(104.13,115.04) --
+	(107.33,116.86) --
+	(110.53,118.67) --
+	(113.73,120.45) --
+	(116.93,122.21) --
+	(120.13,123.96) --
+	(123.33,125.67) --
+	(126.53,127.35) --
+	(129.73,129.01) --
+	(132.93,130.63) --
+	(136.13,132.24) --
+	(139.33,133.82) --
+	(142.53,135.39) --
+	(145.73,136.96) --
+	(148.94,138.52) --
+	(152.14,140.07) --
+	(155.34,141.63) --
+	(158.54,143.18) --
+	(161.74,144.71) --
+	(164.94,146.22) --
+	(168.14,147.72) --
+	(171.34,149.21) --
+	(174.54,150.69) --
+	(177.74,152.15) --
+	(180.94,153.61) --
+	(184.14,155.06) --
+	(187.34,156.51) --
+	(190.54,157.94) --
+	(193.74,159.37) --
+	(196.94,160.79) --
+	(200.14,162.19) --
+	(203.34,163.58) --
+	(206.55,164.97) --
+	(209.75,166.34) --
+	(212.95,167.71) --
+	(216.15,169.06) --
+	(219.35,170.41) --
+	(222.55,171.74) --
+	(225.75,173.07) --
+	(228.95,174.38) --
+	(232.15,175.69) --
+	(235.35,176.98) --
+	(238.55,178.27) --
+	(241.75,179.54) --
+	(244.95,180.81) --
+	(248.15,182.06) --
+	(251.35,183.31) --
+	(254.55,184.54) --
+	(257.75,185.77) --
+	(260.96,186.98) --
+	(264.16,188.19) --
+	(267.36,189.38) --
+	(270.56,190.57) --
+	(273.76,191.74) --
+	(276.96,192.91) --
+	(280.16,194.06);
+\definecolor{fillColor}{RGB}{126,3,168}
+
+\path[fill=fillColor] ( 27.31, 68.04) --
+	( 30.68, 62.21) --
+	( 23.95, 62.21) --
+	cycle;
+
+\path[fill=fillColor] ( 35.74, 70.65) --
+	( 39.11, 64.82) --
+	( 32.38, 64.82) --
+	cycle;
+
+\path[fill=fillColor] ( 44.17, 73.00) --
+	( 47.53, 67.17) --
+	( 40.81, 67.17) --
+	cycle;
+
+\path[fill=fillColor] ( 52.60, 75.66) --
+	( 55.96, 69.83) --
+	( 49.23, 69.83) --
+	cycle;
+
+\path[fill=fillColor] ( 61.03, 78.15) --
+	( 64.39, 72.32) --
+	( 57.66, 72.32) --
+	cycle;
+
+\path[fill=fillColor] ( 69.45, 80.38) --
+	( 72.82, 74.55) --
+	( 66.09, 74.55) --
+	cycle;
+
+\path[fill=fillColor] ( 77.88, 82.50) --
+	( 81.25, 76.67) --
+	( 74.52, 76.67) --
+	cycle;
+
+\path[fill=fillColor] ( 86.31, 84.65) --
+	( 89.67, 78.82) --
+	( 82.95, 78.82) --
+	cycle;
+
+\path[fill=fillColor] ( 94.74, 86.82) --
+	( 98.10, 80.99) --
+	( 91.37, 80.99) --
+	cycle;
+
+\path[fill=fillColor] (103.17, 88.79) --
+	(106.53, 82.96) --
+	( 99.80, 82.96) --
+	cycle;
+
+\path[fill=fillColor] (111.60, 90.70) --
+	(114.96, 84.87) --
+	(108.23, 84.87) --
+	cycle;
+
+\path[fill=fillColor] (120.02, 92.30) --
+	(123.39, 86.48) --
+	(116.66, 86.48) --
+	cycle;
+
+\path[fill=fillColor] (128.45, 94.04) --
+	(131.82, 88.21) --
+	(125.09, 88.21) --
+	cycle;
+
+\path[fill=fillColor] (136.88, 95.68) --
+	(140.24, 89.85) --
+	(133.52, 89.85) --
+	cycle;
+
+\path[fill=fillColor] (145.31, 97.35) --
+	(148.67, 91.53) --
+	(141.94, 91.53) --
+	cycle;
+
+\path[fill=fillColor] (153.74, 98.90) --
+	(157.10, 93.07) --
+	(150.37, 93.07) --
+	cycle;
+
+\path[fill=fillColor] (162.16,100.37) --
+	(165.53, 94.54) --
+	(158.80, 94.54) --
+	cycle;
+
+\path[fill=fillColor] (170.59,101.89) --
+	(173.96, 96.06) --
+	(167.23, 96.06) --
+	cycle;
+
+\path[fill=fillColor] (179.02,103.46) --
+	(182.38, 97.64) --
+	(175.66, 97.64) --
+	cycle;
+
+\path[fill=fillColor] (187.45,104.87) --
+	(190.81, 99.04) --
+	(184.08, 99.04) --
+	cycle;
+
+\path[fill=fillColor] (195.88,106.29) --
+	(199.24,100.47) --
+	(192.51,100.47) --
+	cycle;
+
+\path[fill=fillColor] (204.30,107.65) --
+	(207.67,101.82) --
+	(200.94,101.82) --
+	cycle;
+
+\path[fill=fillColor] (212.73,108.93) --
+	(216.10,103.11) --
+	(209.37,103.11) --
+	cycle;
+
+\path[fill=fillColor] (221.16,110.30) --
+	(224.53,104.48) --
+	(217.80,104.48) --
+	cycle;
+
+\path[fill=fillColor] (229.59,111.62) --
+	(232.95,105.79) --
+	(226.23,105.79) --
+	cycle;
+
+\path[fill=fillColor] (238.02,112.82) --
+	(241.38,106.99) --
+	(234.65,106.99) --
+	cycle;
+
+\path[fill=fillColor] (246.45,114.10) --
+	(249.81,108.28) --
+	(243.08,108.28) --
+	cycle;
+
+\path[fill=fillColor] (254.87,115.26) --
+	(258.24,109.43) --
+	(251.51,109.43) --
+	cycle;
+
+\path[fill=fillColor] (263.30,116.55) --
+	(266.67,110.72) --
+	(259.94,110.72) --
+	cycle;
+
+\path[fill=fillColor] (271.73,117.65) --
+	(275.09,111.83) --
+	(268.37,111.83) --
+	cycle;
+
+\path[fill=fillColor] (280.16,118.80) --
+	(283.52,112.97) --
+	(276.79,112.97) --
+	cycle;
+\definecolor{fillColor}{RGB}{204,70,120}
+
+\path[fill=fillColor] ( 24.82, 61.68) --
+	( 29.81, 61.68) --
+	( 29.81, 66.68) --
+	( 24.82, 66.68) --
+	cycle;
+
+\path[fill=fillColor] ( 33.24, 65.53) --
+	( 38.24, 65.53) --
+	( 38.24, 70.52) --
+	( 33.24, 70.52) --
+	cycle;
+
+\path[fill=fillColor] ( 41.67, 69.01) --
+	( 46.67, 69.01) --
+	( 46.67, 74.00) --
+	( 41.67, 74.00) --
+	cycle;
+
+\path[fill=fillColor] ( 50.10, 72.95) --
+	( 55.10, 72.95) --
+	( 55.10, 77.95) --
+	( 50.10, 77.95) --
+	cycle;
+
+\path[fill=fillColor] ( 58.53, 76.64) --
+	( 63.52, 76.64) --
+	( 63.52, 81.63) --
+	( 58.53, 81.63) --
+	cycle;
+
+\path[fill=fillColor] ( 66.96, 79.97) --
+	( 71.95, 79.97) --
+	( 71.95, 84.96) --
+	( 66.96, 84.96) --
+	cycle;
+
+\path[fill=fillColor] ( 75.38, 83.16) --
+	( 80.38, 83.16) --
+	( 80.38, 88.16) --
+	( 75.38, 88.16) --
+	cycle;
+
+\path[fill=fillColor] ( 83.81, 86.41) --
+	( 88.81, 86.41) --
+	( 88.81, 91.41) --
+	( 83.81, 91.41) --
+	cycle;
+
+\path[fill=fillColor] ( 92.24, 89.65) --
+	( 97.24, 89.65) --
+	( 97.24, 94.65) --
+	( 92.24, 94.65) --
+	cycle;
+
+\path[fill=fillColor] (100.67, 92.60) --
+	(105.66, 92.60) --
+	(105.66, 97.60) --
+	(100.67, 97.60) --
+	cycle;
+
+\path[fill=fillColor] (109.10, 95.42) --
+	(114.09, 95.42) --
+	(114.09,100.42) --
+	(109.10,100.42) --
+	cycle;
+
+\path[fill=fillColor] (117.53, 97.90) --
+	(122.52, 97.90) --
+	(122.52,102.89) --
+	(117.53,102.89) --
+	cycle;
+
+\path[fill=fillColor] (125.95,100.49) --
+	(130.95,100.49) --
+	(130.95,105.49) --
+	(125.95,105.49) --
+	cycle;
+
+\path[fill=fillColor] (134.38,103.01) --
+	(139.38,103.01) --
+	(139.38,108.00) --
+	(134.38,108.00) --
+	cycle;
+
+\path[fill=fillColor] (142.81,105.51) --
+	(147.81,105.51) --
+	(147.81,110.51) --
+	(142.81,110.51) --
+	cycle;
+
+\path[fill=fillColor] (151.24,107.88) --
+	(156.23,107.88) --
+	(156.23,112.88) --
+	(151.24,112.88) --
+	cycle;
+
+\path[fill=fillColor] (159.67,110.12) --
+	(164.66,110.12) --
+	(164.66,115.11) --
+	(159.67,115.11) --
+	cycle;
+
+\path[fill=fillColor] (168.09,112.40) --
+	(173.09,112.40) --
+	(173.09,117.39) --
+	(168.09,117.39) --
+	cycle;
+
+\path[fill=fillColor] (176.52,114.82) --
+	(181.52,114.82) --
+	(181.52,119.82) --
+	(176.52,119.82) --
+	cycle;
+
+\path[fill=fillColor] (184.95,116.97) --
+	(189.95,116.97) --
+	(189.95,121.96) --
+	(184.95,121.96) --
+	cycle;
+
+\path[fill=fillColor] (193.38,119.16) --
+	(198.37,119.16) --
+	(198.37,124.15) --
+	(193.38,124.15) --
+	cycle;
+
+\path[fill=fillColor] (201.81,121.21) --
+	(206.80,121.21) --
+	(206.80,126.20) --
+	(201.81,126.20) --
+	cycle;
+
+\path[fill=fillColor] (210.24,123.21) --
+	(215.23,123.21) --
+	(215.23,128.21) --
+	(210.24,128.21) --
+	cycle;
+
+\path[fill=fillColor] (218.66,125.29) --
+	(223.66,125.29) --
+	(223.66,130.28) --
+	(218.66,130.28) --
+	cycle;
+
+\path[fill=fillColor] (227.09,127.27) --
+	(232.09,127.27) --
+	(232.09,132.26) --
+	(227.09,132.26) --
+	cycle;
+
+\path[fill=fillColor] (235.52,129.12) --
+	(240.52,129.12) --
+	(240.52,134.11) --
+	(235.52,134.11) --
+	cycle;
+
+\path[fill=fillColor] (243.95,131.10) --
+	(248.94,131.10) --
+	(248.94,136.09) --
+	(243.95,136.09) --
+	cycle;
+
+\path[fill=fillColor] (252.38,132.88) --
+	(257.37,132.88) --
+	(257.37,137.87) --
+	(252.38,137.87) --
+	cycle;
+
+\path[fill=fillColor] (260.80,134.82) --
+	(265.80,134.82) --
+	(265.80,139.81) --
+	(260.80,139.81) --
+	cycle;
+
+\path[fill=fillColor] (269.23,136.50) --
+	(274.23,136.50) --
+	(274.23,141.49) --
+	(269.23,141.49) --
+	cycle;
+
+\path[fill=fillColor] (277.66,138.27) --
+	(282.66,138.27) --
+	(282.66,143.27) --
+	(277.66,143.27) --
+	cycle;
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78, 64.15) -- ( 30.85, 64.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31, 60.62) -- ( 27.31, 67.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.21, 69.18) -- ( 39.27, 69.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.74, 65.65) -- ( 35.74, 72.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.64, 73.76) -- ( 47.70, 73.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.17, 70.23) -- ( 44.17, 77.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.07, 78.96) -- ( 56.13, 78.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.60, 75.42) -- ( 52.60, 82.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.49, 83.79) -- ( 64.56, 83.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.03, 80.26) -- ( 61.03, 87.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.92, 88.22) -- ( 72.99, 88.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 69.45, 84.69) -- ( 69.45, 91.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.35, 92.50) -- ( 81.41, 92.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.88, 88.97) -- ( 77.88, 96.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 82.78, 96.86) -- ( 89.84, 96.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.31, 93.33) -- ( 86.31,100.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.21,101.17) -- ( 98.27,101.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.74, 97.63) -- ( 94.74,104.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,105.11) -- (106.70,105.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.17,101.57) -- (103.17,108.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.06,108.80) -- (115.13,108.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (111.60,105.26) -- (111.60,112.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.49,112.21) -- (123.56,112.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.02,108.68) -- (120.02,115.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.92,115.67) -- (131.98,115.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.45,112.14) -- (128.45,119.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.35,119.09) -- (140.41,119.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.88,115.56) -- (136.88,122.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.78,122.43) -- (148.84,122.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.31,118.90) -- (145.31,125.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.20,125.69) -- (157.27,125.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.74,122.16) -- (153.74,129.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.63,128.71) -- (165.70,128.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.16,125.18) -- (162.16,132.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.06,131.76) -- (174.12,131.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.59,128.22) -- (170.59,135.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.49,135.09) -- (182.55,135.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.02,131.55) -- (179.02,138.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.92,138.02) -- (190.98,138.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.45,134.49) -- (187.45,141.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.34,141.02) -- (199.41,141.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.88,137.49) -- (195.88,144.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.77,143.80) -- (207.84,143.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.30,140.26) -- (204.30,147.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.20,146.57) -- (216.27,146.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.73,143.04) -- (212.73,150.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.63,149.39) -- (224.69,149.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.16,145.86) -- (221.16,152.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.06,152.08) -- (233.12,152.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.59,148.55) -- (229.59,155.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.49,154.61) -- (241.55,154.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.02,151.07) -- (238.02,158.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.91,157.36) -- (249.98,157.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.45,153.83) -- (246.45,160.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.34,159.82) -- (258.41,159.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.87,156.28) -- (254.87,163.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.77,162.43) -- (266.83,162.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.30,158.90) -- (263.30,165.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.20,164.72) -- (275.26,164.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.73,161.19) -- (271.73,168.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.63,167.20) -- (283.69,167.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.16,163.67) -- (280.16,170.73);
+\definecolor{drawColor}{RGB}{216,224,30}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 24.82, 61.58) rectangle ( 29.81, 66.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 24.82, 61.58) -- ( 29.81, 66.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 24.82, 66.58) -- ( 29.81, 61.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.24, 67.75) rectangle ( 38.24, 72.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.24, 67.75) -- ( 38.24, 72.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.24, 72.74) -- ( 38.24, 67.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.67, 73.39) rectangle ( 46.67, 78.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.67, 73.39) -- ( 46.67, 78.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.67, 78.39) -- ( 46.67, 73.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.10, 79.80) rectangle ( 55.10, 84.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.10, 79.80) -- ( 55.10, 84.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.10, 84.80) -- ( 55.10, 79.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.53, 85.74) rectangle ( 63.52, 90.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.53, 85.74) -- ( 63.52, 90.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.53, 90.74) -- ( 63.52, 85.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.96, 91.27) rectangle ( 71.95, 96.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.96, 91.27) -- ( 71.95, 96.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.96, 96.26) -- ( 71.95, 91.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.38, 96.65) rectangle ( 80.38,101.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.38, 96.65) -- ( 80.38,101.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.38,101.64) -- ( 80.38, 96.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.81,102.12) rectangle ( 88.81,107.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.81,102.12) -- ( 88.81,107.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.81,107.12) -- ( 88.81,102.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.24,107.48) rectangle ( 97.24,112.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.24,107.48) -- ( 97.24,112.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.24,112.48) -- ( 97.24,107.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.67,112.41) rectangle (105.66,117.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.67,112.41) -- (105.66,117.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.67,117.40) -- (105.66,112.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.10,116.94) rectangle (114.09,121.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.10,116.94) -- (114.09,121.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.10,121.93) -- (114.09,116.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.53,121.34) rectangle (122.52,126.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.53,121.34) -- (122.52,126.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.53,126.34) -- (122.52,121.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.95,125.66) rectangle (130.95,130.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.95,125.66) -- (130.95,130.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.95,130.66) -- (130.95,125.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.38,130.03) rectangle (139.38,135.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.38,130.03) -- (139.38,135.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.38,135.02) -- (139.38,130.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.81,134.21) rectangle (147.81,139.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.81,134.21) -- (147.81,139.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.81,139.21) -- (147.81,134.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.24,138.41) rectangle (156.23,143.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.24,138.41) -- (156.23,143.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.24,143.40) -- (156.23,138.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.67,142.23) rectangle (164.66,147.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.67,142.23) -- (164.66,147.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.67,147.22) -- (164.66,142.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.09,146.06) rectangle (173.09,151.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.09,146.06) -- (173.09,151.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.09,151.05) -- (173.09,146.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.52,150.34) rectangle (181.52,155.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.52,150.34) -- (181.52,155.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.52,155.34) -- (181.52,150.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.95,154.10) rectangle (189.95,159.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.95,154.10) -- (189.95,159.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.95,159.10) -- (189.95,154.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.38,157.97) rectangle (198.37,162.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.38,157.97) -- (198.37,162.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.38,162.96) -- (198.37,157.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.81,161.49) rectangle (206.80,166.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.81,161.49) -- (206.80,166.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.81,166.49) -- (206.80,161.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.24,165.09) rectangle (215.23,170.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.24,165.09) -- (215.23,170.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.24,170.08) -- (215.23,165.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.66,168.70) rectangle (223.66,173.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.66,168.70) -- (223.66,173.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.66,173.69) -- (223.66,168.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.09,172.11) rectangle (232.09,177.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.09,172.11) -- (232.09,177.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.09,177.11) -- (232.09,172.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.52,175.36) rectangle (240.52,180.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.52,175.36) -- (240.52,180.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.52,180.35) -- (240.52,175.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.95,178.96) rectangle (248.94,183.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.95,178.96) -- (248.94,183.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.95,183.95) -- (248.94,178.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.38,182.15) rectangle (257.37,187.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.38,182.15) -- (257.37,187.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.38,187.14) -- (257.37,182.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.80,185.46) rectangle (265.80,190.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.80,185.46) -- (265.80,190.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.80,190.45) -- (265.80,185.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.23,188.38) rectangle (274.23,193.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.23,188.38) -- (274.23,193.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.23,193.38) -- (274.23,188.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.66,191.66) rectangle (282.66,196.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.66,191.66) -- (282.66,196.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.66,196.65) -- (282.66,191.66);
+\definecolor{fillColor}{RGB}{13,8,135}
+
+\path[fill=fillColor] ( 27.31, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 35.74, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 44.17, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 52.60, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 61.03, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 69.45, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 77.88, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 86.31, 63.20) circle (  2.50);
+
+\path[fill=fillColor] ( 94.74, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (103.17, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (111.60, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (120.02, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (128.45, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (136.88, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (145.31, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (153.74, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (162.16, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (170.59, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (179.02, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (187.45, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (195.88, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (204.30, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (212.73, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (221.16, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (229.59, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (238.02, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (246.45, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (254.87, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (263.30, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (271.73, 63.20) circle (  2.50);
+
+\path[fill=fillColor] (280.16, 63.20) circle (  2.50);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.31, 30.69) rectangle (280.16,194.15);
+\end{scope}
+\begin{scope}
+\path[clip] (319.81, 30.69) rectangle (572.66,194.15);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (319.81, 30.69) rectangle (572.66,194.15);
+\definecolor{drawColor}{RGB}{13,8,135}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (319.81, 58.94) --
+	(323.02, 58.94) --
+	(326.22, 58.94) --
+	(329.42, 58.94) --
+	(332.62, 58.94) --
+	(335.82, 58.94) --
+	(339.02, 58.94) --
+	(342.22, 58.94) --
+	(345.42, 58.94) --
+	(348.62, 58.94) --
+	(351.82, 58.94) --
+	(355.02, 58.94) --
+	(358.22, 58.94) --
+	(361.42, 58.94) --
+	(364.62, 58.94) --
+	(367.82, 58.94) --
+	(371.02, 58.94) --
+	(374.22, 58.94) --
+	(377.43, 58.94) --
+	(380.63, 58.94) --
+	(383.83, 58.94) --
+	(387.03, 58.94) --
+	(390.23, 58.94) --
+	(393.43, 58.94) --
+	(396.63, 58.94) --
+	(399.83, 58.94) --
+	(403.03, 58.94) --
+	(406.23, 58.94) --
+	(409.43, 58.94) --
+	(412.63, 58.94) --
+	(415.83, 58.94) --
+	(419.03, 58.94) --
+	(422.23, 58.94) --
+	(425.43, 58.94) --
+	(428.63, 58.94) --
+	(431.83, 58.94) --
+	(435.04, 58.94) --
+	(438.24, 58.94) --
+	(441.44, 58.94) --
+	(444.64, 58.94) --
+	(447.84, 58.94) --
+	(451.04, 58.94) --
+	(454.24, 58.94) --
+	(457.44, 58.94) --
+	(460.64, 58.94) --
+	(463.84, 58.94) --
+	(467.04, 58.94) --
+	(470.24, 58.94) --
+	(473.44, 58.94) --
+	(476.64, 58.94) --
+	(479.84, 58.94) --
+	(483.04, 58.94) --
+	(486.24, 58.94) --
+	(489.45, 58.94) --
+	(492.65, 58.94) --
+	(495.85, 58.94) --
+	(499.05, 58.94) --
+	(502.25, 58.94) --
+	(505.45, 58.94) --
+	(508.65, 58.94) --
+	(511.85, 58.94) --
+	(515.05, 58.94) --
+	(518.25, 58.94) --
+	(521.45, 58.94) --
+	(524.65, 58.94) --
+	(527.85, 58.94) --
+	(531.05, 58.94) --
+	(534.25, 58.94) --
+	(537.45, 58.94) --
+	(540.65, 58.94) --
+	(543.85, 58.94) --
+	(547.06, 58.94) --
+	(550.26, 58.94) --
+	(553.46, 58.94) --
+	(556.66, 58.94) --
+	(559.86, 58.94) --
+	(563.06, 58.94) --
+	(566.26, 58.94) --
+	(569.46, 58.94) --
+	(572.66, 58.94);
+\definecolor{drawColor}{RGB}{126,3,168}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (319.81, 97.64) --
+	(323.02, 97.20) --
+	(326.22, 96.77) --
+	(329.42, 96.35) --
+	(332.62, 95.93) --
+	(335.82, 95.52) --
+	(339.02, 95.12) --
+	(342.22, 94.73) --
+	(345.42, 94.34) --
+	(348.62, 93.96) --
+	(351.82, 93.58) --
+	(355.02, 93.22) --
+	(358.22, 92.86) --
+	(361.42, 92.51) --
+	(364.62, 92.16) --
+	(367.82, 91.82) --
+	(371.02, 91.49) --
+	(374.22, 91.17) --
+	(377.43, 90.85) --
+	(380.63, 90.54) --
+	(383.83, 90.23) --
+	(387.03, 89.94) --
+	(390.23, 89.65) --
+	(393.43, 89.37) --
+	(396.63, 89.10) --
+	(399.83, 88.84) --
+	(403.03, 88.58) --
+	(406.23, 88.32) --
+	(409.43, 88.07) --
+	(412.63, 87.82) --
+	(415.83, 87.59) --
+	(419.03, 87.36) --
+	(422.23, 87.14) --
+	(425.43, 86.92) --
+	(428.63, 86.72) --
+	(431.83, 86.51) --
+	(435.04, 86.31) --
+	(438.24, 86.12) --
+	(441.44, 85.92) --
+	(444.64, 85.72) --
+	(447.84, 85.52) --
+	(451.04, 85.33) --
+	(454.24, 85.14) --
+	(457.44, 84.95) --
+	(460.64, 84.77) --
+	(463.84, 84.59) --
+	(467.04, 84.41) --
+	(470.24, 84.24) --
+	(473.44, 84.07) --
+	(476.64, 83.89) --
+	(479.84, 83.72) --
+	(483.04, 83.55) --
+	(486.24, 83.38) --
+	(489.45, 83.21) --
+	(492.65, 83.04) --
+	(495.85, 82.88) --
+	(499.05, 82.72) --
+	(502.25, 82.56) --
+	(505.45, 82.40) --
+	(508.65, 82.25) --
+	(511.85, 82.09) --
+	(515.05, 81.94) --
+	(518.25, 81.79) --
+	(521.45, 81.64) --
+	(524.65, 81.49) --
+	(527.85, 81.35) --
+	(531.05, 81.20) --
+	(534.25, 81.06) --
+	(537.45, 80.92) --
+	(540.65, 80.79) --
+	(543.85, 80.65) --
+	(547.06, 80.52) --
+	(550.26, 80.39) --
+	(553.46, 80.26) --
+	(556.66, 80.13) --
+	(559.86, 80.00) --
+	(563.06, 79.88) --
+	(566.26, 79.76) --
+	(569.46, 79.64) --
+	(572.66, 79.52);
+\definecolor{drawColor}{RGB}{204,70,120}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (319.81,115.70) --
+	(323.02,114.93) --
+	(326.22,114.17) --
+	(329.42,113.43) --
+	(332.62,112.70) --
+	(335.82,111.98) --
+	(339.02,111.27) --
+	(342.22,110.58) --
+	(345.42,109.90) --
+	(348.62,109.23) --
+	(351.82,108.58) --
+	(355.02,107.94) --
+	(358.22,107.32) --
+	(361.42,106.70) --
+	(364.62,106.10) --
+	(367.82,105.51) --
+	(371.02,104.94) --
+	(374.22,104.37) --
+	(377.43,103.82) --
+	(380.63,103.28) --
+	(383.83,102.76) --
+	(387.03,102.25) --
+	(390.23,101.76) --
+	(393.43,101.28) --
+	(396.63,100.81) --
+	(399.83,100.36) --
+	(403.03, 99.92) --
+	(406.23, 99.48) --
+	(409.43, 99.06) --
+	(412.63, 98.64) --
+	(415.83, 98.23) --
+	(419.03, 97.85) --
+	(422.23, 97.47) --
+	(425.43, 97.11) --
+	(428.63, 96.76) --
+	(431.83, 96.42) --
+	(435.04, 96.09) --
+	(438.24, 95.75) --
+	(441.44, 95.42) --
+	(444.64, 95.09) --
+	(447.84, 94.76) --
+	(451.04, 94.43) --
+	(454.24, 94.12) --
+	(457.44, 93.81) --
+	(460.64, 93.51) --
+	(463.84, 93.21) --
+	(467.04, 92.92) --
+	(470.24, 92.63) --
+	(473.44, 92.34) --
+	(476.64, 92.06) --
+	(479.84, 91.77) --
+	(483.04, 91.49) --
+	(486.24, 91.21) --
+	(489.45, 90.94) --
+	(492.65, 90.67) --
+	(495.85, 90.40) --
+	(499.05, 90.13) --
+	(502.25, 89.87) --
+	(505.45, 89.61) --
+	(508.65, 89.36) --
+	(511.85, 89.11) --
+	(515.05, 88.86) --
+	(518.25, 88.61) --
+	(521.45, 88.37) --
+	(524.65, 88.13) --
+	(527.85, 87.90) --
+	(531.05, 87.67) --
+	(534.25, 87.44) --
+	(537.45, 87.22) --
+	(540.65, 87.00) --
+	(543.85, 86.78) --
+	(547.06, 86.56) --
+	(550.26, 86.35) --
+	(553.46, 86.14) --
+	(556.66, 85.94) --
+	(559.86, 85.74) --
+	(563.06, 85.54) --
+	(566.26, 85.35) --
+	(569.46, 85.16) --
+	(572.66, 84.97);
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (319.81,133.03) --
+	(323.02,131.91) --
+	(326.22,130.81) --
+	(329.42,129.73) --
+	(332.62,128.67) --
+	(335.82,127.63) --
+	(339.02,126.61) --
+	(342.22,125.61) --
+	(345.42,124.63) --
+	(348.62,123.67) --
+	(351.82,122.72) --
+	(355.02,121.80) --
+	(358.22,120.90) --
+	(361.42,120.02) --
+	(364.62,119.15) --
+	(367.82,118.31) --
+	(371.02,117.48) --
+	(374.22,116.67) --
+	(377.43,115.88) --
+	(380.63,115.11) --
+	(383.83,114.36) --
+	(387.03,113.63) --
+	(390.23,112.93) --
+	(393.43,112.25) --
+	(396.63,111.59) --
+	(399.83,110.95) --
+	(403.03,110.32) --
+	(406.23,109.71) --
+	(409.43,109.11) --
+	(412.63,108.52) --
+	(415.83,107.94) --
+	(419.03,107.40) --
+	(422.23,106.87) --
+	(425.43,106.37) --
+	(428.63,105.88) --
+	(431.83,105.40) --
+	(435.04,104.94) --
+	(438.24,104.47) --
+	(441.44,104.01) --
+	(444.64,103.55) --
+	(447.84,103.09) --
+	(451.04,102.64) --
+	(454.24,102.20) --
+	(457.44,101.77) --
+	(460.64,101.35) --
+	(463.84,100.94) --
+	(467.04,100.54) --
+	(470.24,100.14) --
+	(473.44, 99.74) --
+	(476.64, 99.35) --
+	(479.84, 98.96) --
+	(483.04, 98.57) --
+	(486.24, 98.18) --
+	(489.45, 97.81) --
+	(492.65, 97.43) --
+	(495.85, 97.07) --
+	(499.05, 96.71) --
+	(502.25, 96.35) --
+	(505.45, 96.00) --
+	(508.65, 95.65) --
+	(511.85, 95.31) --
+	(515.05, 94.97) --
+	(518.25, 94.63) --
+	(521.45, 94.31) --
+	(524.65, 93.98) --
+	(527.85, 93.66) --
+	(531.05, 93.35) --
+	(534.25, 93.04) --
+	(537.45, 92.74) --
+	(540.65, 92.44) --
+	(543.85, 92.14) --
+	(547.06, 91.86) --
+	(550.26, 91.57) --
+	(553.46, 91.29) --
+	(556.66, 91.02) --
+	(559.86, 90.75) --
+	(563.06, 90.48) --
+	(566.26, 90.23) --
+	(569.46, 89.97) --
+	(572.66, 89.72);
+\definecolor{drawColor}{RGB}{216,224,30}
+
+\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] (319.81,149.67) --
+	(323.02,148.19) --
+	(326.22,146.73) --
+	(329.42,145.31) --
+	(332.62,143.91) --
+	(335.82,142.53) --
+	(339.02,141.18) --
+	(342.22,139.86) --
+	(345.42,138.57) --
+	(348.62,137.30) --
+	(351.82,136.06) --
+	(355.02,134.85) --
+	(358.22,133.66) --
+	(361.42,132.50) --
+	(364.62,131.37) --
+	(367.82,130.26) --
+	(371.02,129.17) --
+	(374.22,128.11) --
+	(377.43,127.07) --
+	(380.63,126.06) --
+	(383.83,125.09) --
+	(387.03,124.14) --
+	(390.23,123.23) --
+	(393.43,122.35) --
+	(396.63,121.49) --
+	(399.83,120.66) --
+	(403.03,119.84) --
+	(406.23,119.05) --
+	(409.43,118.27) --
+	(412.63,117.51) --
+	(415.83,116.77) --
+	(419.03,116.06) --
+	(422.23,115.39) --
+	(425.43,114.74) --
+	(428.63,114.12) --
+	(431.83,113.51) --
+	(435.04,112.91) --
+	(438.24,112.32) --
+	(441.44,111.73) --
+	(444.64,111.14) --
+	(447.84,110.55) --
+	(451.04,109.97) --
+	(454.24,109.41) --
+	(457.44,108.87) --
+	(460.64,108.33) --
+	(463.84,107.81) --
+	(467.04,107.30) --
+	(470.24,106.80) --
+	(473.44,106.29) --
+	(476.64,105.80) --
+	(479.84,105.30) --
+	(483.04,104.81) --
+	(486.24,104.32) --
+	(489.45,103.84) --
+	(492.65,103.37) --
+	(495.85,102.91) --
+	(499.05,102.46) --
+	(502.25,102.01) --
+	(505.45,101.57) --
+	(508.65,101.13) --
+	(511.85,100.70) --
+	(515.05,100.27) --
+	(518.25, 99.86) --
+	(521.45, 99.44) --
+	(524.65, 99.04) --
+	(527.85, 98.64) --
+	(531.05, 98.25) --
+	(534.25, 97.86) --
+	(537.45, 97.48) --
+	(540.65, 97.11) --
+	(543.85, 96.75) --
+	(547.06, 96.39) --
+	(550.26, 96.04) --
+	(553.46, 95.69) --
+	(556.66, 95.35) --
+	(559.86, 95.02) --
+	(563.06, 94.69) --
+	(566.26, 94.37) --
+	(569.46, 94.06) --
+	(572.66, 93.75);
+\definecolor{fillColor}{RGB}{126,3,168}
+
+\path[fill=fillColor] (319.81,101.62) --
+	(323.18, 95.79) --
+	(316.45, 95.79) --
+	cycle;
+
+\path[fill=fillColor] (328.24,100.41) --
+	(331.61, 94.58) --
+	(324.88, 94.58) --
+	cycle;
+
+\path[fill=fillColor] (336.67, 99.32) --
+	(340.03, 93.49) --
+	(333.31, 93.49) --
+	cycle;
+
+\path[fill=fillColor] (345.10, 98.18) --
+	(348.46, 92.35) --
+	(341.74, 92.35) --
+	cycle;
+
+\path[fill=fillColor] (353.53, 97.16) --
+	(356.89, 91.33) --
+	(350.16, 91.33) --
+	cycle;
+
+\path[fill=fillColor] (361.96, 96.27) --
+	(365.32, 90.44) --
+	(358.59, 90.44) --
+	cycle;
+
+\path[fill=fillColor] (370.38, 95.43) --
+	(373.75, 89.61) --
+	(367.02, 89.61) --
+	cycle;
+
+\path[fill=fillColor] (378.81, 94.63) --
+	(382.18, 88.80) --
+	(375.45, 88.80) --
+	cycle;
+
+\path[fill=fillColor] (387.24, 93.76) --
+	(390.60, 87.94) --
+	(383.88, 87.94) --
+	cycle;
+
+\path[fill=fillColor] (395.67, 92.98) --
+	(399.03, 87.16) --
+	(392.30, 87.16) --
+	cycle;
+
+\path[fill=fillColor] (404.10, 92.29) --
+	(407.46, 86.46) --
+	(400.73, 86.46) --
+	cycle;
+
+\path[fill=fillColor] (412.52, 91.68) --
+	(415.89, 85.86) --
+	(409.16, 85.86) --
+	cycle;
+
+\path[fill=fillColor] (420.95, 91.09) --
+	(424.32, 85.26) --
+	(417.59, 85.26) --
+	cycle;
+
+\path[fill=fillColor] (429.38, 90.57) --
+	(432.74, 84.74) --
+	(426.02, 84.74) --
+	cycle;
+
+\path[fill=fillColor] (437.81, 90.05) --
+	(441.17, 84.22) --
+	(434.45, 84.22) --
+	cycle;
+
+\path[fill=fillColor] (446.24, 89.54) --
+	(449.60, 83.72) --
+	(442.87, 83.72) --
+	cycle;
+
+\path[fill=fillColor] (454.67, 89.09) --
+	(458.03, 83.26) --
+	(451.30, 83.26) --
+	cycle;
+
+\path[fill=fillColor] (463.09, 88.59) --
+	(466.46, 82.77) --
+	(459.73, 82.77) --
+	cycle;
+
+\path[fill=fillColor] (471.52, 88.04) --
+	(474.89, 82.21) --
+	(468.16, 82.21) --
+	cycle;
+
+\path[fill=fillColor] (479.95, 87.56) --
+	(483.31, 81.73) --
+	(476.59, 81.73) --
+	cycle;
+
+\path[fill=fillColor] (488.38, 87.14) --
+	(491.74, 81.31) --
+	(485.01, 81.31) --
+	cycle;
+
+\path[fill=fillColor] (496.81, 86.70) --
+	(500.17, 80.87) --
+	(493.44, 80.87) --
+	cycle;
+
+\path[fill=fillColor] (505.23, 86.30) --
+	(508.60, 80.48) --
+	(501.87, 80.48) --
+	cycle;
+
+\path[fill=fillColor] (513.66, 85.86) --
+	(517.03, 80.04) --
+	(510.30, 80.04) --
+	cycle;
+
+\path[fill=fillColor] (522.09, 85.49) --
+	(525.45, 79.67) --
+	(518.73, 79.67) --
+	cycle;
+
+\path[fill=fillColor] (530.52, 85.15) --
+	(533.88, 79.33) --
+	(527.16, 79.33) --
+	cycle;
+
+\path[fill=fillColor] (538.95, 84.78) --
+	(542.31, 78.96) --
+	(535.58, 78.96) --
+	cycle;
+
+\path[fill=fillColor] (547.38, 84.39) --
+	(550.74, 78.57) --
+	(544.01, 78.57) --
+	cycle;
+
+\path[fill=fillColor] (555.80, 84.03) --
+	(559.17, 78.21) --
+	(552.44, 78.21) --
+	cycle;
+
+\path[fill=fillColor] (564.23, 83.73) --
+	(567.60, 77.90) --
+	(560.87, 77.90) --
+	cycle;
+
+\path[fill=fillColor] (572.66, 83.38) --
+	(576.02, 77.56) --
+	(569.30, 77.56) --
+	cycle;
+\definecolor{fillColor}{RGB}{204,70,120}
+
+\path[fill=fillColor] (317.32,113.39) --
+	(322.31,113.39) --
+	(322.31,118.38) --
+	(317.32,118.38) --
+	cycle;
+
+\path[fill=fillColor] (325.75,111.23) --
+	(330.74,111.23) --
+	(330.74,116.23) --
+	(325.75,116.23) --
+	cycle;
+
+\path[fill=fillColor] (334.17,109.33) --
+	(339.17,109.33) --
+	(339.17,114.33) --
+	(334.17,114.33) --
+	cycle;
+
+\path[fill=fillColor] (342.60,107.33) --
+	(347.60,107.33) --
+	(347.60,112.32) --
+	(342.60,112.32) --
+	cycle;
+
+\path[fill=fillColor] (351.03,105.51) --
+	(356.03,105.51) --
+	(356.03,110.51) --
+	(351.03,110.51) --
+	cycle;
+
+\path[fill=fillColor] (359.46,103.96) --
+	(364.45,103.96) --
+	(364.45,108.96) --
+	(359.46,108.96) --
+	cycle;
+
+\path[fill=fillColor] (367.89,102.51) --
+	(372.88,102.51) --
+	(372.88,107.50) --
+	(367.89,107.50) --
+	cycle;
+
+\path[fill=fillColor] (376.31,101.12) --
+	(381.31,101.12) --
+	(381.31,106.11) --
+	(376.31,106.11) --
+	cycle;
+
+\path[fill=fillColor] (384.74, 99.64) --
+	(389.74, 99.64) --
+	(389.74,104.64) --
+	(384.74,104.64) --
+	cycle;
+
+\path[fill=fillColor] (393.17, 98.32) --
+	(398.17, 98.32) --
+	(398.17,103.31) --
+	(393.17,103.31) --
+	cycle;
+
+\path[fill=fillColor] (401.60, 97.13) --
+	(406.59, 97.13) --
+	(406.59,102.13) --
+	(401.60,102.13) --
+	cycle;
+
+\path[fill=fillColor] (410.03, 96.11) --
+	(415.02, 96.11) --
+	(415.02,101.11) --
+	(410.03,101.11) --
+	cycle;
+
+\path[fill=fillColor] (418.46, 95.11) --
+	(423.45, 95.11) --
+	(423.45,100.10) --
+	(418.46,100.10) --
+	cycle;
+
+\path[fill=fillColor] (426.88, 94.21) --
+	(431.88, 94.21) --
+	(431.88, 99.20) --
+	(426.88, 99.20) --
+	cycle;
+
+\path[fill=fillColor] (435.31, 93.32) --
+	(440.31, 93.32) --
+	(440.31, 98.32) --
+	(435.31, 98.32) --
+	cycle;
+
+\path[fill=fillColor] (443.74, 92.49) --
+	(448.73, 92.49) --
+	(448.73, 97.48) --
+	(443.74, 97.48) --
+	cycle;
+
+\path[fill=fillColor] (452.17, 91.72) --
+	(457.16, 91.72) --
+	(457.16, 96.71) --
+	(452.17, 96.71) --
+	cycle;
+
+\path[fill=fillColor] (460.60, 90.90) --
+	(465.59, 90.90) --
+	(465.59, 95.89) --
+	(460.60, 95.89) --
+	cycle;
+
+\path[fill=fillColor] (469.02, 90.00) --
+	(474.02, 90.00) --
+	(474.02, 94.99) --
+	(469.02, 94.99) --
+	cycle;
+
+\path[fill=fillColor] (477.45, 89.22) --
+	(482.45, 89.22) --
+	(482.45, 94.21) --
+	(477.45, 94.21) --
+	cycle;
+
+\path[fill=fillColor] (485.88, 88.51) --
+	(490.88, 88.51) --
+	(490.88, 93.51) --
+	(485.88, 93.51) --
+	cycle;
+
+\path[fill=fillColor] (494.31, 87.80) --
+	(499.30, 87.80) --
+	(499.30, 92.79) --
+	(494.31, 92.79) --
+	cycle;
+
+\path[fill=fillColor] (502.74, 87.15) --
+	(507.73, 87.15) --
+	(507.73, 92.14) --
+	(502.74, 92.14) --
+	cycle;
+
+\path[fill=fillColor] (511.17, 86.43) --
+	(516.16, 86.43) --
+	(516.16, 91.43) --
+	(511.17, 91.43) --
+	cycle;
+
+\path[fill=fillColor] (519.59, 85.84) --
+	(524.59, 85.84) --
+	(524.59, 90.83) --
+	(519.59, 90.83) --
+	cycle;
+
+\path[fill=fillColor] (528.02, 85.28) --
+	(533.02, 85.28) --
+	(533.02, 90.27) --
+	(528.02, 90.27) --
+	cycle;
+
+\path[fill=fillColor] (536.45, 84.68) --
+	(541.44, 84.68) --
+	(541.44, 89.67) --
+	(536.45, 89.67) --
+	cycle;
+
+\path[fill=fillColor] (544.88, 84.07) --
+	(549.87, 84.07) --
+	(549.87, 89.07) --
+	(544.88, 89.07) --
+	cycle;
+
+\path[fill=fillColor] (553.31, 83.47) --
+	(558.30, 83.47) --
+	(558.30, 88.47) --
+	(553.31, 88.47) --
+	cycle;
+
+\path[fill=fillColor] (561.73, 82.98) --
+	(566.73, 82.98) --
+	(566.73, 87.97) --
+	(561.73, 87.97) --
+	cycle;
+
+\path[fill=fillColor] (570.16, 82.43) --
+	(575.16, 82.43) --
+	(575.16, 87.42) --
+	(570.16, 87.42) --
+	cycle;
+\definecolor{drawColor}{RGB}{248,148,65}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.28,133.33) -- (323.35,133.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (319.81,129.79) -- (319.81,136.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.71,130.17) -- (331.78,130.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.24,126.64) -- (328.24,133.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.14,127.42) -- (340.20,127.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.67,123.89) -- (336.67,130.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.57,124.53) -- (348.63,124.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.10,121.00) -- (345.10,128.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.00,121.87) -- (357.06,121.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.53,118.34) -- (353.53,125.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (358.42,119.65) -- (365.49,119.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.96,116.11) -- (361.96,123.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (366.85,117.55) -- (373.92,117.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.38,114.02) -- (370.38,121.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (375.28,115.54) -- (382.34,115.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.81,112.01) -- (378.81,119.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.71,113.47) -- (390.77,113.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.24,109.94) -- (387.24,117.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.14,111.60) -- (399.20,111.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.67,108.06) -- (395.67,115.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (400.56,109.91) -- (407.63,109.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (404.10,106.37) -- (404.10,113.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.99,108.50) -- (416.06,108.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.52,104.97) -- (412.52,112.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.42,107.09) -- (424.48,107.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.95,103.56) -- (420.95,110.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.85,105.80) -- (432.91,105.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.38,102.27) -- (429.38,109.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.28,104.55) -- (441.34,104.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.81,101.02) -- (437.81,108.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.71,103.41) -- (449.77,103.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.24, 99.87) -- (446.24,106.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.13,102.33) -- (458.20,102.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.67, 98.80) -- (454.67,105.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.56,101.17) -- (466.63,101.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.09, 97.64) -- (463.09,104.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.99, 99.96) -- (475.05, 99.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (471.52, 96.42) -- (471.52,103.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.42, 98.89) -- (483.48, 98.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.95, 95.35) -- (479.95,102.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.85, 97.92) -- (491.91, 97.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.38, 94.38) -- (488.38,101.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.27, 96.93) -- (500.34, 96.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.81, 93.40) -- (496.81,100.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.70, 96.04) -- (508.77, 96.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.23, 92.51) -- (505.23, 99.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.13, 95.07) -- (517.19, 95.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (513.66, 91.53) -- (513.66, 98.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.56, 94.27) -- (525.62, 94.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.09, 90.73) -- (522.09, 97.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.99, 93.49) -- (534.05, 93.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (530.52, 89.96) -- (530.52, 97.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.42, 92.69) -- (542.48, 92.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.95, 89.16) -- (538.95, 96.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.84, 91.90) -- (550.91, 91.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.38, 88.37) -- (547.38, 95.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.27, 91.05) -- (559.34, 91.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.80, 87.52) -- (555.80, 94.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.70, 90.38) -- (567.76, 90.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.23, 86.85) -- (564.23, 93.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13, 89.65) -- (576.19, 89.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66, 86.12) -- (572.66, 93.18);
+\definecolor{drawColor}{RGB}{216,224,30}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (317.32,147.59) rectangle (322.31,152.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (317.32,147.59) -- (322.31,152.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (317.32,152.58) -- (322.31,147.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (325.75,143.39) rectangle (330.74,148.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (325.75,143.39) -- (330.74,148.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (325.75,148.38) -- (330.74,143.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.17,139.76) rectangle (339.17,144.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.17,139.76) -- (339.17,144.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.17,144.75) -- (339.17,139.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.60,135.95) rectangle (347.60,140.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.60,135.95) -- (347.60,140.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.60,140.94) -- (347.60,135.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.03,132.41) rectangle (356.03,137.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.03,132.41) -- (356.03,137.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.03,137.40) -- (356.03,132.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.46,129.50) rectangle (364.45,134.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.46,129.50) -- (364.45,134.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.46,134.50) -- (364.45,129.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.89,126.75) rectangle (372.88,131.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.89,126.75) -- (372.88,131.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.89,131.74) -- (372.88,126.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.31,124.08) rectangle (381.31,129.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.31,124.08) -- (381.31,129.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.31,129.08) -- (381.31,124.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.74,121.44) rectangle (389.74,126.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.74,121.44) -- (389.74,126.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.74,126.43) -- (389.74,121.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.17,118.99) rectangle (398.17,123.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.17,118.99) -- (398.17,123.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.17,123.99) -- (398.17,118.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.60,116.78) rectangle (406.59,121.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.60,116.78) -- (406.59,121.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.60,121.77) -- (406.59,116.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.03,115.02) rectangle (415.02,120.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.03,115.02) -- (415.02,120.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.03,120.02) -- (415.02,115.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.46,113.20) rectangle (423.45,118.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.46,113.20) -- (423.45,118.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.46,118.19) -- (423.45,113.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.88,111.53) rectangle (431.88,116.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.88,111.53) -- (431.88,116.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.88,116.52) -- (431.88,111.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.31,109.90) rectangle (440.31,114.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.31,109.90) -- (440.31,114.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.31,114.89) -- (440.31,109.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.74,108.47) rectangle (448.73,113.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.74,108.47) -- (448.73,113.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.74,113.47) -- (448.73,108.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.17,107.09) rectangle (457.16,112.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.17,107.09) -- (457.16,112.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.17,112.08) -- (457.16,107.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.60,105.59) rectangle (465.59,110.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.60,105.59) -- (465.59,110.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.60,110.58) -- (465.59,105.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.02,104.07) rectangle (474.02,109.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.02,104.07) -- (474.02,109.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.02,109.07) -- (474.02,104.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.45,102.72) rectangle (482.45,107.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.45,102.72) -- (482.45,107.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.45,107.72) -- (482.45,102.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.88,101.49) rectangle (490.88,106.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.88,101.49) -- (490.88,106.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.88,106.49) -- (490.88,101.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,100.25) rectangle (499.30,105.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,100.25) -- (499.30,105.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,105.25) -- (499.30,100.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.74, 99.11) rectangle (507.73,104.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.74, 99.11) -- (507.73,104.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.74,104.10) -- (507.73, 99.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.17, 97.90) rectangle (516.16,102.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.17, 97.90) -- (516.16,102.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.17,102.90) -- (516.16, 97.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.59, 96.90) rectangle (524.59,101.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.59, 96.90) -- (524.59,101.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.59,101.90) -- (524.59, 96.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.02, 95.91) rectangle (533.02,100.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.02, 95.91) -- (533.02,100.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.02,100.91) -- (533.02, 95.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.45, 94.94) rectangle (541.44, 99.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.45, 94.94) -- (541.44, 99.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.45, 99.93) -- (541.44, 94.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.88, 94.00) rectangle (549.87, 98.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.88, 94.00) -- (549.87, 98.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.88, 98.99) -- (549.87, 94.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.31, 92.89) rectangle (558.30, 97.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.31, 92.89) -- (558.30, 97.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.31, 97.89) -- (558.30, 92.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.73, 92.04) rectangle (566.73, 97.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.73, 92.04) -- (566.73, 97.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (561.73, 97.04) -- (566.73, 92.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16, 91.16) rectangle (575.16, 96.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16, 91.16) -- (575.16, 96.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (570.16, 96.15) -- (575.16, 91.16);
+\definecolor{fillColor}{RGB}{13,8,135}
+
+\path[fill=fillColor] (319.81, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (328.24, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (336.67, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (345.10, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (353.53, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (361.96, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (370.38, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (378.81, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (387.24, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (395.67, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (404.10, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (412.52, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (420.95, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (429.38, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (437.81, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (446.24, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (454.67, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (463.09, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (471.52, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (479.95, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (488.38, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (496.81, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (505.23, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (513.66, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (522.09, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (530.52, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (538.95, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (547.38, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (555.80, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (564.23, 58.94) circle (  2.50);
+
+\path[fill=fillColor] (572.66, 58.94) circle (  2.50);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (319.81, 30.69) rectangle (572.66,194.15);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (112.74,244.75) --
-	(112.74,247.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (198.16,244.75) --
-	(198.16,247.50);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.60,244.75) --
+	(111.60,247.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.88,244.75) --
+	(195.88,247.50);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (112.74,236.49) {0.1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.16,236.49) {0.2};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (111.60,236.49) {0.1};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (195.88,236.49) {0.2};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (155.45,224.45) {Exponential growth rate $r$ (1/day)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (153.74,224.45) {Exponential growth rate $r$ (1/day)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (319.81,244.75) --
+	(319.81,247.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.10,244.75) --
+	(404.10,247.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (488.38,244.75) --
+	(488.38,247.50);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (319.81,236.49) {0.0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (404.10,236.49) {0.1};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (488.38,236.49) {0.2};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,329.23) {Reproduction number $\mathcal R$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 31.06,332.94) rectangle (192.70,407.25);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 36.56,381.80) rectangle ( 51.02,396.25);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 38.01,389.03) -- ( 49.57,389.03);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] ( 43.79,389.03) circle (  2.50);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 36.56,367.35) rectangle ( 51.02,381.80);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{230,159,0}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 38.01,374.57) -- ( 49.57,374.57);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{230,159,0}
-
-\path[fill=fillColor] ( 43.79,378.46) --
-	( 47.15,372.63) --
-	( 40.43,372.63) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 36.56,352.89) rectangle ( 51.02,367.35);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{86,180,233}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 38.01,360.12) -- ( 49.57,360.12);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{86,180,233}
-
-\path[fill=fillColor] ( 41.29,357.62) --
-	( 46.29,357.62) --
-	( 46.29,362.62) --
-	( 41.29,362.62) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 36.56,338.44) rectangle ( 51.02,352.89);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 38.01,345.67) -- ( 49.57,345.67);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.26,345.67) -- ( 47.32,345.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.79,342.13) -- ( 43.79,349.20);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,386.00) {Intrinsic generation interval};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,371.54) {Forward serial interval ($\rho=0.5$)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,357.09) {Forward serial interval ($\rho=0$)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.52,342.63) {Forward serial interval ($\rho=-0.5$)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.31,419.03) {A};
-\end{scope}
-\begin{scope}
-\path[clip] (289.08,216.81) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{255,255,255}
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.08,216.81) rectangle (578.16,433.62);
-\end{scope}
-\begin{scope}
-\path[clip] (316.39,247.50) rectangle (572.66,410.96);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (316.39,247.50) rectangle (572.66,410.96);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (316.39,247.64) --
-	(319.64,248.49) --
-	(322.88,249.36) --
-	(326.12,250.25) --
-	(329.37,251.16) --
-	(332.61,252.09) --
-	(335.86,253.03) --
-	(339.10,254.00) --
-	(342.34,254.99) --
-	(345.59,255.99) --
-	(348.83,257.01) --
-	(352.08,258.06) --
-	(355.32,259.12) --
-	(358.56,260.20) --
-	(361.81,261.30) --
-	(365.05,262.42) --
-	(368.30,263.56) --
-	(371.54,264.72) --
-	(374.78,265.90) --
-	(378.03,267.10) --
-	(381.27,268.32) --
-	(384.51,269.55) --
-	(387.76,270.81) --
-	(391.00,272.08) --
-	(394.25,273.37) --
-	(397.49,274.68) --
-	(400.73,276.01) --
-	(403.98,277.36) --
-	(407.22,278.74) --
-	(410.47,280.13) --
-	(413.71,281.55) --
-	(416.95,282.99) --
-	(420.20,284.44) --
-	(423.44,285.91) --
-	(426.69,287.40) --
-	(429.93,288.91) --
-	(433.17,290.45) --
-	(436.42,292.02) --
-	(439.66,293.61) --
-	(442.90,295.23) --
-	(446.15,296.88) --
-	(449.39,298.55) --
-	(452.64,300.24) --
-	(455.88,301.95) --
-	(459.12,303.68) --
-	(462.37,305.44) --
-	(465.61,307.23) --
-	(468.86,309.04) --
-	(472.10,310.89) --
-	(475.34,312.76) --
-	(478.59,314.68) --
-	(481.83,316.62) --
-	(485.08,318.59) --
-	(488.32,320.58) --
-	(491.56,322.60) --
-	(494.81,324.66) --
-	(498.05,326.74) --
-	(501.29,328.85) --
-	(504.54,330.99) --
-	(507.78,333.17) --
-	(511.03,335.39) --
-	(514.27,337.63) --
-	(517.51,339.91) --
-	(520.76,342.22) --
-	(524.00,344.56) --
-	(527.25,346.93) --
-	(530.49,349.33) --
-	(533.73,351.76) --
-	(536.98,354.22) --
-	(540.22,356.72) --
-	(543.47,359.24) --
-	(546.71,361.80) --
-	(549.95,364.38) --
-	(553.20,367.00) --
-	(556.44,369.66) --
-	(559.68,372.34) --
-	(562.93,375.05) --
-	(566.17,377.80) --
-	(569.42,380.57) --
-	(572.66,383.38);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (319.64,248.30) --
-	(322.88,249.24) --
-	(326.12,250.18) --
-	(329.37,251.12) --
-	(332.61,252.08) --
-	(335.86,253.04) --
-	(339.10,254.00) --
-	(342.34,254.98) --
-	(345.59,255.96) --
-	(348.83,256.94) --
-	(352.08,257.93) --
-	(355.32,258.93) --
-	(358.56,259.94) --
-	(361.81,260.95) --
-	(365.05,261.97) --
-	(368.30,262.99) --
-	(371.54,264.02) --
-	(374.78,265.05) --
-	(378.03,266.09) --
-	(381.27,267.14) --
-	(384.51,268.20) --
-	(387.76,269.26) --
-	(391.00,270.34) --
-	(394.25,271.42) --
-	(397.49,272.50) --
-	(400.73,273.59) --
-	(403.98,274.68) --
-	(407.22,275.78) --
-	(410.47,276.87) --
-	(413.71,277.98) --
-	(416.95,279.10) --
-	(420.20,280.22) --
-	(423.44,281.36) --
-	(426.69,282.50) --
-	(429.93,283.64) --
-	(433.17,284.78) --
-	(436.42,285.92) --
-	(439.66,287.06) --
-	(442.90,288.19) --
-	(446.15,289.31) --
-	(449.39,290.45) --
-	(452.64,291.59) --
-	(455.88,292.74) --
-	(459.12,293.89) --
-	(462.37,295.05) --
-	(465.61,296.19) --
-	(468.86,297.34) --
-	(472.10,298.47) --
-	(475.34,299.59) --
-	(478.59,300.69) --
-	(481.83,301.79) --
-	(485.08,302.89) --
-	(488.32,303.98) --
-	(491.56,305.07) --
-	(494.81,306.15) --
-	(498.05,307.23) --
-	(501.29,308.29) --
-	(504.54,309.34) --
-	(507.78,310.37) --
-	(511.03,311.39) --
-	(514.27,312.39) --
-	(517.51,313.37) --
-	(520.76,314.35) --
-	(524.00,315.32) --
-	(527.25,316.28) --
-	(530.49,317.22) --
-	(533.73,318.16) --
-	(536.98,319.09) --
-	(540.22,320.00) --
-	(543.47,320.91) --
-	(546.71,321.80) --
-	(549.95,322.67) --
-	(553.20,323.54) --
-	(556.44,324.40) --
-	(559.68,325.24) --
-	(562.93,326.07) --
-	(566.17,326.89) --
-	(569.42,327.70) --
-	(572.66,328.50);
-\definecolor{drawColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (319.64,248.18) --
-	(322.88,249.15) --
-	(326.12,250.12) --
-	(329.37,251.09) --
-	(332.61,252.06) --
-	(335.86,253.02) --
-	(339.10,253.99) --
-	(342.34,254.95) --
-	(345.59,255.91) --
-	(348.83,256.87) --
-	(352.08,257.82) --
-	(355.32,258.78) --
-	(358.56,259.73) --
-	(361.81,260.68) --
-	(365.05,261.63) --
-	(368.30,262.58) --
-	(371.54,263.52) --
-	(374.78,264.45) --
-	(378.03,265.39) --
-	(381.27,266.33) --
-	(384.51,267.27) --
-	(387.76,268.21) --
-	(391.00,269.15) --
-	(394.25,270.09) --
-	(397.49,271.03) --
-	(400.73,271.96) --
-	(403.98,272.88) --
-	(407.22,273.79) --
-	(410.47,274.70) --
-	(413.71,275.60) --
-	(416.95,276.51) --
-	(420.20,277.43) --
-	(423.44,278.34) --
-	(426.69,279.25) --
-	(429.93,280.15) --
-	(433.17,281.03) --
-	(436.42,281.90) --
-	(439.66,282.74) --
-	(442.90,283.56) --
-	(446.15,284.35) --
-	(449.39,285.14) --
-	(452.64,285.93) --
-	(455.88,286.72) --
-	(459.12,287.50) --
-	(462.37,288.26) --
-	(465.61,289.01) --
-	(468.86,289.72) --
-	(472.10,290.40) --
-	(475.34,291.04) --
-	(478.59,291.64) --
-	(481.83,292.21) --
-	(485.08,292.76) --
-	(488.32,293.29) --
-	(491.56,293.79) --
-	(494.81,294.27) --
-	(498.05,294.72) --
-	(501.29,295.13) --
-	(504.54,295.51) --
-	(507.78,295.84) --
-	(511.03,296.12) --
-	(514.27,296.36) --
-	(517.51,296.57) --
-	(520.76,296.74) --
-	(524.00,296.88) --
-	(527.25,296.99) --
-	(530.49,297.06) --
-	(533.73,297.10) --
-	(536.98,297.11) --
-	(540.22,297.08) --
-	(543.47,297.02) --
-	(546.71,296.91) --
-	(549.95,296.77) --
-	(553.20,296.60) --
-	(556.44,296.39) --
-	(559.68,296.14) --
-	(562.93,295.86) --
-	(566.17,295.54) --
-	(569.42,295.19) --
-	(572.66,294.80);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (319.64,248.10) --
-	(322.88,249.10) --
-	(326.12,250.09) --
-	(329.37,251.07) --
-	(332.61,252.04) --
-	(335.86,253.00) --
-	(339.10,253.95) --
-	(342.34,254.90) --
-	(345.59,255.84) --
-	(348.83,256.77) --
-	(352.08,257.69) --
-	(355.32,258.60) --
-	(358.56,259.51) --
-	(361.81,260.40) --
-	(365.05,261.29) --
-	(368.30,262.16) --
-	(371.54,263.02) --
-	(374.78,263.87) --
-	(378.03,264.71) --
-	(381.27,265.55) --
-	(384.51,266.39) --
-	(387.76,267.23) --
-	(391.00,268.05) --
-	(394.25,268.87) --
-	(397.49,269.68) --
-	(400.73,270.47) --
-	(403.98,271.25) --
-	(407.22,272.00) --
-	(410.47,272.74) --
-	(413.71,273.47) --
-	(416.95,274.20) --
-	(420.20,274.93) --
-	(423.44,275.65) --
-	(426.69,276.36) --
-	(429.93,277.05) --
-	(433.17,277.72) --
-	(436.42,278.35) --
-	(439.66,278.95) --
-	(442.90,279.51) --
-	(446.15,280.03) --
-	(449.39,280.54) --
-	(452.64,281.05) --
-	(455.88,281.54) --
-	(459.12,282.01) --
-	(462.37,282.46) --
-	(465.61,282.87) --
-	(468.86,283.25) --
-	(472.10,283.58) --
-	(475.34,283.86) --
-	(478.59,284.08) --
-	(481.83,284.25) --
-	(485.08,284.40) --
-	(488.32,284.51) --
-	(491.56,284.59) --
-	(494.81,284.63) --
-	(498.05,284.63) --
-	(501.29,284.58) --
-	(504.54,284.48) --
-	(507.78,284.34) --
-	(511.03,284.13) --
-	(514.27,283.88) --
-	(517.51,283.57) --
-	(520.76,283.23) --
-	(524.00,282.84) --
-	(527.25,282.40) --
-	(530.49,281.93) --
-	(533.73,281.41) --
-	(536.98,280.84) --
-	(540.22,280.23) --
-	(543.47,279.57) --
-	(546.71,278.87) --
-	(549.95,278.12) --
-	(553.20,277.32) --
-	(556.44,276.47) --
-	(559.68,275.58) --
-	(562.93,274.65) --
-	(566.17,273.66) --
-	(569.42,272.64) --
-	(572.66,271.57);
-\definecolor{fillColor}{RGB}{0,158,115}
-
-\path[fill=fillColor] (316.39,251.38) --
-	(319.76,245.55) --
-	(313.03,245.55) --
-	cycle;
-
-\path[fill=fillColor] (324.94,253.76) --
-	(328.30,247.93) --
-	(321.57,247.93) --
-	cycle;
-
-\path[fill=fillColor] (333.48,256.20) --
-	(336.84,250.37) --
-	(330.11,250.37) --
-	cycle;
-
-\path[fill=fillColor] (342.02,258.70) --
-	(345.38,252.88) --
-	(338.66,252.88) --
-	cycle;
-
-\path[fill=fillColor] (350.56,261.27) --
-	(353.93,255.44) --
-	(347.20,255.44) --
-	cycle;
-
-\path[fill=fillColor] (359.10,263.89) --
-	(362.47,258.07) --
-	(355.74,258.07) --
-	cycle;
-
-\path[fill=fillColor] (367.65,266.57) --
-	(371.01,260.75) --
-	(364.28,260.75) --
-	cycle;
-
-\path[fill=fillColor] (376.19,269.31) --
-	(379.55,263.48) --
-	(372.83,263.48) --
-	cycle;
-
-\path[fill=fillColor] (384.73,272.09) --
-	(388.09,266.27) --
-	(381.37,266.27) --
-	cycle;
-
-\path[fill=fillColor] (393.27,274.93) --
-	(396.64,269.10) --
-	(389.91,269.10) --
-	cycle;
-
-\path[fill=fillColor] (401.82,277.80) --
-	(405.18,271.97) --
-	(398.45,271.97) --
-	cycle;
-
-\path[fill=fillColor] (410.36,280.71) --
-	(413.72,274.89) --
-	(406.99,274.89) --
-	cycle;
-
-\path[fill=fillColor] (418.90,283.66) --
-	(422.26,277.83) --
-	(415.54,277.83) --
-	cycle;
-
-\path[fill=fillColor] (427.44,286.63) --
-	(430.81,280.80) --
-	(424.08,280.80) --
-	cycle;
-
-\path[fill=fillColor] (435.98,289.62) --
-	(439.35,283.79) --
-	(432.62,283.79) --
-	cycle;
-
-\path[fill=fillColor] (444.53,292.62) --
-	(447.89,286.79) --
-	(441.16,286.79) --
-	cycle;
-
-\path[fill=fillColor] (453.07,295.63) --
-	(456.43,289.80) --
-	(449.71,289.80) --
-	cycle;
-
-\path[fill=fillColor] (461.61,298.63) --
-	(464.97,292.81) --
-	(458.25,292.81) --
-	cycle;
-
-\path[fill=fillColor] (470.15,301.63) --
-	(473.52,295.80) --
-	(466.79,295.80) --
-	cycle;
-
-\path[fill=fillColor] (478.70,304.60) --
-	(482.06,298.77) --
-	(475.33,298.77) --
-	cycle;
-
-\path[fill=fillColor] (487.24,307.54) --
-	(490.60,301.71) --
-	(483.87,301.71) --
-	cycle;
-
-\path[fill=fillColor] (495.78,310.43) --
-	(499.14,304.60) --
-	(492.42,304.60) --
-	cycle;
-
-\path[fill=fillColor] (504.32,313.26) --
-	(507.69,307.44) --
-	(500.96,307.44) --
-	cycle;
-
-\path[fill=fillColor] (512.86,316.03) --
-	(516.23,310.20) --
-	(509.50,310.20) --
-	cycle;
-
-\path[fill=fillColor] (521.41,318.70) --
-	(524.77,312.87) --
-	(518.04,312.87) --
-	cycle;
-
-\path[fill=fillColor] (529.95,321.27) --
-	(533.31,315.44) --
-	(526.59,315.44) --
-	cycle;
-
-\path[fill=fillColor] (538.49,323.72) --
-	(541.85,317.89) --
-	(535.13,317.89) --
-	cycle;
-
-\path[fill=fillColor] (547.03,326.03) --
-	(550.40,320.20) --
-	(543.67,320.20) --
-	cycle;
-
-\path[fill=fillColor] (555.58,328.18) --
-	(558.94,322.35) --
-	(552.21,322.35) --
-	cycle;
-
-\path[fill=fillColor] (564.12,330.14) --
-	(567.48,324.32) --
-	(560.75,324.32) --
-	cycle;
-
-\path[fill=fillColor] (572.66,331.91) --
-	(576.02,326.08) --
-	(569.30,326.08) --
-	cycle;
-\definecolor{fillColor}{RGB}{240,228,66}
-
-\path[fill=fillColor] (313.90,245.00) --
-	(318.89,245.00) --
-	(318.89,249.99) --
-	(313.90,249.99) --
-	cycle;
-
-\path[fill=fillColor] (322.44,247.36) --
-	(327.43,247.36) --
-	(327.43,252.36) --
-	(322.44,252.36) --
-	cycle;
-
-\path[fill=fillColor] (330.98,249.77) --
-	(335.98,249.77) --
-	(335.98,254.76) --
-	(330.98,254.76) --
-	cycle;
-
-\path[fill=fillColor] (339.52,252.21) --
-	(344.52,252.21) --
-	(344.52,257.20) --
-	(339.52,257.20) --
-	cycle;
-
-\path[fill=fillColor] (348.06,254.68) --
-	(353.06,254.68) --
-	(353.06,259.67) --
-	(348.06,259.67) --
-	cycle;
-
-\path[fill=fillColor] (356.61,257.17) --
-	(361.60,257.17) --
-	(361.60,262.16) --
-	(356.61,262.16) --
-	cycle;
-
-\path[fill=fillColor] (365.15,259.67) --
-	(370.14,259.67) --
-	(370.14,264.67) --
-	(365.15,264.67) --
-	cycle;
-
-\path[fill=fillColor] (373.69,262.19) --
-	(378.69,262.19) --
-	(378.69,267.19) --
-	(373.69,267.19) --
-	cycle;
-
-\path[fill=fillColor] (382.23,264.71) --
-	(387.23,264.71) --
-	(387.23,269.70) --
-	(382.23,269.70) --
-	cycle;
-
-\path[fill=fillColor] (390.78,267.21) --
-	(395.77,267.21) --
-	(395.77,272.21) --
-	(390.78,272.21) --
-	cycle;
-
-\path[fill=fillColor] (399.32,269.70) --
-	(404.31,269.70) --
-	(404.31,274.69) --
-	(399.32,274.69) --
-	cycle;
-
-\path[fill=fillColor] (407.86,272.15) --
-	(412.86,272.15) --
-	(412.86,277.15) --
-	(407.86,277.15) --
-	cycle;
-
-\path[fill=fillColor] (416.40,274.57) --
-	(421.40,274.57) --
-	(421.40,279.56) --
-	(416.40,279.56) --
-	cycle;
-
-\path[fill=fillColor] (424.94,276.93) --
-	(429.94,276.93) --
-	(429.94,281.93) --
-	(424.94,281.93) --
-	cycle;
-
-\path[fill=fillColor] (433.49,279.22) --
-	(438.48,279.22) --
-	(438.48,284.22) --
-	(433.49,284.22) --
-	cycle;
-
-\path[fill=fillColor] (442.03,281.44) --
-	(447.02,281.44) --
-	(447.02,286.43) --
-	(442.03,286.43) --
-	cycle;
-
-\path[fill=fillColor] (450.57,283.55) --
-	(455.57,283.55) --
-	(455.57,288.55) --
-	(450.57,288.55) --
-	cycle;
-
-\path[fill=fillColor] (459.11,285.55) --
-	(464.11,285.55) --
-	(464.11,290.55) --
-	(459.11,290.55) --
-	cycle;
-
-\path[fill=fillColor] (467.66,287.42) --
-	(472.65,287.42) --
-	(472.65,292.42) --
-	(467.66,292.42) --
-	cycle;
-
-\path[fill=fillColor] (476.20,289.14) --
-	(481.19,289.14) --
-	(481.19,294.14) --
-	(476.20,294.14) --
-	cycle;
-
-\path[fill=fillColor] (484.74,290.69) --
-	(489.74,290.69) --
-	(489.74,295.69) --
-	(484.74,295.69) --
-	cycle;
-
-\path[fill=fillColor] (493.28,292.05) --
-	(498.28,292.05) --
-	(498.28,297.04) --
-	(493.28,297.04) --
-	cycle;
-
-\path[fill=fillColor] (501.82,293.19) --
-	(506.82,293.19) --
-	(506.82,298.19) --
-	(501.82,298.19) --
-	cycle;
-
-\path[fill=fillColor] (510.37,294.09) --
-	(515.36,294.09) --
-	(515.36,299.09) --
-	(510.37,299.09) --
-	cycle;
-
-\path[fill=fillColor] (518.91,294.73) --
-	(523.90,294.73) --
-	(523.90,299.73) --
-	(518.91,299.73) --
-	cycle;
-
-\path[fill=fillColor] (527.45,295.08) --
-	(532.45,295.08) --
-	(532.45,300.07) --
-	(527.45,300.07) --
-	cycle;
-
-\path[fill=fillColor] (535.99,295.11) --
-	(540.99,295.11) --
-	(540.99,300.11) --
-	(535.99,300.11) --
-	cycle;
-
-\path[fill=fillColor] (544.54,294.80) --
-	(549.53,294.80) --
-	(549.53,299.79) --
-	(544.54,299.79) --
-	cycle;
-
-\path[fill=fillColor] (553.08,294.12) --
-	(558.07,294.12) --
-	(558.07,299.12) --
-	(553.08,299.12) --
-	cycle;
-
-\path[fill=fillColor] (561.62,293.05) --
-	(566.62,293.05) --
-	(566.62,298.05) --
-	(561.62,298.05) --
-	cycle;
-
-\path[fill=fillColor] (570.16,291.57) --
-	(575.16,291.57) --
-	(575.16,296.57) --
-	(570.16,296.57) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.86,247.50) -- (319.93,247.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.39,243.96) -- (316.39,251.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.40,249.85) -- (328.47,249.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.94,246.32) -- (324.94,253.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.95,252.22) -- (337.01,252.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.48,248.69) -- (333.48,255.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.49,254.60) -- (345.55,254.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.02,251.07) -- (342.02,258.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.03,256.98) -- (354.09,256.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.56,253.45) -- (350.56,260.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.57,259.35) -- (362.64,259.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.10,255.81) -- (359.10,262.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.11,261.70) -- (371.18,261.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (367.65,258.16) -- (367.65,265.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.66,264.01) -- (379.72,264.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.19,260.48) -- (376.19,267.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.20,266.28) -- (388.26,266.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.73,262.75) -- (384.73,269.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.74,268.50) -- (396.81,268.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.27,264.97) -- (393.27,272.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.28,270.64) -- (405.35,270.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.82,267.11) -- (401.82,274.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.83,272.70) -- (413.89,272.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.36,269.17) -- (410.36,276.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37,274.66) -- (422.43,274.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,271.13) -- (418.90,278.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.91,276.50) -- (430.97,276.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.44,272.97) -- (427.44,280.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,278.21) -- (439.52,278.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.98,274.67) -- (435.98,281.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.99,279.76) -- (448.06,279.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.53,276.23) -- (444.53,283.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.54,281.15) -- (456.60,281.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.07,277.61) -- (453.07,284.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.08,282.34) -- (465.14,282.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.61,278.81) -- (461.61,285.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.62,283.32) -- (473.69,283.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.15,279.79) -- (470.15,286.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.16,284.08) -- (482.23,284.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.70,280.55) -- (478.70,287.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.71,284.58) -- (490.77,284.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.24,281.04) -- (487.24,288.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.25,284.80) -- (499.31,284.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.78,281.27) -- (495.78,288.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.79,284.72) -- (507.85,284.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.32,281.19) -- (504.32,288.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.33,284.32) -- (516.40,284.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.86,280.79) -- (512.86,287.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (517.87,283.58) -- (524.94,283.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.41,280.04) -- (521.41,287.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.42,282.47) -- (533.48,282.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.95,278.94) -- (529.95,286.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,280.98) -- (542.02,280.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (538.49,277.44) -- (538.49,284.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (543.50,279.09) -- (550.57,279.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.03,275.56) -- (547.03,282.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.04,276.80) -- (559.11,276.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (555.58,273.26) -- (555.58,280.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.59,274.10) -- (567.65,274.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.12,270.57) -- (564.12,277.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13,271.01) -- (576.19,271.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66,267.47) -- (572.66,274.54);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] (316.39,247.50) circle (  2.50);
-
-\path[fill=fillColor] (324.94,249.88) circle (  2.50);
-
-\path[fill=fillColor] (333.48,252.37) circle (  2.50);
-
-\path[fill=fillColor] (342.02,254.96) circle (  2.50);
-
-\path[fill=fillColor] (350.56,257.67) circle (  2.50);
-
-\path[fill=fillColor] (359.10,260.49) circle (  2.50);
-
-\path[fill=fillColor] (367.65,263.43) circle (  2.50);
-
-\path[fill=fillColor] (376.19,266.50) circle (  2.50);
-
-\path[fill=fillColor] (384.73,269.69) circle (  2.50);
-
-\path[fill=fillColor] (393.27,273.02) circle (  2.50);
-
-\path[fill=fillColor] (401.82,276.48) circle (  2.50);
-
-\path[fill=fillColor] (410.36,280.09) circle (  2.50);
-
-\path[fill=fillColor] (418.90,283.85) circle (  2.50);
-
-\path[fill=fillColor] (427.44,287.76) circle (  2.50);
-
-\path[fill=fillColor] (435.98,291.82) circle (  2.50);
-
-\path[fill=fillColor] (444.53,296.05) circle (  2.50);
-
-\path[fill=fillColor] (453.07,300.46) circle (  2.50);
-
-\path[fill=fillColor] (461.61,305.04) circle (  2.50);
-
-\path[fill=fillColor] (470.15,309.80) circle (  2.50);
-
-\path[fill=fillColor] (478.70,314.74) circle (  2.50);
-
-\path[fill=fillColor] (487.24,319.89) circle (  2.50);
-
-\path[fill=fillColor] (495.78,325.23) circle (  2.50);
-
-\path[fill=fillColor] (504.32,330.79) circle (  2.50);
-
-\path[fill=fillColor] (512.86,336.55) circle (  2.50);
-
-\path[fill=fillColor] (521.41,342.55) circle (  2.50);
-
-\path[fill=fillColor] (529.95,348.77) circle (  2.50);
-
-\path[fill=fillColor] (538.49,355.23) circle (  2.50);
-
-\path[fill=fillColor] (547.03,361.93) circle (  2.50);
-
-\path[fill=fillColor] (555.58,368.89) circle (  2.50);
-
-\path[fill=fillColor] (564.12,376.12) circle (  2.50);
-
-\path[fill=fillColor] (572.66,383.61) circle (  2.50);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (316.39,247.50) rectangle (572.66,410.96);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,244.47) {1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,291.17) {2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,337.88) {3};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (311.44,384.58) {4};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,247.50) --
-	(316.39,247.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,294.20) --
-	(316.39,294.20);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,340.91) --
-	(316.39,340.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (313.64,387.61) --
-	(316.39,387.61);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (316.39,244.75) --
-	(316.39,247.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (401.82,244.75) --
-	(401.82,247.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (487.24,244.75) --
-	(487.24,247.50);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (316.39,236.49) {0.0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (401.82,236.49) {0.1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (487.24,236.49) {0.2};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (444.53,224.45) {Exponential growth rate $r$ (1/day)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,329.23) {Reproduction number ${\mathcal R}_{\textrm{\tiny intrinsic}}$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (320.07,332.94) rectangle (481.85,407.25);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (325.57,381.80) rectangle (340.02,396.25);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (327.01,389.03) -- (338.58,389.03);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] (332.80,389.03) circle (  2.50);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (325.57,367.35) rectangle (340.02,381.80);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (327.01,374.57) -- (338.58,374.57);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{0,158,115}
-
-\path[fill=fillColor] (332.80,378.46) --
-	(336.16,372.63) --
-	(329.43,372.63) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (325.57,352.89) rectangle (340.02,367.35);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{240,228,66}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (327.01,360.12) -- (338.58,360.12);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{240,228,66}
-
-\path[fill=fillColor] (330.30,357.62) --
-	(335.29,357.62) --
-	(335.29,362.62) --
-	(330.30,362.62) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (325.57,338.44) rectangle (340.02,352.89);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (327.01,345.67) -- (338.58,345.67);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,114,178}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.26,345.67) -- (336.33,345.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (332.80,342.13) -- (332.80,349.20);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,386.00) {Intrinsic generation interval};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,371.54) {Intrinsic serial interval ($\rho=0.5$)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,357.09) {Intrinsic serial interval ($\rho=0$)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (345.52,342.63) {Intrinsic serial interval ($\rho=-0.5$)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (316.39,419.03) {B};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,216.81);
-\definecolor{drawColor}{RGB}{255,255,255}
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (289.08,216.81);
-\end{scope}
-\begin{scope}
-\path[clip] ( 27.31, 30.69) rectangle (283.58,194.15);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 27.31, 30.69) rectangle (283.58,194.15);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31, 54.98) --
-	( 30.56, 54.98) --
-	( 33.80, 54.98) --
-	( 37.04, 54.98) --
-	( 40.29, 54.98) --
-	( 43.53, 54.98) --
-	( 46.78, 54.98) --
-	( 50.02, 54.98) --
-	( 53.26, 54.98) --
-	( 56.51, 54.98) --
-	( 59.75, 54.98) --
-	( 63.00, 54.98) --
-	( 66.24, 54.98) --
-	( 69.48, 54.98) --
-	( 72.73, 54.98) --
-	( 75.97, 54.98) --
-	( 79.22, 54.98) --
-	( 82.46, 54.98) --
-	( 85.70, 54.98) --
-	( 88.95, 54.98) --
-	( 92.19, 54.98) --
-	( 95.43, 54.98) --
-	( 98.68, 54.98) --
-	(101.92, 54.98) --
-	(105.17, 54.98) --
-	(108.41, 54.98) --
-	(111.65, 54.98) --
-	(114.90, 54.98) --
-	(118.14, 54.98) --
-	(121.39, 54.98) --
-	(124.63, 54.98) --
-	(127.87, 54.98) --
-	(131.12, 54.98) --
-	(134.36, 54.98) --
-	(137.61, 54.98) --
-	(140.85, 54.98) --
-	(144.09, 54.98) --
-	(147.34, 54.98) --
-	(150.58, 54.98) --
-	(153.82, 54.98) --
-	(157.07, 54.98) --
-	(160.31, 54.98) --
-	(163.56, 54.98) --
-	(166.80, 54.98) --
-	(170.04, 54.98) --
-	(173.29, 54.98) --
-	(176.53, 54.98) --
-	(179.78, 54.98) --
-	(183.02, 54.98) --
-	(186.26, 54.98) --
-	(189.51, 54.98) --
-	(192.75, 54.98) --
-	(196.00, 54.98) --
-	(199.24, 54.98) --
-	(202.48, 54.98) --
-	(205.73, 54.98) --
-	(208.97, 54.98) --
-	(212.21, 54.98) --
-	(215.46, 54.98) --
-	(218.70, 54.98) --
-	(221.95, 54.98) --
-	(225.19, 54.98) --
-	(228.43, 54.98) --
-	(231.68, 54.98) --
-	(234.92, 54.98) --
-	(238.17, 54.98) --
-	(241.41, 54.98) --
-	(244.65, 54.98) --
-	(247.90, 54.98) --
-	(251.14, 54.98) --
-	(254.39, 54.98) --
-	(257.63, 54.98) --
-	(260.87, 54.98) --
-	(264.12, 54.98) --
-	(267.36, 54.98) --
-	(270.60, 54.98) --
-	(273.85, 54.98) --
-	(277.09, 54.98) --
-	(280.34, 54.98) --
-	(283.58, 54.98);
-\definecolor{drawColor}{RGB}{230,159,0}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31, 55.70) --
-	( 30.56, 56.81) --
-	( 33.80, 57.90) --
-	( 37.04, 58.98) --
-	( 40.29, 60.06) --
-	( 43.53, 61.12) --
-	( 46.78, 62.16) --
-	( 50.02, 63.20) --
-	( 53.26, 64.22) --
-	( 56.51, 65.23) --
-	( 59.75, 66.23) --
-	( 63.00, 67.21) --
-	( 66.24, 68.18) --
-	( 69.48, 69.14) --
-	( 72.73, 70.09) --
-	( 75.97, 71.03) --
-	( 79.22, 71.95) --
-	( 82.46, 72.86) --
-	( 85.70, 73.77) --
-	( 88.95, 74.66) --
-	( 92.19, 75.53) --
-	( 95.43, 76.39) --
-	( 98.68, 77.24) --
-	(101.92, 78.07) --
-	(105.17, 78.90) --
-	(108.41, 79.71) --
-	(111.65, 80.51) --
-	(114.90, 81.30) --
-	(118.14, 82.08) --
-	(121.39, 82.85) --
-	(124.63, 83.61) --
-	(127.87, 84.35) --
-	(131.12, 85.08) --
-	(134.36, 85.79) --
-	(137.61, 86.49) --
-	(140.85, 87.19) --
-	(144.09, 87.87) --
-	(147.34, 88.55) --
-	(150.58, 89.23) --
-	(153.82, 89.91) --
-	(157.07, 90.59) --
-	(160.31, 91.26) --
-	(163.56, 91.92) --
-	(166.80, 92.57) --
-	(170.04, 93.22) --
-	(173.29, 93.86) --
-	(176.53, 94.49) --
-	(179.78, 95.12) --
-	(183.02, 95.75) --
-	(186.26, 96.37) --
-	(189.51, 96.99) --
-	(192.75, 97.61) --
-	(196.00, 98.22) --
-	(199.24, 98.82) --
-	(202.48, 99.42) --
-	(205.73,100.02) --
-	(208.97,100.61) --
-	(212.21,101.20) --
-	(215.46,101.78) --
-	(218.70,102.35) --
-	(221.95,102.93) --
-	(225.19,103.50) --
-	(228.43,104.06) --
-	(231.68,104.62) --
-	(234.92,105.17) --
-	(238.17,105.72) --
-	(241.41,106.27) --
-	(244.65,106.81) --
-	(247.90,107.34) --
-	(251.14,107.87) --
-	(254.39,108.40) --
-	(257.63,108.92) --
-	(260.87,109.43) --
-	(264.12,109.95) --
-	(267.36,110.45) --
-	(270.60,110.95) --
-	(273.85,111.45) --
-	(277.09,111.95) --
-	(280.34,112.43) --
-	(283.58,112.92);
-\definecolor{drawColor}{RGB}{86,180,233}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31, 55.54) --
-	( 30.56, 57.34) --
-	( 33.80, 59.12) --
-	( 37.04, 60.88) --
-	( 40.29, 62.63) --
-	( 43.53, 64.35) --
-	( 46.78, 66.06) --
-	( 50.02, 67.75) --
-	( 53.26, 69.43) --
-	( 56.51, 71.08) --
-	( 59.75, 72.71) --
-	( 63.00, 74.33) --
-	( 66.24, 75.93) --
-	( 69.48, 77.51) --
-	( 72.73, 79.07) --
-	( 75.97, 80.62) --
-	( 79.22, 82.15) --
-	( 82.46, 83.66) --
-	( 85.70, 85.16) --
-	( 88.95, 86.63) --
-	( 92.19, 88.09) --
-	( 95.43, 89.53) --
-	( 98.68, 90.94) --
-	(101.92, 92.34) --
-	(105.17, 93.72) --
-	(108.41, 95.08) --
-	(111.65, 96.43) --
-	(114.90, 97.76) --
-	(118.14, 99.08) --
-	(121.39,100.38) --
-	(124.63,101.67) --
-	(127.87,102.92) --
-	(131.12,104.16) --
-	(134.36,105.37) --
-	(137.61,106.57) --
-	(140.85,107.76) --
-	(144.09,108.93) --
-	(147.34,110.10) --
-	(150.58,111.27) --
-	(153.82,112.43) --
-	(157.07,113.59) --
-	(160.31,114.75) --
-	(163.56,115.89) --
-	(166.80,117.02) --
-	(170.04,118.14) --
-	(173.29,119.26) --
-	(176.53,120.36) --
-	(179.78,121.46) --
-	(183.02,122.55) --
-	(186.26,123.63) --
-	(189.51,124.71) --
-	(192.75,125.78) --
-	(196.00,126.85) --
-	(199.24,127.91) --
-	(202.48,128.96) --
-	(205.73,130.00) --
-	(208.97,131.03) --
-	(212.21,132.06) --
-	(215.46,133.08) --
-	(218.70,134.09) --
-	(221.95,135.10) --
-	(225.19,136.09) --
-	(228.43,137.09) --
-	(231.68,138.07) --
-	(234.92,139.04) --
-	(238.17,140.01) --
-	(241.41,140.97) --
-	(244.65,141.92) --
-	(247.90,142.87) --
-	(251.14,143.81) --
-	(254.39,144.74) --
-	(257.63,145.66) --
-	(260.87,146.58) --
-	(264.12,147.48) --
-	(267.36,148.38) --
-	(270.60,149.28) --
-	(273.85,150.16) --
-	(277.09,151.04) --
-	(280.34,151.91) --
-	(283.58,152.77);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 55.20) --
-	( 30.56, 57.64) --
-	( 33.80, 60.07) --
-	( 37.04, 62.47) --
-	( 40.29, 64.85) --
-	( 43.53, 67.21) --
-	( 46.78, 69.55) --
-	( 50.02, 71.86) --
-	( 53.26, 74.15) --
-	( 56.51, 76.43) --
-	( 59.75, 78.67) --
-	( 63.00, 80.90) --
-	( 66.24, 83.10) --
-	( 69.48, 85.29) --
-	( 72.73, 87.45) --
-	( 75.97, 89.59) --
-	( 79.22, 91.71) --
-	( 82.46, 93.81) --
-	( 85.70, 95.89) --
-	( 88.95, 97.94) --
-	( 92.19, 99.98) --
-	( 95.43,101.98) --
-	( 98.68,103.97) --
-	(101.92,105.93) --
-	(105.17,107.87) --
-	(108.41,109.79) --
-	(111.65,111.69) --
-	(114.90,113.57) --
-	(118.14,115.43) --
-	(121.39,117.28) --
-	(124.63,119.10) --
-	(127.87,120.88) --
-	(131.12,122.64) --
-	(134.36,124.37) --
-	(137.61,126.09) --
-	(140.85,127.78) --
-	(144.09,129.47) --
-	(147.34,131.15) --
-	(150.58,132.82) --
-	(153.82,134.50) --
-	(157.07,136.18) --
-	(160.31,137.85) --
-	(163.56,139.50) --
-	(166.80,141.14) --
-	(170.04,142.77) --
-	(173.29,144.39) --
-	(176.53,146.00) --
-	(179.78,147.60) --
-	(183.02,149.19) --
-	(186.26,150.78) --
-	(189.51,152.36) --
-	(192.75,153.93) --
-	(196.00,155.49) --
-	(199.24,157.04) --
-	(202.48,158.58) --
-	(205.73,160.11) --
-	(208.97,161.63) --
-	(212.21,163.15) --
-	(215.46,164.65) --
-	(218.70,166.14) --
-	(221.95,167.63) --
-	(225.19,169.10) --
-	(228.43,170.57) --
-	(231.68,172.02) --
-	(234.92,173.47) --
-	(238.17,174.91) --
-	(241.41,176.33) --
-	(244.65,177.75) --
-	(247.90,179.16) --
-	(251.14,180.56) --
-	(254.39,181.95) --
-	(257.63,183.33) --
-	(260.87,184.70) --
-	(264.12,186.06) --
-	(267.36,187.41) --
-	(270.60,188.75) --
-	(273.85,190.08) --
-	(277.09,191.40) --
-	(280.34,192.72) --
-	(283.58,194.02);
-\definecolor{fillColor}{RGB}{230,159,0}
-
-\path[fill=fillColor] ( 27.31, 59.60) --
-	( 30.68, 53.77) --
-	( 23.95, 53.77) --
-	cycle;
-
-\path[fill=fillColor] ( 35.86, 62.47) --
-	( 39.22, 56.65) --
-	( 32.49, 56.65) --
-	cycle;
-
-\path[fill=fillColor] ( 44.40, 65.07) --
-	( 47.76, 59.25) --
-	( 41.03, 59.25) --
-	cycle;
-
-\path[fill=fillColor] ( 52.94, 68.02) --
-	( 56.30, 62.19) --
-	( 49.58, 62.19) --
-	cycle;
-
-\path[fill=fillColor] ( 61.48, 70.77) --
-	( 64.85, 64.95) --
-	( 58.12, 64.95) --
-	cycle;
-
-\path[fill=fillColor] ( 70.02, 73.26) --
-	( 73.39, 67.44) --
-	( 66.66, 67.44) --
-	cycle;
-
-\path[fill=fillColor] ( 78.57, 75.65) --
-	( 81.93, 69.83) --
-	( 75.20, 69.83) --
-	cycle;
-
-\path[fill=fillColor] ( 87.11, 78.08) --
-	( 90.47, 72.25) --
-	( 83.75, 72.25) --
-	cycle;
-
-\path[fill=fillColor] ( 95.65, 80.50) --
-	( 99.01, 74.67) --
-	( 92.29, 74.67) --
-	cycle;
-
-\path[fill=fillColor] (104.19, 82.71) --
-	(107.56, 76.88) --
-	(100.83, 76.88) --
-	cycle;
-
-\path[fill=fillColor] (112.74, 84.81) --
-	(116.10, 78.99) --
-	(109.37, 78.99) --
-	cycle;
-
-\path[fill=fillColor] (121.28, 86.66) --
-	(124.64, 80.84) --
-	(117.91, 80.84) --
-	cycle;
-
-\path[fill=fillColor] (129.82, 88.60) --
-	(133.18, 82.78) --
-	(126.46, 82.78) --
-	cycle;
-
-\path[fill=fillColor] (138.36, 90.48) --
-	(141.73, 84.65) --
-	(135.00, 84.65) --
-	cycle;
-
-\path[fill=fillColor] (146.90, 92.35) --
-	(150.27, 86.53) --
-	(143.54, 86.53) --
-	cycle;
-
-\path[fill=fillColor] (155.45, 94.13) --
-	(158.81, 88.30) --
-	(152.08, 88.30) --
-	cycle;
-
-\path[fill=fillColor] (163.99, 95.79) --
-	(167.35, 89.97) --
-	(160.63, 89.97) --
-	cycle;
-
-\path[fill=fillColor] (172.53, 97.50) --
-	(175.89, 91.67) --
-	(169.17, 91.67) --
-	cycle;
-
-\path[fill=fillColor] (181.07, 99.31) --
-	(184.44, 93.48) --
-	(177.71, 93.48) --
-	cycle;
-
-\path[fill=fillColor] (189.62,100.91) --
-	(192.98, 95.09) --
-	(186.25, 95.09) --
-	cycle;
-
-\path[fill=fillColor] (198.16,102.55) --
-	(201.52, 96.72) --
-	(194.79, 96.72) --
-	cycle;
-
-\path[fill=fillColor] (206.70,104.08) --
-	(210.06, 98.25) --
-	(203.34, 98.25) --
-	cycle;
-
-\path[fill=fillColor] (215.24,105.58) --
-	(218.61, 99.75) --
-	(211.88, 99.75) --
-	cycle;
-
-\path[fill=fillColor] (223.78,107.13) --
-	(227.15,101.30) --
-	(220.42,101.30) --
-	cycle;
-
-\path[fill=fillColor] (232.33,108.61) --
-	(235.69,102.78) --
-	(228.96,102.78) --
-	cycle;
-
-\path[fill=fillColor] (240.87,109.99) --
-	(244.23,104.16) --
-	(237.51,104.16) --
-	cycle;
-
-\path[fill=fillColor] (249.41,111.47) --
-	(252.77,105.64) --
-	(246.05,105.64) --
-	cycle;
-
-\path[fill=fillColor] (257.95,112.80) --
-	(261.32,106.97) --
-	(254.59,106.97) --
-	cycle;
-
-\path[fill=fillColor] (266.50,114.25) --
-	(269.86,108.43) --
-	(263.13,108.43) --
-	cycle;
-
-\path[fill=fillColor] (275.04,115.51) --
-	(278.40,109.68) --
-	(271.67,109.68) --
-	cycle;
-
-\path[fill=fillColor] (283.58,116.83) --
-	(286.94,111.01) --
-	(280.22,111.01) --
-	cycle;
-\definecolor{fillColor}{RGB}{86,180,233}
-
-\path[fill=fillColor] ( 24.82, 53.14) --
-	( 29.81, 53.14) --
-	( 29.81, 58.14) --
-	( 24.82, 58.14) --
-	cycle;
-
-\path[fill=fillColor] ( 33.36, 57.75) --
-	( 38.35, 57.75) --
-	( 38.35, 62.75) --
-	( 33.36, 62.75) --
-	cycle;
-
-\path[fill=fillColor] ( 41.90, 61.97) --
-	( 46.90, 61.97) --
-	( 46.90, 66.96) --
-	( 41.90, 66.96) --
-	cycle;
-
-\path[fill=fillColor] ( 50.44, 66.76) --
-	( 55.44, 66.76) --
-	( 55.44, 71.75) --
-	( 50.44, 71.75) --
-	cycle;
-
-\path[fill=fillColor] ( 58.98, 71.20) --
-	( 63.98, 71.20) --
-	( 63.98, 76.19) --
-	( 58.98, 76.19) --
-	cycle;
-
-\path[fill=fillColor] ( 67.53, 75.33) --
-	( 72.52, 75.33) --
-	( 72.52, 80.32) --
-	( 67.53, 80.32) --
-	cycle;
-
-\path[fill=fillColor] ( 76.07, 79.35) --
-	( 81.06, 79.35) --
-	( 81.06, 84.34) --
-	( 76.07, 84.34) --
-	cycle;
-
-\path[fill=fillColor] ( 84.61, 83.44) --
-	( 89.61, 83.44) --
-	( 89.61, 88.43) --
-	( 84.61, 88.43) --
-	cycle;
-
-\path[fill=fillColor] ( 93.15, 87.44) --
-	( 98.15, 87.44) --
-	( 98.15, 92.44) --
-	( 93.15, 92.44) --
-	cycle;
-
-\path[fill=fillColor] (101.70, 91.12) --
-	(106.69, 91.12) --
-	(106.69, 96.12) --
-	(101.70, 96.12) --
-	cycle;
-
-\path[fill=fillColor] (110.24, 94.51) --
-	(115.23, 94.51) --
-	(115.23, 99.50) --
-	(110.24, 99.50) --
-	cycle;
-
-\path[fill=fillColor] (118.78, 97.80) --
-	(123.78, 97.80) --
-	(123.78,102.79) --
-	(118.78,102.79) --
-	cycle;
-
-\path[fill=fillColor] (127.32,101.03) --
-	(132.32,101.03) --
-	(132.32,106.02) --
-	(127.32,106.02) --
-	cycle;
-
-\path[fill=fillColor] (135.86,104.29) --
-	(140.86,104.29) --
-	(140.86,109.28) --
-	(135.86,109.28) --
-	cycle;
-
-\path[fill=fillColor] (144.41,107.42) --
-	(149.40,107.42) --
-	(149.40,112.41) --
-	(144.41,112.41) --
-	cycle;
-
-\path[fill=fillColor] (152.95,110.55) --
-	(157.94,110.55) --
-	(157.94,115.55) --
-	(152.95,115.55) --
-	cycle;
-
-\path[fill=fillColor] (161.49,113.41) --
-	(166.49,113.41) --
-	(166.49,118.40) --
-	(161.49,118.40) --
-	cycle;
-
-\path[fill=fillColor] (170.03,116.27) --
-	(175.03,116.27) --
-	(175.03,121.26) --
-	(170.03,121.26) --
-	cycle;
-
-\path[fill=fillColor] (178.58,119.47) --
-	(183.57,119.47) --
-	(183.57,124.47) --
-	(178.58,124.47) --
-	cycle;
-
-\path[fill=fillColor] (187.12,122.28) --
-	(192.11,122.28) --
-	(192.11,127.28) --
-	(187.12,127.28) --
-	cycle;
-
-\path[fill=fillColor] (195.66,125.17) --
-	(200.66,125.17) --
-	(200.66,130.16) --
-	(195.66,130.16) --
-	cycle;
-
-\path[fill=fillColor] (204.20,127.80) --
-	(209.20,127.80) --
-	(209.20,132.80) --
-	(204.20,132.80) --
-	cycle;
-
-\path[fill=fillColor] (212.74,130.49) --
-	(217.74,130.49) --
-	(217.74,135.48) --
-	(212.74,135.48) --
-	cycle;
-
-\path[fill=fillColor] (221.29,133.19) --
-	(226.28,133.19) --
-	(226.28,138.18) --
-	(221.29,138.18) --
-	cycle;
-
-\path[fill=fillColor] (229.83,135.74) --
-	(234.82,135.74) --
-	(234.82,140.73) --
-	(229.83,140.73) --
-	cycle;
-
-\path[fill=fillColor] (238.37,138.17) --
-	(243.37,138.17) --
-	(243.37,143.16) --
-	(238.37,143.16) --
-	cycle;
-
-\path[fill=fillColor] (246.91,140.85) --
-	(251.91,140.85) --
-	(251.91,145.85) --
-	(246.91,145.85) --
-	cycle;
-
-\path[fill=fillColor] (255.46,143.24) --
-	(260.45,143.24) --
-	(260.45,148.23) --
-	(255.46,148.23) --
-	cycle;
-
-\path[fill=fillColor] (264.00,145.71) --
-	(268.99,145.71) --
-	(268.99,150.71) --
-	(264.00,150.71) --
-	cycle;
-
-\path[fill=fillColor] (272.54,147.90) --
-	(277.54,147.90) --
-	(277.54,152.89) --
-	(272.54,152.89) --
-	cycle;
-
-\path[fill=fillColor] (281.08,150.34) --
-	(286.08,150.34) --
-	(286.08,155.34) --
-	(281.08,155.34) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78, 55.41) -- ( 30.85, 55.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31, 51.87) -- ( 27.31, 58.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32, 61.62) -- ( 39.39, 61.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86, 58.09) -- ( 35.86, 65.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87, 67.34) -- ( 47.93, 67.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40, 63.81) -- ( 44.40, 70.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41, 73.88) -- ( 56.47, 73.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94, 70.35) -- ( 52.94, 77.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95, 79.89) -- ( 65.01, 79.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48, 76.36) -- ( 61.48, 83.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49, 85.65) -- ( 73.56, 85.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02, 82.12) -- ( 70.02, 89.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03, 91.28) -- ( 82.10, 91.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57, 87.75) -- ( 78.57, 94.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58, 97.06) -- ( 90.64, 97.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11, 93.53) -- ( 87.11,100.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,102.60) -- ( 99.18,102.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 99.07) -- ( 95.65,106.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,107.76) -- (107.73,107.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,104.23) -- (104.19,111.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,112.34) -- (116.27,112.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,108.81) -- (112.74,115.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,117.19) -- (124.81,117.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,113.66) -- (121.28,120.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,121.71) -- (133.35,121.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,118.17) -- (129.82,125.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,126.41) -- (141.89,126.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,122.88) -- (138.36,129.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,130.85) -- (150.44,130.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,127.32) -- (146.90,134.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,135.49) -- (158.98,135.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,131.96) -- (155.45,139.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,139.55) -- (167.52,139.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,136.02) -- (163.99,143.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,143.62) -- (176.06,143.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,140.09) -- (172.53,147.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,148.33) -- (184.61,148.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,144.80) -- (181.07,151.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,152.45) -- (193.15,152.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,148.92) -- (189.62,155.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,156.73) -- (201.69,156.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,153.19) -- (198.16,160.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,160.57) -- (210.23,160.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,157.04) -- (206.70,164.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,164.54) -- (218.77,164.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,161.01) -- (215.24,168.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,168.54) -- (227.32,168.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,165.01) -- (223.78,172.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,172.25) -- (235.86,172.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,168.71) -- (232.33,175.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,175.81) -- (244.40,175.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,172.28) -- (240.87,179.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,179.95) -- (252.94,179.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,176.42) -- (249.41,183.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,183.53) -- (261.49,183.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,179.99) -- (257.95,187.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,187.15) -- (270.03,187.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,183.62) -- (266.50,190.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,190.32) -- (278.57,190.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,186.78) -- (275.04,193.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,194.15) -- (287.11,194.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,190.62) -- (283.58,197.68);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] ( 27.31, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 35.86, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 44.40, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 52.94, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 61.48, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 70.02, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 78.57, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 87.11, 54.98) circle (  2.50);
-
-\path[fill=fillColor] ( 95.65, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (104.19, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (112.74, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (121.28, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (129.82, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (138.36, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (146.90, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (155.45, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (163.99, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (172.53, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (181.07, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (189.62, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (198.16, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (206.70, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (215.24, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (223.78, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (232.33, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (240.87, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (249.41, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (257.95, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (266.50, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (275.04, 54.98) circle (  2.50);
-
-\path[fill=fillColor] (283.58, 54.98) circle (  2.50);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.31, 30.69) rectangle (283.58,194.15);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 52.22) {5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,134.09) {6};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 55.25) --
-	( 27.31, 55.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,137.12) --
-	( 27.31,137.12);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (446.24,224.45) {Exponential growth rate $r$ (1/day)};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (112.74, 27.94) --
-	(112.74, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (198.16, 27.94) --
-	(198.16, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.60, 27.94) --
+	(111.60, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.88, 27.94) --
+	(195.88, 30.69);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (112.74, 19.68) {0.1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.16, 19.68) {0.2};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (111.60, 19.68) {0.1};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (195.88, 19.68) {0.2};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (155.45,  7.64) {Exponential growth rate $r$ (1/day)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (153.74,  7.64) {Exponential growth rate $r$ (1/day)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (319.81, 27.94) --
+	(319.81, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.10, 27.94) --
+	(404.10, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (488.38, 27.94) --
+	(488.38, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (319.81, 19.68) {0.0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (404.10, 19.68) {0.1};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (488.38, 19.68) {0.2};
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,112.42) {Mean interval (days)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.31,202.22) {C};
-\end{scope}
-\begin{scope}
-\path[clip] (289.08,  0.00) rectangle (578.16,216.81);
-\definecolor{drawColor}{RGB}{255,255,255}
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (289.08,  0.00) rectangle (578.16,216.81);
-\end{scope}
-\begin{scope}
-\path[clip] (323.24, 30.69) rectangle (572.66,194.15);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (323.24, 30.69) rectangle (572.66,194.15);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (323.24, 58.94) --
-	(326.39, 58.94) --
-	(329.55, 58.94) --
-	(332.71, 58.94) --
-	(335.87, 58.94) --
-	(339.02, 58.94) --
-	(342.18, 58.94) --
-	(345.34, 58.94) --
-	(348.49, 58.94) --
-	(351.65, 58.94) --
-	(354.81, 58.94) --
-	(357.97, 58.94) --
-	(361.12, 58.94) --
-	(364.28, 58.94) --
-	(367.44, 58.94) --
-	(370.60, 58.94) --
-	(373.75, 58.94) --
-	(376.91, 58.94) --
-	(380.07, 58.94) --
-	(383.22, 58.94) --
-	(386.38, 58.94) --
-	(389.54, 58.94) --
-	(392.70, 58.94) --
-	(395.85, 58.94) --
-	(399.01, 58.94) --
-	(402.17, 58.94) --
-	(405.32, 58.94) --
-	(408.48, 58.94) --
-	(411.64, 58.94) --
-	(414.80, 58.94) --
-	(417.95, 58.94) --
-	(421.11, 58.94) --
-	(424.27, 58.94) --
-	(427.43, 58.94) --
-	(430.58, 58.94) --
-	(433.74, 58.94) --
-	(436.90, 58.94) --
-	(440.05, 58.94) --
-	(443.21, 58.94) --
-	(446.37, 58.94) --
-	(449.53, 58.94) --
-	(452.68, 58.94) --
-	(455.84, 58.94) --
-	(459.00, 58.94) --
-	(462.16, 58.94) --
-	(465.31, 58.94) --
-	(468.47, 58.94) --
-	(471.63, 58.94) --
-	(474.78, 58.94) --
-	(477.94, 58.94) --
-	(481.10, 58.94) --
-	(484.26, 58.94) --
-	(487.41, 58.94) --
-	(490.57, 58.94) --
-	(493.73, 58.94) --
-	(496.89, 58.94) --
-	(500.04, 58.94) --
-	(503.20, 58.94) --
-	(506.36, 58.94) --
-	(509.51, 58.94) --
-	(512.67, 58.94) --
-	(515.83, 58.94) --
-	(518.99, 58.94) --
-	(522.14, 58.94) --
-	(525.30, 58.94) --
-	(528.46, 58.94) --
-	(531.62, 58.94) --
-	(534.77, 58.94) --
-	(537.93, 58.94) --
-	(541.09, 58.94) --
-	(544.24, 58.94) --
-	(547.40, 58.94) --
-	(550.56, 58.94) --
-	(553.72, 58.94) --
-	(556.87, 58.94) --
-	(560.03, 58.94) --
-	(563.19, 58.94) --
-	(566.35, 58.94) --
-	(569.50, 58.94) --
-	(572.66, 58.94);
-\definecolor{drawColor}{RGB}{230,159,0}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] (323.24,115.70) --
-	(326.39,114.93) --
-	(329.55,114.17) --
-	(332.71,113.43) --
-	(335.87,112.70) --
-	(339.02,111.98) --
-	(342.18,111.27) --
-	(345.34,110.58) --
-	(348.49,109.90) --
-	(351.65,109.23) --
-	(354.81,108.58) --
-	(357.97,107.94) --
-	(361.12,107.32) --
-	(364.28,106.70) --
-	(367.44,106.10) --
-	(370.60,105.51) --
-	(373.75,104.94) --
-	(376.91,104.37) --
-	(380.07,103.82) --
-	(383.22,103.28) --
-	(386.38,102.76) --
-	(389.54,102.25) --
-	(392.70,101.76) --
-	(395.85,101.28) --
-	(399.01,100.81) --
-	(402.17,100.36) --
-	(405.32, 99.92) --
-	(408.48, 99.48) --
-	(411.64, 99.06) --
-	(414.80, 98.64) --
-	(417.95, 98.23) --
-	(421.11, 97.85) --
-	(424.27, 97.47) --
-	(427.43, 97.11) --
-	(430.58, 96.76) --
-	(433.74, 96.42) --
-	(436.90, 96.09) --
-	(440.05, 95.75) --
-	(443.21, 95.42) --
-	(446.37, 95.09) --
-	(449.53, 94.76) --
-	(452.68, 94.43) --
-	(455.84, 94.12) --
-	(459.00, 93.81) --
-	(462.16, 93.51) --
-	(465.31, 93.21) --
-	(468.47, 92.92) --
-	(471.63, 92.63) --
-	(474.78, 92.34) --
-	(477.94, 92.06) --
-	(481.10, 91.77) --
-	(484.26, 91.49) --
-	(487.41, 91.21) --
-	(490.57, 90.94) --
-	(493.73, 90.67) --
-	(496.89, 90.40) --
-	(500.04, 90.13) --
-	(503.20, 89.87) --
-	(506.36, 89.61) --
-	(509.51, 89.36) --
-	(512.67, 89.11) --
-	(515.83, 88.86) --
-	(518.99, 88.61) --
-	(522.14, 88.37) --
-	(525.30, 88.13) --
-	(528.46, 87.90) --
-	(531.62, 87.67) --
-	(534.77, 87.44) --
-	(537.93, 87.22) --
-	(541.09, 87.00) --
-	(544.24, 86.78) --
-	(547.40, 86.56) --
-	(550.56, 86.35) --
-	(553.72, 86.14) --
-	(556.87, 85.94) --
-	(560.03, 85.74) --
-	(563.19, 85.54) --
-	(566.35, 85.35) --
-	(569.50, 85.16) --
-	(572.66, 84.97);
-\definecolor{drawColor}{RGB}{86,180,233}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] (323.24,149.67) --
-	(326.39,148.19) --
-	(329.55,146.73) --
-	(332.71,145.31) --
-	(335.87,143.91) --
-	(339.02,142.53) --
-	(342.18,141.18) --
-	(345.34,139.86) --
-	(348.49,138.57) --
-	(351.65,137.30) --
-	(354.81,136.06) --
-	(357.97,134.85) --
-	(361.12,133.66) --
-	(364.28,132.50) --
-	(367.44,131.37) --
-	(370.60,130.26) --
-	(373.75,129.17) --
-	(376.91,128.11) --
-	(380.07,127.07) --
-	(383.22,126.06) --
-	(386.38,125.09) --
-	(389.54,124.14) --
-	(392.70,123.23) --
-	(395.85,122.35) --
-	(399.01,121.49) --
-	(402.17,120.66) --
-	(405.32,119.84) --
-	(408.48,119.05) --
-	(411.64,118.27) --
-	(414.80,117.51) --
-	(417.95,116.77) --
-	(421.11,116.06) --
-	(424.27,115.39) --
-	(427.43,114.74) --
-	(430.58,114.12) --
-	(433.74,113.51) --
-	(436.90,112.91) --
-	(440.05,112.32) --
-	(443.21,111.73) --
-	(446.37,111.14) --
-	(449.53,110.55) --
-	(452.68,109.97) --
-	(455.84,109.41) --
-	(459.00,108.87) --
-	(462.16,108.33) --
-	(465.31,107.81) --
-	(468.47,107.30) --
-	(471.63,106.80) --
-	(474.78,106.29) --
-	(477.94,105.80) --
-	(481.10,105.30) --
-	(484.26,104.81) --
-	(487.41,104.32) --
-	(490.57,103.84) --
-	(493.73,103.37) --
-	(496.89,102.91) --
-	(500.04,102.46) --
-	(503.20,102.01) --
-	(506.36,101.57) --
-	(509.51,101.13) --
-	(512.67,100.70) --
-	(515.83,100.27) --
-	(518.99, 99.86) --
-	(522.14, 99.44) --
-	(525.30, 99.04) --
-	(528.46, 98.64) --
-	(531.62, 98.25) --
-	(534.77, 97.86) --
-	(537.93, 97.48) --
-	(541.09, 97.11) --
-	(544.24, 96.75) --
-	(547.40, 96.39) --
-	(550.56, 96.04) --
-	(553.72, 95.69) --
-	(556.87, 95.35) --
-	(560.03, 95.02) --
-	(563.19, 94.69) --
-	(566.35, 94.37) --
-	(569.50, 94.06) --
-	(572.66, 93.75);
-\definecolor{drawColor}{RGB}{0,158,115}
-
-\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] (323.24,180.94) --
-	(326.39,178.70) --
-	(329.55,176.51) --
-	(332.71,174.35) --
-	(335.87,172.23) --
-	(339.02,170.16) --
-	(342.18,168.13) --
-	(345.34,166.14) --
-	(348.49,164.20) --
-	(351.65,162.29) --
-	(354.81,160.43) --
-	(357.97,158.62) --
-	(361.12,156.84) --
-	(364.28,155.11) --
-	(367.44,153.41) --
-	(370.60,151.76) --
-	(373.75,150.14) --
-	(376.91,148.56) --
-	(380.07,147.02) --
-	(383.22,145.52) --
-	(386.38,144.08) --
-	(389.54,142.68) --
-	(392.70,141.34) --
-	(395.85,140.05) --
-	(399.01,138.79) --
-	(402.17,137.57) --
-	(405.32,136.38) --
-	(408.48,135.23) --
-	(411.64,134.09) --
-	(414.80,132.98) --
-	(417.95,131.90) --
-	(421.11,130.89) --
-	(424.27,129.91) --
-	(427.43,128.98) --
-	(430.58,128.09) --
-	(433.74,127.21) --
-	(436.90,126.36) --
-	(440.05,125.52) --
-	(443.21,124.68) --
-	(446.37,123.84) --
-	(449.53,122.99) --
-	(452.68,122.16) --
-	(455.84,121.37) --
-	(459.00,120.59) --
-	(462.16,119.84) --
-	(465.31,119.10) --
-	(468.47,118.37) --
-	(471.63,117.66) --
-	(474.78,116.95) --
-	(477.94,116.25) --
-	(481.10,115.55) --
-	(484.26,114.85) --
-	(487.41,114.17) --
-	(490.57,113.50) --
-	(493.73,112.84) --
-	(496.89,112.20) --
-	(500.04,111.56) --
-	(503.20,110.94) --
-	(506.36,110.32) --
-	(509.51,109.72) --
-	(512.67,109.12) --
-	(515.83,108.53) --
-	(518.99,107.95) --
-	(522.14,107.38) --
-	(525.30,106.82) --
-	(528.46,106.27) --
-	(531.62,105.73) --
-	(534.77,105.20) --
-	(537.93,104.68) --
-	(541.09,104.17) --
-	(544.24,103.68) --
-	(547.40,103.19) --
-	(550.56,102.71) --
-	(553.72,102.24) --
-	(556.87,101.78) --
-	(560.03,101.33) --
-	(563.19,100.89) --
-	(566.35,100.46) --
-	(569.50,100.05) --
-	(572.66, 99.64);
-\definecolor{fillColor}{RGB}{230,159,0}
-
-\path[fill=fillColor] (323.24,119.77) --
-	(326.60,113.94) --
-	(319.87,113.94) --
-	cycle;
-
-\path[fill=fillColor] (331.55,117.61) --
-	(334.91,111.79) --
-	(328.19,111.79) --
-	cycle;
-
-\path[fill=fillColor] (339.86,115.71) --
-	(343.23,109.89) --
-	(336.50,109.89) --
-	cycle;
-
-\path[fill=fillColor] (348.18,113.71) --
-	(351.54,107.88) --
-	(344.81,107.88) --
-	cycle;
-
-\path[fill=fillColor] (356.49,111.89) --
-	(359.86,106.07) --
-	(353.13,106.07) --
-	cycle;
-
-\path[fill=fillColor] (364.81,110.34) --
-	(368.17,104.52) --
-	(361.44,104.52) --
-	cycle;
-
-\path[fill=fillColor] (373.12,108.89) --
-	(376.48,103.06) --
-	(369.76,103.06) --
-	cycle;
-
-\path[fill=fillColor] (381.44,107.50) --
-	(384.80,101.67) --
-	(378.07,101.67) --
-	cycle;
-
-\path[fill=fillColor] (389.75,106.03) --
-	(393.11,100.20) --
-	(386.39,100.20) --
-	cycle;
-
-\path[fill=fillColor] (398.06,104.70) --
-	(401.43, 98.88) --
-	(394.70, 98.88) --
-	cycle;
-
-\path[fill=fillColor] (406.38,103.51) --
-	(409.74, 97.69) --
-	(403.01, 97.69) --
-	cycle;
-
-\path[fill=fillColor] (414.69,102.49) --
-	(418.06, 96.67) --
-	(411.33, 96.67) --
-	cycle;
-
-\path[fill=fillColor] (423.01,101.49) --
-	(426.37, 95.66) --
-	(419.64, 95.66) --
-	cycle;
-
-\path[fill=fillColor] (431.32,100.59) --
-	(434.68, 94.76) --
-	(427.96, 94.76) --
-	cycle;
-
-\path[fill=fillColor] (439.63, 99.70) --
-	(443.00, 93.88) --
-	(436.27, 93.88) --
-	cycle;
-
-\path[fill=fillColor] (447.95, 98.87) --
-	(451.31, 93.04) --
-	(444.58, 93.04) --
-	cycle;
-
-\path[fill=fillColor] (456.26, 98.10) --
-	(459.63, 92.27) --
-	(452.90, 92.27) --
-	cycle;
-
-\path[fill=fillColor] (464.58, 97.28) --
-	(467.94, 91.45) --
-	(461.21, 91.45) --
-	cycle;
-
-\path[fill=fillColor] (472.89, 96.38) --
-	(476.25, 90.55) --
-	(469.53, 90.55) --
-	cycle;
-
-\path[fill=fillColor] (481.20, 95.60) --
-	(484.57, 89.77) --
-	(477.84, 89.77) --
-	cycle;
-
-\path[fill=fillColor] (489.52, 94.90) --
-	(492.88, 89.07) --
-	(486.15, 89.07) --
-	cycle;
-
-\path[fill=fillColor] (497.83, 94.18) --
-	(501.20, 88.35) --
-	(494.47, 88.35) --
-	cycle;
-
-\path[fill=fillColor] (506.15, 93.53) --
-	(509.51, 87.70) --
-	(502.78, 87.70) --
-	cycle;
-
-\path[fill=fillColor] (514.46, 92.81) --
-	(517.82, 86.99) --
-	(511.10, 86.99) --
-	cycle;
-
-\path[fill=fillColor] (522.78, 92.22) --
-	(526.14, 86.39) --
-	(519.41, 86.39) --
-	cycle;
-
-\path[fill=fillColor] (531.09, 91.66) --
-	(534.45, 85.83) --
-	(527.73, 85.83) --
-	cycle;
-
-\path[fill=fillColor] (539.40, 91.06) --
-	(542.77, 85.24) --
-	(536.04, 85.24) --
-	cycle;
-
-\path[fill=fillColor] (547.72, 90.45) --
-	(551.08, 84.63) --
-	(544.35, 84.63) --
-	cycle;
-
-\path[fill=fillColor] (556.03, 89.86) --
-	(559.40, 84.03) --
-	(552.67, 84.03) --
-	cycle;
-
-\path[fill=fillColor] (564.35, 89.36) --
-	(567.71, 83.53) --
-	(560.98, 83.53) --
-	cycle;
-
-\path[fill=fillColor] (572.66, 88.81) --
-	(576.02, 82.98) --
-	(569.30, 82.98) --
-	cycle;
-\definecolor{fillColor}{RGB}{86,180,233}
-
-\path[fill=fillColor] (320.74,147.59) --
-	(325.73,147.59) --
-	(325.73,152.58) --
-	(320.74,152.58) --
-	cycle;
-
-\path[fill=fillColor] (329.05,143.39) --
-	(334.05,143.39) --
-	(334.05,148.38) --
-	(329.05,148.38) --
-	cycle;
-
-\path[fill=fillColor] (337.37,139.76) --
-	(342.36,139.76) --
-	(342.36,144.75) --
-	(337.37,144.75) --
-	cycle;
-
-\path[fill=fillColor] (345.68,135.95) --
-	(350.68,135.95) --
-	(350.68,140.94) --
-	(345.68,140.94) --
-	cycle;
-
-\path[fill=fillColor] (353.99,132.41) --
-	(358.99,132.41) --
-	(358.99,137.40) --
-	(353.99,137.40) --
-	cycle;
-
-\path[fill=fillColor] (362.31,129.50) --
-	(367.30,129.50) --
-	(367.30,134.50) --
-	(362.31,134.50) --
-	cycle;
-
-\path[fill=fillColor] (370.62,126.75) --
-	(375.62,126.75) --
-	(375.62,131.74) --
-	(370.62,131.74) --
-	cycle;
-
-\path[fill=fillColor] (378.94,124.08) --
-	(383.93,124.08) --
-	(383.93,129.08) --
-	(378.94,129.08) --
-	cycle;
-
-\path[fill=fillColor] (387.25,121.44) --
-	(392.25,121.44) --
-	(392.25,126.43) --
-	(387.25,126.43) --
-	cycle;
-
-\path[fill=fillColor] (395.57,118.99) --
-	(400.56,118.99) --
-	(400.56,123.99) --
-	(395.57,123.99) --
-	cycle;
-
-\path[fill=fillColor] (403.88,116.78) --
-	(408.88,116.78) --
-	(408.88,121.77) --
-	(403.88,121.77) --
-	cycle;
-
-\path[fill=fillColor] (412.19,115.02) --
-	(417.19,115.02) --
-	(417.19,120.02) --
-	(412.19,120.02) --
-	cycle;
-
-\path[fill=fillColor] (420.51,113.20) --
-	(425.50,113.20) --
-	(425.50,118.19) --
-	(420.51,118.19) --
-	cycle;
-
-\path[fill=fillColor] (428.82,111.53) --
-	(433.82,111.53) --
-	(433.82,116.52) --
-	(428.82,116.52) --
-	cycle;
-
-\path[fill=fillColor] (437.14,109.90) --
-	(442.13,109.90) --
-	(442.13,114.89) --
-	(437.14,114.89) --
-	cycle;
-
-\path[fill=fillColor] (445.45,108.47) --
-	(450.45,108.47) --
-	(450.45,113.47) --
-	(445.45,113.47) --
-	cycle;
-
-\path[fill=fillColor] (453.76,107.09) --
-	(458.76,107.09) --
-	(458.76,112.08) --
-	(453.76,112.08) --
-	cycle;
-
-\path[fill=fillColor] (462.08,105.59) --
-	(467.07,105.59) --
-	(467.07,110.58) --
-	(462.08,110.58) --
-	cycle;
-
-\path[fill=fillColor] (470.39,104.07) --
-	(475.39,104.07) --
-	(475.39,109.07) --
-	(470.39,109.07) --
-	cycle;
-
-\path[fill=fillColor] (478.71,102.72) --
-	(483.70,102.72) --
-	(483.70,107.72) --
-	(478.71,107.72) --
-	cycle;
-
-\path[fill=fillColor] (487.02,101.49) --
-	(492.02,101.49) --
-	(492.02,106.49) --
-	(487.02,106.49) --
-	cycle;
-
-\path[fill=fillColor] (495.34,100.25) --
-	(500.33,100.25) --
-	(500.33,105.25) --
-	(495.34,105.25) --
-	cycle;
-
-\path[fill=fillColor] (503.65, 99.11) --
-	(508.64, 99.11) --
-	(508.64,104.10) --
-	(503.65,104.10) --
-	cycle;
-
-\path[fill=fillColor] (511.96, 97.90) --
-	(516.96, 97.90) --
-	(516.96,102.90) --
-	(511.96,102.90) --
-	cycle;
-
-\path[fill=fillColor] (520.28, 96.90) --
-	(525.27, 96.90) --
-	(525.27,101.90) --
-	(520.28,101.90) --
-	cycle;
-
-\path[fill=fillColor] (528.59, 95.91) --
-	(533.59, 95.91) --
-	(533.59,100.91) --
-	(528.59,100.91) --
-	cycle;
-
-\path[fill=fillColor] (536.91, 94.94) --
-	(541.90, 94.94) --
-	(541.90, 99.93) --
-	(536.91, 99.93) --
-	cycle;
-
-\path[fill=fillColor] (545.22, 94.00) --
-	(550.22, 94.00) --
-	(550.22, 98.99) --
-	(545.22, 98.99) --
-	cycle;
-
-\path[fill=fillColor] (553.53, 92.89) --
-	(558.53, 92.89) --
-	(558.53, 97.89) --
-	(553.53, 97.89) --
-	cycle;
-
-\path[fill=fillColor] (561.85, 92.04) --
-	(566.84, 92.04) --
-	(566.84, 97.04) --
-	(561.85, 97.04) --
-	cycle;
-
-\path[fill=fillColor] (570.16, 91.16) --
-	(575.16, 91.16) --
-	(575.16, 96.15) --
-	(570.16, 96.15) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (319.70,181.63) -- (326.77,181.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.24,178.10) -- (323.24,185.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.02,175.24) -- (335.08,175.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.55,171.71) -- (331.55,178.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.33,169.74) -- (343.40,169.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.86,166.20) -- (339.86,173.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.65,163.98) -- (351.71,163.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.18,160.45) -- (348.18,167.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.96,158.64) -- (360.02,158.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.49,155.11) -- (356.49,162.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (361.27,154.33) -- (368.34,154.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.81,150.80) -- (364.81,157.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.59,150.19) -- (376.65,150.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.12,146.66) -- (373.12,153.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.90,146.18) -- (384.97,146.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.44,142.65) -- (381.44,149.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.22,142.37) -- (393.28,142.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.75,138.84) -- (389.75,145.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.53,138.78) -- (401.60,138.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.06,135.25) -- (398.06,142.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.85,135.48) -- (409.91,135.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.38,131.95) -- (406.38,139.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.16,133.07) -- (418.22,133.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.69,129.54) -- (414.69,136.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.47,130.41) -- (426.54,130.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.01,126.88) -- (423.01,133.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.79,127.94) -- (434.85,127.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.32,124.40) -- (431.32,131.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.10,125.60) -- (443.17,125.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.63,122.07) -- (439.63,129.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.42,123.66) -- (451.48,123.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.95,120.13) -- (447.95,127.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.73,121.64) -- (459.79,121.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.26,118.11) -- (456.26,125.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.04,119.43) -- (468.11,119.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.58,115.90) -- (464.58,122.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,117.33) -- (476.42,117.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.89,113.80) -- (472.89,120.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.67,115.45) -- (484.74,115.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.20,111.92) -- (481.20,118.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.99,113.73) -- (493.05,113.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.52,110.20) -- (489.52,117.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.30,112.01) -- (501.36,112.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.83,108.48) -- (497.83,115.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,110.34) -- (509.68,110.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.15,106.81) -- (506.15,113.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.93,108.72) -- (517.99,108.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.46,105.19) -- (514.46,112.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.24,107.30) -- (526.31,107.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.78,103.77) -- (522.78,110.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (527.56,105.93) -- (534.62,105.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (531.09,102.40) -- (531.09,109.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (535.87,104.65) -- (542.94,104.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.40,101.12) -- (539.40,108.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (544.19,103.44) -- (551.25,103.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.72, 99.91) -- (547.72,106.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.50,101.84) -- (559.56,101.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (556.03, 98.31) -- (556.03,105.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (560.81,100.61) -- (567.88,100.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (564.35, 97.07) -- (564.35,104.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (569.13, 99.50) -- (576.19, 99.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.66, 95.97) -- (572.66,103.04);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] (323.24, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (331.55, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (339.86, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (348.18, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (356.49, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (364.81, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (373.12, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (381.44, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (389.75, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (398.06, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (406.38, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (414.69, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (423.01, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (431.32, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (439.63, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (447.95, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (456.26, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (464.58, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (472.89, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (481.20, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (489.52, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (497.83, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (506.15, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (514.46, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (522.78, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (531.09, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (539.40, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (547.72, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (556.03, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (564.35, 58.94) circle (  2.50);
-
-\path[fill=fillColor] (572.66, 58.94) circle (  2.50);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (323.24, 30.69) rectangle (572.66,194.15);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29, 27.66) {0.0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29, 66.58) {0.2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,105.50) {0.4};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,144.42) {0.6};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (318.29,183.34) {0.8};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49, 30.69) --
-	(323.24, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49, 69.61) --
-	(323.24, 69.61);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,108.53) --
-	(323.24,108.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,147.45) --
-	(323.24,147.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (320.49,186.37) --
-	(323.24,186.37);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (323.24, 27.94) --
-	(323.24, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.38, 27.94) --
-	(406.38, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (489.52, 27.94) --
-	(489.52, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (323.24, 19.68) {0.0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (406.38, 19.68) {0.1};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (489.52, 19.68) {0.2};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (447.95,  7.64) {Exponential growth rate $r$ (1/day)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (302.16,112.42) {Squared coefficient of variation};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (323.24,202.22) {D};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (446.24,  7.64) {Exponential growth rate $r$ (1/day)};
 \end{scope}

### 2020-10-05 serial.tex
so close

@@
 The reproduction number \RR and the exponential growth rate $r$ are critical quantities for characterizing outbreak dynamics.
-These quantities are linked by generation intervals, defined as the time between infection and transmission.
+These quantities are linked by generation intervals---defined as the time between infection and transmission.
 Because generation intervals are difficult to measure directly, serial intervals---defined as the onset of symptoms in a chain of transmission---are often substituted.
 However, recent studies suggest that the two intervals give different estimates of \RR from $r$.
-We present a general framework for characterizing epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly link \RR with $r$, are not the same as \emph{intrinsic} serial intervals---defined by averaging across individual-level characteristics while neglecting population-level dynamics.
-Instead, the forward serial-interval distribution depends on $r$: 
-When an epidemic is growing exponenially, infectors that develop symptoms on a given day will have shorter incubation periods, on average, than their infectees, thereby affecting the realized serial-interval distribution.
-We provide a heuristic method for addressing biases that can arise from failing to account for changes in serial intervals across cohorts; we apply the method to estimation of \RR for the COVID-19 outbreak in China, outside Hubei province, using serial-interval data (collected between January  21--February  8,  2020).
-Our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by a factor of 2.0--2.6 in the context of COVID-19.
-This study demonstrates the importance of early epidemiological investigation through contact tracing and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
+We show that \emph{forward-looking} serial intervals, which begin in a certain period, correctly describe the renewal process of symptomatic cases and therefore link \RR with $r$.
+These forward intervals are different from \emph{intrinsic} intervals, which neglect population-level dynamics, and \emph{backward-looking} intervals, which end in a certain period.
+Instead, the forward-looking intervals depend on $r$:
+When an epidemic is growing exponentially, infectors that develop symptoms on a given day will have shorter incubation periods, on average, than their infectees, thereby affecting the serial-interval distribution.
+We provide a heuristic method for addressing biases that can arise from neglecting changes in serial intervals. 
+We apply the method to estimation of \RR for the COVID-19 outbreak in China, outside Hubei province, using serial-interval data collected between January 21--February 8, 2020. 
+Our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by up to a factor of 2.6 in the context of COVID-19.
+This study demonstrates the importance of early contact tracing efforts and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
 
@@
 The reproduction number \RR is one of the most important characteristics of an emerging epidemic, such as the current pandemic of coronavirus disease 2019 (COVID-19) \citep{majumder2020early}.
-The reproduction number is defined as the average number of secondary cases caused by a primary case;
-the value in a fully susceptible population --- the ``basic'' reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population, and the amount of intervention necessary to eliminate it in simple cases \citep{anderson1991infectious}.
+The reproduction number is defined as the average number of secondary cases caused by a primary case.
+The value in a fully susceptible population --- the ``basic'' reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population, and the amount of intervention necessary to eliminate it in simple cases \citep{anderson1991infectious}.
 Since the reproduction number represents an average \citep{diekmann1990definition, anderson1991infectious}, it fails to capture heterogeneity among individuals or across space.
@@
 Since generation intervals measure time between infection events, which can be difficult to observe in practice, generation intervals are often replaced with serial intervals.
-The serial interval is defined as the time between when an infector and an infectee become \emph{symptomatic} \citep{svensson2007note}.
+The serial interval is defined as the time between when an infector and an infectee develop symptoms \citep{svensson2007note}.
 While generation and serial intervals both measure the time scale of disease transmission, they measure fundamentally different quantities. 
@@
 This confusion is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
-These studies are exampels of many---indeed, it is a common practice to use the serial and generation intervals interchangeably.
+These studies are examples of many---indeed, it is a common practice to use the serial and generation intervals interchangeably.
 
@@
 Conditioning on individuals whose secondary events have occurred at the same time means that we tend to observe shorter (or longer) inter-event delays when cohort size has been increasing (decreasing) through time.
-When incidence is growing exponentially, we can calculate the amount of bias directly.
+When incidence is growing exponentially, we can calculate the amount of bias exactly.
 Assuming that the forward delay distribution ($f_\psymp(\tau) \approx f_0(\tau)$) and the weight parameter ($W(\psymp) \approx W(0)$) remain constant during the exponential growth phase, we can substitute $\psize(t) = \psize(0) \exp(rt)$ in \eref{backward} to obtain:
@@
 \end{align}
-where $r$ is the exponential growth rate (and $\left[W(0) \psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ since $b_0$ is a probability distribution).
-\swp{JSW: If this is what you mean by 'direct', it's still opaque!  How do you humans interpret this.  It's non trivial!}
-Thus, the mean backward interval will be always shorter than the mean forward interval as long as $r > 0$---even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.
+where $r$ is the exponential growth rate.
+Since $b_0$ is a probability distribution, $\left[W(0) \psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ corresponds to the normalization constant.
+Therefore, the backward delay distribution during the exponential growth phase depends only on the exponential growth rate $r$ and the initial forward forward delay distribution $f_0$.
+
+The mean backward interval will be always shorter than the mean forward interval as long as $r > 0$.
+Even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.
 In general, the backward delay distribution will differ from the forward delay distribution (unless the disease is at equilibrium), even if we are measuring time delays that are intrinsic to the life history of a disease (e.g., the incubation period).
@@
 
-The total density of serial intervals can now be obtained by integrating over all possible infection times for the infector and the infectee:
+The total density of serial intervals between time $\psymp$ and $\ssymp$ can now be obtained by integrating over all possible infection times for the infector and the infectee:
 \begin{equation}
@@
 This framework allows us to understand changes in the realized serial intervals for any epidemic model and properly link serial-interval distributions with the renewal process.
-In particular, we see that the initial forward serial-interval distribution, $f_0(\tau)$, provides a correct link between the exponential growth rate $r$ and the initial serial reproduction number $\Rs(0)$ by substituting $j(t) \approx j(0) \exp(rt)$, $\Rs(t) \approx \Rs(0)$, and $f_{t-\tau}(\tau) \approx f_0(\tau)$:
+In addition,  assuming that the reproduction number as well as the forward serial-interval distribution remain constant during the exponential growth phase, we can substitute $j(t) \approx j(0) \exp(rt)$, $\Rs(t) \approx \Rs(0)$, and $f_{t-\tau}(\tau) \approx f_0(\tau)$ to obtain:
 \begin{equation}
@@
 \end{equation}
-\swp{OK to add this here? Do we needs a concluding sentence for this section?}
+Therefore, the initial forward serial-interval distribution, $f_0(\tau)$, provides a correct link between the exponential growth rate $r$ and the initial serial reproduction number $\Rs(0)$.
+We re-visit this idea later in Section 2.4 and show that the initial forward serial-interval distribution provides the same $r$--\RR link as the intrinsic generation-interval distribution.
 
@@
 Here, we consider a specific example where changes in the reproduction number are driven by susceptible depletion: $\RR(t) = \Ro S(t)$, where \Ro represents the basic reproduction number.
-Although we do not consider non-pharmaceutical interventions or behavioral changes explicitly, the effect of susceptible depletion is mathematically equivalent to the effect of interventions that reduce transmission rate, and therefore \RR(t).
-\swp{JSW: Should say we do not consider NPI and/or behavior explicitly.
-I'm not sure that it's all exactly equivalent; because then R0 would vary and I don't see what the last part of this sentence really means anyway.
-Also, I think Sang Woo would argue this is true even when peaks/declines occur in the absence of susceptible depletion which is the most likely thing happening for COvid-19.
-Write this sentence carefully!}
+Although we do not consider non-pharmaceutical interventions or behavioral changes explicitly, the effect of susceptible depletion is mathematically equivalent to the effect of population-level interventions, such as social-distancing, that reduce \RR(t).
 Then, the forward generation-interval for a cohort of individuals that were infected at time $\psymp$ follows \citep{champredon2015intrinsic}:
@@
 \begin{equation}
-\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
+\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau.
 \label{eq:Rforward}
 \end{equation}
-where the initial forward serial-interval distribution is given by:
+Here, the initial forward serial-interval distribution is given by:
 \begin{equation}
@@
 \end{equation}
-where the normalization constant $\phi$ is determined by the
-requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
-While it is straightforward to see this relationship from the renewal equation (see \eref{Rforward0}),
-we provide a more detailed mathematical proof of this relationship in Supplementary Materials.
+where the normalization constant $\phi$ is determined by the requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
+We provide a more detailed mathematical proof of this relationship in Supplementary Materials.
 Since we do not make any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, \eref{Rforward} holds in general whether presymptomatic transmission is possible or not.
-\bmb{what conclusion specifically? or do you mean this ``formulation'' is robust? Do you need to be more explicit about the inferential status of ``Therefore, we expect \ldots'' above? Is }
-\swp{I tried to deal with the first one. Not sure what he means by the second question?}
 
@@
 The initial forward serial-interval distribution depends on the exponential growth rate $r$.
-For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short (\eref{backexp}), meaning that presymptomatic transmission is less likely to occur; 
-therefore, the initial forward serial-interval distribution will generally have a larger mean than the intrinsic generation- and serial-interval distributions.
+For a fast-growing epidemic (high $r$), we expect the backward incubation periods to be short (\eref{backexp}), meaning that presymptomatic transmission is less likely to occur. 
+Therefore, the initial forward serial-interval distribution will generally have a larger mean than the intrinsic generation- and serial-interval distributions.
 However, the exact shape of the initial forward serial-interval distribution depends on the shape of the joint distribution.
@@
 In this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
-Everywhere else in this paper, however, we do not assume that the incubation and exposed periods are equivalent---instead, we allow for presymptomatic transmission in the model in order to reflect the transmission dynamics of COVID-19.
+Everywhere else in this paper, however, we do not assume that the incubation and exposed periods are equivalent.
+Instead, we allow for presymptomatic transmission in the model in order to reflect the transmission dynamics of COVID-19.
 
@@
 
-We have shown that the dynamics of the serial-interval distribution depends on the joint distribution between incubation periods and generation intervals.
+We have shown that the dynamics of the serial-interval distribution depend on the joint distribution between incubation periods and generation intervals.
 Here, we use a bivariate lognormal distribution to model the joint probability distribution $h$ of intrinsic incubation periods and intrinsic generation intervals (in the renewal equation model, \eref{renewal}) while allowing for the possibility that they might be correlated.
@@
 The intrinsic  incubation period and generation-interval distributions are chosen to match characteristic of COVID-19 to illustrate realistic magnitudes of time-varying/perspective effects in the current pandemic.
-\swp{JSW is confused because exp(1.54)=4.66 but that's because those are parameters of the not log of the mean but rather mean of the normal.
-I tried to clarify that.
-He also wanted me to add $\mu_I$ and $\sigma$ but I think that's confusing because it won't be $\exp(\mu)$...}
 }
@@
 (D) The squared coefficient of variation of the initial forward serial intervals during the exponential growth phase decreases with $r$.
-\bmb{x-axes of B and D don't exactly line up (I realize that's \emph{extremely} fussy)}
 }
@@
 (E--G) Changes in the mean backward incubation period, generation interval, and serial interval.
-Black lines represent the results of a deterministic simulation.
-Orange lines (A) represent the results of 10 stochastic simulations.
-Orange points (B-G) represent the average of 10 stochastic simulations.
+Black (A) and colored (B--G) lines represent the results of a deterministic simulation.
+Gray lines (A) represent the results of 10 stochastic simulations.
+Colored points (B-G) represent the average of 10 stochastic simulations.
 Dashed lines represent the mean initial forward delay.
+Forward and backward delays are colored according to \fref{diagram}.
 In order to remove possible transient dynamics (e.g., left-censoring of time delays and initial stochasticity due to low number of infections), we set $t=0$ to the first time point when daily incidence is greater than 100.
-Intrinsic incubation periods and intrinsic generation intervals are assumed to be independent of each other for simplicity; see Supplementary Materials for simulations with correlated intrinsic incubation periods and intrinsic generation intervals.
+Intrinsic incubation periods and intrinsic generation intervals are assumed to be independent of each other for simplicity.
+See Supplementary Materials for simulations with correlated incubation periods and generation intervals.
 See Table 1 for parameter values.
-\bmb{identical plot titles B/E etc could be confusing at first glance?}
 }
@@
 Future studies trying to model realized serial intervals should consider carefully the joint distribution between the generation intervals and incubation periods.
-\swp{Is this para OK?}
 

### 2020-10-05 forward.R

@@ -79,7 +79,7 @@ g1 <- ggplot(sir_data3) +
   geom_line(data=detdata2, aes(day, cases, col="Deterministic"), lwd=1) +
   scale_x_continuous("Time (days)", expand=c(0, 0), limits=c(-10, 52)) +
   scale_y_continuous("Daily incidence", expand=c(0, 0), limits=c(1, 2400)) +
-  scale_color_manual(values=c(1, "#D55E00")) +
+  scale_color_manual(values=c(1, "gray")) +
   ggtitle("A") +
   theme(
     panel.grid = element_blank(),
@@ -118,13 +118,13 @@ incdet <- data.frame(
 )
 
 g2 <- ggplot(incdata0) +
-  geom_line(data=incdet, aes(tvec, mf), lwd=1) +
-  geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
+  geom_line(data=incdet, aes(tvec, mf), col="#81b214", lwd=1) +
+  geom_point(aes(cc, mean), shape=1, col="#81b214", size=2) +
   geom_hline(yintercept=incdet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(-10, 52)) +
   scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7), oob=scales::squish) +
   scale_fill_gradientn(colors=c("white", "black")) +
-  ggtitle("B. Incubation period") +
+  ggtitle("B. Forward\nIncubation period") +
   theme(
     panel.grid = element_blank(),
     legend.position = "none"
@@ -146,13 +146,13 @@ gendet <- data.frame(
 )
 
 g3 <- ggplot(gendata0) +
-  geom_line(data=gendet, aes(tvec, mf), lwd=1) +
-  geom_point(aes(cc, mean), shape=1, col="#D55E00", size=2) +
+  geom_line(data=gendet, aes(tvec, mf), col="#81b214", lwd=1) +
+  geom_point(aes(cc, mean), shape=1, col="#81b214", size=2) +
   geom_hline(yintercept=gendet$mf[1], lty=2) +
   scale_x_continuous("Primary cohort time (days)", expand=c(0, 0), limits=c(-10, 52)) +
   scale_y_continuous("Forward delay (days)", expand=c(0, 0), limits=c(0, 7), breaks=0:4*2) +
   scale_fill_gradientn(colors=c("white", "black")) +
[…]

### 2020-10-05 rR.R

@@ -1,7 +1,7 @@
 library(dplyr)
 library(ggplot2); theme_set(theme_bw())
 library(tikzDevice)
-library(gridExtra)
+library(egg)
 source("cpalette.R")
 source("rRfun.R")
 
@@ -53,12 +53,18 @@ rRdata <- list(
                               "Forward serial interval ($\\rho=0$)"))
   )
 
+## viridis/C colours; manually extracted (see commented code below)
+vcpal <- c("#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF", "#0D0887FF")
+## reduce luminanance of too-light yellow
+vcpal[4] <- adjustcolor(vcpal[4], red.f = 0.9, green.f = 0.9, blue.f = 0.9)
+vcpal <- vcpal[c(5,1:4)] ## shuffle
+
 g1 <- ggplot(rRdata) +
   geom_smooth(aes(r, R, col=type, lty=type), se=FALSE) +
   geom_point(aes(r, R, col=type, shape=type), size=2) +
   scale_x_continuous("Exponential growth rate $r$ (1/day)", limits=c(0, 0.3), expand=c(0, 0)) +
   scale_y_continuous("Basic reproduction number $\\mathcal R_0$", limits=c(1, 4.5), expand=c(0, 0)) +
-  scale_color_manual(values=cpalette) +
+  scale_colour_manual(values=vcpal) +
   ggtitle("A") +
   theme(
     panel.grid = element_blank(),
@@ -102,20 +108,12 @@ rRdata2 <- list(
                               "Intrinsic serial interval ($\\rho=0$)"))
     )
 
-
-## viridis/C colours; manually extracted (see commented code below)
-vcpal <- c("#7E03A8FF", "#CC4678FF", "#F89441FF", "#F0F921FF", "#0D0887FF")
-## reduce luminanance of too-light yellow
-vcpal[4] <- adjustcolor(vcpal[4], red.f = 0.9, green.f = 0.9, blue.f = 0.9)
-vcpal <- vcpal[c(5,1:4)] ## shuffle
-    
 g2 <- ggplot(rRdata2) +
   geom_smooth(aes(r, R, col=type, lty=type), se=FALSE) +
   geom_point(aes(r, R, col=type, shape=type), size=2) +
   scale_x_continuous("Exponential growth rate $r$ (1/day)", limits=c(0, 0.3), expand=c(0, 0)) +
[…]

### 2020-10-06 response.tex
am i done now

@@
 We have made major revisions to our manuscript to address the reviewers' comments.
-In particular, we have tried to clarify our exposition.
+In particular, we have clarified our exposition.
 Reviewers 1 and 3 both mention that we assume that the latent and incubation periods are equivalent (thus not allowing for presymptomatic transmission). 
@@
 In this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
-Everywhere else in this paper, however, we do not assume that the incubation and exposed periods are equivalent---instead, we allow for presymptomatic transmission in the model in order to reflect the transmission dynamics of COVID-19.''
+Everywhere else in this paper, however, we do not assume that the incubation and exposed periods are equivalent.
+Instead, we allow for presymptomatic transmission in the model in order to reflect the transmission dynamics of COVID-19.''
 
@@
 ``Analogous to the intrinsic generation-interval distribution, 
-forward serial-interval distributions describe the renewal process of infection based on symptom onset dates.
+forward serial-interval distributions describe the renewal process between symptomatic cases.
 Therefore, we expect the forward serial-interval distribution during the exponential growth phase --- which we refer to as the \emph{initial} forward serial-interval distribution $f_0$ --- to estimate the same value of \Ro for a given $r$ as the intrinsic generation-interval distribution (note, however, that the forward serial interval is not necessarily positive):
 \begin{equation}
-\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau,
+\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau.
 \label{eq:Rforward}
 \end{equation}
-where the initial forward serial-interval distribution is given by:
+Here, the initial forward serial-interval distribution is given by:
 \begin{equation}
@@
 \end{equation}
-where the normalization constant $\phi$ is determined by the
-requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
-Since we have not yet made any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, this conclusion is robust, regardless of whether presymptomatic is possible or not.
-It is straightforward to see this relationship from Eq. (10) (by substituting $j(t) \approx j(0) \exp(rt)$ and $\Rs(t) \approx \Ro$);
-in Supplementary Materials, we provide a more detailed mathematical proof of this relationship.''
+where the normalization constant $\phi$ is determined by the requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
+We provide a more detailed mathematical proof of this relationship in Supplementary Materials.
+Since we do not make any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, \eref{Rforward} holds in general whether presymptomatic transmission is possible or not.''
 
@@
 $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
-secondary cohorts then we can express the total density of intervals $\tau$ between calendar time $\psymp$ and $\ssymp$ (i.e., $\tau=\ssymp-\psymp$) as follows:
+secondary cohorts then we can express the total density of intervals $\tau$ between calendar time \psymp and \ssymp (i.e., $\tau=\ssymp-\psymp$) as follows:
 \begin{equation}
 W(\psymp) \psize(\psymp) f_\psymp(\tau) = \ssize(\ssymp) b_\ssymp(\tau) \,,
-%% \label{eq:match}
+\label{eq:match}
 \end{equation}''
@@
 
-``For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical fact of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{kenah2008generation, nishiura2010time, champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.''
+``For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical process of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{kenah2008generation, nishiura2010time, champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.''
 
@@
 
-``Thus, the mean backward interval will be always shorter than the mean forward interval as long as $r > 0$---even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.''
+``The mean backward interval will be always shorter than the mean forward interval as long as $r > 0$.
+Even for different epidemics of the same disease, we expect to observe shorter backward intervals within a fast-growing epidemic (high $r$), all else being equal.''
 
@@
 
-``These studies concluded that the serial and generation intervals have the same mean when $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$ will be identical only if we assume that they are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
-something that is generally true of forward but not backward incubation-period distributions.''
+``These studies concluded that the serial and generation intervals have the same mean when $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
+However, distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$ will be identical only if we assume that they are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
+something that is generally true of forward but not backward incubation-period distributions.
+We refer to the definition \eref{intser} as the intrinsic serial interval (\fref{diagram}A).''
 
@@
 We have made major revisions to the Introduction to clarify this point and make our story more clear.
-\jd{Do we need to change the title?}
 
@@
 
-``Since the reproduction number represents an average \citep{diekmann1990definition, anderson1991infectious}, it does not capture heterogeneity among individuals or across space.
-The reproduction number also does not provide any information about the time scale of disease transmission.''
+``Since the reproduction number represents an average \citep{diekmann1990definition, anderson1991infectious}, it fails to capture heterogeneity among individuals or across space.
+The reproduction number also fails to provide any information about the time scale of disease transmission.''
 
@@
 Then, we discuss the relationship between generation and serial intervals, ending with the knowledge gap.
-We end the introduction by providing examples of how off $\RR$ estimates are in applications.
+We end the introduction by providing examples of how off $\RR$ estimates can be in applications.
 
@@
 
-``The lack of distinction is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.''
+``This confusion is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.''
 
@@
 
-We have revised the abstract according to previous suggestions and have added the following sentence to substantiate the severity: ``our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by up to 50\%--60\%.''
+We have revised the abstract according to previous suggestions and have added the following sentence to substantiate the severity: ``Our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by up to a factor of 2.6 in the context of COVID-19.''
 
@@
 
-``For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro estimates based on aggregated serial interval data underestimated \Ro by 50\%--60\%.''
+``For example, in our analysis of the COVID-19 serial intervals from China, outside Hubei province, we find that the original \Ro estimates based on aggregated serial-interval data underestimated \Ro by a factor of 2.0--2.6.''
 
@@
 We have made the following changes to attempt to improve our visual communication.
-
-\jd{I notice that you didn't fiddle the lengths. This might be worth doing.}
 
@@
 
-\swp{Doesn't this paragraph visually communicate the insights???? It was already there in the previous version...}
-
-\jd{We can add some text to the bottom of this \P, and maybe also refer back to Fig. 1 here.}
+We also color forward and backward intervals in Figure 3 according to the color scheme in Figure 1.
+We refer to figure 1 at the end of Section 3.1 (now Section 3.2):
 
@@
 In general, relative contributions of the three distributions depend on their shapes, correlations between intrinsic incubation periods and generation intervals, and overall epidemiological dynamics.''
+
+We think that making further changes to the figures will make them contain too much information, and therefore difficult to interpret.
 
@@
 ``For example, the Susceptible-Exposed-Infected-Recovered model, under the additional assumption that the incubation and exposed periods are equivalent (i.e.
-that onset of symptoms and infectiousness occur simultaneously), provides a special case where the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
-Everywhere else in this paper, however, we allow for presymptomatic transmission in the model in order to match the transmission dynamics of COVID-19.''
+that onset of symptoms and infectiousness occur simultaneously), provides a special case.
+In this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
+Everywhere else in this paper, however, we do not assume that the incubation and exposed periods are equivalent.
+Instead, we allow for presymptomatic transmission in the model in order to reflect the transmission dynamics of COVID-19.''
 
@@
 $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
-secondary cohorts then we can express the total density of intervals $\tau$ between calendar time $\psymp$ and $\ssymp$ (i.e., $\tau=\ssymp-\psymp$) as follows:
+secondary cohorts then we can express the total density of intervals $\tau$ between calendar time \psymp and \ssymp (i.e., $\tau=\ssymp-\psymp$) as follows:
 \begin{equation}
 W(\psymp) \psize(\psymp) f_\psymp(\tau) = \ssize(\ssymp) b_\ssymp(\tau) \,,
-%% \label{eq:match}
-\end{equation}''
+\end{equation}
+where $W(\psymp)$, the ``weight'' of the primary cohort, represents the average number of forward intervals that an individual in cohort $\psize(\psymp)$ produces over the course of their infection.''
 
@@
 
-``We have shown that the dynamics of the serial-interval distribution depends on the joint distribution between incubation periods and generation intervals.
+``We have shown that the dynamics of the serial-interval distribution depend on the joint distribution between incubation periods and generation intervals.
 Here, we use a bivariate lognormal distribution to model the joint probability distribution $h$ of intrinsic incubation periods and intrinsic generation intervals (in the renewal equation model, \eref{renewal}) while allowing for the possibility that they might be correlated.
-Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset, we generally expect the generation intervals to be positively correlated with the incubation period:
+Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset \citep{he2020temporal}, we generally expect the generation intervals to be positively correlated with the incubation period:
 that is, individuals who develop symptoms later are more likely to transmit later.
@@
 
-``Here, we lay out a few practical principles for analyzing and interpreting serial-interval data.
-First, serial intervals should be cohorted based on the symptom onset date whenever possible.
-Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals is expected to differ from this expectation, and to change through time due to epidemic dynamics.
-Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided as they can be subject to different censoring and epidemiological biases:
+``In closing, we lay out a few practical principles for analyzing and interpreting serial-interval data.
+First, serial intervals should be cohorted based on the symptom onset date of the infector (and not of the infectee) whenever possible.
+Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals differs from this expectation, and changes through time due to epidemic dynamics.
+Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided because the realized serial-interval distribution can be subject to different censoring and epidemiological biases:
 Even when \emph{all} realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR}).
-Third, applying serial interval information from one epidemic of a given disease to another should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.
+Third, applying serial interval information across epidemics of a given disease should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.
 Finally, serial-interval data should be accompanied by a trajectory of the epidemic curve, whenever possible, to provide epidemiological context.

### 2020-10-06 serial.tex
am i done now

@@
 
-Estimating the reproduction number \RR is challenging because it cannot be measured directly.
+Estimating the reproduction number \RR is challenging because it cannot be measured directly for most emerging pathogens.
 Most methods of \RR estimation require a detailed knowledge of the life history along with reliable incidence data.
@@
 Conversely, using inaccurately defined serial intervals or failing to account for changes in the observed serial-interval distributions over the course of an epidemic can considerably bias estimates of \RR.
-For example, in our analysis of the COVID-19 serial intervals from China, we find that the original \Ro estimates based on aggregated serial-interval data underestimated \Ro by a factor of 2.0--2.6.
+For example, in our analysis of the COVID-19 serial intervals from China, outside Hubei province, we find that the original \Ro estimates based on aggregated serial-interval data underestimated \Ro by a factor of 2.0--2.6.
 We further lay out several principles to consider in using information about serial intervals and other epidemiological time delays to correctly infer the initial reproduction number during the early stages of an outbreak.
@@
 interval between the infector and the infectee.
-These studies concluded that the serial and generation intervals have the same mean when $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation};
-however, distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$ will be identical only if we assume that they are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
+These studies concluded that the serial and generation intervals have the same mean when $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
+However, distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$ will be identical only if we assume that they are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
 something that is generally true of forward but not backward incubation-period distributions.
@@
 We further address how the observed serial intervals, measured through contact tracing, are affected by right censoring during an ongoing epidemic and provide a heuristic method for addressing biases that can arise from using serial-interval data to estimate \Ro.
-Finally, we analyze serial-interval data from the COVID-19 epidemic in China, outside Hubei province based on 468 transmission events reported between January 21--February 8, 2020, under our framework.
+Finally, we analyze serial-interval data from the COVID-19 epidemic in China, outside Hubei province, based on 468 transmission events reported between January 21--February 8, 2020, under our framework.
 
@@
 In order to have an unbiased estimate of the basic reproduction number, we need to estimate the initial forward serial-interval distribution --- i.e., serial intervals based on cohorts of infectors who share the same symptom onset time, at the early stage of the epidemic.
-However, researchers typically use all available information to estimate epidemiological parameters (e.g., aggregating all serial intervals observed until certain time of an epidemic);
-for example, \cite{thompson2019improved} recently suggested that up-to-date serial-interval data are necessary to accurately estimate the reproduction number.
+However, researchers typically use all available information to estimate epidemiological parameters (e.g., aggregating all serial intervals observed until certain time of an epidemic).
+For example, \cite{thompson2019improved} recently suggested that up-to-date serial-interval data are necessary to accurately estimate the reproduction number.
 We explore the consequences of neglecting changes in the realized serial-interval distribution on estimates of the basic reproduction number.

### 2020-10-06 serial_guide.R

@@ -57,10 +57,10 @@ g2 <- ggplot(arrow) +
   geom_point(aes(1.5, 0), size=3) +
   geom_point(aes(2.5, 0), size=3) +
   geom_point(aes(3.5, 0), size=3) +
-  geom_point(aes(0.5, 0.2), size=3, col="green") +
-  geom_point(aes(1.5, 0.4), size=3, col="green") +
-  geom_point(aes(2.5, 0.3), size=3, col="green") +
-  geom_point(aes(1.5, 0.1), size=3, col="blue") +
+  geom_point(aes(0.5, 0.2), size=3, col="#81b214") +
+  geom_point(aes(1.5, 0.4), size=3, col="#81b214") +
+  geom_point(aes(2.5, 0.3), size=3, col="#81b214") +
+  geom_point(aes(1.5, 0.1), size=3, col="#07689f") +
   annotate("text", x=1.5, y=-0.05, label="$p$") +
   annotate("text", x=0.5, y=-0.05, label="$p-\\tau_{\\rm i1}$") +
   annotate("text", x=0.5, y=-0.1, label="Infector") +
@@ -69,10 +69,10 @@ g2 <- ggplot(arrow) +
   annotate("text", x=2.5, y=-0.05, label="$p-\\tau_{\\rm i1}+\\tau_{\\rm g}$") +
   annotate("text", x=3.5, y=-0.05, label="$p-\\tau_{\\rm i1}+\\tau_{\\rm g}+\\tau_{\\rm i2}$") +
   geom_segment(aes(x, y, xend=x1, yend=y1), arrow = arrow(length = unit(0.2, "inches")), lwd=1) +
-  geom_segment(aes(1.5, 0.1, xend=0.5, yend=0.1), arrow = arrow(length = unit(0.1, "inches")), lwd=1, col="blue") +
-  geom_segment(aes(0.5, 0.2, xend=2.5, yend=0.2), arrow = arrow(length = unit(0.1, "inches")), lwd=1, col="green") +
-  geom_segment(aes(2.5, 0.3, xend=3.5, yend=0.3), arrow = arrow(length = unit(0.1, "inches")), lwd=1, col="green") +
-  geom_segment(aes(1.5, 0.4, xend=3.5, yend=0.4), arrow = arrow(length = unit(0.1, "inches")), lwd=1.5, col="green") +
[…]

### 2020-10-06 response.tex
really done?

@@
 We provide a more detailed mathematical proof of this relationship in Supplementary Materials.
-Since we do not make any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, \eref{Rforward} holds in general whether presymptomatic transmission is possible or not.''
+Since we do not make any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, Eq.
+(18) holds in general whether presymptomatic transmission is possible or not.''
 
@@
 something that is generally true of forward but not backward incubation-period distributions.
-We refer to the definition \eref{intser} as the intrinsic serial interval (\fref{diagram}A).''
+We refer to the definition Eq. (4) as the intrinsic serial interval (Fig. 1A).''
 
@@
 ``The forward serial-interval distributions depend on distributions of three intervals
-(\fref{diagram}B): (i) the backward incubation period, (ii) the forward generation interval, and (iii) the forward incubation period.
-In these simulations, both forward incubation period (\fref{epi}B) and generation-interval (\fref{epi}C) distributions remain roughly constant;
-therefore, changes in the forward serial-interval distributions (\fref{epi}D) are predominantly driven by changes in the backward incubation period distribution, whose mean increases over time as the growth rate of disease incidence slows and then reverses.
+(Fig. 1{diagram}B): (i) the backward incubation period, (ii) the forward generation interval, and (iii) the forward incubation period.
+In these simulations, both forward incubation period (Fig. 3B) and generation-interval (Fig. 3C) distributions remain roughly constant;
+therefore, changes in the forward serial-interval distributions (Fig.
+3D) are predominantly driven by changes in the backward incubation period distribution, whose mean increases over time as the growth rate of disease incidence slows and then reverses.
 In general, relative contributions of the three distributions depend on their shapes, correlations between intrinsic incubation periods and generation intervals, and overall epidemiological dynamics.''
@@
 ``We have shown that the dynamics of the serial-interval distribution depend on the joint distribution between incubation periods and generation intervals.
-Here, we use a bivariate lognormal distribution to model the joint probability distribution $h$ of intrinsic incubation periods and intrinsic generation intervals (in the renewal equation model, \eref{renewal}) while allowing for the possibility that they might be correlated.
+Here, we use a bivariate lognormal distribution to model the joint probability distribution $h$ of intrinsic incubation periods and intrinsic generation intervals (in the renewal equation model, Eq.
+(12)) while allowing for the possibility that they might be correlated.
 Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset \citep{he2020temporal}, we generally expect the generation intervals to be positively correlated with the incubation period:
@@
 
-``In order to quantify changes in serial intervals, we group them by the symptom onset dates of the primary (\fref{du}B) and secondary (\fref{du}C) cases---corresponding to forward and backward serial-interval distributions, respectively---and compute their mean and 95\% quantiles.''
+``In order to quantify changes in serial intervals, we group them by the symptom onset dates of the primary (Fig.
+5B) and secondary (Fig.
+5C) cases---corresponding to forward and backward serial-interval distributions, respectively---and compute their mean and 95\% quantiles.''
 
@@
 Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided because the realized serial-interval distribution can be subject to different censoring and epidemiological biases:
-Even when \emph{all} realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR}).
+Even when \emph{all} realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (Fig. 4).
 Third, applying serial interval information across epidemics of a given disease should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.

### 2020-10-07 serial.tex
Minor changes responsive to Mike's troublesome comments

@@
 
-Estimating the reproduction number \RR is challenging because it cannot be measured directly for most emerging pathogens.
-Most methods of \RR estimation require a detailed knowledge of the life history along with reliable incidence data.
-Alternatively, near the beginning of an epidemic, \RR can be estimated from the population-level exponential growth rate $r$.
-This rate-based approach is convenient because the growth rate can be estimated robustly from case reports \citep{mills2004transmissibility, ma2014estimating}.
+Estimating the reproduction number \RR is often challenging.
+Direct estimates based on observed infections will typically be biased down when some infections cannot be observed
+A common method of estimating \RR near the beginning of an epidemic is based on the population-level exponential growth rate $r$, which can often be estimated robustly from case reports \citep{mills2004transmissibility, ma2014estimating}.
 The growth rate $r$ and the reproduction number \RR are linked by the generation-interval distribution \cite{wallinga2007generation}, where the generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee) \citep{svensson2007note}.
@@
 While generation and serial intervals both measure the time scale of disease transmission, they measure fundamentally different quantities. 
-In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean, assuming that the incubation periods of the infector and infectee are identically distributed \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
-Serial intervals can also take negative values due to presymptomatic transmission \citep{he2020temporal}, whereas generation intervals must be positive.
+In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
+Serial intervals can in some cases even take negative values in the presence of presymptomatic transmission \citep{he2020temporal}, whereas generation intervals must be positive.
 
@@
 
-A time delay between two epidemiological events can involve either one infected individual (e.g., incubation period: infection and symptom onset of an individual) or two --- an infector and an infectee (e.g., the serial interval).
+A time delay between two epidemiological events can involve either one infected individual (e.g., incubation period: infection and symptom onset of an individual) or two --- an infector and an infectee (e.g., the generation interval).
 We define the delay as the time difference between the \emph{primary} event and the \emph{secondary} event.

### 2020-10-08 serial.tex
a few things

@@
 where $r$ is the exponential growth rate.
+\swp{JSW: If this is what you mean by 'direct', it's still opaque!  How do you humans interpret this.  It's non trivial!}
 Since $b_0$ is a probability distribution, $\left[W(0) \psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ corresponds to the normalization constant.
@@
 Since we do not make any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, \eref{Rforward} holds in general whether presymptomatic transmission is possible or not.
+\swp{here}
 
@@
 
+\swp{heree}
 Our study also underlines the fact that the serial-interval distribution depends not only on the generation-interval and incubation-period distributions, but also on their intrinsic correlations.

### 2020-10-08 serial.tex
edit

@@
 While generation and serial intervals both measure the time scale of disease transmission, they measure fundamentally different quantities. 
-In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
+In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean when the incubation periods of the infector and infectee are identically distributed \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
 Serial intervals can in some cases even take negative values in the presence of presymptomatic transmission \citep{he2020temporal}, whereas generation intervals must be positive.

### 2020-10-08 serial.tex
commit

@@
 where $r$ is the exponential growth rate.
-\swp{JSW: If this is what you mean by 'direct', it's still opaque!  How do you humans interpret this.  It's non trivial!}
 Since $b_0$ is a probability distribution, $\left[W(0) \psize(0)/\ssize(0)\right]^{-1} = \int_{-\infty}^{\infty} \exp(-r\tau') f_0(\tau') \dtau'$ corresponds to the normalization constant.
-Therefore, the backward delay distribution during the exponential growth phase depends only on the exponential growth rate $r$ and the initial forward forward delay distribution $f_0$.
+Therefore, the backward delay distribution during the exponential growth phase depends only on the exponential growth rate $r$ and the initial forward delay distribution $f_0$.
 
@@
 where the normalization constant $\phi$ is determined by the requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
-We provide a more detailed mathematical proof of this relationship in Supplementary Materials.
-Since we do not make any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, \eref{Rforward} holds in general whether presymptomatic transmission is possible or not.
-\swp{here}
+We provide a mathematical proof of this relationship in Supplementary Materials.
+Since we do not make any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, \eref{Rforward} holds in general whether or not there is a presymptomatic transmission period.
 
@@
 
-\swp{heree}
-Our study also underlines the fact that the serial-interval distribution depends not only on the generation-interval and incubation-period distributions, but also on their intrinsic correlations.
-Here, we use a bivariate lognormal distribution to capture their correlations phenomenologically and to show that realized serial intervals can decrease over time in the context of COVID-19.
+Our study underlines the fact that the serial-interval distribution depends not only on the generation-interval and incubation-period distributions, but also on the correlation between their duration in a given individual.
+Here, we use a bivariate lognormal distribution to capture these correlations phenomenologically and to show that realized serial intervals can decrease over time in the context of COVID-19.
 Although their true correlation will depend on viral load dynamics, we expect our conclusions about decreasing serial intervals of COVID-19 to be robust as individuals with longer incubation periods will generally have a longer time window to transmit before symptom onset.

### 2020-10-08 response.tex
done?

@@
 
-We are not positive we understand this comment.
+Thank you for the suggestion, although we are not positive we understand this comment.
 Figure 1 is not really intended to communicate the source of biases: that comes later in the course of our exposition.
@@
 We also color forward and backward intervals in Figure 3 according to the color scheme in Figure 1.
-We refer to figure 1 at the end of Section 3.1 (now Section 3.2):
+We previously referred to figure 1 at the end of Section 3.1 (now Section 3.2); this paragraph (quoted here) carefully outlines the dynamical effects on the realized lengths of the different intervals.
 
@@
 
-We think that making further changes to the figures will make them contain too much information, and therefore difficult to interpret.
+We are concerned that making further changes to the figures would probably make them overly complex, and therefore harder to interpret.
 

### 2020-10-08 serial.tex
abstract tweaks

--- 2020-10-08 serial.tex
@@
 The reproduction number \RR and the exponential growth rate $r$ are critical quantities for characterizing outbreak dynamics.
-These quantities are linked by generation intervals---defined as the time between infection and transmission.
+These quantities are linked by generation intervals, defined as the time between infection and transmission.
 Because generation intervals are difficult to measure directly, serial intervals---defined as the onset of symptoms in a chain of transmission---are often substituted.
-However, recent studies suggest that the two intervals give different estimates of \RR from $r$.
-We show that \emph{forward-looking} serial intervals, which begin in a certain period, correctly describe the renewal process of symptomatic cases and therefore link \RR with $r$.
+However, recent studies suggest that making this substitution can lead to significant changes when using $r$ to estimate \RR.
+Here we explore the differences among these intervals, how they vary over the course of an epidemic, and the implications for estimating epidemic parameters.
+We show that \emph{forward-looking} serial intervals, which begin in a certain period, correctly describe the renewal process of symptomatic cases and therefore reliably link \RR with $r$.
 These forward intervals are different from \emph{intrinsic} intervals, which neglect population-level dynamics, and \emph{backward-looking} intervals, which end in a certain period.
-Instead, the forward-looking intervals depend on $r$:
-When an epidemic is growing exponentially, infectors that develop symptoms on a given day will have shorter incubation periods, on average, than their infectees, thereby affecting the serial-interval distribution.
+The forward-looking intervals depend on $r$:
+During the exponential growth phase of an epidemic, infectors that develop symptoms on a given day will have shorter incubation periods, on average, than their infectees, changing the serial-interval distribution in complex ways that depend on
 We provide a heuristic method for addressing biases that can arise from neglecting changes in serial intervals. 
 We apply the method to estimation of \RR for the COVID-19 outbreak in China, outside Hubei province, using serial-interval data collected between January 21--February 8, 2020. 
-Our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by up to a factor of 2.6 in the context of COVID-19.
+Our analysis shows that using improperly defined serial intervals can bias estimates of initial \RR by up to a factor of 2.6 in the context of COVID-19.
 This study demonstrates the importance of early contact tracing efforts and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.

### 2020-10-08 serial.tex
abstract tweaks

--- 2020-10-08 serial.tex
@@
 
-The reproduction number \RR and the exponential growth rate $r$ are critical quantities for characterizing outbreak dynamics.
-These quantities are linked by generation intervals---defined as the time between infection and transmission.
-Because generation intervals are difficult to measure directly, serial intervals---defined as the onset of symptoms in a chain of transmission---are often substituted.
-However, recent studies suggest that the two intervals give different estimates of \RR from $r$.
-We show that \emph{forward-looking} serial intervals, which begin in a certain period, correctly describe the renewal process of symptomatic cases and therefore link \RR with $r$.
-These forward intervals are different from \emph{intrinsic} intervals, which neglect population-level dynamics, and \emph{backward-looking} intervals, which end in a certain period.
-Instead, the forward-looking intervals depend on $r$:
-When an epidemic is growing exponentially, infectors that develop symptoms on a given day will have shorter incubation periods, on average, than their infectees, thereby affecting the serial-interval distribution.
-We provide a heuristic method for addressing biases that can arise from neglecting changes in serial intervals. 
-We apply the method to estimation of \RR for the COVID-19 outbreak in China, outside Hubei province, using serial-interval data collected between January 21--February 8, 2020. 
-Our analysis shows that using incorrectly defined serial intervals can bias estimates of initial \RR by up to a factor of 2.6 in the context of COVID-19.
-This study demonstrates the importance of early contact tracing efforts and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.
+The reproduction number \RR and the growth rate $r$ are critical quantities for characterizing outbreak dynamics.
+They are linked by generation intervals, the time between infection and onward transmission.
+Because generation intervals are difficult to observe, epidemiologists often substitute serial intervals, the time between symptom onset in successive links in a transmission chain.
+Recent studies suggest that such substitution can bias estimates of \RR based on $r$.
+Here we explore how these intervals vary over the course of an epidemic, and the implications for \RR estimation.
+\emph{Forward-looking} serial intervals, measuring time forward from symptom onset of a focal individual, correctly describe the renewal process of symptomatic cases and therefore reliably link \RR with $r$.
+In contrast, \emph{backward-looking} intervals, which measure time backward, and \emph{intrinsic} intervals, which neglect population-level dynamics, lead to incorrect \RR estimates.
+Forward-looking intervals are affected both by epidemic dynamics and by censoring, changing in complex ways over the course of an epidemic.
+We derive a heuristic method for addressing biases that arise from neglecting changes in serial intervals. 
+We apply the method to early serial-interval-based estimates of  \RR for the COVID-19 outbreak in China outside Hubei province,
+showing that using improperly defined serial intervals in this context can bias estimates of initial \RR by up to a factor of 2.6.
+This study demonstrates the importance of early contact-tracing efforts and provides a framework for reassessing generation intervals, serial intervals, and \RR\ estimates for COVID-19.
 

### 2020-10-08 serial.tex
squoze dates back into abstract

@@
 
-The reproduction number \RR and the growth rate $r$ are critical quantities for characterizing outbreak dynamics.
+The reproduction number \RR and the growth rate $r$ are critical epidemiological quantities.
 They are linked by generation intervals, the time between infection and onward transmission.
 Because generation intervals are difficult to observe, epidemiologists often substitute serial intervals, the time between symptom onset in successive links in a transmission chain.
-Recent studies suggest that such substitution can bias estimates of \RR based on $r$.
+Recent studies suggest that such substitution biases estimates of \RR based on $r$.
 Here we explore how these intervals vary over the course of an epidemic, and the implications for \RR estimation.
 \emph{Forward-looking} serial intervals, measuring time forward from symptom onset of a focal individual, correctly describe the renewal process of symptomatic cases and therefore reliably link \RR with $r$.
-In contrast, \emph{backward-looking} intervals, which measure time backward, and \emph{intrinsic} intervals, which neglect population-level dynamics, lead to incorrect \RR estimates.
+In contrast, \emph{backward-looking} intervals, which measure time backward, and \emph{intrinsic} intervals, which neglect population-level dynamics, give incorrect \RR estimates.
 Forward-looking intervals are affected both by epidemic dynamics and by censoring, changing in complex ways over the course of an epidemic.
-We derive a heuristic method for addressing biases that arise from neglecting changes in serial intervals. 
-We apply the method to early serial-interval-based estimates of  \RR for the COVID-19 outbreak in China outside Hubei province,
-showing that using improperly defined serial intervals in this context can bias estimates of initial \RR by up to a factor of 2.6.
+We present a heuristic method for addressing biases that arise from neglecting changes in serial intervals. 
+We apply the method to early (21 January 21 -- 8 February 8 2020) serial-interval-based estimates of  \RR for the COVID-19 outbreak in China outside Hubei province; using improperly defined serial intervals in this context biases estimates of initial \RR by up to a factor of 2.6.
 This study demonstrates the importance of early contact-tracing efforts and provides a framework for reassessing generation intervals, serial intervals, and \RR\ estimates for COVID-19.

### 2020-10-08 serial.tex
remove some numbers

@@
 We present a heuristic method for addressing biases that arise from neglecting changes in serial intervals. 
-We apply the method to early (21 January 21 -- 8 February 8 2020) serial-interval-based estimates of  \RR for the COVID-19 outbreak in China outside Hubei province; using improperly defined serial intervals in this context biases estimates of initial \RR by up to a factor of 2.6.
+We apply the method to early (21 January -- 8 February 2020) serial-interval-based estimates of  \RR for the COVID-19 outbreak in China outside Hubei province; using improperly defined serial intervals in this context biases estimates of initial \RR by up to a factor of 2.6.
 This study demonstrates the importance of early contact-tracing efforts and provides a framework for reassessing generation intervals, serial intervals, and \RR\ estimates for COVID-19.

### 2020-10-13 response.tex
really close

@@
 Reviewers 1 and 3 both mention that we assume that the latent and incubation periods are equivalent (thus not allowing for presymptomatic transmission). 
-However, we only present this scenario in the appendix as a special case; We do not make this assumption in the main text.
+However, we only present this scenario in the appendix as a special case.
+We do not make this assumption in the main text.
 We have thus tried to make our assumptions clear and our results more accessible.
+We have also re-written a large proportion of the paper, including a new title, to provide a more coherent story.
 Below please find our detailed responses to reviewers.
@@
 We do not assume this.
-Also, Figure 2--3 illustrate that generation and serial intervals have different means, and therefore are different distributions.
+Also, Figure 2--3 illustrate that generation and serial intervals have different means, and therefore are distributed differently.
 We highlight these differences throughout the main text.
@@
 We have made major revisions to the Introduction to clarify this point and make our story more clear.
+
+We have updated the title: ``Forward-looking serial intervals correctly link epidemic growth to reproduction numbers.''
+
+We have also re-written the abstract:
+
+``The reproduction number \RR and the growth rate $r$ are critical epidemiological quantities.
+They are linked by generation intervals, the time between infection and onward transmission.
+Because generation intervals are difficult to observe, epidemiologists often substitute serial intervals, the time between symptom onset in successive links in a transmission chain.
+Recent studies suggest that such substitution biases estimates of \RR based on $r$.
+Here we explore how these intervals vary over the course of an epidemic, and the implications for \RR estimation.
+\emph{Forward-looking} serial intervals, measuring time forward from symptom onset of an infector, correctly describe the renewal process of symptomatic cases and therefore reliably link \RR with $r$.
+In contrast, \emph{backward-looking} intervals, which measure time backward, and \emph{intrinsic} intervals, which neglect population-level dynamics, give incorrect \RR estimates.
+Forward-looking intervals are affected both by epidemic dynamics and by censoring, changing in complex ways over the course of an epidemic.
+We present a heuristic method for addressing biases that arise from neglecting changes in serial intervals. 
+We apply the method to early (21 January -- 8 February 2020) serial-interval-based estimates of  \RR for the COVID-19 outbreak in China outside Hubei province; using improperly defined serial intervals in this context biases estimates of initial \RR by up to a factor of 2.6.
+This study demonstrates the importance of early contact-tracing efforts and provides a framework for reassessing generation intervals, serial intervals, and \RR\ estimates for COVID-19.''
 

### 2020-10-13 serial.tex
really close

@@
 	\textbf\newline{
-		Cohort-based approach to understanding the roles of generation and serial intervals in shaping epidemiological dynamics
+		Forward-looking serial intervals correctly link epidemic growth to reproduction numbers
 	}
@@
 Here we explore how these intervals vary over the course of an epidemic, and the implications for \RR estimation.
-\emph{Forward-looking} serial intervals, measuring time forward from symptom onset of a focal individual, correctly describe the renewal process of symptomatic cases and therefore reliably link \RR with $r$.
+\emph{Forward-looking} serial intervals, measuring time forward from symptom onset of an infector, correctly describe the renewal process of symptomatic cases and therefore reliably link \RR with $r$.
 In contrast, \emph{backward-looking} intervals, which measure time backward, and \emph{intrinsic} intervals, which neglect population-level dynamics, give incorrect \RR estimates.
@@
 Here, we show that estimating \RR based on $r$ and the serial-interval distribution, when defined from the correct reference time and cohort, gives the same estimate as using $r$ and the generation-interval distribution.
-We apply our framework to serial-interval data from the COVID-19 outbreak in China, outside Hubei province, reported between January  21--February 8, 2020, revealing systematic biases in prior inference methods.
+We apply our framework to serial-interval data from the COVID-19 outbreak in China, outside Hubei province (January  21--February 8, 2020), revealing systematic biases in prior inference methods.
 Our study provides the theoretical basis for practical changes to the principled use of serial interval distributions in estimating \RR during epidemics.
@@
 Estimating the reproduction number \RR is often challenging.
-Direct estimates based on observed infections will typically be biased down when some infections cannot be observed
+Direct estimates based on observed infections will typically be biased down when some infections cannot be observed.
 A common method of estimating \RR near the beginning of an epidemic is based on the population-level exponential growth rate $r$, which can often be estimated robustly from case reports \citep{mills2004transmissibility, ma2014estimating}.
@@
 
-A time delay between two epidemiological events can involve either one infected individual (e.g., incubation period: infection and symptom onset of an individual) or two --- an infector and an infectee (e.g., the generation interval).
+A time delay between two epidemiological events can involve either one infected individual (e.g., incubation period: infection and symptom onset of an individual) or two --- an infector and an infectee (e.g., generation and serial intervals).
 We define the delay as the time difference between the \emph{primary} event and the \emph{secondary} event.
@@
 The backward delay distribution describes the time delays between a primary and secondary events given that the secondary event occurred at time \ssymp.
-For example, the backward incubation period distribution at time \ssymp describes incubation periods for a \emph{cohort} of individuals who became symptomatic at time \ssymp.
-Likewise, the backward serial-interval distribution at time \ssymp describes serial intervals for a \emph{cohort} of infectees who became symptomatic at time \ssymp.
+For example, the backward incubation period distribution at time \ssymp\ describes incubation periods for a \emph{cohort} of individuals who became symptomatic at time \ssymp.
+Likewise, the backward serial-interval distribution at time \ssymp\ describes serial intervals for a \emph{cohort} of infectees who became symptomatic at time \ssymp.
 
@@
 $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
-secondary cohorts then we can express the total density of intervals $\tau$ between calendar time \psymp and \ssymp (i.e., $\tau=\ssymp-\psymp$) as follows:
+secondary cohorts then we can express the total density of intervals $\tau$ between calendar time \psymp\ and \ssymp\ (i.e., $\tau=\ssymp-\psymp$) as follows:
 \begin{equation}
@@
 this equation is the probability density that an individual
-who became symptomatic at time \ssymp had an incubation period of
+who became symptomatic at time \ssymp\ had an incubation period of
 length $\tau$.
@@
 }
+\label{fig:du}
 \end{center}
-\label{fig:du}
 \end{figure}
 
-Finally, we re-analyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on 468 transmission events reported between January 21--February 8, 2020;
+Finally, we re-analyze serial intervals of COVID-19 collected by \cite{du2020serial} from mainland China, outside Hubei province, based on 468 transmission events reported between January 21--February 8, 2020.
 \cite{du2020serial} estimated the mean serial interval of 3.96 days (95\% CI 3.53–4.39 days) and \Ro of 1.32 (95\% CI 1.16–1.48).
@@
 Biases in the observed serial intervals will necessarily bias the estimates of \RR. 
-Furthermore, when one of the individuals in a transmission pair is asymptomatic, there is no symptom-based serial interval; 
-neglecting the time scale of asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
+Furthermore, when one of the individuals in a transmission pair is asymptomatic, there is no symptom-based serial interval.
+Neglecting the time scale of asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
 
@@
 \RR---during the COVID-19 pandemic.
+
+\section*{Data availability}
+
+All data and code are stored in a publicly available GitHub repository (https://github.com/parksw3/serial).
 

### 2020-10-13 serial.tex
fix url
done?

@@
 While generation and serial intervals both measure the time scale of disease transmission, they measure fundamentally different quantities. 
-In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean when the incubation periods of the infector and infectee are identically distributed \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
+In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean in many contexts \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
 Serial intervals can in some cases even take negative values in the presence of presymptomatic transmission \citep{he2020temporal}, whereas generation intervals must be positive.
@@
 
-All data and code are stored in a publicly available GitHub repository (https://github.com/parksw3/serial).
+All data and code are stored in a publicly available GitHub repository (\url{https://github.com/parksw3/serial}).
 

### 2020-10-13 serial.tex
Minor changes to S2

@@
 \end{equation}
-Therefore, the initial forward serial-interval distribution, $f_0(\tau)$, provides a correct link between the exponential growth rate $r$ and the initial serial reproduction number $\Rs(0)$.
+Therefore, the initial forward serial-interval distribution, $f_0(\tau)$, provides the correct link between the exponential growth rate $r$ and the initial serial reproduction number $\Rs(0)$.
 We re-visit this idea later in Section 2.4 and show that the initial forward serial-interval distribution provides the same $r$--\RR link as the intrinsic generation-interval distribution.
@@
 
-We illustrate changes in forward and backward serial intervals over the course of an epidemic by applying it to a specific example of an epidemic model.
+We illustrate changes in forward and backward serial intervals over the course of an epidemic by applying our framework to a specific example of an epidemic model.
 We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
@@
 where $\RR(t)$ is the instantaneous reproduction number (i.e., the average number of secondary cases that a primary case infected at time $t$ will generate if conditions at time $t$ remain unchanged \citep{fraser2007estimating}), and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a population where changes in $\RR(t)$ is negligible \citep{champredon2015intrinsic}).
-This model effectively assumes that epidemic dynamics are driven by changes in transmission rate, which may not hold under individual-based intervention such as case isolation \citep{fraser2007estimating};
+This model assumes that $g(\tau)$ remains constant through time -- in other words, that epidemic dynamics are driven by changes in transmission rate. 
+This assumption may not be well suited to individual-based intervention such as case isolation \citep{fraser2007estimating};
 nonetheless, this form has been widely used in the literature and has been successfully applied in modeling the current COVID-19 pandemic \citep{gostic2020practical}.
@@
 \textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
-(A). The initial forward serial-interval distributions give a correct
+(A). The initial forward serial-interval distributions give the correct
 link between the exponential growth rate $r$ and the reproduction

### 2020-10-13 serial.tex
small changes to Discussion

@@
 Generation and serial intervals determine the time scale of disease transmission, and are therefore critical to dynamical modeling of infectious outbreaks.
-Here, we show that the initial \emph{forward} serial-interval distribution --- measured from the cohort of infectors who developed symptoms during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the initial reproduction number \RR.
+We have shown that the initial \emph{forward} serial-interval distribution --- measured from the cohort of infectors who developed symptoms during the exponential growth phase of an epidemic --- provides the correct link between the exponential growth rate $r$ and the initial reproduction number \RR.
 In general, the forward serial-interval distributions will not match the intrinsic serial-interval distribution (which has the same mean as the intrinsic generation-interval distribution) because the incubation period of the infectors (conditional on their symptom onset date of the infector) will be subject to backward biases.
@@
 
-Recently, \cite{ali2020serial} also showed that serial intervals of COVID-19 decreased in China.
-Analogous to our approach, they also grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean forward serial interval decreased from 7.8 days to 2.6 days.
+Recently, \cite{ali2020serial} also showed that forward serial intervals of COVID-19 decreased through time in China.
+They grouped serial intervals by the symptom onset date of infectors across 14-day periods and found that the mean forward serial interval decreased from 7.8 days to 2.6 days.
 While they attributed the decrease in serial intervals to reduction of the isolation delay, their regression analysis showed that isolation delays explain only 51.5\% of the variation in serial intervals (they could explain up to 72\% of the variance by including other intervention measures).
-Our framework provides an explanation for the remaining variation: changes in the backward incubation period during the decreasing phase of an epidemic also shorten serial intervals due to increased amount of presymptomatic transmission (even in the absence of nonpharmaceutical interventions).
-Since isolation delays and other intervention measures affect the amount of onward transmission, and therefore the distribution of realized (forward) generation intervals, it cannot explain all variation in forward serial intervals, which depend on (i) backward incubation period of the infector, (ii) the forward generation interval, and (iii) the forward incubation period of the infectee (\fref{diagram}B).
+Our framework provides an explanation for the remaining variation: changes in the backward incubation period during the decreasing phase of an epidemic act to further shorten serial intervals due to increased amount of presymptomatic transmission (even in the absence of nonpharmaceutical interventions).
+Isolation delays and other intervention measures affect the amount of onward transmission, and therefore the distribution of realized (forward) generation intervals.
+They therefore are not expected to explain all the variation in forward serial intervals, since these additionally depend on both the backward incubation period of the infector and (iii) the forward incubation period of the infectee (\fref{diagram}B).
 
@@
 Future studies should explore how neglecting changes in the forward serial-interval distribution can affect the estimates of \RR beyond the exponential growth phase, and potentially re-assess existing estimates of \RR.
-We also suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions and understand their changes over time.
+We also suggest that modelers should aim to characterize spatiotemporal variation in forward serial-interval distributions.
 These modeling approaches should be coupled with epidemiological investigation through contact tracing. 
@@
 Here, we use a bivariate lognormal distribution to capture these correlations phenomenologically and to show that realized serial intervals can decrease over time in the context of COVID-19.
-Although their true correlation will depend on viral load dynamics, we expect our conclusions about decreasing serial intervals of COVID-19 to be robust as individuals with longer incubation periods will generally have a longer time window to transmit before symptom onset.
-In general, the impact of increasing backward incubation periods on the forward serial intervals are likely to be disease specific---for example, we show in Supplementary Materials that the initial forward serial-interval distribution can be equivalent to the intrinsic generation-interval distribution, regardless of the growth rate $r$, due to independence between the incubation period and time from symptom onset to transmission and the lack of presymptomatic transmission.
-Future studies trying to model realized serial intervals should consider carefully the joint distribution between the generation intervals and incubation periods.
+Although their true correlation will depend on viral load dynamics, we expect our conclusions about decreasing serial intervals of COVID-19 to be robust, as individuals with longer incubation periods will generally have a longer time window to transmit before symptom onset.
+In general, the impact of increasing backward incubation periods on the forward serial intervals are likely to be disease-specific---for example, we show in Supplementary Materials that the initial forward serial-interval distribution can be equivalent to the intrinsic generation-interval distribution, regardless of the growth rate $r$, due to independence between the incubation period and time from symptom onset to transmission and the lack of presymptomatic transmission.
+Future studies trying to interpret realized serial intervals should consider carefully the joint distribution between the generation intervals and incubation periods.
 
@@
 Even when \emph{all} realized serial intervals can be observed throughout an unmitigated epidemic, we do not obtain the intrinsic serial interval distribution due to susceptible depletion (\fref{obsrR}).
-Third, applying serial interval information across epidemics of a given disease should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.
+Third, applying serial-interval information across epidemics of a given disease should be done with care, because serial intervals are epidemic-specific, rather than disease-specific.
 Finally, serial-interval data should be accompanied by a trajectory of the epidemic curve, whenever possible, to provide epidemiological context.
-In practice, these recommendations will sometimes be hard to follow, due to limited data about serial intervals, but these issues should be kept in mind when interpreting serial-interval data and understand transmission dynamics at the individual-level.
+In practice, these recommendations will sometimes be hard to follow, due to limited data about serial intervals, but these issues should be kept in mind when interpreting serial-interval data to inform transmission dynamics.
 
@@
 measurement of generation intervals \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
-we generalize these ideas and show that they apply to any other epidemiological distributions.
+we generalize these ideas and show that they apply to other epidemiological distributions.
 Some studies during the early phases of the COVID-19 epidemics have tried to correct for the backward biases \citep{verity2020estimates}, but changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.

### 2020-10-13 serial.tex
done??

@@
 
-Here, we consider a specific example where changes in the reproduction number are driven by susceptible depletion: $\RR(t) = \Ro S(t)$, where \Ro represents the basic reproduction number.
-Although we do not consider non-pharmaceutical interventions or behavioral changes explicitly, the effect of susceptible depletion is mathematically equivalent to the effect of population-level interventions, such as social-distancing, that reduce \RR(t).
+Here, changes in reproduction number can be modeled as a product of the basic reproduction number $\Ro$, proportion susceptible $S(t)$, and some intervention function $M(t)$, which can either decrease and/or increase in time: $\RR(t) = \Ro S(t) M(t)$;
+\cite{flaxman2020estimating} used a similar framework to evaluate the impact of nonpharmaceutical interventions on the spread of COVID-19 in 11 countries.
 Then, the forward generation-interval for a cohort of individuals that were infected at time $\psymp$ follows \citep{champredon2015intrinsic}:
 \begin{equation}
-\gdist_\psymp (\tau) = \frac{ \gdist(\tau) S(\psymp + \tau)}{\int_0^\infty \gdist(\tau') S(\psymp + \tau') \dtau'},
+\gdist_\psymp (\tau) = \frac{ \gdist(\tau) S(\psymp + \tau) M(\psymp + \tau) }{\int_0^\infty \gdist(\tau') S(\psymp + \tau') M(\psymp + \tau') \dtau'},
 \end{equation}
@@
 \begin{equation}
-h_\psymp (x, \tau) = \frac{h(x, \tau) S(\psymp + \tau)}{\int_0^\infty \int_0^\infty h(x', \tau') S(\psymp + \tau') \dtau' \dx'}.
+h_\psymp (x, \tau) = \frac{h(x, \tau) S(\psymp + \tau) M(\psymp + \tau)}{\int_0^\infty \int_0^\infty h(x', \tau') S(\psymp + \tau') M(\psymp + \tau') \dtau' \dx'}.
 \end{equation}
@@
 \begin{equation}
-\Rc(t) = \Ro \int_0^\infty \gdist(\tau) S(t+\tau) \dtau.
+\Rc(t) = \Ro \int_0^\infty \gdist(\tau) S(t+\tau) M(\psymp + \tau) \dtau.
 \end{equation}
@@
 We use this framework to illustrate how the realized epidemiological time distributions vary over the course of an epidemic and depend on the perspective (i.e., forward vs. backward).
+
+For simplicity, we let $M = 1$ and assume that epidemic dynamics depend only on susceptible depletion in our simulations.
+Since we are interested in the initial epidemic growth phase (i.e., linking $r$ to \RR), the impact of intervention and susceptible depletion is expected to be negligible.
+In addition, the impact of such intervention $M$ that reduces $\RR(t)$ monotonically over time will be identical to the impact of susceptible depletion under this modeling framework. 
+Therefore, general conclusions we draw from our analysis is expected to be robust---however, detailed shape of the epidemic curve and changes in generation- and serial-intervals can still depend on the shape of $M$.
 

### 2020-10-13 serial.tex
actually done

@@
 Isolation delays and other intervention measures affect the amount of onward transmission, and therefore the distribution of realized (forward) generation intervals.
-They therefore are not expected to explain all the variation in forward serial intervals, since these additionally depend on both the backward incubation period of the infector and (iii) the forward incubation period of the infectee (\fref{diagram}B).
+They therefore are not expected to explain all the variation in forward serial intervals, since these additionally depend on both the backward incubation period of the infector and the forward incubation period of the infectee (\fref{diagram}B).
 

### 2020-10-15 serial.tex
minor changes

@@
 
-Here, changes in reproduction number can be modeled as a product of the basic reproduction number $\Ro$, proportion susceptible $S(t)$, and some intervention function $M(t)$, which can either decrease and/or increase in time: $\RR(t) = \Ro S(t) M(t)$;
+Here, changes in reproduction number can be modeled as a product of the basic reproduction number $\Ro$, proportion susceptible $S(t)$, and a time-dependent factor $M(t)$ (for example, accounting for nonpharmaceutical interventions and behavioral changes): $\RR(t) = \Ro S(t) M(t)$;
 \cite{flaxman2020estimating} used a similar framework to evaluate the impact of nonpharmaceutical interventions on the spread of COVID-19 in 11 countries.
@@
 For simplicity, we let $M = 1$ and assume that epidemic dynamics depend only on susceptible depletion in our simulations.
-Since we are interested in the initial epidemic growth phase (i.e., linking $r$ to \RR), the impact of intervention and susceptible depletion is expected to be negligible.
-In addition, the impact of such intervention $M$ that reduces $\RR(t)$ monotonically over time will be identical to the impact of susceptible depletion under this modeling framework. 
+Since we are interested in the initial epidemic growth phase (i.e., linking $r$ to \RR), we expect $\RR(t)$ to remain roughly constant during this period.
+In addition, qualitative effects of $M$ that reduces $\RR(t)$ monotonically over time will be similar to the impact of susceptible depletion under this modeling framework. 
 Therefore, general conclusions we draw from our analysis is expected to be robust---however, detailed shape of the epidemic curve and changes in generation- and serial-intervals can still depend on the shape of $M$.

### 2020-10-17 forward_corr.tex
done

@@
-% Created by tikzDevice version 0.12.3 on 2020-09-28 00:14:35
+% Created by tikzDevice version 0.12.3 on 2020-10-16 22:00:47
 % !TEX encoding = UTF-8 Unicode
@@
 	(572.66,443.99);
-\definecolor{drawColor}{RGB}{59,82,139}
+\definecolor{drawColor}{RGB}{49,104,142}
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
-	( 49.28,444.73) --
-	( 57.86,444.92) --
-	( 66.44,444.92) --
-	( 75.02,444.96) --
-	( 83.60,445.71) --
-	( 92.18,446.68) --
-	(100.76,445.85) --
-	(109.34,447.19) --
-	(117.92,447.52) --
-	(126.50,448.72) --
-	(135.08,449.14) --
-	(143.66,449.79) --
-	(152.24,451.41) --
-	(160.82,453.64) --
+	( 49.28,444.64) --
+	( 57.86,445.01) --
+	( 66.44,444.87) --
+	( 75.02,445.01) --
+	( 83.60,445.57) --
+	( 92.18,446.45) --
+	(100.76,445.89) --
+	(109.34,447.05) --
+	(117.92,447.56) --
+	(126.50,448.77) --
+	(135.08,449.00) --
+	(143.66,449.93) --
+	(152.24,451.46) --
+	(160.82,453.08) --
 	(169.40,455.17) --
-	(177.98,458.28) --
-	(186.56,459.44) --
-	(195.14,462.45) --
-	(203.72,467.93) --
-	(212.30,471.41) --
-	(220.88,478.46) --
-	(229.46,479.53) --
-	(238.04,488.11) --
-	(246.62,497.48) --
-	(255.20,501.28) --
-	(263.78,507.22) --
-	(272.36,516.82) --
-	(280.94,521.69) --
-	(289.52,526.84) --
-	(298.10,534.27) --
-	(306.68,533.80) --
-	(315.26,534.22) --
-	(323.84,531.53) --
-	(332.42,529.67) --
-	(341.00,522.16) --
-	(349.58,514.60) --
-	(358.16,508.15) --
-	(366.74,500.45) --
-	(375.32,493.03) --
-	(383.90,479.80) --
-	(392.48,475.16) --
-	(401.06,472.94) --
-	(409.64,463.98) --
-	(418.22,462.55) --
+	(177.98,458.09) --
+	(186.56,459.35) --
+	(195.14,462.08) --
+	(203.72,467.84) --
+	(212.30,470.66) --
+	(220.88,478.18) --
+	(229.46,478.27) --
+	(238.04,487.04) --
+	(246.62,496.09) --
+	(255.20,501.51) --
+	(263.78,504.58) --
+	(272.36,516.17) --
+	(280.94,520.53) --
+	(289.52,524.89) --
+	(298.10,534.68) --
+	(306.68,532.09) --
+	(315.26,534.31) --
+	(323.84,530.65) --
+	(332.42,530.55) --
+	(341.00,523.78) --
+	(349.58,515.90) --
+	(358.16,510.10) --
+	(366.74,500.63) --
+	(375.32,493.30) --
+	(383.90,484.26) --
+	(392.48,476.37) --
+	(401.06,471.27) --
+	(409.64,466.86) --
+	(418.22,462.92) --
 	(426.80,458.60) --
-	(435.38,455.54) --
-	(443.96,452.99) --
-	(452.54,451.51) --
-	(461.12,449.65) --
-	(469.70,448.30) --
-	(478.28,448.03) --
-	(486.86,447.47) --
-	(495.44,446.36) --
-	(504.02,445.20) --
-	(512.60,445.61) --
-	(521.18,444.92) --
-	(529.76,444.69) --
+	(435.38,456.05) --
+	(443.96,452.94) --
+	(452.54,451.23) --
+	(461.12,449.46) --
+	(469.70,447.98) --
+	(478.28,447.05) --
+	(486.86,447.24) --
+	(495.44,446.12) --
+	(504.02,445.75) --
+	(512.60,445.06) --
+	(521.18,445.01) --
+	(529.76,444.83) --
+	(538.34,444.50) --
+	(546.92,444.41) --
+	(555.50,444.50) --
+	(564.08,444.36) --
+	(572.66,444.18);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
+	( 49.28,444.59) --
+	( 57.86,444.73) --
+	( 66.44,445.10) --
+	( 75.02,444.73) --
+	( 83.60,445.52) --
+	( 92.18,446.12) --
+	(100.76,445.89) --
+	(109.34,446.77) --
+	(117.92,447.10) --
+	(126.50,448.82) --
+	(135.08,448.77) --
+	(143.66,449.70) --
+	(152.24,450.39) --
+	(160.82,451.55) --
+	(169.40,455.26) --
+	(177.98,456.61) --
+	(186.56,458.79) --
+	(195.14,461.43) --
+	(203.72,465.75) --
+	(212.30,469.46) --
+	(220.88,473.82) --
+	(229.46,480.50) --
+	(238.04,485.05) --
+	(246.62,492.56) --
+	(255.20,499.15) --
+	(263.78,503.14) --
+	(272.36,513.16) --
+	(280.94,518.86) --
+	(289.52,524.76) --
+	(298.10,531.20) --
+	(306.68,529.86) --
+	(315.26,535.47) --
+	(323.84,533.52) --
+	(332.42,528.79) --
+	(341.00,526.89) --
+	(349.58,516.03) --
+	(358.16,513.25) --
+	(366.74,505.55) --
+	(375.32,492.61) --
+	(383.90,488.01) --
+	(392.48,477.48) --
+	(401.06,473.12) --
+	(409.64,467.88) --
+	(418.22,465.14) --
+	(426.80,459.39) --
+	(435.38,456.01) --
+	(443.96,455.54) --
+	(452.54,452.11) --
+	(461.12,450.86) --
+	(469.70,449.33) --
+	(478.28,447.70) --
+	(486.86,447.01) --
+	(495.44,446.22) --
+	(504.02,446.59) --
+	(512.60,445.71) --
+	(521.18,444.96) --
+	(529.76,445.20) --
+	(538.34,444.55) --
+	(546.92,444.55) --
+	(555.50,444.87) --
+	(564.08,444.36) --
+	(572.66,444.27);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
+	( 49.28,444.64) --
+	( 57.86,444.96) --
+	( 66.44,444.87) --
+	( 75.02,445.34) --
+	( 83.60,445.57) --
+	( 92.18,446.08) --
+	(100.76,445.89) --
+	(109.34,447.56) --
+	(117.92,447.84) --
+	(126.50,448.58) --
+	(135.08,449.05) --
+	(143.66,451.00) --
+	(152.24,450.72) --
+	(160.82,453.36) --
+	(169.40,455.91) --
+	(177.98,457.91) --
+	(186.56,461.25) --
+	(195.14,463.80) --
+	(203.72,465.98) --
+	(212.30,471.92) --
+	(220.88,479.43) --
+	(229.46,481.98) --
+	(238.04,489.17) --
+	(246.62,495.99) --
+	(255.20,499.61) --
+	(263.78,509.82) --
+	(272.36,518.08) --
+	(280.94,521.00) --
+	(289.52,524.71) --
+	(298.10,531.99) --
+	(306.68,533.57) --
+	(315.26,532.32) --
+	(323.84,533.48) --
+	(332.42,529.30) --
+	(341.00,523.09) --
+	(349.58,515.66) --
+	(358.16,509.59) --
+	(366.74,500.40) --
+	(375.32,488.94) --
+	(383.90,483.75) --
+	(392.48,475.81) --
+	(401.06,472.34) --
+	(409.64,465.14) --
+	(418.22,461.20) --
+	(426.80,457.49) --
+	(435.38,454.85) --
+	(443.96,453.22) --
+	(452.54,450.44) --
+	(461.12,448.54) --
+	(469.70,447.89) --
+	(478.28,446.96) --
+	(486.86,447.33) --
+	(495.44,445.71) --
+	(504.02,444.92) --
+	(512.60,445.43) --
+	(521.18,445.10) --
+	(529.76,444.83) --
 	(538.34,444.87) --
-	(546.92,444.22) --
-	(555.50,444.22) --
-	(564.08,444.22) --
-	(572.66,444.04);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
-	( 49.28,444.59) --
-	( 57.86,444.87) --
-	( 66.44,444.87) --
-	( 75.02,444.92) --
-	( 83.60,445.48) --
-	( 92.18,446.26) --
-	(100.76,445.85) --
-	(109.34,446.77) --
-	(117.92,447.38) --
-	(126.50,448.91) --
-	(135.08,448.86) --
-	(143.66,449.74) --
-	(152.24,450.67) --
-	(160.82,451.97) --
-	(169.40,455.68) --
-	(177.98,456.98) --
-	(186.56,459.21) --
-	(195.14,461.57) --
-	(203.72,466.81) --
-	(212.30,469.97) --
-	(220.88,475.30) --
-	(229.46,480.13) --
-	(238.04,486.11) --
-	(246.62,494.09) --
-	(255.20,499.75) --
-	(263.78,504.90) --
-	(272.36,514.92) --
-	(280.94,519.79) --
-	(289.52,525.64) --
-	(298.10,533.43) --
-	(306.68,530.37) --
-	(315.26,535.47) --
-	(323.84,535.52) --
-	(332.42,528.79) --
-	(341.00,524.29) --
-	(349.58,518.26) --
-	(358.16,510.98) --
-	(366.74,502.95) --
-	(375.32,492.24) --
-	(383.90,485.97) --
-	(392.48,475.16) --
-	(401.06,471.04) --
-	(409.64,468.58) --
-	(418.22,464.03) --
-	(426.80,458.19) --
-	(435.38,456.47) --
-	(443.96,453.59) --
-	(452.54,451.69) --
-	(461.12,449.93) --
-	(469.70,448.86) --
-	(478.28,447.38) --
-	(486.86,447.38) --
-	(495.44,446.31) --
-	(504.02,445.52) --
-	(512.60,445.89) --
-	(521.18,444.78) --
-	(529.76,444.92) --
-	(538.34,444.73) --
-	(546.92,444.45) --
-	(555.50,444.55) --
-	(564.08,444.22) --
-	(572.66,444.13);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
-	( 49.28,445.29) --
-	( 57.86,444.73) --
-	( 66.44,445.52) --
-	( 75.02,445.71) --
-	( 83.60,445.94) --
-	( 92.18,446.54) --
-	(100.76,447.19) --
-	(109.34,448.44) --
-	(117.92,448.49) --
-	(126.50,449.60) --
-	(135.08,450.39) --
-	(143.66,451.32) --
-	(152.24,453.78) --
-	(160.82,456.89) --
-	(169.40,458.56) --
-	(177.98,461.06) --
-	(186.56,464.08) --
-	(195.14,467.79) --
-	(203.72,472.85) --
-	(212.30,479.62) --
-	(220.88,482.40) --
-	(229.46,491.59) --
-	(238.04,496.88) --
-	(246.62,500.63) --
-	(255.20,511.67) --
-	(263.78,517.61) --
-	(272.36,521.51) --
-	(280.94,527.91) --
-	(289.52,532.83) --
-	(298.10,533.94) --
-	(306.68,534.73) --
-	(315.26,530.42) --
-	(323.84,527.91) --
-	(332.42,524.11) --
-	(341.00,513.39) --
-	(349.58,508.89) --
-	(358.16,496.69) --
-	(366.74,489.92) --
-	(375.32,482.45) --
-	(383.90,471.78) --
-	(392.48,470.99) --
-	(401.06,464.40) --
-	(409.64,460.04) --
-	(418.22,456.10) --
-	(426.80,454.66) --
-	(435.38,452.62) --
-	(443.96,450.35) --
-	(452.54,449.19) --
-	(461.12,448.21) --
-	(469.70,446.73) --
-	(478.28,446.82) --
-	(486.86,445.99) --
-	(495.44,445.61) --
-	(504.02,445.01) --
-	(512.60,445.01) --
-	(521.18,444.87) --
-	(529.76,444.64) --
-	(538.34,444.50) --
-	(546.92,444.27) --
-	(555.50,444.04) --
-	(564.08,444.18) --
-	(572.66,443.99);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
-	( 49.28,444.64) --
-	( 57.86,444.83) --
-	( 66.44,444.96) --
-	( 75.02,445.24) --
-	( 83.60,445.52) --
-	( 92.18,446.03) --
-	(100.76,445.85) --
-	(109.34,447.52) --
-	(117.92,447.70) --
-	(126.50,448.72) --
-	(135.08,448.72) --
-	(143.66,450.95) --
-	(152.24,450.72) --
-	(160.82,453.41) --
-	(169.40,455.12) --
-	(177.98,457.86) --
-	(186.56,461.20) --
-	(195.14,463.24) --
-	(203.72,465.70) --
-	(212.30,470.25) --
-	(220.88,478.55) --
-	(229.46,483.05) --
-	(238.04,487.83) --
-	(246.62,496.09) --
-	(255.20,498.78) --
-	(263.78,507.68) --
-	(272.36,517.98) --
-	(280.94,520.07) --
-	(289.52,524.38) --
-	(298.10,531.39) --
-	(306.68,534.13) --
-	(315.26,534.27) --
-	(323.84,531.67) --
-	(332.42,528.65) --
-	(341.00,526.29) --
-	(349.58,513.62) --
-	(358.16,507.31) --
-	(366.74,502.02) --
-	(375.32,490.57) --
-	(383.90,484.35) --
-	(392.48,477.02) --
-	(401.06,473.22) --
-	(409.64,465.52) --
-	(418.22,460.97) --
-	(426.80,458.37) --
-	(435.38,454.89) --
-	(443.96,452.85) --
-	(452.54,451.32) --
-	(461.12,448.63) --
-	(469.70,448.58) --
-	(478.28,447.42) --
-	(486.86,446.68) --
-	(495.44,446.31) --
-	(504.02,445.75) --
-	(512.60,445.29) --
-	(521.18,445.15) --
-	(529.76,444.64) --
-	(538.34,444.32) --
-	(546.92,444.50) --
-	(555.50,444.41) --
-	(564.08,444.36) --
-	(572.66,444.22);
+	(546.92,444.32) --
+	(555.50,444.27) --
+	(564.08,443.99) --
+	(572.66,444.18);
 \definecolor{drawColor}{RGB}{68,1,84}
@@
 	(572.66,444.04);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
-	( 49.28,444.83) --
-	( 57.86,445.20) --
-	( 66.44,444.96) --
-	( 75.02,445.61) --
-	( 83.60,445.75) --
-	( 92.18,446.59) --
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
+	( 49.28,444.78) --
+	( 57.86,445.24) --
+	( 66.44,445.10) --
+	( 75.02,445.48) --
+	( 83.60,445.85) --
+	( 92.18,446.50) --
+	(100.76,446.82) --
+	(109.34,447.47) --
+	(117.92,448.12) --
+	(126.50,449.51) --
+	(135.08,450.53) --
+	(143.66,450.95) --
+	(152.24,454.01) --
+	(160.82,454.89) --
+	(169.40,458.70) --
+	(177.98,459.67) --
+	(186.56,462.45) --
+	(195.14,467.09) --
+	(203.72,471.59) --
+	(212.30,476.37) --
+	(220.88,480.13) --
+	(229.46,488.57) --
+	(238.04,494.65) --
+	(246.62,501.47) --
+	(255.20,509.54) --
+	(263.78,516.68) --
+	(272.36,522.34) --
+	(280.94,526.33) --
+	(289.52,531.20) --
+	(298.10,533.29) --
+	(306.68,535.47) --
+	(315.26,532.78) --
+	(323.84,529.53) --
+	(332.42,521.74) --
+	(341.00,514.69) --
+	(349.58,505.41) --
+	(358.16,500.03) --
+	(366.74,492.28) --
+	(375.32,483.33) --
+	(383.90,477.99) --
+	(392.48,471.45) --
+	(401.06,466.40) --
+	(409.64,462.55) --
+	(418.22,458.42) --
+	(426.80,455.40) --
+	(435.38,453.83) --
+	(443.96,451.55) --
+	(452.54,450.49) --
+	(461.12,448.30) --
+	(469.70,448.07) --
+	(478.28,447.38) --
+	(486.86,446.45) --
+	(495.44,445.34) --
+	(504.02,445.43) --
+	(512.60,445.29) --
+	(521.18,445.06) --
+	(529.76,444.50) --
+	(538.34,444.50) --
+	(546.92,444.36) --
+	(555.50,444.22) --
+	(564.08,444.18) --
+	(572.66,444.18);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.32) --
+	( 49.28,444.64) --
+	( 57.86,445.24) --
+	( 66.44,445.06) --
+	( 75.02,445.29) --
+	( 83.60,445.80) --
+	( 92.18,446.31) --
 	(100.76,446.91) --
-	(109.34,447.79) --
-	(117.92,447.93) --
-	(126.50,449.65) --
-	(135.08,450.53) --
-	(143.66,451.13) --
-	(152.24,454.38) --
-	(160.82,454.80) --
-	(169.40,458.70) --
-	(177.98,460.32) --
-	(186.56,462.87) --
-	(195.14,467.37) --
-	(203.72,472.06) --
-	(212.30,476.60) --
-	(220.88,480.13) --
-	(229.46,489.04) --
-	(238.04,495.25) --
-	(246.62,502.53) --
-	(255.20,509.35) --
-	(263.78,515.52) --
-	(272.36,523.60) --
-	(280.94,528.37) --
-	(289.52,530.23) --
-	(298.10,534.64) --
-	(306.68,537.42) --
-	(315.26,530.55) --
-	(323.84,529.86) --
-	(332.42,520.72) --
-	(341.00,515.20) --
-	(349.58,504.21) --
-	(358.16,501.47) --
-	(366.74,492.33) --
-	(375.32,480.92) --
-	(383.90,476.88) --
-	(392.48,471.45) --
-	(401.06,463.98) --
-	(409.64,462.41) --
-	(418.22,457.68) --
-	(426.80,454.52) --
-	(435.38,453.59) --
-	(443.96,452.02) --
-	(452.54,451.13) --
-	(461.12,447.79) --
+	(109.34,447.52) --
+	(117.92,447.52) --
+	(126.50,448.86) --
+	(135.08,450.21) --
+	(143.66,450.49) --
+	(152.24,452.94) --
+	(160.82,454.94) --
+	(169.40,456.66) --
+	(177.98,460.00) --
+	(186.56,462.04) --
+	(195.14,466.44) --
+	(203.72,469.55) --
+	(212.30,474.19) --
+	(220.88,479.43) --
+	(229.46,486.34) --
+	(238.04,492.84) --
+	(246.62,498.92) --
+	(255.20,508.70) --
+	(263.78,512.79) --
+	(272.36,520.49) --
+	(280.94,525.27) --
+	(289.52,529.02) --
+	(298.10,534.27) --
+	(306.68,534.08) --
+	(315.26,534.27) --
+	(323.84,526.94) --
+	(332.42,525.96) --
+	(341.00,517.29) --
+	(349.58,511.35) --
+	(358.16,501.61) --
+	(366.74,495.30) --
+	(375.32,486.62) --
+	(383.90,478.69) --
+	(392.48,470.85) --
+	(401.06,469.37) --
+	(409.64,463.71) --
+	(418.22,457.54) --
+	(426.80,456.42) --
+	(435.38,453.96) --
+	(443.96,452.53) --
+	(452.54,449.79) --
+	(461.12,449.84) --
+	(469.70,447.61) --
+	(478.28,447.89) --
+	(486.86,446.45) --
+	(495.44,445.75) --
+	(504.02,445.48) --
+	(512.60,445.29) --
+	(521.18,444.92) --
+	(529.76,444.50) --
+	(538.34,444.45) --
+	(546.92,444.27) --
+	(555.50,444.22) --
+	(564.08,444.22) --
+	(572.66,444.18);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
+	( 49.28,444.96) --
+	( 57.86,445.34) --
+	( 66.44,444.78) --
+	( 75.02,445.94) --
+	( 83.60,446.54) --
+	( 92.18,446.50) --
+	(100.76,447.24) --
+	(109.34,447.42) --
+	(117.92,448.49) --
+	(126.50,449.93) --
+	(135.08,450.44) --
+	(143.66,452.39) --
+	(152.24,454.24) --
+	(160.82,456.93) --
+	(169.40,458.33) --
+	(177.98,461.90) --
+	(186.56,465.38) --
+	(195.14,468.21) --
+	(203.72,472.01) --
+	(212.30,478.83) --
+	(220.88,484.12) --
+	(229.46,491.26) --
+	(238.04,498.04) --
+	(246.62,505.04) --
+	(255.20,513.39) --
+	(263.78,519.70) --
+	(272.36,523.69) --
+	(280.94,529.86) --
+	(289.52,531.90) --
+	(298.10,535.94) --
+	(306.68,537.28) --
+	(315.26,529.30) --
+	(323.84,529.12) --
+	(332.42,519.28) --
+	(341.00,513.67) --
+	(349.58,502.81) --
+	(358.16,494.83) --
+	(366.74,488.15) --
+	(375.32,479.99) --
+	(383.90,476.05) --
+	(392.48,467.42) --
+	(401.06,465.38) --
+	(409.64,459.58) --
+	(418.22,455.91) --
+	(426.80,454.94) --
+	(435.38,452.80) --
+	(443.96,451.41) --
+	(452.54,449.46) --
+	(461.12,448.21) --
 	(469.70,447.33) --
-	(478.28,446.91) --
-	(486.86,446.22) --
-	(495.44,445.48) --
-	(504.02,445.34) --
-	(512.60,445.15) --
-	(521.18,444.55) --
-	(529.76,444.69) --
-	(538.34,444.45) --
-	(546.92,444.22) --
-	(555.50,444.13) --
-	(564.08,444.13) --
-	(572.66,444.08);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
-	( 49.28,444.64) --
-	( 57.86,445.15) --
-	( 66.44,445.15) --
-	( 75.02,445.29) --
-	( 83.60,446.03) --
-	( 92.18,446.12) --
-	(100.76,447.05) --
-	(109.34,447.79) --
-	(117.92,447.61) --
-	(126.50,449.05) --
-	(135.08,450.07) --
-	(143.66,450.76) --
-	(152.24,453.32) --
-	(160.82,455.03) --
-	(169.40,457.95) --
-	(177.98,459.07) --
-	(186.56,462.04) --
-	(195.14,466.58) --
-	(203.72,469.83) --
-	(212.30,475.16) --
-	(220.88,479.90) --
-	(229.46,485.28) --
-	(238.04,494.51) --
-	(246.62,499.52) --
-	(255.20,510.70) --
-	(263.78,510.89) --
-	(272.36,521.93) --
-	(280.94,525.73) --
-	(289.52,530.42) --
-	(298.10,534.08) --
-	(306.68,534.96) --
-	(315.26,533.43) --
-	(323.84,529.77) --
-	(332.42,525.87) --
-	(341.00,516.45) --
-	(349.58,507.31) --
-	(358.16,501.98) --
-	(366.74,494.79) --
-	(375.32,484.58) --
-	(383.90,480.27) --
-	(392.48,470.80) --
-	(401.06,468.30) --
-	(409.64,462.08) --
-	(418.22,458.28) --
-	(426.80,456.79) --
-	(435.38,452.94) --
-	(443.96,452.34) --
-	(452.54,450.81) --
-	(461.12,448.86) --
-	(469.70,447.79) --
-	(478.28,447.01) --
-	(486.86,446.73) --
-	(495.44,445.38) --
-	(504.02,446.08) --
-	(512.60,445.15) --
-	(521.18,444.92) --
-	(529.76,444.41) --
-	(538.34,444.45) --
-	(546.92,444.45) --
-	(555.50,444.45) --
-	(564.08,444.55) --
-	(572.66,444.04);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.27) --
-	( 49.28,444.73) --
-	( 57.86,444.96) --
-	( 66.44,445.34) --
-	( 75.02,445.06) --
-	( 83.60,445.85) --
-	( 92.18,446.12) --
-	(100.76,447.01) --
-	(109.34,447.28) --
-	(117.92,447.61) --
-	(126.50,449.05) --
-	(135.08,449.46) --
-	(143.66,450.81) --
-	(152.24,452.29) --
-	(160.82,455.31) --
-	(169.40,455.87) --
-	(177.98,459.67) --
-	(186.56,461.20) --
-	(195.14,466.17) --
-	(203.72,468.44) --
-	(212.30,473.36) --
-	(220.88,478.74) --
-	(229.46,485.65) --
-	(238.04,492.05) --
-	(246.62,498.08) --
-	(255.20,507.96) --
-	(263.78,512.32) --
-	(272.36,521.74) --
-	(280.94,525.87) --
-	(289.52,529.21) --
-	(298.10,535.19) --
-	(306.68,534.17) --
-	(315.26,536.63) --
-	(323.84,529.39) --
-	(332.42,526.24) --
-	(341.00,518.03) --
-	(349.58,511.63) --
-	(358.16,502.77) --
-	(366.74,497.76) --
-	(375.32,484.40) --
-	(383.90,479.57) --
-	(392.48,472.47) --
-	(401.06,469.51) --
-	(409.64,463.20) --
-	(418.22,458.05) --
-	(426.80,456.24) --
-	(435.38,453.22) --
-	(443.96,451.97) --
-	(452.54,449.70) --
-	(461.12,449.51) --
-	(469.70,448.03) --
-	(478.28,447.28) --
-	(486.86,446.91) --
-	(495.44,445.43) --
-	(504.02,445.94) --
-	(512.60,445.24) --
-	(521.18,444.92) --
-	(529.76,444.22) --
-	(538.34,444.50) --
-	(546.92,444.55) --
+	(478.28,446.82) --
+	(486.86,446.08) --
+	(495.44,445.71) --
+	(504.02,444.92) --
+	(512.60,444.50) --
+	(521.18,444.78) --
+	(529.76,444.59) --
+	(538.34,444.69) --
+	(546.92,444.36) --
 	(555.50,444.36) --
-	(564.08,444.36) --
-	(572.66,444.27);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
-	( 49.28,445.01) --
-	( 57.86,445.34) --
-	( 66.44,444.83) --
-	( 75.02,445.66) --
-	( 83.60,446.63) --
-	( 92.18,446.40) --
-	(100.76,447.28) --
-	(109.34,447.33) --
-	(117.92,448.30) --
-	(126.50,449.84) --
-	(135.08,450.30) --
-	(143.66,451.92) --
-	(152.24,454.10) --
-	(160.82,457.17) --
-	(169.40,457.30) --
-	(177.98,461.11) --
-	(186.56,465.65) --
-	(195.14,468.02) --
-	(203.72,472.06) --
-	(212.30,478.41) --
-	(220.88,482.77) --
-	(229.46,491.26) --
-	(238.04,497.71) --
-	(246.62,503.14) --
-	(255.20,512.88) --
-	(263.78,520.12) --
-	(272.36,523.32) --
-	(280.94,528.14) --
-	(289.52,530.09) --
-	(298.10,536.77) --
-	(306.68,538.21) --
-	(315.26,526.57) --
-	(323.84,528.75) --
-	(332.42,518.96) --
-	(341.00,515.99) --
-	(349.58,503.51) --
-	(358.16,497.20) --
-	(366.74,488.11) --
-	(375.32,480.31) --
-	(383.90,476.00) --
-	(392.48,470.15) --
-	(401.06,464.59) --
-	(409.64,460.37) --
-	(418.22,456.19) --
-	(426.80,453.83) --
-	(435.38,453.96) --
-	(443.96,450.72) --
-	(452.54,449.93) --
-	(461.12,448.44) --
-	(469.70,447.56) --
-	(478.28,446.59) --
-	(486.86,445.71) --
-	(495.44,445.61) --
-	(504.02,444.96) --
-	(512.60,444.83) --
-	(521.18,444.78) --
-	(529.76,444.55) --
-	(538.34,444.36) --
-	(546.92,444.36) --
-	(555.50,444.13) --
-	(564.08,444.32);
+	(564.08,444.04) --
+	(572.66,444.18);
 \definecolor{drawColor}{RGB}{68,1,84}
@@
 	(572.66,444.32);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.36) --
-	( 49.28,444.69) --
-	( 57.86,444.64) --
-	( 66.44,445.24) --
-	( 75.02,445.43) --
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.32) --
+	( 49.28,444.73) --
+	( 57.86,444.69) --
+	( 66.44,445.20) --
+	( 75.02,445.34) --
 	( 83.60,445.66) --
-	( 92.18,445.24) --
-	(100.76,446.17) --
-	(109.34,446.73) --
-	(117.92,447.84) --
-	(126.50,448.72) --
-	(135.08,448.26) --
-	(143.66,449.56) --
-	(152.24,451.78) --
-	(160.82,452.29) --
-	(169.40,453.73) --
+	( 92.18,445.38) --
+	(100.76,446.26) --
+	(109.34,446.68) --
+	(117.92,447.89) --
+	(126.50,448.58) --
+	(135.08,448.68) --
+	(143.66,449.42) --
+	(152.24,451.83) --
+	(160.82,452.48) --
+	(169.40,453.92) --
 	(177.98,457.58) --
-	(186.56,458.79) --
-	(195.14,463.10) --
-	(203.72,466.30) --
-	(212.30,471.27) --
-	(220.88,473.82) --
-	(229.46,479.48) --
-	(238.04,487.09) --
-	(246.62,495.90) --
-	(255.20,500.35) --
-	(263.78,505.78) --
-	(272.36,514.18) --
-	(280.94,523.78) --
-	(289.52,526.43) --
-	(298.10,537.23) --
-	(306.68,532.55) --
-	(315.26,533.20) --
-	(323.84,538.63) --
-	(332.42,529.67) --
-	(341.00,520.63) --
-	(349.58,521.28) --
-	(358.16,506.57) --
-	(366.74,500.68) --
-	(375.32,494.14) --
-	(383.90,483.89) --
-	(392.48,475.68) --
-	(401.06,470.99) --
-	(409.64,467.00) --
-	(418.22,460.37) --
-	(426.80,459.02) --
-	(435.38,455.68) --
-	(443.96,453.59) --
-	(452.54,451.37) --
-	(461.12,449.51) --
-	(469.70,448.54) --
-	(478.28,447.93) --
-	(486.86,447.28) --
-	(495.44,445.85) --
+	(186.56,458.56) --
+	(195.14,462.87) --
+	(203.72,467.00) --
+	(212.30,471.13) --
+	(220.88,474.10) --
+	(229.46,478.78) --
+	(238.04,486.72) --
+	(246.62,497.48) --
+	(255.20,500.77) --
+	(263.78,506.20) --
+	(272.36,513.99) --
+	(280.94,525.50) --
+	(289.52,528.10) --
+	(298.10,536.59) --
+	(306.68,532.50) --
+	(315.26,535.10) --
+	(323.84,540.90) --
+	(332.42,532.13) --
+	(341.00,519.70) --
+	(349.58,518.45) --
+	(358.16,507.31) --
+	(366.74,500.73) --
+	(375.32,492.42) --
+	(383.90,482.96) --
+	(392.48,475.21) --
+	(401.06,471.18) --
+	(409.64,465.98) --
+	(418.22,459.16) --
+	(426.80,458.84) --
+	(435.38,455.12) --
+	(443.96,453.13) --
+	(452.54,451.23) --
+	(461.12,449.14) --
+	(469.70,448.77) --
+	(478.28,446.73) --
+	(486.86,446.73) --
+	(495.44,445.94) --
 	(504.02,445.89) --
-	(512.60,445.66) --
-	(521.18,444.73) --
+	(512.60,445.15) --
+	(521.18,444.83) --
 	(529.76,444.96) --
-	(538.34,444.73) --
+	(538.34,444.27) --
 	(546.92,444.36) --
-	(555.50,444.08) --
-	(564.08,444.18) --
-	(572.66,444.27);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
-	( 49.28,444.45) --
-	( 57.86,444.96) --
-	( 66.44,445.38) --
-	( 75.02,445.38) --
-	( 83.60,445.66) --
-	( 92.18,445.52) --
-	(100.76,446.08) --
-	(109.34,447.15) --
-	(117.92,448.03) --
-	(126.50,448.91) --
-	(135.08,448.72) --
-	(143.66,450.39) --
-	(152.24,451.78) --
-	(160.82,453.32) --
-	(169.40,455.12) --
-	(177.98,457.77) --
-	(186.56,459.86) --
-	(195.14,463.80) --
-	(203.72,468.53) --
-	(212.30,472.80) --
-	(220.88,475.58) --
-	(229.46,481.24) --
-	(238.04,487.88) --
-	(246.62,500.08) --
-	(255.20,500.82) --
-	(263.78,508.61) --
-	(272.36,516.31) --
-	(280.94,525.64) --
-	(289.52,527.63) --
-	(298.10,534.40) --
-	(306.68,534.31) --
-	(315.26,534.87) --
-	(323.84,538.77) --
-	(332.42,527.54) --
-	(341.00,518.91) --
-	(349.58,515.29) --
-	(358.16,509.03) --
-	(366.74,501.10) --
-	(375.32,488.01) --
-	(383.90,480.59) --
-	(392.48,475.95) --
-	(401.06,470.99) --
-	(409.64,465.89) --
-	(418.22,460.55) --
-	(426.80,458.14) --
-	(435.38,454.99) --
-	(443.96,453.50) --
-	(452.54,451.69) --
-	(461.12,449.93) --
-	(469.70,447.70) --
-	(478.28,447.52) --
-	(486.86,446.63) --
-	(495.44,446.08) --
-	(504.02,445.34) --
-	(512.60,445.24) --
-	(521.18,445.10) --
-	(529.76,445.01) --
-	(538.34,444.87) --
-	(546.92,444.27) --
 	(555.50,444.36) --
-	(564.08,444.22) --
-	(572.66,444.27);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
-	( 49.28,444.36) --
-	( 57.86,445.06) --
+	(564.08,444.13) --
+	(572.66,444.13);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.32) --
+	( 49.28,445.06) --
+	( 57.86,445.34) --
 	( 66.44,445.57) --
-	( 75.02,445.43) --
-	( 83.60,445.48) --
-	( 92.18,446.22) --
-	(100.76,445.71) --
-	(109.34,447.93) --
-	(117.92,448.03) --
-	(126.50,448.58) --
-	(135.08,449.88) --
-	(143.66,450.44) --
-	(152.24,452.16) --
-	(160.82,453.55) --
-	(169.40,456.79) --
-	(177.98,458.97) --
-	(186.56,461.29) --
-	(195.14,464.63) --
-	(203.72,468.62) --
-	(212.30,473.77) --
-	(220.88,477.44) --
-	(229.46,482.08) --
-	(238.04,493.30) --
-	(246.62,499.71) --
-	(255.20,505.23) --
-	(263.78,512.97) --
-	(272.36,518.77) --
-	(280.94,526.70) --
-	(289.52,531.76) --
-	(298.10,532.69) --
-	(306.68,536.12) --
-	(315.26,534.59) --
-	(323.84,536.12) --
-	(332.42,524.38) --
-	(341.00,520.77) --
-	(349.58,510.98) --
-	(358.16,503.00) --
-	(366.74,497.71) --
-	(375.32,486.67) --
-	(383.90,479.06) --
-	(392.48,473.31) --
-	(401.06,468.72) --
-	(409.64,464.17) --
-	(418.22,459.44) --
-	(426.80,456.38) --
-	(435.38,453.92) --
-	(443.96,452.11) --
-	(452.54,450.21) --
-	(461.12,449.74) --
-	(469.70,447.70) --
-	(478.28,447.24) --
-	(486.86,446.17) --
-	(495.44,445.89) --
-	(504.02,445.24) --
-	(512.60,445.34) --
-	(521.18,444.73) --
-	(529.76,444.92) --
-	(538.34,444.87) --
-	(546.92,444.41) --
-	(555.50,444.13) --
-	(564.08,444.18) --
-	(572.66,444.13);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.22) --
-	( 49.28,444.83) --
-	( 57.86,445.34) --
-	( 66.44,445.34) --
-	( 75.02,445.24) --
-	( 83.60,445.89) --
-	( 92.18,445.85) --
-	(100.76,446.87) --
-	(109.34,447.24) --
-	(117.92,448.49) --
-	(126.50,449.51) --
-	(135.08,450.44) --
-	(143.66,450.30) --
-	(152.24,452.57) --
-	(160.82,454.43) --
-	(169.40,458.09) --
-	(177.98,459.58) --
-	(186.56,461.20) --
-	(195.14,467.97) --
-	(203.72,468.11) --
-	(212.30,476.09) --
-	(220.88,479.48) --
-	(229.46,484.12) --
-	(238.04,495.67) --
-	(246.62,500.68) --
-	(255.20,507.36) --
-	(263.78,513.34) --
-	(272.36,520.26) --
-	(280.94,529.81) --
-	(289.52,533.25) --
-	(298.10,532.36) --
-	(306.68,537.10) --
-	(315.26,533.29) --
-	(323.84,531.99) --
-	(332.42,524.66) --
-	(341.00,517.75) --
-	(349.58,508.01) --
-	(358.16,500.35) --
-	(366.74,493.67) --
-	(375.32,485.37) --
-	(383.90,478.41) --
-	(392.48,470.53) --
-	(401.06,466.86) --
-	(409.64,461.71) --
-	(418.22,458.56) --
-	(426.80,455.40) --
-	(435.38,452.94) --
-	(443.96,451.23) --
-	(452.54,449.46) --
-	(461.12,449.05) --
-	(469.70,447.47) --
-	(478.28,446.26) --
-	(486.86,446.40) --
-	(495.44,445.29) --
-	(504.02,445.48) --
-	(512.60,444.73) --
-	(521.18,444.55) --
-	(529.76,444.55) --
-	(538.34,444.45) --
+	( 75.02,445.48) --
+	( 83.60,445.80) --
+	( 92.18,445.99) --
+	(100.76,447.52) --
+	(109.34,448.40) --
+	(117.92,448.44) --
+	(126.50,448.95) --
+	(135.08,450.62) --
+	(143.66,451.88) --
+	(152.24,453.32) --
+	(160.82,456.10) --
+	(169.40,457.86) --
+	(177.98,460.41) --
+	(186.56,465.10) --
+	(195.14,468.16) --
+	(203.72,473.08) --
+	(212.30,476.42) --
+	(220.88,482.45) --
+	(229.46,489.55) --
+	(238.04,501.38) --
+	(246.62,502.12) --
+	(255.20,510.10) --
+	(263.78,518.31) --
+	(272.36,529.30) --
+	(280.94,530.04) --
+	(289.52,533.11) --
+	(298.10,535.29) --
+	(306.68,533.62) --
+	(315.26,536.35) --
+	(323.84,528.14) --
+	(332.42,520.12) --
+	(341.00,510.14) --
+	(349.58,505.27) --
+	(358.16,499.01) --
+	(366.74,488.85) --
+	(375.32,478.32) --
+	(383.90,476.46) --
+	(392.48,469.27) --
+	(401.06,464.26) --
+	(409.64,460.27) --
+	(418.22,456.84) --
+	(426.80,454.66) --
+	(435.38,453.50) --
+	(443.96,450.07) --
+	(452.54,450.02) --
+	(461.12,447.19) --
+	(469.70,447.19) --
+	(478.28,446.36) --
+	(486.86,445.94) --
+	(495.44,445.66) --
+	(504.02,445.06) --
+	(512.60,444.59) --
+	(521.18,444.92) --
+	(529.76,445.06) --
+	(538.34,444.32) --
 	(546.92,444.22) --
 	(555.50,444.18) --
-	(564.08,444.18) --
-	(572.66,444.18);
+	(564.08,444.04) --
+	(572.66,443.99);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.36) --
+	( 49.28,444.64) --
+	( 57.86,445.20) --
+	( 66.44,445.52) --
+	( 75.02,445.20) --
+	( 83.60,445.66) --
+	( 92.18,446.08) --
+	(100.76,446.59) --
+	(109.34,447.42) --
+	(117.92,448.54) --
+	(126.50,448.91) --
+	(135.08,450.25) --
+	(143.66,450.81) --
+	(152.24,452.02) --
+	(160.82,454.34) --
+	(169.40,458.00) --
+	(177.98,459.21) --
+	(186.56,461.43) --
+	(195.14,467.56) --
+	(203.72,468.76) --
+	(212.30,475.54) --
+	(220.88,479.53) --
+	(229.46,484.03) --
+	(238.04,496.60) --
+	(246.62,499.98) --
+	(255.20,507.03) --
+	(263.78,513.76) --
+	(272.36,519.56) --
+	(280.94,529.44) --
+	(289.52,533.71) --
+	(298.10,530.88) --
+	(306.68,535.75) --
+	(315.26,533.85) --
+	(323.84,533.94) --
+	(332.42,522.58) --
+	(341.00,516.92) --
+	(349.58,507.87) --
+	(358.16,501.65) --
+	(366.74,495.76) --
+	(375.32,485.51) --
+	(383.90,477.44) --
+	(392.48,471.78) --
+	(401.06,466.17) --
+	(409.64,462.96) --
+	(418.22,457.63) --
+	(426.80,456.14) --
+	(435.38,453.27) --
+	(443.96,451.37) --
+	(452.54,450.25) --
+	(461.12,449.00) --
+	(469.70,447.28) --
+	(478.28,446.87) --
+	(486.86,446.40) --
+	(495.44,445.66) --
+	(504.02,445.94) --
+	(512.60,444.83) --
+	(521.18,444.69) --
+	(529.76,444.78) --
+	(538.34,444.27) --
+	(546.92,444.50) --
+	(555.50,444.27) --
+	(564.08,444.04) --
+	(572.66,444.08);
 \definecolor{drawColor}{RGB}{68,1,84}
@@
 	(572.66,444.13);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
-	( 49.28,444.78) --
-	( 57.86,445.38) --
-	( 66.44,445.43) --
-	( 75.02,445.48) --
-	( 83.60,445.85) --
-	( 92.18,446.31) --
-	(100.76,447.70) --
-	(109.34,448.54) --
-	(117.92,448.17) --
-	(126.50,449.88) --
-	(135.08,451.32) --
-	(143.66,452.76) --
-	(152.24,455.40) --
-	(160.82,456.33) --
-	(169.40,459.02) --
-	(177.98,462.87) --
-	(186.56,464.08) --
-	(195.14,469.04) --
-	(203.72,476.74) --
-	(212.30,480.69) --
-	(220.88,482.73) --
-	(229.46,491.96) --
-	(238.04,497.90) --
-	(246.62,505.13) --
-	(255.20,512.42) --
-	(263.78,520.02) --
-	(272.36,528.33) --
-	(280.94,527.12) --
-	(289.52,532.92) --
-	(298.10,535.52) --
-	(306.68,533.06) --
-	(315.26,533.66) --
-	(323.84,524.20) --
-	(332.42,516.08) --
-	(341.00,512.51) --
-	(349.58,500.59) --
-	(358.16,496.88) --
-	(366.74,487.18) --
-	(375.32,478.60) --
-	(383.90,472.80) --
-	(392.48,467.51) --
-	(401.06,462.87) --
-	(409.64,459.95) --
-	(418.22,457.54) --
-	(426.80,453.36) --
-	(435.38,451.60) --
-	(443.96,450.39) --
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
+	( 49.28,444.55) --
+	( 57.86,444.36) --
+	( 66.44,444.83) --
+	( 75.02,445.29) --
+	( 83.60,445.71) --
+	( 92.18,445.20) --
+	(100.76,445.99) --
+	(109.34,446.17) --
+	(117.92,447.56) --
+	(126.50,448.77) --
+	(135.08,448.35) --
+	(143.66,449.70) --
+	(152.24,451.23) --
+	(160.82,452.71) --
+	(169.40,455.40) --
+	(177.98,456.42) --
+	(186.56,458.79) --
+	(195.14,463.01) --
+	(203.72,463.94) --
+	(212.30,468.62) --
+	(220.88,476.97) --
+	(229.46,480.50) --
+	(238.04,483.28) --
+	(246.62,491.12) --
+	(255.20,497.25) --
+	(263.78,504.39) --
+	(272.36,512.51) --
+	(280.94,518.21) --
+	(289.52,527.40) --
+	(298.10,526.38) --
+	(306.68,529.67) --
+	(315.26,536.96) --
+	(323.84,531.02) --
+	(332.42,532.04) --
+	(341.00,526.61) --
+	(349.58,517.52) --
+	(358.16,513.44) --
+	(366.74,502.63) --
+	(375.32,494.79) --
+	(383.90,489.17) --
+	(392.48,480.04) --
+	(401.06,474.70) --
+	(409.64,469.64) --
+	(418.22,462.18) --
+	(426.80,460.00) --
+	(435.38,457.77) --
+	(443.96,454.47) --
+	(452.54,451.51) --
+	(461.12,450.53) --
+	(469.70,448.44) --
+	(478.28,447.75) --
+	(486.86,446.12) --
+	(495.44,446.63) --
+	(504.02,446.31) --
+	(512.60,445.29) --
+	(521.18,445.24) --
+	(529.76,444.73) --
+	(538.34,444.45) --
+	(546.92,444.22) --
+	(555.50,444.22) --
+	(564.08,444.41) --
+	(572.66,444.04);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.87) --
+	( 49.28,444.73) --
+	( 57.86,445.24) --
+	( 66.44,445.48) --
+	( 75.02,445.29) --
+	( 83.60,445.99) --
+	( 92.18,446.08) --
+	(100.76,447.75) --
+	(109.34,448.21) --
+	(117.92,448.03) --
+	(126.50,450.30) --
+	(135.08,451.09) --
+	(143.66,453.64) --
+	(152.24,455.26) --
+	(160.82,456.05) --
+	(169.40,458.93) --
+	(177.98,463.66) --
+	(186.56,464.87) --
+	(195.14,468.99) --
+	(203.72,475.58) --
+	(212.30,481.75) --
+	(220.88,484.07) --
+	(229.46,490.29) --
+	(238.04,499.47) --
+	(246.62,505.36) --
+	(255.20,513.44) --
+	(263.78,518.86) --
+	(272.36,526.01) --
+	(280.94,529.63) --
+	(289.52,535.52) --
+	(298.10,530.93) --
+	(306.68,535.19) --
+	(315.26,530.18) --
+	(323.84,525.96) --
+	(332.42,516.41) --
+	(341.00,511.58) --
+	(349.58,501.14) --
+	(358.16,495.44) --
+	(366.74,486.62) --
+	(375.32,478.27) --
+	(383.90,474.10) --
+	(392.48,468.48) --
+	(401.06,462.50) --
+	(409.64,458.93) --
+	(418.22,456.56) --
+	(426.80,454.24) --
+	(435.38,451.83) --
+	(443.96,450.02) --
 	(452.54,448.40) --
-	(461.12,447.70) --
-	(469.70,446.59) --
-	(478.28,445.80) --
-	(486.86,445.80) --
-	(495.44,445.38) --
+	(461.12,447.24) --
+	(469.70,446.77) --
+	(478.28,446.50) --
+	(486.86,445.75) --
+	(495.44,445.24) --
 	(504.02,445.38) --
-	(512.60,444.59) --
-	(521.18,444.45) --
-	(529.76,444.32) --
-	(538.34,444.41) --
+	(512.60,444.55) --
+	(521.18,444.32) --
+	(529.76,444.50) --
+	(538.34,444.18) --
 	(546.92,444.27) --
-	(555.50,444.08) --
-	(572.66,444.04);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
-	( 49.28,445.01) --
-	( 57.86,445.20) --
-	( 66.44,445.48) --
-	( 75.02,445.38) --
-	( 83.60,445.94) --
-	( 92.18,446.08) --
-	(100.76,447.56) --
-	(109.34,448.49) --
-	(117.92,448.54) --
-	(126.50,449.88) --
-	(135.08,450.90) --
-	(143.66,453.92) --
-	(152.24,455.08) --
-	(160.82,456.38) --
-	(169.40,459.53) --
-	(177.98,462.59) --
-	(186.56,464.82) --
-	(195.14,468.76) --
-	(203.72,476.93) --
-	(212.30,481.89) --
-	(220.88,483.79) --
-	(229.46,490.33) --
-	(238.04,500.22) --
-	(246.62,504.30) --
-	(255.20,514.23) --
-	(263.78,520.07) --
-	(272.36,525.27) --
-	(280.94,527.08) --
-	(289.52,532.97) --
-	(298.10,531.48) --
-	(306.68,535.89) --
-	(315.26,529.12) --
-	(323.84,523.09) --
-	(332.42,517.06) --
-	(341.00,509.86) --
-	(349.58,500.73) --
-	(358.16,495.44) --
-	(366.74,489.31) --
-	(375.32,477.44) --
-	(383.90,472.61) --
-	(392.48,467.79) --
-	(401.06,462.08) --
-	(409.64,459.81) --
-	(418.22,456.84) --
-	(426.80,453.83) --
-	(435.38,452.11) --
-	(443.96,449.98) --
-	(452.54,449.23) --
-	(461.12,448.07) --
-	(469.70,447.28) --
-	(478.28,446.12) --
-	(486.86,445.57) --
-	(495.44,445.71) --
-	(504.02,444.96) --
-	(512.60,444.87) --
-	(521.18,444.45) --
-	(529.76,444.50) --
-	(538.34,444.36) --
-	(546.92,444.08) --
-	(555.50,444.08) --
-	(564.08,444.08);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.78) --
-	( 49.28,444.73) --
-	( 57.86,445.29) --
-	( 66.44,445.34) --
-	( 75.02,445.24) --
-	( 83.60,446.12) --
-	( 92.18,446.03) --
-	(100.76,447.56) --
-	(109.34,448.17) --
-	(117.92,448.03) --
-	(126.50,450.25) --
-	(135.08,451.32) --
-	(143.66,453.13) --
-	(152.24,455.22) --
-	(160.82,456.42) --
-	(169.40,457.95) --
-	(177.98,464.40) --
-	(186.56,463.43) --
-	(195.14,468.76) --
-	(203.72,476.05) --
-	(212.30,483.47) --
-	(220.88,482.96) --
-	(229.46,488.94) --
-	(238.04,499.66) --
-	(246.62,504.76) --
-	(255.20,512.69) --
-	(263.78,522.11) --
-	(272.36,523.64) --
-	(280.94,528.98) --
-	(289.52,533.29) --
-	(298.10,533.25) --
-	(306.68,535.66) --
-	(315.26,531.58) --
-	(323.84,523.69) --
-	(332.42,517.29) --
-	(341.00,510.24) --
-	(349.58,503.83) --
-	(358.16,496.83) --
-	(366.74,490.01) --
-	(375.32,478.50) --
-	(383.90,474.84) --
-	(392.48,468.86) --
-	(401.06,462.69) --
-	(409.64,460.00) --
-	(418.22,456.05) --
-	(426.80,454.94) --
-	(435.38,451.37) --
-	(443.96,450.02) --
-	(452.54,449.00) --
-	(461.12,447.38) --
-	(469.70,446.82) --
-	(478.28,446.03) --
-	(486.86,445.99) --
-	(495.44,445.06) --
-	(504.02,445.20) --
-	(512.60,445.01) --
-	(521.18,444.27) --
-	(529.76,444.27) --
-	(538.34,444.32) --
-	(546.92,444.18) --
 	(555.50,444.04) --
 	(564.08,444.18) --
-	(572.66,444.08);
+	(572.66,443.99);
 \definecolor{drawColor}{RGB}{253,231,37}
@@
 	( 57.86,445.43) --
-	( 66.44,444.96) --
-	( 75.02,445.20) --
-	( 83.60,446.31) --
-	( 92.18,446.08) --
-	(100.76,447.56) --
-	(109.34,448.12) --
-	(117.92,448.30) --
-	(126.50,449.84) --
-	(135.08,451.41) --
-	(143.66,452.67) --
-	(152.24,455.36) --
-	(160.82,456.24) --
+	( 66.44,444.92) --
+	( 75.02,445.24) --
+	( 83.60,446.17) --
+	( 92.18,446.59) --
+	(100.76,447.33) --
+	(109.34,448.03) --
+	(117.92,448.17) --
+	(126.50,450.16) --
+	(135.08,451.32) --
+	(143.66,452.94) --
+	(152.24,455.50) --
+	(160.82,456.01) --
 	(169.40,459.62) --
-	(177.98,462.92) --
-	(186.56,463.47) --
-	(195.14,469.13) --
-	(203.72,477.58) --
-	(212.30,482.26) --
-	(220.88,484.16) --
-	(229.46,489.08) --
-	(238.04,502.44) --
-	(246.62,502.07) --
-	(255.20,514.27) --
-	(263.78,521.32) --
-	(272.36,523.74) --
-	(280.94,530.37) --
-	(289.52,536.45) --
-	(298.10,531.16) --
-	(306.68,537.14) --
-	(315.26,532.73) --
-	(323.84,520.86) --
-	(332.42,519.98) --
-	(341.00,511.30) --
-	(349.58,503.51) --
-	(358.16,494.97) --
-	(366.74,485.74) --
-	(375.32,480.22) --
-	(383.90,472.24) --
-	(392.48,467.09) --
-	(401.06,462.18) --
-	(409.64,460.09) --
-	(418.22,456.33) --
-	(426.80,452.85) --
-	(435.38,452.20) --
-	(443.96,450.72) --
-	(452.54,449.05) --
-	(461.12,446.96) --
-	(469.70,446.82) --
-	(478.28,446.40) --
+	(177.98,463.20) --
+	(186.56,464.31) --
+	(195.14,468.25) --
+	(203.72,478.04) --
+	(212.30,481.94) --
+	(220.88,483.42) --
+	(229.46,488.20) --
+	(238.04,500.86) --
+	(246.62,505.46) --
+	(255.20,514.18) --
+	(263.78,519.51) --
+	(272.36,524.15) --
+	(280.94,529.16) --
+	(289.52,535.84) --
+	(298.10,532.09) --
+	(306.68,533.01) --
+	(315.26,533.15) --
+	(323.84,524.34) --
+	(332.42,519.10) --
+	(341.00,509.96) --
+	(349.58,501.89) --
+	(358.16,496.74) --
+	(366.74,487.64) --
+	(375.32,480.45) --
+	(383.90,473.36) --
+	(392.48,467.32) --
+	(401.06,463.61) --
+	(409.64,460.00) --
+	(418.22,457.35) --
+	(426.80,452.80) --
+	(435.38,451.83) --
+	(443.96,449.74) --
+	(452.54,447.98) --
+	(461.12,447.19) --
+	(469.70,446.87) --
+	(478.28,446.31) --
 	(486.86,445.80) --
-	(495.44,445.66) --
-	(504.02,445.10) --
-	(512.60,444.78) --
-	(521.18,444.69) --
+	(495.44,445.24) --
+	(504.02,444.73) --
+	(512.60,444.87) --
+	(521.18,444.27) --
 	(529.76,444.50) --
-	(538.34,444.41) --
-	(546.92,444.22) --
-	(555.50,444.27);
+	(538.34,444.08) --
+	(546.92,444.27) --
+	(555.50,444.04) --
+	(564.08,443.99) --
+	(572.66,444.04);
 \definecolor{drawColor}{RGB}{68,1,84}
@@
 	(572.66,444.04);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
-	( 49.28,445.34) --
-	( 57.86,444.96) --
-	( 66.44,445.20) --
-	( 75.02,445.61) --
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.73) --
+	( 49.28,445.20) --
+	( 57.86,445.06) --
+	( 66.44,445.15) --
+	( 75.02,445.57) --
 	( 83.60,445.89) --
 	( 92.18,446.40) --
-	(100.76,447.47) --
+	(100.76,447.15) --
 	(109.34,447.61) --
-	(117.92,448.21) --
-	(126.50,449.33) --
-	(135.08,450.25) --
-	(143.66,452.80) --
-	(152.24,452.43) --
-	(160.82,453.87) --
-	(169.40,458.00) --
-	(177.98,460.88) --
-	(186.56,465.33) --
-	(195.14,466.72) --
-	(203.72,471.45) --
-	(212.30,475.86) --
-	(220.88,483.52) --
-	(229.46,489.36) --
-	(238.04,493.12) --
-	(246.62,501.14) --
-	(255.20,509.54) --
-	(263.78,513.16) --
-	(272.36,522.30) --
-	(280.94,527.63) --
-	(289.52,529.81) --
-	(298.10,532.60) --
-	(306.68,535.98) --
-	(315.26,530.23) --
-	(323.84,528.47) --
-	(332.42,522.90) --
-	(341.00,517.33) --
-	(349.58,509.17) --
-	(358.16,498.82) --
-	(366.74,490.94) --
-	(375.32,483.38) --
-	(383.90,479.90) --
-	(392.48,470.34) --
-	(401.06,466.17) --
-	(409.64,462.27) --
-	(418.22,457.81) --
-	(426.80,456.33) --
-	(435.38,452.25) --
-	(443.96,451.51) --
-	(452.54,450.21) --
-	(461.12,448.44) --
-	(469.70,447.38) --
-	(478.28,446.77) --
+	(117.92,448.26) --
+	(126.50,449.28) --
+	(135.08,450.07) --
+	(143.66,452.25) --
+	(152.24,452.25) --
+	(160.82,454.34) --
+	(169.40,457.49) --
+	(177.98,459.86) --
+	(186.56,465.19) --
+	(195.14,466.58) --
+	(203.72,470.90) --
+	(212.30,474.28) --
+	(220.88,483.47) --
+	(229.46,488.39) --
+	(238.04,492.10) --
+	(246.62,499.89) --
+	(255.20,508.24) --
+	(263.78,514.13) --
+	(272.36,521.14) --
+	(280.94,526.94) --
+	(289.52,526.80) --
+	(298.10,532.55) --
+	(306.68,535.89) --
+	(315.26,533.66) --
+	(323.84,528.37) --
+	(332.42,524.48) --
+	(341.00,519.84) --
+	(349.58,508.89) --
+	(358.16,499.98) --
+	(366.74,490.89) --
+	(375.32,483.93) --
+	(383.90,479.06) --
+	(392.48,472.24) --
+	(401.06,465.38) --
+	(409.64,463.20) --
+	(418.22,458.97) --
+	(426.80,457.30) --
+	(435.38,452.76) --
+	(443.96,451.65) --
+	(452.54,449.65) --
+	(461.12,448.54) --
+	(469.70,447.70) --
+	(478.28,446.59) --
 	(486.86,445.89) --
-	(495.44,445.71) --
-	(504.02,445.57) --
-	(512.60,444.73) --
-	(521.18,444.83) --
-	(529.76,444.45) --
-	(538.34,444.59) --
-	(546.92,444.18) --
-	(555.50,444.18) --
-	(564.08,444.18) --
-	(572.66,443.99);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.87) --
-	( 49.28,445.10) --
-	( 57.86,445.20) --
-	( 66.44,445.06) --
-	( 75.02,445.57) --
-	( 83.60,445.57) --
-	( 92.18,446.50) --
-	(100.76,446.87) --
-	(109.34,448.03) --
-	(117.92,447.79) --
-	(126.50,448.77) --
-	(135.08,449.98) --
-	(143.66,451.60) --
-	(152.24,452.99) --
-	(160.82,454.10) --
-	(169.40,455.91) --
-	(177.98,460.51) --
-	(186.56,464.63) --
-	(195.14,465.84) --
-	(203.72,470.11) --
-	(212.30,473.73) --
-	(220.88,482.08) --
-	(229.46,487.69) --
-	(238.04,491.26) --
-	(246.62,500.03) --
-	(255.20,507.87) --
-	(263.78,511.67) --
-	(272.36,518.59) --
-	(280.94,527.17) --
-	(289.52,525.92) --
-	(298.10,535.98) --
-	(306.68,533.29) --
-	(315.26,536.07) --
-	(323.84,527.49) --
-	(332.42,523.55) --
-	(341.00,521.14) --
-	(349.58,511.67) --
-	(358.16,500.73) --
-	(366.74,492.42) --
-	(375.32,486.11) --
-	(383.90,480.45) --
-	(392.48,473.59) --
-	(401.06,467.93) --
-	(409.64,463.52) --
-	(418.22,460.09) --
-	(426.80,456.28) --
-	(435.38,453.50) --
-	(443.96,451.83) --
-	(452.54,450.53) --
-	(461.12,449.65) --
-	(469.70,447.89) --
-	(478.28,447.19) --
-	(486.86,446.36) --
-	(495.44,445.38) --
+	(495.44,446.08) --
 	(504.02,445.38) --
-	(512.60,445.34) --
-	(521.18,444.78) --
-	(529.76,444.73) --
-	(538.34,444.41) --
-	(546.92,444.45) --
-	(555.50,444.04) --
-	(564.08,444.22) --
-	(572.66,444.08);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
-	( 49.28,445.24) --
-	( 57.86,444.92) --
-	( 66.44,445.24) --
-	( 75.02,445.48) --
-	( 83.60,445.48) --
-	( 92.18,446.08) --
-	(100.76,446.87) --
-	(109.34,447.84) --
-	(117.92,447.61) --
-	(126.50,449.14) --
-	(135.08,449.23) --
-	(143.66,451.09) --
-	(152.24,452.85) --
-	(160.82,453.83) --
-	(169.40,454.99) --
-	(177.98,459.21) --
-	(186.56,463.15) --
-	(195.14,466.26) --
-	(203.72,469.27) --
-	(212.30,473.68) --
-	(220.88,479.99) --
-	(229.46,484.63) --
-	(238.04,492.00) --
-	(246.62,499.57) --
-	(255.20,505.09) --
-	(263.78,510.70) --
-	(272.36,517.38) --
-	(280.94,524.66) --
-	(289.52,528.88) --
-	(298.10,531.20) --
-	(306.68,533.57) --
-	(315.26,536.26) --
-	(323.84,528.61) --
-	(332.42,524.94) --
-	(341.00,521.93) --
-	(349.58,513.67) --
-	(358.16,504.34) --
-	(366.74,493.72) --
-	(375.32,485.60) --
-	(383.90,481.47) --
-	(392.48,475.49) --
-	(401.06,467.93) --
-	(409.64,464.45) --
-	(418.22,461.29) --
-	(426.80,457.91) --
-	(435.38,453.92) --
-	(443.96,453.55) --
-	(452.54,450.76) --
-	(461.12,449.42) --
-	(469.70,448.30) --
-	(478.28,447.05) --
-	(486.86,446.73) --
-	(495.44,445.99) --
-	(504.02,445.48) --
-	(512.60,445.01) --
-	(521.18,445.01) --
-	(529.76,444.69) --
+	(512.60,445.24) --
+	(521.18,444.59) --
+	(529.76,444.55) --
 	(538.34,444.64) --
 	(546.92,444.32) --
+	(555.50,444.27) --
+	(564.08,444.22) --
+	(572.66,443.99);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
+	( 49.28,445.29) --
+	( 57.86,445.06) --
+	( 66.44,445.06) --
+	( 75.02,445.66) --
+	( 83.60,445.52) --
+	( 92.18,446.40) --
+	(100.76,446.68) --
+	(109.34,448.17) --
+	(117.92,447.28) --
+	(126.50,449.65) --
+	(135.08,449.33) --
+	(143.66,451.46) --
+	(152.24,452.76) --
+	(160.82,454.20) --
+	(169.40,455.54) --
+	(177.98,460.23) --
+	(186.56,463.15) --
+	(195.14,466.35) --
+	(203.72,469.41) --
+	(212.30,474.24) --
+	(220.88,480.92) --
+	(229.46,485.60) --
+	(238.04,492.89) --
+	(246.62,499.19) --
+	(255.20,506.11) --
+	(263.78,512.23) --
+	(272.36,518.82) --
+	(280.94,524.99) --
+	(289.52,528.88) --
+	(298.10,532.64) --
+	(306.68,533.38) --
+	(315.26,535.05) --
+	(323.84,526.57) --
+	(332.42,523.55) --
+	(341.00,520.77) --
+	(349.58,513.76) --
+	(358.16,503.46) --
+	(366.74,493.12) --
+	(375.32,485.83) --
+	(383.90,479.57) --
+	(392.48,474.01) --
+	(401.06,468.11) --
+	(409.64,462.83) --
+	(418.22,459.21) --
+	(426.80,457.40) --
+	(435.38,453.96) --
+	(443.96,452.67) --
+	(452.54,450.16) --
+	(461.12,448.30) --
+	(469.70,448.26) --
+	(478.28,446.87) --
+	(486.86,446.91) --
+	(495.44,445.61) --
+	(504.02,445.43) --
+	(512.60,444.92) --
+	(521.18,445.01) --
+	(529.76,444.73) --
+	(538.34,444.50) --
+	(546.92,444.22) --
 	(555.50,444.36) --
+	(564.08,444.27) --
+	(572.66,443.99);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
+	( 49.28,444.92) --
+	( 57.86,445.10) --
+	( 66.44,445.01) --
+	( 75.02,445.57) --
+	( 83.60,445.52) --
+	( 92.18,445.80) --
+	(100.76,446.91) --
+	(109.34,447.33) --
+	(117.92,447.84) --
+	(126.50,448.68) --
+	(135.08,449.70) --
+	(143.66,450.21) --
+	(152.24,451.88) --
+	(160.82,453.41) --
+	(169.40,455.50) --
+	(177.98,458.65) --
+	(186.56,461.25) --
+	(195.14,465.24) --
+	(203.72,467.93) --
+	(212.30,474.01) --
+	(220.88,477.35) --
+	(229.46,483.56) --
+	(238.04,490.01) --
+	(246.62,495.58) --
+	(255.20,505.74) --
+	(263.78,507.50) --
+	(272.36,516.68) --
+	(280.94,521.79) --
+	(289.52,527.31) --
+	(298.10,532.27) --
+	(306.68,533.38) --
+	(315.26,536.91) --
+	(323.84,530.18) --
+	(332.42,525.96) --
+	(341.00,521.42) --
+	(349.58,515.48) --
+	(358.16,509.35) --
+	(366.74,497.85) --
+	(375.32,486.76) --
+	(383.90,481.47) --
+	(392.48,476.97) --
+	(401.06,469.92) --
+	(409.64,464.50) --
+	(418.22,461.34) --
+	(426.80,458.00) --
+	(435.38,454.52) --
+	(443.96,451.88) --
+	(452.54,450.86) --
+	(461.12,449.23) --
+	(469.70,449.28) --
+	(478.28,447.28) --
+	(486.86,446.12) --
+	(495.44,446.08) --
+	(504.02,445.85) --
+	(512.60,444.83) --
+	(521.18,444.96) --
+	(529.76,444.78) --
+	(538.34,444.64) --
+	(546.92,444.27) --
+	(555.50,444.13) --
 	(564.08,444.22) --
-	(572.66,444.13);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.73) --
-	( 49.28,445.20) --
-	( 57.86,444.96) --
-	( 66.44,445.52) --
-	( 75.02,445.43) --
-	( 83.60,445.94) --
-	( 92.18,446.54) --
-	(100.76,447.89) --
-	(109.34,447.70) --
-	(117.92,448.54) --
-	(126.50,449.46) --
-	(135.08,450.11) --
-	(143.66,452.06) --
-	(152.24,453.04) --
-	(160.82,455.22) --
-	(169.40,458.14) --
-	(177.98,461.20) --
-	(186.56,464.96) --
-	(195.14,468.16) --
-	(203.72,472.75) --
-	(212.30,478.46) --
-	(220.88,483.14) --
-	(229.46,489.87) --
-	(238.04,495.99) --
-	(246.62,504.16) --
-	(255.20,507.73) --
-	(263.78,519.42) --
-	(272.36,523.32) --
-	(280.94,524.71) --
-	(289.52,532.64) --
-	(298.10,534.54) --
-	(306.68,534.82) --
-	(315.26,531.06) --
-	(323.84,527.63) --
-	(332.42,521.69) --
-	(341.00,515.52) --
-	(349.58,506.80) --
-	(358.16,498.04) --
-	(366.74,488.94) --
-	(375.32,481.01) --
-	(383.90,478.27) --
-	(392.48,469.18) --
-	(401.06,463.80) --
-	(409.64,460.55) --
-	(418.22,458.74) --
-	(426.80,456.14) --
-	(435.38,452.71) --
-	(443.96,450.90) --
-	(452.54,449.19) --
-	(461.12,449.19) --
-	(469.70,448.49) --
-	(478.28,446.96) --
-	(486.86,446.26) --
-	(495.44,446.22) --
-	(504.02,445.24) --
-	(512.60,445.24) --
-	(521.18,445.01) --
-	(529.76,444.69) --
-	(538.34,444.13) --
-	(546.92,444.55) --
-	(555.50,444.08) --
-	(564.08,444.08) --
-	(572.66,444.08);
+	(572.66,444.32);
 \definecolor{drawColor}{RGB}{68,1,84}
@@
 	(572.66,444.13);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
-	( 49.28,444.69) --
-	( 57.86,445.10) --
-	( 66.44,444.96) --
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
+	( 49.28,444.73) --
+	( 57.86,445.20) --
+	( 66.44,444.83) --
 	( 75.02,445.24) --
-	( 83.60,445.52) --
-	( 92.18,446.17) --
-	(100.76,446.54) --
-	(109.34,446.77) --
-	(117.92,447.89) --
-	(126.50,448.72) --
-	(135.08,450.58) --
-	(143.66,450.95) --
-	(152.24,450.53) --
-	(160.82,454.38) --
-	(169.40,456.79) --
-	(177.98,456.75) --
-	(186.56,460.55) --
-	(195.14,463.61) --
+	( 83.60,445.61) --
+	( 92.18,446.26) --
+	(100.76,446.36) --
+	(109.34,447.05) --
+	(117.92,447.61) --
+	(126.50,448.86) --
+	(135.08,450.53) --
+	(143.66,450.62) --
+	(152.24,450.67) --
+	(160.82,454.61) --
+	(169.40,456.52) --
+	(177.98,456.38) --
+	(186.56,460.64) --
+	(195.14,463.15) --
 	(203.72,468.39) --
-	(212.30,473.36) --
-	(220.88,475.30) --
-	(229.46,483.61) --
-	(238.04,488.06) --
-	(246.62,496.64) --
-	(255.20,499.89) --
-	(263.78,507.13) --
-	(272.36,518.73) --
-	(280.94,520.44) --
-	(289.52,526.61) --
-	(298.10,529.07) --
-	(306.68,532.41) --
-	(315.26,533.85) --
-	(323.84,531.44) --
-	(332.42,525.68) --
-	(341.00,521.88) --
-	(349.58,512.74) --
-	(358.16,507.55) --
-	(366.74,498.55) --
-	(375.32,491.45) --
-	(383.90,485.70) --
-	(392.48,475.16) --
-	(401.06,471.27) --
-	(409.64,467.14) --
-	(418.22,463.52) --
-	(426.80,458.23) --
-	(435.38,454.61) --
-	(443.96,453.92) --
-	(452.54,451.83) --
-	(461.12,450.25) --
-	(469.70,449.00) --
-	(478.28,448.40) --
-	(486.86,447.05) --
-	(495.44,446.22) --
-	(504.02,445.57) --
-	(512.60,445.57) --
-	(521.18,445.34) --
-	(529.76,445.43) --
-	(538.34,444.64) --
-	(546.92,444.55) --
+	(212.30,472.52) --
+	(220.88,475.81) --
+	(229.46,482.17) --
+	(238.04,488.15) --
+	(246.62,494.70) --
+	(255.20,500.40) --
+	(263.78,506.11) --
+	(272.36,517.47) --
+	(280.94,520.86) --
+	(289.52,525.36) --
+	(298.10,528.79) --
+	(306.68,531.85) --
+	(315.26,533.62) --
+	(323.84,531.39) --
+	(332.42,525.59) --
+	(341.00,521.93) --
+	(349.58,515.80) --
+	(358.16,505.92) --
+	(366.74,501.28) --
+	(375.32,495.30) --
+	(383.90,484.44) --
+	(392.48,478.09) --
+	(401.06,471.18) --
+	(409.64,468.21) --
+	(418.22,462.13) --
+	(426.80,457.77) --
+	(435.38,456.10) --
+	(443.96,453.78) --
+	(452.54,452.43) --
+	(461.12,449.88) --
+	(469.70,448.26) --
+	(478.28,447.89) --
+	(486.86,447.10) --
+	(495.44,446.26) --
+	(504.02,445.99) --
+	(512.60,445.06) --
+	(521.18,445.24) --
+	(529.76,444.78) --
+	(538.34,444.96) --
+	(546.92,444.18) --
 	(555.50,444.41) --
 	(564.08,444.50) --
+	(572.66,444.27);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.78) --
+	( 49.28,444.87) --
+	( 57.86,444.96) --
+	( 66.44,444.83) --
+	( 75.02,445.89) --
+	( 83.60,445.24) --
+	( 92.18,446.36) --
+	(100.76,446.50) --
+	(109.34,447.05) --
+	(117.92,447.98) --
+	(126.50,448.72) --
+	(135.08,450.62) --
+	(143.66,451.46) --
+	(152.24,451.04) --
+	(160.82,455.26) --
+	(169.40,456.24) --
+	(177.98,458.14) --
+	(186.56,460.64) --
+	(195.14,465.01) --
+	(203.72,469.92) --
+	(212.30,473.40) --
+	(220.88,478.50) --
+	(229.46,485.70) --
+	(238.04,487.69) --
+	(246.62,497.52) --
+	(255.20,503.09) --
+	(263.78,508.33) --
+	(272.36,517.61) --
+	(280.94,521.00) --
+	(289.52,529.02) --
+	(298.10,529.30) --
+	(306.68,531.02) --
+	(315.26,532.13) --
+	(323.84,532.13) --
+	(332.42,525.50) --
+	(341.00,518.03) --
+	(349.58,513.39) --
+	(358.16,504.72) --
+	(366.74,499.94) --
+	(375.32,490.24) --
+	(383.90,482.17) --
+	(392.48,474.47) --
+	(401.06,470.85) --
+	(409.64,465.56) --
+	(418.22,461.80) --
+	(426.80,457.03) --
+	(435.38,454.89) --
+	(443.96,451.97) --
+	(452.54,451.18) --
+	(461.12,450.72) --
+	(469.70,448.30) --
+	(478.28,446.77) --
+	(486.86,447.47) --
+	(495.44,446.26) --
+	(504.02,446.12) --
+	(512.60,445.06) --
+	(521.18,444.78) --
+	(529.76,444.96) --
+	(538.34,444.55) --
+	(546.92,444.50) --
+	(555.50,444.22) --
+	(564.08,444.18) --
 	(572.66,444.22);
-\definecolor{drawColor}{RGB}{33,144,140}
+\definecolor{drawColor}{RGB}{253,231,37}
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.69) --
-	( 49.28,445.06) --
-	( 57.86,444.92) --
-	( 66.44,445.61) --
-	( 75.02,445.48) --
-	( 83.60,446.22) --
-	( 92.18,446.45) --
-	(100.76,447.01) --
-	(109.34,448.17) --
-	(117.92,448.54) --
-	(126.50,450.86) --
-	(135.08,451.00) --
-	(143.66,450.90) --
-	(152.24,455.22) --
-	(160.82,456.56) --
-	(169.40,457.44) --
-	(177.98,461.06) --
-	(186.56,464.36) --
-	(195.14,470.02) --
-	(203.72,473.40) --
-	(212.30,478.32) --
-	(220.88,482.59) --
-	(229.46,489.13) --
-	(238.04,496.92) --
-	(246.62,501.00) --
-	(255.20,508.47) --
-	(263.78,518.03) --
-	(272.36,522.07) --
-	(280.94,527.31) --
-	(289.52,530.37) --
-	(298.10,531.39) --
-	(306.68,535.24) --
-	(315.26,532.13) --
-	(323.84,526.47) --
-	(332.42,519.42) --
-	(341.00,512.74) --
-	(349.58,507.03) --
-	(358.16,497.94) --
-	(366.74,490.24) --
-	(375.32,482.68) --
-	(383.90,475.54) --
-	(392.48,469.92) --
-	(401.06,467.28) --
-	(409.64,460.78) --
-	(418.22,457.21) --
-	(426.80,455.36) --
-	(435.38,451.41) --
-	(443.96,450.95) --
-	(452.54,449.79) --
-	(461.12,448.54) --
-	(469.70,447.61) --
-	(478.28,447.05) --
-	(486.86,446.36) --
-	(495.44,445.66) --
-	(504.02,445.48) --
-	(512.60,444.92) --
-	(521.18,444.83) --
-	(529.76,444.50) --
-	(538.34,444.04) --
-	(546.92,444.45) --
-	(555.50,444.50) --
-	(564.08,444.08) --
-	(572.66,444.13);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.83) --
-	( 49.28,444.92) --
-	( 57.86,445.06) --
-	( 66.44,445.66) --
-	( 75.02,445.38) --
-	( 83.60,446.22) --
-	( 92.18,446.59) --
-	(100.76,447.42) --
-	(109.34,448.17) --
-	(117.92,448.54) --
-	(126.50,450.72) --
-	(135.08,451.55) --
-	(143.66,452.16) --
-	(152.24,455.17) --
-	(160.82,456.38) --
-	(169.40,458.70) --
-	(177.98,461.20) --
-	(186.56,466.40) --
-	(195.14,469.88) --
-	(203.72,473.82) --
-	(212.30,479.94) --
-	(220.88,486.72) --
-	(229.46,487.41) --
-	(238.04,498.55) --
-	(246.62,503.88) --
-	(255.20,509.77) --
-	(263.78,516.45) --
-	(272.36,521.60) --
-	(280.94,529.16) --
-	(289.52,533.52) --
-	(298.10,531.06) --
-	(306.68,531.99) --
-	(315.26,529.67) --
-	(323.84,527.08) --
-	(332.42,517.66) --
-	(341.00,511.44) --
-	(349.58,503.14) --
-	(358.16,498.36) --
-	(366.74,486.34) --
-	(375.32,481.10) --
-	(383.90,475.21) --
-	(392.48,468.99) --
-	(401.06,464.68) --
-	(409.64,461.39) --
-	(418.22,457.30) --
-	(426.80,454.99) --
-	(435.38,452.90) --
-	(443.96,452.02) --
-	(452.54,449.23) --
-	(461.12,449.00) --
-	(469.70,446.68) --
-	(478.28,447.24) --
-	(486.86,446.77) --
-	(495.44,445.61) --
-	(504.02,444.96) --
-	(512.60,444.96) --
-	(521.18,445.10) --
-	(529.76,444.59) --
-	(538.34,444.55) --
-	(546.92,444.18) --
-	(555.50,444.27) --
-	(564.08,444.13) --
-	(572.66,444.13);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
-	( 49.28,444.83) --
-	( 57.86,445.10) --
-	( 66.44,445.24) --
-	( 75.02,445.57) --
-	( 83.60,445.15) --
-	( 92.18,446.45) --
-	(100.76,446.82) --
-	(109.34,447.52) --
-	(117.92,448.49) --
-	(126.50,448.63) --
+	( 49.28,444.64) --
+	( 57.86,445.24) --
+	( 66.44,445.06) --
+	( 75.02,445.71) --
+	( 83.60,445.20) --
+	( 92.18,446.17) --
+	(100.76,447.28) --
+	(109.34,447.19) --
+	(117.92,448.21) --
+	(126.50,449.09) --
 	(135.08,450.16) --
-	(143.66,452.16) --
-	(152.24,452.43) --
-	(160.82,455.40) --
-	(169.40,457.86) --
-	(177.98,458.33) --
-	(186.56,462.36) --
-	(195.14,467.74) --
-	(203.72,469.55) --
-	(212.30,474.28) --
-	(220.88,482.03) --
-	(229.46,485.32) --
-	(238.04,491.35) --
-	(246.62,499.43) --
-	(255.20,506.57) --
-	(263.78,512.79) --
-	(272.36,515.66) --
-	(280.94,525.92) --
-	(289.52,529.58) --
-	(298.10,533.52) --
-	(306.68,528.84) --
-	(315.26,533.15) --
-	(323.84,530.23) --
-	(332.42,520.86) --
-	(341.00,518.35) --
-	(349.58,509.45) --
-	(358.16,501.93) --
-	(366.74,493.21) --
-	(375.32,486.99) --
-	(383.90,479.71) --
-	(392.48,473.31) --
-	(401.06,468.90) --
-	(409.64,462.83) --
-	(418.22,460.13) --
-	(426.80,456.38) --
-	(435.38,453.78) --
-	(443.96,452.16) --
-	(452.54,450.25) --
-	(461.12,449.19) --
-	(469.70,447.98) --
-	(478.28,447.66) --
-	(486.86,446.54) --
-	(495.44,446.96) --
-	(504.02,445.71) --
-	(512.60,445.71) --
-	(521.18,445.20) --
-	(529.76,444.59) --
-	(538.34,444.45) --
-	(546.92,444.96) --
-	(555.50,444.18) --
-	(564.08,444.04) --
-	(572.66,444.22);
+	(143.66,451.92) --
+	(152.24,452.62) --
+	(160.82,455.45) --
+	(169.40,457.68) --
+	(177.98,458.19) --
+	(186.56,462.08) --
+	(195.14,467.93) --
+	(203.72,470.48) --
+	(212.30,473.40) --
+	(220.88,481.66) --
+	(229.46,485.70) --
+	(238.04,491.12) --
+	(246.62,499.75) --
+	(255.20,505.64) --
+	(263.78,515.15) --
+	(272.36,515.85) --
+	(280.94,525.13) --
+	(289.52,531.06) --
+	(298.10,534.82) --
+	(306.68,528.51) --
+	(315.26,533.57) --
+	(323.84,531.95) --
+	(332.42,524.89) --
+	(341.00,516.92) --
+	(349.58,509.63) --
+	(358.16,502.26) --
+	(366.74,494.32) --
+	(375.32,484.86) --
+	(383.90,481.43) --
+	(392.48,473.54) --
+	(401.06,468.72) --
+	(409.64,461.90) --
+	(418.22,460.60) --
+	(426.80,455.50) --
+	(435.38,454.43) --
+	(443.96,452.20) --
+	(452.54,451.13) --
+	(461.12,448.35) --
+	(469.70,447.52) --
+	(478.28,447.93) --
+	(486.86,447.24) --
+	(495.44,446.45) --
+	(504.02,445.06) --
+	(512.60,445.34) --
+	(521.18,445.01) --
+	(529.76,444.73) --
+	(538.34,444.64) --
+	(546.92,444.36) --
+	(555.50,444.32) --
+	(564.08,444.41) --
+	(572.66,444.08);
 \definecolor{drawColor}{RGB}{68,1,84}
@@
 	(572.66,444.04);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.73) --
-	( 49.28,444.96) --
-	( 57.86,444.69) --
-	( 66.44,445.29) --
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.78) --
+	( 49.28,445.01) --
+	( 57.86,444.64) --
+	( 66.44,445.24) --
 	( 75.02,445.15) --
-	( 83.60,445.94) --
-	( 92.18,446.77) --
-	(100.76,446.36) --
-	(109.34,446.45) --
+	( 83.60,445.99) --
+	( 92.18,446.87) --
+	(100.76,446.26) --
+	(109.34,446.50) --
 	(117.92,448.07) --
-	(126.50,449.14) --
-	(135.08,449.98) --
-	(143.66,451.27) --
-	(152.24,452.16) --
+	(126.50,449.19) --
+	(135.08,450.58) --
+	(143.66,451.00) --
+	(152.24,452.48) --
 	(160.82,454.38) --
-	(169.40,455.40) --
-	(177.98,458.56) --
-	(186.56,460.69) --
-	(195.14,465.38) --
-	(203.72,468.48) --
-	(212.30,474.79) --
-	(220.88,477.86) --
-	(229.46,482.59) --
-	(238.04,490.89) --
-	(246.62,495.81) --
-	(255.20,503.05) --
-	(263.78,510.65) --
-	(272.36,515.94) --
-	(280.94,523.04) --
-	(289.52,528.14) --
-	(298.10,529.12) --
-	(306.68,532.73) --
-	(315.26,531.48) --
-	(323.84,527.45) --
-	(332.42,524.89) --
-	(341.00,516.03) --
-	(349.58,512.97) --
-	(358.16,506.43) --
-	(366.74,495.81) --
-	(375.32,488.39) --
-	(383.90,480.41) --
-	(392.48,475.91) --
-	(401.06,473.26) --
-	(409.64,467.05) --
-	(418.22,460.27) --
-	(426.80,457.44) --
-	(435.38,456.33) --
-	(443.96,453.22) --
-	(452.54,451.13) --
-	(461.12,449.60) --
-	(469.70,448.21) --
-	(478.28,447.42) --
-	(486.86,446.63) --
+	(169.40,455.91) --
+	(177.98,458.79) --
+	(186.56,461.57) --
+	(195.14,465.24) --
+	(203.72,469.51) --
+	(212.30,474.89) --
+	(220.88,477.90) --
+	(229.46,484.81) --
+	(238.04,491.96) --
+	(246.62,496.18) --
+	(255.20,502.95) --
+	(263.78,512.32) --
+	(272.36,517.33) --
+	(280.94,523.50) --
+	(289.52,527.26) --
+	(298.10,527.72) --
+	(306.68,533.52) --
+	(315.26,530.93) --
+	(323.84,528.47) --
+	(332.42,523.87) --
+	(341.00,515.15) --
+	(349.58,511.49) --
+	(358.16,504.81) --
+	(366.74,496.78) --
+	(375.32,487.60) --
+	(383.90,480.78) --
+	(392.48,475.03) --
+	(401.06,471.87) --
+	(409.64,466.49) --
+	(418.22,460.74) --
+	(426.80,457.26) --
+	(435.38,455.73) --
+	(443.96,453.59) --
+	(452.54,450.30) --
+	(461.12,449.51) --
+	(469.70,448.03) --
+	(478.28,447.61) --
+	(486.86,446.59) --
+	(495.44,445.75) --
+	(504.02,445.94) --
+	(512.60,445.85) --
+	(521.18,444.78) --
+	(529.76,445.15) --
+	(538.34,444.45) --
+	(546.92,444.32) --
+	(555.50,444.36) --
+	(564.08,444.22) --
+	(572.66,444.13);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.92) --
+	( 49.28,444.55) --
+	( 57.86,445.10) --
+	( 66.44,444.92) --
+	( 75.02,445.57) --
+	( 83.60,445.99) --
+	( 92.18,446.91) --
+	(100.76,446.54) --
+	(109.34,446.54) --
+	(117.92,448.44) --
+	(126.50,449.60) --
+	(135.08,450.49) --
+	(143.66,451.13) --
+	(152.24,453.36) --
+	(160.82,453.64) --
+	(169.40,456.56) --
+	(177.98,459.30) --
+	(186.56,461.67) --
+	(195.14,466.12) --
+	(203.72,470.94) --
+	(212.30,474.24) --
+	(220.88,479.11) --
+	(229.46,485.51) --
+	(238.04,491.22) --
+	(246.62,497.94) --
+	(255.20,506.29) --
+	(263.78,512.56) --
+	(272.36,518.73) --
+	(280.94,524.76) --
+	(289.52,529.02) --
+	(298.10,527.21) --
+	(306.68,535.52) --
+	(315.26,529.63) --
+	(323.84,529.35) --
+	(332.42,522.02) --
+	(341.00,515.66) --
+	(349.58,509.17) --
+	(358.16,503.46) --
+	(366.74,496.92) --
+	(375.32,486.02) --
+	(383.90,479.66) --
+	(392.48,475.21) --
+	(401.06,471.31) --
+	(409.64,465.28) --
+	(418.22,459.67) --
+	(426.80,456.28) --
+	(435.38,453.36) --
+	(443.96,452.57) --
+	(452.54,450.72) --
+	(461.12,448.49) --
+	(469.70,448.30) --
+	(478.28,446.59) --
+	(486.86,446.17) --
 	(495.44,446.31) --
-	(504.02,446.03) --
-	(512.60,445.34) --
-	(521.18,444.87) --
-	(529.76,445.06) --
-	(538.34,444.59) --
-	(546.92,444.36) --
+	(504.02,445.57) --
+	(512.60,445.66) --
+	(521.18,444.50) --
+	(529.76,444.55) --
+	(538.34,444.45) --
+	(546.92,444.59) --
 	(555.50,444.32) --
 	(564.08,444.36) --
-	(572.66,444.18);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.83) --
-	( 49.28,444.83) --
-	( 57.86,444.92) --
-	( 66.44,445.06) --
-	( 75.02,445.29) --
-	( 83.60,445.94) --
-	( 92.18,447.05) --
-	(100.76,446.45) --
-	(109.34,446.59) --
-	(117.92,448.03) --
-	(126.50,449.56) --
-	(135.08,450.58) --
-	(143.66,450.86) --
-	(152.24,452.94) --
-	(160.82,454.15) --
-	(169.40,456.33) --
-	(177.98,459.48) --
-	(186.56,461.29) --
-	(195.14,465.75) --
-	(203.72,470.53) --
-	(212.30,474.28) --
-	(220.88,478.78) --
-	(229.46,485.56) --
-	(238.04,491.59) --
-	(246.62,496.41) --
-	(255.20,506.34) --
-	(263.78,511.53) --
-	(272.36,517.47) --
-	(280.94,525.08) --
-	(289.52,529.16) --
-	(298.10,528.47) --
-	(306.68,534.27) --
-	(315.26,531.95) --
-	(323.84,527.12) --
-	(332.42,522.48) --
-	(341.00,518.77) --
-	(349.58,513.48) --
-	(358.16,503.83) --
-	(366.74,492.75) --
-	(375.32,487.46) --
-	(383.90,479.02) --
-	(392.48,476.00) --
-	(401.06,470.15) --
-	(409.64,464.63) --
-	(418.22,459.76) --
-	(426.80,456.66) --
-	(435.38,455.36) --
-	(443.96,452.53) --
-	(452.54,450.39) --
-	(461.12,448.82) --
-	(469.70,448.77) --
-	(478.28,447.01) --
-	(486.86,445.94) --
-	(495.44,445.71) --
-	(504.02,445.85) --
-	(512.60,445.38) --
-	(521.18,444.87) --
-	(529.76,444.55) --
-	(538.34,444.41) --
-	(546.92,444.27) --
-	(555.50,444.27) --
-	(564.08,444.32) --
-	(572.66,443.99);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.36) --
-	( 49.28,444.96) --
-	( 57.86,444.64) --
-	( 66.44,445.10) --
-	( 75.02,444.78) --
-	( 83.60,445.57) --
-	( 92.18,446.08) --
-	(100.76,447.24) --
-	(109.34,446.54) --
-	(117.92,446.54) --
-	(126.50,448.77) --
-	(135.08,449.74) --
-	(143.66,450.16) --
-	(152.24,451.65) --
-	(160.82,453.73) --
-	(169.40,454.61) --
-	(177.98,457.26) --
-	(186.56,459.62) --
-	(195.14,462.64) --
-	(203.72,466.54) --
-	(212.30,472.34) --
-	(220.88,474.93) --
-	(229.46,482.45) --
-	(238.04,487.18) --
-	(246.62,491.45) --
-	(255.20,499.01) --
-	(263.78,509.26) --
-	(272.36,514.41) --
-	(280.94,519.19) --
-	(289.52,526.52) --
-	(298.10,529.35) --
-	(306.68,531.58) --
-	(315.26,535.47) --
-	(323.84,529.44) --
-	(332.42,524.99) --
-	(341.00,520.86) --
-	(349.58,520.49) --
-	(358.16,506.85) --
-	(366.74,501.28) --
-	(375.32,494.18) --
-	(383.90,483.70) --
-	(392.48,479.99) --
-	(401.06,473.36) --
-	(409.64,468.11) --
-	(418.22,463.24) --
-	(426.80,459.16) --
-	(435.38,455.91) --
-	(443.96,453.64) --
-	(452.54,450.44) --
-	(461.12,449.88) --
-	(469.70,448.86) --
-	(478.28,448.12) --
-	(486.86,446.68) --
-	(495.44,446.50) --
-	(504.02,445.52) --
-	(512.60,445.89) --
-	(521.18,444.69) --
-	(529.76,445.06) --
-	(538.34,444.83) --
-	(546.92,444.27) --
-	(555.50,444.41) --
-	(564.08,444.55) --
 	(572.66,444.08);
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
-	( 49.28,444.92) --
-	( 57.86,444.69) --
-	( 66.44,444.87) --
-	( 75.02,445.24) --
-	( 83.60,445.66) --
-	( 92.18,446.03) --
-	(100.76,446.87) --
-	(109.34,447.28) --
-	(117.92,446.82) --
-	(126.50,448.63) --
-	(135.08,449.33) --
-	(143.66,451.41) --
-	(152.24,451.46) --
-	(160.82,453.92) --
-	(169.40,454.85) --
-	(177.98,457.58) --
-	(186.56,459.95) --
-	(195.14,463.20) --
-	(203.72,468.07) --
-	(212.30,471.87) --
-	(220.88,476.37) --
-	(229.46,482.26) --
-	(238.04,486.07) --
-	(246.62,492.51) --
-	(255.20,501.61) --
-	(263.78,510.47) --
-	(272.36,516.03) --
-	(280.94,522.25) --
-	(289.52,524.89) --
-	(298.10,531.44) --
-	(306.68,534.45) --
-	(315.26,534.36) --
-	(323.84,528.14) --
-	(332.42,522.71) --
-	(341.00,519.47) --
-	(349.58,515.34) --
-	(358.16,509.03) --
-	(366.74,499.75) --
-	(375.32,493.03) --
-	(383.90,485.51) --
-	(392.48,474.98) --
-	(401.06,472.66) --
-	(409.64,468.25) --
-	(418.22,463.01) --
-	(426.80,458.14) --
-	(435.38,455.91) --
-	(443.96,454.52) --
-	(452.54,450.39) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.92) --
+	( 49.28,444.59) --
+	( 57.86,445.01) --
+	( 66.44,445.10) --
+	( 75.02,445.66) --
+	( 83.60,446.08) --
+	( 92.18,447.05) --
+	(100.76,446.73) --
+	(109.34,447.10) --
+	(117.92,448.49) --
+	(126.50,449.46) --
+	(135.08,450.72) --
+	(143.66,451.97) --
+	(152.24,453.64) --
+	(160.82,454.71) --
+	(169.40,457.49) --
+	(177.98,459.90) --
+	(186.56,463.47) --
+	(195.14,466.86) --
+	(203.72,472.43) --
+	(212.30,475.58) --
+	(220.88,483.10) --
+	(229.46,486.02) --
+	(238.04,492.24) --
+	(246.62,500.86) --
+	(255.20,511.07) --
+	(263.78,514.69) --
+	(272.36,518.63) --
+	(280.94,525.31) --
+	(289.52,530.65) --
+	(298.10,532.18) --
+	(306.68,534.36) --
+	(315.26,530.04) --
+	(323.84,526.24) --
+	(332.42,520.35) --
+	(341.00,517.06) --
+	(349.58,507.59) --
+	(358.16,500.35) --
+	(366.74,493.63) --
+	(375.32,483.52) --
+	(383.90,478.50) --
+	(392.48,472.52) --
+	(401.06,467.65) --
+	(409.64,462.73) --
+	(418.22,457.91) --
+	(426.80,456.01) --
+	(435.38,453.83) --
+	(443.96,450.86) --
+	(452.54,449.46) --
 	(461.12,449.51) --
-	(469.70,449.28) --
-	(478.28,447.19) --
-	(486.86,446.82) --
-	(495.44,446.08) --
+	(469.70,448.07) --
+	(478.28,446.63) --
+	(486.86,446.68) --
+	(495.44,445.38) --
 	(504.02,445.66) --
-	(512.60,445.71) --
-	(521.18,444.64) --
-	(529.76,444.87) --
-	(538.34,444.83) --
-	(546.92,444.36) --
-	(555.50,444.27) --
-	(564.08,444.27) --
-	(572.66,443.99);
+	(512.60,445.20) --
+	(521.18,444.96) --
+	(529.76,444.69) --
+	(538.34,444.45) --
+	(546.92,444.27) --
+	(555.50,444.32) --
+	(564.08,444.13);
 \definecolor{drawColor}{RGB}{68,1,84}
@@
 	(572.66,444.04);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,445.01) --
-	( 49.28,444.59) --
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
+	( 49.28,444.45) --
+	( 57.86,445.29) --
+	( 66.44,445.01) --
+	( 75.02,446.08) --
+	( 83.60,446.45) --
+	( 92.18,446.73) --
+	(100.76,446.87) --
+	(109.34,448.30) --
+	(117.92,448.44) --
+	(126.50,449.74) --
+	(135.08,450.76) --
+	(143.66,452.39) --
+	(152.24,454.47) --
+	(160.82,455.68) --
+	(169.40,459.25) --
+	(177.98,461.76) --
+	(186.56,463.06) --
+	(195.14,468.44) --
+	(203.72,475.12) --
+	(212.30,480.04) --
+	(220.88,483.10) --
+	(229.46,492.89) --
+	(238.04,497.43) --
+	(246.62,507.13) --
+	(255.20,512.00) --
+	(263.78,520.77) --
+	(272.36,526.05) --
+	(280.94,532.18) --
+	(289.52,533.85) --
+	(298.10,538.26) --
+	(306.68,534.13) --
+	(315.26,535.19) --
+	(323.84,526.43) --
+	(332.42,521.23) --
+	(341.00,512.00) --
+	(349.58,500.86) --
+	(358.16,496.97) --
+	(366.74,486.25) --
+	(375.32,480.41) --
+	(383.90,472.71) --
+	(392.48,465.38) --
+	(401.06,464.91) --
+	(409.64,458.74) --
+	(418.22,456.70) --
+	(426.80,452.62) --
+	(435.38,451.41) --
+	(443.96,449.84) --
+	(452.54,449.51) --
+	(461.12,448.26) --
+	(469.70,446.36) --
+	(478.28,446.40) --
+	(486.86,445.80) --
+	(495.44,445.20) --
+	(504.02,444.73) --
+	(512.60,444.92) --
+	(521.18,444.73) --
+	(529.76,444.41) --
+	(538.34,444.32) --
+	(546.92,444.41) --
+	(555.50,444.04) --
+	(564.08,443.99) --
+	(572.66,443.99);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.73) --
+	( 49.28,444.87) --
 	( 57.86,444.50) --
-	( 66.44,445.29) --
-	( 75.02,445.20) --
-	( 83.60,446.17) --
-	( 92.18,446.26) --
-	(100.76,446.87) --
-	(109.34,447.05) --
-	(117.92,448.21) --
-	(126.50,448.63) --
-	(135.08,449.93) --
-	(143.66,450.95) --
-	(152.24,452.71) --
-	(160.82,454.71) --
-	(169.40,455.82) --
-	(177.98,460.37) --
-	(186.56,461.62) --
-	(195.14,464.63) --
-	(203.72,471.27) --
-	(212.30,475.63) --
-	(220.88,480.13) --
-	(229.46,486.02) --
-	(238.04,494.37) --
-	(246.62,499.66) --
-	(255.20,508.06) --
-	(263.78,514.69) --
-	(272.36,521.83) --
-	(280.94,526.19) --
-	(289.52,532.97) --
-	(298.10,534.36) --
-	(306.68,536.17) --
-	(315.26,532.60) --
-	(323.84,532.55) --
-	(332.42,526.29) --
-	(341.00,519.84) --
-	(349.58,509.82) --
-	(358.16,498.59) --
-	(366.74,494.51) --
-	(375.32,486.02) --
-	(383.90,478.55) --
-	(392.48,471.59) --
-	(401.06,467.79) --
-	(409.64,463.38) --
-	(418.22,459.07) --
-	(426.80,456.47) --
-	(435.38,452.76) --
-	(443.96,451.27) --
-	(452.54,449.56) --
-	(461.12,449.70) --
-	(469.70,448.17) --
-	(478.28,446.68) --
-	(486.86,446.12) --
-	(495.44,445.80) --
-	(504.02,445.52) --
-	(512.60,445.15) --
-	(521.18,444.83) --
-	(529.76,444.55) --
+	( 66.44,445.01) --
+	( 75.02,445.10) --
+	( 83.60,445.52) --
+	( 92.18,446.31) --
+	(100.76,447.01) --
+	(109.34,446.36) --
+	(117.92,447.47) --
+	(126.50,448.82) --
+	(135.08,449.37) --
+	(143.66,450.35) --
+	(152.24,451.23) --
+	(160.82,453.36) --
+	(169.40,455.31) --
+	(177.98,457.86) --
+	(186.56,461.06) --
+	(195.14,462.69) --
+	(203.72,466.07) --
+	(212.30,473.03) --
+	(220.88,478.04) --
+	(229.46,482.49) --
+	(238.04,489.73) --
+	(246.62,495.76) --
+	(255.20,503.83) --
+	(263.78,508.61) --
+	(272.36,517.75) --
+	(280.94,525.31) --
+	(289.52,529.63) --
+	(298.10,536.49) --
+	(306.68,533.34) --
+	(315.26,536.96) --
+	(323.84,535.29) --
+	(332.42,528.88) --
+	(341.00,522.62) --
+	(349.58,513.25) --
+	(358.16,506.20) --
+	(366.74,498.45) --
+	(375.32,487.92) --
+	(383.90,481.71) --
+	(392.48,475.07) --
+	(401.06,468.02) --
+	(409.64,465.65) --
+	(418.22,461.48) --
+	(426.80,457.63) --
+	(435.38,455.36) --
+	(443.96,452.34) --
+	(452.54,450.58) --
+	(461.12,449.84) --
+	(469.70,447.79) --
+	(478.28,447.56) --
+	(486.86,446.31) --
+	(495.44,445.61) --
+	(504.02,445.71) --
+	(512.60,444.96) --
+	(521.18,444.87) --
+	(529.76,444.78) --
 	(538.34,444.59) --
-	(546.92,444.41) --
-	(555.50,444.36) --
-	(564.08,444.27) --
-	(572.66,444.04);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.78) --
-	( 49.28,444.78) --
-	( 57.86,444.36) --
-	( 66.44,445.24) --
-	( 75.02,445.06) --
-	( 83.60,445.57) --
+	(546.92,444.50) --
+	(555.50,444.04) --
+	(564.08,444.22) --
+	(572.66,444.08);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.92) --
+	( 49.28,444.69) --
+	( 57.86,444.64) --
+	( 66.44,445.43) --
+	( 75.02,445.15) --
+	( 83.60,446.03) --
 	( 92.18,446.59) --
 	(100.76,446.87) --
-	(109.34,446.40) --
-	(117.92,447.89) --
-	(126.50,448.58) --
-	(135.08,449.65) --
-	(143.66,450.53) --
-	(152.24,451.78) --
-	(160.82,453.83) --
-	(169.40,455.17) --
-	(177.98,458.33) --
-	(186.56,461.48) --
-	(195.14,462.96) --
-	(203.72,468.53) --
-	(212.30,472.20) --
-	(220.88,478.88) --
-	(229.46,484.44) --
-	(238.04,488.94) --
-	(246.62,496.18) --
-	(255.20,504.53) --
-	(263.78,512.83) --
-	(272.36,518.31) --
-	(280.94,524.80) --
-	(289.52,528.00) --
-	(298.10,536.31) --
-	(306.68,534.45) --
-	(315.26,535.61) --
-	(323.84,532.73) --
-	(332.42,528.10) --
-	(341.00,519.88) --
-	(349.58,514.64) --
-	(358.16,502.86) --
-	(366.74,498.87) --
-	(375.32,490.38) --
-	(383.90,481.38) --
-	(392.48,475.21) --
-	(401.06,467.23) --
-	(409.64,466.35) --
-	(418.22,461.20) --
-	(426.80,456.61) --
-	(435.38,453.59) --
-	(443.96,452.94) --
-	(452.54,450.86) --
-	(461.12,449.56) --
-	(469.70,447.42) --
-	(478.28,447.93) --
-	(486.86,446.31) --
-	(495.44,446.12) --
-	(504.02,445.06) --
-	(512.60,445.57) --
+	(109.34,446.59) --
+	(117.92,448.26) --
+	(126.50,449.98) --
+	(135.08,449.70) --
+	(143.66,450.76) --
+	(152.24,453.27) --
+	(160.82,454.52) --
+	(169.40,456.75) --
+	(177.98,459.30) --
+	(186.56,462.69) --
+	(195.14,465.47) --
+	(203.72,471.13) --
+	(212.30,475.03) --
+	(220.88,480.04) --
+	(229.46,489.08) --
+	(238.04,494.37) --
+	(246.62,499.84) --
+	(255.20,507.59) --
+	(263.78,514.87) --
+	(272.36,524.80) --
+	(280.94,524.66) --
+	(289.52,535.70) --
+	(298.10,536.59) --
+	(306.68,537.00) --
+	(315.26,536.77) --
+	(323.84,532.13) --
+	(332.42,524.57) --
+	(341.00,517.33) --
+	(349.58,508.47) --
+	(358.16,503.60) --
+	(366.74,491.40) --
+	(375.32,482.49) --
+	(383.90,477.16) --
+	(392.48,470.90) --
+	(401.06,466.07) --
+	(409.64,462.78) --
+	(418.22,457.77) --
+	(426.80,454.99) --
+	(435.38,452.53) --
+	(443.96,451.65) --
+	(452.54,450.02) --
+	(461.12,448.17) --
+	(469.70,447.79) --
+	(478.28,446.73) --
+	(486.86,446.17) --
+	(495.44,445.80) --
+	(504.02,444.87) --
+	(512.60,444.92) --
 	(521.18,444.78) --
-	(529.76,444.59) --
-	(538.34,444.41) --
-	(546.92,444.18) --
-	(555.50,444.32) --
-	(564.08,444.32) --
-	(572.66,444.18);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.92) --
-	( 49.28,444.55) --
-	( 57.86,444.78) --
-	( 66.44,445.38) --
-	( 75.02,445.24) --
-	( 83.60,446.17) --
-	( 92.18,446.96) --
-	(100.76,446.45) --
-	(109.34,447.15) --
-	(117.92,448.54) --
-	(126.50,449.88) --
-	(135.08,450.16) --
-	(143.66,451.13) --
-	(152.24,452.94) --
-	(160.82,454.75) --
-	(169.40,457.72) --
-	(177.98,461.16) --
-	(186.56,463.01) --
-	(195.14,466.07) --
-	(203.72,472.38) --
-	(212.30,477.07) --
-	(220.88,482.08) --
-	(229.46,488.90) --
-	(238.04,495.48) --
-	(246.62,504.76) --
-	(255.20,508.01) --
-	(263.78,514.78) --
-	(272.36,526.84) --
-	(280.94,526.29) --
-	(289.52,536.82) --
-	(298.10,534.78) --
-	(306.68,535.24) --
-	(315.26,536.03) --
-	(323.84,528.05) --
-	(332.42,521.23) --
-	(341.00,515.71) --
-	(349.58,507.64) --
-	(358.16,502.58) --
-	(366.74,488.48) --
-	(375.32,483.75) --
-	(383.90,474.47) --
-	(392.48,469.23) --
-	(401.06,467.32) --
-	(409.64,461.80) --
-	(418.22,456.70) --
-	(426.80,456.33) --
-	(435.38,451.88) --
-	(443.96,451.83) --
-	(452.54,449.79) --
-	(461.12,447.93) --
-	(469.70,447.24) --
-	(478.28,446.08) --
-	(486.86,445.99) --
-	(495.44,445.75) --
-	(504.02,445.06) --
-	(512.60,444.73) --
-	(521.18,444.83) --
-	(529.76,444.50) --
-	(538.34,444.18) --
-	(546.92,444.18) --
-	(555.50,444.27) --
-	(564.08,444.04) --
+	(529.76,444.45) --
+	(538.34,444.78) --
+	(546.92,444.08) --
+	(555.50,444.45) --
+	(564.08,444.08) --
 	(572.66,444.13);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.83) --
-	( 49.28,444.59) --
-	( 57.86,444.83) --
-	( 66.44,445.38) --
-	( 75.02,445.24) --
-	( 83.60,445.89) --
-	( 92.18,446.50) --
-	(100.76,446.91) --
-	(109.34,446.54) --
-	(117.92,448.03) --
-	(126.50,450.07) --
-	(135.08,449.74) --
-	(143.66,450.72) --
-	(152.24,452.94) --
-	(160.82,454.34) --
-	(169.40,456.66) --
-	(177.98,459.76) --
-	(186.56,461.48) --
-	(195.14,465.33) --
-	(203.72,471.18) --
-	(212.30,473.87) --
-	(220.88,479.29) --
-	(229.46,487.60) --
-	(238.04,493.95) --
-	(246.62,499.89) --
-	(255.20,505.60) --
-	(263.78,512.97) --
-	(272.36,522.62) --
-	(280.94,524.15) --
-	(289.52,531.58) --
-	(298.10,534.31) --
-	(306.68,537.61) --
-	(315.26,533.66) --
-	(323.84,533.85) --
-	(332.42,525.08) --
-	(341.00,519.19) --
-	(349.58,509.77) --
-	(358.16,505.36) --
-	(366.74,492.38) --
-	(375.32,484.67) --
-	(383.90,478.88) --
-	(392.48,472.01) --
-	(401.06,467.37) --
-	(409.64,464.08) --
-	(418.22,457.63) --
-	(426.80,455.96) --
-	(435.38,451.78) --
-	(443.96,451.41) --
-	(452.54,449.84) --
-	(461.12,448.17) --
-	(469.70,447.52) --
-	(478.28,446.59) --
-	(486.86,446.17) --
-	(495.44,445.61) --
-	(504.02,445.24) --
-	(512.60,444.96) --
-	(521.18,444.36) --
-	(529.76,444.69) --
-	(538.34,444.45) --
-	(546.92,444.45) --
-	(555.50,443.99) --
-	(564.08,444.18) --
-	(572.66,444.18);
 \definecolor{drawColor}{RGB}{68,1,84}
@@
 	(555.50,444.13);
-\definecolor{drawColor}{RGB}{59,82,139}
+\definecolor{drawColor}{RGB}{49,104,142}
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.69) --
-	( 49.28,444.64) --
-	( 57.86,444.92) --
+	( 49.28,444.73) --
+	( 57.86,444.87) --
 	( 66.44,444.83) --
-	( 75.02,445.34) --
-	( 83.60,445.48) --
-	( 92.18,446.26) --
-	(100.76,446.22) --
-	(109.34,447.84) --
-	(117.92,447.42) --
-	(126.50,449.00) --
-	(135.08,448.95) --
-	(143.66,450.86) --
-	(152.24,452.94) --
-	(160.82,452.94) --
-	(169.40,454.06) --
-	(177.98,458.33) --
-	(186.56,461.29) --
-	(195.14,464.87) --
-	(203.72,466.91) --
-	(212.30,472.80) --
-	(220.88,476.79) --
-	(229.46,482.96) --
-	(238.04,489.64) --
-	(246.62,495.07) --
-	(255.20,504.39) --
-	(263.78,511.72) --
-	(272.36,515.01) --
-	(280.94,521.97) --
-	(289.52,531.48) --
-	(298.10,531.81) --
-	(306.68,536.54) --
-	(315.26,533.85) --
-	(323.84,530.28) --
-	(332.42,528.42) --
-	(341.00,520.07) --
-	(349.58,512.56) --
-	(358.16,503.56) --
-	(366.74,500.03) --
-	(375.32,490.94) --
-	(383.90,482.73) --
-	(392.48,477.53) --
-	(401.06,469.64) --
-	(409.64,465.75) --
-	(418.22,459.76) --
-	(426.80,457.07) --
-	(435.38,453.50) --
-	(443.96,452.16) --
-	(452.54,450.81) --
-	(461.12,449.09) --
-	(469.70,447.98) --
-	(478.28,447.05) --
-	(486.86,446.36) --
-	(495.44,446.31) --
-	(504.02,445.24) --
-	(512.60,445.29) --
-	(521.18,444.59) --
-	(529.76,444.73) --
-	(538.34,444.55) --
-	(546.92,444.45) --
-	(555.50,444.04) --
-	(564.08,444.13) --
-	(572.66,444.08);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
-	( 49.28,444.96) --
-	( 57.86,444.64) --
-	( 66.44,445.01) --
-	( 75.02,445.15) --
+	( 75.02,445.29) --
 	( 83.60,445.75) --
-	( 92.18,445.94) --
-	(100.76,446.54) --
-	(109.34,447.75) --
-	(117.92,447.15) --
-	(126.50,449.51) --
-	(135.08,448.95) --
-	(143.66,451.32) --
+	( 92.18,446.12) --
+	(100.76,446.26) --
+	(109.34,447.93) --
+	(117.92,447.24) --
+	(126.50,449.14) --
+	(135.08,448.91) --
+	(143.66,451.00) --
 	(152.24,452.76) --
 	(160.82,452.71) --
-	(169.40,454.66) --
-	(177.98,457.95) --
-	(186.56,462.69) --
-	(195.14,464.03) --
-	(203.72,467.74) --
-	(212.30,473.54) --
-	(220.88,476.97) --
-	(229.46,482.40) --
-	(238.04,491.08) --
-	(246.62,497.39) --
-	(255.20,503.28) --
-	(263.78,510.51) --
-	(272.36,517.29) --
-	(280.94,521.74) --
-	(289.52,529.77) --
-	(298.10,532.64) --
-	(306.68,537.61) --
-	(315.26,534.82) --
-	(323.84,530.97) --
-	(332.42,526.70) --
-	(341.00,521.93) --
-	(349.58,509.17) --
+	(169.40,454.75) --
+	(177.98,458.28) --
+	(186.56,461.90) --
+	(195.14,464.22) --
+	(203.72,467.65) --
+	(212.30,473.08) --
+	(220.88,477.02) --
+	(229.46,483.28) --
+	(238.04,490.38) --
+	(246.62,495.62) --
+	(255.20,504.39) --
+	(263.78,512.46) --
+	(272.36,516.36) --
+	(280.94,522.95) --
+	(289.52,530.00) --
+	(298.10,531.71) --
+	(306.68,535.84) --
+	(315.26,533.99) --
+	(323.84,531.99) --
+	(332.42,528.19) --
+	(341.00,521.32) --
+	(349.58,510.19) --
+	(358.16,503.00) --
+	(366.74,499.19) --
+	(375.32,490.52) --
+	(383.90,479.66) --
+	(392.48,478.60) --
+	(401.06,469.74) --
+	(409.64,466.21) --
+	(418.22,458.74) --
+	(426.80,456.19) --
+	(435.38,453.92) --
+	(443.96,452.48) --
+	(452.54,451.27) --
+	(461.12,448.72) --
+	(469.70,447.56) --
+	(478.28,447.38) --
+	(486.86,446.08) --
+	(495.44,446.68) --
+	(504.02,445.24) --
+	(512.60,445.15) --
+	(521.18,444.83) --
+	(529.76,444.41) --
+	(538.34,444.83) --
+	(546.92,444.41) --
+	(555.50,444.18) --
+	(564.08,444.13) --
+	(572.66,444.13);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.50) --
+	( 49.28,445.01) --
+	( 57.86,444.73) --
+	( 66.44,444.87) --
+	( 75.02,445.34) --
+	( 83.60,445.75) --
+	( 92.18,446.03) --
+	(100.76,446.59) --
+	(109.34,447.24) --
+	(117.92,448.03) --
+	(126.50,448.82) --
+	(135.08,448.86) --
+	(143.66,451.74) --
+	(152.24,452.48) --
+	(160.82,452.99) --
+	(169.40,455.12) --
+	(177.98,458.93) --
+	(186.56,461.76) --
+	(195.14,463.98) --
+	(203.72,467.65) --
+	(212.30,474.65) --
+	(220.88,476.28) --
+	(229.46,483.52) --
+	(238.04,490.57) --
+	(246.62,498.73) --
+	(255.20,501.56) --
+	(263.78,511.07) --
+	(272.36,515.80) --
+	(280.94,523.87) --
+	(289.52,529.21) --
+	(298.10,531.90) --
+	(306.68,538.63) --
+	(315.26,533.62) --
+	(323.84,529.86) --
+	(332.42,527.96) --
+	(341.00,521.18) --
+	(349.58,513.71) --
 	(358.16,504.25) --
-	(366.74,495.81) --
-	(375.32,487.83) --
-	(383.90,479.29) --
-	(392.48,476.37) --
-	(401.06,469.64) --
-	(409.64,465.79) --
-	(418.22,460.37) --
-	(426.80,457.12) --
-	(435.38,455.36) --
-	(443.96,451.78) --
-	(452.54,450.81) --
-	(461.12,448.68) --
-	(469.70,448.17) --
-	(478.28,446.91) --
-	(486.86,446.91) --
-	(495.44,445.94) --
-	(504.02,445.80) --
-	(512.60,445.06) --
-	(521.18,444.59) --
-	(529.76,444.32) --
-	(538.34,444.36) --
-	(546.92,444.50) --
-	(555.50,444.18) --
-	(564.08,444.27) --
-	(572.66,444.08);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
-	( 49.28,444.96) --
-	( 57.86,444.83) --
-	( 66.44,445.01) --
-	( 75.02,445.29) --
-	( 83.60,445.85) --
-	( 92.18,446.08) --
-	(100.76,446.59) --
-	(109.34,447.42) --
-	(117.92,448.35) --
-	(126.50,448.77) --
-	(135.08,449.05) --
-	(143.66,451.41) --
-	(152.24,453.27) --
-	(160.82,453.04) --
-	(169.40,455.36) --
-	(177.98,459.21) --
-	(186.56,462.13) --
-	(195.14,465.19) --
-	(203.72,467.93) --
-	(212.30,475.35) --
-	(220.88,478.18) --
-	(229.46,482.63) --
-	(238.04,492.56) --
-	(246.62,500.40) --
-	(255.20,503.09) --
-	(263.78,510.37) --
-	(272.36,517.52) --
-	(280.94,526.43) --
-	(289.52,529.49) --
-	(298.10,535.56) --
-	(306.68,534.45) --
-	(315.26,533.57) --
-	(323.84,531.06) --
-	(332.42,524.25) --
-	(341.00,518.31) --
-	(349.58,511.30) --
-	(358.16,502.86) --
-	(366.74,494.23) --
-	(375.32,487.92) --
-	(383.90,480.96) --
-	(392.48,474.84) --
-	(401.06,470.80) --
-	(409.64,463.01) --
-	(418.22,459.21) --
-	(426.80,457.77) --
-	(435.38,453.59) --
-	(443.96,451.69) --
-	(452.54,451.88) --
-	(461.12,448.26) --
-	(469.70,447.70) --
-	(478.28,447.98) --
-	(486.86,446.17) --
-	(495.44,446.17) --
-	(504.02,445.94) --
-	(512.60,444.73) --
-	(521.18,445.10) --
-	(529.76,444.55) --
-	(538.34,444.83) --
-	(546.92,444.08) --
-	(555.50,444.04) --
-	(564.08,444.22) --
-	(572.66,444.13);
+	(366.74,497.57) --
+	(375.32,487.37) --
+	(383.90,479.99) --
+	(392.48,475.77) --
+	(401.06,470.25) --
+	(409.64,466.07) --
+	(418.22,459.48) --
+	(426.80,456.42) --
+	(435.38,454.94) --
+	(443.96,453.13) --
+	(452.54,451.00) --
+	(461.12,448.58) --
+	(469.70,447.38) --
+	(478.28,447.33) --
+	(486.86,446.59) --
+	(495.44,446.63) --
+	(504.02,445.89) --
+	(512.60,445.10) --
+	(521.18,444.83) --
+	(529.76,445.10) --
+	(538.34,444.41) --
+	(546.92,444.41) --
+	(555.50,444.27) --
+	(564.08,444.18) --
+	(572.66,444.18);
 \definecolor{drawColor}{RGB}{253,231,37}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.45) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.59) --
 	( 49.28,444.64) --
 	( 57.86,444.96) --
-	( 66.44,445.24) --
-	( 75.02,445.24) --
+	( 66.44,445.06) --
+	( 75.02,445.43) --
 	( 83.60,445.66) --
-	( 92.18,446.17) --
-	(100.76,446.82) --
+	( 92.18,445.94) --
+	(100.76,446.63) --
 	(109.34,447.52) --
-	(117.92,448.03) --
+	(117.92,448.07) --
 	(126.50,448.72) --
-	(135.08,449.42) --
-	(143.66,451.92) --
-	(152.24,452.20) --
-	(160.82,453.83) --
-	(169.40,456.10) --
-	(177.98,458.74) --
-	(186.56,461.25) --
-	(195.14,465.65) --
-	(203.72,468.81) --
-	(212.30,473.87) --
-	(220.88,478.18) --
-	(229.46,485.97) --
-	(238.04,492.05) --
-	(246.62,498.96) --
-	(255.20,504.99) --
-	(263.78,510.42) --
-	(272.36,518.82) --
-	(280.94,527.68) --
-	(289.52,527.35) --
-	(298.10,536.86) --
-	(306.68,535.19) --
-	(315.26,535.84) --
-	(323.84,528.93) --
-	(332.42,525.96) --
-	(341.00,518.45) --
-	(349.58,511.67) --
-	(358.16,501.05) --
-	(366.74,495.11) --
-	(375.32,485.46) --
-	(383.90,479.90) --
-	(392.48,473.12) --
-	(401.06,469.51) --
-	(409.64,463.75) --
-	(418.22,460.00) --
-	(426.80,455.82) --
-	(435.38,452.94) --
-	(443.96,451.74) --
-	(452.54,450.72) --
-	(461.12,448.21) --
-	(469.70,447.28) --
-	(478.28,447.01) --
-	(486.86,446.22) --
-	(495.44,446.12) --
-	(504.02,445.94) --
-	(512.60,445.06) --
-	(521.18,444.55) --
-	(529.76,444.64) --
-	(538.34,444.45) --
-	(546.92,444.64) --
-	(555.50,444.13) --
+	(135.08,448.86) --
+	(143.66,451.37) --
+	(152.24,452.67) --
+	(160.82,453.36) --
+	(169.40,456.19) --
+	(177.98,458.42) --
+	(186.56,461.06) --
+	(195.14,464.63) --
+	(203.72,468.86) --
+	(212.30,473.91) --
+	(220.88,477.02) --
+	(229.46,484.58) --
+	(238.04,490.71) --
+	(246.62,499.10) --
+	(255.20,502.72) --
+	(263.78,510.10) --
+	(272.36,515.99) --
+	(280.94,525.82) --
+	(289.52,528.05) --
+	(298.10,535.05) --
+	(306.68,536.49) --
+	(315.26,534.03) --
+	(323.84,531.90) --
+	(332.42,526.43) --
+	(341.00,519.75) --
+	(349.58,513.62) --
+	(358.16,503.79) --
+	(366.74,497.11) --
+	(375.32,485.09) --
+	(383.90,481.80) --
+	(392.48,476.19) --
+	(401.06,467.00) --
+	(409.64,465.65) --
+	(418.22,459.25) --
+	(426.80,457.12) --
+	(435.38,454.20) --
+	(443.96,452.16) --
+	(452.54,451.13) --
+	(461.12,448.91) --
+	(469.70,447.79) --
+	(478.28,447.24) --
+	(486.86,446.54) --
+	(495.44,446.54) --
+	(504.02,445.85) --
+	(512.60,444.83) --
+	(521.18,444.78) --
+	(529.76,444.59) --
+	(538.34,444.73) --
+	(546.92,444.59) --
+	(555.50,444.27) --
 	(564.08,444.13) --
-	(572.66,444.04);
+	(572.66,444.27);
 \definecolor{drawColor}{RGB}{68,1,84}
@@
 	(564.08,444.13);
-\definecolor{drawColor}{RGB}{59,82,139}
+\definecolor{drawColor}{RGB}{49,104,142}
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.73) --
-	( 49.28,444.36) --
-	( 57.86,445.20) --
-	( 66.44,445.52) --
-	( 75.02,445.29) --
+	( 49.28,444.32) --
+	( 57.86,445.24) --
+	( 66.44,445.43) --
+	( 75.02,445.34) --
 	( 83.60,446.40) --
-	( 92.18,446.45) --
+	( 92.18,446.36) --
+	(100.76,446.96) --
+	(109.34,447.47) --
+	(117.92,447.98) --
+	(126.50,449.33) --
+	(135.08,450.11) --
+	(143.66,450.62) --
+	(152.24,453.22) --
+	(160.82,455.68) --
+	(169.40,457.26) --
+	(177.98,460.23) --
+	(186.56,461.71) --
+	(195.14,466.91) --
+	(203.72,473.36) --
+	(212.30,477.16) --
+	(220.88,481.06) --
+	(229.46,489.08) --
+	(238.04,495.85) --
+	(246.62,499.43) --
+	(255.20,513.81) --
+	(263.78,516.45) --
+	(272.36,522.48) --
+	(280.94,528.37) --
+	(289.52,533.06) --
+	(298.10,538.81) --
+	(306.68,536.49) --
+	(315.26,530.69) --
+	(323.84,531.06) --
+	(332.42,525.59) --
+	(341.00,515.76) --
+	(349.58,506.52) --
+	(358.16,496.69) --
+	(366.74,490.98) --
+	(375.32,481.52) --
+	(383.90,475.16) --
+	(392.48,469.92) --
+	(401.06,465.84) --
+	(409.64,461.57) --
+	(418.22,457.07) --
+	(426.80,455.50) --
+	(435.38,452.34) --
+	(443.96,450.35) --
+	(452.54,449.88) --
+	(461.12,448.03) --
+	(469.70,446.96) --
+	(478.28,446.82) --
+	(486.86,445.61) --
+	(495.44,445.06) --
+	(504.02,445.75) --
+	(512.60,445.01) --
+	(521.18,444.64) --
+	(529.76,444.45) --
+	(538.34,444.59) --
+	(546.92,444.32) --
+	(555.50,444.32) --
+	(564.08,443.99) --
+	(572.66,444.08);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.55) --
+	( 49.28,444.73) --
+	( 57.86,445.06) --
+	( 66.44,445.38) --
+	( 75.02,445.48) --
+	( 83.60,446.50) --
+	( 92.18,446.50) --
 	(100.76,446.73) --
-	(109.34,447.42) --
-	(117.92,448.26) --
-	(126.50,449.05) --
-	(135.08,450.16) --
-	(143.66,451.18) --
-	(152.24,453.04) --
-	(160.82,455.82) --
+	(109.34,447.75) --
+	(117.92,448.21) --
+	(126.50,449.23) --
+	(135.08,449.98) --
+	(143.66,451.00) --
+	(152.24,453.55) --
+	(160.82,455.17) --
 	(169.40,457.35) --
-	(177.98,460.09) --
-	(186.56,462.50) --
-	(195.14,466.72) --
-	(203.72,473.36) --
-	(212.30,477.76) --
-	(220.88,480.96) --
-	(229.46,487.69) --
-	(238.04,494.93) --
-	(246.62,500.08) --
-	(255.20,512.04) --
-	(263.78,514.78) --
-	(272.36,523.27) --
-	(280.94,527.49) --
-	(289.52,534.03) --
-	(298.10,538.58) --
-	(306.68,535.15) --
-	(315.26,529.67) --
+	(177.98,460.46) --
+	(186.56,462.92) --
+	(195.14,466.81) --
+	(203.72,473.22) --
+	(212.30,476.23) --
+	(220.88,482.45) --
+	(229.46,489.31) --
+	(238.04,494.65) --
+	(246.62,502.58) --
+	(255.20,510.47) --
+	(263.78,519.00) --
+	(272.36,520.44) --
+	(280.94,531.44) --
+	(289.52,531.44) --
+	(298.10,539.83) --
+	(306.68,535.10) --
+	(315.26,530.93) --
 	(323.84,530.55) --
-	(332.42,527.35) --
-	(341.00,514.74) --
-	(349.58,507.64) --
-	(358.16,497.25) --
-	(366.74,493.30) --
-	(375.32,482.45) --
-	(383.90,472.89) --
-	(392.48,470.80) --
-	(401.06,466.03) --
-	(409.64,461.71) --
-	(418.22,455.77) --
-	(426.80,456.38) --
-	(435.38,452.29) --
-	(443.96,450.67) --
-	(452.54,449.56) --
-	(461.12,448.82) --
+	(332.42,523.50) --
+	(341.00,514.50) --
+	(349.58,508.47) --
+	(358.16,499.66) --
+	(366.74,488.57) --
+	(375.32,481.47) --
+	(383.90,475.44) --
+	(392.48,468.35) --
+	(401.06,464.82) --
+	(409.64,459.90) --
+	(418.22,457.68) --
+	(426.80,454.99) --
+	(435.38,451.92) --
+	(443.96,450.62) --
+	(452.54,448.95) --
+	(461.12,448.03) --
+	(469.70,447.89) --
+	(478.28,447.15) --
+	(486.86,445.80) --
+	(495.44,445.20) --
+	(504.02,445.48) --
+	(512.60,444.96) --
+	(521.18,444.36) --
+	(529.76,444.69) --
+	(538.34,444.27) --
+	(546.92,444.41) --
+	(555.50,444.41) --
+	(564.08,444.04) --
+	(572.66,444.22);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.18) --
+	( 49.28,444.78) --
+	( 57.86,445.38) --
+	( 66.44,445.20) --
+	( 75.02,445.52) --
+	( 83.60,446.36) --
+	( 92.18,446.36) --
+	(100.76,446.96) --
+	(109.34,447.56) --
+	(117.92,448.21) --
+	(126.50,449.60) --
+	(135.08,450.21) --
+	(143.66,451.51) --
+	(152.24,452.71) --
+	(160.82,454.43) --
+	(169.40,459.16) --
+	(177.98,459.39) --
+	(186.56,463.94) --
+	(195.14,466.91) --
+	(203.72,472.71) --
+	(212.30,477.30) --
+	(220.88,480.41) --
+	(229.46,489.17) --
+	(238.04,496.55) --
+	(246.62,503.74) --
+	(255.20,506.06) --
+	(263.78,519.37) --
+	(272.36,523.87) --
+	(280.94,528.24) --
+	(289.52,531.81) --
+	(298.10,535.33) --
+	(306.68,538.58) --
+	(315.26,531.99) --
+	(323.84,531.85) --
+	(332.42,520.63) --
+	(341.00,515.52) --
+	(349.58,507.92) --
+	(358.16,500.73) --
+	(366.74,489.73) --
+	(375.32,482.49) --
+	(383.90,473.63) --
+	(392.48,471.96) --
+	(401.06,465.56) --
+	(409.64,460.51) --
+	(418.22,456.98) --
+	(426.80,454.47) --
+	(435.38,451.83) --
+	(443.96,450.76) --
+	(452.54,448.72) --
+	(461.12,448.12) --
 	(469.70,447.52) --
-	(478.28,447.10) --
-	(486.86,445.85) --
-	(495.44,445.24) --
-	(504.02,445.43) --
-	(512.60,445.48) --
-	(521.18,444.73) --
-	(529.76,444.13) --
-	(538.34,444.73) --
+	(478.28,446.82) --
+	(486.86,446.03) --
+	(495.44,445.43) --
+	(504.02,445.24) --
+	(512.60,445.10) --
+	(521.18,444.78) --
+	(529.76,444.50) --
+	(538.34,444.45) --
 	(546.92,444.32) --
 	(555.50,444.08) --
-	(564.08,444.22);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.64) --
-	( 49.28,444.55) --
-	( 57.86,445.29) --
-	( 66.44,445.57) --
-	( 75.02,445.48) --
-	( 83.60,446.12) --
-	( 92.18,446.26) --
-	(100.76,447.24) --
-	(109.34,447.52) --
-	(117.92,448.12) --
-	(126.50,449.42) --
-	(135.08,449.93) --
-	(143.66,451.13) --
-	(152.24,453.41) --
-	(160.82,455.22) --
-	(169.40,457.35) --
-	(177.98,460.37) --
-	(186.56,463.85) --
-	(195.14,466.17) --
-	(203.72,474.05) --
-	(212.30,476.46) --
-	(220.88,481.75) --
-	(229.46,488.94) --
-	(238.04,495.58) --
-	(246.62,501.33) --
-	(255.20,511.67) --
-	(263.78,519.24) --
-	(272.36,521.93) --
-	(280.94,528.61) --
-	(289.52,534.27) --
-	(298.10,536.77) --
-	(306.68,534.96) --
-	(315.26,533.06) --
-	(323.84,528.61) --
-	(332.42,522.95) --
-	(341.00,514.36) --
-	(349.58,509.26) --
-	(358.16,497.71) --
-	(366.74,490.47) --
-	(375.32,481.33) --
-	(383.90,474.98) --
-	(392.48,467.42) --
-	(401.06,464.96) --
-	(409.64,460.69) --
-	(418.22,457.91) --
-	(426.80,454.47) --
-	(435.38,452.29) --
-	(443.96,450.62) --
-	(452.54,449.46) --
-	(461.12,448.12) --
-	(469.70,447.70) --
-	(478.28,446.73) --
-	(486.86,446.50) --
-	(495.44,445.01) --
-	(504.02,445.24) --
-	(512.60,444.78) --
-	(521.18,444.45) --
-	(529.76,444.55) --
-	(538.34,444.27) --
-	(546.92,444.45) --
-	(555.50,444.32) --
-	(564.08,444.08) --
-	(572.66,444.13);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.41) --
-	( 49.28,444.87) --
-	( 57.86,445.01) --
-	( 66.44,445.43) --
-	( 75.02,445.38) --
-	( 83.60,446.40) --
-	( 92.18,446.63) --
-	(100.76,446.96) --
-	(109.34,447.42) --
-	(117.92,447.70) --
-	(126.50,449.56) --
-	(135.08,450.58) --
-	(143.66,450.86) --
-	(152.24,453.69) --
-	(160.82,454.29) --
-	(169.40,459.02) --
-	(177.98,459.62) --
-	(186.56,463.34) --
-	(195.14,466.77) --
-	(203.72,472.66) --
-	(212.30,475.63) --
-	(220.88,482.77) --
-	(229.46,489.08) --
-	(238.04,493.54) --
-	(246.62,503.28) --
-	(255.20,506.20) --
-	(263.78,518.86) --
-	(272.36,521.74) --
-	(280.94,527.86) --
-	(289.52,533.01) --
-	(298.10,537.93) --
-	(306.68,536.03) --
-	(315.26,529.44) --
-	(323.84,530.46) --
-	(332.42,525.50) --
-	(341.00,515.01) --
-	(349.58,506.80) --
-	(358.16,500.45) --
-	(366.74,491.87) --
-	(375.32,482.31) --
-	(383.90,476.37) --
-	(392.48,469.64) --
-	(401.06,464.96) --
-	(409.64,460.55) --
-	(418.22,457.49) --
-	(426.80,454.89) --
-	(435.38,454.38) --
-	(443.96,450.72) --
-	(452.54,448.91) --
-	(461.12,447.79) --
-	(469.70,448.07) --
-	(478.28,446.87) --
-	(486.86,445.99) --
-	(495.44,445.24) --
-	(504.02,445.34) --
-	(512.60,444.73) --
-	(521.18,444.69) --
-	(529.76,444.41) --
-	(538.34,444.41) --
-	(546.92,444.27) --
-	(555.50,444.18) --
-	(564.08,444.32) --
+	(564.08,444.13) --
 	(572.66,444.08);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.70,444.27) --
-	( 49.28,444.55) --
-	( 57.86,445.38) --
-	( 66.44,445.24) --
-	( 75.02,445.61) --
-	( 83.60,446.31) --
-	( 92.18,446.40) --
-	(100.76,446.73) --
-	(109.34,447.61) --
-	(117.92,448.40) --
-	(126.50,449.37) --
-	(135.08,450.58) --
-	(143.66,451.18) --
-	(152.24,452.90) --
-	(160.82,454.06) --
-	(169.40,458.65) --
-	(177.98,459.72) --
-	(186.56,463.52) --
-	(195.14,466.26) --
-	(203.72,472.15) --
-	(212.30,476.83) --
-	(220.88,479.94) --
-	(229.46,488.71) --
-	(238.04,494.46) --
-	(246.62,501.93) --
-	(255.20,506.01) --
-	(263.78,517.43) --
-	(272.36,523.50) --
-	(280.94,527.35) --
-	(289.52,533.38) --
-	(298.10,535.66) --
-	(306.68,535.52) --
-	(315.26,533.99) --
-	(323.84,530.69) --
-	(332.42,524.94) --
-	(341.00,516.50) --
-	(349.58,506.43) --
-	(358.16,501.70) --
-	(366.74,493.72) --
-	(375.32,481.15) --
-	(383.90,474.14) --
-	(392.48,470.76) --
-	(401.06,465.28) --
-	(409.64,461.76) --
-	(418.22,457.40) --
-	(426.80,455.82) --
-	(435.38,452.71) --
-	(443.96,450.02) --
-	(452.54,448.54) --
-	(461.12,448.86) --
-	(469.70,448.21) --
-	(478.28,446.54) --
-	(486.86,446.08) --
-	(495.44,445.29) --
-	(504.02,445.10) --
-	(512.60,445.06) --
-	(521.18,444.78) --
-	(529.76,444.50) --
-	(538.34,444.50) --
-	(546.92,444.27) --
-	(555.50,444.41) --
-	(564.08,444.08) --
-	(572.66,444.18);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[] ( 45.09,453.59) rectangle (121.42,556.81);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
-
-\path[] ( 45.09,453.59) rectangle (121.42,556.81);
+\path[] ( 42.63,462.26) rectangle (123.87,548.14);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+
+\path[] ( 42.63,462.26) rectangle (123.87,548.14);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 50.59,528.47) rectangle ( 67.93,545.81);
+\path[fill=fillColor] ( 48.13,519.79) rectangle ( 65.48,537.14);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,537.14) -- ( 66.20,537.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.87,528.47) -- ( 63.74,528.47);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 50.59,511.12) rectangle ( 67.93,528.47);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,519.79) -- ( 66.20,519.79);
+\path[fill=fillColor] ( 48.13,502.45) rectangle ( 65.48,519.79);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.87,511.12) -- ( 63.74,511.12);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 50.59,493.78) rectangle ( 67.93,511.12);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,502.45) -- ( 66.20,502.45);
+\path[fill=fillColor] ( 48.13,485.11) rectangle ( 65.48,502.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.87,493.78) -- ( 63.74,493.78);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 50.59,476.43) rectangle ( 67.93,493.78);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,485.11) -- ( 66.20,485.11);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 50.59,459.09) rectangle ( 67.93,476.43);
+\path[fill=fillColor] ( 48.13,467.76) rectangle ( 65.48,485.11);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.32,467.76) -- ( 66.20,467.76);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.87,476.43) -- ( 63.74,476.43);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,534.11) {$\rho=0$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 70.98,525.44) {$\rho=0$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,516.76) {$\rho=0.2$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 70.98,508.09) {$\rho=0.25$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,499.42) {$\rho=0.4$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 70.98,490.75) {$\rho=0.5$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,482.07) {$\rho=0.6$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 73.43,464.73) {$\rho=0.8$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 70.98,473.40) {$\rho=0.75$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,356.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,356.89) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,358.01) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.20) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,357.80) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.23) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.98) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,356.51) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,356.56) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,358.10) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.21) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.77) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,357.86) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.16) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,358.00) circle (  2.50);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.72) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.59) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.48) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.72) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.49) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,354.92) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,356.93) circle (  2.50);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,356.64) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.22) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,357.59) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.23) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,357.86) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.20) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.90) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.88) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.66) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.56) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.51) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.78) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.07) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,357.24) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,355.42) circle (  2.50);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,357.11) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.46) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.71) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.65) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.32) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.90) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.54) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,355.14) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,356.97) circle (  2.50);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,356.32) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.12) circle (  2.50);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.37) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.66) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.42) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.60) circle (  2.50);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.20) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.17) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.89) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.89) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.65) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.57) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.40) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.89) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.09) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,357.43) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,355.80) circle (  2.50);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,356.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.51) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,357.35) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.48) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.60) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,358.14) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.09) circle (  2.50);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.88) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.62) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.90) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.61) circle (  2.50);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.38) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.37) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,359.12) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,355.67) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,356.17) circle (  2.50);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,357.29) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.65) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,357.48) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.69) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.34) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,358.05) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.17) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.90) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.90) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.55) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.74) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.36) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.69) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.30) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,357.14) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,357.74) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.25) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,358.04) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.31) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,357.74) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,354.33) circle (  2.50);
 \definecolor{drawColor}{RGB}{253,231,37}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,358.36) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.14) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,357.19) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.54) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.47) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,358.07) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.17) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.84) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.95) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.55) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.66) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.50) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.80) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,357.56) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,358.55) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,356.45) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,357.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,357.12) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,357.17) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,357.73) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,357.54) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,358.09) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,358.01) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,357.91) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,357.98) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,357.53) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,357.67) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,358.42) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,357.88) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,358.05) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,356.27) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,358.69) circle (  2.50);
 \definecolor{drawColor}{RGB}{68,1,84}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,356.77) --
-	( 29.46,356.84) --
-	( 31.41,356.90) --
-	( 33.37,356.97) --
-	( 35.32,357.03) --
-	( 37.28,357.09) --
-	( 39.24,357.15) --
-	( 41.19,357.21) --
-	( 43.15,357.27) --
-	( 45.11,357.32) --
-	( 47.06,357.37) --
-	( 49.02,357.42) --
-	( 50.98,357.47) --
-	( 52.93,357.51) --
-	( 54.89,357.56) --
-	( 56.85,357.60) --
-	( 58.80,357.64) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,356.48) --
+	( 29.46,356.58) --
+	( 31.41,356.67) --
+	( 33.37,356.76) --
+	( 35.32,356.84) --
+	( 37.28,356.92) --
+	( 39.24,357.00) --
+	( 41.19,357.08) --
+	( 43.15,357.15) --
+	( 45.11,357.22) --
+	( 47.06,357.28) --
+	( 49.02,357.35) --
+	( 50.98,357.41) --
+	( 52.93,357.47) --
+	( 54.89,357.52) --
+	( 56.85,357.57) --
+	( 58.80,357.62) --
 	( 60.76,357.67) --
@@
 	( 64.67,357.74) --
-	( 66.63,357.77) --
-	( 68.59,357.79) --
-	( 70.54,357.82) --
-	( 72.50,357.84) --
-	( 74.46,357.86) --
-	( 76.41,357.88) --
-	( 78.37,357.89) --
-	( 80.33,357.91) --
-	( 82.28,357.91) --
-	( 84.24,357.92) --
-	( 86.20,357.92) --
-	( 88.15,357.92) --
-	( 90.11,357.91) --
-	( 92.07,357.91) --
+	( 66.63,357.78) --
+	( 68.59,357.81) --
+	( 70.54,357.84) --
+	( 72.50,357.86) --
+	( 74.46,357.88) --
+	( 76.41,357.90) --
+	( 78.37,357.92) --
+	( 80.33,357.94) --
+	( 82.28,357.94) --
+	( 84.24,357.95) --
+	( 86.20,357.94) --
+	( 88.15,357.94) --
+	( 90.11,357.93) --
+	( 92.07,357.92) --
 	( 94.02,357.91) --
-	( 95.98,357.90) --
+	( 95.98,357.91) --
 	( 97.94,357.90) --
@@
 	(105.76,357.91) --
-	(107.72,357.91) --
-	(109.67,357.91) --
-	(111.63,357.91) --
-	(113.59,357.91) --
-	(115.54,357.91) --
-	(117.50,357.91) --
-	(119.46,357.90) --
-	(121.41,357.90) --
-	(123.37,357.91) --
-	(125.33,357.92) --
-	(127.28,357.93) --
+	(107.72,357.90) --
+	(109.67,357.90) --
+	(111.63,357.90) --
+	(113.59,357.89) --
+	(115.54,357.89) --
+	(117.50,357.89) --
+	(119.46,357.89) --
+	(121.41,357.89) --
+	(123.37,357.89) --
+	(125.33,357.91) --
+	(127.28,357.92) --
 	(129.24,357.94) --
-	(131.20,357.94) --
-	(133.15,357.95) --
-	(135.11,357.95) --
-	(137.07,357.94) --
-	(139.02,357.92) --
-	(140.98,357.88) --
-	(142.94,357.84) --
-	(144.89,357.80) --
-	(146.85,357.75) --
-	(148.81,357.70) --
-	(150.76,357.65) --
-	(152.72,357.59) --
-	(154.68,357.53) --
-	(156.63,357.46) --
-	(158.59,357.39) --
-	(160.55,357.32) --
-	(162.50,357.24) --
-	(164.46,357.16) --
-	(166.42,357.07) --
-	(168.37,356.98) --
-	(170.33,356.88) --
-	(172.28,356.78) --
-	(174.24,356.68) --
-	(176.20,356.57) --
-	(178.15,356.46) --
-	(180.11,356.34) --
-	(182.07,356.22);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,356.74) --
-	( 29.46,356.81) --
-	( 31.41,356.88) --
-	( 33.37,356.94) --
-	( 35.32,357.00) --
-	( 37.28,357.06) --
-	( 39.24,357.12) --
-	( 41.19,357.18) --
-	( 43.15,357.24) --
-	( 45.11,357.29) --
-	( 47.06,357.34) --
-	( 49.02,357.39) --
-	( 50.98,357.44) --
-	( 52.93,357.48) --
-	( 54.89,357.53) --
-	( 56.85,357.57) --
-	( 58.80,357.61) --
-	( 60.76,357.64) --
-	( 62.72,357.68) --
+	(131.20,357.95) --
+	(133.15,357.96) --
+	(135.11,357.96) --
+	(137.07,357.95) --
+	(139.02,357.94) --
+	(140.98,357.91) --
+	(142.94,357.87) --
+	(144.89,357.83) --
+	(146.85,357.79) --
+	(148.81,357.75) --
+	(150.76,357.70) --
+	(152.72,357.64) --
+	(154.68,357.59) --
+	(156.63,357.53) --
+	(158.59,357.46) --
+	(160.55,357.39) --
+	(162.50,357.32) --
+	(164.46,357.24) --
+	(166.42,357.16) --
+	(168.37,357.07) --
+	(170.33,356.98) --
+	(172.28,356.88) --
+	(174.24,356.78) --
+	(176.20,356.68) --
+	(178.15,356.57) --
+	(180.11,356.46) --
+	(182.07,356.34);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,356.47) --
+	( 29.46,356.56) --
+	( 31.41,356.65) --
+	( 33.37,356.73) --
+	( 35.32,356.81) --
+	( 37.28,356.89) --
+	( 39.24,356.97) --
+	( 41.19,357.04) --
+	( 43.15,357.12) --
+	( 45.11,357.18) --
+	( 47.06,357.25) --
+	( 49.02,357.31) --
+	( 50.98,357.37) --
+	( 52.93,357.43) --
+	( 54.89,357.48) --
+	( 56.85,357.54) --
+	( 58.80,357.58) --
+	( 60.76,357.63) --
+	( 62.72,357.67) --
 	( 64.67,357.71) --
 	( 66.63,357.74) --
-	( 68.59,357.77) --
-	( 70.54,357.79) --
-	( 72.50,357.82) --
-	( 74.46,357.84) --
-	( 76.41,357.86) --
-	( 78.37,357.88) --
-	( 80.33,357.89) --
-	( 82.28,357.91) --
-	( 84.24,357.91) --
-	( 86.20,357.92) --
-	( 88.15,357.92) --
-	( 90.11,357.92) --
-	( 92.07,357.92) --
-	( 94.02,357.92) --
-	( 95.98,357.91) --
-	( 97.94,357.92) --
-	( 99.89,357.92) --
-	(101.85,357.92) --
-	(103.80,357.92) --
-	(105.76,357.91) --
-	(107.72,357.91) --
-	(109.67,357.90) --
-	(111.63,357.89) --
-	(113.59,357.88) --
-	(115.54,357.87) --
-	(117.50,357.87) --
-	(119.46,357.86) --
-	(121.41,357.87) --
-	(123.37,357.88) --
-	(125.33,357.90) --
-	(127.28,357.93) --
-	(129.24,357.96) --
-	(131.20,357.99) --
-	(133.15,358.01) --
-	(135.11,358.03) --
-	(137.07,358.03) --
-	(139.02,358.03) --
-	(140.98,358.00) --
-	(142.94,357.97) --
-	(144.89,357.93) --
-	(146.85,357.89) --
-	(148.81,357.85) --
-	(150.76,357.80) --
-	(152.72,357.75) --
-	(154.68,357.68) --
-	(156.63,357.62) --
-	(158.59,357.54) --
-	(160.55,357.45) --
-	(162.50,357.36) --
-	(164.46,357.26) --
-	(166.42,357.15) --
-	(168.37,357.03) --
-	(170.33,356.91) --
-	(172.28,356.78) --
-	(174.24,356.64) --
-	(176.20,356.49) --
-	(178.15,356.34) --
-	(180.11,356.18) --
-	(182.07,356.02);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,357.12) --
-	( 29.46,357.15) --
-	( 31.41,357.19) --
-	( 33.37,357.22) --
-	( 35.32,357.26) --
-	( 37.28,357.29) --
-	( 39.24,357.33) --
-	( 41.19,357.36) --
-	( 43.15,357.40) --
-	( 45.11,357.43) --
-	( 47.06,357.46) --
-	( 49.02,357.50) --
-	( 50.98,357.53) --
-	( 52.93,357.56) --
-	( 54.89,357.59) --
-	( 56.85,357.61) --
-	( 58.80,357.64) --
-	( 60.76,357.67) --
-	( 62.72,357.69) --
-	( 64.67,357.72) --
-	( 66.63,357.75) --
-	( 68.59,357.77) --
-	( 70.54,357.80) --
-	( 72.50,357.82) --
-	( 74.46,357.84) --
-	( 76.41,357.86) --
-	( 78.37,357.88) --
-	( 80.33,357.89) --
-	( 82.28,357.90) --
-	( 84.24,357.91) --
-	( 86.20,357.92) --
-	( 88.15,357.92) --
+	( 68.59,357.78) --
+	( 70.54,357.81) --
+	( 72.50,357.83) --
+	( 74.46,357.86) --
+	( 76.41,357.88) --
+	( 78.37,357.90) --
+	( 80.33,357.92) --
+	( 82.28,357.93) --
+	( 84.24,357.93) --
+	( 86.20,357.94) --
+	( 88.15,357.94) --
 	( 90.11,357.93) --
 	( 92.07,357.93) --
-	( 94.02,357.93) --
-	( 95.98,357.93) --
-	( 97.94,357.93) --
-	( 99.89,357.94) --
-	(101.85,357.93) --
-	(103.80,357.93) --
-	(105.76,357.92) --
-	(107.72,357.91) --
-	(109.67,357.89) --
-	(111.63,357.88) --
-	(113.59,357.86) --
-	(115.54,357.85) --
-	(117.50,357.84) --
-	(119.46,357.84) --
-	(121.41,357.84) --
-	(123.37,357.85) --
-	(125.33,357.87) --
-	(127.28,357.89) --
-	(129.24,357.92) --
-	(131.20,357.95) --
-	(133.15,357.97) --
-	(135.11,357.98) --
-	(137.07,357.98) --
-	(139.02,357.97) --
-	(140.98,357.95) --
-	(142.94,357.91) --
-	(144.89,357.87) --
-	(146.85,357.83) --
-	(148.81,357.78) --
-	(150.76,357.73) --
-	(152.72,357.68) --
-	(154.68,357.62) --
-	(156.63,357.55) --
-	(158.59,357.47) --
-	(160.55,357.39) --
-	(162.50,357.30) --
-	(164.46,357.21) --
-	(166.42,357.11) --
-	(168.37,357.00) --
-	(170.33,356.89) --
-	(172.28,356.77) --
-	(174.24,356.65) --
-	(176.20,356.52) --
-	(178.15,356.38) --
-	(180.11,356.24) --
-	(182.07,356.10);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,357.34) --
-	( 29.46,357.36) --
-	( 31.41,357.39) --
-	( 33.37,357.41) --
-	( 35.32,357.43) --
-	( 37.28,357.45) --
-	( 39.24,357.48) --
-	( 41.19,357.50) --
-	( 43.15,357.52) --
-	( 45.11,357.55) --
-	( 47.06,357.57) --
-	( 49.02,357.59) --
-	( 50.98,357.61) --
-	( 52.93,357.63) --
-	( 54.89,357.65) --
-	( 56.85,357.67) --
-	( 58.80,357.69) --
-	( 60.76,357.71) --
-	( 62.72,357.73) --
-	( 64.67,357.75) --
-	( 66.63,357.76) --
-	( 68.59,357.78) --
-	( 70.54,357.80) --
-	( 72.50,357.82) --
-	( 74.46,357.83) --
-	( 76.41,357.85) --
-	( 78.37,357.86) --
-	( 80.33,357.87) --
-	( 82.28,357.88) --
-	( 84.24,357.89) --
-	( 86.20,357.89) --
-	( 88.15,357.90) --
-	( 90.11,357.90) --
-	( 92.07,357.90) --
-	( 94.02,357.90) --
-	( 95.98,357.91) --
-	( 97.94,357.91) --
-	( 99.89,357.91) --
-	(101.85,357.91) --
-	(103.80,357.91) --
-	(105.76,357.90) --
-	(107.72,357.90) --
-	(109.67,357.89) --
-	(111.63,357.88) --
-	(113.59,357.87) --
-	(115.54,357.86) --
-	(117.50,357.85) --
-	(119.46,357.85) --
-	(121.41,357.85) --
-	(123.37,357.85) --
-	(125.33,357.86) --
-	(127.28,357.87) --
-	(129.24,357.87) --
-	(131.20,357.88) --
-	(133.15,357.88) --
-	(135.11,357.89) --
-	(137.07,357.89) --
-	(139.02,357.89) --
-	(140.98,357.89) --
-	(142.94,357.88) --
-	(144.89,357.87) --
-	(146.85,357.87) --
-	(148.81,357.86) --
-	(150.76,357.85) --
-	(152.72,357.85) --
-	(154.68,357.84) --
-	(156.63,357.83) --
-	(158.59,357.82) --
-	(160.55,357.80) --
-	(162.50,357.79) --
-	(164.46,357.77) --
-	(166.42,357.75) --
-	(168.37,357.74) --
-	(170.33,357.72) --
-	(172.28,357.70) --
-	(174.24,357.67) --
-	(176.20,357.65) --
-	(178.15,357.63) --
-	(180.11,357.60) --
-	(182.07,357.58);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,357.81) --
-	( 29.46,357.77) --
-	( 31.41,357.74) --
-	( 33.37,357.71) --
-	( 35.32,357.69) --
-	( 37.28,357.66) --
-	( 39.24,357.64) --
-	( 41.19,357.63) --
-	( 43.15,357.62) --
-	( 45.11,357.61) --
-	( 47.06,357.60) --
-	( 49.02,357.59) --
-	( 50.98,357.59) --
-	( 52.93,357.59) --
-	( 54.89,357.59) --
-	( 56.85,357.59) --
-	( 58.80,357.59) --
-	( 60.76,357.60) --
-	( 62.72,357.62) --
-	( 64.67,357.64) --
-	( 66.63,357.67) --
-	( 68.59,357.70) --
-	( 70.54,357.74) --
-	( 72.50,357.77) --
-	( 74.46,357.80) --
-	( 76.41,357.83) --
-	( 78.37,357.85) --
-	( 80.33,357.86) --
-	( 82.28,357.88) --
-	( 84.24,357.89) --
-	( 86.20,357.89) --
-	( 88.15,357.90) --
-	( 90.11,357.90) --
-	( 92.07,357.91) --
-	( 94.02,357.91) --
-	( 95.98,357.91) --
+	( 94.02,357.92) --
+	( 95.98,357.92) --
 	( 97.94,357.92) --
@@
 	(113.59,357.87) --
-	(115.54,357.87) --
-	(117.50,357.86) --
+	(115.54,357.86) --
+	(117.50,357.85) --
 	(119.46,357.85) --
@@
 	(123.37,357.86) --
-	(125.33,357.87) --
-	(127.28,357.88) --
-	(129.24,357.90) --
-	(131.20,357.92) --
-	(133.15,357.93) --
-	(135.11,357.94) --
-	(137.07,357.95) --
-	(139.02,357.95) --
-	(140.98,357.94) --
-	(142.94,357.93) --
-	(144.89,357.92) --
+	(125.33,357.88) --
+	(127.28,357.91) --
+	(129.24,357.94) --
+	(131.20,357.97) --
+	(133.15,357.99) --
+	(135.11,358.01) --
+	(137.07,358.02) --
+	(139.02,358.01) --
+	(140.98,357.99) --
+	(142.94,357.97) --
+	(144.89,357.94) --
 	(146.85,357.91) --
-	(148.81,357.90) --
-	(150.76,357.88) --
-	(152.72,357.87) --
-	(154.68,357.85) --
-	(156.63,357.82) --
-	(158.59,357.79) --
-	(160.55,357.76) --
-	(162.50,357.72) --
-	(164.46,357.68) --
-	(166.42,357.63) --
-	(168.37,357.58) --
-	(170.33,357.52) --
-	(172.28,357.46) --
-	(174.24,357.40) --
-	(176.20,357.34) --
-	(178.15,357.27) --
-	(180.11,357.20) --
-	(182.07,357.12);
+	(148.81,357.87) --
+	(150.76,357.84) --
+	(152.72,357.79) --
+	(154.68,357.74) --
+	(156.63,357.69) --
+	(158.59,357.63) --
+	(160.55,357.56) --
+	(162.50,357.48) --
+	(164.46,357.39) --
+	(166.42,357.30) --
+	(168.37,357.20) --
+	(170.33,357.10) --
+	(172.28,356.99) --
+	(174.24,356.87) --
+	(176.20,356.75) --
+	(178.15,356.63) --
+	(180.11,356.49) --
+	(182.07,356.35);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,357.02) --
+	( 29.46,357.07) --
+	( 31.41,357.12) --
+	( 33.37,357.16) --
+	( 35.32,357.21) --
+	( 37.28,357.25) --
+	( 39.24,357.29) --
+	( 41.19,357.34) --
+	( 43.15,357.38) --
+	( 45.11,357.42) --
+	( 47.06,357.46) --
+	( 49.02,357.49) --
+	( 50.98,357.53) --
+	( 52.93,357.56) --
+	( 54.89,357.60) --
+	( 56.85,357.63) --
+	( 58.80,357.66) --
+	( 60.76,357.69) --
+	( 62.72,357.72) --
+	( 64.67,357.74) --
+	( 66.63,357.77) --
+	( 68.59,357.80) --
+	( 70.54,357.82) --
+	( 72.50,357.84) --
+	( 74.46,357.86) --
+	( 76.41,357.88) --
+	( 78.37,357.90) --
+	( 80.33,357.91) --
+	( 82.28,357.92) --
+	( 84.24,357.92) --
+	( 86.20,357.93) --
+	( 88.15,357.93) --
+	( 90.11,357.93) --
+	( 92.07,357.93) --
+	( 94.02,357.92) --
+	( 95.98,357.92) --
+	( 97.94,357.92) --
+	( 99.89,357.92) --
+	(101.85,357.92) --
+	(103.80,357.91) --
+	(105.76,357.90) --
+	(107.72,357.89) --
+	(109.67,357.87) --
+	(111.63,357.85) --
+	(113.59,357.84) --
+	(115.54,357.83) --
+	(117.50,357.82) --
+	(119.46,357.82) --
+	(121.41,357.82) --
+	(123.37,357.85) --
+	(125.33,357.89) --
+	(127.28,357.93) --
+	(129.24,357.99) --
+	(131.20,358.04) --
+	(133.15,358.08) --
+	(135.11,358.12) --
+	(137.07,358.14) --
+	(139.02,358.14) --
+	(140.98,358.12) --
+	(142.94,358.08) --
+	(144.89,358.04) --
+	(146.85,357.99) --
+	(148.81,357.94) --
+	(150.76,357.89) --
+	(152.72,357.82) --
+	(154.68,357.75) --
+	(156.63,357.66) --
+	(158.59,357.56) --
+	(160.55,357.45) --
+	(162.50,357.33) --
+	(164.46,357.19) --
+	(166.42,357.05) --
+	(168.37,356.89) --
+	(170.33,356.73) --
+	(172.28,356.55) --
+	(174.24,356.37) --
+	(176.20,356.17) --
+	(178.15,355.97) --
+	(180.11,355.75) --
+	(182.07,355.53);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,357.53) --
+	( 29.46,357.52) --
+	( 31.41,357.52) --
+	( 33.37,357.52) --
+	( 35.32,357.52) --
+	( 37.28,357.52) --
+	( 39.24,357.52) --
+	( 41.19,357.53) --
+	( 43.15,357.54) --
+	( 45.11,357.54) --
+	( 47.06,357.55) --
+	( 49.02,357.56) --
+	( 50.98,357.58) --
+	( 52.93,357.59) --
+	( 54.89,357.60) --
+	( 56.85,357.61) --
+	( 58.80,357.62) --
+	( 60.76,357.64) --
+	( 62.72,357.66) --
+	( 64.67,357.69) --
+	( 66.63,357.72) --
+	( 68.59,357.75) --
+	( 70.54,357.78) --
+	( 72.50,357.81) --
+	( 74.46,357.84) --
+	( 76.41,357.86) --
+	( 78.37,357.88) --
+	( 80.33,357.90) --
+	( 82.28,357.91) --
+	( 84.24,357.91) --
+	( 86.20,357.92) --
+	( 88.15,357.91) --
+	( 90.11,357.91) --
+	( 92.07,357.91) --
+	( 94.02,357.91) --
+	( 95.98,357.90) --
+	( 97.94,357.90) --
+	( 99.89,357.90) --
+	(101.85,357.91) --
+	(103.80,357.91) --
+	(105.76,357.90) --
+	(107.72,357.90) --
+	(109.67,357.90) --
+	(111.63,357.90) --
+	(113.59,357.89) --
+	(115.54,357.89) --
+	(117.50,357.89) --
+	(119.46,357.89) --
+	(121.41,357.88) --
+	(123.37,357.88) --
+	(125.33,357.88) --
+	(127.28,357.87) --
+	(129.24,357.86) --
+	(131.20,357.86) --
+	(133.15,357.85) --
+	(135.11,357.84) --
+	(137.07,357.83) --
+	(139.02,357.82) --
+	(140.98,357.82) --
+	(142.94,357.81) --
+	(144.89,357.81) --
+	(146.85,357.80) --
+	(148.81,357.79) --
+	(150.76,357.79) --
+	(152.72,357.78) --
+	(154.68,357.78) --
+	(156.63,357.77) --
+	(158.59,357.77) --
+	(160.55,357.77) --
+	(162.50,357.77) --
+	(164.46,357.78) --
+	(166.42,357.78) --
+	(168.37,357.79) --
+	(170.33,357.79) --
+	(172.28,357.80) --
+	(174.24,357.81) --
+	(176.20,357.81) --
+	(178.15,357.82) --
+	(180.11,357.83) --
+	(182.07,357.84);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,345.69) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.39) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.59) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.70) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.86) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.54) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.69) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,345.80) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.38) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.74) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.59) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.92) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.59) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.70) circle (  2.50);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.45) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,340.23) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,342.59) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.54) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,343.75) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,343.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,344.37) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,346.69) circle (  2.50);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,345.65) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.38) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.55) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.62) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.89) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.75) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.83) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,338.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.85) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.79) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.47) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,340.18) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,342.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.60) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,343.66) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,344.17) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,343.66) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,346.81) circle (  2.50);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,346.15) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.49) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.69) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.60) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.69) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.82) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,338.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.75) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.87) circle (  2.50);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.42) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,344.80) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,342.61) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,343.07) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,342.06) circle (  2.50);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,346.03) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.59) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.12) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.74) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.80) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.66) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.87) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,339.00) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.83) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,342.34) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.86) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,343.44) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,343.43) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,338.93) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,340.60) circle (  2.50);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,346.05) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.74) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.09) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.73) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.62) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.87) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,341.03) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,339.16) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.90) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.83) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,342.50) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.60) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,344.19) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,344.00) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,340.09) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,350.98) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.27) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,345.29) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,346.28) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,345.26) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,347.46) circle (  2.50);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,346.10) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.85) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,346.38) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.65) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.83) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.84) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.72) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,339.02) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.76) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.63) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,342.57) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.24) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,344.52) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,346.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,340.89) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,342.09) circle (  2.50);
 \definecolor{drawColor}{RGB}{253,231,37}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,347.09) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,345.85) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,345.51) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.62) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.79) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,341.14) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,339.03) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.61) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,341.84) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,344.33) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,346.47) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,344.80) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,343.58) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,347.56) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,346.83) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,346.09) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,345.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,345.90) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,343.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,342.85) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,340.97) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,339.20) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,338.76) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,339.67) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,341.90) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,345.11) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,345.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,345.16) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,341.99) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,345.00) circle (  2.50);
 \definecolor{drawColor}{RGB}{68,1,84}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.12) --
-	(222.18,346.10) --
-	(224.13,346.08) --
-	(226.09,346.04) --
-	(228.04,346.00) --
-	(230.00,345.94) --
-	(231.96,345.87) --
-	(233.91,345.78) --
-	(235.87,345.68) --
-	(237.83,345.57) --
-	(239.78,345.45) --
-	(241.74,345.33) --
-	(243.70,345.19) --
-	(245.65,345.05) --
-	(247.61,344.91) --
-	(249.57,344.76) --
-	(251.52,344.60) --
-	(253.48,344.43) --
-	(255.44,344.23) --
-	(257.39,344.01) --
-	(259.35,343.78) --
-	(261.31,343.53) --
-	(263.26,343.28) --
-	(265.22,343.03) --
-	(267.18,342.78) --
-	(269.13,342.54) --
-	(271.09,342.32) --
-	(273.05,342.09) --
-	(275.00,341.83) --
-	(276.96,341.53) --
-	(278.92,341.22) --
-	(280.87,340.89) --
-	(282.83,340.57) --
-	(284.79,340.28) --
-	(286.74,340.01) --
-	(288.70,339.79) --
-	(290.66,339.63) --
-	(292.61,339.54) --
-	(294.57,339.51) --
-	(296.52,339.53) --
-	(298.48,339.59) --
-	(300.44,339.69) --
-	(302.39,339.80) --
-	(304.35,339.94) --
-	(306.31,340.09) --
-	(308.26,340.24) --
-	(310.22,340.38) --
-	(312.18,340.52) --
-	(314.13,340.65) --
-	(316.09,340.81) --
-	(318.05,341.00) --
-	(320.00,341.22) --
-	(321.96,341.45) --
-	(323.92,341.70) --
-	(325.87,341.94) --
-	(327.83,342.18) --
-	(329.79,342.41) --
-	(331.74,342.61) --
-	(333.70,342.79) --
-	(335.66,342.95) --
-	(337.61,343.12) --
-	(339.57,343.29) --
-	(341.53,343.46) --
-	(343.48,343.63) --
-	(345.44,343.80) --
-	(347.40,343.97) --
-	(349.35,344.13) --
-	(351.31,344.30) --
-	(353.27,344.45) --
-	(355.22,344.61) --
-	(357.18,344.76) --
-	(359.14,344.90) --
-	(361.09,345.05) --
-	(363.05,345.19) --
-	(365.00,345.34) --
-	(366.96,345.48) --
-	(368.92,345.61) --
-	(370.87,345.75) --
-	(372.83,345.88) --
-	(374.79,346.02);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.05) --
-	(222.18,346.03) --
-	(224.13,346.02) --
-	(226.09,345.99) --
-	(228.04,345.95) --
-	(230.00,345.90) --
-	(231.96,345.83) --
-	(233.91,345.76) --
-	(235.87,345.67) --
-	(237.83,345.57) --
-	(239.78,345.46) --
-	(241.74,345.34) --
-	(243.70,345.21) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.20) --
+	(222.18,346.18) --
+	(224.13,346.15) --
+	(226.09,346.11) --
+	(228.04,346.06) --
+	(230.00,346.00) --
+	(231.96,345.92) --
+	(233.91,345.83) --
+	(235.87,345.73) --
+	(237.83,345.61) --
+	(239.78,345.49) --
+	(241.74,345.36) --
+	(243.70,345.23) --
 	(245.65,345.08) --
 	(247.61,344.94) --
-	(249.57,344.80) --
-	(251.52,344.65) --
-	(253.48,344.48) --
-	(255.44,344.29) --
-	(257.39,344.08) --
+	(249.57,344.78) --
+	(251.52,344.63) --
+	(253.48,344.45) --
+	(255.44,344.25) --
+	(257.39,344.03) --
+	(259.35,343.80) --
+	(261.31,343.55) --
+	(263.26,343.30) --
+	(265.22,343.05) --
+	(267.18,342.80) --
+	(269.13,342.56) --
+	(271.09,342.33) --
+	(273.05,342.11) --
+	(275.00,341.84) --
+	(276.96,341.55) --
+	(278.92,341.23) --
+	(280.87,340.90) --
+	(282.83,340.59) --
+	(284.79,340.29) --
+	(286.74,340.02) --
+	(288.70,339.80) --
+	(290.66,339.64) --
+	(292.61,339.55) --
+	(294.57,339.52) --
+	(296.52,339.54) --
+	(298.48,339.60) --
+	(300.44,339.70) --
+	(302.39,339.81) --
+	(304.35,339.95) --
+	(306.31,340.10) --
+	(308.26,340.25) --
+	(310.22,340.39) --
+	(312.18,340.53) --
+	(314.13,340.66) --
+	(316.09,340.82) --
+	(318.05,341.01) --
+	(320.00,341.23) --
+	(321.96,341.46) --
+	(323.92,341.70) --
+	(325.87,341.95) --
+	(327.83,342.18) --
+	(329.79,342.40) --
+	(331.74,342.60) --
+	(333.70,342.77) --
+	(335.66,342.93) --
+	(337.61,343.09) --
+	(339.57,343.26) --
+	(341.53,343.42) --
+	(343.48,343.58) --
+	(345.44,343.75) --
+	(347.40,343.91) --
+	(349.35,344.07) --
+	(351.31,344.22) --
+	(353.27,344.38) --
+	(355.22,344.52) --
+	(357.18,344.67) --
+	(359.14,344.81) --
+	(361.09,344.95) --
+	(363.05,345.08) --
+	(365.00,345.22) --
+	(366.96,345.35) --
+	(368.92,345.48) --
+	(370.87,345.61) --
+	(372.83,345.74) --
+	(374.79,345.86);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.45) --
+	(222.18,346.40) --
+	(224.13,346.36) --
+	(226.09,346.30) --
+	(228.04,346.23) --
+	(230.00,346.16) --
+	(231.96,346.07) --
+	(233.91,345.96) --
+	(235.87,345.85) --
+	(237.83,345.73) --
+	(239.78,345.60) --
+	(241.74,345.46) --
+	(243.70,345.32) --
+	(245.65,345.17) --
+	(247.61,345.01) --
+	(249.57,344.85) --
+	(251.52,344.69) --
+	(253.48,344.51) --
+	(255.44,344.31) --
+	(257.39,344.09) --
 	(259.35,343.86) --
 	(261.31,343.62) --
-	(263.26,343.38) --
-	(265.22,343.14) --
-	(267.18,342.90) --
-	(269.13,342.67) --
-	(271.09,342.45) --
-	(273.05,342.23) --
-	(275.00,341.96) --
-	(276.96,341.66) --
-	(278.92,341.34) --
-	(280.87,341.01) --
-	(282.83,340.69) --
-	(284.79,340.38) --
-	(286.74,340.11) --
-	(288.70,339.88) --
-	(290.66,339.71) --
-	(292.61,339.62) --
-	(294.57,339.58) --
-	(296.52,339.60) --
-	(298.48,339.65) --
-	(300.44,339.74) --
-	(302.39,339.85) --
-	(304.35,339.98) --
-	(306.31,340.12) --
-	(308.26,340.27) --
-	(310.22,340.40) --
-	(312.18,340.53) --
-	(314.13,340.65) --
-	(316.09,340.82) --
-	(318.05,341.04) --
-	(320.00,341.28) --
-	(321.96,341.54) --
-	(323.92,341.82) --
-	(325.87,342.08) --
-	(327.83,342.33) --
-	(329.79,342.54) --
-	(331.74,342.71) --
-	(333.70,342.83) --
-	(335.66,342.91) --
-	(337.61,343.00) --
-	(339.57,343.08) --
-	(341.53,343.16) --
-	(343.48,343.22) --
-	(345.44,343.28) --
-	(347.40,343.33) --
-	(349.35,343.36) --
-	(351.31,343.37) --
-	(353.27,343.36) --
-	(355.22,343.33) --
-	(357.18,343.29) --
-	(359.14,343.23) --
-	(361.09,343.16) --
-	(363.05,343.08) --
-	(365.00,342.98) --
-	(366.96,342.87) --
-	(368.92,342.75) --
-	(370.87,342.61) --
-	(372.83,342.46) --
-	(374.79,342.30);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.34) --
-	(222.18,346.29) --
-	(224.13,346.24) --
-	(226.09,346.18) --
-	(228.04,346.11) --
-	(230.00,346.03) --
-	(231.96,345.94) --
-	(233.91,345.84) --
-	(235.87,345.72) --
-	(237.83,345.60) --
-	(239.78,345.47) --
-	(241.74,345.34) --
-	(243.70,345.20) --
-	(245.65,345.05) --
-	(247.61,344.90) --
-	(249.57,344.74) --
-	(251.52,344.58) --
-	(253.48,344.41) --
-	(255.44,344.21) --
-	(257.39,344.00) --
-	(259.35,343.78) --
-	(261.31,343.55) --
-	(263.26,343.31) --
-	(265.22,343.07) --
-	(267.18,342.83) --
-	(269.13,342.61) --
-	(271.09,342.39) --
-	(273.05,342.17) --
-	(275.00,341.92) --
-	(276.96,341.63) --
-	(278.92,341.32) --
-	(280.87,341.00) --
-	(282.83,340.69) --
-	(284.79,340.40) --
-	(286.74,340.13) --
-	(288.70,339.92) --
-	(290.66,339.76) --
-	(292.61,339.66) --
-	(294.57,339.64) --
-	(296.52,339.67) --
-	(298.48,339.74) --
-	(300.44,339.84) --
-	(302.39,339.97) --
-	(304.35,340.12) --
-	(306.31,340.27) --
-	(308.26,340.42) --
-	(310.22,340.57) --
-	(312.18,340.69) --
-	(314.13,340.80) --
-	(316.09,340.96) --
-	(318.05,341.16) --
-	(320.00,341.39) --
-	(321.96,341.64) --
-	(323.92,341.89) --
-	(325.87,342.13) --
-	(327.83,342.35) --
-	(329.79,342.52) --
-	(331.74,342.65) --
-	(333.70,342.70) --
-	(335.66,342.72) --
-	(337.61,342.73) --
-	(339.57,342.74) --
-	(341.53,342.73) --
-	(343.48,342.71) --
-	(345.44,342.68) --
-	(347.40,342.63) --
-	(349.35,342.56) --
-	(351.31,342.47) --
-	(353.27,342.35) --
-	(355.22,342.22) --
-	(357.18,342.06) --
-	(359.14,341.88) --
-	(361.09,341.69) --
-	(363.05,341.48) --
-	(365.00,341.25) --
-	(366.96,341.00) --
-	(368.92,340.74) --
-	(370.87,340.45) --
-	(372.83,340.15) --
-	(374.79,339.83);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.38) --
-	(222.18,346.33) --
-	(224.13,346.28) --
-	(226.09,346.22) --
-	(228.04,346.14) --
-	(230.00,346.06) --
-	(231.96,345.97) --
-	(233.91,345.86) --
-	(235.87,345.75) --
-	(237.83,345.63) --
-	(239.78,345.50) --
-	(241.74,345.37) --
-	(243.70,345.22) --
-	(245.65,345.08) --
-	(247.61,344.93) --
-	(249.57,344.77) --
-	(251.52,344.62) --
-	(253.48,344.44) --
-	(255.44,344.25) --
-	(257.39,344.04) --
-	(259.35,343.82) --
-	(261.31,343.59) --
-	(263.26,343.36) --
+	(263.26,343.37) --
 	(265.22,343.13) --
-	(267.18,342.89) --
-	(269.13,342.67) --
-	(271.09,342.46) --
-	(273.05,342.24) --
-	(275.00,341.99) --
-	(276.96,341.70) --
-	(278.92,341.40) --
-	(280.87,341.08) --
-	(282.83,340.78) --
-	(284.79,340.49) --
-	(286.74,340.23) --
-	(288.70,340.02) --
-	(290.66,339.86) --
-	(292.61,339.76) --
-	(294.57,339.73) --
-	(296.52,339.75) --
-	(298.48,339.81) --
-	(300.44,339.89) --
-	(302.39,340.01) --
-	(304.35,340.13) --
-	(306.31,340.27) --
-	(308.26,340.41) --
-	(310.22,340.55) --
-	(312.18,340.67) --
-	(314.13,340.78) --
-	(316.09,340.91) --
-	(318.05,341.05) --
-	(320.00,341.21) --
-	(321.96,341.38) --
-	(323.92,341.56) --
-	(325.87,341.74) --
-	(327.83,341.93) --
-	(329.79,342.11) --
-	(331.74,342.28) --
-	(333.70,342.45) --
-	(335.66,342.61) --
-	(337.61,342.78) --
-	(339.57,342.95) --
-	(341.53,343.12) --
-	(343.48,343.31) --
-	(345.44,343.50) --
-	(347.40,343.70) --
-	(349.35,343.90) --
-	(351.31,344.12) --
-	(353.27,344.34) --
-	(355.22,344.58) --
-	(357.18,344.82) --
-	(359.14,345.07) --
-	(361.09,345.33) --
-	(363.05,345.59) --
-	(365.00,345.86) --
-	(366.96,346.14) --
-	(368.92,346.43) --
-	(370.87,346.72) --
-	(372.83,347.02) --
-	(374.79,347.33);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,347.01) --
-	(222.18,346.89) --
-	(224.13,346.78) --
-	(226.09,346.65) --
-	(228.04,346.52) --
-	(230.00,346.39) --
-	(231.96,346.25) --
-	(233.91,346.10) --
-	(235.87,345.94) --
-	(237.83,345.78) --
-	(239.78,345.62) --
-	(241.74,345.45) --
-	(243.70,345.28) --
-	(245.65,345.10) --
-	(247.61,344.92) --
-	(249.57,344.74) --
-	(251.52,344.56) --
-	(253.48,344.37) --
-	(255.44,344.17) --
-	(257.39,343.96) --
-	(259.35,343.74) --
-	(261.31,343.52) --
-	(263.26,343.29) --
-	(265.22,343.07) --
-	(267.18,342.85) --
-	(269.13,342.63) --
+	(267.18,342.88) --
+	(269.13,342.65) --
 	(271.09,342.42) --
 	(273.05,342.20) --
-	(275.00,341.94) --
-	(276.96,341.65) --
-	(278.92,341.33) --
-	(280.87,341.01) --
-	(282.83,340.69) --
-	(284.79,340.38) --
-	(286.74,340.11) --
-	(288.70,339.89) --
-	(290.66,339.72) --
-	(292.61,339.62) --
-	(294.57,339.58) --
-	(296.52,339.57) --
+	(275.00,341.93) --
+	(276.96,341.63) --
+	(278.92,341.31) --
+	(280.87,340.98) --
+	(282.83,340.65) --
+	(284.79,340.35) --
+	(286.74,340.08) --
+	(288.70,339.85) --
+	(290.66,339.68) --
+	(292.61,339.58) --
+	(294.57,339.54) --
+	(296.52,339.53) --
+	(298.48,339.56) --
+	(300.44,339.61) --
+	(302.39,339.69) --
+	(304.35,339.79) --
+	(306.31,339.91) --
+	(308.26,340.04) --
+	(310.22,340.17) --
+	(312.18,340.32) --
+	(314.13,340.47) --
+	(316.09,340.68) --
+	(318.05,340.93) --
+	(320.00,341.21) --
+	(321.96,341.52) --
+	(323.92,341.84) --
+	(325.87,342.16) --
+	(327.83,342.47) --
+	(329.79,342.77) --
+	(331.74,343.03) --
+	(333.70,343.26) --
+	(335.66,343.47) --
+	(337.61,343.68) --
+	(339.57,343.90) --
+	(341.53,344.12) --
+	(343.48,344.34) --
+	(345.44,344.56) --
+	(347.40,344.78) --
+	(349.35,344.99) --
+	(351.31,345.20) --
+	(353.27,345.40) --
+	(355.22,345.59) --
+	(357.18,345.78) --
+	(359.14,345.96) --
+	(361.09,346.14) --
+	(363.05,346.31) --
+	(365.00,346.49) --
+	(366.96,346.66) --
+	(368.92,346.82) --
+	(370.87,346.98) --
+	(372.83,347.14) --
+	(374.79,347.29);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.49) --
+	(222.18,346.44) --
+	(224.13,346.39) --
+	(226.09,346.33) --
+	(228.04,346.26) --
+	(230.00,346.18) --
+	(231.96,346.08) --
+	(233.91,345.98) --
+	(235.87,345.86) --
+	(237.83,345.74) --
+	(239.78,345.60) --
+	(241.74,345.46) --
+	(243.70,345.32) --
+	(245.65,345.16) --
+	(247.61,345.01) --
+	(249.57,344.85) --
+	(251.52,344.68) --
+	(253.48,344.50) --
+	(255.44,344.30) --
+	(257.39,344.08) --
+	(259.35,343.85) --
+	(261.31,343.60) --
+	(263.26,343.36) --
+	(265.22,343.11) --
+	(267.18,342.87) --
+	(269.13,342.63) --
+	(271.09,342.41) --
+	(273.05,342.18) --
+	(275.00,341.92) --
+	(276.96,341.62) --
+	(278.92,341.30) --
+	(280.87,340.98) --
+	(282.83,340.66) --
+	(284.79,340.36) --
+	(286.74,340.09) --
+	(288.70,339.86) --
+	(290.66,339.70) --
+	(292.61,339.60) --
+	(294.57,339.56) --
+	(296.52,339.56) --
 	(298.48,339.59) --
-	(300.44,339.65) --
-	(302.39,339.73) --
-	(304.35,339.82) --
-	(306.31,339.94) --
-	(308.26,340.06) --
-	(310.22,340.20) --
-	(312.18,340.33) --
-	(314.13,340.48) --
-	(316.09,340.68) --
-	(318.05,340.92) --
-	(320.00,341.19) --
-	(321.96,341.48) --
-	(323.92,341.78) --
-	(325.87,342.09) --
-	(327.83,342.38) --
-	(329.79,342.65) --
-	(331.74,342.90) --
-	(333.70,343.10) --
-	(335.66,343.28) --
+	(300.44,339.66) --
+	(302.39,339.75) --
+	(304.35,339.85) --
+	(306.31,339.98) --
+	(308.26,340.11) --
+	(310.22,340.25) --
+	(312.18,340.39) --
+	(314.13,340.53) --
+	(316.09,340.75) --
+	(318.05,341.02) --
+	(320.00,341.34) --
+	(321.96,341.68) --
+	(323.92,342.03) --
+	(325.87,342.36) --
+	(327.83,342.68) --
+	(329.79,342.94) --
+	(331.74,343.15) --
+	(333.70,343.29) --
+	(335.66,343.38) --
 	(337.61,343.47) --
-	(339.57,343.66) --
-	(341.53,343.86) --
-	(343.48,344.05) --
-	(345.44,344.24) --
-	(347.40,344.43) --
-	(349.35,344.62) --
-	(351.31,344.80) --
-	(353.27,344.97) --
-	(355.22,345.14) --
-	(357.18,345.30) --
-	(359.14,345.45) --
-	(361.09,345.60) --
-	(363.05,345.75) --
-	(365.00,345.89) --
-	(366.96,346.03) --
-	(368.92,346.17) --
-	(370.87,346.30) --
-	(372.83,346.43) --
-	(374.79,346.55);
+	(339.57,343.56) --
+	(341.53,343.64) --
+	(343.48,343.71) --
+	(345.44,343.76) --
+	(347.40,343.80) --
+	(349.35,343.81) --
+	(351.31,343.81) --
+	(353.27,343.78) --
+	(355.22,343.72) --
+	(357.18,343.64) --
+	(359.14,343.55) --
+	(361.09,343.44) --
+	(363.05,343.31) --
+	(365.00,343.16) --
+	(366.96,342.99) --
+	(368.92,342.80) --
+	(370.87,342.60) --
+	(372.83,342.38) --
+	(374.79,342.14);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,346.92) --
+	(222.18,346.83) --
+	(224.13,346.74) --
+	(226.09,346.64) --
+	(228.04,346.53) --
+	(230.00,346.41) --
+	(231.96,346.29) --
+	(233.91,346.15) --
+	(235.87,346.01) --
+	(237.83,345.87) --
+	(239.78,345.71) --
+	(241.74,345.55) --
+	(243.70,345.39) --
+	(245.65,345.22) --
+	(247.61,345.05) --
+	(249.57,344.88) --
+	(251.52,344.71) --
+	(253.48,344.52) --
+	(255.44,344.32) --
+	(257.39,344.11) --
+	(259.35,343.88) --
+	(261.31,343.65) --
+	(263.26,343.42) --
+	(265.22,343.19) --
+	(267.18,342.96) --
+	(269.13,342.74) --
+	(271.09,342.52) --
+	(273.05,342.30) --
+	(275.00,342.03) --
+	(276.96,341.73) --
+	(278.92,341.40) --
+	(280.87,341.07) --
+	(282.83,340.74) --
+	(284.79,340.43) --
+	(286.74,340.15) --
+	(288.70,339.92) --
+	(290.66,339.74) --
+	(292.61,339.65) --
+	(294.57,339.61) --
+	(296.52,339.61) --
+	(298.48,339.65) --
+	(300.44,339.72) --
+	(302.39,339.81) --
+	(304.35,339.93) --
+	(306.31,340.06) --
+	(308.26,340.20) --
+	(310.22,340.34) --
+	(312.18,340.48) --
+	(314.13,340.63) --
+	(316.09,340.83) --
+	(318.05,341.08) --
+	(320.00,341.36) --
+	(321.96,341.67) --
+	(323.92,341.98) --
+	(325.87,342.29) --
+	(327.83,342.59) --
+	(329.79,342.85) --
+	(331.74,343.06) --
+	(333.70,343.22) --
+	(335.66,343.35) --
+	(337.61,343.49) --
+	(339.57,343.62) --
+	(341.53,343.75) --
+	(343.48,343.87) --
+	(345.44,343.98) --
+	(347.40,344.09) --
+	(349.35,344.18) --
+	(351.31,344.26) --
+	(353.27,344.33) --
+	(355.22,344.37) --
+	(357.18,344.41) --
+	(359.14,344.43) --
+	(361.09,344.45) --
+	(363.05,344.45) --
+	(365.00,344.44) --
+	(366.96,344.42) --
+	(368.92,344.39) --
+	(370.87,344.35) --
+	(372.83,344.30) --
+	(374.79,344.23);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,369.28) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,362.39) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,365.59) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,365.00) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,362.95) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,361.48) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,357.71) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,351.53) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,342.52) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,332.39) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,321.34) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,310.19) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,301.60) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,297.53) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,287.48) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,279.29) circle (  2.50);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,365.64) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,358.37) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,361.32) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,361.46) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,361.50) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,359.26) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,356.35) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,351.11) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,343.69) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,334.90) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,325.46) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,316.50) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,309.10) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,302.82) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,299.01) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,295.21) circle (  2.50);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,363.32) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,355.97) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,357.79) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,359.54) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,358.46) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,357.46) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,354.60) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,350.94) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,345.09) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,337.45) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,329.93) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,322.82) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,316.14) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,314.22) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,301.62) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,299.44) circle (  2.50);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,357.59) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,354.25) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,355.79) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,356.74) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,355.19) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,355.24) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,352.83) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,350.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,345.94) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,340.67) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,334.78) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,329.05) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,324.01) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,320.28) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,315.23) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,312.23) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,370.30) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,362.63) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,365.60) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,364.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,363.04) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,361.43) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,357.87) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,351.58) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,342.72) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,332.52) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,321.56) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,310.21) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,301.74) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,297.38) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,287.12) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,277.64) circle (  2.50);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,366.96) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,358.53) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,362.30) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,361.25) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,360.11) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,358.56) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,356.17) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,351.21) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,343.85) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,336.10) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,326.81) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,318.72) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,310.21) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,308.72) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,299.87) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,293.53) circle (  2.50);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,358.62) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,355.20) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,358.93) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,357.01) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,356.84) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,356.12) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,354.21) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,350.86) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,345.40) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,339.09) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,332.75) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,326.12) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,320.57) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,316.84) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,311.60) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,304.21) circle (  2.50);
 \definecolor{drawColor}{RGB}{253,231,37}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,354.57) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,351.30) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,352.97) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,353.67) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,352.63) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,352.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,351.69) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,350.19) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,346.97) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,343.86) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,339.79) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,336.17) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,332.07) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,329.75) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,326.98) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,318.93) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94,355.86) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24,352.16) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55,352.55) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85,354.57) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16,353.09) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46,353.31) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77,352.06) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,350.45) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,346.85) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,342.86) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,338.49) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,334.64) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,330.13) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,328.08) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,323.89) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,320.20) circle (  2.50);
 \definecolor{drawColor}{RGB}{68,1,84}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,365.83) --
-	(414.90,366.04) --
-	(416.85,366.21) --
-	(418.81,366.36) --
-	(420.76,366.47) --
-	(422.72,366.56) --
-	(424.68,366.62) --
-	(426.63,366.66) --
-	(428.59,366.66) --
-	(430.55,366.64) --
-	(432.50,366.59) --
-	(434.46,366.50) --
-	(436.42,366.37) --
-	(438.37,366.21) --
-	(440.33,366.01) --
-	(442.29,365.77) --
-	(444.24,365.49) --
-	(446.20,365.20) --
-	(448.16,364.91) --
-	(450.11,364.61) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,366.60) --
+	(414.90,366.74) --
+	(416.85,366.85) --
+	(418.81,366.93) --
+	(420.76,366.99) --
+	(422.72,367.02) --
+	(424.68,367.03) --
+	(426.63,367.02) --
+	(428.59,366.98) --
+	(430.55,366.91) --
+	(432.50,366.82) --
+	(434.46,366.69) --
+	(436.42,366.54) --
+	(438.37,366.34) --
+	(440.33,366.11) --
+	(442.29,365.85) --
+	(444.24,365.54) --
+	(446.20,365.23) --
+	(448.16,364.93) --
+	(450.11,364.62) --
 	(452.07,364.30) --
@@
 	(455.98,363.57) --
-	(457.94,363.13) --
-	(459.90,362.64) --
-	(461.85,362.08) --
-	(463.81,361.44) --
-	(465.77,360.72) --
-	(467.72,359.95) --
-	(469.68,359.12) --
-	(471.64,358.25) --
-	(473.59,357.31) --
-	(475.55,356.32) --
-	(477.51,355.27) --
-	(479.46,354.16) --
-	(481.42,352.99) --
-	(483.38,351.76) --
-	(485.33,350.46) --
-	(487.29,349.03) --
-	(489.24,347.46) --
-	(491.20,345.76) --
-	(493.16,343.97) --
-	(495.11,342.11) --
-	(497.07,340.21) --
-	(499.03,338.30) --
-	(500.98,336.40) --
-	(502.94,334.54) --
-	(504.90,332.75) --
-	(506.85,331.01) --
-	(508.81,329.22) --
-	(510.77,327.36) --
-	(512.72,325.46) --
-	(514.68,323.53) --
-	(516.64,321.60) --
-	(518.59,319.67) --
-	(520.55,317.77) --
-	(522.51,315.90) --
-	(524.46,314.10) --
-	(526.42,312.37) --
-	(528.38,310.69) --
-	(530.33,309.00) --
-	(532.29,307.33) --
-	(534.25,305.66) --
-	(536.20,304.00) --
-	(538.16,302.35) --
-	(540.12,300.72) --
-	(542.07,299.11) --
-	(544.03,297.51) --
-	(545.99,295.94) --
-	(547.94,294.38) --
-	(549.90,292.85) --
-	(551.86,291.33) --
-	(553.81,289.83) --
-	(555.77,288.34) --
-	(557.72,286.86) --
-	(559.68,285.41) --
-	(561.64,283.97) --
-	(563.59,282.54) --
-	(565.55,281.13) --
-	(567.51,279.73);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,361.86) --
-	(414.90,362.08) --
-	(416.85,362.26) --
-	(418.81,362.42) --
-	(420.76,362.55) --
-	(422.72,362.67) --
-	(424.68,362.76) --
-	(426.63,362.83) --
-	(428.59,362.89) --
-	(430.55,362.91) --
-	(432.50,362.91) --
+	(457.94,363.14) --
+	(459.90,362.65) --
+	(461.85,362.09) --
+	(463.81,361.45) --
+	(465.77,360.74) --
+	(467.72,359.97) --
+	(469.68,359.16) --
+	(471.64,358.29) --
+	(473.59,357.37) --
+	(475.55,356.39) --
+	(477.51,355.35) --
+	(479.46,354.26) --
+	(481.42,353.10) --
+	(483.38,351.87) --
+	(485.33,350.58) --
+	(487.29,349.16) --
+	(489.24,347.59) --
+	(491.20,345.90) --
+	(493.16,344.11) --
+	(495.11,342.26) --
+	(497.07,340.37) --
+	(499.03,338.46) --
+	(500.98,336.56) --
+	(502.94,334.71) --
+	(504.90,332.91) --
+	(506.85,331.18) --
+	(508.81,329.39) --
+	(510.77,327.54) --
+	(512.72,325.65) --
+	(514.68,323.73) --
+	(516.64,321.80) --
+	(518.59,319.87) --
+	(520.55,317.97) --
+	(522.51,316.10) --
+	(524.46,314.28) --
+	(526.42,312.53) --
+	(528.38,310.82) --
+	(530.33,309.10) --
+	(532.29,307.39) --
+	(534.25,305.68) --
+	(536.20,303.98) --
+	(538.16,302.29) --
+	(540.12,300.61) --
+	(542.07,298.94) --
+	(544.03,297.29) --
+	(545.99,295.65) --
+	(547.94,294.03) --
+	(549.90,292.42) --
+	(551.86,290.82) --
+	(553.81,289.23) --
+	(555.77,287.66) --
+	(557.72,286.09) --
+	(559.68,284.54) --
+	(561.64,283.00) --
+	(563.59,281.47) --
+	(565.55,279.95) --
+	(567.51,278.44);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,363.23) --
+	(414.90,363.29) --
+	(416.85,363.32) --
+	(418.81,363.33) --
+	(420.76,363.33) --
+	(422.72,363.31) --
+	(424.68,363.29) --
+	(426.63,363.24) --
+	(428.59,363.18) --
+	(430.55,363.10) --
+	(432.50,363.00) --
 	(434.46,362.88) --
-	(436.42,362.82) --
-	(438.37,362.73) --
-	(440.33,362.61) --
-	(442.29,362.45) --
-	(444.24,362.25) --
-	(446.20,362.06) --
-	(448.16,361.88) --
-	(450.11,361.69) --
-	(452.07,361.49) --
-	(454.03,361.27) --
-	(455.98,361.02) --
-	(457.94,360.72) --
-	(459.90,360.37) --
-	(461.85,359.95) --
-	(463.81,359.46) --
-	(465.77,358.89) --
-	(467.72,358.26) --
-	(469.68,357.59) --
-	(471.64,356.86) --
-	(473.59,356.07) --
-	(475.55,355.24) --
-	(477.51,354.35) --
-	(479.46,353.41) --
-	(481.42,352.42) --
-	(483.38,351.38) --
-	(485.33,350.29) --
-	(487.29,349.09) --
-	(489.24,347.77) --
-	(491.20,346.34) --
-	(493.16,344.83) --
-	(495.11,343.27) --
-	(497.07,341.67) --
-	(499.03,340.05) --
-	(500.98,338.44) --
-	(502.94,336.87) --
-	(504.90,335.34) --
-	(506.85,333.86) --
-	(508.81,332.29) --
-	(510.77,330.66) --
-	(512.72,328.97) --
-	(514.68,327.25) --
-	(516.64,325.52) --
-	(518.59,323.81) --
-	(520.55,322.14) --
-	(522.51,320.53) --
-	(524.46,319.00) --
-	(526.42,317.58) --
-	(528.38,316.22) --
-	(530.33,314.87) --
-	(532.29,313.53) --
-	(534.25,312.20) --
-	(536.20,310.90) --
-	(538.16,309.62) --
-	(540.12,308.37) --
-	(542.07,307.15) --
-	(544.03,305.96) --
-	(545.99,304.82) --
-	(547.94,303.71) --
-	(549.90,302.63) --
-	(551.86,301.58) --
-	(553.81,300.56) --
-	(555.77,299.57) --
-	(557.72,298.61) --
-	(559.68,297.68) --
-	(561.64,296.77) --
-	(563.59,295.90) --
-	(565.55,295.05) --
-	(567.51,294.23);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,359.64) --
-	(414.90,359.75) --
-	(416.85,359.84) --
-	(418.81,359.91) --
-	(420.76,359.96) --
-	(422.72,360.01) --
-	(424.68,360.04) --
-	(426.63,360.06) --
-	(428.59,360.07) --
-	(430.55,360.05) --
-	(432.50,360.03) --
-	(434.46,359.98) --
-	(436.42,359.91) --
-	(438.37,359.82) --
-	(440.33,359.70) --
-	(442.29,359.56) --
-	(444.24,359.39) --
-	(446.20,359.24) --
-	(448.16,359.09) --
-	(450.11,358.96) --
-	(452.07,358.82) --
-	(454.03,358.67) --
-	(455.98,358.49) --
-	(457.94,358.28) --
-	(459.90,358.03) --
-	(461.85,357.72) --
-	(463.81,357.34) --
-	(465.77,356.90) --
-	(467.72,356.41) --
-	(469.68,355.89) --
-	(471.64,355.32) --
-	(473.59,354.70) --
-	(475.55,354.05) --
-	(477.51,353.35) --
-	(479.46,352.61) --
-	(481.42,351.82) --
-	(483.38,350.99) --
-	(485.33,350.11) --
+	(436.42,362.73) --
+	(438.37,362.56) --
+	(440.33,362.37) --
+	(442.29,362.14) --
+	(444.24,361.89) --
+	(446.20,361.64) --
+	(448.16,361.41) --
+	(450.11,361.18) --
+	(452.07,360.94) --
+	(454.03,360.69) --
+	(455.98,360.40) --
+	(457.94,360.09) --
+	(459.90,359.72) --
+	(461.85,359.30) --
+	(463.81,358.81) --
+	(465.77,358.25) --
+	(467.72,357.65) --
+	(469.68,357.02) --
+	(471.64,356.34) --
+	(473.59,355.62) --
+	(475.55,354.85) --
+	(477.51,354.04) --
+	(479.46,353.18) --
+	(481.42,352.26) --
+	(483.38,351.30) --
+	(485.33,350.27) --
 	(487.29,349.15) --
-	(489.24,348.09) --
-	(491.20,346.94) --
-	(493.16,345.73) --
-	(495.11,344.48) --
-	(497.07,343.19) --
-	(499.03,341.89) --
-	(500.98,340.59) --
-	(502.94,339.32) --
-	(504.90,338.09) --
-	(506.85,336.90) --
-	(508.81,335.67) --
-	(510.77,334.39) --
-	(512.72,333.08) --
-	(514.68,331.75) --
-	(516.64,330.41) --
-	(518.59,329.07) --
-	(520.55,327.73) --
-	(522.51,326.42) --
-	(524.46,325.12) --
-	(526.42,323.87) --
-	(528.38,322.63) --
-	(530.33,321.38) --
-	(532.29,320.14) --
-	(534.25,318.89) --
-	(536.20,317.64) --
-	(538.16,316.39) --
-	(540.12,315.15) --
-	(542.07,313.92) --
-	(544.03,312.69) --
-	(545.99,311.47) --
-	(547.94,310.26) --
-	(549.90,309.06) --
-	(551.86,307.86) --
-	(553.81,306.66) --
-	(555.77,305.47) --
-	(557.72,304.28) --
-	(559.68,303.10) --
-	(561.64,301.92) --
-	(563.59,300.75) --
-	(565.55,299.58) --
-	(567.51,298.41);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,355.71) --
-	(414.90,355.88) --
-	(416.85,356.03) --
-	(418.81,356.17) --
-	(420.76,356.28) --
-	(422.72,356.39) --
-	(424.68,356.49) --
-	(426.63,356.57) --
-	(428.59,356.63) --
-	(430.55,356.68) --
-	(432.50,356.71) --
-	(434.46,356.72) --
-	(436.42,356.72) --
-	(438.37,356.70) --
-	(440.33,356.65) --
-	(442.29,356.59) --
-	(444.24,356.50) --
-	(446.20,356.41) --
-	(448.16,356.32) --
-	(450.11,356.23) --
-	(452.07,356.13) --
-	(454.03,356.01) --
-	(455.98,355.88) --
-	(457.94,355.71) --
-	(459.90,355.52) --
-	(461.85,355.29) --
-	(463.81,355.01) --
-	(465.77,354.69) --
-	(467.72,354.35) --
-	(469.68,353.98) --
-	(471.64,353.58) --
-	(473.59,353.16) --
-	(475.55,352.70) --
-	(477.51,352.21) --
-	(479.46,351.68) --
-	(481.42,351.12) --
-	(483.38,350.52) --
-	(485.33,349.88) --
-	(487.29,349.17) --
-	(489.24,348.40) --
-	(491.20,347.56) --
-	(493.16,346.67) --
-	(495.11,345.75) --
-	(497.07,344.80) --
-	(499.03,343.84) --
-	(500.98,342.88) --
-	(502.94,341.92) --
-	(504.90,340.99) --
-	(506.85,340.07) --
-	(508.81,339.10) --
-	(510.77,338.09) --
-	(512.72,337.04) --
-	(514.68,335.97) --
-	(516.64,334.89) --
-	(518.59,333.82) --
-	(520.55,332.75) --
-	(522.51,331.71) --
-	(524.46,330.71) --
-	(526.42,329.76) --
-	(528.38,328.83) --
-	(530.33,327.90) --
-	(532.29,326.97) --
-	(534.25,326.04) --
-	(536.20,325.11) --
-	(538.16,324.19) --
-	(540.12,323.28) --
-	(542.07,322.38) --
-	(544.03,321.49) --
-	(545.99,320.61) --
-	(547.94,319.75) --
-	(549.90,318.90) --
-	(551.86,318.05) --
-	(553.81,317.22) --
-	(555.77,316.39) --
-	(557.72,315.57) --
-	(559.68,314.76) --
-	(561.64,313.96) --
-	(563.59,313.16) --
-	(565.55,312.38) --
-	(567.51,311.60);
+	(489.24,347.90) --
+	(491.20,346.55) --
+	(493.16,345.13) --
+	(495.11,343.65) --
+	(497.07,342.14) --
+	(499.03,340.62) --
+	(500.98,339.10) --
+	(502.94,337.62) --
+	(504.90,336.19) --
+	(506.85,334.81) --
+	(508.81,333.37) --
+	(510.77,331.88) --
+	(512.72,330.36) --
+	(514.68,328.81) --
+	(516.64,327.26) --
+	(518.59,325.71) --
+	(520.55,324.18) --
+	(522.51,322.69) --
+	(524.46,321.25) --
+	(526.42,319.87) --
+	(528.38,318.52) --
+	(530.33,317.18) --
+	(532.29,315.84) --
+	(534.25,314.51) --
+	(536.20,313.18) --
+	(538.16,311.87) --
+	(540.12,310.57) --
+	(542.07,309.28) --
+	(544.03,308.01) --
+	(545.99,306.76) --
+	(547.94,305.52) --
+	(549.90,304.30) --
+	(551.86,303.09) --
+	(553.81,301.89) --
+	(555.77,300.71) --
+	(557.72,299.54) --
+	(559.68,298.38) --
+	(561.64,297.24) --
+	(563.59,296.11) --
+	(565.55,294.99) --
+	(567.51,293.88);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,356.81) --
+	(414.90,357.05) --
+	(416.85,357.26) --
+	(418.81,357.46) --
+	(420.76,357.63) --
+	(422.72,357.79) --
+	(424.68,357.92) --
+	(426.63,358.04) --
+	(428.59,358.14) --
+	(430.55,358.22) --
+	(432.50,358.27) --
+	(434.46,358.30) --
+	(436.42,358.31) --
+	(438.37,358.29) --
+	(440.33,358.25) --
+	(442.29,358.18) --
+	(444.24,358.08) --
+	(446.20,357.98) --
+	(448.16,357.86) --
+	(450.11,357.74) --
+	(452.07,357.60) --
+	(454.03,357.45) --
+	(455.98,357.26) --
+	(457.94,357.05) --
+	(459.90,356.79) --
+	(461.85,356.50) --
+	(463.81,356.16) --
+	(465.77,355.77) --
+	(467.72,355.35) --
+	(469.68,354.90) --
+	(471.64,354.42) --
+	(473.59,353.91) --
+	(475.55,353.35) --
+	(477.51,352.77) --
+	(479.46,352.14) --
+	(481.42,351.48) --
+	(483.38,350.77) --
+	(485.33,350.02) --
+	(487.29,349.20) --
+	(489.24,348.28) --
+	(491.20,347.29) --
+	(493.16,346.25) --
+	(495.11,345.16) --
+	(497.07,344.05) --
+	(499.03,342.92) --
+	(500.98,341.79) --
+	(502.94,340.69) --
+	(504.90,339.61) --
+	(506.85,338.57) --
+	(508.81,337.49) --
+	(510.77,336.37) --
+	(512.72,335.22) --
+	(514.68,334.05) --
+	(516.64,332.88) --
+	(518.59,331.70) --
+	(520.55,330.54) --
+	(522.51,329.39) --
+	(524.46,328.26) --
+	(526.42,327.18) --
+	(528.38,326.11) --
+	(530.33,325.03) --
+	(532.29,323.96) --
+	(534.25,322.88) --
+	(536.20,321.81) --
+	(538.16,320.74) --
+	(540.12,319.66) --
+	(542.07,318.60) --
+	(544.03,317.53) --
+	(545.99,316.47) --
+	(547.94,315.42) --
+	(549.90,314.37) --
+	(551.86,313.32) --
+	(553.81,312.27) --
+	(555.77,311.22) --
+	(557.72,310.18) --
+	(559.68,309.14) --
+	(561.64,308.11) --
+	(563.59,307.07) --
+	(565.55,306.04) --
+	(567.51,305.01);
 \definecolor{drawColor}{RGB}{253,231,37}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,352.93) --
-	(414.90,353.03) --
-	(416.85,353.12) --
-	(418.81,353.20) --
-	(420.76,353.27) --
-	(422.72,353.33) --
-	(424.68,353.39) --
-	(426.63,353.44) --
-	(428.59,353.48) --
-	(430.55,353.52) --
-	(432.50,353.54) --
-	(434.46,353.55) --
-	(436.42,353.56) --
-	(438.37,353.55) --
-	(440.33,353.53) --
-	(442.29,353.50) --
-	(444.24,353.45) --
-	(446.20,353.41) --
-	(448.16,353.37) --
-	(450.11,353.33) --
-	(452.07,353.29) --
-	(454.03,353.24) --
-	(455.98,353.18) --
-	(457.94,353.10) --
-	(459.90,353.00) --
-	(461.85,352.88) --
-	(463.81,352.72) --
-	(465.77,352.54) --
-	(467.72,352.33) --
-	(469.68,352.12) --
-	(471.64,351.88) --
-	(473.59,351.63) --
-	(475.55,351.35) --
-	(477.51,351.05) --
-	(479.46,350.73) --
-	(481.42,350.39) --
-	(483.38,350.01) --
-	(485.33,349.61) --
-	(487.29,349.16) --
-	(489.24,348.67) --
-	(491.20,348.14) --
-	(493.16,347.57) --
-	(495.11,346.98) --
-	(497.07,346.37) --
-	(499.03,345.76) --
-	(500.98,345.13) --
-	(502.94,344.51) --
-	(504.90,343.90) --
-	(506.85,343.30) --
-	(508.81,342.68) --
-	(510.77,342.05) --
-	(512.72,341.39) --
-	(514.68,340.73) --
-	(516.64,340.06) --
-	(518.59,339.38) --
-	(520.55,338.69) --
-	(522.51,338.00) --
-	(524.46,337.32) --
-	(526.42,336.63) --
-	(528.38,335.94) --
-	(530.33,335.25) --
-	(532.29,334.55) --
-	(534.25,333.84) --
-	(536.20,333.12) --
-	(538.16,332.39) --
-	(540.12,331.66) --
-	(542.07,330.91) --
-	(544.03,330.16) --
-	(545.99,329.40) --
-	(547.94,328.62) --
-	(549.90,327.84) --
-	(551.86,327.05) --
-	(553.81,326.25) --
-	(555.77,325.44) --
-	(557.72,324.63) --
-	(559.68,323.80) --
-	(561.64,322.97) --
-	(563.59,322.13) --
-	(565.55,321.28) --
-	(567.51,320.42);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94,353.87) --
+	(414.90,353.94) --
+	(416.85,354.00) --
+	(418.81,354.05) --
+	(420.76,354.09) --
+	(422.72,354.13) --
+	(424.68,354.16) --
+	(426.63,354.19) --
+	(428.59,354.21) --
+	(430.55,354.22) --
+	(432.50,354.23) --
+	(434.46,354.22) --
+	(436.42,354.21) --
+	(438.37,354.18) --
+	(440.33,354.14) --
+	(442.29,354.09) --
+	(444.24,354.02) --
+	(446.20,353.96) --
+	(448.16,353.92) --
+	(450.11,353.88) --
+	(452.07,353.83) --
+	(454.03,353.79) --
+	(455.98,353.73) --
+	(457.94,353.65) --
+	(459.90,353.54) --
+	(461.85,353.41) --
+	(463.81,353.24) --
+	(465.77,353.03) --
+	(467.72,352.80) --
+	(469.68,352.56) --
+	(471.64,352.29) --
+	(473.59,352.00) --
+	(475.55,351.69) --
+	(477.51,351.35) --
+	(479.46,350.99) --
+	(481.42,350.59) --
+	(483.38,350.16) --
+	(485.33,349.71) --
+	(487.29,349.20) --
+	(489.24,348.63) --
+	(491.20,348.02) --
+	(493.16,347.37) --
+	(495.11,346.69) --
+	(497.07,345.99) --
+	(499.03,345.28) --
+	(500.98,344.57) --
+	(502.94,343.86) --
+	(504.90,343.18) --
+	(506.85,342.50) --
+	(508.81,341.79) --
+	(510.77,341.05) --
+	(512.72,340.29) --
+	(514.68,339.51) --
+	(516.64,338.72) --
+	(518.59,337.93) --
+	(520.55,337.15) --
+	(522.51,336.37) --
+	(524.46,335.63) --
+	(526.42,334.90) --
+	(528.38,334.19) --
+	(530.33,333.48) --
+	(532.29,332.77) --
+	(534.25,332.05) --
+	(536.20,331.34) --
+	(538.16,330.62) --
+	(540.12,329.91) --
+	(542.07,329.20) --
+	(544.03,328.49) --
+	(545.99,327.79) --
+	(547.94,327.09) --
+	(549.90,326.39) --
+	(551.86,325.70) --
+	(553.81,325.01) --
+	(555.77,324.32) --
+	(557.72,323.63) --
+	(559.68,322.95) --
+	(561.64,322.27) --
+	(563.59,321.59) --
+	(565.55,320.91) --
+	(567.51,320.23);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.82) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.84) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,104.72) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.49) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.79) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,104.49) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.63) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.02) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.31) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.02) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.77) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.44) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.91) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.13) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.53) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.80) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.48) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,156.80) circle (  2.50);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.67) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,104.40) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.62) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,104.88) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.41) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.06) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.83) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.81) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.33) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.82) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,129.99) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.57) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.74) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.64) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,155.88) circle (  2.50);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.97) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.47) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,104.81) circle (  2.50);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.08) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.28) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.06) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.98) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.85) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.53) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,122.02) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.26) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.54) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.77) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.65) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,156.29) circle (  2.50);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,102.25) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.79) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,104.60) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.51) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,104.85) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.33) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.11) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.94) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.88) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.51) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,122.04) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.29) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.47) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.64) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.10) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,155.45) circle (  2.50);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,102.39) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.44) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,104.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.28) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.03) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.20) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.16) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.89) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.88) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.42) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.89) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.30) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.44) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.62) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.12) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,156.03) circle (  2.50);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.75) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.84) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,105.21) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,103.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.04) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.24) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.15) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.89) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.83) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.39) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.85) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.18) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.51) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.75) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.23) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,156.30) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.01) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.31) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.08) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.82) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.79) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.34) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.74) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.05) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.48) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.63) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,149.85) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,156.36) circle (  2.50);
 \definecolor{drawColor}{RGB}{253,231,37}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.62) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,107.17) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,105.21) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.04) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.02) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.37) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.15) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.82) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.81) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.37) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.75) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.04) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.60) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,150.25) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,155.48) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.50,101.76) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.80,106.78) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.11,105.16) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.41,104.02) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.72,105.06) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.02,105.39) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.33,106.14) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.63,107.79) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.94,110.78) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.24,115.27) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.54,121.64) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.85,130.00) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.15,138.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.46,144.90) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.76,149.99) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.07,157.07) circle (  2.50);
 \definecolor{drawColor}{RGB}{68,1,84}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.12) --
-	( 29.46,104.08) --
-	( 31.41,104.06) --
-	( 33.37,104.04) --
-	( 35.32,104.03) --
-	( 37.28,104.02) --
-	( 39.24,104.01) --
-	( 41.19,104.00) --
-	( 43.15,104.00) --
-	( 45.11,104.01) --
-	( 47.06,104.02) --
-	( 49.02,104.05) --
-	( 50.98,104.08) --
-	( 52.93,104.12) --
-	( 54.89,104.17) --
-	( 56.85,104.23) --
-	( 58.80,104.31) --
-	( 60.76,104.37) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,103.84) --
+	( 29.46,103.83) --
+	( 31.41,103.83) --
+	( 33.37,103.83) --
+	( 35.32,103.84) --
+	( 37.28,103.85) --
+	( 39.24,103.86) --
+	( 41.19,103.87) --
+	( 43.15,103.89) --
+	( 45.11,103.91) --
+	( 47.06,103.94) --
+	( 49.02,103.97) --
+	( 50.98,104.02) --
+	( 52.93,104.07) --
+	( 54.89,104.13) --
+	( 56.85,104.20) --
+	( 58.80,104.29) --
+	( 60.76,104.36) --
 	( 62.72,104.42) --
 	( 64.67,104.46) --
-	( 66.63,104.50) --
-	( 68.59,104.54) --
-	( 70.54,104.60) --
-	( 72.50,104.67) --
-	( 74.46,104.77) --
-	( 76.41,104.90) --
-	( 78.37,105.07) --
-	( 80.33,105.27) --
-	( 82.28,105.45) --
-	( 84.24,105.62) --
+	( 66.63,104.51) --
+	( 68.59,104.55) --
+	( 70.54,104.61) --
+	( 72.50,104.68) --
+	( 74.46,104.78) --
+	( 76.41,104.91) --
+	( 78.37,105.08) --
+	( 80.33,105.28) --
+	( 82.28,105.46) --
+	( 84.24,105.63) --
 	( 86.20,105.80) --
-	( 88.15,105.99) --
-	( 90.11,106.21) --
-	( 92.07,106.47) --
-	( 94.02,106.77) --
-	( 95.98,107.14) --
-	( 97.94,107.58) --
-	( 99.89,108.10) --
-	(101.85,108.68) --
-	(103.80,109.32) --
-	(105.76,109.99) --
-	(107.72,110.71) --
-	(109.67,111.47) --
-	(111.63,112.28) --
-	(113.59,113.12) --
-	(115.54,114.00) --
-	(117.50,114.93) --
-	(119.46,115.88) --
-	(121.41,116.89) --
-	(123.37,117.99) --
-	(125.33,119.17) --
-	(127.28,120.41) --
-	(129.24,121.70) --
-	(131.20,123.03) --
-	(133.15,124.37) --
-	(135.11,125.71) --
-	(137.07,127.04) --
-	(139.02,128.34) --
-	(140.98,129.58) --
-	(142.94,130.82) --
-	(144.89,132.09) --
-	(146.85,133.37) --
-	(148.81,134.67) --
-	(150.76,135.99) --
-	(152.72,137.32) --
-	(154.68,138.65) --
-	(156.63,139.99) --
-	(158.59,141.33) --
-	(160.55,142.67) --
-	(162.50,144.00) --
-	(164.46,145.34) --
-	(166.42,146.68) --
-	(168.37,148.03) --
-	(170.33,149.39) --
-	(172.28,150.75) --
-	(174.24,152.12) --
-	(176.20,153.50) --
-	(178.15,154.88) --
-	(180.11,156.26) --
-	(182.07,157.66);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.38) --
-	( 29.46,104.31) --
-	( 31.41,104.26) --
-	( 33.37,104.22) --
-	( 35.32,104.18) --
-	( 37.28,104.14) --
-	( 39.24,104.11) --
-	( 41.19,104.09) --
-	( 43.15,104.07) --
-	( 45.11,104.06) --
-	( 47.06,104.05) --
-	( 49.02,104.06) --
-	( 50.98,104.08) --
-	( 52.93,104.10) --
-	( 54.89,104.14) --
-	( 56.85,104.20) --
-	( 58.80,104.26) --
-	( 60.76,104.32) --
-	( 62.72,104.37) --
-	( 64.67,104.41) --
-	( 66.63,104.44) --
-	( 68.59,104.49) --
-	( 70.54,104.55) --
-	( 72.50,104.62) --
-	( 74.46,104.73) --
-	( 76.41,104.86) --
-	( 78.37,105.03) --
-	( 80.33,105.23) --
-	( 82.28,105.42) --
-	( 84.24,105.59) --
-	( 86.20,105.78) --
-	( 88.15,105.97) --
-	( 90.11,106.20) --
-	( 92.07,106.46) --
-	( 94.02,106.77) --
-	( 95.98,107.14) --
-	( 97.94,107.58) --
-	( 99.89,108.10) --
-	(101.85,108.69) --
-	(103.80,109.33) --
-	(105.76,110.01) --
-	(107.72,110.73) --
-	(109.67,111.50) --
-	(111.63,112.30) --
-	(113.59,113.15) --
-	(115.54,114.03) --
-	(117.50,114.95) --
-	(119.46,115.91) --
-	(121.41,116.92) --
-	(123.37,118.01) --
-	(125.33,119.19) --
-	(127.28,120.44) --
-	(129.24,121.73) --
-	(131.20,123.06) --
-	(133.15,124.40) --
-	(135.11,125.74) --
-	(137.07,127.06) --
-	(139.02,128.34) --
-	(140.98,129.58) --
-	(142.94,130.80) --
-	(144.89,132.04) --
-	(146.85,133.31) --
-	(148.81,134.59) --
-	(150.76,135.88) --
-	(152.72,137.18) --
-	(154.68,138.48) --
-	(156.63,139.79) --
-	(158.59,141.10) --
-	(160.55,142.40) --
-	(162.50,143.70) --
-	(164.46,145.00) --
-	(166.42,146.30) --
-	(168.37,147.61) --
-	(170.33,148.92) --
-	(172.28,150.23) --
-	(174.24,151.55) --
-	(176.20,152.87) --
-	(178.15,154.20) --
-	(180.11,155.53) --
-	(182.07,156.86);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.38) --
-	( 29.46,104.32) --
-	( 31.41,104.27) --
-	( 33.37,104.22) --
-	( 35.32,104.18) --
-	( 37.28,104.15) --
-	( 39.24,104.12) --
-	( 41.19,104.09) --
-	( 43.15,104.08) --
-	( 45.11,104.06) --
-	( 47.06,104.06) --
-	( 49.02,104.07) --
-	( 50.98,104.08) --
-	( 52.93,104.11) --
-	( 54.89,104.15) --
-	( 56.85,104.20) --
-	( 58.80,104.27) --
-	( 60.76,104.33) --
-	( 62.72,104.37) --
-	( 64.67,104.41) --
-	( 66.63,104.45) --
-	( 68.59,104.50) --
-	( 70.54,104.56) --
-	( 72.50,104.63) --
-	( 74.46,104.74) --
-	( 76.41,104.87) --
-	( 78.37,105.04) --
-	( 80.33,105.24) --
-	( 82.28,105.42) --
-	( 84.24,105.60) --
-	( 86.20,105.77) --
-	( 88.15,105.96) --
-	( 90.11,106.18) --
+	( 88.15,105.98) --
+	( 90.11,106.19) --
 	( 92.07,106.44) --
 	( 94.02,106.74) --
-	( 95.98,107.11) --
-	( 97.94,107.55) --
-	( 99.89,108.07) --
-	(101.85,108.65) --
-	(103.80,109.29) --
-	(105.76,109.96) --
-	(107.72,110.68) --
-	(109.67,111.44) --
-	(111.63,112.25) --
-	(113.59,113.09) --
-	(115.54,113.97) --
-	(117.50,114.89) --
-	(119.46,115.85) --
-	(121.41,116.85) --
-	(123.37,117.94) --
-	(125.33,119.12) --
-	(127.28,120.36) --
-	(129.24,121.65) --
-	(131.20,122.97) --
-	(133.15,124.31) --
-	(135.11,125.64) --
-	(137.07,126.97) --
-	(139.02,128.25) --
-	(140.98,129.49) --
-	(142.94,130.72) --
-	(144.89,131.98) --
-	(146.85,133.25) --
-	(148.81,134.54) --
-	(150.76,135.85) --
-	(152.72,137.16) --
-	(154.68,138.49) --
-	(156.63,139.81) --
-	(158.59,141.14) --
-	(160.55,142.46) --
-	(162.50,143.78) --
-	(164.46,145.11) --
-	(166.42,146.44) --
-	(168.37,147.77) --
-	(170.33,149.11) --
-	(172.28,150.46) --
-	(174.24,151.81) --
-	(176.20,153.17) --
-	(178.15,154.53) --
-	(180.11,155.90) --
-	(182.07,157.27);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.14) --
-	( 29.46,104.10) --
-	( 31.41,104.08) --
-	( 33.37,104.06) --
-	( 35.32,104.04) --
-	( 37.28,104.03) --
-	( 39.24,104.02) --
-	( 41.19,104.01) --
-	( 43.15,104.01) --
-	( 45.11,104.01) --
-	( 47.06,104.02) --
-	( 49.02,104.04) --
-	( 50.98,104.07) --
-	( 52.93,104.11) --
-	( 54.89,104.16) --
-	( 56.85,104.22) --
-	( 58.80,104.29) --
-	( 60.76,104.35) --
-	( 62.72,104.40) --
-	( 64.67,104.44) --
-	( 66.63,104.47) --
-	( 68.59,104.51) --
-	( 70.54,104.56) --
-	( 72.50,104.63) --
-	( 74.46,104.72) --
-	( 76.41,104.85) --
-	( 78.37,105.01) --
-	( 80.33,105.21) --
-	( 82.28,105.39) --
-	( 84.24,105.57) --
-	( 86.20,105.75) --
-	( 88.15,105.94) --
-	( 90.11,106.16) --
-	( 92.07,106.42) --
-	( 94.02,106.73) --
 	( 95.98,107.10) --
-	( 97.94,107.54) --
-	( 99.89,108.06) --
-	(101.85,108.65) --
-	(103.80,109.28) --
-	(105.76,109.95) --
-	(107.72,110.66) --
-	(109.67,111.41) --
-	(111.63,112.21) --
-	(113.59,113.05) --
+	( 97.94,107.53) --
+	( 99.89,108.05) --
+	(101.85,108.63) --
+	(103.80,109.26) --
+	(105.76,109.93) --
+	(107.72,110.64) --
+	(109.67,111.40) --
+	(111.63,112.20) --
+	(113.59,113.04) --
 	(115.54,113.92) --
-	(117.50,114.84) --
+	(117.50,114.83) --
 	(119.46,115.79) --
@@
 	(127.28,120.31) --
-	(129.24,121.60) --
+	(129.24,121.59) --
 	(131.20,122.92) --
 	(133.15,124.26) --
-	(135.11,125.61) --
-	(137.07,126.93) --
-	(139.02,128.23) --
-	(140.98,129.47) --
-	(142.94,130.71) --
-	(144.89,131.97) --
-	(146.85,133.25) --
-	(148.81,134.55) --
-	(150.76,135.87) --
-	(152.72,137.19) --
+	(135.11,125.60) --
+	(137.07,126.92) --
+	(139.02,128.22) --
+	(140.98,129.48) --
+	(142.94,130.72) --
+	(144.89,131.99) --
+	(146.85,133.29) --
+	(148.81,134.60) --
+	(150.76,135.92) --
+	(152.72,137.26) --
+	(154.68,138.61) --
+	(156.63,139.96) --
+	(158.59,141.32) --
+	(160.55,142.67) --
+	(162.50,144.03) --
+	(164.46,145.39) --
+	(166.42,146.76) --
+	(168.37,148.13) --
+	(170.33,149.51) --
+	(172.28,150.90) --
+	(174.24,152.30) --
+	(176.20,153.70) --
+	(178.15,155.12) --
+	(180.11,156.54) --
+	(182.07,157.96);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.00) --
+	( 29.46,103.98) --
+	( 31.41,103.96) --
+	( 33.37,103.95) --
+	( 35.32,103.94) --
+	( 37.28,103.94) --
+	( 39.24,103.94) --
+	( 41.19,103.94) --
+	( 43.15,103.95) --
+	( 45.11,103.96) --
+	( 47.06,103.98) --
+	( 49.02,104.01) --
+	( 50.98,104.04) --
+	( 52.93,104.09) --
+	( 54.89,104.14) --
+	( 56.85,104.21) --
+	( 58.80,104.29) --
+	( 60.76,104.35) --
+	( 62.72,104.41) --
+	( 64.67,104.45) --
+	( 66.63,104.49) --
+	( 68.59,104.53) --
+	( 70.54,104.59) --
+	( 72.50,104.66) --
+	( 74.46,104.76) --
+	( 76.41,104.89) --
+	( 78.37,105.06) --
+	( 80.33,105.26) --
+	( 82.28,105.43) --
+	( 84.24,105.60) --
+	( 86.20,105.78) --
+	( 88.15,105.96) --
+	( 90.11,106.17) --
+	( 92.07,106.42) --
+	( 94.02,106.72) --
+	( 95.98,107.08) --
+	( 97.94,107.51) --
+	( 99.89,108.03) --
+	(101.85,108.61) --
+	(103.80,109.23) --
+	(105.76,109.89) --
+	(107.72,110.60) --
+	(109.67,111.35) --
+	(111.63,112.14) --
+	(113.59,112.97) --
+	(115.54,113.84) --
+	(117.50,114.76) --
+	(119.46,115.71) --
+	(121.41,116.71) --
+	(123.37,117.81) --
+	(125.33,119.00) --
+	(127.28,120.24) --
+	(129.24,121.54) --
+	(131.20,122.88) --
+	(133.15,124.22) --
+	(135.11,125.57) --
+	(137.07,126.91) --
+	(139.02,128.21) --
+	(140.98,129.45) --
+	(142.94,130.69) --
+	(144.89,131.96) --
+	(146.85,133.24) --
+	(148.81,134.54) --
+	(150.76,135.86) --
+	(152.72,137.18) --
 	(154.68,138.52) --
 	(156.63,139.86) --
-	(158.59,141.20) --
-	(160.55,142.54) --
-	(162.50,143.87) --
-	(164.46,145.21) --
-	(166.42,146.56) --
-	(168.37,147.91) --
-	(170.33,149.26) --
-	(172.28,150.63) --
-	(174.24,152.00) --
-	(176.20,153.37) --
-	(178.15,154.76) --
-	(180.11,156.14) --
-	(182.07,157.54);
+	(158.59,141.19) --
+	(160.55,142.53) --
+	(162.50,143.86) --
+	(164.46,145.19) --
+	(166.42,146.53) --
+	(168.37,147.87) --
+	(170.33,149.22) --
+	(172.28,150.58) --
+	(174.24,151.94) --
+	(176.20,153.30) --
+	(178.15,154.67) --
+	(180.11,156.05) --
+	(182.07,157.43);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.08) --
+	( 29.46,104.04) --
+	( 31.41,104.02) --
+	( 33.37,104.01) --
+	( 35.32,103.99) --
+	( 37.28,103.99) --
+	( 39.24,103.98) --
+	( 41.19,103.98) --
+	( 43.15,103.98) --
+	( 45.11,103.98) --
+	( 47.06,104.00) --
+	( 49.02,104.02) --
+	( 50.98,104.05) --
+	( 52.93,104.09) --
+	( 54.89,104.15) --
+	( 56.85,104.21) --
+	( 58.80,104.29) --
+	( 60.76,104.35) --
+	( 62.72,104.40) --
+	( 64.67,104.45) --
+	( 66.63,104.49) --
+	( 68.59,104.53) --
+	( 70.54,104.59) --
+	( 72.50,104.67) --
+	( 74.46,104.77) --
+	( 76.41,104.90) --
+	( 78.37,105.07) --
+	( 80.33,105.26) --
+	( 82.28,105.44) --
+	( 84.24,105.61) --
+	( 86.20,105.78) --
+	( 88.15,105.96) --
+	( 90.11,106.17) --
+	( 92.07,106.41) --
+	( 94.02,106.71) --
+	( 95.98,107.07) --
+	( 97.94,107.50) --
+	( 99.89,108.01) --
+	(101.85,108.59) --
+	(103.80,109.21) --
+	(105.76,109.88) --
+	(107.72,110.59) --
+	(109.67,111.35) --
+	(111.63,112.14) --
+	(113.59,112.98) --
+	(115.54,113.85) --
+	(117.50,114.77) --
+	(119.46,115.72) --
+	(121.41,116.72) --
+	(123.37,117.81) --
+	(125.33,118.98) --
+	(127.28,120.22) --
+	(129.24,121.51) --
+	(131.20,122.83) --
+	(133.15,124.17) --
+	(135.11,125.50) --
+	(137.07,126.83) --
+	(139.02,128.12) --
+	(140.98,129.36) --
+	(142.94,130.60) --
+	(144.89,131.85) --
+	(146.85,133.13) --
+	(148.81,134.43) --
+	(150.76,135.74) --
+	(152.72,137.07) --
+	(154.68,138.40) --
+	(156.63,139.73) --
+	(158.59,141.07) --
+	(160.55,142.41) --
+	(162.50,143.74) --
+	(164.46,145.08) --
+	(166.42,146.43) --
+	(168.37,147.78) --
+	(170.33,149.14) --
+	(172.28,150.51) --
+	(174.24,151.88) --
+	(176.20,153.26) --
+	(178.15,154.64) --
+	(180.11,156.03) --
+	(182.07,157.43);
 \definecolor{drawColor}{RGB}{253,231,37}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.16) --
-	( 29.46,104.13) --
-	( 31.41,104.11) --
-	( 33.37,104.10) --
-	( 35.32,104.09) --
-	( 37.28,104.08) --
-	( 39.24,104.08) --
-	( 41.19,104.07) --
-	( 43.15,104.07) --
-	( 45.11,104.08) --
-	( 47.06,104.09) --
-	( 49.02,104.11) --
-	( 50.98,104.14) --
-	( 52.93,104.18) --
-	( 54.89,104.23) --
-	( 56.85,104.29) --
-	( 58.80,104.37) --
-	( 60.76,104.43) --
-	( 62.72,104.47) --
-	( 64.67,104.50) --
-	( 66.63,104.53) --
-	( 68.59,104.56) --
-	( 70.54,104.61) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.50,104.10) --
+	( 29.46,104.07) --
+	( 31.41,104.05) --
+	( 33.37,104.04) --
+	( 35.32,104.03) --
+	( 37.28,104.02) --
+	( 39.24,104.02) --
+	( 41.19,104.01) --
+	( 43.15,104.02) --
+	( 45.11,104.03) --
+	( 47.06,104.04) --
+	( 49.02,104.06) --
+	( 50.98,104.10) --
+	( 52.93,104.14) --
+	( 54.89,104.19) --
+	( 56.85,104.25) --
+	( 58.80,104.33) --
+	( 60.76,104.39) --
+	( 62.72,104.44) --
+	( 64.67,104.48) --
+	( 66.63,104.51) --
+	( 68.59,104.55) --
+	( 70.54,104.60) --
 	( 72.50,104.67) --
-	( 74.46,104.76) --
-	( 76.41,104.88) --
-	( 78.37,105.04) --
-	( 80.33,105.23) --
-	( 82.28,105.41) --
-	( 84.24,105.58) --
-	( 86.20,105.76) --
+	( 74.46,104.77) --
+	( 76.41,104.89) --
+	( 78.37,105.06) --
+	( 80.33,105.25) --
+	( 82.28,105.43) --
+	( 84.24,105.60) --
+	( 86.20,105.77) --
 	( 88.15,105.95) --
@@
 	( 92.07,106.42) --
-	( 94.02,106.73) --
-	( 95.98,107.10) --
-	( 97.94,107.53) --
-	( 99.89,108.05) --
-	(101.85,108.63) --
-	(103.80,109.25) --
-	(105.76,109.91) --
-	(107.72,110.62) --
-	(109.67,111.36) --
-	(111.63,112.15) --
-	(113.59,112.98) --
-	(115.54,113.85) --
-	(117.50,114.76) --
-	(119.46,115.71) --
-	(121.41,116.72) --
-	(123.37,117.82) --
-	(125.33,119.01) --
-	(127.28,120.26) --
-	(129.24,121.57) --
-	(131.20,122.91) --
-	(133.15,124.26) --
-	(135.11,125.62) --
-	(137.07,126.95) --
-	(139.02,128.25) --
-	(140.98,129.49) --
-	(142.94,130.72) --
-	(144.89,131.98) --
-	(146.85,133.25) --
-	(148.81,134.54) --
-	(150.76,135.85) --
+	( 94.02,106.71) --
+	( 95.98,107.07) --
+	( 97.94,107.51) --
+	( 99.89,108.02) --
+	(101.85,108.60) --
+	(103.80,109.21) --
+	(105.76,109.87) --
+	(107.72,110.57) --
+	(109.67,111.32) --
+	(111.63,112.10) --
+	(113.59,112.93) --
+	(115.54,113.79) --
+	(117.50,114.70) --
+	(119.46,115.65) --
+	(121.41,116.66) --
+	(123.37,117.75) --
+	(125.33,118.92) --
+	(127.28,120.16) --
+	(129.24,121.45) --
+	(131.20,122.78) --
+	(133.15,124.12) --
+	(135.11,125.46) --
+	(137.07,126.79) --
+	(139.02,128.09) --
+	(140.98,129.35) --
+	(142.94,130.60) --
+	(144.89,131.87) --
+	(146.85,133.17) --
+	(148.81,134.48) --
+	(150.76,135.81) --
 	(152.72,137.16) --
-	(154.68,138.48) --
-	(156.63,139.81) --
-	(158.59,141.13) --
-	(160.55,142.44) --
-	(162.50,143.75) --
-	(164.46,145.06) --
-	(166.42,146.38) --
-	(168.37,147.70) --
-	(170.33,149.02) --
-	(172.28,150.35) --
-	(174.24,151.68) --
-	(176.20,153.01) --
-	(178.15,154.35) --
-	(180.11,155.70) --
-	(182.07,157.04);
+	(154.68,138.51) --
+	(156.63,139.87) --
+	(158.59,141.24) --
+	(160.55,142.60) --
+	(162.50,143.96) --
+	(164.46,145.33) --
+	(166.42,146.71) --
+	(168.37,148.10) --
+	(170.33,149.49) --
+	(172.28,150.89) --
+	(174.24,152.30) --
+	(176.20,153.72) --
+	(178.15,155.15) --
+	(180.11,156.58) --
+	(182.07,158.02);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.30) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,101.67) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.43) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,101.12) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.62) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.58) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.97) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.26) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.38) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.65) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.62) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.88) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.70) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,126.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,127.48) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,125.68) circle (  2.50);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.73) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,101.93) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.46) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,101.05) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.63) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.60) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.22) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,101.82) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.26) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,101.18) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.67) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.53) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.99) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.24) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.32) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.53) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.90) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.49) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,126.94) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,127.52) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,125.22) circle (  2.50);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.78) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,102.13) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.33) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,101.19) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.78) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.65) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.92) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.33) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.34) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.63) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.57) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.50) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.11) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,126.74) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,129.23) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,128.52) circle (  2.50);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.39) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,102.44) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.72) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,100.99) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.80) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.46) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.91) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.43) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.25) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.68) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.26) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.87) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,122.84) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,127.31) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,128.80) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,128.33) circle (  2.50);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.29) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,102.77) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.97) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,100.91) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.51) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.53) circle (  2.50);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.39) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.43) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.79) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.65) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.85) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.55) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,126.05) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,128.36) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,123.16) circle (  2.50);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,102.22) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.56) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,100.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.75) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.45) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.92) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.46) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.36) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.49) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,119.03) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.70) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,126.40) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,127.86) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,127.28) circle (  2.50);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.08) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,102.87) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,100.83) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,100.86) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.71) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.37) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.95) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.47) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.55) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.81) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.57) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.85) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.22) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,127.21) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,127.27) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,128.95) circle (  2.50);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,101.01) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.52,102.91) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.83,101.10) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (251.13,100.89) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,101.45) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.74,101.43) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (282.05,101.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.49) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.54) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.52) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.38) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.43) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.35) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,127.24) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,126.77) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,128.39) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.35,103.48) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.66,105.47) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.96,108.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.26,113.34) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.57,118.62) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.87,123.31) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.18,127.28) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.48,128.53) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.79,130.13) circle (  2.50);
 \definecolor{drawColor}{RGB}{68,1,84}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,101.69) --
-	(222.18,101.56) --
-	(224.13,101.44) --
-	(226.09,101.33) --
-	(228.04,101.23) --
-	(230.00,101.13) --
-	(231.96,101.05) --
-	(233.91,100.97) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,101.67) --
+	(222.18,101.54) --
+	(224.13,101.42) --
+	(226.09,101.31) --
+	(228.04,101.21) --
+	(230.00,101.12) --
+	(231.96,101.04) --
+	(233.91,100.96) --
 	(235.87,100.90) --
@@
 	(241.74,100.75) --
-	(243.70,100.72) --
+	(243.70,100.73) --
 	(245.65,100.71) --
-	(247.61,100.70) --
-	(249.57,100.71) --
-	(251.52,100.73) --
-	(253.48,100.75) --
-	(255.44,100.78) --
-	(257.39,100.81) --
-	(259.35,100.85) --
-	(261.31,100.90) --
+	(247.61,100.71) --
+	(249.57,100.72) --
+	(251.52,100.74) --
+	(253.48,100.76) --
+	(255.44,100.79) --
+	(257.39,100.82) --
+	(259.35,100.86) --
+	(261.31,100.91) --
 	(263.26,100.97) --
-	(265.22,101.04) --
-	(267.18,101.13) --
-	(269.13,101.24) --
+	(265.22,101.05) --
+	(267.18,101.14) --
+	(269.13,101.25) --
 	(271.09,101.38) --
@@
 	(276.96,101.77) --
-	(278.92,101.90) --
-	(280.87,102.03) --
-	(282.83,102.18) --
-	(284.79,102.36) --
-	(286.74,102.57) --
-	(288.70,102.82) --
-	(290.66,103.12) --
-	(292.61,103.49) --
-	(294.57,103.91) --
-	(296.52,104.37) --
-	(298.48,104.88) --
-	(300.44,105.42) --
-	(302.39,106.00) --
-	(304.35,106.60) --
-	(306.31,107.22) --
-	(308.26,107.86) --
-	(310.22,108.50) --
-	(312.18,109.16) --
-	(314.13,109.83) --
-	(316.09,110.59) --
-	(318.05,111.43) --
-	(320.00,112.32) --
-	(321.96,113.24) --
-	(323.92,114.18) --
-	(325.87,115.11) --
-	(327.83,116.01) --
-	(329.79,116.85) --
-	(331.74,117.63) --
-	(333.70,118.31) --
-	(335.66,118.95) --
-	(337.61,119.59) --
-	(339.57,120.22) --
-	(341.53,120.85) --
-	(343.48,121.47) --
-	(345.44,122.06) --
-	(347.40,122.64) --
-	(349.35,123.19) --
-	(351.31,123.71) --
-	(353.27,124.20) --
-	(355.22,124.65) --
-	(357.18,125.07) --
-	(359.14,125.48) --
-	(361.09,125.86) --
-	(363.05,126.22) --
-	(365.00,126.55) --
-	(366.96,126.86) --
-	(368.92,127.15) --
-	(370.87,127.41) --
-	(372.83,127.65) --
-	(374.79,127.87);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.09) --
-	(222.18,101.92) --
-	(224.13,101.77) --
-	(226.09,101.62) --
-	(228.04,101.49) --
-	(230.00,101.37) --
-	(231.96,101.26) --
-	(233.91,101.16) --
-	(235.87,101.07) --
-	(237.83,100.99) --
-	(239.78,100.92) --
-	(241.74,100.86) --
-	(243.70,100.81) --
-	(245.65,100.78) --
-	(247.61,100.76) --
-	(249.57,100.76) --
-	(251.52,100.76) --
-	(253.48,100.78) --
-	(255.44,100.80) --
-	(257.39,100.82) --
-	(259.35,100.86) --
-	(261.31,100.91) --
-	(263.26,100.97) --
-	(265.22,101.04) --
-	(267.18,101.13) --
-	(269.13,101.24) --
-	(271.09,101.37) --
-	(273.05,101.52) --
-	(275.00,101.66) --
-	(276.96,101.79) --
-	(278.92,101.92) --
+	(278.92,101.89) --
+	(280.87,102.02) --
+	(282.83,102.17) --
+	(284.79,102.34) --
+	(286.74,102.55) --
+	(288.70,102.80) --
+	(290.66,103.10) --
+	(292.61,103.46) --
+	(294.57,103.88) --
+	(296.52,104.34) --
+	(298.48,104.84) --
+	(300.44,105.38) --
+	(302.39,105.95) --
+	(304.35,106.55) --
+	(306.31,107.16) --
+	(308.26,107.80) --
+	(310.22,108.44) --
+	(312.18,109.10) --
+	(314.13,109.77) --
+	(316.09,110.53) --
+	(318.05,111.37) --
+	(320.00,112.27) --
+	(321.96,113.20) --
+	(323.92,114.14) --
+	(325.87,115.08) --
+	(327.83,115.98) --
+	(329.79,116.83) --
+	(331.74,117.61) --
+	(333.70,118.29) --
+	(335.66,118.92) --
+	(337.61,119.56) --
+	(339.57,120.19) --
+	(341.53,120.82) --
+	(343.48,121.43) --
+	(345.44,122.02) --
+	(347.40,122.59) --
+	(349.35,123.13) --
+	(351.31,123.65) --
+	(353.27,124.12) --
+	(355.22,124.56) --
+	(357.18,124.98) --
+	(359.14,125.36) --
+	(361.09,125.73) --
+	(363.05,126.07) --
+	(365.00,126.39) --
+	(366.96,126.68) --
+	(368.92,126.95) --
+	(370.87,127.20) --
+	(372.83,127.42) --
+	(374.79,127.62);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.15) --
+	(222.18,101.99) --
+	(224.13,101.84) --
+	(226.09,101.70) --
+	(228.04,101.57) --
+	(230.00,101.45) --
+	(231.96,101.34) --
+	(233.91,101.24) --
+	(235.87,101.15) --
+	(237.83,101.07) --
+	(239.78,101.00) --
+	(241.74,100.94) --
+	(243.70,100.89) --
+	(245.65,100.86) --
+	(247.61,100.84) --
+	(249.57,100.83) --
+	(251.52,100.83) --
+	(253.48,100.85) --
+	(255.44,100.86) --
+	(257.39,100.89) --
+	(259.35,100.92) --
+	(261.31,100.96) --
+	(263.26,101.02) --
+	(265.22,101.09) --
+	(267.18,101.18) --
+	(269.13,101.28) --
+	(271.09,101.41) --
+	(273.05,101.55) --
+	(275.00,101.68) --
+	(276.96,101.80) --
+	(278.92,101.93) --
 	(280.87,102.06) --
 	(282.83,102.22) --
-	(284.79,102.41) --
-	(286.74,102.63) --
-	(288.70,102.89) --
-	(290.66,103.20) --
-	(292.61,103.57) --
-	(294.57,103.99) --
-	(296.52,104.46) --
-	(298.48,104.97) --
-	(300.44,105.51) --
-	(302.39,106.08) --
-	(304.35,106.68) --
-	(306.31,107.30) --
-	(308.26,107.94) --
-	(310.22,108.58) --
-	(312.18,109.23) --
-	(314.13,109.90) --
-	(316.09,110.66) --
-	(318.05,111.50) --
-	(320.00,112.40) --
-	(321.96,113.33) --
-	(323.92,114.27) --
-	(325.87,115.20) --
-	(327.83,116.10) --
-	(329.79,116.94) --
-	(331.74,117.70) --
-	(333.70,118.36) --
-	(335.66,118.97) --
-	(337.61,119.58) --
-	(339.57,120.18) --
-	(341.53,120.77) --
-	(343.48,121.35) --
-	(345.44,121.90) --
-	(347.40,122.43) --
-	(349.35,122.93) --
-	(351.31,123.39) --
-	(353.27,123.81) --
-	(355.22,124.19) --
-	(357.18,124.54) --
-	(359.14,124.86) --
-	(361.09,125.15) --
-	(363.05,125.41) --
-	(365.00,125.65) --
-	(366.96,125.86) --
-	(368.92,126.03) --
-	(370.87,126.19) --
-	(372.83,126.31) --
-	(374.79,126.41);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.24) --
-	(222.18,102.06) --
-	(224.13,101.90) --
-	(226.09,101.75) --
-	(228.04,101.61) --
-	(230.00,101.48) --
-	(231.96,101.36) --
-	(233.91,101.25) --
-	(235.87,101.15) --
-	(237.83,101.06) --
-	(239.78,100.99) --
-	(241.74,100.92) --
-	(243.70,100.87) --
-	(245.65,100.83) --
-	(247.61,100.80) --
-	(249.57,100.79) --
-	(251.52,100.79) --
-	(253.48,100.80) --
-	(255.44,100.81) --
-	(257.39,100.83) --
-	(259.35,100.86) --
-	(261.31,100.90) --
-	(263.26,100.95) --
-	(265.22,101.02) --
-	(267.18,101.10) --
-	(269.13,101.21) --
-	(271.09,101.34) --
-	(273.05,101.48) --
-	(275.00,101.61) --
-	(276.96,101.74) --
-	(278.92,101.87) --
-	(280.87,102.01) --
-	(282.83,102.17) --
-	(284.79,102.36) --
-	(286.74,102.58) --
-	(288.70,102.84) --
-	(290.66,103.15) --
+	(284.79,102.40) --
+	(286.74,102.61) --
+	(288.70,102.86) --
+	(290.66,103.16) --
 	(292.61,103.52) --
-	(294.57,103.94) --
-	(296.52,104.41) --
-	(298.48,104.92) --
-	(300.44,105.46) --
-	(302.39,106.04) --
-	(304.35,106.64) --
-	(306.31,107.27) --
-	(308.26,107.91) --
-	(310.22,108.56) --
-	(312.18,109.21) --
-	(314.13,109.88) --
-	(316.09,110.63) --
-	(318.05,111.45) --
-	(320.00,112.32) --
-	(321.96,113.22) --
-	(323.92,114.13) --
-	(325.87,115.04) --
-	(327.83,115.92) --
-	(329.79,116.76) --
-	(331.74,117.53) --
-	(333.70,118.23) --
-	(335.66,118.89) --
-	(337.61,119.55) --
-	(339.57,120.20) --
-	(341.53,120.86) --
-	(343.48,121.50) --
-	(345.44,122.13) --
-	(347.40,122.75) --
-	(349.35,123.34) --
-	(351.31,123.91) --
-	(353.27,124.45) --
-	(355.22,124.96) --
-	(357.18,125.45) --
-	(359.14,125.92) --
-	(361.09,126.38) --
-	(363.05,126.81) --
-	(365.00,127.23) --
-	(366.96,127.63) --
-	(368.92,128.00) --
-	(370.87,128.37) --
-	(372.83,128.71) --
-	(374.79,129.03);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.10) --
+	(294.57,103.93) --
+	(296.52,104.38) --
+	(298.48,104.87) --
+	(300.44,105.39) --
+	(302.39,105.94) --
+	(304.35,106.52) --
+	(306.31,107.12) --
+	(308.26,107.74) --
+	(310.22,108.37) --
+	(312.18,109.01) --
+	(314.13,109.68) --
+	(316.09,110.42) --
+	(318.05,111.22) --
+	(320.00,112.08) --
+	(321.96,112.96) --
+	(323.92,113.87) --
+	(325.87,114.77) --
+	(327.83,115.65) --
+	(329.79,116.49) --
+	(331.74,117.29) --
+	(333.70,118.01) --
+	(335.66,118.70) --
+	(337.61,119.40) --
+	(339.57,120.10) --
+	(341.53,120.80) --
+	(343.48,121.49) --
+	(345.44,122.18) --
+	(347.40,122.85) --
+	(349.35,123.51) --
+	(351.31,124.14) --
+	(353.27,124.76) --
+	(355.22,125.35) --
+	(357.18,125.92) --
+	(359.14,126.49) --
+	(361.09,127.03) --
+	(363.05,127.57) --
+	(365.00,128.09) --
+	(366.96,128.59) --
+	(368.92,129.09) --
+	(370.87,129.57) --
+	(372.83,130.03) --
+	(374.79,130.48);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.09) --
 	(222.18,101.94) --
@@
 	(233.91,101.24) --
-	(235.87,101.15) --
+	(235.87,101.16) --
 	(237.83,101.08) --
-	(239.78,101.01) --
-	(241.74,100.95) --
-	(243.70,100.91) --
-	(245.65,100.88) --
-	(247.61,100.86) --
-	(249.57,100.85) --
-	(251.52,100.85) --
-	(253.48,100.86) --
-	(255.44,100.87) --
-	(257.39,100.88) --
-	(259.35,100.90) --
-	(261.31,100.92) --
-	(263.26,100.96) --
-	(265.22,101.02) --
-	(267.18,101.09) --
-	(269.13,101.19) --
-	(271.09,101.31) --
-	(273.05,101.45) --
-	(275.00,101.58) --
-	(276.96,101.72) --
-	(278.92,101.86) --
+	(239.78,101.02) --
+	(241.74,100.96) --
+	(243.70,100.92) --
+	(245.65,100.89) --
+	(247.61,100.87) --
+	(249.57,100.86) --
+	(251.52,100.87) --
+	(253.48,100.88) --
+	(255.44,100.89) --
+	(257.39,100.91) --
+	(259.35,100.93) --
+	(261.31,100.96) --
+	(263.26,101.01) --
+	(265.22,101.07) --
+	(267.18,101.15) --
+	(269.13,101.24) --
+	(271.09,101.36) --
+	(273.05,101.50) --
+	(275.00,101.63) --
+	(276.96,101.75) --
+	(278.92,101.88) --
+	(280.87,102.01) --
+	(282.83,102.17) --
+	(284.79,102.35) --
+	(286.74,102.56) --
+	(288.70,102.82) --
+	(290.66,103.12) --
+	(292.61,103.48) --
+	(294.57,103.89) --
+	(296.52,104.34) --
+	(298.48,104.83) --
+	(300.44,105.36) --
+	(302.39,105.91) --
+	(304.35,106.49) --
+	(306.31,107.09) --
+	(308.26,107.71) --
+	(310.22,108.34) --
+	(312.18,108.99) --
+	(314.13,109.66) --
+	(316.09,110.40) --
+	(318.05,111.21) --
+	(320.00,112.08) --
+	(321.96,112.97) --
+	(323.92,113.88) --
+	(325.87,114.79) --
+	(327.83,115.68) --
+	(329.79,116.53) --
+	(331.74,117.32) --
+	(333.70,118.05) --
+	(335.66,118.74) --
+	(337.61,119.43) --
+	(339.57,120.13) --
+	(341.53,120.82) --
+	(343.48,121.51) --
+	(345.44,122.19) --
+	(347.40,122.86) --
+	(349.35,123.51) --
+	(351.31,124.13) --
+	(353.27,124.74) --
+	(355.22,125.32) --
+	(357.18,125.88) --
+	(359.14,126.43) --
+	(361.09,126.96) --
+	(363.05,127.48) --
+	(365.00,127.98) --
+	(366.96,128.47) --
+	(368.92,128.94) --
+	(370.87,129.40) --
+	(372.83,129.85) --
+	(374.79,130.28);
+\definecolor{drawColor}{RGB}{253,231,37}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.20) --
+	(222.18,102.04) --
+	(224.13,101.89) --
+	(226.09,101.76) --
+	(228.04,101.63) --
+	(230.00,101.51) --
+	(231.96,101.40) --
+	(233.91,101.30) --
+	(235.87,101.21) --
+	(237.83,101.13) --
+	(239.78,101.06) --
+	(241.74,101.00) --
+	(243.70,100.95) --
+	(245.65,100.92) --
+	(247.61,100.89) --
+	(249.57,100.88) --
+	(251.52,100.89) --
+	(253.48,100.89) --
+	(255.44,100.90) --
+	(257.39,100.91) --
+	(259.35,100.93) --
+	(261.31,100.95) --
+	(263.26,100.99) --
+	(265.22,101.05) --
+	(267.18,101.12) --
+	(269.13,101.22) --
+	(271.09,101.33) --
+	(273.05,101.47) --
+	(275.00,101.60) --
+	(276.96,101.73) --
+	(278.92,101.87) --
 	(280.87,102.02) --
@@
 	(284.79,102.39) --
-	(286.74,102.62) --
-	(288.70,102.90) --
-	(290.66,103.21) --
-	(292.61,103.58) --
-	(294.57,104.00) --
-	(296.52,104.47) --
-	(298.48,104.98) --
-	(300.44,105.52) --
-	(302.39,106.09) --
-	(304.35,106.69) --
-	(306.31,107.30) --
-	(308.26,107.94) --
-	(310.22,108.58) --
-	(312.18,109.23) --
-	(314.13,109.90) --
-	(316.09,110.64) --
-	(318.05,111.44) --
-	(320.00,112.29) --
-	(321.96,113.17) --
-	(323.92,114.06) --
-	(325.87,114.95) --
-	(327.83,115.82) --
-	(329.79,116.65) --
-	(331.74,117.43) --
-	(333.70,118.14) --
-	(335.66,118.81) --
-	(337.61,119.49) --
-	(339.57,120.16) --
-	(341.53,120.84) --
-	(343.48,121.51) --
-	(345.44,122.16) --
-	(347.40,122.81) --
-	(349.35,123.44) --
-	(351.31,124.05) --
-	(353.27,124.64) --
-	(355.22,125.20) --
-	(357.18,125.75) --
-	(359.14,126.29) --
-	(361.09,126.81) --
-	(363.05,127.32) --
-	(365.00,127.81) --
-	(366.96,128.29) --
-	(368.92,128.75) --
-	(370.87,129.20) --
-	(372.83,129.64) --
-	(374.79,130.06);
-\definecolor{drawColor}{RGB}{253,231,37}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (220.22,102.10) --
-	(222.18,101.95) --
-	(224.13,101.82) --
-	(226.09,101.69) --
-	(228.04,101.57) --
-	(230.00,101.46) --
-	(231.96,101.36) --
-	(233.91,101.27) --
-	(235.87,101.18) --
-	(237.83,101.10) --
-	(239.78,101.04) --
-	(241.74,100.98) --
-	(243.70,100.94) --
-	(245.65,100.91) --
-	(247.61,100.89) --
-	(249.57,100.88) --
-	(251.52,100.88) --
-	(253.48,100.89) --
-	(255.44,100.89) --
-	(257.39,100.90) --
-	(259.35,100.91) --
-	(261.31,100.94) --
-	(263.26,100.97) --
-	(265.22,101.02) --
-	(267.18,101.09) --
-	(269.13,101.18) --
-	(271.09,101.30) --
-	(273.05,101.43) --
-	(275.00,101.57) --
-	(276.96,101.70) --
-	(278.92,101.84) --
-	(280.87,101.99) --
-	(282.83,102.16) --
-	(284.79,102.36) --
-	(286.74,102.59) --
-	(288.70,102.86) --
-	(290.66,103.18) --
-	(292.61,103.54) --
-	(294.57,103.95) --
-	(296.52,104.41) --
+	(286.74,102.61) --
+	(288.70,102.88) --
+	(290.66,103.19) --
+	(292.61,103.55) --
+	(294.57,103.96) --
+	(296.52,104.42) --
 	(298.48,104.90) --
-	(300.44,105.43) --
-	(302.39,105.98) --
-	(304.35,106.57) --
-	(306.31,107.17) --
-	(308.26,107.79) --
-	(310.22,108.42) --
-	(312.18,109.07) --
-	(314.13,109.73) --
-	(316.09,110.47) --
-	(318.05,111.27) --
-	(320.00,112.13) --
-	(321.96,113.01) --
-	(323.92,113.91) --
-	(325.87,114.80) --
-	(327.83,115.67) --
-	(329.79,116.50) --
-	(331.74,117.28) --
-	(333.70,117.98) --
-	(335.66,118.64) --
-	(337.61,119.31) --
-	(339.57,119.98) --
-	(341.53,120.65) --
-	(343.48,121.31) --
-	(345.44,121.96) --
-	(347.40,122.59) --
-	(349.35,123.21) --
-	(351.31,123.81) --
-	(353.27,124.38) --
-	(355.22,124.93) --
-	(357.18,125.47) --
-	(359.14,125.98) --
-	(361.09,126.49) --
-	(363.05,126.97) --
-	(365.00,127.45) --
-	(366.96,127.90) --
-	(368.92,128.34) --
-	(370.87,128.77) --
-	(372.83,129.18) --
-	(374.79,129.58);
+	(300.44,105.42) --
+	(302.39,105.97) --
+	(304.35,106.55) --
+	(306.31,107.15) --
+	(308.26,107.77) --
+	(310.22,108.40) --
+	(312.18,109.04) --
+	(314.13,109.71) --
+	(316.09,110.44) --
+	(318.05,111.24) --
+	(320.00,112.09) --
+	(321.96,112.97) --
+	(323.92,113.86) --
+	(325.87,114.75) --
+	(327.83,115.63) --
+	(329.79,116.47) --
+	(331.74,117.27) --
+	(333.70,118.01) --
+	(335.66,118.71) --
+	(337.61,119.43) --
+	(339.57,120.14) --
+	(341.53,120.86) --
+	(343.48,121.58) --
+	(345.44,122.29) --
+	(347.40,122.99) --
+	(349.35,123.68) --
+	(351.31,124.35) --
+	(353.27,125.00) --
+	(355.22,125.64) --
+	(357.18,126.26) --
+	(359.14,126.87) --
+	(361.09,127.47) --
+	(363.05,128.07) --
+	(365.00,128.65) --
+	(366.96,129.22) --
+	(368.92,129.78) --
+	(370.87,130.33) --
+	(372.83,130.87) --
+	(374.79,131.39);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 76.98) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 86.83) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 85.55) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 86.31) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 86.44) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 88.43) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 88.90) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 91.38) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38, 94.91) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,101.20) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,110.57) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,122.63) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,135.35) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,145.96) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,153.70) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,162.89) circle (  2.50);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 76.53) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 87.79) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 88.68) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 89.22) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 89.67) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 90.63) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 91.04) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 93.34) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38, 96.81) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,102.70) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,111.21) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,122.45) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,133.90) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,143.31) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,151.06) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,157.71) circle (  2.50);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 80.80) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 92.10) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 91.50) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 90.92) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 92.43) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 92.32) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 93.28) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 95.39) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38, 98.80) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,103.90) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,111.72) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,122.19) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,133.10) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,141.14) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,148.25) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,156.21) circle (  2.50);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 85.03) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 94.32) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 94.35) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 92.82) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 94.57) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 94.98) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 95.66) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 97.29) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,100.66) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,105.31) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,112.94) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,121.90) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,131.34) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,138.75) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,145.17) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,151.07) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 76.85) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 86.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 85.75) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 86.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 86.32) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 88.36) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 88.81) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 91.36) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38, 94.82) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,101.07) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,110.42) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,122.41) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,135.30) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,145.90) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,153.64) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,163.17) circle (  2.50);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 75.76) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 88.86) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 89.39) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 88.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 90.29) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 90.98) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 91.99) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 93.59) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38, 97.21) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,102.97) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,111.07) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,122.03) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,133.67) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,142.63) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,151.12) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,157.98) circle (  2.50);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 86.18) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 92.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 92.73) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 91.68) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 92.95) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 94.30) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 94.60) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 96.08) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38, 99.66) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,104.59) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,112.09) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,121.78) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,132.20) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,139.98) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,145.80) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,154.16) circle (  2.50);
 \definecolor{drawColor}{RGB}{253,231,37}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 88.35) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 97.39) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 96.60) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 95.29) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 96.55) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 97.57) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 97.67) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 99.36) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,102.45) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,106.99) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,113.52) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,121.76) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,130.25) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,136.75) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,141.69) circle (  2.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,147.05) circle (  2.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.94, 89.43) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.24, 94.38) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.55, 96.42) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.85, 95.08) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.16, 96.19) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.46, 96.84) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.77, 97.29) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07, 98.74) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.38,101.96) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.68,106.49) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.98,113.00) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.29,121.70) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.59,130.84) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (546.90,137.37) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (557.20,142.61) circle (  2.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (567.51,149.06) circle (  2.50);
 \definecolor{drawColor}{RGB}{68,1,84}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 80.73) --
-	(414.90, 81.08) --
-	(416.85, 81.42) --
-	(418.81, 81.77) --
-	(420.76, 82.11) --
-	(422.72, 82.43) --
-	(424.68, 82.74) --
-	(426.63, 83.04) --
-	(428.59, 83.33) --
+\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 80.61) --
+	(414.90, 80.97) --
+	(416.85, 81.34) --
+	(418.81, 81.70) --
+	(420.76, 82.05) --
+	(422.72, 82.39) --
+	(424.68, 82.71) --
+	(426.63, 83.02) --
+	(428.59, 83.32) --
 	(430.55, 83.62) --
-	(432.50, 83.90) --
-	(434.46, 84.18) --
-	(436.42, 84.45) --
-	(438.37, 84.73) --
-	(440.33, 85.01) --
-	(442.29, 85.29) --
-	(444.24, 85.58) --
-	(446.20, 85.84) --
-	(448.16, 86.05) --
-	(450.11, 86.23) --
-	(452.07, 86.38) --
-	(454.03, 86.53) --
-	(455.98, 86.69) --
-	(457.94, 86.85) --
+	(432.50, 83.91) --
+	(434.46, 84.19) --
+	(436.42, 84.47) --
+	(438.37, 84.75) --
+	(440.33, 85.04) --
+	(442.29, 85.33) --
+	(444.24, 85.62) --
+	(446.20, 85.87) --
+	(448.16, 86.08) --
+	(450.11, 86.26) --
+	(452.07, 86.42) --
+	(454.03, 86.56) --
+	(455.98, 86.71) --
+	(457.94, 86.87) --
 	(459.90, 87.05) --
 	(461.85, 87.28) --
-	(463.81, 87.56) --
-	(465.77, 87.87) --
-	(467.72, 88.13) --
-	(469.68, 88.36) --
-	(471.64, 88.56) --
-	(473.59, 88.78) --
-	(475.55, 89.03) --
-	(477.51, 89.32) --
-	(479.46, 89.69) --
-	(481.42, 90.15) --
-	(483.38, 90.73) --
-	(485.33, 91.44) --
-	(487.29, 92.24) --
-	(489.24, 93.08) --
-	(491.20, 93.96) --
-	(493.16, 94.90) --
-	(495.11, 95.90) --
-	(497.07, 96.95) --
-	(499.03, 98.08) --
-	(500.98, 99.27) --
-	(502.94,100.53) --
-	(504.90,101.88) --
-	(506.85,103.32) --
-	(508.81,104.91) --
-	(510.77,106.62) --
-	(512.72,108.43) --
-	(514.68,110.31) --
-	(516.64,112.26) --
-	(518.59,114.23) --
-	(520.55,116.21) --
+	(463.81, 87.55) --
+	(465.77, 87.86) --
+	(467.72, 88.12) --
+	(469.68, 88.33) --
+	(471.64, 88.53) --
+	(473.59, 88.74) --
+	(475.55, 88.97) --
+	(477.51, 89.26) --
+	(479.46, 89.61) --
+	(481.42, 90.07) --
+	(483.38, 90.64) --
+	(485.33, 91.35) --
+	(487.29, 92.14) --
+	(489.24, 92.97) --
+	(491.20, 93.86) --
+	(493.16, 94.79) --
+	(495.11, 95.79) --
+	(497.07, 96.84) --
+	(499.03, 97.96) --
+	(500.98, 99.15) --
+	(502.94,100.42) --
+	(504.90,101.76) --
+	(506.85,103.20) --
+	(508.81,104.78) --
+	(510.77,106.49) --
+	(512.72,108.29) --
+	(514.68,110.18) --
+	(516.64,112.11) --
+	(518.59,114.08) --
+	(520.55,116.06) --
+	(522.51,118.02) --
+	(524.46,119.95) --
+	(526.42,121.81) --
+	(528.38,123.67) --
+	(530.33,125.57) --
+	(532.29,127.50) --
+	(534.25,129.47) --
+	(536.20,131.47) --
+	(538.16,133.50) --
+	(540.12,135.54) --
+	(542.07,137.59) --
+	(544.03,139.65) --
+	(545.99,141.71) --
+	(547.94,143.78) --
+	(549.90,145.86) --
+	(551.86,147.95) --
+	(553.81,150.06) --
+	(555.77,152.18) --
+	(557.72,154.32) --
+	(559.68,156.48) --
+	(561.64,158.65) --
+	(563.59,160.84) --
+	(565.55,163.04) --
+	(567.51,165.25);
+\definecolor{drawColor}{RGB}{49,104,142}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 80.55) --
+	(414.90, 81.20) --
+	(416.85, 81.85) --
+	(418.81, 82.47) --
+	(420.76, 83.07) --
+	(422.72, 83.64) --
+	(424.68, 84.19) --
+	(426.63, 84.70) --
+	(428.59, 85.20) --
+	(430.55, 85.67) --
+	(432.50, 86.13) --
+	(434.46, 86.57) --
+	(436.42, 87.00) --
+	(438.37, 87.41) --
+	(440.33, 87.82) --
+	(442.29, 88.22) --
+	(444.24, 88.61) --
+	(446.20, 88.94) --
+	(448.16, 89.21) --
+	(450.11, 89.43) --
+	(452.07, 89.60) --
+	(454.03, 89.75) --
+	(455.98, 89.90) --
+	(457.94, 90.05) --
+	(459.90, 90.22) --
+	(461.85, 90.42) --
+	(463.81, 90.68) --
+	(465.77, 90.97) --
+	(467.72, 91.21) --
+	(469.68, 91.40) --
+	(471.64, 91.57) --
+	(473.59, 91.74) --
+	(475.55, 91.93) --
+	(477.51, 92.17) --
+	(479.46, 92.47) --
+	(481.42, 92.87) --
+	(483.38, 93.37) --
+	(485.33, 94.01) --
+	(487.29, 94.72) --
+	(489.24, 95.47) --
+	(491.20, 96.27) --
+	(493.16, 97.11) --
+	(495.11, 98.00) --
+	(497.07, 98.95) --
+	(499.03, 99.96) --
+	(500.98,101.03) --
+	(502.94,102.16) --
+	(504.90,103.37) --
+	(506.85,104.67) --
+	(508.81,106.10) --
+	(510.77,107.64) --
+	(512.72,109.27) --
+	(514.68,110.98) --
+	(516.64,112.73) --
+	(518.59,114.51) --
+	(520.55,116.30) --
+	(522.51,118.07) --
+	(524.46,119.81) --
+	(526.42,121.49) --
+	(528.38,123.16) --
+	(530.33,124.87) --
+	(532.29,126.61) --
+	(534.25,128.39) --
+	(536.20,130.19) --
+	(538.16,132.01) --
+	(540.12,133.84) --
+	(542.07,135.68) --
+	(544.03,137.53) --
+	(545.99,139.38) --
+	(547.94,141.23) --
+	(549.90,143.09) --
+	(551.86,144.96) --
+	(553.81,146.84) --
+	(555.77,148.74) --
+	(557.72,150.65) --
+	(559.68,152.57) --
+	(561.64,154.50) --
+	(563.59,156.45) --
+	(565.55,158.41) --
+	(567.51,160.38);
+\definecolor{drawColor}{RGB}{53,183,121}
+
+\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 88.80) --
+	(414.90, 89.01) --
+	(416.85, 89.22) --
+	(418.81, 89.44) --
+	(420.76, 89.65) --
+	(422.72, 89.85) --
+	(424.68, 90.05) --
+	(426.63, 90.24) --
+	(428.59, 90.43) --
+	(430.55, 90.61) --
+	(432.50, 90.79) --
+	(434.46, 90.98) --
+	(436.42, 91.16) --
+	(438.37, 91.35) --
+	(440.33, 91.54) --
+	(442.29, 91.74) --
+	(444.24, 91.94) --
+	(446.20, 92.12) --
+	(448.16, 92.27) --
+	(450.11, 92.40) --
+	(452.07, 92.52) --
+	(454.03, 92.63) --
+	(455.98, 92.74) --
+	(457.94, 92.87) --
+	(459.90, 93.02) --
+	(461.85, 93.21) --
+	(463.81, 93.43) --
+	(465.77, 93.68) --
+	(467.72, 93.89) --
+	(469.68, 94.07) --
+	(471.64, 94.24) --
+	(473.59, 94.42) --
+	(475.55, 94.63) --
+	(477.51, 94.87) --
+	(479.46, 95.18) --
+	(481.42, 95.56) --
+	(483.38, 96.03) --
+	(485.33, 96.61) --
+	(487.29, 97.25) --
+	(489.24, 97.94) --
+	(491.20, 98.66) --
+	(493.16, 99.43) --
+	(495.11,100.24) --
+	(497.07,101.11) --
+	(499.03,102.02) --
+	(500.98,102.99) --
+	(502.94,104.02) --
+	(504.90,105.10) --
+	(506.85,106.26) --
+	(508.81,107.54) --
+	(510.77,108.91) --
+	(512.72,110.36) --
+	(514.68,111.88) --
+	(516.64,113.44) --
+	(518.59,115.02) --
+	(520.55,116.60) --
 	(522.51,118.17) --
-	(524.46,120.09) --
-	(526.42,121.95) --
-	(528.38,123.80) --
-	(530.33,125.70) --
-	(532.29,127.63) --
-	(534.25,129.59) --
-	(536.20,131.58) --
-	(538.16,133.59) --
-	(540.12,135.62) --
-	(542.07,137.66) --
-	(544.03,139.71) --
-	(545.99,141.76) --
-	(547.94,143.81) --
-	(549.90,145.87) --
-	(551.86,147.95) --
-	(553.81,150.04) --
-	(555.77,152.14) --
-	(557.72,154.26) --
-	(559.68,156.39) --
-	(561.64,158.54) --
-	(563.59,160.70) --
-	(565.55,162.87) --
-	(567.51,165.06);
-\definecolor{drawColor}{RGB}{59,82,139}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 80.69) --
-	(414.90, 81.29) --
-	(416.85, 81.89) --
-	(418.81, 82.47) --
-	(420.76, 83.03) --
-	(422.72, 83.56) --
-	(424.68, 84.07) --
-	(426.63, 84.55) --
-	(428.59, 85.01) --
-	(430.55, 85.45) --
-	(432.50, 85.87) --
-	(434.46, 86.29) --
-	(436.42, 86.68) --
-	(438.37, 87.07) --
-	(440.33, 87.46) --
-	(442.29, 87.83) --
-	(444.24, 88.21) --
-	(446.20, 88.53) --
-	(448.16, 88.79) --
-	(450.11, 89.00) --
-	(452.07, 89.17) --
-	(454.03, 89.32) --
-	(455.98, 89.47) --
-	(457.94, 89.62) --
-	(459.90, 89.79) --
-	(461.85, 90.00) --
-	(463.81, 90.26) --
-	(465.77, 90.55) --
-	(467.72, 90.77) --
-	(469.68, 90.95) --
-	(471.64, 91.10) --
-	(473.59, 91.25) --
-	(475.55, 91.43) --
-	(477.51, 91.65) --
-	(479.46, 91.94) --
-	(481.42, 92.33) --
-	(483.38, 92.84) --
-	(485.33, 93.48) --
-	(487.29, 94.22) --
-	(489.24, 95.00) --
-	(491.20, 95.82) --
-	(493.16, 96.71) --
-	(495.11, 97.64) --
-	(497.07, 98.63) --
-	(499.03, 99.69) --
-	(500.98,100.80) --
-	(502.94,101.98) --
-	(504.90,103.23) --
-	(506.85,104.56) --
-	(508.81,106.02) --
-	(510.77,107.61) --
-	(512.72,109.29) --
-	(514.68,111.04) --
-	(516.64,112.84) --
-	(518.59,114.66) --
-	(520.55,116.49) --
-	(522.51,118.29) --
-	(524.46,120.05) --
-	(526.42,121.75) --
-	(528.38,123.43) --
-	(530.33,125.15) --
-	(532.29,126.90) --
-	(534.25,128.68) --
-	(536.20,130.48) --
-	(538.16,132.30) --
-	(540.12,134.12) --
-	(542.07,135.96) --
-	(544.03,137.79) --
-	(545.99,139.63) --
-	(547.94,141.45) --
-	(549.90,143.29) --
-	(551.86,145.13) --
-	(553.81,146.98) --
-	(555.77,148.84) --
-	(557.72,150.71) --
-	(559.68,152.59) --
-	(561.64,154.48) --
-	(563.59,156.38) --
-	(565.55,158.29) --
-	(567.51,160.20);
-\definecolor{drawColor}{RGB}{33,144,140}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 85.11) --
-	(414.90, 85.56) --
-	(416.85, 86.01) --
-	(418.81, 86.45) --
-	(420.76, 86.87) --
-	(422.72, 87.27) --
-	(424.68, 87.65) --
-	(426.63, 88.01) --
-	(428.59, 88.36) --
-	(430.55, 88.69) --
-	(432.50, 89.01) --
-	(434.46, 89.32) --
-	(436.42, 89.62) --
-	(438.37, 89.92) --
-	(440.33, 90.22) --
-	(442.29, 90.51) --
-	(444.24, 90.80) --
-	(446.20, 91.05) --
-	(448.16, 91.24) --
-	(450.11, 91.39) --
-	(452.07, 91.51) --
-	(454.03, 91.61) --
-	(455.98, 91.71) --
-	(457.94, 91.82) --
-	(459.90, 91.96) --
-	(461.85, 92.13) --
-	(463.81, 92.35) --
-	(465.77, 92.60) --
-	(467.72, 92.81) --
-	(469.68, 92.99) --
-	(471.64, 93.14) --
-	(473.59, 93.31) --
-	(475.55, 93.50) --
-	(477.51, 93.73) --
-	(479.46, 94.03) --
-	(481.42, 94.41) --
-	(483.38, 94.89) --
-	(485.33, 95.49) --
-	(487.29, 96.17) --
-	(489.24, 96.90) --
-	(491.20, 97.67) --
-	(493.16, 98.49) --
-	(495.11, 99.36) --
-	(497.07,100.28) --
-	(499.03,101.25) --
-	(500.98,102.29) --
-	(502.94,103.38) --
-	(504.90,104.53) --
-	(506.85,105.76) --
-	(508.81,107.10) --
-	(510.77,108.55) --
-	(512.72,110.08) --
-	(514.68,111.67) --
-	(516.64,113.31) --
-	(518.59,114.97) --
-	(520.55,116.64) --
-	(522.51,118.29) --
-	(524.46,119.92) --
-	(526.42,121.49) --
-	(528.38,123.05) --
-	(530.33,124.65) --
-	(532.29,126.27) --
-	(534.25,127.93) --
-	(536.20,129.61) --
-	(538.16,131.30) --
-	(540.12,133.01) --
-	(542.07,134.73) --
-	(544.03,136.46) --
-	(545.99,138.19) --
-	(547.94,139.92) --
-	(549.90,141.66) --
-	(551.86,143.41) --
-	(553.81,145.17) --
-	(555.77,146.95) --
-	(557.72,148.74) --
-	(559.68,150.54) --
-	(561.64,152.35) --
-	(563.59,154.17) --
-	(565.55,156.01) --
-	(567.51,157.86);
-\definecolor{drawColor}{RGB}{93,200,99}
-
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 88.68) --
-	(414.90, 89.03) --
-	(416.85, 89.38) --
-	(418.81, 89.72) --
-	(420.76, 90.06) --
-	(422.72, 90.37) --
-	(424.68, 90.67) --
-	(426.63, 90.96) --
-	(428.59, 91.23) --
-	(430.55, 91.50) --
-	(432.50, 91.76) --
-	(434.46, 92.01) --
-	(436.42, 92.26) --
-	(438.37, 92.50) --
-	(440.33, 92.75) --
-	(442.29, 92.99) --
-	(444.24, 93.24) --
-	(446.20, 93.45) --
-	(448.16, 93.61) --
-	(450.11, 93.74) --
-	(452.07, 93.85) --
-	(454.03, 93.94) --
-	(455.98, 94.03) --
-	(457.94, 94.14) --
-	(459.90, 94.26) --
-	(461.85, 94.42) --
-	(463.81, 94.63) --
-	(465.77, 94.86) --
-	(467.72, 95.06) --
-	(469.68, 95.23) --
-	(471.64, 95.40) --
-	(473.59, 95.57) --
-	(475.55, 95.76) --
-	(477.51, 95.99) --
-	(479.46, 96.28) --
-	(481.42, 96.64) --
-	(483.38, 97.10) --
-	(485.33, 97.66) --
-	(487.29, 98.29) --
-	(489.24, 98.96) --
-	(491.20, 99.67) --
-	(493.16,100.43) --
-	(495.11,101.23) --
-	(497.07,102.08) --
-	(499.03,102.98) --
-	(500.98,103.92) --
-	(502.94,104.92) --
-	(504.90,105.96) --
-	(506.85,107.07) --
-	(508.81,108.29) --
-	(510.77,109.61) --
-	(512.72,111.00) --
-	(514.68,112.45) --
-	(516.64,113.94) --
-	(518.59,115.45) --
-	(520.55,116.96) --
-	(522.51,118.45) --
-	(524.46,119.90) --
-	(526.42,121.30) --
-	(528.38,122.69) --
-	(530.33,124.11) --
-	(532.29,125.55) --
-	(534.25,127.01) --
-	(536.20,128.49) --
-	(538.16,129.99) --
-	(540.12,131.49) --
-	(542.07,132.99) --
-	(544.03,134.50) --
-	(545.99,136.01) --
-	(547.94,137.51) --
-	(549.90,139.01) --
-	(551.86,140.52) --
-	(553.81,142.04) --
-	(555.77,143.57) --
-	(557.72,145.10) --
-	(559.68,146.64) --
-	(561.64,148.19) --
-	(563.59,149.74) --
-	(565.55,151.30) --
-	(567.51,152.87);
+	(524.46,119.71) --
+	(526.42,121.19) --
+	(528.38,122.67) --
+	(530.33,124.17) --
+	(532.29,125.71) --
+	(534.25,127.27) --
+	(536.20,128.85) --
+	(538.16,130.45) --
+	(540.12,132.06) --
+	(542.07,133.68) --
+	(544.03,135.31) --
+	(545.99,136.94) --
+	(547.94,138.56) --
+	(549.90,140.20) --
+	(551.86,141.85) --
+	(553.81,143.51) --
+	(555.77,145.18) --
+	(557.72,146.86) --
+	(559.68,148.55) --
+	(561.64,150.25) --
+	(563.59,151.97) --
+	(565.55,153.69) --
+	(567.51,155.43);
 \definecolor{drawColor}{RGB}{253,231,37}
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 91.91) --
-	(414.90, 92.20) --
-	(416.85, 92.48) --
-	(418.81, 92.77) --
-	(420.76, 93.04) --
-	(422.72, 93.30) --
-	(424.68, 93.55) --
-	(426.63, 93.78) --
-	(428.59, 94.01) --
-	(430.55, 94.23) --
-	(432.50, 94.44) --
-	(434.46, 94.65) --
-	(436.42, 94.86) --
-	(438.37, 95.06) --
-	(440.33, 95.27) --
-	(442.29, 95.48) --
-	(444.24, 95.69) --
-	(446.20, 95.86) --
-	(448.16, 96.00) --
-	(450.11, 96.10) --
-	(452.07, 96.18) --
-	(454.03, 96.26) --
-	(455.98, 96.33) --
-	(457.94, 96.42) --
-	(459.90, 96.52) --
-	(461.85, 96.66) --
-	(463.81, 96.84) --
-	(465.77, 97.06) --
-	(467.72, 97.25) --
-	(469.68, 97.41) --
-	(471.64, 97.58) --
-	(473.59, 97.75) --
-	(475.55, 97.94) --
-	(477.51, 98.17) --
-	(479.46, 98.45) --
-	(481.42, 98.80) --
-	(483.38, 99.22) --
-	(485.33, 99.74) --
-	(487.29,100.32) --
-	(489.24,100.94) --
-	(491.20,101.59) --
-	(493.16,102.29) --
-	(495.11,103.03) --
-	(497.07,103.81) --
-	(499.03,104.63) --
-	(500.98,105.50) --
-	(502.94,106.40) --
-	(504.90,107.36) --
-	(506.85,108.36) --
-	(508.81,109.47) --
-	(510.77,110.66) --
-	(512.72,111.92) --
-	(514.68,113.24) --
-	(516.64,114.59) --
-	(518.59,115.95) --
-	(520.55,117.31) --
-	(522.51,118.65) --
-	(524.46,119.95) --
-	(526.42,121.20) --
-	(528.38,122.43) --
-	(530.33,123.68) --
-	(532.29,124.95) --
-	(534.25,126.24) --
-	(536.20,127.54) --
-	(538.16,128.85) --
-	(540.12,130.16) --
-	(542.07,131.48) --
-	(544.03,132.79) --
-	(545.99,134.10) --
-	(547.94,135.40) --
-	(549.90,136.70) --
-	(551.86,138.00) --
-	(553.81,139.31) --
-	(555.77,140.62) --
-	(557.72,141.94) --
-	(559.68,143.26) --
-	(561.64,144.58) --
-	(563.59,145.90) --
-	(565.55,147.23) --
-	(567.51,148.56);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (412.94, 91.57) --
+	(414.90, 91.82) --
+	(416.85, 92.08) --
+	(418.81, 92.33) --
+	(420.76, 92.57) --
+	(422.72, 92.81) --
+	(424.68, 93.03) --
+	(426.63, 93.25) --
+	(428.59, 93.45) --
+	(430.55, 93.66) --
+	(432.50, 93.86) --
+	(434.46, 94.05) --
+	(436.42, 94.25) --
+	(438.37, 94.45) --
+	(440.33, 94.64) --
+	(442.29, 94.85) --
+	(444.24, 95.05) --
+	(446.20, 95.23) --
+	(448.16, 95.38) --
+	(450.11, 95.51) --
+	(452.07, 95.62) --
+	(454.03, 95.72) --
+	(455.98, 95.83) --
+	(457.94, 95.94) --
+	(459.90, 96.08) --
+	(461.85, 96.24) --
+	(463.81, 96.44) --
+	(465.77, 96.66) --
+	(467.72, 96.84) --
+	(469.68, 96.99) --
+	(471.64, 97.13) --
+	(473.59, 97.27) --
+	(475.55, 97.44) --
+	(477.51, 97.64) --
+	(479.46, 97.90) --
+	(481.42, 98.22) --
+	(483.38, 98.63) --
+	(485.33, 99.15) --
+	(487.29, 99.73) --
+	(489.24,100.35) --
+	(491.20,101.01) --
+	(493.16,101.71) --
+	(495.11,102.46) --
+	(497.07,103.25) --
+	(499.03,104.09) --
+	(500.98,104.97) --
+	(502.94,105.89) --
+	(504.90,106.87) --
+	(506.85,107.90) --
+	(508.81,109.04) --
+	(510.77,110.26) --
+	(512.72,111.56) --
+	(514.68,112.91) --
+	(516.64,114.29) --
+	(518.59,115.70) --
+	(520.55,117.10) --
+	(522.51,118.49) --
+	(524.46,119.84) --
+	(526.42,121.14) --
+	(528.38,122.42) --
+	(530.33,123.74) --
+	(532.29,125.07) --
+	(534.25,126.43) --
+	(536.20,127.80) --
+	(538.16,129.18) --
+	(540.12,130.57) --
+	(542.07,131.97) --
+	(544.03,133.37) --
+	(545.99,134.76) --
+	(547.94,136.15) --
+	(549.90,137.55) --
+	(551.86,138.95) --
+	(553.81,140.36) --
+	(555.77,141.77) --
+	(557.72,143.20) --
+	(559.68,144.63) --
+	(561.64,146.06) --
+	(563.59,147.50) --
+	(565.55,148.95) --
+	(567.51,150.40);
 \definecolor{drawColor}{gray}{0.20}

### 2020-10-17 forward_corr.R

@@ -7,8 +7,8 @@ library(tikzDevice)
 load("sir_sim_corr.rda")
 
 corr_data <- data.frame(
-  corr=1:5,
-  type=paste0("$\\rho=", c(0, 0.2, 0.4, 0.6, 0.8), "$")
+  corr=1:4,
+  type=paste0("$\\rho=", c(0, 0.25, 0.5, 0.75), "$")
 ) %>%
   mutate(
     type=factor(type, levels=type)

### 2020-10-17 sir_sim_corr.R

@@ -2,7 +2,7 @@ source("sir_corr.R")
 
 nsim <- 10
 
-corr <- c(0, 0.2, 0.4, 0.6, 0.8)
+corr <- c(0, 0.25, 0.5, 0.75)
 
 simlist_corr <- vector('list', length(corr))
 

### 2020-10-17 serial.tex
figure label
sig state

@@
 The generation- and serial-interval distributions are key, but different, quantities in outbreak analyses.
-Recent theoretical studies suggest that the two distributions give different estimates of the reproduction number \RR as inferred from the observed exponential growth rate $r$;
-however, both intervals, by definition, describe disease transmission at the individual level.
+Recent theoretical studies suggest that the two distributions give different estimates of the reproduction number \RR as inferred from the observed exponential growth rate $r$.
 Here, we show that estimating \RR based on $r$ and the serial-interval distribution, when defined from the correct reference time and cohort, gives the same estimate as using $r$ and the generation-interval distribution.
@@
 
+\renewcommand\thefigure{S\arabic{figure}}    
+\setcounter{figure}{0}
+
 \subsection{Simulations with correlated intrinsic incubation periods and intrinsic generation intervals.}

### 2020-11-08 serial.tex
submitted
no competing interests
format & supp

@@
 \usepackage{natbib}
-\bibliographystyle{chicago}
+\bibliographystyle{unsrt}
 \date{\today}
@@
 
-The reproduction number \RR is one of the most important characteristics of an emerging epidemic, such as the current pandemic of coronavirus disease 2019 (COVID-19) \citep{majumder2020early}.
+The reproduction number \RR is one of the most important characteristics of an emerging epidemic, such as the current pandemic of coronavirus disease 2019 (COVID-19) \cite{majumder2020early}.
 The reproduction number is defined as the average number of secondary cases caused by a primary case.
-The value in a fully susceptible population --- the ``basic'' reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population, and the amount of intervention necessary to eliminate it in simple cases \citep{anderson1991infectious}.
-Since the reproduction number represents an average \citep{diekmann1990definition, anderson1991infectious}, it fails to capture heterogeneity among individuals or across space.
+The value in a fully susceptible population --- the ``basic'' reproduction number \Ro --- allows us to predict the extent to which an infection will spread in the population, and the amount of intervention necessary to eliminate it in simple cases \cite{anderson1991infectious}.
+Since the reproduction number represents an average \cite{anderson1991infectious,diekmann1990definition}, it fails to capture heterogeneity among individuals or across space.
 The reproduction number also fails to provide any information about the time scale of disease transmission.
@@
 Direct estimates based on observed infections will typically be biased down when some infections cannot be observed.
-A common method of estimating \RR near the beginning of an epidemic is based on the population-level exponential growth rate $r$, which can often be estimated robustly from case reports \citep{mills2004transmissibility, ma2014estimating}.
-The growth rate $r$ and the reproduction number \RR are linked by the generation-interval distribution \cite{wallinga2007generation}, where the generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee) \citep{svensson2007note}.
+A common method of estimating \RR near the beginning of an epidemic is based on the population-level exponential growth rate $r$, which can often be estimated robustly from case reports \cite{mills2004transmissibility, ma2014estimating}.
+The growth rate $r$ and the reproduction number \RR are linked by the generation-interval distribution \cite{wallinga2007generation}, where the generation interval is defined as the time between when an individual (infector) is infected and when that individual infects another person (infectee) \cite{svensson2007note}.
 
 Since generation intervals measure time between infection events, which can be difficult to observe in practice, generation intervals are often replaced with serial intervals.
-The serial interval is defined as the time between when an infector and an infectee develop symptoms \citep{svensson2007note}.
+The serial interval is defined as the time between when an infector and an infectee develop symptoms \cite{svensson2007note}.
 While generation and serial intervals both measure the time scale of disease transmission, they measure fundamentally different quantities. 
-In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean in many contexts \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
-Serial intervals can in some cases even take negative values in the presence of presymptomatic transmission \citep{he2020temporal}, whereas generation intervals must be positive.
+In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean in many contexts \cite{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
+Serial intervals can in some cases even take negative values in the presence of presymptomatic transmission \cite{he2020temporal}, whereas generation intervals must be positive.
 
-Although these distributions were clearly and distinctly defined over a decade ago \citep{svensson2007note}, 
+Although these distributions were clearly and distinctly defined over a decade ago \cite{svensson2007note}, 
 the need for a better conceptual and theoretical framework for understanding their differences is becoming clearer as the COVID-19 pandemic unfolds.
 Researchers continue to base inferences about COVID-19 on both generation and serial intervals without clearly distinguishing between them (e.g., \cite{tempvar,du2020serial,he2020temporal,wu2020nowcasting,zhao2020serial}), and, in some cases, explicitly conflate the definitions of the two intervals (e.g., \cite{anderson2020will,hellewell2020feasibility}).
-This confusion is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \citep{thompson2019improved}.
+This confusion is apparent even in standard software for estimating \RR, such as \texttt{EpiEstim}, in which the serial-interval distribution is used to infer time-dependent \RR \cite{thompson2019improved}.
 These studies are examples of many---indeed, it is a common practice to use the serial and generation intervals interchangeably.
@@
 While the epidemic is growing exponentially, the spread of infection can be characterized as a \emph{renewal process} based on previous incidence of infection, the associated generation-interval distribution, and the average infectiousness of an infected individual.
-It is well established that this renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \citep{wallinga2007generation}.
+It is well established that this renewal formulation allows us to link the exponential growth rate of an epidemic $r$ with its reproduction number \RR using the generation-interval distribution \cite{wallinga2007generation}.
 However, the serial-interval distribution also describes a renewal process --- in this case, the creation of a new \emph{symptomatic} case based on a symptomatic case in the previous generation.
@@
 In contexts where the serial- and generation-interval distributions differ, current theory has no explanation for how two different distributions could provide identical estimates of \RR from $r$. 
-In fact, recent theory suggest that using the serial-interval can underestimate the reproduction number \citep{britton2019estimation, ganyani2020estimating}.
+In fact, recent theory suggest that using the serial-interval can underestimate the reproduction number \cite{britton2019estimation, ganyani2020estimating}.
 However, these studies rely on \emph{intrinsic} distributions of incubation periods and generation intervals that neglect the population-level dynamics of disease spread.
@@
 Here we show that, by correctly defining and calculating the ``forward'' serial-interval distribution (i.e., a distribution of serial intervals from a cohort of infectors that developed symptoms at the same time) that connects symptom onset dates, we can resolve this discrepancy.
-These forward intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
+These forward intervals are different from the ``intrinsic'' serial intervals that previous studies have relied on \cite{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence, britton2019estimation}.
 During an ongoing epidemic, all observed epidemiological delays (e.g., incubation period) between primary (e.g., infection) and secondary (e.g., symptom onset) events are subject to backward biases: when the incidence of primary events is increasing (or decreasing), we are more likely to observe shorter (respectively longer) intervals.
@@
 For example, an infectious contact results in infection only if the contacted individual is susceptible (and has not already been infected) ---
-this is one mechanism that causes realized generation intervals (time between actual infection events) to differ from from the intrinsic generation intervals (time between infection and infectious contacts) \citep{park2020inferring}.
+this is one mechanism that causes realized generation intervals (time between actual infection events) to differ from from the intrinsic generation intervals (time between infection and infectious contacts) \cite{park2020inferring}.
 In this example, the difference between intrinsic and realized time distributions can be attributed to the fact that the fraction of susceptible individuals is itself dynamic.
@@
 Between-individual forward delay distributions, such as generation- or serial-interval distributions, depend on epidemic dynamics.
-For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical process of susceptible depletion, as well as due to other factors like behavioral change or interventions \citep{kenah2008generation, nishiura2010time, champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.
+For example, forward generation intervals often become shorter as an epidemic progresses due to the dynamical process of susceptible depletion, as well as due to other factors like behavioral change or interventions \cite{kenah2008generation, nishiura2010time, champredon2015intrinsic}: if it is harder to infect later in the course of infection, then proportionally more intervals will be short.
 
@@
 
-The serial interval is defined as the time between when an infector becomes symptomatic and when their infectee becomes symptomatic \citep{svensson2007note}.
+The serial interval is defined as the time between when an infector becomes symptomatic and when their infectee becomes symptomatic \cite{svensson2007note}.
 Previous studies have often expressed serial intervals $\tau_{\rm s}$ in the form (\fref{diagram}A):
@@
 interval between the infector and the infectee.
-These studies concluded that the serial and generation intervals have the same mean when $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
+These studies concluded that the serial and generation intervals have the same mean when $\tau_{\rm i1}$ and $\tau_{\rm i2}$ are drawn from the same distributions \cite{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}.
 However, distributions of realized incubation periods, $\tau_{\rm i1}$ and $\tau_{\rm i2}$ will be identical only if we assume that they are intrinsic to individuals (and not dependent on epidemic dynamics at the population-level) ---
@@
 \end{equation}
-where the case reproduction number $\Rc (\pinf)$ is defined as the average number of secondary cases that a primary case infected at time $\pinf$ will generate over the course of their infection \citep{fraser2007estimating}.
+where the case reproduction number $\Rc (\pinf)$ is defined as the average number of secondary cases that a primary case infected at time $\pinf$ will generate over the course of their infection \cite{fraser2007estimating}.
 We describe the forward incubation periods and the forward generation intervals using a joint probability distribution because onset of symptoms and transmission potential jointly depend on the life history of a disease;
@@
 We illustrate changes in forward and backward serial intervals over the course of an epidemic by applying our framework to a specific example of an epidemic model.
-We model disease spread with a renewal-equation model \citep{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
+We model disease spread with a renewal-equation model \cite{heesterbeek1996concept, diekmann2000mathematical, roberts2004modelling, aldis2005integral, roberts2007model, champredon2018equivalence}.
 Ignoring births and deaths, changes in the proportion of susceptible individuals $S(t)$ and incidence of infection $i(t)$ can be described as:
@@
 \end{align}
-where $\RR(t)$ is the instantaneous reproduction number (i.e., the average number of secondary cases that a primary case infected at time $t$ will generate if conditions at time $t$ remain unchanged \citep{fraser2007estimating}), and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a population where changes in $\RR(t)$ is negligible \citep{champredon2015intrinsic}).
+where $\RR(t)$ is the instantaneous reproduction number (i.e., the average number of secondary cases that a primary case infected at time $t$ will generate if conditions at time $t$ remain unchanged \cite{fraser2007estimating}), and $\gdist(\tau)$ is the intrinsic generation-interval distribution (i.e., the forward generation-interval distribution of a primary case in a population where changes in $\RR(t)$ is negligible \cite{champredon2015intrinsic}).
 This model assumes that $g(\tau)$ remains constant through time -- in other words, that epidemic dynamics are driven by changes in transmission rate. 
-This assumption may not be well suited to individual-based intervention such as case isolation \citep{fraser2007estimating};
-nonetheless, this form has been widely used in the literature and has been successfully applied in modeling the current COVID-19 pandemic \citep{gostic2020practical}.
+This assumption may not be well suited to individual-based intervention such as case isolation \cite{fraser2007estimating};
+nonetheless, this form has been widely used in the literature and has been successfully applied in modeling the current COVID-19 pandemic \cite{gostic2020practical}.
 
@@
 \cite{flaxman2020estimating} used a similar framework to evaluate the impact of nonpharmaceutical interventions on the spread of COVID-19 in 11 countries.
-Then, the forward generation-interval for a cohort of individuals that were infected at time $\psymp$ follows \citep{champredon2015intrinsic}:
+Then, the forward generation-interval for a cohort of individuals that were infected at time $\psymp$ follows \cite{champredon2015intrinsic}:
 \begin{equation}
@@
 During the initial phase of an epidemic, the proportion susceptible remains approximately constant ($S(t) \approx S(0)$) and incidence of infection grows exponentially: $i(t) \approx i_0\exp(rt)$.
-During this period, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the initial reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \citep{wallinga2007generation}.
+During this period, the intrinsic generation-interval distribution provides the correct link between the exponential growth rate $r$ and the initial reproduction number $\RR=\Ro S(0)$ based on the Euler-Lotka equation \cite{wallinga2007generation}.
 Here, we focus on the estimates of the basic reproduction number \Ro (the value of \RR in a fully susceptible population, $S(t) \approx 1$):
@@
 where the normalization constant $\phi$ is determined by the requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
-We provide a mathematical proof of this relationship in Supplementary Materials.
+We provide a mathematical proof of this relationship in SI Appendix S3.
 Since we do not make any assumptions about the shape of the joint distribution $h$ between incubation periods and the generation intervals, \eref{Rforward} holds in general whether or not there is a presymptomatic transmission period.
@@
 requirement that $\int_{-\infty}^\infty q(\tau)\,\dtau=1$.
-Rather than numerically integrating over closed forms of $g$, $f_0$, and $q$ to estimate $\Ro$, we use simulation-based approaches for simplicity (Supplementary Materials).
+Rather than numerically integrating over closed forms of $g$, $f_0$, and $q$ to estimate $\Ro$, we use simulation-based approaches for simplicity (see SI Appendix S4).
 
@@
 that onset of symptoms and infectiousness occur simultaneously), provides a special case.
-In this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see Supplementary Materials).
+In this case, the forward serial- and generation-intervals follow the same distributions during the exponential growth phase because (i) infected individuals can only transmit after symptom onset and (ii) the time between symptom onset and infection is independent of the incubation period of an infector (see SI Appendix S5).
 Everywhere else in this paper, however, we do not assume that the incubation and exposed periods are equivalent.
@@
 Here, we use a bivariate lognormal distribution to model the joint probability distribution $h$ of intrinsic incubation periods and intrinsic generation intervals (in the renewal equation model, \eref{renewal}) while allowing for the possibility that they might be correlated.
-Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset \citep{he2020temporal}, we generally expect the generation intervals to be positively correlated with the incubation period:
+Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset \cite{he2020temporal}, we generally expect the generation intervals to be positively correlated with the incubation period:
 that is, individuals who develop symptoms later are more likely to transmit later.
@@
 Comparing the shapes of the initial forward serial-interval distribution (\eref{initialSI}) and the intrinsic generation-interval distribution allows us to better understand how different forward distributions lead to identical estimates of \Ro.
-In general, distributions with higher means and less variability lead to higher \Ro for a given $r$ \citep{wallinga2007generation, weitz2015modeling, park2019practical}.
+In general, distributions with higher means and less variability lead to higher \Ro for a given $r$ \cite{wallinga2007generation, weitz2015modeling, park2019practical}.
 When incidence is growing exponentially, forward serial intervals have higher means (\fref{rR}C) and squared coefficients of variation (\fref{rR}D) than the intrinsic generation-interval distribution.
@@
 Intrinsic incubation periods and intrinsic generation intervals are assumed to be independent of each other for simplicity.
-See Supplementary Materials for simulations with correlated incubation periods and generation intervals.
+See SI Appendix Figure S1 for simulations with correlated incubation periods and generation intervals.
 See Table 1 for parameter values.
@@
 The initial forward serial-interval distribution captures the exponential growth phase of an epidemic.
-We now explore how forward and backward serial intervals can vary over the course of an epidemic using deterministic and stochastic simulations based on the renewal equations (see Supplementary Materials) using parameters in Table 1;
-we further assume $\Ro=2.5$ to reflect the transmission dynamics of COVID-19 in China \citep{doi:10.1098/rsif.2020.0144}.
+We now explore how forward and backward serial intervals can vary over the course of an epidemic using deterministic and stochastic simulations based on the renewal equations (see SI Appendix S1--S2) using parameters in Table 1;
+we further assume $\Ro=2.5$ to reflect the transmission dynamics of COVID-19 in China \cite{doi:10.1098/rsif.2020.0144}.
 While the forward serial-interval distribution is our primary focus, understanding the differences between the forward and the backward distributions is important because the observed intervals during an ongoing epidemic are often the backward ones:
@@
 The dashed line represents the maximum and minimum observable delays across the range of reported symptom onset dates.
-(D) Cohort-averaged estimates of \Ro assuming doubling period of 6 and 8 days \citep{li2020early, wu2020nowcasting}.
+(D) Cohort-averaged estimates of \Ro assuming doubling period of 6 and 8 days \cite{li2020early, wu2020nowcasting}.
 Ribbons represent the associated 95\% bootstrap confidence intervals.
@@
 this sudden decrease is due to changes in the forward serial intervals consistent with the dynamics seen in our simulations (\fref{obsrR}).
-The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \citep{majumder2020early, doi:10.1098/rsif.2020.0144}:
+The cohort-averaged estimates of \Ro based on the early forward serial intervals are also consistent with previous estimates of \Ro of the COVID-19 epidemic in China \cite{majumder2020early, doi:10.1098/rsif.2020.0144}:
 $\Ro = 2.6$ (95\% CI: 2.2--3.1) and $\Ro = 3.4$ (95\% CI: 2.7 -- 4.3) based on a doubling period of 8 or 6 days, respectively, using serial-interval data from infectors who developed symptoms by January 17th.
@@
 Although their true correlation will depend on viral load dynamics, we expect our conclusions about decreasing serial intervals of COVID-19 to be robust, as individuals with longer incubation periods will generally have a longer time window to transmit before symptom onset.
-In general, the impact of increasing backward incubation periods on the forward serial intervals are likely to be disease-specific---for example, we show in Supplementary Materials that the initial forward serial-interval distribution can be equivalent to the intrinsic generation-interval distribution, regardless of the growth rate $r$, due to independence between the incubation period and time from symptom onset to transmission and the lack of presymptomatic transmission.
+In general, the impact of increasing backward incubation periods on the forward serial intervals are likely to be disease-specific---for example, we show in SI Appendix S5 that the initial forward serial-interval distribution can be equivalent to the intrinsic generation-interval distribution, regardless of the growth rate $r$, due to independence between the incubation period and time from symptom onset to transmission and the lack of presymptomatic transmission.
 Future studies trying to interpret realized serial intervals should consider carefully the joint distribution between the generation intervals and incubation periods.
@@
 First, serial intervals should be cohorted based on the symptom onset date of the infector (and not of the infectee) whenever possible.
-Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals differs from this expectation, and changes through time due to epidemic dynamics.
+Previous studies have often regarded serial intervals as an intrinsic quantity, having the same mean as the intrinsic generation interval \cite{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}, but the distribution (and the mean) of observed serial intervals differs from this expectation, and changes through time due to epidemic dynamics.
 Second, aggregating serial intervals across different cohorts and epidemic periods should be avoided because the realized serial-interval distribution can be subject to different censoring and epidemiological biases:
@@
 Previous studies have shown the importance of forward vs. backward
-measurement of generation intervals \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
+measurement of generation intervals \cite{nishiura2010time,champredon2015intrinsic,britton2019estimation};
 we generalize these ideas and show that they apply to other epidemiological distributions.
-Some studies during the early phases of the COVID-19 epidemics have tried to correct for the backward biases \citep{verity2020estimates}, but changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
+Some studies during the early phases of the COVID-19 epidemics have tried to correct for the backward biases \cite{verity2020estimates}, but changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
 Cohorting epidemiological delays by the primary event time can help avoid backward biases (although censoring biases can still exist) as well as detect potential changes in the distribution.
@@
 Here, we assume that all individuals develop symptoms and that the entire transmission process, including all relevant epidemiological delays, is known exactly.
-In practice, identifying who infected whom is difficult in general, and asymptomatic and presymptomatic transmission of COVID-19 exacerbates this difficulty \citep{bai2020presumed,he2020temporal,wei2020presymptomatic}.
+In practice, identifying who infected whom is difficult in general, and asymptomatic and presymptomatic transmission of COVID-19 exacerbates this difficulty \cite{bai2020presumed,he2020temporal,wei2020presymptomatic}.
 Biases in the observed serial intervals will necessarily bias the estimates of \RR. 
 Furthermore, when one of the individuals in a transmission pair is asymptomatic, there is no symptom-based serial interval.
-Neglecting the time scale of asymptomatic transmission may also bias the estimates of \RR \citep{park2020time}.
+Neglecting the time scale of asymptomatic transmission may also bias the estimates of \RR \cite{park2020time}.
 
 Despite these limitations, our analysis of serial intervals of COVID-19 from China provides further support for our theoretical framework, demonstrating temporal variation in serial intervals and its effect on the estimates of \RR.
-Most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
+Most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \cite{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
 Our study provides a rationale for reassessing estimates of
@@
 
-\pagebreak
+\section*{Competing interests}
 
-\section{Supplementary Materials}
-
-\subsection{Deterministic simulation}
-
-We simulate the renewal equation model using a discrete-time approximation:
-\begin{align}
-i(t) &= \Ro S(t-\Delta t) \sum_{m=1}^{\tsub{m}{max}} i(t-m \Delta t) \hat{\gdist}(m \Delta t) \nonumber \\
-S(t) &= S(t-\Delta t) - i(t)
-\end{align}
-where $\hat{\gdist}$ is a discrete-time intrinsic generation-interval distribution that satisfies the following:
-\begin{equation}
-\hat{\gdist}(m \Delta t) = \frac{\gdist(m \Delta t)}{\sum_{i=1}^\ell \gdist(m \Delta t)}, \quad m=1, \dots, \tsub{m}{max}.
-\end{equation}
-The continuous-time intrinsic generation-interval distribution is parameterized using a log-normal distribution (Table 1). We define the intrinsic incubation period distribution in a similar manner:
-\begin{equation}
-\hat{\idist}(m \Delta t) = \frac{\idist(m \Delta t)}{\sum_{i=1}^\ell \idist(m \Delta t)}, \quad m=1, \dots, \tsub{m}{max},
-\end{equation}
-where its continuous-time analog is also based on a log-normal distribution.
-For simplicity, we assume that the forward incubation periods and intrinsic generation intervals are independent:
-\begin{equation}
-\hat{h}(m \Delta t, n \Delta t) = \hat{\idist}(m \Delta t)\hat{\gdist}(n \Delta t), \quad m,n=1, \dots, \tsub{m}{max}.
-\end{equation}
-We use $\Delta t = 0.025\,\textrm{days}$ and $\tsub{m}{max}=2001$ for discretization steps.
-
-We initialize the simulation with population size $N$=40,000 as follows:
-\begin{align}
-i(m \Delta t) &= C \exp(r m \Delta t), \quad m=1, \dots, \tsub{m}{max}\nonumber \\
-S(m \Delta t) &= N - \sum_{n=1}^m i(n \Delta t), \quad m=1, \dots, \tsub{m}{max}
-\end{align}
-where $C$ is chosen such that $\sum_{n=1}^{\tsub{m}{max}} i(m \Delta t)=10$.
-These initial conditions allow the model to follow exponential growth from time $\Delta t (\tsub{m}{max} + 1)$ without any transient behaviors.
-
-\subsection{Stochastic simulation}
-
-We run stochastic simulations of the renewal equation model using an individual-based model on a fully connected network (i.e., homogeneous population) based on the Gillespie algorithm that we developed earlier \citep{park2020inferring}.
-First, we initialize an epidemic with $I(0)$ infected individuals (nodes) in a fully connected network of size $N$. 
-For each initially infected individual, we draw number of infectious contacts from a Poisson distribution with the mean of \Ro and the corresponding generation intervals for each contact from a log-normal distribution (Table 1).
-Contactees are uniformly sampled from the total population.
-All contactees are sorted into event queues based on their infection time.
-We update the current time to the infection time of the first person in the queue.
-Then, the first person in the queue makes contacts based on the Poisson offspring distribution described earlier and their contactees are added to the sorted queue.
-Whenever contactees are added to the sorted queue, we remove all duplicated contacts (but keep the first one) as well as contacts made to individuals that have already been infected.
-Simulations continue until there are no more individuals in the queue.
-We simulate 10 epidemics with $I(0)=10$ and $N$=40,000.
-
-\subsection{Linking $r$ and \Ro using serial-interval distributions}
-
-The intrinsic generation-interval distribution $\gdist(\tau)$ provides a link between $r$ and \Ro via the Euler-Lotka equation \citep{wallinga2007generation}:
-\begin{equation}
-\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) \gdist(\tau) \dtau\,.
-\end{equation}
-In this section, we prove that the initial forward serial-interval distribution $f_0(\tau)$ also estimates the same \Ro from $r$, except that integral extends to $\tau=-\infty$ rather than beginning at $\tau=0$, because serial intervals can be negative:
-\begin{equation}
-\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \dtau\,.
-\label{eq:ptarget}
-\end{equation}
-Here, the initial forward serial-interval distribution $f_{0}(\tau)$ is defined as:
-\begin{equation}
-f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1\,,
-\label{eq:fdist}
-\end{equation}
-where $h$ is the joint probability distribution describing the
-intrinsic generation-interval distribution $g$ and the intrinsic
-incubation period distribution $\idist$ (see \eref{marginal} in the
-main text), and the normalization constant $\phi$ is determined by the
-requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.
-
-In order to verify \eref{ptarget}, we first rewrite the integral in \eref{fdist} by substituting $-\alpha_1$ for $\alpha_1$, and then changing the order of integration:
-\begin{align}
-f_{0}(\tau) &= \frac{1}{\phi} \int_0^\infty \int_{-\pinf}^{\tau} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \idist(\tau - \sinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf\,,\nonumber \\
-&= \frac{1}{\phi} \int_{-\infty}^{\tau} \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\idist(\tau - \sinf)\,\mathrm{d}\pinf\, \mathrm{d}\sinf\,.
-\label{eq:newforward}
-\end{align}
-To further simplify the expression, we define $z(\sinf)$ as follows:
-\begin{equation}
-z(\sinf) = \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \,\mathrm{d}\pinf\,.
-\end{equation}
-Substituting $z(\sinf)$ into \eref{newforward} we obtain:
-\begin{equation}
-f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{\tau} z(\sinf) \idist(\tau - \sinf) \,\mathrm{d}\sinf\,,.
-\end{equation}
-Writing $\hat{z}$ for a normalized version of $z$,
-\begin{equation}\hat{z}(\sinf) = \frac{z(\sinf)}{\int_{-\infty}^\infty z(x) \dx}\,,\end{equation}
-we can now express the initial forward serial-interval distribution
-$f_0$ as a convolution of $\hat{z}$ and $\idist$:
-\begin{equation}
-f_{0}(\tau) = \frac{1}{\hat{\phi}} \int_{-\infty}^{\tau} \hat{z}(\sinf) \idist(\tau - \sinf)\, \mathrm{d}\sinf\,,
-\end{equation}
-where $\hat{\phi} = \phi/\int_{-\infty}^\infty z(x) \dx$.
-
-Since the right hand side of \eref{ptarget} is also a
-Laplace transform of $f_0=\hat{z}*\idist$, we can express it as the product
-of Laplace transforms of $\hat{z}$ and $\idist$:
-\begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) \hat{z}(\tau)\, \mathrm{d} \tau \int_{0}^\infty \exp(-r\tau) \idist(\tau) \dtau\,.
-\label{eq:newtarget}
-\end{equation}
-In order to derive an expression for a Laplace transform of $\hat{z}$, we have to first derive an analytical expression for $\int_{-\infty}^\infty z(x) \dx$.
-By changing the order of integration, we have:
-\begin{align}
-\int_{-\infty}^\infty z(\sinf) \mathrm{d}\sinf &= \int_{-\infty}^\infty \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf \,\mathrm{d}\sinf\nonumber\,,\\
-&= \int_{0}^\infty \int_{-\pinf}^\infty \exp(- r \pinf) h(\pinf, \sinf+\pinf)\, \mathrm{d}\sinf\,\mathrm{d} \pinf\,.
-\end{align}
-Since $\idist$ is a marginal probability distribution of $h$, it follows that:
-\begin{equation}
-\int_{-\infty}^\infty z(\sinf) \mathrm{d}\sinf = \int_{0}^\infty \exp(- r \pinf) \idist(\pinf)\, \mathrm{d}\pinf\,.
-\end{equation}
-Then, we have:
-\begin{equation}
-\hat{z}(\sinf) = \frac{\int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf}{\int_{0}^\infty \exp(- r \pinf) \idist(\pinf)\, \mathrm{d}\pinf}\,.
-\end{equation}
-Substituting the expression into \eref{newtarget}, we have:
-\begin{equation}
-\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau = \int_{-\infty}^\infty \exp(-r\sinf) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf\,\mathrm{d}\sinf\,.
-\label{eq:newtarget2}
-\end{equation}
-
-Recall that $g$ is also a marginal probability distribution of $h$:
-\begin{equation}
-g(\tau) = \int_0^\infty h(x, \tau) \,\mathrm{d}x\,.
-\end{equation}
-We can then substitute $\tau = \pinf + \sinf$ into \eref{newtarget2} and apply change of variables to obtain:
-\begin{align}
-&\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau\\
-&=\int_{-\infty}^{\infty} \exp(-r\sinf) \int_{\max(0, -\sinf)}^\infty \exp(- r \pinf) h(\pinf, \sinf+\pinf) \,\mathrm{d} \pinf \,\mathrm{d}\sinf \\
-&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \tau) h(\pinf, \tau)\, \mathrm{d} \pinf\, \mathrm{d}\tau\\
-&=\int_{0}^{\infty} \exp(-r\tau) g(\tau) \dtau =\frac{1}{\Ro}
-\end{align}
-Therefore, the initial forward serial-interval distribution and the intrinsic generation-interval distribution give the same estimates of \Ro from $r$.\qed
-
-\subsection{Comparing the estimates of \Ro using the initial forward and the intrinsic serial-interval distributions}
-
-We use a simulation-based approach to compare the estimates of \Ro based on the serial- and generation-interval distributions. 
-To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and log-scale correlation $\rho$;
-the multivariate log-normal distribution is parameterized based on parameter estimates for COVID-19 (Table 1).
-We construct forward serial intervals during the exponential growth period as follows:
-\begin{equation}
-F_i = -X_{1,i} + (G_i|X_{1,i}) + X_{2,i},
-\end{equation}
-where the backward incubation period $X_{1,i}$ of an infector is simulated by drawing random log-normal samples $Y_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $Y_i$, each weighted by the inverse of the exponential growth function $\exp(-rY_i)$;
-the intrinsic generation interval conditional on the incubation period of the infector $(G_i|X_{1,i})$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(X_{1,i}) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
-the forward incubation period $X_{2,i}$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
-We then calculate the basic reproduction number \Ro using the empirical estimator:
-\begin{equation}
-\Ro = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r F_i)}.
-\end{equation}
-We compare this with an estimate of \Ro based on the intrinsic serial-interval distribution which has the same mean as the intrinsic generation-interval distribution \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
-\begin{equation}
-  \Rintrinsic = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r Q_i)},
-\end{equation}
-where
-\begin{equation}
-Q_i = -Y_i + (G_i|Y_i) + X_{2,i}.
-\end{equation}
-
-\subsection{Applications: SEIR model}
-
-Consider a Susceptible-Exposed-Infectious-Recovered model:
-\begin{align}
-\frac{\mathrm{d}S}{\mathrm{d}t} &= - \beta S I \nonumber \\
-\frac{\mathrm{d}E}{\mathrm{d}t} &= \beta S I - \gamma_E E\nonumber\\
-\frac{\mathrm{d}I}{\mathrm{d}t} &= \gamma_E E - \gamma_I I\nonumber \\
-\frac{\mathrm{d}R}{\mathrm{d}t} &= \gamma_I I
-\end{align}
-where $\beta$ is the transmission rate, $1/\gamma_E$ is the mean latent period, and $1/\gamma_I$ is the mean infectious period.
-We further assume that the latent period is equivalent to incubation period; in other words, infected individuals can only transmit after symptom onset.
-Then, the generation interval will be always longer than the incubation period.
-
-The joint probability distribution of the intrinsic incubation periods and intrinsic generation intervals for this model can be written as:
-\begin{equation}
-h(x, \tau) = \begin{cases}
-0 & x > \tau\\
-\gamma_I \gamma_E \exp(-\gamma_I (\tau-x)-\gamma_E x) & x \leq \tau
-\end{cases}
-\end{equation}
-Then, the intrinsic generation-interval distribution is given by:
-\begin{align}
-g(\tau) &= \int_0^\tau h(x, \tau) \dx\nonumber \\
-&= \frac{\gamma_I \gamma_E}{\gamma_E-\gamma_I} (\exp(-\gamma_I \tau) - \exp(-\gamma_E \tau))
-\end{align}
-On the other hand, the initial forward serial-interval distribution is given by:
-\begin{align}
-f_{0}(\tau) &\propto \int_{-\infty}^{0} \int_{0}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf \nonumber \\
-&\propto \int_{-\infty}^{0} \int_{0}^{\tau}\exp(r \pinf) \exp(-\gamma_I \sinf+ \gamma_E \pinf) \exp(-\gamma_E(\tau-\sinf)) \, \mathrm{d}\sinf\,\mathrm{d}\pinf \nonumber \\
-&\propto  \exp(-\gamma_E \tau) \int_{-\infty}^{0} \int_{0}^{\tau} \exp((\gamma_E-\gamma_I) \sinf) \exp((r+ \gamma_E) \pinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf \nonumber \\
-&\propto  (\exp(-\gamma_I \tau) - \exp(-\gamma_E \tau)) \int_{-\infty}^{0} \exp((r+ \gamma_E) \pinf)\,\mathrm{d}\pinf \nonumber \\
-&\propto  \exp(-\gamma_I \tau) - \exp(-\gamma_E \tau)
-\end{align}
-Therefore, both the intrinsic generation intervals and the initial forward serial intervals are identically distributed and have the same mean.
-
-\renewcommand\thefigure{S\arabic{figure}}    
-\setcounter{figure}{0}
-
-\subsection{Simulations with correlated intrinsic incubation periods and intrinsic generation intervals.}
-
-\begin{figure}[!pht]
-\begin{center}
-\includegraphics[width=0.95\textwidth]{forward_corr.pdf}
-\caption{
-\textbf{Epidemiological dynamics and changes in mean forward and backward delay distributions.}
-(A) Daily incidence over time.
-(B--D) Changes in the mean forward incubation period, generation interval, and serial interval.
-(E--G) Changes in the mean backward incubation period, generation interval, and serial interval.
-Intrinsic incubation periods and intrinsic generation intervals are modeled using a correlated bivariate lognormal distribution; 
-therefore, generation intervals are drawn from the corresponding conditional distributions (given a incubation period), instead of the marginal distribution.
-Higher correlation reduces the amount of changes in the mean forward serial interval because shorter (longer) backward incubation periods of infectors during the increasing (decreasing) phase of an epidemic are associated with shorter (longer) forward generation intervals.
-See Figure 3 in the main text for a detailed description.
-}
-\end{center}
-\end{figure}
+We declare no competing interests.
 

### 2020-11-08 supp.tex
format & supp

\documentclass[12pt]{article}
\usepackage[top=1in,left=1in, right = 1in, footskip=1in]{geometry}

\usepackage{graphicx}
\usepackage{xspace}
%\usepackage{adjustbox}

\newcommand{\comment}{\showcomment}
%% \newcommand{\comment}{\nocomment}

\newcommand{\showcomment}[3]{\textcolor{#1}{\textbf{[#2: }\textsl{#3}\textbf{]}}}
\newcommand{\nocomment}[3]{}

\newcommand{\jd}[1]{\comment{cyan}{JD}{#1}}
\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
\newcommand{\bmb}[1]{\comment{blue}{BMB}{#1}}
\newcommand{\djde}[1]{\comment{red}{DJDE}{#1}}

\newcommand{\eref}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\fref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Fref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\sref}[1]{Sec.~\ref{#1}}
\newcommand{\frange}[2]{Fig.~\ref{fig:#1}--\ref{fig:#2}}
\newcommand{\tref}[1]{Table~\ref{tab:#1}}
\newcommand{\tlab}[1]{\label{tab:#1}}
\newcommand{\seminar}{SE\mbox{$^m$}I\mbox{$^n$}R}

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc} % make sure fancy dashes etc. don't get dropped

\usepackage{lineno}

\usepackage[pdfencoding=auto, psdextra]{hyperref}

\usepackage{natbib}
\bibliographystyle{chicago}
\date{\today}

\usepackage{xspace}
\newcommand*{\ie}{i.e.\@\xspace}

\usepackage{color}

\newcommand{\Rx}[1]{\ensuremath{{\mathcal R}_{#1}}\xspace} 
\newcommand{\Ro}{\Rx{0}}
\newcommand{\Rc}{\Rx{\mathrm{c}}}
\newcommand{\Rs}{\Rx{\mathrm{s}}}
\newcommand{\RR}{\ensuremath{{\mathcal R}}\xspace}
\newcommand{\Rhat}{\ensuremath{{\hat\RR}}}
\newcommand{\Rintrinsic}{\ensuremath{{\mathcal R}_{\textrm{\tiny intrinsic}}}\xspace}
\newcommand{\tsub}[2]{#1_{{\textrm{\tiny #2}}}}
\newcommand{\dd}[1]{\ensuremath{\, \mathrm{d}#1}}
\newcommand{\dtau}{\dd{\tau}}
\newcommand{\dx}{\dd{x}}
\newcommand{\dsigma}{\dd{\sigma}}

\newcommand{\psymp}{\ensuremath{p}} %% primary symptom time
\newcommand{\ssymp}{\ensuremath{s}} %% secondary symptom time
\newcommand{\pinf}{\ensuremath{\alpha_1}} %% primary infection time
\newcommand{\sinf}{\ensuremath{\alpha_2}} %% secondary infection time

\newcommand{\psize}{{\mathcal P}} %% primary cohort size
\newcommand{\ssize}{{\mathcal S}} %% secondary cohort size

\newcommand{\gtime}{\tau_{\rm g}} %% generation interval
\newcommand{\gdist}{g} %% generation-interval distribution
\newcommand{\idist}{\ell} %% incubation period distribution

\newcommand{\total}{{\mathcal T}} %% total number of serial intervals

\usepackage{lettrine}

\newcommand{\dropcapfont}{\fontfamily{lmss}\bfseries\fontsize{26pt}{28pt}\selectfont}
\newcommand{\dropcap}[1]{\lettrine[lines=2,lraise=0.05,findent=0.1em, nindent=0em]{{\dropcapfont{#1}}}{}}

\renewcommand{\thesection}{S\arabic{section}}

\begin{document}

\begin{flushleft}{
	\Large
	\textbf\newline{Supporting Information}\\
	\textbf\newline{
		Forward-looking serial intervals correctly link epidemic growth to reproduction numbers
	}
}
\newline
\\
Sang Woo Park\textsuperscript{1,*}
Kaiyuan Sun\textsuperscript{2}
David Champredon\textsuperscript{3}
Michael Li\textsuperscript{4}
Benjamin M.\ Bolker\textsuperscript{4,5,6}
David J.\,D.\ Earn\textsuperscript{5,6}
Joshua S.\ Weitz\textsuperscript{7, 8}
Bryan T.\ Grenfell\textsuperscript{1,2,9}
Jonathan Dushoff\textsuperscript{4,5,6}
\\
\bigskip
\textbf{1} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, NJ, USA
\\
\textbf{2} Fogarty International Center, National Institutes of Health, Bethesda, MD, USA
\\
\textbf{3} Department of Pathology and Laboratory Medicine, University of Western Ontario, London, Ontario, Canada
\\
\textbf{4} Department of Biology, McMaster University, Hamilton, ON, Canada
\\
\textbf{5} Department of Mathematics and Statistics, McMaster University, Hamilton, ON, Canada
\\
\textbf{6} M.\,G.\,DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, ON, Canada
\\
\textbf{7} School of Biological Sciences, Georgia Institute of Technology, Atlanta, GA, USA
\\
\textbf{8} School of Physics, Georgia Institute of Technology, Atlanta, GA, USA
\\
\textbf{9} Woodrow Wilson School of Public and International Affairs, Princeton University, Princeton, NJ, USA
\\
\bigskip

*Corresponding author: swp2@princeton.edu
\bigskip

Disclaimer: The findings and conclusions in this report are those of the authors and do not necessarily represent the official position of the U.S. National Institutes of Health or Department of Health and Human Services.
\end{flushleft}

\pagebreak

\section{Deterministic simulation}

We simulate the renewal equation model using a discrete-time approximation:
\begin{align}
i(t) &= \Ro S(t-\Delta t) \sum_{m=1}^{\tsub{m}{max}} i(t-m \Delta t) \hat{\gdist}(m \Delta t) \nonumber \\
S(t) &= S(t-\Delta t) - i(t)
\end{align}
where $\hat{\gdist}$ is a discrete-time intrinsic generation-interval distribution that satisfies the following:
\begin{equation}
\hat{\gdist}(m \Delta t) = \frac{\gdist(m \Delta t)}{\sum_{i=1}^\ell \gdist(m \Delta t)}, \quad m=1, \dots, \tsub{m}{max}.
\end{equation}
The continuous-time intrinsic generation-interval distribution is parameterized using a log-normal distribution (Table 1). We define the intrinsic incubation period distribution in a similar manner:
\begin{equation}
\hat{\idist}(m \Delta t) = \frac{\idist(m \Delta t)}{\sum_{i=1}^\ell \idist(m \Delta t)}, \quad m=1, \dots, \tsub{m}{max},
\end{equation}
where its continuous-time analog is also based on a log-normal distribution.
For simplicity, we assume that the forward incubation periods and intrinsic generation intervals are independent:
\begin{equation}
\hat{h}(m \Delta t, n \Delta t) = \hat{\idist}(m \Delta t)\hat{\gdist}(n \Delta t), \quad m,n=1, \dots, \tsub{m}{max}.
\end{equation}
We use $\Delta t = 0.025\,\textrm{days}$ and $\tsub{m}{max}=2001$ for discretization steps.

We initialize the simulation with population size $N$=40,000 as follows:
\begin{align}
i(m \Delta t) &= C \exp(r m \Delta t), \quad m=1, \dots, \tsub{m}{max}\nonumber \\
S(m \Delta t) &= N - \sum_{n=1}^m i(n \Delta t), \quad m=1, \dots, \tsub{m}{max}
\end{align}
where $C$ is chosen such that $\sum_{n=1}^{\tsub{m}{max}} i(m \Delta t)=10$.
These initial conditions allow the model to follow exponential growth from time $\Delta t (\tsub{m}{max} + 1)$ without any transient behaviors.

\pagebreak

\section{Stochastic simulation}

We run stochastic simulations of the renewal equation model using an individual-based model on a fully connected network (i.e., homogeneous population) based on the Gillespie algorithm that we developed earlier \citep{park2020inferring}.
First, we initialize an epidemic with $I(0)$ infected individuals (nodes) in a fully connected network of size $N$. 
For each initially infected individual, we draw number of infectious contacts from a Poisson distribution with the mean of \Ro and the corresponding generation intervals for each contact from a log-normal distribution (Table 1).
Contactees are uniformly sampled from the total population.
All contactees are sorted into event queues based on their infection time.
We update the current time to the infection time of the first person in the queue.
Then, the first person in the queue makes contacts based on the Poisson offspring distribution described earlier and their contactees are added to the sorted queue.
Whenever contactees are added to the sorted queue, we remove all duplicated contacts (but keep the first one) as well as contacts made to individuals that have already been infected.
Simulations continue until there are no more individuals in the queue.
We simulate 10 epidemics with $I(0)=10$ and $N$=40,000.

\pagebreak

\section{Linking $r$ and \Ro using serial-interval distributions}

The intrinsic generation-interval distribution $\gdist(\tau)$ provides a link between $r$ and \Ro via the Euler-Lotka equation \citep{wallinga2007generation}:
\begin{equation}
\frac{1}{\Ro} = \int_0^\infty \exp(-r\tau) \gdist(\tau) \dtau\,.
\end{equation}
In this section, we prove that the initial forward serial-interval distribution $f_0(\tau)$ also estimates the same \Ro from $r$, except that integral extends to $\tau=-\infty$ rather than beginning at $\tau=0$, because serial intervals can be negative:
\begin{equation}
\frac{1}{\Ro} = \int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \dtau\,.
\label{eq:ptarget}
\end{equation}
Here, the initial forward serial-interval distribution $f_{0}(\tau)$ is defined as:
\begin{equation}
f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{0} \int_{\alpha_1}^{\tau} \exp(r \alpha_1) h(-\alpha_1, \alpha_2 - \alpha_1) \idist(\tau - \alpha_2) \, \mathrm{d}\alpha_2\,\mathrm{d}\alpha_1\,,
\label{eq:fdist}
\end{equation}
where $h$ is the joint probability distribution describing the
intrinsic generation-interval distribution $g$ and the intrinsic
incubation period distribution $\idist$ (see \eref{marginal} in the
main text), and the normalization constant $\phi$ is determined by the
requirement that $\int_{-\infty}^\infty f_{0}(\tau)\,\dtau=1$.

In order to verify \eref{ptarget}, we first rewrite the integral in \eref{fdist} by substituting $-\alpha_1$ for $\alpha_1$, and then changing the order of integration:
\begin{align}
f_{0}(\tau) &= \frac{1}{\phi} \int_0^\infty \int_{-\pinf}^{\tau} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \idist(\tau - \sinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf\,,\nonumber \\
&= \frac{1}{\phi} \int_{-\infty}^{\tau} \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\idist(\tau - \sinf)\,\mathrm{d}\pinf\, \mathrm{d}\sinf\,.
\label{eq:newforward}
\end{align}
To further simplify the expression, we define $z(\sinf)$ as follows:
\begin{equation}
z(\sinf) = \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf) \,\mathrm{d}\pinf\,.
\end{equation}
Substituting $z(\sinf)$ into \eref{newforward} we obtain:
\begin{equation}
f_{0}(\tau) = \frac{1}{\phi} \int_{-\infty}^{\tau} z(\sinf) \idist(\tau - \sinf) \,\mathrm{d}\sinf\,,.
\end{equation}
Writing $\hat{z}$ for a normalized version of $z$,
\begin{equation}\hat{z}(\sinf) = \frac{z(\sinf)}{\int_{-\infty}^\infty z(x) \dx}\,,\end{equation}
we can now express the initial forward serial-interval distribution
$f_0$ as a convolution of $\hat{z}$ and $\idist$:
\begin{equation}
f_{0}(\tau) = \frac{1}{\hat{\phi}} \int_{-\infty}^{\tau} \hat{z}(\sinf) \idist(\tau - \sinf)\, \mathrm{d}\sinf\,,
\end{equation}
where $\hat{\phi} = \phi/\int_{-\infty}^\infty z(x) \dx$.

Since the right hand side of \eref{ptarget} is also a
Laplace transform of $f_0=\hat{z}*\idist$, we can express it as the product
of Laplace transforms of $\hat{z}$ and $\idist$:
\begin{equation}
\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau) \mathrm{d} \tau = \int_{-\infty}^\infty \exp(-r\tau) \hat{z}(\tau)\, \mathrm{d} \tau \int_{0}^\infty \exp(-r\tau) \idist(\tau) \dtau\,.
\label{eq:newtarget}
\end{equation}
In order to derive an expression for a Laplace transform of $\hat{z}$, we have to first derive an analytical expression for $\int_{-\infty}^\infty z(x) \dx$. By changing the order of integration, we have:
\begin{align}
\int_{-\infty}^\infty z(\sinf) \mathrm{d}\sinf &= \int_{-\infty}^\infty \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf \,\mathrm{d}\sinf\nonumber\,,\\
&= \int_{0}^\infty \int_{-\pinf}^\infty \exp(- r \pinf) h(\pinf, \sinf+\pinf)\, \mathrm{d}\sinf\,\mathrm{d} \pinf\,.
\end{align}
Since $\idist$ is a marginal probability distribution of $h$, it follows that:
\begin{equation}
\int_{-\infty}^\infty z(\sinf) \mathrm{d}\sinf = \int_{0}^\infty \exp(- r \pinf) \idist(\pinf)\, \mathrm{d}\pinf\,.
\end{equation}
Then, we have:
\begin{equation}
\hat{z}(\sinf) = \frac{\int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf}{\int_{0}^\infty \exp(- r \pinf) \idist(\pinf)\, \mathrm{d}\pinf}\,.
\end{equation}
Substituting the expression into \eref{newtarget}, we have:
\begin{equation}
\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau = \int_{-\infty}^\infty \exp(-r\sinf) \int_{\max{(0,-\sinf)}}^{\infty} \exp(-r\pinf) h(\pinf, \sinf + \pinf)\, \mathrm{d}\pinf\,\mathrm{d}\sinf\,.
\label{eq:newtarget2}
\end{equation}

Recall that $g$ is also a marginal probability distribution of $h$:
\begin{equation}
g(\tau) = \int_0^\infty h(x, \tau) \,\mathrm{d}x\,.
\end{equation}
We can then substitute $\tau = \pinf + \sinf$ into \eref{newtarget2} and apply change of variables to obtain:
\begin{align}
&\int_{-\infty}^\infty \exp(-r\tau) f_{0}(\tau)\dtau\\
&=\int_{-\infty}^{\infty} \exp(-r\sinf) \int_{\max(0, -\sinf)}^\infty \exp(- r \pinf) h(\pinf, \sinf+\pinf) \,\mathrm{d} \pinf \,\mathrm{d}\sinf \\
&=\int_{0}^{\infty} \int_{0}^\infty \exp(- r \tau) h(\pinf, \tau)\, \mathrm{d} \pinf\, \mathrm{d}\tau\\
&=\int_{0}^{\infty} \exp(-r\tau) g(\tau) \dtau =\frac{1}{\Ro}
\end{align}
Therefore, the initial forward serial-interval distribution and the intrinsic generation-interval distribution give the same estimates of \Ro from $r$.\qed

\pagebreak

\section{Comparing the estimates of \Ro using the initial forward and the intrinsic serial-interval distributions}

We use a simulation-based approach to compare the estimates of \Ro based on the serial- and generation-interval distributions. 
To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and log-scale correlation $\rho$;
the multivariate log-normal distribution is parameterized based on parameter estimates for COVID-19 (Table 1).
We construct forward serial intervals during the exponential growth period as follows:
\begin{equation}
F_i = -X_{1,i} + (G_i|X_{1,i}) + X_{2,i},
\end{equation}
where the backward incubation period $X_{1,i}$ of an infector is simulated by drawing random log-normal samples $Y_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $Y_i$, each weighted by the inverse of the exponential growth function $\exp(-rY_i)$;
the intrinsic generation interval conditional on the incubation period of the infector $(G_i|X_{1,i})$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(X_{1,i}) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
the forward incubation period $X_{2,i}$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
We then calculate the basic reproduction number \Ro using the empirical estimator:
\begin{equation}
\Ro = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r F_i)}.
\end{equation}
We compare this with an estimate of \Ro based on the intrinsic serial-interval distribution which has the same mean as the intrinsic generation-interval distribution \citep{svensson2007note,klinkenberg2011correlation,champredon2018equivalence, britton2019estimation}:
\begin{equation}
  \Rintrinsic = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r Q_i)},
\end{equation}
where
\begin{equation}
Q_i = -Y_i + (G_i|Y_i) + X_{2,i}.
\end{equation}

\pagebreak

\section{Applications: SEIR model}

Consider a Susceptible-Exposed-Infectious-Recovered model:
\begin{align}
\frac{\mathrm{d}S}{\mathrm{d}t} &= - \beta S I \nonumber \\
\frac{\mathrm{d}E}{\mathrm{d}t} &= \beta S I - \gamma_E E\nonumber\\
\frac{\mathrm{d}I}{\mathrm{d}t} &= \gamma_E E - \gamma_I I\nonumber \\
\frac{\mathrm{d}R}{\mathrm{d}t} &= \gamma_I I
\end{align}
where $\beta$ is the transmission rate, $1/\gamma_E$ is the mean latent period, and $1/\gamma_I$ is the mean infectious period.
We further assume that the latent period is equivalent to incubation period; in other words, infected individuals can only transmit after symptom onset.
Then, the generation interval will be always longer than the incubation period.

The joint probability distribution of the intrinsic incubation periods and intrinsic generation intervals for this model can be written as:
\begin{equation}
h(x, \tau) = \begin{cases}
0 & x > \tau\\
\gamma_I \gamma_E \exp(-\gamma_I (\tau-x)-\gamma_E x) & x \leq \tau
\end{cases}
\end{equation}
Then, the intrinsic generation-interval distribution is given by:
\begin{align}
g(\tau) &= \int_0^\tau h(x, \tau) \dx\nonumber \\
&= \frac{\gamma_I \gamma_E}{\gamma_E-\gamma_I} (\exp(-\gamma_I \tau) - \exp(-\gamma_E \tau))
\end{align}
On the other hand, the initial forward serial-interval distribution is given by:
\begin{align}
f_{0}(\tau) &\propto \int_{-\infty}^{0} \int_{0}^{\tau} \exp(r \pinf) h(-\pinf, \sinf - \pinf) \idist(\tau - \sinf) \, \mathrm{d}\sinf\,\mathrm{d}\pinf \nonumber \\
&\propto \int_{-\infty}^{0} \int_{0}^{\tau}\exp(r \pinf) \exp(-\gamma_I \sinf+ \gamma_E \pinf) \exp(-\gamma_E(\tau-\sinf)) \, \mathrm{d}\sinf\,\mathrm{d}\pinf \nonumber \\
&\propto  \exp(-\gamma_E \tau) \int_{-\infty}^{0} \int_{0}^{\tau} \exp((\gamma_E-\gamma_I) \sinf) \exp((r+ \gamma_E) \pinf)\, \mathrm{d}\sinf\,\mathrm{d}\pinf \nonumber \\
&\propto  (\exp(-\gamma_I \tau) - \exp(-\gamma_E \tau)) \int_{-\infty}^{0} \exp((r+ \gamma_E) \pinf)\,\mathrm{d}\pinf \nonumber \\
&\propto  \exp(-\gamma_I \tau) - \exp(-\gamma_E \tau)
\end{align}
Therefore, both the intrinsic generation intervals and the initial forward serial intervals are identically distributed and have the same mean.

\pagebreak

\renewcommand\thefigure{S\arabic{figure}}    
\setcounter{figure}{0}

\section{Simulations with correlated intrinsic incubation periods and intrinsic generation intervals.}

\begin{figure}[!pht]
\begin{center}
\includegraphics[width=0.8\textwidth]{forward_corr.pdf}
\caption{
\textbf{Epidemiological dynamics and changes in mean forward and backward delay distributions.}
(A) Daily incidence over time.
(B--D) Changes in the mean forward incubation period, generation interval, and serial interval.
(E--G) Changes in the mean backward incubation period, generation interval, and serial interval.
Intrinsic incubation periods and intrinsic generation intervals are modeled using a correlated bivariate lognormal distribution; 
therefore, generation intervals are drawn from the corresponding conditional distributions (given a incubation period), instead of the marginal distribution.
Higher correlation reduces the amount of changes in the mean forward serial interval because shorter (longer) backward incubation periods of infectors during the increasing (decreasing) phase of an epidemic are associated with shorter (longer) forward generation intervals.
See Figure 3 in the main text for a detailed description.
}
\end{center}
\end{figure}

\pagebreak

\bibliography{serial}

\end{document}

### 2020-12-07 supp.tex
fix supp

@@
 \usepackage{color}
+
+\renewcommand{\theequation}{S.\arabic{equation}}
 
@@
 intrinsic generation-interval distribution $g$ and the intrinsic
-incubation period distribution $\idist$ (see \eref{marginal} in the
+incubation period distribution $\idist$ (see Eq.~(15) in the
 main text), and the normalization constant $\phi$ is determined by the
